### 2017-01-14 data and analysis/analysis.Rmd
First

---
title: "WordRec Experiment"
author: "A. Fourtassi & M. Frank"
date: "January 13, 2017"
output:
  html_document:
    number_sections: yes
    toc: yes
---

Libraries.

```{r}
library(readr)
library(dplyr)
library(tidyr)
library(ggplot2)
library(langcog)
theme_set(theme_bw())
```

The following analysis is done using pilot data with 25 subjects.

We plan to collect data for 100 subjects

Data.

```{r}

#Skip the pre task trials 
#Filter subjects who had no technical problem
#Select subjects who got more than 50% correct answers on the pre task trials

d <- read_delim("data_pilot.txt", delim = " ") %>%
  filter(type == "Task", problem=="No", score>0.5)
```

Break out by conditions. 
```{r}
sounds <- d %>%
  filter(condition == "sound") %>%
  group_by(sound_dist) %>%
  multi_boot_standard(col = "answer")

concepts <- d %>%
  filter(condition == "concept") %>%
  group_by(concept_dist) %>%
  multi_boot_standard(col = "answer")

joint <- d %>%
  filter(condition == "joint") %>%
  group_by(concept_dist, sound_dist) %>%
  multi_boot_standard(col = "answer")

ggplot(joint, 
       aes(x = sound_dist, y = mean, col = factor(concept_dist))) + 
  geom_pointrange(aes(ymin = ci_lower, ymax = ci_upper), 
                  position = position_dodge(width = .1)) + 
  geom_line(lty = 2) + 
  geom_line(data = sounds, aes(col = 1), col = "black") + 
  geom_pointrange(data = sounds, aes(ymin = ci_lower, ymax = ci_upper, 
                                     col = 1), col = "black")+
  xlab("Auditory distance") +ylab("% different")+
  scale_colour_discrete(name="Visual Dist")+
theme(legend.title = element_text(size=8))

ggplot(joint, 
       aes(x = concept_dist, y = mean, col = factor(sound_dist))) + 
  geom_pointrange(aes(ymin = ci_lower, ymax = ci_upper), 
                  position = position_dodge(width = .1)) + 
  geom_line(lty = 2) + 
  geom_line(data = concepts, aes(col = 1), col = "black") + 
  geom_pointrange(data = concepts, aes(ymin = ci_lower, ymax = ci_upper, 
                                     col = 1), col = "black") + 
  scale_colour_solarized() +
  xlab("Visual distance") +ylab("% different")+
  scale_colour_discrete(name="Auditory Dist")+
theme(legend.title = element_text(size=8))

```

Fit the models.
```{r}

#Fit the uniomodal sound condition
sound_data <- d %>%
    filter(condition == "sound")

concept_data <- d %>%
    filter(condition == "concept")

joint_data <- d %>%
    filter(condition == "joint")

#Fit the uniomodal sound condition with a logistic regression
fit_sound <- glm(answer ~ sound_dist, data=sound_data, family = binomial())

##extract coefficient
s_coef <- coef(fit_sound)["sound_dist"]
s_inter <- coef(fit_sound)["(Intercept)"]

#prameters of the sound distribution
s_var=4/(s_coef)
s_sum=-1*s_inter/s_coef

#Fit the uniomodal visual conditon
fit_concept <- glm(answer ~ concept_dist, data=concept_data, family = binomial())

##extract coefficient
c_coef <- coef(fit_concept)["concept_dist"]
c_inter <- coef(fit_concept)["(Intercept)"]

#prameters of the sound distribution
v_var=4/(c_coef)
v_sum=-1*c_inter/c_coef

#Fit the bimodal conditon
fit_joint <- glm(answer ~ sound_dist+concept_dist, data=joint_data, family = binomial())

##extract coefficient
j_coef_a <- coef(fit_joint)["sound_dist"]
j_coef_v <- coef(fit_joint)["concept_dist"]
j_inter <- coef(fit_joint)["(Intercept)"]

#prameters of the sound distribution (approx: the average mean sum equal to 0+4/2=2)
j_var_a=4/(j_coef_a)
j_var_v=4/(j_coef_v)

```

Analysis of the unimodal cases.
```{r}

#Recogniton functions from the unimodal fit 
x <- seq(0, 4, 0.01)

y_sound <- predict(fit_sound, list(sound_dist = x), type="response")
y_concept <- predict(fit_concept, list(concept_dist = x), type="response")

uniS <- data.frame(xS=x,yS=y_sound)
uniV <- data.frame(xV=x,yV=y_concept)

#Recognition functions from the bimodal fit (marginal distributions)
Logistic_a = function (x, A = j_coef_a , B = 2*j_coef_a) {
    1 / (1 + exp(-1*(-B +A * x)))
}

Logistic_v = function (x, A = j_coef_v , B = 2*j_coef_v) {
    1 / (1 + exp(-1*(-B +A * x)))
}

#Plot all these functions in the same graph

##The auditory case
ggplot(sounds, 
       aes(x = sound_dist, y = mean)) + 
  geom_pointrange(aes(ymin = ci_lower, ymax = ci_upper), 
                  position = position_dodge(width = .1)) + 
  geom_line(data=uniS,aes(x=xS, y=yS))+
  xlab("Auditory distance") +ylab("% different")+
  scale_y_continuous(limits = c(0, 1))+
  stat_function(fun = Logistic_a, colour="red")

##The visual case
ggplot(concepts, 
       aes(x = concept_dist, y = mean)) + 
  geom_pointrange(aes(ymin = ci_lower, ymax = ci_upper), 
                  position = position_dodge(width = .1)) + 
  geom_line(data=uniV,aes(x=xV, y=yV))+
  xlab("Visual distance") +ylab("% different")+
  scale_y_continuous(limits = c(0, 1))+
  stat_function(fun = Logistic_v, colour="red")

```

The bimodal case
```{r}

# Bimodal recognition functions

##the bimodal fit 
model_fit <- function (x,y) {
   1/(1 + exp(-x*j_coef_a-y*j_coef_v+2*j_coef_a+2*j_coef_v))
}

##Values of the baseline
model_base <- function (x,y) {
   1/(1 + exp(-x*s_coef-y*c_coef+2*s_coef+2*c_coef))
}

# Add the fit the baeline to data

ms_all <- joint %>% 
  rename(joint = mean) %>%
  left_join(select(concepts, concept_dist, mean) %>% 
              rename(concepts = mean)) %>%
  left_join(select(sounds, sound_dist, mean) %>% 
              rename(sounds = mean)) %>%
  mutate(fit = model_fit(sound_dist, concept_dist)) %>%
  mutate(base = model_base(sound_dist, concept_dist)) %>%
  gather(model, pred, concepts, sounds, base, fit)

#Plot Heat map for the data
ggplot(data = ms_all, aes(x=sound_dist, y=concept_dist, fill=joint)) + 
  geom_tile()+scale_fill_continuous(limits=c(0, 1))+xlab("Auditory distance") +ylab("Visual distance")

#Plot Heatmap for the baseline
mybase <- ms_all %>%
  filter(model=="base")

ggplot(data = mybase, aes(x=sound_dist, y=concept_dist, fill=pred)) + 
  geom_tile()+scale_fill_continuous(limits=c(0, 1))+xlab("Auditory distance") +ylab("Visual distance")

myfilter <- ms_all %>%
  filter(model=="fit" | model=="base")

#Correlation models (baseline and fit) to bimodal data 
ggplot(myfilter, 
       aes(x = pred, y = joint, col = factor(concept_dist), 
           shape = factor(sound_dist))) +
 geom_pointrange(aes(ymin = ci_lower, ymax = ci_upper), 
                  position = position_dodge(width = .1)) + 
  geom_abline(slope = 1, lty = 2) +
  facet_grid(model~.)

```

The modality dominance
```{r}

#Modality dominance coeficent
a_fit=j_var_v/j_var_a
a_base=v_var/s_var
a_Vdom=2*a_base
a_Sdom=0.5*a_base

#Classification thresholds (prob=0.5) for:

##The basline (combination of the unimodal cases)
classif_base = function (x, A=a_base) {
    2*(A+1)-A*x
}

##Best bivariate fit 
classif_fit = function (x, A=a_fit) {
    2*(A+1)-A*x
}

##A baseline for visual domiance
classif_Vdom = function (x, A=a_Vdom) {
    2*(A+1)-A*x
}

##A baseline for auditory domiance
classif_Sdom = function (x, A=a_Sdom) {
    2*(A+1)-A*x
}

#Sample from the baseline bivariate distribution
Gaus_base <- data.frame(x=c(rnorm(1000,0,sqrt(s_var)),rnorm(1000,4,sqrt(s_var))),
          y=c(rnorm(1000,0,sqrt(v_var)),rnorm(1000,4,sqrt(v_var))))

#Plot samples from the bivariate distribution
ggplot(Gaus_base, aes(x,y)) +  stat_density2d(geom="contour",aes(alpha=..level..))+
  scale_alpha_continuous(limits=c(0,0.03),breaks=1e-6*seq(0,10,by=2))+
  stat_function(fun = classif_base, colour = "red") +xlab("Auditory") +ylab("Visual")+ scale_x_continuous(limits = c(-6, 10))+scale_y_continuous(limits = c(-6, 10))

#Sample from the best bivariate fit 
Gaus_fit <- data.frame(x=c(rnorm(1000,0,sqrt(j_var_a)),rnorm(1000,4,sqrt(j_var_a))),
          y=c(rnorm(1000,0,sqrt(j_var_v)),rnorm(1000,4,sqrt(j_var_v))))

#Plot samples from the best bivariate fit
ggplot(Gaus_fit, aes(x,y)) +  stat_density2d(geom="contour",aes(alpha=..level..))+
  scale_alpha_continuous(limits=c(0,0.03),breaks=1e-6*seq(0,10,by=2))+
  stat_function(fun = classif_fit, colour = "red") +xlab("Auditory") +ylab("Visual") + scale_x_continuous(limits = c(-6, 10))+scale_y_continuous(limits = c(-6, 10))

#Modality dominance?
ggplot(Gaus_fit, aes(x,y)) +
  stat_function(fun = classif_base, colour = "red", lty=2) +
  stat_function(fun = classif_Vdom, colour = "blue", lty=2 )+
  stat_function(fun = classif_Sdom, colour = "blue", lty=2)+
  stat_function(fun = classif_fit, colour = "black")+
  xlab("Auditory") +ylab("Visual") + scale_x_continuous(limits = c(-6, 10))+
  scale_y_continuous(limits = c(-6, 10))+theme(aspect.ratio = 1)

```

### 2017-01-14 experiment1.js

@@ -1,0 +1,878 @@
+//////////////////
+//Helper functions
+///////////////////
+
+// Shows slides. We're using jQuery here - the **$** is the jQuery selector function, which takes as input either a DOM element or a CSS selector string.
+function randomInteger(n) {
+	return Math.floor(Math.random()*n);
+}
+
+function randomElement(array) {
+  return array[randomInteger(array.length)];
+}
+
+function randomInt(min,max)
+{
+    return Math.floor(Math.random()*(max-min+1)+min);
+}
+
+function showSlide(id) {
+  // Hide all slides
+	$(".slide").hide();
+	// Show just the slide we want to show
+	$("#"+id).show();
+}
+
+//shuffle an array
+function shuffleArray(a) {
+
+    for (var i = a.length - 1; i > 0; i--) {
+        var j = Math.floor(Math.random() * (i + 1));
+        var temp = a[i];
+        a[i] = a[j];
+        a[j] = temp;
+    }
+    return a;
+}
+
+function randomElement(array) {
+  return array[randomInteger(array.length)];
+}
+
+//I should now work on the randomization
+var rando = randomInt(0,3);
+var first_word ='', second_word='', first_obj='', first_obj='';
+
+if (rando ==0) {
+//Dog-ABA, Cat-ADA    
+//Dog is the standard
+first_word="ABA";
+second_word="ADA";
+first_obj="Dog";
+second_obj="Cat";
+    
+var ConStim = ['dog1','dog2','dog3','dog4', 'dog5'];   
+var SounStim = ['aba01','aba03','aba05','aba07', 'aba09'];
+    
+var ConStim_preTask=['dog1','dog1', 'dog5','dog5'];
+var SounStim_preTask = ['aba01','aba01','aba09','aba09'];
+}
+
+if (rando ==1) {
+//Dog-ADA, Cat-ABA
+//Dog is the standard
+first_word="ADA";
+second_word="ABA";
+first_obj="Dog";
+second_obj="Cat";
+    
+var ConStim = ['dog1','dog2','dog3','dog4', 'dog5'];   
+var SounStim = ['aba09','aba07','aba05','aba03', 'aba01'];
+    
+var ConStim_preTask=['dog1','dog1', 'dog5','dog5'];
+var SounStim_preTask = ['aba09','aba09','aba01','aba01'];
+    
+}
+if (rando ==2) {
+//Dog-ADA, Cat-ABA
[…]

### 2017-01-14 mmturkey-0.6_server.js

@@ -1,0 +1,264 @@
+// Bundle in Crockford's JSON2.js
+var JSON;JSON||(JSON={});
+(function(){function k(a){return a<10?"0"+a:a}function o(a){p.lastIndex=0;return p.test(a)?'"'+a.replace(p,function(a){var c=r[a];return typeof c==="string"?c:"\\u"+("0000"+a.charCodeAt(0).toString(16)).slice(-4)})+'"':'"'+a+'"'}function l(a,j){var c,d,h,m,g=e,f,b=j[a];b&&typeof b==="object"&&typeof b.toJSON==="function"&&(b=b.toJSON(a));typeof i==="function"&&(b=i.call(j,a,b));switch(typeof b){case "string":return o(b);case "number":return isFinite(b)?String(b):"null";case "boolean":case "null":return String(b);case "object":if(!b)return"null";
+e+=n;f=[];if(Object.prototype.toString.apply(b)==="[object Array]"){m=b.length;for(c=0;c<m;c+=1)f[c]=l(c,b)||"null";h=f.length===0?"[]":e?"[\n"+e+f.join(",\n"+e)+"\n"+g+"]":"["+f.join(",")+"]";e=g;return h}if(i&&typeof i==="object"){m=i.length;for(c=0;c<m;c+=1)typeof i[c]==="string"&&(d=i[c],(h=l(d,b))&&f.push(o(d)+(e?": ":":")+h))}else for(d in b)Object.prototype.hasOwnProperty.call(b,d)&&(h=l(d,b))&&f.push(o(d)+(e?": ":":")+h);h=f.length===0?"{}":e?"{\n"+e+f.join(",\n"+e)+"\n"+g+"}":"{"+f.join(",")+
+"}";e=g;return h}}if(typeof Date.prototype.toJSON!=="function")Date.prototype.toJSON=function(){return isFinite(this.valueOf())?this.getUTCFullYear()+"-"+k(this.getUTCMonth()+1)+"-"+k(this.getUTCDate())+"T"+k(this.getUTCHours())+":"+k(this.getUTCMinutes())+":"+k(this.getUTCSeconds())+"Z":null},String.prototype.toJSON=Number.prototype.toJSON=Boolean.prototype.toJSON=function(){return this.valueOf()};var q=/[\u0000\u00ad\u0600-\u0604\u070f\u17b4\u17b5\u200c-\u200f\u2028-\u202f\u2060-\u206f\ufeff\ufff0-\uffff]/g,
[…]

### 2017-01-14 mmturkey.js

@@ -1,0 +1,263 @@
+// Bundle in Crockford's JSON2.js
+var JSON;JSON||(JSON={});
+(function(){function k(a){return a<10?"0"+a:a}function o(a){p.lastIndex=0;return p.test(a)?'"'+a.replace(p,function(a){var c=r[a];return typeof c==="string"?c:"\\u"+("0000"+a.charCodeAt(0).toString(16)).slice(-4)})+'"':'"'+a+'"'}function l(a,j){var c,d,h,m,g=e,f,b=j[a];b&&typeof b==="object"&&typeof b.toJSON==="function"&&(b=b.toJSON(a));typeof i==="function"&&(b=i.call(j,a,b));switch(typeof b){case "string":return o(b);case "number":return isFinite(b)?String(b):"null";case "boolean":case "null":return String(b);case "object":if(!b)return"null";
+e+=n;f=[];if(Object.prototype.toString.apply(b)==="[object Array]"){m=b.length;for(c=0;c<m;c+=1)f[c]=l(c,b)||"null";h=f.length===0?"[]":e?"[\n"+e+f.join(",\n"+e)+"\n"+g+"]":"["+f.join(",")+"]";e=g;return h}if(i&&typeof i==="object"){m=i.length;for(c=0;c<m;c+=1)typeof i[c]==="string"&&(d=i[c],(h=l(d,b))&&f.push(o(d)+(e?": ":":")+h))}else for(d in b)Object.prototype.hasOwnProperty.call(b,d)&&(h=l(d,b))&&f.push(o(d)+(e?": ":":")+h);h=f.length===0?"{}":e?"{\n"+e+f.join(",\n"+e)+"\n"+g+"}":"{"+f.join(",")+
+"}";e=g;return h}}if(typeof Date.prototype.toJSON!=="function")Date.prototype.toJSON=function(){return isFinite(this.valueOf())?this.getUTCFullYear()+"-"+k(this.getUTCMonth()+1)+"-"+k(this.getUTCDate())+"T"+k(this.getUTCHours())+":"+k(this.getUTCMinutes())+":"+k(this.getUTCSeconds())+"Z":null},String.prototype.toJSON=Number.prototype.toJSON=Boolean.prototype.toJSON=function(){return this.valueOf()};var q=/[\u0000\u00ad\u0600-\u0604\u070f\u17b4\u17b5\u200c-\u200f\u2028-\u202f\u2060-\u206f\ufeff\ufff0-\uffff]/g,
[…]

### 2017-01-29 write-up/main.tex
write-up

% 
% Annual Cognitive Science Conference
% Sample LaTeX Paper -- Proceedings Format
%

% Original : Ashwin Ram (ashwin@cc.gatech.edu)       04/01/1994
% Modified : Johanna Moore (jmoore@cs.pitt.edu)      03/17/1995
% Modified : David Noelle (noelle@ucsd.edu)          03/15/1996
% Modified : Pat Langley (langley@cs.stanford.edu)   01/26/1997
% Latex2e corrections by Ramin Charles Nakisa        01/28/1997 
% Modified : Tina Eliassi-Rad (eliassi@cs.wisc.edu)  01/31/1998
% Modified : Trisha Yannuzzi (trisha@ircs.upenn.edu) 12/28/1999 (in process)
% Modified : Mary Ellen Foster (M.E.Foster@ed.ac.uk) 12/11/2000
% Modified : Ken Forbus                              01/23/2004
% Modified : Eli M. Silk (esilk@pitt.edu)            05/24/2005
% Modified : Niels Taatgen (taatgen@cmu.edu)         10/24/2006
% Modified : David Noelle (dnoelle@ucmerced.edu)     11/19/2014

%% Change "letterpaper" in the following line to "a4paper" if you must.

%%% MAX = 6 Pages (including references)

\documentclass[10pt,letterpaper]{article}

\usepackage{cogsci}
\usepackage{pslatex}
\usepackage{graphicx}
\usepackage{apacite}
\usepackage{color}

\title{Word identification under multimodal Uncertainty}

\author{{\large \bf Abdellah Fourtassi} \\ afourtas@stanford.edu \\
  Department of Psychology\\ Stanford University\\
  \And {\large \bf Michael C. Frank}\\ mcfrank@stanford.edu \\
  Department of Psychology\\ Stanford University}

\begin{document}

\maketitle

\begin{abstract}

Language requires the ability to process arbitrary multimodal input. It also requires the ability to infer categories under uncertainty. In this paper, we introduce a task that allows us to examine how adults identify word categories under uncertainty from the auditory and the visual modality. We propose a Bayesian model of the task which provides an optimal baseline. The predictions are tested in two experiments where category recognition is made under two kinds of uncertainty: ambiguity and noise. In both cases, human data shows many patterns of optimal behaviour, and the baseline explains most of the variance. However, when one modality is noisy, we found evidence for a systematic preference for the non-noisy modality.

\textbf{Keywords:} 
Language; audio-visual processing; word learning; speech perception; computational modeling. 
\end{abstract}

Language uses symbols expressed in one modality (e.g., the auditory modality in the case of speech) to communicate about things in the world, which we perceive through  various sensory modalities (e.g., the visual modality in the case of concrete objects). Therefore, understanding language requires the ability to process arbitrary multisensory input. This processing, however, is only a first step. When a speaker utters a word and points to an object, it is not enough for the observer to be able to encode these precise sound and object tokens. They should, on top of that, be able to identify the underlying categories (such as the phonemes, the concept, and the word category). This challenge is quite obvious when a person has to learn these categories (e.g., a baby who starts learning language). But a challenge is present even when the person already knows the categories, but has to recognize them. This is because individual tokens are often ambiguous or/and noisy\cite<e.g.,>{hillenbrand1995}. They do not indicate with absolute certainty their category membership, they do so only in probabilistic terms. For example, the speaker may make a mispronunciation, or their utterance may get distorted because of ambient noise. Similarly, the identity of the object that is being referred to may be uncertain when there exist other surrounding and/or similar looking objects, or when the observer's view is partially obstructed.

It follows that, in order to identify the speaker's intended categories, an observer has to be able to reason under a great deal of uncertainty. To characterize this ability, it has been suggested that people encode tokens with their probability distributions, base their decisions on these probabilities, and adjust their behavior when these probabilities change \cite<e.g.,>{clayard08}. However, previous work in this line of research has largely focused on the unimodal case, that is, when categories can be defined along one modality, such as the phonemes \cite<e.g.,>{feldman2009}. A few studies did explore some aspects of cross-modal processing in this framework \cite<e.g.,>{bejjanki2011, kleinschmidt2015}, but focused on the specific case of phoneme recognition from speech and lip movement, wherein people assume information from both modalities to be tightly correlated.

In the present work, we study the case of word category recognition, where a word is an \textit{arbitrary} mapping between a sound category and a visual category. We test people on their ability to encode audio-visual tokens and use them to recognize the underlying word category. Crucially, this recognition is made under uncertainty from both the auditory category (the phoneme) and the visual category (the concept being referred to). Our goal is to explore how adults deal with such multimodal ambiguity in a categorical task. To this end, we propose a model that combines uncertainty in an optimal way, and we use it as a baseline for human data. More precisely, we examine the extent to which human data conform to, or deviate from the baseline, and whether the deviation involves a systematic preference for a particular modality?

The paper is organized as follows. First, we introduce our audio-visual word recognition task. Second, we present the model and explain how it generate an optimal baseline. Then we present the behavioral experiments where we test category recognition under audio-visual uncertainty. In experiment 1, audio-visual tokens are clear but their category membership is ambiguous.  In experiment 2, input to one modality is ambiguous, and input to the other is ambiguous as well as noisy. We analyse and discuss the results of the experiments in the light of the model's predictions.

\section{The audio-visual word recognition task}

We introduce a new task that tests audio-visual category recognition. We use two visual categories (cat and dog) and two auditory categories (/b/ and /d/ embedded in the minimal pair /aba/-/ada/). For each participant, an arbitrary pairing is set between the auditory and the visual categories, leading to two audio-visual word categories (e.g., dog-/aba/, cat-/ada/).

In each trial, participants are presented with an audio-visual target (the prototype of the target category), immediately followed by an audio-visual test. 
The test may differ from the target in both the auditory and the visual components. The auditory component is sampled from a continuum along the second formant (F2) linking the words /aba/ and /ada/. The visual component is sampled from a morph that links the prototypical pictures of the dog and the cat.  After these two presentations, participants are instructed to press `same' or `different'.

This task is similar to the task introduced by \citeA{sloutsky2003} and used in subsequent research to probe audio-visual encoding. However, unlike this previous line of research, here participants are not asked whether the two audio-visual presentations are identical, instead, they are asked to press `same' if they think the second item (the test) belonged to the same word category as the prototype (e.g.,  dog-/aba/), even if there is a slight sound mispronunciation,  a slight difference in the object’s shape, or a slight difference in both the pronunciation and the shape. They are instructed to press `different' if they think that the test was, rather, an audio-visual instance to the other word category (cat-/ada/).

As shown in figure \ref{fig:task}, besides the audio-visual trials where both the sounds and the pictures are presented, there are also unimodal trials where the pictures are hidden (auditory-only) or where the sounds are muted (visual-only). These unimodal trials are crucial since they provide us with the probability distributions of the auditory and visual categories over their tokens. In fact, the goal is to examine whether participants' responses on the bimodal trial are optimal combination of the probabilities derived from their responses on the unimodal trials.

Next, we explain how we modeled this task in a Bayesian framework.

\begin{figure}[tp]
\centering
\includegraphics[width=0.4\textwidth]{task1.png}
\caption{Overview of the task}
\label{fig:task}
\end{figure}

\section{What would an ideal recognizer do?}

The unimodal conditions (auditory-only or visual-only)  are used to characterize the probability distributions of the auditory and the visual categories.  We assume, for the sake of simplicity, that the probability distributions are normally distributed:

$$ a | A \sim  N(\mu_A, \sigma^2_A) $$
$$ v | V \sim  N(\mu_V, \sigma^2_V) $$

In each modality, we have two categories: /ada/ ($A=1$) and /aba/ ($A=2$) in the auditory dimension, and \textit{cat} ($V=1$) and \textit{dog} ($V=2$) in the visual dimension (the identity of the categories was randomized in the experimental setup).

In the bimodal condition, participants see word tokens made of audio-visual input, and have to make a categorical decision. We represent word tokens as vectors in the audio-visual space $\mathbf{w}=(a,v)$.
A word category $W$ is defined as the joint distribution of the auditory and visual categories. It can be characterized with a bivariate normal distribution in the audio-visual space:
$$ \mathbf{w} | W \sim  N(M_W, \Sigma_W) $$
\begin{figure}[tp]
\centering
\includegraphics[width=0.4\textwidth]{MyTask.png}
\caption{Model of the task: a word category is defined as the joint bivariate distribution of an auditory category (bottom) and a visual semantic category (left). Upon the presentation of a word token $w$, participants guess whether it is sampled from the word category $W1$ or from $W2$. Decision threshold is where the guess probability is 0.5. (Plotted distributions are for illustration only)}
\label{fig:space}
\end{figure}
We have two word categories: dog-/aba/ ($W=1$) and cat-/ada/ ($W=2$). Participants can be understood as choosing one of these two word categories (figure \ref{fig:space}). For an ideal ``recognizer'', the probability of choosing category 2 when presented with an audio-visual instance $\mathbf{w}=(a,v)$ is the posterior probability of this category:
\begin{equation}
\small
p(W=2 | \mathbf{w})=\frac{p(\mathbf{w}|W=2)p(W=2)}{p(\mathbf{w}|W=2)p(W=2)+p(\mathbf{w}|W=1)p(W=1)}
\end{equation}
We make the assumption that, given a particular word category, the auditory and visual tokens are independently generated:
\begin{equation}
p(\mathbf{w} | W) = p(a,v| W) = p(a| W)p(v| W)
\end{equation}

Under this assumption, the posterior probability reduces to:
\begin{equation}
p(W=2 | \mathbf{w})=\frac{1}{1+(1+\epsilon)\exp(\beta_0+\beta_aa+\beta_vv)}
\label{eq:pred}
\end{equation}

with $\beta_a=\frac{\mu_{A1}-\mu_{A2}}{\sigma^2_{A}}$, 
$\beta_v=\frac{\mu_{V1}-\mu_{V2}}{\sigma^2_{V}}$,
$\beta_0=\frac{\mu^2_{A2}-\mu^2_{A1}}{2\sigma^2_{A}}+\frac{\mu^2_{V2}-\mu^2_{V1}}{2\sigma^2_{V}}$

and $1+\epsilon=\frac{p(W=1)}{p(W=2)}$ is the proportion of the prior probabilities. If the identity of word categories is randomized, and if $W1$ is the target, then $\epsilon$ measures a response bias to `same' if $\epsilon > 0 $, and a response bias to `different' if $\epsilon < 0 $.

In sum, the posterior \ref{eq:pred} provides a baseline for how probabilities that characterize uncertainty in each modality can be combined to make categorical decision about bimodal input.

Next, we present the behavioral experiments. Our goal is twofold: 1) examine the extent to which human responses correspond or deviate from the predictions of the optimal baseline. 2) if there is a deviation from the baseline, examine whether this deviation involves a systematic preference for a particular modality.

\section{experiments}

In experiment 1, we test the predictions of the model in the case where uncertainty is due to ambiguity in terms of category membership.

\subsection{experiment 1}

\subsubsection{Participants}
We planned to run 100 participants recruited from Amazon Mechanical Turk. Only participants with US IP addresses and a task approval rate above 85\% were allowed to participate. They were paid at an hourly rate of \$6/hour.  Data
were excluded if participants completed the task more than
once (2 participants). Moreover, as specified in the preregistration (\url{https://osf.io/h7mzp/}), participants were excluded if they had less than 50\% accurate responses on the unambiguous training trials (6), and if they reported having experienced a technical problem of any sort during the online experiment (14). The final sample consisted of 76 participants.

\subsubsection{Stimuli}
For the auditory stimuli, we used the continuum introduced in \citeA{vroomen2004}. It is a 9-point /aba/--/ada/ speech continuum which was created by varying the frequency of the second (F2) formant in equal steps. We selected 5 equally spaced points from the original continuum by keeping the end-points (prototypes) 1 and 9, as well as the three points: 3, 5, and 7 along the continuum.

For the visual stimuli, we used a morph continuum introduced in \citeA{freedman2001}. In the original stimuli, a continuous set of images was generated from three cat prototypes and
three dog prototypes. We selected a morph along the dog and cat prototypes that seemed most natural. Moreover, from the original 14 points, we selected 5 points as follows: we kept the item that seemed most ambiguous (point 8), the 2 preceding points (i.e., 7 and 6) and the 2 following points (i.e., 8 and 9). The 6 and 9 points along the morph were quite distinguishable, and we took them to be our prototypes (figure \ref{fig:morph}).

\begin{figure}[tp]
\centering
\includegraphics[width=0.4\textwidth]{morph.png}
\caption{Visual stimuli}
\label{fig:morph}
\end{figure}

\subsubsection{Design and Procedure}
We told participants that an alien was naming two objects: a dog, called /aba/ in the alien language, and a cat called /ada/. In each trial, we presented the first object (the target) on the left side of the screen simultaneously with the corresponding sound. The target was always the same (e.g., dog-/aba/). The second sound-object pair (the test) followed after half a second. It showed up on the right side of the screen and was supposed to be either another dog-/aba/, or a cat-/ada/. For both the target and the test, we displayed the object when the corresponding sound started playing, and we made it disappear when the sound stoped (for a total of around 800ms). For each participant, we randomized the sound-object mapping as well as the identity of the target. Finally, we instructed participants to press S (for same) if they thought the alien was naming another dog-/aba/, and D (for different) if they thought the alien was naming a cat-/ada/.

The first part of the experiment was a training to familiarize the participants with the task and the stimuli. In this training phase, we used only the prototype pictures and the prototype sounds, and each trial had a correct answer: the test item was either exactly the same as the target, or the prototype of the other word category. There were a total of 12 trials, half same, and half different. The second part was the real task. In this part, we told participants that, like in the training, the first sound-object pair would be the same. However, in the second pair, both the sound and the picture could be ambiguous. We told them that each trial was different. Finally, we encouraged participants to base their answers on both the sounds and the pictures in the bimodal condition. Each test item was made of a sound sampled from the /aba/-/ada/ continuum, and the picture form the dog-cat morph. There was a total of 25 possible combinations in the bimodal condition, and 5 in each of the unimodal conditions. Each participants answered twice to each possible trial in each condition for a total of 70 trials/participants. For each participant,  we randomized the order of conditions (auditory-only, visual-only, and bimodal). We designed the experiment to take between 10 to 15 minutes to complete.
\begin{figure}
\centering
\includegraphics[width=0.4\textwidth]{unimodal.png}
\caption{Average human responses in the auditory-only condition (left), and visual-only condition (right). Error bars are 95\% confidence intervals. Solid lines represent the unimodal fits. }
\label{fig:unimodal}
\end{figure}

\subsubsection{Results}

\begin{figure}[h]
\centering
\includegraphics[width=0.4\textwidth]{correlation.png}
\caption{Human responses vs. the baseline predictions. Error bars are 95\% confidence intervals. In experiment 1, the baseline and the fit explained 89\%, and 94\% of total variance, respectively. In experiment 2, the baseline and the fit explained 91\%, and 97\% of total variance, respectively}
\label{fig:corr}
\end{figure}

\begin{figure*}
\centering
\includegraphics[width=0.83\textwidth]{Exp.png}
\caption{Proportion of `different' as a function of the auditory distance. Solid lines represent average human responses (left), predictions of the baseline (middle), and the bimodal fit (left). Dotted lines represent average human responses in the unimodal conditions. Colors represent values in the visual continuum. }
\label{fig:Exp}
\end{figure*}

\textit{Unimodal conditions:} Let's take the auditory-only case as an example, participants can be understood as choosing one of two auditory categories. For an ideal recognizer, the probability of choosing category 2 (that is, to answer `different') when presented with an audio instance $a$ is the posterior probability of this category $p(A=2|a)$. If we assume that both categories have equal variances, the posterior probability reduces to:
\begin{equation}
p(A=2 | a)=\frac{1}{1+(1+\epsilon_A)\exp(\beta_{a0}+\beta_aa)}
\end{equation}
with $\beta_a=\frac{\mu_{A1}-\mu_{A2}}{\sigma^2_{A}}$ and  $\beta_{a0}=\frac{\mu^2_{A2}-\mu^2_{A1}}{2\sigma^2_{A}}$. $\epsilon_A$ is the response bias in the auditory-only trials.

For this model (as well all other models), we fixed the values of the means to be the end-points of the corresponding continuum: $\mu_{A1}=0$ and $\mu_{A2}=4$ (and similarly $\mu_{V1}=0$, and $\mu_{V2}=4$). To determine the values of the bias and the variance, we fitted a model for each modality, collapsed across participants. For the auditory modality, we got $\epsilon_A=-0.20$ and $\sigma^2_A=2.04$. For the visual modality, we got $\epsilon_V=-0.11$ and $\sigma^2_V=3.34$.  In figure \ref{fig:unimodal} (top) we plotted responses in the unimodal conditions as well as the unimodal fits.

\textit{Bimodal condition:} we fitted a model to human responses in the bimodal condition, collapsed across participants. We got $\epsilon=-0.32$, $\sigma^2_{Ab}=5.00$ and $\sigma^2_{Vb}=7.27$.

\textit{Baseline model:} we derived the predictions of the baseline model by using the values of the variances derived from the unimodal conditions, and the response bias derived from the bimodal condition, and by plugging these values into the expression of the posterior \ref{eq:pred}.

In figure \ref{fig:Exp} (top) we plotted the participants' responses in the bimodal condition (left), as well as the prediction of the baseline (middle) and the bimodal fit (right). Correlation of human data vs. the bimodal baseline and fit are shown in figure \ref{fig:corr} (top).

\subsubsection{Discussion}
Compare human responses (figure \ref{fig:Exp}, top left) to the baseline (figure \ref{fig:Exp}, top middle). Qualitatively speaking, the participants showed many patterns of optimal behaviour (as defined by the baseline). Let's, for instance, explore how behaviour changed when participants moved from the auditory-only case (dotted black line) to the bimodal case (solid colored lines).  We see that, similar to the baseline, higher certainty in the visual modality either towards `different' (points 3 and 4 in the visual continuum), or towards `same' (points 1 and 0), generally drove responses accordingly, i.e., either towards more 'different' (as the curves moved up, compared to the auditory-only curve), or towards more `same' responses (as the curves moved down). Moreover, the amount of change was generally a function of the strength of evidence brought by the visual modality, with, for example, responses on visual point 4 being generally `higher' than responses on visual point 3. Similarly, responses on visual 0 were generally `lower' than responses on visual 1. Similar things can be said about the pattern of change from the visual-only (dotted colored horizontal lines) to the bimodal case: at each point along the auditory scale, we see that a point of a given color was generally below its corresponding horizontal line (i.e., same color) when the evidence brought by the auditory modality pointed more toward `same' (point 0 and 1), and was above its corresponding line when evidence pointed more toward `different' (point 3 and 4 along the auditory scale). These qualitative patterns were quite similar to the baseline model. Indeed, we found that the latter explained almost 90\% of the variance  ($r^2=0.89$).

Though we see a qualitative resemblance between human data and the baseline, there were quantitative differences: predictions of the baseline were either a bit too high, or a bit too low. We can see this phenomenon clearly in the shape of the correlation graph (figure \ref{fig:corr}, top left). It is as though participants were less certain about responses than expected. Formally speaking, this translated as an increase in the value of the variance associated with each modality (compare the variance values in the baseline model to the values derived from the bimodal fit).  Since the variance characterizes the reliability of a given cue, it seems as if the bimodal presentation caused reliance on both modalities to decrease.  This effect can possibly be attributed to the arbitrary nature of the form-meaning mapping. In fact, previous studies suggest that while redundant mapping improves performance (e.g., determining the frequency of a bouncing ball from visual and auditory cues), arbitrary mappings generally tends to hinder performance (see \citeA{robinson2010} for a review).

\textit{Modality preference?} we would like to know if part of the observed discrepancy between the baseline and human responses involved a systematic preference (albeit small) for a particular modality when making decisions in the bimodal condition. This preference, if real, should manifest as a deviation from the decision threshold predicted by the baseline model. The decision threshold is defined as the set of values in the audio-visual space along which the posterior (expression \ref{eq:pred}) is equal to 0.5. As illustrated in \ref{fig:space}, above this line participants are more likely to choose one word category, and below this line, they are more likely to choose the other word category. 
The decision threshold takes the following form:
\begin{equation}
v=-\frac{\sigma^2_V}{\sigma^2_A}a+v_0
\label{eq:threshold}
\end{equation}
If the slope derived from the fit is bigger than the slope of the baseline, this would suggest a general preference for the auditory modality, and a smaller slope would suggest a general preference for the visual modality. The limit cases are when there is exclusive reliance on the auditory cue (a vertical line), and where there is exclusive reliance on the visual (a horizontal line). In figure \ref{fig:pref} (top left) we plotted some decision thresholds in the audio-visual space when the intercept was kept constant. The fit to human data  (solid black line) was very close to the baseline threshold (red line). Indeed non-parametric bootstrap sampling over the data showed no proof of significant deviation from the baseline (\ref{fig:pref}, bottom left).

Finally, we found negative values in all response bias terms, which suggests a general bias toward answering `different'.  This bias is probably due to the categorical nature of the task: when two items are ambiguous but perceptually different, this could cause a slight preference for `different' over `same'.

\subsection{experiment 2}

In experiment 1, we tested the ability of people to recognize a word category under ambiguous tokens. In particular, the tokens were clear but their category membership was uncertain. In real life situations, however, even the identity of the token can be uncertain due to various distorting factors. In order to account for this kind of uncertainty in the auditory modality, we can imagine, following \citeA{feldman2009}, that the speaker generates a target production $t$ from an auditory category
$t | A \sim N(\mu_{A}, \sigma^2_{A})$. The Listener, in a noisy condition, does not hear exactly this produced target, but the target with noise, which is assumed to be normally distributed: $a | t \sim N(t, \sigma^2_{N})$. When we integrate over $t$, we get:
\begin{equation}
a | A \sim N(\mu_{A}, \sigma^2_{A}+\sigma^2_{N})
\end{equation}
In this experiment, we explored the effect of noise on performance in our audio-visual recognition task. More precisely, we tested a case where one modality was ambiguous and noisy (auditory), and where the other modality was ambiguous but not noisy (visual). We were interested to know if participants would treat this new source of uncertainty as predicted by the optimal baseline, and whether noise in one modality would trigger some systematic preference for the non-noisy modality?   
\subsubsection{Participants}

100 participants were recruited online through Amazon Mechanical Turk. We used similar exclusion criteria as in the previous experiment. The final sample consisted of 93 participants.

\subsubsection{Stimuli}
We used the exact same visual stimuli. As for the auditory stimuli, we used the same /aba/-/ada/ continuum as in experiment 1, but we convoluted each item with Brown noise of amplitude 1 using the audio editor Audacity (2.1.2).

\subsubsection{Procedure}
The procedure was exactly the same as in the previous experiment, except that the auditory stimuli in the test were replaced by the new noisy stimuli. The latter were not used for the target item nor during the training part.

\subsubsection{Results}

\textit{Unimodal conditions:} we fitted a model for each modality, collapsed across participants. For the auditory modality, we got $\epsilon_A=-0.18$ and $\sigma^2_A+\sigma^2_N=4.70$. For the visual modality, we got $\epsilon_V=-0.24$ and $\sigma^2_V=3.93$.  In figure \ref{fig:unimodal} (bottom) we plotted responses in the unimodal conditions as well as the unimodal fits.

\textit{Bimodal condition:} we fitted a model to human responses in the bimodal condition, collapsed across participants. We got $\epsilon=-0.38$, $\sigma^2_{Vb}=5.21$, and  $\sigma^2_{Ab}+\sigma^2_{Nb}=9.84$.

\textit{Baseline model:} we generated the predictions of the baseline model by using the values of the variances derived from the unimodal conditions, and the response bias derived from the bimodal condition, and by plugging these values into the expression of the posterior (expression \ref{eq:pred}).

Results are shown on  figure \ref{fig:Exp} (bottom).  Correlation of human data to the bimodal baseline and the fit are shown in figure \ref{fig:corr} (bottom).

\subsubsection{Discussion}

\begin{figure}[h]
\centering
\includegraphics[width=0.4\textwidth]{preference.png}
\caption{Top: decision thresholds in the audio-visual space. Red dotted line is the prediction of the baseline. Blue dotted lines are cases where modality preference is twice as strong as the baseline. Solid line is the threshold derived from human data. Bottom: comparison of the threshold slope between the baseline and the fit to human data. Error bars are 95\% confidence intervals computed through non-parametric bootstrap sampling (10.000 samples)}
\label{fig:pref}
\end{figure}

We found, similar to experiment 1, that participants generally showed qualitative patterns similar to the baseline model. The latter explained 91\% of total variance. We also found a similar discrepancy at the quantitative level: there was a decrease in the reliability of both modalities, as could be inferred from the increase in the variance associated with the auditory modality and the visual modality in the bimodal fit.

An interesting difference with experiment 1, however, was that participants' decision threshold suggested a preference for the visual modality (the non-noisy modality). Indeed non-parametric bootstrap sampling over the data showed there to be a significant decrease in the value of the slope.

\section{Conclusion}

In this work, we tested word category recognition under audio-visual uncertainty. We modeled uncertainty as a probability distribution over tokens from auditory and visual continua. Our baseline model proposed a way these probability distributions can be combined in an ideal way. The model's predictions were examined in two experiments where we tested two kinds of uncertainty: in experiment 1, audio-visual tokens were clear but their category membership was ambiguous. In experiment 2, input to one modality was ambiguous, and input to the other was ambiguous as well as noisy. In both experiments, participants showed many patterns of optimal behaviour, with the model's predictions explaining 89\% and 91\% of the variance, respectively. We found, however, that a bimodal presentation caused the reliability of both modalities to decrease.
We explored whether part of the unexplained variance could involve to a systematic preference for a given modality. Our analysis showed no evidence of such modality preference in experiment 1. However, we found a preference for the non-noisy modality in experiment 2.

This paper addressed the problem of recognizing words whose underlying phonemic and semantic categories were supposed to be familiar. An intriguing challenge is to understand how these underlying categories are acquired in the first place. Previous developmental work addressed cases when one modality was supposed to provide a stable and certain cue to the other modality \cite<e.g.,>{waxman1995, yeung09}. The present paper invites investigations on category acquisition in the more general case where there is uncertainty in both modalities.

\bibliographystyle{apacite}

\setlength{\bibleftmargin}{.125in}
\setlength{\bibindent}{-\bibleftmargin}

\bibliography{CogSci_Template}

\end{document}

### 2017-01-31 write-up/main.tex

@@
 
-\title{Word identification under multimodal Uncertainty}
+\title{Word Identification Under Multimodal Uncertainty}
 
@@
 
-Language requires the ability to process arbitrary multimodal input.
-It also requires the ability to infer categories under uncertainty.
-In this paper, we introduce a task that allows us to examine how adults identify word categories under uncertainty from the auditory and the visual modality.
+Identifying the visual referent of a spoken word -- that a particular insect is referred to by the word ``bee'' -- requires both the ability to process and integrate multi-modal input and the ability to identify categories under uncertainty.
+How do these tasks interact with one another?
+We introduce a task that allows us to examine how adults identify word categories under joint uncertainty in the auditory and visual modalities.
 We propose a Bayesian model of the task which provides an optimal baseline.
-The predictions are tested in two experiments where category recognition is made under two kinds of uncertainty: ambiguity and noise.
-In both cases, human data shows many patterns of optimal behaviour, and the baseline explains most of the variance.
-However, when one modality is noisy, we found evidence for a systematic preference for the non-noisy modality.
+Model predictions are tested in two experiments where category recognition is made under two kinds of uncertainty: ambiguity and noise.
+In both cases, the optimal baseline model explains much of the variance in human judgments.
+But when one modality had noise added to it, human perceivers systematically preferred the unperturbed modality to a greater extent than the optimal baseline model did.
 
@@
 
-Language uses symbols expressed in one modality (e.g., the auditory modality in the case of speech) to communicate about things in the world, which we perceive through  various sensory modalities (e.g., the visual modality in the case of concrete objects).
-Therefore, understanding language requires the ability to process arbitrary multisensory input.
-This processing, however, is only a first step.
-When a speaker utters a word and points to an object, it is not enough for the observer to be able to encode these precise sound and object tokens.
-They should, on top of that, be able to identify the underlying categories (such as the phonemes, the concept, and the word category).
-This challenge is quite obvious when a person has to learn these categories (e.g., a baby who starts learning language).
-But a challenge is present even when the person already knows the categories, but has to recognize them.
-This is because individual tokens are often ambiguous or/and noisy\cite<e.g.,>{hillenbrand1995}.
-They do not indicate with absolute certainty their category membership, they do so only in probabilistic terms.
-For example, the speaker may make a mispronunciation, or their utterance may get distorted because of ambient noise.
-Similarly, the identity of the object that is being referred to may be uncertain when there exist other surrounding and/or similar looking objects, or when the observer's view is partially obstructed.
+ % (e.g., the visual modality in the case of concrete objects)
+Language uses symbols expressed in one modality (e.g., the auditory modality, in the case of speech) to communicate about the world, which we perceive through many different sensory modalities.
+Consider hearing someone yell ``bee!" at a picnic, as a honeybee buzzes around the food.
+Determining reference involves processing the auditory information and linking it with other perceptual signals (e.g., the visual image of the bee, the sound of its wings, the sensation of the bee flying by your arm).
+But processing this linguistic input also requires categorization.
+On the linguistic side,  individual sounds must be identified as members of phonetic categories for the word to be understood.
+On the referential side, individual sensory impressions must be categorized as coming from a bee.
+Once these two sets of category-identification tasks have been completed, then a listener can make the referential link between word and world.
 
-It follows that, in order to identify the speaker's intended categories, an observer has to be able to reason under a great deal of uncertainty.
-To characterize this ability, it has been suggested that people encode tokens with their probability distributions, base their decisions on these probabilities, and adjust their behavior when these probabilities change \cite<e.g.,>{clayard08}.
-However, previous work in this line of research has largely focused on the unimodal case, that is, when categories can be defined along one modality, such as the phonemes \cite<e.g.,>{feldman2009}.
-A few studies did explore some aspects of cross-modal processing in this framework \cite<e.g.,>{bejjanki2011, kleinschmidt2015}, but focused on the specific case of phoneme recognition from speech and lip movement, wherein people assume information from both modalities to be tightly correlated.
+This comprehension task takes place in a noisy world.
+On the auditory side, individual acoustic word tokens are almost always ambiguous with respect to the particular sequence of phonemes they represent \cite<e.g.,>{hillenbrand1995}.
+And some tokens may be distorted additionally by mispronunciation or ambient noise.
+Perhaps the speaker was yelling ``pea" and not ``bee.'' Similarly, a sensory impression may not be enough to make a definitive identification of a visual category.\footnote{In the general case, language can of course be visual as well as auditory, and object identification can be done through many modalities.
+For simplicity, we focus on audio-visual matching here.} Perhaps the quickly flying insect was a beetle or a fly instead.
 
-In the present work, we study the case of word category recognition, where a word is an \textit{arbitrary} mapping between a sound category and a visual category.
-We test people on their ability to encode audio-visual tokens and use them to recognize the underlying word category.
-Crucially, this recognition is made under uncertainty from both the auditory category (the phoneme) and the visual category (the concept being referred to).
-Our goal is to explore how adults deal with such multimodal ambiguity in a categorical task.
-To this end, we propose a model that combines uncertainty in an optimal way, and we use it as a baseline for human data.
-More precisely, we examine the extent to which human data conform to, or deviate from the baseline, and whether the deviation involves a systematic preference for a particular modality?
+Thus, establishing reference requires reasoning under a great deal of uncertainty.
+Work on phoneme categorization has suggested that perceivers encode tokens probabilistically: they base their decisions on these probabilities and adjust their behavior when these probabilities change \cite<e.g.,>{clayard08}.
+However, previous work in this line of research has largely focused on the unimodal case, that is, when category uncertainty is only in one modality \cite<e.g.,>{feldman2009}.
+A few studies have explored some aspects of cross-modal processing  \cite<e.g.,>{bejjanki2011, kleinschmidt2015}.
+This work has focused on the specific case of phoneme recognition from speech and lip movement, however, where information from both modalities is tightly correlated.
+
+In the present work, we study the case of word recognition, where a word is an \textit{arbitrary} mapping between a sound category and a visual category.
+We test participants on their ability to process audio-visual stimuli and use them to recognize the underlying word category.
+Crucially, this recognition is made under uncertainty about both the auditory category (a single phoneme, in our case) and the visual category (the concept being referred to).
+Our goal is to explore how adults deal with such multimodal ambiguity in a categorization task.
+To this end, we propose a model that combines uncertainty in an optimal way, and we use it as a baseline for interpreting human data.
+More precisely, we examine the extent to which human data conform to, or deviate from the baseline, and whether the deviation involves a systematic preference for a particular modality.
 
@@
 First, we introduce our audio-visual word recognition task.
-Second, we present the model and explain how it generate an optimal baseline.
-Then we present the behavioral experiments where we test category recognition under audio-visual uncertainty.
-In experiment 1, audio-visual tokens are clear but their category membership is ambiguous.
-In experiment 2, input to one modality is ambiguous, and input to the other is ambiguous as well as noisy.
-We analyse and discuss the results of the experiments in the light of the model's predictions.
+We next present the model and explain how it provides an optimal baseline.
+Then we present two behavioral experiments where we test category recognition under audio-visual uncertainty.
+In Experiment 1, audio-visual tokens are clear but their category membership is ambiguous.
+In Experiment 2, we intervene by adding additional perceptual noise to one modality.
+While participants show no modality preference in Experiment 1, in Experiment 2 they over-rely on visual input when the auditory modality is noisy.
 
-\section{The audio-visual word recognition task}
+\section{The Audio-Visual Word Recognition Task}
 
@@
 
-In each trial, participants are presented with an audio-visual target (the prototype of the target category), immediately followed by an audio-visual test. 
-The test may differ from the target in both the auditory and the visual components.
+In each trial, participants are presented with an audio-visual target (the prototype of the target category), immediately followed by an audio-visual test stimulus (Figure \ref{fig:task}).
+The test stimulus may differ from the target in both the auditory and the visual components.
 The auditory component is sampled from a continuum along the second formant (F2) linking the words /aba/ and /ada/.
 The visual component is sampled from a morph that links the prototypical pictures of the dog and the cat.
-After these two presentations, participants are instructed to press `same' or `different'.
+After these two presentations, participants are instructed to press ``same'' or ``different.''
 
 This task is similar to the task introduced by \citeA{sloutsky2003} and used in subsequent research to probe audio-visual encoding.
-However, unlike this previous line of research, here participants are not asked whether the two audio-visual presentations are identical, instead, they are asked to press `same' if they think the second item (the test) belonged to the same word category as the prototype (e.g.,  dog-/aba/), even if there is a slight sound mispronunciation,  a slight difference in the object’s shape, or a slight difference in both the pronunciation and the shape.
-They are instructed to press `different' if they think that the test was, rather, an audio-visual instance to the other word category (cat-/ada/).
+However, unlike this previous line of research, here participants are not asked whether the two audio-visual presentations are identical.
+Instead, the task is category-based: They are asked to press `same' if they think the second item (the test) belonged to the same category as the first (e.g.,  dog-/aba/), even if there is a slight difference in the word, in the object, or in both.
+They are instructed to press `different' only if they think that the second stimulus was an instance of the other word category (cat-/ada/).
 
-As shown in figure \ref{fig:task}, besides the audio-visual trials where both the sounds and the pictures are presented, there are also unimodal trials where the pictures are hidden (auditory-only) or where the sounds are muted (visual-only).
-These unimodal trials are crucial since they provide us with the probability distributions of the auditory and visual categories over their tokens.
-In fact, the goal is to examine whether participants' responses on the bimodal trial are optimal combination of the probabilities derived from their responses on the unimodal trials.
-
-Next, we explain how we modeled this task in a Bayesian framework.
+The task also included trials where pictures were hidden (audio-only) or where sounds were muted (visual-only).
+These unimodal trials provide us with participants' categorization functions for the auditory and visual categories and are used as inputs to the optimal model, described below.
 
@@
 
-\section{What would an ideal recognizer do?}
+\section{Ideal Observer Model}
 
-The unimodal conditions (auditory-only or visual-only)  are used to characterize the probability distributions of the auditory and the visual categories.
-We assume, for the sake of simplicity, that the probability distributions are normally distributed:
+The basis of our ideal observer model is that individual categorization functions from each modality should be combined optimally.
+In each modality, we have two categories: /ada/ ($A=1$) and /aba/ ($A=2$) in the auditory dimension, and \textit{cat} ($V=1$) and \textit{dog} ($V=2$) in the visual dimension.
+% \footnote{The identity of the categories was randomized in the experimental setup.}
+We assume, for the sake of simplicity, that the probability of membership in each category is normally distributed:
 
-$$ a | A \sim  N(\mu_A, \sigma^2_A) $$
-$$ v | V \sim  N(\mu_V, \sigma^2_V) $$
+$$ p(a | A) \sim  N(\mu_A, \sigma^2_A) $$
+$$ p(v | V) \sim  N(\mu_V, \sigma^2_V) $$
 
-In each modality, we have two categories: /ada/ ($A=1$) and /aba/ ($A=2$) in the auditory dimension, and \textit{cat} ($V=1$) and \textit{dog} ($V=2$) in the visual dimension (the identity of the categories was randomized in the experimental setup).
+In the bimodal condition, participants see word tokens with audio-visual input, and have to make a categorization decision.
+We represent word tokens as vectors in the audio-visual space, $\mathbf{w}=(a,v)$.
+A word category $W$ is defined as the joint distribution of auditory and visual categories. It can be characterized with a bivariate normal distribution in the audio-visual space:
+$$ p(\mathbf{w} | W) \sim  N(M_W, \Sigma_W) $$
 
-In the bimodal condition, participants see word tokens made of audio-visual input, and have to make a categorical decision.
-We represent word tokens as vectors in the audio-visual space $\mathbf{w}=(a,v)$.
-A word category $W$ is defined as the joint distribution of the auditory and visual categories. It can be characterized with a bivariate normal distribution in the audio-visual space:
-$$ \mathbf{w} | W \sim  N(M_W, \Sigma_W) $$
 \begin{figure}[tp]
   \centering
-\includegraphics[width=0.4\textwidth]{MyTask.png}
-\caption{Model of the task: a word category is defined as the joint bivariate distribution of an auditory category (bottom) and a visual semantic category (left).
-Upon the presentation of a word token $w$, participants guess whether it is sampled from the word category $W1$ or from $W2$.
-Decision threshold is where the guess probability is 0.5.
-(Plotted distributions are for illustration only)}
+  \includegraphics[width=3.25in]{MyTask.png}
+  \caption{Illustration of our model using simulated data.
+A word category is defined as the joint bivariate distribution of an auditory category (horizontal, bottom panel) and a visual semantic category (vertical, left panel).
+Upon the presentation of a word token $w$, participants guess whether it is sampled from the word category $W_1$ or from $W_2$.
+Decision threshold is where the guessing probability is 0.5.}
   \label{fig:space}
 \end{figure}
-We have two word categories: dog-/aba/ ($W=1$) and cat-/ada/ ($W=2$).
+
+We have two word categories: dog-/aba/ ($W_1$) and cat-/ada/ ($W_2$).
 Participants can be understood as choosing one of these two word categories (figure \ref{fig:space}).
 For an ideal ``recognizer'', the probability of choosing category 2 when presented with an audio-visual instance $\mathbf{w}=(a,v)$ is the posterior probability of this category:
+
 \begin{equation}
-\small
-p(W=2 | \mathbf{w})=\frac{p(\mathbf{w}|W=2)p(W=2)}{p(\mathbf{w}|W=2)p(W=2)+p(\mathbf{w}|W=1)p(W=1)}
+% \small
+p(W_2 | \mathbf{w})=\frac{p(\mathbf{w}|W_2)p(W_2)}{p(\mathbf{w}|W_2)p(W_2)+p(\mathbf{w}|W_1)p(W_1)}
 \end{equation}
+
 We make the assumption that, given a particular word category, the auditory and visual tokens are independently generated:
+
 \begin{equation}
@@
 \begin{equation}
-p(W=2 | \mathbf{w})=\frac{1}{1+(1+\epsilon)\exp(\beta_0+\beta_aa+\beta_vv)}
+p(W_2 | \mathbf{w})=\frac{1}{1+(1+\epsilon)\exp(\beta_0+\beta_aa+\beta_vv)}
 \label{eq:pred}
@@
 
-and $1+\epsilon=\frac{p(W=1)}{p(W=2)}$ is the proportion of the prior probabilities.
-If the identity of word categories is randomized, and if $W1$ is the target, then $\epsilon$ measures a response bias to `same' if $\epsilon > 0 $, and a response bias to `different' if $\epsilon < 0 $.
+and $1+\epsilon=\frac{p(W_1)}{p(W_2)}$ is the proportion of the prior probabilities.
+If the identity of word categories is randomized, and if $W_1$ is the target, then $\epsilon$ measures a response bias to ``same'' if $\epsilon > 0 $, and a response bias to ``different'' if $\epsilon < 0 $.
 
@@
 
-Next, we present the behavioral experiments.
-Our goal is twofold: 1) examine the extent to which human responses correspond or deviate from the predictions of the optimal baseline.
-2) if there is a deviation from the baseline, examine whether this deviation involves a systematic preference for a particular modality.
+\section{Experiment 1}
 
-\section{experiments}
+In experiment 1, we test the predictions of the model in the case where uncertainty is due to perceptual ambiguity in terms of category membership.
+This experiment had two goals.
+First, we wanted to examine the extent to which human responses corresponded to the predictions of the ideal observer model.
+Second, if there was a deviation from the baseline, we wanted to be able to measure whether this deviation involved a systematic preference for a particular modality.
 
-In experiment 1, we test the predictions of the model in the case where uncertainty is due to ambiguity in terms of category membership.
-
-\subsection{experiment 1}
+\subsection{Methods}
 
 \subsubsection{Participants}
-We planned to run 100 participants recruited from Amazon Mechanical Turk.
+
+We recruited a planned sample of 100 participants, recruited from Amazon Mechanical Turk.
 Only participants with US IP addresses and a task approval rate above 85\% were allowed to participate.
 They were paid at an hourly rate of \$6/hour.
-Data
-were excluded if participants completed the task more than
+Data were excluded if participants completed the task more than
 once (2 participants).
@@
 \subsubsection{Stimuli}
-For the auditory stimuli, we used the continuum introduced in \citeA{vroomen2004}.
-It is a 9-point /aba/--/ada/ speech continuum which was created by varying the frequency of the second (F2) formant in equal steps.
-We selected 5 equally spaced points from the original continuum by keeping the end-points (prototypes) 1 and 9, as well as the three points: 3, 5, and 7 along the continuum.
 
-For the visual stimuli, we used a morph continuum introduced in \citeA{freedman2001}. In the original stimuli, a continuous set of images was generated from three cat prototypes and
-three dog prototypes.
-We selected a morph along the dog and cat prototypes that seemed most natural.
-Moreover, from the original 14 points, we selected 5 points as follows: we kept the item that seemed most ambiguous (point 8), the 2 preceding points (i.e., 7 and 6) and the 2 following points (i.e., 8 and 9).
-The 6 and 9 points along the morph were quite distinguishable, and we took them to be our prototypes (figure \ref{fig:morph}).
+For  auditory stimuli, we used the continuum introduced in \citeA{vroomen2004}, a 9-point /aba/--/ada/ speech continuum created by varying the frequency of the second (F2) formant in equal steps.
+We selected 5 equally spaced points from the original continuum by keeping the end-points (prototypes) 1 and 9, as well as points 3, 5, and 7 along the continuum.
+For visual stimuli, we used a morph continuum introduced in \citeA{freedman2001}: a continuous set of images was generated from three cat prototypes and three dog prototypes.
+From the original 14 points, we selected 5 points as follows: we kept the item that seemed most ambiguous (point 8), the 2 preceding points (i.e., 7 and 6) and the 2 following points (i.e., 8 and 9).
+The 6 and 9 points along the morph were quite distinguishable, and we took them to be our prototypes.
 
-\begin{figure}[tp]
-\centering
-\includegraphics[width=0.4\textwidth]{morph.png}
-\caption{Visual stimuli}
-\label{fig:morph}
-\end{figure}
+ % (Figure \ref{fig:morph})
+%
+% \begin{figure}[tp]
+% \centering
+% \includegraphics[width=0.4\textwidth]{morph.png}
+% \caption{Visual stimuli for our experiments.}
+% \label{fig:morph}
+% \end{figure}
 
 \subsubsection{Design and Procedure}
-We told participants that an alien was naming two objects: a dog, called /aba/ in the alien language, and a cat called /ada/.
+
+We told participants that an alien was naming two objects: a dog, called /aba/ in the alien language, and a cat, called /ada/.
 In each trial, we presented the first object (the target) on the left side of the screen simultaneously with the corresponding sound.
 The target was always the same (e.g., dog-/aba/).
-The second sound-object pair (the test) followed after half a second.
-It showed up on the right side of the screen and was supposed to be either another dog-/aba/, or a cat-/ada/.
-For both the target and the test, we displayed the object when the corresponding sound started playing, and we made it disappear when the sound stoped (for a total of around 800ms).
+The second sound-object pair (the test) followed on the other side of the screen after 500ms and varied in its category membership.
+For both the target and the test, visual stimuli were present for the duration of hte sound clip ($\sim$800ms).
+We instructed participants to press ``S'' for same if they thought the alien was naming another dog-/aba/, and ``D'' for different if they thought the alien was naming a cat-/ada/.
 For each participant, we randomized the sound-object mapping as well as the identity of the target.
-Finally, we instructed participants to press S (for same) if they thought the alien was naming another dog-/aba/, and D (for different) if they thought the alien was naming a cat-/ada/.
 
-The first part of the experiment was a training to familiarize the participants with the task and the stimuli.
-In this training phase, we used only the prototype pictures and the prototype sounds, and each trial had a correct answer: the test item was either exactly the same as the target, or the prototype of the other word category.
-There were a total of 12 trials, half same, and half different.
-The second part was the real task.
-In this part, we told participants that, like in the training, the first sound-object pair would be the same.
-However, in the second pair, both the sound and the picture could be ambiguous.
-We told them that each trial was different.
-Finally, we encouraged participants to base their answers on both the sounds and the pictures in the bimodal condition.
-Each test item was made of a sound sampled from the /aba/-/ada/ continuum, and the picture form the dog-cat morph.
-There was a total of 25 possible combinations in the bimodal condition, and 5 in each of the unimodal conditions.
-Each participants answered twice to each possible trial in each condition for a total of 70 trials/participants.
-For each participant,  we randomized the order of conditions (auditory-only, visual-only, and bimodal).
-We designed the experiment to take between 10 to 15 minutes to complete.
+The first part of the experiment trained participants using only the prototype pictures and the prototype sounds (12 trials, 4 each from the bimodal, audio-only, and visual-only conditions).
+After completing training, we instructed participants on the structure of the task and encouraged them to base their answers on both the sounds and the pictures (in the bimodal condition).
+There were a total of 25 possible combinations in the bimodal condition, and 5 in each of the unimodal conditions.
+Each participant saw each possible trial in each condition twice, for a total of 70 trials/participants.
+Trials were blocked by condition and blocks were presented in random order.
+% We designed the experiment to take between 10 to 15 minutes to complete.
+
 \begin{figure}
 \centering
-\includegraphics[width=0.4\textwidth]{unimodal.png}
-\caption{Average human responses in the auditory-only condition (left), and visual-only condition (right). Error bars are 95\% confidence intervals. Solid lines represent the unimodal fits. }
+\includegraphics[width=3.25in\textwidth]{unimodal.png}
+\caption{Average human responses in the auditory-only condition (left), and visual-only condition (right). Error bars are 95\% confidence intervals. Solid lines represent unimodal logistic fits.}
 \label{fig:unimodal}
@@
 
-\subsubsection{Results}
-
-\begin{figure}[h]
-\centering
-\includegraphics[width=0.4\textwidth]{correlation.png}
-\caption{Human responses vs.
+\subsection{Results}
+%
+% \begin{figure}[h]
+% \centering
+% \includegraphics[width=3.25in\textwidth]{correlation.png}
+% \caption{Human responses vs.
 the baseline predictions.
@@
 In experiment 2, the baseline and the fit explained 91\%, and 97\% of total variance, respectively}
-\label{fig:corr}
-\end{figure}
+% \label{fig:corr}
+% \end{figure}
 
-\begin{figure*}
+\begin{figure*}[t]
 \centering
-\includegraphics[width=0.83\textwidth]{Exp.png}
-\caption{Proportion of `different' as a function of the auditory distance.
+\includegraphics[width=.83\textwidth]{Exp.png}
+\caption{Proportion of ``different'' judgments as a function of auditory distance.
 Solid lines represent average human responses (left), predictions of the baseline (middle), and the bimodal fit (left).
-Dotted lines represent average human responses in the unimodal conditions.
-Colors represent values in the visual continuum.
-}
+Dashed lines represent average human responses in the unimodal conditions.
+Colors represent values in the visual continuum.}
 \label{fig:Exp}
+% \vspace{10ex}
 \end{figure*}
 
-\textit{Unimodal conditions:} Let's take the auditory-only case as an example, participants can be understood as choosing one of two auditory categories.
-For an ideal recognizer, the probability of choosing category 2 (that is, to answer `different') when presented with an audio instance $a$ is the posterior probability of this category $p(A=2|a)$.
+% Let's take the auditory-only case as an example,
+\subsubsection{Unimodal conditions}
+
+Average categorization judgments and fits are shown in Figure \ref{fig:unimodal}.
+Auditory judgements were somewhat sharper and more pronounced than visual judgments.
+For an ideal recognizer, the probability of choosing category 2 (that is, to answer ``different'') when presented with e.g., an audio instance $a$, is the posterior probability of this category $p(A_2|a)$.
 If we assume that both categories have equal variances, the posterior probability reduces to:
+
 \begin{equation}
-p(A=2 | a)=\frac{1}{1+(1+\epsilon_A)\exp(\beta_{a0}+\beta_aa)}
+p(A_2 | a)=\frac{1}{1+(1+\epsilon_A)\exp(\beta_{a0}+\beta_aa)}
 \end{equation}
-with $\beta_a=\frac{\mu_{A1}-\mu_{A2}}{\sigma^2_{A}}$ and  $\beta_{a0}=\frac{\mu^2_{A2}-\mu^2_{A1}}{2\sigma^2_{A}}$. $\epsilon_A$ is the response bias in the auditory-only trials.
+
+with $\beta_a=\frac{\mu_{A_1}-\mu_{A_2}}{\sigma^2_{A}}$ and  $\beta_{a0}=\frac{\mu^2_{A_2}-\mu^2_{A_1}}{2\sigma^2_{A}}$. $\epsilon_A$ is the response bias in the auditory-only trials.
 
 For this model (as well all other models), we fixed the values of the means to be the end-points of the corresponding continuum: $\mu_{A1}=0$ and $\mu_{A2}=4$ (and similarly $\mu_{V1}=0$, and $\mu_{V2}=4$).
-To determine the values of the bias and the variance, we fitted a model for each modality, collapsed across participants.
+To determine the values of the bias and the variance, we fit a model for each modality, collapsed across participants.
 For the auditory modality, we got $\epsilon_A=-0.20$ and $\sigma^2_A=2.04$.
 For the visual modality, we got $\epsilon_V=-0.11$ and $\sigma^2_V=3.34$.
-In figure \ref{fig:unimodal} (top) we plotted responses in the unimodal conditions as well as the unimodal fits.
+% In figure \ref{fig:unimodal} (top) we plotted responses in the unimodal conditions as well as the unimodal fits.
 
-\textit{Bimodal condition:} we fitted a model to human responses in the bimodal condition, collapsed across participants. We got $\epsilon=-0.32$, $\sigma^2_{Ab}=5.00$ and $\sigma^2_{Vb}=7.27$.
+\subsubsection{Bimodal condition}
 
-\textit{Baseline model:} we derived the predictions of the baseline model by using the values of the variances derived from the unimodal conditions, and the response bias derived from the bimodal condition, and by plugging these values into the expression of the posterior \ref{eq:pred}.
+We fit a model to human responses in the bimodal condition, collapsed across participants, finding $\epsilon=-0.32$, $\sigma^2_{Ab}=5.00$ and $\sigma^2_{Vb}=7.27$.
 
-In figure \ref{fig:Exp} (top) we plotted the participants' responses in the bimodal condition (left), as well as the prediction of the baseline (middle) and the bimodal fit (right).
-Correlation of human data vs.
-the bimodal baseline and fit are shown in figure \ref{fig:corr} (top).
+\subsubsection{Baseline model}
 
-\subsubsection{Discussion}
-Compare human responses (figure \ref{fig:Exp}, top left) to the baseline (figure \ref{fig:Exp}, top middle).
-Qualitatively speaking, the participants showed many patterns of optimal behaviour (as defined by the baseline).
-Let's, for instance, explore how behaviour changed when participants moved from the auditory-only case (dotted black line) to the bimodal case (solid colored lines).
-We see that, similar to the baseline, higher certainty in the visual modality either towards `different' (points 3 and 4 in the visual continuum), or towards `same' (points 1 and 0), generally drove responses accordingly, i.e., either towards more 'different' (as the curves moved up, compared to the auditory-only curve), or towards more `same' responses (as the curves moved down).
-Moreover, the amount of change was generally a function of the strength of evidence brought by the visual modality, with, for example, responses on visual point 4 being generally `higher' than responses on visual point 3.
-Similarly, responses on visual 0 were generally `lower' than responses on visual 1.
-Similar things can be said about the pattern of change from the visual-only (dotted colored horizontal lines) to the bimodal case: at each point along the auditory scale, we see that a point of a given color was generally below its corresponding horizontal line (i.e., same color) when the evidence brought by the auditory modality pointed more toward `same' (point 0 and 1), and was above its corresponding line when evidence pointed more toward `different' (point 3 and 4 along the auditory scale).
-These qualitative patterns were quite similar to the baseline model.
-Indeed, we found that the latter explained almost 90\% of the variance  ($r^2=0.89$).
+We derived the predictions of the baseline model by using the values of the variances derived from the unimodal conditions, and the response bias derived from the bimodal condition, and by substituting these values into the expression of the posterior in Eq.~\ref{eq:pred}.
+Figure \ref{fig:Exp} shows participants' responses in the bimodal condition (left), as well as the prediction of the baseline (middle), and the bimodal fit models (right).
+% Correlation of human data and the bimodal baseline/fitted model are shown in Figure \ref{fig:corr} (top).
 
-Though we see a qualitative resemblance between human data and the baseline, there were quantitative differences: predictions of the baseline were either a bit too high, or a bit too low.
-We can see this phenomenon clearly in the shape of the correlation graph (figure \ref{fig:corr}, top left).
-It is as though participants were less certain about responses than expected.
-Formally speaking, this translated as an increase in the value of the variance associated with each modality (compare the variance values in the baseline model to the values derived from the bimodal fit).
-Since the variance characterizes the reliability of a given cue, it seems as if the bimodal presentation caused reliance on both modalities to decrease.
-This effect can possibly be attributed to the arbitrary nature of the form-meaning mapping.
-In fact, previous studies suggest that while redundant mapping improves performance (e.g., determining the frequency of a bouncing ball from visual and auditory cues), arbitrary mappings generally tends to hinder performance (see \citeA{robinson2010} for a review).
+\subsubsection{Response bias}
 
-\textit{Modality preference?} we would like to know if part of the observed discrepancy between the baseline and human responses involved a systematic preference (albeit small) for a particular modality when making decisions in the bimodal condition.
-This preference, if real, should manifest as a deviation from the decision threshold predicted by the baseline model.
-The decision threshold is defined as the set of values in the audio-visual space along which the posterior (expression \ref{eq:pred}) is equal to 0.5.
-As illustrated in \ref{fig:space}, above this line participants are more likely to choose one word category, and below this line, they are more likely to choose the other word category.
+We found negative values for in all response bias terms, which suggests a general bias toward answering ``different.''  This bias is probably due to the categorical nature of the task: when two items are ambiguous but perceptually different, this could cause a slight preference for ``different'' over ``same.''
+
+\subsubsection{Modality preferences}
+
+We next analyzed whether there was a preference for one or the other modality when making decisions in the bimodal condition, beyond that explained by the variance in categories implied by the unimodal responses.
+This preference would manifest as a deviation from the decision threshold predicted by the baseline model.
+The decision threshold is defined as the set of values in the audio-visual space along which the posterior (Eq.~\ref{eq:pred}) is equal to 0.5.
 The decision threshold takes the following form:
+% As illustrated in \ref{fig:space}, above this line participants are more likely to choose one word category, and below this line, they are more likely to choose the other word category.
+
 \begin{equation}
@@
 \end{equation}
-If the slope derived from the fit is bigger than the slope of the baseline, this would suggest a general preference for the auditory modality, and a smaller slope would suggest a general preference for the visual modality.
+
+If the slope derived from the fit is bigger than the slope of the baseline, this finding would suggest a general preference for the auditory modality (similarly, a smaller slope would suggest a preference for the visual modality).
 The limit cases are when there is exclusive reliance on the auditory cue (a vertical line), and where there is exclusive reliance on the visual (a horizontal line).
-In figure \ref{fig:pref} (top left) we plotted some decision thresholds in the audio-visual space when the intercept was kept constant.
-The fit to human data  (solid black line) was very close to the baseline threshold (red line).
-Indeed non-parametric bootstrap sampling over the data showed no proof of significant deviation from the baseline (\ref{fig:pref}, bottom left).
+Figure \ref{fig:pref} (top left) shows the decision threshold in the audio-visual space with a constant intercept; the fit to human data  (solid black line) was very close to the baseline threshold (red line).
+Non-parametric resampling sampling of the data showed no evidence of a deviation from the baseline (\ref{fig:pref}, bottom left).
 
-Finally, we found negative values in all response bias terms, which suggests a general bias toward answering `different'.
-This bias is probably due to the categorical nature of the task: when two items are ambiguous but perceptually different, this could cause a slight preference for `different' over `same'.
+\subsection{Discussion}
 
-\subsection{experiment 2}
+% Compare human responses (figure \ref{fig:Exp}, top left) to the baseline (figure \ref{fig:Exp}, top middle).
+Qualitatively, participants' judgments were similar to the predictions of the optimal baseline model (when fit to the unimodal data).
+Consider the contrast between the auditory-only case (dashed black line in Figure \ref{fig:Exp}, top left) and the bimodal case (solid colored lines).
+Higher certainty in the visual modality generally influenced responses, with greater visual distance leading to more ``different'' ratings and less visual distance leading to more ``same'' ratings.
+Indeed, we found that the baseline model explained almost 90\% of the variance in judgments ($r^2=0.89$).
+In addition, as described above, we did not see any evidence for a modality preference.
 
-In experiment 1, we tested the ability of people to recognize a word category under ambiguous tokens.
+But although we see a qualitative resemblance data and baseline model, there were quantitative differences.
+Model predictions were more influenced by the visual modality at the auditory midpoint (the point of highest uncertainty) than human judgements, and were more compressed at the endpoints (the points of lowest uncertainty).
+Formally speaking, this trend translated into an increase in the value of the variance associated with each modality (e.g., compare the variance values in the baseline model to the values derived from the bimodal fit).
+Since the variance characterizes the reliability of a given cue, it seems as if bimodal presentation caused reliance on both modalities to decrease.
+This effect could possibly be attributed to the arbitrary nature of the form-meaning mapping.
+In fact, previous studies suggest that while redundant multi-modal information improves performance (e.g., determining the frequency of a bouncing ball from visual and auditory cues), arbitrary mappings generally tends to hinder performance \citeA<for review, see>{robinson2010}.
+
+\section{Experiment 2}
+
+In Experiment 1, we tested the ability of people to recognize a word category under ambiguous tokens.
 In particular, the tokens were clear but their category membership was uncertain.
 In real life situations, however, even the identity of the token can be uncertain due to various distorting factors.
-In order to account for this kind of uncertainty in the auditory modality, we can imagine, following \citeA{feldman2009}, that the speaker generates a target production $t$ from an auditory category
+In order to account for this kind of uncertainty in the auditory modality, we can imagine \cite<following>{feldman2009}, that the speaker generates a target production $t$ from an auditory category
 $t | A \sim N(\mu_{A}, \sigma^2_{A})$.
-The Listener, in a noisy condition, does not hear exactly this produced target, but the target with noise, which is assumed to be normally distributed: $a | t \sim N(t, \sigma^2_{N})$.
+The listener, in a noisy condition, does not hear exactly this produced target, but the target perturbed by normally distributed noise: $a | t \sim N(t, \sigma^2_{N})$.
 When we integrate over $t$, we get:
+
 \begin{equation}
@@
 \end{equation}
-In this experiment, we explored the effect of noise on performance in our audio-visual recognition task.
-More precisely, we tested a case where one modality was ambiguous and noisy (auditory), and where the other modality was ambiguous but not noisy (visual).
-We were interested to know if participants would treat this new source of uncertainty as predicted by the optimal baseline, and whether noise in one modality would trigger some systematic preference for the non-noisy modality?
+
+In Experiment 2, we explored the effect of noise on performance in our task.
+We tested a case where one modality was ambiguous and noisy (auditory), and where the other modality was ambiguous but not noisy (visual).
+We were interested to know if participants would treat this new source of uncertainty as predicted by the optimal baseline, and whether noise in one modality would lead to some systematic preference for the non-noisy modality.
+
+\subsection{Methods}
+
 \subsubsection{Participants}
 
-100 participants were recruited online through Amazon Mechanical Turk. We used similar exclusion criteria as in the previous experiment. The final sample consisted of 93 participants.
+A planned sample of 100 participants was recruited online through Amazon Mechanical Turk.
+We used the same exclusion criteria as in the previous experiment; the final sample consisted of 93 participants.
 
-\subsubsection{Stimuli}
-We used the exact same visual stimuli.
-As for the auditory stimuli, we used the same /aba/-/ada/ continuum as in experiment 1, but we convoluted each item with Brown noise of amplitude 1 using the audio editor Audacity (2.1.2).
+\subsubsection{Stimuli and Procedure}
 
-\subsubsection{Procedure}
-The procedure was exactly the same as in the previous experiment, except that the auditory stimuli in the test were replaced by the new noisy stimuli.
-The latter were not used for the target item nor during the training part.
+We used the same visual stimuli as in Experiment 1.
+We also used the same auditory stimuli , but we convolved each item with Brown noise of amplitude 1 using the audio editor Audacity (2.1.2).
+The procedure was exactly the same as in the previous experiment, except that target stimuli were presented with the new noisy auditory stimuli.
 
-\subsubsection{Results}
+\subsection{Results}
 
-\textit{Unimodal conditions:} we fitted a model for each modality, collapsed across participants.
-For the auditory modality, we got $\epsilon_A=-0.18$ and $\sigma^2_A+\sigma^2_N=4.70$.
-For the visual modality, we got $\epsilon_V=-0.24$ and $\sigma^2_V=3.93$.
-In figure \ref{fig:unimodal} (bottom) we plotted responses in the unimodal conditions as well as the unimodal fits.
+\subsubsection{Unimodal conditions}
 
-\textit{Bimodal condition:} we fitted a model to human responses in the bimodal condition, collapsed across participants.
-We got $\epsilon=-0.38$, $\sigma^2_{Vb}=5.21$, and  $\sigma^2_{Ab}+\sigma^2_{Nb}=9.84$.
+We fit a model for each modality, collapsed across participants.
+For the auditory modality, our parameter estimates were $\epsilon_A=-0.18$ and $\sigma^2_A+\sigma^2_N=4.70$.
+For the visual modality, we found $\epsilon_V=-0.24$ and $\sigma^2_V=3.93$.
+Figure \ref{fig:unimodal} (bottom) shows responses in the unimodal conditions as well as the unimodal fits.
+In contrast to Experiment 1, auditory responses were flatter (showing more uncertainty).
 
-\textit{Baseline model:} we generated the predictions of the baseline model by using the values of the variances derived from the unimodal conditions, and the response bias derived from the bimodal condition, and by plugging these values into the expression of the posterior (expression \ref{eq:pred}).
+\subsubsection{Bimodal condition}
 
-Results are shown on  figure \ref{fig:Exp} (bottom).  Correlation of human data to the bimodal baseline and the fit are shown in figure \ref{fig:corr} (bottom).
+We fit a model to human responses in the bimodal condition, collapsed across participants. We estimated $\epsilon=-0.38$, $\sigma^2_{Vb}=5.21$, and  $\sigma^2_{Ab}+\sigma^2_{Nb}=9.84$.
+
+\subsubsection{Baseline model}
+
+We generated the predictions of the baseline model by using the values of the variances derived from the unimodal conditions, and the response bias derived from the bimodal condition, and by plugging these values into Eq.~\ref{eq:pred}.
+Results are shown in Figure \ref{fig:Exp} (bottom).
+ % Correlation of human data to the bimodal baseline and the fit are shown in figure \ref{fig:corr} (bottom).
 
@@
 
-We found, similar to experiment 1, that participants generally showed qualitative patterns similar to the baseline model.
-The latter explained 91\% of total variance.
-We also found a similar discrepancy at the quantitative level: there was a decrease in the reliability of both modalities, as could be inferred from the increase in the variance associated with the auditory modality and the visual modality in the bimodal fit.
-
-An interesting difference with experiment 1, however, was that participants' decision threshold suggested a preference for the visual modality (the non-noisy modality).
+We found, similar to experiment 1, that participants generally showed qualitative patterns similar to the baseline model ($r^2 = .91$).
+But we also found a similar discrepancy at the quantitative level: There was a decrease in the reliability of both modalities, as could be inferred from the increase in the variance associated with the auditory modality and the visual modality in the bimodal fit.
+An interesting difference with Experiment 1, however, was that participants' decision threshold suggested a preference for the visual modality (the non-noisy modality).
 Indeed non-parametric bootstrap sampling over the data showed there to be a significant decrease in the value of the slope.
@@
 We modeled uncertainty as a probability distribution over tokens from auditory and visual continua.
-Our baseline model proposed a way these probability distributions can be combined in an ideal way.
+Our baseline model instantiated an ideal observer, optimally combining participant data from unimodal decisions.
 The model's predictions were examined in two experiments where we tested two kinds of uncertainty: in experiment 1, audio-visual tokens were clear but their category membership was ambiguous.
 In experiment 2, input to one modality was ambiguous, and input to the other was ambiguous as well as noisy.
-In both experiments, participants showed many patterns of optimal behaviour, with the model's predictions explaining 89\% and 91\% of the variance, respectively.
-We found, however, that a bimodal presentation caused the reliability of both modalities to decrease.
+In both experiments, the ideal observer model explained the majority of variance in participant judgments.
+In both experiments, however, we found that bimodal presentation caused the reliability of both modalities to decrease relative to the ideal observer.
+
 We explored whether part of the unexplained variance could involve to a systematic preference for a given modality.

### 2017-01-31 data and analysis/analysis2.Rmd
new analysis

---
title: "WordRec Experiment"
author: "A. Fourtassi & M. Frank"
date: "January 13, 2017"
output:
  html_document:
    number_sections: yes
    toc: yes
---

Libraries.

```{r}
library(readr)
library(dplyr)
library(tidyr)
library(ggplot2)
library(langcog)
library(boot)
theme_set(theme_bw())
```

Data, and exclusion

```{r}

d <- read_delim("data_experiment2_complete.txt", delim = " ") %>%
  filter(ID !="AR1IWBDA7MC86", ID !="A3GOKNZGZGHL45") %>% #took the experiment twice
  filter(type == "Task", problem=="No")  %>% #had a technical problem during the experiment
  filter(score > 0.5)  #got more less than 50% correct on the training trials

```

Break out by conditions. 
```{r}
sounds <- d %>%
  filter(condition == "sound") %>%
  group_by(sound_dist) %>%
  multi_boot_standard(col = "answer")

concepts <- d %>%
  filter(condition == "concept") %>%
  group_by(concept_dist) %>%
  multi_boot_standard(col = "answer")

joint <- d %>%
  filter(condition == "joint") %>%
  group_by(concept_dist, sound_dist) %>%
  multi_boot_standard(col = "answer")

ggplot(joint, 
       aes(x = sound_dist, y = mean, col = factor(concept_dist))) + 
  #geom_pointrange(aes(ymin = ci_lower, ymax = ci_upper), 
                 # position = position_dodge(width = .1), size=0.3) + 
  geom_point(size=2) +
  geom_line(size=0.7) + 
  geom_line(data = sounds, aes(col = 1), col = "black",size=0.7) + 
  #geom_pointrange(data = sounds, aes(ymin = ci_lower, ymax = ci_upper, 
                             #        col = 1), col = "black", size=0.4)+
  geom_hline(data = concepts, aes(yintercept=mean, col = factor(concept_dist)), lty = 2)+
  xlab("Auditory distance") +ylab("% different")+
  scale_colour_discrete(name="Visual Dist")+
theme(legend.title = element_text(size=8))

ggplot(joint, 
       aes(x = concept_dist, y = mean, col = factor(sound_dist))) + 
  geom_pointrange(aes(ymin = ci_lower, ymax = ci_upper), 
                  position = position_dodge(width = .1), size=0.3) + 
  geom_line(lty = 2) + 
  geom_line(data = concepts, aes(col = 1), col = "black") + 
  geom_pointrange(data = concepts, aes(ymin = ci_lower, ymax = ci_upper, 
                                     col = 1), col = "black", size=0.4) + 
  scale_colour_solarized() +
  xlab("Visual distance") +ylab("% different")+
  scale_colour_discrete(name="Auditory Dist")+
theme(legend.title = element_text(size=8))

```

Fit the models.
```{r}

#Fit the uniomodal sound condition
sound_data <- d %>%
    filter(condition == "sound")

concept_data <- d %>%
    filter(condition == "concept")

joint_data <- d %>%
    filter(condition == "joint")

#Fit the non-linear function

sound_nl <- nls(answer ~ 1/(1+(1-e)*exp((-4/vrA)*sound_dist+(8/vrA))), data=sound_data, start = list(e=0, vrA=2))

concept_nl <- nls(answer ~ 1/(1+(1-e)*exp((-4/vrV)*concept_dist+(8/vrV))), data=concept_data, start = list(e=0, vrV=2))

joint_nl <- nls(answer ~ 1/(1+(1-e)*exp((-4/vrA_j)*sound_dist+(-4/vrV_j)*concept_dist+(8/vrA_j)+(8/vrV_j))), data=joint_data, start = list(e=0, vrA_j=2, vrV_j=2))

##extract coefficient
eA_nl <- coef(sound_nl)["e"]
vrA_nl <- coef(sound_nl)["vrA"]

eV_nl <- coef(concept_nl)["e"]
vrV_nl <- coef(concept_nl)["vrV"]

eJ_nl <- coef(joint_nl)["e"]
vrJ_A_nl <- coef(joint_nl)["vrA_j"]
vrJ_V_nl <- coef(joint_nl)["vrV_j"]

```

Bootstrap sampling on the model's parameters
```{r}
lmfit <- function(data, indices) {

  myd = data[indices, ]

  s_data <- myd %>%
    filter(condition == "sound")

  v_data <- myd %>%
    filter(condition == "concept")

  j_data <- myd %>%
    filter(condition == "joint")

  s_nl <- nls(answer ~ 1/(1+(1-e)*exp((-4/vrA)*sound_dist+(8/vrA))), data=s_data, start = list(e=0, vrA=2), nls.control(warnOnly = TRUE))

 c_nl <- nls(answer ~ 1/(1+(1-e)*exp((-4/vrV)*concept_dist+(8/vrV))), data=v_data, start = list(e=0, vrV=2), nls.control(warnOnly = TRUE))

 j_nl <- nls(answer ~ 1/(1+(1-e)*exp((-4/vrA_j)*sound_dist+(-4/vrV_j)*concept_dist+(8/vrA_j)+(8/vrV_j))), data=j_data, start = list(e=0, vrA_j=2, vrV_j=2), nls.control(warnOnly = TRUE))

  s_va <- coef(s_nl)["vrA"]
  v_va <- coef(c_nl)["vrV"]

  model_baseline=v_va/s_va

  j_va_s=coef(j_nl)["vrA_j"]
  j_va_v=coef(j_nl)["vrV_j"]

  model_data=j_va_v/j_va_s

  preference=c(model_baseline, model_data)

  return(preference)

  }

results <- boot(data= d, statistic = lmfit, R = 1)

results
myCI1=boot.ci(results, index = 1, conf = 0.95)
myCI2=boot.ci(results, index = 2, conf = 0.95)
print(myCI1)
print(myCI2)

```
Modalitiy preference plot
```{r}
#I make a data frame 
model = c('baseline', 'fit')
mean=c(1.64,1.45)
ci_low=c(1.24,1.29)
ci_up=c(2.02,1.65)
pref=data.frame(mean, ci_low, ci_up,model)

ggplot(pref, 
       aes(x = model, y=mean)) +
geom_bar(stat = "identity", width=0.5, fill='grey')+
  geom_errorbar(aes(ymin = ci_low, ymax = ci_up), 
                  width = 0.1
                ,
                  position = position_dodge(width = 0.1))+
  theme(aspect.ratio = 1, axis.text=element_text(size=15))

```
Analysis of the unimodal cases.
```{r}

#Recogniton functions from the unimodal fit 
x <- seq(0, 4, 0.01)

y_sound_nl <- predict(sound_nl, list(sound_dist = x), type="response")
y_concept_nl <- predict(concept_nl, list(concept_dist = x), type="response")

uniS_nl <- data.frame(xS_nl=x,yS_nl=y_sound_nl)
uniV_nl <- data.frame(xV_nl=x,yV_nl=y_concept_nl)

##The auditory case
ggplot(sounds, 
       aes(x = sound_dist, y = mean)) + 
  geom_pointrange(aes(ymin = ci_lower, ymax = ci_upper), 
                  position = position_dodge(width = .1)) + 
  #geom_line(data=uniS,aes(x=xS, y=yS))+
  geom_line(data=uniS_nl,aes(x=xS_nl, y=yS_nl), col='black')+
  xlab("Auditory distance") +ylab("% different")+
  scale_y_continuous(limits = c(0, 1))+theme(aspect.ratio = 0.7)
  #stat_function(fun = Logistic_a, colour="red")

##The visual case
ggplot(concepts, 
       aes(x = concept_dist, y = mean)) + 
  geom_pointrange(aes(ymin = ci_lower, ymax = ci_upper), 
                  position = position_dodge(width = .1)) + 
  #geom_line(data=uniV,aes(x=xV, y=yV))+
  geom_line(data=uniV_nl,aes(x=xV_nl, y=yV_nl), col='black')+
  xlab("Visual distance") +ylab("% different")+
  scale_y_continuous(limits = c(0, 1))+theme(aspect.ratio = 0.7)
  #stat_function(fun = Logistic_v, colour="red")

```

The bimodal case, all plots
```{r}

#The fit
model_fit <- function (x,y) {
   1/(1 + (1-eJ_nl)*exp((-4/vrJ_A_nl)*x+(-4/vrJ_V_nl)*y+(8/vrJ_A_nl)+(8/vrJ_V_nl)))
}

#The baseline
model_base <- function (x,y) {
    1/(1 + (1-eJ_nl)*exp((-4/vrA_nl)*x+(-4/vrV_nl)*y+(8/vrA_nl)+(8/vrV_nl)))
}

#Add the fit and the baeline to data
ms_all <- joint %>% 
  rename(joint = mean) %>%
  left_join(select(concepts, concept_dist, mean) %>% 
              rename(concepts = mean)) %>%
  left_join(select(sounds, sound_dist, mean) %>% 
              rename(sounds = mean)) %>%
  mutate(fit = model_fit(sound_dist, concept_dist)) %>%
  mutate(base = model_base(sound_dist, concept_dist)) %>%
  gather(model, pred, concepts, sounds, base, fit)

#Here plot human data
ggplot(joint, 
       aes(x = sound_dist, y = mean, col = factor(concept_dist))) + 
  #geom_pointrange(aes(ymin = ci_lower, ymax = ci_upper), 
                 # position = position_dodge(width = .1), size=0.3) + 
  geom_point(size=2.5) +
  geom_line(size=0.6) + 
  geom_line(data = sounds, aes(col = 1), col = "black",size=0.8, lty=2) + 
  #geom_pointrange(data = sounds, aes(ymin = ci_lower, ymax = ci_upper, 
                             #        col = 1), col = "black", size=0.4)+
  geom_hline(data = concepts, aes(yintercept=mean, col = factor(concept_dist)), lty = 2)+
  xlab("Auditory distance") +ylab("% different")+
  scale_colour_discrete(name="Visual Dist")+
theme(legend.title = element_text(size=8))+
  scale_y_continuous(limits = c(0, 1))+
  theme(aspect.ratio = 0.7)

#Plot predictions of the baseline
mybase <- ms_all %>%
  filter(model=="base")

ggplot(mybase, 
       aes(x = sound_dist, y = pred, col = factor(concept_dist))) + 
  geom_point(size=2.5) + 
  geom_line(size = 0.6) + 
  geom_line(data = sounds, aes(y=mean, col = 1), col = "black",size=0.8, lty=2) + 
  geom_hline(data = concepts, aes(yintercept=mean, col = factor(concept_dist)), lty = 2)+
  #scale_colour_solarized() +
  xlab("Auditory distance") +ylab("% different")+
  scale_colour_discrete(name="Visual Dist")+
theme(legend.title = element_text(size=8))+
  scale_y_continuous(limits = c(0, 1))+
  theme(aspect.ratio = 0.7)

#Plot the predictions of the bimodal fit
myfit <- ms_all %>%
  filter(model=="fit")

ggplot(myfit, 
       aes(x = sound_dist, y = pred, col = factor(concept_dist))) + 
  geom_point(size=2.5) + 
  geom_line(size= 0.6) + 
  geom_line(data = sounds, aes(y=mean, col = 1), col = "black" ,size=0.8, lty=2) +
  geom_hline(data = concepts, aes(yintercept=mean, col = factor(concept_dist)), lty = 2)+
  #scale_colour_solarized() +
  xlab("Auditory distance") +ylab("% different")+
  scale_colour_discrete(name="Visual Dist")+
theme(legend.title = element_text(size=8))+
  scale_y_continuous(limits = c(0, 1))+
theme(aspect.ratio = 0.7)

#Plot the correlation figure
myfilter <- ms_all %>%
  filter(model=="fit" | model=="base")

#Correlation models (baseline and fit) to bimodal data 
ggplot(myfilter, 
       aes(x = pred, y = joint, col = factor(concept_dist), 
           shape = factor(sound_dist))) +
 geom_pointrange(aes(ymin = ci_lower, ymax = ci_upper), 
                  position = position_dodge(width = .1), size=0.2) + 
  geom_abline(slope = 1, lty = 2) +
  facet_grid(.~model)+
theme(aspect.ratio = 0.7)

#The correlation values
base_pred <- subset(myfilter, model=='base')
fit_pred <- subset(myfilter, model=='fit')
r_base <- cor(base_pred$joint,base_pred$pred)
r_base
r_base*r_base
r_fit <- cor(fit_pred$joint,fit_pred$pred)
r_fit
r_fit*r_fit
```

Modality preference
```{r}

#Modality dominance coeficent
a_fit=vrJ_V_nl/vrJ_A_nl
a_base=vrV_nl/vrA_nl
a_Vdom=2*a_base
a_Sdom=0.5*a_base

#Classification thresholds (prob=0.5) for:

##The basline (combination of the unimodal cases)
classif_base = function (x, A=a_base) {
    2*A+2-A*x
}

##Bimodal fit 
classif_fit = function (x, A=a_fit) {
    2*A+2-A*x
}

##A baseline for visual dominance
classif_Vdom = function (x, A=a_Vdom) {
    2*A+2-A*x
}

##A baseline for auditory domiance
classif_Sdom = function (x, A=a_Sdom) {
    2*A+2-A*x
}

Gaus_fit <- data.frame(x=c(rnorm(1000,0,2),rnorm(1000,4,2)),
          y=c(rnorm(1000,0,2),rnorm(1000,4,2)))

#Modality dominance?
ggplot(Gaus_fit, aes(x,y)) +
  stat_function(fun = classif_base, colour = "red", lty=2) +
  stat_function(fun = classif_Vdom, colour = "blue", lty=2 )+
  stat_function(fun = classif_Sdom, colour = "blue", lty=2)+
  stat_function(fun = classif_fit, colour = "black")+
  xlab("Auditory") +ylab("Visual") + scale_x_continuous(limits = c(-6, 10))+
  scale_y_continuous(limits = c(-6, 10))+theme(aspect.ratio = 1)

```

### 2017-02-02 write-up/main.tex
draft new

@@
 
-Identifying the visual referent of a spoken word -- that a particular insect is referred to by the word ``bee'' -- requires both the ability to process and integrate multi-modal input and the ability to identify categories under uncertainty.
+Identifying the visual referent of a spoken word -- that a particular insect is referred to by the word ``bee'' -- requires both the ability to process and integrate multi-modal input and the ability to reason under uncertainty.
 How do these tasks interact with one another?
-We introduce a task that allows us to examine how adults identify word categories under joint uncertainty in the auditory and visual modalities.
-We propose a Bayesian model of the task which provides an optimal baseline.
-Model predictions are tested in two experiments where category recognition is made under two kinds of uncertainty: ambiguity and noise.
-In both cases, the optimal baseline model explains much of the variance in human judgments.
-But when one modality had noise added to it, human perceivers systematically preferred the unperturbed modality to a greater extent than the optimal baseline model did.
+We introduce a task that allows us to examine how adults identify words under joint uncertainty in the auditory and visual modalities.
+We propose a ideal observer model of the task which provides an optimal baseline.
+Model predictions are tested in two experiments where word recognition is made under two kinds of uncertainty: category ambiguity and distorting noise.
+In both cases, the ideal observer model explains much of the variance in human judgments.
+But when one modality had noise added to it, human perceivers systematically preferred the unperturbed modality to a greater extent than the ideal observer model did.
 
@@
 
- % (e.g., the visual modality in the case of concrete objects)
 Language uses symbols expressed in one modality (e.g., the auditory modality, in the case of speech) to communicate about the world, which we perceive through many different sensory modalities.
@@
 Determining reference involves processing the auditory information and linking it with other perceptual signals (e.g., the visual image of the bee, the sound of its wings, the sensation of the bee flying by your arm).
-But processing this linguistic input also requires categorization.
-On the linguistic side,  individual sounds must be identified as members of phonetic categories for the word to be understood.
-On the referential side, individual sensory impressions must be categorized as coming from a bee.
-Once these two sets of category-identification tasks have been completed, then a listener can make the referential link between word and world.
 
-This comprehension task takes place in a noisy world.
-On the auditory side, individual acoustic word tokens are almost always ambiguous with respect to the particular sequence of phonemes they represent \cite<e.g.,>{hillenbrand1995}.
+This multi-modal integration task takes place in a noisy world.
+On the auditory side, individual acoustic word tokens are almost always ambiguous with respect to the particular sequence of phonemes they represent, which is due to the inherent variability of how a phonetic category is realized acoustically \cite<e.g.,>{hillenbrand1995}.
 And some tokens may be distorted additionally by mispronunciation or ambient noise.
@@
 
-Thus, establishing reference requires reasoning under a great deal of uncertainty.
-Work on phoneme categorization has suggested that perceivers encode tokens probabilistically: they base their decisions on these probabilities and adjust their behavior when these probabilities change \cite<e.g.,>{clayard08}.
-However, previous work in this line of research has largely focused on the unimodal case, that is, when category uncertainty is only in one modality \cite<e.g.,>{feldman2009}.
-A few studies have explored some aspects of cross-modal processing  \cite<e.g.,>{bejjanki2011, kleinschmidt2015}.
-This work has focused on the specific case of phoneme recognition from speech and lip movement, however, where information from both modalities is tightly correlated.
+Thus, establishing reference requires reasoning under a great deal of uncertainty in both modalities.
+The goal of this work is to characterize such reasoning.
+Imagine, for example, that someone is uncertain whether they heard ``pea" or ``bee'', does it make them rely more on the visual modality (e.g., the object being pointed at)?
+Vice versa, if they are not sure if they saw a bee or a fly, does that make them rely more on the auditory modality (i.e., the label)?
+More importantly, when input in both modalities is uncertain to varying degrees, do they weight each modality according to its relative reliability, or do they over-rely on a particular modality?
 
-In the present work, we study the case of word recognition, where a word is an \textit{arbitrary} mapping between a sound category and a visual category.
-We test participants on their ability to process audio-visual stimuli and use them to recognize the underlying word category.
-Crucially, this recognition is made under uncertainty about both the auditory category (a single phoneme, in our case) and the visual category (the concept being referred to).
-Our goal is to explore how adults deal with such multimodal ambiguity in a categorization task.
-To this end, we propose a model that combines uncertainty in an optimal way, and we use it as a baseline for interpreting human data.
-More precisely, we examine the extent to which human data conform to, or deviate from the baseline, and whether the deviation involves a systematic preference for a particular modality.
+In this paper, we propose a probabilistic framework where such reasoning can be expressed in a precise way.
+We characterize uncertainty, in each modality, with a probability distribution, and we predict ideal responses by combining these probabilities in a optimal way.
+Our work can be seen as an extension to previous Bayesian models of phoneme identification \cite<e.g.,>{feldman2009}, where, instead of a unimodal input, we model a bimodal one.
+A few studies have explored some aspects of audio-visual processing in a probabilistic framework  \cite<e.g.,>{bejjanki2011, kleinschmidt2015}.
+In these studies, the researchers focused on the specific case of phoneme recognition from speech and lip movement, however, where information from both modalities is tightly correlated.
+
+In the present work, we study, rather, the case of arbitrary mapping between sounds and visual objects.
+We test participants on their ability to process audio-visual stimuli and use them to recognize the underlying word.
+More precisely we study the case where both the word's form and the word's referent are ambiguous, and we examine the extent to which humans conform to, or deviate from the predictions of the ideal observer model.
+Moreover, since some previous studies on audio-visual processing documented cases of modality preference (i.e., when people rely predominantly on the visual modality \cite<e.g., >{colavita74} or the auditory modality \cite<e.g., >{sloutsky2003}), we will  explore if, in our task as well, people show evidence of a modality preference.
 
 The paper is organized as follows.
-First, we introduce our audio-visual word recognition task.
-We next present the model and explain how it provides an optimal baseline.
-Then we present two behavioral experiments where we test category recognition under audio-visual uncertainty.
-In Experiment 1, audio-visual tokens are clear but their category membership is ambiguous.
-In Experiment 2, we intervene by adding additional perceptual noise to one modality.
-While participants show no modality preference in Experiment 1, in Experiment 2 they over-rely on visual input when the auditory modality is noisy.
+First, we introduce our audio-visual recognition task.
+We next present the ideal observer model.
+Then we present two behavioral experiments where we test word recognition under audio-visual uncertainty.
+In Experiment 1, audio-visual tokens are ambiguous with respect to their category membership.
+In Experiment 2, we intervene by adding  noise to one modality.
+In both experiments participants show qualitative patterns of optimal behaviour.
+Moreover, while participants show no modality preference in Experiment 1, in Experiment 2 they over-rely on visual input when the auditory modality is noisy.
 
@@
 
-We introduce a new task that tests audio-visual category recognition.
+We introduce a new task that tests audio-visual word recognition.
 We use two visual categories (cat and dog) and two auditory categories (/b/ and /d/ embedded in the minimal pair /aba/-/ada/).
@@
 The test stimulus may differ from the target in both the auditory and the visual components.
-The auditory component is sampled from a continuum along the second formant (F2) linking the words /aba/ and /ada/.
-The visual component is sampled from a morph that links the prototypical pictures of the dog and the cat.
 After these two presentations, participants are instructed to press ``same'' or ``different.''
@@
 However, unlike this previous line of research, here participants are not asked whether the two audio-visual presentations are identical.
-Instead, the task is category-based: They are asked to press `same' if they think the second item (the test) belonged to the same category as the first (e.g.,  dog-/aba/), even if there is a slight difference in the word, in the object, or in both.
+Instead, the task is category-based: They are asked to press `same' if they think the second item (the test) belonged to the same category as the first (target) (e.g.,  dog-/aba/), even if there is a slight difference in the word, in the object, or in both.
 They are instructed to press `different' only if they think that the second stimulus was an instance of the other word category (cat-/ada/).
@@
 The task also included trials where pictures were hidden (audio-only) or where sounds were muted (visual-only).
-These unimodal trials provide us with participants' categorization functions for the auditory and visual categories and are used as inputs to the optimal model, described below.
+These unimodal trials provide us with participants' categorization functions for the auditory and visual categories and are used as inputs to the ideal observer model, described below.
 
@@
 In each modality, we have two categories: /ada/ ($A=1$) and /aba/ ($A=2$) in the auditory dimension, and \textit{cat} ($V=1$) and \textit{dog} ($V=2$) in the visual dimension.
-% \footnote{The identity of the categories was randomized in the experimental setup.}
 We assume, for the sake of simplicity, that the probability of membership in each category is normally distributed:
@@
 In the bimodal condition, participants see word tokens with audio-visual input, and have to make a categorization decision.
-We represent word tokens as vectors in the audio-visual space, $\mathbf{w}=(a,v)$.
+We define word tokens as vectors in the audio-visual space, $\mathbf{w}=(a,v)$.
 A word category $W$ is defined as the joint distribution of auditory and visual categories. It can be characterized with a bivariate normal distribution in the audio-visual space:
@@
 We have two word categories: dog-/aba/ ($W_1$) and cat-/ada/ ($W_2$).
-Participants can be understood as choosing one of these two word categories (figure \ref{fig:space}).
-For an ideal ``recognizer'', the probability of choosing category 2 when presented with an audio-visual instance $\mathbf{w}=(a,v)$ is the posterior probability of this category:
+Participants can be understood as choosing one of these two word categories (Figure \ref{fig:space}).
+For an ideal observer, the probability of choosing category 2 when presented with an audio-visual instance $\mathbf{w}=(a,v)$ is the posterior probability of this category:
 
@@
 
-In sum, the posterior \ref{eq:pred} provides a baseline for how probabilities that characterize uncertainty in each modality can be combined to make categorical decision about bimodal input.
+In sum, the posterior \ref{eq:pred} provides the predictions of ideal observer for how probabilities that characterize uncertainty in each modality can be combined to make categorical decision about bimodal input.
 
@@
 
-In experiment 1, we test the predictions of the model in the case where uncertainty is due to perceptual ambiguity in terms of category membership.
-This experiment had two goals.
-First, we wanted to examine the extent to which human responses corresponded to the predictions of the ideal observer model.
-Second, if there was a deviation from the baseline, we wanted to be able to measure whether this deviation involved a systematic preference for a particular modality.
+In Experiment 1, we test the predictions of the model in the case where uncertainty is due to similar auditory categories, and similar visual categories.
+Crucially, the similarity is such that the distributions overlap.
+To simulate such uncertainty in a controlled fashion, we use a continuum along the second formant (F2) linking the words /aba/ and /ada/, and we use a morph that links the prototypical pictures of the dog and the cat.
 
@@
 For visual stimuli, we used a morph continuum introduced in \citeA{freedman2001}: a continuous set of images was generated from three cat prototypes and three dog prototypes.
-From the original 14 points, we selected 5 points as follows: we kept the item that seemed most ambiguous (point 8), the 2 preceding points (i.e., 7 and 6) and the 2 following points (i.e., 8 and 9).
-The 6 and 9 points along the morph were quite distinguishable, and we took them to be our prototypes.
+From the original 14 points, we selected 5 points as follows: we kept the item that seemed most ambiguous (point 8), the 2 preceding points (i.e., 7 and 6) and the 2 following points (i.e., 9 and 10).
+The 6 and 10 points along the morph were quite distinguishable, and we took them to be our prototypes.
 
@@
 The second sound-object pair (the test) followed on the other side of the screen after 500ms and varied in its category membership.
-For both the target and the test, visual stimuli were present for the duration of hte sound clip ($\sim$800ms).
+For both the target and the test, visual stimuli were present for the duration of the sound clip ($\sim$800ms).
 We instructed participants to press ``S'' for same if they thought the alien was naming another dog-/aba/, and ``D'' for different if they thought the alien was naming a cat-/ada/.
@@
 % \caption{Human responses vs.
-the baseline predictions.
+the ideal observer predictions.
 Error bars are 95\% confidence intervals.
-In experiment 1, the baseline and the fit explained 89\%, and 94\% of total variance, respectively.
-In experiment 2, the baseline and the fit explained 91\%, and 97\% of total variance, respectively}
+In experiment 1, the ideal observer and the fit explained 89\%, and 94\% of total variance, respectively.
+In experiment 2, the ideal observer and the fit explained 91\%, and 97\% of total variance, respectively}
 % \label{fig:corr}
@@
 \caption{Proportion of ``different'' judgments as a function of auditory distance.
-Solid lines represent average human responses (left), predictions of the baseline (middle), and the bimodal fit (left).
+Solid lines represent average human responses (left), predictions of the ideal observer (middle), and the bimodal fit (left).
 Dashed lines represent average human responses in the unimodal conditions.
@@
 % Let's take the auditory-only case as an example,
-\subsubsection{Unimodal conditions}
-
+\subsubsection{Unimodal conditions} this is the case where the pictures were hidden, or where the sounds were muted.
 Average categorization judgments and fits are shown in Figure \ref{fig:unimodal}.
 Auditory judgements were somewhat sharper and more pronounced than visual judgments.
-For an ideal recognizer, the probability of choosing category 2 (that is, to answer ``different'') when presented with e.g., an audio instance $a$, is the posterior probability of this category $p(A_2|a)$.
+The fit was done as follows.
+For an ideal recognizer, the probability of choosing category 2 (that is, to answer ``different'') when presented with an audio instance $a$, is the posterior probability of this category $p(A_2|a)$.
 If we assume that both categories have equal variances, the posterior probability reduces to:
@@
 To determine the values of the bias and the variance, we fit a model for each modality, collapsed across participants.
-For the auditory modality, we got $\epsilon_A=-0.20$ and $\sigma^2_A=2.04$.
-For the visual modality, we got $\epsilon_V=-0.11$ and $\sigma^2_V=3.34$.
-% In figure \ref{fig:unimodal} (top) we plotted responses in the unimodal conditions as well as the unimodal fits.
+For the auditory modality, we obtained $\epsilon_A=-0.20$ and $\sigma^2_A=2.04$.
+For the visual modality, we obtained $\epsilon_V=-0.11$ and $\sigma^2_V=3.34$.
 
 \subsubsection{Bimodal condition}
+We fit a model to human responses in the bimodal condition, collapsed across participants, finding $\epsilon=-0.32$, $\sigma^2_{Ab}=5.00$ and $\sigma^2_{Vb}=7.27$.
+The fit explained XX of the variance.
 
-We fit a model to human responses in the bimodal condition, collapsed across participants, finding $\epsilon=-0.32$, $\sigma^2_{Ab}=5.00$ and $\sigma^2_{Vb}=7.27$.
+\subsubsection{Ideal observer model}
 
-\subsubsection{Baseline model}
-
-We derived the predictions of the baseline model by using the values of the variances derived from the unimodal conditions, and the response bias derived from the bimodal condition, and by substituting these values into the expression of the posterior in Eq.~\ref{eq:pred}.
-Figure \ref{fig:Exp} shows participants' responses in the bimodal condition (left), as well as the prediction of the baseline (middle), and the bimodal fit models (right).
-% Correlation of human data and the bimodal baseline/fitted model are shown in Figure \ref{fig:corr} (top).
+We derived the predictions of the ideal observer model by using the values of the variances derived from the unimodal conditions, and the response bias derived from the bimodal condition, and by substituting these values into the expression of the posterior in Eq.~\ref{eq:pred}.
+Figure \ref{fig:Exp} shows participants' responses in the bimodal condition (left), as well as the prediction of the ideal observer (middle), and the bimodal fit models (right).
 
@@
 
-We found negative values for in all response bias terms, which suggests a general bias toward answering ``different.''  This bias is probably due to the categorical nature of the task: when two items are ambiguous but perceptually different, this could cause a slight preference for ``different'' over ``same.''
+We found negative values in all response bias terms, which suggests a general bias toward answering ``different.''  This bias is probably due to the categorical nature of our same-different task: when two items are ambiguous but perceptually different, this could cause a slight preference for ``different'' over ``same''.
 
@@
 We next analyzed whether there was a preference for one or the other modality when making decisions in the bimodal condition, beyond that explained by the variance in categories implied by the unimodal responses.
-This preference would manifest as a deviation from the decision threshold predicted by the baseline model.
+This preference would manifest as a deviation from the decision threshold predicted by the ideal observer model.
 The decision threshold is defined as the set of values in the audio-visual space along which the posterior (Eq.~\ref{eq:pred}) is equal to 0.5.
 The decision threshold takes the following form:
-% As illustrated in \ref{fig:space}, above this line participants are more likely to choose one word category, and below this line, they are more likely to choose the other word category.
 
@@
 
-If the slope derived from the fit is bigger than the slope of the baseline, this finding would suggest a general preference for the auditory modality (similarly, a smaller slope would suggest a preference for the visual modality).
+If the slope derived from the bimodal fit is greater than the slope of the ideal observer, this finding would suggest a general preference for the auditory modality (similarly, a smaller slope would suggest a preference for the visual modality).
 The limit cases are when there is exclusive reliance on the auditory cue (a vertical line), and where there is exclusive reliance on the visual (a horizontal line).
-Figure \ref{fig:pref} (top left) shows the decision threshold in the audio-visual space with a constant intercept; the fit to human data  (solid black line) was very close to the baseline threshold (red line).
-Non-parametric resampling sampling of the data showed no evidence of a deviation from the baseline (\ref{fig:pref}, bottom left).
+Figure \ref{fig:pref} (top left) shows the decision threshold in the audio-visual space with a constant intercept; the fit to human data  (solid black line) was very close to the ideal observer threshold (red line).
+Non-parametric resampling of the data showed no evidence of a deviation from the slope of the ideal observer (\ref{fig:pref}, bottom left).
 
@@
 
-% Compare human responses (figure \ref{fig:Exp}, top left) to the baseline (figure \ref{fig:Exp}, top middle).
-Qualitatively, participants' judgments were similar to the predictions of the optimal baseline model (when fit to the unimodal data).
-Consider the contrast between the auditory-only case (dashed black line in Figure \ref{fig:Exp}, top left) and the bimodal case (solid colored lines).
+Qualitatively, participants' judgments were similar to the predictions of the ideal observer model (remember that the latter was obtained by optimally combining fits to the unimodal data).
+Consider, for example, the contrast between the auditory-only case (dashed black line in Figure \ref{fig:Exp}, top left) and the bimodal case (solid colored lines).
 Higher certainty in the visual modality generally influenced responses, with greater visual distance leading to more ``different'' ratings and less visual distance leading to more ``same'' ratings.
-Indeed, we found that the baseline model explained almost 90\% of the variance in judgments ($r^2=0.89$).
-In addition, as described above, we did not see any evidence for a modality preference.
+Similar observations can be made about the contrast between the visual-only case and the bimodal case.
+Overall, we found that the ideal observer model explained almost 90\% of the variance in judgments ($r^2=0.89$).
 
-But although we see a qualitative resemblance data and baseline model, there were quantitative differences.
-Model predictions were more influenced by the visual modality at the auditory midpoint (the point of highest uncertainty) than human judgements, and were more compressed at the endpoints (the points of lowest uncertainty).
-Formally speaking, this trend translated into an increase in the value of the variance associated with each modality (e.g., compare the variance values in the baseline model to the values derived from the bimodal fit).
-Since the variance characterizes the reliability of a given cue, it seems as if bimodal presentation caused reliance on both modalities to decrease.
-This effect could possibly be attributed to the arbitrary nature of the form-meaning mapping.
-In fact, previous studies suggest that while redundant multi-modal information improves performance (e.g., determining the frequency of a bouncing ball from visual and auditory cues), arbitrary mappings generally tends to hinder performance \citeA<for review, see>{robinson2010}.
+But although we see a qualitative resemblance between human data and the ideal observer model, there were quantitative differences.
+For example, model predictions were more influenced by the visual modality at the auditory midpoint (the point of highest uncertainty) than human judgements, and were more compressed at the endpoints (the points of lowest uncertainty).
+
+Formally speaking, there was an increase in the value of the variance associated with each modality.
+More precisely, whereas the ideal observer model predicted the weights to be proportional to $1/\sigma^2_{A}$ and $1/\sigma^2_{V}$, for the auditory and the visual modalities, respectively (see expression \ref{eq:pred}), the fit to human data suggested that the real weights were proportional to $1/\sigma^2_{Ab}$ and $1/\sigma^2_{Vb}$.
+Interestingly, our analysis of modality preference showed that the relative values of these variances (i.e., $\frac{\sigma^2_V}{\sigma^2_A}$ vs.
+$\frac{\sigma^2_{Vb}}{\sigma^2_{Ab}}$) were almost the same (Figure \ref{fig:pref}, left).
+This means two things: 1) the bimodal presentation caused reliance on both modalities to decrease, and 2) this decrease did not affect the relative weighting of both modalities, i.e., participants were weighting modalities according to their relative reliability.
+The latter explains the qualitative resemblance between the predictions of the ideal observer and human data, and the former explains the quantitative discrepancy.
+\newline
+
+In Experiment 1, we tested the ability of people to recognize a a word under audio-visual uncertainty linked to category membership.
+We found that, generally speaking, participants followed the ideal observer model in that they weighted modalities according to their relative reliability.
+In real life situations, however, tokens can undergo distortions due to noisy factors in the environment.
+In Experiment 2, we try to account for this additional level of uncertainty.
 
@@
 
-In Experiment 1, we tested the ability of people to recognize a word category under ambiguous tokens.
-In particular, the tokens were clear but their category membership was uncertain.
-In real life situations, however, even the identity of the token can be uncertain due to various distorting factors.
-In order to account for this kind of uncertainty in the auditory modality, we can imagine \cite<following>{feldman2009}, that the speaker generates a target production $t$ from an auditory category
+Imagine that the speaker generates a target production $t$ from an auditory category
 $t | A \sim N(\mu_{A}, \sigma^2_{A})$.
-The listener, in a noisy condition, does not hear exactly this produced target, but the target perturbed by normally distributed noise: $a | t \sim N(t, \sigma^2_{N})$.
+In Experiment 1, we assumed that the observed could directly retrieve this production token.
+But if the observer is in a noisy environment, they do not hear exactly this produced target, but the target perturbed by noise, which we assume, following \citeA{feldman2009}, that it is normally distributed: $a | t \sim N(t, \sigma^2_{N})$.
 When we integrate over $t$, we get:
@@
 
-In Experiment 2, we explored the effect of noise on performance in our task.
+In this experiment, we explored the effect of this added noise\footnote{Note that we are considering environmental noise, which is different from the noise inherent to perception.} on performance in our task.
 We tested a case where one modality was ambiguous and noisy (auditory), and where the other modality was ambiguous but not noisy (visual).
-We were interested to know if participants would treat this new source of uncertainty as predicted by the optimal baseline, and whether noise in one modality would lead to some systematic preference for the non-noisy modality.
+We were interested to know if participants would treat this new source of uncertainty as predicted by the ideal observer model, and whether noise in one modality would lead to some systematic preference for the non-noisy modality.
 
@@
 We used the same visual stimuli as in Experiment 1.
-We also used the same auditory stimuli , but we convolved each item with Brown noise of amplitude 1 using the audio editor Audacity (2.1.2).
-The procedure was exactly the same as in the previous experiment, except that target stimuli were presented with the new noisy auditory stimuli.
+We also used the same auditory stimuli, but we convolved each item with Brown noise of amplitude 1 using the audio editor Audacity (2.1.2).
+The signal-to-noise ratio was XXX dB.
+The procedure was exactly the same as in the previous experiment, except that test stimuli were presented with the new noisy auditory stimuli.
 
@@
 
-\subsubsection{Baseline model}
+\subsubsection{ideal observer model}
 
-We generated the predictions of the baseline model by using the values of the variances derived from the unimodal conditions, and the response bias derived from the bimodal condition, and by plugging these values into Eq.~\ref{eq:pred}.
+We generated the predictions of the ideal observer model by using the values of the variances derived from the unimodal conditions, and the response bias derived from the bimodal condition, and by substituting these values into the expression of the posterior in Eq.~\ref{eq:pred}.
 Results are shown in Figure \ref{fig:Exp} (bottom).
- % Correlation of human data to the bimodal baseline and the fit are shown in figure \ref{fig:corr} (bottom).
+
+\subsubsection{Modality preferences}
+
+Participants' decision threshold suggested a preference for the visual modality (the non-noisy modality).
+Indeed non-parametric resampling of the data showed there to be a decrease in the value of the slope (\ref{fig:pref}, right).
 
@@
 \caption{Top: decision thresholds in the audio-visual space.
-Red dotted line is the prediction of the baseline.
-Blue dotted lines are cases where modality preference is twice as strong as the baseline.
+Red dotted line is the prediction of the ideal observer.
+Blue dotted lines are cases where modality preference is twice as strong as the ideal observer.
 Solid line is the threshold derived from human data.
-Bottom: comparison of the threshold slope between the baseline and the fit to human data.
+Bottom: comparison of the threshold slope between the ideal observer and the fit to human data.
 Error bars are 95\% confidence intervals computed through non-parametric bootstrap sampling (10.000 samples)}
@@
 
-We found, similar to experiment 1, that participants generally showed qualitative patterns similar to the baseline model ($r^2 = .91$).
-But we also found a similar discrepancy at the quantitative level: There was a decrease in the reliability of both modalities, as could be inferred from the increase in the variance associated with the auditory modality and the visual modality in the bimodal fit.
-An interesting difference with Experiment 1, however, was that participants' decision threshold suggested a preference for the visual modality (the non-noisy modality).
-Indeed non-parametric bootstrap sampling over the data showed there to be a significant decrease in the value of the slope.
+We found, similar to Experiment 1, that participants generally showed qualitative patterns similar to the ideal observer model ($r^2 = .91$).
+But we also found a similar discrepancy at the quantitative level, suggesting an effect of bimodal presentation on performance.
+Formally speaking, the ideal observer model predicted the modality weights to be proportional to $1/(\sigma^2_{A}+\sigma^2_{N})$ and $1/\sigma^2_{V}$, for the auditory and the visual modalities, respectively.
+The fit to human data suggested that the empirical weights were proportional to $1/\sigma^2_{Ab}$ and $1/\sigma^2_{Vb}$.
+An interesting difference with Experiment 1, however, was that participants had a clear preference for the non-noisy modality, as the values of the relative variances $\frac{\sigma^2_V}{\sigma^2_A + \sigma^2_N}$ vs.
+$\frac{\sigma^2_{Vb}}{\sigma^2_{Ab}}$ were different (\ref{fig:pref}, right).
+This preference affected the relative weighting, where, contrary to Experiment 1, the visual modality now has a greater weight than what could be expected from the relative reliability alone.
 
-\section{Conclusion}
+It is important to understand that this preference was not the mere consequence of the added noise increasing the variance of the auditory modality, since this increase was already accounted for in the ideal observer model.
+The preference was, rather, a form of over-reliance on the visual modality.
 
-In this work, we tested word category recognition under audio-visual uncertainty.
-We modeled uncertainty as a probability distribution over tokens from auditory and visual continua.
-Our baseline model instantiated an ideal observer, optimally combining participant data from unimodal decisions.
-The model's predictions were examined in two experiments where we tested two kinds of uncertainty: in experiment 1, audio-visual tokens were clear but their category membership was ambiguous.
-In experiment 2, input to one modality was ambiguous, and input to the other was ambiguous as well as noisy.
-In both experiments, the ideal observer model explained the majority of variance in participant judgments.
-In both experiments, however, we found that bimodal presentation caused the reliability of both modalities to decrease relative to the ideal observer.
+\section{General discussion}
 
-We explored whether part of the unexplained variance could involve to a systematic preference for a given modality.
-Our analysis showed no evidence of such modality preference in experiment 1.
-However, we found a preference for the non-noisy modality in experiment 2.
+Understanding language requires both the ability to integrate multi-modal input, and the ability to deal with uncertainty.
+In this work, we explored a case where both abilities were at play.
+We studied the case of identifying a word when both its form (auditory) and its referent (visual) were ambiguous with respect to their category membership (Experiment 1), and when the form was perturbed with additional noise (Experiment 2).
+We introduced a model that instantiated an ideal observer, predicting how information from each modality could be combined in an optimal way.
+In both experiments, participants showed the qualitative patterns of the ideal observer.
 
-This paper addressed the problem of recognizing words whose underlying phonemic and semantic categories were supposed to be familiar.
-An intriguing challenge is to understand how these underlying categories are acquired in the first place.
-Previous developmental work addressed cases when one modality was supposed to provide a stable and certain cue to the other modality \cite<e.g.,>{waxman1995, yeung09}.
-The present paper invites investigations on category acquisition in the more general case where there is uncertainty in both modalities.
+There were, however, quantitative differences: the audio-visual presentation caused the reliance on both modalities to decrease to a lower extent than the ideal observer model expected.
+This phenomenon could be attributed to the arbitrary nature of the form-meaning mapping.
+Previous studies suggest, indeed, that while redundant multi-modal information improves performance (e.g., determining the frequency of a bouncing ball from visual and auditory cues), arbitrary mappings generally tends to hinder performance \cite<for review, see>{robinson2010}.
+Another possibility could be that the ideal model failed to capture some other features of multi-modal integration.
+Further work is needed to understand this result.
+
+Interestingly, however, in Experiment 1 this decrease in reliance (or the increase in variance) occurred at a similar rate for both the auditory and the visual modality, and thus, it did not affect their relative weighting.
+The latter was primarily determined by informational reliability.
+Only when we intervened by adding  noise to one modality in Experiment 2, did participants show a systematic preference for the non-noisy modality.
+One possible explanation for this preference could be that people do not combine cross-modal uncertainties of a similar kind (e.g., category ambiguity in both modalities) in the same way they would combine uncertainties of different kinds (e.g., category ambiguity in one modality and noise in the other).
+Further work is needed to determine the extent to which this is the case.
+
+Overall, in both Experiments, the majority of the variance (around 90\%) could be explained by an ideal observer that combined multi-modal information in an optimal way.
+In the light of this main results, we can revisit some previous findings in the literature.
+For instance, \citeA{sloutsky2003} reported a dominance for the auditory modality in children.
+This dominance disappear or reverses in adults.
+Could this developmental difference be driven by changes in the intrinsic relative reliability of modalities?
+More work is needed to carefully examine this (and other) speculations, and more generally, to determine the extent to which the optimal combination account helps us better understand the mechanisms of word precessing and learning.
+
+%However, is it the case that children weight modalities differently because a sound is inherently more salient than any visual contrast?
+or could part of this effect stem from the fact that the precise sound and visual contrasts used as stimuli differ in their relative salience to children?
+In particular, what happens if the sound contrast is reduced to a perceptual minimum and when the visual contrast is enhanced?
+Can we reverse the weighting in this case as our optimal combination account would suggest?
+Moreover, could the developmental difference be driven by changes in the relative reliability of modalities?
+
+%In a different line of work, it has been shown that infants have difficulties mapping minimally different words to two novel objects, despite the fact that they can perceptually differentiate these words \cite<e.g.,>{stager1997}.
+Is it possible that what had been interpreted as `failure' in learning could, at least to some extent, be explained by a categorical decision (similar to what adults performed in our task).
+More precisely, it is possible that the visual stimuli were quite similar in the children’s early conceptual space, which made them believe that both objects were possible instances of the same semantic category.
+This, in turn, would make them interpret the sound difference as alternative pronunciations of the same word.
+In particular, what happens if the object contrast is maximized?
+More work is needed to carefully examine these (and other) speculations, and more generally, to determine the extent to which the optimal combination account helps us better understand the mechanisms of word precessing and learning.
 

### 2017-02-02 write-up/main.tex
text tweaks, length

@@
 Perhaps the speaker was yelling ``pea" and not ``bee.'' Similarly, a sensory impression may not be enough to make a definitive identification of a visual category.\footnote{In the general case, language can of course be visual as well as auditory, and object identification can be done through many modalities.
-For simplicity, we focus on audio-visual matching here.} Perhaps the quickly flying insect was a beetle or a fly instead.
+For simplicity, we focus on audio-visual matching here.} Perhaps the insect was a beetle or a fly instead.
 
@@
 
-In this paper, we propose a probabilistic framework where such reasoning can be expressed in a precise way.
-We characterize uncertainty, in each modality, with a probability distribution, and we predict ideal responses by combining these probabilities in a optimal way.
+In this paper, we propose a probabilistic framework where such reasoning can be expressed precisely.
+We characterize uncertainty in each modality with a probability distribution, and we predict ideal responses by combining these probabilities in a optimal way.
 Our work can be seen as an extension to previous Bayesian models of phoneme identification \cite<e.g.,>{feldman2009}, where, instead of a unimodal input, we model a bimodal one.
-A few studies have explored some aspects of audio-visual processing in a probabilistic framework  \cite<e.g.,>{bejjanki2011, kleinschmidt2015}.
-In these studies, the researchers focused on the specific case of phoneme recognition from speech and lip movement, however, where information from both modalities is tightly correlated.
+A few studies have explored some aspects of audio-visual processing in a probabilistic framework  \cite{bejjanki2011, kleinschmidt2015}.
+In these studies, the researchers focused on the specific case of phoneme recognition from speech and lip movement, however, where information is tightly correlated across modalities.
 
@@
 More precisely we study the case where both the word's form and the word's referent are ambiguous, and we examine the extent to which humans conform to, or deviate from the predictions of the ideal observer model.
-Moreover, since some previous studies on audio-visual processing documented cases of modality preference (i.e., when people rely predominantly on the visual modality \cite<e.g., >{colavita74} or the auditory modality \cite<e.g., >{sloutsky2003}), we will  explore if, in our task as well, people show evidence of a modality preference.
+Moreover, some previous studies on audio-visual processing documented cases of modality preference, when people rely predominantly on the visual modality \cite<e.g., >{colavita1974} or the auditory modality \cite<e.g., >{sloutsky2003}.
+Thus, we will explore if participants in our task show evidence of a modality preference.
 
@@
 In Experiment 2, we intervene by adding  noise to one modality.
-In both experiments participants show qualitative patterns of optimal behaviour.
+In both experiments participants show qualitative patterns of optimal behavior.
 Moreover, while participants show no modality preference in Experiment 1, in Experiment 2 they over-rely on visual input when the auditory modality is noisy.
@@
 The test stimulus may differ from the target in both the auditory and the visual components.
-After these two presentations, participants are instructed to press ``same'' or ``different.''
+After these two presentations, participants press ``same'' or ``different.''
 
@@
 We define word tokens as vectors in the audio-visual space, $\mathbf{w}=(a,v)$.
-A word category $W$ is defined as the joint distribution of auditory and visual categories. It can be characterized with a bivariate normal distribution in the audio-visual space:
+A word category $W$ is defined as the joint distribution of auditory and visual categories. It can be characterized with a bivariate normal distribution:
 $$ p(\mathbf{w} | W) \sim  N(M_W, \Sigma_W) $$
@@
 
-We make the assumption that, given a particular word category, the auditory and visual tokens are independently generated:
+We make the assumption that, given a particular word category, the auditory and visual tokens are independent:
 
@@
 
- with $\beta_a=\frac{\mu_{A1}-\mu_{A2}}{\sigma^2_{A}}$,
+\noindent with $\beta_a=\frac{\mu_{A1}-\mu_{A2}}{\sigma^2_{A}}$,
 $\beta_v=\frac{\mu_{V1}-\mu_{V2}}{\sigma^2_{V}}$,
 $\beta_0=\frac{\mu^2_{A2}-\mu^2_{A1}}{2\sigma^2_{A}}+\frac{\mu^2_{V2}-\mu^2_{V1}}{2\sigma^2_{V}}$
-
 and $1+\epsilon=\frac{p(W_1)}{p(W_2)}$ is the proportion of the prior probabilities.
@@
 Crucially, the similarity is such that the distributions overlap.
-To simulate such uncertainty in a controlled fashion, we use a continuum along the second formant (F2) linking the words /aba/ and /ada/, and we use a morph that links the prototypical pictures of the dog and the cat.
+To simulate such uncertainty in a controlled fashion, we use a continuum along the second formant (F2) linking the words /aba/ and /ada/, and we use a morph that links dogs and cats.
 
@@
 There were a total of 25 possible combinations in the bimodal condition, and 5 in each of the unimodal conditions.
-Each participant saw each possible trial in each condition twice, for a total of 70 trials/participants.
+Each participant saw each possible trial twice, for a total of 70 trials/participant.
 Trials were blocked by condition and blocks were presented in random order.
@@
 \centering
-\includegraphics[width=3.25in\textwidth]{unimodal.png}
+\includegraphics[width=3.25in]{unimodal.png}
 \caption{Average human responses in the auditory-only condition (left), and visual-only condition (right). Error bars are 95\% confidence intervals. Solid lines represent unimodal logistic fits.}
@@
 
-with $\beta_a=\frac{\mu_{A_1}-\mu_{A_2}}{\sigma^2_{A}}$ and  $\beta_{a0}=\frac{\mu^2_{A_2}-\mu^2_{A_1}}{2\sigma^2_{A}}$. $\epsilon_A$ is the response bias in the auditory-only trials.
+\noindent with $\beta_a=\frac{\mu_{A_1}-\mu_{A_2}}{\sigma^2_{A}}$ and  $\beta_{a0}=\frac{\mu^2_{A_2}-\mu^2_{A_1}}{2\sigma^2_{A}}$. $\epsilon_A$ is the response bias in the auditory-only trials.
 
@@
 Similar observations can be made about the contrast between the visual-only case and the bimodal case.
-Overall, we found that the ideal observer model explained almost 90\% of the variance in judgments ($r^2=0.89$).
 
-But although we see a qualitative resemblance between human data and the ideal observer model, there were quantitative differences.
+Overall, we found that the ideal observer model explained much of the variance in judgments ($r^2=0.89$).
+But although we see a qualitative resemblance between human data and the model, there were quantitative differences.
 For example, model predictions were more influenced by the visual modality at the auditory midpoint (the point of highest uncertainty) than human judgements, and were more compressed at the endpoints (the points of lowest uncertainty).
 
-Formally speaking, there was an increase in the value of the variance associated with each modality.
-More precisely, whereas the ideal observer model predicted the weights to be proportional to $1/\sigma^2_{A}$ and $1/\sigma^2_{V}$, for the auditory and the visual modalities, respectively (see expression \ref{eq:pred}), the fit to human data suggested that the real weights were proportional to $1/\sigma^2_{Ab}$ and $1/\sigma^2_{Vb}$.
-Interestingly, our analysis of modality preference showed that the relative values of these variances (i.e., $\frac{\sigma^2_V}{\sigma^2_A}$ vs.
-$\frac{\sigma^2_{Vb}}{\sigma^2_{Ab}}$) were almost the same (Figure \ref{fig:pref}, left).
-This means two things: 1) the bimodal presentation caused reliance on both modalities to decrease, and 2) this decrease did not affect the relative weighting of both modalities, i.e., participants were weighting modalities according to their relative reliability.
+Formally, there was an increase in the value of the variance associated with each modality.
+Whereas the ideal observer model predicted the weights to be proportional to $1/\sigma^2_{A}$ and $1/\sigma^2_{V}$, for the auditory and the visual modalities, respectively (see expression \ref{eq:pred}), the fit to human data suggested that the real weights were proportional to $1/\sigma^2_{Ab}$ and $1/\sigma^2_{Vb}$.
+Our analysis of modality preference showed that the relative values of these variances were almost the same (Figure \ref{fig:pref}, left).
+Thus, 1) the bimodal presentation caused reliance on both modalities to decrease, and 2) this decrease did not affect the relative weighting of both modalities, i.e., participants were weighting modalities according to their relative reliability.
 The latter explains the qualitative resemblance between the predictions of the ideal observer and human data, and the former explains the quantitative discrepancy.
-\newline
 
-In Experiment 1, we tested the ability of people to recognize a a word under audio-visual uncertainty linked to category membership.
-We found that, generally speaking, participants followed the ideal observer model in that they weighted modalities according to their relative reliability.
-In real life situations, however, tokens can undergo distortions due to noisy factors in the environment.
-In Experiment 2, we try to account for this additional level of uncertainty.
+% (i.e., $\frac{\sigma^2_V}{\sigma^2_A}$ vs. $\frac{\sigma^2_{Vb}}{\sigma^2_{Ab}}$)
+
+In sum, we found that participants followed the ideal observer model in that they weighted modalities according to their reliabilities.
+In real life, however, tokens can undergo distortions due to noisy factors in the environment.
+In Experiment 2, we explore this additional level of uncertainty.
 
@@
 Participants' decision threshold suggested a preference for the visual modality (the non-noisy modality).
-Indeed non-parametric resampling of the data showed there to be a decrease in the value of the slope (\ref{fig:pref}, right).
+Indeed non-parametric resampling of the data showed a decrease in the value of the slope (\ref{fig:pref}, right).
 
-\subsubsection{Discussion}
+\subsection{Discussion}
 
@@
 Bottom: comparison of the threshold slope between the ideal observer and the fit to human data.
-Error bars are 95\% confidence intervals computed through non-parametric bootstrap sampling (10.000 samples)}
+Error bars are 95\% confidence intervals computed via non-parametric bootstrap.}
 \label{fig:pref}
@@
 We found, similar to Experiment 1, that participants generally showed qualitative patterns similar to the ideal observer model ($r^2 = .91$).
-But we also found a similar discrepancy at the quantitative level, suggesting an effect of bimodal presentation on performance.
-Formally speaking, the ideal observer model predicted the modality weights to be proportional to $1/(\sigma^2_{A}+\sigma^2_{N})$ and $1/\sigma^2_{V}$, for the auditory and the visual modalities, respectively.
+But we also found a similar discrepancy at the quantitative level.
+The ideal observer model predicted the modality weights to be proportional to $1/(\sigma^2_{A}+\sigma^2_{N})$ and $1/\sigma^2_{V}$, for the auditory and the visual modalities, respectively.
 The fit to human data suggested that the empirical weights were proportional to $1/\sigma^2_{Ab}$ and $1/\sigma^2_{Vb}$.
-An interesting difference with Experiment 1, however, was that participants had a clear preference for the non-noisy modality, as the values of the relative variances $\frac{\sigma^2_V}{\sigma^2_A + \sigma^2_N}$ vs.
-$\frac{\sigma^2_{Vb}}{\sigma^2_{Ab}}$ were different (\ref{fig:pref}, right).
-This preference affected the relative weighting, where, contrary to Experiment 1, the visual modality now has a greater weight than what could be expected from the relative reliability alone.
+An interesting difference with Experiment 1, however, was that participants had a clear preference for the non-noisy modality, as the values of the relative variances were different (Figure \ref{fig:pref}, right).
+This preference affected the relative weighting, where, contrary to Experiment 1, the visual modality had greater weight than what could be expected from its relative reliability alone.
+% $\frac{\sigma^2_V}{\sigma^2_A + \sigma^2_N}$ vs. $\frac{\sigma^2_{Vb}}{\sigma^2_{Ab}}$
 
@@
 
-\section{General discussion}
+\section{General Discussion}
 
@@
 
-There were, however, quantitative differences: the audio-visual presentation caused the reliance on both modalities to decrease to a lower extent than the ideal observer model expected.
-This phenomenon could be attributed to the arbitrary nature of the form-meaning mapping.
-Previous studies suggest, indeed, that while redundant multi-modal information improves performance (e.g., determining the frequency of a bouncing ball from visual and auditory cues), arbitrary mappings generally tends to hinder performance \cite<for review, see>{robinson2010}.
-Another possibility could be that the ideal model failed to capture some other features of multi-modal integration.
-Further work is needed to understand this result.
+There were, however, quantitative differences.
+Audio-visual presentation caused the reliance on both modalities to decrease to a lower extent than the ideal observer model expected.
+One possbible explanation is that this phenomenon was caused by the arbitrary nature of the form-meaning mapping.
+Previous studies suggest that while redundant multi-modal information improves performance (e.g., determining the frequency of a bouncing ball from visual and auditory cues), arbitrary mappings generally tends to hinder performance \cite<for review, see>{robinson2010}.
+% Or perhaps the ideal model failed to capture some other features of multi-modal integration.
+% Further work is needed to understand this result.
 
@@
 Only when we intervened by adding  noise to one modality in Experiment 2, did participants show a systematic preference for the non-noisy modality.
-One possible explanation for this preference could be that people do not combine cross-modal uncertainties of a similar kind (e.g., category ambiguity in both modalities) in the same way they would combine uncertainties of different kinds (e.g., category ambiguity in one modality and noise in the other).
-Further work is needed to determine the extent to which this is the case.
+One possible explanation for this preference could be that people do not combine cross-modal uncertainties of a similar kind (e.g., ambiguity in both modalities) in the same way they would combine uncertainties of different kinds (e.g., ambiguity in one modality and noise in the other).
+% Further work is needed to determine the extent to which this is the case.
 
-Overall, in both Experiments, the majority of the variance (around 90\%) could be explained by an ideal observer that combined multi-modal information in an optimal way.
-In the light of this main results, we can revisit some previous findings in the literature.
+Overall, in both Experiments, the majority of the variance could be explained by an ideal observer that combined multi-modal information optimally.
+In the light of this main result, we can revisit some previous findings in the literature.
 For instance, \citeA{sloutsky2003} reported a dominance for the auditory modality in children.
 This dominance disappear or reverses in adults.
-Could this developmental difference be driven by changes in the intrinsic relative reliability of modalities?
+Could this developmental difference be driven by changes in the intrinsic relative reliability of modalities across development?
 More work is needed to carefully examine this (and other) speculations, and more generally, to determine the extent to which the optimal combination account helps us better understand the mechanisms of word precessing and learning.
-
-%However, is it the case that children weight modalities differently because a sound is inherently more salient than any visual contrast?
-or could part of this effect stem from the fact that the precise sound and visual contrasts used as stimuli differ in their relative salience to children?
-In particular, what happens if the sound contrast is reduced to a perceptual minimum and when the visual contrast is enhanced?
-Can we reverse the weighting in this case as our optimal combination account would suggest?
-Moreover, could the developmental difference be driven by changes in the relative reliability of modalities?
-
-%In a different line of work, it has been shown that infants have difficulties mapping minimally different words to two novel objects, despite the fact that they can perceptually differentiate these words \cite<e.g.,>{stager1997}.
-Is it possible that what had been interpreted as `failure' in learning could, at least to some extent, be explained by a categorical decision (similar to what adults performed in our task).
-More precisely, it is possible that the visual stimuli were quite similar in the children’s early conceptual space, which made them believe that both objects were possible instances of the same semantic category.
-This, in turn, would make them interpret the sound difference as alternative pronunciations of the same word.
-In particular, what happens if the object contrast is maximized?
-More work is needed to carefully examine these (and other) speculations, and more generally, to determine the extent to which the optimal combination account helps us better understand the mechanisms of word precessing and learning.
 

### 2017-02-02 data and analysis/analysis3.Rmd
exp3

--- 2017-01-31 data and analysis/analysis2.Rmd
@@
 
-Data, and exclusion
+The following analysis is done using pilot data with 25 subjects.
+
+We plan to collect data for 100 subjects
+
+Data.
 
@@
 
-d <- read_delim("data_experiment2_complete.txt", delim = " ") %>%
-  filter(ID !="AR1IWBDA7MC86", ID !="A3GOKNZGZGHL45") %>% #took the experiment twice
-  filter(type == "Task", problem=="No")  %>% #had a technical problem during the experiment
-  filter(score > 0.5)  #got more less than 50% correct on the training trials
+#Skip the pre task trials 
+#Filter subjects who had no technical problem
+#Select subjects who got more than 50% correct answers on the pre task trials
 
+d <- read_delim("data_experiment3.txt", delim = " ") %>%
+  filter(type == "Task", problem=="No") %>%
+  filter(score > 0.5)
 ```
@@
        aes(x = sound_dist, y = mean, col = factor(concept_dist))) + 
-  #geom_pointrange(aes(ymin = ci_lower, ymax = ci_upper), 
-                 # position = position_dodge(width = .1), size=0.3) + 
-  geom_point(size=2) +
-  geom_line(size=0.7) + 
-  geom_line(data = sounds, aes(col = 1), col = "black",size=0.7) + 
-  #geom_pointrange(data = sounds, aes(ymin = ci_lower, ymax = ci_upper, 
-                             #        col = 1), col = "black", size=0.4)+
-  geom_hline(data = concepts, aes(yintercept=mean, col = factor(concept_dist)), lty = 2)+
+  geom_pointrange(aes(ymin = ci_lower, ymax = ci_upper), 
+                  position = position_dodge(width = .1), size=0.3) + 
+  geom_line(lty = 2) + 
+  geom_line(data = sounds, aes(col = 1), col = "black") + 
+  geom_pointrange(data = sounds, aes(ymin = ci_lower, ymax = ci_upper, 
+                                     col = 1), col = "black", size=0.4)+
   xlab("Auditory distance") +ylab("% different")+
@@
 ```
-
 Fit the models.
@@
 ```
-Modalitiy preference plot
+
 ```{r}
@@
 model = c('baseline', 'fit')
-mean=c(1.64,1.45)
-ci_low=c(1.24,1.29)
-ci_up=c(2.02,1.65)
+mean=c(0.84,0.53)
+ci_low=c(0.68,0.46)
+ci_up=c(1.04,0.60)
 pref=data.frame(mean, ci_low, ci_up,model)
@@
 ```
+
 Analysis of the unimodal cases.
@@
   scale_y_continuous(limits = c(0, 1))+theme(aspect.ratio = 0.7)
-  #stat_function(fun = Logistic_v, colour="red")
+  #stat_function(fun = Logistic_v, colour="red"))
 
@@
 
-The bimodal case, all plots
+The bimodal case
+
 ```{r}
@@
 
-Modality preference
+The modality dominance
 ```{r}

### 2017-02-07 Data_and_analysis/analysis_exp1.Rmd
new organization

--- 2017-01-31 data and analysis/analysis2.Rmd
@@
 ---
-title: "WordRec Experiment"
-author: "A. Fourtassi & M. Frank"
+title: "WordRec Experiment 1"
+author: "A. Fourtassi & M. C. Frank"
 date: "January 13, 2017"
@@
 
-Data, and exclusion
+Data and exclusion
 
@@
 
-d <- read_delim("data_experiment2_complete.txt", delim = " ") %>%
-  filter(ID !="AR1IWBDA7MC86", ID !="A3GOKNZGZGHL45") %>% #took the experiment twice
-  filter(type == "Task", problem=="No")  %>% #had a technical problem during the experiment
-  filter(score > 0.5)  #got more less than 50% correct on the training trials
+#subject 32 and subject 59 are the same person
+#subject 42 and subject 100 are the same person
+#They will be excluded because they took the same experiment twice
+
+d <- read_delim("data_exp1_anonym.txt", delim = " ") %>%
+  filter(ID !="subject_32", ID !="subject_59", ID !="subject_42", ID !="subject_100") %>% 
+  filter(type == "Task", problem=="No")  %>% #keep subjects who did not encounter a technical problem during the experiment
+  filter(score > 0.5)  #.. and got more than 50% correct on the training trials
 
@@
   multi_boot_standard(col = "answer")
+```
 
+Initial plot
+```{r}
 ggplot(joint, 
@@
 
-ggplot(joint, 
-       aes(x = concept_dist, y = mean, col = factor(sound_dist))) + 
-  geom_pointrange(aes(ymin = ci_lower, ymax = ci_upper), 
-                  position = position_dodge(width = .1), size=0.3) + 
-  geom_line(lty = 2) + 
-  geom_line(data = concepts, aes(col = 1), col = "black") + 
-  geom_pointrange(data = concepts, aes(ymin = ci_lower, ymax = ci_upper, 
-                                     col = 1), col = "black", size=0.4) + 
-  scale_colour_solarized() +
-  xlab("Visual distance") +ylab("% different")+
-  scale_colour_discrete(name="Auditory Dist")+
-theme(legend.title = element_text(size=8))
-
 ```
@@
 
-#Fit the uniomodal sound condition
 sound_data <- d %>%
@@
 #Fit the non-linear function
+#
 
@@
 
-##extract coefficient
-eA_nl <- coef(sound_nl)["e"]
-vrA_nl <- coef(sound_nl)["vrA"]
+##extract parameters
 
-eV_nl <- coef(concept_nl)["e"]
-vrV_nl <- coef(concept_nl)["vrV"]
+#The sound-ony bias term:
+eA <- coef(sound_nl)["e"]
+#The sound-only variance
+vrA <- coef(sound_nl)["vrA"]
 
-eJ_nl <- coef(joint_nl)["e"]
-vrJ_A_nl <- coef(joint_nl)["vrA_j"]
-vrJ_V_nl <- coef(joint_nl)["vrV_j"]
+#The visual-ony bias term:
+eV <- coef(concept_nl)["e"]
+#The visual-ony variance:
+vrV <- coef(concept_nl)["vrV"]
+
+#The bimodal bias term:
+eJ <- coef(joint_nl)["e"]
+
+#The bimodal auditory variance:
+vrJ_A <- coef(joint_nl)["vrA_j"]
+#The bimodal visual variance:
+vrJ_V <- coef(joint_nl)["vrV_j"]
 
@@
 
-results <- boot(data= d, statistic = lmfit, R = 1)
+results <- boot(data= d, statistic = lmfit, R = 10000)
 
@@
 ```
-Modalitiy preference plot
-```{r}
-#I make a data frame 
-model = c('baseline', 'fit')
-mean=c(1.64,1.45)
-ci_low=c(1.24,1.29)
-ci_up=c(2.02,1.65)
-pref=data.frame(mean, ci_low, ci_up,model)
 
-ggplot(pref, 
-       aes(x = model, y=mean)) +
-geom_bar(stat = "identity", width=0.5, fill='grey')+
-  geom_errorbar(aes(ymin = ci_low, ymax = ci_up), 
-                  width = 0.1
-                ,
-                  position = position_dodge(width = 0.1))+
-  theme(aspect.ratio = 1, axis.text=element_text(size=15))
-
-```
 Analysis of the unimodal cases.
@@
 
-#The fit
+#The bimodal fit
 model_fit <- function (x,y) {
-   1/(1 + (1-eJ_nl)*exp((-4/vrJ_A_nl)*x+(-4/vrJ_V_nl)*y+(8/vrJ_A_nl)+(8/vrJ_V_nl)))
+   1/(1 + (1-eJ)*exp((-4/vrJ_A)*x+(-4/vrJ_V)*y+(8/vrJ_A)+(8/vrJ_V)))
 }
 
-#The baseline
+#The ideal observer model
 model_base <- function (x,y) {
-    1/(1 + (1-eJ_nl)*exp((-4/vrA_nl)*x+(-4/vrV_nl)*y+(8/vrA_nl)+(8/vrV_nl)))
+    1/(1 + (1-eJ)*exp((-4/vrA)*x+(-4/vrV)*y+(8/vrA)+(8/vrV)))
 }
@@
 
-#Plot predictions of the baseline
+#Plot predictions of the ideal observer model (or the baseline)
 mybase <- ms_all %>%
@@
 theme(aspect.ratio = 0.7)
+```
+
+The correlations models vs. human data
+```{r}
 
@@
 #Modality dominance coeficent
-a_fit=vrJ_V_nl/vrJ_A_nl
-a_base=vrV_nl/vrA_nl
+a_fit=vrJ_V/vrJ_A
+a_base=vrV/vrA
 a_Vdom=2*a_base

### 2017-02-07 Data_and_analysis/analysis_exp2.Rmd
new organization

--- 2017-02-07 Data_and_analysis/analysis_exp1.Rmd
@@
 ---
-title: "WordRec Experiment 1"
+title: "WordRec Experiment 2"
 author: "A. Fourtassi & M. C. Frank"
@@
 Data and exclusion
-
 ```{r}
 
-#subject 32 and subject 59 are the same person
-#subject 42 and subject 100 are the same person
-#They will be excluded because they took the same experiment twice
+#Skip the pre task trials 
+#Filter subjects who had no technical problem
+#Select subjects who got more than 50% correct answers on the pre task trials
 
-d <- read_delim("data_exp1_anonym.txt", delim = " ") %>%
-  filter(ID !="subject_32", ID !="subject_59", ID !="subject_42", ID !="subject_100") %>% 
-  filter(type == "Task", problem=="No")  %>% #keep subjects who did not encounter a technical problem during the experiment
-  filter(score > 0.5)  #.. and got more than 50% correct on the training trials
-
+d <- read_delim("data_exp2_anonym.txt", delim = " ") %>%
+  filter(type == "Task", problem=="No") %>%
+  filter(score > 0.5)
 ```
@@
 ```{r}
+
 ggplot(joint, 
        aes(x = sound_dist, y = mean, col = factor(concept_dist))) + 
-  #geom_pointrange(aes(ymin = ci_lower, ymax = ci_upper), 
-                 # position = position_dodge(width = .1), size=0.3) + 
-  geom_point(size=2) +
-  geom_line(size=0.7) + 
-  geom_line(data = sounds, aes(col = 1), col = "black",size=0.7) + 
-  #geom_pointrange(data = sounds, aes(ymin = ci_lower, ymax = ci_upper, 
-                             #        col = 1), col = "black", size=0.4)+
-  geom_hline(data = concepts, aes(yintercept=mean, col = factor(concept_dist)), lty = 2)+
+  geom_pointrange(aes(ymin = ci_lower, ymax = ci_upper), 
+                  position = position_dodge(width = .1), size=0.3) + 
+  geom_line(lty = 2) + 
+  geom_line(data = sounds, aes(col = 1), col = "black") + 
+  geom_pointrange(data = sounds, aes(ymin = ci_lower, ymax = ci_upper, 
+                                     col = 1), col = "black", size=0.4)+
   xlab("Auditory distance") +ylab("% different")+
@@
 vrJ_V <- coef(joint_nl)["vrV_j"]
-
 ```
@@
 theme(aspect.ratio = 0.7)
+
 ```

### 2017-02-07 Writeup/main.tex
new organization

--- 2017-02-02 write-up/main.tex
@@
 We introduce a task that allows us to examine how adults identify words under joint uncertainty in the auditory and visual modalities.
-We propose a ideal observer model of the task which provides an optimal baseline.
+We propose an ideal observer model of the task which provides an optimal baseline.
 Model predictions are tested in two experiments where word recognition is made under two kinds of uncertainty: category ambiguity and distorting noise.
@@
 More precisely we study the case where both the word's form and the word's referent are ambiguous, and we examine the extent to which humans conform to, or deviate from the predictions of the ideal observer model.
-Moreover, some previous studies on audio-visual processing documented cases of modality preference, when people rely predominantly on the visual modality \cite<e.g., >{colavita1974} or the auditory modality \cite<e.g., >{sloutsky2003}.
+Moreover, some previous studies on audio-visual processing documented cases of modality preference, when people rely predominantly on the visual modality \cite<e.g., >{colavita74} or the auditory modality \cite<e.g., >{sloutsky2003}.
 Thus, we will explore if participants in our task show evidence of a modality preference.
@@
 However, unlike this previous line of research, here participants are not asked whether the two audio-visual presentations are identical.
-Instead, the task is category-based: They are asked to press `same' if they think the second item (the test) belonged to the same category as the first (target) (e.g.,  dog-/aba/), even if there is a slight difference in the word, in the object, or in both.
-They are instructed to press `different' only if they think that the second stimulus was an instance of the other word category (cat-/ada/).
+Instead, the task is category-based: They are asked to press ``same'' if they think the second item (the test) belonged to the same category as the first (target) (e.g.,  dog-/aba/), even if there is a slight difference in the word, in the object, or in both.
+They are instructed to press ``different'' only if they think that the second stimulus was an instance of the other word category (cat-/ada/).
 
@@
 \centering
-\includegraphics[width=0.4\textwidth]{task1.png}
+\includegraphics[width=0.4\textwidth]{pictures/task.png}
 \caption{Overview of the task}
@@
   \centering
-  \includegraphics[width=3.25in]{MyTask.png}
+  \includegraphics[width=3.25in]{pictures/model.png}
   \caption{Illustration of our model using simulated data.
@@
 
-In sum, the posterior \ref{eq:pred} provides the predictions of ideal observer for how probabilities that characterize uncertainty in each modality can be combined to make categorical decision about bimodal input.
+In sum, the posterior \ref{eq:pred} provides the ideal observer's predictions for how probabilities that characterize uncertainty in each modality can be combined to make categorical decision about bimodal input.
 
@@
 The 6 and 10 points along the morph were quite distinguishable, and we took them to be our prototypes.
-
- % (Figure \ref{fig:morph})
+%(Figure \ref{fig:morph}).
 %
-% \begin{figure}[tp]
-% \centering
-% \includegraphics[width=0.4\textwidth]{morph.png}
-% \caption{Visual stimuli for our experiments.}
-% \label{fig:morph}
-% \end{figure}
+%\begin{figure}[tp]
+%\centering
+%includegraphics[width=0.4\textwidth]{morph.png}
+%\caption{Visual stimuli for our experiments.}
+%label{fig:morph}
+%\end{figure}
 
@@
 \centering
-\includegraphics[width=3.25in]{unimodal.png}
-\caption{Average human responses in the auditory-only condition (left), and visual-only condition (right). Error bars are 95\% confidence intervals. Solid lines represent unimodal logistic fits.}
+\includegraphics[width=3.25in]{pictures/unimodal.pdf}
+\caption{Average human responses in the auditory-only condition (left), and visual-only condition (right).
+A) represents data from Experiment 1, and B) data from Experiment 2.
+Error bars are 95\% confidence intervals.
+Solid lines represent unimodal logistic fits.}
 \label{fig:unimodal}
@@
 \centering
-\includegraphics[width=.83\textwidth]{Exp.png}
+\includegraphics[width=1\textwidth]{pictures/bimodal.pdf}
 \caption{Proportion of ``different'' judgments as a function of auditory distance.
@@
 Dashed lines represent average human responses in the unimodal conditions.
-Colors represent values in the visual continuum.}
+Colors represent values in the visual continuum.
+A) represents data from Experiment 1, and B) data from Experiment 2.}
 \label{fig:Exp}
@@
 \subsubsection{Unimodal conditions} this is the case where the pictures were hidden, or where the sounds were muted.
-Average categorization judgments and fits are shown in Figure \ref{fig:unimodal}.
+Average categorization judgments and fits are shown in Figure (\ref{fig:unimodal}, A).
 Auditory judgements were somewhat sharper and more pronounced than visual judgments.
-The fit was done as follows.
+The fit was done using the Nonlinear Least Squares (NLS) R package, as follows.
 For an ideal recognizer, the probability of choosing category 2 (that is, to answer ``different'') when presented with an audio instance $a$, is the posterior probability of this category $p(A_2|a)$.
@@
 We fit a model to human responses in the bimodal condition, collapsed across participants, finding $\epsilon=-0.32$, $\sigma^2_{Ab}=5.00$ and $\sigma^2_{Vb}=7.27$.
-The fit explained XX of the variance.
+The fit explained 94\% of total variance.
 
@@
 We derived the predictions of the ideal observer model by using the values of the variances derived from the unimodal conditions, and the response bias derived from the bimodal condition, and by substituting these values into the expression of the posterior in Eq.~\ref{eq:pred}.
-Figure \ref{fig:Exp} shows participants' responses in the bimodal condition (left), as well as the prediction of the ideal observer (middle), and the bimodal fit models (right).
+Figure (\ref{fig:Exp}, A) shows participants' responses in the bimodal condition (left), as well as the prediction of the ideal observer (middle), and the bimodal fit models (right).
 
@@
 We also used the same auditory stimuli, but we convolved each item with Brown noise of amplitude 1 using the audio editor Audacity (2.1.2).
-The signal-to-noise ratio was XXX dB.
 The procedure was exactly the same as in the previous experiment, except that test stimuli were presented with the new noisy auditory stimuli.
@@
 
-We fit a model to human responses in the bimodal condition, collapsed across participants. We estimated $\epsilon=-0.38$, $\sigma^2_{Vb}=5.21$, and  $\sigma^2_{Ab}+\sigma^2_{Nb}=9.84$.
+We fit a model to human responses in the bimodal condition, collapsed across participants.
+We estimated $\epsilon=-0.38$, $\sigma^2_{Vb}=5.21$, and  $\sigma^2_{Ab}+\sigma^2_{Nb}=9.84$.
+The fit explained 97\% of total variance.
 
@@
 \centering
-\includegraphics[width=0.4\textwidth]{preference.png}
+\includegraphics[width=0.4\textwidth]{pictures/preference.png}
 \caption{Top: decision thresholds in the audio-visual space.
@@
 For instance, \citeA{sloutsky2003} reported a dominance for the auditory modality in children.
-This dominance disappear or reverses in adults.
+This dominance disappears or reverses in adults.
 Could this developmental difference be driven by changes in the intrinsic relative reliability of modalities across development?

### 2017-02-07 Data_and_analysis/process_rawdata.py

@@ -1,0 +1,71 @@
+import os
+import sys
+import shutil
+import numpy
+from optparse import OptionParser
+import random
+from math import *
+import glob
+import pprint
+import json
+
+def main():
+    usage = "usage: %prog [options] CORPUS_TEXT"
+    parser = OptionParser(usage)
+    (options, args) = parser.parse_args()
+
+    ExpN=args[0]
+    subjN=0
+    myFiles= glob.glob("../Raw_data/rawdata_experiment"+ExpN+"/*json")
+    for f in myFiles:
+        cur=open(f,'r')
+        cur_json=json.load(cur)
+        subjN=subjN+1
+
+#extract info
+        id=cur_json["WorkerId"]
+        condition=cur_json["answers"]["data"]["data"]["condition"]
+        rando=cur_json["answers"]["data"]["data"]["rando"]
+        type=cur_json["answers"]["data"]["data"]["tri_type"]
+        order=cur_json["answers"]["data"]["data"]["tri_order"]
+        block=cur_json["answers"]["data"]["data"]["block"]
+        sound_dist=cur_json["answers"]["data"]["data"]["sou_dist"]
+        concept_dist=cur_json["answers"]["data"]["data"]["con_dist"]
+        answer=cur_json["answers"]["data"]["data"]["answer"]
+        RT=cur_json["answers"]["data"]["data"]["rt"]
+        problem=cur_json["answers"]["data"]["brief"]["problem"]
+        gender=cur_json["answers"]["data"]["brief"]["gender"]
+        age=cur_json["answers"]["data"]["brief"]["age"]
+        native=cur_json["answers"]["data"]["brief"]["native"]
+        ifproblem=cur_json["answers"]["data"]["brief"]["ifproblem"]
+        if problem =='':
+	    problem='Yes'
+    #comment=cur_json["answers"]["data"]["brief"]["comment"]
+    
+        trials=cur_json["answers"]["data"]["data"]["tri_number"]
+        score=0
+
+        for i in range(len(trials)):
+	
+	    if type[i]=="preTask":
+	    
+	        if int(order[i])==int(answer[i]):
+		    score=score+1
+
+         
+            if sound_dist[i]=='':
+	        sound_dist[i]='NA'
+            if concept_dist[i]=='':
+	        concept_dist[i]='NA'
+   
+        score=float(score)/12 
+
+        for i in range(len(trials)):
+	    
[…]

### 2017-02-07 Experiments/experiment1.js

@@ -1,0 +1,887 @@
+//////////////////
+//Helper functions
+///////////////////
+
+// Shows slides. We're using jQuery here - the **$** is the jQuery selector function, which takes as input either a DOM element or a CSS selector string.
+function randomInteger(n) {
+	return Math.floor(Math.random()*n);
+}
+
+function randomElement(array) {
+  return array[randomInteger(array.length)];
+}
+
+function randomInt(min,max)
+{
+    return Math.floor(Math.random()*(max-min+1)+min);
+}
+
+function showSlide(id) {
+  // Hide all slides
+	$(".slide").hide();
+	// Show just the slide we want to show
+	$("#"+id).show();
+}
+
+//shuffle an array
+function shuffleArray(a) {
+
+    for (var i = a.length - 1; i > 0; i--) {
+        var j = Math.floor(Math.random() * (i + 1));
+        var temp = a[i];
+        a[i] = a[j];
+        a[j] = temp;
+    }
+    return a;
+}
+
+function randomElement(array) {
+  return array[randomInteger(array.length)];
+}
+
+//I should now work on the randomization
+var rando = randomInt(0,3);
+var first_word ='', second_word='', first_obj='', first_obj='';
+
+if (rando ==0) {
+//Dog-ABA, Cat-ADA    
+//Dog is the standard
+first_word="ABA";
+second_word="ADA";
+first_obj="Dog";
+second_obj="Cat";
+    
+var ConStim = ['dog1','dog2','dog3','dog4', 'dog5'];   
+var SounStim = ['aba01','aba03','aba05','aba07', 'aba09'];
+    
+var ConStim_preTask=['dog1','dog1', 'dog5','dog5'];
+var SounStim_preTask = ['aba01','aba01','aba09','aba09'];
+}
+
+if (rando ==1) {
+//Dog-ADA, Cat-ABA
+//Dog is the standard
+first_word="ADA";
+second_word="ABA";
+first_obj="Dog";
+second_obj="Cat";
+    
+var ConStim = ['dog1','dog2','dog3','dog4', 'dog5'];   
+var SounStim = ['aba09','aba07','aba05','aba03', 'aba01'];
+    
+var ConStim_preTask=['dog1','dog1', 'dog5','dog5'];
+var SounStim_preTask = ['aba09','aba09','aba01','aba01'];
+    
+}
+if (rando ==2) {
[…]

### 2017-02-07 Experiments/experiment2.js

@@ -1,0 +1,891 @@
+//////////////////
+//Helper functions
+///////////////////
+
+// Shows slides. We're using jQuery here - the **$** is the jQuery selector function, which takes as input either a DOM element or a CSS selector string.
+function randomInteger(n) {
+	return Math.floor(Math.random()*n);
+}
+
+function randomElement(array) {
+  return array[randomInteger(array.length)];
+}
+
+function randomInt(min,max)
+{
+    return Math.floor(Math.random()*(max-min+1)+min);
+}
+
+function showSlide(id) {
+  // Hide all slides
+	$(".slide").hide();
+	// Show just the slide we want to show
+	$("#"+id).show();
+}
+
+//shuffle an array
+function shuffleArray(a) {
+
+    for (var i = a.length - 1; i > 0; i--) {
+        var j = Math.floor(Math.random() * (i + 1));
+        var temp = a[i];
+        a[i] = a[j];
+        a[j] = temp;
+    }
+    return a;
+}
+
+function randomElement(array) {
+  return array[randomInteger(array.length)];
+}
+
+//I should now work on the randomization
+var rando = randomInt(0,3);
+var first_word ='', second_word='', first_obj='', first_obj='';
+
+if (rando ==0) {
+//Dog-ABA, Cat-ADA    
+//Dog is the standard
+first_word="ABA";
+second_word="ADA";
+first_obj="Dog";
+second_obj="Cat";
+    
+var ConStim = ['dog1','dog2','dog3','dog4', 'dog5'];   
+var SounStim = ['aba01','aba03','aba05','aba07', 'aba09'];
+var SounStim_noise = ['aba01_noise','aba03_noise','aba05_noise','aba07_noise', 'aba09_noise'];
+    
+var ConStim_preTask=['dog1','dog1', 'dog5','dog5'];
+var SounStim_preTask = ['aba01','aba01','aba09','aba09'];
+}
+
+if (rando ==1) {
+//Dog-ADA, Cat-ABA
+//Dog is the standard
+first_word="ADA";
+second_word="ABA";
+first_obj="Dog";
+second_obj="Cat";
+    
+var ConStim = ['dog1','dog2','dog3','dog4', 'dog5'];   
+var SounStim = ['aba09','aba07','aba05','aba03', 'aba01'];
[…]

### 2017-02-07 experiment1.js

@@ -1,878 +1,0 @@
-//////////////////
-//Helper functions
-///////////////////
-
-// Shows slides. We're using jQuery here - the **$** is the jQuery selector function, which takes as input either a DOM element or a CSS selector string.
-function randomInteger(n) {
-	return Math.floor(Math.random()*n);
-}
-
-function randomElement(array) {
-  return array[randomInteger(array.length)];
-}
-
-function randomInt(min,max)
-{
-    return Math.floor(Math.random()*(max-min+1)+min);
-}
-
-function showSlide(id) {
-  // Hide all slides
-	$(".slide").hide();
-	// Show just the slide we want to show
-	$("#"+id).show();
-}
-
-//shuffle an array
-function shuffleArray(a) {
-
-    for (var i = a.length - 1; i > 0; i--) {
-        var j = Math.floor(Math.random() * (i + 1));
-        var temp = a[i];
-        a[i] = a[j];
-        a[j] = temp;
-    }
-    return a;
-}
-
-function randomElement(array) {
-  return array[randomInteger(array.length)];
-}
-
-//I should now work on the randomization
-var rando = randomInt(0,3);
-var first_word ='', second_word='', first_obj='', first_obj='';
-
-if (rando ==0) {
-//Dog-ABA, Cat-ADA    
-//Dog is the standard
-first_word="ABA";
-second_word="ADA";
-first_obj="Dog";
-second_obj="Cat";
-    
-var ConStim = ['dog1','dog2','dog3','dog4', 'dog5'];   
-var SounStim = ['aba01','aba03','aba05','aba07', 'aba09'];
-    
-var ConStim_preTask=['dog1','dog1', 'dog5','dog5'];
-var SounStim_preTask = ['aba01','aba01','aba09','aba09'];
-}
-
-if (rando ==1) {
-//Dog-ADA, Cat-ABA
-//Dog is the standard
-first_word="ADA";
-second_word="ABA";
-first_obj="Dog";
-second_obj="Cat";
-    
-var ConStim = ['dog1','dog2','dog3','dog4', 'dog5'];   
-var SounStim = ['aba09','aba07','aba05','aba03', 'aba01'];
-    
-var ConStim_preTask=['dog1','dog1', 'dog5','dog5'];
-var SounStim_preTask = ['aba09','aba09','aba01','aba01'];
-    
-}
-if (rando ==2) {
-//Dog-ADA, Cat-ABA
[…]

### 2017-07-12 Data_and_analysis/analysis3_pilot.Rmd
pilot experiment 3

--- 2017-02-02 data and analysis/analysis3.Rmd
@@
 
-The following analysis is done using pilot data with 25 subjects.
-
-We plan to collect data for 100 subjects
-
 Data.
@@
 
-d <- read_delim("data_experiment3.txt", delim = " ") %>%
+d <- read_delim("data_exp3_pilot6.txt", delim = " ") %>%
   filter(type == "Task", problem=="No") %>%
   filter(score > 0.5)
+
+#Sample size in the real experiment will be 100
 ```

### 2017-07-12 Experiments/experiment3.js
experiment 3 pilot

@@ -1,0 +1,890 @@
+//////////////////
+//Helper functions
+///////////////////
+
+// Shows slides. We're using jQuery here - the **$** is the jQuery selector function, which takes as input either a DOM element or a CSS selector string.
+function randomInteger(n) {
+	return Math.floor(Math.random()*n);
+}
+
+function randomElement(array) {
+  return array[randomInteger(array.length)];
+}
+
+function randomInt(min,max)
+{
+    return Math.floor(Math.random()*(max-min+1)+min);
+}
+
+function showSlide(id) {
+  // Hide all slides
+	$(".slide").hide();
+	// Show just the slide we want to show
+	$("#"+id).show();
+}
+
+//shuffle an array
+function shuffleArray(a) {
+
+    for (var i = a.length - 1; i > 0; i--) {
+        var j = Math.floor(Math.random() * (i + 1));
+        var temp = a[i];
+        a[i] = a[j];
+        a[j] = temp;
+    }
+    return a;
+}
+
+function randomElement(array) {
+  return array[randomInteger(array.length)];
+}
+
+//I should now work on the randomization
+var rando = randomInt(0,3);
+var first_word ='', second_word='', first_obj='', first_obj='';
+
+if (rando ==0) {
+//Dog-ABA, Cat-ADA    
+//Dog is the standard
+first_word="ABA";
+second_word="ADA";
+first_obj="Dog";
+second_obj="Cat";
+    
+var ConStim = ['dog1','dog2','dog3','dog4', 'dog5'];   
+var ConStim_blur = ['dog1_blur10','dog2_blur10','dog3_blur10','dog4_blur10', 'dog5_blur10'];
+var SounStim = ['aba01','aba03','aba05','aba07', 'aba09'];
+    
+var ConStim_preTask=['dog1','dog1', 'dog5','dog5'];
+var SounStim_preTask = ['aba01','aba01','aba09','aba09'];
+}
+
+if (rando ==1) {
+//Dog-ADA, Cat-ABA
+//Dog is the standard
+first_word="ADA";
+second_word="ABA";
+first_obj="Dog";
+second_obj="Cat";
+    
+var ConStim = ['dog1','dog2','dog3','dog4', 'dog5'];   
+var ConStim_blur = ['dog1_blur10','dog2_blur10','dog3_blur10','dog4_blur10', 'dog5_blur10'];
[…]

### 2017-10-23 Writeup/ms.Rmd
new write-up

---
title             : "Word Identification Under Multimodal Uncertainty"
shorttitle        : "Word Identification Under Multimodal Uncertainty"

author: 
  - name          : "Abdellah Fourtassi"
    affiliation   : "1"
    corresponding : yes    # Define only one corresponding author
    address       : "Postal address"
    email         : "afourtas@stanford.edu"
  - name          : "Michael C. Frank"
    affiliation   : "1"

affiliation:
  - id            : "1"
    institution   : "Department of Psychoogy, Stanford University"

author_note: |

  Abdellah Fourtassi

  Deprtment of Psychology

  Stanford Univerisity

  50 Serra Mall

  Jordan Hall, Building 420

  Stanford, CA 94301

abstract: |
  Identifying the visual referent of a spoken word -- that a particular insect is referred to by the word ``bee'' -- requires both the ability to process and integrate multimodal input and the ability to reason under uncertainty. How do these tasks interact with one another? We introduce a task that allows us to examine how adults identify words under joint uncertainty in the auditory and visual modalities. We propose an ideal observer model of the task which provides an optimal account of how auditory and visual cues are combined. Model predictions are tested in three experiments where word recognition is made under two kinds of uncertainty: category ambiguity and/or distorting noise. In all cases, the optimal model explains much of the variance in human judgments. In particular, when the signal was not distorted with noise, participants weighted the auditory and visual cues optimally, that is, according to the relative reliability of each modality. But when one modality had noise added to it, human perceivers systematically preferred the unperturbed modality to a greater extent than the optimal model did. We discuss the broad implications of the results, especially in relation to early language acuquisition.

keywords          : "Language; audio-visual processing; word learning; speech perception; computational modeling."

wordcount         : "X"

bibliography      : ["references.bib"]

figsintext        : no
figurelist        : no
tablelist         : no
footnotelist      : no
lineno            : yes

lang              : "english"
class             : "man"
output            : papaja::apa6_pdf
---

```{r load_packages, include = FALSE}
library("papaja")
library(readr)
library(tidyr)
library(ggplot2)
library(cowplot)
library(knitr)
library(boot)
library(dplyr)
library(langcog)
theme_set(theme_bw())
```

```{r}

#Data from the 3 experiments 
#############################
exp1 <- read_delim("../Data_and_analysis/data_exp1_Anonym.txt", delim = " ") %>%
  filter(type == "Task") %>%
  mutate(experiment='Experiment1')

exp2 <- read_delim("../Data_and_analysis/data_exp2_Anonym.txt", delim = " ") %>%
  filter(type == "Task") %>%
  mutate(experiment='Experiment2')

exp3 <- read_delim("../Data_and_analysis/data_exp3_Anonym.txt", delim = " ") %>%
  filter(type == "Task") %>%
  mutate(experiment='Experiment3')
```

```{r}
#First deal with all data
```

```{r}
#First Exlusion criteria:
#############################

#All data
N_all_1 <- exp1 %>%
  distinct(ID) %>%
  nrow()

N_all_2 <- exp2 %>%
  distinct(ID) %>%
  nrow()

N_all_3 <- exp3 %>%
  distinct(ID) %>%
  nrow()

#Filter who took the experiment more than once

#Exp1
 token_data_1 <- exp1 %>%
   group_by(ID) %>%
   dplyr::summarise(N_tokens=n())

 N_twice_1 <- token_data_1 %>%
   filter(N_tokens > 70) %>%
   nrow()

 exp1_once <- exp1 %>%
   left_join(token_data_1) %>%
   filter(N_tokens == 70) #every subject is supposed to produce exactly 70 tokens

 #Exp2
token_data_2 <- exp2 %>%
   group_by(ID) %>%
   dplyr::summarise(N_tokens=n())

 N_twice_2 <- token_data_2 %>%
   filter(N_tokens > 70) %>%
   nrow()

 exp2_once <- exp2 %>%
   left_join(token_data_2) %>%
   filter(N_tokens == 70)

 #Exp3
token_data_3 <- exp3 %>%
   group_by(ID) %>%
   dplyr::summarise(N_tokens=n())

 N_twice_3 <- token_data_3 %>%
   filter(N_tokens > 70) %>%
   nrow()

 exp3_once <- exp3 %>%
   left_join(token_data_3) %>%
   filter(N_tokens == 70)

#Participants who did not encounter a technical problem with the online experiment

#Exp1
exp1_noProb <- exp1_once %>%
  filter(problem=="No")

N_noProb_1 <- exp1_noProb %>%
  distinct(ID) %>%
  nrow()

#Exp2
exp2_noProb <- exp2_once %>%
  filter(problem=="No")

N_noProb_2 <- exp2_noProb %>%
  distinct(ID) %>%
  nrow()

#Exp3
exp3_noProb <- exp3_once %>%
  filter(problem=="No")

N_noProb_3 <- exp3_noProb %>%
  distinct(ID) %>%
  nrow()

#Participants who who did not encounter a problem AND were above 50% accuracy on obvious trials

#Exp1
exp1_good <- exp1_noProb %>%
  filter(score > 0.5)

N_good_1 <- exp1_good %>%
  distinct(ID) %>%
  nrow()

#Exp2
exp2_good <- exp2_noProb %>%
  filter(score > 0.5)

N_good_2 <- exp2_good %>%
  distinct(ID) %>%
  nrow()

#Exp3
exp3_good <- exp3_noProb %>%
  filter(score > 0.5)

N_good_3 <- exp3_good %>%
  distinct(ID) %>%
  nrow()

```

```{r}

#Data subseting

#Experiment 1
##############

sound_all_exp1 <- exp1_good %>%
    filter(condition == "sound")

concept_all_exp1 <- exp1_good %>%
    filter(condition == "concept")

joint_all_exp1 <- exp1_good %>%
    filter(condition == "joint")

#Summary
sounds_exp1 <- exp1_good %>%
  filter(condition == "sound") %>%
  group_by(sound_dist) %>%
  #multi_boot_standard(col = "answer")
  summarise(mean = mean(answer)) %>%
  mutate(Experiment="Experiment 1", 
         Condition="Auditory") %>%
  rename(distance = sound_dist)

concepts_exp1 <- exp1_good %>%
  filter(condition == "concept") %>%
  group_by(concept_dist) %>%
  #multi_boot_standard(col = "answer")
  summarise(mean = mean(answer)) %>%
  mutate(Experiment="Experiment 1", 
         Condition="Visual") %>%
  rename(distance = concept_dist)

joint_exp1 <- exp1_good %>%
  filter(condition == "joint") %>%
  group_by(concept_dist, sound_dist) %>%
  #multi_boot_standard(col = "answer")
  summarise(mean = mean(answer)) %>%
  mutate(Experiment="Experiment 1", 
         Condition="Joint")

#Experiment2
############

sound_all_exp2 <- exp2_good %>%
    filter(condition == "sound")

concept_all_exp2 <- exp2_good %>%
    filter(condition == "concept")

joint_all_exp2 <- exp2_good %>%
    filter(condition == "joint")

#Summary
sounds_exp2 <- exp2_good %>%
  filter(condition == "sound") %>%
  group_by(sound_dist) %>%
  #multi_boot_standard(col = "answer")
  summarise(mean = mean(answer)) %>%
  mutate(Experiment="Experiment 2", 
         Condition="Auditory") %>%
  rename(distance = sound_dist)

concepts_exp2 <- exp2_good %>%
  filter(condition == "concept") %>%
  group_by(concept_dist) %>%
  #multi_boot_standard(col = "answer")
  summarise(mean = mean(answer)) %>%
  mutate(Experiment="Experiment 2", 
         Condition="Visual") %>%
  rename(distance = concept_dist)

joint_exp2 <- exp2_good %>%
  filter(condition == "joint") %>%
  group_by(concept_dist, sound_dist) %>%
  #multi_boot_standard(col = "answer")
  summarise(mean = mean(answer)) %>%
  mutate(Experiment="Experiment 2", 
         Condition="Joint")

#Experiment3
############

sound_all_exp3 <- exp3_good %>%
    filter(condition == "sound")

concept_all_exp3 <- exp3_good %>%
    filter(condition == "concept")

joint_all_exp3 <- exp3_good %>%
    filter(condition == "joint")

#Summary
sounds_exp3 <- exp3_good %>%
  filter(condition == "sound") %>%
  group_by(sound_dist) %>%
  #multi_boot_standard(col = "answer")
  summarise(mean = mean(answer)) %>%
  mutate(Experiment="Experiment 3", 
         Condition="Auditory") %>%
  rename(distance = sound_dist)

concepts_exp3 <- exp3_good %>%
  filter(condition == "concept") %>%
  group_by(concept_dist) %>%
  #multi_boot_standard(col = "answer")
  summarise(mean = mean(answer)) %>%
  mutate(Experiment="Experiment 3", 
         Condition="Visual") %>%
  rename(distance = concept_dist)

joint_exp3 <- exp3_good %>%
  filter(condition == "joint") %>%
  group_by(concept_dist, sound_dist) %>%
  #multi_boot_standard(col = "answer")
  summarise(mean = mean(answer)) %>%
  mutate(Experiment="Experiment 3", 
         Condition="Joint")

exp_uni_data <- bind_rows(sounds_exp1, concepts_exp1,
                     sounds_exp2, concepts_exp2,
                     sounds_exp3, concepts_exp3)

```

Language uses symbols expressed in one modality (e.g., the auditory modality, in the case of speech) to communicate about the world, which we perceive through many different sensory modalities. Consider hearing someone yell "bee!" at a picnic, as a honey bee buzzes around the food. Determining reference involves processing the auditory information and linking it with other perceptual signals (e.g., the visual image of the bee, the sound of its wings, the sensation of the bee flying by your arm).

This multimodal integration task takes place in a noisy world. On the auditory side, individual acoustic word tokens are almost always ambiguous with respect to the particular sequence of phonemes they represent, which is due to the inherent variability of how a phonetic category is realized acoustically [@hillenbrand1995]. And some tokens may be distorted additionally by mispronunciation or ambient noise. Perhaps the speaker was yelling "pea" and not "bee". Similarly, a sensory impression may not be enough to make a definitive identification of a visual category.\footnote{In the general case, language can of course be visual as well as auditory, and object identification can be done through many modalities. For simplicity, we focus on audio-visual matching here.} Perhaps the insect was a beetle or a fly instead.

How does the brain deal with uncertainty to process and understand language? Previous research showed that the brain encodes speech cues probabilistically, in a way that mirrors the inherent noise/ambiguity in the input. From this probabilistic representation, the brain tends to make the statistically optimal judgement about the identity of the intended categories [e.g., @clayard08; @feldman2009]. Previous work in this line of research has largely focused on testing optimal inference using cues from the auditory modality. A few studies did explore some aspects of audio-visual processing in a probabilistic framework [@bejjanki2011; @kleinschmidt2015]. These studies focused on the case of audio-visual speech perception, that is, recognizing speech categories using cues from the auditory signal accompagnied with lip movements. To our knowledge, however, no study explored whether word recogniton is statistially optimal in a *referential* context, that is, when the brain has to combine cues from the sound and the meaning/referent. Imagine, for example, that someone is uncertain whether they heard "pea" or "bee", does it make them rely more on the referent (e.g., the object being pointed at)? Vice versa, if they are not sure if they saw a bee or a fly, does that make them rely more on the sound? More importantly, when input in both modalities is uncertain to varying degrees, do they weight each modality according to its relative reliability, or do they over-rely on a particular modality?

Outside the realm of language per se, research on multisensory integration suggests that the brain integrates information from different modalities in a statistically optimal way, that is, the integration results in a higher overall precision, and modalities are weighed according to their relative reliability [@ernst02]. However, it is not a priori obvious whether this finding can be extended to word-referent recognition under multimodal uncertainty.  Indeed, there seems to be at least two fundamental differences between these two cases, and both can influence the cue combination strategy.

First, in the case of optimal multisensory integration, modalities are understood to differ only in terms of their reliability. In a referential conext, however, modalities also differ in terms of their roles in the referential process: the auditory input represents the symbol (i.e., the word) whereas the visual input represents the referent. It has been suggested that because of the referential property of speech, it is a privileged signal for humans from infancy [see @vouloumanos2014 for a review]. Thus, it is possible that the brain does not treat the auditory and visual modalities as equivalent sources of information. Instead, there could be a bias for the auditory modality beyond what is expected from informational reliability alone.

Second, research on optimal multisensory integration typically deals with multisensory associations that are supposed to be *redundant*. An example of such integration is when we determine the size of an object using the visual and haptic modalities [@ernst02], or when we determe the spacial location of a stimulus using the visual and the auditory modalities [@alais04]. In the case of language, however, the multimodal input is rather *arbitrary* [@saussure1916].  For instance, there is no logical connection between the sound "bee" and the corresponding insect. Moreover, variation in the way the sound "bee" is pronounced does not correlate perceptually with variation in the shape (or any other visual property) in the category of bees. It turns out the nature of the multi-modal associations (redundant vs. arbitrary) influences the quality of multi-modal processing in both children and adults: the processing and integration is easier in the case of redundant input, than it in the case of arbitrary input [see @robinson2010 for a review]. Thus, there is a priori no obvious reason multimodal cue combination in the case of arbitrary assoiations (such as the case of word-referent) should be optimal in the same way redundant associations are. For instance, the former is more likely to show patterns of sub-optimality.

<!--

TRY TO CONTRAST TWO THINGS: WORK ON PERCEPTUAL INTEGRATION WHEN THERE IS CORRELATION AND WORK OF AUDIO-VISUAL ENCODING OF ARBITRARY ASSOCIATIONS, SHOW THAT THE FIRST IS NOT ARBIRARY, AND MOSTY CONTINUOUS (ANS PRODUCE OPTIMALITY), THE SECOND DOES NOT INVOVLE CATEGORIES OR A SEMANTIC CONTEX, WHERE A WORD REFER TO AN OBJECT, INSTEAD OF BEING JUST ARBITRARY (AND PRODUCE HINDRANCE AND SUB-OPTIMALITY). THUS OUR WORK TRIES TO DEAL WITH CASE

A few studies have explored some aspects of audio-visual processing in a probabilistic framework  [e.g., @bejjanki2011; @kleinschmidt2015]. In these studies, the researchers focused on the specific case of audio-visual speech  where information is *redundant* across modalities. In the present work, we study the case of word reference where the audio-visual associations are usually *arbitrary* (Cite Saussure). For instance, whereas in the case of audio-visual speech, the sound "bee" and the corresponding lip movements are supposed to merge into a unified percept, there is nothing in the sound "bee" or in the way it can be pronounced, that correlates perceptually with the shape (or some other visual property) of the insect.

More generally, we know that the nature of the multi-modal associations (redundant vs. arbitrary) influences the quality of the processing in both children and adults [see @robinson2010 for a review]. In the case of redundant multimodal information (e.g. determining the size of an object through the visual and haptic modality), the sensory integration is often statistically optimal (Ernst and Banks, 2002). Optimality in this context means two things: first, the precision of the bimodal estimate increases compared to the unimodal estimates, and second, the cues from different modalities are combined according to their relative reliability. In the case of arbitrary associations, empirical studies suggest, rather, sub-optimality. In fact, processing of the bimodal input does not increase the precision, it tends to hinder performance instead (Sloutsky, Palmer, Stager, ... I should dig into the literature on the arbitrary associations). Moreover, modalities are not optimally weighted according to their reliability, instead, one modality dominates the other depending on the task, e.g., Sloutsky et al. reported auditory dominance (for kids) and then prefernce for adults (..), and Colovita et al. reported visual dominance for adults.

-->

In this paper, we studied the mechanism of processing/combination of audiovisual cues in a referential context, under multiple sources of uncertainty. More precisely, we tested if the cue combination was statistically optimal. Besides, we quantified any sub-optimality that might have been induced, among other things, by the suggested privileged status of speech or by the arbitrariness of the referential associations. To test optimality, we characterized uncertainty in each modality with a probability distribution, and we predicted responses by combining these probabilities in an optimal way. To study possible patterns of sub-optimality, we compared the optimal model to a descriptive model where the parameters of the bimodal probability distributions were fitted to human judgements. We tested the model's predictions in three behavioral experiments where we varied the source of uncertainty. In Experiment 1, audio-visual tokens were ambiguous with respect to their category membership. In Experiment 2, we intervened by adding background noise to the auditory modality, and in Experiment 3, we intervened by adding background noise to the visual modality. In all Experiments, participants were quantitatively near-optimal, though precision dropped slightly in the bimodal condition. Moreover, in Experiment 1 where neither of the modalities was perturbed with background noise, participants weighed auditory and visual cues according to the relative reliability predicted by the optimal model. In other words, we found no evidence for a modality bias towards either the auditory or the visual modality. However, In Experiment 2 and 3, participants over-relied on one modality when the other modality was perturbed with additional noise.  Finally, we discuss the broad implications of these results, especially in relation to some developmental findings in early word learning [e.g., @stager1997].

# Model

In this section we describe the multimodal integration model. First, we briefly introduce the experimental paradigm, and second we explain how this paradigm can be modeled in a probabilistic framework.

## The Audio-Visual Word Recognition Task

We introduce a new task that tests word recognition in a referential context.  We use two visual categories (cat and dog) and two auditory categories (/b/ and /d/ embedded in the minimal pair /aba/-/ada/). For each participant, an arbitrary pairing is set between the auditory and the visual categories, leading to two audio-visual word categories (e.g., dog-/aba/, cat-/ada/).

In each trial, participants are presented with an audio-visual target (the prototype of the target category), immediately followed by an audio-visual test stimulus (Figure\ \@ref(fig:task)). The test stimulus may differ from the target in both the auditory and the visual components.  After these two presentations, participants press "same" or "different".

```{r task, fig.cap = "Overview of the task. In the audio-visual condition, participants are first presented with an audio-visual target (the prototype of the target category), immediately followed by an audio-visual test. The test may differ from the target in both the auditory and the visual components. After these two presentations, participants press same' (i.e., the same category as the target) or `different' (not the same category). The auditory-only and visual-only conditions are similar, expect only the sounds are heard, or only the pictures are shown, respectively.", fig.align = "center", out.width = "400px"}
knitr::include_graphics("pictures/task.png", dpi = 108)
```

This itask is similar to the task introduced by @sloutsky2003. However, in that study, as well as subsequent ones, participants were asked whether or not the two audio-visual presentations were *identical*. Such task would allow us to probe audio-visual encoding, but not necessarily speech perception. The latter requires---in addition to the perceptual encoding---a categorical judgement, i.e, determining wheather two similar tokens are members of the same phonological/semantic category. Thus, our task is category-based: participants are asked to press "same" if they think the second item (the test) belonged to the same category as the first (target) (e.g.,  dog-/aba/), even if there is a slight difference in the word, in the referent, or in both. They are instructed to press "different" only if they think that the second stimulus was an instance of the other word category (cat-/ada/).

We assume, for the sake of simplicity, that category tokens vary along a single dimension. Phonetic tokens are sampled from an acoustic continuum linking /aba/ to /aba/, and obtained by continuously varying the value of the second formant [@vroomen2004]. Visual tokens are sampled from a morph continuum linking the picture of a dog and the picture of a cat [@freedman2001].

The task also includes trials where pictures are hidden (audio-only) or where sounds are muted (visual-only). These unimodal trials provide us with participants' categorization functions for the auditory and visual categories and are used as inputs to the optimal model, described below.

## Optimal Model

The basis of our optimal model is that individual probabilistic representations from each modality should be combined optimally. First we describe how probabilistic representations in each modality are derived/fitted, and second we explain how they are combined to yield optimal predictions.

### Unimodal representations

In each modality, we have two categories: /ada/ ($A=1$) and /aba/ ($A=2$) in the auditory dimension, and *cat* ($V=1$) and *dog* ($V=2$) in the visual dimension.

We assume the probability of membership in each category is normally distributed:

$$ p(a | A) \sim  N(\mu_A, \sigma^2_A) $$
$$ p(v | V) \sim  N(\mu_V, \sigma^2_V) $$
The parameters of these distributions are fitted to the participants' judgement in the unimodal case, i.e., when they only hear the sounds, and when they only see the objects. For an ideal recognizer, the probability of choosing category 2 (that is, to answer "different") when presented with, say, an audio instance $a$, is the posterior probability of this category $p(A_2|a)$. If we assume that both categories have equal variances, the posterior probability reduces to:

$$p(A_2 | a)=\frac{1}{1+(1+\epsilon_A)\exp(\beta_{a0}+\beta_aa)}$$

with $\beta_a=\frac{\mu_{A_1}-\mu_{A_2}}{\sigma^2_{A}}$, $\beta_{a0}=\frac{\mu^2_{A_2}-\mu^2_{A_1}}{2\sigma^2_{A}}$, and $1+\epsilon_A=\frac{p(A_1)}{p(A_2)}$ is the proportion of the prior probabilities. If the identity of the auditory categories is randomized, and if $A_1$ is the target, then $\epsilon$ measures a response bias to "same" if $\epsilon > 0$, and a response bias to "different" if $\epsilon < 0$.

We modeled the visual representation in exactly the same way.

### Optimal model

In the bimodal condition, participants see audio-visual tokens. They have to combine information from both modalities and make a categorical decision. How can this task be characterized in a formal way, and what would be the optimal behavior? Work on multisensory integration generally considers the outcome of multiplying the distributions derived from each modality [e.g., @ernst02]. However, this way of combining multi-modal cues is more adequate to examine continuous perceptual dimensions (e.g., size). It is less applicable to categorical dimensions (e.g., phonemes) [see @bejjanki2011; @Bankieris17 for futher detail]

<!-- more adequate to the case of redundant information, where, for instance, cues are in the same units, the same coordinates and about the same aspect of the environmental property. It is less adequate to describe the case of arbitrary associations where cues are in different units, coordinate systems, or about complementary aspects of the same environmental property [see @ernst04 for further detail]. -->

We followed a formal approach similar in spirit to the one adopted by @bejjanki2011. In this approach, the bimodal optimal distribution is defined, not as the product of the unimodal distribution $p(A)$ and $p(V)$, but as their joint distribution in a higher dimensional space, which we call the audio-visual space.  Thus, a word token is defined as a vector in this space, $w=(a,v)$, and a word category $W$ can be characterized with a bivariate normal distribution:
$$ p(w | W) \sim  N(M_W, \Sigma_W) $$
```{r model, fig.cap = "Illustration of the model using simulated data. A word category is defined as the joint bivariate distribution of an auditory category (horizontal, bottom panel) and a visual semantic category (vertical, left panel). Upon the presentation of a word token $w$, participants guess whether it is sampled from the word type $W_1$ or from the word type $W_2$. Decision threshold is where the guessing probability is 0.5.", fig.align = "center", out.width = "400px"}
knitr::include_graphics("pictures/model.png", dpi = 108)
```

We have two word categories: dog-/aba/ ($W_1$) and cat-/ada/ ($W_2$). Participants can be understood as choosing one of these two word categories (Figure\ \@ref(fig:model)). For an ideal observer, the probability of choosing category 2 when presented with an audio-visual instance $w=(a,v)$ is the posterior probability of this category:

$$
p(W_2 | w)=\frac{p(w|W_2)p(W_2)}{p(w|W_2)p(W_2)+p(w|W_1)p(W_1)}
$$
We make the assumption that, given a particular word category, the auditory and visual tokens are independent:

$$p(w | W) = p(a,v| W) = p(a| W)p(v| W)$$
This assumptions simply says that, given a word-object mapping, e.g., W=("bee"-BEE), variation in the way "bee" is pronounced does not correlate with changes in any visual property of the object BEE\footnote{Note that this assumptions is more adequate to the case of arbitrary associations such as ours, and less so in the case of redundant association such as audio-visual speech. In the latter, variation in the pronounciation is expected to correlate, at least to some extent, with lip movements.}.

Under this assumption, the posterior probability reduces to:
$$ p(W_2 | w)=\frac{1}{1+(1+\epsilon)\exp(\beta_0+\beta_aa+\beta_vv)}$$

with $\beta_a=\frac{\mu_{A1}-\mu_{A2}}{\sigma^2_{A}}$,
$\beta_v=\frac{\mu_{V1}-\mu_{V2}}{\sigma^2_{V}}$, $\beta_0=\frac{\mu^2_{A2}-\mu^2_{A1}}{2\sigma^2_{A}}+\frac{\mu^2_{V2}-\mu^2_{V1}}{2\sigma^2_{V}}$ 
and $1+\epsilon=\frac{p(W_1)}{p(W_2)}$ is the proportion of the prior probabilities. If the identity of word categories is randomized, and if $W_1$ is the target, then $\epsilon$ measures a response bias to "same" if $\epsilon > 0$, and a response bias to "different" if $\epsilon < 0$. We expect a general bias towards answering "different" because of the categorical nature of our same-different task: when two items are ambiguous but perceptually different, this could cause a slight preference for "different" over "same".

We fix the values of the means to be the endpoints of the corresponding continuum. For example, if both the auditory and visual continua are made of 5 steps going from 0 to 4, then $\mu_{A1}=0$ and $\mu_{A2}=4$ (and similarly $\mu_{V1}=0$, and $\mu_{V2}=4$). When we fix th values of the means, observations from each modality ($a$ and $v$) become weighted according to their reliability, i.e., in the posterior we have $\beta_a \propto \frac{1}{\sigma^2_{A}}$ and $\beta_v \propto \frac{1}{\sigma^2_{V}}$ for the auditory and visual token, respectively.

## Auditory and Visual baselines

The posterior provides the optimal model's predictions for how probabilities that characterize uncertainty in each modality can be combined to make categorical decision about the bimodal input. The predictions of the optimal model will be compared to human responses in the bimodal case. Besides the optimal model, we also test the predictions of two baselines models: the **visual model**, which assumes that participants rely only on visual information, and the **auditory model**, which assumes that participants rely only on auditory information. If participants rely on both the auditory and the visual modalities, the optimal model would explain more variance in human responses than  the visual model alone or the auditory model alone.

## Descriptive model

The visual, auditory, and optimal models are *normative* models. Their predictions are made about human data in the bimodal condition, although their crucial parameters (i.e., variances associated with the visual and auditory modalities) are derived from data in the unimodal conditions.
In addition to these normative models, we consider a *descriptive* model. The parameters of this model are fitted to human data in the bimodal condition. If the referential task induces sub-optimality (due, for instance, to the arbitrary nature of the sound-object association), then we predict the descriptive model to explain more variance than the optimal model does.

A systematic comparison of the optimal and the descriptive models would allow us, not only to quantify how much people deviate from optimality, but also to understand qualitatively how they deviate from this optimality. Let $\sigma^2_{A}$ and $\sigma^2_{V}$ be the values of the variances used in the optimal model (derived from the unimodal conditions), and $\sigma^2_{Ab}$ and $\sigma^2_{Vb}$ be the values observed through the descriptive model in the bimodal condition. There are three possible cases of sub-optimality:

1) Precision decreases equally for both modalities. That is, $\frac{1}{\sigma^2_{Ab}} < \frac{1}{\sigma^2_{A}}$ and $\frac{1}{\sigma^2_{Vb}} < \frac{1}{\sigma^2_{V}}$, but  $\frac{\sigma^2_{Ab}}{\sigma^2_{Vb}} \approx \frac{\sigma^2_{A}}{\sigma^2_{V}}$. In this case, sub-optimality would be due to increased randomness in human responses in the bimodal condition. However, this randomness would not affect the relative weighting of both modalities, i.e., participants would still weigh modalities according to the relative reliability predicted by the optimal model.

2) The precision of the auditory modality decreases at a higher rate.  That is, $\frac{1}{\sigma^2_{Ab}} \ll \frac{1}{\sigma^2_{A}}$ and $\frac{1}{\sigma^2_{Vb}} \leq \frac{1}{\sigma^2_{V}}$, leading to $\frac{\sigma^2_{Ab}}{\sigma^2_{Vb}} > \frac{\sigma^2_{A}}{\sigma^2_{V}}$. In this case, sub-optimally would consist not only in participants being more random in the bimodal condition, but also in them thaving a systematic preference for the visual modality, even after accounting for informational reliability.

3) The precision of the visual modality decreases at a higher rate. That is, $\frac{1}{\sigma^2_{Vb}} \ll \frac{1}{\sigma^2_{V}}$, and  $\frac{1}{\sigma^2_{Ab}} \leq \frac{1}{\sigma^2_{A}}$, leading to $\frac{\sigma^2_{Ab}}{\sigma^2_{Vb}} > \frac{\sigma^2_{A}}{\sigma^2_{V}}$. This case is the reverse of case 2, i.e., in addition to increased randomness in the bimodal condition, there is a systematic preference for the auditory modality, even after accounting for informational reliability.

A more principled way to understand these three cases of sub-optimality, especially with regard to modality preference, is to study deviations from the optimal decision threshold. The decision threshold is defined as the set of values in the audio-visual space along which the posterior is equal to 0.5. The decision threshold takes the following form:

$$v=-\frac{\sigma^2_V}{\sigma^2_A}a+v_0$$

If the slope derived from the descriptive model is greater than the slope of the optimal model, the corresponding shift in the decision threshold indicate that participants have a preference for the auditory modality in the bimodal case. similarly, a smaller slope would lead to a preference for the visual modality. The limit cases are when there is exclusive reliance on the auditory cue (a vertical line), and where there is exclusive reliance on the visual (a horizontal line). Figure\ \@ref(fig:subOptim) illustrate the three cases of sub-optimality discussed above.

```{r subOptim, fig.cap = "Illustration using simulated data showing the prediction of the optimal model (top), and three possible ways human responses, as characterized by the descriptive model, can deviate from the optimal predictions (bottom). There are three possible cases of sub-optimlaity: 1) the precision drops equally for both modalities, and the cue weighing is still optimal (bottom, left), 2) the precision of the visual modality drops at a higher rate, leading to bias towards the auditory modality (bottom, middle), and 3) the precision of the auditory modality drops at a higher rate, leading to bias towards the visual modality (bottom, right)", fig.align = "center", out.width = "400px"}
knitr::include_graphics("pictures/sub-optimal", dpi = 108)
```

In the following, we test these predictions in three Experiments. In Experiment 1, we study the case where bimodal uncertainty is due to ambiguity in terms of category membership, without any additional background noise. In Experiment 2 and 3 we add background noise on top of ambiguity in category membership. In Experiment 2 we add background noise to the auditory modality, and in Experiment 3 we add background noise to the visual modality.

# Experiment 1

In this Experiment, we start with testing the predictions in the case where uncertainty is due to ambiguity in terms of category membership, without any additional noise in the background.

## Methods

### Participants:

We recruited a planned sample of `r N_all_1` participants from Amazon Mechanical Turk. Only participants with US IP addresses and a task approval rate above 85\% were allowed to participate. They were paid at an hourly rate of \$6/hour. participants were excluded if they took the experiment more than once (N=`r  N_twice_1`), then if they reported having experienced a technical problem of any sort during the online experiment (N=`r N_all_1 - N_noProb_1`), and finally if they had less than 50\% accurate responses on the unambiguous training trials (N=`r N_noProb_1 - N_good_1`). The final sample consisted of (N = `r N_good_1`) participants\footnote{The sample size and exclusion criteria were specified in the pre-registration at https://osf.io/h7mzp/}.

### Stimuli:
For auditory stimuli, we used the continuum introduced in @vroomen2004, a 9-point /aba/--/ada/ speech continuum created by varying the frequency of the second (F2) formant in equal steps. We selected 5 equally spaced points from the original continuum by keeping the endpoints (prototypes) 1 and 9, as well as points 3, 5, and 7 along the continuum. For visual stimuli, we used a morph continuum introduced in @freedman2001. From the original 14 points, we selected 5 points as follows: we kept the item that seemed most ambiguous (point 8), the 2 preceding points (i.e., 7 and 6) and the 2 following points (i.e., 9 and 10). The 6 and 10 points along the morph were quite distinguishable, and we took them to be our prototypes.

### Design and Procedure
We told participants that an alien was naming two objects: a dog, called "aba"" in the alien language, and a cat, called "ada". In each trial, we presented the first object (the target) on the left side of the screen simultaneously with the corresponding sound. The target was always the same (e.g., dog-/aba/). The second sound-object pair (the test) followed on the other side of the screen after 500ms and varied in its category membership. For both the target and the test, visual stimuli were present for the duration of the sound clip ($\sim$ 800ms). We instructed participants to press "S" for same if they thought the alien was naming another dog-/aba/, and "D" for different if they thought the alien was naming a cat-/ada/. For each participant, we randomized the sound-object mapping as well as the identity of the target.

The first part of the experiment trained participants using only the prototype pictures and the prototype sounds (12 trials, 4 each from the bimodal, audio-only, and visual-only conditions). After completing training, we instructed participants on the structure of the task and encouraged them to base their answers on both the sounds and the pictures (in the bimodal condition). There were a total of 25 possible combinations in the bimodal condition, and 5 in each of the unimodal conditions. Each participant saw each possible trial twice, for a total of 70 trials/participant. Trials were blocked by condition and blocks were presented in random order.

## Results and analysis

```{r echo=FALSE}

#Bootstrap sample parameters

lmfit <- function(data, indices) {

  myd = data[indices, ]

  s_data <- myd %>%
    filter(condition == "sound")

  v_data <- myd %>%
    filter(condition == "concept")

  j_data <- myd %>%
    filter(condition == "joint")

  s_nl <- nls(answer ~ 1/(1+(1-e)*exp((-4/vrA)*sound_dist+(8/vrA))), data=s_data, start = list(e=0, vrA=2), nls.control(warnOnly = TRUE))

 c_nl <- nls(answer ~ 1/(1+(1-e)*exp((-4/vrV)*concept_dist+(8/vrV))), data=v_data, start = list(e=0, vrV=2), nls.control(warnOnly = TRUE))

 j_nl <- nls(answer ~ 1/(1+(1-e)*exp((-4/vrA_j)*sound_dist+(-4/vrV_j)*concept_dist+(8/vrA_j)+(8/vrV_j))), data=j_data, start = list(e=0, vrA_j=2, vrV_j=2), nls.control(warnOnly = TRUE))

  s_va <- coef(s_nl)["vrA"]
  s_e <- coef(s_nl)["e"]

  v_va <- coef(c_nl)["vrV"]
  v_e <- coef(c_nl)["e"]

  decision_ideal=v_va/s_va

  j_va_s=coef(j_nl)["vrA_j"]
  j_va_v=coef(j_nl)["vrV_j"]
  j_e=coef(j_nl)["e"]

  decision_fit=j_va_v/j_va_s

  preference = decision_fit/decision_ideal

  MyBoot=c(s_va, s_e, v_va, v_e, j_va_s, j_va_v, j_e, decision_ideal, decision_fit, preference)

  return(MyBoot)

  }

results1 <- boot(data=exp1_good, statistic = lmfit, R = 10000)

#Auditory variance:
audVar=boot.ci(results1, index = 1, type = c("bca"), conf = 0.95)
audVar_val=audVar$t0 
audVar_ci1=audVar$bca[4]
audVar_ci2=audVar$bca[5]

#Auditory bias:
audBias=boot.ci(results1, index = 2, type = c("bca"), conf = 0.95)
audBias_val=audBias$t0 
audBias_ci1=audBias$bca[4]
audBias_ci2=audBias$bca[5]

#Visual variance:
visVar=boot.ci(results1, index = 3, type = c("bca"), conf = 0.95)
visVar_val=visVar$t0 
visVar_ci1=visVar$bca[4]
visVar_ci2=visVar$bca[5]

#Visual bias:
visBias=boot.ci(results1, index = 4, type = c("bca"), conf = 0.95)
visBias_val=visBias$t0 
visBias_ci1=visBias$bca[4]
visBias_ci2=visBias$bca[5]

#Bimodal Auditory variance:
audVarBi=boot.ci(results1, index = 5, type = c("bca"), conf = 0.95)
audVarBi_val=audVarBi$t0 
audVarBi_ci1=audVarBi$bca[4]
audVarBi_ci2=audVarBi$bca[5]

#Bimodal Visual variance:
visVarBi=boot.ci(results1, index = 6, type = c("bca"), conf = 0.95)
visVarBi_val=visVarBi$t0 
visVarBi_ci1=visVarBi$bca[4]
visVarBi_ci2=visVarBi$bca[5]

#Bimodal bias:
BiasBi=boot.ci(results1, index = 7, type = c("bca"), conf = 0.95)
BiasBi_val=BiasBi$t0 
BiasBi_ci1=BiasBi$bca[4]
BiasBi_ci2=BiasBi$bca[5]

#Ideal modality wieghing
prefIdeal=boot.ci(results1, index = 8, type = c("bca"), conf = 0.95)
prefIdeal_val=prefIdeal$t0 
prefIdeal_ci1=prefIdeal$bca[4]
prefIdeal_ci2=prefIdeal$bca[5]

#fit modality wieghing
prefFit=boot.ci(results1, index = 9, type = c("bca"), conf = 0.95)
prefFit_val=prefFit$t0 
prefFit_ci1=prefFit$bca[4]
prefFit_ci2=prefFit$bca[5]

#Modality bias 
bias=boot.ci(results1, index = 10, type = c("bca"), conf = 0.95)
bias_val_1=bias$t0 
bias_ci1_1=bias$bca[4]
bias_ci2_1=bias$bca[5]

```

### Unimodal conditions

```{r}

#Fit the non-linear function

##Experiment 1
#############
sound_nl1 <- nls(answer ~ 1/(1+(1-e)*exp((-4/vrA)*sound_dist+(8/vrA))), data=sound_all_exp1, start = list(e=0, vrA=2))

concept_nl1 <- nls(answer ~ 1/(1+(1-e)*exp((-4/vrV)*concept_dist+(8/vrV))), data=concept_all_exp1, start = list(e=0, vrV=2))

joint_nl1 <- nls(answer ~ 1/(1+(1-e)*exp((-4/vrA_j)*sound_dist+(-4/vrV_j)*concept_dist+(8/vrA_j)+(8/vrV_j))), data=joint_all_exp1, start = list(e=0, vrA_j=2, vrV_j=2))

##extract coefficient
eA_nl1 <- coef(sound_nl1)["e"]
vrA_nl1 <- coef(sound_nl1)["vrA"]

eV_nl1 <- coef(concept_nl1)["e"]
vrV_nl1 <- coef(concept_nl1)["vrV"]

eJ_nl1 <- coef(joint_nl1)["e"]
vrJ_A_nl1 <- coef(joint_nl1)["vrA_j"]
vrJ_V_nl1 <- coef(joint_nl1)["vrV_j"]
#######

x <- seq(0, 4, 0.01)

y_sound_nl1 <- predict(sound_nl1, list(sound_dist = x), type="response")
y_concept_nl1 <- predict(concept_nl1, list(concept_dist = x), type="response")

uniS_nl1 <- data.frame(distance=x, prediction=y_sound_nl1) %>%
  mutate(Condition = 'Auditory', 
         Experiment ='Experiment 1')

uniV_nl1 <- data.frame(distance=x, prediction=y_concept_nl1) %>%
  mutate(Condition = 'Visual',
         Experiment ='Experiment 1')

##Experiment 2
###############

sound_nl2 <- nls(answer ~ 1/(1+(1-e)*exp((-4/vrA)*sound_dist+(8/vrA))), data=sound_all_exp2, start = list(e=0, vrA=2))

concept_nl2 <- nls(answer ~ 1/(1+(1-e)*exp((-4/vrV)*concept_dist+(8/vrV))), data=concept_all_exp2, start = list(e=0, vrV=2))

joint_nl2 <- nls(answer ~ 1/(1+(1-e)*exp((-4/vrA_j)*sound_dist+(-4/vrV_j)*concept_dist+(8/vrA_j)+(8/vrV_j))), data=joint_all_exp2, start = list(e=0, vrA_j=2, vrV_j=2))

##extract coefficient
eA_nl2 <- coef(sound_nl2)["e"]
vrA_nl2 <- coef(sound_nl2)["vrA"]

eV_nl2 <- coef(concept_nl2)["e"]
vrV_nl2 <- coef(concept_nl2)["vrV"]

eJ_nl2 <- coef(joint_nl2)["e"]
vrJ_A_nl2 <- coef(joint_nl2)["vrA_j"]
vrJ_V_nl2 <- coef(joint_nl2)["vrV_j"]
#######

x <- seq(0, 4, 0.01)

y_sound_nl2 <- predict(sound_nl2, list(sound_dist = x), type="response")
y_concept_nl2 <- predict(concept_nl2, list(concept_dist = x), type="response")

uniS_nl2 <- data.frame(distance=x, prediction=y_sound_nl2) %>%
  mutate(Condition = 'Auditory', 
         Experiment ='Experiment 2')

uniV_nl2 <- data.frame(distance=x, prediction=y_concept_nl2) %>%
  mutate(Condition = 'Visual', 
         Experiment ='Experiment 2')

##Experiment 3
###############

sound_nl3 <- nls(answer ~ 1/(1+(1-e)*exp((-4/vrA)*sound_dist+(8/vrA))), data=sound_all_exp3, start = list(e=0, vrA=2))

concept_nl3 <- nls(answer ~ 1/(1+(1-e)*exp((-4/vrV)*concept_dist+(8/vrV))), data=concept_all_exp3, start = list(e=0, vrV=2))

joint_nl3 <- nls(answer ~ 1/(1+(1-e)*exp((-4/vrA_j)*sound_dist+(-4/vrV_j)*concept_dist+(8/vrA_j)+(8/vrV_j))), data=joint_all_exp3, start = list(e=0, vrA_j=2, vrV_j=2))

##extract coefficient
eA_nl3 <- coef(sound_nl3)["e"]
vrA_nl3 <- coef(sound_nl3)["vrA"]

eV_nl3 <- coef(concept_nl3)["e"]
vrV_nl3 <- coef(concept_nl3)["vrV"]

eJ_nl3 <- coef(joint_nl3)["e"]
vrJ_A_nl3 <- coef(joint_nl3)["vrA_j"]
vrJ_V_nl3 <- coef(joint_nl3)["vrV_j"]
#######

x <- seq(0, 4, 0.01)

y_sound_nl3 <- predict(sound_nl3, list(sound_dist = x), type="response")
y_concept_nl3 <- predict(concept_nl3, list(concept_dist = x), type="response")

uniS_nl3 <- data.frame(distance=x, prediction=y_sound_nl3) %>%
  mutate(Condition = 'Auditory', 
         Experiment ='Experiment 3')

uniV_nl3 <- data.frame(distance=x, prediction=y_concept_nl3) %>%
  mutate(Condition = 'Visual', 
         Experiment ='Experiment 3')

all_uni_model <- bind_rows(uniS_nl1, uniV_nl1,
                           uniS_nl2, uniV_nl2,
                           uniS_nl3, uniV_nl3)

all_plot <- ggplot(exp_uni_data, 
       aes(x = distance, y = mean)) + 
  geom_point()+
  #geom_pointrange(aes(ymin = summary_ci_lower, ymax = summary_ci_upper), 
  #                position = position_dodge(width = .1)) + 
  #geom_line(data=uniV,aes(x=xV, y=yV))+
  geom_line(data=all_uni_model, aes(x=distance, y=prediction), col='black')+
  xlab("Distance") +ylab("Prob. different")+
  scale_y_continuous(limits = c(0, 1))+#theme(aspect.ratio = 0.7)+
  theme(aspect.ratio = 0.7) + facet_grid(Experiment ~ Condition)
  #stat_function(fun = Logistic_v, colour="red"))

```

```{r unimodal, fig.cap = "Dots represent the proportion of `different' to `same' responses in the auditory-only condition (left), and visual-only condition (right), across the three Experiments. Error bars are 0.95 confidence intervals. Solid lines represent logistic fits.", fig.align = "center", out.width = "400px"}

all_plot

```

We first analysed the unimodal cases. These are the cases where the pictures were hidden, or where the sounds were muted. Average categorization judgments and fits are shown in Figure\ \@ref(fig:unimodal). The categorization function of the auditory condition was slightly steeper than that of the visual condition, meaning that participants perceived the sound tokens slightly more categorically and whih higher certainty than they did with the visual tokens.

Since we fixed the values of the means to be the endpoints of the corresponding continuum: $\mu_{A1}=0$ and $\mu_{A2}=4$ (and similarly $\mu_{V1}=0$, and $\mu_{V2}=4$), this leaves us with two free parameters: the bias and the variance. To determine the values of these parameters, we fit a model for each modality, collapsed across all participants. For the auditory modality, we obtained\footnote{all CIs in the paper are 95% confidence intervals} $\epsilon_A=$ `r audBias_val` CI [`r audBias_ci2`, `r audBias_ci1`] and $\sigma^2_A=$ `r audVar_val` CI [`r audVar_ci1`, `r audVar_ci2`]. For the visual modality, we obtained $\epsilon_V=$ `r visBias_val` CI [`r visBias_ci2`, `r visBias_ci1`] and $\sigma^2_V=$ `r visVar_val` CI [`r visVar_ci1`, `r visVar_ci2`]`.

### Bimodal condition

```{r  echo=FALSE}

#All models

##Experiment 1
##############

#The fit
model_fit1 <- function (x,y) {
   1/(1 + (1-eJ_nl1)*exp((-4/vrJ_A_nl1)*x+(-4/vrJ_V_nl1)*y+(8/vrJ_A_nl1)+(8/vrJ_V_nl1)))
}

#The ideal
model_ideal1 <- function (x,y) {
    1/(1 + (1-eJ_nl1)*exp((-4/vrA_nl1)*x+(-4/vrV_nl1)*y+(8/vrA_nl1)+(8/vrV_nl1)))
}

#The sound-only model
model_sound1 <- function (x,y) {
  1/(1 + (1-eJ_nl1)*exp((-4/vrA_nl1)*x+(8/vrA_nl1)))
}

#The visual-only model
model_concept1 <- function (x,y) {
  1/(1 + (1-eJ_nl1)*exp((-4/vrV_nl1)*y+(8/vrV_nl1)))
}

##Experiment 2
##############

#The fit
model_fit2 <- function (x,y) {
   1/(1 + (1-eJ_nl2)*exp((-4/vrJ_A_nl2)*x+(-4/vrJ_V_nl2)*y+(8/vrJ_A_nl2)+(8/vrJ_V_nl2)))
}

#The ideal
model_ideal2 <- function (x,y) {
    1/(1 + (1-eJ_nl2)*exp((-4/vrA_nl2)*x+(-4/vrV_nl2)*y+(8/vrA_nl2)+(8/vrV_nl2)))
}

#The sound-only model
model_sound2 <- function (x,y) {
  1/(1 + (1-eJ_nl2)*exp((-4/vrA_nl2)*x+(8/vrA_nl2)))
}

#The visual-only model
model_concept2 <- function (x,y) {
  1/(1 + (1-eJ_nl2)*exp((-4/vrV_nl2)*y+(8/vrV_nl2)))
}

##Experiment 3
##############

#The fit
model_fit3 <- function (x,y) {
   1/(1 + (1-eJ_nl3)*exp((-4/vrJ_A_nl3)*x+(-4/vrJ_V_nl3)*y+(8/vrJ_A_nl3)+(8/vrJ_V_nl3)))
}

#The ideal
model_ideal3 <- function (x,y) {
    1/(1 + (1-eJ_nl3)*exp((-4/vrA_nl3)*x+(-4/vrV_nl3)*y+(8/vrA_nl3)+(8/vrV_nl3)))
}

#The sound-only model
model_sound3 <- function (x,y) {
  1/(1 + (1-eJ_nl3)*exp((-4/vrA_nl3)*x+(8/vrA_nl3)))
}

#The visual-only model
model_concept3 <- function (x,y) {
  1/(1 + (1-eJ_nl3)*exp((-4/vrV_nl3)*y+(8/vrV_nl3)))
}

```

```{r echo=FALSE, fig.width=7, fig.height=8}

models_exp1 <- joint_exp1 %>% 
  rename(joint = mean) %>%
  mutate(Descriptive = model_fit1(sound_dist, concept_dist)) %>%
  mutate(Optimal = model_ideal1(sound_dist, concept_dist)) %>%
  mutate(Auditory = model_sound1(sound_dist, concept_dist)) %>%
  mutate(Visual = model_concept1(sound_dist, concept_dist)) %>%
  gather(model, pred, Visual, Auditory, Optimal, Descriptive) %>%
  mutate(experiment = 'Experiment 1')

models_exp2 <- joint_exp2 %>% 
  rename(joint = mean) %>%
  mutate(Descriptive = model_fit2(sound_dist, concept_dist)) %>%
  mutate(Optimal = model_ideal2(sound_dist, concept_dist)) %>%
  mutate(Auditory = model_sound2(sound_dist, concept_dist)) %>%
  mutate(Visual = model_concept2(sound_dist, concept_dist)) %>%
  gather(model, pred, Visual, Auditory, Optimal, Descriptive) %>%
  mutate(experiment = 'Experiment 2')

models_exp3 <- joint_exp3 %>% 
  rename(joint = mean) %>%
  mutate(Descriptive = model_fit3(sound_dist, concept_dist)) %>%
  mutate(Optimal = model_ideal3(sound_dist, concept_dist)) %>%
  mutate(Auditory = model_sound3(sound_dist, concept_dist)) %>%
  mutate(Visual = model_concept3(sound_dist, concept_dist)) %>%
  gather(model, pred, Visual, Auditory, Optimal, Descriptive) %>%
  mutate(experiment = 'Experiment 3')

models_all <- bind_rows (models_exp1, models_exp2, models_exp3)

models_all$model <- factor(models_all$model, levels = c('Visual','Auditory', 'Optimal', 'Descriptive'))

correlation_plot <- ggplot(models_all, 
       aes(x = pred, y = joint, col = factor(concept_dist), 
           shape = factor(sound_dist))) + 
  geom_point()+
 #geom_pointrange(aes(ymin = summary_ci_lower, ymax = summary_ci_upper), 
  #                position = position_dodge(width = .1), size=0.2) +

  geom_abline(slope = 1, lty = 2) +
  xlab("Predictions") +ylab("Human data")+
  facet_grid(experiment ~ model)+
theme(aspect.ratio = 0.7, 
      axis.text=element_text(size=6),
      strip.text.y = element_text(size = 8))+
  guides(color=guide_legend(title="Visual Distance")) +
  guides(shape=guide_legend(title="Auditory Distance"))

#Correlation values

#Exp 1
optimal_1 <- subset(models_all, model=='Optimal' & experiment=='Experiment 1')
descriptive_1 <- subset(models_all, model=='Descriptive' & experiment=='Experiment 1')
auditory_1 <- subset(models_all, model=='Auditory' & experiment=='Experiment 1')
visual_1 <- subset(models_all, model=='Visual' & experiment=='Experiment 1')

R2_optimal_1  <- cor(optimal_1$joint, optimal_1$pred)^2 %>%
  round(2)
R2_descriptive_1 <- cor(descriptive_1$joint, descriptive_1$pred)^2 %>%
  round(2)
R2_auditory_1  <- cor(auditory_1$joint, auditory_1$pred)^2 %>%
  round(2)
R2_visual_1  <- cor(visual_1$joint, visual_1$pred)^2 %>%
  round(2)

#Exp 2
optimal_2 <- subset(models_all, model=='Optimal' & experiment=='Experiment 2')
descriptive_2 <- subset(models_all, model=='Descriptive' & experiment=='Experiment 2')
auditory_2 <- subset(models_all, model=='Auditory' & experiment=='Experiment 2')
visual_2 <- subset(models_all, model=='Visual' & experiment=='Experiment 2')

R2_optimal_2  <- cor(optimal_2$joint, optimal_2$pred)^2  %>%
  round(2)
R2_descriptive_2 <- cor(descriptive_2$joint, descriptive_2$pred)^2 %>%
  round(2)
R2_auditory_2  <- cor(auditory_2$joint, auditory_2$pred)^2 %>%
  round(2)
R2_visual_2  <- cor(visual_2$joint, visual_2$pred)^2 %>%
  round(2)

#Exp 3
optimal_3 <- subset(models_all, model=='Optimal' & experiment=='Experiment 3')
descriptive_3 <- subset(models_all, model=='Descriptive' & experiment=='Experiment 3')
auditory_3 <- subset(models_all, model=='Auditory' & experiment=='Experiment 3')
visual_3 <- subset(models_all, model=='Visual' & experiment=='Experiment 3')

R2_optimal_3  <- cor(optimal_3$joint, optimal_3$pred)^2 %>%
  round(2)
R2_descriptive_3 <- cor(descriptive_3$joint, descriptive_3$pred)^2 %>%
  round(2)
R2_auditory_3  <- cor(auditory_3$joint, auditory_3$pred)^2 %>%
  round(2)
R2_visual_3  <- cor(visual_3$joint, visual_3$pred)^2 %>%
  round(2)

```

```{r bimodal, fig.cap = "Human responses vs. models' predictions across the three Experiments. Shape represents auditory distance from the target, and color represents visual distance from the target.", fig.align = "center", out.width = "400px", fig.width=7, fig.height=8}

correlation_plot

```

Now we analyse the bimodal case. This is the case where the participants saw the pictures and heard the sounds.

#### Descriptive model
We first consider the descriptive model where all parameters are fitted to human responses in the bimodal condition. We found $\epsilon=$ `r BiasBi_val` CI [`r BiasBi_ci2`, `r BiasBi_ci1`], $\sigma^2_{Ab}=$ `r audVarBi_val` CI [`r audVarBi_ci1`, `r audVarBi_ci2`] and $\sigma^2_{Vb}=$ `r visVarBi_val` CI [`r visVarBi_ci1`, `r visVarBi_ci2`]. Note that the precision of both the auditory and visual modalities decreased compared to the unimodal conditions. The descriptive model explained `r 100*R2_descriptive_1`% of total variance.

#### Normative models
We derived the predictions of the auditory, visual and optimal model by using the values of the variances derived from the unimodal conditions, and the response bias derived from the descriptive model.  Figure\ \@ref(fig:bimodal) compares the predictions of these three models to human responses. The visual, auditory and optimal model explained, respectively, `r 100*R2_visual_1`%, `r 100*R2_auditory_1`%, and `r 100*R2_optimal_1`% of total variance.

#### Cue combination and Modality preference
We next analyzed the extent to which cue combination was performed in an optimal way, or whether there was a systematic preference for one modality when making decisions in the bimodal condition. We saw that response precision in the auditory modality was slightly higher than that of the visual modality (i.e., $\frac{1}{\sigma^2_A} > \frac{1}{\sigma^2_V}$ ). If modalities were weighed according to their relative reliability (that is, optimally), we would naturally expect the auditory modality to have a higher weight. But this is not what we mean by modality preference. Rather, the phrase refers to the case of potential sub-optimality where participants would rely on one modality beyond what is explained by the relative reliability of the optimal model.

As explained above, modality preference can be characterized formally as a deviation from the decision threshold's slope predicted by the optimal model. Figure\ \@ref(fig:bias) shows the value of the slope derived from the descriptive model (i.e., $-\frac{\sigma^2_{Vb}}{\sigma^2_{Ab}}$) relative the slope of the optimal model (i.e., $-\frac{\sigma^2_V}{\sigma^2_A}$). The red dotted line represents the case where this proportion is optimal, meaning that both slopes are equal. The blue dotted lines represents the cases where the value of the slope from the descriptive model is double or half that of the optimal model, suggesting a preference for the auditory or the visual modality, respectively. Non-parametric resampling of the data showed no evidence of a deviation from the optimal prediction.

## Discussion
Overall, we found that the optimal model explained much of the variance in judgments, and largely more than what can be explained with the auditory or the visual models alone. The relatively high value of the coefficient of determination in the optimal model (`r 100*R2_optimal_1`%) suggests that participants were near-optimal in their responses. However, we see from Figure\ \@ref(fig:bimodal) that responses deviated from the optimal prediction in that they were slightly pulled toward chance (i.e., the value 0.5). This is due to the increase in the value of the variance associated with each modality. Note however that, despite this increase in randomness, our analysis of modality preference showed that the relative values of these variances were not different Figure\ \@ref(fig:bias). Thus, 1) the bimodal presentation introduced a certain level of randomness in the participants' responses, and 2) this increased randomness did not affect the relative weighting of both modalities, i.e., participants were weighting modalities according to their relative reliability.  This situation corresponds to the first case of sub-optimally described in the predictions, above.

In Experiment 1, we tested word recognition when there was multimodal uncertainty in terms of category membership only. In real life, however, tokens can undergo distortions due to noisy factors in the environment (e.g., car noise in the background, blurry vision in a foggy weather,..)\footnote{Note that we are considering environmental noise, which is different from the noise inherent to perception.}. In Experiment 2 and 3, we explore this additional level of uncertainty.

# Experiment 2

Imagine that the speaker generates a target production $t$ from an auditory category
$t | A \sim N(\mu_{A}, \sigma^2_{A})$. In Experiment 1, we assumed that the observer could directly retrieve this production token. But if the observer is in a noisy environment, they do not hear exactly this produced target, but the target perturbed by noise. We assume this noise to be normally distributed: $a | t \sim N(t, \sigma^2_{N})$, and we integrate over $t$. We obtain the following simple expression:

$$ a | A \sim N(\mu_{A}, \sigma^2_{A}+\sigma^2_{N})$$

In this experiment, we explored the effect of this added noise on performance in our task. We tested a case where the background noise was added to the auditory modality. We were interested to know if participants would treat this new source of uncertainty as predicted by the optimal model, and whether noise in one modality would lead to some systematic preference for the non-noisy modality.

## Methods

### Participants

A sample of `r N_all_2` participants was recruited online through Amazon Mechanical Turk. We used the same exclusion criteria as in the previous experiment. The final sample consisted of (N = `r N_good_2`) participants.

### Stimuli and Procedure

We used the same visual stimuli as in Experiment 1. We also used the same auditory stimuli, but we convolved each item with Brown noise of amplitude 1 using the audio editor Audacity (2.1.2) (signal to noise ratio XXXX). The procedure was exactly the same as in the previous experiment, except that test stimuli (but not the target) were presented with the new noisy auditory stimuli.

## Results and analysis

```{r echo=FALSE}

#Bootstrap sample parameters

lmfit <- function(data, indices) {

  myd = data[indices, ]

  s_data <- myd %>%
    filter(condition == "sound")

  v_data <- myd %>%
    filter(condition == "concept")

  j_data <- myd %>%
    filter(condition == "joint")

  s_nl <- nls(answer ~ 1/(1+(1-e)*exp((-4/vrA)*sound_dist+(8/vrA))), data=s_data, start = list(e=0, vrA=2), nls.control(warnOnly = TRUE))

 c_nl <- nls(answer ~ 1/(1+(1-e)*exp((-4/vrV)*concept_dist+(8/vrV))), data=v_data, start = list(e=0, vrV=2), nls.control(warnOnly = TRUE))

 j_nl <- nls(answer ~ 1/(1+(1-e)*exp((-4/vrA_j)*sound_dist+(-4/vrV_j)*concept_dist+(8/vrA_j)+(8/vrV_j))), data=j_data, start = list(e=0, vrA_j=2, vrV_j=2), nls.control(warnOnly = TRUE))

  s_va <- coef(s_nl)["vrA"]
  s_e <- coef(s_nl)["e"]

  v_va <- coef(c_nl)["vrV"]
  v_e <- coef(c_nl)["e"]

  decision_ideal=v_va/s_va

  j_va_s=coef(j_nl)["vrA_j"]
  j_va_v=coef(j_nl)["vrV_j"]
  j_e=coef(j_nl)["e"]

  decision_fit=j_va_v/j_va_s

  preference = decision_fit/decision_ideal

  MyBoot=c(s_va, s_e, v_va, v_e, j_va_s, j_va_v, j_e, decision_ideal, decision_fit, preference)

  return(MyBoot)

  }

results1 <- boot(data=exp2_good, statistic = lmfit, R = 10000)

#Auditory variance:
audVar=boot.ci(results1, index = 1, type = c("bca"), conf = 0.95)
audVar_val=audVar$t0 
audVar_ci1=audVar$bca[4]
audVar_ci2=audVar$bca[5]

#Auditory bias:
audBias=boot.ci(results1, index = 2, type = c("bca"), conf = 0.95)
audBias_val=audBias$t0 
audBias_ci1=audBias$bca[4]
audBias_ci2=audBias$bca[5]

#Visual variance:
visVar=boot.ci(results1, index = 3, type = c("bca"), conf = 0.95)
visVar_val=visVar$t0 
visVar_ci1=visVar$bca[4]
visVar_ci2=visVar$bca[5]

#Visual bias:
visBias=boot.ci(results1, index = 4, type = c("bca"), conf = 0.95)
visBias_val=visBias$t0 
visBias_ci1=visBias$bca[4]
visBias_ci2=visBias$bca[5]

#Bimodal Auditory variance:
audVarBi=boot.ci(results1, index = 5, type = c("bca"), conf = 0.95)
audVarBi_val=audVarBi$t0 
audVarBi_ci1=audVarBi$bca[4]
audVarBi_ci2=audVarBi$bca[5]

#Bimodal Visual variance:
visVarBi=boot.ci(results1, index = 6, type = c("bca"), conf = 0.95)
visVarBi_val=visVarBi$t0 
visVarBi_ci1=visVarBi$bca[4]
visVarBi_ci2=visVarBi$bca[5]

#Bimodal bias:
BiasBi=boot.ci(results1, index = 7, type = c("bca"), conf = 0.95)
BiasBi_val=BiasBi$t0 
BiasBi_ci1=BiasBi$bca[4]
BiasBi_ci2=BiasBi$bca[5]

#Ideal modality wieghing
prefIdeal=boot.ci(results1, index = 8, type = c("bca"), conf = 0.95)
prefIdeal_val=prefIdeal$t0 
prefIdeal_ci1=prefIdeal$bca[4]
prefIdeal_ci2=prefIdeal$bca[5]

#fit modality wieghing
prefFit=boot.ci(results1, index = 9, type = c("bca"), conf = 0.95)
prefFit_val=prefFit$t0 
prefFit_ci1=prefFit$bca[4]
prefFit_ci2=prefFit$bca[5]

#Modality bias 
bias=boot.ci(results1, index = 10, type = c("bca"), conf = 0.95)
bias_val_2=bias$t0 
bias_ci1_2=bias$bca[4]
bias_ci2_2=bias$bca[5]

```

### Unimodal conditions

We fit a model for each modality, collapsed across all participants. For the auditory modality, our parameter estimates were $\epsilon_A=$ `r audBias_val` CI [`r audBias_ci2`, `r audBias_ci1`] and $\sigma^2_A+\sigma^2_N=$ `r audVar_val` CI [`r audVar_ci1`, `r audVar_ci2`]. For the visual modality, we found $\epsilon_V=$ `r visBias_val` CI [`r visBias_ci2`, `r visBias_ci1`] and $\sigma^2_V=$ `r visVar_val` CI [`r visVar_ci1`, `r visVar_ci2`].  Figure\ \@ref(fig:unimodal) shows responses in the unimodal conditions as well as the corresponding fits. The visual data is a replication of the vidual data in Experiment 1. As for the auditory data, we see that, in contrast to Experiment 1, responses were less categorical/flatter (showing more uncertainty).

### Bimodal condition

#### Descriptive model
We fit the descriptive model to human responses in the bimodal condition, collapsed across all articipants. We estimated $\epsilon=$ `r BiasBi_val` CI [`r BiasBi_ci2`, `r BiasBi_ci1`], $\sigma^2_{Ab}+\sigma^2_{Nb}=$ `r audVarBi_val` CI [`r audVarBi_ci1`, `r audVarBi_ci2`], and $\sigma^2_{Vb}=$ `r visVarBi_val` CI [`r visVarBi_ci1`, `r visVarBi_ci2`]. The fit explained `r R2_descriptive_2`% of total variance.

#### Normative models
We derived the predictions of the auditory, visual and optimal model by using the values of the variances derived from the unimodal conditions, and the response bias derived from the descriptive model. Figure\ \@ref(fig:bimodal) compares the predictions of these three models to human responses. The visual, auditory and optimal model explained, respectively, `r 100*R2_visual_2`%, `r 100*R2_auditory_2`%, and `r 100*R2_optimal_2`% of total variance. Note that, in contrast to Experiment 1, the visual model explains more variance than the auditory model.

#### Modality preferences
Participants' decision threshold suggested a preference for the visual modality (the non-noisy modality). Indeed non-parametric resampling of the data showed a decrease in the value of the slope in the descriptive model compared to the optimal model Figure\ \@ref(fig:bias).

## Discussion
We found, similar to Experiment 1, that participants were generally near optimal (explaining  `r 100*R2_optimal_2`% of total variance), and that the optimal model explained more variance than the auditory or the visual models alone.  We also found a similar discrepancy from the optimal model as precision dropped for both the auditory and the visual modalities. As for the weghting scheme used by participants, contrary to Experiment 1 where modalities were weighted according to their optimal relative reliability, we found in this experiment that the visual modality had a greater weight than what is  expected from its relative reliability. This situation corresponds to the second case of sub-optimally described in the predictions above.

In Experiment 2, we tested the case where we added background noise to the auditory modality. In Experiment 3, we test the situation where we added noise to the visual modality.

# Experiment 3

We follow exactly the same formal reasoning in this case, as we did in Experiment 2. Imagine that the speaker points towards a target referent $t_v$ from a visual category $t_v | V \sim N(\mu_{V}, \sigma^2_{V})$. If the observer is in a noisy environment (e.g., foggy weather), they might see this target referent in a blurry way. We assume the blur to be normally distributed: $a | t_v \sim N(t_v, \sigma^2_{N})$, and we integrate over $t_v$. We obtain an expression formally similar to the one obtained in Experiment 2:

$$ v | V \sim N(\mu_{V}, \sigma^2_{V}+\sigma^2_{N})$$

Below we explored the effect of this added visual blur on performance in our task.

## Methods

### Participants
A planned sample of `r N_all_3` participants was recruited online through Amazon Mechanical Turk. We used the same exclusion criteria as in the previous experiment. The final sample consisted of (N = `r N_good_3`) participants.

### Stimuli and Procedure
We used the same auditory stimuli as in Experiment 1. We also used the same visual stimuli, but we blurred the tokens using the editor XXX (signal to noise ration XXX). The experimental procedure was exactly the same as in the previous Experiments.

## Results and analysis

```{r echo=FALSE}

#Bootstrap sample parameters

lmfit <- function(data, indices) {

  myd = data[indices, ]

  s_data <- myd %>%
    filter(condition == "sound")

  v_data <- myd %>%
    filter(condition == "concept")

  j_data <- myd %>%
    filter(condition == "joint")

  s_nl <- nls(answer ~ 1/(1+(1-e)*exp((-4/vrA)*sound_dist+(8/vrA))), data=s_data, start = list(e=0, vrA=2), nls.control(warnOnly = TRUE))

 c_nl <- nls(answer ~ 1/(1+(1-e)*exp((-4/vrV)*concept_dist+(8/vrV))), data=v_data, start = list(e=0, vrV=2), nls.control(warnOnly = TRUE))

 j_nl <- nls(answer ~ 1/(1+(1-e)*exp((-4/vrA_j)*sound_dist+(-4/vrV_j)*concept_dist+(8/vrA_j)+(8/vrV_j))), data=j_data, start = list(e=0, vrA_j=2, vrV_j=2), nls.control(warnOnly = TRUE))

  s_va <- coef(s_nl)["vrA"]
  s_e <- coef(s_nl)["e"]

  v_va <- coef(c_nl)["vrV"]
  v_e <- coef(c_nl)["e"]

  decision_ideal=v_va/s_va

  j_va_s=coef(j_nl)["vrA_j"]
  j_va_v=coef(j_nl)["vrV_j"]
  j_e=coef(j_nl)["e"]

  decision_fit=j_va_v/j_va_s

  preference = decision_fit/decision_ideal

  MyBoot=c(s_va, s_e, v_va, v_e, j_va_s, j_va_v, j_e, decision_ideal, decision_fit, preference)

  return(MyBoot)

  }

results1 <- boot(data=exp3_good, statistic = lmfit, R = 10000)

#Auditory variance:
audVar=boot.ci(results1, index = 1, type = c("bca"), conf = 0.95)
audVar_val=audVar$t0 
audVar_ci1=audVar$bca[4]
audVar_ci2=audVar$bca[5]

#Auditory bias:
audBias=boot.ci(results1, index = 2, type = c("bca"), conf = 0.95)
audBias_val=audBias$t0 
audBias_ci1=audBias$bca[4]
audBias_ci2=audBias$bca[5]

#Visual variance:
visVar=boot.ci(results1, index = 3, type = c("bca"), conf = 0.95)
visVar_val=visVar$t0 
visVar_ci1=visVar$bca[4]
visVar_ci2=visVar$bca[5]

#Visual bias:
visBias=boot.ci(results1, index = 4, type = c("bca"), conf = 0.95)
visBias_val=visBias$t0 
visBias_ci1=visBias$bca[4]
visBias_ci2=visBias$bca[5]

#Bimodal Auditory variance:
audVarBi=boot.ci(results1, index = 5, type = c("bca"), conf = 0.95)
audVarBi_val=audVarBi$t0 
audVarBi_ci1=audVarBi$bca[4]
audVarBi_ci2=audVarBi$bca[5]

#Bimodal Visual variance:
visVarBi=boot.ci(results1, index = 6, type = c("bca"), conf = 0.95)
visVarBi_val=visVarBi$t0 
visVarBi_ci1=visVarBi$bca[4]
visVarBi_ci2=visVarBi$bca[5]

#Bimodal bias:
BiasBi=boot.ci(results1, index = 7, type = c("bca"), conf = 0.95)
BiasBi_val=BiasBi$t0 
BiasBi_ci1=BiasBi$bca[4]
BiasBi_ci2=BiasBi$bca[5]

#Ideal modality wieghing
prefIdeal=boot.ci(results1, index = 8, type = c("bca"), conf = 0.95)
prefIdeal_val=prefIdeal$t0 
prefIdeal_ci1=prefIdeal$bca[4]
prefIdeal_ci2=prefIdeal$bca[5]

#fit modality wieghing
prefFit=boot.ci(results1, index = 9, type = c("bca"), conf = 0.95)
prefFit_val=prefFit$t0 
prefFit_ci1=prefFit$bca[4]
prefFit_ci2=prefFit$bca[5]

#Modality bias 
bias=boot.ci(results1, index = 10, type = c("bca"), conf = 0.95)
bias_val_3=bias$t0 
bias_ci1_3=bias$bca[4]
bias_ci2_3=bias$bca[5]

```

### Unimodal conditions
We fit a model for each modality, collapsed across participants. For the auditory modality, our parameter estimates were $\epsilon_A=$ `r audBias_val` CI [`r audBias_ci2`, `r audBias_ci1`] and $\sigma^2_A=$ `r audVar_val` CI [`r audVar_ci1`, `r audVar_ci2`]. For the visual modality, we found $\epsilon_V=$ `r visBias_val` CI [`r visBias_ci2`, `r visBias_ci1`] and $\sigma^2_V+\sigma^2_N=$ `r visVar_val` CI [`r visVar_ci1`, `r visVar_ci2`].  Figure\ \@ref(fig:unimodal) shows responses in the unimodal conditions as well as the corresponding fits.
The auditory data is a replication of the auditory data in Experiment 1. As for the visual data, we see that, in contrast to Experiment 1 and 2, responses were flatter, showing much more uncertainty.

### Bimodal condition

#### Descriptive model
We fit the descriptive model to human responses in the bimodal condition, collapsed across participants. We estimated $\epsilon=$ `r BiasBi_val` CI [`r BiasBi_ci2`, `r BiasBi_ci1`], $\sigma^2_{Ab}=$ `r audVarBi_val` CI [`r audVarBi_ci1`, `r audVarBi_ci2`], and $\sigma^2_{Vb}+\sigma^2_{Nb}=$ `r visVarBi_val` CI [`r visVarBi_ci1`, `r visVarBi_ci2`]. The fit explained `r 100*R2_descriptive_3`% of total variance.

#### Normative models
We derived the predictions of the auditory, visual and optimal model by using the values of the variances derived from the unimodal conditions, and the response bias derived from the descriptive model.  Figure\ \@ref(fig:bimodal) compares the predictions of these three models to the human responses. The visual, auditory and optimal model explained, respectively, `r 100*R2_visual_3`%, `r 100*R2_auditory_3`%, and `r 100*R2_optimal_3`% of total variance.

#### Modality preferences
Participants' decision threshold suggested a preference for the auditory modality (the non-noisy modality). Indeed non-parametric resampling of the data showed an increase in the value of the slope in the descriptive model compared to the optimal model Figure\ \@ref(fig:bias).

## Discussion
We found that the optimal model accounted for almost all the variance ($r^2 =$ `r R2_optimal_3`). However, whereas in previous experiments, the optimal model explained more variance than the auditory or the visual models, here the auditory model explained at least as much variance ($r^2 =$ `r R2_auditory_3`). Thus, though participants were still sensitive to variation in the noisy visual data in the unimodal condition, they tended to ignore this information in the bimodal condition, and relied almost exclusively on the non-noisy auditory modality. This behaviour is not so much a qualitative difference from Experiment 2 (where participants relied on both the noisy and the non-noisy modality in the bimodal condition), as much as it is the result of a floor effect. Indeed, noise made the visual modality way less steep and barely perceptible in the unimodal condition Figure\ \@ref(fig:unimodal). So when we had an additional general drop in precision in the bimodal condition (similar to what we found in Experiment 1 and 2),  participants were no longer able to extract any useful information. The reason why we saw this floor effect when we added noise to the visual modality (Experiment 3), and not when added noise to the auditory modality (Experiment 2), is the fact that our visual stimuli was originally perceived less categorically and with less certainty than the auditory data was. This made it more likely for the visual categorization function to become flat and uninformative after a few drops in precision due to noise on the one had, and to the randomness induced by the arbitrary association on the other hand.

The general finding corresponds to the third case of sub-optimality described above. Indeed, precision dropped for both modalities in the bimodal condition compared to the unimodal condition. But the drop was much greater for the visual modality, resulting in a much lower weight assigned to it than what is expected from its optimal relative reliability. Therefore, just like participants over-relied on the visual modality when the auditory modality was noisy (Experiment 2), they also over-relied on the auditory modality when the visual modality was noisy (Experiment 3).

```{r }
#Modality bias

preference = c(bias_val_1, bias_val_2, bias_val_3 )
experiment =c("Exp 1 \n", "Exp 2 \n (noisy audio)", "Exp 3 \n (noisy visual)")
ci_low=c(bias_ci1_1, bias_ci1_2, bias_ci1_3)
ci_up=c(bias_ci2_1, bias_ci2_2, bias_ci2_3)

pref = data.frame(preference, ci_low, ci_up)

bias <- ggplot(pref, 
       aes(x = experiment, y=preference)) +
geom_point(size=3)+
  geom_errorbar(aes(ymin = ci_low, ymax = ci_up), 
                  width = 0.1,
                  position = position_dodge(width = 0.1))+
  geom_hline(yintercept = 1, linetype=2, color="red", size=1)+

  geom_hline(yintercept = 0.5, linetype=2, color="blue")+

  geom_hline(yintercept = 2, linetype=2, color="blue")+

  theme(aspect.ratio = 1, axis.text=element_text(size=10))+
  xlab("") +ylab("Relative weighing")+
  scale_y_log10(breaks=c(0.5,1,2),labels=c("Visual bias","Optimal","Auditory bias"))
  #coord_cartesian(ylim=c(0, 2.5))

```

```{r bias, fig.cap = "Relative weighing of evidence from the auditory stimulus vs. evidence from the visual stimulus across the three Experiments (log-scaled). The red dashed  line  shows the  prediction  of the model  if the weighting is optimal,  and the  blue dashed lines  show   predictions if participants deviated from  optimality by relying  twice  as much  on the meaning  category  (strong meaning bias) or twice   as  much  on  the sound category (strong  sound bias).", fig.align = "center", out.width = "400px"}
bias

```

# General Discussion
Understanding language, such as word-referent associations, often requires both the ability to combine arbitrary multimodal input, and the ability to deal with uncertainty. In this work, we explored a case where both abilities were at play. We studied the case of identifying a word when both its form (auditory) and its referent (visual) were ambiguous with respect to their category membership (Experiment 1), when the form was perturbed with additional background noise (Experiment 2), and when the referent was perturbed with additional visual noise (Experiment 3). We introduced a model that instantiated an ideal/optimal observer, predicting how information from each modality could be combined in an optimal way. In all Experiments, participants showed many patterns of optimal behaviour. Quantitatively speaking, the optimal model accounted, respectively, for `r 100*R2_optimal_1`%, `r 100*R2_optimal_2`%, and `r 100*R2_optimal_3`% of the variance in human data.  When compared to the predictions of the visual or the auditory models, participants generally relied on both modalities to make their decisions in the bimodal condition. Indeed, in Experiment 1 and 2, the optimal model accounted for more variance in human data than the auditory or the visual models did. In Experiment 3, participants appeared to rely on one modality, but as we explained in the intermediate discussion, this is likely a floor effect, due to the fact that noise made the visual input barely perceivable. Moreover, in Experiment 1, which did not involve background noise, participants not only relied on both modalities, but weighted these modalities according to the prediction of the optimal model, that is, according to their relative reliability.

Besides these patterns of optimal behavior, we documented two interesting cases of sub-optimality. First, in all Experiments, the variance associated with each modality increased in the bimodal condition compared to the unimodal conditions. This means that participants responded slightly more randomly in the bimodal condition than they did in the unimodal conditions. This finding contrasts with research on optimal multisensory integration where associations tend to lead to a higher precision [@ernst02]. However, there is a crucial difference between these two situations. Research on optimal multisensory integration deals with redundant multimodal cues, and these cues are integrated into a unified percept (such as the size or the location of an object). In contrast, the word-referent association is usually arbitrary and, in particular, the cues are not supposed to correlate perceptually. Therefore the brain cannot form a unified percept, rather, it must encode information separately from both modalities and retain this encoding through the decision making process. Retaining two separate cues at the same time instead of forming one unified percept (as in multisensory integration of redundant cues), or instead of retaining only one cue (as in the unimodal case), is likely to place extra-demand on cognitive resources, which, in turn, can cause general performance to drop. Indeed, there is evidence that cognitive load has a detrimetnal effect on word recognition, which can be explained by a reduction in perceptual acuity [@mattys11].

The second case of sub-optimality is related to how participants weighed the cues from the visual and the auditory in a noisy context. In contrast to Experiment 1 where the combination was indistinguishable from the optimal prediction, resutls of Experiment 2 and 3 which involved noise in one modality, showed that participants had a preference for the other (non-noisy) modality. Crucially, this preference was beyond what is explained by the relative reliability (hence the sub-optimality). From previous empirical studies, we know that when the speech signal is degraded, people tend to compensate by relying more on other sources of information such as the accompanying visual cues (i.e., lip movements) or the semantic/syntactic context [see @mattys12 for a review]. However, and generally speaking, these studies do not differentiate between an optimal compensatory strategy (i.e., relying more on the alternative source while using all information still available in the distorted signal), and a sub-optimal strategy (i.e., relying more on the alternative source while ignoring at least some of the information still available in the distorted signal). The sub-optimal behavior is possibly related to the fact that language understanding under degraded listening conditions is cognitively more taxing than language understanding under normal conditions [@Ronnberg10]. This fact can lead to a preference/bias towards alternative sources of information when these sources are available.

## Implication for word learning

In this study, we explored the mechanism of word identification, but in a simple case when the underlying visual and auditory categories were familiar. Indeed, on the visual side, cat and dog tokens belong obviously to existing visual categories. On the auditory side, though the words ("ada"/"aba") are novel, the phonemic categories that differentiate the words are familiar (i.e., /d/ and /b/). In the context of early word learning, however, children are often learning both the categories and their mapping at the same time. In fact, children start learning visual and sound categories at an early age [e.g., @quinn93;@werker1984], and there is evidence that word-referent-like interaction operates at the same time, even when the categories are not yet fully mastered [e.g., @waxman1995; @yeung09]. In fact, @fourtassi2014a proposed that this interaction can create a synergy (or a bootstrapping effect) whereby progress made on one level (e.g., the meaning categories) can benefit the other level (the sound categories).

In what follows we explain how an account that combines both category learning and optimal multimodal integration can proceed, and how such account can provide us with a useful developmental framework. In the light of this framework, we speculate about possible new interpretation of some puzzling results in early word learning [@stager1997 and seq]. For starters, remember that one assumption of the model is that visual and auditory categories can be characterized with a variance that determines their precision/reliability. At the behavioral level, the variance is related to the shape of the categorization function: a small variance corresponds to a rather steep categorization function, meaning that one can tell with high certainty whether or not a token belongs to the category at hand. Vice versa, a large value of the variance corresponds to a rather flat categorization function, which means that for most tokens, one cannot tell with high certainty whether or not these tokens belong to the category at hand.

How can this formal characterization fit in a developmental scenario? One could imagine that, initially, visual and auditory categories have relatively large variances, and that development consists in reducing the values of the variances as evidence accumulates, making the categories more refined and precise. A scenario similar to this one has been previously suggested to explain the development of early sound categories. For example, @yoshida2009 suggested that the early categories may be noisier or that they may be encoded with relatively lower confidence. For the semantic categories, we can find similar (although perhaps not identical) ideas. For instance, Clark (1973) suggested that the initial meaning categories tend to be larger than adult categories, since fewer features are used to pick out referents (e.g., dog for all four-legged animal, ball for all round objects).

The combination of this developmental scenario in terms of category variance with the optimal integration account introduced in this paper provides possible new insights into the mechanism of word learning. Let's elucidate this idea through an example in the developmental literature. @stager1997 showed that 14 m.o (as opposed to 17 m.o) have difficulties mapping two minimally different sounds (e.g., "bih"/"dih") to two novel objects, despite the fact that they can perceptually differentiate these sounds. Our proposal explains these patterns of failure and success in terms of developmental changes in the variances associated with the visual and phonological categories, combined with the ability to integrate sound and visual cues according to their reliability. Suppose that both members of a given sound contrast ("bin"/"din") initially fall within the uncertainty range of a single sound category. If this uncertainty diminishes with age (as the category gets more refined), then what used to be likely at a certain point in development (e.g., 14 m.o), may later become unlikely. In particular, at 17, m.o, it may become necessary to attribute the sound contrast to two neighboring categories instead of a single one. But how can 14 m.o possibly consider one broad category for both sounds if these sounds are paired with different objects? This is where the optimal combination account may come into play. Indeed, even if the objects are perceptually different, they may still be similar in the 14 m.o's early semantic space. If babies make categorical decision based on both auditory and visual cues, then having evidence that the auditory tokens belong to the same category can prompt them to consider the possibility that even the objects are variations within the same (broad) semantic category. Thus, 14 m.o may be learning one broad word-referent association instead of two specific associations. So what was conidered a "failure" in learning might, in fact, be the optimal decision within the 14 m.o's own developmental context!

This account makes two main predictions. First, if the sounds are more acoustically different (e.g., "lif"/"neem" instead of ""bih"/"dih"), babies would be more likely to posit and learn two word-referent associations, because there would be more evidence pointing in that direction from the auditory side. Second, if the objects are more semantically distant (a living object vs. a non-living object, instead of the two perceptually different toys used in the original study), babies would be more likely to posit and learn two word-referent associations, because now there would be more evidence pointing in that direction from the visual side. In fact, @stager1997 tested and proved the first prediction. The second prediction remains to be tested. If proven, it would provides support to the optimal combination account in early language learning.

# References
```{r create_r-references}
r_refs(file = "references.bib")
```

\setlength{\parindent}{-0.5in}
\setlength{\leftskip}{0.5in}

### 2018-02-17 Writeup/ms.Rmd
changes to journal write-up

@@
   - id            : "1"
-    institution   : "Department of Psychoogy, Stanford University"
+    institution   : "Department of Psychology, Stanford University"
 
@@
 We introduce a task that allows us to examine how adults identify words under joint uncertainty in the auditory and visual modalities.
-We propose an ideal observer model of the task which provides an optimal account of how auditory and visual cues are combined.
+We propose an ideal observer model of the task which provides an account of how auditory and visual cues are combined optimally.
 Model predictions are tested in three experiments where word recognition is made under two kinds of uncertainty: category ambiguity and/or distorting noise.
 In all cases, the optimal model explains much of the variance in human judgments.
-In particular, when the signal was not distorted with noise, participants weighted the auditory and visual cues optimally, that is, according to the relative reliability of each modality.
-But when one modality had noise added to it, human perceivers systematically preferred the unperturbed modality to a greater extent than the optimal model did.
+In particular, when the signal is not distorted with noise, participants weight the auditory and visual cues optimally, that is, according to the relative reliability of each modality.
+But when one modality has noise added to it, human perceivers systematically prefer the unperturbed modality to a greater extent than the optimal model does.
 We discuss the broad implications of the results, especially in relation to early language acuquisition.
@@
 wordcount         : "X"
+
+header-includes:
+   #- \usepackage{bibentry}
+   - \usepackage[sortcites=false,sorting=none]{biblatex}
 
@@
 output            : papaja::apa6_pdf
+
+citation_package: biblatex
+
 ---
@@
 ```{r load_packages, include = FALSE}
-library("papaja")
+library(papaja)
 library(readr)
@@
 theme_set(theme_bw())
+library(broom)
+#library("knitcitations")
+#cleanbib()
+#options("citation_format" = "pandoc")
 ```
@@
 #############################
-exp1 <- read_delim("../Data_and_analysis/data_exp1_Anonym.txt", delim = " ") %>%
+exp1 <- read_delim("../Analysis/exp1_data_NoAnonym.txt", delim = " ") %>%
   filter(type == "Task") %>%
@@
 
-exp2 <- read_delim("../Data_and_analysis/data_exp2_Anonym.txt", delim = " ") %>%
+exp2 <- read_delim("../Analysis/exp2_data_NoAnonym.txt", delim = " ") %>%
   filter(type == "Task") %>%
@@
 
-exp3 <- read_delim("../Data_and_analysis/data_exp3_Anonym.txt", delim = " ") %>%
+exp3 <- read_delim("../Analysis/exp3_data_NoAnonym.txt", delim = " ") %>%
   filter(type == "Task") %>%
@@
 ```{r}
-#First deal with all data
+summarise <- dplyr::summarise
+rename <- dplyr::rename
 ```
@@
 
-#Filter who took the experiment more than once
+#Participants who did not encounter a technical problem with the online experiment
 
 #Exp1
- token_data_1 <- exp1 %>%
-   group_by(ID) %>%
-   dplyr::summarise(N_tokens=n())
-
- N_twice_1 <- token_data_1 %>%
-   filter(N_tokens > 70) %>%
-   nrow()
-
- exp1_once <- exp1 %>%
-   left_join(token_data_1) %>%
-   filter(N_tokens == 70) #every subject is supposed to produce exactly 70 tokens
-
- #Exp2
-token_data_2 <- exp2 %>%
-   group_by(ID) %>%
-   dplyr::summarise(N_tokens=n())
-
- N_twice_2 <- token_data_2 %>%
-   filter(N_tokens > 70) %>%
-   nrow()
-
- exp2_once <- exp2 %>%
-   left_join(token_data_2) %>%
-   filter(N_tokens == 70)
-
- #Exp3
-token_data_3 <- exp3 %>%
-   group_by(ID) %>%
-   dplyr::summarise(N_tokens=n())
-
- N_twice_3 <- token_data_3 %>%
-   filter(N_tokens > 70) %>%
-   nrow()
-
- exp3_once <- exp3 %>%
-   left_join(token_data_3) %>%
-   filter(N_tokens == 70)
-
-#Participants who did not encounter a technical problem with the online experiment
-
-#Exp1
-exp1_noProb <- exp1_once %>%
+exp1_noProb <- exp1 %>%
   filter(problem=="No")
@@
 #Exp2
-exp2_noProb <- exp2_once %>%
+exp2_noProb <- exp2 %>%
   filter(problem=="No")
@@
 #Exp3
-exp3_noProb <- exp3_once %>%
+exp3_noProb <- exp3 %>%
   filter(problem=="No")
@@
   group_by(sound_dist) %>%
-  #multi_boot_standard(col = "answer")
-  summarise(mean = mean(answer)) %>%
+  dplyr::summarise(mean = mean(answer),
+                   sd = sd(answer),
+                   n = n()) %>%
+  mutate(se = sd / sqrt(n),
+         lower = mean - qt(1 - (0.05 / 2), n - 1) * se,
+         upper = mean + qt(1 - (0.05 / 2), n - 1) * se) %>%
+  select(-sd, -n, -se,) %>%
   mutate(Experiment="Experiment 1", 
@@
   group_by(concept_dist) %>%
-  #multi_boot_standard(col = "answer")
-  summarise(mean = mean(answer)) %>%
+  dplyr::summarise(mean = mean(answer),
+                   sd = sd(answer),
+                   n = n()) %>%
+  mutate(se = sd / sqrt(n),
+         lower = mean - qt(1 - (0.05 / 2), n - 1) * se,
+         upper = mean + qt(1 - (0.05 / 2), n - 1) * se) %>%
+  select(-sd, -n, -se,) %>%
   mutate(Experiment="Experiment 1", 
@@
   group_by(concept_dist, sound_dist) %>%
-  #multi_boot_standard(col = "answer")
   summarise(mean = mean(answer)) %>%
@@
   group_by(sound_dist) %>%
-  #multi_boot_standard(col = "answer")
-  summarise(mean = mean(answer)) %>%
+  dplyr::summarise(mean = mean(answer),
+                   sd = sd(answer),
+                   n = n()) %>%
+  mutate(se = sd / sqrt(n),
+         lower = mean - qt(1 - (0.05 / 2), n - 1) * se,
+         upper = mean + qt(1 - (0.05 / 2), n - 1) * se) %>%
+  select(-sd, -n, -se,) %>%
   mutate(Experiment="Experiment 2", 
@@
   group_by(concept_dist) %>%
-  #multi_boot_standard(col = "answer")
-  summarise(mean = mean(answer)) %>%
+  dplyr::summarise(mean = mean(answer),
+                   sd = sd(answer),
+                   n = n()) %>%
+  mutate(se = sd / sqrt(n),
+         lower = mean - qt(1 - (0.05 / 2), n - 1) * se,
+         upper = mean + qt(1 - (0.05 / 2), n - 1) * se) %>%
+  select(-sd, -n, -se,) %>%
   mutate(Experiment="Experiment 2", 
@@
   group_by(sound_dist) %>%
-  #multi_boot_standard(col = "answer")
-  summarise(mean = mean(answer)) %>%
+  dplyr::summarise(mean = mean(answer),
+                   sd = sd(answer),
+                   n = n()) %>%
+  mutate(se = sd / sqrt(n),
+         lower = mean - qt(1 - (0.05 / 2), n - 1) * se,
+         upper = mean + qt(1 - (0.05 / 2), n - 1) * se) %>%
+  select(-sd, -n, -se,) %>%
   mutate(Experiment="Experiment 3", 
@@
   group_by(concept_dist) %>%
-  #multi_boot_standard(col = "answer")
-  summarise(mean = mean(answer)) %>%
+  dplyr::summarise(mean = mean(answer),
+                   sd = sd(answer),
+                   n = n()) %>%
+  mutate(se = sd / sqrt(n),
+         lower = mean - qt(1 - (0.05 / 2), n - 1) * se,
+         upper = mean + qt(1 - (0.05 / 2), n - 1) * se) %>%
+  select(-sd, -n, -se,) %>%
   mutate(Experiment="Experiment 3", 
@@
 Consider hearing someone yell "bee!" at a picnic, as a honey bee buzzes around the food.
-Determining reference involves processing the auditory information and linking it with other perceptual signals (e.g., the visual image of the bee, the sound of its wings, the sensation of the bee flying by your arm).
-
-This multimodal integration task takes place in a noisy world.
+Identifying a word involves processing the auditory information as well as other perceptual signals (e.g., the visual image of the bee, the sound of its wings, the sensation of the bee flying by your arm).
+A word is successfully identified when information from these modalities provide convergent evidence.
+However, word identification takes place in a noisy world, and the cues received through each modality may not provide a definitive answer.
 On the auditory side, individual acoustic word tokens are almost always ambiguous with respect to the particular sequence of phonemes they represent, which is due to the inherent variability of how a phonetic category is realized acoustically [@hillenbrand1995].
@@
 
-How does the brain deal with uncertainty to process and understand language?
-Previous research showed that the brain encodes speech cues probabilistically, in a way that mirrors the inherent noise/ambiguity in the input.
-From this probabilistic representation, the brain tends to make the statistically optimal judgement about the identity of the intended categories [e.g., @clayard08; @feldman2009].
-Previous work in this line of research has largely focused on testing optimal inference using cues from the auditory modality.
-A few studies did explore some aspects of audio-visual processing in a probabilistic framework [@bejjanki2011; @kleinschmidt2015].
-These studies focused on the case of audio-visual speech perception, that is, recognizing speech categories using cues from the auditory signal accompagnied with lip movements.
-To our knowledge, however, no study explored whether word recogniton is statistially optimal in a *referential* context, that is, when the brain has to combine cues from the sound and the meaning/referent.
-Imagine, for example, that someone is uncertain whether they heard "pea" or "bee", does it make them rely more on the referent (e.g., the object being pointed at)?
+How does the mind deal with uncertainty to identify the speaker's intended word?
+To address this question, many researchers in recent years have adopted the rational approach to cognition [@anderson90], which corresponds to Marr's computational level of analysis.
+This approach has had a tremendous impact not only on speech related research [@Norris08; @clayard08; @feldman2009; @kleinschmidt2015], but also on many other disciplines in the cognitive sciences [for reviews, see @chater06; @Knill04; @tenenbaum11].
+Within this framework, researchers typically consider an "ideal observer" model which provides a characterization of the task/goal and shows what the optimal performance should be under this characterization.
+When there is uncertainty in the input, the ideal observer performs an optimal probabilistic inference.
+For example, in order to recognize an ambiguous linguistic input, the model uses all available probabilistic knowledge in order to maximize the accuracy of this recognition.
+Thus, when the task is well specified, the ideal observer model can be seen as a theoretical upper limit on performance.
+It is often used, not so much as a realistic model of human performance, as much as a baseline against which human performance can be compared [@Geisler2003].
+When there is a deviation from the ideal, this can reveal extra constraints on human cognition, such as limitations on working memory or attentional resources.
+
+In this line of research, @clayard08 simulated auditory uncertainty by manipulating the probability distribution of a cue (VOT) that differentiated similar words (e.g., "beach" and "peach").
+They found that humans were sensitive to these probabilistic cues and their judgments closely reflected the optimal predictions.
+In another work, @feldman2009 studied the perceptual magnet effect, that is, the fact that categories influence the way the stimuli are perceived.
+They showed that this effect can be explained as the consequence of optimally solving the problem of perception under uncertainty.
+Both studies explored optimal performance under uncertainty from one modality, i.e., the auditory modality.
+There is however extensive evidence that information from the visual modality, in particular the speaker's facial features,  influences the perception of auditory information [see @Campbell2008 for a review].
+@bejjanki2011 offered a mathematical characterization of how cues from speech and lip movements can be optimally combined and showed that human performance during audio-visual phonemic labeling was consistent (at least at the qualitative level) with the behavior of the ideal observer.
+
+The speaker's facial features are not the only visual information that can be used to disambiguate the auditory input, however.
+For instance, in a referential context, information about the identity of the semantic referent can be integrated with linguistic information to resolve lexical and syntactic ambiguities in speech [e.g., @Eberhard1995; @Tanenhaus1995; @spivey2002].
+To our knowledge, however, no study offered an ideal observer analysis of word identification in such context, that is, when the mind has to combine cues from the sound and the referent.
+Imagine, for example, that someone is uncertain whether they heard "pea" or "bee", does this uncertainty make them rely more on the referent (e.g., the object being pointed at)?
 Vice versa, if they are not sure if they saw a bee or a fly, does that make them rely more on the sound?
-More importantly, when input in both modalities is uncertain to varying degrees, do they weight each modality according to its relative reliability, or do they over-rely on a particular modality?
-
-Outside the realm of language per se, research on multisensory integration suggests that the brain integrates information from different modalities in a statistically optimal way, that is, the integration results in a higher overall precision, and modalities are weighed according to their relative reliability [@ernst02].
+More importantly, when input in both modalities is uncertain to varying degrees, do they weight each modality according to its relative reliability (which is the optimal strategy), or do they over-rely on a particular modality (which is a sub-optimal strategy)?
+
+The visual information provided by the referent is arguably different from the visual information provided by the speaker's facial features (such as lip movements).
+There seems to be at least two fundamental differences between these two cases, and both can influence the cue combination strategy:
+
+<!-- Outside the realm of language per se, research on multisensory integration suggests that the brain integrates information from different modalities in a statistically optimal way, that is, the integration results in a higher overall precision, and modalities are weighed according to their relative reliability [@ernst02].
 However, it is not a priori obvious whether this finding can be extended to word-referent recognition under multimodal uncertainty.
 Indeed, there seems to be at least two fundamental differences between these two cases, and both can influence the cue combination strategy.
-
-First, in the case of optimal multisensory integration, modalities are understood to differ only in terms of their reliability.
-In a referential conext, however, modalities also differ in terms of their roles in the referential process: the auditory input represents the symbol (i.e., the word) whereas the visual input represents the referent.
-It has been suggested that because of the referential property of speech, it is a privileged signal for humans from infancy [see @vouloumanos2014 for a review].
-Thus, it is possible that the brain does not treat the auditory and visual modalities as equivalent sources of information.
+-->
+
+First, in the case of audio-visual speech, modalities are understood to differ only in terms of their reliability.
+In a referential context, however, modalities also differ in terms of their roles in the referential process: the auditory input represents the symbol (i.e., the word) whereas the visual input represents the referent.
+It has been suggested that because of the referential property of speech, it is a privileged signal for humans starting in infancy [see @vouloumanos2014 for a review].\footnote{There is a debate over whether speech is privileged for infant and adults for the same reasons.
+Whereas Waxman and colleagues suggest that speech is privileged for both infants and adults because of its ability to refer, Sloutsky and colleagues suggest that speech might not have a referential status from the start.
+Rather, they argue tha speech seems to be prefered by infants only because of a low level auditory "overshadowing".} Thus, in a referential context, it is possible that we do not treat the auditory and visual modalities as equivalent sources of information.
 Instead, there could be a bias for the auditory modality beyond what is expected from informational reliability alone.
 
-Second, research on optimal multisensory integration typically deals with multisensory associations that are supposed to be *redundant*.
-An example of such integration is when we determine the size of an object using the visual and haptic modalities [@ernst02], or when we determe the spacial location of a stimulus using the visual and the auditory modalities [@alais04].
-In the case of language, however, the multimodal input is rather *arbitrary* [@saussure1916].
-For instance, there is no logical connection between the sound "bee" and the corresponding insect.
-Moreover, variation in the way the sound "bee" is pronounced does not correlate perceptually with variation in the shape (or any other visual property) in the category of bees.
-It turns out the nature of the multi-modal associations (redundant vs.
+<!--An example of such integration is when we determine the size of an object using the visual and haptic modalities [@ernst02], or when we determine the spacial location of a stimulus using the visual and the auditory modalities [@alais04] -->
+Second, in the case of audio-visual speech, the associations are expected to be perceptually correlated.
+The expectation for this correlation is such that when there is a mismatch between auditory and visual input, people still integrate them into a unified (but illusory) percept [@mcgurk1976].
+In the case of referential language, however, the multimodal association is by nature *arbitrary* [@saussure1916; @greenberg1957].
+For instance, there is no logical/perceptual connection between the sound "bee" and the corresponding insect.
+Moreover, variation in the way the sound "bee" is pronounced is generally not expected to correlate perceptually with variation in the shape (or any other visual property) in the category of bees.
+Thus, one could imagine that cue combination in the case of arbitrary audio-visual associations (word-referent) is less automatic, more effortful, and therefore less conducive to optimal integration than it is in the case of perceptually correlated associations (as in audio-visual speech perception).
+
+In the current study, we investigate how people combine cues from the auditory and the visual modality to recognize words in a referential context.
+In particular, we study how this combination is performed under various degrees of uncertainty in both the auditory and the visual modality.
+We perform a rational analysis of the task.
+First we propose an ideal observer model that performs the combination in an optimal fashion.
+Second we compare the predictions of the optimal model to human responses.
+Humans can deviate from the ideal for several reasons.
+For instance, as mentioned above, a sub-optimality can be induced by the suggested privileged status of speech or by the arbitrariness of the referential association.
+In order to study possible patterns of sub-optimality, we compare the optimal model (which provides a normative benchmark) to a descriptive model which is identical to the optimal model, except that the parameters in the former are fitted to human responses.
+<!--We do not perform the ideal observer analysis at the individual level, but at the population level.
+There might be some individual variation, but this study addresses the overall performance in the population as a whole.-->
+
+We test the ideal observer model's predictions in three behavioral experiments where we vary the source of uncertainty.
+In Experiment 1, audio-visual tokens are ambiguous with respect to their category membership only.
+In Experiment 2, we intervene by adding background noise to the auditory modality, and in Experiment 3, we intervene by adding background noise to the visual modality.
+In all experiments, participants were quantitatively near-optimal, though overall response precision was slightly lower than expected.
+Moreover, in Experiment 1 where neither of the modalities was perturbed with background noise, participants weighed auditory and visual cues according to the relative reliability predicted by the optimal model.
+In other words, we found no evidence for a modality bias towards either the auditory or the visual modality.
+However, in Experiment 2 and 3, participants over-relied on one modality when the other modality was perturbed with additional noise.
+<!-- In the discussion, we talk about the broad implications of these results and especially in relation to some developmental findings in early word learning [e.g., @stager1997].
+-->
+
+<!--The nature of the multi-modal associations (redundant vs.
 arbitrary) influences the quality of multi-modal processing in both children and adults: the processing and integration is easier in the case of redundant input, than it in the case of arbitrary input [see @robinson2010 for a review].
-Thus, there is a priori no obvious reason multimodal cue combination in the case of arbitrary assoiations (such as the case of word-referent) should be optimal in the same way redundant associations are.
-For instance, the former is more likely to show patterns of sub-optimality.
-
+Thus, there is a priori no obvious reason multimodal cue combination in the case of arbitrary assoiations (such as the case of word-referent) should be optimal in the same way cue combination of redundant associations is.
+-->
 <!--
-
-TRY TO CONTRAST TWO THINGS: WORK ON PERCEPTUAL INTEGRATION WHEN THERE IS CORRELATION AND WORK OF AUDIO-VISUAL ENCODING OF ARBITRARY ASSOCIATIONS, SHOW THAT THE FIRST IS NOT ARBIRARY, AND MOSTY CONTINUOUS (ANS PRODUCE OPTIMALITY), THE SECOND DOES NOT INVOVLE CATEGORIES OR A SEMANTIC CONTEX, WHERE A WORD REFER TO AN OBJECT, INSTEAD OF BEING JUST ARBITRARY (AND PRODUCE HINDRANCE AND SUB-OPTIMALITY).
-THUS OUR WORK TRIES TO DEAL WITH CASE
 
@@
 
-In this paper, we studied the mechanism of processing/combination of audiovisual cues in a referential context, under multiple sources of uncertainty.
-More precisely, we tested if the cue combination was statistically optimal.
-Besides, we quantified any sub-optimality that might have been induced, among other things, by the suggested privileged status of speech or by the arbitrariness of the referential associations.
-To test optimality, we characterized uncertainty in each modality with a probability distribution, and we predicted responses by combining these probabilities in an optimal way.
-To study possible patterns of sub-optimality, we compared the optimal model to a descriptive model where the parameters of the bimodal probability distributions were fitted to human judgements.
-We tested the model's predictions in three behavioral experiments where we varied the source of uncertainty.
-In Experiment 1, audio-visual tokens were ambiguous with respect to their category membership.
-In Experiment 2, we intervened by adding background noise to the auditory modality, and in Experiment 3, we intervened by adding background noise to the visual modality.
-In all Experiments, participants were quantitatively near-optimal, though precision dropped slightly in the bimodal condition.
-Moreover, in Experiment 1 where neither of the modalities was perturbed with background noise, participants weighed auditory and visual cues according to the relative reliability predicted by the optimal model.
-In other words, we found no evidence for a modality bias towards either the auditory or the visual modality.
-However, In Experiment 2 and 3, participants over-relied on one modality when the other modality was perturbed with additional noise.
-Finally, we discuss the broad implications of these results, especially in relation to some developmental findings in early word learning [e.g., @stager1997].
-
-# Model
+# Models and predictions
 
 In this section we describe the multimodal integration model.
-First, we briefly introduce the experimental paradigm, and second we explain how this paradigm can be modeled in a probabilistic framework.
+First, we briefly introduce the experimental paradigm, and second we explain how behavior in this paradigm can be characteized optimally with an ideal observer model.
 
@@
 For each participant, an arbitrary pairing is set between the auditory and the visual categories, leading to two audio-visual word categories (e.g., dog-/aba/, cat-/ada/).
-
 In each trial, participants are presented with an audio-visual target (the prototype of the target category), immediately followed by an audio-visual test stimulus (Figure\ \@ref(fig:task)).
@@
 
-This itask is similar to the task introduced by @sloutsky2003.
-However, in that study, as well as subsequent ones, participants were asked whether or not the two audio-visual presentations were *identical*.
-Such task would allow us to probe audio-visual encoding, but not necessarily speech perception.
-The latter requires---in addition to the perceptual encoding---a categorical judgement, i.e, determining wheather two similar tokens are members of the same phonological/semantic category.
-Thus, our task is category-based: participants are asked to press "same" if they think the second item (the test) belonged to the same category as the first (target) (e.g.,  dog-/aba/), even if there is a slight difference in the word, in the referent, or in both.
+This task is similar to the task introduced by @sloutsky2003, and used in subsequent studies in both children and adults [see @robinson2010 for a review].
+However, in this original task, participants are asked whether or not the two audio-visual presentations are *identical*.
+Such task would allow us to probe audio-visual encoding, but not necessarily language understanding.
+The latter requires---in addition to the perceptual encoding---a categorical judgement, i.e, determining wheather or not two similar tokens are members of the same phonological/semantic category.
+Thus, our task is category-based: participants are asked to press "same" if they think the second item (the test) belonged to the same category as the first (target) (e.g.,  dog-/aba/), even if there is a slight difference in the sound, in the referent, or in both.
 They are instructed to press "different" only if they think that the second stimulus was an instance of the other word category (cat-/ada/).
-
-We assume, for the sake of simplicity, that category tokens vary along a single dimension.
+The task also includes trials where pictures are hidden (audio-only) or where sounds are muted (visual-only).
+These unimodal trials provide us with participants' evaluation of the probabilistic information present in the auditory and visual categories.
+This unimodal distributions are used as inputs to the optimal combination model, described below.
+
+<!--We assume, for the sake of simplicity, that category tokens vary along a single dimension.
 Phonetic tokens are sampled from an acoustic continuum linking /aba/ to /aba/, and obtained by continuously varying the value of the second formant [@vroomen2004].
 Visual tokens are sampled from a morph continuum linking the picture of a dog and the picture of a cat [@freedman2001].
-
-The task also includes trials where pictures are hidden (audio-only) or where sounds are muted (visual-only).
-These unimodal trials provide us with participants' categorization functions for the auditory and visual categories and are used as inputs to the optimal model, described below.
+-->
 
@@
 
-The basis of our optimal model is that individual probabilistic representations from each modality should be combined optimally.
-First we describe how probabilistic representations in each modality are derived/fitted, and second we explain how they are combined to yield optimal predictions.
-
-### Unimodal representations
+<!--First we describe how probabilistic representations in each modality are derived, and second we explain how they are combined to yield optimal predictions. -->
+
+<!--
+### Unimodal condition
 
@@
 
-We assume the probability of membership in each category is normally distributed:
+We assume a token's probability of membership in each category to be normally distributed:
 
@@
 
-with $\beta_a=\frac{\mu_{A_1}-\mu_{A_2}}{\sigma^2_{A}}$, $\beta_{a0}=\frac{\mu^2_{A_2}-\mu^2_{A_1}}{2\sigma^2_{A}}$, and $1+\epsilon_A=\frac{p(A_1)}{p(A_2)}$ is the proportion of the prior probabilities.
+with $\beta_a=\frac{\mu_{A_1}-\mu_{A_2}}{\sigma^2_{A}}$, $\beta_{a0}=\frac{\mu^2_{A_2}-\mu^2_{A_1}}{2\sigma^2_{A}}$ and $1+\epsilon_A=\frac{p(A_1)}{p(A_2)}$ is the proportion of the prior probabilities.
 If the identity of the auditory categories is randomized, and if $A_1$ is the target, then $\epsilon$ measures a response bias to "same" if $\epsilon > 0$, and a response bias to "different" if $\epsilon < 0$.
@@
 
-### Optimal model
-
-In the bimodal condition, participants see audio-visual tokens.
-They have to combine information from both modalities and make a categorical decision.
+-->
+
+The ideal observer model has to combine probabilistic information from auditory and the visual modalities and make a categorical decision.
 How can this task be characterized in a formal way, and what would be the optimal behavior?
-Work on multisensory integration generally considers the outcome of multiplying the distributions derived from each modality [e.g., @ernst02].
-However, this way of combining multi-modal cues is more adequate to examine continuous perceptual dimensions (e.g., size).
-It is less applicable to categorical dimensions (e.g., phonemes) [see @bejjanki2011; @Bankieris17 for futher detail]
+If the stimuli were continuous (e.g., size, location), cues derived from each modality would be characterized with their sensory noise variance only, and (assuming conditional independence) their combined information would be characterized with a simple linear combination rule where the combined estimate is an average of the indivisual estimates, each wighted according to its relative reliability [@ernst02; @alais04].
+However, in our case decison is made over categorical variables (phonemes and concepts), the optimal model should take into account, not only the noise variability arround an individual perceptual estimate, but also its categorical variability (i.e., the probability with which the estimate belongs to a given category).
+
+One way to account for the categorical variability is to model the decision step which maps sensory input onto task-dependent categories [@Bankieris17; @bejjanki2011].
+We represent the decision step as follows (see Figure\ \@ref(fig:model) for illustration).
+If we assume that both the visual and the auditory cues vary along a single dimension, an audio-visual signal $(a,v)$ can be represented as a point in this two-dimensionl space, and a word category can be characterized with a bivariate probability distribution over audio-visual tokens.\footnote{For the sake of clarity, we assume here that the sensory noise around this point is small/negligeable compared to the categorical vriability, but see below how the noise can be integrated when its effect is realtively large} Each category is peaked around the most typical audio-visual token, and the probability of membreship in the category (the likelihood probability) decreases gradually as the auditory token deviates from the typical sound instance (depending on the variance of the auditory category) and/or as the visual token deviates from the typical visual instance (depending on the variance of the visual category).
+<!--To illustrate how categorical decision is made within this formal framework, suppose we receive an ambiguous image which can be either of a cat or of a dog, associated with a slightly noisy auditory input that sounds more like "cat".
+If the judgment is based on the picture only, this would lead to a random choice between cat and dog.
+However, if the judgement is based on both the picture and the sound (which is less ambiguous), the combined information should lead to a preference for the word cat  we illustrate the cateorical decision making.
+Audio-visual points along this line lead to random responses, meaning that both the auditory and the visual components are maximally ambiguous.
+Audio-visual points that lay on either side of the decision threshold lead to decisions in favor of one word or the other.
+This means that at least one component of this audio-visual token is not totally ambiguous, which leads to a diambiguated combined information.
+-->
+A crucial feature of the ideal observer model is that it makes use of the entire probability distribution of a given category in order to make optimal decisions [e.g., @clayard08].
+This means that the probability of picking a word (the posterior probability) should mirror closely the probability of the combined information (the likelihood probability).
+For instance, the model becomes less ambiguous and more certain as the tokens get closer to the typical instance of the category.
+This intuition will be formalized below.
+<!--characterized with a likelihood function, e.g., $P(S_V | S)$ and $P(S_A | S)$ for a visual and an auditory cue, respectively.
+If these cues are conditionally independent, their combined information can be written as $P(S_V, S_A | S)=P(S_A | S)P(S_V | S)$.
+The maximum likelihood estimate of this combined information $\hat{S}$ is an average of the individual maximum liklihoods $\hat{S}=w_V\hat{S_V}+w_A\hat{S_A}$, each wighted according to its relative reliability:
+$w_V=\frac{1/\sigma_V^2}{1/\sigma_V^2 + 1/\sigma_A^2}$, and $w_A=\frac{1/\sigma_A^2}{1/\sigma_V^2 + 1/\sigma_A^2}$.
+
+If, however, the target is a categorical dimension, the optimal model should take into account, not only the noise variability arround an individual perceptual estimate, but also its categorical variability (i.e., the probability with which this estimate belongs to a given category).
+For example, upon hearing an audio-visual signal (the sound "cat" associated with the image of a cat), the ideal obsever has both to identify the sensory input and to map it onto the task-dependent categories.
+
+The optimal model that takes into account categorical variability is somewhat different, since -->
 
@@
 
-We followed a formal approach similar in spirit to the one adopted by @bejjanki2011.
-In this approach, the bimodal optimal distribution is defined, not as the product of the unimodal distribution $p(A)$ and $p(V)$, but as their joint distribution in a higher dimensional space, which we call the audio-visual space.
-Thus, a word token is defined as a vector in this space, $w=(a,v)$, and a word category $W$ can be characterized with a bivariate normal distribution:
+An auditory categoy $A$ and a visual category $V$ are defined as distributions in the auditory and the visual dimensions, respectively.
+A word category $W$ is defined as a bivariate distribution in the audio-visual.
+More specifically, we define it as the joint distribution of the auditory and the visual categories.
+For simplicity, we assume both auditory and visual categories to be normally distributed.
+That is, if $w=(a,v)$ is an audio-visual token, then:
+$$ p(a | A) \sim  N(\mu_A, \sigma^2_A) $$
+where $\mu_A$ and $\sigma^2_A$ are respectively the mean and the variance of the auditory category,
+$$ p(v | V) \sim  N(\mu_V, \sigma^2_V) $$
+where $\mu_V$ and $\sigma^2_V$ are  the mean and the variance of the visual category, and
+
 $$ p(w | W) \sim  N(M_W, \Sigma_W) $$
+where $M_W=(\mu_A, \mu_V)$ and $\Sigma_W$ are mean and the covariance matrix of the word category.
+We assume that auditory and visual variables are independent (i.e., uncorrelated), so the covariance matrix is simply:
+ \[
+   \Sigma_W=
+  \left[ {\begin{array}{cc}
+   \sigma^2_A & 0 \\
+   0 & \sigma^2_V \\
+  \end{array} } \right]
+\]
+
 ```{r model, fig.cap = "Illustration of the model using simulated data.
@@
 
-We have two word categories: dog-/aba/ ($W_1$) and cat-/ada/ ($W_2$).
-Participants can be understood as choosing one of these two word categories (Figure\ \@ref(fig:model)).
+This assumption simply says that, given a word-object mapping, e.g., W=("cat"-CAT), variation in the way "cat" is pronounced does not correlate with changes in any visual property of the object CAT, which is a valid assumption.\footnote{Note that this assumptions is more adequate to the case of arbitrary associations such as ours, and less so in the case of redundant association such as audio-visual speech.
+In the latter, variation in the pronounciation is expected to correlate, at least to some extent, with lip movements.}
+
+Now we turn to the crucial question of modeling how optimal decision should proceed based on the probabilistic information in the auditory and the visual modalities.
+In our task, we have two word categories: dog-/aba/ ($W_1$) and cat-/ada/ ($W_2$).\footnote{This mapping is randomized in the experiments.} Participants can be understood as choosing one of these two word categories (Figure\ \@ref(fig:model)).
 For an ideal observer, the probability of choosing category 2 when presented with an audio-visual instance $w=(a,v)$ is the posterior probability of this category:
-
 $$
@@
 $$
-We make the assumption that, given a particular word category, the auditory and visual tokens are independent:
-
-$$p(w | W) = p(a,v| W) = p(a| W)p(v| W)$$
-This assumptions simply says that, given a word-object mapping, e.g., W=("bee"-BEE), variation in the way "bee" is pronounced does not correlate with changes in any visual property of the object BEE\footnote{Note that this assumptions is more adequate to the case of arbitrary associations such as ours, and less so in the case of redundant association such as audio-visual speech.
-In the latter, variation in the pronounciation is expected to correlate, at least to some extent, with lip movements.}.
-
-Under this assumption, the posterior probability reduces to:
-$$ p(W_2 | w)=\frac{1}{1+(1+\epsilon)\exp(\beta_0+\beta_aa+\beta_vv)}$$
-
-with $\beta_a=\frac{\mu_{A1}-\mu_{A2}}{\sigma^2_{A}}$,
-$\beta_v=\frac{\mu_{V1}-\mu_{V2}}{\sigma^2_{V}}$, $\beta_0=\frac{\mu^2_{A2}-\mu^2_{A1}}{2\sigma^2_{A}}+\frac{\mu^2_{V2}-\mu^2_{V1}}{2\sigma^2_{V}}$ 
-and $1+\epsilon=\frac{p(W_1)}{p(W_2)}$ is the proportion of the prior probabilities.
-If the identity of word categories is randomized, and if $W_1$ is the target, then $\epsilon$ measures a response bias to "same" if $\epsilon > 0$, and a response bias to "different" if $\epsilon < 0$.
-We expect a general bias towards answering "different" because of the categorical nature of our same-different task: when two items are ambiguous but perceptually different, this could cause a slight preference for "different" over "same".
-
-We fix the values of the means to be the endpoints of the corresponding continuum.
-For example, if both the auditory and visual continua are made of 5 steps going from 0 to 4, then $\mu_{A1}=0$ and $\mu_{A2}=4$ (and similarly $\mu_{V1}=0$, and $\mu_{V2}=4$).
-When we fix th values of the means, observations from each modality ($a$ and $v$) become weighted according to their reliability, i.e., in the posterior we have $\beta_a \propto \frac{1}{\sigma^2_{A}}$ and $\beta_v \propto \frac{1}{\sigma^2_{V}}$ for the auditory and visual token, respectively.
-
-## Auditory and Visual baselines
-
-The posterior provides the optimal model's predictions for how probabilities that characterize uncertainty in each modality can be combined to make categorical decision about the bimodal input.
-The predictions of the optimal model will be compared to human responses in the bimodal case.
-Besides the optimal model, we also test the predictions of two baselines models: the **visual model**, which assumes that participants rely only on visual information, and the **auditory model**, which assumes that participants rely only on auditory information.
+Using our assumption that the cues are uncorrelated, we have
+$$p(w | W) = p(a,v| W) = p(a| A)p(v| V)$$
+Under this assumption, the posterior probability reduces to:\footnote{see the appendix for the details of the derivation}
+\begin{equation}
+ p(W_2 | w)=\frac{1}{1+(1+\epsilon)\exp(\beta_0+\beta_aa+\beta_vv)}
+\end{equation}
+where 
+$$1+\epsilon=\frac{p(W_1)}{p(W_2)}$$
+$$\beta_0=\frac{\mu^2_{A2}-\mu^2_{A1}}{2\sigma^2_{A}}+\frac{\mu^2_{V2}-\mu^2_{V1}}{2\sigma^2_{V}}$$
+
+$$\beta_a=\frac{\mu_{A1}-\mu_{A2}}{\sigma^2_{A}}$$
+$$\beta_v=\frac{\mu_{V1}-\mu_{V2}}{\sigma^2_{V}}$$
+
+The parameter $\epsilon$ represents the differential between the categories' prior probabilities.
+However, since the identity of word categories is randomized across participants, $\epsilon$ measures, rather, a response bias to "same" if $\epsilon > 0$, and a response bias to "different" if $\epsilon < 0$.
+We expect a general bias towards answering "different" because of the categorical nature of our same-different task: when two items are ambiguous but perceptually different, participants might have a slight preference for "different" over "same".
+
+<!--
+We fix the values of the means as follows.
+Since the endpoints of the auditory and the visual continua are the most typical tokens, we assume that the categories are peaked around these endpoints, so we fix the values of the mean to be these endponts.
+to be the endpoints of the corresponding continuum, meaning that <!--For example, if both the auditory and visual continua are made of 5 steps going from 0 to 4, then $\mu_{A1}=0$ and $\mu_{A2}=4$ (and similarly $\mu_{V1}=0$, and $\mu_{V2}=4$).
+--> The values of the means are fixed: They correspond to the value of the most typical tokens in our stimuli.
+Thus, observations from each modality ($a$ and $v$) are weighted according to their reliability in the posterior: $$\beta_a \propto \frac{1}{\sigma^2_{A}}$$ $$\beta_v \propto \frac{1}{\sigma^2_{V}}$$.
+
+Note that the weights account for categorical variability only. For instance, if the speaker generates a target production $a_t$ from an auditory category
+$p(a_t | A) \sim N(\mu_{A}, \sigma^2_{A})$, the ideal model assumes that it has direct access to this production token (i.e., $a=a_t$), and that all uncertainty is about the category membership of this token.
+However, we might also want to account for noise in the brain and/or in the environment.
+For example, the observer might not have access to the exact produced target, but only to the target perturbed by noise.
+If we assume this noise to be normally distributed, that is,  $p(a | a_t) \sim N(a_t, \sigma^2_{N})$, then integrating over $a_t$ lead to the following simple expression:
+$$ p(a | A) \sim N(\mu_{A}, \sigma^2_{A}+\sigma^2_{N})$$
+Using an identical reasoning for the case of the visual modality, we end up with the following multimodal weighting scheme in the optimal combination model:
+
+ $$\beta_a \propto \frac{1}{\sigma^2_{A}+\sigma^2_{N_A}}$$ $$\beta_v \propto \frac{1}{\sigma^2_{V} +\sigma^2_{N_V}}$$
+To summarize, the posterior provides the optimal model's predictions for how probabilities that characterize uncertainty in each modality can be combined to make categorical decision about the bimodal input.
+The model will be constructed based on data from the unimodal trials, but the predictions of the optimal model will be compared to human responses in the bimodal trials.
+
+## Auditory and Visual baseline models
+
+Besides the optimal model, we also test the predictions of two baselines models: a visual model, which assumes that participants rely only on visual information, and a auditory model, which assumes that participants rely only on auditory information.
 If participants rely on both the auditory and the visual modalities, the optimal model would explain more variance in human responses than the visual model alone or the auditory model alone.
@@
 The visual, auditory, and optimal models are *normative* models.
-Their predictions are made about human data in the bimodal condition, although their crucial parameters (i.e., variances associated with the visual and auditory modalities) are derived from data in the unimodal conditions.
+Their predictions are made about human data in the bimodal condition, but their crucial parameters (i.e., variances associated with the visual and auditory modalities) are derived from data in the unimodal conditions.
 In addition to these normative models, we consider a *descriptive* model.
-The parameters of this model are fitted to human data in the bimodal condition.
-If the referential task induces sub-optimality (due, for instance, to the arbitrary nature of the sound-object association), then we predict the descriptive model to explain more variance than the optimal model does.
-
-A systematic comparison of the optimal and the descriptive models would allow us, not only to quantify how much people deviate from optimality, but also to understand qualitatively how they deviate from this optimality.
+The parameters of this model are fit to human data in the bimodal condition.
+If the referential task induces sub-optimality (due, for instance, to the arbitrary nature of the sound-object association), then we predict that the descriptive model should explain more variance than the optimal model does.
+
+A systematic comparison of the optimal and the descriptive models would allow us, not only to quantify how much people deviate from optimality, but also to understand precisely how they deviate from this optimality.
 Let $\sigma^2_{A}$ and $\sigma^2_{V}$ be the values of the variances used in the optimal model (derived from the unimodal conditions), and $\sigma^2_{Ab}$ and $\sigma^2_{Vb}$ be the values observed through the descriptive model in the bimodal condition.
-There are three possible cases of sub-optimality:
-
-1) Precision decreases equally for both modalities.
-That is, $\frac{1}{\sigma^2_{Ab}} < \frac{1}{\sigma^2_{A}}$ and $\frac{1}{\sigma^2_{Vb}} < \frac{1}{\sigma^2_{V}}$, but  $\frac{\sigma^2_{Ab}}{\sigma^2_{Vb}} \approx \frac{\sigma^2_{A}}{\sigma^2_{V}}$.
+Deviation from optimality can be quantified in two ways.
+First, we quantify changes in the values of the variances specific to each modality, that is, how $\sigma^2_{A}$ compares to $\sigma^2_{Ab}$, and how $\sigma^2_{V}$ compares to $\sigma^2_{Vb}$.
+Second,  we quantify changes in the proportion of the visual and auditory variances, i.e., how $\frac{\sigma^2_{A}}{\sigma^2_{V}}$ compares to $\frac{\sigma^2_{Ab}}{\sigma^2_{Vb}}$.
+The first comparison allows us to test if precision varies for each modality, and the second, allows us to test whether or not the weighing scheme folows the prediction of the optimal model.
+The reason we used the proportion of the variances as an measure of cross-modal weighing is because it correponds to the slope of the decision threshold in the audio-visual space (Figure\ \@ref(fig:model)).
+The decision threshold is defined as the set of values in this audio-visual space along which the posterior is equal to 0.5.
+Formally speaking, the decision threshold takes the following form:
+
+$$v=-\frac{\sigma^2_V}{\sigma^2_A}a+v_0$$
+
+If the slope derived from the descriptive model is greater than the slope of the optimal model, the corresponding shift in the decision threshold indicates that participants have a preference for the auditory modality in the bimodal case.
+Similarly, a smaller slope would lead to a preference for the visual modality.
+The limit cases are when there is exclusive reliance on the auditory cue (a vertical line), and where there is exclusive reliance on the visual (a horizontal line).
+
+There are three possible scenarios for sub-optimality, as illustrated in Figure\ \@ref(fig:subOptim):
+
+1) Both variances may increase, but their proportion remains the same.
+That is, $\frac{1}{\sigma^2_{Ab}} \leqslant \frac{1}{\sigma^2_{A}}$ and $\frac{1}{\sigma^2_{Vb}} \leqslant \frac{1}{\sigma^2_{V}}$, but  $\frac{\sigma^2_{Ab}}{\sigma^2_{Vb}} \approx \frac{\sigma^2_{A}}{\sigma^2_{V}}$.
 In this case, sub-optimality would be due to increased randomness in human responses in the bimodal condition.
@@
 
-2) The precision of the auditory modality decreases at a higher rate.
+2) The auditory variance increases at a higher rate.
 That is, $\frac{1}{\sigma^2_{Ab}} \ll \frac{1}{\sigma^2_{A}}$ and $\frac{1}{\sigma^2_{Vb}} \leq \frac{1}{\sigma^2_{V}}$, leading to $\frac{\sigma^2_{Ab}}{\sigma^2_{Vb}} > \frac{\sigma^2_{A}}{\sigma^2_{V}}$.
-In this case, sub-optimally would consist not only in participants being more random in the bimodal condition, but also in them thaving a systematic preference for the visual modality, even after accounting for informational reliability.
-
-3) The precision of the visual modality decreases at a higher rate.
+In this case, sub-optimally would consist not only in participants being more random in the bimodal condition, but also in having a systematic preference for the visual modality, even after accounting for informational reliability.
+
+3) The visual variance increases at a higher rate.
 That is, $\frac{1}{\sigma^2_{Vb}} \ll \frac{1}{\sigma^2_{V}}$, and  $\frac{1}{\sigma^2_{Ab}} \leq \frac{1}{\sigma^2_{A}}$, leading to $\frac{\sigma^2_{Ab}}{\sigma^2_{Vb}} > \frac{\sigma^2_{A}}{\sigma^2_{V}}$.
@@
 
-A more principled way to understand these three cases of sub-optimality, especially with regard to modality preference, is to study deviations from the optimal decision threshold.
-The decision threshold is defined as the set of values in the audio-visual space along which the posterior is equal to 0.5.
-The decision threshold takes the following form:
-
-$$v=-\frac{\sigma^2_V}{\sigma^2_A}a+v_0$$
-
-If the slope derived from the descriptive model is greater than the slope of the optimal model, the corresponding shift in the decision threshold indicate that participants have a preference for the auditory modality in the bimodal case.
-similarly, a smaller slope would lead to a preference for the visual modality.
-The limit cases are when there is exclusive reliance on the auditory cue (a vertical line), and where there is exclusive reliance on the visual (a horizontal line).
-Figure\ \@ref(fig:subOptim) illustrate the three cases of sub-optimality discussed above.
-
-```{r subOptim, fig.cap = "Illustration using simulated data showing the prediction of the optimal model (top), and three possible ways human responses, as characterized by the descriptive model, can deviate from the optimal predictions (bottom).
-There are three possible cases of sub-optimlaity: 1) the precision drops equally for both modalities, and the cue weighing is still optimal (bottom, left), 2) the precision of the visual modality drops at a higher rate, leading to bias towards the auditory modality (bottom, middle), and 3) the precision of the auditory modality drops at a higher rate, leading to bias towards the visual modality (bottom, right)", fig.align = "center", out.width = "400px"}
+```{r subOptim, fig.cap = "Illustration using simulated data showing the prediction of the optimal model (top), and the three possible ways human responses can deviate from the optimal predictions (bottom).
+These cases are: 1) the variance increases equally for both modalities, but the cue weighting is still optimal, 2) The auditory variance increases at a higher rate, leading to a preference for the auditory modality, and 3) The visual variance increases at a higher rate, leading to a preference for the visual modality", fig.align = "center", out.width = "400px"}
 knitr::include_graphics("pictures/sub-optimal", dpi = 108)
@@
 
-In the following, we test these predictions in three Experiments.
-In Experiment 1, we study the case where bimodal uncertainty is due to ambiguity in terms of category membership, without any additional background noise.
-In Experiment 2 and 3 we add background noise on top of ambiguity in category membership.
-In Experiment 2 we add background noise to the auditory modality, and in Experiment 3 we add background noise to the visual modality.
+We tested these predictions in three experiments.
+In Experiment 1, we studied the case where bimodal uncertainty is due to ambiguity in terms of category membership, without any additional background noise.
+In Experiment 2 and 3 we added background noise on top of ambiguity in category membership.
 
@@
 
-In this Experiment, we start with testing the predictions in the case where uncertainty is due to ambiguity in terms of category membership, without any additional noise in the background.
+In this Experiment, we start with testing the predictions in the case where uncertainty is due to ambiguity in terms of category membership only, that is, according to the following weighting scheme:  $$\beta_a \propto \frac{1}{\sigma^2_{A}}$$ $$\beta_v \propto \frac{1}{\sigma^2_{V}}$$ We do not introduce any additional noise in the background, and we assume that sensory noise is negligeable compared to categorical variability.
 
@@
 They were paid at an hourly rate of \$6/hour.
-participants were excluded if they took the experiment more than once (N=`r  N_twice_1`), then if they reported having experienced a technical problem of any sort during the online experiment (N=`r N_all_1 - N_noProb_1`), and finally if they had less than 50\% accurate responses on the unambiguous training trials (N=`r N_noProb_1 - N_good_1`).
-The final sample consisted of (N = `r N_good_1`) participants\footnote{The sample size and exclusion criteria were specified in the pre-registration at https://osf.io/h7mzp/}.
+Participants were excluded if they reported having experienced a technical problem of any sort during the online experiment (N=`r N_all_1 - N_noProb_1`), or if they had less than 50\% accurate responses on the unambiguous training trials (N=`r N_noProb_1 - N_good_1`).
+The final sample consisted of (N = `r N_good_1`) participants.\footnote{The sample size and exclusion criteria were specified in the pre-registration at https://osf.io/h7mzp/.}
 
@@
 ### Design and Procedure
-We told participants that an alien was naming two objects: a dog, called "aba"" in the alien language, and a cat, called "ada".
+We told participants that an alien was naming two objects: a dog, called "aba" in the alien language, and a cat, called "ada".
 In each trial, we presented the first object (the target) on the left side of the screen simultaneously with the corresponding sound.
-The target was always the same (e.g., dog-/aba/).
+For each participant, the target was always the same (e.g., dog-/aba/).
 The second sound-object pair (the test) followed on the other side of the screen after 500ms and varied in its category membership.
@@
 We instructed participants to press "S" for same if they thought the alien was naming another dog-/aba/, and "D" for different if they thought the alien was naming a cat-/ada/.
-For each participant, we randomized the sound-object mapping as well as the identity of the target.
+We randomized the sound-object mapping (e.g., dog-/aba/, cat-/ada/) as well as the identity of the target (dog or cat) across participants.
 
@@
 
-## Results and analysis
-
 ```{r echo=FALSE}
@@
 
-results1 <- boot(data=exp1_good, statistic = lmfit, R = 10000)
+#results1 <- boot(data=exp1_good, statistic = lmfit, R = 10000)
+
+#dataSave1 <- data.frame(matrix(ncol = 5, nrow = 0))
+#data_names <- c("variable", "estimate", "lower","upper", "Experiment")
+#colnames(dataSave1) <- data_names
 
 #Auditory variance:
-audVar=boot.ci(results1, index = 1, type = c("bca"), conf = 0.95)
-audVar_val=audVar$t0 
-audVar_ci1=audVar$bca[4]
-audVar_ci2=audVar$bca[5]
+#audVar=boot.ci(results1, index = 1, type = c("bca"), conf = 0.95)
+
+#v1 <- data.frame('audVar', as.numeric(audVar$t0), as.numeric(audVar$bca[4]), as.numeric(audVar$bca[5]), 'Exp1')
+#  colnames(v1) <- data_names
 
 #Auditory bias:
-audBias=boot.ci(results1, index = 2, type = c("bca"), conf = 0.95)
-audBias_val=audBias$t0 
-audBias_ci1=audBias$bca[4]
-audBias_ci2=audBias$bca[5]
+#audBias=boot.ci(results1, index = 2, type = c("bca"), conf = 0.95)
+
+#v2 <- data.frame('audBias', as.numeric(audBias$t0), as.numeric(audBias$bca[4]), as.numeric(audBias$bca[5]), 'Exp1')
+#colnames(v2) <- data_names
 
 #Visual variance:
-visVar=boot.ci(results1, index = 3, type = c("bca"), conf = 0.95)
-visVar_val=visVar$t0 
-visVar_ci1=visVar$bca[4]
-visVar_ci2=visVar$bca[5]
+#visVar=boot.ci(results1, index = 3, type = c("bca"), conf = 0.95)
+
+#v3 <- data.frame('visVar', as.numeric(visVar$t0), as.numeric(visVar$bca[4]), as.numeric(visVar$bca[5]), 'Exp1')
+#colnames(v3) <- data_names
 
 #Visual bias:
-visBias=boot.ci(results1, index = 4, type = c("bca"), conf = 0.95)
-visBias_val=visBias$t0 
-visBias_ci1=visBias$bca[4]
-visBias_ci2=visBias$bca[5]
+#visBias=boot.ci(results1, index = 4, type = c("bca"), conf = 0.95)
+
+#v4 <- data.frame('visBias', as.numeric(visBias$t0), as.numeric(visBias$bca[4]), as.numeric(visBias$bca[5]), 'Exp1')
+#colnames(v4) <- data_names
 
 #Bimodal Auditory variance:
-audVarBi=boot.ci(results1, index = 5, type = c("bca"), conf = 0.95)
-audVarBi_val=audVarBi$t0 
-audVarBi_ci1=audVarBi$bca[4]
-audVarBi_ci2=audVarBi$bca[5]
+#audVarBi=boot.ci(results1, index = 5, type = c("bca"), conf = 0.95)
+
+#v5 <- data.frame('audVarBi', as.numeric(audVarBi$t0), as.numeric(audVarBi$bca[4]), as.numeric(audVarBi$bca[5]), 'Exp1')
+#colnames(v5) <- data_names
 
 #Bimodal Visual variance:
-visVarBi=boot.ci(results1, index = 6, type = c("bca"), conf = 0.95)
-visVarBi_val=visVarBi$t0 
-visVarBi_ci1=visVarBi$bca[4]
-visVarBi_ci2=visVarBi$bca[5]
+#visVarBi=boot.ci(results1, index = 6, type = c("bca"), conf = 0.95)
+
+#v6 <- data.frame('visVarBi', as.numeric(visVarBi$t0), as.numeric(visVarBi$bca[4]), as.numeric(visVarBi$bca[5]), 'Exp1')
+#colnames(v6) <- data_names
 
 #Bimodal bias:
-BiasBi=boot.ci(results1, index = 7, type = c("bca"), conf = 0.95)
-BiasBi_val=BiasBi$t0 
-BiasBi_ci1=BiasBi$bca[4]
-BiasBi_ci2=BiasBi$bca[5]
+#BiasBi=boot.ci(results1, index = 7, type = c("bca"), conf = 0.95)
+
+#v7 <- data.frame('BiasBi', as.numeric(BiasBi$t0), as.numeric(BiasBi$bca[4]), as.numeric(BiasBi$bca[5]), 'Exp1')
+#colnames(v7) <- data_names
 
 #Ideal modality wieghing
-prefIdeal=boot.ci(results1, index = 8, type = c("bca"), conf = 0.95)
-prefIdeal_val=prefIdeal$t0 
-prefIdeal_ci1=prefIdeal$bca[4]
-prefIdeal_ci2=prefIdeal$bca[5]
+#prefIdeal=boot.ci(results1, index = 8, type = c("bca"), conf = 0.95)
+
+#v8 <- data.frame('prefIdeal', as.numeric(prefIdeal$t0), as.numeric(prefIdeal$bca[4]), as.numeric(prefIdeal$bca[5]), 'Exp1')
+#colnames(v8) <- data_names
 
 #fit modality wieghing
-prefFit=boot.ci(results1, index = 9, type = c("bca"), conf = 0.95)
-prefFit_val=prefFit$t0 
-prefFit_ci1=prefFit$bca[4]
-prefFit_ci2=prefFit$bca[5]
+#prefFit=boot.ci(results1, index = 9, type = c("bca"), conf = 0.95)
+
+#v9 <- data.frame('prefFit', as.numeric(prefFit$t0), as.numeric(prefFit$bca[4]), as.numeric(prefFit$bca[5]), 'Exp1')
+#colnames(v9) <- data_names
 
 #Modality bias 
-bias=boot.ci(results1, index = 10, type = c("bca"), conf = 0.95)
-bias_val_1=bias$t0 
-bias_ci1_1=bias$bca[4]
-bias_ci2_1=bias$bca[5]
-
-```
-
-### Unimodal conditions
+#bias=boot.ci(results1, index = 10, type = c("bca"), conf = 0.95)
+
+#v10 <- data.frame('bias', as.numeric(bias$t0), as.numeric(bias$bca[4]), as.numeric(bias$bca[5]), 'Exp1')
+#colnames(v10) <- data_names
+
+#dataSave1 <- bind_rows(dataSave1, v1, v2, v3, v4, v5, v6, v7, v8, v9, v10)
+
+#feather::write_feather(dataSave1, "dataExp1.feather")
+
+dataSave1 <- feather::read_feather("dataExp1.feather")
+
+###### Extract values from saved data
+
+audVar_val=dataSave1$estimate[which(dataSave1$variable == "audVar")]
+audVar_ci1=dataSave1$lower[which(dataSave1$variable == "audVar")]
+audVar_ci2=dataSave1$upper[which(dataSave1$variable == "audVar")]
+
+audBias_val=-dataSave1$estimate[which(dataSave1$variable == "audBias")]
+audBias_ci1=-dataSave1$upper[which(dataSave1$variable == "audBias")]
+audBias_ci2=-dataSave1$lower[which(dataSave1$variable == "audBias")]
+
+visVar_val=dataSave1$estimate[which(dataSave1$variable == "visVar")]
+visVar_ci1=dataSave1$lower[which(dataSave1$variable == "visVar")]
+visVar_ci2=dataSave1$upper[which(dataSave1$variable == "visVar")]
+
+visBias_val=-dataSave1$estimate[which(dataSave1$variable == "visBias")]
+visBias_ci1=-dataSave1$upper[which(dataSave1$variable == "visBias")]
+visBias_ci2=-dataSave1$lower[which(dataSave1$variable == "visBias")]
+
+audVarBi_val=dataSave1$estimate[which(dataSave1$variable == "audVarBi")]
+audVarBi_ci1=dataSave1$lower[which(dataSave1$variable == "audVarBi")]
+audVarBi_ci2=dataSave1$upper[which(dataSave1$variable == "audVarBi")]
+
+visVarBi_val=dataSave1$estimate[which(dataSave1$variable == "visVarBi")]
+visVarBi_ci1=dataSave1$lower[which(dataSave1$variable == "visVarBi")]
+visVarBi_ci2=dataSave1$upper[which(dataSave1$variable == "visVarBi")]
+
+BiasBi_val=-dataSave1$estimate[which(dataSave1$variable == "BiasBi")]
+BiasBi_ci1=-dataSave1$upper[which(dataSave1$variable == "BiasBi")]
+BiasBi_ci2=-dataSave1$lower[which(dataSave1$variable == "BiasBi")]
+
+prefIdeal_val_1=dataSave1$estimate[which(dataSave1$variable == "prefIdeal")]
+prefIdeal_ci1_1=dataSave1$lower[which(dataSave1$variable == "prefIdeal")]
+prefIdeal_ci2_1=dataSave1$upper[which(dataSave1$variable == "prefIdeal")]
+
+bias_val_1=dataSave1$estimate[which(dataSave1$variable == "bias")]
+bias_ci1_1=dataSave1$lower[which(dataSave1$variable == "bias")]
+bias_ci2_1=dataSave1$upper[which(dataSave1$variable == "bias")]
+
+```
+
+```{r}
+#Michael suggestion:
+#For a given particiapnts, sample
+
+```
 
@@
 concept_nl1 <- nls(answer ~ 1/(1+(1-e)*exp((-4/vrV)*concept_dist+(8/vrV))), data=concept_all_exp1, start = list(e=0, vrV=2))
+
+#Here I should test the cross-validation
 
@@
   geom_point()+
-  #geom_pointrange(aes(ymin = summary_ci_lower, ymax = summary_ci_upper), 
-  #                position = position_dodge(width = .1)) + 
+  geom_pointrange(aes(ymin = lower, ymax = upper), 
+                  position = position_dodge(width = .1)) + 
   #geom_line(data=uniV,aes(x=xV, y=yV))+
@@
 
-We first analysed the unimodal cases.
-These are the cases where the pictures were hidden, or where the sounds were muted.
-Average categorization judgments and fits are shown in Figure\ \@ref(fig:unimodal).
+### Model fitting details
+
+We first discuss the model fitting details of the unimodal conditions.
+Remember that data in this conditions allow us to derive the variances of both the auditory and the visual categories, and that these variances are used to make predictions about bimodal data (in the visual and auditory baselines as well as in the optimal model).
+These individual variances are derived as follows (we will explain the derivation for the auditory-only case, but the same applies for the visual-only case).
+For an ideal observer, when presented with an audio instance $a$, the probability of choosing the sound category 2 (that is, to answer "different") is the posterior probability of this category $p(A_2|a)$.
+If we assume that both sound categories have equal variances, the posterior probability reduces to:
+
+$$p(A_2 | a)=\frac{1}{1+(1+\epsilon_A)\exp(\beta_{a0}+\beta_aa)}$$
+
+with $\beta_a=\frac{\mu_{A_1}-\mu_{A_2}}{\sigma^2_{A}}$ and  $\beta_{a0}=\frac{\mu^2_{A_2}-\mu^2_{A_1}}{2\sigma^2_{A}}$.
+$\epsilon_A$ is the response bias in the auditory-only condition.
+For this model (as well all models in this study), we fixed the values of the means to be the end-points of the corresponding continuum, since these points are the most typical instances in our stimuli.
+Thus, we have $\mu_{A1}=0$ and $\mu_{A2}=4$ (and similarly $\mu_{V1}=0$, and $\mu_{V2}=4$).
+This leaves us with two free parameters: the bias $\epsilon_A$ and the variance $\sigma^2_{A}$.
+To determine the values of these parameteres, we fit the unimodal posterior to human data in the unimodal case.
+
+In the bimodal condition, only the desciptive model is fit to the data, using the posterior (Equation 1).
+Since the values of the means are fixed, we have 3 free parameteres: the variances for the visual and the auditory modalities, respectively, and $\epsilon$, the response bias.
+The visual and auditory baselines as well as the optimal model are not fit to bimodal data, but their predictions are tested against these bimodal data.
+All these notmative models use the variances derived from the unimodal data and the bias term derived from the bimodal data.
+
+Although the paradigm is within-subjcts, we did not have enough statistical power to fit a different model for each individual participant.
+Instead, models are constructed with data collapsed across all participants.
+The fit was done with a nonlinear least squares regression using the NLS package in R [@bates88].
+We computed the values of the parameters, as well as their 95% confidence intervals, through non-parametric bootstrap (with 10000 iterations).
+
+## Results and analysis
+
+### Unimodal conditions
+
+Average categorization judgments and best fits are shown in Figure\ \@ref(fig:unimodal).
 The categorization function of the auditory condition was slightly steeper than that of the visual condition, meaning that participants perceived the sound tokens slightly more categorically and whih higher certainty than they did with the visual tokens.
-
-Since we fixed the values of the means to be the endpoints of the corresponding continuum: $\mu_{A1}=0$ and $\mu_{A2}=4$ (and similarly $\mu_{V1}=0$, and $\mu_{V2}=4$), this leaves us with two free parameters: the bias and the variance.
-To determine the values of these parameters, we fit a model for each modality, collapsed across all participants.
-For the auditory modality, we obtained\footnote{all CIs in the paper are 95% confidence intervals} $\epsilon_A=$ `r audBias_val` CI [`r audBias_ci2`, `r audBias_ci1`] and $\sigma^2_A=$ `r audVar_val` CI [`r audVar_ci1`, `r audVar_ci2`].
-For the visual modality, we obtained $\epsilon_V=$ `r visBias_val` CI [`r visBias_ci2`, `r visBias_ci1`] and $\sigma^2_V=$ `r visVar_val` CI [`r visVar_ci1`, `r visVar_ci2`]`.
+For the auditory modality, we obtained the following values:^[all CIs in the paper are 95% confidence intervals] $\epsilon_A=$ `r audBias_val`  [`r audBias_ci2`, `r audBias_ci1`] and $\sigma^2_A=$ `r audVar_val` [`r audVar_ci1`, `r audVar_ci2`].
+For the visual modality, we obtained $\epsilon_V=$ `r visBias_val` [`r visBias_ci2`, `r visBias_ci1`] and $\sigma^2_V=$ `r visVar_val` [`r visVar_ci1`, `r visVar_ci2`]`.
 
@@
 #All models
+
+#Here we use the values obtained from the fitting using bootstrap sampling to
 
@@
 
+```{r}
+
+#Explore cross-validation here.
+As the numbers show, the predictions on the held-out subset is almost as acurate as the predcitions on the training set.
+Over-fitting is generally not a problem with such simple models)
+
+#Here is use hald the responses to predic the other half
+#The function takes the data to be cross-validated and return a score (coefficient of determination)
+
+crossValid <- function(data) {
+
+n <- nrow(data)
+frac <- 0.5
+ix <- sample(n, frac * n) # indexes of in sample rows
+
+fo <- answer ~ 1/(1+(1-e)*exp((-4/vrA_j)*sound_dist+(-4/vrV_j)*concept_dist+(8/vrA_j)+(8/vrV_j)))
+
+fm <- nls(fo, data, start = list(e=0, vrA_j=2, vrV_j=2), subset = ix) # fit the model to a subset (here half) the responses
+
+#Extract the values of the parameter
+
+data.test <- data[-ix, ] # out of sample data
+data.train <- data[ix, ]
+
+data.train.means <- data.train %>%
+  group_by(concept_dist, sound_dist) %>%
+  summarise(mean = mean(answer))
+
+data.test.means <- data.test %>%
+  group_by(concept_dist, sound_dist) %>%
+  summarise(mean = mean(answer))
+
+pred.train <-  predict(fm, new = data.train.means)
+pred.test <- predict(fm, new = data.test.means)
+
+cor.train <- cor(data.train.means$mean, pred.train)^2 
+cor.test <- cor(data.test.means$mean, pred.test)^2
+
+return(cor.test)
+
+}
+
+crossValid_exp1 <- replicate(10, {
+  crossValid(joint_all_exp1)
+  })
+
+CV_exp1_mean = mean(crossValid_exp1)
+error <- qt(0.975,df=length(crossValid_exp1)-1)*sd(crossValid_exp1)/sqrt(length(crossValid_exp1))
+CV_exp1_lower = CV_exp1_mean - error
+CV_exp1_upper = CV_exp1_mean + error
+
+crossValid_exp2 <- replicate(10, {
+  crossValid(joint_all_exp2)
+  })
+
+CV_exp2_mean = mean(crossValid_exp2)
+error <- qt(0.975,df=length(crossValid_exp2)-1)*sd(crossValid_exp2)/sqrt(length(crossValid_exp2))
+CV_exp2_lower = CV_exp2_mean - error
+CV_exp2_upper = CV_exp2_mean + error
+
+crossValid_exp3 <- replicate(10, {
+  crossValid(joint_all_exp3)
+  })
+
+CV_exp3_mean = mean(crossValid_exp3)
+error <- qt(0.975,df=length(crossValid_exp3)-1)*sd(crossValid_exp3)/sqrt(length(crossValid_exp3))
+CV_exp3_lower = CV_exp3_mean - error
+CV_exp3_upper = CV_exp3_mean + error
+
+```
+
 ```{r bimodal, fig.cap = "Human responses vs.
@@
 
-Now we analyse the bimodal case. This is the case where the participants saw the pictures and heard the sounds.
+Now we analyse the bimodal case. This is the case where the participants saw the pictures and heard the sounds simulateously.
+
+#### Normative models
+Figure\ \@ref(fig:bimodal) compares the predictions of the normative models against human responses.
+The visual, auditory and optimal model explained, respectively, `r 100*R2_visual_1`%, `r 100*R2_auditory_1`%, and `r 100*R2_optimal_1`% of total variance.
 
 #### Descriptive model
-We first consider the descriptive model where all parameters are fitted to human responses in the bimodal condition.
-We found $\epsilon=$ `r BiasBi_val` CI [`r BiasBi_ci2`, `r BiasBi_ci1`], $\sigma^2_{Ab}=$ `r audVarBi_val` CI [`r audVarBi_ci1`, `r audVarBi_ci2`] and $\sigma^2_{Vb}=$ `r visVarBi_val` CI [`r visVarBi_ci1`, `r visVarBi_ci2`].
+In the descriptive model, all parameters are fit to human responses in the bimodal condition.
+We found $\epsilon=$ `r BiasBi_val` [`r BiasBi_ci2`, `r BiasBi_ci1`], $\sigma^2_{Ab}=$ `r audVarBi_val` [`r audVarBi_ci1`, `r audVarBi_ci2`] and $\sigma^2_{Vb}=$ `r visVarBi_val` [`r visVarBi_ci1`, `r visVarBi_ci2`].
 Note that the precision of both the auditory and visual modalities decreased compared to the unimodal conditions.
+
 The descriptive model explained `r 100*R2_descriptive_1`% of total variance.
-
-#### Normative models
-We derived the predictions of the auditory, visual and optimal model by using the values of the variances derived from the unimodal conditions, and the response bias derived from the descriptive model.
-Figure\ \@ref(fig:bimodal) compares the predictions of these three models to human responses.
-The visual, auditory and optimal model explained, respectively, `r 100*R2_visual_1`%, `r 100*R2_auditory_1`%, and `r 100*R2_optimal_1`% of total variance.
+However, since the descriptive model was fit to the same data it is predicting, there is a risque this high correlation is due to overfitting.
+To examine this possibility, we cross-validated the model using half the responses to predict the other half (averaging across 1000 random partitions).
+The predictive power of the model remained high ($r^2$=`r CV_exp1_mean`).
 
@@
 We next analyzed the extent to which cue combination was performed in an optimal way, or whether there was a systematic preference for one modality when making decisions in the bimodal condition.
-We saw that response precision in the auditory modality was slightly higher than that of the visual modality (i.e., $\frac{1}{\sigma^2_A} > \frac{1}{\sigma^2_V}$ ).
-If modalities were weighed according to their relative reliability (that is, optimally), we would naturally expect the auditory modality to have a higher weight.
-But this is not what we mean by modality preference.
-Rather, the phrase refers to the case of potential sub-optimality where participants would rely on one modality beyond what is explained by the relative reliability of the optimal model.
-
-As explained above, modality preference can be characterized formally as a deviation from the decision threshold's slope predicted by the optimal model.
+As explained above, modality preference can be characterized formally as a deviation from the decision threshold predicted by the optimal model.
 Figure\ \@ref(fig:bias) shows the value of the slope derived from the descriptive model (i.e., $-\frac{\sigma^2_{Vb}}{\sigma^2_{Ab}}$) relative the slope of the optimal model (i.e., $-\frac{\sigma^2_V}{\sigma^2_A}$).
@@
 ## Discussion
-Overall, we found that the optimal model explained much of the variance in judgments, and largely more than what can be explained with the auditory or the visual models alone.
-The relatively high value of the coefficient of determination in the optimal model (`r 100*R2_optimal_1`%) suggests that participants were near-optimal in their responses.
-However, we see from Figure\ \@ref(fig:bimodal) that responses deviated from the optimal prediction in that they were slightly pulled toward chance (i.e., the value 0.5).
+Overall, we found that the optimal model explained much of the variance in the mean judgments, and largely more than what can be explained with the auditory or the visual models alone.
+The relatively high value of the coefficient of determination in the optimal model ($r^2$=`r R2_optimal_1`) suggests that the population was near-optimal.
+However, we see from Figure\ \@ref(fig:bimodal) that the mean responses deviated from the optimal prediction in that they were slightly pulled toward chance (i.e., the probability value of 0.5).
 This is due to the increase in the value of the variance associated with each modality.
-Note however that, despite this increase in randomness, our analysis of modality preference showed that the relative values of these variances were not different Figure\ \@ref(fig:bias).
-Thus, 1) the bimodal presentation introduced a certain level of randomness in the participants' responses, and 2) this increased randomness did not affect the relative weighting of both modalities, i.e., participants were weighting modalities according to their relative reliability.
-This situation corresponds to the first case of sub-optimally described in the predictions, above.
+Note however that, despite this increase in randomness, our analysis of modality preference showed that the relative values of these variances were not different (Figure\ \@ref(fig:bias)), meaning that there was no evidence for a modality preference.<!--\footnote{The absence of modality preference does not mean that participants weight modalities equally in the bimodal condtion.
+Rather, it means that they weight modalities according to their relative relaibility, as measure in the unimodal conditions.}In the unimodal analysis, we saw that the precision of the auditory modality was slightly higher than that of the visual modality (i.e., $\frac{1}{\sigma^2_A} > \frac{1}{\sigma^2_V}$ ).
+If modalities were weighed according to their relative reliability (that is, optimally), we would naturally expect the auditory modality to have a higher weight in the bimodal presentation.
+But this is not what we mean by modality preference.
+Rather, the phrase refers to the case of potential sub-optimality where participants would rely on one modality beyond what is explained by the relative reliability of the optimal model.
+--> Thus, 1) There was a simultaneous increase in the values of the auditory and visual variances in the bimodal condition compared to the unimodal condition, meaning that the bimodal input lead to an increase in response randomness, and 2) this increased randomness did not affect the relative weighting of both modalities, i.e., the population was weighting modalities according to their relative reliability predicted by the optimal model.
+This situation corresponds to the first case of sub-optimally described in the predictions.
+
+```{r echo=FALSE, warning = FALSE}
+
+joint_bysub_1 <- joint_all_exp1 %>%
+  group_by(ID) %>%
+  do(fit_joint_1 = glm(answer ~ concept_dist+ sound_dist, data=., family = binomial()))
+
+joint_bysub_2 <- joint_all_exp2 %>%
+  group_by(ID) %>%
+  do(fit_joint_2 = glm(answer ~ concept_dist+ sound_dist, data=., family = binomial()))
+
+joint_bysub_3 <- joint_all_exp3 %>%
+  group_by(ID) %>%
+  do(fit_joint_3 = glm(answer ~ concept_dist+ sound_dist, data=., family = binomial()))
+
+bimodal_bysub_1 = tidy(joint_bysub_1, fit_joint_1) %>%
+  filter(term == 'concept_dist' | term == 'sound_dist') %>%
+  mutate(j_var = 4/(estimate)) %>%
+  select(ID, term, j_var) %>%
+  spread(term, j_var) %>%
+  rename(j_c_var = concept_dist, 
+         j_s_var = sound_dist) %>%
+  mutate(bimod = j_c_var/j_s_var)
+
+bimodal_bysub_2 = tidy(joint_bysub_2, fit_joint_2) %>%
+  filter(term == 'concept_dist' | term == 'sound_dist') %>%
+  mutate(j_var = 4/(estimate)) %>%
+  select(ID, term, j_var) %>%
+  spread(term, j_var) %>%
+  rename(j_c_var = concept_dist, 
+         j_s_var = sound_dist) %>%
+  mutate(bimod = j_c_var/j_s_var)
+
+bimodal_bysub_3 = tidy(joint_bysub_3, fit_joint_3) %>%
+  filter(term == 'concept_dist' | term == 'sound_dist') %>%
+  mutate(j_var = 4/(estimate)) %>%
+  select(ID, term, j_var) %>%
+  spread(term, j_var) %>%
+  rename(j_c_var = concept_dist, 
+         j_s_var = sound_dist) %>%
+  mutate(bimod = j_c_var/j_s_var)
+
+```
+
+```{r echo=FALSE}
+#number of participants relying exlusiviely on one modality
+#cut off is a factor of 10
+
+bimodal_bysub_good_1 <- bimodal_bysub_1 %>%
+  filter(bimod > 0.1) %>%
+  filter(bimod < 10)
+
+#Visual modality 
+only_visual_N_1 <- bimodal_bysub_1 %>%
+  filter(abs(bimod) < 0.1) %>%
+  nrow()
+
+#Sound modality 
+only_sound_N_1 <- bimodal_bysub_1 %>%
+  filter(abs(bimod) > 10) %>%
+  nrow()
+
+#the rest
+both_N_1 <- bimodal_bysub_1 %>%
+  filter(abs(bimod) > 0.1) %>%
+  filter(abs(bimod) < 10) %>%
+  nrow()
+
+neg_N_1 <- bimodal_bysub_1 %>%
+  filter(bimod <  -0.1) %>%
+  filter(bimod > -10) %>%
+  nrow()
+
+exlusive_prop_1 = only_visual_N_1/only_sound_N_1
+
+```
+
+```{r echo=FALSE, warning = FALSE}
+#What does the mean data say 
+#generate two data point from a binomial with probabilty model_fit1()
+#loop over visual and auditory distance/ or create  adataframe with
+
+simulations <- data.frame()
+#x <- c("ID", "bimod")
+#colnames(simlations) <- x
+
+for (i in 1:50) {
+Simul_exp1 <- joint_all_exp1 %>%
+  select(ID, sound_dist, concept_dist) %>%
+  mutate(prob = model_fit1(sound_dist, concept_dist)) %>%
+  rowwise() %>%
+  mutate(answer = rbinom(1, 1, prob=prob))
+
+joint_bysub_sim_1 <- Simul_exp1 %>%
+  group_by(ID) %>%
+  do(fit_joint_sim_1 = glm(answer ~ concept_dist+ sound_dist, data=., family = binomial()))
+
+bimodal_bysub_sim_1 = tidy(joint_bysub_sim_1, fit_joint_sim_1) %>%
+  filter(term == 'concept_dist' | term == 'sound_dist') %>%
+  mutate(j_var = 4/(estimate)) %>%
+  select(ID, term, j_var) %>%
+  spread(term, j_var) %>%
+  rename(j_c_var = concept_dist, 
+         j_s_var = sound_dist) %>%
+  mutate(bimod = j_c_var/j_s_var) %>%
+  select(ID, bimod) %>%
+  filter(bimod > 0.1) %>%
+  filter(bimod < 10)
+
+  simulations <- bind_rows(simulations, bimodal_bysub_sim_1)
+}
+
+  #I need to take the average of this over multiple runs
+
+  bimod_sim <- simulations  %>%
+    mutate(data='simulation')
+
+  bimod_real <- bimodal_bysub_good_1  %>%
+    select(ID, bimod) %>%
+    mutate(data='real')
+
+  #n_remove <- nrow(bimod_sim)-nrow(bimod_real)
+
+  #bimod_sim <- head(bimod_sim, -n_remove)
+
+  bimod_all <- bind_rows(bimod_real, bimod_sim) 
+```
+
+```{r echo=FALSE, individual, fig.cap = "Histogram of the weighting values in the bimodal condition (the visual variance relative to the auditory variance) derived from each individual participants.", fig.align = "center", out.width = "400px", fig.width=7, fig.height=8}
+
+ggplot(data=bimod_all, aes(x=bimod, y=..ncount..)) +
+  geom_histogram(data=subset(bimod_all, data=='real'), fill="red", alpha=0.2, binwidth = 0.2)+
+  geom_histogram(data=subset(bimod_all, data=='simulation'), fill="blue", alpha=0.2, binwidth = 0.2)+
+  #geom_histogram(binwidth = 0.2) +
+  scale_x_log10() +
+   xlab("Visual variance relative to sound variance") +ylab("Count")+
+  theme(aspect.ratio = 0.7)
+
+```
+
+As we noted earlier, the model adresses the issue of optimality at the poplation level.
+However, it is important to have a general sense of the individual distribution.
+In fact, one could think of an extreme case where optimality at the poupulation level would be misleading.
+Imagine, for instance, that in the bimodal condition half the participants relied exclusively on the visual modality, whereas the other half relied exclusively on the auditory modality.
+This case could still lead to an agregate behaviour which appears optimal, but this optimality would be spurious.
+
+To examine this possibility, we consider the distribution of individual cross-modal weighting in the bimodal condition (i.e., $\frac{\sigma^2_{Vb}}{\sigma^2_{Ab}}$).
+Using a factor of 10 as a cut-off, we found that `r only_visual_N_1` participants relied almost exlusively on the visual modality, and `r only_sound_N_1` relied almost exclusively on the auditory modality.
+The percentage of both these cases reamined liminted compared to the total number of participants (`r 100*(only_visual_N_1+only_sound_N_1)/(only_visual_N_1+only_sound_N_1+both_N_1)`%).
+An additional number of participants (N=`r neg_N_1`) relied on both modalities, but privided noisy responses which lead to negative variances (probably because they mistook 'same' for 'different' or vice versa).
+When these outliers  were removed, the distribution had an unimodal shape (Figure\ \@ref(fig:individual)).
+This finding indicates that the population's near optimality is not spurious, but based mostly on geniune cue combination at the individual level.
+
+As a second analysis, we asked whether the observed variability at the individual level corresponded to mere sampling errors or whether it corresponded to a real between-subject varation.
+To answer this question, we simulated individual responses from the posterior distribution whose parameters were fit to the population as a whole (i.e., the descriptive posterior).
+The simulated distribution was super-imposed to the real distribution in Figure\ \@ref(fig:individual).
+The real distribution is braoder than the simulated distribution, indivating that there is evidence for a between-subject variation beyond sampling errors.
+This means that the particiapnts varied in terms of how they wheighed modalities: Compared to the predictions of the global descriptive model, some participants relied more on the auditory modality, and some relied more on the visual modality.
+
+<!--If, according to the extreme hypothetical case, the observed near-optimality is spurious, with participants relying exclusively on one or the other modality, we should observe a bimodal distribution (with modes centred around a very small and a very large number).
+If, instead, participants relied on both modalities, we should observe a unimodal distribution centered around a number whose order of magnitude is similar to the one observed with collapsed data.
+-->
 
 In Experiment 1, we tested word recognition when there was multimodal uncertainty in terms of category membership only.
-In real life, however, tokens can undergo distortions due to noisy factors in the environment (e.g., car noise in the background, blurry vision in a foggy weather,..)\footnote{Note that we are considering environmental noise, which is different from the noise inherent to perception.}.
+In real life, however, tokens can undergo distortions due to noisy factors in the environment (e.g., car noise in the background, blurry vision in a foggy weather,..).
 In Experiment 2 and 3, we explore this additional level of uncertainty.
@@
 
-Imagine that the speaker generates a target production $t$ from an auditory category
-$t | A \sim N(\mu_{A}, \sigma^2_{A})$.
-In Experiment 1, we assumed that the observer could directly retrieve this production token.
-But if the observer is in a noisy environment, they do not hear exactly this produced target, but the target perturbed by noise.
-We assume this noise to be normally distributed: $a | t \sim N(t, \sigma^2_{N})$, and we integrate over $t$.
-We obtain the following simple expression:
-
-$$ a | A \sim N(\mu_{A}, \sigma^2_{A}+\sigma^2_{N})$$
-
-In this experiment, we explored the effect of this added noise on performance in our task.
+In this Experiment, we explored the effect of added noise on performance.
 We tested a case where the background noise was added to the auditory modality.
-We were interested to know if participants would treat this new source of uncertainty as predicted by the optimal model, and whether noise in one modality would lead to some systematic preference for the non-noisy modality.
+We were interested to know if participants would treat this new source of uncertainty as predicted by the optimal model, that is, according to the following weighting scheme  $$\beta_a \propto \frac{1}{\sigma^2_{A}+\sigma^2_{N_A}}$$ $$\beta_v \propto \frac{1}{\sigma^2_{V}}$$
+The alternative hypothesies is that noise in one modality leads to a systematic preference for the non-noisy modality.
 
@@
 A sample of `r N_all_2` participants was recruited online through Amazon Mechanical Turk.
-We used the same exclusion criteria as in the previous experiment.
+We used the same exclusion criteria as in Experiment 1.
+`r N_noProb_2 - N_good_2` participants were excluded because they had less than 50\% accurate responses on the unambiguous training trials.
 The final sample consisted of (N = `r N_good_2`) participants.
@@
 We used the same visual stimuli as in Experiment 1.
-We also used the same auditory stimuli, but we convolved each item with Brown noise of amplitude 1 using the audio editor Audacity (2.1.2) (signal to noise ratio XXXX).
+We also used the same auditory stimuli, but we convolved each item with Brown noise of amplitude 1 using the free sound editor Audacity (2.1.2).
+The average signal-to-noise ratio was - 4.4 dB.
 The procedure was exactly the same as in the previous experiment, except that test stimuli (but not the target) were presented with the new noisy auditory stimuli.
@@
 
-results1 <- boot(data=exp2_good, statistic = lmfit, R = 10000)
+#results2 <- boot(data=exp2_good, statistic = lmfit, R = 10000)
+
+#dataSave2 <- data.frame(matrix(ncol = 5, nrow = 0))
+#data_names <- c("variable", "estimate", "lower","upper", "Experiment")
+#colnames(dataSave2) <- data_names
 
 #Auditory variance:
-audVar=boot.ci(results1, index = 1, type = c("bca"), conf = 0.95)
-audVar_val=audVar$t0 
-audVar_ci1=audVar$bca[4]
-audVar_ci2=audVar$bca[5]
+#audVar=boot.ci(results2, index = 1, type = c("bca"), conf = 0.95)
+
+#v1 <- data.frame('audVar', as.numeric(audVar$t0), as.numeric(audVar$bca[4]), as.numeric(audVar$bca[5]), 'Exp2')
+#  colnames(v1) <- data_names
 
 #Auditory bias:
-audBias=boot.ci(results1, index = 2, type = c("bca"), conf = 0.95)
-audBias_val=audBias$t0 
-audBias_ci1=audBias$bca[4]
-audBias_ci2=audBias$bca[5]
+#audBias=boot.ci(results2, index = 2, type = c("bca"), conf = 0.95)
+
+#v2 <- data.frame('audBias', as.numeric(audBias$t0), as.numeric(audBias$bca[4]), as.numeric(audBias$bca[5]), 'Exp2')
+#  colnames(v2) <- data_names
 
 #Visual variance:
-visVar=boot.ci(results1, index = 3, type = c("bca"), conf = 0.95)
-visVar_val=visVar$t0 
-visVar_ci1=visVar$bca[4]
-visVar_ci2=visVar$bca[5]
+#visVar=boot.ci(results2, index = 3, type = c("bca"), conf = 0.95)
+
+#v3 <- data.frame('visVar', as.numeric(visVar$t0), as.numeric(visVar$bca[4]), as.numeric(visVar$bca[5]), 'Exp1')
+#  colnames(v3) <- data_names
 
 #Visual bias:
-visBias=boot.ci(results1, index = 4, type = c("bca"), conf = 0.95)
-visBias_val=visBias$t0 
-visBias_ci1=visBias$bca[4]
-visBias_ci2=visBias$bca[5]
+#visBias=boot.ci(results2, index = 4, type = c("bca"), conf = 0.95)
+
+#v4 <- data.frame('visBias', as.numeric(visBias$t0), as.numeric(visBias$bca[4]), as.numeric(visBias$bca[5]), 'Exp2')
+#colnames(v4) <- data_names
 
 #Bimodal Auditory variance:
-audVarBi=boot.ci(results1, index = 5, type = c("bca"), conf = 0.95)
-audVarBi_val=audVarBi$t0 
-audVarBi_ci1=audVarBi$bca[4]
-audVarBi_ci2=audVarBi$bca[5]
+#audVarBi=boot.ci(results2, index = 5, type = c("bca"), conf = 0.95)
+
+#v5 <- data.frame('audVarBi', as.numeric(audVarBi$t0), as.numeric(audVarBi$bca[4]), as.numeric(audVarBi$bca[5]), 'Exp2')
+#  colnames(v5) <- data_names
+#
 
 #Bimodal Visual variance:
-visVarBi=boot.ci(results1, index = 6, type = c("bca"), conf = 0.95)
-visVarBi_val=visVarBi$t0 
-visVarBi_ci1=visVarBi$bca[4]
-visVarBi_ci2=visVarBi$bca[5]
+#visVarBi=boot.ci(results2, index = 6, type = c("bca"), conf = 0.95)
+
+#v6 <- data.frame('visVarBi', as.numeric(visVarBi$t0), as.numeric(visVarBi$bca[4]), as.numeric(visVarBi$bca[5]), 'Exp2')
+#  colnames(v6) <- data_names
 
 #Bimodal bias:
-BiasBi=boot.ci(results1, index = 7, type = c("bca"), conf = 0.95)
-BiasBi_val=BiasBi$t0 
-BiasBi_ci1=BiasBi$bca[4]
-BiasBi_ci2=BiasBi$bca[5]
+#BiasBi=boot.ci(results2, index = 7, type = c("bca"), conf = 0.95)
+
+#v7 <- data.frame('BiasBi', as.numeric(BiasBi$t0), as.numeric(BiasBi$bca[4]), as.numeric(BiasBi$bca[5]), 'Exp2')
+#  colnames(v7) <- data_names
 
 #Ideal modality wieghing
-prefIdeal=boot.ci(results1, index = 8, type = c("bca"), conf = 0.95)
-prefIdeal_val=prefIdeal$t0 
-prefIdeal_ci1=prefIdeal$bca[4]
-prefIdeal_ci2=prefIdeal$bca[5]
+#prefIdeal=boot.ci(results2, index = 8, type = c("bca"), conf = 0.95)
+
+#v8 <- data.frame('prefIdeal', as.numeric(prefIdeal$t0), as.numeric(prefIdeal$bca[4]), as.numeric(prefIdeal$bca[5]), 'Exp2')
+#  colnames(v8) <- data_names
 
 #fit modality wieghing
-prefFit=boot.ci(results1, index = 9, type = c("bca"), conf = 0.95)
-prefFit_val=prefFit$t0 
-prefFit_ci1=prefFit$bca[4]
-prefFit_ci2=prefFit$bca[5]
+#prefFit=boot.ci(results2, index = 9, type = c("bca"), conf = 0.95)
+
+#v9 <- data.frame('prefFit', as.numeric(prefFit$t0), as.numeric(prefFit$bca[4]), as.numeric(prefFit$bca[5]), 'Exp2')
+#  colnames(v9) <- data_names
 
 #Modality bias 
-bias=boot.ci(results1, index = 10, type = c("bca"), conf = 0.95)
-bias_val_2=bias$t0 
-bias_ci1_2=bias$bca[4]
-bias_ci2_2=bias$bca[5]
+#bias=boot.ci(results2, index = 10, type = c("bca"), conf = 0.95)
+
+#v10 <- data.frame('bias', as.numeric(bias$t0), as.numeric(bias$bca[4]), as.numeric(bias$bca[5]), 'Exp2')
+#  colnames(v10) <- data_names
+
+#dataSave2 <- bind_rows(dataSave2, v1, v2, v3, v4, v5, v6, v7, v8, v9, v10)
+
+#feather::write_feather(dataSave2, "dataExp2.feather")
+
+dataSave2 <- feather::read_feather("dataExp2.feather")
+
+#Extract values 
+audVar_val=dataSave2$estimate[which(dataSave2$variable == "audVar")]
+audVar_ci1=dataSave2$lower[which(dataSave2$variable == "audVar")]
+audVar_ci2=dataSave2$upper[which(dataSave2$variable == "audVar")]
+
+audBias_val=-dataSave2$estimate[which(dataSave2$variable == "audBias")]
+audBias_ci1=-dataSave2$upper[which(dataSave2$variable == "audBias")]
+audBias_ci2=-dataSave2$lower[which(dataSave2$variable == "audBias")]
+
+visVar_val=dataSave2$estimate[which(dataSave2$variable == "visVar")]
+visVar_ci1=dataSave2$lower[which(dataSave2$variable == "visVar")]
+visVar_ci2=dataSave2$upper[which(dataSave2$variable == "visVar")]
+
+visBias_val=-dataSave2$estimate[which(dataSave2$variable == "visBias")]
+visBias_ci1=-dataSave2$upper[which(dataSave2$variable == "visBias")]
+visBias_ci2=-dataSave2$lower[which(dataSave2$variable == "visBias")]
+
+audVarBi_val=dataSave2$estimate[which(dataSave2$variable == "audVarBi")]
+audVarBi_ci1=dataSave2$lower[which(dataSave2$variable == "audVarBi")]
+audVarBi_ci2=dataSave2$upper[which(dataSave2$variable == "audVarBi")]
+
+visVarBi_val=dataSave2$estimate[which(dataSave2$variable == "visVarBi")]
+visVarBi_ci1=dataSave2$lower[which(dataSave2$variable == "visVarBi")]
+visVarBi_ci2=dataSave2$upper[which(dataSave2$variable == "visVarBi")]
+
+BiasBi_val=-dataSave2$estimate[which(dataSave2$variable == "BiasBi")]
+BiasBi_ci1=-dataSave2$upper[which(dataSave2$variable == "BiasBi")]
+BiasBi_ci2=-dataSave2$lower[which(dataSave2$variable == "BiasBi")]
+
+prefIdeal_val_2=dataSave2$estimate[which(dataSave2$variable == "prefIdeal")]
+prefIdeal_ci1_2=dataSave2$lower[which(dataSave2$variable == "prefIdeal")]
+prefIdeal_ci2_2=dataSave2$upper[which(dataSave2$variable == "prefIdeal")]
+
+bias_val_2=dataSave2$estimate[which(dataSave2$variable == "bias")]
+bias_ci1_2=dataSave2$lower[which(dataSave2$variable == "bias")]
+bias_ci2_2=dataSave2$upper[which(dataSave2$variable == "bias")]
 
@@
 We fit a model for each modality, collapsed across all participants.
-For the auditory modality, our parameter estimates were $\epsilon_A=$ `r audBias_val` CI [`r audBias_ci2`, `r audBias_ci1`] and $\sigma^2_A+\sigma^2_N=$ `r audVar_val` CI [`r audVar_ci1`, `r audVar_ci2`].
-For the visual modality, we found $\epsilon_V=$ `r visBias_val` CI [`r visBias_ci2`, `r visBias_ci1`] and $\sigma^2_V=$ `r visVar_val` CI [`r visVar_ci1`, `r visVar_ci2`].
-Figure\ \@ref(fig:unimodal) shows responses in the unimodal conditions as well as the corresponding fits.
+For the auditory modality, our parameter estimates were $\epsilon_A=$ `r audBias_val` [`r audBias_ci2`, `r audBias_ci1`] and $\sigma^2_A+\sigma^2_N=$ `r audVar_val` [`r audVar_ci1`, `r audVar_ci2`].
+For the visual modality, we found $\epsilon_V=$ `r visBias_val` [`r visBias_ci2`, `r visBias_ci1`] and $\sigma^2_V=$ `r visVar_val` [`r visVar_ci1`, `r visVar_ci2`].
+Figure\ \@ref(fig:unimodal) shows responses in the unimodal conditions as well as the corresponding best fits.
 The visual data is a replication of the vidual data in Experiment 1.
-As for the auditory data, we see that, in contrast to Experiment 1, responses were less categorical/flatter (showing more uncertainty).
+As for the auditory data, we see that, in contrast to Experiment 1, responses were less categorical/flatter, showing more uncertainty.
 
@@
 We fit the descriptive model to human responses in the bimodal condition, collapsed across all articipants.
-We estimated $\epsilon=$ `r BiasBi_val` CI [`r BiasBi_ci2`, `r BiasBi_ci1`], $\sigma^2_{Ab}+\sigma^2_{Nb}=$ `r audVarBi_val` CI [`r audVarBi_ci1`, `r audVarBi_ci2`], and $\sigma^2_{Vb}=$ `r visVarBi_val` CI [`r visVarBi_ci1`, `r visVarBi_ci2`].
+We estimated $\epsilon=$ `r BiasBi_val` [`r BiasBi_ci2`, `r BiasBi_ci1`], $\sigma^2_{Ab}+\sigma^2_{Nb}=$ `r audVarBi_val` [`r audVarBi_ci1`, `r audVarBi_ci2`], and $\sigma^2_{Vb}=$ `r visVarBi_val` [`r visVarBi_ci1`, `r visVarBi_ci2`].
 The fit explained `r R2_descriptive_2`% of total variance.
+Cross-validation using half the responses to predict tho other half yields $r^2=$`r CV_exp2_mean` [`r CV_exp2_lower`, `r CV_exp2_upper`].
 
@@
 Participants' decision threshold suggested a preference for the visual modality (the non-noisy modality).
-Indeed non-parametric resampling of the data showed a decrease in the value of the slope in the descriptive model compared to the optimal model Figure\ \@ref(fig:bias).
+Indeed non-parametric resampling of the data showed a decrease in the value of the slope in the descriptive model compared to the optimal model (Figure\ \@ref(fig:bias)).
 
 ## Discussion
-We found, similar to Experiment 1, that participants were generally near optimal (explaining  `r 100*R2_optimal_2`% of total variance), and that the optimal model explained more variance than the auditory or the visual models alone.
+We found, similar to Experiment 1, that participants were generally near optimal ($r^2 =$ `r R2_optimal_2`% of total variance), and that the optimal model explained more variance than the auditory or the visual models alone.
 We also found a similar discrepancy from the optimal model as precision dropped for both the auditory and the visual modalities.
@@
 
+```{r echo=FALSE}
+#number of participants relying exlusiviely on one modality
+#cut off is a factor of 10
+
+bimodal_bysub_good_2 <- bimodal_bysub_2 %>%
+  filter(bimod > 0.1) %>%
+  filter(bimod < 10)
+
+#Visual modality 
+only_visual_N_2 <- bimodal_bysub_2 %>%
+  filter(abs(bimod) < 0.1) %>%
+  nrow()
+
+#Sound modality 
+only_sound_N_2 <- bimodal_bysub_2 %>%
+  filter(abs(bimod) > 10) %>%
+  nrow()
+
+#the rest
+both_N_2 <- bimodal_bysub_2 %>%
+  filter(abs(bimod) > 0.1) %>%
+  filter(abs(bimod) < 10) %>%
+  nrow()
+
+neg_N_2 <- bimodal_bysub_2 %>%
+  filter(bimod <  -0.1) %>%
+  filter(bimod > -10) %>%
+  nrow()
+
+exlusive_prop_2 = only_visual_N_2/only_sound_N_2
+
+```
+We were also interested in whether noise in the auditory modality lead more participants to rely exclusviely on the visual modality at the indivual level.
+Using the same cut-off as in Experiment 1 (a factor of 10), the percentage of particpants who relied exclusively on eiter modalities was `r 100*(only_visual_N_2+only_sound_N_2)/(only_visual_N_2+only_sound_N_2+both_N_2)`%, which is much higher than the percentage abtained in Experiment 1 (`r 100*(only_visual_N_1+only_sound_N_1)/(only_visual_N_1+only_sound_N_1+both_N_1)`%).
+Moreover, the propotion of participants relying exclusively on the visual modality relative to the sound modality reversed from `r exlusive_prop_1` in Experiment 1 to `r exlusive_prop_2` in the present experiment, suggesting that noise in the auditory modality prompted more participants to rely exclusively and disproportionately on the visual modality.
+
 In Experiment 2, we tested the case where we added background noise to the auditory modality. In Experiment 3, we test the situation where we added noise to the visual modality.
@@
 
-We follow exactly the same formal reasoning in this case, as we did in Experiment 2.
-Imagine that the speaker points towards a target referent $t_v$ from a visual category $t_v | V \sim N(\mu_{V}, \sigma^2_{V})$.
-If the observer is in a noisy environment (e.g., foggy weather), they might see this target referent in a blurry way.
-We assume the blur to be normally distributed: $a | t_v \sim N(t_v, \sigma^2_{N})$, and we integrate over $t_v$.
-We obtain an expression formally similar to the one obtained in Experiment 2:
-
-$$ v | V \sim N(\mu_{V}, \sigma^2_{V}+\sigma^2_{N})$$
-
-Below we explored the effect of this added visual blur on performance in our task.
+In this Experiment, we tested the case where the background noise was added to the visual modality.
+Similar to Experiment 2, we were interested to know if participants would treat this new source of uncertainty as predicted by the optimal model, that is, according to the following weighting scheme  $$\beta_a \propto \frac{1}{\sigma^2_{A}}$$ $$\beta_v \propto \frac{1}{\sigma^2_{V}+\sigma^2_{N_V}}$$
+The alternative hypothesies is that, just like noise in the auditory modality lead to a preference for the visual input, noise in the visual modality leads to a  preference for the auditory input.
 
@@
 ### Participants
+
 A planned sample of `r N_all_3` participants was recruited online through Amazon Mechanical Turk.
-We used the same exclusion criteria as in the previous experiment.
+We used the same exclusion criteria as in both previous experiments.
+`r N_all_3 - N_noProb_3` participants were excluded because they reported having a technical problem, and `r N_noProb_3 - N_good_3` participants were excluded because they had less than 50\% accurate responses on the unambiguous training trials.
 The final sample consisted of (N = `r N_good_3`) participants.
@@
 We used the same auditory stimuli as in Experiment 1.
-We also used the same visual stimuli, but we blurred the tokens using the editor XXX (signal to noise ration XXX).
+We also used the same visual stimuli, but we blurred the tokens using the free image editor GIMP (2.8.20).
+We used a Gaussian blur with a radius\footnote{A features of the filter that afftects the intensity of the blur} of 10 pixels.
 The experimental procedure was exactly the same as in the previous Experiments.
@@
 
-results1 <- boot(data=exp3_good, statistic = lmfit, R = 10000)
+#results3 <- boot(data=exp3_good, statistic = lmfit, R = 10000)
+
+#dataSave3 <- data.frame(matrix(ncol = 5, nrow = 0))
+#data_names <- c("variable", "estimate", "lower","upper", "Experiment")
+#colnames(dataSave3) <- data_names
 
 #Auditory variance:
-audVar=boot.ci(results1, index = 1, type = c("bca"), conf = 0.95)
-audVar_val=audVar$t0 
-audVar_ci1=audVar$bca[4]
-audVar_ci2=audVar$bca[5]
+#audVar=boot.ci(results3, index = 1, type = c("bca"), conf = 0.95)
+
+#v1 <- data.frame('audVar', as.numeric(audVar$t0), as.numeric(audVar$bca[4]), as.numeric(audVar$bca[5]), 'Exp3')
+#  colnames(v1) <- data_names
 
 #Auditory bias:
-audBias=boot.ci(results1, index = 2, type = c("bca"), conf = 0.95)
-audBias_val=audBias$t0 
-audBias_ci1=audBias$bca[4]
-audBias_ci2=audBias$bca[5]
+#audBias=boot.ci(results3, index = 2, type = c("bca"), conf = 0.95)
+
+#v2 <- data.frame('audBias', as.numeric(audBias$t0), as.numeric(audBias$bca[4]), as.numeric(audBias$bca[5]), 'Exp3')
+#  colnames(v2) <- data_names
 
 #Visual variance:
-visVar=boot.ci(results1, index = 3, type = c("bca"), conf = 0.95)
-visVar_val=visVar$t0 
-visVar_ci1=visVar$bca[4]
-visVar_ci2=visVar$bca[5]
+#visVar=boot.ci(results3, index = 3, type = c("bca"), conf = 0.95)
+
+#v3 <- data.frame('visVar', as.numeric(visVar$t0), as.numeric(visVar$bca[4]), as.numeric(visVar$bca[5]), 'Exp3')
+#  colnames(v3) <- data_names
 
 #Visual bias:
-visBias=boot.ci(results1, index = 4, type = c("bca"), conf = 0.95)
-visBias_val=visBias$t0 
-visBias_ci1=visBias$bca[4]
-visBias_ci2=visBias$bca[5]
+#visBias=boot.ci(results3, index = 4, type = c("bca"), conf = 0.95)
+
+#v4 <- data.frame('visBias', as.numeric(visBias$t0), as.numeric(visBias$bca[4]), as.numeric(visBias$bca[5]), 'Exp3')
+#  colnames(v4) <- data_names
 
 #Bimodal Auditory variance:
-audVarBi=boot.ci(results1, index = 5, type = c("bca"), conf = 0.95)
-audVarBi_val=audVarBi$t0 
-audVarBi_ci1=audVarBi$bca[4]
-audVarBi_ci2=audVarBi$bca[5]
+#audVarBi=boot.ci(results3, index = 5, type = c("bca"), conf = 0.95)
+
+#v5 <- data.frame('audVarBi', as.numeric(audVarBi$t0), as.numeric(audVarBi$bca[4]), as.numeric(audVarBi$bca[5]), 'Exp3')
+#  colnames(v5) <- data_names
 
 #Bimodal Visual variance:
-visVarBi=boot.ci(results1, index = 6, type = c("bca"), conf = 0.95)
-visVarBi_val=visVarBi$t0 
-visVarBi_ci1=visVarBi$bca[4]
-visVarBi_ci2=visVarBi$bca[5]
+#visVarBi=boot.ci(results3, index = 6, type = c("bca"), conf = 0.95)
+
+#v6 <- data.frame('visVarBi', as.numeric(visVarBi$t0), as.numeric(visVarBi$bca[4]), as.numeric(visVarBi$bca[5]), 'Exp3')
+#  colnames(v6) <- data_names
 
 #Bimodal bias:
-BiasBi=boot.ci(results1, index = 7, type = c("bca"), conf = 0.95)
-BiasBi_val=BiasBi$t0 
-BiasBi_ci1=BiasBi$bca[4]
-BiasBi_ci2=BiasBi$bca[5]
+#BiasBi=boot.ci(results3, index = 7, type = c("bca"), conf = 0.95)
+
+#v7 <- data.frame('BiasBi', as.numeric(BiasBi$t0), as.numeric(BiasBi$bca[4]), as.numeric(BiasBi$bca[5]), 'Exp3')
+#  colnames(v7) <- data_names
 
 #Ideal modality wieghing
-prefIdeal=boot.ci(results1, index = 8, type = c("bca"), conf = 0.95)
-prefIdeal_val=prefIdeal$t0 
-prefIdeal_ci1=prefIdeal$bca[4]
-prefIdeal_ci2=prefIdeal$bca[5]
+#prefIdeal=boot.ci(results3, index = 8, type = c("bca"), conf = 0.95)
+
+#v8 <- data.frame('prefIdeal', as.numeric(prefIdeal$t0), as.numeric(prefIdeal$bca[4]), as.numeric(prefIdeal$bca[5]), 'Exp3')
+#  colnames(v8) <- data_names
 
 #fit modality wieghing
-prefFit=boot.ci(results1, index = 9, type = c("bca"), conf = 0.95)
-prefFit_val=prefFit$t0 
-prefFit_ci1=prefFit$bca[4]
-prefFit_ci2=prefFit$bca[5]
+#prefFit=boot.ci(results3, index = 9, type = c("bca"), conf = 0.95)
+
+#v9 <- data.frame('prefFit', as.numeric(prefFit$t0), as.numeric(prefFit$bca[4]), as.numeric(prefFit$bca[5]), 'Exp3')
+#  colnames(v9) <- data_names
 
 #Modality bias 
-bias=boot.ci(results1, index = 10, type = c("bca"), conf = 0.95)
-bias_val_3=bias$t0 
-bias_ci1_3=bias$bca[4]
-bias_ci2_3=bias$bca[5]
+#bias=boot.ci(results3, index = 10, type = c("bca"), conf = 0.95)
+
+#v10 <- data.frame('bias', as.numeric(bias$t0), as.numeric(bias$bca[4]), as.numeric(bias$bca[5]), 'Exp3')
+#  colnames(v10) <- data_names
+
+#dataSave3 <- bind_rows(dataSave3, v1, v2, v3, v4, v5, v6, v7, v8, v9, v10)
+#feather::write_feather(dataSave3, "dataExp3.feather")
+
+dataSave3 <- feather::read_feather("dataExp3.feather")
+
+#Extract values 
+audVar_val=dataSave3$estimate[which(dataSave3$variable == "audVar")]
+audVar_ci1=dataSave3$lower[which(dataSave3$variable == "audVar")]
+audVar_ci2=dataSave3$upper[which(dataSave3$variable == "audVar")]
+
+audBias_val=-dataSave3$estimate[which(dataSave3$variable == "audBias")]
+audBias_ci1=-dataSave3$upper[which(dataSave3$variable == "audBias")]
+audBias_ci2=-dataSave3$lower[which(dataSave3$variable == "audBias")]
+
+visVar_val=dataSave3$estimate[which(dataSave3$variable == "visVar")]
+visVar_ci1=dataSave3$lower[which(dataSave3$variable == "visVar")]
+visVar_ci2=dataSave3$upper[which(dataSave3$variable == "visVar")]
+
+visBias_val=-dataSave3$estimate[which(dataSave3$variable == "visBias")]
+visBias_ci1=-dataSave3$upper[which(dataSave3$variable == "visBias")]
+visBias_ci2=-dataSave3$lower[which(dataSave3$variable == "visBias")]
+
+audVarBi_val=dataSave3$estimate[which(dataSave3$variable == "audVarBi")]
+audVarBi_ci1=dataSave3$lower[which(dataSave3$variable == "audVarBi")]
+audVarBi_ci2=dataSave3$upper[which(dataSave3$variable == "audVarBi")]
+
+visVarBi_val=dataSave3$estimate[which(dataSave3$variable == "visVarBi")]
+visVarBi_ci1=dataSave3$lower[which(dataSave3$variable == "visVarBi")]
+visVarBi_ci2=dataSave3$upper[which(dataSave3$variable == "visVarBi")]
+
+BiasBi_val=-dataSave3$estimate[which(dataSave3$variable == "BiasBi")]
+BiasBi_ci1=-dataSave3$upper[which(dataSave3$variable == "BiasBi")]
+BiasBi_ci2=-dataSave3$lower[which(dataSave3$variable == "BiasBi")]
+
+prefIdeal_val_3=dataSave3$estimate[which(dataSave3$variable == "prefIdeal")]
+prefIdeal_ci1_3=dataSave3$lower[which(dataSave3$variable == "prefIdeal")]
+prefIdeal_ci2_3=dataSave3$upper[which(dataSave3$variable == "prefIdeal")]
+
+bias_val_3=dataSave3$estimate[which(dataSave3$variable == "bias")]
+bias_ci1_3=dataSave3$lower[which(dataSave3$variable == "bias")]
+bias_ci2_3=dataSave3$upper[which(dataSave3$variable == "bias")]
 
@@
 We fit a model for each modality, collapsed across participants.
-For the auditory modality, our parameter estimates were $\epsilon_A=$ `r audBias_val` CI [`r audBias_ci2`, `r audBias_ci1`] and $\sigma^2_A=$ `r audVar_val` CI [`r audVar_ci1`, `r audVar_ci2`].
-For the visual modality, we found $\epsilon_V=$ `r visBias_val` CI [`r visBias_ci2`, `r visBias_ci1`] and $\sigma^2_V+\sigma^2_N=$ `r visVar_val` CI [`r visVar_ci1`, `r visVar_ci2`].
+For the auditory modality, our parameter estimates were $\epsilon_A=$ `r audBias_val` [`r audBias_ci2`, `r audBias_ci1`] and $\sigma^2_A=$ `r audVar_val` [`r audVar_ci1`, `r audVar_ci2`].
+For the visual modality, we found $\epsilon_V=$ `r visBias_val` [`r visBias_ci2`, `r visBias_ci1`] and $\sigma^2_V+\sigma^2_N=$ `r visVar_val` [`r visVar_ci1`, `r visVar_ci2`].
 Figure\ \@ref(fig:unimodal) shows responses in the unimodal conditions as well as the corresponding fits.
@@
 We fit the descriptive model to human responses in the bimodal condition, collapsed across participants.
-We estimated $\epsilon=$ `r BiasBi_val` CI [`r BiasBi_ci2`, `r BiasBi_ci1`], $\sigma^2_{Ab}=$ `r audVarBi_val` CI [`r audVarBi_ci1`, `r audVarBi_ci2`], and $\sigma^2_{Vb}+\sigma^2_{Nb}=$ `r visVarBi_val` CI [`r visVarBi_ci1`, `r visVarBi_ci2`].
+We estimated $\epsilon=$ `r BiasBi_val` [`r BiasBi_ci2`, `r BiasBi_ci1`], $\sigma^2_{Ab}=$ `r audVarBi_val` [`r audVarBi_ci1`, `r audVarBi_ci2`], and $\sigma^2_{Vb}+\sigma^2_{Nb}=$ `r visVarBi_val` [`r visVarBi_ci1`, `r visVarBi_ci2`].
 The fit explained `r 100*R2_descriptive_3`% of total variance.
+Cross-validation using half the responses to predict tho other half yields $R^2=$`r CV_exp3_mean` [`r CV_exp3_lower`, `r CV_exp3_upper`].
 
@@
 Participants' decision threshold suggested a preference for the auditory modality (the non-noisy modality).
-Indeed non-parametric resampling of the data showed an increase in the value of the slope in the descriptive model compared to the optimal model Figure\ \@ref(fig:bias).
+Indeed non-parametric resampling of the data showed an increase in the value of the slope in the descriptive model compared to the optimal model (Figure\ \@ref(fig:bias)).
 
@@
 Thus, though participants were still sensitive to variation in the noisy visual data in the unimodal condition, they tended to ignore this information in the bimodal condition, and relied almost exclusively on the non-noisy auditory modality.
-This behaviour is not so much a qualitative difference from Experiment 2 (where participants relied on both the noisy and the non-noisy modality in the bimodal condition), as much as it is the result of a floor effect.
+The reason why we saw this (floor) effect when we added noise to the visual modality (Experiment 3), and not when added noise to the auditory modality (Experiment 2), is the fact that our visual stimuli were originally perceived less categorically and with less certainty than the auditory stimuli.
+This made it more likely for the visual categorization function to become flat and uninformative after a few drops in precision due to noise on the one had, and to the additional randomness induced by the bimodal presentation on the other hand.
+
+<!--This behaviour is not so much a qualitative difference from Experiment 2 (where participants relied on both the noisy and the non-noisy modality in the bimodal condition), as much as it is the result of a floor effect.
 Indeed, noise made the visual modality way less steep and barely perceptible in the unimodal condition Figure\ \@ref(fig:unimodal).
 So when we had an additional general drop in precision in the bimodal condition (similar to what we found in Experiment 1 and 2),  participants were no longer able to extract any useful information.
-The reason why we saw this floor effect when we added noise to the visual modality (Experiment 3), and not when added noise to the auditory modality (Experiment 2), is the fact that our visual stimuli was originally perceived less categorically and with less certainty than the auditory data was.
-This made it more likely for the visual categorization function to become flat and uninformative after a few drops in precision due to noise on the one had, and to the randomness induced by the arbitrary association on the other hand.
-
+-->
 The general finding corresponds to the third case of sub-optimality described above.
@@
 
-```{r }
+```{r echo=FALSE}
+#number of participants relying exlusiviely on one modality
+#cut off is a factor of 10
+
+bimodal_bysub_good_3 <- bimodal_bysub_3 %>%
+  filter(bimod > 0.1) %>%
+  filter(bimod < 10)
+
+#Visual modality 
+only_visual_N_3 <- bimodal_bysub_3 %>%
+  filter(abs(bimod) < 0.1) %>%
+  nrow()
+
+#Sound modality 
+only_sound_N_3 <- bimodal_bysub_3 %>%
+  filter(abs(bimod) > 10) %>%
+  nrow()
+
+#the rest
+both_N_3 <- bimodal_bysub_3 %>%
+  filter(abs(bimod) > 0.1) %>%
+  filter(abs(bimod) < 10) %>%
+  nrow()
+
+neg_N_3 <- bimodal_bysub_3 %>%
+  filter(bimod <  -0.1) %>%
+  filter(bimod > -10) %>%
+  nrow()
+
+exlusive_prop_3 = only_visual_N_3/only_sound_N_3
+
+```
+The percentage of participants who relied exclusively on either the visual modality or the auditory modality was `r 100*(only_visual_N_3+only_sound_N_3)/(only_visual_N_3+only_sound_N_3+both_N_3)`%, which is closer to the percentage of Experiment 2, except that most of these participants relied exclusively on the auditory modality  instead of the visual modality: The propotion of participants relying exclusively on the visual modality relative to the sound modality was `r exlusive_prop_3` (compared to `r exlusive_prop_2` in Experiment 2).
+
+```{r echo=FALSE, warning = FALSE}
+
+#Modality preference in an audio-vidual space
+
+prefIdeal_val_1=1.637216
+prefFit_val_1=1.454367
+
+prefIdeal_val_2=0.8367816
+prefFit_val_2=0.529517
+
+prefIdeal_val_3=6.68829 
+prefFit_val_3=13.15958
+
+# Decision threshold
+classif = function (x, A) {
+    2*A+2-A*x
+}
+
+pref_data <- data.frame(matrix(ncol = 7, nrow = 0))
+names <- c("Auditory", "Visual", "Optimal", "Auditory bias", "Visual bias", "Fit", "Experiment")
+colnames(pref_data) <- names
+
+x=seq(-1,5,0.02)
+
+pref_exp1 <- data.frame(x, x, 
+                        classif(x, prefIdeal_val_1),
+                        classif(x, 2*prefIdeal_val_1),
+                        classif(x, 0.5*prefIdeal_val_1),
+                        classif(x, prefFit_val_1),
+                        'Exp1')
+colnames(pref_exp1) <- names
+
+pref_exp2 <- data.frame(x, x, 
+                        classif(x, prefIdeal_val_2),
+                        classif(x, 2*prefIdeal_val_2),
+                        classif(x, 0.5*prefIdeal_val_2),
+                        classif(x, prefFit_val_2),
+                        'Exp2')
+colnames(pref_exp2) <- names
+
+pref_exp3 <- data.frame(x, x, 
+                        classif(x, prefIdeal_val_3),
+                        classif(x, 2*prefIdeal_val_3),
+                        classif(x, 0.5*prefIdeal_val_3),
+                        classif(x, prefFit_val_3),
+                        'Exp3')
+colnames(pref_exp3) <- names
+
+pref_data <- bind_rows(pref_data, pref_exp1, pref_exp2, pref_exp3) %>%
+  gather(model, value, Optimal:Fit)
+
+pref_data$model <- factor(pref_data$model, levels = c("Optimal", "Fit","Auditory bias", "Visual bias"))
+
+pref_thres <- ggplot(pref_data, aes(x=Auditory, y=value, col = factor(model))) +
+  geom_line(aes(linetype = factor(model) )) +
+  facet_grid(.~Experiment)+
+  scale_colour_manual(values = c("Optimal" = "red", "Auditory bias" = "blue", "Visual bias" = "green", "Fit" = "black"))+
+  scale_linetype_manual(values = c("Optimal" = "solid", "Auditory bias" = "dashed", "Visual bias" = "dashed", "Fit" = "solid"))+
+  xlab("Auditory") +ylab("Visual") +
+  scale_x_continuous(limits = c(1.7, 2.3))+
+  scale_y_continuous(limits = c(1.7, 2.3))+theme(aspect.ratio = 1)+
+  theme(legend.title = element_blank())
+
+```
+
+```{r echo=FALSE, warning = FALSE}
 #Modality bias
@@
 preference = c(bias_val_1, bias_val_2, bias_val_3 )
-experiment =c("Exp 1 \n", "Exp 2 \n (noisy audio)", "Exp 3 \n (noisy visual)")
+experiment =c("Exp 1 \n", "Exp 2", "Exp 3")
 ci_low=c(bias_ci1_1, bias_ci1_2, bias_ci1_3)
@@
                   position = position_dodge(width = 0.1))+
-  geom_hline(yintercept = 1, linetype=2, color="red", size=1)+
-
-  geom_hline(yintercept = 0.5, linetype=2, color="blue")+
+  geom_hline(yintercept = 1, linetype='solid', color="red", size=1)+
+
+  geom_hline(yintercept = 0.5, linetype=2, color="green")+
 
@@
 
-```{r bias, fig.cap = "Relative weighing of evidence from the auditory stimulus vs.
+```{r bias, echo=FALSE, warning = FALSE, fig.cap = "Relative weighing of evidence from the auditory stimulus vs.
 evidence from the visual stimulus across the three Experiments (log-scaled).
-The red dashed  line  shows the  prediction  of the model  if the weighting is optimal,  and the  blue dashed lines  show   predictions if participants deviated from  optimality by relying  twice  as much  on the meaning  category  (strong meaning bias) or twice   as  much  on  the sound category (strong  sound bias).", fig.align = "center", out.width = "400px"}
-bias
+The red dashed  line  shows the  prediction  of the model  if the weighting is optimal,  and the  blue dashed lines  show   predictions if participants deviated from  optimality by relying  twice  as much  on the visual  input  (strong visual bias), or by relying twice as much on  the auditory input (strong  sound bias).", fig.align = "center", out.width = "400px"}
+
+legend <- get_legend(pref_thres)
+plot_noLegend <- plot_grid(pref_thres + theme(legend.position="none"), NULL, bias, labels = c("A", "", "B"), ncol = 1, align = "v", rel_heights = c(1.1, 0.1, 1.3))
+plot_grid(plot_noLegend, legend, rel_widths = c(2, .5))
 
@@
 # General Discussion
-Understanding language, such as word-referent associations, often requires both the ability to combine arbitrary multimodal input, and the ability to deal with uncertainty.
-In this work, we explored a case where both abilities were at play.
-We studied the case of identifying a word when both its form (auditory) and its referent (visual) were ambiguous with respect to their category membership (Experiment 1), when the form was perturbed with additional background noise (Experiment 2), and when the referent was perturbed with additional visual noise (Experiment 3).
-We introduced a model that instantiated an ideal/optimal observer, predicting how information from each modality could be combined in an optimal way.
-In all Experiments, participants showed many patterns of optimal behaviour.
-Quantitatively speaking, the optimal model accounted, respectively, for `r 100*R2_optimal_1`%, `r 100*R2_optimal_2`%, and `r 100*R2_optimal_3`% of the variance in human data.
+
+When identifying a spoken word under uncertainty, one often needs to combine and make the most of the available multimodal cues.
+While most previous studies focued on the case of audio-viusual speech where people combine cues from speech and facial features, this work explored the case of identifying an ambiguous word when the available multimodal cues are speech and the visual referent.
+More specifically, we conducted an ideal observer analysis of the task whereby a model provided predictions about how information from each modality should be combined in an optimal fashion.
+The predictions of the model were tested in a series of three experiments where instances of both the form and the referent were ambiguous with respect to their category membership only (Experiment 1), when instances of the form were perturbed with additional background noise (Experiment 2), and when instances of the referent were perturbed with additional visual noise (Experiment 3).
+
+In all Experiments, we found many patterns of optimal behaviour.
+Quantitatively speaking, the optimal model accounted, respectively, for `r 100*R2_optimal_1`%, `r 100*R2_optimal_2`%, and `r 100*R2_optimal_3`% of the variance in the mean responses.
 When compared to the predictions of the visual or the auditory models, participants generally relied on both modalities to make their decisions in the bimodal condition.
-Indeed, in Experiment 1 and 2, the optimal model accounted for more variance in human data than the auditory or the visual models did.
-In Experiment 3, participants appeared to rely on one modality, but as we explained in the intermediate discussion, this is likely a floor effect, due to the fact that noise made the visual input barely perceivable.
-Moreover, in Experiment 1, which did not involve background noise, participants not only relied on both modalities, but weighted these modalities according to the prediction of the optimal model, that is, according to their relative reliability.
-
-Besides these patterns of optimal behavior, we documented two interesting cases of sub-optimality.
+Indeed, in Experiment 1 and 2, the optimal model accounted for more variance in mean responses than the auditory or the visual models did.
+In Experiment 3, participants appeared to rely on one modality, but this was likely a floor effect, due to the fact that noise made the visual input barely perceivable.
+In Experiment 1, which did not involve background noise, participants not only relied on both modalities, but generally weighted these modalities according to the prediction of the optimal model, that is, according to their relative reliability.
+At the indiviual level, however, we found evidence of a between-subject variation: Some particiapnts relied slighly more on the visual modality, whereas others relied slighly more on the auditory modality.
+
+We documented two major cases of sub-optimality.
 First, in all Experiments, the variance associated with each modality increased in the bimodal condition compared to the unimodal conditions.
 This means that participants responded slightly more randomly in the bimodal condition than they did in the unimodal conditions.
-This finding contrasts with research on optimal multisensory integration where associations tend to lead to a higher precision [@ernst02].
-However, there is a crucial difference between these two situations.
-Research on optimal multisensory integration deals with redundant multimodal cues, and these cues are integrated into a unified percept (such as the size or the location of an object).
-In contrast, the word-referent association is usually arbitrary and, in particular, the cues are not supposed to correlate perceptually.
-Therefore the brain cannot form a unified percept, rather, it must encode information separately from both modalities and retain this encoding through the decision making process.
+This finding contrasts with research on optimal multisensory integration where associations tend to lead to a higher precision [e.g., @ernst02].
+Nevertheless, there is a crucial difference between these two situations.
+Research on optimal multisensory integration (of which audio-visual speech is arguably an instance) deals with redundant multimodal cues, and these cues are integrated into a unified percept.
+In contrast, the word-referent association is usually arbitrary and, in particular, the cues are not expected to be correlated perceptually.
+Therefore the mind cannot form a unified percept, rather, it must encode information separately from both modalities and retain this encoding through the decision making process.
 Retaining two separate cues at the same time instead of forming one unified percept (as in multisensory integration of redundant cues), or instead of retaining only one cue (as in the unimodal case), is likely to place extra-demand on cognitive resources, which, in turn, can cause general performance to drop.
-Indeed, there is evidence that cognitive load has a detrimetnal effect on word recognition, which can be explained by a reduction in perceptual acuity [@mattys11].
-
-The second case of sub-optimality is related to how participants weighed the cues from the visual and the auditory in a noisy context.
-In contrast to Experiment 1 where the combination was indistinguishable from the optimal prediction, resutls of Experiment 2 and 3 which involved noise in one modality, showed that participants had a preference for the other (non-noisy) modality.
-Crucially, this preference was beyond what is explained by the relative reliability (hence the sub-optimality).
+Indeed, there is evidence that cognitive load has a detrimental effect on word recognition, which can be due to a reduction in perceptual acuity [@mattys11].
+Similar to our finding, previous experimental studies reported that in both children and adults, identifing new ambiguous form-referent mappings is usually associated with what appears to be a decrease in speech perception acuity [@stager1997; @pajak2016].
+@hofer2017 provided a probabilistic model of this phenomenon, which they similarly characterized as an increase in the noise variance of the auditory modality.
+Our finding replicates this previously documented fact, and additionaly suggests that the reduction in percetual acuity occurs simultaneousely in both the auditory and the visual modalities.
+
+The second case of sub-optimality is related to how participants weighed the cues from the visual and the auditory modalities in a noisy context.
+In contrast to Experiment 1 where the combination was indistinguishable from the optimal prediction, results of Experiment 2 and 3 which both involved background noise in one modality, showed that participants had a systematic preference for the other (non-noisy) modality.
 From previous empirical studies, we know that when the speech signal is degraded, people tend to compensate by relying more on other sources of information such as the accompanying visual cues (i.e., lip movements) or the semantic/syntactic context [see @mattys12 for a review].
 However, and generally speaking, these studies do not differentiate between an optimal compensatory strategy (i.e., relying more on the alternative source while using all information still available in the distorted signal), and a sub-optimal strategy (i.e., relying more on the alternative source while ignoring at least some of the information still available in the distorted signal).
-The sub-optimal behavior is possibly related to the fact that language understanding under degraded listening conditions is cognitively more taxing than language understanding under normal conditions [@Ronnberg10].
+The formal appraoch followed in this paper allowed us to tease apart these two possibilities, and the analysis supports the sub-optimal compensatory strategy: The preference for the non-noisy modality is above and beyond what can be explained by the relative reliability alone, meaning that the participant tend ignore at least part of the information still avialable in the noisy modality.
+
+This second case of sub-optimal behavior is possibly related to the fact that language understanding under degraded listening conditions is cognitively more taxing than language understanding under normal conditions [@Ronnberg10].
 This fact can lead to a preference/bias towards alternative sources of information when these sources are available.
-
-## Implication for word learning
-
-In this study, we explored the mechanism of word identification, but in a simple case when the underlying visual and auditory categories were familiar.
+One could explain this phenomenon in terms of the metacognitive experience about the fluency with which information is processed.
+The perceived perceptual fluency (e.g., the ease with which a stimulus’ physical identity can be identified) can affect a wide variety of human judgements [see @schwarz2004 for a review].
+In particular, variables that improve fluency tends to increase liking/preference [@reber98].
+In our case, the subjective experience of lower fluency in the noisy modality might cause people to underestimate information that can be extracted from this modality, especially when presented simultaneously with a higher fluency alternative.
+
+In this study, we tested the extent to which people would be optimal in combining uncertain auditory and visual cues to recognize words.
+This required that we use a case of double ambiguity, that is, a case where both the word forms ("ada"-"aba") and the referents (cat-dog) were similar and, thus, confusable.
+One could wonder about the extent to which such case occurs in real languages?
+Cross-linguistic corpus analyses suggest that the lexical encoding tends towards double ambiguity in many languages [@dautriche17; @Monaghan2014; @Tamariz2008].
+For instance, @dautriche17 analysed 100 languages and found that word that are similar phonologically  tend to be similar semantically as well, beyond what could be explained by chance.
+Crucially, they found this trend in a set of monomorphemic lemmas in four languages, suggesting that the effect is not driven by morphological regularities.
+These studies suggest that the case of double uncertainty, though perhaps not pervasive, could be a real issue in language as it increase the probability of confusability.
+Moreover, it is important to keep in mind that ambiguity in both the form and the referent can be induced by an external noisy context even when these forms and referents are not confusable in normal situations.
+
+Though we only tested adults in this paper, the problem of word recognition under uncertainty, as well as the need to make the most of ambiguous cues, is a particularly pressing issue for children.
+In fact, whereas adults are mostly faced with uncertainty in the *input*, children have to deal with the additional uncertainty that results from their early unrefined *representations* of both phonological and semantic categories.
+For example, upon hearing a noisy instance of "bee", adults may have to decide whether the speaker intended to say "pea" or "bee", but children can additionally be uncertain whether "bee" is a different word from "pee" (as opposed to, say, a valid within category variation), especially if these similar sounding words are newly learned [@stager1997; @Merriman91; @Creel2012; @Swingley2016; @white2008b].
+Though new word form representation can be shown to be differetnited under some circumstances [e.g., @yoshida2009], this differentition is still not mature enough and is probably noisier than the adult-like representation and/or encoded with lower confidence [see @Swingley2007].
+
+At the semantic level, early representations have, similarly, an intrinsically fragile and uncertain status.
+For example, upon seeing a bee in a foggy weather, adults may be uncertain if they saw a bee or a fly.
+But on top of this perceptual uncerainty, children may not be certain if the semantic categoy being named is that of bees and only bees, or if it includes other small flying insects like flies and beetles.
+In fact,  though children can be fast at learning a first approximation of a given word's referent [@carey1978b], the refinement of this early approximantion into a mature semantic category is a slow and gradual process [see also @bion2013;; @carey2010; @fernald2006; @mcmurray2012].
+Among other things, children have to enrich this early representation with new features, and revise its extension in the light of new referential exposures.
+
+A multi-modal cue combination strategy might help children not only recognize an individual word instance, but also refine the underlying phonological and semantic representations in the process.
+Previous research in early word learning has---whether implicitly or explicitly---largely treated the process of learning form and of learning meaning as independent.
+<!--Babies are understood to first master the form, learning to ignore phonologically irrelevant variation (such as differences in talker, speech rate, emotion, and linguistic context) (see Kuhl, 2004 for a review).
+Only when the form representation is refined and ready, can they start mapping the form to meaning (Bloom, 2000)-->However, the developmental data reviewed above shows that children do not wait to have completed the acquisition of form to start learning meanings, and that both form and meaning representations develop, rather, in a parallel fashion.
+A few studies pointed to the possibility of an interaction between sound and meaning in early acquisition.
+For instance, @waxman1995 showed that labeling various objects with the same name helps infants form the broad semantic category [but see @sloutsky2003].
+Vice versa, @yeung09 showed that pairing similar sounds with different objects help infants pay attention to subtle phonological contrasts.
+The present study proposes a first step towards a formal framework where accounts of sound-meaning synergy in development can be unified and further explored.
+For example, one could imagine that, initially, visual and auditory categories have relatively large noise variances, and that development consists in reducing the values of the variances through a mutually constraining process as further multimodal data accumulates.
+
+In conclusion, this work studied the mechanism of word identification under uncertainty in both the word form and the word meaning.
+To our knowledge, this is the first study that performs an ideal observer analysis of this task.
+We found people to be optimal in their cue combination: They weighted each modality according to its relative reliability.
+However, they also showed patterns of sub-optimality especially when the stimuli were perturbed with additional background noise.
+Future work will extend the present formal framework in order to account for how children use multimodal cues to refine their early phonological and semantic representations.
+
+# Appendix: derivation of the posterior (equation 1)
+
+For an ideal observer, the probability of choosing category 2 when presented with an audio-visual instance $w = (a, v)$ is the posterior probability of this category:
+
+$$p(W_2 | w)=\frac{p(w|W_2)p(W_2)}{p(w|W_2)p(W_2)+p(w|W_1)p(W_1)}$$
+
+Which reduces to:
+
+$$p(W_2 | w)=\frac{1}{1+\frac{p(w|W_1)}{p(w|W_2)} \frac{p(W_1)}{p(W_2)}}$$
+In order to further simplify the quantity $\frac{p(w|W_1)}{p(w|W_2)}$, we use our assumption that the cues are uncorrelated, 
+$$p(w | W) = p(a,v| W) = p(a| A)p(v| V)$$
+Using the $\log$ transformation, we get:
+
+$$ \ln(\frac{p(w |W_1)}{p(w|W_2)})=\ln(\frac{p(a|W_1)}{p(a|W_2)})+\ln(\frac{p(v|W_1)}{p(v|W_2)}) $$ 
+Under the assumption that the categories are normally distributed and that, within each modality, the categories have equal variances, we get (after simplification):
+
+$$\ln(\frac{p(a|W_1)}{p(a|W_2)})=\frac{\mu_{A1}-\mu_{A2}}{\sigma^2_{A}}\times a+ \frac{\mu^2_{A2}-\mu^2_{A1}}{2\sigma^2_{A}}$$
+
+and similarly:
+
+$$\ln(\frac{p(v|W_1)}{p(v|W_2)})=\frac{\mu_{V1}-\mu_{V2}}{\sigma^2_{V}}\times v+ \frac{\mu^2_{V2}-\mu^2_{V1}}{2\sigma^2_{V}}$$
+
+When putting all these terms tegether, we the get this final expression for the posterori:
+$$p(W_2 | w)=\frac{1}{1+(1+\epsilon)\exp(\beta_0+\beta_aa+\beta_vv)}$$
+
+where
+
+$$1+\epsilon=\frac{p(W_1)}{p(W_2)}$$
+$$\beta_0=\frac{\mu^2_{A2}-\mu^2_{A1}}{2\sigma^2_{A}}+\frac{\mu^2_{V2}-\mu^2_{V1}}{2\sigma^2_{V}}$$
+
+$$\beta_a=\frac{\mu_{A1}-\mu_{A2}}{\sigma^2_{A}}$$
+$$\beta_v=\frac{\mu_{V1}-\mu_{V2}}{\sigma^2_{V}}$$ 
+<!--
+as further data about sound-meanining associations accumulate, making the categories more refined and precise.
+
+Moreover, modeling studies the possibility of an interaction or synergy between early represention interaction between sound and menaning
+
+A few studies explicitely pointed to the possibility of an interaction between sound and meaning in early acqusition. For instance, Waxman and Markow (1995) showed that a
+
+It follows that Cue combination is not only necessary to recognize a word (as with ault), but also to lrefine the underlying representations, leading to a leaning synergy (Fourtass and Dupoux, 2014).
+Waxman and Yeung, but they assume an ambiguous state.
+Here we suggest that even if non of the representation
+
+If we take the perspective of infromation theory, communication is basically a process of information transfer in a noisy channel (Shannon, 1948), and information encoding should be such that the listener is able to recover what is being said.
+Therefore, the confusability of distinct words should be minimized.
+In particular, similar meanings should be encoded with phonologically distinct words.
+As it turns out, cross-lingusitc corpus analyses reveal an opposite trend, suggesting that the constraints of communication might not be the only force shaping the struture of the lexicon (Dautriche et al.
+2016; Monaghan et al., 2014; Shillcock et al., 2001; Tamariz, 2008).
+For instace, Dautriche et al.
+2015 analysed 100 languages and found that word that are similar phonologically  tend to be more similar semantically as well, above what could be explained by chance.
+Crucially, they found this trend in a set of monomorphemic lemmas in four languags, suggesting that the effect is not driven by morphological regularities.
+These studies suggest that the case of souble uncertainty, though perhabps not pervasive, could be a real issue beyond our controlled experiment, and that an optimal cue combination strategy might be crucial for word recognition in real life situations.
+
+Here talk about development
+
+They found that minimal pairs are more likely to be found among semantically related words than semantically different words.
+
+Crucially,
+
+From an information theory perspective, communication can be modeled as the transfer of information over a noisy channel (Shannon, 1948).
+Successful commu- nication requires listeners to be able to recover what is being said; therefore, the likeli- hood that two distinct words would be confusable should be minimized according to this constraint.
+There is much evidence that perceptual distinctiveness plays an important role in shaping the phonology of languages
+
+However, in order for the optimal combination strategy to be relevant to our understading of word recognion, we need   play any role beyond a mere controlled experiment, cross-lingsuitic corpus analyses indicate that this is not an infrequent phenomeon in real languages.
+For example,
+
+analyzed the relationship between semantic relatedness and the likelihood of finding a minimal pair and found that minimal pairs are more likely among semantically similar words than semantically distant words.
+
+The arbitraniess of the sign in natural language means that the word form is not necessarilly related to the features of the semantic catgory, and a corrola
+
+in rather extreme situation  tested a rather extreme case of uncertainty where both
+
+To explore how the mind However, insights in this work can shed light on   but in a simple case when the underlying visual and auditory categories were familiar.
 Indeed, on the visual side, cat and dog tokens belong obviously to existing visual categories.
@@
 Our proposal explains these patterns of failure and success in terms of developmental changes in the variances associated with the visual and phonological categories, combined with the ability to integrate sound and visual cues according to their reliability.
-Suppose that both members of a given sound contrast ("bin"/"din") initially fall within the uncertainty range of a single sound category.
+Suppose that both members of a given sound contrast ("bih"/"dih") initially fall within the uncertainty range of a single sound category.
 If this uncertainty diminishes with age (as the category gets more refined), then what used to be likely at a certain point in development (e.g., 14 m.o), may later become unlikely.
@@
 Thus, 14 m.o may be learning one broad word-referent association instead of two specific associations.
-So what was conidered a "failure" in learning might, in fact, be the optimal decision within the 14 m.o's own developmental context!
+According to the present account, what was considered a "failure" in learning might, in fact, be the optimal decision within the 14 m.o's own developmental context!
 
 This account makes two main predictions.
-First, if the sounds are more acoustically different (e.g., "lif"/"neem" instead of ""bih"/"dih"), babies would be more likely to posit and learn two word-referent associations, because there would be more evidence pointing in that direction from the auditory side.
+First, if the sounds are more acoustically different (e.g., "lif"/"neem" instead of "bih"/"dih"), babies would be more likely to posit and learn two word-referent associations, because there would be more evidence pointing in that direction from the auditory side.
 Second, if the objects are more semantically distant (a living object vs.
@@
 
+In a similar study that used eye tracking in addition to overt responses, Creel (2012) replicted these findings and showed that the chidlren's visual fixations revealed slower recognition for the novel word, suggesting a hightened uncertainty.
+
+(Merriman and Schuster, 1991; Creel, 2012).
+
+In fact, though children start learning the categories at an early age, typically before their first birthday [e.g., @werker1984], this learning is not perfect from the start.
+In particular, early categories can be noisier and/or encoded with lower confidence.
+It follows that recognizing familar or novel words might be a greater challenge for children than it is for adults.
+For example, in a word recognition task, though toddlers prefer the correct pronounciation of a familiar word (e.g., "baby") over a novel but phononlogically similar word ("vaby"), they do not totally reject the novel word: they still look at the familiar word's referent more than a different object (Swingley and Aslin, 2000).
+A similar pattern was found with preschoolers using a mutual exclusivity paradigm.
+Mutual exclusivity is a bias that children have to interpret novel words as referring to novel objects rather than familiar objects (Markman & Wachtel, 1988).
+For example, when presented with a ball and a novel object and asked to select, say, a "dax", participants typically point to the novel object.
+Merriman and Schuster (1991) found that this effect decreases markedly in 4-year-olds if the novel word is phonologically similar to a familiar word.
+In other words, children do not necessarily interpret a novel word "bool" to be a label for the novel object, but tend to extend it to the familiar object (a ball).
+In a similar study that used eye tracking in addition to overt responses, Creel (2012) found that preschoolers, similar to Merriman and Schuster (1991), mostly select the familiar objet.
+Moreover, the chidlren's visual fixations indicated slower recognition for the novel word, suggesting a hightened uncertainty.
+
+Children representeation of newly learned words is even more fragile than their representation of familair words (Swingley, 2007).
+For example, @stager1997 showed that 14 m.o have difficulties mapping two minimally different sounds (e.g., "bih"/"dih") to two novel objects, despite the fact that they can perceptually differentiate these sounds.
+Specifically, their task required that infants reject the switch trials, that is, when an object (e.g.
+the one associated with the word "bih") is labelled with the wrong name ("dih").
+Yoshida et al.
+(2009) tested infants with a preferential looking paradigm that reduced the memory demands in the orginal task.
+After the leanrning phase, they monitored the infants' looking patterns when presented with both objects at the same time, instead of comparing their attitude to the correct vs.
+the wrong associaton.
+In this simplified task, they found that infants succeeded in picking the correct object.
+In order to explain why infants fail in the switch task but succeed in the simpler preferential looking paradigm, Yoshida et al.
+(2009) proposed that phonological features might be encoded probabilistically.
+Early word representations for "din" and "bin"", though distinct, might be encoded with a relatively lower confidence.
+Thus, uncertainty generated by  the matching bin label, may  not  surpass  the  threshold  levelrequired  for  rejection  of   the  pairing,  resulting  in  nodifference  between  the  same  and  Switch  trials
+In the visual choice paradigm, thecritical  criterion  involves  a  direct  comparison  of,  and  aforced choice between, the two objects.
+Here, the relativelyslight difference in uncertainty is sufficient; the 60% matchwould be considered to be a better fit than the 40% match,allowing infants to demonstrate their learning ability.
+
+Actually this probabilistic accout can also explain the case of famialr words
+Talk about Swingley 2007
+For the semantic, see here:
+https://www.ncbi.nlm.nih.gov/pubmed/12003515
+
+Yoshida et al. (2009)
+
+Our proposal explains these patterns of failure and success in terms of developmental changes in the variances associated with the visual and phonological categories, combined with the ability to integrate sound and visual cues according to their reliability.
+Suppose that both members of a given sound contrast ("bih"/"dih") initially fall within the uncertainty range of a single sound category.
+If t
+
+There is evidence supporting (albeit indirectly) the possibility of effects of phonological similarityon induction.
+In particular,Merriman and Schuster (1991)demonstrated that phonological similarityof words led to attenuated ‘‘mutual exclusivity’’ effects in 2- and 4-year-olds.
+Mutual exclusivity is atendency of toddlers and young children to interpret novel words as referring to novel items ratherthan familiar items (Markman & Wachtel, 1988).
+For example, when presented with an apple and anovel object and asked to select adax, participants pointed to the novel object.Merriman and Schuster(1991)found that the effect decreases markedly or disappears if the novel word is phonologically sim-ilar to a familiar word; children would not necessarily extend a novel wordjappleto a novel object butmight instead extend it to an apple
+
+More generally, toddler's eye fixation show a graded pattern in terms of recognition, that is, they look less often at the correct object as the mispronouciation gets gradually more different from the correct the pronounciation
+more different the mispronouciation is to the correct pronooucition, the more
+
+children's looking patterns show a graded recognition uncertainty as the misponounciation's phonetic dissimilarity to the typical proniucaution increases (Morgan while...).
+
+One could even argue that the problem of word learning/recognition under multimodal uncertanty is a more pressing issue for children in the process of language acqiusition than it is for adults who already master the language.
+forms with high phonetic details
+
+Talk about Swingley work for familar words:
+
+Talk about Yoshida for novel words
+
+Talk about the fact that this uncertainty develops into early chidhood
+
+However, children do not wait to have fully mastered the speech and semantic categories before they start attempting to map form to meaning.
+
+Because  of  the  greater  noise  inherent  in  children’s  perceptual- processing  systems,  the  same  acoustic  stimulus  may  effectively be less reliable for children than adults (Lyons &  Ghetti,  2011;  Neuman  &  Hochberg,  1983)
+
+How can this formal characterization fit in a developmental scenario?
+One could imagine that, initially, visual and auditory categories have relatively large variances, and that development consists in reducing the values of the variances as evidence accumulates, making the categories more refined and precise.
+A scenario similar to this one has been previously suggested to explain the development of early sound categories.
+For example, @yoshida2009 suggested that the early categories may be noisier or that they may be encoded with relatively lower confidence.
+For the semantic categories, we can find similar (although perhaps not identical) ideas.
+For instance, Clark (1973) suggested that the initial meaning categories tend to be larger than adult categories, since fewer features are used to pick out referents (e.g., dog for all four-legged animal, ball for all round objects).
+
+They also start to map sound a
+
+However, this learning is not perfect from the start ,
+
+Indeed, since both the speech categories and the semantic categories are still not fully mastered by children, the lingusitic input can in generarl be more uncertain for the latter, which makes the problem of inference under uncertainty a more pressing issue.
+
+In early development, the combination of statistics from the auditory and the visual referent can be crucial to learn the
+
+Recognition of novel words 
+For kids the uncertainty is higher 
+word referent 
+In this study, we explored the mechanism of word identification, but in a simple case when the underlying visual and auditory categories were familiar.
+Indeed, on the visual side, cat and dog tokens belong obviously to existing visual categories.
+On the auditory side, though the words ("ada"/"aba") are novel, the phonemic categories that differentiate the words are familiar (i.e., /d/ and /b/).
+In the context of early word learning, however, children are often learning both the categories and their mapping at the same time.
+In fact, children start learning visual and sound categories at an early age [e.g., @quinn93;@werker1984], and there is evidence that word-referent-like interaction operates at the same time, even when the categories are not yet fully mastered [e.g., @waxman1995; @yeung09].
+In fact, @fourtassi2014a proposed that this interaction can create a synergy (or a bootstrapping effect) whereby progress made on one level (e.g., the meaning categories) can benefit the other level (the sound categories).
+
+<!--This work, as well as the model, is about the mechanism of word-referent recognition when the underlying visual and auditory categories are supposed to be already familiar.
+On the visual side, cat and dog tokens belong obviousely to existing categories.
+Uncertainty is about where the boundary lies, and how this perceived boundary changes when evidence from the auditory data varies from clear to ambiguous.
+On the auditory side, though the words ("ada"/"aba") are novel, the phonemic categories that differentiate the words are familiar (i.e., /d/ and /b/).
+Thus, similar to the visual categories, uncertainty is about where the phonological boudary lies, and also how this perceived boundary changes when evidence from the visual data varies from clear to ambiguous.
+The main finding of this paper is that people shift the categories' boudary depending on evidence form both auditory and visual input, and that, generally speaking, evidence from both modalities are weighted in a near optimal way.
+-->
+
+<!--
+
+This, in turn, would make them interpret the sound difference as alternative pronunciations of the same word\footnote{The reverse reasining is plausible as well, and in fact, can explain why in the same experiment, the use of acoustically distant words ("lif"/"neem"" instead of "bin"/"din) made 14 m.o succeed in the same task}.
+A prediction of the optimal model would be that the use of semantically distant objects can induce success with the same similar sounding words.
+
+new explanations for some findings in the developmental literature.
+We will focus on two influenceial lines of work relatad to multimodal processing: the development of modality dominance (Robertson and Sloutsky, 2004), and the development of the learning of similar sounding words (Stagter and Werker, 1997).
+
+Sloutsky and Napolitano (2003) reported a dominance for the auditory modality in children, and showed that this dominance disappears or reverses in adults.
+The authors attribute this dominance to the fact that auditory is more transient, and therefore tend to attract more attention.
+According to this interpretation, children should weight modalities in the same way regerdless of the stimuli used.
+Another interpretation, inspired by our model, would suggest that the precise sound and object contrasts used as stimuli in this series of experiments differ in their relative salience to children.
+One way to disentangle these two interpretations is to use an audio-visual stimuli where the sound contrast is reduced to a perceptual minimum and/or where the visual contrast is enhanced.
+An optimal-based account would suggest that the weighting would reverse in this case.
+
+it  may allow us to account for some findings in the dedvelopment literature
+
+The main finding of the present work is that when the input is multimodal, behavior is largely predicted by the value of the variance of the auditory category relative to the variance of the visual category.
+
+revisit some  findings in the develomental literature and speculate about possible explanations.
+We will focus on two influencial findings, one is the development of a phenomeon dubbed Auditory Overshadowing (Napolitano, Robertson, ...), and the other is the development of the ability to learn similar sounding words (Stager & Werker, 1997).
+
+we can still use its general idea (especially the fact that cues from a given modality are used according to their relative reliability) to revisit some findings in the literature and specualate about new interpretations.
+For instance, Sloutsky and Napolitano (2003) reported a peceptual dominance for the auditory modality in children, and showed that this dominance disappears or reverses in adults.
+The authors attribute this dominance to the fact that auditory is more transient, and therefore tend to attract more attention (I should elaborate more on this).
+According to this interpretation, children should weight modalities in the same way regerdless of the stimuli used.
+Another interpretation, inspired by our model, would suggest that the precise sound and object contrasts used as stimuli in this series of experiments differ in their relative salience to children.
+One way to disentangle these two interpretations is to use an audio-visual stimuli where the sound contrast is reduced to a perceptual minimum and/or where the visual contrast is enhanced.
+An optimal-based account would suggest that the weighting would reverse in this case.
+
+In a different line of work, it has been shown that infants have difficulties mapping two minimally different words to two novel objects, despite the fact that they can perceptually differentiate these words (e.g., Stager & Werker, 1997).
+This pattern of results has mostly been undertood as ‘failure’ in learning.
+Another interpretation  would explain this pattern of results based on developmental changes in the variance associated with the visual and phonological categories.
+If the categories get refined over time (that is, if the variances become smaller), then contrasts that used to fall under one category, may later fall under two separate categories.
+That is, rather than interpreting the null result as a failure in learning, these children might just have learned one word category instead of two categories.
+In particular, it is possible that the visual stimuli used in Stage and Werker (1997) were quite similar in the 14 m.o's early conceptual space, which made them believe that both objects were possible instances of the same semantic category.
+This, in turn, would make them interpret the sound difference as alternative pronunciations of the same word\footnote{The reverse reasining is plausible as well, and in fact, can explain why in the same experiment, the use of acoustically distant words ("lif"/"neem"" instead of "bin"/"din) made 14 m.o succeed in the same task}.
+A prediction of the optimal model would be that the use of semantically distant objects can induce success with the same similar sounding words.
+
+CONCLUSION
+
+To estimate the reliability (e.g., whether a token belong to one or the other category), one has to have access to the full probability distribution of the tokens,  For instance, @sloutsky2003 reported a dominance for the auditory modality in children, and This dominance disappears or reverses in adults
+
+n account helps us better understand the mechanisms of word processing and learning.
+
+We are working on extending this general framework to the case where neither the phonological, not the semantic categories are assumed to be present.
+Thus quantifying the synergy that might take place in development
+
+Can we understand word learning (and failure in learning as in Stager and Werker, 1997) in terms of developmental changes in the reliability (or the relative reliability) in the visual and auditory modalities?
+
+Computational principle behind bla bla
+
+What influence the combination is both the category dstribution (example), and also how rliabile at all (regarless of whether the token in)
+Here talk about theories of modality approp
+riateness theory. 
+Say that this is not what is going on here
+
+Talk about development
+In Experiment 1, the unceratinty was
+
+ One possible explanation for this preference could be that people do not combine cross-modal uncertainties of a similar kind (e.g., ambiguity in both modalities) in the same way they would combine uncertainties of different kinds (e.g., ambiguity in one modality and noise in the other).
+For instance, it could be that the latter, but not the former, cause the over-reliance on a particular modality.
+
+There were, however, quantitative differences.
+Audio-visual presentation increased the level of randomness in the participants' responses.
+One possible explanation is that this phenomenon was caused by the arbitrary nature of the form-meaning mapping.
+Previous studies suggest that while redundant multimodal information improves performance (e.g., determining the frequency of a bouncing ball from visual and auditory cues), arbitrary mappings generally tends to hinder performance [for review, see @robinson2010].
+
+Interestingly, however, in Experiment 1 this increase in randomness occurred at a similar rate for both the auditory and the visual modality, and thus, it did not affect their relative weighting.
+The latter was primarily determined by informational reliability.
+Only when we intervened by adding  noise to one modality in Experiment 2, did participants show a systematic preference for the non-noisy modality.
+One possible explanation for this preference could be that people do not combine cross-modal uncertainties of a similar kind (e.g., ambiguity in both modalities) in the same way they would combine uncertainties of different kinds (e.g., ambiguity in one modality and noise in the other).
+For instance, it could be that the latter, but not the former, cause the over-reliance on a particular modality.
+
+Overall, in both Experiments, the majority of the variance could be explained by an ideal observer that combined multimodal information optimally.
+In the light of this main result, we can revisit some previous findings in the literature.
+For instance, @sloutsky2003 reported a dominance for the auditory modality in children.
+This dominance disappears or reverses in adults.
+Could this difference be driven by changes across development in the level of perceptual noise affecting the intrinsic relative reliability of modalities (by analogy to Experiment 2)?
+More work is needed to carefully examine this (and other) speculations, and more generally, to determine the extent to which the optimal combination account helps us better understand the mechanisms of word processing and learning.
+
+-->
+
 # References

### 2018-02-24 Writeup/ms.Rmd
second draft journal write-up

@@
 ---
-title             : "Word Identification Under Multimodal Uncertainty"
+title             : "Word-Referent Identification Under Multimodal Uncertainty"
 shorttitle        : "Word Identification Under Multimodal Uncertainty"
@@
 
-  Deprtment of Psychology
-
-  Stanford Univerisity
+  Department of Psychology
+
+  Stanford University
 
@@
 abstract: |
- Identifying the visual referent of a spoken word -- that a particular insect is referred to by the word ``bee'' -- requires both the ability to process and integrate multimodal input and the ability to reason under uncertainty.
+
+ Identifying a spoken word in a referential context requires both the ability to process and integrate multimodal input and the ability to reason under uncertainty.
 How do these tasks interact with one another?
@@
 Model predictions are tested in three experiments where word recognition is made under two kinds of uncertainty: category ambiguity and/or distorting noise.
-In all cases, the optimal model explains much of the variance in human judgments.
+In all cases, the optimal model explains much of the variance in human mean judgments.
 In particular, when the signal is not distorted with noise, participants weight the auditory and visual cues optimally, that is, according to the relative reliability of each modality.
 But when one modality has noise added to it, human perceivers systematically prefer the unperturbed modality to a greater extent than the optimal model does.
-We discuss the broad implications of the results, especially in relation to early language acuquisition.
-
-keywords          : "Language; audio-visual processing; word learning; speech perception; computational modeling."
+The study provides a formal framework which helps us understand precisely how word form and word meaning interact in word recognition under uncertainty.
+Moreover it offers a first step towards a model that accounts for form-meaning synergy in early word learning.
+
+keywords          : "Language understanding; audio-visual processing; word learning; speech perception; computational modeling."
 
@@
 #############################
-exp1 <- read_delim("../Analysis/exp1_data_NoAnonym.txt", delim = " ") %>%
+exp1 <- read_delim("../Data_and_analysis/data_exp1_anonym.txt", delim = " ") %>%
   filter(type == "Task") %>%
@@
 
-exp2 <- read_delim("../Analysis/exp2_data_NoAnonym.txt", delim = " ") %>%
+exp2 <- read_delim("../Data_and_analysis/data_exp2_anonym.txt", delim = " ") %>%
   filter(type == "Task") %>%
@@
 
-exp3 <- read_delim("../Analysis/exp3_data_NoAnonym.txt", delim = " ") %>%
+exp3 <- read_delim("../Data_and_analysis/data_exp3_anonym.txt", delim = " ") %>%
   filter(type == "Task") %>%
@@
 They found that humans were sensitive to these probabilistic cues and their judgments closely reflected the optimal predictions.
-In another work, @feldman2009 studied the perceptual magnet effect, that is, the fact that categories influence the way the stimuli are perceived.
+In another work, @feldman2009 studied the perceptual magnet effect, which is related to how categories influence the way the stimuli are perceived.
 They showed that this effect can be explained as the consequence of optimally solving the problem of perception under uncertainty.
@@
 Imagine, for example, that someone is uncertain whether they heard "pea" or "bee", does this uncertainty make them rely more on the referent (e.g., the object being pointed at)?
-Vice versa, if they are not sure if they saw a bee or a fly, does that make them rely more on the sound?
+Vice versa, if they are not sure if they saw a bee or a fly, does it make them rely more on the sound?
 More importantly, when input in both modalities is uncertain to varying degrees, do they weight each modality according to its relative reliability (which is the optimal strategy), or do they over-rely on a particular modality (which is a sub-optimal strategy)?
@@
 In a referential context, however, modalities also differ in terms of their roles in the referential process: the auditory input represents the symbol (i.e., the word) whereas the visual input represents the referent.
-It has been suggested that because of the referential property of speech, it is a privileged signal for humans starting in infancy [see @vouloumanos2014 for a review].\footnote{There is a debate over whether speech is privileged for infant and adults for the same reasons.
+It has been suggested that because of its referential property, speech is a privileged signal for humans, starting in infancy [see @vouloumanos2014 for a review].\footnote{There is a debate over whether speech is privileged for infant and adults for the same reasons.
 Whereas Waxman and colleagues suggest that speech is privileged for both infants and adults because of its ability to refer, Sloutsky and colleagues suggest that speech might not have a referential status from the start.
-Rather, they argue tha speech seems to be prefered by infants only because of a low level auditory "overshadowing".} Thus, in a referential context, it is possible that we do not treat the auditory and visual modalities as equivalent sources of information.
+Rather, according to Sloutsky and colleagues, speech seems to be prefered by infants only because of a low level auditory "overshadowing".} Thus, in a referential context, it is possible that we do not treat the auditory and visual modalities as equivalent sources of information.
 Instead, there could be a bias for the auditory modality beyond what is expected from informational reliability alone.
@@
 
-We test the ideal observer model's predictions in three behavioral experiments where we vary the source of uncertainty.
-In Experiment 1, audio-visual tokens are ambiguous with respect to their category membership only.
-In Experiment 2, we intervene by adding background noise to the auditory modality, and in Experiment 3, we intervene by adding background noise to the visual modality.
+We tested the ideal observer model's predictions in three behavioral experiments where we varied the source of uncertainty.
+In Experiment 1, audio-visual tokens were ambiguous with respect to their category membership only.
+In Experiment 2, we intervened by adding background noise to the auditory modality, and in Experiment 3, we intervened by adding background noise to the visual modality.
 In all experiments, participants were quantitatively near-optimal, though overall response precision was slightly lower than expected.
@@
 
-In this section we describe the multimodal integration model.
-First, we briefly introduce the experimental paradigm, and second we explain how behavior in this paradigm can be characteized optimally with an ideal observer model.
+In this section we describe the multimodal cue combination model.
+First, we briefly introduce the experimental paradigm, and second we explain how behavior in this paradigm can be characterized optimally with an ideal observer model.
 
@@
 The test may differ from the target in both the auditory and the visual components.
-After these two presentations, participants press same' (i.e., the same category as the target) or `different' (not the same category).
-The auditory-only and visual-only conditions are similar, expect only the sounds are heard, or only the pictures are shown, respectively.", fig.align = "center", out.width = "400px"}
+After these two presentations, participants press `same' (i.e., the same category as the target) or `different' (not the same category).
+The auditory-only and visual-only conditions are similar to the audio-visual condition, except that only the sounds are heard, or only the pictures are shown, respectively.", fig.align = "center", out.width = "400px"}
 knitr::include_graphics("pictures/task.png", dpi = 108)
@@
 Such task would allow us to probe audio-visual encoding, but not necessarily language understanding.
-The latter requires---in addition to the perceptual encoding---a categorical judgement, i.e, determining wheather or not two similar tokens are members of the same phonological/semantic category.
-Thus, our task is category-based: participants are asked to press "same" if they think the second item (the test) belonged to the same category as the first (target) (e.g.,  dog-/aba/), even if there is a slight difference in the sound, in the referent, or in both.
+The latter requires---in addition to the perceptual encoding---a categorical judgement, i.e, determining whether or not two similar tokens are members of the same phonological/semantic category.
+Thus, our task is category-based: Participants are asked to press "same" if they think the second item (the test) belonged to the same category as the first (target) (e.g.,  dog-/aba/), even if there is a slight difference in the sound, in the referent, or in both.
 They are instructed to press "different" only if they think that the second stimulus was an instance of the other word category (cat-/ada/).
 The task also includes trials where pictures are hidden (audio-only) or where sounds are muted (visual-only).
-These unimodal trials provide us with participants' evaluation of the probabilistic information present in the auditory and visual categories.
+These unimodal trials provide us with the participants' evaluation of the probabilistic information present in the auditory and visual categories.
 This unimodal distributions are used as inputs to the optimal combination model, described below.
@@
 
-The ideal observer model has to combine probabilistic information from auditory and the visual modalities and make a categorical decision.
+The ideal observer model combines probabilistic information from the auditory and visual modalities, and makes a categorical decision.
 How can this task be characterized in a formal way, and what would be the optimal behavior?
-If the stimuli were continuous (e.g., size, location), cues derived from each modality would be characterized with their sensory noise variance only, and (assuming conditional independence) their combined information would be characterized with a simple linear combination rule where the combined estimate is an average of the indivisual estimates, each wighted according to its relative reliability [@ernst02; @alais04].
-However, in our case decison is made over categorical variables (phonemes and concepts), the optimal model should take into account, not only the noise variability arround an individual perceptual estimate, but also its categorical variability (i.e., the probability with which the estimate belongs to a given category).
+If the stimuli were continuous (e.g., size, location), cues derived from each modality would be characterized with their sensory noise variance only, and (assuming conditional independence) their combined information would be characterized with a simple linear combination rule where the combined estimate is an average of the individual estimates, each weighted according to its relative reliability [@ernst02; @alais04].
+However, in our case decision is made over categorical variables (phonemes and concepts), the optimal model should take into account, not only the noise variability around an individual perceptual estimate, but also its categorical variability (i.e., the probability with which the estimate belongs to a given category).
 
@@
 We represent the decision step as follows (see Figure\ \@ref(fig:model) for illustration).
-If we assume that both the visual and the auditory cues vary along a single dimension, an audio-visual signal $(a,v)$ can be represented as a point in this two-dimensionl space, and a word category can be characterized with a bivariate probability distribution over audio-visual tokens.\footnote{For the sake of clarity, we assume here that the sensory noise around this point is small/negligeable compared to the categorical vriability, but see below how the noise can be integrated when its effect is realtively large} Each category is peaked around the most typical audio-visual token, and the probability of membreship in the category (the likelihood probability) decreases gradually as the auditory token deviates from the typical sound instance (depending on the variance of the auditory category) and/or as the visual token deviates from the typical visual instance (depending on the variance of the visual category).
+If we assume that both the visual and the auditory cues vary along a single dimension, an audio-visual signal $(a,v)$ can be represented as a point in this two-dimensional space, and a word category can be characterized with a bivariate probability distribution over audio-visual tokens.\footnote{For the sake of clarity, we assume here that the sensory noise around this point is small/negligible compared to the categorical variability.
+But see below how the noise can be integrated when its effect is relatively large} Each category is peaked around the most typical audio-visual token, and the probability of membership in the category (the likelihood probability) decreases gradually as the auditory token deviates from the typical sound instance (depending on the variance of the auditory category) and/or as the visual token deviates from the typical visual instance (depending on the variance of the visual category).
 <!--To illustrate how categorical decision is made within this formal framework, suppose we receive an ambiguous image which can be either of a cat or of a dog, associated with a slightly noisy auditory input that sounds more like "cat".
@@
 -->
+
 A crucial feature of the ideal observer model is that it makes use of the entire probability distribution of a given category in order to make optimal decisions [e.g., @clayard08].
@@
 For instance, the model becomes less ambiguous and more certain as the tokens get closer to the typical instance of the category.
-This intuition will be formalized below.
+In what follows, we formalize this sense of optimality using a Bayesian framework.
 <!--characterized with a likelihood function, e.g., $P(S_V | S)$ and $P(S_A | S)$ for a visual and an auditory cue, respectively.
@@
 
-An auditory categoy $A$ and a visual category $V$ are defined as distributions in the auditory and the visual dimensions, respectively.
+An auditory category $A$ and a visual category $V$ are defined as distributions in the auditory and the visual dimensions, respectively.
 A word category $W$ is defined as a bivariate distribution in the audio-visual.
@@
 
-This assumption simply says that, given a word-object mapping, e.g., W=("cat"-CAT), variation in the way "cat" is pronounced does not correlate with changes in any visual property of the object CAT, which is a valid assumption.\footnote{Note that this assumptions is more adequate to the case of arbitrary associations such as ours, and less so in the case of redundant association such as audio-visual speech.
-In the latter, variation in the pronounciation is expected to correlate, at least to some extent, with lip movements.}
+This assumption simply says that, given a word-object mapping, e.g., W=("cat"-CAT), variation in the way "cat" is pronounced does not correlate with changes in any visual property of the object CAT, which is a valid assumption.\footnote{Note that this assumptions is more adequate in the case of arbitrary associations such as ours, and less so in the case of redundant association such as audio-visual speech.
+In the latter, variation in the pronunciation is expected to correlate, at least to some extent, with lip movements.}
 
@@
 $$p(w | W) = p(a,v| W) = p(a| A)p(v| V)$$
-Under this assumption, the posterior probability reduces to:\footnote{see the appendix for the details of the derivation}
+Under this assumption, the posterior probability reduces to:\footnote{See the appendix for the details of the derivation}
 \begin{equation}
@@
 However, since the identity of word categories is randomized across participants, $\epsilon$ measures, rather, a response bias to "same" if $\epsilon > 0$, and a response bias to "different" if $\epsilon < 0$.
-We expect a general bias towards answering "different" because of the categorical nature of our same-different task: when two items are ambiguous but perceptually different, participants might have a slight preference for "different" over "same".
+We expect a general bias towards answering "different" because of the categorical nature of our same-different task: When two items are ambiguous but perceptually different, participants might have a slight preference for "different" over "same".
 
@@
 
-## Auditory and Visual baseline models
-
-Besides the optimal model, we also test the predictions of two baselines models: a visual model, which assumes that participants rely only on visual information, and a auditory model, which assumes that participants rely only on auditory information.
+## Auditory and Visual models
+
+Besides the optimal model, we also test the predictions of two baselines models: a visual model, which assumes that participants rely only on visual information, and an auditory model, which assumes that participants rely only on auditory information.
 If participants rely on both the auditory and the visual modalities, the optimal model would explain more variance in human responses than the visual model alone or the auditory model alone.
@@
 Let $\sigma^2_{A}$ and $\sigma^2_{V}$ be the values of the variances used in the optimal model (derived from the unimodal conditions), and $\sigma^2_{Ab}$ and $\sigma^2_{Vb}$ be the values observed through the descriptive model in the bimodal condition.
-Deviation from optimality can be quantified in two ways.
-First, we quantify changes in the values of the variances specific to each modality, that is, how $\sigma^2_{A}$ compares to $\sigma^2_{Ab}$, and how $\sigma^2_{V}$ compares to $\sigma^2_{Vb}$.
-Second,  we quantify changes in the proportion of the visual and auditory variances, i.e., how $\frac{\sigma^2_{A}}{\sigma^2_{V}}$ compares to $\frac{\sigma^2_{Ab}}{\sigma^2_{Vb}}$.
-The first comparison allows us to test if precision varies for each modality, and the second, allows us to test whether or not the weighing scheme folows the prediction of the optimal model.
-The reason we used the proportion of the variances as an measure of cross-modal weighing is because it correponds to the slope of the decision threshold in the audio-visual space (Figure\ \@ref(fig:model)).
+Deviation from optimality is measured in two ways.
+First, we measure the change in the values of the variances specific to each modality, that is, how $\sigma^2_{A}$ compares to $\sigma^2_{Ab}$, and how $\sigma^2_{V}$ compares to $\sigma^2_{Vb}$.
+Second, we measure changes in the proportion of the visual and auditory variances, i.e., how $\frac{\sigma^2_{A}}{\sigma^2_{V}}$ compares to $\frac{\sigma^2_{Ab}}{\sigma^2_{Vb}}$.
+The first measure allows us to test if precision changes for each modality when we move from the unimodal to the bimodal conditions.
+The second allows us to test whether or not the weighting scheme follows the prediction of the optimal model.
+The reason we used the proportion of the variances as a measure of cross-modal weighing is because it corresponds to the slope\footnote{Or more precisely the absolute value of the slope} of the decision threshold in the audio-visual space (Figure\ \@ref(fig:model)).
 The decision threshold is defined as the set of values in this audio-visual space along which the posterior is equal to 0.5.
@@
 
-If the slope derived from the descriptive model is greater than the slope of the optimal model, the corresponding shift in the decision threshold indicates that participants have a preference for the auditory modality in the bimodal case.
-Similarly, a smaller slope would lead to a preference for the visual modality.
+If the absolute value of the slope derived from the descriptive model is greater than that of the optimal model, the corresponding shift in the decision threshold indicates that participants have a preference for the auditory modality in the bimodal case.
+Similarly, a smaller absolute value of the slope would lead to a preference for the visual modality.
 The limit cases are when there is exclusive reliance on the auditory cue (a vertical line), and where there is exclusive reliance on the visual (a horizontal line).
 
-There are three possible scenarios for sub-optimality, as illustrated in Figure\ \@ref(fig:subOptim):
+It follows that there are three possible scenarios describing how humans can deviate from optimality. These scenarios are illustrated in Figure\ \@ref(fig:subOptim) and are as follows:
 
 1) Both variances may increase, but their proportion remains the same.
-That is, $\frac{1}{\sigma^2_{Ab}} \leqslant \frac{1}{\sigma^2_{A}}$ and $\frac{1}{\sigma^2_{Vb}} \leqslant \frac{1}{\sigma^2_{V}}$, but  $\frac{\sigma^2_{Ab}}{\sigma^2_{Vb}} \approx \frac{\sigma^2_{A}}{\sigma^2_{V}}$.
+That is, $\sigma^2_{Ab} \geqslant \sigma^2_{A}$ and $\sigma^2_{Vb} \geqslant \sigma^2_{V}$, but  $\frac{\sigma^2_{Ab}}{\sigma^2_{Vb}} \approx \frac{\sigma^2_{A}}{\sigma^2_{V}}$.
 In this case, sub-optimality would be due to increased randomness in human responses in the bimodal condition.
@@
 2) The auditory variance increases at a higher rate.
-That is, $\frac{1}{\sigma^2_{Ab}} \ll \frac{1}{\sigma^2_{A}}$ and $\frac{1}{\sigma^2_{Vb}} \leq \frac{1}{\sigma^2_{V}}$, leading to $\frac{\sigma^2_{Ab}}{\sigma^2_{Vb}} > \frac{\sigma^2_{A}}{\sigma^2_{V}}$.
+That is, $\sigma^2_{Ab} \gg \sigma^2_{A}$ and $\sigma^2_{Vb} \geqslant \sigma^2_{V}$, leading to $\frac{\sigma^2_{Ab}}{\sigma^2_{Vb}} > \frac{\sigma^2_{A}}{\sigma^2_{V}}$.
 In this case, sub-optimally would consist not only in participants being more random in the bimodal condition, but also in having a systematic preference for the visual modality, even after accounting for informational reliability.
@@
 3) The visual variance increases at a higher rate.
-That is, $\frac{1}{\sigma^2_{Vb}} \ll \frac{1}{\sigma^2_{V}}$, and  $\frac{1}{\sigma^2_{Ab}} \leq \frac{1}{\sigma^2_{A}}$, leading to $\frac{\sigma^2_{Ab}}{\sigma^2_{Vb}} > \frac{\sigma^2_{A}}{\sigma^2_{V}}$.
+That is, $\sigma^2_{Vb} \gg \sigma^2_{V}$, and  $\sigma^2_{Ab} \geqslant \sigma^2_{A}$, leading to $\frac{\sigma^2_{Ab}}{\sigma^2_{Vb}} > \frac{\sigma^2_{A}}{\sigma^2_{V}}$.
 This case is the reverse of case 2, i.e., in addition to increased randomness in the bimodal condition, there is a systematic preference for the auditory modality, even after accounting for informational reliability.
 
-```{r subOptim, fig.cap = "Illustration using simulated data showing the prediction of the optimal model (top), and the three possible ways human responses can deviate from the optimal predictions (bottom).
-These cases are: 1) the variance increases equally for both modalities, but the cue weighting is still optimal, 2) The auditory variance increases at a higher rate, leading to a preference for the auditory modality, and 3) The visual variance increases at a higher rate, leading to a preference for the visual modality", fig.align = "center", out.width = "400px"}
+```{r subOptim, fig.cap = "Illustration using simulated data showing the example of a prediction made by the optimal model (top), and the three possible ways human participants can deviate from this prediction (bottom).
+These cases are the following: 1) The variance increases equally for both modalities, but the weighting scheme (characterized by the decision threshold) is optimal, 2) The auditory variance increases at a higher rate, leading to a preference for the auditory modality, and 3) The visual variance increases at a higher rate, leading to a preference for the visual modality", fig.align = "center", out.width = "400px"}
 knitr::include_graphics("pictures/sub-optimal", dpi = 108)
@@
 
-We tested these predictions in three experiments.
-In Experiment 1, we studied the case where bimodal uncertainty is due to ambiguity in terms of category membership, without any additional background noise.
+We tested the predictions of the optimal model in three experiments.
+In Experiment 1, we studied the case where bimodal uncertainty was due to ambiguity in terms of category membership, without any additional background noise.
 In Experiment 2 and 3 we added background noise on top of ambiguity in category membership.
@@
 
-In this Experiment, we start with testing the predictions in the case where uncertainty is due to ambiguity in terms of category membership only, that is, according to the following weighting scheme:  $$\beta_a \propto \frac{1}{\sigma^2_{A}}$$ $$\beta_v \propto \frac{1}{\sigma^2_{V}}$$ We do not introduce any additional noise in the background, and we assume that sensory noise is negligeable compared to categorical variability.
+In this Experiment, we start with testing the predictions in the case where uncertainty is due to ambiguity in terms of category membership only, that is, according to the following weighting scheme:  $$\beta_a \propto \frac{1}{\sigma^2_{A}}$$ $$\beta_v \propto \frac{1}{\sigma^2_{V}}$$ We do not introduce any additional noise in the background, and we assume that sensory noise is negligible compared to categorical variability.
 
@@
 
-```{r unimodal, fig.cap = "Dots represent the proportion of `different' to `same' responses in the auditory-only condition (left), and visual-only condition (right), across the three Experiments.
-Error bars are 0.95 confidence intervals.
+```{r unimodal, fig.cap = "Human responses in the unimodal condition.
+Points represent the proportion of `different' to `same' responses in the auditory-only condition (left), and visual-only condition (right).
+Error bars are 95\\% confidence intervals.
 Solid lines represent logistic fits.", fig.align = "center", out.width = "400px"}
@@
 ### Model fitting details
-
-We first discuss the model fitting details of the unimodal conditions.
+#### Unimodal condition
 Remember that data in this conditions allow us to derive the variances of both the auditory and the visual categories, and that these variances are used to make predictions about bimodal data (in the visual and auditory baselines as well as in the optimal model).
-These individual variances are derived as follows (we will explain the derivation for the auditory-only case, but the same applies for the visual-only case).
-For an ideal observer, when presented with an audio instance $a$, the probability of choosing the sound category 2 (that is, to answer "different") is the posterior probability of this category $p(A_2|a)$.
+These individual variances were derived as follows (we explain the derivation for the auditory-only case, but the same applies for the visual-only case).
+We use the same Bayesian reasoning as we did in the derivation of the bimodal model: When presented with an audio instance $a$, the probability of choosing the sound category 2 (that is, to answer "different") is the posterior probability of this category $p(A_2|a)$.
 If we assume that both sound categories have equal variances, the posterior probability reduces to:
@@
 $\epsilon_A$ is the response bias in the auditory-only condition.
-For this model (as well all models in this study), we fixed the values of the means to be the end-points of the corresponding continuum, since these points are the most typical instances in our stimuli.
+For this model (as well as all other models in this study), we fixed the values of the means to be the end-points of the corresponding continuum, since these points are the most typical instances in our stimuli.
 Thus, we have $\mu_{A1}=0$ and $\mu_{A2}=4$ (and similarly $\mu_{V1}=0$, and $\mu_{V2}=4$).
 This leaves us with two free parameters: the bias $\epsilon_A$ and the variance $\sigma^2_{A}$.
-To determine the values of these parameteres, we fit the unimodal posterior to human data in the unimodal case.
-
-In the bimodal condition, only the desciptive model is fit to the data, using the posterior (Equation 1).
-Since the values of the means are fixed, we have 3 free parameteres: the variances for the visual and the auditory modalities, respectively, and $\epsilon$, the response bias.
+To determine the values of these parameters, we fit the unimodal posterior to human data in the unimodal case.
+
+#### Bimodal condition
+In this condition, only the descriptive model is fit to the data, using the expression of the posterior (Equation 1).
+Since the values of the means are fixed, we have 3 free parameters: the variances for the visual and the auditory modalities, respectively, and $\epsilon$, the response bias.
 The visual and auditory baselines as well as the optimal model are not fit to bimodal data, but their predictions are tested against these bimodal data.
-All these notmative models use the variances derived from the unimodal data and the bias term derived from the bimodal data.
-
-Although the paradigm is within-subjcts, we did not have enough statistical power to fit a different model for each individual participant.
+All these normative models use the variances derived from the unimodal data and the bias term derived from the bimodal data.
+
+Although the paradigm is within-subjects, we did not have enough statistical power to fit a different model for each individual participant.
 Instead, models are constructed with data collapsed across all participants.
 The fit was done with a nonlinear least squares regression using the NLS package in R [@bates88].
-We computed the values of the parameters, as well as their 95% confidence intervals, through non-parametric bootstrap (with 10000 iterations).
+We computed the values of the parameters, as well as their 95% confidence intervals, through non-parametric bootstrap (using 10000 iterations).
 
@@
 ```{r bimodal, fig.cap = "Human responses vs.
-models' predictions across the three Experiments.
+models' predictions in the bimodal condition.
 Shape represents auditory distance from the target, and color represents visual distance from the target.", fig.align = "center", out.width = "400px", fig.width=7, fig.height=8}
@@
 ```
-
-Now we analyse the bimodal case. This is the case where the participants saw the pictures and heard the sounds simulateously.
 
@@
 Figure\ \@ref(fig:bimodal) compares the predictions of the normative models against human responses.
-The visual, auditory and optimal model explained, respectively, `r 100*R2_visual_1`%, `r 100*R2_auditory_1`%, and `r 100*R2_optimal_1`% of total variance.
+The visual, auditory and optimal model explained, respectively, `r 100*R2_visual_1`%, `r 100*R2_auditory_1`%, and `r 100*R2_optimal_1`% of total variance in mean responses.
 
@@
 We found $\epsilon=$ `r BiasBi_val` [`r BiasBi_ci2`, `r BiasBi_ci1`], $\sigma^2_{Ab}=$ `r audVarBi_val` [`r audVarBi_ci1`, `r audVarBi_ci2`] and $\sigma^2_{Vb}=$ `r visVarBi_val` [`r visVarBi_ci1`, `r visVarBi_ci2`].
-Note that the precision of both the auditory and visual modalities decreased compared to the unimodal conditions.
+Note that the variance of both the auditory and visual modalities increased compared to the unimodal conditions.
 
 The descriptive model explained `r 100*R2_descriptive_1`% of total variance.
-However, since the descriptive model was fit to the same data it is predicting, there is a risque this high correlation is due to overfitting.
+However, since the descriptive model was fit to the same data, there is a risque that this high correlation is due to overfitting.
 To examine this possibility, we cross-validated the model using half the responses to predict the other half (averaging across 1000 random partitions).
-The predictive power of the model remained high ($r^2$=`r CV_exp1_mean`).
+The predictive power of the model remained very high ($r^2$=`r CV_exp1_mean`).
 
 #### Cue combination and Modality preference
-We next analyzed the extent to which cue combination was performed in an optimal way, or whether there was a systematic preference for one modality when making decisions in the bimodal condition.
+We next analyzed if cue combination was performed in an optimal way, or if there was a systematic preference for one modality when making decisions in the bimodal condition.
 As explained above, modality preference can be characterized formally as a deviation from the decision threshold predicted by the optimal model.
-Figure\ \@ref(fig:bias) shows the value of the slope derived from the descriptive model (i.e., $-\frac{\sigma^2_{Vb}}{\sigma^2_{Ab}}$) relative the slope of the optimal model (i.e., $-\frac{\sigma^2_V}{\sigma^2_A}$).
+Figure\ \@ref(fig:bias) (top) shows both the decision threshold derived from the descriptive model (in black) and the decision threshold predicted by the optimal model (in red).
+The deviation from optimality is compared to two hypothetical cases of modality preference (dotted lines).
+We found that the descriptive and optimal decision thresholds were almost identical.
+Indeed, non-parametric resampling of the data showed no evidence of a deviation from the optimal prediction (Figure\ \@ref(fig:bias), bottom).
+
+<!--the value of the slope derived from the descriptive model (i.e., $-\frac{\sigma^2_{Vb}}{\sigma^2_{Ab}}$) relative the slope of the optimal model (i.e., $-\frac{\sigma^2_V}{\sigma^2_A}$).
 The red dotted line represents the case where this proportion is optimal, meaning that both slopes are equal.
@@
 Non-parametric resampling of the data showed no evidence of a deviation from the optimal prediction.
+-->
 
@@
 Overall, we found that the optimal model explained much of the variance in the mean judgments, and largely more than what can be explained with the auditory or the visual models alone.
-The relatively high value of the coefficient of determination in the optimal model ($r^2$=`r R2_optimal_1`) suggests that the population was near-optimal.
-However, we see from Figure\ \@ref(fig:bimodal) that the mean responses deviated from the optimal prediction in that they were slightly pulled toward chance (i.e., the probability value of 0.5).
+Moreover, the high value of the coefficient of determination in the optimal model ($r^2$=`r R2_optimal_1`) suggests that the population was near-optimal.
+However, we see in Figure\ \@ref(fig:bimodal) that the mean responses deviated systematically from the optimal prediction in that they were slightly pulled toward chance (i.e., the probability 0.5).
 This is due to the increase in the value of the variance associated with each modality.
@@
 Rather, the phrase refers to the case of potential sub-optimality where participants would rely on one modality beyond what is explained by the relative reliability of the optimal model.
---> Thus, 1) There was a simultaneous increase in the values of the auditory and visual variances in the bimodal condition compared to the unimodal condition, meaning that the bimodal input lead to an increase in response randomness, and 2) this increased randomness did not affect the relative weighting of both modalities, i.e., the population was weighting modalities according to their relative reliability predicted by the optimal model.
-This situation corresponds to the first case of sub-optimally described in the predictions.
+--> Thus, 1) There was a simultaneous increase in the values of the auditory and visual variances in the bimodal condition compared to the unimodal condition, meaning that the bimodal input lead to an increase in response randomness, and 2) this increased randomness did not affect the relative weighting of both modalities, i.e., the population was weighting modalities according to the relative reliability predicted by the optimal model.
+This situation corresponds to the first case of sub-optimally described in Figure\ \@ref(fig:subOptim).
 
@@
 
-exlusive_prop_1 = only_visual_N_1/only_sound_N_1
+exlusive_prop_1 = only_visual_N_1/(only_sound_N_1+only_visual_N_1)
 
@@
 
-```{r echo=FALSE, individual, fig.cap = "Histogram of the weighting values in the bimodal condition (the visual variance relative to the auditory variance) derived from each individual participants.", fig.align = "center", out.width = "400px", fig.width=7, fig.height=8}
+```{r echo=FALSE, individual, fig.cap = "Histograms of the values of the visual variance relative to the auditory variance in Experiment 1.
+Light color represents the values derived from each individual participant, and dark color represents simulated data sampled from the descriptive model.", fig.align = "center", out.width = "400px", fig.width=7, fig.height=8}
 
@@
 
-As we noted earlier, the model adresses the issue of optimality at the poplation level.
-However, it is important to have a general sense of the individual distribution.
-In fact, one could think of an extreme case where optimality at the poupulation level would be misleading.
+As we noted earlier, the model addresses the question of optimality at the population level.
+However, it is important to  know how individual responses are distributed.
+In fact, one could think of an extreme case where optimality at the population level would be misleading.
 Imagine, for instance, that in the bimodal condition half the participants relied exclusively on the visual modality, whereas the other half relied exclusively on the auditory modality.
-This case could still lead to an agregate behaviour which appears optimal, but this optimality would be spurious.
+This case could still lead to an aggregate behaviour which appears optimal, but this optimality would be spurious.
 
 To examine this possibility, we consider the distribution of individual cross-modal weighting in the bimodal condition (i.e., $\frac{\sigma^2_{Vb}}{\sigma^2_{Ab}}$).
-Using a factor of 10 as a cut-off, we found that `r only_visual_N_1` participants relied almost exlusively on the visual modality, and `r only_sound_N_1` relied almost exclusively on the auditory modality.
-The percentage of both these cases reamined liminted compared to the total number of participants (`r 100*(only_visual_N_1+only_sound_N_1)/(only_visual_N_1+only_sound_N_1+both_N_1)`%).
-An additional number of participants (N=`r neg_N_1`) relied on both modalities, but privided noisy responses which lead to negative variances (probably because they mistook 'same' for 'different' or vice versa).
-When these outliers  were removed, the distribution had an unimodal shape (Figure\ \@ref(fig:individual)).
-This finding indicates that the population's near optimality is not spurious, but based mostly on geniune cue combination at the individual level.
-
-As a second analysis, we asked whether the observed variability at the individual level corresponded to mere sampling errors or whether it corresponded to a real between-subject varation.
-To answer this question, we simulated individual responses from the posterior distribution whose parameters were fit to the population as a whole (i.e., the descriptive posterior).
-The simulated distribution was super-imposed to the real distribution in Figure\ \@ref(fig:individual).
-The real distribution is braoder than the simulated distribution, indivating that there is evidence for a between-subject variation beyond sampling errors.
-This means that the particiapnts varied in terms of how they wheighed modalities: Compared to the predictions of the global descriptive model, some participants relied more on the auditory modality, and some relied more on the visual modality.
+Using a factor of 10 as a cut-off, we found that `r only_visual_N_1` participants relied almost exclusively on the visual modality, and `r only_sound_N_1` relied almost exclusively on the auditory modality.
+The percentage of both cases was relatively small compared to the total number of participants (`r 100*(only_visual_N_1+only_sound_N_1)/(only_visual_N_1+only_sound_N_1+both_N_1)`%).
+An additional number of participants (N=`r neg_N_1`) relied on both modalities, but provided noisy responses which lead to negative variances (probably due to mistaking 'same' for 'different' or vice versa).
+When these outliers  were removed, the distribution had a rather unimodal shape (Figure\ \@ref(fig:individual)).
+This finding indicates that the population's near optimality is not spurious, but based mostly on genuine cue combination at the individual level.
+
+As a second analysis, we asked whether the observed variance in the individual distribution was due to mere sampling errors or whether it corresponded to a real between-subject variability.
+We simulated individual responses from the posterior distribution whose parameters were fit to the population as a whole (i.e., the descriptive posterior).
+The resulting distribution is shown in Figure\ \@ref(fig:individual).
+For ease of comparison, the simulated distribution was superimposed to the real distribution.
+We found that the real distribution was broader than the simulated distribution, indicating real between-subject variation beyond sampling errors.
+This means that the participants varied in terms of how they wheigthed modalities: Compared to the predictions of the global descriptive model, some participants relied more on the auditory modality, and some relied more on the visual modality.
 
@@
 We were interested to know if participants would treat this new source of uncertainty as predicted by the optimal model, that is, according to the following weighting scheme  $$\beta_a \propto \frac{1}{\sigma^2_{A}+\sigma^2_{N_A}}$$ $$\beta_v \propto \frac{1}{\sigma^2_{V}}$$
-The alternative hypothesies is that noise in one modality leads to a systematic preference for the non-noisy modality.
+The alternative hypothesis is that noise in one modality leads to a systematic preference for the non-noisy modality.
 
@@
 The average signal-to-noise ratio was - 4.4 dB.
-The procedure was exactly the same as in the previous experiment, except that test stimuli (but not the target) were presented with the new noisy auditory stimuli.
+The procedure was exactly the same as in the previous experiment, except that the test stimuli (but not the target) were presented with the new noisy auditory stimuli.
 
@@
 
-We fit a model for each modality, collapsed across all participants.
+We fit a model for each modality.
 For the auditory modality, our parameter estimates were $\epsilon_A=$ `r audBias_val` [`r audBias_ci2`, `r audBias_ci1`] and $\sigma^2_A+\sigma^2_N=$ `r audVar_val` [`r audVar_ci1`, `r audVar_ci2`].
@@
 Figure\ \@ref(fig:unimodal) shows responses in the unimodal conditions as well as the corresponding best fits.
-The visual data is a replication of the vidual data in Experiment 1.
-As for the auditory data, we see that, in contrast to Experiment 1, responses were less categorical/flatter, showing more uncertainty.
+The visual data is a replication of the visual data in Experiment 1.
+As for the auditory data, in contrast to Experiment 1, responses were flatter, showing more uncertainty.
 
@@
 
+#### Normative models
+Figure\ \@ref(fig:bimodal) compares the predictions of the visual, auditory and optimal models to human responses.
+These normative models explained, respectively, `r 100*R2_visual_2`%, `r 100*R2_auditory_2`%, and `r 100*R2_optimal_2`% of total variance in mean judgements.
+Note that, in contrast to Experiment 1, the visual model explains more variance than the auditory model.
+
 #### Descriptive model
-We fit the descriptive model to human responses in the bimodal condition, collapsed across all articipants.
 We estimated $\epsilon=$ `r BiasBi_val` [`r BiasBi_ci2`, `r BiasBi_ci1`], $\sigma^2_{Ab}+\sigma^2_{Nb}=$ `r audVarBi_val` [`r audVarBi_ci1`, `r audVarBi_ci2`], and $\sigma^2_{Vb}=$ `r visVarBi_val` [`r visVarBi_ci1`, `r visVarBi_ci2`].
 The fit explained `r R2_descriptive_2`% of total variance.
-Cross-validation using half the responses to predict tho other half yields $r^2=$`r CV_exp2_mean` [`r CV_exp2_lower`, `r CV_exp2_upper`].
-
-#### Normative models
-We derived the predictions of the auditory, visual and optimal model by using the values of the variances derived from the unimodal conditions, and the response bias derived from the descriptive model.
-Figure\ \@ref(fig:bimodal) compares the predictions of these three models to human responses.
-The visual, auditory and optimal model explained, respectively, `r 100*R2_visual_2`%, `r 100*R2_auditory_2`%, and `r 100*R2_optimal_2`% of total variance.
-Note that, in contrast to Experiment 1, the visual model explains more variance than the auditory model.
+Cross-validation using half the responses to predict the other half yielded $r^2 =$ `r CV_exp2_mean`.
 
 #### Modality preferences
-Participants' decision threshold suggested a preference for the visual modality (the non-noisy modality).
-Indeed non-parametric resampling of the data showed a decrease in the value of the slope in the descriptive model compared to the optimal model (Figure\ \@ref(fig:bias)).
+Figure\ \@ref(fig:bias) (top) shows that the participants' decision threshold deviated from optimality, and that this deviation was biased towards the visual modality (the non-noisy modality).
+Indeed non-parametric resampling of the data showed a decrease in the value of the slope in the descriptive model compared to the optimal model (Figure\ \@ref(fig:bias), bottom).
 
 ## Discussion
-We found, similar to Experiment 1, that participants were generally near optimal ($r^2 =$ `r R2_optimal_2`% of total variance), and that the optimal model explained more variance than the auditory or the visual models alone.
+We found, similar to Experiment 1, that the population was generally near optimal ($r^2 =$ `r R2_optimal_2`), and that the optimal model explained more variance than the auditory or the visual models alone.
 We also found a similar discrepancy from the optimal model as precision dropped for both the auditory and the visual modalities.
-As for the weghting scheme used by participants, contrary to Experiment 1 where modalities were weighted according to their optimal relative reliability, we found in this experiment that the visual modality had a greater weight than what is  expected from its relative reliability.
-This situation corresponds to the second case of sub-optimally described in the predictions above.
+As for the weighting scheme used by participants, contrary to Experiment 1 where modalities were weighted according to their relative reliability, we found in this experiment that the visual modality had a greater weight than what is expected from its relative reliability.
+This situation corresponds to the second case of sub-optimally described in Figure\ \@ref(fig:subOptim).
 
@@
 
-exlusive_prop_2 = only_visual_N_2/only_sound_N_2
-
-```
-We were also interested in whether noise in the auditory modality lead more participants to rely exclusviely on the visual modality at the indivual level.
-Using the same cut-off as in Experiment 1 (a factor of 10), the percentage of particpants who relied exclusively on eiter modalities was `r 100*(only_visual_N_2+only_sound_N_2)/(only_visual_N_2+only_sound_N_2+both_N_2)`%, which is much higher than the percentage abtained in Experiment 1 (`r 100*(only_visual_N_1+only_sound_N_1)/(only_visual_N_1+only_sound_N_1+both_N_1)`%).
-Moreover, the propotion of participants relying exclusively on the visual modality relative to the sound modality reversed from `r exlusive_prop_1` in Experiment 1 to `r exlusive_prop_2` in the present experiment, suggesting that noise in the auditory modality prompted more participants to rely exclusively and disproportionately on the visual modality.
-
-In Experiment 2, we tested the case where we added background noise to the auditory modality. In Experiment 3, we test the situation where we added noise to the visual modality.
+exlusive_prop_2 = only_visual_N_2/(only_sound_N_2+only_visual_N_2)
+
+```
+We were also interested in whether noise in the auditory modality lead more participants to rely exclusively on the visual modality at the individual level.
+Using the same cut-off as in Experiment 1 (a factor of 10), the percentage of participants who relied exclusively on either modalities was `r 100*(only_visual_N_2+only_sound_N_2)/(only_visual_N_2+only_sound_N_2+both_N_2)`%, which is much higher than the percentage obtained in Experiment 1 (`r 100*(only_visual_N_1+only_sound_N_1)/(only_visual_N_1+only_sound_N_1+both_N_1)`%).
+Moreover, the subset of participants relying exclusively on the visual modality (compared to those who relied exclusively on the auditory modality)  increased from `r 100*exlusive_prop_1`% in Experiment 1 to `r 100*exlusive_prop_2`% in Experiment 2, indicating that noise in the auditory modality prompted more participants to rely exclusively and disproportionately on the visual modality.
+
+In Experiment 2, we tested the case of added background noise to the auditory modality. In Experiment 3, we test the case of added noise to the visual modality.
 
@@
 Similar to Experiment 2, we were interested to know if participants would treat this new source of uncertainty as predicted by the optimal model, that is, according to the following weighting scheme  $$\beta_a \propto \frac{1}{\sigma^2_{A}}$$ $$\beta_v \propto \frac{1}{\sigma^2_{V}+\sigma^2_{N_V}}$$
-The alternative hypothesies is that, just like noise in the auditory modality lead to a preference for the visual input, noise in the visual modality leads to a  preference for the auditory input.
+The alternative hypothesis is that, just like noise in the auditory modality lead to a preference for the visual input in Experiment 2, noise in the visual modality would lead to a  preference for the auditory input.
 
@@
 We also used the same visual stimuli, but we blurred the tokens using the free image editor GIMP (2.8.20).
-We used a Gaussian blur with a radius\footnote{A features of the filter that afftects the intensity of the blur} of 10 pixels.
+We used a Gaussian blur with a radius\footnote{A features of the filter that affects the intensity of the blur} of 10 pixels.
 The experimental procedure was exactly the same as in the previous Experiments.
@@
 ### Unimodal conditions
-We fit a model for each modality, collapsed across participants.
 For the auditory modality, our parameter estimates were $\epsilon_A=$ `r audBias_val` [`r audBias_ci2`, `r audBias_ci1`] and $\sigma^2_A=$ `r audVar_val` [`r audVar_ci1`, `r audVar_ci2`].
@@
 
+#### Normative models
+Figure\ \@ref(fig:bimodal) compares the predictions of the visual, auditory and optimal models to human responses.
+These normative models explained, respectively, `r 100*R2_visual_3`%, `r 100*R2_auditory_3`%, and `r 100*R2_optimal_3`% of total variance in mean judgement.
+
 #### Descriptive model
-We fit the descriptive model to human responses in the bimodal condition, collapsed across participants.
 We estimated $\epsilon=$ `r BiasBi_val` [`r BiasBi_ci2`, `r BiasBi_ci1`], $\sigma^2_{Ab}=$ `r audVarBi_val` [`r audVarBi_ci1`, `r audVarBi_ci2`], and $\sigma^2_{Vb}+\sigma^2_{Nb}=$ `r visVarBi_val` [`r visVarBi_ci1`, `r visVarBi_ci2`].
 The fit explained `r 100*R2_descriptive_3`% of total variance.
-Cross-validation using half the responses to predict tho other half yields $R^2=$`r CV_exp3_mean` [`r CV_exp3_lower`, `r CV_exp3_upper`].
-
-#### Normative models
-We derived the predictions of the auditory, visual and optimal model by using the values of the variances derived from the unimodal conditions, and the response bias derived from the descriptive model.
-Figure\ \@ref(fig:bimodal) compares the predictions of these three models to the human responses.
-The visual, auditory and optimal model explained, respectively, `r 100*R2_visual_3`%, `r 100*R2_auditory_3`%, and `r 100*R2_optimal_3`% of total variance.
+Cross-validation using half the responses to predict the other half yielded $r^2= $ `r CV_exp3_mean`.
 
@@
 Thus, though participants were still sensitive to variation in the noisy visual data in the unimodal condition, they tended to ignore this information in the bimodal condition, and relied almost exclusively on the non-noisy auditory modality.
-The reason why we saw this (floor) effect when we added noise to the visual modality (Experiment 3), and not when added noise to the auditory modality (Experiment 2), is the fact that our visual stimuli were originally perceived less categorically and with less certainty than the auditory stimuli.
+The reason why we saw this (floor) effect when we added noise to the visual modality (Experiment 3), and not when we added noise to the auditory modality (Experiment 2), is the fact that our visual stimuli were originally perceived less categorically and with less certainty than the auditory stimuli.
 This made it more likely for the visual categorization function to become flat and uninformative after a few drops in precision due to noise on the one had, and to the additional randomness induced by the bimodal presentation on the other hand.
@@
 -->
-The general finding corresponds to the third case of sub-optimality described above.
+The general finding corresponds to the third case of sub-optimality described in Figure\ \@ref(fig:subOptim).
 Indeed, precision dropped for both modalities in the bimodal condition compared to the unimodal condition.
@@
 
-exlusive_prop_3 = only_visual_N_3/only_sound_N_3
-
-```
-The percentage of participants who relied exclusively on either the visual modality or the auditory modality was `r 100*(only_visual_N_3+only_sound_N_3)/(only_visual_N_3+only_sound_N_3+both_N_3)`%, which is closer to the percentage of Experiment 2, except that most of these participants relied exclusively on the auditory modality  instead of the visual modality: The propotion of participants relying exclusively on the visual modality relative to the sound modality was `r exlusive_prop_3` (compared to `r exlusive_prop_2` in Experiment 2).
+exlusive_prop_3 = only_visual_N_3/(only_sound_N_3+only_visual_N_3)
+
+```
+The percentage of participants who relied exclusively on either the visual modality or the auditory modality was `r 100*(only_visual_N_3+only_sound_N_3)/(only_visual_N_3+only_sound_N_3+both_N_3)`%, which is closer to the percentage of Experiment 2, except that now almost all of them relied on the auditory modality (`r 100*(1-exlusive_prop_3)`%).
 
@@
 
-```{r bias, echo=FALSE, warning = FALSE, fig.cap = "Relative weighing of evidence from the auditory stimulus vs.
-evidence from the visual stimulus across the three Experiments (log-scaled).
-The red dashed  line  shows the  prediction  of the model  if the weighting is optimal,  and the  blue dashed lines  show   predictions if participants deviated from  optimality by relying  twice  as much  on the visual  input  (strong visual bias), or by relying twice as much on  the auditory input (strong  sound bias).", fig.align = "center", out.width = "400px"}
+```{r bias, echo=FALSE, warning = FALSE, fig.cap = "Modality preference is characterized as a deviation from the optimal decision threshold.
+A) The decision thresholds of both the optimal and the descriptive models (solid red and black lines respectively).
+Deviation from optimality is compared to two hypothetical cases of modality preference.
+In these cases, deviation from  optimality is due to over-lying on the visual or the auditory input (green and blue dotted lines, respectively) by a factor of 2.
+B) The value of the decision threshold's slope derived from the descriptive model relative to that of the optimal model.
+Error bars represent 95\\% confidence intervals over the distribution obtained through non-parametric resampling.", fig.align = "center", out.width = "400px"}
 
@@
 When identifying a spoken word under uncertainty, one often needs to combine and make the most of the available multimodal cues.
-While most previous studies focued on the case of audio-viusual speech where people combine cues from speech and facial features, this work explored the case of identifying an ambiguous word when the available multimodal cues are speech and the visual referent.
+While most previous studies focused on the case of audio-visual speech where people combine cues from speech and facial features, this work explored the case of identifying an ambiguous word when the available multimodal cues are speech and the visual referent.
 More specifically, we conducted an ideal observer analysis of the task whereby a model provided predictions about how information from each modality should be combined in an optimal fashion.
@@
 In all Experiments, we found many patterns of optimal behaviour.
-Quantitatively speaking, the optimal model accounted, respectively, for `r 100*R2_optimal_1`%, `r 100*R2_optimal_2`%, and `r 100*R2_optimal_3`% of the variance in the mean responses.
+Quantitatively speaking, the optimal model accounted, respectively, for `r 100*R2_optimal_1`%, `r 100*R2_optimal_2`%, and `r 100*R2_optimal_3`% of the variance in mean responses.
 When compared to the predictions of the visual or the auditory models, participants generally relied on both modalities to make their decisions in the bimodal condition.
@@
 In Experiment 1, which did not involve background noise, participants not only relied on both modalities, but generally weighted these modalities according to the prediction of the optimal model, that is, according to their relative reliability.
-At the indiviual level, however, we found evidence of a between-subject variation: Some particiapnts relied slighly more on the visual modality, whereas others relied slighly more on the auditory modality.
+At the individual level, however, we found evidence of a between-subject variation: Some participants relied slighly more on the visual modality, whereas others relied slighly more on the auditory modality.
 
@@
 This means that participants responded slightly more randomly in the bimodal condition than they did in the unimodal conditions.
-This finding contrasts with research on optimal multisensory integration where associations tend to lead to a higher precision [e.g., @ernst02].
+This finding contrasts with research on  multisensory integration where associations tend to lead to a higher precision [e.g., @ernst02].
 Nevertheless, there is a crucial difference between these two situations.
-Research on optimal multisensory integration (of which audio-visual speech is arguably an instance) deals with redundant multimodal cues, and these cues are integrated into a unified percept.
+Research on  multisensory integration (of which audio-visual speech is arguably an instance) deals with redundant multimodal cues, and these cues are integrated into a unified percept.
 In contrast, the word-referent association is usually arbitrary and, in particular, the cues are not expected to be correlated perceptually.
@@
 Indeed, there is evidence that cognitive load has a detrimental effect on word recognition, which can be due to a reduction in perceptual acuity [@mattys11].
-Similar to our finding, previous experimental studies reported that in both children and adults, identifing new ambiguous form-referent mappings is usually associated with what appears to be a decrease in speech perception acuity [@stager1997; @pajak2016].
+Similar to our finding, previous experimental studies reported that in both children and adults, identifying new ambiguous form-referent mappings is usually associated with what appears to be a decrease in speech perception acuity [@stager1997; @pajak2016].
 @hofer2017 provided a probabilistic model of this phenomenon, which they similarly characterized as an increase in the noise variance of the auditory modality.
-Our finding replicates this previously documented fact, and additionaly suggests that the reduction in percetual acuity occurs simultaneousely in both the auditory and the visual modalities.
+Our finding replicates this previously documented fact, and additionally suggests that the reduction in perceptual acuity occurs simultaneously in both the auditory and the visual modalities.
 
@@
 However, and generally speaking, these studies do not differentiate between an optimal compensatory strategy (i.e., relying more on the alternative source while using all information still available in the distorted signal), and a sub-optimal strategy (i.e., relying more on the alternative source while ignoring at least some of the information still available in the distorted signal).
-The formal appraoch followed in this paper allowed us to tease apart these two possibilities, and the analysis supports the sub-optimal compensatory strategy: The preference for the non-noisy modality is above and beyond what can be explained by the relative reliability alone, meaning that the participant tend ignore at least part of the information still avialable in the noisy modality.
+The formal approach followed in this paper allowed us to tease apart these two possibilities, and the analysis supports the sub-optimal compensatory strategy: The preference for the non-noisy modality is above and beyond what can be explained by the relative reliability alone, meaning that the participant tend to ignore at least part of the information still available in the noisy modality.
 
@@
 For example, upon hearing a noisy instance of "bee", adults may have to decide whether the speaker intended to say "pea" or "bee", but children can additionally be uncertain whether "bee" is a different word from "pee" (as opposed to, say, a valid within category variation), especially if these similar sounding words are newly learned [@stager1997; @Merriman91; @Creel2012; @Swingley2016; @white2008b].
-Though new word form representation can be shown to be differetnited under some circumstances [e.g., @yoshida2009], this differentition is still not mature enough and is probably noisier than the adult-like representation and/or encoded with lower confidence [see @Swingley2007].
+Though new word form representation can be shown to be differentiated under some circumstances [e.g., @yoshida2009], this differentiation is still not mature enough and is probably noisier than the adult-like representation and/or encoded with lower confidence [see @Swingley2007].
 
@@
 For example, upon seeing a bee in a foggy weather, adults may be uncertain if they saw a bee or a fly.
-But on top of this perceptual uncerainty, children may not be certain if the semantic categoy being named is that of bees and only bees, or if it includes other small flying insects like flies and beetles.
-In fact,  though children can be fast at learning a first approximation of a given word's referent [@carey1978b], the refinement of this early approximantion into a mature semantic category is a slow and gradual process [see also @bion2013;; @carey2010; @fernald2006; @mcmurray2012].
+But on top of this perceptual uncertainty, children may not be certain if the semantic category being named is that of bees and only bees, or if it includes other small flying insects like flies and beetles.
+In fact,  though children can be fast at learning a first approximation of a given word's referent [@carey1978b], the refinement of this early approximation into a mature semantic category is a slow and gradual process [see also @bion2013;; @carey2010; @fernald2006; @mcmurray2012].
 Among other things, children have to enrich this early representation with new features, and revise its extension in the light of new referential exposures.
 
-A multi-modal cue combination strategy might help children not only recognize an individual word instance, but also refine the underlying phonological and semantic representations in the process.
+Thus, uncertainty in the representation associated with one modality (e.g., a bee and a fly) can be mitigated through the possibly more differentiated representations associated with the other modality (e.g., the sound "bee" is acoustically different from the sound "fly").
+That being said, a multi-modal cue combination strategy might help children not only recognize an individual word instance, but also refine the underlying phonological and semantic representations in the process.
 Previous research in early word learning has---whether implicitly or explicitly---largely treated the process of learning form and of learning meaning as independent.
@@
 To our knowledge, this is the first study that performs an ideal observer analysis of this task.
-We found people to be optimal in their cue combination: They weighted each modality according to its relative reliability.
+We found people to be near optimal in their cue combination: They weighted each modality according to its relative reliability.
 However, they also showed patterns of sub-optimality especially when the stimuli were perturbed with additional background noise.
@@
 
-When putting all these terms tegether, we the get this final expression for the posterori:
+When putting all these terms together, we the get this final expression for the posterior:
 $$p(W_2 | w)=\frac{1}{1+(1+\epsilon)\exp(\beta_0+\beta_aa+\beta_vv)}$$

### 2018-02-24 Writeup/ms.tex
second draft journal write-up

--- 2017-10-23 Writeup/ms.Rmd
@@
----
-title             : "Word Identification Under Multimodal Uncertainty"
-shorttitle        : "Word Identification Under Multimodal Uncertainty"
-
-author: 
-  - name          : "Abdellah Fourtassi"
-    affiliation   : "1"
-    corresponding : yes    # Define only one corresponding author
-    address       : "Postal address"
-    email         : "afourtas@stanford.edu"
-  - name          : "Michael C. Frank"
-    affiliation   : "1"
-
-affiliation:
-  - id            : "1"
-    institution   : "Department of Psychoogy, Stanford University"
-
-author_note: |
-
+\documentclass[english,man]{apa6}
+
+\usepackage{amssymb,amsmath}
+\usepackage{ifxetex,ifluatex}
+\usepackage{fixltx2e} % provides \textsubscript
+\ifnum 0\ifxetex 1\fi\ifluatex 1\fi=0 % if pdftex
+  \usepackage[T1]{fontenc}
+  \usepackage[utf8]{inputenc}
+\else % if luatex or xelatex
+  \ifxetex
+    \usepackage{mathspec}
+    \usepackage{xltxtra,xunicode}
+  \else
+    \usepackage{fontspec}
+  \fi
+  \defaultfontfeatures{Mapping=tex-text,Scale=MatchLowercase}
+  \newcommand{\euro}{€}
+\fi
+% use upquote if available, for straight quotes in verbatim environments
+\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
+% use microtype if available
+\IfFileExists{microtype.sty}{\usepackage{microtype}}{}
+
+% Table formatting
+\usepackage{longtable, booktabs}
+\usepackage{lscape}
+% \usepackage[counterclockwise]{rotating}   % Landscape page setup for large tables
+\usepackage{multirow}		% Table styling
+\usepackage{tabularx}		% Control Column width
+\usepackage[flushleft]{threeparttable}	% Allows for three part tables with a specified notes section
+\usepackage{threeparttablex}            % Lets threeparttable work with longtable
+
+% Create new environments so endfloat can handle them
+% \newenvironment{ltable}
+%   {\begin{landscape}\begin{center}\begin{threeparttable}}
+%   {\end{threeparttable}\end{center}\end{landscape}}
+
+\newenvironment{lltable}
+  {\begin{landscape}\begin{center}\begin{ThreePartTable}}
+  {\end{ThreePartTable}\end{center}\end{landscape}}
+
+  \usepackage{ifthen} % Only add declarations when endfloat package is loaded
+  \ifthenelse{\equal{\string man}{\string man}}{%
+   \DeclareDelayedFloatFlavor{ThreePartTable}{table} % Make endfloat play with longtable
+   % \DeclareDelayedFloatFlavor{ltable}{table} % Make endfloat play with lscape
+   \DeclareDelayedFloatFlavor{lltable}{table} % Make endfloat play with lscape & longtable
+  }{}%
+
+% The following enables adjusting longtable caption width to table width
+% Solution found at http://golatex.de/longtable-mit-caption-so-breit-wie-die-tabelle-t15767.html
+\makeatletter
+\newcommand\LastLTentrywidth{1em}
+\newlength\longtablewidth
+\setlength{\longtablewidth}{1in}
+\newcommand\getlongtablewidth{%
+ \begingroup
+  \ifcsname LT@\roman{LT@tables}\endcsname
+  \global\longtablewidth=0pt
+  \renewcommand\LT@entry[2]{\global\advance\longtablewidth by ##2\relax\gdef\LastLTentrywidth{##2}}%
+  \@nameuse{LT@\roman{LT@tables}}%
+  \fi
+\endgroup}
+
+\ifxetex
+  \usepackage[setpagesize=false, % page size defined by xetex
+              unicode=false, % unicode breaks when used with xetex
+              xetex]{hyperref}
+\else
+  \usepackage[unicode=true]{hyperref}
+\fi
+\hypersetup{breaklinks=true,
+            pdfauthor={},
+            pdftitle={Word-Referent Identification Under Multimodal Uncertainty},
+            colorlinks=true,
+            citecolor=blue,
+            urlcolor=blue,
+            linkcolor=black,
+            pdfborder={0 0 0}}
+\urlstyle{same}  % don't use monospace font for urls
+
+\setlength{\parindent}{0pt}
+%\setlength{\parskip}{0pt plus 0pt minus 0pt}
+
+\setlength{\emergencystretch}{3em}  % prevent overfull lines
+
+\ifxetex
+  \usepackage{polyglossia}
+  \setmainlanguage{}
+\else
+  \usepackage[english]{babel}
+\fi
+
+% Manuscript styling
+\captionsetup{font=singlespacing,justification=justified}
+\usepackage{csquotes}
+\usepackage{upgreek}
+
+ % Line numbering
+  \usepackage{lineno}
+  \linenumbers
+
+\usepackage{tikz} % Variable definition to generate author note
+
+% fix for \tightlist problem in pandoc 1.14
+\providecommand{\tightlist}{%
+  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}
+
+% Essential manuscript parts
+  \title{Word-Referent Identification Under Multimodal Uncertainty}
+
+  \shorttitle{Word Identification Under Multimodal Uncertainty}
+
+  \author{Abdellah Fourtassi\textsuperscript{1}~\& Michael C. Frank\textsuperscript{1}}
+
+  % \def\affdep{{"", ""}}%
+  % \def\affcity{{"", ""}}%
+
+  \affiliation{
+    \vspace{0.5cm}
+          \textsuperscript{1} Department of Psychology, Stanford University  }
+
+  \authornote{
     Abdellah Fourtassi
 
-  Deprtment of Psychology
-
-  Stanford Univerisity
+    Department of Psychology
+
+    Stanford University
 
@@
 
-abstract: |
-  Identifying the visual referent of a spoken word -- that a particular insect is referred to by the word ``bee'' -- requires both the ability to process and integrate multimodal input and the ability to reason under uncertainty.
-How do these tasks interact with one another?
-We introduce a task that allows us to examine how adults identify words under joint uncertainty in the auditory and visual modalities.
-We propose an ideal observer model of the task which provides an optimal account of how auditory and visual cues are combined.
-Model predictions are tested in three experiments where word recognition is made under two kinds of uncertainty: category ambiguity and/or distorting noise.
-In all cases, the optimal model explains much of the variance in human judgments.
-In particular, when the signal was not distorted with noise, participants weighted the auditory and visual cues optimally, that is, according to the relative reliability of each modality.
-But when one modality had noise added to it, human perceivers systematically preferred the unperturbed modality to a greater extent than the optimal model did.
-We discuss the broad implications of the results, especially in relation to early language acuquisition.
-
-keywords          : "Language; audio-visual processing; word learning; speech perception; computational modeling."
-
-wordcount         : "X"
-
-bibliography      : ["references.bib"]
-
-figsintext        : no
-figurelist        : no
-tablelist         : no
-footnotelist      : no
-lineno            : yes
-
-lang              : "english"
-class             : "man"
-output            : papaja::apa6_pdf
----
-
-```{r load_packages, include = FALSE}
-library("papaja")
-library(readr)
-library(tidyr)
-library(ggplot2)
-library(cowplot)
-library(knitr)
-library(boot)
-library(dplyr)
-library(langcog)
-theme_set(theme_bw())
-```
-
-```{r}
-
-#Data from the 3 experiments 
-#############################
-exp1 <- read_delim("../Data_and_analysis/data_exp1_Anonym.txt", delim = " ") %>%
-  filter(type == "Task") %>%
-  mutate(experiment='Experiment1')
-
-exp2 <- read_delim("../Data_and_analysis/data_exp2_Anonym.txt", delim = " ") %>%
-  filter(type == "Task") %>%
-  mutate(experiment='Experiment2')
-
-exp3 <- read_delim("../Data_and_analysis/data_exp3_Anonym.txt", delim = " ") %>%
-  filter(type == "Task") %>%
-  mutate(experiment='Experiment3')
-```
-
-```{r}
-#First deal with all data
-```
-
-```{r}
-#First Exlusion criteria:
-#############################
-
-#All data
-N_all_1 <- exp1 %>%
-  distinct(ID) %>%
-  nrow()
-
-N_all_2 <- exp2 %>%
-  distinct(ID) %>%
-  nrow()
-
-N_all_3 <- exp3 %>%
-  distinct(ID) %>%
-  nrow()
-
-#Filter who took the experiment more than once
-
-#Exp1
- token_data_1 <- exp1 %>%
-   group_by(ID) %>%
-   dplyr::summarise(N_tokens=n())
-
- N_twice_1 <- token_data_1 %>%
-   filter(N_tokens > 70) %>%
-   nrow()
-
- exp1_once <- exp1 %>%
-   left_join(token_data_1) %>%
-   filter(N_tokens == 70) #every subject is supposed to produce exactly 70 tokens
-
- #Exp2
-token_data_2 <- exp2 %>%
-   group_by(ID) %>%
-   dplyr::summarise(N_tokens=n())
-
- N_twice_2 <- token_data_2 %>%
-   filter(N_tokens > 70) %>%
-   nrow()
-
- exp2_once <- exp2 %>%
-   left_join(token_data_2) %>%
-   filter(N_tokens == 70)
-
- #Exp3
-token_data_3 <- exp3 %>%
-   group_by(ID) %>%
-   dplyr::summarise(N_tokens=n())
-
- N_twice_3 <- token_data_3 %>%
-   filter(N_tokens > 70) %>%
-   nrow()
-
- exp3_once <- exp3 %>%
-   left_join(token_data_3) %>%
-   filter(N_tokens == 70)
-
-#Participants who did not encounter a technical problem with the online experiment
-
-#Exp1
-exp1_noProb <- exp1_once %>%
-  filter(problem=="No")
-
-N_noProb_1 <- exp1_noProb %>%
-  distinct(ID) %>%
-  nrow()
-
-#Exp2
-exp2_noProb <- exp2_once %>%
-  filter(problem=="No")
-
-N_noProb_2 <- exp2_noProb %>%
-  distinct(ID) %>%
-  nrow()
-
-#Exp3
-exp3_noProb <- exp3_once %>%
-  filter(problem=="No")
-
-N_noProb_3 <- exp3_noProb %>%
-  distinct(ID) %>%
-  nrow()
-
-#Participants who who did not encounter a problem AND were above 50% accuracy on obvious trials
-
-#Exp1
-exp1_good <- exp1_noProb %>%
-  filter(score > 0.5)
-
-N_good_1 <- exp1_good %>%
-  distinct(ID) %>%
-  nrow()
-
-#Exp2
-exp2_good <- exp2_noProb %>%
-  filter(score > 0.5)
-
-N_good_2 <- exp2_good %>%
-  distinct(ID) %>%
-  nrow()
-
-#Exp3
-exp3_good <- exp3_noProb %>%
-  filter(score > 0.5)
-
-N_good_3 <- exp3_good %>%
-  distinct(ID) %>%
-  nrow()
-
-```
-
-```{r}
-
-#Data subseting
-
-#Experiment 1
-##############
-
-sound_all_exp1 <- exp1_good %>%
-    filter(condition == "sound")
-
-concept_all_exp1 <- exp1_good %>%
-    filter(condition == "concept")
-
-joint_all_exp1 <- exp1_good %>%
-    filter(condition == "joint")
-
-#Summary
-sounds_exp1 <- exp1_good %>%
-  filter(condition == "sound") %>%
-  group_by(sound_dist) %>%
-  #multi_boot_standard(col = "answer")
-  summarise(mean = mean(answer)) %>%
-  mutate(Experiment="Experiment 1", 
-         Condition="Auditory") %>%
-  rename(distance = sound_dist)
-
-concepts_exp1 <- exp1_good %>%
-  filter(condition == "concept") %>%
-  group_by(concept_dist) %>%
-  #multi_boot_standard(col = "answer")
-  summarise(mean = mean(answer)) %>%
-  mutate(Experiment="Experiment 1", 
-         Condition="Visual") %>%
-  rename(distance = concept_dist)
-
-joint_exp1 <- exp1_good %>%
-  filter(condition == "joint") %>%
-  group_by(concept_dist, sound_dist) %>%
-  #multi_boot_standard(col = "answer")
-  summarise(mean = mean(answer)) %>%
-  mutate(Experiment="Experiment 1", 
-         Condition="Joint")
-
-#Experiment2
-############
-
-sound_all_exp2 <- exp2_good %>%
-    filter(condition == "sound")
-
-concept_all_exp2 <- exp2_good %>%
-    filter(condition == "concept")
-
-joint_all_exp2 <- exp2_good %>%
-    filter(condition == "joint")
-
-#Summary
-sounds_exp2 <- exp2_good %>%
-  filter(condition == "sound") %>%
-  group_by(sound_dist) %>%
-  #multi_boot_standard(col = "answer")
-  summarise(mean = mean(answer)) %>%
-  mutate(Experiment="Experiment 2", 
-         Condition="Auditory") %>%
-  rename(distance = sound_dist)
-
-concepts_exp2 <- exp2_good %>%
-  filter(condition == "concept") %>%
-  group_by(concept_dist) %>%
-  #multi_boot_standard(col = "answer")
-  summarise(mean = mean(answer)) %>%
-  mutate(Experiment="Experiment 2", 
-         Condition="Visual") %>%
-  rename(distance = concept_dist)
-
-joint_exp2 <- exp2_good %>%
-  filter(condition == "joint") %>%
-  group_by(concept_dist, sound_dist) %>%
-  #multi_boot_standard(col = "answer")
-  summarise(mean = mean(answer)) %>%
-  mutate(Experiment="Experiment 2", 
-         Condition="Joint")
-
-#Experiment3
-############
-
-sound_all_exp3 <- exp3_good %>%
-    filter(condition == "sound")
-
-concept_all_exp3 <- exp3_good %>%
-    filter(condition == "concept")
-
-joint_all_exp3 <- exp3_good %>%
-    filter(condition == "joint")
-
-#Summary
-sounds_exp3 <- exp3_good %>%
-  filter(condition == "sound") %>%
-  group_by(sound_dist) %>%
-  #multi_boot_standard(col = "answer")
-  summarise(mean = mean(answer)) %>%
-  mutate(Experiment="Experiment 3", 
-         Condition="Auditory") %>%
-  rename(distance = sound_dist)
-
-concepts_exp3 <- exp3_good %>%
-  filter(condition == "concept") %>%
-  group_by(concept_dist) %>%
-  #multi_boot_standard(col = "answer")
-  summarise(mean = mean(answer)) %>%
-  mutate(Experiment="Experiment 3", 
-         Condition="Visual") %>%
-  rename(distance = concept_dist)
-
-joint_exp3 <- exp3_good %>%
-  filter(condition == "joint") %>%
-  group_by(concept_dist, sound_dist) %>%
-  #multi_boot_standard(col = "answer")
-  summarise(mean = mean(answer)) %>%
-  mutate(Experiment="Experiment 3", 
-         Condition="Joint")
-
-exp_uni_data <- bind_rows(sounds_exp1, concepts_exp1,
-                     sounds_exp2, concepts_exp2,
-                     sounds_exp3, concepts_exp3)
-
-```
-
-Language uses symbols expressed in one modality (e.g., the auditory modality, in the case of speech) to communicate about the world, which we perceive through many different sensory modalities.
-Consider hearing someone yell "bee!" at a picnic, as a honey bee buzzes around the food.
-Determining reference involves processing the auditory information and linking it with other perceptual signals (e.g., the visual image of the bee, the sound of its wings, the sensation of the bee flying by your arm).
-
-This multimodal integration task takes place in a noisy world.
-On the auditory side, individual acoustic word tokens are almost always ambiguous with respect to the particular sequence of phonemes they represent, which is due to the inherent variability of how a phonetic category is realized acoustically [@hillenbrand1995].
-And some tokens may be distorted additionally by mispronunciation or ambient noise.
-Perhaps the speaker was yelling "pea" and not "bee".
-Similarly, a sensory impression may not be enough to make a definitive identification of a visual category.\footnote{In the general case, language can of course be visual as well as auditory, and object identification can be done through many modalities.
-For simplicity, we focus on audio-visual matching here.} Perhaps the insect was a beetle or a fly instead.
-
-How does the brain deal with uncertainty to process and understand language?
-Previous research showed that the brain encodes speech cues probabilistically, in a way that mirrors the inherent noise/ambiguity in the input.
-From this probabilistic representation, the brain tends to make the statistically optimal judgement about the identity of the intended categories [e.g., @clayard08; @feldman2009].
-Previous work in this line of research has largely focused on testing optimal inference using cues from the auditory modality.
-A few studies did explore some aspects of audio-visual processing in a probabilistic framework [@bejjanki2011; @kleinschmidt2015].
-These studies focused on the case of audio-visual speech perception, that is, recognizing speech categories using cues from the auditory signal accompagnied with lip movements.
-To our knowledge, however, no study explored whether word recogniton is statistially optimal in a *referential* context, that is, when the brain has to combine cues from the sound and the meaning/referent.
-Imagine, for example, that someone is uncertain whether they heard "pea" or "bee", does it make them rely more on the referent (e.g., the object being pointed at)?
-Vice versa, if they are not sure if they saw a bee or a fly, does that make them rely more on the sound?
-More importantly, when input in both modalities is uncertain to varying degrees, do they weight each modality according to its relative reliability, or do they over-rely on a particular modality?
-
-Outside the realm of language per se, research on multisensory integration suggests that the brain integrates information from different modalities in a statistically optimal way, that is, the integration results in a higher overall precision, and modalities are weighed according to their relative reliability [@ernst02].
-However, it is not a priori obvious whether this finding can be extended to word-referent recognition under multimodal uncertainty.
-Indeed, there seems to be at least two fundamental differences between these two cases, and both can influence the cue combination strategy.
-
-First, in the case of optimal multisensory integration, modalities are understood to differ only in terms of their reliability.
-In a referential conext, however, modalities also differ in terms of their roles in the referential process: the auditory input represents the symbol (i.e., the word) whereas the visual input represents the referent.
-It has been suggested that because of the referential property of speech, it is a privileged signal for humans from infancy [see @vouloumanos2014 for a review].
-Thus, it is possible that the brain does not treat the auditory and visual modalities as equivalent sources of information.
-Instead, there could be a bias for the auditory modality beyond what is expected from informational reliability alone.
-
-Second, research on optimal multisensory integration typically deals with multisensory associations that are supposed to be *redundant*.
-An example of such integration is when we determine the size of an object using the visual and haptic modalities [@ernst02], or when we determe the spacial location of a stimulus using the visual and the auditory modalities [@alais04].
-In the case of language, however, the multimodal input is rather *arbitrary* [@saussure1916].
-For instance, there is no logical connection between the sound "bee" and the corresponding insect.
-Moreover, variation in the way the sound "bee" is pronounced does not correlate perceptually with variation in the shape (or any other visual property) in the category of bees.
-It turns out the nature of the multi-modal associations (redundant vs.
-arbitrary) influences the quality of multi-modal processing in both children and adults: the processing and integration is easier in the case of redundant input, than it in the case of arbitrary input [see @robinson2010 for a review].
-Thus, there is a priori no obvious reason multimodal cue combination in the case of arbitrary assoiations (such as the case of word-referent) should be optimal in the same way redundant associations are.
-For instance, the former is more likely to show patterns of sub-optimality.
-
-<!--
-
-TRY TO CONTRAST TWO THINGS: WORK ON PERCEPTUAL INTEGRATION WHEN THERE IS CORRELATION AND WORK OF AUDIO-VISUAL ENCODING OF ARBITRARY ASSOCIATIONS, SHOW THAT THE FIRST IS NOT ARBIRARY, AND MOSTY CONTINUOUS (ANS PRODUCE OPTIMALITY), THE SECOND DOES NOT INVOVLE CATEGORIES OR A SEMANTIC CONTEX, WHERE A WORD REFER TO AN OBJECT, INSTEAD OF BEING JUST ARBITRARY (AND PRODUCE HINDRANCE AND SUB-OPTIMALITY).
-THUS OUR WORK TRIES TO DEAL WITH CASE
-
-A few studies have explored some aspects of audio-visual processing in a probabilistic framework  [e.g., @bejjanki2011; @kleinschmidt2015].
-In these studies, the researchers focused on the specific case of audio-visual speech  where information is *redundant* across modalities.
-In the present work, we study the case of word reference where the audio-visual associations are usually *arbitrary* (Cite Saussure).
-For instance, whereas in the case of audio-visual speech, the sound "bee" and the corresponding lip movements are supposed to merge into a unified percept, there is nothing in the sound "bee" or in the way it can be pronounced, that correlates perceptually with the shape (or some other visual property) of the insect.
-
-More generally, we know that the nature of the multi-modal associations (redundant vs.
-arbitrary) influences the quality of the processing in both children and adults [see @robinson2010 for a review].
-In the case of redundant multimodal information (e.g.
-determining the size of an object through the visual and haptic modality), the sensory integration is often statistically optimal (Ernst and Banks, 2002).
-Optimality in this context means two things: first, the precision of the bimodal estimate increases compared to the unimodal estimates, and second, the cues from different modalities are combined according to their relative reliability.
-In the case of arbitrary associations, empirical studies suggest, rather, sub-optimality.
-In fact, processing of the bimodal input does not increase the precision, it tends to hinder performance instead (Sloutsky, Palmer, Stager, ...
-I should dig into the literature on the arbitrary associations).
-Moreover, modalities are not optimally weighted according to their reliability, instead, one modality dominates the other depending on the task, e.g., Sloutsky et al.
-reported auditory dominance (for kids) and then prefernce for adults (..), and Colovita et al.
-reported visual dominance for adults.
-
--->
-
-In this paper, we studied the mechanism of processing/combination of audiovisual cues in a referential context, under multiple sources of uncertainty.
-More precisely, we tested if the cue combination was statistically optimal.
-Besides, we quantified any sub-optimality that might have been induced, among other things, by the suggested privileged status of speech or by the arbitrariness of the referential associations.
-To test optimality, we characterized uncertainty in each modality with a probability distribution, and we predicted responses by combining these probabilities in an optimal way.
-To study possible patterns of sub-optimality, we compared the optimal model to a descriptive model where the parameters of the bimodal probability distributions were fitted to human judgements.
-We tested the model's predictions in three behavioral experiments where we varied the source of uncertainty.
-In Experiment 1, audio-visual tokens were ambiguous with respect to their category membership.
-In Experiment 2, we intervened by adding background noise to the auditory modality, and in Experiment 3, we intervened by adding background noise to the visual modality.
-In all Experiments, participants were quantitatively near-optimal, though precision dropped slightly in the bimodal condition.
-Moreover, in Experiment 1 where neither of the modalities was perturbed with background noise, participants weighed auditory and visual cues according to the relative reliability predicted by the optimal model.
-In other words, we found no evidence for a modality bias towards either the auditory or the visual modality.
-However, In Experiment 2 and 3, participants over-relied on one modality when the other modality was perturbed with additional noise.
-Finally, we discuss the broad implications of these results, especially in relation to some developmental findings in early word learning [e.g., @stager1997].
-
-# Model
-
-In this section we describe the multimodal integration model.
-First, we briefly introduce the experimental paradigm, and second we explain how this paradigm can be modeled in a probabilistic framework.
-
-## The Audio-Visual Word Recognition Task
-
-We introduce a new task that tests word recognition in a referential context.
-We use two visual categories (cat and dog) and two auditory categories (/b/ and /d/ embedded in the minimal pair /aba/-/ada/).
-For each participant, an arbitrary pairing is set between the auditory and the visual categories, leading to two audio-visual word categories (e.g., dog-/aba/, cat-/ada/).
-
-In each trial, participants are presented with an audio-visual target (the prototype of the target category), immediately followed by an audio-visual test stimulus (Figure\ \@ref(fig:task)).
-The test stimulus may differ from the target in both the auditory and the visual components.
-After these two presentations, participants press "same" or "different".
-
-```{r task, fig.cap = "Overview of the task.
+    Correspondence concerning this article should be addressed to Abdellah
+    Fourtassi, Postal address. E-mail:
+    \href{mailto:afourtas@stanford.edu}{\nolinkurl{afourtas@stanford.edu}}
+  }
+
+  \abstract{Identifying a spoken word in a referential context requires both the
+ability to process and integrate multimodal input and the ability to
+reason under uncertainty. How do these tasks interact with one another?
+We introduce a task that allows us to examine how adults identify words
+under joint uncertainty in the auditory and visual modalities. We
+propose an ideal observer model of the task which provides an account of
+how auditory and visual cues are combined optimally. Model predictions
+are tested in three experiments where word recognition is made under two
+kinds of uncertainty: category ambiguity and/or distorting noise. In all
+cases, the optimal model explains much of the variance in human mean
+judgments. In particular, when the signal is not distorted with noise,
+participants weight the auditory and visual cues optimally, that is,
+according to the relative reliability of each modality. But when one
+modality has noise added to it, human perceivers systematically prefer
+the unperturbed modality to a greater extent than the optimal model
+does. The study provides a formal framework which helps us understand
+precisely how word form and word meaning interact in word recognition
+under uncertainty. Moreover it offers a first step towards a model that
+accounts for form-meaning synergy in early word learning.}
+  \keywords{Language understanding; audio-visual processing; word learning; speech
+perception; computational modeling. \\
+
+    \indent Word count: X
+  }
+
+  \usepackage[sortcites=false,sorting=none]{biblatex}
+
+\usepackage{amsthm}
+\newtheorem{theorem}{Theorem}
+\newtheorem{lemma}{Lemma}
+\theoremstyle{definition}
+\newtheorem{definition}{Definition}
+\newtheorem{corollary}{Corollary}
+\newtheorem{proposition}{Proposition}
+\theoremstyle{definition}
+\newtheorem{example}{Example}
+\theoremstyle{definition}
+\newtheorem{exercise}{Exercise}
+\theoremstyle{remark}
+\newtheorem*{remark}{Remark}
+\newtheorem*{solution}{Solution}
+\begin{document}
+
+\maketitle
+
+\setcounter{secnumdepth}{0}
+
+Language uses symbols expressed in one modality (e.g., the auditory
+modality, in the case of speech) to communicate about the world, which
+we perceive through many different sensory modalities. Consider hearing
+someone yell \enquote{bee!} at a picnic, as a honey bee buzzes around
+the food. Identifying a word involves processing the auditory
+information as well as other perceptual signals (e.g., the visual image
+of the bee, the sound of its wings, the sensation of the bee flying by
+your arm). A word is successfully identified when information from these
+modalities provide convergent evidence. However, word identification
+takes place in a noisy world, and the cues received through each
+modality may not provide a definitive answer. On the auditory side,
+individual acoustic word tokens are almost always ambiguous with respect
+to the particular sequence of phonemes they represent, which is due to
+the inherent variability of how a phonetic category is realized
+acoustically (Hillenbrand, Getty, Clark, \& Wheeler, 1995). And some
+tokens may be distorted additionally by mispronunciation or ambient
+noise. Perhaps the speaker was yelling \enquote{pea} and not
+\enquote{bee}. Similarly, a sensory impression may not be enough to make
+a definitive identification of a visual
+category.\footnote{In the general case, language can of course be visual as well as auditory, and object identification can be done through many modalities.
+For simplicity, we focus on audio-visual matching here.}
+Perhaps the insect was a beetle or a fly instead.
+
+How does the mind deal with uncertainty to identify the speaker's
+intended word? To address this question, many researchers in recent
+years have adopted the rational approach to cognition (Anderson, 1990),
+which corresponds to Marr's computational level of analysis. This
+approach has had a tremendous impact not only on speech related research
+(Clayards, Tanenhaus, Aslin, \& Jacobs, 2008; Feldman, Griffiths, \&
+Morgan, 2009; Kleinschmidt \& Jaeger, 2015; Norris \& McQueen, 2008),
+but also on many other disciplines in the cognitive sciences (for
+reviews, see Chater \& Manning, 2006; Knill \& Pouget, 2004; Tenenbaum,
+Kemp, Griffiths, \& Goodman, 2011). Within this framework, researchers
+typically consider an \enquote{ideal observer} model which provides a
+characterization of the task/goal and shows what the optimal performance
+should be under this characterization. When there is uncertainty in the
+input, the ideal observer performs an optimal probabilistic inference.
+For example, in order to recognize an ambiguous linguistic input, the
+model uses all available probabilistic knowledge in order to maximize
+the accuracy of this recognition. Thus, when the task is well specified,
+the ideal observer model can be seen as a theoretical upper limit on
+performance. It is often used, not so much as a realistic model of human
+performance, as much as a baseline against which human performance can
+be compared (Geisler, 2003). When there is a deviation from the ideal,
+this can reveal extra constraints on human cognition, such as
+limitations on working memory or attentional resources.
+
+In this line of research, Clayards et al. (2008) simulated auditory
+uncertainty by manipulating the probability distribution of a cue (VOT)
+that differentiated similar words (e.g., \enquote{beach} and
+\enquote{peach}). They found that humans were sensitive to these
+probabilistic cues and their judgments closely reflected the optimal
+predictions. In another work, Feldman et al. (2009) studied the
+perceptual magnet effect, which is related to how categories influence
+the way the stimuli are perceived. They showed that this effect can be
+explained as the consequence of optimally solving the problem of
+perception under uncertainty. Both studies explored optimal performance
+under uncertainty from one modality, i.e., the auditory modality. There
+is however extensive evidence that information from the visual modality,
+in particular the speaker's facial features, influences the perception
+of auditory information (see Campbell, 2008 for a review). Bejjanki,
+Clayards, Knill, and Aslin (2011) offered a mathematical
+characterization of how cues from speech and lip movements can be
+optimally combined and showed that human performance during audio-visual
+phonemic labeling was consistent (at least at the qualitative level)
+with the behavior of the ideal observer.
+
+The speaker's facial features are not the only visual information that
+can be used to disambiguate the auditory input, however. For instance,
+in a referential context, information about the identity of the semantic
+referent can be integrated with linguistic information to resolve
+lexical and syntactic ambiguities in speech (e.g., Eberhard,
+Spivey-Knowlton, Sedivy, \& Tanenhaus, 1995; Spivey, Tanenhaus,
+Eberhard, \& Sedivy, 2002; Tanenhaus, Spivey-Knowlton, Eberhard, \&
+Sedivy, 1995). To our knowledge, however, no study offered an ideal
+observer analysis of word identification in such context, that is, when
+the mind has to combine cues from the sound and the referent. Imagine,
+for example, that someone is uncertain whether they heard \enquote{pea}
+or \enquote{bee}, does this uncertainty make them rely more on the
+referent (e.g., the object being pointed at)? Vice versa, if they are
+not sure if they saw a bee or a fly, does it make them rely more on the
+sound? More importantly, when input in both modalities is uncertain to
+varying degrees, do they weight each modality according to its relative
+reliability (which is the optimal strategy), or do they over-rely on a
+particular modality (which is a sub-optimal strategy)?
+
+The visual information provided by the referent is arguably different
+from the visual information provided by the speaker's facial features
+(such as lip movements). There seems to be at least two fundamental
+differences between these two cases, and both can influence the cue
+combination strategy:
+
+First, in the case of audio-visual speech, modalities are understood to
+differ only in terms of their reliability. In a referential context,
+however, modalities also differ in terms of their roles in the
+referential process: the auditory input represents the symbol (i.e., the
+word) whereas the visual input represents the referent. It has been
+suggested that because of its referential property, speech is a
+privileged signal for humans, starting in infancy (see Vouloumanos \&
+Waxman, 2014 for a
+review).\footnote{There is a debate over whether speech is privileged for infant and adults for the same reasons.
+Whereas Waxman and colleagues suggest that speech is privileged for both infants and adults because of its ability to refer, Sloutsky and colleagues suggest that speech might not have a referential status from the start.
+Rather, according to Sloutsky and colleagues, speech seems to be prefered by infants only because of a low level auditory "overshadowing".}
+Thus, in a referential context, it is possible that we do not treat the
+auditory and visual modalities as equivalent sources of information.
+Instead, there could be a bias for the auditory modality beyond what is
+expected from informational reliability alone.
+
+Second, in the case of audio-visual speech, the associations are
+expected to be perceptually correlated. The expectation for this
+correlation is such that when there is a mismatch between auditory and
+visual input, people still integrate them into a unified (but illusory)
+percept (McGurk \& MacDonald, 1976). In the case of referential
+language, however, the multimodal association is by nature
+\emph{arbitrary} (Greenberg, 1957; Saussure, 1916). For instance, there
+is no logical/perceptual connection between the sound \enquote{bee} and
+the corresponding insect. Moreover, variation in the way the sound
+\enquote{bee} is pronounced is generally not expected to correlate
+perceptually with variation in the shape (or any other visual property)
+in the category of bees. Thus, one could imagine that cue combination in
+the case of arbitrary audio-visual associations (word-referent) is less
+automatic, more effortful, and therefore less conducive to optimal
+integration than it is in the case of perceptually correlated
+associations (as in audio-visual speech perception).
+
+In the current study, we investigate how people combine cues from the
+auditory and the visual modality to recognize words in a referential
+context. In particular, we study how this combination is performed under
+various degrees of uncertainty in both the auditory and the visual
+modality. We perform a rational analysis of the task. First we propose
+an ideal observer model that performs the combination in an optimal
+fashion. Second we compare the predictions of the optimal model to human
+responses. Humans can deviate from the ideal for several reasons. For
+instance, as mentioned above, a sub-optimality can be induced by the
+suggested privileged status of speech or by the arbitrariness of the
+referential association. In order to study possible patterns of
+sub-optimality, we compare the optimal model (which provides a normative
+benchmark) to a descriptive model which is identical to the optimal
+model, except that the parameters in the former are fitted to human
+responses.
+
+We tested the ideal observer model's predictions in three behavioral
+experiments where we varied the source of uncertainty. In Experiment 1,
+audio-visual tokens were ambiguous with respect to their category
+membership only. In Experiment 2, we intervened by adding background
+noise to the auditory modality, and in Experiment 3, we intervened by
+adding background noise to the visual modality. In all experiments,
+participants were quantitatively near-optimal, though overall response
+precision was slightly lower than expected. Moreover, in Experiment 1
+where neither of the modalities was perturbed with background noise,
+participants weighed auditory and visual cues according to the relative
+reliability predicted by the optimal model. In other words, we found no
+evidence for a modality bias towards either the auditory or the visual
+modality. However, in Experiment 2 and 3, participants over-relied on
+one modality when the other modality was perturbed with additional
+noise.
+
+\section{Models and predictions}\label{models-and-predictions}
+
+In this section we describe the multimodal cue combination model. First,
+we briefly introduce the experimental paradigm, and second we explain
+how behavior in this paradigm can be characterized optimally with an
+ideal observer model.
+
+\subsection{The Audio-Visual Word Recognition
+Task}\label{the-audio-visual-word-recognition-task}
+
+We introduce a new task that tests word recognition in a referential
+context. We use two visual categories (cat and dog) and two auditory
+categories (/b/ and /d/ embedded in the minimal pair /aba/-/ada/). For
+each participant, an arbitrary pairing is set between the auditory and
+the visual categories, leading to two audio-visual word categories
+(e.g., dog-/aba/, cat-/ada/). In each trial, participants are presented
+with an audio-visual target (the prototype of the target category),
+immediately followed by an audio-visual test stimulus
+(Figure~\ref{fig:task}). The test stimulus may differ from the target in
+both the auditory and the visual components. After these two
+presentations, participants press \enquote{same} or \enquote{different}.
+
+\begin{figure}
+
+{\centering \includegraphics[width=400px]{pictures/task}
+
+}
+
+\caption{Overview of the task.
 In the audio-visual condition, participants are first presented with an audio-visual target (the prototype of the target category), immediately followed by an audio-visual test.
 The test may differ from the target in both the auditory and the visual components.
-After these two presentations, participants press same' (i.e., the same category as the target) or `different' (not the same category).
-The auditory-only and visual-only conditions are similar, expect only the sounds are heard, or only the pictures are shown, respectively.", fig.align = "center", out.width = "400px"}
-knitr::include_graphics("pictures/task.png", dpi = 108)
-```
-
-This itask is similar to the task introduced by @sloutsky2003.
-However, in that study, as well as subsequent ones, participants were asked whether or not the two audio-visual presentations were *identical*.
-Such task would allow us to probe audio-visual encoding, but not necessarily speech perception.
-The latter requires---in addition to the perceptual encoding---a categorical judgement, i.e, determining wheather two similar tokens are members of the same phonological/semantic category.
-Thus, our task is category-based: participants are asked to press "same" if they think the second item (the test) belonged to the same category as the first (target) (e.g.,  dog-/aba/), even if there is a slight difference in the word, in the referent, or in both.
-They are instructed to press "different" only if they think that the second stimulus was an instance of the other word category (cat-/ada/).
-
-We assume, for the sake of simplicity, that category tokens vary along a single dimension.
-Phonetic tokens are sampled from an acoustic continuum linking /aba/ to /aba/, and obtained by continuously varying the value of the second formant [@vroomen2004].
-Visual tokens are sampled from a morph continuum linking the picture of a dog and the picture of a cat [@freedman2001].
-
-The task also includes trials where pictures are hidden (audio-only) or where sounds are muted (visual-only).
-These unimodal trials provide us with participants' categorization functions for the auditory and visual categories and are used as inputs to the optimal model, described below.
-
-## Optimal Model
-
-The basis of our optimal model is that individual probabilistic representations from each modality should be combined optimally.
-First we describe how probabilistic representations in each modality are derived/fitted, and second we explain how they are combined to yield optimal predictions.
-
-### Unimodal representations
-
-In each modality, we have two categories: /ada/ ($A=1$) and /aba/ ($A=2$) in the auditory dimension, and *cat* ($V=1$) and *dog* ($V=2$) in the visual dimension.
-
-We assume the probability of membership in each category is normally distributed:
-
-$$ p(a | A) \sim  N(\mu_A, \sigma^2_A) $$
-$$ p(v | V) \sim  N(\mu_V, \sigma^2_V) $$
-The parameters of these distributions are fitted to the participants' judgement in the unimodal case, i.e., when they only hear the sounds, and when they only see the objects.
-For an ideal recognizer, the probability of choosing category 2 (that is, to answer "different") when presented with, say, an audio instance $a$, is the posterior probability of this category $p(A_2|a)$.
-If we assume that both categories have equal variances, the posterior probability reduces to:
-
-$$p(A_2 | a)=\frac{1}{1+(1+\epsilon_A)\exp(\beta_{a0}+\beta_aa)}$$
-
-with $\beta_a=\frac{\mu_{A_1}-\mu_{A_2}}{\sigma^2_{A}}$, $\beta_{a0}=\frac{\mu^2_{A_2}-\mu^2_{A_1}}{2\sigma^2_{A}}$, and $1+\epsilon_A=\frac{p(A_1)}{p(A_2)}$ is the proportion of the prior probabilities.
-If the identity of the auditory categories is randomized, and if $A_1$ is the target, then $\epsilon$ measures a response bias to "same" if $\epsilon > 0$, and a response bias to "different" if $\epsilon < 0$.
-
-We modeled the visual representation in exactly the same way.
-
-### Optimal model
-
-In the bimodal condition, participants see audio-visual tokens.
-They have to combine information from both modalities and make a categorical decision.
-How can this task be characterized in a formal way, and what would be the optimal behavior?
-Work on multisensory integration generally considers the outcome of multiplying the distributions derived from each modality [e.g., @ernst02].
-However, this way of combining multi-modal cues is more adequate to examine continuous perceptual dimensions (e.g., size).
-It is less applicable to categorical dimensions (e.g., phonemes) [see @bejjanki2011; @Bankieris17 for futher detail]
-
-<!-- more adequate to the case of redundant information, where, for instance, cues are in the same units, the same coordinates and about the same aspect of the environmental property.
-It is less adequate to describe the case of arbitrary associations where cues are in different units, coordinate systems, or about complementary aspects of the same environmental property [see @ernst04 for further detail].
--->
-
-We followed a formal approach similar in spirit to the one adopted by @bejjanki2011.
-In this approach, the bimodal optimal distribution is defined, not as the product of the unimodal distribution $p(A)$ and $p(V)$, but as their joint distribution in a higher dimensional space, which we call the audio-visual space.
-Thus, a word token is defined as a vector in this space, $w=(a,v)$, and a word category $W$ can be characterized with a bivariate normal distribution:
-$$ p(w | W) \sim  N(M_W, \Sigma_W) $$
-```{r model, fig.cap = "Illustration of the model using simulated data.
+After these two presentations, participants press `same' (i.e., the same category as the target) or `different' (not the same category).
+The auditory-only and visual-only conditions are similar to the audio-visual condition, except that only the sounds are heard, or only the pictures are shown, respectively.}\label{fig:task}
+\end{figure}
+
+This task is similar to the task introduced by Sloutsky and Napolitano
+(2003), and used in subsequent studies in both children and adults (see
+Robinson \& Sloutsky, 2010 for a review). However, in this original
+task, participants are asked whether or not the two audio-visual
+presentations are \emph{identical}. Such task would allow us to probe
+audio-visual encoding, but not necessarily language understanding. The
+latter requires---in addition to the perceptual encoding---a categorical
+judgement, i.e, determining whether or not two similar tokens are
+members of the same phonological/semantic category. Thus, our task is
+category-based: Participants are asked to press \enquote{same} if they
+think the second item (the test) belonged to the same category as the
+first (target) (e.g., dog-/aba/), even if there is a slight difference
+in the sound, in the referent, or in both. They are instructed to press
+\enquote{different} only if they think that the second stimulus was an
+instance of the other word category (cat-/ada/). The task also includes
+trials where pictures are hidden (audio-only) or where sounds are muted
+(visual-only). These unimodal trials provide us with the participants'
+evaluation of the probabilistic information present in the auditory and
+visual categories. This unimodal distributions are used as inputs to the
+optimal combination model, described below.
+
+\subsection{Optimal Model}\label{optimal-model}
+
+The ideal observer model combines probabilistic information from the
+auditory and visual modalities, and makes a categorical decision. How
+can this task be characterized in a formal way, and what would be the
+optimal behavior? If the stimuli were continuous (e.g., size, location),
+cues derived from each modality would be characterized with their
+sensory noise variance only, and (assuming conditional independence)
+their combined information would be characterized with a simple linear
+combination rule where the combined estimate is an average of the
+individual estimates, each weighted according to its relative
+reliability (Alais \& Burr, 2004; Ernst \& Banks, 2002). However, in our
+case decision is made over categorical variables (phonemes and
+concepts), the optimal model should take into account, not only the
+noise variability around an individual perceptual estimate, but also its
+categorical variability (i.e., the probability with which the estimate
+belongs to a given category).
+
+One way to account for the categorical variability is to model the
+decision step which maps sensory input onto task-dependent categories
+(Bankieris, Bejjanki, \& Aslin, 2017; Bejjanki et al., 2011). We
+represent the decision step as follows (see Figure~\ref{fig:model} for
+illustration). If we assume that both the visual and the auditory cues
+vary along a single dimension, an audio-visual signal \((a,v)\) can be
+represented as a point in this two-dimensional space, and a word
+category can be characterized with a bivariate probability distribution
+over audio-visual
+tokens.\footnote{For the sake of clarity, we assume here that the sensory noise around this point is small/negligible compared to the categorical variability.
+But see below how the noise can be integrated when its effect is relatively large}
+Each category is peaked around the most typical audio-visual token, and
+the probability of membership in the category (the likelihood
+probability) decreases gradually as the auditory token deviates from the
+typical sound instance (depending on the variance of the auditory
+category) and/or as the visual token deviates from the typical visual
+instance (depending on the variance of the visual category).
+
+A crucial feature of the ideal observer model is that it makes use of
+the entire probability distribution of a given category in order to make
+optimal decisions (e.g., Clayards et al., 2008). This means that the
+probability of picking a word (the posterior probability) should mirror
+closely the probability of the combined information (the likelihood
+probability). For instance, the model becomes less ambiguous and more
+certain as the tokens get closer to the typical instance of the
+category. In what follows, we formalize this sense of optimality using a
+Bayesian framework.
+
+An auditory category \(A\) and a visual category \(V\) are defined as
+distributions in the auditory and the visual dimensions, respectively. A
+word category \(W\) is defined as a bivariate distribution in the
+audio-visual. More specifically, we define it as the joint distribution
+of the auditory and the visual categories. For simplicity, we assume
+both auditory and visual categories to be normally distributed. That is,
+if \(w=(a,v)\) is an audio-visual token, then:
+\[ p(a | A) \sim  N(\mu_A, \sigma^2_A) \] where \(\mu_A\) and
+\(\sigma^2_A\) are respectively the mean and the variance of the
+auditory category, \[ p(v | V) \sim  N(\mu_V, \sigma^2_V) \] where
+\(\mu_V\) and \(\sigma^2_V\) are the mean and the variance of the visual
+category, and
+
+\[ p(w | W) \sim  N(M_W, \Sigma_W) \] where \(M_W=(\mu_A, \mu_V)\) and
+\(\Sigma_W\) are mean and the covariance matrix of the word category. We
+assume that auditory and visual variables are independent (i.e.,
+uncorrelated), so the covariance matrix is simply: \[
+   \Sigma_W=
+  \left[ {\begin{array}{cc}
+   \sigma^2_A & 0 \\
+   0 & \sigma^2_V \\
+  \end{array} } \right]
+\]
+
+\begin{figure}
+
+{\centering \includegraphics[width=400px]{pictures/model}
+
+}
+
+\caption{Illustration of the model using simulated data.
 A word category is defined as the joint bivariate distribution of an auditory category (horizontal, bottom panel) and a visual semantic category (vertical, left panel).
 Upon the presentation of a word token $w$, participants guess whether it is sampled from the word type $W_1$ or from the word type $W_2$.
-Decision threshold is where the guessing probability is 0.5.", fig.align = "center", out.width = "400px"}
-knitr::include_graphics("pictures/model.png", dpi = 108)
-```
-
-We have two word categories: dog-/aba/ ($W_1$) and cat-/ada/ ($W_2$).
-Participants can be understood as choosing one of these two word categories (Figure\ \@ref(fig:model)).
-For an ideal observer, the probability of choosing category 2 when presented with an audio-visual instance $w=(a,v)$ is the posterior probability of this category:
-
-$$
+Decision threshold is where the guessing probability is 0.5.}\label{fig:model}
+\end{figure}
+
+This assumption simply says that, given a word-object mapping, e.g.,
+W=(\enquote{cat}-CAT), variation in the way \enquote{cat} is pronounced
+does not correlate with changes in any visual property of the object
+CAT, which is a valid
+assumption.\footnote{Note that this assumptions is more adequate in the case of arbitrary associations such as ours, and less so in the case of redundant association such as audio-visual speech.
+In the latter, variation in the pronunciation is expected to correlate, at least to some extent, with lip movements.}
+
+Now we turn to the crucial question of modeling how optimal decision
+should proceed based on the probabilistic information in the auditory
+and the visual modalities. In our task, we have two word categories:
+dog-/aba/ (\(W_1\)) and cat-/ada/
+(\(W_2\)).\footnote{This mapping is randomized in the experiments.}
+Participants can be understood as choosing one of these two word
+categories (Figure~\ref{fig:model}). For an ideal observer, the
+probability of choosing category 2 when presented with an audio-visual
+instance \(w=(a,v)\) is the posterior probability of this category: \[
 p(W_2 | w)=\frac{p(w|W_2)p(W_2)}{p(w|W_2)p(W_2)+p(w|W_1)p(W_1)}
-$$
-We make the assumption that, given a particular word category, the auditory and visual tokens are independent:
-
-$$p(w | W) = p(a,v| W) = p(a| W)p(v| W)$$
-This assumptions simply says that, given a word-object mapping, e.g., W=("bee"-BEE), variation in the way "bee" is pronounced does not correlate with changes in any visual property of the object BEE\footnote{Note that this assumptions is more adequate to the case of arbitrary associations such as ours, and less so in the case of redundant association such as audio-visual speech.
-In the latter, variation in the pronounciation is expected to correlate, at least to some extent, with lip movements.}.
-
-Under this assumption, the posterior probability reduces to:
-$$ p(W_2 | w)=\frac{1}{1+(1+\epsilon)\exp(\beta_0+\beta_aa+\beta_vv)}$$
-
-with $\beta_a=\frac{\mu_{A1}-\mu_{A2}}{\sigma^2_{A}}$,
-$\beta_v=\frac{\mu_{V1}-\mu_{V2}}{\sigma^2_{V}}$, $\beta_0=\frac{\mu^2_{A2}-\mu^2_{A1}}{2\sigma^2_{A}}+\frac{\mu^2_{V2}-\mu^2_{V1}}{2\sigma^2_{V}}$ 
-and $1+\epsilon=\frac{p(W_1)}{p(W_2)}$ is the proportion of the prior probabilities.
-If the identity of word categories is randomized, and if $W_1$ is the target, then $\epsilon$ measures a response bias to "same" if $\epsilon > 0$, and a response bias to "different" if $\epsilon < 0$.
-We expect a general bias towards answering "different" because of the categorical nature of our same-different task: when two items are ambiguous but perceptually different, this could cause a slight preference for "different" over "same".
-
-We fix the values of the means to be the endpoints of the corresponding continuum.
-For example, if both the auditory and visual continua are made of 5 steps going from 0 to 4, then $\mu_{A1}=0$ and $\mu_{A2}=4$ (and similarly $\mu_{V1}=0$, and $\mu_{V2}=4$).
-When we fix th values of the means, observations from each modality ($a$ and $v$) become weighted according to their reliability, i.e., in the posterior we have $\beta_a \propto \frac{1}{\sigma^2_{A}}$ and $\beta_v \propto \frac{1}{\sigma^2_{V}}$ for the auditory and visual token, respectively.
-
-## Auditory and Visual baselines
-
-The posterior provides the optimal model's predictions for how probabilities that characterize uncertainty in each modality can be combined to make categorical decision about the bimodal input.
-The predictions of the optimal model will be compared to human responses in the bimodal case.
-Besides the optimal model, we also test the predictions of two baselines models: the **visual model**, which assumes that participants rely only on visual information, and the **auditory model**, which assumes that participants rely only on auditory information.
-If participants rely on both the auditory and the visual modalities, the optimal model would explain more variance in human responses than  the visual model alone or the auditory model alone.
-
-## Descriptive model
-
-The visual, auditory, and optimal models are *normative* models.
-Their predictions are made about human data in the bimodal condition, although their crucial parameters (i.e., variances associated with the visual and auditory modalities) are derived from data in the unimodal conditions.
-In addition to these normative models, we consider a *descriptive* model.
-The parameters of this model are fitted to human data in the bimodal condition.
-If the referential task induces sub-optimality (due, for instance, to the arbitrary nature of the sound-object association), then we predict the descriptive model to explain more variance than the optimal model does.
-
-A systematic comparison of the optimal and the descriptive models would allow us, not only to quantify how much people deviate from optimality, but also to understand qualitatively how they deviate from this optimality.
-Let $\sigma^2_{A}$ and $\sigma^2_{V}$ be the values of the variances used in the optimal model (derived from the unimodal conditions), and $\sigma^2_{Ab}$ and $\sigma^2_{Vb}$ be the values observed through the descriptive model in the bimodal condition.
-There are three possible cases of sub-optimality:
-
-1) Precision decreases equally for both modalities.
-That is, $\frac{1}{\sigma^2_{Ab}} < \frac{1}{\sigma^2_{A}}$ and $\frac{1}{\sigma^2_{Vb}} < \frac{1}{\sigma^2_{V}}$, but  $\frac{\sigma^2_{Ab}}{\sigma^2_{Vb}} \approx \frac{\sigma^2_{A}}{\sigma^2_{V}}$.
-In this case, sub-optimality would be due to increased randomness in human responses in the bimodal condition.
-However, this randomness would not affect the relative weighting of both modalities, i.e., participants would still weigh modalities according to the relative reliability predicted by the optimal model.
-
-2) The precision of the auditory modality decreases at a higher rate.
-That is, $\frac{1}{\sigma^2_{Ab}} \ll \frac{1}{\sigma^2_{A}}$ and $\frac{1}{\sigma^2_{Vb}} \leq \frac{1}{\sigma^2_{V}}$, leading to $\frac{\sigma^2_{Ab}}{\sigma^2_{Vb}} > \frac{\sigma^2_{A}}{\sigma^2_{V}}$.
-In this case, sub-optimally would consist not only in participants being more random in the bimodal condition, but also in them thaving a systematic preference for the visual modality, even after accounting for informational reliability.
-
-3) The precision of the visual modality decreases at a higher rate.
-That is, $\frac{1}{\sigma^2_{Vb}} \ll \frac{1}{\sigma^2_{V}}$, and  $\frac{1}{\sigma^2_{Ab}} \leq \frac{1}{\sigma^2_{A}}$, leading to $\frac{\sigma^2_{Ab}}{\sigma^2_{Vb}} > \frac{\sigma^2_{A}}{\sigma^2_{V}}$.
-This case is the reverse of case 2, i.e., in addition to increased randomness in the bimodal condition, there is a systematic preference for the auditory modality, even after accounting for informational reliability.
-
-A more principled way to understand these three cases of sub-optimality, especially with regard to modality preference, is to study deviations from the optimal decision threshold.
-The decision threshold is defined as the set of values in the audio-visual space along which the posterior is equal to 0.5.
-The decision threshold takes the following form:
-
-$$v=-\frac{\sigma^2_V}{\sigma^2_A}a+v_0$$
-
-If the slope derived from the descriptive model is greater than the slope of the optimal model, the corresponding shift in the decision threshold indicate that participants have a preference for the auditory modality in the bimodal case.
-similarly, a smaller slope would lead to a preference for the visual modality.
-The limit cases are when there is exclusive reliance on the auditory cue (a vertical line), and where there is exclusive reliance on the visual (a horizontal line).
-Figure\ \@ref(fig:subOptim) illustrate the three cases of sub-optimality discussed above.
-
-```{r subOptim, fig.cap = "Illustration using simulated data showing the prediction of the optimal model (top), and three possible ways human responses, as characterized by the descriptive model, can deviate from the optimal predictions (bottom).
-There are three possible cases of sub-optimlaity: 1) the precision drops equally for both modalities, and the cue weighing is still optimal (bottom, left), 2) the precision of the visual modality drops at a higher rate, leading to bias towards the auditory modality (bottom, middle), and 3) the precision of the auditory modality drops at a higher rate, leading to bias towards the visual modality (bottom, right)", fig.align = "center", out.width = "400px"}
-knitr::include_graphics("pictures/sub-optimal", dpi = 108)
-```
-
-In the following, we test these predictions in three Experiments.
-In Experiment 1, we study the case where bimodal uncertainty is due to ambiguity in terms of category membership, without any additional background noise.
-In Experiment 2 and 3 we add background noise on top of ambiguity in category membership.
-In Experiment 2 we add background noise to the auditory modality, and in Experiment 3 we add background noise to the visual modality.
-
-# Experiment 1
-
-In this Experiment, we start with testing the predictions in the case where uncertainty is due to ambiguity in terms of category membership, without any additional noise in the background.
-
-## Methods
-
-### Participants:
-
-We recruited a planned sample of `r N_all_1` participants from Amazon Mechanical Turk.
-Only participants with US IP addresses and a task approval rate above 85\% were allowed to participate.
-They were paid at an hourly rate of \$6/hour.
-participants were excluded if they took the experiment more than once (N=`r  N_twice_1`), then if they reported having experienced a technical problem of any sort during the online experiment (N=`r N_all_1 - N_noProb_1`), and finally if they had less than 50\% accurate responses on the unambiguous training trials (N=`r N_noProb_1 - N_good_1`).
-The final sample consisted of (N = `r N_good_1`) participants\footnote{The sample size and exclusion criteria were specified in the pre-registration at https://osf.io/h7mzp/}.
-
-### Stimuli:
-For auditory stimuli, we used the continuum introduced in @vroomen2004, a 9-point /aba/--/ada/ speech continuum created by varying the frequency of the second (F2) formant in equal steps.
-We selected 5 equally spaced points from the original continuum by keeping the endpoints (prototypes) 1 and 9, as well as points 3, 5, and 7 along the continuum.
-For visual stimuli, we used a morph continuum introduced in @freedman2001.
-From the original 14 points, we selected 5 points as follows: we kept the item that seemed most ambiguous (point 8), the 2 preceding points (i.e., 7 and 6) and the 2 following points (i.e., 9 and 10).
-The 6 and 10 points along the morph were quite distinguishable, and we took them to be our prototypes.
-
-### Design and Procedure
-We told participants that an alien was naming two objects: a dog, called "aba"" in the alien language, and a cat, called "ada".
-In each trial, we presented the first object (the target) on the left side of the screen simultaneously with the corresponding sound.
-The target was always the same (e.g., dog-/aba/).
-The second sound-object pair (the test) followed on the other side of the screen after 500ms and varied in its category membership.
-For both the target and the test, visual stimuli were present for the duration of the sound clip ($\sim$ 800ms).
-We instructed participants to press "S" for same if they thought the alien was naming another dog-/aba/, and "D" for different if they thought the alien was naming a cat-/ada/.
-For each participant, we randomized the sound-object mapping as well as the identity of the target.
-
-The first part of the experiment trained participants using only the prototype pictures and the prototype sounds (12 trials, 4 each from the bimodal, audio-only, and visual-only conditions).
-After completing training, we instructed participants on the structure of the task and encouraged them to base their answers on both the sounds and the pictures (in the bimodal condition).
-There were a total of 25 possible combinations in the bimodal condition, and 5 in each of the unimodal conditions.
-Each participant saw each possible trial twice, for a total of 70 trials/participant.
-Trials were blocked by condition and blocks were presented in random order.
-
-## Results and analysis
-
-```{r echo=FALSE}
-
-#Bootstrap sample parameters
-
-lmfit <- function(data, indices) {
-
-  myd = data[indices, ]
-
-  s_data <- myd %>%
-    filter(condition == "sound")
-
-  v_data <- myd %>%
-    filter(condition == "concept")
-
-  j_data <- myd %>%
-    filter(condition == "joint")
-
-  s_nl <- nls(answer ~ 1/(1+(1-e)*exp((-4/vrA)*sound_dist+(8/vrA))), data=s_data, start = list(e=0, vrA=2), nls.control(warnOnly = TRUE))
-
- c_nl <- nls(answer ~ 1/(1+(1-e)*exp((-4/vrV)*concept_dist+(8/vrV))), data=v_data, start = list(e=0, vrV=2), nls.control(warnOnly = TRUE))
-
- j_nl <- nls(answer ~ 1/(1+(1-e)*exp((-4/vrA_j)*sound_dist+(-4/vrV_j)*concept_dist+(8/vrA_j)+(8/vrV_j))), data=j_data, start = list(e=0, vrA_j=2, vrV_j=2), nls.control(warnOnly = TRUE))
-
-  s_va <- coef(s_nl)["vrA"]
-  s_e <- coef(s_nl)["e"]
-
-  v_va <- coef(c_nl)["vrV"]
-  v_e <- coef(c_nl)["e"]
-
-  decision_ideal=v_va/s_va
-
-  j_va_s=coef(j_nl)["vrA_j"]
-  j_va_v=coef(j_nl)["vrV_j"]
-  j_e=coef(j_nl)["e"]
-
-  decision_fit=j_va_v/j_va_s
-
-  preference = decision_fit/decision_ideal
-
-  MyBoot=c(s_va, s_e, v_va, v_e, j_va_s, j_va_v, j_e, decision_ideal, decision_fit, preference)
-
-  return(MyBoot)
+\] Using our assumption that the cues are uncorrelated, we have
+\[p(w | W) = p(a,v| W) = p(a| A)p(v| V)\] Under this assumption, the
+posterior probability reduces
+to:\footnote{See the appendix for the details of the derivation}
+
+\begin{equation}
+ p(W_2 | w)=\frac{1}{1+(1+\epsilon)\exp(\beta_0+\beta_aa+\beta_vv)}
+\end{equation}
+
+where \[1+\epsilon=\frac{p(W_1)}{p(W_2)}\]
+\[\beta_0=\frac{\mu^2_{A2}-\mu^2_{A1}}{2\sigma^2_{A}}+\frac{\mu^2_{V2}-\mu^2_{V1}}{2\sigma^2_{V}}\]
+
+\[\beta_a=\frac{\mu_{A1}-\mu_{A2}}{\sigma^2_{A}}\]
+\[\beta_v=\frac{\mu_{V1}-\mu_{V2}}{\sigma^2_{V}}\]
+
+The parameter \(\epsilon\) represents the differential between the
+categories' prior probabilities. However, since the identity of word
+categories is randomized across participants, \(\epsilon\) measures,
+rather, a response bias to \enquote{same} if \(\epsilon > 0\), and a
+response bias to \enquote{different} if \(\epsilon < 0\). We expect a
+general bias towards answering \enquote{different} because of the
+categorical nature of our same-different task: When two items are
+ambiguous but perceptually different, participants might have a slight
+preference for \enquote{different} over \enquote{same}.
+
+The values of the means are fixed: They correspond to the value of the
+most typical tokens in our stimuli. Thus, observations from each
+modality (\(a\) and \(v\)) are weighted according to their reliability
+in the posterior: \[\beta_a \propto \frac{1}{\sigma^2_{A}}\]
+\[\beta_v \propto \frac{1}{\sigma^2_{V}}\].
+
+Note that the weights account for categorical variability only. For
+instance, if the speaker generates a target production \(a_t\) from an
+auditory category \(p(a_t | A) \sim N(\mu_{A}, \sigma^2_{A})\), the
+ideal model assumes that it has direct access to this production token
+(i.e., \(a=a_t\)), and that all uncertainty is about the category
+membership of this token. However, we might also want to account for
+noise in the brain and/or in the environment. For example, the observer
+might not have access to the exact produced target, but only to the
+target perturbed by noise. If we assume this noise to be normally
+distributed, that is, \(p(a | a_t) \sim N(a_t, \sigma^2_{N})\), then
+integrating over \(a_t\) lead to the following simple expression:
+\[ p(a | A) \sim N(\mu_{A}, \sigma^2_{A}+\sigma^2_{N})\] Using an
+identical reasoning for the case of the visual modality, we end up with
+the following multimodal weighting scheme in the optimal combination
+model:
+
+\[\beta_a \propto \frac{1}{\sigma^2_{A}+\sigma^2_{N_A}}\]
+\[\beta_v \propto \frac{1}{\sigma^2_{V} +\sigma^2_{N_V}}\] To summarize,
+the posterior provides the optimal model's predictions for how
+probabilities that characterize uncertainty in each modality can be
+combined to make categorical decision about the bimodal input. The model
+will be constructed based on data from the unimodal trials, but the
+predictions of the optimal model will be compared to human responses in
+the bimodal trials.
+
+\subsection{Auditory and Visual
+models}\label{auditory-and-visual-models}
+
+Besides the optimal model, we also test the predictions of two baselines
+models: a visual model, which assumes that participants rely only on
+visual information, and an auditory model, which assumes that
+participants rely only on auditory information. If participants rely on
+both the auditory and the visual modalities, the optimal model would
+explain more variance in human responses than the visual model alone or
+the auditory model alone.
+
+\subsection{Descriptive model}\label{descriptive-model}
+
+The visual, auditory, and optimal models are \emph{normative} models.
+Their predictions are made about human data in the bimodal condition,
+but their crucial parameters (i.e., variances associated with the visual
+and auditory modalities) are derived from data in the unimodal
+conditions. In addition to these normative models, we consider a
+\emph{descriptive} model. The parameters of this model are fit to human
+data in the bimodal condition. If the referential task induces
+sub-optimality (due, for instance, to the arbitrary nature of the
+sound-object association), then we predict that the descriptive model
+should explain more variance than the optimal model does.
+
+A systematic comparison of the optimal and the descriptive models would
+allow us, not only to quantify how much people deviate from optimality,
+but also to understand precisely how they deviate from this optimality.
+Let \(\sigma^2_{A}\) and \(\sigma^2_{V}\) be the values of the variances
+used in the optimal model (derived from the unimodal conditions), and
+\(\sigma^2_{Ab}\) and \(\sigma^2_{Vb}\) be the values observed through
+the descriptive model in the bimodal condition. Deviation from
+optimality is measured in two ways. First, we measure the change in the
+values of the variances specific to each modality, that is, how
+\(\sigma^2_{A}\) compares to \(\sigma^2_{Ab}\), and how \(\sigma^2_{V}\)
+compares to \(\sigma^2_{Vb}\). Second, we measure changes in the
+proportion of the visual and auditory variances, i.e., how
+\(\frac{\sigma^2_{A}}{\sigma^2_{V}}\) compares to
+\(\frac{\sigma^2_{Ab}}{\sigma^2_{Vb}}\). The first measure allows us to
+test if precision changes for each modality when we move from the
+unimodal to the bimodal conditions. The second allows us to test whether
+or not the weighting scheme follows the prediction of the optimal model.
+The reason we used the proportion of the variances as a measure of
+cross-modal weighing is because it corresponds to the
+slope\footnote{Or more precisely the absolute value of the slope} of the
+decision threshold in the audio-visual space (Figure~\ref{fig:model}).
+The decision threshold is defined as the set of values in this
+audio-visual space along which the posterior is equal to 0.5. Formally
+speaking, the decision threshold takes the following form:
+
+\[v=-\frac{\sigma^2_V}{\sigma^2_A}a+v_0\]
+
+If the absolute value of the slope derived from the descriptive model is
+greater than that of the optimal model, the corresponding shift in the
+decision threshold indicates that participants have a preference for the
+auditory modality in the bimodal case. Similarly, a smaller absolute
+value of the slope would lead to a preference for the visual modality.
+The limit cases are when there is exclusive reliance on the auditory cue
+(a vertical line), and where there is exclusive reliance on the visual
+(a horizontal line).
+
+It follows that there are three possible scenarios describing how humans
+can deviate from optimality. These scenarios are illustrated in
+Figure~\ref{fig:subOptim} and are as follows:
+
+\begin{enumerate}
+\def\labelenumi{\arabic{enumi})}
+\item
+  Both variances may increase, but their proportion remains the same.
+  That is, \(\sigma^2_{Ab} \geqslant \sigma^2_{A}\) and
+  \(\sigma^2_{Vb} \geqslant \sigma^2_{V}\), but
+  \(\frac{\sigma^2_{Ab}}{\sigma^2_{Vb}} \approx \frac{\sigma^2_{A}}{\sigma^2_{V}}\).
+  In this case, sub-optimality would be due to increased randomness in
+  human responses in the bimodal condition. However, this randomness
+  would not affect the relative weighting of both modalities, i.e.,
+  participants would still weigh modalities according to the relative
+  reliability predicted by the optimal model.
+\item
+  The auditory variance increases at a higher rate. That is,
+  \(\sigma^2_{Ab} \gg \sigma^2_{A}\) and
+  \(\sigma^2_{Vb} \geqslant \sigma^2_{V}\), leading to
+  \(\frac{\sigma^2_{Ab}}{\sigma^2_{Vb}} > \frac{\sigma^2_{A}}{\sigma^2_{V}}\).
+  In this case, sub-optimally would consist not only in participants
+  being more random in the bimodal condition, but also in having a
+  systematic preference for the visual modality, even after accounting
+  for informational reliability.
+\item
+  The visual variance increases at a higher rate. That is,
+  \(\sigma^2_{Vb} \gg \sigma^2_{V}\), and
+  \(\sigma^2_{Ab} \geqslant \sigma^2_{A}\), leading to
+  \(\frac{\sigma^2_{Ab}}{\sigma^2_{Vb}} > \frac{\sigma^2_{A}}{\sigma^2_{V}}\).
+  This case is the reverse of case 2, i.e., in addition to increased
+  randomness in the bimodal condition, there is a systematic preference
+  for the auditory modality, even after accounting for informational
+  reliability.
+\end{enumerate}
+
+\begin{figure}
+
+{\centering \includegraphics[width=400px]{pictures/sub-optimal}
 
@@
 
-results1 <- boot(data=exp1_good, statistic = lmfit, R = 10000)
-
-#Auditory variance:
-audVar=boot.ci(results1, index = 1, type = c("bca"), conf = 0.95)
-audVar_val=audVar$t0 
-audVar_ci1=audVar$bca[4]
-audVar_ci2=audVar$bca[5]
-
-#Auditory bias:
-audBias=boot.ci(results1, index = 2, type = c("bca"), conf = 0.95)
-audBias_val=audBias$t0 
-audBias_ci1=audBias$bca[4]
-audBias_ci2=audBias$bca[5]
-
-#Visual variance:
-visVar=boot.ci(results1, index = 3, type = c("bca"), conf = 0.95)
-visVar_val=visVar$t0 
-visVar_ci1=visVar$bca[4]
-visVar_ci2=visVar$bca[5]
-
-#Visual bias:
-visBias=boot.ci(results1, index = 4, type = c("bca"), conf = 0.95)
-visBias_val=visBias$t0 
-visBias_ci1=visBias$bca[4]
-visBias_ci2=visBias$bca[5]
-
-#Bimodal Auditory variance:
-audVarBi=boot.ci(results1, index = 5, type = c("bca"), conf = 0.95)
-audVarBi_val=audVarBi$t0 
-audVarBi_ci1=audVarBi$bca[4]
-audVarBi_ci2=audVarBi$bca[5]
-
-#Bimodal Visual variance:
-visVarBi=boot.ci(results1, index = 6, type = c("bca"), conf = 0.95)
-visVarBi_val=visVarBi$t0 
-visVarBi_ci1=visVarBi$bca[4]
-visVarBi_ci2=visVarBi$bca[5]
-
-#Bimodal bias:
-BiasBi=boot.ci(results1, index = 7, type = c("bca"), conf = 0.95)
-BiasBi_val=BiasBi$t0 
-BiasBi_ci1=BiasBi$bca[4]
-BiasBi_ci2=BiasBi$bca[5]
-
-#Ideal modality wieghing
-prefIdeal=boot.ci(results1, index = 8, type = c("bca"), conf = 0.95)
-prefIdeal_val=prefIdeal$t0 
-prefIdeal_ci1=prefIdeal$bca[4]
-prefIdeal_ci2=prefIdeal$bca[5]
-
-#fit modality wieghing
-prefFit=boot.ci(results1, index = 9, type = c("bca"), conf = 0.95)
-prefFit_val=prefFit$t0 
-prefFit_ci1=prefFit$bca[4]
-prefFit_ci2=prefFit$bca[5]
-
-#Modality bias 
-bias=boot.ci(results1, index = 10, type = c("bca"), conf = 0.95)
-bias_val_1=bias$t0 
-bias_ci1_1=bias$bca[4]
-bias_ci2_1=bias$bca[5]
-
-```
-
-### Unimodal conditions
-
-```{r}
-
-#Fit the non-linear function
-
-##Experiment 1
-#############
-sound_nl1 <- nls(answer ~ 1/(1+(1-e)*exp((-4/vrA)*sound_dist+(8/vrA))), data=sound_all_exp1, start = list(e=0, vrA=2))
-
-concept_nl1 <- nls(answer ~ 1/(1+(1-e)*exp((-4/vrV)*concept_dist+(8/vrV))), data=concept_all_exp1, start = list(e=0, vrV=2))
-
-joint_nl1 <- nls(answer ~ 1/(1+(1-e)*exp((-4/vrA_j)*sound_dist+(-4/vrV_j)*concept_dist+(8/vrA_j)+(8/vrV_j))), data=joint_all_exp1, start = list(e=0, vrA_j=2, vrV_j=2))
-
-##extract coefficient
-eA_nl1 <- coef(sound_nl1)["e"]
-vrA_nl1 <- coef(sound_nl1)["vrA"]
-
-eV_nl1 <- coef(concept_nl1)["e"]
-vrV_nl1 <- coef(concept_nl1)["vrV"]
-
-eJ_nl1 <- coef(joint_nl1)["e"]
-vrJ_A_nl1 <- coef(joint_nl1)["vrA_j"]
-vrJ_V_nl1 <- coef(joint_nl1)["vrV_j"]
-#######
-
-x <- seq(0, 4, 0.01)
-
-y_sound_nl1 <- predict(sound_nl1, list(sound_dist = x), type="response")
-y_concept_nl1 <- predict(concept_nl1, list(concept_dist = x), type="response")
-
-uniS_nl1 <- data.frame(distance=x, prediction=y_sound_nl1) %>%
-  mutate(Condition = 'Auditory', 
-         Experiment ='Experiment 1')
-
-uniV_nl1 <- data.frame(distance=x, prediction=y_concept_nl1) %>%
-  mutate(Condition = 'Visual',
-         Experiment ='Experiment 1')
-
-##Experiment 2
-###############
-
-sound_nl2 <- nls(answer ~ 1/(1+(1-e)*exp((-4/vrA)*sound_dist+(8/vrA))), data=sound_all_exp2, start = list(e=0, vrA=2))
-
-concept_nl2 <- nls(answer ~ 1/(1+(1-e)*exp((-4/vrV)*concept_dist+(8/vrV))), data=concept_all_exp2, start = list(e=0, vrV=2))
-
-joint_nl2 <- nls(answer ~ 1/(1+(1-e)*exp((-4/vrA_j)*sound_dist+(-4/vrV_j)*concept_dist+(8/vrA_j)+(8/vrV_j))), data=joint_all_exp2, start = list(e=0, vrA_j=2, vrV_j=2))
-
-##extract coefficient
-eA_nl2 <- coef(sound_nl2)["e"]
-vrA_nl2 <- coef(sound_nl2)["vrA"]
-
-eV_nl2 <- coef(concept_nl2)["e"]
-vrV_nl2 <- coef(concept_nl2)["vrV"]
-
-eJ_nl2 <- coef(joint_nl2)["e"]
-vrJ_A_nl2 <- coef(joint_nl2)["vrA_j"]
-vrJ_V_nl2 <- coef(joint_nl2)["vrV_j"]
-#######
-
-x <- seq(0, 4, 0.01)
-
-y_sound_nl2 <- predict(sound_nl2, list(sound_dist = x), type="response")
-y_concept_nl2 <- predict(concept_nl2, list(concept_dist = x), type="response")
-
-uniS_nl2 <- data.frame(distance=x, prediction=y_sound_nl2) %>%
-  mutate(Condition = 'Auditory', 
-         Experiment ='Experiment 2')
-
-uniV_nl2 <- data.frame(distance=x, prediction=y_concept_nl2) %>%
-  mutate(Condition = 'Visual', 
-         Experiment ='Experiment 2')
-
-##Experiment 3
-###############
-
-sound_nl3 <- nls(answer ~ 1/(1+(1-e)*exp((-4/vrA)*sound_dist+(8/vrA))), data=sound_all_exp3, start = list(e=0, vrA=2))
-
-concept_nl3 <- nls(answer ~ 1/(1+(1-e)*exp((-4/vrV)*concept_dist+(8/vrV))), data=concept_all_exp3, start = list(e=0, vrV=2))
-
-joint_nl3 <- nls(answer ~ 1/(1+(1-e)*exp((-4/vrA_j)*sound_dist+(-4/vrV_j)*concept_dist+(8/vrA_j)+(8/vrV_j))), data=joint_all_exp3, start = list(e=0, vrA_j=2, vrV_j=2))
-
-##extract coefficient
-eA_nl3 <- coef(sound_nl3)["e"]
-vrA_nl3 <- coef(sound_nl3)["vrA"]
-
-eV_nl3 <- coef(concept_nl3)["e"]
-vrV_nl3 <- coef(concept_nl3)["vrV"]
-
-eJ_nl3 <- coef(joint_nl3)["e"]
-vrJ_A_nl3 <- coef(joint_nl3)["vrA_j"]
-vrJ_V_nl3 <- coef(joint_nl3)["vrV_j"]
-#######
-
-x <- seq(0, 4, 0.01)
-
-y_sound_nl3 <- predict(sound_nl3, list(sound_dist = x), type="response")
-y_concept_nl3 <- predict(concept_nl3, list(concept_dist = x), type="response")
-
-uniS_nl3 <- data.frame(distance=x, prediction=y_sound_nl3) %>%
-  mutate(Condition = 'Auditory', 
-         Experiment ='Experiment 3')
-
-uniV_nl3 <- data.frame(distance=x, prediction=y_concept_nl3) %>%
-  mutate(Condition = 'Visual', 
-         Experiment ='Experiment 3')
-
-all_uni_model <- bind_rows(uniS_nl1, uniV_nl1,
-                           uniS_nl2, uniV_nl2,
-                           uniS_nl3, uniV_nl3)
-
-all_plot <- ggplot(exp_uni_data, 
-       aes(x = distance, y = mean)) + 
-  geom_point()+
-  #geom_pointrange(aes(ymin = summary_ci_lower, ymax = summary_ci_upper), 
-  #                position = position_dodge(width = .1)) + 
-  #geom_line(data=uniV,aes(x=xV, y=yV))+
-  geom_line(data=all_uni_model, aes(x=distance, y=prediction), col='black')+
-  xlab("Distance") +ylab("Prob. different")+
-  scale_y_continuous(limits = c(0, 1))+#theme(aspect.ratio = 0.7)+
-  theme(aspect.ratio = 0.7) + facet_grid(Experiment ~ Condition)
-  #stat_function(fun = Logistic_v, colour="red"))
-
-```
-
-```{r unimodal, fig.cap = "Dots represent the proportion of `different' to `same' responses in the auditory-only condition (left), and visual-only condition (right), across the three Experiments.
-Error bars are 0.95 confidence intervals.
-Solid lines represent logistic fits.", fig.align = "center", out.width = "400px"}
-
-all_plot
-
-```
-
-We first analysed the unimodal cases.
-These are the cases where the pictures were hidden, or where the sounds were muted.
-Average categorization judgments and fits are shown in Figure\ \@ref(fig:unimodal).
-The categorization function of the auditory condition was slightly steeper than that of the visual condition, meaning that participants perceived the sound tokens slightly more categorically and whih higher certainty than they did with the visual tokens.
-
-Since we fixed the values of the means to be the endpoints of the corresponding continuum: $\mu_{A1}=0$ and $\mu_{A2}=4$ (and similarly $\mu_{V1}=0$, and $\mu_{V2}=4$), this leaves us with two free parameters: the bias and the variance.
-To determine the values of these parameters, we fit a model for each modality, collapsed across all participants.
-For the auditory modality, we obtained\footnote{all CIs in the paper are 95% confidence intervals} $\epsilon_A=$ `r audBias_val` CI [`r audBias_ci2`, `r audBias_ci1`] and $\sigma^2_A=$ `r audVar_val` CI [`r audVar_ci1`, `r audVar_ci2`].
-For the visual modality, we obtained $\epsilon_V=$ `r visBias_val` CI [`r visBias_ci2`, `r visBias_ci1`] and $\sigma^2_V=$ `r visVar_val` CI [`r visVar_ci1`, `r visVar_ci2`]`.
-
-### Bimodal condition
-
-```{r  echo=FALSE}
-
-#All models
-
-##Experiment 1
-##############
-
-#The fit
-model_fit1 <- function (x,y) {
-   1/(1 + (1-eJ_nl1)*exp((-4/vrJ_A_nl1)*x+(-4/vrJ_V_nl1)*y+(8/vrJ_A_nl1)+(8/vrJ_V_nl1)))
+\caption{Illustration using simulated data showing the example of a prediction made by the optimal model (top), and the three possible ways human participants can deviate from this prediction (bottom).
+These cases are the following: 1) The variance increases equally for both modalities, but the weighting scheme (characterized by the decision threshold) is optimal, 2) The auditory variance increases at a higher rate, leading to a preference for the auditory modality, and 3) The visual variance increases at a higher rate, leading to a preference for the visual modality}\label{fig:subOptim}
+\end{figure}
+
+We tested the predictions of the optimal model in three experiments. In
+Experiment 1, we studied the case where bimodal uncertainty was due to
+ambiguity in terms of category membership, without any additional
+background noise. In Experiment 2 and 3 we added background noise on top
+of ambiguity in category membership.
+
+\section{Experiment 1}\label{experiment-1}
+
+In this Experiment, we start with testing the predictions in the case
+where uncertainty is due to ambiguity in terms of category membership
+only, that is, according to the following weighting scheme:
+\[\beta_a \propto \frac{1}{\sigma^2_{A}}\]
+\[\beta_v \propto \frac{1}{\sigma^2_{V}}\] We do not introduce any
+additional noise in the background, and we assume that sensory noise is
+negligible compared to categorical variability.
+
+\subsection{Methods}\label{methods}
+
+\subsubsection{Participants:}\label{participants}
+
+We recruited a planned sample of 100 participants from Amazon Mechanical
+Turk. Only participants with US IP addresses and a task approval rate
+above 85\% were allowed to participate. They were paid at an hourly rate
+of \$6/hour. Participants were excluded if they reported having
+experienced a technical problem of any sort during the online experiment
+(N=14), or if they had less than 50\% accurate responses on the
+unambiguous training trials (N=6). The final sample consisted of (N =
+80)
+participants.\footnote{The sample size and exclusion criteria were specified in the pre-registration at https://osf.io/h7mzp/.}
+
+\subsubsection{Stimuli:}\label{stimuli}
+
+For auditory stimuli, we used the continuum introduced in Vroomen,
+Linden, Keetels, Gelder, and Bertelson (2004), a 9-point /aba/--/ada/
+speech continuum created by varying the frequency of the second (F2)
+formant in equal steps. We selected 5 equally spaced points from the
+original continuum by keeping the endpoints (prototypes) 1 and 9, as
+well as points 3, 5, and 7 along the continuum. For visual stimuli, we
+used a morph continuum introduced in Freedman, Riesenhuber, Poggio, and
+Miller (2001). From the original 14 points, we selected 5 points as
+follows: we kept the item that seemed most ambiguous (point 8), the 2
+preceding points (i.e., 7 and 6) and the 2 following points (i.e., 9 and
+10). The 6 and 10 points along the morph were quite distinguishable, and
+we took them to be our prototypes.
+
+\subsubsection{Design and Procedure}\label{design-and-procedure}
+
+We told participants that an alien was naming two objects: a dog, called
+\enquote{aba} in the alien language, and a cat, called \enquote{ada}. In
+each trial, we presented the first object (the target) on the left side
+of the screen simultaneously with the corresponding sound. For each
+participant, the target was always the same (e.g., dog-/aba/). The
+second sound-object pair (the test) followed on the other side of the
+screen after 500ms and varied in its category membership. For both the
+target and the test, visual stimuli were present for the duration of the
+sound clip (\(\sim\) 800ms). We instructed participants to press
+\enquote{S} for same if they thought the alien was naming another
+dog-/aba/, and \enquote{D} for different if they thought the alien was
+naming a cat-/ada/. We randomized the sound-object mapping (e.g.,
+dog-/aba/, cat-/ada/) as well as the identity of the target (dog or cat)
+across participants.
+
+The first part of the experiment trained participants using only the
+prototype pictures and the prototype sounds (12 trials, 4 each from the
+bimodal, audio-only, and visual-only conditions). After completing
+training, we instructed participants on the structure of the task and
+encouraged them to base their answers on both the sounds and the
+pictures (in the bimodal condition). There were a total of 25 possible
+combinations in the bimodal condition, and 5 in each of the unimodal
+conditions. Each participant saw each possible trial twice, for a total
+of 70 trials/participant. Trials were blocked by condition and blocks
+were presented in random order.
+
+\begin{figure}
+
+{\centering \includegraphics[width=400px]{ms_files/figure-latex/unimodal-1}
+
 }
 
-#The ideal
-model_ideal1 <- function (x,y) {
-    1/(1 + (1-eJ_nl1)*exp((-4/vrA_nl1)*x+(-4/vrV_nl1)*y+(8/vrA_nl1)+(8/vrV_nl1)))
+\caption{Human responses in the unimodal condition.
+Points represent the proportion of `different' to `same' responses in the auditory-only condition (left), and visual-only condition (right).
+Error bars are 95\% confidence intervals.
+Solid lines represent logistic fits.}\label{fig:unimodal}
+\end{figure}
+
+\subsubsection{Model fitting details}\label{model-fitting-details}
+
+\paragraph{Unimodal condition}\label{unimodal-condition}
+
+Remember that data in this conditions allow us to derive the variances
+of both the auditory and the visual categories, and that these variances
+are used to make predictions about bimodal data (in the visual and
+auditory baselines as well as in the optimal model). These individual
+variances were derived as follows (we explain the derivation for the
+auditory-only case, but the same applies for the visual-only case). We
+use the same Bayesian reasoning as we did in the derivation of the
+bimodal model: When presented with an audio instance \(a\), the
+probability of choosing the sound category 2 (that is, to answer
+\enquote{different}) is the posterior probability of this category
+\(p(A_2|a)\). If we assume that both sound categories have equal
+variances, the posterior probability reduces to:
+
+\[p(A_2 | a)=\frac{1}{1+(1+\epsilon_A)\exp(\beta_{a0}+\beta_aa)}\]
+
+with \(\beta_a=\frac{\mu_{A_1}-\mu_{A_2}}{\sigma^2_{A}}\) and
+\(\beta_{a0}=\frac{\mu^2_{A_2}-\mu^2_{A_1}}{2\sigma^2_{A}}\).
+\(\epsilon_A\) is the response bias in the auditory-only condition. For
+this model (as well as all other models in this study), we fixed the
+values of the means to be the end-points of the corresponding continuum,
+since these points are the most typical instances in our stimuli. Thus,
+we have \(\mu_{A1}=0\) and \(\mu_{A2}=4\) (and similarly \(\mu_{V1}=0\),
+and \(\mu_{V2}=4\)). This leaves us with two free parameters: the bias
+\(\epsilon_A\) and the variance \(\sigma^2_{A}\). To determine the
+values of these parameters, we fit the unimodal posterior to human data
+in the unimodal case.
+
+\paragraph{Bimodal condition}\label{bimodal-condition}
+
+In this condition, only the descriptive model is fit to the data, using
+the expression of the posterior (Equation 1). Since the values of the
+means are fixed, we have 3 free parameters: the variances for the visual
+and the auditory modalities, respectively, and \(\epsilon\), the
+response bias. The visual and auditory baselines as well as the optimal
+model are not fit to bimodal data, but their predictions are tested
+against these bimodal data. All these normative models use the variances
+derived from the unimodal data and the bias term derived from the
+bimodal data.
+
+Although the paradigm is within-subjects, we did not have enough
+statistical power to fit a different model for each individual
+participant. Instead, models are constructed with data collapsed across
+all participants. The fit was done with a nonlinear least squares
+regression using the NLS package in R (Bates \& Watts, 1988). We
+computed the values of the parameters, as well as their 95\% confidence
+intervals, through non-parametric bootstrap (using 10000 iterations).
+
+\subsection{Results and analysis}\label{results-and-analysis}
+
+\subsubsection{Unimodal conditions}\label{unimodal-conditions}
+
+Average categorization judgments and best fits are shown in
+Figure~\ref{fig:unimodal}. The categorization function of the auditory
+condition was slightly steeper than that of the visual condition,
+meaning that participants perceived the sound tokens slightly more
+categorically and whih higher certainty than they did with the visual
+tokens. For the auditory modality, we obtained the following
+values:\footnote{all CIs in the paper are 95\% confidence intervals}
+\(\epsilon_A=\) -0.20 {[}0.02, -0.38{]} and \(\sigma^2_A=\) 2.04
+{[}1.66, 2.53{]}. For the visual modality, we obtained \(\epsilon_V=\)
+-0.12 {[}0.06, -0.28{]} and \(\sigma^2_V=\) 3.33 {[}2.83, 3.92{]}`.
+
+\subsubsection{Bimodal condition}\label{bimodal-condition-1}
+
+\begin{figure}
+
+{\centering \includegraphics[width=400px]{ms_files/figure-latex/bimodal-1}
+
 }
 
-#The sound-only model
-model_sound1 <- function (x,y) {
-  1/(1 + (1-eJ_nl1)*exp((-4/vrA_nl1)*x+(8/vrA_nl1)))
+\caption{Human responses vs. models' predictions in the bimodal condition. Shape represents auditory distance from the target, and color represents visual distance from the target.}\label{fig:bimodal}
+\end{figure}
+
+\paragraph{Normative models}\label{normative-models}
+
+Figure~\ref{fig:bimodal} compares the predictions of the normative
+models against human responses. The visual, auditory and optimal model
+explained, respectively, 30\%, 67\%, and 89\% of total variance in mean
+responses.
+
+\paragraph{Descriptive model}\label{descriptive-model-1}
+
+In the descriptive model, all parameters are fit to human responses in
+the bimodal condition. We found \(\epsilon=\) -0.34 {[}-0.28, -0.39{]},
+\(\sigma^2_{Ab}=\) 4.96 {[}4.58, 5.40{]} and \(\sigma^2_{Vb}=\) 7.06
+{[}6.40, 7.84{]}. Note that the variance of both the auditory and visual
+modalities increased compared to the unimodal conditions.
+
+The descriptive model explained 95\% of total variance. However, since
+the descriptive model was fit to the same data, there is a risque that
+this high correlation is due to overfitting. To examine this
+possibility, we cross-validated the model using half the responses to
+predict the other half (averaging across 1000 random partitions). The
+predictive power of the model remained very high (\(r^2\)=0.92).
+
+\paragraph{Cue combination and Modality
+preference}\label{cue-combination-and-modality-preference}
+
+We next analyzed if cue combination was performed in an optimal way, or
+if there was a systematic preference for one modality when making
+decisions in the bimodal condition. As explained above, modality
+preference can be characterized formally as a deviation from the
+decision threshold predicted by the optimal model. Figure~\ref{fig:bias}
+(top) shows both the decision threshold derived from the descriptive
+model (in black) and the decision threshold predicted by the optimal
+model (in red). The deviation from optimality is compared to two
+hypothetical cases of modality preference (dotted lines). We found that
+the descriptive and optimal decision thresholds were almost identical.
+Indeed, non-parametric resampling of the data showed no evidence of a
+deviation from the optimal prediction (Figure~\ref{fig:bias}, bottom).
+
+\subsection{Discussion}\label{discussion}
+
+Overall, we found that the optimal model explained much of the variance
+in the mean judgments, and largely more than what can be explained with
+the auditory or the visual models alone. Moreover, the high value of the
+coefficient of determination in the optimal model (\(r^2\)=0.89)
+suggests that the population was near-optimal. However, we see in
+Figure~\ref{fig:bimodal} that the mean responses deviated systematically
+from the optimal prediction in that they were slightly pulled toward
+chance (i.e., the probability 0.5). This is due to the increase in the
+value of the variance associated with each modality. Note however that,
+despite this increase in randomness, our analysis of modality preference
+showed that the relative values of these variances were not different
+(Figure~\ref{fig:bias}), meaning that there was no evidence for a
+modality preference. Thus, 1) There was a simultaneous increase in the
+values of the auditory and visual variances in the bimodal condition
+compared to the unimodal condition, meaning that the bimodal input lead
+to an increase in response randomness, and 2) this increased randomness
+did not affect the relative weighting of both modalities, i.e., the
+population was weighting modalities according to the relative
+reliability predicted by the optimal model. This situation corresponds
+to the first case of sub-optimally described in
+Figure~\ref{fig:subOptim}.
+
+\begin{figure}
+
+{\centering \includegraphics[width=400px]{ms_files/figure-latex/individual-1}
+
 }
 
-#The visual-only model
-model_concept1 <- function (x,y) {
-  1/(1 + (1-eJ_nl1)*exp((-4/vrV_nl1)*y+(8/vrV_nl1)))
+\caption{Histograms of the values of the visual variance relative to the auditory variance in Experiment 1.
+Light color represents the values derived from each individual participant, and dark color represents simulated data sampled from the descriptive model.}\label{fig:individual}
+\end{figure}
+
+As we noted earlier, the model addresses the question of optimality at
+the population level. However, it is important to know how individual
+responses are distributed. In fact, one could think of an extreme case
+where optimality at the population level would be misleading. Imagine,
+for instance, that in the bimodal condition half the participants relied
+exclusively on the visual modality, whereas the other half relied
+exclusively on the auditory modality. This case could still lead to an
+aggregate behaviour which appears optimal, but this optimality would be
+spurious.
+
+To examine this possibility, we consider the distribution of individual
+cross-modal weighting in the bimodal condition (i.e.,
+\(\frac{\sigma^2_{Vb}}{\sigma^2_{Ab}}\)). Using a factor of 10 as a
+cut-off, we found that 5 participants relied almost exclusively on the
+visual modality, and 12 relied almost exclusively on the auditory
+modality. The percentage of both cases was relatively small compared to
+the total number of participants (21.25\%). An additional number of
+participants (N=7) relied on both modalities, but provided noisy
+responses which lead to negative variances (probably due to mistaking
+\enquote{same} for \enquote{different} or vice versa). When these
+outliers were removed, the distribution had a rather unimodal shape
+(Figure~\ref{fig:individual}). This finding indicates that the
+population's near optimality is not spurious, but based mostly on
+genuine cue combination at the individual level.
+
+As a second analysis, we asked whether the observed variance in the
+individual distribution was due to mere sampling errors or whether it
+corresponded to a real between-subject variability. We simulated
+individual responses from the posterior distribution whose parameters
+were fit to the population as a whole (i.e., the descriptive posterior).
+The resulting distribution is shown in Figure~\ref{fig:individual}. For
+ease of comparison, the simulated distribution was superimposed to the
+real distribution. We found that the real distribution was broader than
+the simulated distribution, indicating real between-subject variation
+beyond sampling errors. This means that the participants varied in terms
+of how they wheigthed modalities: Compared to the predictions of the
+global descriptive model, some participants relied more on the auditory
+modality, and some relied more on the visual modality.
+
+In Experiment 1, we tested word recognition when there was multimodal
+uncertainty in terms of category membership only. In real life, however,
+tokens can undergo distortions due to noisy factors in the environment
+(e.g., car noise in the background, blurry vision in a foggy
+weather,..). In Experiment 2 and 3, we explore this additional level of
+uncertainty.
+
+\section{Experiment 2}\label{experiment-2}
+
+In this Experiment, we explored the effect of added noise on
+performance. We tested a case where the background noise was added to
+the auditory modality. We were interested to know if participants would
+treat this new source of uncertainty as predicted by the optimal model,
+that is, according to the following weighting scheme
+\[\beta_a \propto \frac{1}{\sigma^2_{A}+\sigma^2_{N_A}}\]
+\[\beta_v \propto \frac{1}{\sigma^2_{V}}\] The alternative hypothesis is
+that noise in one modality leads to a systematic preference for the
+non-noisy modality.
+
+\subsection{Methods}\label{methods-1}
+
+\subsubsection{Participants}\label{participants-1}
+
+A sample of 100 participants was recruited online through Amazon
+Mechanical Turk. We used the same exclusion criteria as in Experiment 1.
+7 participants were excluded because they had less than 50\% accurate
+responses on the unambiguous training trials. The final sample consisted
+of (N = 93) participants.
+
+\subsubsection{Stimuli and Procedure}\label{stimuli-and-procedure}
+
+We used the same visual stimuli as in Experiment 1. We also used the
+same auditory stimuli, but we convolved each item with Brown noise of
+amplitude 1 using the free sound editor Audacity (2.1.2). The average
+signal-to-noise ratio was - 4.4 dB. The procedure was exactly the same
+as in the previous experiment, except that the test stimuli (but not the
+target) were presented with the new noisy auditory stimuli.
+
+\subsection{Results and analysis}\label{results-and-analysis-1}
+
+\subsubsection{Unimodal conditions}\label{unimodal-conditions-1}
+
+We fit a model for each modality. For the auditory modality, our
+parameter estimates were \(\epsilon_A=\) -0.18 {[}-0.05, -0.30{]} and
+\(\sigma^2_A+\sigma^2_N=\) 4.70 {[}4.03, 5.55{]}. For the visual
+modality, we found \(\epsilon_V=\) -0.24 {[}-0.10, -0.36{]} and
+\(\sigma^2_V=\) 3.93 {[}3.43, 4.55{]}. Figure~\ref{fig:unimodal} shows
+responses in the unimodal conditions as well as the corresponding best
+fits. The visual data is a replication of the visual data in Experiment
+1. As for the auditory data, in contrast to Experiment 1, responses were
+flatter, showing more uncertainty.
+
+\subsubsection{Bimodal condition}\label{bimodal-condition-2}
+
+\paragraph{Normative models}\label{normative-models-1}
+
+Figure~\ref{fig:bimodal} compares the predictions of the visual,
+auditory and optimal models to human responses. These normative models
+explained, respectively, 77\%, 21\%, and 91\% of total variance in mean
+judgements. Note that, in contrast to Experiment 1, the visual model
+explains more variance than the auditory model.
+
+\paragraph{Descriptive model}\label{descriptive-model-2}
+
+We estimated \(\epsilon=\) -0.38 {[}-0.33, -0.42{]},
+\(\sigma^2_{Ab}+\sigma^2_{Nb}=\) 9.84 {[}8.75, 11.27{]}, and
+\(\sigma^2_{Vb}=\) 5.21 {[}4.84, 5.64{]}. The fit explained 0.97\% of
+total variance. Cross-validation using half the responses to predict the
+other half yielded \(r^2 =\) 0.96.
+
+\paragraph{Modality preferences}\label{modality-preferences}
+
+Figure~\ref{fig:bias} (top) shows that the participants' decision
+threshold deviated from optimality, and that this deviation was biased
+towards the visual modality (the non-noisy modality). Indeed
+non-parametric resampling of the data showed a decrease in the value of
+the slope in the descriptive model compared to the optimal model
+(Figure~\ref{fig:bias}, bottom).
+
+\subsection{Discussion}\label{discussion-1}
+
+We found, similar to Experiment 1, that the population was generally
+near optimal (\(r^2 =\) 0.91), and that the optimal model explained more
+variance than the auditory or the visual models alone. We also found a
+similar discrepancy from the optimal model as precision dropped for both
+the auditory and the visual modalities. As for the weighting scheme used
+by participants, contrary to Experiment 1 where modalities were weighted
+according to their relative reliability, we found in this experiment
+that the visual modality had a greater weight than what is expected from
+its relative reliability. This situation corresponds to the second case
+of sub-optimally described in Figure~\ref{fig:subOptim}.
+
+We were also interested in whether noise in the auditory modality lead
+more participants to rely exclusively on the visual modality at the
+individual level. Using the same cut-off as in Experiment 1 (a factor of
+10), the percentage of participants who relied exclusively on either
+modalities was 34.41\%, which is much higher than the percentage
+obtained in Experiment 1 (21.25\%). Moreover, the subset of participants
+relying exclusively on the visual modality (compared to those who relied
+exclusively on the auditory modality) increased from 29.41\% in
+Experiment 1 to 68.75\% in Experiment 2, indicating that noise in the
+auditory modality prompted more participants to rely exclusively and
+disproportionately on the visual modality.
+
+In Experiment 2, we tested the case of added background noise to the
+auditory modality. In Experiment 3, we test the case of added noise to
+the visual modality.
+
+\section{Experiment 3}\label{experiment-3}
+
+In this Experiment, we tested the case where the background noise was
+added to the visual modality. Similar to Experiment 2, we were
+interested to know if participants would treat this new source of
+uncertainty as predicted by the optimal model, that is, according to the
+following weighting scheme \[\beta_a \propto \frac{1}{\sigma^2_{A}}\]
+\[\beta_v \propto \frac{1}{\sigma^2_{V}+\sigma^2_{N_V}}\] The
+alternative hypothesis is that, just like noise in the auditory modality
+lead to a preference for the visual input in Experiment 2, noise in the
+visual modality would lead to a preference for the auditory input.
+
+\subsection{Methods}\label{methods-2}
+
+\subsubsection{Participants}\label{participants-2}
+
+A planned sample of 100 participants was recruited online through Amazon
+Mechanical Turk. We used the same exclusion criteria as in both previous
+experiments. 2 participants were excluded because they reported having a
+technical problem, and 10 participants were excluded because they had
+less than 50\% accurate responses on the unambiguous training trials.
+The final sample consisted of (N = 88) participants.
+
+\subsubsection{Stimuli and Procedure}\label{stimuli-and-procedure-1}
+
+We used the same auditory stimuli as in Experiment 1. We also used the
+same visual stimuli, but we blurred the tokens using the free image
+editor GIMP (2.8.20). We used a Gaussian blur with a
+radius\footnote{A features of the filter that affects the intensity of the blur}
+of 10 pixels. The experimental procedure was exactly the same as in the
+previous Experiments.
+
+\subsection{Results and analysis}\label{results-and-analysis-2}
+
+\subsubsection{Unimodal conditions}\label{unimodal-conditions-2}
+
+For the auditory modality, our parameter estimates were \(\epsilon_A=\)
+-0.24 {[}-0.04, -0.42{]} and \(\sigma^2_A=\) 1.94 {[}1.61, 2.33{]}. For
+the visual modality, we found \(\epsilon_V=\) 0.11 {[}0.27, -0.03{]} and
+\(\sigma^2_V+\sigma^2_N=\) 13.00 {[}9.92, 18.94{]}.
+Figure~\ref{fig:unimodal} shows responses in the unimodal conditions as
+well as the corresponding fits. The auditory data is a replication of
+the auditory data in Experiment 1. As for the visual data, we see that,
+in contrast to Experiment 1 and 2, responses were flatter, showing much
+more uncertainty.
+
+\subsubsection{Bimodal condition}\label{bimodal-condition-3}
+
+\paragraph{Normative models}\label{normative-models-2}
+
+Figure~\ref{fig:bimodal} compares the predictions of the visual,
+auditory and optimal models to human responses. These normative models
+explained, respectively, 1\%, 98\%, and 97\% of total variance in mean
+judgement.
+
+\paragraph{Descriptive model}\label{descriptive-model-3}
+
+We estimated \(\epsilon=\) -0.35 {[}-0.29, -0.40{]}, \(\sigma^2_{Ab}=\)
+3.00 {[}2.75, 3.25{]}, and \(\sigma^2_{Vb}+\sigma^2_{Nb}=\) 39.42
+{[}25.06, 98.96{]}. The fit explained 97\% of total variance.
+Cross-validation using half the responses to predict the other half
+yielded \$r\^{}2= \$ 0.96.
+
+\paragraph{Modality preferences}\label{modality-preferences-1}
+
+Participants' decision threshold suggested a preference for the auditory
+modality (the non-noisy modality). Indeed non-parametric resampling of
+the data showed an increase in the value of the slope in the descriptive
+model compared to the optimal model (Figure~\ref{fig:bias}).
+
+\subsection{Discussion}\label{discussion-2}
+
+We found that the optimal model accounted for almost all the variance
+(\(r^2 =\) 0.97). However, whereas in previous experiments, the optimal
+model explained more variance than the auditory or the visual models,
+here the auditory model explained at least as much variance (\(r^2 =\)
+0.98). Thus, though participants were still sensitive to variation in
+the noisy visual data in the unimodal condition, they tended to ignore
+this information in the bimodal condition, and relied almost exclusively
+on the non-noisy auditory modality. The reason why we saw this (floor)
+effect when we added noise to the visual modality (Experiment 3), and
+not when we added noise to the auditory modality (Experiment 2), is the
+fact that our visual stimuli were originally perceived less
+categorically and with less certainty than the auditory stimuli. This
+made it more likely for the visual categorization function to become
+flat and uninformative after a few drops in precision due to noise on
+the one had, and to the additional randomness induced by the bimodal
+presentation on the other hand.
+
+The general finding corresponds to the third case of sub-optimality
+described in Figure~\ref{fig:subOptim}. Indeed, precision dropped for
+both modalities in the bimodal condition compared to the unimodal
+condition. But the drop was much greater for the visual modality,
+resulting in a much lower weight assigned to it than what is expected
+from its optimal relative reliability. Therefore, just like participants
+over-relied on the visual modality when the auditory modality was noisy
+(Experiment 2), they also over-relied on the auditory modality when the
+visual modality was noisy (Experiment 3).
+
+The percentage of participants who relied exclusively on either the
+visual modality or the auditory modality was 38.64\%, which is closer to
+the percentage of Experiment 2, except that now almost all of them
+relied on the auditory modality (94.12\%).
+
+\begin{figure}
+
+{\centering \includegraphics[width=400px]{ms_files/figure-latex/bias-1}
+
 }
 
-##Experiment 2
-##############
-
-#The fit
-model_fit2 <- function (x,y) {
-   1/(1 + (1-eJ_nl2)*exp((-4/vrJ_A_nl2)*x+(-4/vrJ_V_nl2)*y+(8/vrJ_A_nl2)+(8/vrJ_V_nl2)))
-}
-
-#The ideal
-model_ideal2 <- function (x,y) {
-    1/(1 + (1-eJ_nl2)*exp((-4/vrA_nl2)*x+(-4/vrV_nl2)*y+(8/vrA_nl2)+(8/vrV_nl2)))
-}
-
-#The sound-only model
-model_sound2 <- function (x,y) {
-  1/(1 + (1-eJ_nl2)*exp((-4/vrA_nl2)*x+(8/vrA_nl2)))
-}
-
-#The visual-only model
-model_concept2 <- function (x,y) {
-  1/(1 + (1-eJ_nl2)*exp((-4/vrV_nl2)*y+(8/vrV_nl2)))
-}
-
-##Experiment 3
-##############
-
-#The fit
-model_fit3 <- function (x,y) {
-   1/(1 + (1-eJ_nl3)*exp((-4/vrJ_A_nl3)*x+(-4/vrJ_V_nl3)*y+(8/vrJ_A_nl3)+(8/vrJ_V_nl3)))
-}
-
-#The ideal
-model_ideal3 <- function (x,y) {
-    1/(1 + (1-eJ_nl3)*exp((-4/vrA_nl3)*x+(-4/vrV_nl3)*y+(8/vrA_nl3)+(8/vrV_nl3)))
-}
-
-#The sound-only model
-model_sound3 <- function (x,y) {
-  1/(1 + (1-eJ_nl3)*exp((-4/vrA_nl3)*x+(8/vrA_nl3)))
-}
-
-#The visual-only model
-model_concept3 <- function (x,y) {
-  1/(1 + (1-eJ_nl3)*exp((-4/vrV_nl3)*y+(8/vrV_nl3)))
-}
-
-```
-
-```{r echo=FALSE, fig.width=7, fig.height=8}
-
-models_exp1 <- joint_exp1 %>% 
-  rename(joint = mean) %>%
-  mutate(Descriptive = model_fit1(sound_dist, concept_dist)) %>%
-  mutate(Optimal = model_ideal1(sound_dist, concept_dist)) %>%
-  mutate(Auditory = model_sound1(sound_dist, concept_dist)) %>%
-  mutate(Visual = model_concept1(sound_dist, concept_dist)) %>%
-  gather(model, pred, Visual, Auditory, Optimal, Descriptive) %>%
-  mutate(experiment = 'Experiment 1')
-
-models_exp2 <- joint_exp2 %>% 
-  rename(joint = mean) %>%
-  mutate(Descriptive = model_fit2(sound_dist, concept_dist)) %>%
-  mutate(Optimal = model_ideal2(sound_dist, concept_dist)) %>%
-  mutate(Auditory = model_sound2(sound_dist, concept_dist)) %>%
-  mutate(Visual = model_concept2(sound_dist, concept_dist)) %>%
-  gather(model, pred, Visual, Auditory, Optimal, Descriptive) %>%
-  mutate(experiment = 'Experiment 2')
-
-models_exp3 <- joint_exp3 %>% 
-  rename(joint = mean) %>%
-  mutate(Descriptive = model_fit3(sound_dist, concept_dist)) %>%
-  mutate(Optimal = model_ideal3(sound_dist, concept_dist)) %>%
-  mutate(Auditory = model_sound3(sound_dist, concept_dist)) %>%
-  mutate(Visual = model_concept3(sound_dist, concept_dist)) %>%
-  gather(model, pred, Visual, Auditory, Optimal, Descriptive) %>%
-  mutate(experiment = 'Experiment 3')
-
-models_all <- bind_rows (models_exp1, models_exp2, models_exp3)
-
-models_all$model <- factor(models_all$model, levels = c('Visual','Auditory', 'Optimal', 'Descriptive'))
-
-correlation_plot <- ggplot(models_all, 
-       aes(x = pred, y = joint, col = factor(concept_dist), 
-           shape = factor(sound_dist))) + 
-  geom_point()+
- #geom_pointrange(aes(ymin = summary_ci_lower, ymax = summary_ci_upper), 
-  #                position = position_dodge(width = .1), size=0.2) +
-
-  geom_abline(slope = 1, lty = 2) +
-  xlab("Predictions") +ylab("Human data")+
-  facet_grid(experiment ~ model)+
-theme(aspect.ratio = 0.7, 
-      axis.text=element_text(size=6),
-      strip.text.y = element_text(size = 8))+
-  guides(color=guide_legend(title="Visual Distance")) +
-  guides(shape=guide_legend(title="Auditory Distance"))
-
-#Correlation values
-
-#Exp 1
-optimal_1 <- subset(models_all, model=='Optimal' & experiment=='Experiment 1')
-descriptive_1 <- subset(models_all, model=='Descriptive' & experiment=='Experiment 1')
-auditory_1 <- subset(models_all, model=='Auditory' & experiment=='Experiment 1')
-visual_1 <- subset(models_all, model=='Visual' & experiment=='Experiment 1')
-
-R2_optimal_1  <- cor(optimal_1$joint, optimal_1$pred)^2 %>%
-  round(2)
-R2_descriptive_1 <- cor(descriptive_1$joint, descriptive_1$pred)^2 %>%
-  round(2)
-R2_auditory_1  <- cor(auditory_1$joint, auditory_1$pred)^2 %>%
-  round(2)
-R2_visual_1  <- cor(visual_1$joint, visual_1$pred)^2 %>%
-  round(2)
-
-#Exp 2
-optimal_2 <- subset(models_all, model=='Optimal' & experiment=='Experiment 2')
-descriptive_2 <- subset(models_all, model=='Descriptive' & experiment=='Experiment 2')
-auditory_2 <- subset(models_all, model=='Auditory' & experiment=='Experiment 2')
-visual_2 <- subset(models_all, model=='Visual' & experiment=='Experiment 2')
-
-R2_optimal_2  <- cor(optimal_2$joint, optimal_2$pred)^2  %>%
-  round(2)
-R2_descriptive_2 <- cor(descriptive_2$joint, descriptive_2$pred)^2 %>%
-  round(2)
-R2_auditory_2  <- cor(auditory_2$joint, auditory_2$pred)^2 %>%
-  round(2)
-R2_visual_2  <- cor(visual_2$joint, visual_2$pred)^2 %>%
-  round(2)
-
-#Exp 3
-optimal_3 <- subset(models_all, model=='Optimal' & experiment=='Experiment 3')
-descriptive_3 <- subset(models_all, model=='Descriptive' & experiment=='Experiment 3')
-auditory_3 <- subset(models_all, model=='Auditory' & experiment=='Experiment 3')
-visual_3 <- subset(models_all, model=='Visual' & experiment=='Experiment 3')
-
-R2_optimal_3  <- cor(optimal_3$joint, optimal_3$pred)^2 %>%
-  round(2)
-R2_descriptive_3 <- cor(descriptive_3$joint, descriptive_3$pred)^2 %>%
-  round(2)
-R2_auditory_3  <- cor(auditory_3$joint, auditory_3$pred)^2 %>%
-  round(2)
-R2_visual_3  <- cor(visual_3$joint, visual_3$pred)^2 %>%
-  round(2)
-
-```
-
-```{r bimodal, fig.cap = "Human responses vs.
-models' predictions across the three Experiments.
-Shape represents auditory distance from the target, and color represents visual distance from the target.", fig.align = "center", out.width = "400px", fig.width=7, fig.height=8}
-
-correlation_plot
-
-```
-
-Now we analyse the bimodal case. This is the case where the participants saw the pictures and heard the sounds.
-
-#### Descriptive model
-We first consider the descriptive model where all parameters are fitted to human responses in the bimodal condition.
-We found $\epsilon=$ `r BiasBi_val` CI [`r BiasBi_ci2`, `r BiasBi_ci1`], $\sigma^2_{Ab}=$ `r audVarBi_val` CI [`r audVarBi_ci1`, `r audVarBi_ci2`] and $\sigma^2_{Vb}=$ `r visVarBi_val` CI [`r visVarBi_ci1`, `r visVarBi_ci2`].
-Note that the precision of both the auditory and visual modalities decreased compared to the unimodal conditions.
-The descriptive model explained `r 100*R2_descriptive_1`% of total variance.
-
-#### Normative models
-We derived the predictions of the auditory, visual and optimal model by using the values of the variances derived from the unimodal conditions, and the response bias derived from the descriptive model.
-Figure\ \@ref(fig:bimodal) compares the predictions of these three models to human responses.
-The visual, auditory and optimal model explained, respectively, `r 100*R2_visual_1`%, `r 100*R2_auditory_1`%, and `r 100*R2_optimal_1`% of total variance.
-
-#### Cue combination and Modality preference
-We next analyzed the extent to which cue combination was performed in an optimal way, or whether there was a systematic preference for one modality when making decisions in the bimodal condition.
-We saw that response precision in the auditory modality was slightly higher than that of the visual modality (i.e., $\frac{1}{\sigma^2_A} > \frac{1}{\sigma^2_V}$ ).
-If modalities were weighed according to their relative reliability (that is, optimally), we would naturally expect the auditory modality to have a higher weight.
-But this is not what we mean by modality preference.
-Rather, the phrase refers to the case of potential sub-optimality where participants would rely on one modality beyond what is explained by the relative reliability of the optimal model.
-
-As explained above, modality preference can be characterized formally as a deviation from the decision threshold's slope predicted by the optimal model.
-Figure\ \@ref(fig:bias) shows the value of the slope derived from the descriptive model (i.e., $-\frac{\sigma^2_{Vb}}{\sigma^2_{Ab}}$) relative the slope of the optimal model (i.e., $-\frac{\sigma^2_V}{\sigma^2_A}$).
-The red dotted line represents the case where this proportion is optimal, meaning that both slopes are equal.
-The blue dotted lines represents the cases where the value of the slope from the descriptive model is double or half that of the optimal model, suggesting a preference for the auditory or the visual modality, respectively.
-Non-parametric resampling of the data showed no evidence of a deviation from the optimal prediction.
-
-## Discussion
-Overall, we found that the optimal model explained much of the variance in judgments, and largely more than what can be explained with the auditory or the visual models alone.
-The relatively high value of the coefficient of determination in the optimal model (`r 100*R2_optimal_1`%) suggests that participants were near-optimal in their responses.
-However, we see from Figure\ \@ref(fig:bimodal) that responses deviated from the optimal prediction in that they were slightly pulled toward chance (i.e., the value 0.5).
-This is due to the increase in the value of the variance associated with each modality.
-Note however that, despite this increase in randomness, our analysis of modality preference showed that the relative values of these variances were not different Figure\ \@ref(fig:bias).
-Thus, 1) the bimodal presentation introduced a certain level of randomness in the participants' responses, and 2) this increased randomness did not affect the relative weighting of both modalities, i.e., participants were weighting modalities according to their relative reliability.
-This situation corresponds to the first case of sub-optimally described in the predictions, above.
-
-In Experiment 1, we tested word recognition when there was multimodal uncertainty in terms of category membership only.
-In real life, however, tokens can undergo distortions due to noisy factors in the environment (e.g., car noise in the background, blurry vision in a foggy weather,..)\footnote{Note that we are considering environmental noise, which is different from the noise inherent to perception.}.
-In Experiment 2 and 3, we explore this additional level of uncertainty.
-
-# Experiment 2
-
-Imagine that the speaker generates a target production $t$ from an auditory category
-$t | A \sim N(\mu_{A}, \sigma^2_{A})$.
-In Experiment 1, we assumed that the observer could directly retrieve this production token.
-But if the observer is in a noisy environment, they do not hear exactly this produced target, but the target perturbed by noise.
-We assume this noise to be normally distributed: $a | t \sim N(t, \sigma^2_{N})$, and we integrate over $t$.
-We obtain the following simple expression:
-
-$$ a | A \sim N(\mu_{A}, \sigma^2_{A}+\sigma^2_{N})$$
-
-In this experiment, we explored the effect of this added noise on performance in our task.
-We tested a case where the background noise was added to the auditory modality.
-We were interested to know if participants would treat this new source of uncertainty as predicted by the optimal model, and whether noise in one modality would lead to some systematic preference for the non-noisy modality.
-
-## Methods
-
-### Participants
-
-A sample of `r N_all_2` participants was recruited online through Amazon Mechanical Turk.
-We used the same exclusion criteria as in the previous experiment.
-The final sample consisted of (N = `r N_good_2`) participants.
-
-### Stimuli and Procedure
-
-We used the same visual stimuli as in Experiment 1.
-We also used the same auditory stimuli, but we convolved each item with Brown noise of amplitude 1 using the audio editor Audacity (2.1.2) (signal to noise ratio XXXX).
-The procedure was exactly the same as in the previous experiment, except that test stimuli (but not the target) were presented with the new noisy auditory stimuli.
-
-## Results and analysis
-
-```{r echo=FALSE}
-
-#Bootstrap sample parameters
-
-lmfit <- function(data, indices) {
-
-  myd = data[indices, ]
-
-  s_data <- myd %>%
-    filter(condition == "sound")
-
-  v_data <- myd %>%
-    filter(condition == "concept")
-
-  j_data <- myd %>%
-    filter(condition == "joint")
-
-  s_nl <- nls(answer ~ 1/(1+(1-e)*exp((-4/vrA)*sound_dist+(8/vrA))), data=s_data, start = list(e=0, vrA=2), nls.control(warnOnly = TRUE))
-
- c_nl <- nls(answer ~ 1/(1+(1-e)*exp((-4/vrV)*concept_dist+(8/vrV))), data=v_data, start = list(e=0, vrV=2), nls.control(warnOnly = TRUE))
-
- j_nl <- nls(answer ~ 1/(1+(1-e)*exp((-4/vrA_j)*sound_dist+(-4/vrV_j)*concept_dist+(8/vrA_j)+(8/vrV_j))), data=j_data, start = list(e=0, vrA_j=2, vrV_j=2), nls.control(warnOnly = TRUE))
-
-  s_va <- coef(s_nl)["vrA"]
-  s_e <- coef(s_nl)["e"]
-
-  v_va <- coef(c_nl)["vrV"]
-  v_e <- coef(c_nl)["e"]
-
-  decision_ideal=v_va/s_va
-
-  j_va_s=coef(j_nl)["vrA_j"]
-  j_va_v=coef(j_nl)["vrV_j"]
-  j_e=coef(j_nl)["e"]
-
-  decision_fit=j_va_v/j_va_s
-
-  preference = decision_fit/decision_ideal
-
-  MyBoot=c(s_va, s_e, v_va, v_e, j_va_s, j_va_v, j_e, decision_ideal, decision_fit, preference)
-
-  return(MyBoot)
-
-  }
-
-results1 <- boot(data=exp2_good, statistic = lmfit, R = 10000)
-
-#Auditory variance:
-audVar=boot.ci(results1, index = 1, type = c("bca"), conf = 0.95)
-audVar_val=audVar$t0 
-audVar_ci1=audVar$bca[4]
-audVar_ci2=audVar$bca[5]
-
-#Auditory bias:
-audBias=boot.ci(results1, index = 2, type = c("bca"), conf = 0.95)
-audBias_val=audBias$t0 
-audBias_ci1=audBias$bca[4]
-audBias_ci2=audBias$bca[5]
-
-#Visual variance:
-visVar=boot.ci(results1, index = 3, type = c("bca"), conf = 0.95)
-visVar_val=visVar$t0 
-visVar_ci1=visVar$bca[4]
-visVar_ci2=visVar$bca[5]
-
-#Visual bias:
-visBias=boot.ci(results1, index = 4, type = c("bca"), conf = 0.95)
-visBias_val=visBias$t0 
-visBias_ci1=visBias$bca[4]
-visBias_ci2=visBias$bca[5]
-
-#Bimodal Auditory variance:
-audVarBi=boot.ci(results1, index = 5, type = c("bca"), conf = 0.95)
-audVarBi_val=audVarBi$t0 
-audVarBi_ci1=audVarBi$bca[4]
-audVarBi_ci2=audVarBi$bca[5]
-
-#Bimodal Visual variance:
-visVarBi=boot.ci(results1, index = 6, type = c("bca"), conf = 0.95)
-visVarBi_val=visVarBi$t0 
-visVarBi_ci1=visVarBi$bca[4]
-visVarBi_ci2=visVarBi$bca[5]
-
-#Bimodal bias:
-BiasBi=boot.ci(results1, index = 7, type = c("bca"), conf = 0.95)
-BiasBi_val=BiasBi$t0 
-BiasBi_ci1=BiasBi$bca[4]
-BiasBi_ci2=BiasBi$bca[5]
-
-#Ideal modality wieghing
-prefIdeal=boot.ci(results1, index = 8, type = c("bca"), conf = 0.95)
-prefIdeal_val=prefIdeal$t0 
-prefIdeal_ci1=prefIdeal$bca[4]
-prefIdeal_ci2=prefIdeal$bca[5]
-
-#fit modality wieghing
-prefFit=boot.ci(results1, index = 9, type = c("bca"), conf = 0.95)
-prefFit_val=prefFit$t0 
-prefFit_ci1=prefFit$bca[4]
-prefFit_ci2=prefFit$bca[5]
-
-#Modality bias 
-bias=boot.ci(results1, index = 10, type = c("bca"), conf = 0.95)
-bias_val_2=bias$t0 
-bias_ci1_2=bias$bca[4]
-bias_ci2_2=bias$bca[5]
-
-```
-
-### Unimodal conditions
-
-We fit a model for each modality, collapsed across all participants.
-For the auditory modality, our parameter estimates were $\epsilon_A=$ `r audBias_val` CI [`r audBias_ci2`, `r audBias_ci1`] and $\sigma^2_A+\sigma^2_N=$ `r audVar_val` CI [`r audVar_ci1`, `r audVar_ci2`].
-For the visual modality, we found $\epsilon_V=$ `r visBias_val` CI [`r visBias_ci2`, `r visBias_ci1`] and $\sigma^2_V=$ `r visVar_val` CI [`r visVar_ci1`, `r visVar_ci2`].
-Figure\ \@ref(fig:unimodal) shows responses in the unimodal conditions as well as the corresponding fits.
-The visual data is a replication of the vidual data in Experiment 1.
-As for the auditory data, we see that, in contrast to Experiment 1, responses were less categorical/flatter (showing more uncertainty).
-
-### Bimodal condition
-
-#### Descriptive model
-We fit the descriptive model to human responses in the bimodal condition, collapsed across all articipants.
-We estimated $\epsilon=$ `r BiasBi_val` CI [`r BiasBi_ci2`, `r BiasBi_ci1`], $\sigma^2_{Ab}+\sigma^2_{Nb}=$ `r audVarBi_val` CI [`r audVarBi_ci1`, `r audVarBi_ci2`], and $\sigma^2_{Vb}=$ `r visVarBi_val` CI [`r visVarBi_ci1`, `r visVarBi_ci2`].
-The fit explained `r R2_descriptive_2`% of total variance.
-
-#### Normative models
-We derived the predictions of the auditory, visual and optimal model by using the values of the variances derived from the unimodal conditions, and the response bias derived from the descriptive model.
-Figure\ \@ref(fig:bimodal) compares the predictions of these three models to human responses.
-The visual, auditory and optimal model explained, respectively, `r 100*R2_visual_2`%, `r 100*R2_auditory_2`%, and `r 100*R2_optimal_2`% of total variance.
-Note that, in contrast to Experiment 1, the visual model explains more variance than the auditory model.
-
-#### Modality preferences
-Participants' decision threshold suggested a preference for the visual modality (the non-noisy modality).
-Indeed non-parametric resampling of the data showed a decrease in the value of the slope in the descriptive model compared to the optimal model Figure\ \@ref(fig:bias).
-
-## Discussion
-We found, similar to Experiment 1, that participants were generally near optimal (explaining  `r 100*R2_optimal_2`% of total variance), and that the optimal model explained more variance than the auditory or the visual models alone.
-We also found a similar discrepancy from the optimal model as precision dropped for both the auditory and the visual modalities.
-As for the weghting scheme used by participants, contrary to Experiment 1 where modalities were weighted according to their optimal relative reliability, we found in this experiment that the visual modality had a greater weight than what is  expected from its relative reliability.
-This situation corresponds to the second case of sub-optimally described in the predictions above.
-
-In Experiment 2, we tested the case where we added background noise to the auditory modality. In Experiment 3, we test the situation where we added noise to the visual modality.
-
-# Experiment 3
-
-We follow exactly the same formal reasoning in this case, as we did in Experiment 2.
-Imagine that the speaker points towards a target referent $t_v$ from a visual category $t_v | V \sim N(\mu_{V}, \sigma^2_{V})$.
-If the observer is in a noisy environment (e.g., foggy weather), they might see this target referent in a blurry way.
-We assume the blur to be normally distributed: $a | t_v \sim N(t_v, \sigma^2_{N})$, and we integrate over $t_v$.
-We obtain an expression formally similar to the one obtained in Experiment 2:
-
-$$ v | V \sim N(\mu_{V}, \sigma^2_{V}+\sigma^2_{N})$$
-
-Below we explored the effect of this added visual blur on performance in our task.
-
-## Methods
-
-### Participants
-A planned sample of `r N_all_3` participants was recruited online through Amazon Mechanical Turk.
-We used the same exclusion criteria as in the previous experiment.
-The final sample consisted of (N = `r N_good_3`) participants.
-
-### Stimuli and Procedure
-We used the same auditory stimuli as in Experiment 1.
-We also used the same visual stimuli, but we blurred the tokens using the editor XXX (signal to noise ration XXX).
-The experimental procedure was exactly the same as in the previous Experiments.
-
-## Results and analysis
-
-```{r echo=FALSE}
-
-#Bootstrap sample parameters
-
-lmfit <- function(data, indices) {
-
-  myd = data[indices, ]
-
-  s_data <- myd %>%
-    filter(condition == "sound")
-
-  v_data <- myd %>%
-    filter(condition == "concept")
-
-  j_data <- myd %>%
-    filter(condition == "joint")
-
-  s_nl <- nls(answer ~ 1/(1+(1-e)*exp((-4/vrA)*sound_dist+(8/vrA))), data=s_data, start = list(e=0, vrA=2), nls.control(warnOnly = TRUE))
-
- c_nl <- nls(answer ~ 1/(1+(1-e)*exp((-4/vrV)*concept_dist+(8/vrV))), data=v_data, start = list(e=0, vrV=2), nls.control(warnOnly = TRUE))
-
- j_nl <- nls(answer ~ 1/(1+(1-e)*exp((-4/vrA_j)*sound_dist+(-4/vrV_j)*concept_dist+(8/vrA_j)+(8/vrV_j))), data=j_data, start = list(e=0, vrA_j=2, vrV_j=2), nls.control(warnOnly = TRUE))
-
-  s_va <- coef(s_nl)["vrA"]
-  s_e <- coef(s_nl)["e"]
-
-  v_va <- coef(c_nl)["vrV"]
-  v_e <- coef(c_nl)["e"]
-
-  decision_ideal=v_va/s_va
-
-  j_va_s=coef(j_nl)["vrA_j"]
-  j_va_v=coef(j_nl)["vrV_j"]
-  j_e=coef(j_nl)["e"]
-
-  decision_fit=j_va_v/j_va_s
-
-  preference = decision_fit/decision_ideal
-
-  MyBoot=c(s_va, s_e, v_va, v_e, j_va_s, j_va_v, j_e, decision_ideal, decision_fit, preference)
-
-  return(MyBoot)
-
-  }
-
-results1 <- boot(data=exp3_good, statistic = lmfit, R = 10000)
-
-#Auditory variance:
-audVar=boot.ci(results1, index = 1, type = c("bca"), conf = 0.95)
-audVar_val=audVar$t0 
-audVar_ci1=audVar$bca[4]
-audVar_ci2=audVar$bca[5]
-
-#Auditory bias:
-audBias=boot.ci(results1, index = 2, type = c("bca"), conf = 0.95)
-audBias_val=audBias$t0 
-audBias_ci1=audBias$bca[4]
-audBias_ci2=audBias$bca[5]
-
-#Visual variance:
-visVar=boot.ci(results1, index = 3, type = c("bca"), conf = 0.95)
-visVar_val=visVar$t0 
-visVar_ci1=visVar$bca[4]
-visVar_ci2=visVar$bca[5]
-
-#Visual bias:
-visBias=boot.ci(results1, index = 4, type = c("bca"), conf = 0.95)
-visBias_val=visBias$t0 
-visBias_ci1=visBias$bca[4]
-visBias_ci2=visBias$bca[5]
-
-#Bimodal Auditory variance:
-audVarBi=boot.ci(results1, index = 5, type = c("bca"), conf = 0.95)
-audVarBi_val=audVarBi$t0 
-audVarBi_ci1=audVarBi$bca[4]
-audVarBi_ci2=audVarBi$bca[5]
-
-#Bimodal Visual variance:
-visVarBi=boot.ci(results1, index = 6, type = c("bca"), conf = 0.95)
-visVarBi_val=visVarBi$t0 
-visVarBi_ci1=visVarBi$bca[4]
-visVarBi_ci2=visVarBi$bca[5]
-
-#Bimodal bias:
-BiasBi=boot.ci(results1, index = 7, type = c("bca"), conf = 0.95)
-BiasBi_val=BiasBi$t0 
-BiasBi_ci1=BiasBi$bca[4]
-BiasBi_ci2=BiasBi$bca[5]
-
-#Ideal modality wieghing
-prefIdeal=boot.ci(results1, index = 8, type = c("bca"), conf = 0.95)
-prefIdeal_val=prefIdeal$t0 
-prefIdeal_ci1=prefIdeal$bca[4]
-prefIdeal_ci2=prefIdeal$bca[5]
-
-#fit modality wieghing
-prefFit=boot.ci(results1, index = 9, type = c("bca"), conf = 0.95)
-prefFit_val=prefFit$t0 
-prefFit_ci1=prefFit$bca[4]
-prefFit_ci2=prefFit$bca[5]
-
-#Modality bias 
-bias=boot.ci(results1, index = 10, type = c("bca"), conf = 0.95)
-bias_val_3=bias$t0 
-bias_ci1_3=bias$bca[4]
-bias_ci2_3=bias$bca[5]
-
-```
-
-### Unimodal conditions
-We fit a model for each modality, collapsed across participants.
-For the auditory modality, our parameter estimates were $\epsilon_A=$ `r audBias_val` CI [`r audBias_ci2`, `r audBias_ci1`] and $\sigma^2_A=$ `r audVar_val` CI [`r audVar_ci1`, `r audVar_ci2`].
-For the visual modality, we found $\epsilon_V=$ `r visBias_val` CI [`r visBias_ci2`, `r visBias_ci1`] and $\sigma^2_V+\sigma^2_N=$ `r visVar_val` CI [`r visVar_ci1`, `r visVar_ci2`].
-Figure\ \@ref(fig:unimodal) shows responses in the unimodal conditions as well as the corresponding fits.
-The auditory data is a replication of the auditory data in Experiment 1. As for the visual data, we see that, in contrast to Experiment 1 and 2, responses were flatter, showing much more uncertainty.
-
-### Bimodal condition
-
-#### Descriptive model
-We fit the descriptive model to human responses in the bimodal condition, collapsed across participants.
-We estimated $\epsilon=$ `r BiasBi_val` CI [`r BiasBi_ci2`, `r BiasBi_ci1`], $\sigma^2_{Ab}=$ `r audVarBi_val` CI [`r audVarBi_ci1`, `r audVarBi_ci2`], and $\sigma^2_{Vb}+\sigma^2_{Nb}=$ `r visVarBi_val` CI [`r visVarBi_ci1`, `r visVarBi_ci2`].
-The fit explained `r 100*R2_descriptive_3`% of total variance.
-
-#### Normative models
-We derived the predictions of the auditory, visual and optimal model by using the values of the variances derived from the unimodal conditions, and the response bias derived from the descriptive model.
-Figure\ \@ref(fig:bimodal) compares the predictions of these three models to the human responses.
-The visual, auditory and optimal model explained, respectively, `r 100*R2_visual_3`%, `r 100*R2_auditory_3`%, and `r 100*R2_optimal_3`% of total variance.
-
-#### Modality preferences
-Participants' decision threshold suggested a preference for the auditory modality (the non-noisy modality).
-Indeed non-parametric resampling of the data showed an increase in the value of the slope in the descriptive model compared to the optimal model Figure\ \@ref(fig:bias).
-
-## Discussion
-We found that the optimal model accounted for almost all the variance ($r^2 =$ `r R2_optimal_3`).
-However, whereas in previous experiments, the optimal model explained more variance than the auditory or the visual models, here the auditory model explained at least as much variance ($r^2 =$ `r R2_auditory_3`).
-Thus, though participants were still sensitive to variation in the noisy visual data in the unimodal condition, they tended to ignore this information in the bimodal condition, and relied almost exclusively on the non-noisy auditory modality.
-This behaviour is not so much a qualitative difference from Experiment 2 (where participants relied on both the noisy and the non-noisy modality in the bimodal condition), as much as it is the result of a floor effect.
-Indeed, noise made the visual modality way less steep and barely perceptible in the unimodal condition Figure\ \@ref(fig:unimodal).
-So when we had an additional general drop in precision in the bimodal condition (similar to what we found in Experiment 1 and 2),  participants were no longer able to extract any useful information.
-The reason why we saw this floor effect when we added noise to the visual modality (Experiment 3), and not when added noise to the auditory modality (Experiment 2), is the fact that our visual stimuli was originally perceived less categorically and with less certainty than the auditory data was.
-This made it more likely for the visual categorization function to become flat and uninformative after a few drops in precision due to noise on the one had, and to the randomness induced by the arbitrary association on the other hand.
-
-The general finding corresponds to the third case of sub-optimality described above.
-Indeed, precision dropped for both modalities in the bimodal condition compared to the unimodal condition.
-But the drop was much greater for the visual modality, resulting in a much lower weight assigned to it than what is expected from its optimal relative reliability.
-Therefore, just like participants over-relied on the visual modality when the auditory modality was noisy (Experiment 2), they also over-relied on the auditory modality when the visual modality was noisy (Experiment 3).
-
-```{r }
-#Modality bias
-
-preference = c(bias_val_1, bias_val_2, bias_val_3 )
-experiment =c("Exp 1 \n", "Exp 2 \n (noisy audio)", "Exp 3 \n (noisy visual)")
-ci_low=c(bias_ci1_1, bias_ci1_2, bias_ci1_3)
-ci_up=c(bias_ci2_1, bias_ci2_2, bias_ci2_3)
-
-pref = data.frame(preference, ci_low, ci_up)
-
-bias <- ggplot(pref, 
-       aes(x = experiment, y=preference)) +
-geom_point(size=3)+
-  geom_errorbar(aes(ymin = ci_low, ymax = ci_up), 
-                  width = 0.1,
-                  position = position_dodge(width = 0.1))+
-  geom_hline(yintercept = 1, linetype=2, color="red", size=1)+
-
-  geom_hline(yintercept = 0.5, linetype=2, color="blue")+
-
-  geom_hline(yintercept = 2, linetype=2, color="blue")+
-
-  theme(aspect.ratio = 1, axis.text=element_text(size=10))+
-  xlab("") +ylab("Relative weighing")+
-  scale_y_log10(breaks=c(0.5,1,2),labels=c("Visual bias","Optimal","Auditory bias"))
-  #coord_cartesian(ylim=c(0, 2.5))
-
-```
-
-```{r bias, fig.cap = "Relative weighing of evidence from the auditory stimulus vs.
-evidence from the visual stimulus across the three Experiments (log-scaled).
-The red dashed  line  shows the  prediction  of the model  if the weighting is optimal,  and the  blue dashed lines  show   predictions if participants deviated from  optimality by relying  twice  as much  on the meaning  category  (strong meaning bias) or twice   as  much  on  the sound category (strong  sound bias).", fig.align = "center", out.width = "400px"}
-bias
-
-```
-
-# General Discussion
-Understanding language, such as word-referent associations, often requires both the ability to combine arbitrary multimodal input, and the ability to deal with uncertainty.
-In this work, we explored a case where both abilities were at play.
-We studied the case of identifying a word when both its form (auditory) and its referent (visual) were ambiguous with respect to their category membership (Experiment 1), when the form was perturbed with additional background noise (Experiment 2), and when the referent was perturbed with additional visual noise (Experiment 3).
-We introduced a model that instantiated an ideal/optimal observer, predicting how information from each modality could be combined in an optimal way.
-In all Experiments, participants showed many patterns of optimal behaviour.
-Quantitatively speaking, the optimal model accounted, respectively, for `r 100*R2_optimal_1`%, `r 100*R2_optimal_2`%, and `r 100*R2_optimal_3`% of the variance in human data.
-When compared to the predictions of the visual or the auditory models, participants generally relied on both modalities to make their decisions in the bimodal condition.
-Indeed, in Experiment 1 and 2, the optimal model accounted for more variance in human data than the auditory or the visual models did.
-In Experiment 3, participants appeared to rely on one modality, but as we explained in the intermediate discussion, this is likely a floor effect, due to the fact that noise made the visual input barely perceivable.
-Moreover, in Experiment 1, which did not involve background noise, participants not only relied on both modalities, but weighted these modalities according to the prediction of the optimal model, that is, according to their relative reliability.
-
-Besides these patterns of optimal behavior, we documented two interesting cases of sub-optimality.
-First, in all Experiments, the variance associated with each modality increased in the bimodal condition compared to the unimodal conditions.
-This means that participants responded slightly more randomly in the bimodal condition than they did in the unimodal conditions.
-This finding contrasts with research on optimal multisensory integration where associations tend to lead to a higher precision [@ernst02].
-However, there is a crucial difference between these two situations.
-Research on optimal multisensory integration deals with redundant multimodal cues, and these cues are integrated into a unified percept (such as the size or the location of an object).
-In contrast, the word-referent association is usually arbitrary and, in particular, the cues are not supposed to correlate perceptually.
-Therefore the brain cannot form a unified percept, rather, it must encode information separately from both modalities and retain this encoding through the decision making process.
-Retaining two separate cues at the same time instead of forming one unified percept (as in multisensory integration of redundant cues), or instead of retaining only one cue (as in the unimodal case), is likely to place extra-demand on cognitive resources, which, in turn, can cause general performance to drop.
-Indeed, there is evidence that cognitive load has a detrimetnal effect on word recognition, which can be explained by a reduction in perceptual acuity [@mattys11].
-
-The second case of sub-optimality is related to how participants weighed the cues from the visual and the auditory in a noisy context.
-In contrast to Experiment 1 where the combination was indistinguishable from the optimal prediction, resutls of Experiment 2 and 3 which involved noise in one modality, showed that participants had a preference for the other (non-noisy) modality.
-Crucially, this preference was beyond what is explained by the relative reliability (hence the sub-optimality).
-From previous empirical studies, we know that when the speech signal is degraded, people tend to compensate by relying more on other sources of information such as the accompanying visual cues (i.e., lip movements) or the semantic/syntactic context [see @mattys12 for a review].
-However, and generally speaking, these studies do not differentiate between an optimal compensatory strategy (i.e., relying more on the alternative source while using all information still available in the distorted signal), and a sub-optimal strategy (i.e., relying more on the alternative source while ignoring at least some of the information still available in the distorted signal).
-The sub-optimal behavior is possibly related to the fact that language understanding under degraded listening conditions is cognitively more taxing than language understanding under normal conditions [@Ronnberg10].
-This fact can lead to a preference/bias towards alternative sources of information when these sources are available.
-
-## Implication for word learning
-
-In this study, we explored the mechanism of word identification, but in a simple case when the underlying visual and auditory categories were familiar.
-Indeed, on the visual side, cat and dog tokens belong obviously to existing visual categories.
-On the auditory side, though the words ("ada"/"aba") are novel, the phonemic categories that differentiate the words are familiar (i.e., /d/ and /b/).
-In the context of early word learning, however, children are often learning both the categories and their mapping at the same time.
-In fact, children start learning visual and sound categories at an early age [e.g., @quinn93;@werker1984], and there is evidence that word-referent-like interaction operates at the same time, even when the categories are not yet fully mastered [e.g., @waxman1995; @yeung09].
-In fact, @fourtassi2014a proposed that this interaction can create a synergy (or a bootstrapping effect) whereby progress made on one level (e.g., the meaning categories) can benefit the other level (the sound categories).
-
-In what follows we explain how an account that combines both category learning and optimal multimodal integration can proceed, and how such account can provide us with a useful developmental framework.
-In the light of this framework, we speculate about possible new interpretation of some puzzling results in early word learning [@stager1997 and seq].
-For starters, remember that one assumption of the model is that visual and auditory categories can be characterized with a variance that determines their precision/reliability.
-At the behavioral level, the variance is related to the shape of the categorization function: a small variance corresponds to a rather steep categorization function, meaning that one can tell with high certainty whether or not a token belongs to the category at hand.
-Vice versa, a large value of the variance corresponds to a rather flat categorization function, which means that for most tokens, one cannot tell with high certainty whether or not these tokens belong to the category at hand.
-
-How can this formal characterization fit in a developmental scenario?
-One could imagine that, initially, visual and auditory categories have relatively large variances, and that development consists in reducing the values of the variances as evidence accumulates, making the categories more refined and precise.
-A scenario similar to this one has been previously suggested to explain the development of early sound categories.
-For example, @yoshida2009 suggested that the early categories may be noisier or that they may be encoded with relatively lower confidence.
-For the semantic categories, we can find similar (although perhaps not identical) ideas.
-For instance, Clark (1973) suggested that the initial meaning categories tend to be larger than adult categories, since fewer features are used to pick out referents (e.g., dog for all four-legged animal, ball for all round objects).
-
-The combination of this developmental scenario in terms of category variance with the optimal integration account introduced in this paper provides possible new insights into the mechanism of word learning.
-Let's elucidate this idea through an example in the developmental literature.
-@stager1997 showed that 14 m.o (as opposed to 17 m.o) have difficulties mapping two minimally different sounds (e.g., "bih"/"dih") to two novel objects, despite the fact that they can perceptually differentiate these sounds.
-Our proposal explains these patterns of failure and success in terms of developmental changes in the variances associated with the visual and phonological categories, combined with the ability to integrate sound and visual cues according to their reliability.
-Suppose that both members of a given sound contrast ("bin"/"din") initially fall within the uncertainty range of a single sound category.
-If this uncertainty diminishes with age (as the category gets more refined), then what used to be likely at a certain point in development (e.g., 14 m.o), may later become unlikely.
-In particular, at 17, m.o, it may become necessary to attribute the sound contrast to two neighboring categories instead of a single one.
-But how can 14 m.o possibly consider one broad category for both sounds if these sounds are paired with different objects?
-This is where the optimal combination account may come into play.
-Indeed, even if the objects are perceptually different, they may still be similar in the 14 m.o's early semantic space.
-If babies make categorical decision based on both auditory and visual cues, then having evidence that the auditory tokens belong to the same category can prompt them to consider the possibility that even the objects are variations within the same (broad) semantic category.
-Thus, 14 m.o may be learning one broad word-referent association instead of two specific associations.
-So what was conidered a "failure" in learning might, in fact, be the optimal decision within the 14 m.o's own developmental context!
-
-This account makes two main predictions.
-First, if the sounds are more acoustically different (e.g., "lif"/"neem" instead of ""bih"/"dih"), babies would be more likely to posit and learn two word-referent associations, because there would be more evidence pointing in that direction from the auditory side.
-Second, if the objects are more semantically distant (a living object vs.
-a non-living object, instead of the two perceptually different toys used in the original study), babies would be more likely to posit and learn two word-referent associations, because now there would be more evidence pointing in that direction from the visual side.
-In fact, @stager1997 tested and proved the first prediction.
-The second prediction remains to be tested.
-If proven, it would provides support to the optimal combination account in early language learning.
-
-# References
-```{r create_r-references}
-r_refs(file = "references.bib")
-```
-
-\setlength{\parindent}{-0.5in}
-\setlength{\leftskip}{0.5in}
+\caption{Modality preference is characterized as a deviation from the optimal decision threshold.
+A) The decision thresholds of both the optimal and the descriptive models (solid red and black lines respectively).
+Deviation from optimality is compared to two hypothetical cases of modality preference.
+In these cases, deviation from  optimality is due to over-lying on the visual or the auditory input (green and blue dotted lines, respectively) by a factor of 2.
+B) The value of the decision threshold's slope derived from the descriptive model relative to that of the optimal model.
+Error bars represent 95\% confidence intervals over the distribution obtained through non-parametric resampling.}\label{fig:bias}
+\end{figure}
+
+\section{General Discussion}\label{general-discussion}
+
+When identifying a spoken word under uncertainty, one often needs to
+combine and make the most of the available multimodal cues. While most
+previous studies focused on the case of audio-visual speech where people
+combine cues from speech and facial features, this work explored the
+case of identifying an ambiguous word when the available multimodal cues
+are speech and the visual referent. More specifically, we conducted an
+ideal observer analysis of the task whereby a model provided predictions
+about how information from each modality should be combined in an
+optimal fashion. The predictions of the model were tested in a series of
+three experiments where instances of both the form and the referent were
+ambiguous with respect to their category membership only (Experiment 1),
+when instances of the form were perturbed with additional background
+noise (Experiment 2), and when instances of the referent were perturbed
+with additional visual noise (Experiment 3).
+
+In all Experiments, we found many patterns of optimal behaviour.
+Quantitatively speaking, the optimal model accounted, respectively, for
+89\%, 91\%, and 97\% of the variance in mean responses. When compared to
+the predictions of the visual or the auditory models, participants
+generally relied on both modalities to make their decisions in the
+bimodal condition. Indeed, in Experiment 1 and 2, the optimal model
+accounted for more variance in mean responses than the auditory or the
+visual models did. In Experiment 3, participants appeared to rely on one
+modality, but this was likely a floor effect, due to the fact that noise
+made the visual input barely perceivable. In Experiment 1, which did not
+involve background noise, participants not only relied on both
+modalities, but generally weighted these modalities according to the
+prediction of the optimal model, that is, according to their relative
+reliability. At the individual level, however, we found evidence of a
+between-subject variation: Some participants relied slighly more on the
+visual modality, whereas others relied slighly more on the auditory
+modality.
+
+We documented two major cases of sub-optimality. First, in all
+Experiments, the variance associated with each modality increased in the
+bimodal condition compared to the unimodal conditions. This means that
+participants responded slightly more randomly in the bimodal condition
+than they did in the unimodal conditions. This finding contrasts with
+research on multisensory integration where associations tend to lead to
+a higher precision (e.g., Ernst \& Banks, 2002). Nevertheless, there is
+a crucial difference between these two situations. Research on
+multisensory integration (of which audio-visual speech is arguably an
+instance) deals with redundant multimodal cues, and these cues are
+integrated into a unified percept. In contrast, the word-referent
+association is usually arbitrary and, in particular, the cues are not
+expected to be correlated perceptually. Therefore the mind cannot form a
+unified percept, rather, it must encode information separately from both
+modalities and retain this encoding through the decision making process.
+Retaining two separate cues at the same time instead of forming one
+unified percept (as in multisensory integration of redundant cues), or
+instead of retaining only one cue (as in the unimodal case), is likely
+to place extra-demand on cognitive resources, which, in turn, can cause
+general performance to drop. Indeed, there is evidence that cognitive
+load has a detrimental effect on word recognition, which can be due to a
+reduction in perceptual acuity (Mattys \& Wiget, 2011). Similar to our
+finding, previous experimental studies reported that in both children
+and adults, identifying new ambiguous form-referent mappings is usually
+associated with what appears to be a decrease in speech perception
+acuity (Pajak, Creel, \& Levy, 2016; Stager \& Werker, 1997). Hofer and
+Levy (2017) provided a probabilistic model of this phenomenon, which
+they similarly characterized as an increase in the noise variance of the
+auditory modality. Our finding replicates this previously documented
+fact, and additionally suggests that the reduction in perceptual acuity
+occurs simultaneously in both the auditory and the visual modalities.
+
+The second case of sub-optimality is related to how participants weighed
+the cues from the visual and the auditory modalities in a noisy context.
+In contrast to Experiment 1 where the combination was indistinguishable
+from the optimal prediction, results of Experiment 2 and 3 which both
+involved background noise in one modality, showed that participants had
+a systematic preference for the other (non-noisy) modality. From
+previous empirical studies, we know that when the speech signal is
+degraded, people tend to compensate by relying more on other sources of
+information such as the accompanying visual cues (i.e., lip movements)
+or the semantic/syntactic context (see Mattys, Davis, Bradlow, \& Scott,
+2012 for a review). However, and generally speaking, these studies do
+not differentiate between an optimal compensatory strategy (i.e.,
+relying more on the alternative source while using all information still
+available in the distorted signal), and a sub-optimal strategy (i.e.,
+relying more on the alternative source while ignoring at least some of
+the information still available in the distorted signal). The formal
+approach followed in this paper allowed us to tease apart these two
+possibilities, and the analysis supports the sub-optimal compensatory
+strategy: The preference for the non-noisy modality is above and beyond
+what can be explained by the relative reliability alone, meaning that
+the participant tend to ignore at least part of the information still
+available in the noisy modality.
+
+This second case of sub-optimal behavior is possibly related to the fact
+that language understanding under degraded listening conditions is
+cognitively more taxing than language understanding under normal
+conditions (Ronnberg, Rudner, Lunner, \& Zekveld, 2010). This fact can
+lead to a preference/bias towards alternative sources of information
+when these sources are available. One could explain this phenomenon in
+terms of the metacognitive experience about the fluency with which
+information is processed. The perceived perceptual fluency (e.g., the
+ease with which a stimulus' physical identity can be identified) can
+affect a wide variety of human judgements (see Schwarz, 2004 for a
+review). In particular, variables that improve fluency tends to increase
+liking/preference (Reber, Winkielman, \& Schwarz, 1998). In our case,
+the subjective experience of lower fluency in the noisy modality might
+cause people to underestimate information that can be extracted from
+this modality, especially when presented simultaneously with a higher
+fluency alternative.
+
+In this study, we tested the extent to which people would be optimal in
+combining uncertain auditory and visual cues to recognize words. This
+required that we use a case of double ambiguity, that is, a case where
+both the word forms (\enquote{ada}-\enquote{aba}) and the referents
+(cat-dog) were similar and, thus, confusable. One could wonder about the
+extent to which such case occurs in real languages? Cross-linguistic
+corpus analyses suggest that the lexical encoding tends towards double
+ambiguity in many languages (Dautriche, Mahowald, Gibson, \& Piantadosi,
+2017; Monaghan, Shillcock, Christiansen, \& Kirby, 2014; Tamariz, 2008).
+For instance, Dautriche et al. (2017) analysed 100 languages and found
+that word that are similar phonologically tend to be similar
+semantically as well, beyond what could be explained by chance.
+Crucially, they found this trend in a set of monomorphemic lemmas in
+four languages, suggesting that the effect is not driven by
+morphological regularities. These studies suggest that the case of
+double uncertainty, though perhaps not pervasive, could be a real issue
+in language as it increase the probability of confusability. Moreover,
+it is important to keep in mind that ambiguity in both the form and the
+referent can be induced by an external noisy context even when these
+forms and referents are not confusable in normal situations.
+
+Though we only tested adults in this paper, the problem of word
+recognition under uncertainty, as well as the need to make the most of
+ambiguous cues, is a particularly pressing issue for children. In fact,
+whereas adults are mostly faced with uncertainty in the \emph{input},
+children have to deal with the additional uncertainty that results from
+their early unrefined \emph{representations} of both phonological and
+semantic categories. For example, upon hearing a noisy instance of
+\enquote{bee}, adults may have to decide whether the speaker intended to
+say \enquote{pea} or \enquote{bee}, but children can additionally be
+uncertain whether \enquote{bee} is a different word from \enquote{pee}
+(as opposed to, say, a valid within category variation), especially if
+these similar sounding words are newly learned (Creel, 2012; Merriman \&
+Schuster, 1991; Stager \& Werker, 1997; Swingley, 2016; White \& Morgan,
+2008). Though new word form representation can be shown to be
+differentiated under some circumstances (e.g., Yoshida, Fennell,
+Swingley, \& Werker, 2009), this differentiation is still not mature
+enough and is probably noisier than the adult-like representation and/or
+encoded with lower confidence (see Swingley, 2007).
+
+At the semantic level, early representations have, similarly, an
+intrinsically fragile and uncertain status. For example, upon seeing a
+bee in a foggy weather, adults may be uncertain if they saw a bee or a
+fly. But on top of this perceptual uncertainty, children may not be
+certain if the semantic category being named is that of bees and only
+bees, or if it includes other small flying insects like flies and
+beetles. In fact, though children can be fast at learning a first
+approximation of a given word's referent (Carey \& Bartlett, 1978), the
+refinement of this early approximation into a mature semantic category
+is a slow and gradual process (see also Bion, Borovsky, \& Fernald,
+2013; Carey, 2010; Fernald, Perfors, \& Marchman, 2006; McMurray, Horst,
+\& Samuelson, 2012). Among other things, children have to enrich this
+early representation with new features, and revise its extension in the
+light of new referential exposures.
+
+Thus, uncertainty in the representation associated with one modality
+(e.g., a bee and a fly) can be mitigated through the possibly more
+differentiated representations associated with the other modality (e.g.,
+the sound \enquote{bee} is acoustically different from the sound
+\enquote{fly}). That being said, a multi-modal cue combination strategy
+might help children not only recognize an individual word instance, but
+also refine the underlying phonological and semantic representations in
+the process. Previous research in early word learning has---whether
+implicitly or explicitly---largely treated the process of learning form
+and of learning meaning as independent. However, the developmental data
+reviewed above shows that children do not wait to have completed the
+acquisition of form to start learning meanings, and that both form and
+meaning representations develop, rather, in a parallel fashion. A few
+studies pointed to the possibility of an interaction between sound and
+meaning in early acquisition. For instance, Waxman and Markow (1995)
+showed that labeling various objects with the same name helps infants
+form the broad semantic category (but see Sloutsky \& Napolitano, 2003).
+Vice versa, Yeung and Werker (2009) showed that pairing similar sounds
+with different objects help infants pay attention to subtle phonological
+contrasts. The present study proposes a first step towards a formal
+framework where accounts of sound-meaning synergy in development can be
+unified and further explored. For example, one could imagine that,
+initially, visual and auditory categories have relatively large noise
+variances, and that development consists in reducing the values of the
+variances through a mutually constraining process as further multimodal
+data accumulates.
+
+In conclusion, this work studied the mechanism of word identification
+under uncertainty in both the word form and the word meaning. To our
+knowledge, this is the first study that performs an ideal observer
+analysis of this task. We found people to be near optimal in their cue
+combination: They weighted each modality according to its relative
+reliability. However, they also showed patterns of sub-optimality
+especially when the stimuli were perturbed with additional background
+noise. Future work will extend the present formal framework in order to
+account for how children use multimodal cues to refine their early
+phonological and semantic representations.
+
+\section{Appendix: derivation of the posterior (equation
+1)}\label{appendix-derivation-of-the-posterior-equation-1}
+
+For an ideal observer, the probability of choosing category 2 when
+presented with an audio-visual instance \(w = (a, v)\) is the posterior
+probability of this category:
+
+\[p(W_2 | w)=\frac{p(w|W_2)p(W_2)}{p(w|W_2)p(W_2)+p(w|W_1)p(W_1)}\]
+
+Which reduces to:
+
+\[p(W_2 | w)=\frac{1}{1+\frac{p(w|W_1)}{p(w|W_2)} \frac{p(W_1)}{p(W_2)}}\]
+In order to further simplify the quantity \(\frac{p(w|W_1)}{p(w|W_2)}\),
+we use our assumption that the cues are uncorrelated,
+\[p(w | W) = p(a,v| W) = p(a| A)p(v| V)\] Using the \(\log\)
+transformation, we get:
+
+\[ \ln(\frac{p(w |W_1)}{p(w|W_2)})=\ln(\frac{p(a|W_1)}{p(a|W_2)})+\ln(\frac{p(v|W_1)}{p(v|W_2)}) \]
+Under the assumption that the categories are normally distributed and
+that, within each modality, the categories have equal variances, we get
+(after simplification):
+
+\[\ln(\frac{p(a|W_1)}{p(a|W_2)})=\frac{\mu_{A1}-\mu_{A2}}{\sigma^2_{A}}\times a+ \frac{\mu^2_{A2}-\mu^2_{A1}}{2\sigma^2_{A}}\]
+
+and similarly:
+
+\[\ln(\frac{p(v|W_1)}{p(v|W_2)})=\frac{\mu_{V1}-\mu_{V2}}{\sigma^2_{V}}\times v+ \frac{\mu^2_{V2}-\mu^2_{V1}}{2\sigma^2_{V}}\]
+
+When putting all these terms together, we the get this final expression
+for the posterior:
+\[p(W_2 | w)=\frac{1}{1+(1+\epsilon)\exp(\beta_0+\beta_aa+\beta_vv)}\]
+
+where
+
+\[1+\epsilon=\frac{p(W_1)}{p(W_2)}\]
+\[\beta_0=\frac{\mu^2_{A2}-\mu^2_{A1}}{2\sigma^2_{A}}+\frac{\mu^2_{V2}-\mu^2_{V1}}{2\sigma^2_{V}}\]
+
+\[\beta_a=\frac{\mu_{A1}-\mu_{A2}}{\sigma^2_{A}}\]
+\[\beta_v=\frac{\mu_{V1}-\mu_{V2}}{\sigma^2_{V}}\]
+
+\section{References}\label{references}
+
+\setlength{\parindent}{-0.5in} \setlength{\leftskip}{0.5in}
+
+\hypertarget{refs}{}
+\hypertarget{ref-alais04}{}
+Alais, D., \& Burr, D. (2004). The ventriloquist effect results from
+near-optimal bimodal integration. \emph{Current Biology}, \emph{14}(3),
+257--262.
+
+\hypertarget{ref-anderson90}{}
+Anderson, J. R. (1990). \emph{The adaptive character of thought}.
+Hillsdale, NJ: Erlbaum.
+
+\hypertarget{ref-Bankieris17}{}
+Bankieris, K. R., Bejjanki, V., \& Aslin, R. N. (2017). Sensory
+cue-combination in the context of newly learned categories.
+\emph{Scientific Reports}, \emph{7}(1), 10890.
+
+\hypertarget{ref-bates88}{}
+Bates, D., \& Watts, D. (1988). \emph{Nonlinear regression analysis and
+its applications}. Wiley.
+
+\hypertarget{ref-bejjanki2011}{}
+Bejjanki, V., Clayards, M., Knill, D., \& Aslin, R. (2011). Cue
+integration in categorical tasks: Insights from audio-visual speech
+perception. \emph{PLoS ONE}, \emph{6}.
+
+\hypertarget{ref-bion2013}{}
+Bion, R. A., Borovsky, A., \& Fernald, A. (2013). Fast mapping, slow
+learning: Disambiguation of novel word-object mappings in relation to
+vocabulary learning at 18, 24, and 30 months. \emph{Cognition},
+\emph{126}(1), 39--53.
+
+\hypertarget{ref-Campbell2008}{}
+Campbell, R. (2008). The processing of audio-visual speech: Empirical
+and neural bases. \emph{Philosophical Transactions of the Royal Society
+of London B: Biological Sciences}, \emph{363}(1493), 1001--1010.
+
+\hypertarget{ref-carey2010}{}
+Carey, S. (2010). Beyond fast mapping. \emph{Language Learning and
+Development}, \emph{6}(3), 184--205.
+
+\hypertarget{ref-carey1978b}{}
+Carey, S., \& Bartlett, E. (1978). Acquiring a single new word. In
+\emph{Proceedings of the Stanford Child Language Conference} (Vol. 15,
+pp. 17--29).
+
+\hypertarget{ref-chater06}{}
+Chater, N., \& Manning, C. D. (2006). Probabilistic models of language
+processing and acquisition. \emph{Trends in Cognitive Sciences},
+\emph{10}, 335--344.
+
+\hypertarget{ref-clayard08}{}
+Clayards, M., Tanenhaus, M., Aslin, R., \& Jacobs, R. (2008). Perception
+of speech reflects optimal use of probabilistic speech cues.
+\emph{Cognition}, \emph{108}.
+
+\hypertarget{ref-Creel2012}{}
+Creel, S. (2012). Phonological similarity and mutual exclusivity:
+On-line recognition of atypical pronunciations in 3--5-year-olds.
+\emph{Developmental Science}, \emph{15}(5), 697--713.
+
+\hypertarget{ref-dautriche17}{}
+Dautriche, I., Mahowald, K., Gibson, E., \& Piantadosi, S. (2017).
+Wordform similarity increases with semantic similarity: An analysis of
+100 languages. \emph{Cognitive Science}, \emph{41}(8), 2149--2169.
+
+\hypertarget{ref-Eberhard1995}{}
+Eberhard, K., Spivey-Knowlton, M. J., Sedivy, J. C., \& Tanenhaus, M.
+(1995). Eye movements as a window into real-time spoken language
+comprehension in natural contexts. \emph{Journal of Psycholinguistic
+Research}, \emph{24}(6), 409--436.
+
+\hypertarget{ref-ernst02}{}
+Ernst, M. O., \& Banks, M. S. (2002). Humans integrate visual and haptic
+information in a statistically optimal fashion. \emph{Nature},
+\emph{415}(6870), 429--433.
+
+\hypertarget{ref-feldman2009}{}
+Feldman, N., Griffiths, T., \& Morgan, J. (2009). The influence of
+categories on perception: Explaining the perceptual magnet effect as
+optimal statistical inference. \emph{Psychological Review},
+\emph{116}(4), 752--782.
+
+\hypertarget{ref-fernald2006}{}
+Fernald, A., Perfors, A., \& Marchman, V. (2006). Picking up speed in
+understanding: Speech processing efficiency and vocabulary growth across
+the 2nd year. \emph{Developmental Psychology}, \emph{42}(1), 98--116.
+
+\hypertarget{ref-freedman2001}{}
+Freedman, D., Riesenhuber, M., Poggio, T., \& Miller, E. and. (2001).
+Categorical representation of visual stimuli in the primate prefrontal
+cortex. \emph{Science}, \emph{291}.
+
+\hypertarget{ref-Geisler2003}{}
+Geisler, W. S. (2003). Ideal observer analysis. In \emph{The visual
+neurosciences} (pp. 825--837)). Cambridge, MA: MIT Press.
+
+\hypertarget{ref-greenberg1957}{}
+Greenberg, J. (1957). \emph{Essays in linguistics}. Chicago: University
+of Chicago Press.
+
+\hypertarget{ref-hillenbrand1995}{}
+Hillenbrand, J., Getty, L. A., Clark, M. J., \& Wheeler, K. (1995).
+Acoustic characteristics of american english vowels. \emph{Journal of
+the Acoustical Society of America}, \emph{97}.
+
+\hypertarget{ref-hofer2017}{}
+Hofer, M., \& Levy, R. (2017). Modeling Sources of Uncertainty in Spoken
+Word Learning. In \emph{Proceedings of the 39th Annual Meeting of the
+Cognitive Science Society}.
+
+\hypertarget{ref-kleinschmidt2015}{}
+Kleinschmidt, D. F., \& Jaeger, T. F. (2015). Robust speech perception:
+Recognize the familiar, generalize to the similar, and adapt to the
+novel. \emph{Psychological Review}, \emph{148}.
+
+\hypertarget{ref-Knill04}{}
+Knill, D., \& Pouget, A. (2004). The bayesian brain: The role of
+uncertainty in neural coding and computation. \emph{Trends in
+Neurosciences}, \emph{27}(12), 712--719.
+
+\hypertarget{ref-mattys11}{}
+Mattys, S. L., \& Wiget, L. (2011). Effects of cognitive load on speech
+recognition. \emph{Journal of Memory and Language}, \emph{65}(2),
+145--160.
+
+\hypertarget{ref-mattys12}{}
+Mattys, S. L., Davis, M. H., Bradlow, A. R., \& Scott, S. K. (2012).
+Speech recognition in adverse conditions: A review. \emph{Language and
+Cognitive Processes}, \emph{27}(7-8), 953--978.
+
+\hypertarget{ref-mcgurk1976}{}
+McGurk, H., \& MacDonald, J. (1976). Hearing lips and seeing voices.
+\emph{Nature}, \emph{264}, 746--748.
+
+\hypertarget{ref-mcmurray2012}{}
+McMurray, B., Horst, J. S., \& Samuelson, L. K. (2012). Word learning
+emerges from the interaction of online referent selection and slow
+associative learning. \emph{Psychological Review}, \emph{119}.
+
+\hypertarget{ref-Merriman91}{}
+Merriman, W., \& Schuster, J. (1991). Young children's disambiguation of
+object name reference. \emph{Child Development}, \emph{62}(6),
+1288--1301.
+
+\hypertarget{ref-Monaghan2014}{}
+Monaghan, P., Shillcock, R. C., Christiansen, M. H., \& Kirby, S.
+(2014). How arbitrary is language? \emph{Philosophical Transactions of
+the Royal Society of London B: Biological Sciences}, \emph{369}(1651).
+
+\hypertarget{ref-Norris08}{}
+Norris, D., \& McQueen, J. M. (2008). Shortlist B: A bayesian model of
+continuous speech recognition. \emph{Psychological Review},
+\emph{115}(2), 357--395.
+
+\hypertarget{ref-pajak2016}{}
+Pajak, B., Creel, S., \& Levy, R. (2016). Difficulty in learning
+similar-sounding words: A developmental stage or a general property of
+learning? \emph{Journal of Experimental Psychology: Learning, Memory,
+and Cognition}, \emph{42}(9).
+
+\hypertarget{ref-reber98}{}
+Reber, R., Winkielman, P., \& Schwarz, N. (1998). Effects of perceptual
+fluency on affective judgments. \emph{Psychological Science},
+\emph{9}(1), 45--48.
+
+\hypertarget{ref-robinson2010}{}
+Robinson, C. W., \& Sloutsky, V. M. (2010). Development of cross-modal
+processing. \emph{Wiley Interdisciplinary Reviews: Cognitive Science},
+\emph{1}.
+
+\hypertarget{ref-Ronnberg10}{}
+Ronnberg, J., Rudner, M., Lunner, T., \& Zekveld, A. (2010). When
+cognition kicks in: Working memory and speech understanding in noise.
+\emph{Noise and Health}, \emph{12}(49), 263--269.
+
+\hypertarget{ref-saussure1916}{}
+Saussure, F. (1916). \emph{Course in general linguistics.} New York:
+McGraw-Hill.
+
+\hypertarget{ref-schwarz2004}{}
+Schwarz, N. (2004). Metacognitive experiences in consumer judgment and
+decision making. \emph{Journal of Consumer Psychology}, \emph{14}(4),
+332--348.
+
+\hypertarget{ref-sloutsky2003}{}
+Sloutsky, V. M., \& Napolitano, A. (2003). Is a picture worth a thousand
+words? Preference for auditory modality in young children. \emph{Child
+Development}, \emph{74}.
+
+\hypertarget{ref-spivey2002}{}
+Spivey, M. J., Tanenhaus, M., Eberhard, K., \& Sedivy, J. C. (2002). Eye
+movements and spoken language comprehension: Effects of visual context
+on syntactic ambiguity resolution. \emph{Cognitive Psychology},
+\emph{45}(4), 447--481.
+
+\hypertarget{ref-stager1997}{}
+Stager, C. L., \& Werker, J. F. (1997). Infants listen for more phonetic
+detail in speech perception than in word-learning tasks. \emph{Nature},
+\emph{388}(6640).
+
+\hypertarget{ref-Swingley2007}{}
+Swingley, D. (2007). Lexical exposure and word-form encoding in
+1.5-year-olds. \emph{Developmental Psychology}, \emph{43}(2), 454--464.
+
+\hypertarget{ref-Swingley2016}{}
+Swingley, D. (2016). Two-year-olds interpret novel phonological
+neighbors as familiar words. \emph{Developmental Psychology},
+\emph{52}(7), 1011--1023.
+
+\hypertarget{ref-Tamariz2008}{}
+Tamariz, M. (2008). Exploring systematicity between phonological and
+context-cooccurrence representations of the mental lexicon. \emph{The
+Mental Lexicon}, \emph{3}(2).
+
+\hypertarget{ref-Tanenhaus1995}{}
+Tanenhaus, M., Spivey-Knowlton, M., Eberhard, K., \& Sedivy, J. (1995).
+Integration of visual and linguistic information in spoken language
+comprehension. \emph{Science}, \emph{268}(5217), 1632--1634.
+
+\hypertarget{ref-tenenbaum11}{}
+Tenenbaum, J., Kemp, C., Griffiths, T., \& Goodman, N. (2011). How to
+grow a mind: Statistics, structure, and abstraction. \emph{Science},
+\emph{331}(11 March 2011), 1279--1285.
+
+\hypertarget{ref-vouloumanos2014}{}
+Vouloumanos, A., \& Waxman, S. (2014). Listen up! Speech is for thinking
+during infancy. \emph{Trends in Cognitive Sciences}, \emph{18}(12),
+642--646.
+
+\hypertarget{ref-vroomen2004}{}
+Vroomen, J., Linden, S. van, Keetels, M., Gelder, B. de, \& Bertelson,
+P. (2004). Selective adaptation and recalibration of auditory speech by
+lipread information: Dissipation. \emph{Speech Communication},
+\emph{44}.
+
+\hypertarget{ref-waxman1995}{}
+Waxman, S., \& Markow, D. (1995). Words as invitations to form
+categories: Evidence from 12-to 13-month-old infants. \emph{Cognitive
+Psychology}, \emph{29}(3), 257--302.
+
+\hypertarget{ref-white2008b}{}
+White, K., \& Morgan, J. (2008). Sub-segmental detail in early lexical
+representations. \emph{Journal of Memory and Language}, \emph{59}.
+
+\hypertarget{ref-yeung09}{}
+Yeung, H., \& Werker, J. (2009). Learning words' sounds before learning
+how words sound: 9-month-olds use distinct objects as cues to categorize
+speech information. \emph{Cognition}, \emph{113}, 234--243.
+
+\hypertarget{ref-yoshida2009}{}
+Yoshida, K., Fennell, C., Swingley, D., \& Werker, J. (2009).
+14-month-olds learn similar-sounding words. \emph{Developmental
+Science}, \emph{12}.
+
+\end{document}

### 2018-04-13 Writeup/ms copy.Rmd
changes on ms

--- 2018-02-24 Writeup/ms.Rmd
@@
 
-figsintext        : no
+figsintext        : yes
 figurelist        : no
@@
 library(langcog)
-theme_set(theme_bw())
+library(ggthemes)
+#theme_set(theme_few())
 library(broom)
@@
 
-How does the mind deal with uncertainty to identify the speaker's intended word?
-To address this question, many researchers in recent years have adopted the rational approach to cognition [@anderson90], which corresponds to Marr's computational level of analysis.
-This approach has had a tremendous impact not only on speech related research [@Norris08; @clayard08; @feldman2009; @kleinschmidt2015], but also on many other disciplines in the cognitive sciences [for reviews, see @chater06; @Knill04; @tenenbaum11].
-Within this framework, researchers typically consider an "ideal observer" model which provides a characterization of the task/goal and shows what the optimal performance should be under this characterization.
-When there is uncertainty in the input, the ideal observer performs an optimal probabilistic inference.
+How does the listener deal with uncertainty to identify the speaker's intended word?
+One rigorous way to approach this question is through conducting an *ideal observer* analysis.
+This research strategy provides a characterization of the task/goal and shows what the optimal performance should be under this characterization.\footnote{This strategy is, thus, a general instance of the rational approach to cognition [@anderson90], as well as Marr's computational level of analysis.} When there is uncertainty in the input, the ideal observer performs an optimal probabilistic inference.
 For example, in order to recognize an ambiguous linguistic input, the model uses all available probabilistic knowledge in order to maximize the accuracy of this recognition.
@@
 It is often used, not so much as a realistic model of human performance, as much as a baseline against which human performance can be compared [@Geisler2003].
-When there is a deviation from the ideal, this can reveal extra constraints on human cognition, such as limitations on working memory or attentional resources.
-
-In this line of research, @clayard08 simulated auditory uncertainty by manipulating the probability distribution of a cue (VOT) that differentiated similar words (e.g., "beach" and "peach").
+When there is a deviation from the ideal, this can reveal extra constraints on human cognition, such as limitations on working memory or attentional resources (see Rahnev and Denison, 2018 for further discussion).
+
+The ideal observer analysis has had a tremendous impact not only on speech related research [@Norris08; @clayard08; @feldman2009; @kleinschmidt2015], but also on many other disciplines in the cognitive sciences [for reviews, see @chater06; @Knill04; @tenenbaum11].
+In particular, using this research strategy, @clayard08 simulated auditory uncertainty by manipulating the probability distribution of a cue (VOT) that differentiated similar words (e.g., "beach" and "peach").
 They found that humans were sensitive to these probabilistic cues and their judgments closely reflected the optimal predictions.
-In another work, @feldman2009 studied the perceptual magnet effect, which is related to how categories influence the way the stimuli are perceived.
+In another work, @feldman2009 studied the perceptual magnet effect, which is a phenomenon that involves reduced discriminability near prototypical sounds in the native language (Kuhl, 1991).
 They showed that this effect can be explained as the consequence of optimally solving the problem of perception under uncertainty.
-Both studies explored optimal performance under uncertainty from one modality, i.e., the auditory modality.
-There is however extensive evidence that information from the visual modality, in particular the speaker's facial features,  influences the perception of auditory information [see @Campbell2008 for a review].
+Both @clayard08 and @feldman2009 explored optimal performance under uncertainty in the auditory modality.
+There is, however, extensive evidence that information from the visual modality, such as the speaker's facial features,  also influences speech understanding [see @Campbell2008 for a review].
 @bejjanki2011 offered a mathematical characterization of how cues from speech and lip movements can be optimally combined and showed that human performance during audio-visual phonemic labeling was consistent (at least at the qualitative level) with the behavior of the ideal observer.
 
-The speaker's facial features are not the only visual information that can be used to disambiguate the auditory input, however.
-For instance, in a referential context, information about the identity of the semantic referent can be integrated with linguistic information to resolve lexical and syntactic ambiguities in speech [e.g., @Eberhard1995; @Tanenhaus1995; @spivey2002].
-To our knowledge, however, no study offered an ideal observer analysis of word identification in such context, that is, when the mind has to combine cues from the sound and the referent.
+This previous reseach, however, did not systematically study speech inderstanding when the visual information is obtained, not through the speaker's facial features, but through the referential context.
+In fact, experimental findings showed that information about the identity of the semantic referent can be integrated with linguistic information to resolve lexical and syntactic ambiguities in speech [e.g., @Eberhard1995; @Tanenhaus1995; @spivey2002].
+To our knowledge, however, no study offered an ideal observer analysis of word identification in such context, that is, when the listener has to combine cues from the sound and the referent.
 Imagine, for example, that someone is uncertain whether they heard "pea" or "bee", does this uncertainty make them rely more on the referent (e.g., the object being pointed at)?
@@
 
-The visual information provided by the referent is arguably different from the visual information provided by the speaker's facial features (such as lip movements).
-There seems to be at least two fundamental differences between these two cases, and both can influence the cue combination strategy:
-
-<!-- Outside the realm of language per se, research on multisensory integration suggests that the brain integrates information from different modalities in a statistically optimal way, that is, the integration results in a higher overall precision, and modalities are weighed according to their relative reliability [@ernst02].
-However, it is not a priori obvious whether this finding can be extended to word-referent recognition under multimodal uncertainty.
-Indeed, there seems to be at least two fundamental differences between these two cases, and both can influence the cue combination strategy.
--->
-
-First, in the case of audio-visual speech, modalities are understood to differ only in terms of their reliability.
-In a referential context, however, modalities also differ in terms of their roles in the referential process: the auditory input represents the symbol (i.e., the word) whereas the visual input represents the referent.
-It has been suggested that because of its referential property, speech is a privileged signal for humans, starting in infancy [see @vouloumanos2014 for a review].\footnote{There is a debate over whether speech is privileged for infant and adults for the same reasons.
-Whereas Waxman and colleagues suggest that speech is privileged for both infants and adults because of its ability to refer, Sloutsky and colleagues suggest that speech might not have a referential status from the start.
-Rather, according to Sloutsky and colleagues, speech seems to be prefered by infants only because of a low level auditory "overshadowing".} Thus, in a referential context, it is possible that we do not treat the auditory and visual modalities as equivalent sources of information.
-Instead, there could be a bias for the auditory modality beyond what is expected from informational reliability alone.
+On the face of it, the question of combining information from the sound and the visual referent might seem similar to that of audio-visual speech integration.
+Nevertheless, there are at least two fundamental differences between these two cases, and both can influence the way the auditory and visual cues are integrated.
+First, in the case of audio-visual speech, modalities may difffer only in terms of their informational reliability.
+In a referential context, however, modalities also differ in terms of their roles in the referential process: the auditory input represents the *symbol* whereas the visual input represents the *meaning*.
+It has been suggested that because of its referential property, speech is a privileged signal for humans, starting in infancy [see @vouloumanos2014 for a review].\footnote{There is a debate as to whether speech is privileged for infant and adults for the same reasons.
+Whereas some researchers suggest that speech is privileged for both infants and adults because of its ability to refer (Waxman et al.
+XX), others suggest that speech might not have a referential status from the start.
+Rather, speech might be prefered by infants only because of a low level auditory "overshadowing" (Sloutsky et al.
+XX).} Thus, in a referential context, it is possible that listeners do not treat the auditory and visual modalities as equivalent sources of information.
+Instead, there could be a sub-optimal bias for the auditory modality beyond what is expected from informational reliability alone.
 
 <!--An example of such integration is when we determine the size of an object using the visual and haptic modalities [@ernst02], or when we determine the spacial location of a stimulus using the visual and the auditory modalities [@alais04] -->
-Second, in the case of audio-visual speech, the associations are expected to be perceptually correlated.
-The expectation for this correlation is such that when there is a mismatch between auditory and visual input, people still integrate them into a unified (but illusory) percept [@mcgurk1976].
+Second, in the case of audio-visual speech, the auditory and visual stimuli are expected to be perceptually correlated.
+The expectation for this correlation is such that when there is a mismatch between the auditory and visual input, people still integrate them into a unified (but illusory) percept [@mcgurk1976].
 In the case of referential language, however, the multimodal association is by nature *arbitrary* [@saussure1916; @greenberg1957].
@@
 Moreover, variation in the way the sound "bee" is pronounced is generally not expected to correlate perceptually with variation in the shape (or any other visual property) in the category of bees.
-Thus, one could imagine that cue combination in the case of arbitrary audio-visual associations (word-referent) is less automatic, more effortful, and therefore less conducive to optimal integration than it is in the case of perceptually correlated associations (as in audio-visual speech perception).
+In sum, cue combination in the case of arbitrary audio-visual associations (word-referent) is likely to be less automatic, more effortful, and therefore less conducive to optimal integration than it is in the case of perceptually correlated associations (as in audio-visual speech perception).
 
@@
 For instance, as mentioned above, a sub-optimality can be induced by the suggested privileged status of speech or by the arbitrariness of the referential association.
-In order to study possible patterns of sub-optimality, we compare the optimal model (which provides a normative benchmark) to a descriptive model which is identical to the optimal model, except that the parameters in the former are fitted to human responses.
+In order to study possible patterns of sub-optimality, we compare the optimal model (which provides a normative benchmark) to a descriptive model (which is fit to human responses).
+Comparing parameter estimates between these two formulations allows us to quantify the degree of deviation from optimality.
+
 <!--We do not perform the ideal observer analysis at the individual level, but at the population level.
@@
 
-# Models and predictions
-
-In this section we describe the multimodal cue combination model.
-First, we briefly introduce the experimental paradigm, and second we explain how behavior in this paradigm can be characterized optimally with an ideal observer model.
+<!-- Outside the realm of language per se, research on multisensory integration suggests that the brain integrates information from different modalities in a statistically optimal way, that is, the integration results in a higher overall precision, and modalities are weighed according to their relative reliability [@ernst02].
+However, it is not a priori obvious whether this finding can be extended to word-referent recognition under multimodal uncertainty.
+Indeed, there seems to be at least two fundamental differences between these two cases, and both can influence the cue combination strategy.
+-->
+
+# Pardigm and Models
+
+In this section we, first, briefly introduce the multimodal combination task. Then we explain how behavior in this paradigm can be characterized optimally with an ideal observer model.
 
@@
 The test stimulus may differ from the target in both the auditory and the visual components.
-After these two presentations, participants press "same" or "different".
+After these two presentations, participants press "same" or "different."
 
@@
 
-This task is similar to the task introduced by @sloutsky2003, and used in subsequent studies in both children and adults [see @robinson2010 for a review].
-However, in this original task, participants are asked whether or not the two audio-visual presentations are *identical*.
-Such task would allow us to probe audio-visual encoding, but not necessarily language understanding.
-The latter requires---in addition to the perceptual encoding---a categorical judgement, i.e, determining whether or not two similar tokens are members of the same phonological/semantic category.
-Thus, our task is category-based: Participants are asked to press "same" if they think the second item (the test) belonged to the same category as the first (target) (e.g.,  dog-/aba/), even if there is a slight difference in the sound, in the referent, or in both.
+This paradim is adapted from a task by @sloutsky2003, in which participants are asked whether or not the two audio-visual presentations are *identical*.
+The original task has been used with both chidlren and adults to probe  audio-visual encoding [see @robinson2010 for a review].
+We are rather interested in categorization responses, i.e., determining whether or not two similar tokens are members of the same phonological/semantic category.
+Therefore, testing in our task is category-based: Participants are asked to press "same" if they think the second item (the test) belonged to the same category as the first (target) (e.g.,  dog-/aba/), even if there is a slight difference in the sound, in the referent, or in both.
 They are instructed to press "different" only if they think that the second stimulus was an instance of the other word category (cat-/ada/).
@@
 
-<!--We assume, for the sake of simplicity, that category tokens vary along a single dimension.
-Phonetic tokens are sampled from an acoustic continuum linking /aba/ to /aba/, and obtained by continuously varying the value of the second formant [@vroomen2004].
-Visual tokens are sampled from a morph continuum linking the picture of a dog and the picture of a cat [@freedman2001].
--->
-
 ## Optimal Model
 
-<!--First we describe how probabilistic representations in each modality are derived, and second we explain how they are combined to yield optimal predictions. -->
-
-<!--
-### Unimodal condition
-
-In each modality, we have two categories: /ada/ ($A=1$) and /aba/ ($A=2$) in the auditory dimension, and *cat* ($V=1$) and *dog* ($V=2$) in the visual dimension.
-
-We assume a token's probability of membership in each category to be normally distributed:
-
+We construct an ideal observer model that combines probabilistic information from the auditory and visual modalities.
+In contrast to the  model used in most research on multisensory integation [@ernst02; @alais04]---which typically studies continuous stimuli (e.g., size, location)---this probabilistic information cannot be characterized with sensory noise/variability, only.
+Indeed, our task involves repsonses over categorical variables (phonemes and concepts), and therefore, the optimal model in our case should take into account, not only the noise variability around an individual perceptual estimate, but also its *within category variability*, i.e., the uncertainty related to whether this perceptual estimate belongs to a given category [see also @Bankieris17; @bejjanki2011].
+In what follows, we describe a model that accounts for both type of varibility.
+First, we describe the model in the simplified case of categorical variability only.
+Second, we augment this simplified model to account for sensory noise.
+
+### Categorical variability
+We assume that both the auditory categories (i.e., /aba/ and /ada/) and the visual categories (cat and dog) are distributed along a single acoustic and semantic dimension, respectively (Figure\ \@ref(fig:model)).
+Moreover, we assume that all categories are normally distributed.
+Formally speaking, if $A$ denotes an auditory category (/ada/ or /aba/), then the probability that a point $a$ along the acoustic dimension belongs to the category $A$ is
 $$ p(a | A) \sim  N(\mu_A, \sigma^2_A) $$
+where $\mu_A$ and $\sigma^2_A$ are respectively the mean and the variance of the auditory category.
+Similarly, the probability that a point $v$ along the visual dimension belongs to the category $V$ is
 $$ p(v | V) \sim  N(\mu_V, \sigma^2_V) $$
-The parameters of these distributions are fitted to the participants' judgement in the unimodal case, i.e., when they only hear the sounds, and when they only see the objects.
-For an ideal recognizer, the probability of choosing category 2 (that is, to answer "different") when presented with, say, an audio instance $a$, is the posterior probability of this category $p(A_2|a)$.
-If we assume that both categories have equal variances, the posterior probability reduces to:
-
-$$p(A_2 | a)=\frac{1}{1+(1+\epsilon_A)\exp(\beta_{a0}+\beta_aa)}$$
-
-with $\beta_a=\frac{\mu_{A_1}-\mu_{A_2}}{\sigma^2_{A}}$, $\beta_{a0}=\frac{\mu^2_{A_2}-\mu^2_{A_1}}{2\sigma^2_{A}}$ and $1+\epsilon_A=\frac{p(A_1)}{p(A_2)}$ is the proportion of the prior probabilities.
-If the identity of the auditory categories is randomized, and if $A_1$ is the target, then $\epsilon$ measures a response bias to "same" if $\epsilon > 0$, and a response bias to "different" if $\epsilon < 0$.
-
-We modeled the visual representation in exactly the same way.
-
--->
-
-The ideal observer model combines probabilistic information from the auditory and visual modalities, and makes a categorical decision.
-How can this task be characterized in a formal way, and what would be the optimal behavior?
-If the stimuli were continuous (e.g., size, location), cues derived from each modality would be characterized with their sensory noise variance only, and (assuming conditional independence) their combined information would be characterized with a simple linear combination rule where the combined estimate is an average of the individual estimates, each weighted according to its relative reliability [@ernst02; @alais04].
-However, in our case decision is made over categorical variables (phonemes and concepts), the optimal model should take into account, not only the noise variability around an individual perceptual estimate, but also its categorical variability (i.e., the probability with which the estimate belongs to a given category).
-
-One way to account for the categorical variability is to model the decision step which maps sensory input onto task-dependent categories [@Bankieris17; @bejjanki2011].
-We represent the decision step as follows (see Figure\ \@ref(fig:model) for illustration).
-If we assume that both the visual and the auditory cues vary along a single dimension, an audio-visual signal $(a,v)$ can be represented as a point in this two-dimensional space, and a word category can be characterized with a bivariate probability distribution over audio-visual tokens.\footnote{For the sake of clarity, we assume here that the sensory noise around this point is small/negligible compared to the categorical variability.
-But see below how the noise can be integrated when its effect is relatively large} Each category is peaked around the most typical audio-visual token, and the probability of membership in the category (the likelihood probability) decreases gradually as the auditory token deviates from the typical sound instance (depending on the variance of the auditory category) and/or as the visual token deviates from the typical visual instance (depending on the variance of the visual category).
-<!--To illustrate how categorical decision is made within this formal framework, suppose we receive an ambiguous image which can be either of a cat or of a dog, associated with a slightly noisy auditory input that sounds more like "cat".
-If the judgment is based on the picture only, this would lead to a random choice between cat and dog.
-However, if the judgement is based on both the picture and the sound (which is less ambiguous), the combined information should lead to a preference for the word cat  we illustrate the cateorical decision making.
-Audio-visual points along this line lead to random responses, meaning that both the auditory and the visual components are maximally ambiguous.
-Audio-visual points that lay on either side of the decision threshold lead to decisions in favor of one word or the other.
-This means that at least one component of this audio-visual token is not totally ambiguous, which leads to a diambiguated combined information.
--->
-
-A crucial feature of the ideal observer model is that it makes use of the entire probability distribution of a given category in order to make optimal decisions [e.g., @clayard08].
-This means that the probability of picking a word (the posterior probability) should mirror closely the probability of the combined information (the likelihood probability).
-For instance, the model becomes less ambiguous and more certain as the tokens get closer to the typical instance of the category.
-In what follows, we formalize this sense of optimality using a Bayesian framework.
-<!--characterized with a likelihood function, e.g., $P(S_V | S)$ and $P(S_A | S)$ for a visual and an auditory cue, respectively.
-If these cues are conditionally independent, their combined information can be written as $P(S_V, S_A | S)=P(S_A | S)P(S_V | S)$.
-The maximum likelihood estimate of this combined information $\hat{S}$ is an average of the individual maximum liklihoods $\hat{S}=w_V\hat{S_V}+w_A\hat{S_A}$, each wighted according to its relative reliability:
-$w_V=\frac{1/\sigma_V^2}{1/\sigma_V^2 + 1/\sigma_A^2}$, and $w_A=\frac{1/\sigma_A^2}{1/\sigma_V^2 + 1/\sigma_A^2}$.
-
-If, however, the target is a categorical dimension, the optimal model should take into account, not only the noise variability arround an individual perceptual estimate, but also its categorical variability (i.e., the probability with which this estimate belongs to a given category).
-For example, upon hearing an audio-visual signal (the sound "cat" associated with the image of a cat), the ideal obsever has both to identify the sensory input and to map it onto the task-dependent categories.
-
-The optimal model that takes into account categorical variability is somewhat different, since -->
-
-<!-- more adequate to the case of redundant information, where, for instance, cues are in the same units, the same coordinates and about the same aspect of the environmental property.
-It is less adequate to describe the case of arbitrary associations where cues are in different units, coordinate systems, or about complementary aspects of the same environmental property [see @ernst04 for further detail].
--->
-
-An auditory category $A$ and a visual category $V$ are defined as distributions in the auditory and the visual dimensions, respectively.
-A word category $W$ is defined as a bivariate distribution in the audio-visual.
-More specifically, we define it as the joint distribution of the auditory and the visual categories.
-For simplicity, we assume both auditory and visual categories to be normally distributed.
-That is, if $w=(a,v)$ is an audio-visual token, then:
-$$ p(a | A) \sim  N(\mu_A, \sigma^2_A) $$
-where $\mu_A$ and $\sigma^2_A$ are respectively the mean and the variance of the auditory category,
-$$ p(v | V) \sim  N(\mu_V, \sigma^2_V) $$
-where $\mu_V$ and $\sigma^2_V$ are  the mean and the variance of the visual category, and
-
+where $\mu_V$ and $\sigma^2_V$ are the mean and the variance of the visual category.
+An audio-visual signal $w=(a,v)$ can be represented as a point in the audio-visual space.
+These tokens belong to bivariate distributions in this bi-dimentional sapce.
+We call these bivariate distributions *Word categories*, noted $W$, and are distributed as follows:
 $$ p(w | W) \sim  N(M_W, \Sigma_W) $$
-where $M_W=(\mu_A, \mu_V)$ and $\Sigma_W$ are mean and the covariance matrix of the word category.
-We assume that auditory and visual variables are independent (i.e., uncorrelated), so the covariance matrix is simply:
+where $M_W=(\mu_A, \mu_V)$ and $\Sigma_W$ are the mean and the covariance matrix of the word category.
+The main assumption of the model is that the auditory and visual variables are independent (i.e., uncorrelated), so the covariance matrix is simply:
  \[
@@
 
-```{r model, fig.cap = "Illustration of the model using simulated data.
+```{r model, out.width = "\\textwidth", fig.pos = "!h", fig.cap = "Illustration of the model using simulated data.
 A word category is defined as the joint bivariate distribution of an auditory category (horizontal, bottom panel) and a visual semantic category (vertical, left panel).
-Upon the presentation of a word token $w$, participants guess whether it is sampled from the word type $W_1$ or from the word type $W_2$.
-Decision threshold is where the guessing probability is 0.5.", fig.align = "center", out.width = "400px"}
+Upon the presentation of a word token w, participants guess whether it is sampled from the word type W1 or from the word type W2.
+Decision threshold is where the guessing probability is 0.5."}
 knitr::include_graphics("pictures/model.png", dpi = 108)
@@
 
-Now we turn to the crucial question of modeling how optimal decision should proceed based on the probabilistic information in the auditory and the visual modalities.
-In our task, we have two word categories: dog-/aba/ ($W_1$) and cat-/ada/ ($W_2$).\footnote{This mapping is randomized in the experiments.} Participants can be understood as choosing one of these two word categories (Figure\ \@ref(fig:model)).
+Now we turn to the crucial question of modeling how optimal decision should proceed given the probabilistic (categorical) information in the auditory and the visual modalities, as characterized above.
+We have two word categories: dog-/aba/ ($W_1$) and cat-/ada/ ($W_2$).\footnote{This mapping is randomized in the experiments.} When making decisons, participants can be understood as choosing one of these two word categories (Figure\ \@ref(fig:model)).
 For an ideal observer, the probability of choosing category 2 when presented with an audio-visual instance $w=(a,v)$ is the posterior probability of this category:
@@
 \begin{equation}
- p(W_2 | w)=\frac{1}{1+(1+\epsilon)\exp(\beta_0+\beta_aa+\beta_vv)}
+ p(W_2 | w)=\frac{1}{1+(1+b)\exp(\beta_0+\beta_aa+\beta_vv)}
 \end{equation}
 where 
-$$1+\epsilon=\frac{p(W_1)}{p(W_2)}$$
+$$1+b=\frac{p(W_1)}{p(W_2)}$$
 $$\beta_0=\frac{\mu^2_{A2}-\mu^2_{A1}}{2\sigma^2_{A}}+\frac{\mu^2_{V2}-\mu^2_{V1}}{2\sigma^2_{V}}$$
@@
 
-The parameter $\epsilon$ represents the differential between the categories' prior probabilities.
-However, since the identity of word categories is randomized across participants, $\epsilon$ measures, rather, a response bias to "same" if $\epsilon > 0$, and a response bias to "different" if $\epsilon < 0$.
+The parameter $b$ represents the differential between the categories' prior probabilities.
+However, since the identity of word categories is randomized across participants, $b$ measures, rather, a response bias to "same" if $b > 0$, and a response bias to "different" if $b < 0$.
 We expect a general bias towards answering "different" because of the categorical nature of our same-different task: When two items are ambiguous but perceptually different, participants might have a slight preference for "different" over "same".
-
-<!--
-We fix the values of the means as follows.
-Since the endpoints of the auditory and the visual continua are the most typical tokens, we assume that the categories are peaked around these endpoints, so we fix the values of the mean to be these endponts.
-to be the endpoints of the corresponding continuum, meaning that <!--For example, if both the auditory and visual continua are made of 5 steps going from 0 to 4, then $\mu_{A1}=0$ and $\mu_{A2}=4$ (and similarly $\mu_{V1}=0$, and $\mu_{V2}=4$).
---> The values of the means are fixed: They correspond to the value of the most typical tokens in our stimuli.
+As for the means, their values are fixed, and they correspond to the most typical tokens in our stimuli.
 Thus, observations from each modality ($a$ and $v$) are weighted according to their reliability in the posterior: $$\beta_a \propto \frac{1}{\sigma^2_{A}}$$ $$\beta_v \propto \frac{1}{\sigma^2_{V}}$$.
 
-Note that the weights account for categorical variability only. For instance, if the speaker generates a target production $a_t$ from an auditory category
+### Sensory variability
+
+So far, we only accounted for categorical variability. For instance, if the speaker generates a target production $a_t$ from an auditory category
 $p(a_t | A) \sim N(\mu_{A}, \sigma^2_{A})$, the ideal model assumes that it has direct access to this production token (i.e., $a=a_t$), and that all uncertainty is about the category membership of this token.
@@
 For example, the observer might not have access to the exact produced target, but only to the target perturbed by noise.
-If we assume this noise to be normally distributed, that is,  $p(a | a_t) \sim N(a_t, \sigma^2_{N})$, then integrating over $a_t$ lead to the following simple expression:
-$$ p(a | A) \sim N(\mu_{A}, \sigma^2_{A}+\sigma^2_{N})$$
-Using an identical reasoning for the case of the visual modality, we end up with the following multimodal weighting scheme in the optimal combination model:
+If we assume this noise to be normally distributed, that is,  $p(a | a_t) \sim N(a_t, \sigma^2_{N_A})$, then integrating over $a_t$ leads to the following simple expression:
+$$ p(a | A) \sim N(\mu_{A}, \sigma^2_{A}+\sigma^2_{N_A})$$
+Similarly, in the case of sensory noise in the visual modality, we get
+$$ p(a | V) \sim N(\mu_{V}, \sigma^2_{V}+\sigma^2_{N_V})$$
+Finally, using exactly the same derivation as above, we end up with the following multimodal weighting scheme in the optimal combination model (Equation 1) which takes into account both categorical and sensory variability:
 
  $$\beta_a \propto \frac{1}{\sigma^2_{A}+\sigma^2_{N_A}}$$ $$\beta_v \propto \frac{1}{\sigma^2_{V} +\sigma^2_{N_V}}$$
-To summarize, the posterior provides the optimal model's predictions for how probabilities that characterize uncertainty in each modality can be combined to make categorical decision about the bimodal input.
-The model will be constructed based on data from the unimodal trials, but the predictions of the optimal model will be compared to human responses in the bimodal trials.
-
-## Auditory and Visual models
-
-Besides the optimal model, we also test the predictions of two baselines models: a visual model, which assumes that participants rely only on visual information, and an auditory model, which assumes that participants rely only on auditory information.
-If participants rely on both the auditory and the visual modalities, the optimal model would explain more variance in human responses than the visual model alone or the auditory model alone.
-
-## Descriptive model
-
-The visual, auditory, and optimal models are *normative* models.
+
+### Optimal cue combination
+
+The posterior (Equation 1) provides the optimal model's predictions for how probabilities that characterize uncertainty in the auditory and the viusal modalities can be combined to make categorical decisions.
+Estimates of the probability distributions in each modality are derived by fitting logistic regressions to participants' responses in the unimodal conditions, where participants only hear the sounds or only see the pictures (Figure\ \@ref(fig:task)) \footnote{Further technical detail about model fitting in the unimodal conditions will be given in the method section of Experiment 1}.
+Using these derived parameters, the optimal model makes predictions about responses in the bimodal condition where participants both hear the sounds and see the pictures.
+
+### Auditory and Visual baselines
+
+The predictions of the optimal model will be compared to two baselines.
+The first basline is a visual model which assumes that participants rely only on visual information, and the auditory model, which assumes that participants rely only on auditory information.
+More precisely, these baseline models assumes that the participants' respones in the bimodal condition will not be different from their response in one of the unimodal conditions.
+If, as we expect, the participants rely on both the auditory and the visual modalities to make decision in the bimodal condition, the optimal model would explain more variance in human responses than the visual model alone or the auditory model alone.
+
+## Descriptive model and analysis of sub-obtimality
+
+The optimal models (as well as the auditory and visual baselines) are *normative* models.
 Their predictions are made about human data in the bimodal condition, but their crucial parameters (i.e., variances associated with the visual and auditory modalities) are derived from data in the unimodal conditions.
 In addition to these normative models, we consider a *descriptive* model.
-The parameters of this model are fit to human data in the bimodal condition.
-If the referential task induces sub-optimality (due, for instance, to the arbitrary nature of the sound-object association), then we predict that the descriptive model should explain more variance than the optimal model does.
-
-A systematic comparison of the optimal and the descriptive models would allow us, not only to quantify how much people deviate from optimality, but also to understand precisely how they deviate from this optimality.
+The parameters of this model are fit to actual respnses in the bimodal condition.
+If the referential task induces sub-optimality (due, for instance, to the arbitrary nature of the sound-object association), then the descriptive model should explain more variance than the optimal model does.
+
+Comparison between the optimal and the descriptive models allows us, not only to quantify how much people deviate from optimality, but also to understand precisely how they deviate from this optimality.
 Let $\sigma^2_{A}$ and $\sigma^2_{V}$ be the values of the variances used in the optimal model (derived from the unimodal conditions), and $\sigma^2_{Ab}$ and $\sigma^2_{Vb}$ be the values observed through the descriptive model in the bimodal condition.
@@
 
-```{r subOptim, fig.cap = "Illustration using simulated data showing the example of a prediction made by the optimal model (top), and the three possible ways human participants can deviate from this prediction (bottom).
-These cases are the following: 1) The variance increases equally for both modalities, but the weighting scheme (characterized by the decision threshold) is optimal, 2) The auditory variance increases at a higher rate, leading to a preference for the auditory modality, and 3) The visual variance increases at a higher rate, leading to a preference for the visual modality", fig.align = "center", out.width = "400px"}
+```{r subOptim, out.width = "\\textwidth", fig.pos = "!h", fig.cap = "Illustration using simulated data showing the example of a prediction made by the optimal model (top), and the three possible ways human participants can deviate from this prediction (bottom).
+These cases are the following: 1) The variance increases equally for both modalities, but the weighting scheme (characterized by the decision threshold) is optimal, 2) The auditory variance increases at a higher rate, leading to a preference for the auditory modality, and 3) The visual variance increases at a higher rate, leading to a preference for the visual modality"}
+
 knitr::include_graphics("pictures/sub-optimal", dpi = 108)
@@
 
-We tested the predictions of the optimal model in three experiments.
+We compared these models to human responses in three experiments.
 In Experiment 1, we studied the case where bimodal uncertainty was due to ambiguity in terms of category membership, without any additional background noise.
@@
 
-In this Experiment, we start with testing the predictions in the case where uncertainty is due to ambiguity in terms of category membership only, that is, according to the following weighting scheme:  $$\beta_a \propto \frac{1}{\sigma^2_{A}}$$ $$\beta_v \propto \frac{1}{\sigma^2_{V}}$$ We do not introduce any additional noise in the background, and we assume that sensory noise is negligible compared to categorical variability.
+In this Experiment, we start with testing the predictions in the case where uncertainty is due to categorical variability only (i.e., ambiguity in terms of category memebership).
+We assume that sensory noise is negligible compared to categorical variability.
+Thus, we use the following cue weighing scheme:
+
+$$\beta_a \propto \frac{1}{\sigma^2_{A}}$$
+$$\beta_v \propto \frac{1}{\sigma^2_{V}}$$
 
@@
 
-### Participants:
+### Participants
 
@@
 Participants were excluded if they reported having experienced a technical problem of any sort during the online experiment (N=`r N_all_1 - N_noProb_1`), or if they had less than 50\% accurate responses on the unambiguous training trials (N=`r N_noProb_1 - N_good_1`).
-The final sample consisted of (N = `r N_good_1`) participants.\footnote{The sample size and exclusion criteria were specified in the pre-registration at https://osf.io/h7mzp/.}
-
-### Stimuli:
+The final sample consisted of N = `r N_good_1` participants.\footnote{The sample size and exclusion criteria were specified in the pre-registration at https://osf.io/h7mzp/.}
+
+### Stimuli
 For auditory stimuli, we used the continuum introduced in @vroomen2004, a 9-point /aba/--/ada/ speech continuum created by varying the frequency of the second (F2) formant in equal steps.
 We selected 5 equally spaced points from the original continuum by keeping the endpoints (prototypes) 1 and 9, as well as points 3, 5, and 7 along the continuum.
-For visual stimuli, we used a morph continuum introduced in @freedman2001.
+For visual stimuli, we used a cat/dog morph continuum introduced in @freedman2001.
 From the original 14 points, we selected 5 points as follows: we kept the item that seemed most ambiguous (point 8), the 2 preceding points (i.e., 7 and 6) and the 2 following points (i.e., 9 and 10).
@@
 bias_ci2_1=dataSave1$upper[which(dataSave1$variable == "bias")]
-
-```
-
-```{r}
-#Michael suggestion:
-#For a given particiapnts, sample
 
@@
   scale_y_continuous(limits = c(0, 1))+#theme(aspect.ratio = 0.7)+
+  theme_few()+
   theme(aspect.ratio = 0.7) + facet_grid(Experiment ~ Condition)
@@
 
-```{r unimodal, fig.cap = "Human responses in the unimodal condition.
+```{r unimodal, out.width = "\\textwidth", fig.pos = "!h", fig.cap = "Human responses in the unimodal condition.
 Points represent the proportion of `different' to `same' responses in the auditory-only condition (left), and visual-only condition (right).
 Error bars are 95\\% confidence intervals.
-Solid lines represent logistic fits.", fig.align = "center", out.width = "400px"}
+Solid lines represent logistic fits."}
 
@@
 
-$$p(A_2 | a)=\frac{1}{1+(1+\epsilon_A)\exp(\beta_{a0}+\beta_aa)}$$
+$$p(A_2 | a)=\frac{1}{1+(1+b_A)\exp(\beta_{a0}+\beta_aa)}$$
 
 with $\beta_a=\frac{\mu_{A_1}-\mu_{A_2}}{\sigma^2_{A}}$ and  $\beta_{a0}=\frac{\mu^2_{A_2}-\mu^2_{A_1}}{2\sigma^2_{A}}$.
-$\epsilon_A$ is the response bias in the auditory-only condition.
+$b_A$ is the response bias in the auditory-only condition.
 For this model (as well as all other models in this study), we fixed the values of the means to be the end-points of the corresponding continuum, since these points are the most typical instances in our stimuli.
 Thus, we have $\mu_{A1}=0$ and $\mu_{A2}=4$ (and similarly $\mu_{V1}=0$, and $\mu_{V2}=4$).
-This leaves us with two free parameters: the bias $\epsilon_A$ and the variance $\sigma^2_{A}$.
+This leaves us with two free parameters: the bias $b_A$ and the variance $\sigma^2_{A}$.
 To determine the values of these parameters, we fit the unimodal posterior to human data in the unimodal case.
@@
 In this condition, only the descriptive model is fit to the data, using the expression of the posterior (Equation 1).
-Since the values of the means are fixed, we have 3 free parameters: the variances for the visual and the auditory modalities, respectively, and $\epsilon$, the response bias.
+Since the values of the means are fixed, we have 3 free parameters: the variances for the visual and the auditory modalities, respectively, and $b$, the response bias.
 The visual and auditory baselines as well as the optimal model are not fit to bimodal data, but their predictions are tested against these bimodal data.
@@
 The categorization function of the auditory condition was slightly steeper than that of the visual condition, meaning that participants perceived the sound tokens slightly more categorically and whih higher certainty than they did with the visual tokens.
-For the auditory modality, we obtained the following values:^[all CIs in the paper are 95% confidence intervals] $\epsilon_A=$ `r audBias_val`  [`r audBias_ci2`, `r audBias_ci1`] and $\sigma^2_A=$ `r audVar_val` [`r audVar_ci1`, `r audVar_ci2`].
-For the visual modality, we obtained $\epsilon_V=$ `r visBias_val` [`r visBias_ci2`, `r visBias_ci1`] and $\sigma^2_V=$ `r visVar_val` [`r visVar_ci1`, `r visVar_ci2`]`.
+For the auditory modality, we obtained the following values:^[all CIs in the paper are 95% confidence intervals] $b_A=$ `r audBias_val`  [`r audBias_ci2`, `r audBias_ci1`] and $\sigma^2_A=$ `r audVar_val` [`r audVar_ci1`, `r audVar_ci2`].
+For the visual modality, we obtained $b_V=$ `r visBias_val` [`r visBias_ci2`, `r visBias_ci1`] and $\sigma^2_V=$ `r visVar_val` [`r visVar_ci1`, `r visVar_ci2`]`.
 
@@
 #Here we use the values obtained from the fitting using bootstrap sampling to
+
+#The fit
+model_fit0 <- function (x,y) {
+   1/(1 + exp((-4/vrJ_A_nl1)*x+(-4/vrJ_V_nl1)*y+(8/vrJ_A_nl1)+(8/vrJ_V_nl1)))
+}
 
@@
   facet_grid(experiment ~ model)+
+  theme_few()+
 theme(aspect.ratio = 0.7, 
@@
 
-```{r bimodal, fig.cap = "Human responses vs.
+```{r bimodal, out.width = "\\textwidth", fig.pos = "!h", fig.cap = "Human responses vs.
 models' predictions in the bimodal condition.
-Shape represents auditory distance from the target, and color represents visual distance from the target.", fig.align = "center", out.width = "400px", fig.width=7, fig.height=8}
+Shape represents auditory distance from the target, and color represents visual distance from the target."}
 
@@
 In the descriptive model, all parameters are fit to human responses in the bimodal condition.
-We found $\epsilon=$ `r BiasBi_val` [`r BiasBi_ci2`, `r BiasBi_ci1`], $\sigma^2_{Ab}=$ `r audVarBi_val` [`r audVarBi_ci1`, `r audVarBi_ci2`] and $\sigma^2_{Vb}=$ `r visVarBi_val` [`r visVarBi_ci1`, `r visVarBi_ci2`].
+We found $b=$ `r BiasBi_val` [`r BiasBi_ci2`, `r BiasBi_ci1`], $\sigma^2_{Ab}=$ `r audVarBi_val` [`r audVarBi_ci1`, `r audVarBi_ci2`] and $\sigma^2_{Vb}=$ `r visVarBi_val` [`r visVarBi_ci1`, `r visVarBi_ci2`].
 Note that the variance of both the auditory and visual modalities increased compared to the unimodal conditions.
@@
 The descriptive model explained `r 100*R2_descriptive_1`% of total variance.
-However, since the descriptive model was fit to the same data, there is a risque that this high correlation is due to overfitting.
+However, since the descriptive model was fit to the same data, there is a risk that this high correlation is due to overfitting.
 To examine this possibility, we cross-validated the model using half the responses to predict the other half (averaging across 1000 random partitions).
@@
   select(ID, sound_dist, concept_dist) %>%
-  mutate(prob = model_fit1(sound_dist, concept_dist)) %>%
+  mutate(prob = model_fit0(sound_dist, concept_dist)) %>%
   rowwise() %>%
@@
   bimod_all <- bind_rows(bimod_real, bimod_sim)
-```
-
-```{r echo=FALSE, individual, fig.cap = "Histograms of the values of the visual variance relative to the auditory variance in Experiment 1.
-Light color represents the values derived from each individual participant, and dark color represents simulated data sampled from the descriptive model.", fig.align = "center", out.width = "400px", fig.width=7, fig.height=8}
+
+#Here do some quatiative measure:
+
+#compare the sd of the distribtutions
+ sd_ind<- bimod_all %>%
+  group_by(data) %>%
+  summarise(mean= mean(bimod),
+            sd = sd(bimod))
+```
+
+```{r echo=FALSE, individual, out.width = "\\textwidth", fig.pos = "!h",fig.cap = "Histograms of the values of the visual variance relative to the auditory variance in Experiment 1.
+Light color represents the values derived from each individual participant, and dark color represents simulated data sampled from the descriptive model."}
 
@@
    xlab("Visual variance relative to sound variance") +ylab("Count")+
+  theme_few()+
   theme(aspect.ratio = 0.7)
@@
 For ease of comparison, the simulated distribution was superimposed to the real distribution.
-We found that the real distribution was broader than the simulated distribution, indicating real between-subject variation beyond sampling errors.
-This means that the participants varied in terms of how they wheigthed modalities: Compared to the predictions of the global descriptive model, some participants relied more on the auditory modality, and some relied more on the visual modality.
+We found that the real distribution was broader ($sd=$ `r subset(sd_ind, data=='real')$sd`) than the simulated distribution ($sd=$ `r subset(sd_ind, data=='simulation')$sd`), indicating real between-subject variation beyond sampling errors.
+This means that the participants varied in terms of how they weighted modalities: Compared to the predictions of the global descriptive model, some participants relied more on the auditory modality, and some relied more on the visual modality.
 
@@
 We fit a model for each modality.
-For the auditory modality, our parameter estimates were $\epsilon_A=$ `r audBias_val` [`r audBias_ci2`, `r audBias_ci1`] and $\sigma^2_A+\sigma^2_N=$ `r audVar_val` [`r audVar_ci1`, `r audVar_ci2`].
-For the visual modality, we found $\epsilon_V=$ `r visBias_val` [`r visBias_ci2`, `r visBias_ci1`] and $\sigma^2_V=$ `r visVar_val` [`r visVar_ci1`, `r visVar_ci2`].
+For the auditory modality, our parameter estimates were $b_A=$ `r audBias_val` [`r audBias_ci2`, `r audBias_ci1`] and $\sigma^2_A+\sigma^2_N=$ `r audVar_val` [`r audVar_ci1`, `r audVar_ci2`].
+For the visual modality, we found $b_V=$ `r visBias_val` [`r visBias_ci2`, `r visBias_ci1`] and $\sigma^2_V=$ `r visVar_val` [`r visVar_ci1`, `r visVar_ci2`].
 Figure\ \@ref(fig:unimodal) shows responses in the unimodal conditions as well as the corresponding best fits.
@@
 #### Descriptive model
-We estimated $\epsilon=$ `r BiasBi_val` [`r BiasBi_ci2`, `r BiasBi_ci1`], $\sigma^2_{Ab}+\sigma^2_{Nb}=$ `r audVarBi_val` [`r audVarBi_ci1`, `r audVarBi_ci2`], and $\sigma^2_{Vb}=$ `r visVarBi_val` [`r visVarBi_ci1`, `r visVarBi_ci2`].
+We estimated $b=$ `r BiasBi_val` [`r BiasBi_ci2`, `r BiasBi_ci1`], $\sigma^2_{Ab}+\sigma^2_{Nb}=$ `r audVarBi_val` [`r audVarBi_ci1`, `r audVarBi_ci2`], and $\sigma^2_{Vb}=$ `r visVarBi_val` [`r visVarBi_ci1`, `r visVarBi_ci2`].
 The fit explained `r R2_descriptive_2`% of total variance.
@@
 ### Unimodal conditions
-For the auditory modality, our parameter estimates were $\epsilon_A=$ `r audBias_val` [`r audBias_ci2`, `r audBias_ci1`] and $\sigma^2_A=$ `r audVar_val` [`r audVar_ci1`, `r audVar_ci2`].
-For the visual modality, we found $\epsilon_V=$ `r visBias_val` [`r visBias_ci2`, `r visBias_ci1`] and $\sigma^2_V+\sigma^2_N=$ `r visVar_val` [`r visVar_ci1`, `r visVar_ci2`].
+For the auditory modality, our parameter estimates were $b_A=$ `r audBias_val` [`r audBias_ci2`, `r audBias_ci1`] and $\sigma^2_A=$ `r audVar_val` [`r audVar_ci1`, `r audVar_ci2`].
+For the visual modality, we found $b_V=$ `r visBias_val` [`r visBias_ci2`, `r visBias_ci1`] and $\sigma^2_V+\sigma^2_N=$ `r visVar_val` [`r visVar_ci1`, `r visVar_ci2`].
 Figure\ \@ref(fig:unimodal) shows responses in the unimodal conditions as well as the corresponding fits.
@@
 #### Descriptive model
-We estimated $\epsilon=$ `r BiasBi_val` [`r BiasBi_ci2`, `r BiasBi_ci1`], $\sigma^2_{Ab}=$ `r audVarBi_val` [`r audVarBi_ci1`, `r audVarBi_ci2`], and $\sigma^2_{Vb}+\sigma^2_{Nb}=$ `r visVarBi_val` [`r visVarBi_ci1`, `r visVarBi_ci2`].
+We estimated $b=$ `r BiasBi_val` [`r BiasBi_ci2`, `r BiasBi_ci1`], $\sigma^2_{Ab}=$ `r audVarBi_val` [`r audVarBi_ci1`, `r audVarBi_ci2`], and $\sigma^2_{Vb}+\sigma^2_{Nb}=$ `r visVarBi_val` [`r visVarBi_ci1`, `r visVarBi_ci2`].
 The fit explained `r 100*R2_descriptive_3`% of total variance.
@@
 ```
+
+```{r results = "asis", landscape = FALSE}
+#Here make a table to analyze the exlusive reliance on one modality
+
+total_excl_exp1 <- (only_visual_N_1+only_sound_N_1)/(only_visual_N_1+only_sound_N_1+both_N_1)
+total_excl_exp2 <- (only_visual_N_2+only_sound_N_2)/(only_visual_N_2+only_sound_N_2+both_N_2)
+total_excl_exp3 <- (only_visual_N_3+only_sound_N_3)/(only_visual_N_3+only_sound_N_3+both_N_3)
+
+unimod <- data.frame(
+  Experiment = c('Exp1', 'Exp2', 'Exp3'),
+  Total = c(100*total_excl_exp1, 100*total_excl_exp2, 100*total_excl_exp3),
+  Auditory = c(100*(1-exlusive_prop_1), 100*(1-exlusive_prop_2), 100*(1-exlusive_prop_3)),
+  Visual = c(100*exlusive_prop_1, 100*exlusive_prop_2, 100*exlusive_prop_3)
+)
+
+apa_table(
+  unimod
+  , caption = "The percentage of participants who relied exclusively on either the visual modality or the auditory modality, using a factor of 10 as a cut-off (e.g., we consider that a participant relied exclusively on the visual modality when their auditory variance is a at least 10 times larger than their visual variance).
+We show the percentage compared to the total number of particiapnts in each Experiment (`Total').
+From this subset of participants, we show the percentage of those who relied on the  auditory modality (`Auditory'), and the percentage of those who relied on the visual  modality (Visual')."
+
+)
+
+```
+
 The percentage of participants who relied exclusively on either the visual modality or the auditory modality was `r 100*(only_visual_N_3+only_sound_N_3)/(only_visual_N_3+only_sound_N_3+both_N_3)`%, which is closer to the percentage of Experiment 2, except that now almost all of them relied on the auditory modality (`r 100*(1-exlusive_prop_3)`%).
@@
   scale_x_continuous(limits = c(1.7, 2.3))+
-  scale_y_continuous(limits = c(1.7, 2.3))+theme(aspect.ratio = 1)+
+  scale_y_continuous(limits = c(1.7, 2.3))+
+  theme_few()+
+  theme(aspect.ratio = 1)+
   theme(legend.title = element_blank())
@@
 
+  theme_few()+
+
   theme(aspect.ratio = 1, axis.text=element_text(size=10))+
@@
   scale_y_log10(breaks=c(0.5,1,2),labels=c("Visual bias","Optimal","Auditory bias"))
+
   #coord_cartesian(ylim=c(0, 2.5))
@@
 
-```{r bias, echo=FALSE, warning = FALSE, fig.cap = "Modality preference is characterized as a deviation from the optimal decision threshold.
+```{r bias, echo=FALSE, warning = FALSE, out.width = "\\textwidth", fig.pos = "!h", fig.cap = "Modality preference is characterized as a deviation from the optimal decision threshold.
 A) The decision thresholds of both the optimal and the descriptive models (solid red and black lines respectively).
@@
 B) The value of the decision threshold's slope derived from the descriptive model relative to that of the optimal model.
-Error bars represent 95\\% confidence intervals over the distribution obtained through non-parametric resampling.", fig.align = "center", out.width = "400px"}
+Error bars represent 95\\% confidence intervals over the distribution obtained through non-parametric resampling."}
 
@@
 When putting all these terms together, we the get this final expression for the posterior:
-$$p(W_2 | w)=\frac{1}{1+(1+\epsilon)\exp(\beta_0+\beta_aa+\beta_vv)}$$
+$$p(W_2 | w)=\frac{1}{1+(1+b)\exp(\beta_0+\beta_aa+\beta_vv)}$$
 
@@
 
-$$1+\epsilon=\frac{p(W_1)}{p(W_2)}$$
+$$1+b=\frac{p(W_1)}{p(W_2)}$$
 $$\beta_0=\frac{\mu^2_{A2}-\mu^2_{A1}}{2\sigma^2_{A}}+\frac{\mu^2_{V2}-\mu^2_{V1}}{2\sigma^2_{V}}$$

### 2018-04-13 Writeup/ms.Rmd
changes on ms

@@
 
-How does the mind deal with uncertainty to identify the speaker's intended word?
-To address this question, many researchers in recent years have adopted the rational approach to cognition [@anderson90], which corresponds to Marr's computational level of analysis.
-This approach has had a tremendous impact not only on speech related research [@Norris08; @clayard08; @feldman2009; @kleinschmidt2015], but also on many other disciplines in the cognitive sciences [for reviews, see @chater06; @Knill04; @tenenbaum11].
-Within this framework, researchers typically consider an "ideal observer" model which provides a characterization of the task/goal and shows what the optimal performance should be under this characterization.
-When there is uncertainty in the input, the ideal observer performs an optimal probabilistic inference.
+How does the listener deal with uncertainty to identify the speaker's intended word?
+One rigorous way to approach this question is through conducting an *ideal observer* analysis.
+This research strategy provides a characterization of the task/goal and shows what the optimal performance should be under this characterization.^[It is, thus, a general instance of the rational approach to cognition [@anderson90].
+It can also be seens as an instance Marr's computational level of analysis.] When there is uncertainty in the input, the ideal observer performs an optimal probabilistic inference.
 For example, in order to recognize an ambiguous linguistic input, the model uses all available probabilistic knowledge in order to maximize the accuracy of this recognition.
-Thus, when the task is well specified, the ideal observer model can be seen as a theoretical upper limit on performance.
-It is often used, not so much as a realistic model of human performance, as much as a baseline against which human performance can be compared [@Geisler2003].
-When there is a deviation from the ideal, this can reveal extra constraints on human cognition, such as limitations on working memory or attentional resources.
-
-In this line of research, @clayard08 simulated auditory uncertainty by manipulating the probability distribution of a cue (VOT) that differentiated similar words (e.g., "beach" and "peach").
+When the task is well specified, the ideal observer model can be seen as a theoretical upper limit on performance.
+Thus, it is supposed to be used, not so much as a realistic model of human performance, as much as a baseline against which human performance can be compared [@Geisler2003; @rahnev2018].
+When there is a deviation from the ideal, it can reveal extra constraints on human cognition, such as limitations on the working memory or attentional resources.
+
+The ideal observer analysis has had a tremendous impact not only on speech related research [@Norris08; @clayard08; @feldman2009; @kleinschmidt2015], but also on many other disciplines in the cognitive sciences [for reviews, see @chater06; @Knill04; @tenenbaum11].
+In particular, using this research strategy, @clayard08 simulated auditory uncertainty by manipulating the probability distribution of a cue (VOT) that differentiated similar words (e.g., "beach" and "peach").
 They found that humans were sensitive to these probabilistic cues and their judgments closely reflected the optimal predictions.
-In another work, @feldman2009 studied the perceptual magnet effect, which is related to how categories influence the way the stimuli are perceived.
+In another work, @feldman2009 studied the perceptual magnet effect, which is a phenomenon that involves reduced discriminability near prototypical sounds in the native language [@kuhl1991].
 They showed that this effect can be explained as the consequence of optimally solving the problem of perception under uncertainty.
-Both studies explored optimal performance under uncertainty from one modality, i.e., the auditory modality.
-There is however extensive evidence that information from the visual modality, in particular the speaker's facial features,  influences the perception of auditory information [see @Campbell2008 for a review].
-@bejjanki2011 offered a mathematical characterization of how cues from speech and lip movements can be optimally combined and showed that human performance during audio-visual phonemic labeling was consistent (at least at the qualitative level) with the behavior of the ideal observer.
-
-The speaker's facial features are not the only visual information that can be used to disambiguate the auditory input, however.
-For instance, in a referential context, information about the identity of the semantic referent can be integrated with linguistic information to resolve lexical and syntactic ambiguities in speech [e.g., @Eberhard1995; @Tanenhaus1995; @spivey2002].
-To our knowledge, however, no study offered an ideal observer analysis of word identification in such context, that is, when the mind has to combine cues from the sound and the referent.
+Both @clayard08 and @feldman2009 explored optimal performance under uncertainty in the auditory modality.
+There is, however, extensive evidence that information from the visual modality, such as the speaker's facial features,  also influences speech understanding [see @Campbell2008 for a review].
+@bejjanki2011 offered a mathematical characterization of how probabilistic cues from speech and lip movements can be optimally combined.
+They showed that human performance during audio-visual phonemic labeling was consistent (at least at the qualitative level) with the behavior of the ideal observer.
+
+This previous research, however, did not systematically study speech understanding when the visual information is obtained, not through the speaker's facial features, but through the referential context.
+In fact, experimental findings showed that information about the identity of the semantic referent can be integrated with linguistic information to resolve lexical and syntactic ambiguities in speech [e.g., @Eberhard1995; @Tanenhaus1995; @spivey2002].
+To our knowledge, however, no study offered an ideal observer analysis of word identification in such context, that is, when the listener has to combine cues from the sound and the referent.
 Imagine, for example, that someone is uncertain whether they heard "pea" or "bee", does this uncertainty make them rely more on the referent (e.g., the object being pointed at)?
@@
 
-The visual information provided by the referent is arguably different from the visual information provided by the speaker's facial features (such as lip movements).
-There seems to be at least two fundamental differences between these two cases, and both can influence the cue combination strategy:
-
-<!-- Outside the realm of language per se, research on multisensory integration suggests that the brain integrates information from different modalities in a statistically optimal way, that is, the integration results in a higher overall precision, and modalities are weighed according to their relative reliability [@ernst02].
-However, it is not a priori obvious whether this finding can be extended to word-referent recognition under multimodal uncertainty.
-Indeed, there seems to be at least two fundamental differences between these two cases, and both can influence the cue combination strategy.
--->
-
-First, in the case of audio-visual speech, modalities are understood to differ only in terms of their reliability.
-In a referential context, however, modalities also differ in terms of their roles in the referential process: the auditory input represents the symbol (i.e., the word) whereas the visual input represents the referent.
-It has been suggested that because of its referential property, speech is a privileged signal for humans, starting in infancy [see @vouloumanos2014 for a review].\footnote{There is a debate over whether speech is privileged for infant and adults for the same reasons.
-Whereas Waxman and colleagues suggest that speech is privileged for both infants and adults because of its ability to refer, Sloutsky and colleagues suggest that speech might not have a referential status from the start.
-Rather, according to Sloutsky and colleagues, speech seems to be prefered by infants only because of a low level auditory "overshadowing".} Thus, in a referential context, it is possible that we do not treat the auditory and visual modalities as equivalent sources of information.
-Instead, there could be a bias for the auditory modality beyond what is expected from informational reliability alone.
-
-<!--An example of such integration is when we determine the size of an object using the visual and haptic modalities [@ernst02], or when we determine the spacial location of a stimulus using the visual and the auditory modalities [@alais04] -->
-Second, in the case of audio-visual speech, the associations are expected to be perceptually correlated.
-The expectation for this correlation is such that when there is a mismatch between auditory and visual input, people still integrate them into a unified (but illusory) percept [@mcgurk1976].
+On the face of it, the question of combining information from the sound and the visual referent might seem similar to that of audio-visual speech integration.
+Nevertheless, there are at least two fundamental differences between these two cases, and both can influence the way the auditory and visual cues are integrated:
+
+\noindent First, in the case of audio-visual speech, both modalities offer information about the same underlying speech category.
+They may differ only in terms of their informational reliability.
+In a referential context, however, the auditory and visual modalities are additionally different in terms of the roles they play in the referential process: the auditory input represents the *symbol* whereas the visual input represents the *meaning*.
+It has been suggested that because of its referential property, speech is a privileged signal for humans, starting in infancy [see @vouloumanos2014 for a review].^[There is a debate as to whether speech is privileged for infant and adults for the same reasons.
+Whereas some researchers suggest that speech is privileged for both infants and adults because of its ability to refer [e.g., @waxman1995], others suggest that speech might *not* have a referential status from the start.
+Rather, speech might be prefered by infants only because of a low level auditory ``overshadowing'' [e.g., @sloutsky2003].] Thus, in a referential context, it is possible that listeners do not treat the auditory and visual modalities as equivalent sources of information.
+Instead, there could be a sub-optimal bias for the auditory modality beyond what is expected from informational reliability alone.
+
+\noindent Second in the case of audio-visual speech, the auditory and visual stimuli are expected to be perceptually correlated.
+The expectation for this correlation is such that when there is a mismatch between the auditory and visual input, people still integrate them into a unified (but illusory) percept [@mcgurk1976].
 In the case of referential language, however, the multimodal association is by nature *arbitrary* [@saussure1916; @greenberg1957].
@@
 For instance, as mentioned above, a sub-optimality can be induced by the suggested privileged status of speech or by the arbitrariness of the referential association.
-In order to study possible patterns of sub-optimality, we compare the optimal model (which provides a normative benchmark) to a descriptive model which is identical to the optimal model, except that the parameters in the former are fitted to human responses.
-<!--We do not perform the ideal observer analysis at the individual level, but at the population level.
-There might be some individual variation, but this study addresses the overall performance in the population as a whole.-->
+In order to study possible patterns of sub-optimality, we compare the optimal model (which provides a normative benchmark) to a descriptive model (which is fit to human responses).
+Comparing parameter estimates between these two formulations allows us to quantify the degree of deviation from optimality.
 
@@
 However, in Experiment 2 and 3, participants over-relied on one modality when the other modality was perturbed with additional noise.
-<!-- In the discussion, we talk about the broad implications of these results and especially in relation to some developmental findings in early word learning [e.g., @stager1997].
--->
-
-<!--The nature of the multi-modal associations (redundant vs.
-arbitrary) influences the quality of multi-modal processing in both children and adults: the processing and integration is easier in the case of redundant input, than it in the case of arbitrary input [see @robinson2010 for a review].
-Thus, there is a priori no obvious reason multimodal cue combination in the case of arbitrary assoiations (such as the case of word-referent) should be optimal in the same way cue combination of redundant associations is.
--->
-<!--
-
-A few studies have explored some aspects of audio-visual processing in a probabilistic framework  [e.g., @bejjanki2011; @kleinschmidt2015].
-In these studies, the researchers focused on the specific case of audio-visual speech  where information is *redundant* across modalities.
-In the present work, we study the case of word reference where the audio-visual associations are usually *arbitrary* (Cite Saussure).
-For instance, whereas in the case of audio-visual speech, the sound "bee" and the corresponding lip movements are supposed to merge into a unified percept, there is nothing in the sound "bee" or in the way it can be pronounced, that correlates perceptually with the shape (or some other visual property) of the insect.
-
-More generally, we know that the nature of the multi-modal associations (redundant vs.
-arbitrary) influences the quality of the processing in both children and adults [see @robinson2010 for a review].
-In the case of redundant multimodal information (e.g.
-determining the size of an object through the visual and haptic modality), the sensory integration is often statistically optimal (Ernst and Banks, 2002).
-Optimality in this context means two things: first, the precision of the bimodal estimate increases compared to the unimodal estimates, and second, the cues from different modalities are combined according to their relative reliability.
-In the case of arbitrary associations, empirical studies suggest, rather, sub-optimality.
-In fact, processing of the bimodal input does not increase the precision, it tends to hinder performance instead (Sloutsky, Palmer, Stager, ...
-I should dig into the literature on the arbitrary associations).
-Moreover, modalities are not optimally weighted according to their reliability, instead, one modality dominates the other depending on the task, e.g., Sloutsky et al.
-reported auditory dominance (for kids) and then prefernce for adults (..), and Colovita et al.
-reported visual dominance for adults.
-
--->
-
-# Models and predictions
-
-In this section we describe the multimodal cue combination model.
-First, we briefly introduce the experimental paradigm, and second we explain how behavior in this paradigm can be characterized optimally with an ideal observer model.
+
+# Paradigm and Models
+
+In this section we, first, briefly introduce the multimodal combination task. Then we explain how behavior in this paradigm can be characterized optimally with an ideal observer model.
 
@@
 
-This task is similar to the task introduced by @sloutsky2003, and used in subsequent studies in both children and adults [see @robinson2010 for a review].
-However, in this original task, participants are asked whether or not the two audio-visual presentations are *identical*.
-Such task would allow us to probe audio-visual encoding, but not necessarily language understanding.
-The latter requires---in addition to the perceptual encoding---a categorical judgement, i.e, determining whether or not two similar tokens are members of the same phonological/semantic category.
-Thus, our task is category-based: Participants are asked to press "same" if they think the second item (the test) belonged to the same category as the first (target) (e.g.,  dog-/aba/), even if there is a slight difference in the sound, in the referent, or in both.
-They are instructed to press "different" only if they think that the second stimulus was an instance of the other word category (cat-/ada/).
+This paradigm is adapted from a previous task [@sloutsky2003], which has been used with both children and adults to probe audio-visual encoding [see @robinson2010 for a review].
+In the testing phase of the original task, participants are asked whether or not the two audio-visual presentations are *identical*.
+In the current study, we are interested, rather, in the categorization, i.e., determining whether or not two similar tokens are members of the same phonological/semantic category.
+Therefore, testing in our task is category-based: Participants are asked to press "same" if they think the second item (the test) belongs to the same category as the first (target) (e.g.,  dog-/aba/), even if there is a slight difference in the sound, in the referent, or in both.
+They are instructed to press "different" only if they think that the second stimulus was an instance of the other category (cat-/ada/).
 The task also includes trials where pictures are hidden (audio-only) or where sounds are muted (visual-only).
 These unimodal trials provide us with the participants' evaluation of the probabilistic information present in the auditory and visual categories.
-This unimodal distributions are used as inputs to the optimal combination model, described below.
-
-<!--We assume, for the sake of simplicity, that category tokens vary along a single dimension.
-Phonetic tokens are sampled from an acoustic continuum linking /aba/ to /aba/, and obtained by continuously varying the value of the second formant [@vroomen2004].
-Visual tokens are sampled from a morph continuum linking the picture of a dog and the picture of a cat [@freedman2001].
--->
+As we shall see, these unimodal distributions are used as inputs to the optimal cue combination model.
 
@@
 
-<!--First we describe how probabilistic representations in each modality are derived, and second we explain how they are combined to yield optimal predictions. -->
-
-<!--
-### Unimodal condition
-
-In each modality, we have two categories: /ada/ ($A=1$) and /aba/ ($A=2$) in the auditory dimension, and *cat* ($V=1$) and *dog* ($V=2$) in the visual dimension.
-
-We assume a token's probability of membership in each category to be normally distributed:
-
+We construct an ideal observer model that combines probabilistic information from the auditory and visual modalities.
+In contrast to the  model used in most research on multisensory integration [e.g., @ernst02]---which typically studies continuous stimuli (e.g., size, location)---this probabilistic information cannot be characterized with *sensory noise/variability*, only.
+Indeed, our task involves responses over categorical variables (phonemes and concepts), and therefore, the optimal model in our case should take into account, not only the noise variability around an individual perceptual estimate, but also its *within category variability*, i.e., the uncertainty related to whether this perceptual estimate belongs to a given category [see also @Bankieris17; @bejjanki2011].
+In what follows, we describe a model that accounts for both type of variability.
+First, we describe the model in the simplified case of categorical variability only.
+Second, we augment this simplified model to account for sensory noise.
+
+### Categorical variability
+We assume that both the auditory categories (i.e., /aba/ and /ada/) and the visual categories (cat and dog) are distributed along a single acoustic and semantic dimension, respectively (Figure\ \@ref(fig:model)).
+Moreover, we assume that all categories are normally distributed.
+Formally speaking, if $A$ denotes an auditory category (/ada/ or /aba/), then the probability that a point $a$ along the acoustic dimension belongs to the category $A$ is
 $$ p(a | A) \sim  N(\mu_A, \sigma^2_A) $$
+where $\mu_A$ and $\sigma^2_A$ are respectively the mean and the variance of the auditory category.
+Similarly, the probability that a point $v$ along the visual dimension belongs to the category $V$ is
 $$ p(v | V) \sim  N(\mu_V, \sigma^2_V) $$
-The parameters of these distributions are fitted to the participants' judgement in the unimodal case, i.e., when they only hear the sounds, and when they only see the objects.
-For an ideal recognizer, the probability of choosing category 2 (that is, to answer "different") when presented with, say, an audio instance $a$, is the posterior probability of this category $p(A_2|a)$.
-If we assume that both categories have equal variances, the posterior probability reduces to:
-
-$$p(A_2 | a)=\frac{1}{1+(1+\epsilon_A)\exp(\beta_{a0}+\beta_aa)}$$
-
-with $\beta_a=\frac{\mu_{A_1}-\mu_{A_2}}{\sigma^2_{A}}$, $\beta_{a0}=\frac{\mu^2_{A_2}-\mu^2_{A_1}}{2\sigma^2_{A}}$ and $1+\epsilon_A=\frac{p(A_1)}{p(A_2)}$ is the proportion of the prior probabilities.
-If the identity of the auditory categories is randomized, and if $A_1$ is the target, then $\epsilon$ measures a response bias to "same" if $\epsilon > 0$, and a response bias to "different" if $\epsilon < 0$.
-
-We modeled the visual representation in exactly the same way.
-
--->
-
-The ideal observer model combines probabilistic information from the auditory and visual modalities, and makes a categorical decision.
-How can this task be characterized in a formal way, and what would be the optimal behavior?
-If the stimuli were continuous (e.g., size, location), cues derived from each modality would be characterized with their sensory noise variance only, and (assuming conditional independence) their combined information would be characterized with a simple linear combination rule where the combined estimate is an average of the individual estimates, each weighted according to its relative reliability [@ernst02; @alais04].
-However, in our case decision is made over categorical variables (phonemes and concepts), the optimal model should take into account, not only the noise variability around an individual perceptual estimate, but also its categorical variability (i.e., the probability with which the estimate belongs to a given category).
-
-One way to account for the categorical variability is to model the decision step which maps sensory input onto task-dependent categories [@Bankieris17; @bejjanki2011].
-We represent the decision step as follows (see Figure\ \@ref(fig:model) for illustration).
-If we assume that both the visual and the auditory cues vary along a single dimension, an audio-visual signal $(a,v)$ can be represented as a point in this two-dimensional space, and a word category can be characterized with a bivariate probability distribution over audio-visual tokens.\footnote{For the sake of clarity, we assume here that the sensory noise around this point is small/negligible compared to the categorical variability.
-But see below how the noise can be integrated when its effect is relatively large} Each category is peaked around the most typical audio-visual token, and the probability of membership in the category (the likelihood probability) decreases gradually as the auditory token deviates from the typical sound instance (depending on the variance of the auditory category) and/or as the visual token deviates from the typical visual instance (depending on the variance of the visual category).
-<!--To illustrate how categorical decision is made within this formal framework, suppose we receive an ambiguous image which can be either of a cat or of a dog, associated with a slightly noisy auditory input that sounds more like "cat".
-If the judgment is based on the picture only, this would lead to a random choice between cat and dog.
-However, if the judgement is based on both the picture and the sound (which is less ambiguous), the combined information should lead to a preference for the word cat  we illustrate the cateorical decision making.
-Audio-visual points along this line lead to random responses, meaning that both the auditory and the visual components are maximally ambiguous.
-Audio-visual points that lay on either side of the decision threshold lead to decisions in favor of one word or the other.
-This means that at least one component of this audio-visual token is not totally ambiguous, which leads to a diambiguated combined information.
--->
-
-A crucial feature of the ideal observer model is that it makes use of the entire probability distribution of a given category in order to make optimal decisions [e.g., @clayard08].
-This means that the probability of picking a word (the posterior probability) should mirror closely the probability of the combined information (the likelihood probability).
-For instance, the model becomes less ambiguous and more certain as the tokens get closer to the typical instance of the category.
-In what follows, we formalize this sense of optimality using a Bayesian framework.
-<!--characterized with a likelihood function, e.g., $P(S_V | S)$ and $P(S_A | S)$ for a visual and an auditory cue, respectively.
-If these cues are conditionally independent, their combined information can be written as $P(S_V, S_A | S)=P(S_A | S)P(S_V | S)$.
-The maximum likelihood estimate of this combined information $\hat{S}$ is an average of the individual maximum liklihoods $\hat{S}=w_V\hat{S_V}+w_A\hat{S_A}$, each wighted according to its relative reliability:
-$w_V=\frac{1/\sigma_V^2}{1/\sigma_V^2 + 1/\sigma_A^2}$, and $w_A=\frac{1/\sigma_A^2}{1/\sigma_V^2 + 1/\sigma_A^2}$.
-
-If, however, the target is a categorical dimension, the optimal model should take into account, not only the noise variability arround an individual perceptual estimate, but also its categorical variability (i.e., the probability with which this estimate belongs to a given category).
-For example, upon hearing an audio-visual signal (the sound "cat" associated with the image of a cat), the ideal obsever has both to identify the sensory input and to map it onto the task-dependent categories.
-
-The optimal model that takes into account categorical variability is somewhat different, since -->
-
-<!-- more adequate to the case of redundant information, where, for instance, cues are in the same units, the same coordinates and about the same aspect of the environmental property.
-It is less adequate to describe the case of arbitrary associations where cues are in different units, coordinate systems, or about complementary aspects of the same environmental property [see @ernst04 for further detail].
--->
-
-An auditory category $A$ and a visual category $V$ are defined as distributions in the auditory and the visual dimensions, respectively.
-A word category $W$ is defined as a bivariate distribution in the audio-visual.
-More specifically, we define it as the joint distribution of the auditory and the visual categories.
-For simplicity, we assume both auditory and visual categories to be normally distributed.
-That is, if $w=(a,v)$ is an audio-visual token, then:
-$$ p(a | A) \sim  N(\mu_A, \sigma^2_A) $$
-where $\mu_A$ and $\sigma^2_A$ are respectively the mean and the variance of the auditory category,
-$$ p(v | V) \sim  N(\mu_V, \sigma^2_V) $$
-where $\mu_V$ and $\sigma^2_V$ are  the mean and the variance of the visual category, and
-
+where $\mu_V$ and $\sigma^2_V$ are the mean and the variance of the visual category.
+An audio-visual signal $w=(a,v)$ can be represented as a point in the audio-visual space.
+These audio-visual tokens define bivariate distributions in the bi-dimentional space.
+We call these bivariate distributions *Word categories*, noted $W$, and are distributed as follows:
 $$ p(w | W) \sim  N(M_W, \Sigma_W) $$
-where $M_W=(\mu_A, \mu_V)$ and $\Sigma_W$ are mean and the covariance matrix of the word category.
-We assume that auditory and visual variables are independent (i.e., uncorrelated), so the covariance matrix is simply:
+where $M_W=(\mu_A, \mu_V)$ and $\Sigma_W$ are the mean and the covariance matrix of the word category.
+The main assumption of the model is that the auditory and visual variables are independent (i.e., uncorrelated), so the covariance matrix is simply:
  \[
@@
 
-```{r model, fig.cap = "Illustration of the model using simulated data.
+```{r model, out.width = "\\textwidth", fig.pos = "!h", fig.cap = "Illustration of the model using simulated data.
 A word category is defined as the joint bivariate distribution of an auditory category (horizontal, bottom panel) and a visual semantic category (vertical, left panel).
 Upon the presentation of a word token $w$, participants guess whether it is sampled from the word type $W_1$ or from the word type $W_2$.
-Decision threshold is where the guessing probability is 0.5.", fig.align = "center", out.width = "400px"}
+Decision threshold is where the guessing probability is 0.5."}
 knitr::include_graphics("pictures/model.png", dpi = 108)
@@
 
-This assumption simply says that, given a word-object mapping, e.g., W=("cat"-CAT), variation in the way "cat" is pronounced does not correlate with changes in any visual property of the object CAT, which is a valid assumption.\footnote{Note that this assumptions is more adequate in the case of arbitrary associations such as ours, and less so in the case of redundant association such as audio-visual speech.
+\noindent This assumption simply says that, given a word-object mapping, e.g., $W=$("cat"-CAT), variation in the way "cat" is pronounced does not correlate with changes in any visual property of the object CAT, which is a valid assumption.\footnote{Note that this assumptions is more adequate in the case of arbitrary associations such as ours, and less so in the case of redundant association such as audio-visual speech.
 In the latter, variation in the pronunciation is expected to correlate, at least to some extent, with lip movements.}
 
-Now we turn to the crucial question of modeling how optimal decision should proceed based on the probabilistic information in the auditory and the visual modalities.
-In our task, we have two word categories: dog-/aba/ ($W_1$) and cat-/ada/ ($W_2$).\footnote{This mapping is randomized in the experiments.} Participants can be understood as choosing one of these two word categories (Figure\ \@ref(fig:model)).
+Now we turn to the crucial question of modeling how the optimal decision should proceed given the probabilistic (categorical) information in the auditory and the visual modalities, as characterized above.
+We have two word categories: dog-/aba/ ($W_1$) and cat-/ada/ ($W_2$).\footnote{This mapping is randomized in the experiments.} When making decisions, participants can be understood as choosing one of these two word categories (Figure\ \@ref(fig:model)).
 For an ideal observer, the probability of choosing category 2 when presented with an audio-visual instance $w=(a,v)$ is the posterior probability of this category:
@@
 $$
-Using our assumption that the cues are uncorrelated, we have
+Using our assumption that the cues are uncorrelated, we have:
 $$p(w | W) = p(a,v| W) = p(a| A)p(v| V)$$
-Under this assumption, the posterior probability reduces to:\footnote{See the appendix for the details of the derivation}
+Under this assumption, the posterior probability reduces to the following formula (see Appendix 1 for the details of the derivation):
 \begin{equation}
- p(W_2 | w)=\frac{1}{1+(1+\epsilon)\exp(\beta_0+\beta_aa+\beta_vv)}
+ p(W_2 | w)=\frac{1}{1+(1+b)\exp(\beta_0+\beta_aa+\beta_vv)}
 \end{equation}
 where 
-$$1+\epsilon=\frac{p(W_1)}{p(W_2)}$$
+$$1+b=\frac{p(W_1)}{p(W_2)}$$
 $$\beta_0=\frac{\mu^2_{A2}-\mu^2_{A1}}{2\sigma^2_{A}}+\frac{\mu^2_{V2}-\mu^2_{V1}}{2\sigma^2_{V}}$$
@@
 $$\beta_a=\frac{\mu_{A1}-\mu_{A2}}{\sigma^2_{A}}$$
-$$\beta_v=\frac{\mu_{V1}-\mu_{V2}}{\sigma^2_{V}}$$
-
-The parameter $\epsilon$ represents the differential between the categories' prior probabilities.
-However, since the identity of word categories is randomized across participants, $\epsilon$ measures, rather, a response bias to "same" if $\epsilon > 0$, and a response bias to "different" if $\epsilon < 0$.
+$$\beta_v=\frac{\mu_{V1}-\mu_{V2}}{\sigma^2_{V}}.$$
+
+The parameter $b$ represents the differential between the categories' prior probabilities.
+However, since the identity of word categories is randomized across participants, $b$ measures, rather, a response bias to "same" if $b > 0$, and a response bias to "different" if $b < 0$.
 We expect a general bias towards answering "different" because of the categorical nature of our same-different task: When two items are ambiguous but perceptually different, participants might have a slight preference for "different" over "same".
-
-<!--
-We fix the values of the means as follows.
-Since the endpoints of the auditory and the visual continua are the most typical tokens, we assume that the categories are peaked around these endpoints, so we fix the values of the mean to be these endponts.
-to be the endpoints of the corresponding continuum, meaning that <!--For example, if both the auditory and visual continua are made of 5 steps going from 0 to 4, then $\mu_{A1}=0$ and $\mu_{A2}=4$ (and similarly $\mu_{V1}=0$, and $\mu_{V2}=4$).
---> The values of the means are fixed: They correspond to the value of the most typical tokens in our stimuli.
-Thus, observations from each modality ($a$ and $v$) are weighted according to their reliability in the posterior: $$\beta_a \propto \frac{1}{\sigma^2_{A}}$$ $$\beta_v \propto \frac{1}{\sigma^2_{V}}$$.
-
-Note that the weights account for categorical variability only. For instance, if the speaker generates a target production $a_t$ from an auditory category
+As for the means, their values are fixed, and they correspond to the most typical tokens in our stimuli.
+Finally, observations from each modality ($a$ and $v$) are weighted in Equation 1 according to their reliability: $$\beta_a \propto \frac{1}{\sigma^2_{A}}$$ $$\beta_v \propto \frac{1}{\sigma^2_{V}}.$$
+
+### Sensory variability
+
+So far, we only accounted for categorical variability. For instance, if the speaker generates a target production $a_t$ from an auditory category
 $p(a_t | A) \sim N(\mu_{A}, \sigma^2_{A})$, the ideal model assumes that it has direct access to this production token (i.e., $a=a_t$), and that all uncertainty is about the category membership of this token.
@@
 For example, the observer might not have access to the exact produced target, but only to the target perturbed by noise.
-If we assume this noise to be normally distributed, that is,  $p(a | a_t) \sim N(a_t, \sigma^2_{N})$, then integrating over $a_t$ lead to the following simple expression:
-$$ p(a | A) \sim N(\mu_{A}, \sigma^2_{A}+\sigma^2_{N})$$
-Using an identical reasoning for the case of the visual modality, we end up with the following multimodal weighting scheme in the optimal combination model:
-
- $$\beta_a \propto \frac{1}{\sigma^2_{A}+\sigma^2_{N_A}}$$ $$\beta_v \propto \frac{1}{\sigma^2_{V} +\sigma^2_{N_V}}$$
-To summarize, the posterior provides the optimal model's predictions for how probabilities that characterize uncertainty in each modality can be combined to make categorical decision about the bimodal input.
-The model will be constructed based on data from the unimodal trials, but the predictions of the optimal model will be compared to human responses in the bimodal trials.
-
-## Auditory and Visual models
-
-Besides the optimal model, we also test the predictions of two baselines models: a visual model, which assumes that participants rely only on visual information, and an auditory model, which assumes that participants rely only on auditory information.
-If participants rely on both the auditory and the visual modalities, the optimal model would explain more variance in human responses than the visual model alone or the auditory model alone.
-
-## Descriptive model
-
-The visual, auditory, and optimal models are *normative* models.
+If we assume this noise to be normally distributed, that is,  $p(a | a_t) \sim N(a_t, \sigma^2_{N_A})$, then integrating over $a_t$ leads to the following simple expression:
+$$ p(a | A) \sim N(\mu_{A}, \sigma^2_{A}+\sigma^2_{N_A})$$
+Similarly, in the case of sensory noise in the visual modality, we get
+$$ p(a | V) \sim N(\mu_{V}, \sigma^2_{V}+\sigma^2_{N_V})$$
+Finally, using exactly the same derivation as above, we end up with the following multimodal weighting scheme in the optimal combination model (Equation 1) which takes into account both categorical and sensory variability:
+
+ $$\beta_a \propto \frac{1}{\sigma^2_{A}+\sigma^2_{N_A}}$$ $$\beta_v \propto \frac{1}{\sigma^2_{V} +\sigma^2_{N_V}}.$$
+
+### Optimal cue combination
+
+Equation 1 provides the optimal model's predictions for how probabilities that characterize uncertainty in the auditory and the visual modalities can be combined to make categorical decisions.
+Parameters' estimates of the probability distributions in each modality are derived by fitting unimodal posteriors to the participants' responses in the unimodal conditions, i.e., the condition where only the sounds are heard  or only the pictures are seen (Figure\ \@ref(fig:task)).\footnote{Further technical detail about model fitting in the unimodal conditions will be given in the method section of Experiment 1} Using these derived parameters, the optimal model makes predictions about responses in the bimodal condition where participants both hear the sounds and see the pictures.
+
+### Auditory and Visual baselines
+
+The predictions of the optimal model will be compared to two baselines.
+The first baseline is a visual model which assumes that participants rely only on visual information, and an auditory model, which assumes that participants rely only on auditory information.
+More precisely, these baseline models assumes that the participants' responses in the bimodal condition will not be different from their response in either the visual-only or the auditory-only condition.
+If, as we expect, the participants rely on both the auditory and the visual modalities to make decision in the bimodal condition, the optimal model would explain more variance in human responses than the visual or the auditory model do.
+
+## Descriptive model and analysis of sub-optimality
+
+The optimal model (as well as the auditory and visual baselines) are *normative* models.
 Their predictions are made about human data in the bimodal condition, but their crucial parameters (i.e., variances associated with the visual and auditory modalities) are derived from data in the unimodal conditions.
 In addition to these normative models, we consider a *descriptive* model.
-The parameters of this model are fit to human data in the bimodal condition.
-If the referential task induces sub-optimality (due, for instance, to the arbitrary nature of the sound-object association), then we predict that the descriptive model should explain more variance than the optimal model does.
-
-A systematic comparison of the optimal and the descriptive models would allow us, not only to quantify how much people deviate from optimality, but also to understand precisely how they deviate from this optimality.
+The parameters of this model are fit to actual responses in the bimodal condition.
+If the referential task induces sub-optimality (due, for instance, to the arbitrary nature of the sound-object association), then the descriptive model should explain more variance than the optimal model does.
+
+Comparison of the optimal and the descriptive models allows us, not only to quantify how much people deviate from optimality, but also to understand precisely the nature of this deviation.
 Let $\sigma^2_{A}$ and $\sigma^2_{V}$ be the values of the variances used in the optimal model (derived from the unimodal conditions), and $\sigma^2_{Ab}$ and $\sigma^2_{Vb}$ be the values observed through the descriptive model in the bimodal condition.
 Deviation from optimality is measured in two ways.
-First, we measure the change in the values of the variances specific to each modality, that is, how $\sigma^2_{A}$ compares to $\sigma^2_{Ab}$, and how $\sigma^2_{V}$ compares to $\sigma^2_{Vb}$.
-Second, we measure changes in the proportion of the visual and auditory variances, i.e., how $\frac{\sigma^2_{A}}{\sigma^2_{V}}$ compares to $\frac{\sigma^2_{Ab}}{\sigma^2_{Vb}}$.
-The first measure allows us to test if precision changes for each modality when we move from the unimodal to the bimodal conditions.
-The second allows us to test whether or not the weighting scheme follows the prediction of the optimal model.
-The reason we used the proportion of the variances as a measure of cross-modal weighing is because it corresponds to the slope\footnote{Or more precisely the absolute value of the slope} of the decision threshold in the audio-visual space (Figure\ \@ref(fig:model)).
+First, we measure the change in the values of the variance specific to each modality, that is, how $\sigma^2_{A}$ compares to $\sigma^2_{Ab}$, and how $\sigma^2_{V}$ compares to $\sigma^2_{Vb}$.
+Second, we measure changes in the proportion of the visual and auditory variances, i.e., we examine how $\frac{\sigma^2_{A}}{\sigma^2_{V}}$ compares to $\frac{\sigma^2_{Ab}}{\sigma^2_{Vb}}$.
+The first measure allows us to test if response precision changes for each modality when we move from the unimodal to the bimodal conditions.
+The second allows us to test the extent to which the weighting scheme follows the prediction of the optimal model.
+The reason we used the proportion of the variances as a measure of cross-modal weighting is because this proportion corresponds to the slope\footnote{Or more precisely the absolute value of the slope} of the decision threshold in the audio-visual space (Figure\ \@ref(fig:model)).
 The decision threshold is defined as the set of values in this audio-visual space along which the posterior is equal to 0.5.
-Formally speaking, the decision threshold takes the following form:
+Formally speaking, the decision threshold has the following form:
 
@@
 
-It follows that there are three possible scenarios describing how humans can deviate from optimality. These scenarios are illustrated in Figure\ \@ref(fig:subOptim) and are as follows:
+There are three possible ways human responses can deviate from optimality. These scenarios are illustrated in Figure\ \@ref(fig:subOptim) and are as follows:
 
@@
 
-```{r subOptim, fig.cap = "Illustration using simulated data showing the example of a prediction made by the optimal model (top), and the three possible ways human participants can deviate from this prediction (bottom).
-These cases are the following: 1) The variance increases equally for both modalities, but the weighting scheme (characterized by the decision threshold) is optimal, 2) The auditory variance increases at a higher rate, leading to a preference for the auditory modality, and 3) The visual variance increases at a higher rate, leading to a preference for the visual modality", fig.align = "center", out.width = "400px"}
+```{r subOptim, out.width = "\\textwidth", fig.pos = "!h", fig.cap = "Illustration using simulated data showing the example of a prediction made by the optimal model (top), and the three possible ways human participants can deviate from this prediction (bottom).
+These cases are the following: 1) The variance increases equally for both modalities, but the weighting scheme (characterized by the decision threshold) is optimal, 2) The auditory variance increases at a higher rate, leading to a preference for the auditory modality, and 3) The visual variance increases at a higher rate, leading to a preference for the visual modality."}
+
 knitr::include_graphics("pictures/sub-optimal", dpi = 108)
@@
 
-In this Experiment, we start with testing the predictions in the case where uncertainty is due to ambiguity in terms of category membership only, that is, according to the following weighting scheme:  $$\beta_a \propto \frac{1}{\sigma^2_{A}}$$ $$\beta_v \propto \frac{1}{\sigma^2_{V}}$$ We do not introduce any additional noise in the background, and we assume that sensory noise is negligible compared to categorical variability.
+In this Experiment, we start with testing the predictions in the case where uncertainty is due to categorical variability only (i.e., ambiguity in terms of category memebership).
+We do not add any external noise to the background and we assume that internal sensory noise is negligible compared to categorical variability ($\sigma^2_{A} \gg \sigma^2_{N_A}$, and $\sigma^2_{V} \gg \sigma^2_{N_V}$).
+Thus, we use the following cue weighting scheme:
+
+$$\beta_a \propto \frac{1}{\sigma^2_{A} + \sigma^2_{N_A}} \approx  \frac{1}{\sigma^2_{A} }$$
+$$\beta_v \propto \frac{1}{\sigma^2_{V} + \sigma^2_{N_V}} \approx  \frac{1}{\sigma^2_{V} }.$$
 
@@
 Trials were blocked by condition and blocks were presented in random order.
+The experiment lasted around 15 minutes.
 
@@
 
+prefFit_val_1=dataSave1$estimate[which(dataSave1$variable == "prefFit")]
+prefFit_ci1_1=dataSave1$lower[which(dataSave1$variable == "prefFit")]
+prefFit_ci2_1=dataSave1$upper[which(dataSave1$variable == "prefFit")]
+
 bias_val_1=dataSave1$estimate[which(dataSave1$variable == "bias")]
@@
   scale_y_continuous(limits = c(0, 1))+#theme(aspect.ratio = 0.7)+
+  theme_few()+
   theme(aspect.ratio = 0.7) + facet_grid(Experiment ~ Condition)
   #stat_function(fun = Logistic_v, colour="red"))
-
-```
-
-```{r unimodal, fig.cap = "Human responses in the unimodal condition.
-Points represent the proportion of `different' to `same' responses in the auditory-only condition (left), and visual-only condition (right).
-Error bars are 95\\% confidence intervals.
-Solid lines represent logistic fits.", fig.align = "center", out.width = "400px"}
-
-all_plot
 
@@
 Although the paradigm is within-subjects, we did not have enough statistical power to fit a different model for each individual participant.
-Instead, models are constructed with data collapsed across all participants.
+Instead, models were constructed with data collapsed across all participants.
+That being said, the distribution of responses from individual participants will also be studied.
 The fit was done with a nonlinear least squares regression using the NLS package in R [@bates88].
@@
 The categorization function of the auditory condition was slightly steeper than that of the visual condition, meaning that participants perceived the sound tokens slightly more categorically and whih higher certainty than they did with the visual tokens.
-For the auditory modality, we obtained the following values:^[all CIs in the paper are 95% confidence intervals] $\epsilon_A=$ `r audBias_val`  [`r audBias_ci2`, `r audBias_ci1`] and $\sigma^2_A=$ `r audVar_val` [`r audVar_ci1`, `r audVar_ci2`].
-For the visual modality, we obtained $\epsilon_V=$ `r visBias_val` [`r visBias_ci2`, `r visBias_ci1`] and $\sigma^2_V=$ `r visVar_val` [`r visVar_ci1`, `r visVar_ci2`]`.
+For the auditory modality, we obtained the following values:^[all CIs in the paper are 95% confidence intervals.] $b_A=$ `r audBias_val`  [`r audBias_ci2`, `r audBias_ci1`] and $\sigma^2_A=$ `r audVar_val` [`r audVar_ci1`, `r audVar_ci2`].
+For the visual modality, we obtained $b_V=$ `r visBias_val` [`r visBias_ci2`, `r visBias_ci1`] and $\sigma^2_V=$ `r visVar_val` [`r visVar_ci1`, `r visVar_ci2`].
+
+```{r unimodal, out.width = "\\textwidth", fig.pos = "!h", fig.cap = "Human responses in the unimodal conditions.
+Points represent the proportion of `different' to `same' responses in the auditory-only condition (left), and visual-only condition (right).
+Error bars are 95\\% confidence intervals.
+Solid lines represent best fits."}
+
+all_plot
+
+```
 
@@
 
-```{r bimodal, fig.cap = "Human responses vs.
-models' predictions in the bimodal condition.
-Shape represents auditory distance from the target, and color represents visual distance from the target.", fig.align = "center", out.width = "400px", fig.width=7, fig.height=8}
-
-correlation_plot
-
-```
-
 #### Normative models
@@
 In the descriptive model, all parameters are fit to human responses in the bimodal condition.
-We found $\epsilon=$ `r BiasBi_val` [`r BiasBi_ci2`, `r BiasBi_ci1`], $\sigma^2_{Ab}=$ `r audVarBi_val` [`r audVarBi_ci1`, `r audVarBi_ci2`] and $\sigma^2_{Vb}=$ `r visVarBi_val` [`r visVarBi_ci1`, `r visVarBi_ci2`].
+We found $b=$ `r BiasBi_val` [`r BiasBi_ci2`, `r BiasBi_ci1`], $\sigma^2_{Ab}=$ `r audVarBi_val` [`r audVarBi_ci1`, `r audVarBi_ci2`] and $\sigma^2_{Vb}=$ `r visVarBi_val` [`r visVarBi_ci1`, `r visVarBi_ci2`].
 Note that the variance of both the auditory and visual modalities increased compared to the unimodal conditions.
 
-The descriptive model explained `r 100*R2_descriptive_1`% of total variance.
-However, since the descriptive model was fit to the same data, there is a risque that this high correlation is due to overfitting.
+\noindent The descriptive model explained `r 100*R2_descriptive_1`% of total variance.
+However, since the descriptive model was fit to the same data, there is a risk that this high correlation is due to overfitting.
 To examine this possibility, we cross-validated the model using half the responses to predict the other half (averaging across 1000 random partitions).
 The predictive power of the model remained very high ($r^2$=`r CV_exp1_mean`).
+
+```{r bimodal, out.width = "\\textwidth", fig.pos = "!h", fig.cap = "Human responses vs.
+models' predictions in the bimodal condition.
+Shape represents auditory distance from the target, and color represents visual distance from the target."}
+
+correlation_plot
+
+```
 
@@
 
-<!--the value of the slope derived from the descriptive model (i.e., $-\frac{\sigma^2_{Vb}}{\sigma^2_{Ab}}$) relative the slope of the optimal model (i.e., $-\frac{\sigma^2_V}{\sigma^2_A}$).
-The red dotted line represents the case where this proportion is optimal, meaning that both slopes are equal.
-The blue dotted lines represents the cases where the value of the slope from the descriptive model is double or half that of the optimal model, suggesting a preference for the auditory or the visual modality, respectively.
-Non-parametric resampling of the data showed no evidence of a deviation from the optimal prediction.
--->
-
 ## Discussion
@@
 This is due to the increase in the value of the variance associated with each modality.
-Note however that, despite this increase in randomness, our analysis of modality preference showed that the relative values of these variances were not different (Figure\ \@ref(fig:bias)), meaning that there was no evidence for a modality preference.<!--\footnote{The absence of modality preference does not mean that participants weight modalities equally in the bimodal condtion.
-Rather, it means that they weight modalities according to their relative relaibility, as measure in the unimodal conditions.}In the unimodal analysis, we saw that the precision of the auditory modality was slightly higher than that of the visual modality (i.e., $\frac{1}{\sigma^2_A} > \frac{1}{\sigma^2_V}$ ).
-If modalities were weighed according to their relative reliability (that is, optimally), we would naturally expect the auditory modality to have a higher weight in the bimodal presentation.
-But this is not what we mean by modality preference.
-Rather, the phrase refers to the case of potential sub-optimality where participants would rely on one modality beyond what is explained by the relative reliability of the optimal model.
---> Thus, 1) There was a simultaneous increase in the values of the auditory and visual variances in the bimodal condition compared to the unimodal condition, meaning that the bimodal input lead to an increase in response randomness, and 2) this increased randomness did not affect the relative weighting of both modalities, i.e., the population was weighting modalities according to the relative reliability predicted by the optimal model.
+Note however that, despite this increase in randomness, our analysis of modality preference showed that the relative values of these variances were not different (Figure\ \@ref(fig:bias)), meaning that there was no evidence for a modality preference.
+Thus, 1) There was a simultaneous increase in the values of the auditory and visual variances in the bimodal condition compared to the unimodal condition, meaning that the bimodal input lead to an increase in response randomness, and 2) this increased randomness did not affect the relative weighting of both modalities, i.e., the population was weighting modalities according to the relative reliability predicted by the optimal model.
 This situation corresponds to the first case of sub-optimally described in Figure\ \@ref(fig:subOptim).
@@
 For ease of comparison, the simulated distribution was superimposed to the real distribution.
-We found that the real distribution was broader than the simulated distribution, indicating real between-subject variation beyond sampling errors.
-This means that the participants varied in terms of how they wheigthed modalities: Compared to the predictions of the global descriptive model, some participants relied more on the auditory modality, and some relied more on the visual modality.
-
-<!--If, according to the extreme hypothetical case, the observed near-optimality is spurious, with participants relying exclusively on one or the other modality, we should observe a bimodal distribution (with modes centred around a very small and a very large number).
-If, instead, participants relied on both modalities, we should observe a unimodal distribution centered around a number whose order of magnitude is similar to the one observed with collapsed data.
--->
+We found that the real distribution was broader ($sd=$ `r subset(sd_ind, data=='real')$sd`) than the simulated distribution ($sd=$ `r subset(sd_ind, data=='simulation')$sd`), indicating that there was a real between-subject variation beyond sampling errors.
+This means that the participants varied in terms of how they weighted modalities: Compared to the predictions of the global descriptive model, some participants relied more on the auditory modality, whereas others relied more on the visual modality.
 
@@
 We tested a case where the background noise was added to the auditory modality.
-We were interested to know if participants would treat this new source of uncertainty as predicted by the optimal model, that is, according to the following weighting scheme  $$\beta_a \propto \frac{1}{\sigma^2_{A}+\sigma^2_{N_A}}$$ $$\beta_v \propto \frac{1}{\sigma^2_{V}}$$
+We were interested to know if participants would treat this new source of uncertainty as predicted by the optimal model, that is, according to the following weighting scheme  $$\beta_a \propto \frac{1}{\sigma^2_{A}+\sigma^2_{N_A}}$$ $$\beta_v \propto \frac{1}{\sigma^2_{V}}.$$
 The alternative hypothesis is that noise in one modality leads to a systematic preference for the non-noisy modality.
@@
 `r N_noProb_2 - N_good_2` participants were excluded because they had less than 50\% accurate responses on the unambiguous training trials.
-The final sample consisted of (N = `r N_good_2`) participants.
+The final sample consisted of N = `r N_good_2` participants.
 
@@
 
+prefFit_val_2=dataSave2$estimate[which(dataSave2$variable == "prefFit")]
+prefFit_ci1_2=dataSave2$lower[which(dataSave2$variable == "prefFit")]
+prefFit_ci2_2=dataSave2$upper[which(dataSave2$variable == "prefFit")]
+
 bias_val_2=dataSave2$estimate[which(dataSave2$variable == "bias")]
@@
 These normative models explained, respectively, `r 100*R2_visual_2`%, `r 100*R2_auditory_2`%, and `r 100*R2_optimal_2`% of total variance in mean judgements.
-Note that, in contrast to Experiment 1, the visual model explains more variance than the auditory model.
+Note that, in contrast to Experiment 1, the visual model explained more variance than the auditory model did.
 
 #### Descriptive model
-We estimated $\epsilon=$ `r BiasBi_val` [`r BiasBi_ci2`, `r BiasBi_ci1`], $\sigma^2_{Ab}+\sigma^2_{Nb}=$ `r audVarBi_val` [`r audVarBi_ci1`, `r audVarBi_ci2`], and $\sigma^2_{Vb}=$ `r visVarBi_val` [`r visVarBi_ci1`, `r visVarBi_ci2`].
+We estimated $b=$ `r BiasBi_val` [`r BiasBi_ci2`, `r BiasBi_ci1`], $\sigma^2_{Ab}+\sigma^2_{Nb}=$ `r audVarBi_val` [`r audVarBi_ci1`, `r audVarBi_ci2`], and $\sigma^2_{Vb}=$ `r visVarBi_val` [`r visVarBi_ci1`, `r visVarBi_ci2`].
 The fit explained `r R2_descriptive_2`% of total variance.
@@
 We also found a similar discrepancy from the optimal model as precision dropped for both the auditory and the visual modalities.
-As for the weighting scheme used by participants, contrary to Experiment 1 where modalities were weighted according to their relative reliability, we found in this experiment that the visual modality had a greater weight than what is expected from its relative reliability.
+As for the weighting scheme used by participants, contrary to Experiment 1 where modalities were weighted according to their relative reliability, we found in this experiment that the visual modality had a greater weight than what was expected from its relative reliability.
 This situation corresponds to the second case of sub-optimally described in Figure\ \@ref(fig:subOptim).
@@
 
-In this Experiment, we tested the case where the background noise was added to the visual modality.
-Similar to Experiment 2, we were interested to know if participants would treat this new source of uncertainty as predicted by the optimal model, that is, according to the following weighting scheme  $$\beta_a \propto \frac{1}{\sigma^2_{A}}$$ $$\beta_v \propto \frac{1}{\sigma^2_{V}+\sigma^2_{N_V}}$$
+In this Experiment, we added background noise to the visual modality.
+Similar to Experiment 2, we were interested to know if participants would treat this new source of uncertainty as predicted by the optimal model, that is, according to the following weighting scheme:  $$\beta_a \propto \frac{1}{\sigma^2_{A}}$$ $$\beta_v \propto \frac{1}{\sigma^2_{V}+\sigma^2_{N_V}}.$$
 The alternative hypothesis is that, just like noise in the auditory modality lead to a preference for the visual input in Experiment 2, noise in the visual modality would lead to a  preference for the auditory input.
@@
 We used the same exclusion criteria as in both previous experiments.
-`r N_all_3 - N_noProb_3` participants were excluded because they reported having a technical problem, and `r N_noProb_3 - N_good_3` participants were excluded because they had less than 50\% accurate responses on the unambiguous training trials.
-The final sample consisted of (N = `r N_good_3`) participants.
+N=`r N_all_3 - N_noProb_3` participants were excluded because they reported having a technical problem, and N=`r N_noProb_3 - N_good_3` participants were excluded because they had less than 50\% accurate responses on the unambiguous training trials.
+The final sample consisted of N = `r N_good_3` participants.
 
@@
 We also used the same visual stimuli, but we blurred the tokens using the free image editor GIMP (2.8.20).
-We used a Gaussian blur with a radius\footnote{A features of the filter that affects the intensity of the blur} of 10 pixels.
+We used a Gaussian blur with a radius\footnote{A features that modulates the intensity of the blur} of 10 pixels.
 The experimental procedure was exactly the same as in the previous Experiments.
@@
 
+prefFit_val_3=dataSave3$estimate[which(dataSave3$variable == "prefFit")]
+prefFit_ci1_3=dataSave3$lower[which(dataSave3$variable == "prefFit")]
+prefFit_ci2_3=dataSave3$upper[which(dataSave3$variable == "prefFit")]
+
 bias_val_3=dataSave3$estimate[which(dataSave3$variable == "bias")]
@@
 
-### Unimodal conditions
-For the auditory modality, our parameter estimates were $\epsilon_A=$ `r audBias_val` [`r audBias_ci2`, `r audBias_ci1`] and $\sigma^2_A=$ `r audVar_val` [`r audVar_ci1`, `r audVar_ci2`].
-For the visual modality, we found $\epsilon_V=$ `r visBias_val` [`r visBias_ci2`, `r visBias_ci1`] and $\sigma^2_V+\sigma^2_N=$ `r visVar_val` [`r visVar_ci1`, `r visVar_ci2`].
-Figure\ \@ref(fig:unimodal) shows responses in the unimodal conditions as well as the corresponding fits.
-The auditory data is a replication of the auditory data in Experiment 1. As for the visual data, we see that, in contrast to Experiment 1 and 2, responses were flatter, showing much more uncertainty.
-
-### Bimodal condition
-
-#### Normative models
-Figure\ \@ref(fig:bimodal) compares the predictions of the visual, auditory and optimal models to human responses.
-These normative models explained, respectively, `r 100*R2_visual_3`%, `r 100*R2_auditory_3`%, and `r 100*R2_optimal_3`% of total variance in mean judgement.
-
-#### Descriptive model
-We estimated $\epsilon=$ `r BiasBi_val` [`r BiasBi_ci2`, `r BiasBi_ci1`], $\sigma^2_{Ab}=$ `r audVarBi_val` [`r audVarBi_ci1`, `r audVarBi_ci2`], and $\sigma^2_{Vb}+\sigma^2_{Nb}=$ `r visVarBi_val` [`r visVarBi_ci1`, `r visVarBi_ci2`].
-The fit explained `r 100*R2_descriptive_3`% of total variance.
-Cross-validation using half the responses to predict the other half yielded $r^2= $ `r CV_exp3_mean`.
-
-#### Modality preferences
-Participants' decision threshold suggested a preference for the auditory modality (the non-noisy modality).
-Indeed non-parametric resampling of the data showed an increase in the value of the slope in the descriptive model compared to the optimal model (Figure\ \@ref(fig:bias)).
-
-## Discussion
-We found that the optimal model accounted for almost all the variance ($r^2 =$ `r R2_optimal_3`).
-However, whereas in previous experiments, the optimal model explained more variance than the auditory or the visual models, here the auditory model explained at least as much variance ($r^2 =$ `r R2_auditory_3`).
-Thus, though participants were still sensitive to variation in the noisy visual data in the unimodal condition, they tended to ignore this information in the bimodal condition, and relied almost exclusively on the non-noisy auditory modality.
-The reason why we saw this (floor) effect when we added noise to the visual modality (Experiment 3), and not when we added noise to the auditory modality (Experiment 2), is the fact that our visual stimuli were originally perceived less categorically and with less certainty than the auditory stimuli.
-This made it more likely for the visual categorization function to become flat and uninformative after a few drops in precision due to noise on the one had, and to the additional randomness induced by the bimodal presentation on the other hand.
-
-<!--This behaviour is not so much a qualitative difference from Experiment 2 (where participants relied on both the noisy and the non-noisy modality in the bimodal condition), as much as it is the result of a floor effect.
-Indeed, noise made the visual modality way less steep and barely perceptible in the unimodal condition Figure\ \@ref(fig:unimodal).
-So when we had an additional general drop in precision in the bimodal condition (similar to what we found in Experiment 1 and 2),  participants were no longer able to extract any useful information.
--->
-The general finding corresponds to the third case of sub-optimality described in Figure\ \@ref(fig:subOptim).
-Indeed, precision dropped for both modalities in the bimodal condition compared to the unimodal condition.
-But the drop was much greater for the visual modality, resulting in a much lower weight assigned to it than what is expected from its optimal relative reliability.
-Therefore, just like participants over-relied on the visual modality when the auditory modality was noisy (Experiment 2), they also over-relied on the auditory modality when the visual modality was noisy (Experiment 3).
-
-```{r echo=FALSE}
-#number of participants relying exlusiviely on one modality
-#cut off is a factor of 10
-
-bimodal_bysub_good_3 <- bimodal_bysub_3 %>%
-  filter(bimod > 0.1) %>%
-  filter(bimod < 10)
-
-#Visual modality 
-only_visual_N_3 <- bimodal_bysub_3 %>%
-  filter(abs(bimod) < 0.1) %>%
-  nrow()
-
-#Sound modality 
-only_sound_N_3 <- bimodal_bysub_3 %>%
-  filter(abs(bimod) > 10) %>%
-  nrow()
-
-#the rest
-both_N_3 <- bimodal_bysub_3 %>%
-  filter(abs(bimod) > 0.1) %>%
-  filter(abs(bimod) < 10) %>%
-  nrow()
-
-neg_N_3 <- bimodal_bysub_3 %>%
-  filter(bimod <  -0.1) %>%
-  filter(bimod > -10) %>%
-  nrow()
-
-exlusive_prop_3 = only_visual_N_3/(only_sound_N_3+only_visual_N_3)
-
-```
-The percentage of participants who relied exclusively on either the visual modality or the auditory modality was `r 100*(only_visual_N_3+only_sound_N_3)/(only_visual_N_3+only_sound_N_3+both_N_3)`%, which is closer to the percentage of Experiment 2, except that now almost all of them relied on the auditory modality (`r 100*(1-exlusive_prop_3)`%).
-
 ```{r echo=FALSE, warning = FALSE}
@@
 #Modality preference in an audio-vidual space
-
-prefIdeal_val_1=1.637216
-prefFit_val_1=1.454367
-
-prefIdeal_val_2=0.8367816
-prefFit_val_2=0.529517
-
-prefIdeal_val_3=6.68829 
-prefFit_val_3=13.15958
 
@@
 
+  theme_few()+
+
   theme(aspect.ratio = 1, axis.text=element_text(size=10))+
-  xlab("") +ylab("Relative weighing")+
+  xlab("") +ylab("Relative weighting")+
   scale_y_log10(breaks=c(0.5,1,2),labels=c("Visual bias","Optimal","Auditory bias"))
+
   #coord_cartesian(ylim=c(0, 2.5))
@@
 
+### Unimodal conditions
+For the auditory modality, our parameter estimates were $b_A=$ `r audBias_val` [`r audBias_ci2`, `r audBias_ci1`] and $\sigma^2_A=$ `r audVar_val` [`r audVar_ci1`, `r audVar_ci2`].
+For the visual modality, we found $b_V=$ `r visBias_val` [`r visBias_ci2`, `r visBias_ci1`] and $\sigma^2_V+\sigma^2_N=$ `r visVar_val` [`r visVar_ci1`, `r visVar_ci2`].
+Figure\ \@ref(fig:unimodal) shows responses in the unimodal conditions as well as the corresponding fits.
+The auditory data is a replication of the auditory data in Experiment 1.
+As for the visual data, we found that, in contrast to Experiment 1 and 2, responses were flatter, showing much more uncertainty.
+
+### Bimodal condition
+
+#### Normative models
+Figure\ \@ref(fig:bimodal) compares the predictions of the visual, auditory and optimal models to human responses.
+These normative models explained, respectively, `r 100*R2_visual_3`%, `r 100*R2_auditory_3`%, and `r 100*R2_optimal_3`% of total variance in the mean judgements.
+
+#### Descriptive model
+We estimated $b=$ `r BiasBi_val` [`r BiasBi_ci2`, `r BiasBi_ci1`], $\sigma^2_{Ab}=$ `r audVarBi_val` [`r audVarBi_ci1`, `r audVarBi_ci2`], and $\sigma^2_{Vb}+\sigma^2_{Nb}=$ `r visVarBi_val` [`r visVarBi_ci1`, `r visVarBi_ci2`].
+The fit explained `r 100*R2_descriptive_3`% of total variance.
+Cross-validation using half the responses to predict the other half yielded $r^2=$ `r CV_exp3_mean`.
+
+#### Modality preferences
+Participants' decision threshold suggested a preference for the auditory modality (the non-noisy modality).
+Indeed non-parametric resampling of the data showed an increase in the value of the slope in the descriptive model compared to the optimal model (Figure\ \@ref(fig:bias)).
+
+## Discussion
+We found that the optimal model accounted for almost all the variance ($r^2 =$ `r R2_optimal_3`).
+However, whereas in previous experiments the optimal model explained more variance than the auditory or the visual models, here the auditory model explained at least as much variance ($r^2 =$ `r R2_auditory_3`).
+Thus, though participants were still sensitive to variation in the noisy visual data in the unimodal condition, they tended to ignore this information in the bimodal condition, and relied almost exclusively on the non-noisy auditory modality.
+The reason why we saw this (floor) effect when we added noise to the visual modality (Experiment 3), and not when we added noise to the auditory modality (Experiment 2), is the fact that our visual stimuli were originally perceived less categorically and with less certainty than the auditory stimuli.
+This made it more likely for the visual categorization function to become flat and uninformative after a few drops in precision due to noise on the one had, and to the additional randomness induced by the bimodal presentation on the other hand.
+
+The general finding corresponds to the third case of sub-optimality described in Figure\ \@ref(fig:subOptim).
+Indeed, precision dropped for both modalities in the bimodal condition compared to the unimodal condition.
+But the drop was much greater for the visual modality, resulting in a much lower weight assigned to it than what is expected from its reliability.
+Therefore, just like participants over-relied on the visual modality when the auditory modality was noisy (Experiment 2), they also over-relied on the auditory modality when the visual modality was noisy (Experiment 3).
+
+```{r echo=FALSE}
+#number of participants relying exlusiviely on one modality
+#cut off is a factor of 10
+
+bimodal_bysub_good_3 <- bimodal_bysub_3 %>%
+  filter(bimod > 0.1) %>%
+  filter(bimod < 10)
+
+#Visual modality 
+only_visual_N_3 <- bimodal_bysub_3 %>%
+  filter(abs(bimod) < 0.1) %>%
+  nrow()
+
+#Sound modality 
+only_sound_N_3 <- bimodal_bysub_3 %>%
+  filter(abs(bimod) > 10) %>%
+  nrow()
+
+#the rest
+both_N_3 <- bimodal_bysub_3 %>%
+  filter(abs(bimod) > 0.1) %>%
+  filter(abs(bimod) < 10) %>%
+  nrow()
+
+neg_N_3 <- bimodal_bysub_3 %>%
+  filter(bimod <  -0.1) %>%
+  filter(bimod > -10) %>%
+  nrow()
+
+exlusive_prop_3 = only_visual_N_3/(only_sound_N_3+only_visual_N_3)
+
+```
+
+```{r exclusive, results = "asis", landscape = FALSE}
+#Here make a table to analyze the exlusive reliance on one modality
+
+total_excl_exp1 <- (only_visual_N_1+only_sound_N_1)/(only_visual_N_1+only_sound_N_1+both_N_1)
+total_excl_exp2 <- (only_visual_N_2+only_sound_N_2)/(only_visual_N_2+only_sound_N_2+both_N_2)
+total_excl_exp3 <- (only_visual_N_3+only_sound_N_3)/(only_visual_N_3+only_sound_N_3+both_N_3)
+
+unimod <- data.frame(
+  Experiment = c('Exp1', 'Exp2', 'Exp3'),
+  Total = c(100*total_excl_exp1, 100*total_excl_exp2, 100*total_excl_exp3),
+  Auditory = c(100*(1-exlusive_prop_1), 100*(1-exlusive_prop_2), 100*(1-exlusive_prop_3)),
+  Visual = c(100*exlusive_prop_1, 100*exlusive_prop_2, 100*exlusive_prop_3)
+)
+
+apa_table(
+  unimod
+  , caption = "The percentage of participants who relied exclusively on either the visual modality or the auditory modality, using a factor of 10 as a cut-off (e.g., we consider that a participant relied exclusively on the visual modality when their auditory variance is a at least 10 times larger than their visual variance).
+We show the percentage compared to the total number of participants in each Experiment (`Total').
+From this subset of participants, we show the percentage of those who relied on the  auditory modality (`Auditory'), and the percentage of those who relied on the visual  modality (Visual')."
+
+)
+
+```
+
+The percentage of participants who relied exclusively on either the visual modality or the auditory modality was `r 100*(only_visual_N_3+only_sound_N_3)/(only_visual_N_3+only_sound_N_3+both_N_3)`%, which is closer to the percentage of Experiment 2, except that now almost all of them relied on the auditory modality (`r 100*(1-exlusive_prop_3)`%).
+For ease of comparison, Table \@ref(tab:exclusive) provides a summary of the numbers across the three Experiments.
+
 # General Discussion
 
-When identifying a spoken word under uncertainty, one often needs to combine and make the most of the available multimodal cues.
-While most previous studies focused on the case of audio-visual speech where people combine cues from speech and facial features, this work explored the case of identifying an ambiguous word when the available multimodal cues are speech and the visual referent.
+When identifying a spoken word under uncertainty, one often needs to make the most of the available cues.
+Some previous work studied optimal behavior under uncertainty from the auditory input only [e.g., @clayard08; @feldman2009], and others studied optimality under multimodal uncertainty in auditory speech and visual facial features [e.g.
+@bejjanki2011].
+The current work explored, for the first time, the case of word identification under uncertainty in speech (word form) and the visual word *referent*.
 More specifically, we conducted an ideal observer analysis of the task whereby a model provided predictions about how information from each modality should be combined in an optimal fashion.
-The predictions of the model were tested in a series of three experiments where instances of both the form and the referent were ambiguous with respect to their category membership only (Experiment 1), when instances of the form were perturbed with additional background noise (Experiment 2), and when instances of the referent were perturbed with additional visual noise (Experiment 3).
+The predictions of the model were tested in a series of three experiments where instances of both the form and the meaning were ambiguous with respect to their category membership only (Experiment 1), when instances of the form were perturbed with additional background noise (Experiment 2), and when instances of the referent were perturbed with additional visual noise (Experiment 3).
 
@@
 In Experiment 1, which did not involve background noise, participants not only relied on both modalities, but generally weighted these modalities according to the prediction of the optimal model, that is, according to their relative reliability.
-At the individual level, however, we found evidence of a between-subject variation: Some participants relied slighly more on the visual modality, whereas others relied slighly more on the auditory modality.
+At the individual level, however, we found evidence of a between-subject variation: Some participants relied slightly more on the visual modality, whereas others relied slightly more on the auditory modality.
 
@@
 This finding contrasts with research on  multisensory integration where associations tend to lead to a higher precision [e.g., @ernst02].
-Nevertheless, there is a crucial difference between these two situations.
+Nevertheless, there is a crucial difference between these two situations (besides the obvious difference in terms of the models used).
 Research on  multisensory integration (of which audio-visual speech is arguably an instance) deals with redundant multimodal cues, and these cues are integrated into a unified percept.
 In contrast, the word-referent association is usually arbitrary and, in particular, the cues are not expected to be correlated perceptually.
-Therefore the mind cannot form a unified percept, rather, it must encode information separately from both modalities and retain this encoding through the decision making process.
+Therefore the observer cannot form a unified percept, rather, it must encode information separately from both modalities and retain this encoding through the decision making process.
 Retaining two separate cues at the same time instead of forming one unified percept (as in multisensory integration of redundant cues), or instead of retaining only one cue (as in the unimodal case), is likely to place extra-demand on cognitive resources, which, in turn, can cause general performance to drop.
-Indeed, there is evidence that cognitive load has a detrimental effect on word recognition, which can be due to a reduction in perceptual acuity [@mattys11].
-Similar to our finding, previous experimental studies reported that in both children and adults, identifying new ambiguous form-referent mappings is usually associated with what appears to be a decrease in speech perception acuity [@stager1997; @pajak2016].
-@hofer2017 provided a probabilistic model of this phenomenon, which they similarly characterized as an increase in the noise variance of the auditory modality.
-Our finding replicates this previously documented fact, and additionally suggests that the reduction in perceptual acuity occurs simultaneously in both the auditory and the visual modalities.
+Indeed, there is evidence that cognitive load has a detrimental effect on word recognition.
+This phenomenon  can be due to a reduction in perceptual acuity [e.g., @mattys11].
+
+Some previous research found a similar case of suboptimal behavior.
+For instance, studies that explored  the identification of ambiguous, newly learned pairs of word-referent associations all reported what appears to be a decrease in speech perception acuity in both children [@stager1997] and adults [@pajak2016].
+Recently, @hofer2017 provided a probabilistic model of this phenomenon.
+In agreement with the finding in the current study, @hofer2017 characterized the apparent reduction in perceptual acuity as an increase in the noise variance of the auditory modality.
+Our finding, besides providing more evidence to this documented fact, suggests that the reduction in perceptual acuity may occurs simultaneously in both the auditory *and* the visual modalities.
 
@@
 However, and generally speaking, these studies do not differentiate between an optimal compensatory strategy (i.e., relying more on the alternative source while using all information still available in the distorted signal), and a sub-optimal strategy (i.e., relying more on the alternative source while ignoring at least some of the information still available in the distorted signal).
-The formal approach followed in this paper allowed us to tease apart these two possibilities, and the analysis supports the sub-optimal compensatory strategy: The preference for the non-noisy modality is above and beyond what can be explained by the relative reliability alone, meaning that the participant tend to ignore at least part of the information still available in the noisy modality.
-
-This second case of sub-optimal behavior is possibly related to the fact that language understanding under degraded listening conditions is cognitively more taxing than language understanding under normal conditions [@Ronnberg10].
-This fact can lead to a preference/bias towards alternative sources of information when these sources are available.
-One could explain this phenomenon in terms of the metacognitive experience about the fluency with which information is processed.
-The perceived perceptual fluency (e.g., the ease with which a stimulus’ physical identity can be identified) can affect a wide variety of human judgements [see @schwarz2004 for a review].
+The formal approach followed in this paper allowed us to tease apart these two possibilities, and the analysis supports the sub-optimal compensatory strategy: The preference for the non-noisy modality is above and beyond what can be explained by the relative reliability alone, meaning that the participants tend to ignore at least part of the information still available in the noisy modality.
+
+This second case of sub-optimal behavior is possibly related to the fact that language understanding under degraded  conditions is cognitively more taxing than language understanding under normal conditions [e.g., @Ronnberg10].
+This fact can lead to a bias against the more noisy cue.
+One could also explain this phenomenon in terms of the metacognitive experience about the fluency with which information is processed.
+The perceived perceptual fluency (e.g., the ease with which a stimulus' physical identity can be identified) can affect a wide variety of human judgements [see @schwarz2004 for a review].
 In particular, variables that improve fluency tends to increase liking/preference [@reber98].
@@
 
-In this study, we tested the extent to which people would be optimal in combining uncertain auditory and visual cues to recognize words.
-This required that we use a case of double ambiguity, that is, a case where both the word forms ("ada"-"aba") and the referents (cat-dog) were similar and, thus, confusable.
-One could wonder about the extent to which such case occurs in real languages?
-Cross-linguistic corpus analyses suggest that the lexical encoding tends towards double ambiguity in many languages [@dautriche17; @Monaghan2014; @Tamariz2008].
-For instance, @dautriche17 analysed 100 languages and found that word that are similar phonologically  tend to be similar semantically as well, beyond what could be explained by chance.
-Crucially, they found this trend in a set of monomorphemic lemmas in four languages, suggesting that the effect is not driven by morphological regularities.
-These studies suggest that the case of double uncertainty, though perhaps not pervasive, could be a real issue in language as it increase the probability of confusability.
-Moreover, it is important to keep in mind that ambiguity in both the form and the referent can be induced by an external noisy context even when these forms and referents are not confusable in normal situations.
+An important question to ask is how the combination mechanism---as revealed in our controlled study---scales up to real life situations.
+Note that in order to test audio-visual cue combination under uncertainty, we had to use a case of double ambiguity, that is, a case where both the word forms ("ada"-"aba") and the referents (cat-dog) were similar and, thus, confusable.
+However, to what extent does such case occur in real languages?
+Cross-linguistic corpus analyses suggest that lexical encoding tends, surprisingly, towards double ambiguity in many languages [@dautriche17; @Monaghan2014; @Tamariz2008].
+For instance, @dautriche17 analyzed 100 languages and found that words that are similar phonologically  tend to be similar semantically as well, beyond what could be explained by chance.
+These studies suggest that the case of double uncertainty, though perhaps not pervasive, could be a real issue in language as it increase the probability of confusability for many words.\linebreak Besides the case of double ambiguity intrinsic to language, there are two situations where our mechanism might play a significant role.
+The first is when ambiguity in both the form and/or the referent is induced by an external noisy context even when these forms and referents are not confusable in normal situations.
+The second case is that of early word learning, and we will discuss this case in more detail in what follows.
 
@@
 Previous research in early word learning has---whether implicitly or explicitly---largely treated the process of learning form and of learning meaning as independent.
-<!--Babies are understood to first master the form, learning to ignore phonologically irrelevant variation (such as differences in talker, speech rate, emotion, and linguistic context) (see Kuhl, 2004 for a review).
-Only when the form representation is refined and ready, can they start mapping the form to meaning (Bloom, 2000)-->However, the developmental data reviewed above shows that children do not wait to have completed the acquisition of form to start learning meanings, and that both form and meaning representations develop, rather, in a parallel fashion.
+However, the developmental data reviewed above shows that children do not wait to have completed the acquisition of form to start learning meanings, and that both form and meaning representations develop, rather, in a parallel fashion.
 A few studies pointed to the possibility of an interaction between sound and meaning in early acquisition.
@@
 
-In conclusion, this work studied the mechanism of word identification under uncertainty in both the word form and the word meaning.
+One limitation of the work is that we used simplified stimuli.
+For the auditory modality, we used speech categories that varied along a single acoustic dimension.
+While this dimension might be sufficient to recognize  words in our specific case, in general the speech signal may be more complex, varying along several acoustic/phonetic dimensions.
+Additionally, these dimensions may be highly variable due to various kinds of speaker and context differences.
+The same thing can be said about the referential stimuli.
+Here we used a continuum along a single morph dimension in order to construct a multimodal input where the auditory and visual components have symmetrical properties.
+Though such morph is not the exact visual variability that people would encounter in they daily lives, it allowed us to precisely test the role of auditory and visual information in the cue combination process.
+Parameterizing semantic dimensions is a notoriously difficult problem, but morphs have been used in previous research as a reasonable proxy [@freedman2001; @havy2016; @sloutsky2004].
+It is an open question as to whether people use the same strategy in controlled laboratory conditions, as in more naturalistic settings where they have to deal with various levels of variability.
+However an answer to this question is likely to involve a multifaceted approach, involving---besides laboratory experiments---analyses of corpora with a more realistic multimodal input [e.g., @fourtassi2014b; @harwath2016; @roy2015].
+
+In conclusion, this work studied the mechanism of word identification under uncertainty in both the word form and the word referent.
 To our knowledge, this is the first study that performs an ideal observer analysis of this task.
@@
 However, they also showed patterns of sub-optimality especially when the stimuli were perturbed with additional background noise.
-Future work will extend the present formal framework in order to account for how children use multimodal cues to refine their early phonological and semantic representations.
-
-# Appendix: derivation of the posterior (equation 1)
+Though the present study did not directly address the issue of early word learning, it provides a framework where developmental questions can also be investigated.
+For instance, future work should explore whether children, like adults, use probabilistic cues from both the auditory and the visual input to recognize ambiguous words,  the extent to which they combine these cues in an optimal fashion, and whether these combination help them with refining their early phonological and semantic representations.
+
+# Appendix 1: derivation of the posterior (Equation 1)
 
@@
 $$p(W_2 | w)=\frac{1}{1+\frac{p(w|W_1)}{p(w|W_2)} \frac{p(W_1)}{p(W_2)}}$$
-In order to further simplify the quantity $\frac{p(w|W_1)}{p(w|W_2)}$, we use our assumption that the cues are uncorrelated, 
+In order to further simplify the quantity $\frac{p(w|W_1)}{p(w|W_2)}$, we use our assumption that the cues are uncorrelated:
 $$p(w | W) = p(a,v| W) = p(a| A)p(v| V)$$
@@
 
-When putting all these terms together, we the get this final expression for the posterior:
-$$p(W_2 | w)=\frac{1}{1+(1+\epsilon)\exp(\beta_0+\beta_aa+\beta_vv)}$$
+When putting all these terms together, we obtain this final expression for the posterior:
+$$p(W_2 | w)=\frac{1}{1+(1+b)\exp(\beta_0+\beta_aa+\beta_vv)}$$
 
@@
 $$\beta_a=\frac{\mu_{A1}-\mu_{A2}}{\sigma^2_{A}}$$
-$$\beta_v=\frac{\mu_{V1}-\mu_{V2}}{\sigma^2_{V}}$$ 
-<!--
-as further data about sound-meanining associations accumulate, making the categories more refined and precise.
-
-Moreover, modeling studies the possibility of an interaction or synergy between early represention interaction between sound and menaning
-
-A few studies explicitely pointed to the possibility of an interaction between sound and meaning in early acqusition. For instance, Waxman and Markow (1995) showed that a
-
-It follows that Cue combination is not only necessary to recognize a word (as with ault), but also to lrefine the underlying representations, leading to a leaning synergy (Fourtass and Dupoux, 2014).
-Waxman and Yeung, but they assume an ambiguous state.
-Here we suggest that even if non of the representation
-
-If we take the perspective of infromation theory, communication is basically a process of information transfer in a noisy channel (Shannon, 1948), and information encoding should be such that the listener is able to recover what is being said.
-Therefore, the confusability of distinct words should be minimized.
-In particular, similar meanings should be encoded with phonologically distinct words.
-As it turns out, cross-lingusitc corpus analyses reveal an opposite trend, suggesting that the constraints of communication might not be the only force shaping the struture of the lexicon (Dautriche et al.
-2016; Monaghan et al., 2014; Shillcock et al., 2001; Tamariz, 2008).
-For instace, Dautriche et al.
-2015 analysed 100 languages and found that word that are similar phonologically  tend to be more similar semantically as well, above what could be explained by chance.
-Crucially, they found this trend in a set of monomorphemic lemmas in four languags, suggesting that the effect is not driven by morphological regularities.
-These studies suggest that the case of souble uncertainty, though perhabps not pervasive, could be a real issue beyond our controlled experiment, and that an optimal cue combination strategy might be crucial for word recognition in real life situations.
-
-Here talk about development
-
-They found that minimal pairs are more likely to be found among semantically related words than semantically different words.
-
-Crucially,
-
-From an information theory perspective, communication can be modeled as the transfer of information over a noisy channel (Shannon, 1948).
-Successful commu- nication requires listeners to be able to recover what is being said; therefore, the likeli- hood that two distinct words would be confusable should be minimized according to this constraint.
-There is much evidence that perceptual distinctiveness plays an important role in shaping the phonology of languages
-
-However, in order for the optimal combination strategy to be relevant to our understading of word recognion, we need   play any role beyond a mere controlled experiment, cross-lingsuitic corpus analyses indicate that this is not an infrequent phenomeon in real languages.
-For example,
-
-analyzed the relationship between semantic relatedness and the likelihood of finding a minimal pair and found that minimal pairs are more likely among semantically similar words than semantically distant words.
-
-The arbitraniess of the sign in natural language means that the word form is not necessarilly related to the features of the semantic catgory, and a corrola
-
-in rather extreme situation  tested a rather extreme case of uncertainty where both
-
-To explore how the mind However, insights in this work can shed light on   but in a simple case when the underlying visual and auditory categories were familiar.
-Indeed, on the visual side, cat and dog tokens belong obviously to existing visual categories.
-On the auditory side, though the words ("ada"/"aba") are novel, the phonemic categories that differentiate the words are familiar (i.e., /d/ and /b/).
-In the context of early word learning, however, children are often learning both the categories and their mapping at the same time.
-In fact, children start learning visual and sound categories at an early age [e.g., @quinn93;@werker1984], and there is evidence that word-referent-like interaction operates at the same time, even when the categories are not yet fully mastered [e.g., @waxman1995; @yeung09].
-In fact, @fourtassi2014a proposed that this interaction can create a synergy (or a bootstrapping effect) whereby progress made on one level (e.g., the meaning categories) can benefit the other level (the sound categories).
-
-In what follows we explain how an account that combines both category learning and optimal multimodal integration can proceed, and how such account can provide us with a useful developmental framework.
-In the light of this framework, we speculate about possible new interpretation of some puzzling results in early word learning [@stager1997 and seq].
-For starters, remember that one assumption of the model is that visual and auditory categories can be characterized with a variance that determines their precision/reliability.
-At the behavioral level, the variance is related to the shape of the categorization function: a small variance corresponds to a rather steep categorization function, meaning that one can tell with high certainty whether or not a token belongs to the category at hand.
-Vice versa, a large value of the variance corresponds to a rather flat categorization function, which means that for most tokens, one cannot tell with high certainty whether or not these tokens belong to the category at hand.
-
-How can this formal characterization fit in a developmental scenario?
-One could imagine that, initially, visual and auditory categories have relatively large variances, and that development consists in reducing the values of the variances as evidence accumulates, making the categories more refined and precise.
-A scenario similar to this one has been previously suggested to explain the development of early sound categories.
-For example, @yoshida2009 suggested that the early categories may be noisier or that they may be encoded with relatively lower confidence.
-For the semantic categories, we can find similar (although perhaps not identical) ideas.
-For instance, Clark (1973) suggested that the initial meaning categories tend to be larger than adult categories, since fewer features are used to pick out referents (e.g., dog for all four-legged animal, ball for all round objects).
-
-The combination of this developmental scenario in terms of category variance with the optimal integration account introduced in this paper provides possible new insights into the mechanism of word learning.
-Let's elucidate this idea through an example in the developmental literature.
-@stager1997 showed that 14 m.o (as opposed to 17 m.o) have difficulties mapping two minimally different sounds (e.g., "bih"/"dih") to two novel objects, despite the fact that they can perceptually differentiate these sounds.
-Our proposal explains these patterns of failure and success in terms of developmental changes in the variances associated with the visual and phonological categories, combined with the ability to integrate sound and visual cues according to their reliability.
-Suppose that both members of a given sound contrast ("bih"/"dih") initially fall within the uncertainty range of a single sound category.
-If this uncertainty diminishes with age (as the category gets more refined), then what used to be likely at a certain point in development (e.g., 14 m.o), may later become unlikely.
-In particular, at 17, m.o, it may become necessary to attribute the sound contrast to two neighboring categories instead of a single one.
-But how can 14 m.o possibly consider one broad category for both sounds if these sounds are paired with different objects?
-This is where the optimal combination account may come into play.
-Indeed, even if the objects are perceptually different, they may still be similar in the 14 m.o's early semantic space.
-If babies make categorical decision based on both auditory and visual cues, then having evidence that the auditory tokens belong to the same category can prompt them to consider the possibility that even the objects are variations within the same (broad) semantic category.
-Thus, 14 m.o may be learning one broad word-referent association instead of two specific associations.
-According to the present account, what was considered a "failure" in learning might, in fact, be the optimal decision within the 14 m.o's own developmental context!
-
-This account makes two main predictions.
-First, if the sounds are more acoustically different (e.g., "lif"/"neem" instead of "bih"/"dih"), babies would be more likely to posit and learn two word-referent associations, because there would be more evidence pointing in that direction from the auditory side.
-Second, if the objects are more semantically distant (a living object vs.
-a non-living object, instead of the two perceptually different toys used in the original study), babies would be more likely to posit and learn two word-referent associations, because now there would be more evidence pointing in that direction from the visual side.
-In fact, @stager1997 tested and proved the first prediction.
-The second prediction remains to be tested.
-If proven, it would provides support to the optimal combination account in early language learning.
-
-In a similar study that used eye tracking in addition to overt responses, Creel (2012) replicted these findings and showed that the chidlren's visual fixations revealed slower recognition for the novel word, suggesting a hightened uncertainty.
-
-(Merriman and Schuster, 1991; Creel, 2012).
-
-In fact, though children start learning the categories at an early age, typically before their first birthday [e.g., @werker1984], this learning is not perfect from the start.
-In particular, early categories can be noisier and/or encoded with lower confidence.
-It follows that recognizing familar or novel words might be a greater challenge for children than it is for adults.
-For example, in a word recognition task, though toddlers prefer the correct pronounciation of a familiar word (e.g., "baby") over a novel but phononlogically similar word ("vaby"), they do not totally reject the novel word: they still look at the familiar word's referent more than a different object (Swingley and Aslin, 2000).
-A similar pattern was found with preschoolers using a mutual exclusivity paradigm.
-Mutual exclusivity is a bias that children have to interpret novel words as referring to novel objects rather than familiar objects (Markman & Wachtel, 1988).
-For example, when presented with a ball and a novel object and asked to select, say, a "dax", participants typically point to the novel object.
-Merriman and Schuster (1991) found that this effect decreases markedly in 4-year-olds if the novel word is phonologically similar to a familiar word.
-In other words, children do not necessarily interpret a novel word "bool" to be a label for the novel object, but tend to extend it to the familiar object (a ball).
-In a similar study that used eye tracking in addition to overt responses, Creel (2012) found that preschoolers, similar to Merriman and Schuster (1991), mostly select the familiar objet.
-Moreover, the chidlren's visual fixations indicated slower recognition for the novel word, suggesting a hightened uncertainty.
-
-Children representeation of newly learned words is even more fragile than their representation of familair words (Swingley, 2007).
-For example, @stager1997 showed that 14 m.o have difficulties mapping two minimally different sounds (e.g., "bih"/"dih") to two novel objects, despite the fact that they can perceptually differentiate these sounds.
-Specifically, their task required that infants reject the switch trials, that is, when an object (e.g.
-the one associated with the word "bih") is labelled with the wrong name ("dih").
-Yoshida et al.
-(2009) tested infants with a preferential looking paradigm that reduced the memory demands in the orginal task.
-After the leanrning phase, they monitored the infants' looking patterns when presented with both objects at the same time, instead of comparing their attitude to the correct vs.
-the wrong associaton.
-In this simplified task, they found that infants succeeded in picking the correct object.
-In order to explain why infants fail in the switch task but succeed in the simpler preferential looking paradigm, Yoshida et al.
-(2009) proposed that phonological features might be encoded probabilistically.
-Early word representations for "din" and "bin"", though distinct, might be encoded with a relatively lower confidence.
-Thus, uncertainty generated by  the matching bin label, may  not  surpass  the  threshold  levelrequired  for  rejection  of   the  pairing,  resulting  in  nodifference  between  the  same  and  Switch  trials
-In the visual choice paradigm, thecritical  criterion  involves  a  direct  comparison  of,  and  aforced choice between, the two objects.
-Here, the relativelyslight difference in uncertainty is sufficient; the 60% matchwould be considered to be a better fit than the 40% match,allowing infants to demonstrate their learning ability.
-
-Actually this probabilistic accout can also explain the case of famialr words
-Talk about Swingley 2007
-For the semantic, see here:
-https://www.ncbi.nlm.nih.gov/pubmed/12003515
-
-Yoshida et al. (2009)
-
-Our proposal explains these patterns of failure and success in terms of developmental changes in the variances associated with the visual and phonological categories, combined with the ability to integrate sound and visual cues according to their reliability.
-Suppose that both members of a given sound contrast ("bih"/"dih") initially fall within the uncertainty range of a single sound category.
-If t
-
-There is evidence supporting (albeit indirectly) the possibility of effects of phonological similarityon induction.
-In particular,Merriman and Schuster (1991)demonstrated that phonological similarityof words led to attenuated ‘‘mutual exclusivity’’ effects in 2- and 4-year-olds.
-Mutual exclusivity is atendency of toddlers and young children to interpret novel words as referring to novel items ratherthan familiar items (Markman & Wachtel, 1988).
-For example, when presented with an apple and anovel object and asked to select adax, participants pointed to the novel object.Merriman and Schuster(1991)found that the effect decreases markedly or disappears if the novel word is phonologically sim-ilar to a familiar word; children would not necessarily extend a novel wordjappleto a novel object butmight instead extend it to an apple
-
-More generally, toddler's eye fixation show a graded pattern in terms of recognition, that is, they look less often at the correct object as the mispronouciation gets gradually more different from the correct the pronounciation
-more different the mispronouciation is to the correct pronooucition, the more
-
-children's looking patterns show a graded recognition uncertainty as the misponounciation's phonetic dissimilarity to the typical proniucaution increases (Morgan while...).
-
-One could even argue that the problem of word learning/recognition under multimodal uncertanty is a more pressing issue for children in the process of language acqiusition than it is for adults who already master the language.
-forms with high phonetic details
-
-Talk about Swingley work for familar words:
-
-Talk about Yoshida for novel words
-
-Talk about the fact that this uncertainty develops into early chidhood
-
-However, children do not wait to have fully mastered the speech and semantic categories before they start attempting to map form to meaning.
-
-Because  of  the  greater  noise  inherent  in  children’s  perceptual- processing  systems,  the  same  acoustic  stimulus  may  effectively be less reliable for children than adults (Lyons &  Ghetti,  2011;  Neuman  &  Hochberg,  1983)
-
-How can this formal characterization fit in a developmental scenario?
-One could imagine that, initially, visual and auditory categories have relatively large variances, and that development consists in reducing the values of the variances as evidence accumulates, making the categories more refined and precise.
-A scenario similar to this one has been previously suggested to explain the development of early sound categories.
-For example, @yoshida2009 suggested that the early categories may be noisier or that they may be encoded with relatively lower confidence.
-For the semantic categories, we can find similar (although perhaps not identical) ideas.
-For instance, Clark (1973) suggested that the initial meaning categories tend to be larger than adult categories, since fewer features are used to pick out referents (e.g., dog for all four-legged animal, ball for all round objects).
-
-They also start to map sound a
-
-However, this learning is not perfect from the start ,
-
-Indeed, since both the speech categories and the semantic categories are still not fully mastered by children, the lingusitic input can in generarl be more uncertain for the latter, which makes the problem of inference under uncertainty a more pressing issue.
-
-In early development, the combination of statistics from the auditory and the visual referent can be crucial to learn the
-
-Recognition of novel words 
-For kids the uncertainty is higher 
-word referent 
-In this study, we explored the mechanism of word identification, but in a simple case when the underlying visual and auditory categories were familiar.
-Indeed, on the visual side, cat and dog tokens belong obviously to existing visual categories.
-On the auditory side, though the words ("ada"/"aba") are novel, the phonemic categories that differentiate the words are familiar (i.e., /d/ and /b/).
-In the context of early word learning, however, children are often learning both the categories and their mapping at the same time.
-In fact, children start learning visual and sound categories at an early age [e.g., @quinn93;@werker1984], and there is evidence that word-referent-like interaction operates at the same time, even when the categories are not yet fully mastered [e.g., @waxman1995; @yeung09].
-In fact, @fourtassi2014a proposed that this interaction can create a synergy (or a bootstrapping effect) whereby progress made on one level (e.g., the meaning categories) can benefit the other level (the sound categories).
-
-<!--This work, as well as the model, is about the mechanism of word-referent recognition when the underlying visual and auditory categories are supposed to be already familiar.
-On the visual side, cat and dog tokens belong obviousely to existing categories.
-Uncertainty is about where the boundary lies, and how this perceived boundary changes when evidence from the auditory data varies from clear to ambiguous.
-On the auditory side, though the words ("ada"/"aba") are novel, the phonemic categories that differentiate the words are familiar (i.e., /d/ and /b/).
-Thus, similar to the visual categories, uncertainty is about where the phonological boudary lies, and also how this perceived boundary changes when evidence from the visual data varies from clear to ambiguous.
-The main finding of this paper is that people shift the categories' boudary depending on evidence form both auditory and visual input, and that, generally speaking, evidence from both modalities are weighted in a near optimal way.
--->
-
-<!--
-
-This, in turn, would make them interpret the sound difference as alternative pronunciations of the same word\footnote{The reverse reasining is plausible as well, and in fact, can explain why in the same experiment, the use of acoustically distant words ("lif"/"neem"" instead of "bin"/"din) made 14 m.o succeed in the same task}.
-A prediction of the optimal model would be that the use of semantically distant objects can induce success with the same similar sounding words.
-
-new explanations for some findings in the developmental literature.
-We will focus on two influenceial lines of work relatad to multimodal processing: the development of modality dominance (Robertson and Sloutsky, 2004), and the development of the learning of similar sounding words (Stagter and Werker, 1997).
-
-Sloutsky and Napolitano (2003) reported a dominance for the auditory modality in children, and showed that this dominance disappears or reverses in adults.
-The authors attribute this dominance to the fact that auditory is more transient, and therefore tend to attract more attention.
-According to this interpretation, children should weight modalities in the same way regerdless of the stimuli used.
-Another interpretation, inspired by our model, would suggest that the precise sound and object contrasts used as stimuli in this series of experiments differ in their relative salience to children.
-One way to disentangle these two interpretations is to use an audio-visual stimuli where the sound contrast is reduced to a perceptual minimum and/or where the visual contrast is enhanced.
-An optimal-based account would suggest that the weighting would reverse in this case.
-
-it  may allow us to account for some findings in the dedvelopment literature
-
-The main finding of the present work is that when the input is multimodal, behavior is largely predicted by the value of the variance of the auditory category relative to the variance of the visual category.
-
-revisit some  findings in the develomental literature and speculate about possible explanations.
-We will focus on two influencial findings, one is the development of a phenomeon dubbed Auditory Overshadowing (Napolitano, Robertson, ...), and the other is the development of the ability to learn similar sounding words (Stager & Werker, 1997).
-
-we can still use its general idea (especially the fact that cues from a given modality are used according to their relative reliability) to revisit some findings in the literature and specualate about new interpretations.
-For instance, Sloutsky and Napolitano (2003) reported a peceptual dominance for the auditory modality in children, and showed that this dominance disappears or reverses in adults.
-The authors attribute this dominance to the fact that auditory is more transient, and therefore tend to attract more attention (I should elaborate more on this).
-According to this interpretation, children should weight modalities in the same way regerdless of the stimuli used.
-Another interpretation, inspired by our model, would suggest that the precise sound and object contrasts used as stimuli in this series of experiments differ in their relative salience to children.
-One way to disentangle these two interpretations is to use an audio-visual stimuli where the sound contrast is reduced to a perceptual minimum and/or where the visual contrast is enhanced.
-An optimal-based account would suggest that the weighting would reverse in this case.
-
-In a different line of work, it has been shown that infants have difficulties mapping two minimally different words to two novel objects, despite the fact that they can perceptually differentiate these words (e.g., Stager & Werker, 1997).
-This pattern of results has mostly been undertood as ‘failure’ in learning.
-Another interpretation  would explain this pattern of results based on developmental changes in the variance associated with the visual and phonological categories.
-If the categories get refined over time (that is, if the variances become smaller), then contrasts that used to fall under one category, may later fall under two separate categories.
-That is, rather than interpreting the null result as a failure in learning, these children might just have learned one word category instead of two categories.
-In particular, it is possible that the visual stimuli used in Stage and Werker (1997) were quite similar in the 14 m.o's early conceptual space, which made them believe that both objects were possible instances of the same semantic category.
-This, in turn, would make them interpret the sound difference as alternative pronunciations of the same word\footnote{The reverse reasining is plausible as well, and in fact, can explain why in the same experiment, the use of acoustically distant words ("lif"/"neem"" instead of "bin"/"din) made 14 m.o succeed in the same task}.
-A prediction of the optimal model would be that the use of semantically distant objects can induce success with the same similar sounding words.
-
-CONCLUSION
-
-To estimate the reliability (e.g., whether a token belong to one or the other category), one has to have access to the full probability distribution of the tokens,  For instance, @sloutsky2003 reported a dominance for the auditory modality in children, and This dominance disappears or reverses in adults
-
-n account helps us better understand the mechanisms of word processing and learning.
-
-We are working on extending this general framework to the case where neither the phonological, not the semantic categories are assumed to be present.
-Thus quantifying the synergy that might take place in development
-
-Can we understand word learning (and failure in learning as in Stager and Werker, 1997) in terms of developmental changes in the reliability (or the relative reliability) in the visual and auditory modalities?
-
-Computational principle behind bla bla
-
-What influence the combination is both the category dstribution (example), and also how rliabile at all (regarless of whether the token in)
-Here talk about theories of modality approp
-riateness theory. 
-Say that this is not what is going on here
-
-Talk about development
-In Experiment 1, the unceratinty was
-
- One possible explanation for this preference could be that people do not combine cross-modal uncertainties of a similar kind (e.g., ambiguity in both modalities) in the same way they would combine uncertainties of different kinds (e.g., ambiguity in one modality and noise in the other).
-For instance, it could be that the latter, but not the former, cause the over-reliance on a particular modality.
-
-There were, however, quantitative differences.
-Audio-visual presentation increased the level of randomness in the participants' responses.
-One possible explanation is that this phenomenon was caused by the arbitrary nature of the form-meaning mapping.
-Previous studies suggest that while redundant multimodal information improves performance (e.g., determining the frequency of a bouncing ball from visual and auditory cues), arbitrary mappings generally tends to hinder performance [for review, see @robinson2010].
-
-Interestingly, however, in Experiment 1 this increase in randomness occurred at a similar rate for both the auditory and the visual modality, and thus, it did not affect their relative weighting.
-The latter was primarily determined by informational reliability.
-Only when we intervened by adding  noise to one modality in Experiment 2, did participants show a systematic preference for the non-noisy modality.
-One possible explanation for this preference could be that people do not combine cross-modal uncertainties of a similar kind (e.g., ambiguity in both modalities) in the same way they would combine uncertainties of different kinds (e.g., ambiguity in one modality and noise in the other).
-For instance, it could be that the latter, but not the former, cause the over-reliance on a particular modality.
-
-Overall, in both Experiments, the majority of the variance could be explained by an ideal observer that combined multimodal information optimally.
-In the light of this main result, we can revisit some previous findings in the literature.
-For instance, @sloutsky2003 reported a dominance for the auditory modality in children.
-This dominance disappears or reverses in adults.
-Could this difference be driven by changes across development in the level of perceptual noise affecting the intrinsic relative reliability of modalities (by analogy to Experiment 2)?
-More work is needed to carefully examine this (and other) speculations, and more generally, to determine the extent to which the optimal combination account helps us better understand the mechanisms of word processing and learning.
-
--->
+$$\beta_v=\frac{\mu_{V1}-\mu_{V2}}{\sigma^2_{V}}.$$
 

### 2018-04-13 Writeup/ms.tex
changes on ms

@@
-\documentclass[english,man]{apa6}
+\documentclass[english,floatsintext,man]{apa6}
 
@@
   {\end{ThreePartTable}\end{center}\end{landscape}}
-
-  \usepackage{ifthen} % Only add declarations when endfloat package is loaded
-  \ifthenelse{\equal{\string man}{\string man}}{%
-   \DeclareDelayedFloatFlavor{ThreePartTable}{table} % Make endfloat play with longtable
-   % \DeclareDelayedFloatFlavor{ltable}{table} % Make endfloat play with lscape
-   \DeclareDelayedFloatFlavor{lltable}{table} % Make endfloat play with lscape & longtable
-  }{}%
 
@@
 
-How does the mind deal with uncertainty to identify the speaker's
-intended word? To address this question, many researchers in recent
-years have adopted the rational approach to cognition (Anderson, 1990),
-which corresponds to Marr's computational level of analysis. This
-approach has had a tremendous impact not only on speech related research
-(Clayards, Tanenhaus, Aslin, \& Jacobs, 2008; Feldman, Griffiths, \&
-Morgan, 2009; Kleinschmidt \& Jaeger, 2015; Norris \& McQueen, 2008),
-but also on many other disciplines in the cognitive sciences (for
-reviews, see Chater \& Manning, 2006; Knill \& Pouget, 2004; Tenenbaum,
-Kemp, Griffiths, \& Goodman, 2011). Within this framework, researchers
-typically consider an \enquote{ideal observer} model which provides a
-characterization of the task/goal and shows what the optimal performance
-should be under this characterization. When there is uncertainty in the
-input, the ideal observer performs an optimal probabilistic inference.
-For example, in order to recognize an ambiguous linguistic input, the
-model uses all available probabilistic knowledge in order to maximize
-the accuracy of this recognition. Thus, when the task is well specified,
-the ideal observer model can be seen as a theoretical upper limit on
-performance. It is often used, not so much as a realistic model of human
+How does the listener deal with uncertainty to identify the speaker's
+intended word? One rigorous way to approach this question is through
+conducting an \emph{ideal observer} analysis. This research strategy
+provides a characterization of the task/goal and shows what the optimal
+performance should be under this characterization.\footnote{It is, thus,
+  a general instance of the rational approach to cognition (Anderson,
+  1990). It can also be seens as an instance Marr's computational level
+  of analysis.} When there is uncertainty in the input, the ideal
+observer performs an optimal probabilistic inference. For example, in
+order to recognize an ambiguous linguistic input, the model uses all
+available probabilistic knowledge in order to maximize the accuracy of
+this recognition. When the task is well specified, the ideal observer
+model can be seen as a theoretical upper limit on performance. Thus, it
+is supposed to be used, not so much as a realistic model of human
 performance, as much as a baseline against which human performance can
-be compared (Geisler, 2003). When there is a deviation from the ideal,
-this can reveal extra constraints on human cognition, such as
-limitations on working memory or attentional resources.
-
-In this line of research, Clayards et al. (2008) simulated auditory
-uncertainty by manipulating the probability distribution of a cue (VOT)
-that differentiated similar words (e.g., \enquote{beach} and
-\enquote{peach}). They found that humans were sensitive to these
-probabilistic cues and their judgments closely reflected the optimal
-predictions. In another work, Feldman et al. (2009) studied the
-perceptual magnet effect, which is related to how categories influence
-the way the stimuli are perceived. They showed that this effect can be
-explained as the consequence of optimally solving the problem of
-perception under uncertainty. Both studies explored optimal performance
-under uncertainty from one modality, i.e., the auditory modality. There
-is however extensive evidence that information from the visual modality,
-in particular the speaker's facial features, influences the perception
-of auditory information (see Campbell, 2008 for a review). Bejjanki,
-Clayards, Knill, and Aslin (2011) offered a mathematical
-characterization of how cues from speech and lip movements can be
-optimally combined and showed that human performance during audio-visual
+be compared (Geisler, 2003; Rahnev \& Denison, 2018). When there is a
+deviation from the ideal, it can reveal extra constraints on human
+cognition, such as limitations on the working memory or attentional
+resources.
+
+The ideal observer analysis has had a tremendous impact not only on
+speech related research (Clayards, Tanenhaus, Aslin, \& Jacobs, 2008;
+Feldman, Griffiths, \& Morgan, 2009; Kleinschmidt \& Jaeger, 2015;
+Norris \& McQueen, 2008), but also on many other disciplines in the
+cognitive sciences (for reviews, see Chater \& Manning, 2006; Knill \&
+Pouget, 2004; Tenenbaum, Kemp, Griffiths, \& Goodman, 2011). In
+particular, using this research strategy, Clayards et al. (2008)
+simulated auditory uncertainty by manipulating the probability
+distribution of a cue (VOT) that differentiated similar words (e.g.,
+\enquote{beach} and \enquote{peach}). They found that humans were
+sensitive to these probabilistic cues and their judgments closely
+reflected the optimal predictions. In another work, Feldman et al.
+(2009) studied the perceptual magnet effect, which is a phenomenon that
+involves reduced discriminability near prototypical sounds in the native
+language (Kuhl, 1991). They showed that this effect can be explained as
+the consequence of optimally solving the problem of perception under
+uncertainty. Both Clayards et al. (2008) and Feldman et al. (2009)
+explored optimal performance under uncertainty in the auditory modality.
+There is, however, extensive evidence that information from the visual
+modality, such as the speaker's facial features, also influences speech
+understanding (see Campbell, 2008 for a review). Bejjanki, Clayards,
+Knill, and Aslin (2011) offered a mathematical characterization of how
+probabilistic cues from speech and lip movements can be optimally
+combined. They showed that human performance during audio-visual
 phonemic labeling was consistent (at least at the qualitative level)
@@
 
-The speaker's facial features are not the only visual information that
-can be used to disambiguate the auditory input, however. For instance,
-in a referential context, information about the identity of the semantic
-referent can be integrated with linguistic information to resolve
-lexical and syntactic ambiguities in speech (e.g., Eberhard,
+This previous research, however, did not systematically study speech
+understanding when the visual information is obtained, not through the
+speaker's facial features, but through the referential context. In fact,
+experimental findings showed that information about the identity of the
+semantic referent can be integrated with linguistic information to
+resolve lexical and syntactic ambiguities in speech (e.g., Eberhard,
 Spivey-Knowlton, Sedivy, \& Tanenhaus, 1995; Spivey, Tanenhaus,
@@
 observer analysis of word identification in such context, that is, when
-the mind has to combine cues from the sound and the referent. Imagine,
-for example, that someone is uncertain whether they heard \enquote{pea}
-or \enquote{bee}, does this uncertainty make them rely more on the
-referent (e.g., the object being pointed at)? Vice versa, if they are
-not sure if they saw a bee or a fly, does it make them rely more on the
-sound? More importantly, when input in both modalities is uncertain to
-varying degrees, do they weight each modality according to its relative
-reliability (which is the optimal strategy), or do they over-rely on a
-particular modality (which is a sub-optimal strategy)?
-
-The visual information provided by the referent is arguably different
-from the visual information provided by the speaker's facial features
-(such as lip movements). There seems to be at least two fundamental
-differences between these two cases, and both can influence the cue
-combination strategy:
-
-First, in the case of audio-visual speech, modalities are understood to
-differ only in terms of their reliability. In a referential context,
-however, modalities also differ in terms of their roles in the
-referential process: the auditory input represents the symbol (i.e., the
-word) whereas the visual input represents the referent. It has been
+the listener has to combine cues from the sound and the referent.
+Imagine, for example, that someone is uncertain whether they heard
+\enquote{pea} or \enquote{bee}, does this uncertainty make them rely
+more on the referent (e.g., the object being pointed at)? Vice versa, if
+they are not sure if they saw a bee or a fly, does it make them rely
+more on the sound? More importantly, when input in both modalities is
+uncertain to varying degrees, do they weight each modality according to
+its relative reliability (which is the optimal strategy), or do they
+over-rely on a particular modality (which is a sub-optimal strategy)?
+
+On the face of it, the question of combining information from the sound
+and the visual referent might seem similar to that of audio-visual
+speech integration. Nevertheless, there are at least two fundamental
+differences between these two cases, and both can influence the way the
+auditory and visual cues are integrated:
+
+\noindent First, in the case of audio-visual speech, both modalities
+offer information about the same underlying speech category. They may
+differ only in terms of their informational reliability. In a
+referential context, however, the auditory and visual modalities are
+additionally different in terms of the roles they play in the
+referential process: the auditory input represents the \emph{symbol}
+whereas the visual input represents the \emph{meaning}. It has been
 suggested that because of its referential property, speech is a
 privileged signal for humans, starting in infancy (see Vouloumanos \&
-Waxman, 2014 for a
-review).\footnote{There is a debate over whether speech is privileged for infant and adults for the same reasons.
-Whereas Waxman and colleagues suggest that speech is privileged for both infants and adults because of its ability to refer, Sloutsky and colleagues suggest that speech might not have a referential status from the start.
-Rather, according to Sloutsky and colleagues, speech seems to be prefered by infants only because of a low level auditory "overshadowing".}
-Thus, in a referential context, it is possible that we do not treat the
-auditory and visual modalities as equivalent sources of information.
-Instead, there could be a bias for the auditory modality beyond what is
-expected from informational reliability alone.
-
-Second, in the case of audio-visual speech, the associations are
-expected to be perceptually correlated. The expectation for this
-correlation is such that when there is a mismatch between auditory and
-visual input, people still integrate them into a unified (but illusory)
-percept (McGurk \& MacDonald, 1976). In the case of referential
-language, however, the multimodal association is by nature
-\emph{arbitrary} (Greenberg, 1957; Saussure, 1916). For instance, there
-is no logical/perceptual connection between the sound \enquote{bee} and
-the corresponding insect. Moreover, variation in the way the sound
-\enquote{bee} is pronounced is generally not expected to correlate
-perceptually with variation in the shape (or any other visual property)
-in the category of bees. Thus, one could imagine that cue combination in
-the case of arbitrary audio-visual associations (word-referent) is less
-automatic, more effortful, and therefore less conducive to optimal
+Waxman, 2014 for a review).\footnote{There is a debate as to whether
+  speech is privileged for infant and adults for the same reasons.
+  Whereas some researchers suggest that speech is privileged for both
+  infants and adults because of its ability to refer (e.g., Waxman \&
+  Markow, 1995), others suggest that speech might \emph{not} have a
+  referential status from the start. Rather, speech might be prefered by
+  infants only because of a low level auditory ``overshadowing'' (e.g.,
+  Sloutsky \& Napolitano, 2003).} Thus, in a referential context, it is
+possible that listeners do not treat the auditory and visual modalities
+as equivalent sources of information. Instead, there could be a
+sub-optimal bias for the auditory modality beyond what is expected from
+informational reliability alone.
+
+\noindent Second in the case of audio-visual speech, the auditory and
+visual stimuli are expected to be perceptually correlated. The
+expectation for this correlation is such that when there is a mismatch
+between the auditory and visual input, people still integrate them into
+a unified (but illusory) percept (McGurk \& MacDonald, 1976). In the
+case of referential language, however, the multimodal association is by
+nature \emph{arbitrary} (Greenberg, 1957; Saussure, 1916). For instance,
+there is no logical/perceptual connection between the sound
+\enquote{bee} and the corresponding insect. Moreover, variation in the
+way the sound \enquote{bee} is pronounced is generally not expected to
+correlate perceptually with variation in the shape (or any other visual
+property) in the category of bees. In sum, cue combination in the case
+of arbitrary audio-visual associations (word-referent) is likely to be
+less automatic, more effortful, and therefore less conducive to optimal
 integration than it is in the case of perceptually correlated
@@
 sub-optimality, we compare the optimal model (which provides a normative
-benchmark) to a descriptive model which is identical to the optimal
-model, except that the parameters in the former are fitted to human
-responses.
+benchmark) to a descriptive model (which is fit to human responses).
+Comparing parameter estimates between these two formulations allows us
+to quantify the degree of deviation from optimality.
 
@@
 
-\section{Models and predictions}\label{models-and-predictions}
-
-In this section we describe the multimodal cue combination model. First,
-we briefly introduce the experimental paradigm, and second we explain
-how behavior in this paradigm can be characterized optimally with an
-ideal observer model.
+\section{Paradigm and Models}\label{paradigm-and-models}
+
+In this section we, first, briefly introduce the multimodal combination
+task. Then we explain how behavior in this paradigm can be characterized
+optimally with an ideal observer model.
 
@@
 both the auditory and the visual components. After these two
-presentations, participants press \enquote{same} or \enquote{different}.
+presentations, participants press \enquote{same} or \enquote{different.}
 
@@
 
-This task is similar to the task introduced by Sloutsky and Napolitano
-(2003), and used in subsequent studies in both children and adults (see
-Robinson \& Sloutsky, 2010 for a review). However, in this original
-task, participants are asked whether or not the two audio-visual
-presentations are \emph{identical}. Such task would allow us to probe
-audio-visual encoding, but not necessarily language understanding. The
-latter requires---in addition to the perceptual encoding---a categorical
-judgement, i.e, determining whether or not two similar tokens are
-members of the same phonological/semantic category. Thus, our task is
+This paradigm is adapted from a previous task (Sloutsky \& Napolitano,
+2003), which has been used with both children and adults to probe
+audio-visual encoding (see Robinson \& Sloutsky, 2010 for a review). In
+the testing phase of the original task, participants are asked whether
+or not the two audio-visual presentations are \emph{identical}. In the
+current study, we are interested, rather, in the categorization, i.e.,
+determining whether or not two similar tokens are members of the same
+phonological/semantic category. Therefore, testing in our task is
 category-based: Participants are asked to press \enquote{same} if they
-think the second item (the test) belonged to the same category as the
+think the second item (the test) belongs to the same category as the
 first (target) (e.g., dog-/aba/), even if there is a slight difference
@@
 \enquote{different} only if they think that the second stimulus was an
-instance of the other word category (cat-/ada/). The task also includes
+instance of the other category (cat-/ada/). The task also includes
 trials where pictures are hidden (audio-only) or where sounds are muted
@@
 evaluation of the probabilistic information present in the auditory and
-visual categories. This unimodal distributions are used as inputs to the
-optimal combination model, described below.
+visual categories. As we shall see, these unimodal distributions are
+used as inputs to the optimal cue combination model.
 
@@
 
-The ideal observer model combines probabilistic information from the
-auditory and visual modalities, and makes a categorical decision. How
-can this task be characterized in a formal way, and what would be the
-optimal behavior? If the stimuli were continuous (e.g., size, location),
-cues derived from each modality would be characterized with their
-sensory noise variance only, and (assuming conditional independence)
-their combined information would be characterized with a simple linear
-combination rule where the combined estimate is an average of the
-individual estimates, each weighted according to its relative
-reliability (Alais \& Burr, 2004; Ernst \& Banks, 2002). However, in our
-case decision is made over categorical variables (phonemes and
-concepts), the optimal model should take into account, not only the
-noise variability around an individual perceptual estimate, but also its
-categorical variability (i.e., the probability with which the estimate
-belongs to a given category).
-
-One way to account for the categorical variability is to model the
-decision step which maps sensory input onto task-dependent categories
-(Bankieris, Bejjanki, \& Aslin, 2017; Bejjanki et al., 2011). We
-represent the decision step as follows (see Figure~\ref{fig:model} for
-illustration). If we assume that both the visual and the auditory cues
-vary along a single dimension, an audio-visual signal \((a,v)\) can be
-represented as a point in this two-dimensional space, and a word
-category can be characterized with a bivariate probability distribution
-over audio-visual
-tokens.\footnote{For the sake of clarity, we assume here that the sensory noise around this point is small/negligible compared to the categorical variability.
-But see below how the noise can be integrated when its effect is relatively large}
-Each category is peaked around the most typical audio-visual token, and
-the probability of membership in the category (the likelihood
-probability) decreases gradually as the auditory token deviates from the
-typical sound instance (depending on the variance of the auditory
-category) and/or as the visual token deviates from the typical visual
-instance (depending on the variance of the visual category).
-
-A crucial feature of the ideal observer model is that it makes use of
-the entire probability distribution of a given category in order to make
-optimal decisions (e.g., Clayards et al., 2008). This means that the
-probability of picking a word (the posterior probability) should mirror
-closely the probability of the combined information (the likelihood
-probability). For instance, the model becomes less ambiguous and more
-certain as the tokens get closer to the typical instance of the
-category. In what follows, we formalize this sense of optimality using a
-Bayesian framework.
-
-An auditory category \(A\) and a visual category \(V\) are defined as
-distributions in the auditory and the visual dimensions, respectively. A
-word category \(W\) is defined as a bivariate distribution in the
-audio-visual. More specifically, we define it as the joint distribution
-of the auditory and the visual categories. For simplicity, we assume
-both auditory and visual categories to be normally distributed. That is,
-if \(w=(a,v)\) is an audio-visual token, then:
+We construct an ideal observer model that combines probabilistic
+information from the auditory and visual modalities. In contrast to the
+model used in most research on multisensory integration (e.g., Ernst \&
+Banks, 2002)---which typically studies continuous stimuli (e.g., size,
+location)---this probabilistic information cannot be characterized with
+\emph{sensory noise/variability}, only. Indeed, our task involves
+responses over categorical variables (phonemes and concepts), and
+therefore, the optimal model in our case should take into account, not
+only the noise variability around an individual perceptual estimate, but
+also its \emph{within category variability}, i.e., the uncertainty
+related to whether this perceptual estimate belongs to a given category
+(see also Bankieris, Bejjanki, \& Aslin, 2017; Bejjanki et al., 2011).
+In what follows, we describe a model that accounts for both type of
+variability. First, we describe the model in the simplified case of
+categorical variability only. Second, we augment this simplified model
+to account for sensory noise.
+
+\subsubsection{Categorical variability}\label{categorical-variability}
+
+We assume that both the auditory categories (i.e., /aba/ and /ada/) and
+the visual categories (cat and dog) are distributed along a single
+acoustic and semantic dimension, respectively (Figure~\ref{fig:model}).
+Moreover, we assume that all categories are normally distributed.
+Formally speaking, if \(A\) denotes an auditory category (/ada/ or
+/aba/), then the probability that a point \(a\) along the acoustic
+dimension belongs to the category \(A\) is
 \[ p(a | A) \sim  N(\mu_A, \sigma^2_A) \] where \(\mu_A\) and
 \(\sigma^2_A\) are respectively the mean and the variance of the
-auditory category, \[ p(v | V) \sim  N(\mu_V, \sigma^2_V) \] where
-\(\mu_V\) and \(\sigma^2_V\) are the mean and the variance of the visual
-category, and
-
-\[ p(w | W) \sim  N(M_W, \Sigma_W) \] where \(M_W=(\mu_A, \mu_V)\) and
-\(\Sigma_W\) are mean and the covariance matrix of the word category. We
-assume that auditory and visual variables are independent (i.e.,
-uncorrelated), so the covariance matrix is simply: \[
+auditory category. Similarly, the probability that a point \(v\) along
+the visual dimension belongs to the category \(V\) is
+\[ p(v | V) \sim  N(\mu_V, \sigma^2_V) \] where \(\mu_V\) and
+\(\sigma^2_V\) are the mean and the variance of the visual category. An
+audio-visual signal \(w=(a,v)\) can be represented as a point in the
+audio-visual space. These audio-visual tokens define bivariate
+distributions in the bi-dimentional space. We call these bivariate
+distributions \emph{Word categories}, noted \(W\), and are distributed
+as follows: \[ p(w | W) \sim  N(M_W, \Sigma_W) \] where
+\(M_W=(\mu_A, \mu_V)\) and \(\Sigma_W\) are the mean and the covariance
+matrix of the word category. The main assumption of the model is that
+the auditory and visual variables are independent (i.e., uncorrelated),
+so the covariance matrix is simply: \[
    \Sigma_W=
@@
 
-\begin{figure}
-
-{\centering \includegraphics[width=400px]{pictures/model}
-
-}
-
-\caption{Illustration of the model using simulated data.
+\begin{figure}[!h]
+\includegraphics[width=\textwidth]{pictures/model} \caption{Illustration of the model using simulated data.
 A word category is defined as the joint bivariate distribution of an auditory category (horizontal, bottom panel) and a visual semantic category (vertical, left panel).
@@
 
-This assumption simply says that, given a word-object mapping, e.g.,
-W=(\enquote{cat}-CAT), variation in the way \enquote{cat} is pronounced
-does not correlate with changes in any visual property of the object
-CAT, which is a valid
+\noindent This assumption simply says that, given a word-object mapping,
+e.g., \(W=\)(\enquote{cat}-CAT), variation in the way \enquote{cat} is
+pronounced does not correlate with changes in any visual property of the
+object CAT, which is a valid
 assumption.\footnote{Note that this assumptions is more adequate in the case of arbitrary associations such as ours, and less so in the case of redundant association such as audio-visual speech.
@@
 
-Now we turn to the crucial question of modeling how optimal decision
-should proceed based on the probabilistic information in the auditory
-and the visual modalities. In our task, we have two word categories:
-dog-/aba/ (\(W_1\)) and cat-/ada/
-(\(W_2\)).\footnote{This mapping is randomized in the experiments.}
-Participants can be understood as choosing one of these two word
-categories (Figure~\ref{fig:model}). For an ideal observer, the
-probability of choosing category 2 when presented with an audio-visual
-instance \(w=(a,v)\) is the posterior probability of this category: \[
+Now we turn to the crucial question of modeling how the optimal decision
+should proceed given the probabilistic (categorical) information in the
+auditory and the visual modalities, as characterized above. We have two
+word categories: dog-/aba/ (\(W_1\)) and cat-/ada/
+(\(W_2\)).\footnote{This mapping is randomized in the experiments.} When
+making decisions, participants can be understood as choosing one of
+these two word categories (Figure~\ref{fig:model}). For an ideal
+observer, the probability of choosing category 2 when presented with an
+audio-visual instance \(w=(a,v)\) is the posterior probability of this
+category: \[
 p(W_2 | w)=\frac{p(w|W_2)p(W_2)}{p(w|W_2)p(W_2)+p(w|W_1)p(W_1)}
-\] Using our assumption that the cues are uncorrelated, we have
+\] Using our assumption that the cues are uncorrelated, we have:
 \[p(w | W) = p(a,v| W) = p(a| A)p(v| V)\] Under this assumption, the
-posterior probability reduces
-to:\footnote{See the appendix for the details of the derivation}
+posterior probability reduces to the following formula (see Appendix 1
+for the details of the derivation):
 
 \begin{equation}
- p(W_2 | w)=\frac{1}{1+(1+\epsilon)\exp(\beta_0+\beta_aa+\beta_vv)}
+ p(W_2 | w)=\frac{1}{1+(1+b)\exp(\beta_0+\beta_aa+\beta_vv)}
 \end{equation}
 
-where \[1+\epsilon=\frac{p(W_1)}{p(W_2)}\]
+where \[1+b=\frac{p(W_1)}{p(W_2)}\]
 \[\beta_0=\frac{\mu^2_{A2}-\mu^2_{A1}}{2\sigma^2_{A}}+\frac{\mu^2_{V2}-\mu^2_{V1}}{2\sigma^2_{V}}\]
@@
 \[\beta_a=\frac{\mu_{A1}-\mu_{A2}}{\sigma^2_{A}}\]
-\[\beta_v=\frac{\mu_{V1}-\mu_{V2}}{\sigma^2_{V}}\]
-
-The parameter \(\epsilon\) represents the differential between the
-categories' prior probabilities. However, since the identity of word
-categories is randomized across participants, \(\epsilon\) measures,
-rather, a response bias to \enquote{same} if \(\epsilon > 0\), and a
-response bias to \enquote{different} if \(\epsilon < 0\). We expect a
-general bias towards answering \enquote{different} because of the
-categorical nature of our same-different task: When two items are
-ambiguous but perceptually different, participants might have a slight
-preference for \enquote{different} over \enquote{same}.
-
-The values of the means are fixed: They correspond to the value of the
-most typical tokens in our stimuli. Thus, observations from each
-modality (\(a\) and \(v\)) are weighted according to their reliability
-in the posterior: \[\beta_a \propto \frac{1}{\sigma^2_{A}}\]
-\[\beta_v \propto \frac{1}{\sigma^2_{V}}\].
-
-Note that the weights account for categorical variability only. For
-instance, if the speaker generates a target production \(a_t\) from an
-auditory category \(p(a_t | A) \sim N(\mu_{A}, \sigma^2_{A})\), the
-ideal model assumes that it has direct access to this production token
-(i.e., \(a=a_t\)), and that all uncertainty is about the category
-membership of this token. However, we might also want to account for
-noise in the brain and/or in the environment. For example, the observer
-might not have access to the exact produced target, but only to the
-target perturbed by noise. If we assume this noise to be normally
-distributed, that is, \(p(a | a_t) \sim N(a_t, \sigma^2_{N})\), then
-integrating over \(a_t\) lead to the following simple expression:
-\[ p(a | A) \sim N(\mu_{A}, \sigma^2_{A}+\sigma^2_{N})\] Using an
-identical reasoning for the case of the visual modality, we end up with
-the following multimodal weighting scheme in the optimal combination
-model:
+\[\beta_v=\frac{\mu_{V1}-\mu_{V2}}{\sigma^2_{V}}.\]
+
+The parameter \(b\) represents the differential between the categories'
+prior probabilities. However, since the identity of word categories is
+randomized across participants, \(b\) measures, rather, a response bias
+to \enquote{same} if \(b > 0\), and a response bias to
+\enquote{different} if \(b < 0\). We expect a general bias towards
+answering \enquote{different} because of the categorical nature of our
+same-different task: When two items are ambiguous but perceptually
+different, participants might have a slight preference for
+\enquote{different} over \enquote{same}. As for the means, their values
+are fixed, and they correspond to the most typical tokens in our
+stimuli. Finally, observations from each modality (\(a\) and \(v\)) are
+weighted in Equation 1 according to their reliability:
+\[\beta_a \propto \frac{1}{\sigma^2_{A}}\]
+\[\beta_v \propto \frac{1}{\sigma^2_{V}}.\]
+
+\subsubsection{Sensory variability}\label{sensory-variability}
+
+So far, we only accounted for categorical variability. For instance, if
+the speaker generates a target production \(a_t\) from an auditory
+category \(p(a_t | A) \sim N(\mu_{A}, \sigma^2_{A})\), the ideal model
+assumes that it has direct access to this production token (i.e.,
+\(a=a_t\)), and that all uncertainty is about the category membership of
+this token. However, we might also want to account for noise in the
+brain and/or in the environment. For example, the observer might not
+have access to the exact produced target, but only to the target
+perturbed by noise. If we assume this noise to be normally distributed,
+that is, \(p(a | a_t) \sim N(a_t, \sigma^2_{N_A})\), then integrating
+over \(a_t\) leads to the following simple expression:
+\[ p(a | A) \sim N(\mu_{A}, \sigma^2_{A}+\sigma^2_{N_A})\] Similarly, in
+the case of sensory noise in the visual modality, we get
+\[ p(a | V) \sim N(\mu_{V}, \sigma^2_{V}+\sigma^2_{N_V})\] Finally,
+using exactly the same derivation as above, we end up with the following
+multimodal weighting scheme in the optimal combination model (Equation
+1) which takes into account both categorical and sensory variability:
 
 \[\beta_a \propto \frac{1}{\sigma^2_{A}+\sigma^2_{N_A}}\]
-\[\beta_v \propto \frac{1}{\sigma^2_{V} +\sigma^2_{N_V}}\] To summarize,
-the posterior provides the optimal model's predictions for how
-probabilities that characterize uncertainty in each modality can be
-combined to make categorical decision about the bimodal input. The model
-will be constructed based on data from the unimodal trials, but the
-predictions of the optimal model will be compared to human responses in
-the bimodal trials.
-
-\subsection{Auditory and Visual
-models}\label{auditory-and-visual-models}
-
-Besides the optimal model, we also test the predictions of two baselines
-models: a visual model, which assumes that participants rely only on
-visual information, and an auditory model, which assumes that
-participants rely only on auditory information. If participants rely on
-both the auditory and the visual modalities, the optimal model would
-explain more variance in human responses than the visual model alone or
-the auditory model alone.
-
-\subsection{Descriptive model}\label{descriptive-model}
-
-The visual, auditory, and optimal models are \emph{normative} models.
-Their predictions are made about human data in the bimodal condition,
-but their crucial parameters (i.e., variances associated with the visual
-and auditory modalities) are derived from data in the unimodal
-conditions. In addition to these normative models, we consider a
-\emph{descriptive} model. The parameters of this model are fit to human
-data in the bimodal condition. If the referential task induces
-sub-optimality (due, for instance, to the arbitrary nature of the
-sound-object association), then we predict that the descriptive model
-should explain more variance than the optimal model does.
-
-A systematic comparison of the optimal and the descriptive models would
-allow us, not only to quantify how much people deviate from optimality,
-but also to understand precisely how they deviate from this optimality.
-Let \(\sigma^2_{A}\) and \(\sigma^2_{V}\) be the values of the variances
-used in the optimal model (derived from the unimodal conditions), and
-\(\sigma^2_{Ab}\) and \(\sigma^2_{Vb}\) be the values observed through
-the descriptive model in the bimodal condition. Deviation from
-optimality is measured in two ways. First, we measure the change in the
-values of the variances specific to each modality, that is, how
-\(\sigma^2_{A}\) compares to \(\sigma^2_{Ab}\), and how \(\sigma^2_{V}\)
-compares to \(\sigma^2_{Vb}\). Second, we measure changes in the
-proportion of the visual and auditory variances, i.e., how
+\[\beta_v \propto \frac{1}{\sigma^2_{V} +\sigma^2_{N_V}}.\]
+
+\subsubsection{Optimal cue combination}\label{optimal-cue-combination}
+
+Equation 1 provides the optimal model's predictions for how
+probabilities that characterize uncertainty in the auditory and the
+visual modalities can be combined to make categorical decisions.
+Parameters' estimates of the probability distributions in each modality
+are derived by fitting unimodal posteriors to the participants'
+responses in the unimodal conditions, i.e., the condition where only the
+sounds are heard or only the pictures are seen
+(Figure~\ref{fig:task}).\footnote{Further technical detail about model fitting in the unimodal conditions will be given in the method section of Experiment 1}
+Using these derived parameters, the optimal model makes predictions
+about responses in the bimodal condition where participants both hear
+the sounds and see the pictures.
+
+\subsubsection{Auditory and Visual
+baselines}\label{auditory-and-visual-baselines}
+
+The predictions of the optimal model will be compared to two baselines.
+The first baseline is a visual model which assumes that participants
+rely only on visual information, and an auditory model, which assumes
+that participants rely only on auditory information. More precisely,
+these baseline models assumes that the participants' responses in the
+bimodal condition will not be different from their response in either
+the visual-only or the auditory-only condition. If, as we expect, the
+participants rely on both the auditory and the visual modalities to make
+decision in the bimodal condition, the optimal model would explain more
+variance in human responses than the visual or the auditory model do.
+
+\subsection{Descriptive model and analysis of
+sub-optimality}\label{descriptive-model-and-analysis-of-sub-optimality}
+
+The optimal model (as well as the auditory and visual baselines) are
+\emph{normative} models. Their predictions are made about human data in
+the bimodal condition, but their crucial parameters (i.e., variances
+associated with the visual and auditory modalities) are derived from
+data in the unimodal conditions. In addition to these normative models,
+we consider a \emph{descriptive} model. The parameters of this model are
+fit to actual responses in the bimodal condition. If the referential
+task induces sub-optimality (due, for instance, to the arbitrary nature
+of the sound-object association), then the descriptive model should
+explain more variance than the optimal model does.
+
+Comparison of the optimal and the descriptive models allows us, not only
+to quantify how much people deviate from optimality, but also to
+understand precisely the nature of this deviation. Let \(\sigma^2_{A}\)
+and \(\sigma^2_{V}\) be the values of the variances used in the optimal
+model (derived from the unimodal conditions), and \(\sigma^2_{Ab}\) and
+\(\sigma^2_{Vb}\) be the values observed through the descriptive model
+in the bimodal condition. Deviation from optimality is measured in two
+ways. First, we measure the change in the values of the variance
+specific to each modality, that is, how \(\sigma^2_{A}\) compares to
+\(\sigma^2_{Ab}\), and how \(\sigma^2_{V}\) compares to
+\(\sigma^2_{Vb}\). Second, we measure changes in the proportion of the
+visual and auditory variances, i.e., we examine how
 \(\frac{\sigma^2_{A}}{\sigma^2_{V}}\) compares to
 \(\frac{\sigma^2_{Ab}}{\sigma^2_{Vb}}\). The first measure allows us to
-test if precision changes for each modality when we move from the
-unimodal to the bimodal conditions. The second allows us to test whether
-or not the weighting scheme follows the prediction of the optimal model.
-The reason we used the proportion of the variances as a measure of
-cross-modal weighing is because it corresponds to the
-slope\footnote{Or more precisely the absolute value of the slope} of the
-decision threshold in the audio-visual space (Figure~\ref{fig:model}).
-The decision threshold is defined as the set of values in this
-audio-visual space along which the posterior is equal to 0.5. Formally
-speaking, the decision threshold takes the following form:
+test if response precision changes for each modality when we move from
+the unimodal to the bimodal conditions. The second allows us to test the
+extent to which the weighting scheme follows the prediction of the
+optimal model. The reason we used the proportion of the variances as a
+measure of cross-modal weighting is because this proportion corresponds
+to the slope\footnote{Or more precisely the absolute value of the slope}
+of the decision threshold in the audio-visual space
+(Figure~\ref{fig:model}). The decision threshold is defined as the set
+of values in this audio-visual space along which the posterior is equal
+to 0.5. Formally speaking, the decision threshold has the following
+form:
 
@@
 
-It follows that there are three possible scenarios describing how humans
-can deviate from optimality. These scenarios are illustrated in
-Figure~\ref{fig:subOptim} and are as follows:
+There are three possible ways human responses can deviate from
+optimality. These scenarios are illustrated in Figure~\ref{fig:subOptim}
+and are as follows:
 
@@
 
-\begin{figure}
-
-{\centering \includegraphics[width=400px]{pictures/sub-optimal}
-
-}
-
-\caption{Illustration using simulated data showing the example of a prediction made by the optimal model (top), and the three possible ways human participants can deviate from this prediction (bottom).
-These cases are the following: 1) The variance increases equally for both modalities, but the weighting scheme (characterized by the decision threshold) is optimal, 2) The auditory variance increases at a higher rate, leading to a preference for the auditory modality, and 3) The visual variance increases at a higher rate, leading to a preference for the visual modality}\label{fig:subOptim}
+\begin{figure}[!h]
+\includegraphics[width=\textwidth]{pictures/sub-optimal} \caption{Illustration using simulated data showing the example of a prediction made by the optimal model (top), and the three possible ways human participants can deviate from this prediction (bottom).
+These cases are the following: 1) The variance increases equally for both modalities, but the weighting scheme (characterized by the decision threshold) is optimal, 2) The auditory variance increases at a higher rate, leading to a preference for the auditory modality, and 3) The visual variance increases at a higher rate, leading to a preference for the visual modality.}\label{fig:subOptim}
 \end{figure}
 
-We tested the predictions of the optimal model in three experiments. In
+We compared these models to human responses in three experiments. In
 Experiment 1, we studied the case where bimodal uncertainty was due to
@@
 In this Experiment, we start with testing the predictions in the case
-where uncertainty is due to ambiguity in terms of category membership
-only, that is, according to the following weighting scheme:
-\[\beta_a \propto \frac{1}{\sigma^2_{A}}\]
-\[\beta_v \propto \frac{1}{\sigma^2_{V}}\] We do not introduce any
-additional noise in the background, and we assume that sensory noise is
-negligible compared to categorical variability.
+where uncertainty is due to categorical variability only (i.e.,
+ambiguity in terms of category memebership). We do not add any external
+noise to the background and we assume that internal sensory noise is
+negligible compared to categorical variability
+(\(\sigma^2_{A} \gg \sigma^2_{N_A}\), and
+\(\sigma^2_{V} \gg \sigma^2_{N_V}\)). Thus, we use the following cue
+weighting scheme:
+
+\[\beta_a \propto \frac{1}{\sigma^2_{A} + \sigma^2_{N_A}} \approx  \frac{1}{\sigma^2_{A} }\]
+\[\beta_v \propto \frac{1}{\sigma^2_{V} + \sigma^2_{N_V}} \approx  \frac{1}{\sigma^2_{V} }.\]
 
@@
 
-\subsubsection{Participants:}\label{participants}
+\subsubsection{Participants}\label{participants}
 
@@
 (N=14), or if they had less than 50\% accurate responses on the
-unambiguous training trials (N=6). The final sample consisted of (N =
-80)
+unambiguous training trials (N=6). The final sample consisted of N = 80
 participants.\footnote{The sample size and exclusion criteria were specified in the pre-registration at https://osf.io/h7mzp/.}
 
-\subsubsection{Stimuli:}\label{stimuli}
+\subsubsection{Stimuli}\label{stimuli}
 
@@
 well as points 3, 5, and 7 along the continuum. For visual stimuli, we
-used a morph continuum introduced in Freedman, Riesenhuber, Poggio, and
-Miller (2001). From the original 14 points, we selected 5 points as
-follows: we kept the item that seemed most ambiguous (point 8), the 2
-preceding points (i.e., 7 and 6) and the 2 following points (i.e., 9 and
-10). The 6 and 10 points along the morph were quite distinguishable, and
-we took them to be our prototypes.
+used a cat/dog morph continuum introduced in Freedman, Riesenhuber,
+Poggio, and Miller (2001). From the original 14 points, we selected 5
+points as follows: we kept the item that seemed most ambiguous (point
+8), the 2 preceding points (i.e., 7 and 6) and the 2 following points
+(i.e., 9 and 10). The 6 and 10 points along the morph were quite
+distinguishable, and we took them to be our prototypes.
 
@@
 of 70 trials/participant. Trials were blocked by condition and blocks
-were presented in random order.
-
-\begin{figure}
-
-{\centering \includegraphics[width=400px]{ms_files/figure-latex/unimodal-1}
-
-}
-
-\caption{Human responses in the unimodal condition.
-Points represent the proportion of `different' to `same' responses in the auditory-only condition (left), and visual-only condition (right).
-Error bars are 95\% confidence intervals.
-Solid lines represent logistic fits.}\label{fig:unimodal}
-\end{figure}
+were presented in random order. The experiment lasted around 15 minutes.
 
@@
 
-\[p(A_2 | a)=\frac{1}{1+(1+\epsilon_A)\exp(\beta_{a0}+\beta_aa)}\]
+\[p(A_2 | a)=\frac{1}{1+(1+b_A)\exp(\beta_{a0}+\beta_aa)}\]
 
 with \(\beta_a=\frac{\mu_{A_1}-\mu_{A_2}}{\sigma^2_{A}}\) and
-\(\beta_{a0}=\frac{\mu^2_{A_2}-\mu^2_{A_1}}{2\sigma^2_{A}}\).
-\(\epsilon_A\) is the response bias in the auditory-only condition. For
-this model (as well as all other models in this study), we fixed the
-values of the means to be the end-points of the corresponding continuum,
-since these points are the most typical instances in our stimuli. Thus,
-we have \(\mu_{A1}=0\) and \(\mu_{A2}=4\) (and similarly \(\mu_{V1}=0\),
-and \(\mu_{V2}=4\)). This leaves us with two free parameters: the bias
-\(\epsilon_A\) and the variance \(\sigma^2_{A}\). To determine the
-values of these parameters, we fit the unimodal posterior to human data
-in the unimodal case.
+\(\beta_{a0}=\frac{\mu^2_{A_2}-\mu^2_{A_1}}{2\sigma^2_{A}}\). \(b_A\) is
+the response bias in the auditory-only condition. For this model (as
+well as all other models in this study), we fixed the values of the
+means to be the end-points of the corresponding continuum, since these
+points are the most typical instances in our stimuli. Thus, we have
+\(\mu_{A1}=0\) and \(\mu_{A2}=4\) (and similarly \(\mu_{V1}=0\), and
+\(\mu_{V2}=4\)). This leaves us with two free parameters: the bias
+\(b_A\) and the variance \(\sigma^2_{A}\). To determine the values of
+these parameters, we fit the unimodal posterior to human data in the
+unimodal case.
 
@@
 means are fixed, we have 3 free parameters: the variances for the visual
-and the auditory modalities, respectively, and \(\epsilon\), the
-response bias. The visual and auditory baselines as well as the optimal
-model are not fit to bimodal data, but their predictions are tested
-against these bimodal data. All these normative models use the variances
-derived from the unimodal data and the bias term derived from the
-bimodal data.
+and the auditory modalities, respectively, and \(b\), the response bias.
+The visual and auditory baselines as well as the optimal model are not
+fit to bimodal data, but their predictions are tested against these
+bimodal data. All these normative models use the variances derived from
+the unimodal data and the bias term derived from the bimodal data.
 
@@
 statistical power to fit a different model for each individual
-participant. Instead, models are constructed with data collapsed across
-all participants. The fit was done with a nonlinear least squares
-regression using the NLS package in R (Bates \& Watts, 1988). We
-computed the values of the parameters, as well as their 95\% confidence
-intervals, through non-parametric bootstrap (using 10000 iterations).
+participant. Instead, models were constructed with data collapsed across
+all participants. That being said, the distribution of responses from
+individual participants will also be studied. The fit was done with a
+nonlinear least squares regression using the NLS package in R (Bates \&
+Watts, 1988). We computed the values of the parameters, as well as their
+95\% confidence intervals, through non-parametric bootstrap (using 10000
+iterations).
 
@@
 tokens. For the auditory modality, we obtained the following
-values:\footnote{all CIs in the paper are 95\% confidence intervals}
-\(\epsilon_A=\) -0.20 {[}0.02, -0.38{]} and \(\sigma^2_A=\) 2.04
-{[}1.66, 2.53{]}. For the visual modality, we obtained \(\epsilon_V=\)
--0.12 {[}0.06, -0.28{]} and \(\sigma^2_V=\) 3.33 {[}2.83, 3.92{]}`.
+values:\footnote{all CIs in the paper are 95\% confidence intervals.}
+\(b_A=\) -0.20 {[}0.02, -0.38{]} and \(\sigma^2_A=\) 2.04 {[}1.66,
+2.53{]}. For the visual modality, we obtained \(b_V=\) -0.12 {[}0.06,
+-0.28{]} and \(\sigma^2_V=\) 3.33 {[}2.83, 3.92{]}.
+
+\begin{figure}[!h]
+\includegraphics[width=\textwidth]{ms_files/figure-latex/unimodal-1} \caption{Human responses in the unimodal conditions.
+Points represent the proportion of `different' to `same' responses in the auditory-only condition (left), and visual-only condition (right).
+Error bars are 95\% confidence intervals.
+Solid lines represent best fits.}\label{fig:unimodal}
+\end{figure}
 
 \subsubsection{Bimodal condition}\label{bimodal-condition-1}
-
-\begin{figure}
-
-{\centering \includegraphics[width=400px]{ms_files/figure-latex/bimodal-1}
-
-}
-
-\caption{Human responses vs. models' predictions in the bimodal condition. Shape represents auditory distance from the target, and color represents visual distance from the target.}\label{fig:bimodal}
-\end{figure}
 
@@
 
-\paragraph{Descriptive model}\label{descriptive-model-1}
+\paragraph{Descriptive model}\label{descriptive-model}
 
 In the descriptive model, all parameters are fit to human responses in
-the bimodal condition. We found \(\epsilon=\) -0.34 {[}-0.28, -0.39{]},
+the bimodal condition. We found \(b=\) -0.34 {[}-0.28, -0.39{]},
 \(\sigma^2_{Ab}=\) 4.96 {[}4.58, 5.40{]} and \(\sigma^2_{Vb}=\) 7.06
@@
 
-The descriptive model explained 95\% of total variance. However, since
-the descriptive model was fit to the same data, there is a risque that
-this high correlation is due to overfitting. To examine this
+\noindent The descriptive model explained 95\% of total variance.
+However, since the descriptive model was fit to the same data, there is
+a risk that this high correlation is due to overfitting. To examine this
 possibility, we cross-validated the model using half the responses to
 predict the other half (averaging across 1000 random partitions). The
-predictive power of the model remained very high (\(r^2\)=0.92).
+predictive power of the model remained very high (\(r^2\)=0.93).
+
+\begin{figure}[!h]
+\includegraphics[width=\textwidth]{ms_files/figure-latex/bimodal-1} \caption{Human responses vs.
+models' predictions in the bimodal condition.
+Shape represents auditory distance from the target, and color represents visual distance from the target.}\label{fig:bimodal}
+\end{figure}
 
@@
 
-\begin{figure}
-
-{\centering \includegraphics[width=400px]{ms_files/figure-latex/individual-1}
-
-}
-
-\caption{Histograms of the values of the visual variance relative to the auditory variance in Experiment 1.
+\begin{figure}[!h]
+\includegraphics[width=\textwidth]{ms_files/figure-latex/individual-1} \caption{Histograms of the values of the visual variance relative to the auditory variance in Experiment 1.
 Light color represents the values derived from each individual participant, and dark color represents simulated data sampled from the descriptive model.}\label{fig:individual}
@@
 ease of comparison, the simulated distribution was superimposed to the
-real distribution. We found that the real distribution was broader than
-the simulated distribution, indicating real between-subject variation
-beyond sampling errors. This means that the participants varied in terms
-of how they wheigthed modalities: Compared to the predictions of the
-global descriptive model, some participants relied more on the auditory
-modality, and some relied more on the visual modality.
+real distribution. We found that the real distribution was broader
+(\(sd=\) 2.24) than the simulated distribution (\(sd=\) 1.17),
+indicating that there was a real between-subject variation beyond
+sampling errors. This means that the participants varied in terms of how
+they weighted modalities: Compared to the predictions of the global
+descriptive model, some participants relied more on the auditory
+modality, whereas others relied more on the visual modality.
 
@@
 \[\beta_a \propto \frac{1}{\sigma^2_{A}+\sigma^2_{N_A}}\]
-\[\beta_v \propto \frac{1}{\sigma^2_{V}}\] The alternative hypothesis is
-that noise in one modality leads to a systematic preference for the
+\[\beta_v \propto \frac{1}{\sigma^2_{V}}.\] The alternative hypothesis
+is that noise in one modality leads to a systematic preference for the
 non-noisy modality.
@@
 responses on the unambiguous training trials. The final sample consisted
-of (N = 93) participants.
+of N = 93 participants.
 
@@
 We fit a model for each modality. For the auditory modality, our
-parameter estimates were \(\epsilon_A=\) -0.18 {[}-0.05, -0.30{]} and
+parameter estimates were \(b_A=\) -0.18 {[}-0.05, -0.30{]} and
 \(\sigma^2_A+\sigma^2_N=\) 4.70 {[}4.03, 5.55{]}. For the visual
-modality, we found \(\epsilon_V=\) -0.24 {[}-0.10, -0.36{]} and
-\(\sigma^2_V=\) 3.93 {[}3.43, 4.55{]}. Figure~\ref{fig:unimodal} shows
-responses in the unimodal conditions as well as the corresponding best
-fits. The visual data is a replication of the visual data in Experiment
-1. As for the auditory data, in contrast to Experiment 1, responses were
-flatter, showing more uncertainty.
+modality, we found \(b_V=\) -0.24 {[}-0.10, -0.36{]} and \(\sigma^2_V=\)
+3.93 {[}3.43, 4.55{]}. Figure~\ref{fig:unimodal} shows responses in the
+unimodal conditions as well as the corresponding best fits. The visual
+data is a replication of the visual data in Experiment 1. As for the
+auditory data, in contrast to Experiment 1, responses were flatter,
+showing more uncertainty.
 
@@
 judgements. Note that, in contrast to Experiment 1, the visual model
-explains more variance than the auditory model.
-
-\paragraph{Descriptive model}\label{descriptive-model-2}
-
-We estimated \(\epsilon=\) -0.38 {[}-0.33, -0.42{]},
+explained more variance than the auditory model did.
+
+\paragraph{Descriptive model}\label{descriptive-model-1}
+
+We estimated \(b=\) -0.38 {[}-0.33, -0.42{]},
 \(\sigma^2_{Ab}+\sigma^2_{Nb}=\) 9.84 {[}8.75, 11.27{]}, and
@@
 total variance. Cross-validation using half the responses to predict the
-other half yielded \(r^2 =\) 0.96.
+other half yielded \(r^2 =\) 0.95.
 
@@
 according to their relative reliability, we found in this experiment
-that the visual modality had a greater weight than what is expected from
-its relative reliability. This situation corresponds to the second case
-of sub-optimally described in Figure~\ref{fig:subOptim}.
+that the visual modality had a greater weight than what was expected
+from its relative reliability. This situation corresponds to the second
+case of sub-optimally described in Figure~\ref{fig:subOptim}.
 
@@
 
-In this Experiment, we tested the case where the background noise was
-added to the visual modality. Similar to Experiment 2, we were
-interested to know if participants would treat this new source of
-uncertainty as predicted by the optimal model, that is, according to the
-following weighting scheme \[\beta_a \propto \frac{1}{\sigma^2_{A}}\]
-\[\beta_v \propto \frac{1}{\sigma^2_{V}+\sigma^2_{N_V}}\] The
+In this Experiment, we added background noise to the visual modality.
+Similar to Experiment 2, we were interested to know if participants
+would treat this new source of uncertainty as predicted by the optimal
+model, that is, according to the following weighting scheme:
+\[\beta_a \propto \frac{1}{\sigma^2_{A}}\]
+\[\beta_v \propto \frac{1}{\sigma^2_{V}+\sigma^2_{N_V}}.\] The
 alternative hypothesis is that, just like noise in the auditory modality
@@
 Mechanical Turk. We used the same exclusion criteria as in both previous
-experiments. 2 participants were excluded because they reported having a
-technical problem, and 10 participants were excluded because they had
-less than 50\% accurate responses on the unambiguous training trials.
-The final sample consisted of (N = 88) participants.
+experiments. N=2 participants were excluded because they reported having
+a technical problem, and N=10 participants were excluded because they
+had less than 50\% accurate responses on the unambiguous training
+trials. The final sample consisted of N = 88 participants.
 
@@
 editor GIMP (2.8.20). We used a Gaussian blur with a
-radius\footnote{A features of the filter that affects the intensity of the blur}
-of 10 pixels. The experimental procedure was exactly the same as in the
+radius\footnote{A features that modulates the intensity of the blur} of
+10 pixels. The experimental procedure was exactly the same as in the
 previous Experiments.
@@
 
+\begin{figure}[!h]
+\includegraphics[width=\textwidth]{ms_files/figure-latex/bias-1} \caption{Modality preference is characterized as a deviation from the optimal decision threshold.
+A) The decision thresholds of both the optimal and the descriptive models (solid red and black lines respectively).
+Deviation from optimality is compared to two hypothetical cases of modality preference.
+In these cases, deviation from  optimality is due to over-lying on the visual or the auditory input (green and blue dotted lines, respectively) by a factor of 2.
+B) The value of the decision threshold's slope derived from the descriptive model relative to that of the optimal model.
+Error bars represent 95\% confidence intervals over the distribution obtained through non-parametric resampling.}\label{fig:bias}
+\end{figure}
+
 \subsubsection{Unimodal conditions}\label{unimodal-conditions-2}
 
-For the auditory modality, our parameter estimates were \(\epsilon_A=\)
--0.24 {[}-0.04, -0.42{]} and \(\sigma^2_A=\) 1.94 {[}1.61, 2.33{]}. For
-the visual modality, we found \(\epsilon_V=\) 0.11 {[}0.27, -0.03{]} and
+For the auditory modality, our parameter estimates were \(b_A=\) -0.24
+{[}-0.04, -0.42{]} and \(\sigma^2_A=\) 1.94 {[}1.61, 2.33{]}. For the
+visual modality, we found \(b_V=\) 0.11 {[}0.27, -0.03{]} and
 \(\sigma^2_V+\sigma^2_N=\) 13.00 {[}9.92, 18.94{]}.
@@
 well as the corresponding fits. The auditory data is a replication of
-the auditory data in Experiment 1. As for the visual data, we see that,
-in contrast to Experiment 1 and 2, responses were flatter, showing much
-more uncertainty.
+the auditory data in Experiment 1. As for the visual data, we found
+that, in contrast to Experiment 1 and 2, responses were flatter, showing
+much more uncertainty.
 
@@
 auditory and optimal models to human responses. These normative models
-explained, respectively, 1\%, 98\%, and 97\% of total variance in mean
-judgement.
-
-\paragraph{Descriptive model}\label{descriptive-model-3}
-
-We estimated \(\epsilon=\) -0.35 {[}-0.29, -0.40{]}, \(\sigma^2_{Ab}=\)
-3.00 {[}2.75, 3.25{]}, and \(\sigma^2_{Vb}+\sigma^2_{Nb}=\) 39.42
-{[}25.06, 98.96{]}. The fit explained 97\% of total variance.
-Cross-validation using half the responses to predict the other half
-yielded \$r\^{}2= \$ 0.96.
+explained, respectively, 1\%, 98\%, and 97\% of total variance in the
+mean judgements.
+
+\paragraph{Descriptive model}\label{descriptive-model-2}
+
+We estimated \(b=\) -0.35 {[}-0.29, -0.40{]}, \(\sigma^2_{Ab}=\) 3.00
+{[}2.75, 3.25{]}, and \(\sigma^2_{Vb}+\sigma^2_{Nb}=\) 39.42 {[}25.06,
+98.96{]}. The fit explained 97\% of total variance. Cross-validation
+using half the responses to predict the other half yielded \(r^2=\)
+0.96.
 
@@
 We found that the optimal model accounted for almost all the variance
-(\(r^2 =\) 0.97). However, whereas in previous experiments, the optimal
+(\(r^2 =\) 0.97). However, whereas in previous experiments the optimal
 model explained more variance than the auditory or the visual models,
@@
 resulting in a much lower weight assigned to it than what is expected
-from its optimal relative reliability. Therefore, just like participants
-over-relied on the visual modality when the auditory modality was noisy
-(Experiment 2), they also over-relied on the auditory modality when the
-visual modality was noisy (Experiment 3).
+from its reliability. Therefore, just like participants over-relied on
+the visual modality when the auditory modality was noisy (Experiment 2),
+they also over-relied on the auditory modality when the visual modality
+was noisy (Experiment 3).
+
+\begin{table}[tbp]
+\begin{center}
+\begin{threeparttable}
+\caption{\label{tab:exclusive}The percentage of participants who relied exclusively on either the visual modality or the auditory modality, using a factor of 10 as a cut-off (e.g., we consider that a participant relied exclusively on the visual modality when their auditory variance is a at least 10 times larger than their visual variance).
+We show the percentage compared to the total number of participants in each Experiment (`Total').
+From this subset of participants, we show the percentage of those who relied on the  auditory modality (`Auditory'), and the percentage of those who relied on the visual  modality (Visual').}
+\begin{tabular}{llll}
+\toprule
+Experiment & \multicolumn{1}{c}{Total} & \multicolumn{1}{c}{Auditory} & \multicolumn{1}{c}{Visual}\\
+\midrule
+Exp1 & 21.25 & 70.59 & 29.41\\
+Exp2 & 34.41 & 31.25 & 68.75\\
+Exp3 & 38.64 & 94.12 & 5.88\\
+\bottomrule
+\end{tabular}
+\end{threeparttable}
+\end{center}
+\end{table}
 
@@
 the percentage of Experiment 2, except that now almost all of them
-relied on the auditory modality (94.12\%).
-
-\begin{figure}
-
-{\centering \includegraphics[width=400px]{ms_files/figure-latex/bias-1}
-
-}
-
-\caption{Modality preference is characterized as a deviation from the optimal decision threshold.
-A) The decision thresholds of both the optimal and the descriptive models (solid red and black lines respectively).
-Deviation from optimality is compared to two hypothetical cases of modality preference.
-In these cases, deviation from  optimality is due to over-lying on the visual or the auditory input (green and blue dotted lines, respectively) by a factor of 2.
-B) The value of the decision threshold's slope derived from the descriptive model relative to that of the optimal model.
-Error bars represent 95\% confidence intervals over the distribution obtained through non-parametric resampling.}\label{fig:bias}
-\end{figure}
+relied on the auditory modality (94.12\%). For ease of comparison, Table
+\ref{tab:exclusive} provides a summary of the numbers across the three
+Experiments.
 
@@
 When identifying a spoken word under uncertainty, one often needs to
-combine and make the most of the available multimodal cues. While most
-previous studies focused on the case of audio-visual speech where people
-combine cues from speech and facial features, this work explored the
-case of identifying an ambiguous word when the available multimodal cues
-are speech and the visual referent. More specifically, we conducted an
-ideal observer analysis of the task whereby a model provided predictions
-about how information from each modality should be combined in an
-optimal fashion. The predictions of the model were tested in a series of
-three experiments where instances of both the form and the referent were
-ambiguous with respect to their category membership only (Experiment 1),
-when instances of the form were perturbed with additional background
-noise (Experiment 2), and when instances of the referent were perturbed
-with additional visual noise (Experiment 3).
+make the most of the available cues. Some previous work studied optimal
+behavior under uncertainty from the auditory input only (e.g., Clayards
+et al., 2008; Feldman et al., 2009), and others studied optimality under
+multimodal uncertainty in auditory speech and visual facial features
+(e.g. Bejjanki et al., 2011). The current work explored, for the first
+time, the case of word identification under uncertainty in speech (word
+form) and the visual word \emph{referent}. More specifically, we
+conducted an ideal observer analysis of the task whereby a model
+provided predictions about how information from each modality should be
+combined in an optimal fashion. The predictions of the model were tested
+in a series of three experiments where instances of both the form and
+the meaning were ambiguous with respect to their category membership
+only (Experiment 1), when instances of the form were perturbed with
+additional background noise (Experiment 2), and when instances of the
+referent were perturbed with additional visual noise (Experiment 3).
 
@@
 reliability. At the individual level, however, we found evidence of a
-between-subject variation: Some participants relied slighly more on the
-visual modality, whereas others relied slighly more on the auditory
+between-subject variation: Some participants relied slightly more on the
+visual modality, whereas others relied slightly more on the auditory
 modality.
@@
 a higher precision (e.g., Ernst \& Banks, 2002). Nevertheless, there is
-a crucial difference between these two situations. Research on
-multisensory integration (of which audio-visual speech is arguably an
-instance) deals with redundant multimodal cues, and these cues are
-integrated into a unified percept. In contrast, the word-referent
-association is usually arbitrary and, in particular, the cues are not
-expected to be correlated perceptually. Therefore the mind cannot form a
-unified percept, rather, it must encode information separately from both
-modalities and retain this encoding through the decision making process.
-Retaining two separate cues at the same time instead of forming one
-unified percept (as in multisensory integration of redundant cues), or
-instead of retaining only one cue (as in the unimodal case), is likely
-to place extra-demand on cognitive resources, which, in turn, can cause
-general performance to drop. Indeed, there is evidence that cognitive
-load has a detrimental effect on word recognition, which can be due to a
-reduction in perceptual acuity (Mattys \& Wiget, 2011). Similar to our
-finding, previous experimental studies reported that in both children
-and adults, identifying new ambiguous form-referent mappings is usually
-associated with what appears to be a decrease in speech perception
-acuity (Pajak, Creel, \& Levy, 2016; Stager \& Werker, 1997). Hofer and
-Levy (2017) provided a probabilistic model of this phenomenon, which
-they similarly characterized as an increase in the noise variance of the
-auditory modality. Our finding replicates this previously documented
-fact, and additionally suggests that the reduction in perceptual acuity
-occurs simultaneously in both the auditory and the visual modalities.
+a crucial difference between these two situations (besides the obvious
+difference in terms of the models used). Research on multisensory
+integration (of which audio-visual speech is arguably an instance) deals
+with redundant multimodal cues, and these cues are integrated into a
+unified percept. In contrast, the word-referent association is usually
+arbitrary and, in particular, the cues are not expected to be correlated
+perceptually. Therefore the observer cannot form a unified percept,
+rather, it must encode information separately from both modalities and
+retain this encoding through the decision making process. Retaining two
+separate cues at the same time instead of forming one unified percept
+(as in multisensory integration of redundant cues), or instead of
+retaining only one cue (as in the unimodal case), is likely to place
+extra-demand on cognitive resources, which, in turn, can cause general
+performance to drop. Indeed, there is evidence that cognitive load has a
+detrimental effect on word recognition. This phenomenon can be due to a
+reduction in perceptual acuity (e.g., Mattys \& Wiget, 2011).
+
+Some previous research found a similar case of suboptimal behavior. For
+instance, studies that explored the identification of ambiguous, newly
+learned pairs of word-referent associations all reported what appears to
+be a decrease in speech perception acuity in both children (Stager \&
+Werker, 1997) and adults (Pajak, Creel, \& Levy, 2016). Recently, Hofer
+and Levy (2017) provided a probabilistic model of this phenomenon. In
+agreement with the finding in the current study, Hofer and Levy (2017)
+characterized the apparent reduction in perceptual acuity as an increase
+in the noise variance of the auditory modality. Our finding, besides
+providing more evidence to this documented fact, suggests that the
+reduction in perceptual acuity may occurs simultaneously in both the
+auditory \emph{and} the visual modalities.
 
@@
 what can be explained by the relative reliability alone, meaning that
-the participant tend to ignore at least part of the information still
+the participants tend to ignore at least part of the information still
 available in the noisy modality.
@@
 This second case of sub-optimal behavior is possibly related to the fact
-that language understanding under degraded listening conditions is
-cognitively more taxing than language understanding under normal
-conditions (Ronnberg, Rudner, Lunner, \& Zekveld, 2010). This fact can
-lead to a preference/bias towards alternative sources of information
-when these sources are available. One could explain this phenomenon in
-terms of the metacognitive experience about the fluency with which
+that language understanding under degraded conditions is cognitively
+more taxing than language understanding under normal conditions (e.g.,
+Ronnberg, Rudner, Lunner, \& Zekveld, 2010). This fact can lead to a
+bias against the more noisy cue. One could also explain this phenomenon
+in terms of the metacognitive experience about the fluency with which
 information is processed. The perceived perceptual fluency (e.g., the
@@
 
-In this study, we tested the extent to which people would be optimal in
-combining uncertain auditory and visual cues to recognize words. This
-required that we use a case of double ambiguity, that is, a case where
-both the word forms (\enquote{ada}-\enquote{aba}) and the referents
-(cat-dog) were similar and, thus, confusable. One could wonder about the
-extent to which such case occurs in real languages? Cross-linguistic
-corpus analyses suggest that the lexical encoding tends towards double
-ambiguity in many languages (Dautriche, Mahowald, Gibson, \& Piantadosi,
-2017; Monaghan, Shillcock, Christiansen, \& Kirby, 2014; Tamariz, 2008).
-For instance, Dautriche et al. (2017) analysed 100 languages and found
-that word that are similar phonologically tend to be similar
-semantically as well, beyond what could be explained by chance.
-Crucially, they found this trend in a set of monomorphemic lemmas in
-four languages, suggesting that the effect is not driven by
-morphological regularities. These studies suggest that the case of
-double uncertainty, though perhaps not pervasive, could be a real issue
-in language as it increase the probability of confusability. Moreover,
-it is important to keep in mind that ambiguity in both the form and the
-referent can be induced by an external noisy context even when these
-forms and referents are not confusable in normal situations.
+An important question to ask is how the combination mechanism---as
+revealed in our controlled study---scales up to real life situations.
+Note that in order to test audio-visual cue combination under
+uncertainty, we had to use a case of double ambiguity, that is, a case
+where both the word forms (\enquote{ada}-\enquote{aba}) and the
+referents (cat-dog) were similar and, thus, confusable. However, to what
+extent does such case occur in real languages? Cross-linguistic corpus
+analyses suggest that lexical encoding tends, surprisingly, towards
+double ambiguity in many languages (Dautriche, Mahowald, Gibson, \&
+Piantadosi, 2017; Monaghan, Shillcock, Christiansen, \& Kirby, 2014;
+Tamariz, 2008). For instance, Dautriche et al. (2017) analyzed 100
+languages and found that words that are similar phonologically tend to
+be similar semantically as well, beyond what could be explained by
+chance. These studies suggest that the case of double uncertainty,
+though perhaps not pervasive, could be a real issue in language as it
+increase the probability of confusability for many
+words.\linebreak Besides the case of double ambiguity intrinsic to
+language, there are two situations where our mechanism might play a
+significant role. The first is when ambiguity in both the form and/or
+the referent is induced by an external noisy context even when these
+forms and referents are not confusable in normal situations. The second
+case is that of early word learning, and we will discuss this case in
+more detail in what follows.
 
@@
 
+One limitation of the work is that we used simplified stimuli. For the
+auditory modality, we used speech categories that varied along a single
+acoustic dimension. While this dimension might be sufficient to
+recognize words in our specific case, in general the speech signal may
+be more complex, varying along several acoustic/phonetic dimensions.
+Additionally, these dimensions may be highly variable due to various
+kinds of speaker and context differences. The same thing can be said
+about the referential stimuli. Here we used a continuum along a single
+morph dimension in order to construct a multimodal input where the
+auditory and visual components have symmetrical properties. Though such
+morph is not the exact visual variability that people would encounter in
+they daily lives, it allowed us to precisely test the role of auditory
+and visual information in the cue combination process. Parameterizing
+semantic dimensions is a notoriously difficult problem, but morphs have
+been used in previous research as a reasonable proxy (Freedman et al.,
+2001; Havy \& Waxman, 2016; Sloutsky \& Fisher, 2004). It is an open
+question as to whether people use the same strategy in controlled
+laboratory conditions, as in more naturalistic settings where they have
+to deal with various levels of variability. However an answer to this
+question is likely to involve a multifaceted approach,
+involving---besides laboratory experiments---analyses of corpora with a
+more realistic multimodal input (e.g., Fourtassi, Schatz, Varadarajan,
+\& Dupoux, 2014; Harwath, Torralba, \& Glass, 2016; B. C. Roy, Frank,
+DeCamp, \& Roy, 2015).
+
 In conclusion, this work studied the mechanism of word identification
-under uncertainty in both the word form and the word meaning. To our
+under uncertainty in both the word form and the word referent. To our
 knowledge, this is the first study that performs an ideal observer
@@
 especially when the stimuli were perturbed with additional background
-noise. Future work will extend the present formal framework in order to
-account for how children use multimodal cues to refine their early
+noise. Though the present study did not directly address the issue of
+early word learning, it provides a framework where developmental
+questions can also be investigated. For instance, future work should
+explore whether children, like adults, use probabilistic cues from both
+the auditory and the visual input to recognize ambiguous words, the
+extent to which they combine these cues in an optimal fashion, and
+whether these combination help them with refining their early
 phonological and semantic representations.
 
-\section{Appendix: derivation of the posterior (equation
-1)}\label{appendix-derivation-of-the-posterior-equation-1}
+\section{Appendix 1: derivation of the posterior (Equation
+1)}\label{appendix-1-derivation-of-the-posterior-equation-1}
 
@@
 In order to further simplify the quantity \(\frac{p(w|W_1)}{p(w|W_2)}\),
-we use our assumption that the cues are uncorrelated,
+we use our assumption that the cues are uncorrelated:
 \[p(w | W) = p(a,v| W) = p(a| A)p(v| V)\] Using the \(\log\)
@@
 
-When putting all these terms together, we the get this final expression
+When putting all these terms together, we obtain this final expression
 for the posterior:
-\[p(W_2 | w)=\frac{1}{1+(1+\epsilon)\exp(\beta_0+\beta_aa+\beta_vv)}\]
+\[p(W_2 | w)=\frac{1}{1+(1+b)\exp(\beta_0+\beta_aa+\beta_vv)}\]
 
@@
 
-\[1+\epsilon=\frac{p(W_1)}{p(W_2)}\]
+\[1+b=\frac{p(W_1)}{p(W_2)}\]
 \[\beta_0=\frac{\mu^2_{A2}-\mu^2_{A1}}{2\sigma^2_{A}}+\frac{\mu^2_{V2}-\mu^2_{V1}}{2\sigma^2_{V}}\]
@@
 \[\beta_a=\frac{\mu_{A1}-\mu_{A2}}{\sigma^2_{A}}\]
-\[\beta_v=\frac{\mu_{V1}-\mu_{V2}}{\sigma^2_{V}}\]
+\[\beta_v=\frac{\mu_{V1}-\mu_{V2}}{\sigma^2_{V}}.\]
 
@@
 \hypertarget{refs}{}
-\hypertarget{ref-alais04}{}
-Alais, D., \& Burr, D. (2004). The ventriloquist effect results from
-near-optimal bimodal integration. \emph{Current Biology}, \emph{14}(3),
-257--262.
-
 \hypertarget{ref-anderson90}{}
@@
 
+\hypertarget{ref-fourtassi2014b}{}
+Fourtassi, A., Schatz, T., Varadarajan, B., \& Dupoux, E. (2014).
+Exploring the relative role of bottom-up and top-down information in
+phoneme learning. In \emph{Proceedings of the 52nd annual meeting of the
+association for computational linguistics (volume 2: Short papers)}
+(Vol. 2, pp. 1--6).
+
 \hypertarget{ref-freedman2001}{}
@@
 
+\hypertarget{ref-harwath2016}{}
+Harwath, D., Torralba, A., \& Glass, J. (2016). Unsupervised learning of
+spoken language with visual context. In \emph{Advances in neural
+information processing systems} (pp. 1858--1866).
+
+\hypertarget{ref-havy2016}{}
+Havy, M., \& Waxman, S. R. (2016). Naming influences 9-month-olds'
+identification of discrete categories along a perceptual continuum.
+\emph{Cognition}, \emph{156}, 41--51.
+
 \hypertarget{ref-hillenbrand1995}{}
@@
 Neurosciences}, \emph{27}(12), 712--719.
+
+\hypertarget{ref-kuhl1991}{}
+Kuhl, P. K. (1991). Human adults and human infants show a ``perceptual
+magnet effect'' for the prototypes of speech categories, monkeys do not.
+\emph{Perception \& Psychophysics}, \emph{50}(2), 93--107.
 
@@
 
+\hypertarget{ref-rahnev2018}{}
+Rahnev, D., \& Denison, R. N. (2018). Suboptimality in perceptual
+decision making. \emph{Behavioral and Brain Sciences}, 1?107.
+
 \hypertarget{ref-reber98}{}
@@
 \hypertarget{ref-robinson2010}{}
-Robinson, C. W., \& Sloutsky, V. M. (2010). Development of cross-modal
+Robinson, C. W., \& Sloutsky, V. (2010). Development of cross-modal
 processing. \emph{Wiley Interdisciplinary Reviews: Cognitive Science},
@@
 
+\hypertarget{ref-roy2015}{}
+Roy, B. C., Frank, M. C., DeCamp, M., P., \& Roy, D. (2015). Predicting
+the birth of a spoken word. \emph{Proceedings of the National Academy of
+Sciences}, \emph{112}.
+
 \hypertarget{ref-saussure1916}{}
@@
 
+\hypertarget{ref-sloutsky2004}{}
+Sloutsky, V., \& Fisher, A. V. (2004). Induction and categorization in
+young children: A similarity-based model. \emph{Journal of Experimental
+Psychology: General}, \emph{133}(2), 166.
+
 \hypertarget{ref-sloutsky2003}{}
-Sloutsky, V. M., \& Napolitano, A. (2003). Is a picture worth a thousand
+Sloutsky, V., \& Napolitano, A. (2003). Is a picture worth a thousand
 words? Preference for auditory modality in young children. \emph{Child

### 2018-04-15 Writeup/ms.Rmd
modif to ms

@@
 This research strategy provides a characterization of the task/goal and shows what the optimal performance should be under this characterization.^[It is, thus, a general instance of the rational approach to cognition [@anderson90].
-It can also be seens as an instance Marr's computational level of analysis.] When there is uncertainty in the input, the ideal observer performs an optimal probabilistic inference.
+It can also be seens as an instance of Marr's computational level of analysis.] When there is uncertainty in the input, the ideal observer performs an optimal probabilistic inference.
 For example, in order to recognize an ambiguous linguistic input, the model uses all available probabilistic knowledge in order to maximize the accuracy of this recognition.
 When the task is well specified, the ideal observer model can be seen as a theoretical upper limit on performance.
-Thus, it is supposed to be used, not so much as a realistic model of human performance, as much as a baseline against which human performance can be compared [@Geisler2003; @rahnev2018].
+It is supposed to be used, not so much as a realistic model of human performance, as much as a baseline against which human performance can be compared [@Geisler2003; @rahnev2018].
 When there is a deviation from the ideal, it can reveal extra constraints on human cognition, such as limitations on the working memory or attentional resources.
@@
 On the face of it, the question of combining information from the sound and the visual referent might seem similar to that of audio-visual speech integration.
-Nevertheless, there are at least two fundamental differences between these two cases, and both can influence the way the auditory and visual cues are integrated:
+Nevertheless, there are at least two fundamental differences between these two cases, and both can influence the way the auditory and visual cues are combined:
 
@@
 In a referential context, however, the auditory and visual modalities are additionally different in terms of the roles they play in the referential process: the auditory input represents the *symbol* whereas the visual input represents the *meaning*.
-It has been suggested that because of its referential property, speech is a privileged signal for humans, starting in infancy [see @vouloumanos2014 for a review].^[There is a debate as to whether speech is privileged for infant and adults for the same reasons.
-Whereas some researchers suggest that speech is privileged for both infants and adults because of its ability to refer [e.g., @waxman1995], others suggest that speech might *not* have a referential status from the start.
-Rather, speech might be prefered by infants only because of a low level auditory ``overshadowing'' [e.g., @sloutsky2003].] Thus, in a referential context, it is possible that listeners do not treat the auditory and visual modalities as equivalent sources of information.
+It has been suggested that because of its referential property, speech is a privileged signal for humans, starting in infancy [see @vouloumanos2014 for a review].^[There is a debate as to whether speech is privileged for children and adults for the same reasons.
+Whereas some researchers suggest that speech is privileged for both children and adults because of its ability to refer [e.g., @waxman1995], others suggest that speech might *not* have a referential status from the start.
+Rather, speech might be prefered by children only because of a low level auditory ``overshadowing'' [e.g., @sloutsky2003].] Thus, in a referential context, it is possible that listeners do not treat the auditory and visual modalities as equivalent sources of information.
 Instead, there could be a sub-optimal bias for the auditory modality beyond what is expected from informational reliability alone.
@@
 In all experiments, participants were quantitatively near-optimal, though overall response precision was slightly lower than expected.
-Moreover, in Experiment 1 where neither of the modalities was perturbed with background noise, participants weighed auditory and visual cues according to the relative reliability predicted by the optimal model.
+Moreover, in Experiment 1 where neither of the modalities was perturbed with background noise, participants weighted auditory and visual cues according to the relative reliability predicted by the optimal model.
 In other words, we found no evidence for a modality bias towards either the auditory or the visual modality.
@@
 We construct an ideal observer model that combines probabilistic information from the auditory and visual modalities.
-In contrast to the  model used in most research on multisensory integration [e.g., @ernst02]---which typically studies continuous stimuli (e.g., size, location)---this probabilistic information cannot be characterized with *sensory noise/variability*, only.
-Indeed, our task involves responses over categorical variables (phonemes and concepts), and therefore, the optimal model in our case should take into account, not only the noise variability around an individual perceptual estimate, but also its *within category variability*, i.e., the uncertainty related to whether this perceptual estimate belongs to a given category [see also @Bankieris17; @bejjanki2011].
+In contrast to the  model used in most research on multisensory integration [e.g., @ernst02]---which typically studies continuous stimuli (e.g., size, location)---this probabilistic information in our case cannot be characterized with *sensory noise/variability*, only.
+Indeed, our task involves responses over categorical variables (phonemes and concepts), and therefore, the optimal model in our case should take into account, not only the noise variability around an individual perceptual estimate, but also its *categorical variability*, i.e., the uncertainty related to whether this perceptual estimate belongs to a given category [see also @Bankieris17; @bejjanki2011].
 In what follows, we describe a model that accounts for both type of variability.
@@
 The first baseline is a visual model which assumes that participants rely only on visual information, and an auditory model, which assumes that participants rely only on auditory information.
-More precisely, these baseline models assumes that the participants' responses in the bimodal condition will not be different from their response in either the visual-only or the auditory-only condition.
+More precisely, these baseline models assume that the participants' responses in the bimodal condition will not be different from their response in either the visual-only or the auditory-only condition.
 If, as we expect, the participants rely on both the auditory and the visual modalities to make decision in the bimodal condition, the optimal model would explain more variance in human responses than the visual or the auditory model do.
@@
 In addition to these normative models, we consider a *descriptive* model.
-The parameters of this model are fit to actual responses in the bimodal condition.
+It is formally identical to the normative optimal model (Equation 1), except that the parameters are fit to actual responses in the bimodal condition.
 If the referential task induces sub-optimality (due, for instance, to the arbitrary nature of the sound-object association), then the descriptive model should explain more variance than the optimal model does.
@@
 
-There are three possible ways human responses can deviate from optimality. These scenarios are illustrated in Figure\ \@ref(fig:subOptim) and are as follows:
+There are three possible ways human responses can deviate from optimality. These scenarios are illustrated in Figure\ \@ref(fig:subOptim), and are as follows:
 
@@
 The percentage of participants who relied exclusively on either the visual modality or the auditory modality was `r 100*(only_visual_N_3+only_sound_N_3)/(only_visual_N_3+only_sound_N_3+both_N_3)`%, which is closer to the percentage of Experiment 2, except that now almost all of them relied on the auditory modality (`r 100*(1-exlusive_prop_3)`%).
-For ease of comparison, Table \@ref(tab:exclusive) provides a summary of the numbers across the three Experiments.
+For ease of comparison, Table \@ref(tab:exclusive) provides a summary of the numbers across the three experiments.
 
@@
 @bejjanki2011].
-The current work explored, for the first time, the case of word identification under uncertainty in speech (word form) and the visual word *referent*.
+The current work explored, for the first time, the case of word identification under uncertainty in speech (word form) and the visual *referent*.
 More specifically, we conducted an ideal observer analysis of the task whereby a model provided predictions about how information from each modality should be combined in an optimal fashion.
@@
 
-The second case of sub-optimality is related to how participants weighed the cues from the visual and the auditory modalities in a noisy context.
+The second case of sub-optimality is related to how participants weighted the cues from the visual and the auditory modalities in a noisy context.
 In contrast to Experiment 1 where the combination was indistinguishable from the optimal prediction, results of Experiment 2 and 3 which both involved background noise in one modality, showed that participants had a systematic preference for the other (non-noisy) modality.
@@
 For example, upon hearing a noisy instance of "bee", adults may have to decide whether the speaker intended to say "pea" or "bee", but children can additionally be uncertain whether "bee" is a different word from "pee" (as opposed to, say, a valid within category variation), especially if these similar sounding words are newly learned [@stager1997; @Merriman91; @Creel2012; @Swingley2016; @white2008b].
-Though new word form representation can be shown to be differentiated under some circumstances [e.g., @yoshida2009], this differentiation is still not mature enough and is probably noisier than the adult-like representation and/or encoded with lower confidence [see @Swingley2007].
+Though similar word form representation can be shown to be differentiated under some circumstances [e.g., @yoshida2009], this differentiation is still not mature enough and is probably noisier than the adult-like representation and/or encoded with lower confidence [see @Swingley2007].
 
@@
 Vice versa, @yeung09 showed that pairing similar sounds with different objects help infants pay attention to subtle phonological contrasts.
-The present study proposes a first step towards a formal framework where accounts of sound-meaning synergy in development can be unified and further explored.
-For example, one could imagine that, initially, visual and auditory categories have relatively large noise variances, and that development consists in reducing the values of the variances through a mutually constraining process as further multimodal data accumulates.
-
-One limitation of the work is that we used simplified stimuli.
+The present study proposes a first step towards a formal framework where isolated accounts of sound-meaning interaction in development can be unified and further explored.
+<!--For example, one could imagine that, initially, visual and auditory categories have relatively large noise variances, and that development consists in reducing the values of the variances through a mutually constraining process as further multimodal data accumulates.
+--->
+
+One limitation of this work is that we used simplified stimuli.
 For the auditory modality, we used speech categories that varied along a single acoustic dimension.
@@
 Here we used a continuum along a single morph dimension in order to construct a multimodal input where the auditory and visual components have symmetrical properties.
-Though such morph is not the exact visual variability that people would encounter in they daily lives, it allowed us to precisely test the role of auditory and visual information in the cue combination process.
+Though such morph is not the exact visual variability that people would encounter in their daily lives, it allowed us to precisely test the role of auditory and visual information in the cue combination process.
 Parameterizing semantic dimensions is a notoriously difficult problem, but morphs have been used in previous research as a reasonable proxy [@freedman2001; @havy2016; @sloutsky2004].
 It is an open question as to whether people use the same strategy in controlled laboratory conditions, as in more naturalistic settings where they have to deal with various levels of variability.
-However an answer to this question is likely to involve a multifaceted approach, involving---besides laboratory experiments---analyses of corpora with a more realistic multimodal input [e.g., @fourtassi2014b; @harwath2016; @roy2015].
-
-In conclusion, this work studied the mechanism of word identification under uncertainty in both the word form and the word referent.
+However an answer to this question is likely to involve a multifaceted research approach, involving---besides laboratory experiments---analyses of corpora with a more realistic multimodal input [e.g., @fourtassi2014b; @harwath2016; @roy2015].
+
+# Conclusion 
+This work studied the mechanism of word identification under uncertainty in both the word form and the word referent.
 To our knowledge, this is the first study that performs an ideal observer analysis of this task.

### 2018-04-15 Writeup/ms.tex
modif to ms

@@
   a general instance of the rational approach to cognition (Anderson,
-  1990). It can also be seens as an instance Marr's computational level
-  of analysis.} When there is uncertainty in the input, the ideal
+  1990). It can also be seens as an instance of Marr's computational
+  level of analysis.} When there is uncertainty in the input, the ideal
 observer performs an optimal probabilistic inference. For example, in
@@
 this recognition. When the task is well specified, the ideal observer
-model can be seen as a theoretical upper limit on performance. Thus, it
-is supposed to be used, not so much as a realistic model of human
+model can be seen as a theoretical upper limit on performance. It is
+supposed to be used, not so much as a realistic model of human
 performance, as much as a baseline against which human performance can
@@
 differences between these two cases, and both can influence the way the
-auditory and visual cues are integrated:
+auditory and visual cues are combined:
 
@@
 Waxman, 2014 for a review).\footnote{There is a debate as to whether
-  speech is privileged for infant and adults for the same reasons.
+  speech is privileged for children and adults for the same reasons.
   Whereas some researchers suggest that speech is privileged for both
-  infants and adults because of its ability to refer (e.g., Waxman \&
+  children and adults because of its ability to refer (e.g., Waxman \&
   Markow, 1995), others suggest that speech might \emph{not} have a
   referential status from the start. Rather, speech might be prefered by
-  infants only because of a low level auditory ``overshadowing'' (e.g.,
+  children only because of a low level auditory ``overshadowing'' (e.g.,
   Sloutsky \& Napolitano, 2003).} Thus, in a referential context, it is
@@
 where neither of the modalities was perturbed with background noise,
-participants weighed auditory and visual cues according to the relative
+participants weighted auditory and visual cues according to the relative
 reliability predicted by the optimal model. In other words, we found no
@@
 Banks, 2002)---which typically studies continuous stimuli (e.g., size,
-location)---this probabilistic information cannot be characterized with
-\emph{sensory noise/variability}, only. Indeed, our task involves
-responses over categorical variables (phonemes and concepts), and
-therefore, the optimal model in our case should take into account, not
-only the noise variability around an individual perceptual estimate, but
-also its \emph{within category variability}, i.e., the uncertainty
-related to whether this perceptual estimate belongs to a given category
-(see also Bankieris, Bejjanki, \& Aslin, 2017; Bejjanki et al., 2011).
-In what follows, we describe a model that accounts for both type of
-variability. First, we describe the model in the simplified case of
-categorical variability only. Second, we augment this simplified model
-to account for sensory noise.
+location)---this probabilistic information in our case cannot be
+characterized with \emph{sensory noise/variability}, only. Indeed, our
+task involves responses over categorical variables (phonemes and
+concepts), and therefore, the optimal model in our case should take into
+account, not only the noise variability around an individual perceptual
+estimate, but also its \emph{categorical variability}, i.e., the
+uncertainty related to whether this perceptual estimate belongs to a
+given category (see also Bankieris, Bejjanki, \& Aslin, 2017; Bejjanki
+et al., 2011). In what follows, we describe a model that accounts for
+both type of variability. First, we describe the model in the simplified
+case of categorical variability only. Second, we augment this simplified
+model to account for sensory noise.
 
@@
 that participants rely only on auditory information. More precisely,
-these baseline models assumes that the participants' responses in the
+these baseline models assume that the participants' responses in the
 bimodal condition will not be different from their response in either
@@
 data in the unimodal conditions. In addition to these normative models,
-we consider a \emph{descriptive} model. The parameters of this model are
-fit to actual responses in the bimodal condition. If the referential
-task induces sub-optimality (due, for instance, to the arbitrary nature
-of the sound-object association), then the descriptive model should
-explain more variance than the optimal model does.
+we consider a \emph{descriptive} model. It is formally identical to the
+normative optimal model (Equation 1), except that the parameters are fit
+to actual responses in the bimodal condition. If the referential task
+induces sub-optimality (due, for instance, to the arbitrary nature of
+the sound-object association), then the descriptive model should explain
+more variance than the optimal model does.
 
@@
 There are three possible ways human responses can deviate from
-optimality. These scenarios are illustrated in Figure~\ref{fig:subOptim}
-and are as follows:
+optimality. These scenarios are illustrated in
+Figure~\ref{fig:subOptim}, and are as follows:
 
@@
 real distribution. We found that the real distribution was broader
-(\(sd=\) 2.24) than the simulated distribution (\(sd=\) 1.17),
+(\(sd=\) 2.24) than the simulated distribution (\(sd=\) 1.19),
 indicating that there was a real between-subject variation beyond
@@
 \ref{tab:exclusive} provides a summary of the numbers across the three
-Experiments.
+experiments.
 
@@
 time, the case of word identification under uncertainty in speech (word
-form) and the visual word \emph{referent}. More specifically, we
-conducted an ideal observer analysis of the task whereby a model
-provided predictions about how information from each modality should be
-combined in an optimal fashion. The predictions of the model were tested
-in a series of three experiments where instances of both the form and
-the meaning were ambiguous with respect to their category membership
-only (Experiment 1), when instances of the form were perturbed with
-additional background noise (Experiment 2), and when instances of the
-referent were perturbed with additional visual noise (Experiment 3).
+form) and the visual \emph{referent}. More specifically, we conducted an
+ideal observer analysis of the task whereby a model provided predictions
+about how information from each modality should be combined in an
+optimal fashion. The predictions of the model were tested in a series of
+three experiments where instances of both the form and the meaning were
+ambiguous with respect to their category membership only (Experiment 1),
+when instances of the form were perturbed with additional background
+noise (Experiment 2), and when instances of the referent were perturbed
+with additional visual noise (Experiment 3).
 
@@
 
-The second case of sub-optimality is related to how participants weighed
-the cues from the visual and the auditory modalities in a noisy context.
-In contrast to Experiment 1 where the combination was indistinguishable
-from the optimal prediction, results of Experiment 2 and 3 which both
-involved background noise in one modality, showed that participants had
-a systematic preference for the other (non-noisy) modality. From
-previous empirical studies, we know that when the speech signal is
-degraded, people tend to compensate by relying more on other sources of
-information such as the accompanying visual cues (i.e., lip movements)
-or the semantic/syntactic context (see Mattys, Davis, Bradlow, \& Scott,
-2012 for a review). However, and generally speaking, these studies do
-not differentiate between an optimal compensatory strategy (i.e.,
-relying more on the alternative source while using all information still
-available in the distorted signal), and a sub-optimal strategy (i.e.,
-relying more on the alternative source while ignoring at least some of
-the information still available in the distorted signal). The formal
-approach followed in this paper allowed us to tease apart these two
-possibilities, and the analysis supports the sub-optimal compensatory
-strategy: The preference for the non-noisy modality is above and beyond
-what can be explained by the relative reliability alone, meaning that
-the participants tend to ignore at least part of the information still
-available in the noisy modality.
+The second case of sub-optimality is related to how participants
+weighted the cues from the visual and the auditory modalities in a noisy
+context. In contrast to Experiment 1 where the combination was
+indistinguishable from the optimal prediction, results of Experiment 2
+and 3 which both involved background noise in one modality, showed that
+participants had a systematic preference for the other (non-noisy)
+modality. From previous empirical studies, we know that when the speech
+signal is degraded, people tend to compensate by relying more on other
+sources of information such as the accompanying visual cues (i.e., lip
+movements) or the semantic/syntactic context (see Mattys, Davis,
+Bradlow, \& Scott, 2012 for a review). However, and generally speaking,
+these studies do not differentiate between an optimal compensatory
+strategy (i.e., relying more on the alternative source while using all
+information still available in the distorted signal), and a sub-optimal
+strategy (i.e., relying more on the alternative source while ignoring at
+least some of the information still available in the distorted signal).
+The formal approach followed in this paper allowed us to tease apart
+these two possibilities, and the analysis supports the sub-optimal
+compensatory strategy: The preference for the non-noisy modality is
+above and beyond what can be explained by the relative reliability
+alone, meaning that the participants tend to ignore at least part of the
+information still available in the noisy modality.
 
@@
 Schuster, 1991; Stager \& Werker, 1997; Swingley, 2016; White \& Morgan,
-2008). Though new word form representation can be shown to be
+2008). Though similar word form representation can be shown to be
 differentiated under some circumstances (e.g., Yoshida, Fennell,
@@
 contrasts. The present study proposes a first step towards a formal
-framework where accounts of sound-meaning synergy in development can be
-unified and further explored. For example, one could imagine that,
-initially, visual and auditory categories have relatively large noise
-variances, and that development consists in reducing the values of the
-variances through a mutually constraining process as further multimodal
-data accumulates.
-
-One limitation of the work is that we used simplified stimuli. For the
+framework where isolated accounts of sound-meaning interaction in
+development can be unified and further explored.
+
+One limitation of this work is that we used simplified stimuli. For the
 auditory modality, we used speech categories that varied along a single
@@
 morph is not the exact visual variability that people would encounter in
-they daily lives, it allowed us to precisely test the role of auditory
+their daily lives, it allowed us to precisely test the role of auditory
 and visual information in the cue combination process. Parameterizing
@@
 to deal with various levels of variability. However an answer to this
-question is likely to involve a multifaceted approach,
+question is likely to involve a multifaceted research approach,
 involving---besides laboratory experiments---analyses of corpora with a
@@
 
-In conclusion, this work studied the mechanism of word identification
-under uncertainty in both the word form and the word referent. To our
-knowledge, this is the first study that performs an ideal observer
-analysis of this task. We found people to be near optimal in their cue
-combination: They weighted each modality according to its relative
-reliability. However, they also showed patterns of sub-optimality
-especially when the stimuli were perturbed with additional background
-noise. Though the present study did not directly address the issue of
-early word learning, it provides a framework where developmental
-questions can also be investigated. For instance, future work should
-explore whether children, like adults, use probabilistic cues from both
-the auditory and the visual input to recognize ambiguous words, the
-extent to which they combine these cues in an optimal fashion, and
-whether these combination help them with refining their early
-phonological and semantic representations.
+\section{Conclusion}\label{conclusion}
+
+This work studied the mechanism of word identification under uncertainty
+in both the word form and the word referent. To our knowledge, this is
+the first study that performs an ideal observer analysis of this task.
+We found people to be near optimal in their cue combination: They
+weighted each modality according to its relative reliability. However,
+they also showed patterns of sub-optimality especially when the stimuli
+were perturbed with additional background noise. Though the present
+study did not directly address the issue of early word learning, it
+provides a framework where developmental questions can also be
+investigated. For instance, future work should explore whether children,
+like adults, use probabilistic cues from both the auditory and the
+visual input to recognize ambiguous words, the extent to which they
+combine these cues in an optimal fashion, and whether these combination
+help them with refining their early phonological and semantic
+representations.
 

### 2018-04-20 Writeup/ms.Rmd
modif to manuscript

@@
 We introduce a task that allows us to examine how adults identify words under joint uncertainty in the auditory and visual modalities.
-We propose an ideal observer model of the task which provides an account of how auditory and visual cues are combined optimally.
+We propose an ideal observer model which provides an account of how auditory and visual cues are combined optimally.
 Model predictions are tested in three experiments where word recognition is made under two kinds of uncertainty: category ambiguity and/or distorting noise.
@@
 library(ggthemes)
-#theme_set(theme_few())
 library(broom)
@@
 ```{r}
-summarise <- dplyr::summarise
-rename <- dplyr::rename
-```
-
-```{r}
 #First Exlusion criteria:
@@
 #Summary
+
 sounds_exp1 <- exp1_good %>%
@@
 
+#Combine all
 exp_uni_data <- bind_rows(sounds_exp1, concepts_exp1,
@@
 
-Language uses symbols expressed in one modality (e.g., the auditory modality, in the case of speech) to communicate about the world, which we perceive through many different sensory modalities.
+Language uses symbols expressed in one modality, e.g., the auditory modality, in the case of speech, to communicate about the world, which we perceive through many different sensory modalities.
 Consider hearing someone yell "bee!" at a picnic, as a honey bee buzzes around the food.
@@
 For simplicity, we focus on audio-visual matching here.} Perhaps the insect was a beetle or a fly instead.
-
-How does the listener deal with uncertainty to identify the speaker's intended word?
+How does the listener deal with such multimodal uncertainty to recognize the speaker's intended word?
+
+The task of matching the sound to the corresponding visual object has been extensively studied in the developmental literature since it is considered to be an crucial instance of early word learning.
+For example, many studies focused on how children succeed in this task despite high referential ambiguity [@smith08; @pinker1989; @medina2011; @vouloumanos2008; @yurovsky2015; @suanda2014; @vlach2013].
+However, even when they know the exact meanings of the words, listeners (both children and adults) often face the task of recognizing which word the speaker has uttered, especially under noisy circumstances.
+The purpose of the current study is to explore the special case of word recognition under uncertainty when adult observers have access to multimodal cues from the speech and the referent.
+
 One rigorous way to approach this question is through conducting an *ideal observer* analysis.
 This research strategy provides a characterization of the task/goal and shows what the optimal performance should be under this characterization.^[It is, thus, a general instance of the rational approach to cognition [@anderson90].
-It can also be seens as an instance of Marr's computational level of analysis.] When there is uncertainty in the input, the ideal observer performs an optimal probabilistic inference.
+It can also be seen as an instance of Marr's computational level of analysis.] When there is uncertainty in the input, the ideal observer performs an optimal probabilistic inference.
 For example, in order to recognize an ambiguous linguistic input, the model uses all available probabilistic knowledge in order to maximize the accuracy of this recognition.
-When the task is well specified, the ideal observer model can be seen as a theoretical upper limit on performance.
-It is supposed to be used, not so much as a realistic model of human performance, as much as a baseline against which human performance can be compared [@Geisler2003; @rahnev2018].
+The ideal observer model can be seen as a theoretical upper limit on performance.
+It is not so much a realistic model of human performance, as much as a baseline against which human performance can be compared [@Geisler2003; @rahnev2018].
 When there is a deviation from the ideal, it can reveal extra constraints on human cognition, such as limitations on the working memory or attentional resources.
-
-The ideal observer analysis has had a tremendous impact not only on speech related research [@Norris08; @clayard08; @feldman2009; @kleinschmidt2015], but also on many other disciplines in the cognitive sciences [for reviews, see @chater06; @Knill04; @tenenbaum11].
-In particular, using this research strategy, @clayard08 simulated auditory uncertainty by manipulating the probability distribution of a cue (VOT) that differentiated similar words (e.g., "beach" and "peach").
+The ideal observer analysis has had a tremendous impact not only on speech related research [@Norris08; @clayard08; @feldman2009; @kleinschmidt2015], but also on many other disciplines in the cognitive sciences [for reviews, see @chater06; @Knill04; @tenenbaum11]
+
+Some of these ideal-observer-based studies are closely related to the question we are addressing in the current work.
+For instance, @clayard08 simulated auditory uncertainty by manipulating the probability distribution of a cue (Voice Onset Time) that differentiated similar words (e.g., "beach" and "peach").
 They found that humans were sensitive to these probabilistic cues and their judgments closely reflected the optimal predictions.
@@
 They showed that this effect can be explained as the consequence of optimally solving the problem of perception under uncertainty.
-Both @clayard08 and @feldman2009 explored optimal performance under uncertainty in the auditory modality.
-There is, however, extensive evidence that information from the visual modality, such as the speaker's facial features,  also influences speech understanding [see @Campbell2008 for a review].
+
+Besides the acoustic cues explored in @clayard08 and @feldman2009, there is extensive evidence that information from the visual modality, such as the speaker's facial features,  also influences speech understanding [see @Campbell2008 for a review].
 @bejjanki2011 offered a mathematical characterization of how probabilistic cues from speech and lip movements can be optimally combined.
 They showed that human performance during audio-visual phonemic labeling was consistent (at least at the qualitative level) with the behavior of the ideal observer.
-
-This previous research, however, did not systematically study speech understanding when the visual information is obtained, not through the speaker's facial features, but through the referential context.
+This previous research, however, did not systematically study speech understanding when the visual information is obtained, not through the speaker's facial features---as in audio-visual speech perception, but through the referential context.
 In fact, experimental findings showed that information about the identity of the semantic referent can be integrated with linguistic information to resolve lexical and syntactic ambiguities in speech [e.g., @Eberhard1995; @Tanenhaus1995; @spivey2002].
 To our knowledge, however, no study offered an ideal observer analysis of word identification in such context, that is, when the listener has to combine cues from the sound and the referent.
-Imagine, for example, that someone is uncertain whether they heard "pea" or "bee", does this uncertainty make them rely more on the referent (e.g., the object being pointed at)?
-Vice versa, if they are not sure if they saw a bee or a fly, does it make them rely more on the sound?
-More importantly, when input in both modalities is uncertain to varying degrees, do they weight each modality according to its relative reliability (which is the optimal strategy), or do they over-rely on a particular modality (which is a sub-optimal strategy)?
 
 On the face of it, the question of combining information from the sound and the visual referent might seem similar to that of audio-visual speech integration.
-Nevertheless, there are at least two fundamental differences between these two cases, and both can influence the way the auditory and visual cues are combined:
-
-\noindent First, in the case of audio-visual speech, both modalities offer information about the same underlying speech category.
+Nevertheless, there are at least two fundamental differences between these two cases, and both can influence the way the auditory and visual cues are combined: First, in the case of audio-visual speech, both modalities offer information about the same underlying speech category.
 They may differ only in terms of their informational reliability.
-In a referential context, however, the auditory and visual modalities are additionally different in terms of the roles they play in the referential process: the auditory input represents the *symbol* whereas the visual input represents the *meaning*.
+In a referential context, however, the auditory and visual modalities play different roles in the referential process---in addition to possible differences in informational reliability.
+Indeed, the auditory input represents the *symbol* whereas the visual input represents the *meaning*.
 It has been suggested that because of its referential property, speech is a privileged signal for humans, starting in infancy [see @vouloumanos2014 for a review].^[There is a debate as to whether speech is privileged for children and adults for the same reasons.
 Whereas some researchers suggest that speech is privileged for both children and adults because of its ability to refer [e.g., @waxman1995], others suggest that speech might *not* have a referential status from the start.
-Rather, speech might be prefered by children only because of a low level auditory ``overshadowing'' [e.g., @sloutsky2003].] Thus, in a referential context, it is possible that listeners do not treat the auditory and visual modalities as equivalent sources of information.
+Rather, speech might be preferred by children only because of a low level auditory ``overshadowing'' [e.g., @sloutsky2003].] Thus, in a referential context, it is possible that listeners do not treat the auditory and visual modalities as equivalent sources of information.
 Instead, there could be a sub-optimal bias for the auditory modality beyond what is expected from informational reliability alone.
 
-\noindent Second in the case of audio-visual speech, the auditory and visual stimuli are expected to be perceptually correlated.
+Second, in the case of audio-visual speech, the auditory and visual stimuli are expected to be perceptually correlated.
 The expectation for this correlation is such that when there is a mismatch between the auditory and visual input, people still integrate them into a unified (but illusory) percept [@mcgurk1976].
@@
 
-In the current study, we investigate how people combine cues from the auditory and the visual modality to recognize words in a referential context.
+## The current study
+
+We investigate how people combine cues from the auditory and the visual modality to recognize words in a referential context.
 In particular, we study how this combination is performed under various degrees of uncertainty in both the auditory and the visual modality.
+Imagine, for example, that someone is uncertain whether they heard "pea" or "bee", does this uncertainty make them rely more on the referent (e.g., the object being pointed at)?
+Vice versa, if they are not sure if they saw a bee or a fly, does it make them rely more on the sound?
+More importantly, when input in both modalities is uncertain to varying degrees, do they weight each modality according to its relative reliability (which is the optimal strategy), or do they over-rely on a particular modality (which is a sub-optimal strategy)?
+
 We perform a rational analysis of the task.
@@
 We construct an ideal observer model that combines probabilistic information from the auditory and visual modalities.
-In contrast to the  model used in most research on multisensory integration [e.g., @ernst02]---which typically studies continuous stimuli (e.g., size, location)---this probabilistic information in our case cannot be characterized with *sensory noise/variability*, only.
-Indeed, our task involves responses over categorical variables (phonemes and concepts), and therefore, the optimal model in our case should take into account, not only the noise variability around an individual perceptual estimate, but also its *categorical variability*, i.e., the uncertainty related to whether this perceptual estimate belongs to a given category [see also @Bankieris17; @bejjanki2011].
+In contrast to the  model used in most research on multisensory integration [e.g., @ernst02]---which typically studies continuous stimuli (e.g., size, location)---the probabilistic information in our case cannot be characterized with *sensory noise*, only.
+Indeed, our task involves responses over categorical variables (phonemes and concepts), and therefore, the optimal model should take into account, not only the noise variability around an individual perceptual estimate, but also its *categorical variability*, i.e., the uncertainty related to whether this perceptual estimate belongs to a given category [see also @Bankieris17; @bejjanki2011].
 In what follows, we describe a model that accounts for both type of variability.
@@
 
-\noindent This assumption simply says that, given a word-object mapping, e.g., $W=$("cat"-CAT), variation in the way "cat" is pronounced does not correlate with changes in any visual property of the object CAT, which is a valid assumption.\footnote{Note that this assumptions is more adequate in the case of arbitrary associations such as ours, and less so in the case of redundant association such as audio-visual speech.
+\noindent This assumption says that, given a word-object mapping, e.g., $W=$("cat"-CAT), variation in the way "cat" is pronounced does not correlate with changes in any visual property of the object CAT, which is a valid assumption.\footnote{Note that this assumptions is more adequate in the case of arbitrary associations such as ours, and less so in the case of redundant association such as audio-visual speech.
 In the latter, variation in the pronunciation is expected to correlate, at least to some extent, with lip movements.}
@@
 $p(a_t | A) \sim N(\mu_{A}, \sigma^2_{A})$, the ideal model assumes that it has direct access to this production token (i.e., $a=a_t$), and that all uncertainty is about the category membership of this token.
-However, we might also want to account for noise in the brain and/or in the environment.
+However, we might also want to account for internal noise in the brain and/or external noise in the environment.
 For example, the observer might not have access to the exact produced target, but only to the target perturbed by noise.
@@
 More precisely, these baseline models assume that the participants' responses in the bimodal condition will not be different from their response in either the visual-only or the auditory-only condition.
-If, as we expect, the participants rely on both the auditory and the visual modalities to make decision in the bimodal condition, the optimal model would explain more variance in human responses than the visual or the auditory model do.
+However, if the participants rely on both the auditory and the visual modalities to make decision in the bimodal condition, the optimal model would explain more variance in human responses than the visual or the auditory model do.
 
@@
 We compared these models to human responses in three experiments.
-In Experiment 1, we studied the case where bimodal uncertainty was due to ambiguity in terms of category membership, without any additional background noise.
-In Experiment 2 and 3 we added background noise on top of ambiguity in category membership.
+In Experiment 1, we studied the case where bimodal uncertainty was due to categorical variability, only.
+In Experiment 2 and 3 we added noise in the background on top of categorical variability.
 
@@
 
-In this Experiment, we start with testing the predictions in the case where uncertainty is due to categorical variability only (i.e., ambiguity in terms of category memebership).
+In this Experiment, we test the predictions of the model in the case where uncertainty is due to categorical variability only (i.e., ambiguity in terms of category membership).
 We do not add any external noise to the background and we assume that internal sensory noise is negligible compared to categorical variability ($\sigma^2_{A} \gg \sigma^2_{N_A}$, and $\sigma^2_{V} \gg \sigma^2_{N_V}$).
@@
 
-#Bootstrap sample parameters
+#Bootstrap sample of parameters
 
@@
 ###### Extract values from saved data 
+##To reproduce the values, please uncomment the previous code following the function "lmfit"
 
@@
 
-#Fit the non-linear function
+#Fit the posteriors to the reponses
 
@@
 #############
+
+#Posterior for auditory-only condition
 sound_nl1 <- nls(answer ~ 1/(1+(1-e)*exp((-4/vrA)*sound_dist+(8/vrA))), data=sound_all_exp1, start = list(e=0, vrA=2))
 
+#Posterior for visual-only condition
 concept_nl1 <- nls(answer ~ 1/(1+(1-e)*exp((-4/vrV)*concept_dist+(8/vrV))), data=concept_all_exp1, start = list(e=0, vrV=2))
 
-#Here I should test the cross-validation
-
+#Posterior for audio-visual condition (this is the descriptive model)
 joint_nl1 <- nls(answer ~ 1/(1+(1-e)*exp((-4/vrA_j)*sound_dist+(-4/vrV_j)*concept_dist+(8/vrA_j)+(8/vrV_j))), data=joint_all_exp1, start = list(e=0, vrA_j=2, vrV_j=2))
@@
 
+### the fit functions
 x <- seq(0, 4, 0.01)
@@
 
+#### Combine all the fit functions
 all_uni_model <- bind_rows(uniS_nl1, uniV_nl1,
@@
 
+### plot unimodal data + fit functions 
 all_plot <- ggplot(exp_uni_data, 
@@
 Since the values of the means are fixed, we have 3 free parameters: the variances for the visual and the auditory modalities, respectively, and $b$, the response bias.
-The visual and auditory baselines as well as the optimal model are not fit to bimodal data, but their predictions are tested against these bimodal data.
-All these normative models use the variances derived from the unimodal data and the bias term derived from the bimodal data.
+The visual and auditory baselines as well as the optimal model are not fit to the bimodal data, but their predictions are tested against these bimodal data.
+All these normative models use the variances derived from the unimodal data and the bias term derived from the fit to bimodal data.
 
@@
 Instead, models were constructed with data collapsed across all participants.
-That being said, the distribution of responses from individual participants will also be studied.
+That being said, the distribution of responses from individual participants will also be analyzed.
 The fit was done with a nonlinear least squares regression using the NLS package in R [@bates88].
@@
 
-#All models
-
-#Here we use the values obtained from the fitting using bootstrap sampling to
-
-#The fit
+###Models to be tested against responses in the bimodal condition
+
+#Descriptive model without a terms for response bias 
 model_fit0 <- function (x,y) {
@@
 
-#The fit
+#Descriptive model (parameters are derived from fit to bimodal data)
 model_fit1 <- function (x,y) {
@@
 
-#The ideal
+#The optimal model (parameters are derived from fit to unimodal data)
 model_ideal1 <- function (x,y) {
@@
 
-#The fit
+#Descriptive model (parameters are derived from fit to bimodal data)
 model_fit2 <- function (x,y) {
@@
 
-#The ideal
+#The optimal model (parameters are derived from fit to unimodal data)
 model_ideal2 <- function (x,y) {
@@
 
-#The fit
+#Descriptive model (parameters are derived from fit to bimodal data)
 model_fit3 <- function (x,y) {
@@
 
-#The ideal
+#The optimal model (parameters are derived from fit to unimodal data)
 model_ideal3 <- function (x,y) {
@@
 ```{r echo=FALSE, fig.width=7, fig.height=8}
+
+#Generate prediction in the bimodal condition
 
@@
 
+##Combine all predictions
+
 models_all <- bind_rows (models_exp1, models_exp2, models_exp3)
@@
   geom_point()+
+  scale_colour_solarized()+
  #geom_pointrange(aes(ymin = summary_ci_lower, ymax = summary_ci_upper), 
@@
 
-#Explore cross-validation here.
-As the numbers show, the predictions on the held-out subset is almost as acurate as the predcitions on the training set.
-Over-fitting is generally not a problem with such simple models)
-
-#Here is use hald the responses to predic the other half
-#The function takes the data to be cross-validated and return a score (coefficient of determination)
+#Here we conduct cross-validation for the descriptive model, since this model is trained and tested on the same data
+
+#As the numbers show, the predictions on the held-out subset is almost as accurate as the predictions on the training set.  Over-fitting is generally not a problem with such simple models)
+
+#We conduct a cross-validation where half the responses are used predict the other half
+
+#The function "crossValid", below, takes the data to be cross-validated and return a score (coefficient of determination)
 
@@
 
-crossValid_exp1 <- replicate(10, {
+#Average across N partions, to render the pdf I am using a small value, but higher values can be used for the final version
+N_partitions = 10
+
+crossValid_exp1 <- replicate(N_partitions, {
   crossValid(joint_all_exp1)
@@
 
-crossValid_exp2 <- replicate(10, {
+crossValid_exp2 <- replicate(N_partitions, {
   crossValid(joint_all_exp2)
@@
 
-crossValid_exp3 <- replicate(10, {
+crossValid_exp3 <- replicate(N_partitions, {
   crossValid(joint_all_exp3)
@@
 However, since the descriptive model was fit to the same data, there is a risk that this high correlation is due to overfitting.
-To examine this possibility, we cross-validated the model using half the responses to predict the other half (averaging across 1000 random partitions).
+To examine this possibility, we cross-validated the model using half the responses to predict the other half (averaging across `r N_partitions` random partitions).
 The predictive power of the model remained very high ($r^2$=`r CV_exp1_mean`).
@@
 However, we see in Figure\ \@ref(fig:bimodal) that the mean responses deviated systematically from the optimal prediction in that they were slightly pulled toward chance (i.e., the probability 0.5).
-This is due to the increase in the value of the variance associated with each modality.
+This fact is due to the increase in the value of the variance associated with each modality.
 Note however that, despite this increase in randomness, our analysis of modality preference showed that the relative values of these variances were not different (Figure\ \@ref(fig:bias)), meaning that there was no evidence for a modality preference.
@@
 
+##Here we fit logistic regression to each participant
+##The logitic regression is equivalent to the descriptive model without the bias term
+##We use logistic regressions  instead of the full descriptive model becuase the latter would not converge given the small data points available for each participant
+
 joint_bysub_1 <- joint_all_exp1 %>%
@@
 
+##Extract auitory and visual variances for each participant
+
+#Exp1
 bimodal_bysub_1 = tidy(joint_bysub_1, fit_joint_1) %>%
@@
 
+#Exp2
 bimodal_bysub_2 = tidy(joint_bysub_2, fit_joint_2) %>%
@@
 
+#Exp3
 bimodal_bysub_3 = tidy(joint_bysub_3, fit_joint_3) %>%
@@
 #number of participants relying exlusiviely on one modality
-#cut off is a factor of 10
-
+#cut off: a factor of 10
+
+#participants who rely on both modalities 
 bimodal_bysub_good_1 <- bimodal_bysub_1 %>%
@@
 
-#Visual modality 
+#participants who rely only on the visual modality
+#(this includes participants who relied  only on the visual modality but gave noisy responses, leading to negative values of the variance, probably due to mistaking "same" for "different", or vice versa)
 only_visual_N_1 <- bimodal_bysub_1 %>%
@@
 
-#Sound modality 
+#participants who rely only on the auditory modality
+
 only_sound_N_1 <- bimodal_bysub_1 %>%
@@
 
-#the rest
+#participants who relied on both modalities 
 both_N_1 <- bimodal_bysub_1 %>%
@@
 
+#participants with noisy negative variances
 neg_N_1 <- bimodal_bysub_1 %>%
@@
 
+#Proportion of participants who relied only on the visual modality
 exlusive_prop_1 = only_visual_N_1/(only_sound_N_1+only_visual_N_1)
@@
 ```{r echo=FALSE, warning = FALSE}
-#What does the mean data say 
-#generate two data point from a binomial with probabilty model_fit1()
-#loop over visual and auditory distance/ or create  adataframe with
+
+#Simulated individual data from descriptive model model_fit0 without a bias term (equivalent to logitic regression)
+#(but the values are very similar to descriptive model with bias the term model_fit1)
 
 simulations <- data.frame()
-#x <- c("ID", "bimod")
-#colnames(simlations) <- x
-
+
+#We aggregate simulted values for 50 times the number of participants  (in order to get a stable final distribution)
 for (i in 1:50) {
@@
 
-  #I need to take the average of this over multiple runs
+#Process and combine Real and Simulated data
 
@@
 
-  #n_remove <- nrow(bimod_sim)-nrow(bimod_real)
-
-  #bimod_sim <- head(bimod_sim, -n_remove)
-
   bimod_all <- bind_rows(bimod_real, bimod_sim)
-
-#Here do some quatiative measure:
 
@@
 
-```{r echo=FALSE, individual, out.width = "\\textwidth", fig.pos = "!h",fig.cap = "Histograms of the values of the visual variance relative to the auditory variance in Experiment 1.
-Light color represents the values derived from each individual participant, and dark color represents simulated data sampled from the descriptive model."}
+```{r echo=FALSE, individual, out.width = "\\textwidth", fig.pos = "!h",fig.cap = "Histograms of the individual values of the visual variance relative to the auditory variance in Experiment 1.
+Light color represents the values derived from each individual participant, and dark color represents simulated individual responses sampled from the descriptive model."}
 
@@
 Imagine, for instance, that in the bimodal condition half the participants relied exclusively on the visual modality, whereas the other half relied exclusively on the auditory modality.
-This case could still lead to an aggregate behaviour which appears optimal, but this optimality would be spurious.
+This case could still lead to an aggregate behavior which appears optimal, but this optimality would be spurious.
 
@@
 The percentage of both cases was relatively small compared to the total number of participants (`r 100*(only_visual_N_1+only_sound_N_1)/(only_visual_N_1+only_sound_N_1+both_N_1)`%).
-An additional number of participants (N=`r neg_N_1`) relied on both modalities, but provided noisy responses which lead to negative variances (probably due to mistaking 'same' for 'different' or vice versa).
 When these outliers  were removed, the distribution had a rather unimodal shape (Figure\ \@ref(fig:individual)).
@@
 For ease of comparison, the simulated distribution was superimposed to the real distribution.
-We found that the real distribution was broader ($sd=$ `r subset(sd_ind, data=='real')$sd`) than the simulated distribution ($sd=$ `r subset(sd_ind, data=='simulation')$sd`), indicating that there was a real between-subject variation beyond sampling errors.
-This means that the participants varied in terms of how they weighted modalities: Compared to the predictions of the global descriptive model, some participants relied more on the auditory modality, whereas others relied more on the visual modality.
+We found that the real distribution had a standard deviation of $sd=$ `r subset(sd_ind, data=='real')$sd` which was larger than that of the simulated distribution ($sd=$ `r subset(sd_ind, data=='simulation')$sd`), indicating that there was real between-subject variation beyond sampling errors.
+This finding means that the participants varied in terms of how they weighted modalities: Compared to the predictions of the population-level model, some participants relied more on the auditory modality, whereas others relied more on the visual modality.
 
@@
 
-#the rest
+#Both
 both_N_2 <- bimodal_bysub_2 %>%
@@
 Using the same cut-off as in Experiment 1 (a factor of 10), the percentage of participants who relied exclusively on either modalities was `r 100*(only_visual_N_2+only_sound_N_2)/(only_visual_N_2+only_sound_N_2+both_N_2)`%, which is much higher than the percentage obtained in Experiment 1 (`r 100*(only_visual_N_1+only_sound_N_1)/(only_visual_N_1+only_sound_N_1+both_N_1)`%).
-Moreover, the subset of participants relying exclusively on the visual modality (compared to those who relied exclusively on the auditory modality)  increased from `r 100*exlusive_prop_1`% in Experiment 1 to `r 100*exlusive_prop_2`% in Experiment 2, indicating that noise in the auditory modality prompted more participants to rely exclusively and disproportionately on the visual modality.
+Moreover, the subset of participants relying exclusively on the visual modality (compared to those who relied exclusively on the auditory modality)  increased from `r 100*exlusive_prop_1`% in Experiment 1 to `r 100*exlusive_prop_2`% in Experiment 2, indicating that noise in the auditory modality prompted more participants to rely exclusively and disproportionately on the visual modality (see Table \@ref(tab:exclusive)).
 
@@
 Similar to Experiment 2, we were interested to know if participants would treat this new source of uncertainty as predicted by the optimal model, that is, according to the following weighting scheme:  $$\beta_a \propto \frac{1}{\sigma^2_{A}}$$ $$\beta_v \propto \frac{1}{\sigma^2_{V}+\sigma^2_{N_V}}.$$
-The alternative hypothesis is that, just like noise in the auditory modality lead to a preference for the visual input in Experiment 2, noise in the visual modality would lead to a  preference for the auditory input.
+The alternative hypothesis is that noise in the visual modality would lead to a preference for the auditory input, just like noise in the auditory modality lead to a preference for the visual input in Experiment 2.
 
@@
 ```{r echo=FALSE, warning = FALSE}
+
 #Modality bias
-
 preference = c(bias_val_1, bias_val_2, bias_val_3 )
@@
 ```{r bias, echo=FALSE, warning = FALSE, out.width = "\\textwidth", fig.pos = "!h", fig.cap = "Modality preference is characterized as a deviation from the optimal decision threshold.
-A) The decision thresholds of both the optimal and the descriptive models (solid red and black lines respectively).
+A) The decision thresholds of both the optimal and the descriptive models (solid red and black lines, respectively).
 Deviation from optimality is compared to two hypothetical cases of modality preference.
-In these cases, deviation from  optimality is due to over-lying on the visual or the auditory input (green and blue dotted lines, respectively) by a factor of 2.
+In these cases, deviation from  optimality is due to over-lying on the visual or the auditory input by a factor of 2 (green and blue dotted lines, respectively).
 B) The value of the decision threshold's slope derived from the descriptive model relative to that of the optimal model.
@@
 The reason why we saw this (floor) effect when we added noise to the visual modality (Experiment 3), and not when we added noise to the auditory modality (Experiment 2), is the fact that our visual stimuli were originally perceived less categorically and with less certainty than the auditory stimuli.
-This made it more likely for the visual categorization function to become flat and uninformative after a few drops in precision due to noise on the one had, and to the additional randomness induced by the bimodal presentation on the other hand.
+This fact made it more likely for the visual categorization function to become flat and uninformative after a few drops in precision due to noise on the one had, and to the additional randomness induced by the bimodal presentation on the other hand.
 
@@
 
-#the rest
+#Both
 both_N_3 <- bimodal_bysub_3 %>%
@@
 # General Discussion
-
 When identifying a spoken word under uncertainty, one often needs to make the most of the available cues.
@@
 
-In all Experiments, we found many patterns of optimal behaviour.
+In all Experiments, we found many patterns of optimal behavior.
 Quantitatively speaking, the optimal model accounted, respectively, for `r 100*R2_optimal_1`%, `r 100*R2_optimal_2`%, and `r 100*R2_optimal_3`% of the variance in mean responses.
@@
 First, in all Experiments, the variance associated with each modality increased in the bimodal condition compared to the unimodal conditions.
-This means that participants responded slightly more randomly in the bimodal condition than they did in the unimodal conditions.
+This fact means that participants responded slightly more randomly in the bimodal condition than they did in the unimodal conditions.
 This finding contrasts with research on  multisensory integration where associations tend to lead to a higher precision [e.g., @ernst02].
@@
 Recently, @hofer2017 provided a probabilistic model of this phenomenon.
-In agreement with the finding in the current study, @hofer2017 characterized the apparent reduction in perceptual acuity as an increase in the noise variance of the auditory modality.
-Our finding, besides providing more evidence to this documented fact, suggests that the reduction in perceptual acuity may occurs simultaneously in both the auditory *and* the visual modalities.
+In agreement with the method and finding in the current study, @hofer2017 characterized the apparent reduction in perceptual acuity as an increase in the noise variance of the auditory modality.
+Our finding, besides providing more evidence to this documented fact, suggests that the apparent reduction in perceptual acuity may occurs simultaneously in both the auditory *and* the visual modalities.
 
@@
 However, and generally speaking, these studies do not differentiate between an optimal compensatory strategy (i.e., relying more on the alternative source while using all information still available in the distorted signal), and a sub-optimal strategy (i.e., relying more on the alternative source while ignoring at least some of the information still available in the distorted signal).
-The formal approach followed in this paper allowed us to tease apart these two possibilities, and the analysis supports the sub-optimal compensatory strategy: The preference for the non-noisy modality is above and beyond what can be explained by the relative reliability alone, meaning that the participants tend to ignore at least part of the information still available in the noisy modality.
+The formal approach followed in this paper allowed us to tease apart these two possibilities, and our analysis supports the sub-optimal compensatory strategy: The preference for the non-noisy modality is above and beyond what can be explained by the relative reliability alone, meaning that the participants tend to ignore at least part of the information still available in the noisy modality.
 
@@
 Cross-linguistic corpus analyses suggest that lexical encoding tends, surprisingly, towards double ambiguity in many languages [@dautriche17; @Monaghan2014; @Tamariz2008].
-For instance, @dautriche17 analyzed 100 languages and found that words that are similar phonologically  tend to be similar semantically as well, beyond what could be explained by chance.
-These studies suggest that the case of double uncertainty, though perhaps not pervasive, could be a real issue in language as it increase the probability of confusability for many words.\linebreak Besides the case of double ambiguity intrinsic to language, there are two situations where our mechanism might play a significant role.
+For instance, @dautriche17 analyzed 100 languages and found that words that are similar phonologically  tend to be similar semantically as well.
+These studies suggest that the case of double uncertainty, though perhaps not pervasive, could be a real issue in language as it increase the probability of confusability for many words.\linebreak That being said, besides the case of double ambiguity intrinsic to language, there are two situations where our mechanism might play a significant role.
 The first is when ambiguity in both the form and/or the referent is induced by an external noisy context even when these forms and referents are not confusable in normal situations.
-The second case is that of early word learning, and we will discuss this case in more detail in what follows.
+The second case is that of early word recognition/learning, and we will discuss this case in more detail in what follows.
 
@@
 Among other things, children have to enrich this early representation with new features, and revise its extension in the light of new referential exposures.
-
-Thus, uncertainty in the representation associated with one modality (e.g., a bee and a fly) can be mitigated through the possibly more differentiated representations associated with the other modality (e.g., the sound "bee" is acoustically different from the sound "fly").
-That being said, a multi-modal cue combination strategy might help children not only recognize an individual word instance, but also refine the underlying phonological and semantic representations in the process.
+In sum, uncertainty in the representation associated with one modality (e.g., a bee and a fly) can be mitigated through the possibly more differentiated representations associated with the other modality (e.g., the sound "bee" is acoustically different from the sound "fly").
+
+The multi-modal cue combination strategy might help children not only recognize an individual word instance, but also refine the underlying phonological and semantic representations in the process.
 Previous research in early word learning has---whether implicitly or explicitly---largely treated the process of learning form and of learning meaning as independent.
@@
 It is an open question as to whether people use the same strategy in controlled laboratory conditions, as in more naturalistic settings where they have to deal with various levels of variability.
-However an answer to this question is likely to involve a multifaceted research approach, involving---besides laboratory experiments---analyses of corpora with a more realistic multimodal input [e.g., @fourtassi2014b; @harwath2016; @roy2015].
+An answer to this question is likely to involve a multifaceted research approach, involving---besides laboratory experiments---analyses of corpora with a more realistic multimodal input [e.g., @fourtassi2014b; @harwath2016; @roy2015].
 
@@
 
+\vspace{1em} \fbox{\parbox[b][][c]{14cm}{\centering All data and code for these analyses are available at\ \url{https://github.com/afourtassi/WordRec}}} \vspace{1em}
+
 # Appendix 1: derivation of the posterior (Equation 1)
@@
 
+# Acknowledgements
+
+This work was supported by a post-doctoral grant from the Fyssen Foundation + XXX
+
 # References

### 2018-04-20 Writeup/ms.tex
modif to manuscript

@@
 under joint uncertainty in the auditory and visual modalities. We
-propose an ideal observer model of the task which provides an account of
-how auditory and visual cues are combined optimally. Model predictions
-are tested in three experiments where word recognition is made under two
+propose an ideal observer model which provides an account of how
+auditory and visual cues are combined optimally. Model predictions are
+tested in three experiments where word recognition is made under two
 kinds of uncertainty: category ambiguity and/or distorting noise. In all
@@
 
-Language uses symbols expressed in one modality (e.g., the auditory
-modality, in the case of speech) to communicate about the world, which
+Language uses symbols expressed in one modality, e.g., the auditory
+modality, in the case of speech, to communicate about the world, which
 we perceive through many different sensory modalities. Consider hearing
@@
 For simplicity, we focus on audio-visual matching here.}
-Perhaps the insect was a beetle or a fly instead.
-
-How does the listener deal with uncertainty to identify the speaker's
-intended word? One rigorous way to approach this question is through
-conducting an \emph{ideal observer} analysis. This research strategy
-provides a characterization of the task/goal and shows what the optimal
-performance should be under this characterization.\footnote{It is, thus,
-  a general instance of the rational approach to cognition (Anderson,
-  1990). It can also be seens as an instance of Marr's computational
-  level of analysis.} When there is uncertainty in the input, the ideal
-observer performs an optimal probabilistic inference. For example, in
-order to recognize an ambiguous linguistic input, the model uses all
-available probabilistic knowledge in order to maximize the accuracy of
-this recognition. When the task is well specified, the ideal observer
-model can be seen as a theoretical upper limit on performance. It is
-supposed to be used, not so much as a realistic model of human
+Perhaps the insect was a beetle or a fly instead. How does the listener
+deal with such multimodal uncertainty to recognize the speaker's
+intended word?
+
+The task of matching the sound to the corresponding visual object has
+been extensively studied in the developmental literature since it is
+considered to be an crucial instance of early word learning. For
+example, many studies focused on how children succeed in this task
+despite high referential ambiguity (Medina, Snedeker, Trueswell, \&
+Gleitman, 2011; Pinker, 1989; Smith \& Yu, 2008; Suanda, Mugwanya, \&
+Namy, 2014; Vlach \& Johnson, 2013; Vouloumanos, 2008; Yurovsky \&
+Frank, 2015). However, even when they know the exact meanings of the
+words, listeners (both children and adults) often face the task of
+recognizing which word the speaker has uttered, especially under noisy
+circumstances. The purpose of the current study is to explore the
+special case of word recognition under uncertainty when adult observers
+have access to multimodal cues from the speech and the referent.
+
+One rigorous way to approach this question is through conducting an
+\emph{ideal observer} analysis. This research strategy provides a
+characterization of the task/goal and shows what the optimal performance
+should be under this characterization.\footnote{It is, thus, a general
+  instance of the rational approach to cognition (Anderson, 1990). It
+  can also be seen as an instance of Marr's computational level of
+  analysis.} When there is uncertainty in the input, the ideal observer
+performs an optimal probabilistic inference. For example, in order to
+recognize an ambiguous linguistic input, the model uses all available
+probabilistic knowledge in order to maximize the accuracy of this
+recognition. The ideal observer model can be seen as a theoretical upper
+limit on performance. It is not so much a realistic model of human
 performance, as much as a baseline against which human performance can
@@
 cognition, such as limitations on the working memory or attentional
-resources.
-
-The ideal observer analysis has had a tremendous impact not only on
-speech related research (Clayards, Tanenhaus, Aslin, \& Jacobs, 2008;
-Feldman, Griffiths, \& Morgan, 2009; Kleinschmidt \& Jaeger, 2015;
+resources. The ideal observer analysis has had a tremendous impact not
+only on speech related research (Clayards, Tanenhaus, Aslin, \& Jacobs,
+2008; Feldman, Griffiths, \& Morgan, 2009; Kleinschmidt \& Jaeger, 2015;
 Norris \& McQueen, 2008), but also on many other disciplines in the
 cognitive sciences (for reviews, see Chater \& Manning, 2006; Knill \&
-Pouget, 2004; Tenenbaum, Kemp, Griffiths, \& Goodman, 2011). In
-particular, using this research strategy, Clayards et al. (2008)
-simulated auditory uncertainty by manipulating the probability
-distribution of a cue (VOT) that differentiated similar words (e.g.,
-\enquote{beach} and \enquote{peach}). They found that humans were
-sensitive to these probabilistic cues and their judgments closely
-reflected the optimal predictions. In another work, Feldman et al.
-(2009) studied the perceptual magnet effect, which is a phenomenon that
-involves reduced discriminability near prototypical sounds in the native
-language (Kuhl, 1991). They showed that this effect can be explained as
-the consequence of optimally solving the problem of perception under
-uncertainty. Both Clayards et al. (2008) and Feldman et al. (2009)
-explored optimal performance under uncertainty in the auditory modality.
-There is, however, extensive evidence that information from the visual
-modality, such as the speaker's facial features, also influences speech
-understanding (see Campbell, 2008 for a review). Bejjanki, Clayards,
-Knill, and Aslin (2011) offered a mathematical characterization of how
-probabilistic cues from speech and lip movements can be optimally
-combined. They showed that human performance during audio-visual
-phonemic labeling was consistent (at least at the qualitative level)
-with the behavior of the ideal observer.
-
-This previous research, however, did not systematically study speech
+Pouget, 2004; Tenenbaum, Kemp, Griffiths, \& Goodman, 2011)
+
+Some of these ideal-observer-based studies are closely related to the
+question we are addressing in the current work. For instance, Clayards
+et al. (2008) simulated auditory uncertainty by manipulating the
+probability distribution of a cue (Voice Onset Time) that differentiated
+similar words (e.g., \enquote{beach} and \enquote{peach}). They found
+that humans were sensitive to these probabilistic cues and their
+judgments closely reflected the optimal predictions. In another work,
+Feldman et al. (2009) studied the perceptual magnet effect, which is a
+phenomenon that involves reduced discriminability near prototypical
+sounds in the native language (Kuhl, 1991). They showed that this effect
+can be explained as the consequence of optimally solving the problem of
+perception under uncertainty.
+
+Besides the acoustic cues explored in Clayards et al. (2008) and Feldman
+et al. (2009), there is extensive evidence that information from the
+visual modality, such as the speaker's facial features, also influences
+speech understanding (see Campbell, 2008 for a review). Bejjanki,
+Clayards, Knill, and Aslin (2011) offered a mathematical
+characterization of how probabilistic cues from speech and lip movements
+can be optimally combined. They showed that human performance during
+audio-visual phonemic labeling was consistent (at least at the
+qualitative level) with the behavior of the ideal observer. This
+previous research, however, did not systematically study speech
 understanding when the visual information is obtained, not through the
-speaker's facial features, but through the referential context. In fact,
-experimental findings showed that information about the identity of the
-semantic referent can be integrated with linguistic information to
-resolve lexical and syntactic ambiguities in speech (e.g., Eberhard,
-Spivey-Knowlton, Sedivy, \& Tanenhaus, 1995; Spivey, Tanenhaus,
-Eberhard, \& Sedivy, 2002; Tanenhaus, Spivey-Knowlton, Eberhard, \&
-Sedivy, 1995). To our knowledge, however, no study offered an ideal
-observer analysis of word identification in such context, that is, when
-the listener has to combine cues from the sound and the referent.
-Imagine, for example, that someone is uncertain whether they heard
-\enquote{pea} or \enquote{bee}, does this uncertainty make them rely
-more on the referent (e.g., the object being pointed at)? Vice versa, if
-they are not sure if they saw a bee or a fly, does it make them rely
-more on the sound? More importantly, when input in both modalities is
-uncertain to varying degrees, do they weight each modality according to
-its relative reliability (which is the optimal strategy), or do they
-over-rely on a particular modality (which is a sub-optimal strategy)?
+speaker's facial features---as in audio-visual speech perception, but
+through the referential context. In fact, experimental findings showed
+that information about the identity of the semantic referent can be
+integrated with linguistic information to resolve lexical and syntactic
+ambiguities in speech (e.g., Eberhard, Spivey-Knowlton, Sedivy, \&
+Tanenhaus, 1995; Spivey, Tanenhaus, Eberhard, \& Sedivy, 2002;
+Tanenhaus, Spivey-Knowlton, Eberhard, \& Sedivy, 1995). To our
+knowledge, however, no study offered an ideal observer analysis of word
+identification in such context, that is, when the listener has to
+combine cues from the sound and the referent.
 
@@
 differences between these two cases, and both can influence the way the
-auditory and visual cues are combined:
-
-\noindent First, in the case of audio-visual speech, both modalities
-offer information about the same underlying speech category. They may
-differ only in terms of their informational reliability. In a
-referential context, however, the auditory and visual modalities are
-additionally different in terms of the roles they play in the
-referential process: the auditory input represents the \emph{symbol}
+auditory and visual cues are combined: First, in the case of
+audio-visual speech, both modalities offer information about the same
+underlying speech category. They may differ only in terms of their
+informational reliability. In a referential context, however, the
+auditory and visual modalities play different roles in the referential
+process---in addition to possible differences in informational
+reliability. Indeed, the auditory input represents the \emph{symbol}
 whereas the visual input represents the \emph{meaning}. It has been
@@
   Markow, 1995), others suggest that speech might \emph{not} have a
-  referential status from the start. Rather, speech might be prefered by
-  children only because of a low level auditory ``overshadowing'' (e.g.,
-  Sloutsky \& Napolitano, 2003).} Thus, in a referential context, it is
-possible that listeners do not treat the auditory and visual modalities
-as equivalent sources of information. Instead, there could be a
-sub-optimal bias for the auditory modality beyond what is expected from
-informational reliability alone.
-
-\noindent Second in the case of audio-visual speech, the auditory and
-visual stimuli are expected to be perceptually correlated. The
-expectation for this correlation is such that when there is a mismatch
-between the auditory and visual input, people still integrate them into
-a unified (but illusory) percept (McGurk \& MacDonald, 1976). In the
-case of referential language, however, the multimodal association is by
-nature \emph{arbitrary} (Greenberg, 1957; Saussure, 1916). For instance,
-there is no logical/perceptual connection between the sound
-\enquote{bee} and the corresponding insect. Moreover, variation in the
-way the sound \enquote{bee} is pronounced is generally not expected to
-correlate perceptually with variation in the shape (or any other visual
-property) in the category of bees. In sum, cue combination in the case
-of arbitrary audio-visual associations (word-referent) is likely to be
-less automatic, more effortful, and therefore less conducive to optimal
+  referential status from the start. Rather, speech might be preferred
+  by children only because of a low level auditory ``overshadowing''
+  (e.g., Sloutsky \& Napolitano, 2003).} Thus, in a referential context,
+it is possible that listeners do not treat the auditory and visual
+modalities as equivalent sources of information. Instead, there could be
+a sub-optimal bias for the auditory modality beyond what is expected
+from informational reliability alone.
+
+Second, in the case of audio-visual speech, the auditory and visual
+stimuli are expected to be perceptually correlated. The expectation for
+this correlation is such that when there is a mismatch between the
+auditory and visual input, people still integrate them into a unified
+(but illusory) percept (McGurk \& MacDonald, 1976). In the case of
+referential language, however, the multimodal association is by nature
+\emph{arbitrary} (Greenberg, 1957; Saussure, 1916). For instance, there
+is no logical/perceptual connection between the sound \enquote{bee} and
+the corresponding insect. Moreover, variation in the way the sound
+\enquote{bee} is pronounced is generally not expected to correlate
+perceptually with variation in the shape (or any other visual property)
+in the category of bees. In sum, cue combination in the case of
+arbitrary audio-visual associations (word-referent) is likely to be less
+automatic, more effortful, and therefore less conducive to optimal
 integration than it is in the case of perceptually correlated
@@
 
-In the current study, we investigate how people combine cues from the
-auditory and the visual modality to recognize words in a referential
-context. In particular, we study how this combination is performed under
-various degrees of uncertainty in both the auditory and the visual
-modality. We perform a rational analysis of the task. First we propose
-an ideal observer model that performs the combination in an optimal
-fashion. Second we compare the predictions of the optimal model to human
+\subsection{The current study}\label{the-current-study}
+
+We investigate how people combine cues from the auditory and the visual
+modality to recognize words in a referential context. In particular, we
+study how this combination is performed under various degrees of
+uncertainty in both the auditory and the visual modality. Imagine, for
+example, that someone is uncertain whether they heard \enquote{pea} or
+\enquote{bee}, does this uncertainty make them rely more on the referent
+(e.g., the object being pointed at)? Vice versa, if they are not sure if
+they saw a bee or a fly, does it make them rely more on the sound? More
+importantly, when input in both modalities is uncertain to varying
+degrees, do they weight each modality according to its relative
+reliability (which is the optimal strategy), or do they over-rely on a
+particular modality (which is a sub-optimal strategy)?
+
+We perform a rational analysis of the task. First we propose an ideal
+observer model that performs the combination in an optimal fashion.
+Second we compare the predictions of the optimal model to human
 responses. Humans can deviate from the ideal for several reasons. For
@@
 Banks, 2002)---which typically studies continuous stimuli (e.g., size,
-location)---this probabilistic information in our case cannot be
-characterized with \emph{sensory noise/variability}, only. Indeed, our
-task involves responses over categorical variables (phonemes and
-concepts), and therefore, the optimal model in our case should take into
-account, not only the noise variability around an individual perceptual
-estimate, but also its \emph{categorical variability}, i.e., the
-uncertainty related to whether this perceptual estimate belongs to a
-given category (see also Bankieris, Bejjanki, \& Aslin, 2017; Bejjanki
-et al., 2011). In what follows, we describe a model that accounts for
-both type of variability. First, we describe the model in the simplified
-case of categorical variability only. Second, we augment this simplified
-model to account for sensory noise.
+location)---the probabilistic information in our case cannot be
+characterized with \emph{sensory noise}, only. Indeed, our task involves
+responses over categorical variables (phonemes and concepts), and
+therefore, the optimal model should take into account, not only the
+noise variability around an individual perceptual estimate, but also its
+\emph{categorical variability}, i.e., the uncertainty related to whether
+this perceptual estimate belongs to a given category (see also
+Bankieris, Bejjanki, \& Aslin, 2017; Bejjanki et al., 2011). In what
+follows, we describe a model that accounts for both type of variability.
+First, we describe the model in the simplified case of categorical
+variability only. Second, we augment this simplified model to account
+for sensory noise.
 
@@
 
-\noindent This assumption simply says that, given a word-object mapping,
-e.g., \(W=\)(\enquote{cat}-CAT), variation in the way \enquote{cat} is
+\noindent This assumption says that, given a word-object mapping, e.g.,
+\(W=\)(\enquote{cat}-CAT), variation in the way \enquote{cat} is
 pronounced does not correlate with changes in any visual property of the
@@
 \(a=a_t\)), and that all uncertainty is about the category membership of
-this token. However, we might also want to account for noise in the
-brain and/or in the environment. For example, the observer might not
-have access to the exact produced target, but only to the target
-perturbed by noise. If we assume this noise to be normally distributed,
-that is, \(p(a | a_t) \sim N(a_t, \sigma^2_{N_A})\), then integrating
-over \(a_t\) leads to the following simple expression:
+this token. However, we might also want to account for internal noise in
+the brain and/or external noise in the environment. For example, the
+observer might not have access to the exact produced target, but only to
+the target perturbed by noise. If we assume this noise to be normally
+distributed, that is, \(p(a | a_t) \sim N(a_t, \sigma^2_{N_A})\), then
+integrating over \(a_t\) leads to the following simple expression:
 \[ p(a | A) \sim N(\mu_{A}, \sigma^2_{A}+\sigma^2_{N_A})\] Similarly, in
@@
 bimodal condition will not be different from their response in either
-the visual-only or the auditory-only condition. If, as we expect, the
+the visual-only or the auditory-only condition. However, if the
 participants rely on both the auditory and the visual modalities to make
@@
 Experiment 1, we studied the case where bimodal uncertainty was due to
-ambiguity in terms of category membership, without any additional
-background noise. In Experiment 2 and 3 we added background noise on top
-of ambiguity in category membership.
+categorical variability, only. In Experiment 2 and 3 we added noise in
+the background on top of categorical variability.
 
@@
 
-In this Experiment, we start with testing the predictions in the case
+In this Experiment, we test the predictions of the model in the case
 where uncertainty is due to categorical variability only (i.e.,
-ambiguity in terms of category memebership). We do not add any external
+ambiguity in terms of category membership). We do not add any external
 noise to the background and we assume that internal sensory noise is
@@
 The visual and auditory baselines as well as the optimal model are not
-fit to bimodal data, but their predictions are tested against these
+fit to the bimodal data, but their predictions are tested against these
 bimodal data. All these normative models use the variances derived from
-the unimodal data and the bias term derived from the bimodal data.
+the unimodal data and the bias term derived from the fit to bimodal
+data.
 
@@
 all participants. That being said, the distribution of responses from
-individual participants will also be studied. The fit was done with a
+individual participants will also be analyzed. The fit was done with a
 nonlinear least squares regression using the NLS package in R (Bates \&
@@
 possibility, we cross-validated the model using half the responses to
-predict the other half (averaging across 1000 random partitions). The
+predict the other half (averaging across 10 random partitions). The
 predictive power of the model remained very high (\(r^2\)=0.93).
@@
 from the optimal prediction in that they were slightly pulled toward
-chance (i.e., the probability 0.5). This is due to the increase in the
-value of the variance associated with each modality. Note however that,
-despite this increase in randomness, our analysis of modality preference
-showed that the relative values of these variances were not different
-(Figure~\ref{fig:bias}), meaning that there was no evidence for a
-modality preference. Thus, 1) There was a simultaneous increase in the
-values of the auditory and visual variances in the bimodal condition
+chance (i.e., the probability 0.5). This fact is due to the increase in
+the value of the variance associated with each modality. Note however
+that, despite this increase in randomness, our analysis of modality
+preference showed that the relative values of these variances were not
+different (Figure~\ref{fig:bias}), meaning that there was no evidence
+for a modality preference. Thus, 1) There was a simultaneous increase in
+the values of the auditory and visual variances in the bimodal condition
 compared to the unimodal condition, meaning that the bimodal input lead
@@
 \begin{figure}[!h]
-\includegraphics[width=\textwidth]{ms_files/figure-latex/individual-1} \caption{Histograms of the values of the visual variance relative to the auditory variance in Experiment 1.
-Light color represents the values derived from each individual participant, and dark color represents simulated data sampled from the descriptive model.}\label{fig:individual}
+\includegraphics[width=\textwidth]{ms_files/figure-latex/individual-1} \caption{Histograms of the individual values of the visual variance relative to the auditory variance in Experiment 1.
+Light color represents the values derived from each individual participant, and dark color represents simulated individual responses sampled from the descriptive model.}\label{fig:individual}
 \end{figure}
@@
 exclusively on the auditory modality. This case could still lead to an
-aggregate behaviour which appears optimal, but this optimality would be
+aggregate behavior which appears optimal, but this optimality would be
 spurious.
@@
 modality. The percentage of both cases was relatively small compared to
-the total number of participants (21.25\%). An additional number of
-participants (N=7) relied on both modalities, but provided noisy
-responses which lead to negative variances (probably due to mistaking
-\enquote{same} for \enquote{different} or vice versa). When these
-outliers were removed, the distribution had a rather unimodal shape
+the total number of participants (21.25\%). When these outliers were
+removed, the distribution had a rather unimodal shape
 (Figure~\ref{fig:individual}). This finding indicates that the
@@
 ease of comparison, the simulated distribution was superimposed to the
-real distribution. We found that the real distribution was broader
-(\(sd=\) 2.24) than the simulated distribution (\(sd=\) 1.19),
-indicating that there was a real between-subject variation beyond
-sampling errors. This means that the participants varied in terms of how
-they weighted modalities: Compared to the predictions of the global
-descriptive model, some participants relied more on the auditory
-modality, whereas others relied more on the visual modality.
+real distribution. We found that the real distribution had a standard
+deviation of \(sd=\) 2.24 which was larger than that of the simulated
+distribution (\(sd=\) 1.16), indicating that there was real
+between-subject variation beyond sampling errors. This finding means
+that the participants varied in terms of how they weighted modalities:
+Compared to the predictions of the population-level model, some
+participants relied more on the auditory modality, whereas others relied
+more on the visual modality.
 
@@
 auditory modality prompted more participants to rely exclusively and
-disproportionately on the visual modality.
+disproportionately on the visual modality (see Table
+\ref{tab:exclusive}).
 
@@
 \[\beta_v \propto \frac{1}{\sigma^2_{V}+\sigma^2_{N_V}}.\] The
-alternative hypothesis is that, just like noise in the auditory modality
-lead to a preference for the visual input in Experiment 2, noise in the
-visual modality would lead to a preference for the auditory input.
+alternative hypothesis is that noise in the visual modality would lead
+to a preference for the auditory input, just like noise in the auditory
+modality lead to a preference for the visual input in Experiment 2.
 
@@
 \includegraphics[width=\textwidth]{ms_files/figure-latex/bias-1} \caption{Modality preference is characterized as a deviation from the optimal decision threshold.
-A) The decision thresholds of both the optimal and the descriptive models (solid red and black lines respectively).
+A) The decision thresholds of both the optimal and the descriptive models (solid red and black lines, respectively).
 Deviation from optimality is compared to two hypothetical cases of modality preference.
-In these cases, deviation from  optimality is due to over-lying on the visual or the auditory input (green and blue dotted lines, respectively) by a factor of 2.
+In these cases, deviation from  optimality is due to over-lying on the visual or the auditory input by a factor of 2 (green and blue dotted lines, respectively).
 B) The value of the decision threshold's slope derived from the descriptive model relative to that of the optimal model.
@@
 categorically and with less certainty than the auditory stimuli. This
-made it more likely for the visual categorization function to become
-flat and uninformative after a few drops in precision due to noise on
-the one had, and to the additional randomness induced by the bimodal
-presentation on the other hand.
+fact made it more likely for the visual categorization function to
+become flat and uninformative after a few drops in precision due to
+noise on the one had, and to the additional randomness induced by the
+bimodal presentation on the other hand.
 
@@
 
-In all Experiments, we found many patterns of optimal behaviour.
+In all Experiments, we found many patterns of optimal behavior.
 Quantitatively speaking, the optimal model accounted, respectively, for
@@
 Experiments, the variance associated with each modality increased in the
-bimodal condition compared to the unimodal conditions. This means that
-participants responded slightly more randomly in the bimodal condition
-than they did in the unimodal conditions. This finding contrasts with
-research on multisensory integration where associations tend to lead to
-a higher precision (e.g., Ernst \& Banks, 2002). Nevertheless, there is
-a crucial difference between these two situations (besides the obvious
-difference in terms of the models used). Research on multisensory
-integration (of which audio-visual speech is arguably an instance) deals
-with redundant multimodal cues, and these cues are integrated into a
-unified percept. In contrast, the word-referent association is usually
-arbitrary and, in particular, the cues are not expected to be correlated
-perceptually. Therefore the observer cannot form a unified percept,
-rather, it must encode information separately from both modalities and
-retain this encoding through the decision making process. Retaining two
-separate cues at the same time instead of forming one unified percept
-(as in multisensory integration of redundant cues), or instead of
-retaining only one cue (as in the unimodal case), is likely to place
-extra-demand on cognitive resources, which, in turn, can cause general
-performance to drop. Indeed, there is evidence that cognitive load has a
-detrimental effect on word recognition. This phenomenon can be due to a
-reduction in perceptual acuity (e.g., Mattys \& Wiget, 2011).
+bimodal condition compared to the unimodal conditions. This fact means
+that participants responded slightly more randomly in the bimodal
+condition than they did in the unimodal conditions. This finding
+contrasts with research on multisensory integration where associations
+tend to lead to a higher precision (e.g., Ernst \& Banks, 2002).
+Nevertheless, there is a crucial difference between these two situations
+(besides the obvious difference in terms of the models used). Research
+on multisensory integration (of which audio-visual speech is arguably an
+instance) deals with redundant multimodal cues, and these cues are
+integrated into a unified percept. In contrast, the word-referent
+association is usually arbitrary and, in particular, the cues are not
+expected to be correlated perceptually. Therefore the observer cannot
+form a unified percept, rather, it must encode information separately
+from both modalities and retain this encoding through the decision
+making process. Retaining two separate cues at the same time instead of
+forming one unified percept (as in multisensory integration of redundant
+cues), or instead of retaining only one cue (as in the unimodal case),
+is likely to place extra-demand on cognitive resources, which, in turn,
+can cause general performance to drop. Indeed, there is evidence that
+cognitive load has a detrimental effect on word recognition. This
+phenomenon can be due to a reduction in perceptual acuity (e.g., Mattys
+\& Wiget, 2011).
 
@@
 and Levy (2017) provided a probabilistic model of this phenomenon. In
-agreement with the finding in the current study, Hofer and Levy (2017)
-characterized the apparent reduction in perceptual acuity as an increase
-in the noise variance of the auditory modality. Our finding, besides
-providing more evidence to this documented fact, suggests that the
-reduction in perceptual acuity may occurs simultaneously in both the
-auditory \emph{and} the visual modalities.
+agreement with the method and finding in the current study, Hofer and
+Levy (2017) characterized the apparent reduction in perceptual acuity as
+an increase in the noise variance of the auditory modality. Our finding,
+besides providing more evidence to this documented fact, suggests that
+the apparent reduction in perceptual acuity may occurs simultaneously in
+both the auditory \emph{and} the visual modalities.
 
@@
 The formal approach followed in this paper allowed us to tease apart
-these two possibilities, and the analysis supports the sub-optimal
+these two possibilities, and our analysis supports the sub-optimal
 compensatory strategy: The preference for the non-noisy modality is
@@
 languages and found that words that are similar phonologically tend to
-be similar semantically as well, beyond what could be explained by
-chance. These studies suggest that the case of double uncertainty,
-though perhaps not pervasive, could be a real issue in language as it
-increase the probability of confusability for many
-words.\linebreak Besides the case of double ambiguity intrinsic to
-language, there are two situations where our mechanism might play a
-significant role. The first is when ambiguity in both the form and/or
-the referent is induced by an external noisy context even when these
-forms and referents are not confusable in normal situations. The second
-case is that of early word learning, and we will discuss this case in
-more detail in what follows.
+be similar semantically as well. These studies suggest that the case of
+double uncertainty, though perhaps not pervasive, could be a real issue
+in language as it increase the probability of confusability for many
+words.\linebreak That being said, besides the case of double ambiguity
+intrinsic to language, there are two situations where our mechanism
+might play a significant role. The first is when ambiguity in both the
+form and/or the referent is induced by an external noisy context even
+when these forms and referents are not confusable in normal situations.
+The second case is that of early word recognition/learning, and we will
+discuss this case in more detail in what follows.
 
@@
 early representation with new features, and revise its extension in the
-light of new referential exposures.
-
-Thus, uncertainty in the representation associated with one modality
-(e.g., a bee and a fly) can be mitigated through the possibly more
-differentiated representations associated with the other modality (e.g.,
-the sound \enquote{bee} is acoustically different from the sound
-\enquote{fly}). That being said, a multi-modal cue combination strategy
-might help children not only recognize an individual word instance, but
-also refine the underlying phonological and semantic representations in
-the process. Previous research in early word learning has---whether
-implicitly or explicitly---largely treated the process of learning form
-and of learning meaning as independent. However, the developmental data
+light of new referential exposures. In sum, uncertainty in the
+representation associated with one modality (e.g., a bee and a fly) can
+be mitigated through the possibly more differentiated representations
+associated with the other modality (e.g., the sound \enquote{bee} is
+acoustically different from the sound \enquote{fly}).
+
+The multi-modal cue combination strategy might help children not only
+recognize an individual word instance, but also refine the underlying
+phonological and semantic representations in the process. Previous
+research in early word learning has---whether implicitly or
+explicitly---largely treated the process of learning form and of
+learning meaning as independent. However, the developmental data
 reviewed above shows that children do not wait to have completed the
@@
 laboratory conditions, as in more naturalistic settings where they have
-to deal with various levels of variability. However an answer to this
-question is likely to involve a multifaceted research approach,
+to deal with various levels of variability. An answer to this question
+is likely to involve a multifaceted research approach,
 involving---besides laboratory experiments---analyses of corpora with a
@@
 
+\vspace{1em}
+
+\fbox{\parbox[b][][c]{14cm}{\centering All data and code for these analyses are available at\ \url{https://github.com/afourtassi/WordRec}}}
+\vspace{1em}
+
 \section{Appendix 1: derivation of the posterior (Equation
@@
 \[\beta_v=\frac{\mu_{V1}-\mu_{V2}}{\sigma^2_{V}}.\]
+
+\section{Acknowledgements}\label{acknowledgements}
+
+This work was supported by a post-doctoral grant from the Fyssen
+Foundation + XXX
 
@@
 
+\hypertarget{ref-medina2011}{}
+Medina, T., Snedeker, J., Trueswell, J., \& Gleitman, L. (2011). How
+words can and cannot be learned by observation. \emph{Proceedings of the
+National Academy of Sciences}, \emph{108}(22), 9014.
+
 \hypertarget{ref-Merriman91}{}
@@
 
+\hypertarget{ref-pinker1989}{}
+Pinker, S. (1989). \emph{Learnability and cognition: The acquisition of
+argument structure}. Cambridge, MA: MIT press.
+
 \hypertarget{ref-rahnev2018}{}
@@
 Development}, \emph{74}.
+
+\hypertarget{ref-smith08}{}
+Smith, L. B., \& Yu, C. (2008). Infants rapidly learn word-referent
+mappings via cross-situational statistics. \emph{Cognition},
+\emph{106}(3), 1558--1568.
 
@@
 
+\hypertarget{ref-suanda2014}{}
+Suanda, S. H., Mugwanya, N., \& Namy, L. L. (2014). Cross-situational
+statistical word learning in young children. \emph{Journal of
+Experimental Child Psychology}, \emph{126}.
+
 \hypertarget{ref-Swingley2007}{}
@@
 \emph{331}(11 March 2011), 1279--1285.
+
+\hypertarget{ref-vlach2013}{}
+Vlach, H. A., \& Johnson, S. P. (2013). Memory constraints on infants'
+cross-situational statistical learning. \emph{Cognition}, \emph{127}.
+
+\hypertarget{ref-vouloumanos2008}{}
+Vouloumanos, A. (2008). Fine-grained sensitivity to statistical
+information in adult word learning. \emph{Cognition}, \emph{107}(2),
+729--742.
 
@@
 
+\hypertarget{ref-yurovsky2015}{}
+Yurovsky, D., \& Frank, M. C. (2015). An Integrative Account of
+Constraints on Cross-Situational Learning. \emph{Cognition}, \emph{145}.
+
 \end{document}

### 2018-04-20 Writeup/ms.Rmd
minor

@@
 In agreement with the method and finding in the current study, @hofer2017 characterized the apparent reduction in perceptual acuity as an increase in the noise variance of the auditory modality.
-Our finding, besides providing more evidence to this documented fact, suggests that the apparent reduction in perceptual acuity may occurs simultaneously in both the auditory *and* the visual modalities.
+Our finding, besides providing more evidence to this documented fact, suggests that the  reduction in perceptual acuity may occurs simultaneously in both the auditory *and* the visual modalities.
 

### 2018-04-26 Writeup/ms copy.Rmd
modif ms

@@
 library(ggthemes)
-#theme_set(theme_few())
 library(broom)
+library(nlme)
+library(brms)
 #library("knitcitations")
@@
 ```{r}
-summarise <- dplyr::summarise
-rename <- dplyr::rename
+b <- c(2, 0.75)
+x <- rnorm(100)
+y <- rnorm(100, mean = b[1] * exp(b[2] * x))
+dat1 <- data.frame(x, y)
+
+prior1 <- prior(normal(1, 2), nlpar = "b1") +
+  prior(normal(0, 2), nlpar = "b2")
+fit1 <- brm(bf(y ~ b1 * exp(b2 * x), b1 + b2 ~ 1, nl = TRUE),
+            data = dat1, prior = prior1)
 ```
@@
 For simplicity, we focus on audio-visual matching here.} Perhaps the insect was a beetle or a fly instead.
-
-How does the listener deal with uncertainty to identify the speaker's intended word?
+How does the listener deal with such multimodal uncertainty to recognize the speaker's intended word?
+
+The task of matching the sound to the corresponding visual object has been extensively studied in the developmental literature since it is considered to be an crucial instance of early word learning.
+For example, many studies focused on how children succeed in this task despite high referential ambiguity [@smith08; @pinker1989; @medina2011; @vouloumanos2008; @yurovsky2015; @suanda2014; @vlach2013].
+However, even when they know the exact meanings of the words, listeners (both children and adults) often face the task of recognizing which word the speaker has uttered, especially under noisy circumstances.
+The purpose of the current study is to explore the special case of word recognition under uncertainty when adult observers have access to multimodal cues from the speech and the referent.
+
 One rigorous way to approach this question is through conducting an *ideal observer* analysis.
-This research strategy provides a characterization of the task/goal and shows what the optimal performance should be under this characterization.\footnote{This strategy is, thus, a general instance of the rational approach to cognition [@anderson90], as well as Marr's computational level of analysis.} When there is uncertainty in the input, the ideal observer performs an optimal probabilistic inference.
+This research strategy provides a characterization of the task/goal and shows what the optimal performance should be under this characterization.^[It is, thus, a general instance of the rational approach to cognition [@anderson90].
+It can also be seen as an instance of Marr's computational level of analysis.] When there is uncertainty in the input, the ideal observer performs an optimal probabilistic inference.
 For example, in order to recognize an ambiguous linguistic input, the model uses all available probabilistic knowledge in order to maximize the accuracy of this recognition.
-Thus, when the task is well specified, the ideal observer model can be seen as a theoretical upper limit on performance.
-It is often used, not so much as a realistic model of human performance, as much as a baseline against which human performance can be compared [@Geisler2003].
-When there is a deviation from the ideal, this can reveal extra constraints on human cognition, such as limitations on working memory or attentional resources (see Rahnev and Denison, 2018 for further discussion).
-
-The ideal observer analysis has had a tremendous impact not only on speech related research [@Norris08; @clayard08; @feldman2009; @kleinschmidt2015], but also on many other disciplines in the cognitive sciences [for reviews, see @chater06; @Knill04; @tenenbaum11].
-In particular, using this research strategy, @clayard08 simulated auditory uncertainty by manipulating the probability distribution of a cue (VOT) that differentiated similar words (e.g., "beach" and "peach").
+The ideal observer model can be seen as a theoretical upper limit on performance.
+It is not so much a realistic model of human performance, as much as a baseline against which human performance can be compared [@Geisler2003; @rahnev2018].
+When there is a deviation from the ideal, it can reveal extra constraints on human cognition, such as limitations on the working memory or attentional resources.
+The ideal observer analysis has had a tremendous impact not only on speech related research [@Norris08; @clayard08; @feldman2009; @kleinschmidt2015], but also on many other disciplines in the cognitive sciences [for reviews, see @chater06; @Knill04; @tenenbaum11]
+
+Some of these ideal-observer-based studies are closely related to the question we are addressing in the current work.
+For instance, @clayard08 simulated auditory uncertainty by manipulating the probability distribution of a cue (Voice Onset Time) that differentiated similar words (e.g., "beach" and "peach").
 They found that humans were sensitive to these probabilistic cues and their judgments closely reflected the optimal predictions.
-In another work, @feldman2009 studied the perceptual magnet effect, which is a phenomenon that involves reduced discriminability near prototypical sounds in the native language (Kuhl, 1991).
+In another work, @feldman2009 studied the perceptual magnet effect, which is a phenomenon that involves reduced discriminability near prototypical sounds in the native language [@kuhl1991].
 They showed that this effect can be explained as the consequence of optimally solving the problem of perception under uncertainty.
-Both @clayard08 and @feldman2009 explored optimal performance under uncertainty in the auditory modality.
-There is, however, extensive evidence that information from the visual modality, such as the speaker's facial features,  also influences speech understanding [see @Campbell2008 for a review].
-@bejjanki2011 offered a mathematical characterization of how cues from speech and lip movements can be optimally combined and showed that human performance during audio-visual phonemic labeling was consistent (at least at the qualitative level) with the behavior of the ideal observer.
-
-This previous reseach, however, did not systematically study speech inderstanding when the visual information is obtained, not through the speaker's facial features, but through the referential context.
+
+Besides the acoustic cues explored in @clayard08 and @feldman2009, there is extensive evidence that information from the visual modality, such as the speaker's facial features,  also influences speech understanding [see @Campbell2008 for a review].
+@bejjanki2011 offered a mathematical characterization of how probabilistic cues from speech and lip movements can be optimally combined.
+They showed that human performance during audio-visual phonemic labeling was consistent (at least at the qualitative level) with the behavior of the ideal observer.
+This previous research, however, did not systematically study speech understanding when the visual information is obtained, not through the speaker's facial features---as in audio-visual speech perception, but through the referential context.
 In fact, experimental findings showed that information about the identity of the semantic referent can be integrated with linguistic information to resolve lexical and syntactic ambiguities in speech [e.g., @Eberhard1995; @Tanenhaus1995; @spivey2002].
 To our knowledge, however, no study offered an ideal observer analysis of word identification in such context, that is, when the listener has to combine cues from the sound and the referent.
-Imagine, for example, that someone is uncertain whether they heard "pea" or "bee", does this uncertainty make them rely more on the referent (e.g., the object being pointed at)?
-Vice versa, if they are not sure if they saw a bee or a fly, does it make them rely more on the sound?
-More importantly, when input in both modalities is uncertain to varying degrees, do they weight each modality according to its relative reliability (which is the optimal strategy), or do they over-rely on a particular modality (which is a sub-optimal strategy)?
 
 On the face of it, the question of combining information from the sound and the visual referent might seem similar to that of audio-visual speech integration.
-Nevertheless, there are at least two fundamental differences between these two cases, and both can influence the way the auditory and visual cues are integrated.
-First, in the case of audio-visual speech, modalities may difffer only in terms of their informational reliability.
-In a referential context, however, modalities also differ in terms of their roles in the referential process: the auditory input represents the *symbol* whereas the visual input represents the *meaning*.
-It has been suggested that because of its referential property, speech is a privileged signal for humans, starting in infancy [see @vouloumanos2014 for a review].\footnote{There is a debate as to whether speech is privileged for infant and adults for the same reasons.
-Whereas some researchers suggest that speech is privileged for both infants and adults because of its ability to refer (Waxman et al.
-XX), others suggest that speech might not have a referential status from the start.
-Rather, speech might be prefered by infants only because of a low level auditory "overshadowing" (Sloutsky et al.
-XX).} Thus, in a referential context, it is possible that listeners do not treat the auditory and visual modalities as equivalent sources of information.
+Nevertheless, there are at least two fundamental differences between these two cases, and both can influence the way the auditory and visual cues are combined: First, in the case of audio-visual speech, both modalities offer information about the same underlying speech category.
+They may differ only in terms of their informational reliability.
+In a referential context, however, the auditory and visual modalities play different roles in the referential process---in addition to possible differences in informational reliability.
+Indeed, the auditory input represents the *symbol* whereas the visual input represents the *meaning*.
+It has been suggested that because of its referential property, speech is a privileged signal for humans, starting in infancy [see @vouloumanos2014 for a review].^[There is a debate as to whether speech is privileged for children and adults for the same reasons.
+Whereas some researchers suggest that speech is privileged for both children and adults because of its ability to refer [e.g., @waxman1995], others suggest that speech might *not* have a referential status from the start.
+Rather, speech might be preferred by children only because of a low level auditory ``overshadowing'' [e.g., @sloutsky2003].] Thus, in a referential context, it is possible that listeners do not treat the auditory and visual modalities as equivalent sources of information.
 Instead, there could be a sub-optimal bias for the auditory modality beyond what is expected from informational reliability alone.
 
-<!--An example of such integration is when we determine the size of an object using the visual and haptic modalities [@ernst02], or when we determine the spacial location of a stimulus using the visual and the auditory modalities [@alais04] -->
 Second, in the case of audio-visual speech, the auditory and visual stimuli are expected to be perceptually correlated.
@@
 
-<!--We do not perform the ideal observer analysis at the individual level, but at the population level.
-There might be some individual variation, but this study addresses the overall performance in the population as a whole.-->
-
 We tested the ideal observer model's predictions in three behavioral experiments where we varied the source of uncertainty.
@@
 In all experiments, participants were quantitatively near-optimal, though overall response precision was slightly lower than expected.
-Moreover, in Experiment 1 where neither of the modalities was perturbed with background noise, participants weighed auditory and visual cues according to the relative reliability predicted by the optimal model.
+Moreover, in Experiment 1 where neither of the modalities was perturbed with background noise, participants weighted auditory and visual cues according to the relative reliability predicted by the optimal model.
 In other words, we found no evidence for a modality bias towards either the auditory or the visual modality.
 However, in Experiment 2 and 3, participants over-relied on one modality when the other modality was perturbed with additional noise.
-<!-- In the discussion, we talk about the broad implications of these results and especially in relation to some developmental findings in early word learning [e.g., @stager1997].
--->
-
-<!--The nature of the multi-modal associations (redundant vs.
-arbitrary) influences the quality of multi-modal processing in both children and adults: the processing and integration is easier in the case of redundant input, than it in the case of arbitrary input [see @robinson2010 for a review].
-Thus, there is a priori no obvious reason multimodal cue combination in the case of arbitrary assoiations (such as the case of word-referent) should be optimal in the same way cue combination of redundant associations is.
--->
-<!--
-
-A few studies have explored some aspects of audio-visual processing in a probabilistic framework  [e.g., @bejjanki2011; @kleinschmidt2015].
-In these studies, the researchers focused on the specific case of audio-visual speech  where information is *redundant* across modalities.
-In the present work, we study the case of word reference where the audio-visual associations are usually *arbitrary* (Cite Saussure).
-For instance, whereas in the case of audio-visual speech, the sound "bee" and the corresponding lip movements are supposed to merge into a unified percept, there is nothing in the sound "bee" or in the way it can be pronounced, that correlates perceptually with the shape (or some other visual property) of the insect.
-
-More generally, we know that the nature of the multi-modal associations (redundant vs.
-arbitrary) influences the quality of the processing in both children and adults [see @robinson2010 for a review].
-In the case of redundant multimodal information (e.g.
-determining the size of an object through the visual and haptic modality), the sensory integration is often statistically optimal (Ernst and Banks, 2002).
-Optimality in this context means two things: first, the precision of the bimodal estimate increases compared to the unimodal estimates, and second, the cues from different modalities are combined according to their relative reliability.
-In the case of arbitrary associations, empirical studies suggest, rather, sub-optimality.
-In fact, processing of the bimodal input does not increase the precision, it tends to hinder performance instead (Sloutsky, Palmer, Stager, ...
-I should dig into the literature on the arbitrary associations).
-Moreover, modalities are not optimally weighted according to their reliability, instead, one modality dominates the other depending on the task, e.g., Sloutsky et al.
-reported auditory dominance (for kids) and then prefernce for adults (..), and Colovita et al.
-reported visual dominance for adults.
-
--->
-
-<!-- Outside the realm of language per se, research on multisensory integration suggests that the brain integrates information from different modalities in a statistically optimal way, that is, the integration results in a higher overall precision, and modalities are weighed according to their relative reliability [@ernst02].
-However, it is not a priori obvious whether this finding can be extended to word-referent recognition under multimodal uncertainty.
-Indeed, there seems to be at least two fundamental differences between these two cases, and both can influence the cue combination strategy.
--->
-
-# Pardigm and Models
+
+# Paradigm and Models
 
@@
 
-This paradim is adapted from a task by @sloutsky2003, in which participants are asked whether or not the two audio-visual presentations are *identical*.
-The original task has been used with both chidlren and adults to probe  audio-visual encoding [see @robinson2010 for a review].
-We are rather interested in categorization responses, i.e., determining whether or not two similar tokens are members of the same phonological/semantic category.
-Therefore, testing in our task is category-based: Participants are asked to press "same" if they think the second item (the test) belonged to the same category as the first (target) (e.g.,  dog-/aba/), even if there is a slight difference in the sound, in the referent, or in both.
-They are instructed to press "different" only if they think that the second stimulus was an instance of the other word category (cat-/ada/).
+This paradigm is adapted from a previous task [@sloutsky2003], which has been used with both children and adults to probe audio-visual encoding [see @robinson2010 for a review].
+In the testing phase of the original task, participants are asked whether or not the two audio-visual presentations are *identical*.
+In the current study, we are interested, rather, in the categorization, i.e., determining whether or not two similar tokens are members of the same phonological/semantic category.
+Therefore, testing in our task is category-based: Participants are asked to press "same" if they think the second item (the test) belongs to the same category as the first (target) (e.g.,  dog-/aba/), even if there is a slight difference in the sound, in the referent, or in both.
+They are instructed to press "different" only if they think that the second stimulus was an instance of the other category (cat-/ada/).
 The task also includes trials where pictures are hidden (audio-only) or where sounds are muted (visual-only).
 These unimodal trials provide us with the participants' evaluation of the probabilistic information present in the auditory and visual categories.
-This unimodal distributions are used as inputs to the optimal combination model, described below.
+As we shall see, these unimodal distributions are used as inputs to the optimal cue combination model.
 
@@
 We construct an ideal observer model that combines probabilistic information from the auditory and visual modalities.
-In contrast to the  model used in most research on multisensory integation [@ernst02; @alais04]---which typically studies continuous stimuli (e.g., size, location)---this probabilistic information cannot be characterized with sensory noise/variability, only.
-Indeed, our task involves repsonses over categorical variables (phonemes and concepts), and therefore, the optimal model in our case should take into account, not only the noise variability around an individual perceptual estimate, but also its *within category variability*, i.e., the uncertainty related to whether this perceptual estimate belongs to a given category [see also @Bankieris17; @bejjanki2011].
-In what follows, we describe a model that accounts for both type of varibility.
+In contrast to the  model used in most research on multisensory integration [e.g., @ernst02]---which typically studies continuous stimuli (e.g., size, location)---the probabilistic information in our case cannot be characterized with *sensory noise*, only.
+Indeed, our task involves responses over categorical variables (phonemes and concepts), and therefore, the optimal model should take into account, not only the noise variability around an individual perceptual estimate, but also its *categorical variability*, i.e., the uncertainty related to whether this perceptual estimate belongs to a given category [see also @Bankieris17; @bejjanki2011].
+In what follows, we describe a model that accounts for both type of variability.
 First, we describe the model in the simplified case of categorical variability only.
@@
 An audio-visual signal $w=(a,v)$ can be represented as a point in the audio-visual space.
-These tokens belong to bivariate distributions in this bi-dimentional sapce.
+These audio-visual tokens define bivariate distributions in the bi-dimentional space.
 We call these bivariate distributions *Word categories*, noted $W$, and are distributed as follows:
@@
 A word category is defined as the joint bivariate distribution of an auditory category (horizontal, bottom panel) and a visual semantic category (vertical, left panel).
-Upon the presentation of a word token w, participants guess whether it is sampled from the word type W1 or from the word type W2.
+Upon the presentation of a word token $w$, participants guess whether it is sampled from the word type $W_1$ or from the word type $W_2$.
 Decision threshold is where the guessing probability is 0.5."}
@@
 
-This assumption simply says that, given a word-object mapping, e.g., W=("cat"-CAT), variation in the way "cat" is pronounced does not correlate with changes in any visual property of the object CAT, which is a valid assumption.\footnote{Note that this assumptions is more adequate in the case of arbitrary associations such as ours, and less so in the case of redundant association such as audio-visual speech.
+\noindent This assumption says that, given a word-object mapping, e.g., $W=$("cat"-CAT), variation in the way "cat" is pronounced does not correlate with changes in any visual property of the object CAT, which is a valid assumption.\footnote{Note that this assumptions is more adequate in the case of arbitrary associations such as ours, and less so in the case of redundant association such as audio-visual speech.
 In the latter, variation in the pronunciation is expected to correlate, at least to some extent, with lip movements.}
 
-Now we turn to the crucial question of modeling how optimal decision should proceed given the probabilistic (categorical) information in the auditory and the visual modalities, as characterized above.
-We have two word categories: dog-/aba/ ($W_1$) and cat-/ada/ ($W_2$).\footnote{This mapping is randomized in the experiments.} When making decisons, participants can be understood as choosing one of these two word categories (Figure\ \@ref(fig:model)).
+Now we turn to the crucial question of modeling how the optimal decision should proceed given the probabilistic (categorical) information in the auditory and the visual modalities, as characterized above.
+We have two word categories: dog-/aba/ ($W_1$) and cat-/ada/ ($W_2$).\footnote{This mapping is randomized in the experiments.} When making decisions, participants can be understood as choosing one of these two word categories (Figure\ \@ref(fig:model)).
 For an ideal observer, the probability of choosing category 2 when presented with an audio-visual instance $w=(a,v)$ is the posterior probability of this category:
@@
 $$
-Using our assumption that the cues are uncorrelated, we have
+Using our assumption that the cues are uncorrelated, we have:
 $$p(w | W) = p(a,v| W) = p(a| A)p(v| V)$$
-Under this assumption, the posterior probability reduces to:\footnote{See the appendix for the details of the derivation}
+Under this assumption, the posterior probability reduces to the following formula (see Appendix 1 for the details of the derivation):
 \begin{equation}
@@
 $$\beta_a=\frac{\mu_{A1}-\mu_{A2}}{\sigma^2_{A}}$$
-$$\beta_v=\frac{\mu_{V1}-\mu_{V2}}{\sigma^2_{V}}$$
+$$\beta_v=\frac{\mu_{V1}-\mu_{V2}}{\sigma^2_{V}}.$$
 
@@
 As for the means, their values are fixed, and they correspond to the most typical tokens in our stimuli.
-Thus, observations from each modality ($a$ and $v$) are weighted according to their reliability in the posterior: $$\beta_a \propto \frac{1}{\sigma^2_{A}}$$ $$\beta_v \propto \frac{1}{\sigma^2_{V}}$$.
+Finally, observations from each modality ($a$ and $v$) are weighted in Equation 1 according to their reliability: $$\beta_a \propto \frac{1}{\sigma^2_{A}}$$ $$\beta_v \propto \frac{1}{\sigma^2_{V}}.$$
 
@@
 
- $$\beta_a \propto \frac{1}{\sigma^2_{A}+\sigma^2_{N_A}}$$ $$\beta_v \propto \frac{1}{\sigma^2_{V} +\sigma^2_{N_V}}$$
+ $$\beta_a \propto \frac{1}{\sigma^2_{A}+\sigma^2_{N_A}}$$ $$\beta_v \propto \frac{1}{\sigma^2_{V} +\sigma^2_{N_V}}.$$
 
@@
 
-The posterior (Equation 1) provides the optimal model's predictions for how probabilities that characterize uncertainty in the auditory and the viusal modalities can be combined to make categorical decisions.
-Estimates of the probability distributions in each modality are derived by fitting logistic regressions to participants' responses in the unimodal conditions, where participants only hear the sounds or only see the pictures (Figure\ \@ref(fig:task)) \footnote{Further technical detail about model fitting in the unimodal conditions will be given in the method section of Experiment 1}.
-Using these derived parameters, the optimal model makes predictions about responses in the bimodal condition where participants both hear the sounds and see the pictures.
+Equation 1 provides the optimal model's predictions for how probabilities that characterize uncertainty in the auditory and the visual modalities can be combined to make categorical decisions.
+Parameters' estimates of the probability distributions in each modality are derived by fitting unimodal posteriors to the participants' responses in the unimodal conditions, i.e., the condition where only the sounds are heard  or only the pictures are seen (Figure\ \@ref(fig:task)).\footnote{Further technical detail about model fitting in the unimodal conditions will be given in the method section of Experiment 1} Using these derived parameters, the optimal model makes predictions about responses in the bimodal condition where participants both hear the sounds and see the pictures.
 
@@
 The predictions of the optimal model will be compared to two baselines.
-The first basline is a visual model which assumes that participants rely only on visual information, and the auditory model, which assumes that participants rely only on auditory information.
-More precisely, these baseline models assumes that the participants' respones in the bimodal condition will not be different from their response in one of the unimodal conditions.
-If, as we expect, the participants rely on both the auditory and the visual modalities to make decision in the bimodal condition, the optimal model would explain more variance in human responses than the visual model alone or the auditory model alone.
-
-## Descriptive model and analysis of sub-obtimality
-
-The optimal models (as well as the auditory and visual baselines) are *normative* models.
+The first baseline is a visual model which assumes that participants rely only on visual information, and an auditory model, which assumes that participants rely only on auditory information.
+More precisely, these baseline models assume that the participants' responses in the bimodal condition will not be different from their response in either the visual-only or the auditory-only condition.
+However, if the participants rely on both the auditory and the visual modalities to make decision in the bimodal condition, the optimal model would explain more variance in human responses than the visual or the auditory model do.
+
+## Descriptive model and analysis of sub-optimality
+
+The optimal model (as well as the auditory and visual baselines) are *normative* models.
 Their predictions are made about human data in the bimodal condition, but their crucial parameters (i.e., variances associated with the visual and auditory modalities) are derived from data in the unimodal conditions.
 In addition to these normative models, we consider a *descriptive* model.
-The parameters of this model are fit to actual respnses in the bimodal condition.
+It is formally identical to the normative optimal model (Equation 1), except that the parameters are fit to actual responses in the bimodal condition.
 If the referential task induces sub-optimality (due, for instance, to the arbitrary nature of the sound-object association), then the descriptive model should explain more variance than the optimal model does.
 
-Comparison between the optimal and the descriptive models allows us, not only to quantify how much people deviate from optimality, but also to understand precisely how they deviate from this optimality.
+Comparison of the optimal and the descriptive models allows us, not only to quantify how much people deviate from optimality, but also to understand precisely the nature of this deviation.
 Let $\sigma^2_{A}$ and $\sigma^2_{V}$ be the values of the variances used in the optimal model (derived from the unimodal conditions), and $\sigma^2_{Ab}$ and $\sigma^2_{Vb}$ be the values observed through the descriptive model in the bimodal condition.
 Deviation from optimality is measured in two ways.
-First, we measure the change in the values of the variances specific to each modality, that is, how $\sigma^2_{A}$ compares to $\sigma^2_{Ab}$, and how $\sigma^2_{V}$ compares to $\sigma^2_{Vb}$.
-Second, we measure changes in the proportion of the visual and auditory variances, i.e., how $\frac{\sigma^2_{A}}{\sigma^2_{V}}$ compares to $\frac{\sigma^2_{Ab}}{\sigma^2_{Vb}}$.
-The first measure allows us to test if precision changes for each modality when we move from the unimodal to the bimodal conditions.
-The second allows us to test whether or not the weighting scheme follows the prediction of the optimal model.
-The reason we used the proportion of the variances as a measure of cross-modal weighing is because it corresponds to the slope\footnote{Or more precisely the absolute value of the slope} of the decision threshold in the audio-visual space (Figure\ \@ref(fig:model)).
+First, we measure the change in the values of the variance specific to each modality, that is, how $\sigma^2_{A}$ compares to $\sigma^2_{Ab}$, and how $\sigma^2_{V}$ compares to $\sigma^2_{Vb}$.
+Second, we measure changes in the proportion of the visual and auditory variances, i.e., we examine how $\frac{\sigma^2_{A}}{\sigma^2_{V}}$ compares to $\frac{\sigma^2_{Ab}}{\sigma^2_{Vb}}$.
+The first measure allows us to test if response precision changes for each modality when we move from the unimodal to the bimodal conditions.
+The second allows us to test the extent to which the weighting scheme follows the prediction of the optimal model.
+The reason we used the proportion of the variances as a measure of cross-modal weighting is because this proportion corresponds to the slope\footnote{Or more precisely the absolute value of the slope} of the decision threshold in the audio-visual space (Figure\ \@ref(fig:model)).
 The decision threshold is defined as the set of values in this audio-visual space along which the posterior is equal to 0.5.
-Formally speaking, the decision threshold takes the following form:
+Formally speaking, the decision threshold has the following form:
 
@@
 
-It follows that there are three possible scenarios describing how humans can deviate from optimality. These scenarios are illustrated in Figure\ \@ref(fig:subOptim) and are as follows:
+There are three possible ways human responses can deviate from optimality. These scenarios are illustrated in Figure\ \@ref(fig:subOptim), and are as follows:
 
@@
 ```{r subOptim, out.width = "\\textwidth", fig.pos = "!h", fig.cap = "Illustration using simulated data showing the example of a prediction made by the optimal model (top), and the three possible ways human participants can deviate from this prediction (bottom).
-These cases are the following: 1) The variance increases equally for both modalities, but the weighting scheme (characterized by the decision threshold) is optimal, 2) The auditory variance increases at a higher rate, leading to a preference for the auditory modality, and 3) The visual variance increases at a higher rate, leading to a preference for the visual modality"}
+These cases are the following: 1) The variance increases equally for both modalities, but the weighting scheme (characterized by the decision threshold) is optimal, 2) The auditory variance increases at a higher rate, leading to a preference for the auditory modality, and 3) The visual variance increases at a higher rate, leading to a preference for the visual modality."}
 
@@
 
-In this Experiment, we start with testing the predictions in the case where uncertainty is due to categorical variability only (i.e., ambiguity in terms of category memebership).
-We assume that sensory noise is negligible compared to categorical variability.
-Thus, we use the following cue weighing scheme:
-
-$$\beta_a \propto \frac{1}{\sigma^2_{A}}$$
-$$\beta_v \propto \frac{1}{\sigma^2_{V}}$$
+In this Experiment, we test the predictions of the model in the case where uncertainty is due to categorical variability only (i.e., ambiguity in terms of category membership).
+We do not add any external noise to the background and we assume that internal sensory noise is negligible compared to categorical variability ($\sigma^2_{A} \gg \sigma^2_{N_A}$, and $\sigma^2_{V} \gg \sigma^2_{N_V}$).
+Thus, we use the following cue weighting scheme:
+
+$$\beta_a \propto \frac{1}{\sigma^2_{A} + \sigma^2_{N_A}} \approx  \frac{1}{\sigma^2_{A} }$$
+$$\beta_v \propto \frac{1}{\sigma^2_{V} + \sigma^2_{N_V}} \approx  \frac{1}{\sigma^2_{V} }.$$
 
@@
 #############
-sound_nl1 <- nls(answer ~ 1/(1+(1-e)*exp((-4/vrA)*sound_dist+(8/vrA))), data=sound_all_exp1, start = list(e=0, vrA=2))
-
+
+#Posterior for auditory-only condition
+
+#Non-linear
+sound_nls <- nls(answer ~ 1/(1+(1-e)*exp((-4/vrA)*sound_dist+(8/vrA))),
+                 data=sound_all_exp1,
+                 start = list(e=0, vrA=2))
+
+#Non-linear mixed effect
+sound_nlme <- nlme(answer ~ 1/(1+(1-e)*exp((-4/vrA)*sound_dist+(8/vrA))),
+                 data=sound_all_exp1,
+                 fixed = list(e + vrA ~ 1),
+                 random = e+vrA ~ 1 | ID,
+                 start = list(fixed =c(e=0, vrA=2)))
+
+joint_nlme <- nlme(answer ~ 1/(1+exp((-4/vrA_j)*sound_dist+(-4/vrV_j)*concept_dist+(8/vrA_j)+(8/vrV_j))),
+                   data=joint_all_exp1,
+                   fixed = list(vrA_j + vrV_j ~ 1),
+                   random = vrA_j ~ 1 | ID,
+                   start = list(fixed =c(vrA_j=2, vrV_j=2)))
+
+#Non-linear mixed effect (Bayesian inference)
+
+prior0 <- prior(normal(2,5), nlpar = "vrA")#,
+             #set_prior("normal(0, 1)", nlpar = "e"))
+
+sound_brms <- brm(bf(answer ~ 1/(1+exp((-4/vrA)*sound_dist+(8/vrA))),
+                     vrA ~ 1, nl=T),
+                 data=sound_all_exp1,
+                 prior = prior0, 
+                 chains = 1,
+                 iter =500 )
+
+#Posterior for visual-only condition
 concept_nl1 <- nls(answer ~ 1/(1+(1-e)*exp((-4/vrV)*concept_dist+(8/vrV))), data=concept_all_exp1, start = list(e=0, vrV=2))
 
-#Here I should test the cross-validation
-
+#Posterior for audio-visual condition (this is the descriptive model)
 joint_nl1 <- nls(answer ~ 1/(1+(1-e)*exp((-4/vrA_j)*sound_dist+(-4/vrV_j)*concept_dist+(8/vrA_j)+(8/vrV_j))), data=joint_all_exp1, start = list(e=0, vrA_j=2, vrV_j=2))
@@
 
-```{r unimodal, out.width = "\\textwidth", fig.pos = "!h", fig.cap = "Human responses in the unimodal condition.
-Points represent the proportion of `different' to `same' responses in the auditory-only condition (left), and visual-only condition (right).
-Error bars are 95\\% confidence intervals.
-Solid lines represent logistic fits."}
-
-all_plot
-
-```
-
 ### Model fitting details
@@
 Since the values of the means are fixed, we have 3 free parameters: the variances for the visual and the auditory modalities, respectively, and $b$, the response bias.
-The visual and auditory baselines as well as the optimal model are not fit to bimodal data, but their predictions are tested against these bimodal data.
-All these normative models use the variances derived from the unimodal data and the bias term derived from the bimodal data.
+The visual and auditory baselines as well as the optimal model are not fit to the bimodal data, but their predictions are tested against these bimodal data.
+All these normative models use the variances derived from the unimodal data and the bias term derived from the fit to bimodal data.
 
 Although the paradigm is within-subjects, we did not have enough statistical power to fit a different model for each individual participant.
-Instead, models are constructed with data collapsed across all participants.
+Instead, models were constructed with data collapsed across all participants.
+That being said, the distribution of responses from individual participants will also be analyzed.
 The fit was done with a nonlinear least squares regression using the NLS package in R [@bates88].
@@
 The categorization function of the auditory condition was slightly steeper than that of the visual condition, meaning that participants perceived the sound tokens slightly more categorically and whih higher certainty than they did with the visual tokens.
-For the auditory modality, we obtained the following values:^[all CIs in the paper are 95% confidence intervals] $b_A=$ `r audBias_val`  [`r audBias_ci2`, `r audBias_ci1`] and $\sigma^2_A=$ `r audVar_val` [`r audVar_ci1`, `r audVar_ci2`].
-For the visual modality, we obtained $b_V=$ `r visBias_val` [`r visBias_ci2`, `r visBias_ci1`] and $\sigma^2_V=$ `r visVar_val` [`r visVar_ci1`, `r visVar_ci2`]`.
+For the auditory modality, we obtained the following values:^[all CIs in the paper are 95% confidence intervals.] $b_A=$ `r audBias_val`  [`r audBias_ci2`, `r audBias_ci1`] and $\sigma^2_A=$ `r audVar_val` [`r audVar_ci1`, `r audVar_ci2`].
+For the visual modality, we obtained $b_V=$ `r visBias_val` [`r visBias_ci2`, `r visBias_ci1`] and $\sigma^2_V=$ `r visVar_val` [`r visVar_ci1`, `r visVar_ci2`].
+
+```{r unimodal, out.width = "\\textwidth", fig.pos = "!h", fig.cap = "Human responses in the unimodal conditions.
+Points represent the proportion of `different' to `same' responses in the auditory-only condition (left), and visual-only condition (right).
+Error bars are 95\\% confidence intervals.
+Solid lines represent best fits."}
+
+all_plot
+
+```
 
@@
 
-```{r bimodal, out.width = "\\textwidth", fig.pos = "!h", fig.cap = "Human responses vs.
-models' predictions in the bimodal condition.
-Shape represents auditory distance from the target, and color represents visual distance from the target."}
-
-correlation_plot
-
-```
-
 #### Normative models
@@
 
-The descriptive model explained `r 100*R2_descriptive_1`% of total variance.
+\noindent The descriptive model explained `r 100*R2_descriptive_1`% of total variance.
 However, since the descriptive model was fit to the same data, there is a risk that this high correlation is due to overfitting.
-To examine this possibility, we cross-validated the model using half the responses to predict the other half (averaging across 1000 random partitions).
+To examine this possibility, we cross-validated the model using half the responses to predict the other half (averaging across `r N_partitions` random partitions).
 The predictive power of the model remained very high ($r^2$=`r CV_exp1_mean`).
+
+```{r bimodal, out.width = "\\textwidth", fig.pos = "!h", fig.cap = "Human responses vs.
+models' predictions in the bimodal condition.
+Shape represents auditory distance from the target, and color represents visual distance from the target."}
+
+correlation_plot
+
+```
 
@@
 However, we see in Figure\ \@ref(fig:bimodal) that the mean responses deviated systematically from the optimal prediction in that they were slightly pulled toward chance (i.e., the probability 0.5).
-This is due to the increase in the value of the variance associated with each modality.
-Note however that, despite this increase in randomness, our analysis of modality preference showed that the relative values of these variances were not different (Figure\ \@ref(fig:bias)), meaning that there was no evidence for a modality preference.<!--\footnote{The absence of modality preference does not mean that participants weight modalities equally in the bimodal condtion.
-Rather, it means that they weight modalities according to their relative relaibility, as measure in the unimodal conditions.}In the unimodal analysis, we saw that the precision of the auditory modality was slightly higher than that of the visual modality (i.e., $\frac{1}{\sigma^2_A} > \frac{1}{\sigma^2_V}$ ).
-If modalities were weighed according to their relative reliability (that is, optimally), we would naturally expect the auditory modality to have a higher weight in the bimodal presentation.
-But this is not what we mean by modality preference.
-Rather, the phrase refers to the case of potential sub-optimality where participants would rely on one modality beyond what is explained by the relative reliability of the optimal model.
---> Thus, 1) There was a simultaneous increase in the values of the auditory and visual variances in the bimodal condition compared to the unimodal condition, meaning that the bimodal input lead to an increase in response randomness, and 2) this increased randomness did not affect the relative weighting of both modalities, i.e., the population was weighting modalities according to the relative reliability predicted by the optimal model.
+This fact is due to the increase in the value of the variance associated with each modality.
+Note however that, despite this increase in randomness, our analysis of modality preference showed that the relative values of these variances were not different (Figure\ \@ref(fig:bias)), meaning that there was no evidence for a modality preference.
+Thus, 1) There was a simultaneous increase in the values of the auditory and visual variances in the bimodal condition compared to the unimodal condition, meaning that the bimodal input lead to an increase in response randomness, and 2) this increased randomness did not affect the relative weighting of both modalities, i.e., the population was weighting modalities according to the relative reliability predicted by the optimal model.
 This situation corresponds to the first case of sub-optimally described in Figure\ \@ref(fig:subOptim).
@@
 ```{r echo=FALSE, warning = FALSE}
+
+##Here we fit logistic regression to each participant
+##The logitic regression is equivalent to the descriptive model without the bias term
+##We use logistic regressions  instead of the full descriptive model becuase the latter would not converge given the small data points available for each participant
 
@@
 For ease of comparison, the simulated distribution was superimposed to the real distribution.
-We found that the real distribution was broader ($sd=$ `r subset(sd_ind, data=='real')$sd`) than the simulated distribution ($sd=$ `r subset(sd_ind, data=='simulation')$sd`), indicating real between-subject variation beyond sampling errors.
-This means that the participants varied in terms of how they weighted modalities: Compared to the predictions of the global descriptive model, some participants relied more on the auditory modality, and some relied more on the visual modality.
-
-<!--If, according to the extreme hypothetical case, the observed near-optimality is spurious, with participants relying exclusively on one or the other modality, we should observe a bimodal distribution (with modes centred around a very small and a very large number).
-If, instead, participants relied on both modalities, we should observe a unimodal distribution centered around a number whose order of magnitude is similar to the one observed with collapsed data.
--->
+We found that the real distribution had a standard deviation of $sd=$ `r subset(sd_ind, data=='real')$sd` which was larger than that of the simulated distribution ($sd=$ `r subset(sd_ind, data=='simulation')$sd`), indicating that there was real between-subject variation beyond sampling errors.
+This finding means that the participants varied in terms of how they weighted modalities: Compared to the predictions of the population-level model, some participants relied more on the auditory modality, whereas others relied more on the visual modality.
 
@@
 prefIdeal_ci2_2=dataSave2$upper[which(dataSave2$variable == "prefIdeal")]
+
+prefFit_val_2=dataSave2$estimate[which(dataSave2$variable == "prefFit")]
+prefFit_ci1_2=dataSave2$lower[which(dataSave2$variable == "prefFit")]
+prefFit_ci2_2=dataSave2$upper[which(dataSave2$variable == "prefFit")]
 
@@
 These normative models explained, respectively, `r 100*R2_visual_2`%, `r 100*R2_auditory_2`%, and `r 100*R2_optimal_2`% of total variance in mean judgements.
-Note that, in contrast to Experiment 1, the visual model explains more variance than the auditory model.
+Note that, in contrast to Experiment 1, the visual model explained more variance than the auditory model did.
 
@@
 
-In this Experiment, we tested the case where the background noise was added to the visual modality.
-Similar to Experiment 2, we were interested to know if participants would treat this new source of uncertainty as predicted by the optimal model, that is, according to the following weighting scheme  $$\beta_a \propto \frac{1}{\sigma^2_{A}}$$ $$\beta_v \propto \frac{1}{\sigma^2_{V}+\sigma^2_{N_V}}$$
-The alternative hypothesis is that, just like noise in the auditory modality lead to a preference for the visual input in Experiment 2, noise in the visual modality would lead to a  preference for the auditory input.
+In this Experiment, we added background noise to the visual modality.
+Similar to Experiment 2, we were interested to know if participants would treat this new source of uncertainty as predicted by the optimal model, that is, according to the following weighting scheme:  $$\beta_a \propto \frac{1}{\sigma^2_{A}}$$ $$\beta_v \propto \frac{1}{\sigma^2_{V}+\sigma^2_{N_V}}.$$
+The alternative hypothesis is that noise in the visual modality would lead to a preference for the auditory input, just like noise in the auditory modality lead to a preference for the visual input in Experiment 2.
 
@@
 
-### Unimodal conditions
-For the auditory modality, our parameter estimates were $b_A=$ `r audBias_val` [`r audBias_ci2`, `r audBias_ci1`] and $\sigma^2_A=$ `r audVar_val` [`r audVar_ci1`, `r audVar_ci2`].
-For the visual modality, we found $b_V=$ `r visBias_val` [`r visBias_ci2`, `r visBias_ci1`] and $\sigma^2_V+\sigma^2_N=$ `r visVar_val` [`r visVar_ci1`, `r visVar_ci2`].
-Figure\ \@ref(fig:unimodal) shows responses in the unimodal conditions as well as the corresponding fits.
-The auditory data is a replication of the auditory data in Experiment 1. As for the visual data, we see that, in contrast to Experiment 1 and 2, responses were flatter, showing much more uncertainty.
-
-### Bimodal condition
-
-#### Normative models
-Figure\ \@ref(fig:bimodal) compares the predictions of the visual, auditory and optimal models to human responses.
-These normative models explained, respectively, `r 100*R2_visual_3`%, `r 100*R2_auditory_3`%, and `r 100*R2_optimal_3`% of total variance in mean judgement.
-
-#### Descriptive model
-We estimated $b=$ `r BiasBi_val` [`r BiasBi_ci2`, `r BiasBi_ci1`], $\sigma^2_{Ab}=$ `r audVarBi_val` [`r audVarBi_ci1`, `r audVarBi_ci2`], and $\sigma^2_{Vb}+\sigma^2_{Nb}=$ `r visVarBi_val` [`r visVarBi_ci1`, `r visVarBi_ci2`].
-The fit explained `r 100*R2_descriptive_3`% of total variance.
-Cross-validation using half the responses to predict the other half yielded $r^2= $ `r CV_exp3_mean`.
-
-#### Modality preferences
-Participants' decision threshold suggested a preference for the auditory modality (the non-noisy modality).
-Indeed non-parametric resampling of the data showed an increase in the value of the slope in the descriptive model compared to the optimal model (Figure\ \@ref(fig:bias)).
-
-## Discussion
-We found that the optimal model accounted for almost all the variance ($r^2 =$ `r R2_optimal_3`).
-However, whereas in previous experiments, the optimal model explained more variance than the auditory or the visual models, here the auditory model explained at least as much variance ($r^2 =$ `r R2_auditory_3`).
-Thus, though participants were still sensitive to variation in the noisy visual data in the unimodal condition, they tended to ignore this information in the bimodal condition, and relied almost exclusively on the non-noisy auditory modality.
-The reason why we saw this (floor) effect when we added noise to the visual modality (Experiment 3), and not when we added noise to the auditory modality (Experiment 2), is the fact that our visual stimuli were originally perceived less categorically and with less certainty than the auditory stimuli.
-This made it more likely for the visual categorization function to become flat and uninformative after a few drops in precision due to noise on the one had, and to the additional randomness induced by the bimodal presentation on the other hand.
-
-<!--This behaviour is not so much a qualitative difference from Experiment 2 (where participants relied on both the noisy and the non-noisy modality in the bimodal condition), as much as it is the result of a floor effect.
-Indeed, noise made the visual modality way less steep and barely perceptible in the unimodal condition Figure\ \@ref(fig:unimodal).
-So when we had an additional general drop in precision in the bimodal condition (similar to what we found in Experiment 1 and 2),  participants were no longer able to extract any useful information.
--->
-The general finding corresponds to the third case of sub-optimality described in Figure\ \@ref(fig:subOptim).
-Indeed, precision dropped for both modalities in the bimodal condition compared to the unimodal condition.
-But the drop was much greater for the visual modality, resulting in a much lower weight assigned to it than what is expected from its optimal relative reliability.
-Therefore, just like participants over-relied on the visual modality when the auditory modality was noisy (Experiment 2), they also over-relied on the auditory modality when the visual modality was noisy (Experiment 3).
-
-```{r echo=FALSE}
-#number of participants relying exlusiviely on one modality
-#cut off is a factor of 10
-
-bimodal_bysub_good_3 <- bimodal_bysub_3 %>%
-  filter(bimod > 0.1) %>%
-  filter(bimod < 10)
-
-#Visual modality 
-only_visual_N_3 <- bimodal_bysub_3 %>%
-  filter(abs(bimod) < 0.1) %>%
-  nrow()
-
-#Sound modality 
-only_sound_N_3 <- bimodal_bysub_3 %>%
-  filter(abs(bimod) > 10) %>%
-  nrow()
-
-#the rest
-both_N_3 <- bimodal_bysub_3 %>%
-  filter(abs(bimod) > 0.1) %>%
-  filter(abs(bimod) < 10) %>%
-  nrow()
-
-neg_N_3 <- bimodal_bysub_3 %>%
-  filter(bimod <  -0.1) %>%
-  filter(bimod > -10) %>%
-  nrow()
-
-exlusive_prop_3 = only_visual_N_3/(only_sound_N_3+only_visual_N_3)
-
-```
-
-```{r results = "asis", landscape = FALSE}
-#Here make a table to analyze the exlusive reliance on one modality
-
-total_excl_exp1 <- (only_visual_N_1+only_sound_N_1)/(only_visual_N_1+only_sound_N_1+both_N_1)
-total_excl_exp2 <- (only_visual_N_2+only_sound_N_2)/(only_visual_N_2+only_sound_N_2+both_N_2)
-total_excl_exp3 <- (only_visual_N_3+only_sound_N_3)/(only_visual_N_3+only_sound_N_3+both_N_3)
-
-unimod <- data.frame(
-  Experiment = c('Exp1', 'Exp2', 'Exp3'),
-  Total = c(100*total_excl_exp1, 100*total_excl_exp2, 100*total_excl_exp3),
-  Auditory = c(100*(1-exlusive_prop_1), 100*(1-exlusive_prop_2), 100*(1-exlusive_prop_3)),
-  Visual = c(100*exlusive_prop_1, 100*exlusive_prop_2, 100*exlusive_prop_3)
-)
-
-apa_table(
-  unimod
-  , caption = "The percentage of participants who relied exclusively on either the visual modality or the auditory modality, using a factor of 10 as a cut-off (e.g., we consider that a participant relied exclusively on the visual modality when their auditory variance is a at least 10 times larger than their visual variance).
-We show the percentage compared to the total number of particiapnts in each Experiment (`Total').
-From this subset of participants, we show the percentage of those who relied on the  auditory modality (`Auditory'), and the percentage of those who relied on the visual  modality (Visual')."
-
-)
-
-```
-
-The percentage of participants who relied exclusively on either the visual modality or the auditory modality was `r 100*(only_visual_N_3+only_sound_N_3)/(only_visual_N_3+only_sound_N_3+both_N_3)`%, which is closer to the percentage of Experiment 2, except that now almost all of them relied on the auditory modality (`r 100*(1-exlusive_prop_3)`%).
-
 ```{r echo=FALSE, warning = FALSE}
@@
   theme(aspect.ratio = 1, axis.text=element_text(size=10))+
-  xlab("") +ylab("Relative weighing")+
+  xlab("") +ylab("Relative weighting")+
   scale_y_log10(breaks=c(0.5,1,2),labels=c("Visual bias","Optimal","Auditory bias"))
@@
 
+### Unimodal conditions
+For the auditory modality, our parameter estimates were $b_A=$ `r audBias_val` [`r audBias_ci2`, `r audBias_ci1`] and $\sigma^2_A=$ `r audVar_val` [`r audVar_ci1`, `r audVar_ci2`].
+For the visual modality, we found $b_V=$ `r visBias_val` [`r visBias_ci2`, `r visBias_ci1`] and $\sigma^2_V+\sigma^2_N=$ `r visVar_val` [`r visVar_ci1`, `r visVar_ci2`].
+Figure\ \@ref(fig:unimodal) shows responses in the unimodal conditions as well as the corresponding fits.
+The auditory data is a replication of the auditory data in Experiment 1.
+As for the visual data, we found that, in contrast to Experiment 1 and 2, responses were flatter, showing much more uncertainty.
+
+### Bimodal condition
+
+#### Normative models
+Figure\ \@ref(fig:bimodal) compares the predictions of the visual, auditory and optimal models to human responses.
+These normative models explained, respectively, `r 100*R2_visual_3`%, `r 100*R2_auditory_3`%, and `r 100*R2_optimal_3`% of total variance in the mean judgements.
+
+#### Descriptive model
+We estimated $b=$ `r BiasBi_val` [`r BiasBi_ci2`, `r BiasBi_ci1`], $\sigma^2_{Ab}=$ `r audVarBi_val` [`r audVarBi_ci1`, `r audVarBi_ci2`], and $\sigma^2_{Vb}+\sigma^2_{Nb}=$ `r visVarBi_val` [`r visVarBi_ci1`, `r visVarBi_ci2`].
+The fit explained `r 100*R2_descriptive_3`% of total variance.
+Cross-validation using half the responses to predict the other half yielded $r^2=$ `r CV_exp3_mean`.
+
+#### Modality preferences
+Participants' decision threshold suggested a preference for the auditory modality (the non-noisy modality).
+Indeed non-parametric resampling of the data showed an increase in the value of the slope in the descriptive model compared to the optimal model (Figure\ \@ref(fig:bias)).
+
+## Discussion
+We found that the optimal model accounted for almost all the variance ($r^2 =$ `r R2_optimal_3`).
+However, whereas in previous experiments the optimal model explained more variance than the auditory or the visual models, here the auditory model explained at least as much variance ($r^2 =$ `r R2_auditory_3`).
+Thus, though participants were still sensitive to variation in the noisy visual data in the unimodal condition, they tended to ignore this information in the bimodal condition, and relied almost exclusively on the non-noisy auditory modality.
+The reason why we saw this (floor) effect when we added noise to the visual modality (Experiment 3), and not when we added noise to the auditory modality (Experiment 2), is the fact that our visual stimuli were originally perceived less categorically and with less certainty than the auditory stimuli.
+This fact made it more likely for the visual categorization function to become flat and uninformative after a few drops in precision due to noise on the one had, and to the additional randomness induced by the bimodal presentation on the other hand.
+
+The general finding corresponds to the third case of sub-optimality described in Figure\ \@ref(fig:subOptim).
+Indeed, precision dropped for both modalities in the bimodal condition compared to the unimodal condition.
+But the drop was much greater for the visual modality, resulting in a much lower weight assigned to it than what is expected from its reliability.
+Therefore, just like participants over-relied on the visual modality when the auditory modality was noisy (Experiment 2), they also over-relied on the auditory modality when the visual modality was noisy (Experiment 3).
+
+```{r echo=FALSE}
+#number of participants relying exlusiviely on one modality
+#cut off is a factor of 10
+
+bimodal_bysub_good_3 <- bimodal_bysub_3 %>%
+  filter(bimod > 0.1) %>%
+  filter(bimod < 10)
+
+#Visual modality 
+only_visual_N_3 <- bimodal_bysub_3 %>%
+  filter(abs(bimod) < 0.1) %>%
+  nrow()
+
+#Sound modality 
+only_sound_N_3 <- bimodal_bysub_3 %>%
+  filter(abs(bimod) > 10) %>%
+  nrow()
+
+#Both
+both_N_3 <- bimodal_bysub_3 %>%
+  filter(abs(bimod) > 0.1) %>%
+  filter(abs(bimod) < 10) %>%
+  nrow()
+
+neg_N_3 <- bimodal_bysub_3 %>%
+  filter(bimod <  -0.1) %>%
+  filter(bimod > -10) %>%
+  nrow()
+
+exlusive_prop_3 = only_visual_N_3/(only_sound_N_3+only_visual_N_3)
+
+```
+
+```{r exclusive, results = "asis", landscape = FALSE}
+#Here make a table to analyze the exlusive reliance on one modality
+
+total_excl_exp1 <- (only_visual_N_1+only_sound_N_1)/(only_visual_N_1+only_sound_N_1+both_N_1)
+total_excl_exp2 <- (only_visual_N_2+only_sound_N_2)/(only_visual_N_2+only_sound_N_2+both_N_2)
+total_excl_exp3 <- (only_visual_N_3+only_sound_N_3)/(only_visual_N_3+only_sound_N_3+both_N_3)
+
+unimod <- data.frame(
+  Experiment = c('Exp1', 'Exp2', 'Exp3'),
+  Total = c(100*total_excl_exp1, 100*total_excl_exp2, 100*total_excl_exp3),
+  Auditory = c(100*(1-exlusive_prop_1), 100*(1-exlusive_prop_2), 100*(1-exlusive_prop_3)),
+  Visual = c(100*exlusive_prop_1, 100*exlusive_prop_2, 100*exlusive_prop_3)
+)
+
+apa_table(
+  unimod
+  , caption = "The percentage of participants who relied exclusively on either the visual modality or the auditory modality, using a factor of 10 as a cut-off (e.g., we consider that a participant relied exclusively on the visual modality when their auditory variance is a at least 10 times larger than their visual variance).
+We show the percentage compared to the total number of participants in each Experiment (`Total').
+From this subset of participants, we show the percentage of those who relied on the  auditory modality (`Auditory'), and the percentage of those who relied on the visual  modality (Visual')."
+
+)
+
+```
+
+The percentage of participants who relied exclusively on either the visual modality or the auditory modality was `r 100*(only_visual_N_3+only_sound_N_3)/(only_visual_N_3+only_sound_N_3+both_N_3)`%, which is closer to the percentage of Experiment 2, except that now almost all of them relied on the auditory modality (`r 100*(1-exlusive_prop_3)`%).
+For ease of comparison, Table \@ref(tab:exclusive) provides a summary of the numbers across the three experiments.
+
 # General Discussion
-
-When identifying a spoken word under uncertainty, one often needs to combine and make the most of the available multimodal cues.
-While most previous studies focused on the case of audio-visual speech where people combine cues from speech and facial features, this work explored the case of identifying an ambiguous word when the available multimodal cues are speech and the visual referent.
+When identifying a spoken word under uncertainty, one often needs to make the most of the available cues.
+Some previous work studied optimal behavior under uncertainty from the auditory input only [e.g., @clayard08; @feldman2009], and others studied optimality under multimodal uncertainty in auditory speech and visual facial features [e.g.
+@bejjanki2011].
+The current work explored, for the first time, the case of word identification under uncertainty in speech (word form) and the visual *referent*.
 More specifically, we conducted an ideal observer analysis of the task whereby a model provided predictions about how information from each modality should be combined in an optimal fashion.
-The predictions of the model were tested in a series of three experiments where instances of both the form and the referent were ambiguous with respect to their category membership only (Experiment 1), when instances of the form were perturbed with additional background noise (Experiment 2), and when instances of the referent were perturbed with additional visual noise (Experiment 3).
-
-In all Experiments, we found many patterns of optimal behaviour.
+The predictions of the model were tested in a series of three experiments where instances of both the form and the meaning were ambiguous with respect to their category membership only (Experiment 1), when instances of the form were perturbed with additional background noise (Experiment 2), and when instances of the referent were perturbed with additional visual noise (Experiment 3).
+
+In all Experiments, we found many patterns of optimal behavior.
 Quantitatively speaking, the optimal model accounted, respectively, for `r 100*R2_optimal_1`%, `r 100*R2_optimal_2`%, and `r 100*R2_optimal_3`% of the variance in mean responses.
@@
 First, in all Experiments, the variance associated with each modality increased in the bimodal condition compared to the unimodal conditions.
-This means that participants responded slightly more randomly in the bimodal condition than they did in the unimodal conditions.
+This fact means that participants responded slightly more randomly in the bimodal condition than they did in the unimodal conditions.
 This finding contrasts with research on  multisensory integration where associations tend to lead to a higher precision [e.g., @ernst02].
-Nevertheless, there is a crucial difference between these two situations.
+Nevertheless, there is a crucial difference between these two situations (besides the obvious difference in terms of the models used).
 Research on  multisensory integration (of which audio-visual speech is arguably an instance) deals with redundant multimodal cues, and these cues are integrated into a unified percept.
 In contrast, the word-referent association is usually arbitrary and, in particular, the cues are not expected to be correlated perceptually.
-Therefore the mind cannot form a unified percept, rather, it must encode information separately from both modalities and retain this encoding through the decision making process.
+Therefore the observer cannot form a unified percept, rather, it must encode information separately from both modalities and retain this encoding through the decision making process.
 Retaining two separate cues at the same time instead of forming one unified percept (as in multisensory integration of redundant cues), or instead of retaining only one cue (as in the unimodal case), is likely to place extra-demand on cognitive resources, which, in turn, can cause general performance to drop.
-Indeed, there is evidence that cognitive load has a detrimental effect on word recognition, which can be due to a reduction in perceptual acuity [@mattys11].
-Similar to our finding, previous experimental studies reported that in both children and adults, identifying new ambiguous form-referent mappings is usually associated with what appears to be a decrease in speech perception acuity [@stager1997; @pajak2016].
-@hofer2017 provided a probabilistic model of this phenomenon, which they similarly characterized as an increase in the noise variance of the auditory modality.
-Our finding replicates this previously documented fact, and additionally suggests that the reduction in perceptual acuity occurs simultaneously in both the auditory and the visual modalities.
-
-The second case of sub-optimality is related to how participants weighed the cues from the visual and the auditory modalities in a noisy context.
+Indeed, there is evidence that cognitive load has a detrimental effect on word recognition.
+This phenomenon  can be due to a reduction in perceptual acuity [e.g., @mattys11].
+
+Some previous research found a similar case of suboptimal behavior.
+For instance, studies that explored  the identification of ambiguous, newly learned pairs of word-referent associations all reported what appears to be a decrease in speech perception acuity in both children [@stager1997] and adults [@pajak2016].
+Recently, @hofer2017 provided a probabilistic model of this phenomenon.
+In agreement with the method and finding in the current study, @hofer2017 characterized the apparent reduction in perceptual acuity as an increase in the noise variance of the auditory modality.
+Our finding, besides providing more evidence to this documented fact, suggests that the  reduction in perceptual acuity may occurs simultaneously in both the auditory *and* the visual modalities.
+
+The second case of sub-optimality is related to how participants weighted the cues from the visual and the auditory modalities in a noisy context.
 In contrast to Experiment 1 where the combination was indistinguishable from the optimal prediction, results of Experiment 2 and 3 which both involved background noise in one modality, showed that participants had a systematic preference for the other (non-noisy) modality.
@@
 However, and generally speaking, these studies do not differentiate between an optimal compensatory strategy (i.e., relying more on the alternative source while using all information still available in the distorted signal), and a sub-optimal strategy (i.e., relying more on the alternative source while ignoring at least some of the information still available in the distorted signal).
-The formal approach followed in this paper allowed us to tease apart these two possibilities, and the analysis supports the sub-optimal compensatory strategy: The preference for the non-noisy modality is above and beyond what can be explained by the relative reliability alone, meaning that the participant tend to ignore at least part of the information still available in the noisy modality.
-
-This second case of sub-optimal behavior is possibly related to the fact that language understanding under degraded listening conditions is cognitively more taxing than language understanding under normal conditions [@Ronnberg10].
-This fact can lead to a preference/bias towards alternative sources of information when these sources are available.
-One could explain this phenomenon in terms of the metacognitive experience about the fluency with which information is processed.
-The perceived perceptual fluency (e.g., the ease with which a stimulus’ physical identity can be identified) can affect a wide variety of human judgements [see @schwarz2004 for a review].
+The formal approach followed in this paper allowed us to tease apart these two possibilities, and our analysis supports the sub-optimal compensatory strategy: The preference for the non-noisy modality is above and beyond what can be explained by the relative reliability alone, meaning that the participants tend to ignore at least part of the information still available in the noisy modality.
+
+This second case of sub-optimal behavior is possibly related to the fact that language understanding under degraded  conditions is cognitively more taxing than language understanding under normal conditions [e.g., @Ronnberg10].
+This fact can lead to a bias against the more noisy cue.
+One could also explain this phenomenon in terms of the metacognitive experience about the fluency with which information is processed.
+The perceived perceptual fluency (e.g., the ease with which a stimulus' physical identity can be identified) can affect a wide variety of human judgements [see @schwarz2004 for a review].
 In particular, variables that improve fluency tends to increase liking/preference [@reber98].
@@
 
-In this study, we tested the extent to which people would be optimal in combining uncertain auditory and visual cues to recognize words.
-This required that we use a case of double ambiguity, that is, a case where both the word forms ("ada"-"aba") and the referents (cat-dog) were similar and, thus, confusable.
-One could wonder about the extent to which such case occurs in real languages?
-Cross-linguistic corpus analyses suggest that the lexical encoding tends towards double ambiguity in many languages [@dautriche17; @Monaghan2014; @Tamariz2008].
-For instance, @dautriche17 analysed 100 languages and found that word that are similar phonologically  tend to be similar semantically as well, beyond what could be explained by chance.
-Crucially, they found this trend in a set of monomorphemic lemmas in four languages, suggesting that the effect is not driven by morphological regularities.
-These studies suggest that the case of double uncertainty, though perhaps not pervasive, could be a real issue in language as it increase the probability of confusability.
-Moreover, it is important to keep in mind that ambiguity in both the form and the referent can be induced by an external noisy context even when these forms and referents are not confusable in normal situations.
+An important question to ask is how the combination mechanism---as revealed in our controlled study---scales up to real life situations.
+Note that in order to test audio-visual cue combination under uncertainty, we had to use a case of double ambiguity, that is, a case where both the word forms ("ada"-"aba") and the referents (cat-dog) were similar and, thus, confusable.
+However, to what extent does such case occur in real languages?
+Cross-linguistic corpus analyses suggest that lexical encoding tends, surprisingly, towards double ambiguity in many languages [@dautriche17; @Monaghan2014; @Tamariz2008].
+For instance, @dautriche17 analyzed 100 languages and found that words that are similar phonologically  tend to be similar semantically as well.
+These studies suggest that the case of double uncertainty, though perhaps not pervasive, could be a real issue in language as it increase the probability of confusability for many words.\linebreak That being said, besides the case of double ambiguity intrinsic to language, there are two situations where our mechanism might play a significant role.
+The first is when ambiguity in both the form and/or the referent is induced by an external noisy context even when these forms and referents are not confusable in normal situations.
+The second case is that of early word recognition/learning, and we will discuss this case in more detail in what follows.
 
@@
 Among other things, children have to enrich this early representation with new features, and revise its extension in the light of new referential exposures.
-
-Thus, uncertainty in the representation associated with one modality (e.g., a bee and a fly) can be mitigated through the possibly more differentiated representations associated with the other modality (e.g., the sound "bee" is acoustically different from the sound "fly").
-That being said, a multi-modal cue combination strategy might help children not only recognize an individual word instance, but also refine the underlying phonological and semantic representations in the process.
+In sum, uncertainty in the representation associated with one modality (e.g., a bee and a fly) can be mitigated through the possibly more differentiated representations associated with the other modality (e.g., the sound "bee" is acoustically different from the sound "fly").
+
+The multi-modal cue combination strategy might help children not only recognize an individual word instance, but also refine the underlying phonological and semantic representations in the process.
 Previous research in early word learning has---whether implicitly or explicitly---largely treated the process of learning form and of learning meaning as independent.
-<!--Babies are understood to first master the form, learning to ignore phonologically irrelevant variation (such as differences in talker, speech rate, emotion, and linguistic context) (see Kuhl, 2004 for a review).
-Only when the form representation is refined and ready, can they start mapping the form to meaning (Bloom, 2000)-->However, the developmental data reviewed above shows that children do not wait to have completed the acquisition of form to start learning meanings, and that both form and meaning representations develop, rather, in a parallel fashion.
+However, the developmental data reviewed above shows that children do not wait to have completed the acquisition of form to start learning meanings, and that both form and meaning representations develop, rather, in a parallel fashion.
 A few studies pointed to the possibility of an interaction between sound and meaning in early acquisition.
@@
 Vice versa, @yeung09 showed that pairing similar sounds with different objects help infants pay attention to subtle phonological contrasts.
-The present study proposes a first step towards a formal framework where accounts of sound-meaning synergy in development can be unified and further explored.
-For example, one could imagine that, initially, visual and auditory categories have relatively large noise variances, and that development consists in reducing the values of the variances through a mutually constraining process as further multimodal data accumulates.
-
-In conclusion, this work studied the mechanism of word identification under uncertainty in both the word form and the word meaning.
+The present study proposes a first step towards a formal framework where isolated accounts of sound-meaning interaction in development can be unified and further explored.
+<!--For example, one could imagine that, initially, visual and auditory categories have relatively large noise variances, and that development consists in reducing the values of the variances through a mutually constraining process as further multimodal data accumulates.
+--->
+
+One limitation of this work is that we used simplified stimuli.
+For the auditory modality, we used speech categories that varied along a single acoustic dimension.
+While this dimension might be sufficient to recognize  words in our specific case, in general the speech signal may be more complex, varying along several acoustic/phonetic dimensions.
+Additionally, these dimensions may be highly variable due to various kinds of speaker and context differences.
+The same thing can be said about the referential stimuli.
+Here we used a continuum along a single morph dimension in order to construct a multimodal input where the auditory and visual components have symmetrical properties.
+Though such morph is not the exact visual variability that people would encounter in their daily lives, it allowed us to precisely test the role of auditory and visual information in the cue combination process.
+Parameterizing semantic dimensions is a notoriously difficult problem, but morphs have been used in previous research as a reasonable proxy [@freedman2001; @havy2016; @sloutsky2004].
+It is an open question as to whether people use the same strategy in controlled laboratory conditions, as in more naturalistic settings where they have to deal with various levels of variability.
+An answer to this question is likely to involve a multifaceted research approach, involving---besides laboratory experiments---analyses of corpora with a more realistic multimodal input [e.g., @fourtassi2014b; @harwath2016; @roy2015].
+
+# Conclusion 
+This work studied the mechanism of word identification under uncertainty in both the word form and the word referent.
 To our knowledge, this is the first study that performs an ideal observer analysis of this task.
@@
 However, they also showed patterns of sub-optimality especially when the stimuli were perturbed with additional background noise.
-Future work will extend the present formal framework in order to account for how children use multimodal cues to refine their early phonological and semantic representations.
-
-# Appendix: derivation of the posterior (equation 1)
+Though the present study did not directly address the issue of early word learning, it provides a framework where developmental questions can also be investigated.
+For instance, future work should explore whether children, like adults, use probabilistic cues from both the auditory and the visual input to recognize ambiguous words,  the extent to which they combine these cues in an optimal fashion, and whether these combination help them with refining their early phonological and semantic representations.
+
+\vspace{1em} \fbox{\parbox[b][][c]{14cm}{\centering All data and code for these analyses are available at\ \url{https://github.com/afourtassi/WordRec}}} \vspace{1em}
+
+# Appendix 1: derivation of the posterior (Equation 1)
 
@@
 
-When putting all these terms together, we the get this final expression for the posterior:
+When putting all these terms together, we obtain this final expression for the posterior:
 $$p(W_2 | w)=\frac{1}{1+(1+b)\exp(\beta_0+\beta_aa+\beta_vv)}$$
@@
 $$\beta_a=\frac{\mu_{A1}-\mu_{A2}}{\sigma^2_{A}}$$
-$$\beta_v=\frac{\mu_{V1}-\mu_{V2}}{\sigma^2_{V}}$$ 
-<!--
-as further data about sound-meanining associations accumulate, making the categories more refined and precise.
-
-Moreover, modeling studies the possibility of an interaction or synergy between early represention interaction between sound and menaning
-
-A few studies explicitely pointed to the possibility of an interaction between sound and meaning in early acqusition. For instance, Waxman and Markow (1995) showed that a
-
-It follows that Cue combination is not only necessary to recognize a word (as with ault), but also to lrefine the underlying representations, leading to a leaning synergy (Fourtass and Dupoux, 2014).
-Waxman and Yeung, but they assume an ambiguous state.
-Here we suggest that even if non of the representation
-
-If we take the perspective of infromation theory, communication is basically a process of information transfer in a noisy channel (Shannon, 1948), and information encoding should be such that the listener is able to recover what is being said.
-Therefore, the confusability of distinct words should be minimized.
-In particular, similar meanings should be encoded with phonologically distinct words.
-As it turns out, cross-lingusitc corpus analyses reveal an opposite trend, suggesting that the constraints of communication might not be the only force shaping the struture of the lexicon (Dautriche et al.
-2016; Monaghan et al., 2014; Shillcock et al., 2001; Tamariz, 2008).
-For instace, Dautriche et al.
-2015 analysed 100 languages and found that word that are similar phonologically  tend to be more similar semantically as well, above what could be explained by chance.
-Crucially, they found this trend in a set of monomorphemic lemmas in four languags, suggesting that the effect is not driven by morphological regularities.
-These studies suggest that the case of souble uncertainty, though perhabps not pervasive, could be a real issue beyond our controlled experiment, and that an optimal cue combination strategy might be crucial for word recognition in real life situations.
-
-Here talk about development
-
-They found that minimal pairs are more likely to be found among semantically related words than semantically different words.
-
-Crucially,
-
-From an information theory perspective, communication can be modeled as the transfer of information over a noisy channel (Shannon, 1948).
-Successful commu- nication requires listeners to be able to recover what is being said; therefore, the likeli- hood that two distinct words would be confusable should be minimized according to this constraint.
-There is much evidence that perceptual distinctiveness plays an important role in shaping the phonology of languages
-
-However, in order for the optimal combination strategy to be relevant to our understading of word recognion, we need   play any role beyond a mere controlled experiment, cross-lingsuitic corpus analyses indicate that this is not an infrequent phenomeon in real languages.
-For example,
-
-analyzed the relationship between semantic relatedness and the likelihood of finding a minimal pair and found that minimal pairs are more likely among semantically similar words than semantically distant words.
-
-The arbitraniess of the sign in natural language means that the word form is not necessarilly related to the features of the semantic catgory, and a corrola
-
-in rather extreme situation  tested a rather extreme case of uncertainty where both
-
-To explore how the mind However, insights in this work can shed light on   but in a simple case when the underlying visual and auditory categories were familiar.
-Indeed, on the visual side, cat and dog tokens belong obviously to existing visual categories.
-On the auditory side, though the words ("ada"/"aba") are novel, the phonemic categories that differentiate the words are familiar (i.e., /d/ and /b/).
-In the context of early word learning, however, children are often learning both the categories and their mapping at the same time.
-In fact, children start learning visual and sound categories at an early age [e.g., @quinn93;@werker1984], and there is evidence that word-referent-like interaction operates at the same time, even when the categories are not yet fully mastered [e.g., @waxman1995; @yeung09].
-In fact, @fourtassi2014a proposed that this interaction can create a synergy (or a bootstrapping effect) whereby progress made on one level (e.g., the meaning categories) can benefit the other level (the sound categories).
-
-In what follows we explain how an account that combines both category learning and optimal multimodal integration can proceed, and how such account can provide us with a useful developmental framework.
-In the light of this framework, we speculate about possible new interpretation of some puzzling results in early word learning [@stager1997 and seq].
-For starters, remember that one assumption of the model is that visual and auditory categories can be characterized with a variance that determines their precision/reliability.
-At the behavioral level, the variance is related to the shape of the categorization function: a small variance corresponds to a rather steep categorization function, meaning that one can tell with high certainty whether or not a token belongs to the category at hand.
-Vice versa, a large value of the variance corresponds to a rather flat categorization function, which means that for most tokens, one cannot tell with high certainty whether or not these tokens belong to the category at hand.
-
-How can this formal characterization fit in a developmental scenario?
-One could imagine that, initially, visual and auditory categories have relatively large variances, and that development consists in reducing the values of the variances as evidence accumulates, making the categories more refined and precise.
-A scenario similar to this one has been previously suggested to explain the development of early sound categories.
-For example, @yoshida2009 suggested that the early categories may be noisier or that they may be encoded with relatively lower confidence.
-For the semantic categories, we can find similar (although perhaps not identical) ideas.
-For instance, Clark (1973) suggested that the initial meaning categories tend to be larger than adult categories, since fewer features are used to pick out referents (e.g., dog for all four-legged animal, ball for all round objects).
-
-The combination of this developmental scenario in terms of category variance with the optimal integration account introduced in this paper provides possible new insights into the mechanism of word learning.
-Let's elucidate this idea through an example in the developmental literature.
-@stager1997 showed that 14 m.o (as opposed to 17 m.o) have difficulties mapping two minimally different sounds (e.g., "bih"/"dih") to two novel objects, despite the fact that they can perceptually differentiate these sounds.
-Our proposal explains these patterns of failure and success in terms of developmental changes in the variances associated with the visual and phonological categories, combined with the ability to integrate sound and visual cues according to their reliability.
-Suppose that both members of a given sound contrast ("bih"/"dih") initially fall within the uncertainty range of a single sound category.
-If this uncertainty diminishes with age (as the category gets more refined), then what used to be likely at a certain point in development (e.g., 14 m.o), may later become unlikely.
-In particular, at 17, m.o, it may become necessary to attribute the sound contrast to two neighboring categories instead of a single one.
-But how can 14 m.o possibly consider one broad category for both sounds if these sounds are paired with different objects?
-This is where the optimal combination account may come into play.
-Indeed, even if the objects are perceptually different, they may still be similar in the 14 m.o's early semantic space.
-If babies make categorical decision based on both auditory and visual cues, then having evidence that the auditory tokens belong to the same category can prompt them to consider the possibility that even the objects are variations within the same (broad) semantic category.
-Thus, 14 m.o may be learning one broad word-referent association instead of two specific associations.
-According to the present account, what was considered a "failure" in learning might, in fact, be the optimal decision within the 14 m.o's own developmental context!
-
-This account makes two main predictions.
-First, if the sounds are more acoustically different (e.g., "lif"/"neem" instead of "bih"/"dih"), babies would be more likely to posit and learn two word-referent associations, because there would be more evidence pointing in that direction from the auditory side.
-Second, if the objects are more semantically distant (a living object vs.
-a non-living object, instead of the two perceptually different toys used in the original study), babies would be more likely to posit and learn two word-referent associations, because now there would be more evidence pointing in that direction from the visual side.
-In fact, @stager1997 tested and proved the first prediction.
-The second prediction remains to be tested.
-If proven, it would provides support to the optimal combination account in early language learning.
-
-In a similar study that used eye tracking in addition to overt responses, Creel (2012) replicted these findings and showed that the chidlren's visual fixations revealed slower recognition for the novel word, suggesting a hightened uncertainty.
-
-(Merriman and Schuster, 1991; Creel, 2012).
-
-In fact, though children start learning the categories at an early age, typically before their first birthday [e.g., @werker1984], this learning is not perfect from the start.
-In particular, early categories can be noisier and/or encoded with lower confidence.
-It follows that recognizing familar or novel words might be a greater challenge for children than it is for adults.
-For example, in a word recognition task, though toddlers prefer the correct pronounciation of a familiar word (e.g., "baby") over a novel but phononlogically similar word ("vaby"), they do not totally reject the novel word: they still look at the familiar word's referent more than a different object (Swingley and Aslin, 2000).
-A similar pattern was found with preschoolers using a mutual exclusivity paradigm.
-Mutual exclusivity is a bias that children have to interpret novel words as referring to novel objects rather than familiar objects (Markman & Wachtel, 1988).
-For example, when presented with a ball and a novel object and asked to select, say, a "dax", participants typically point to the novel object.
-Merriman and Schuster (1991) found that this effect decreases markedly in 4-year-olds if the novel word is phonologically similar to a familiar word.
-In other words, children do not necessarily interpret a novel word "bool" to be a label for the novel object, but tend to extend it to the familiar object (a ball).
-In a similar study that used eye tracking in addition to overt responses, Creel (2012) found that preschoolers, similar to Merriman and Schuster (1991), mostly select the familiar objet.
-Moreover, the chidlren's visual fixations indicated slower recognition for the novel word, suggesting a hightened uncertainty.
-
-Children representeation of newly learned words is even more fragile than their representation of familair words (Swingley, 2007).
-For example, @stager1997 showed that 14 m.o have difficulties mapping two minimally different sounds (e.g., "bih"/"dih") to two novel objects, despite the fact that they can perceptually differentiate these sounds.
-Specifically, their task required that infants reject the switch trials, that is, when an object (e.g.
-the one associated with the word "bih") is labelled with the wrong name ("dih").
-Yoshida et al.
-(2009) tested infants with a preferential looking paradigm that reduced the memory demands in the orginal task.
-After the leanrning phase, they monitored the infants' looking patterns when presented with both objects at the same time, instead of comparing their attitude to the correct vs.
-the wrong associaton.
-In this simplified task, they found that infants succeeded in picking the correct object.
-In order to explain why infants fail in the switch task but succeed in the simpler preferential looking paradigm, Yoshida et al.
-(2009) proposed that phonological features might be encoded probabilistically.
-Early word representations for "din" and "bin"", though distinct, might be encoded with a relatively lower confidence.
-Thus, uncertainty generated by  the matching bin label, may  not  surpass  the  threshold  levelrequired  for  rejection  of   the  pairing,  resulting  in  nodifference  between  the  same  and  Switch  trials
-In the visual choice paradigm, thecritical  criterion  involves  a  direct  comparison  of,  and  aforced choice between, the two objects.
-Here, the relativelyslight difference in uncertainty is sufficient; the 60% matchwould be considered to be a better fit than the 40% match,allowing infants to demonstrate their learning ability.
-
-Actually this probabilistic accout can also explain the case of famialr words
-Talk about Swingley 2007
-For the semantic, see here:
-https://www.ncbi.nlm.nih.gov/pubmed/12003515
-
-Yoshida et al. (2009)
-
-Our proposal explains these patterns of failure and success in terms of developmental changes in the variances associated with the visual and phonological categories, combined with the ability to integrate sound and visual cues according to their reliability.
-Suppose that both members of a given sound contrast ("bih"/"dih") initially fall within the uncertainty range of a single sound category.
-If t
-
-There is evidence supporting (albeit indirectly) the possibility of effects of phonological similarityon induction.
-In particular,Merriman and Schuster (1991)demonstrated that phonological similarityof words led to attenuated ‘‘mutual exclusivity’’ effects in 2- and 4-year-olds.
-Mutual exclusivity is atendency of toddlers and young children to interpret novel words as referring to novel items ratherthan familiar items (Markman & Wachtel, 1988).
-For example, when presented with an apple and anovel object and asked to select adax, participants pointed to the novel object.Merriman and Schuster(1991)found that the effect decreases markedly or disappears if the novel word is phonologically sim-ilar to a familiar word; children would not necessarily extend a novel wordjappleto a novel object butmight instead extend it to an apple
-
-More generally, toddler's eye fixation show a graded pattern in terms of recognition, that is, they look less often at the correct object as the mispronouciation gets gradually more different from the correct the pronounciation
-more different the mispronouciation is to the correct pronooucition, the more
-
-children's looking patterns show a graded recognition uncertainty as the misponounciation's phonetic dissimilarity to the typical proniucaution increases (Morgan while...).
-
-One could even argue that the problem of word learning/recognition under multimodal uncertanty is a more pressing issue for children in the process of language acqiusition than it is for adults who already master the language.
-forms with high phonetic details
-
-Talk about Swingley work for familar words:
-
-Talk about Yoshida for novel words
-
-Talk about the fact that this uncertainty develops into early chidhood
-
-However, children do not wait to have fully mastered the speech and semantic categories before they start attempting to map form to meaning.
-
-Because  of  the  greater  noise  inherent  in  children’s  perceptual- processing  systems,  the  same  acoustic  stimulus  may  effectively be less reliable for children than adults (Lyons &  Ghetti,  2011;  Neuman  &  Hochberg,  1983)
-
-How can this formal characterization fit in a developmental scenario?
-One could imagine that, initially, visual and auditory categories have relatively large variances, and that development consists in reducing the values of the variances as evidence accumulates, making the categories more refined and precise.
-A scenario similar to this one has been previously suggested to explain the development of early sound categories.
-For example, @yoshida2009 suggested that the early categories may be noisier or that they may be encoded with relatively lower confidence.
-For the semantic categories, we can find similar (although perhaps not identical) ideas.
-For instance, Clark (1973) suggested that the initial meaning categories tend to be larger than adult categories, since fewer features are used to pick out referents (e.g., dog for all four-legged animal, ball for all round objects).
-
-They also start to map sound a
-
-However, this learning is not perfect from the start ,
-
-Indeed, since both the speech categories and the semantic categories are still not fully mastered by children, the lingusitic input can in generarl be more uncertain for the latter, which makes the problem of inference under uncertainty a more pressing issue.
-
-In early development, the combination of statistics from the auditory and the visual referent can be crucial to learn the
-
-Recognition of novel words 
-For kids the uncertainty is higher 
-word referent 
-In this study, we explored the mechanism of word identification, but in a simple case when the underlying visual and auditory categories were familiar.
-Indeed, on the visual side, cat and dog tokens belong obviously to existing visual categories.
-On the auditory side, though the words ("ada"/"aba") are novel, the phonemic categories that differentiate the words are familiar (i.e., /d/ and /b/).
-In the context of early word learning, however, children are often learning both the categories and their mapping at the same time.
-In fact, children start learning visual and sound categories at an early age [e.g., @quinn93;@werker1984], and there is evidence that word-referent-like interaction operates at the same time, even when the categories are not yet fully mastered [e.g., @waxman1995; @yeung09].
-In fact, @fourtassi2014a proposed that this interaction can create a synergy (or a bootstrapping effect) whereby progress made on one level (e.g., the meaning categories) can benefit the other level (the sound categories).
-
-<!--This work, as well as the model, is about the mechanism of word-referent recognition when the underlying visual and auditory categories are supposed to be already familiar.
-On the visual side, cat and dog tokens belong obviousely to existing categories.
-Uncertainty is about where the boundary lies, and how this perceived boundary changes when evidence from the auditory data varies from clear to ambiguous.
-On the auditory side, though the words ("ada"/"aba") are novel, the phonemic categories that differentiate the words are familiar (i.e., /d/ and /b/).
-Thus, similar to the visual categories, uncertainty is about where the phonological boudary lies, and also how this perceived boundary changes when evidence from the visual data varies from clear to ambiguous.
-The main finding of this paper is that people shift the categories' boudary depending on evidence form both auditory and visual input, and that, generally speaking, evidence from both modalities are weighted in a near optimal way.
--->
-
-<!--
-
-This, in turn, would make them interpret the sound difference as alternative pronunciations of the same word\footnote{The reverse reasining is plausible as well, and in fact, can explain why in the same experiment, the use of acoustically distant words ("lif"/"neem"" instead of "bin"/"din) made 14 m.o succeed in the same task}.
-A prediction of the optimal model would be that the use of semantically distant objects can induce success with the same similar sounding words.
-
-new explanations for some findings in the developmental literature.
-We will focus on two influenceial lines of work relatad to multimodal processing: the development of modality dominance (Robertson and Sloutsky, 2004), and the development of the learning of similar sounding words (Stagter and Werker, 1997).
-
-Sloutsky and Napolitano (2003) reported a dominance for the auditory modality in children, and showed that this dominance disappears or reverses in adults.
-The authors attribute this dominance to the fact that auditory is more transient, and therefore tend to attract more attention.
-According to this interpretation, children should weight modalities in the same way regerdless of the stimuli used.
-Another interpretation, inspired by our model, would suggest that the precise sound and object contrasts used as stimuli in this series of experiments differ in their relative salience to children.
-One way to disentangle these two interpretations is to use an audio-visual stimuli where the sound contrast is reduced to a perceptual minimum and/or where the visual contrast is enhanced.
-An optimal-based account would suggest that the weighting would reverse in this case.
-
-it  may allow us to account for some findings in the dedvelopment literature
-
-The main finding of the present work is that when the input is multimodal, behavior is largely predicted by the value of the variance of the auditory category relative to the variance of the visual category.
-
-revisit some  findings in the develomental literature and speculate about possible explanations.
-We will focus on two influencial findings, one is the development of a phenomeon dubbed Auditory Overshadowing (Napolitano, Robertson, ...), and the other is the development of the ability to learn similar sounding words (Stager & Werker, 1997).
-
-we can still use its general idea (especially the fact that cues from a given modality are used according to their relative reliability) to revisit some findings in the literature and specualate about new interpretations.
-For instance, Sloutsky and Napolitano (2003) reported a peceptual dominance for the auditory modality in children, and showed that this dominance disappears or reverses in adults.
-The authors attribute this dominance to the fact that auditory is more transient, and therefore tend to attract more attention (I should elaborate more on this).
-According to this interpretation, children should weight modalities in the same way regerdless of the stimuli used.
-Another interpretation, inspired by our model, would suggest that the precise sound and object contrasts used as stimuli in this series of experiments differ in their relative salience to children.
-One way to disentangle these two interpretations is to use an audio-visual stimuli where the sound contrast is reduced to a perceptual minimum and/or where the visual contrast is enhanced.
-An optimal-based account would suggest that the weighting would reverse in this case.
-
-In a different line of work, it has been shown that infants have difficulties mapping two minimally different words to two novel objects, despite the fact that they can perceptually differentiate these words (e.g., Stager & Werker, 1997).
-This pattern of results has mostly been undertood as ‘failure’ in learning.
-Another interpretation  would explain this pattern of results based on developmental changes in the variance associated with the visual and phonological categories.
-If the categories get refined over time (that is, if the variances become smaller), then contrasts that used to fall under one category, may later fall under two separate categories.
-That is, rather than interpreting the null result as a failure in learning, these children might just have learned one word category instead of two categories.
-In particular, it is possible that the visual stimuli used in Stage and Werker (1997) were quite similar in the 14 m.o's early conceptual space, which made them believe that both objects were possible instances of the same semantic category.
-This, in turn, would make them interpret the sound difference as alternative pronunciations of the same word\footnote{The reverse reasining is plausible as well, and in fact, can explain why in the same experiment, the use of acoustically distant words ("lif"/"neem"" instead of "bin"/"din) made 14 m.o succeed in the same task}.
-A prediction of the optimal model would be that the use of semantically distant objects can induce success with the same similar sounding words.
-
-CONCLUSION
-
-To estimate the reliability (e.g., whether a token belong to one or the other category), one has to have access to the full probability distribution of the tokens,  For instance, @sloutsky2003 reported a dominance for the auditory modality in children, and This dominance disappears or reverses in adults
-
-n account helps us better understand the mechanisms of word processing and learning.
-
-We are working on extending this general framework to the case where neither the phonological, not the semantic categories are assumed to be present.
-Thus quantifying the synergy that might take place in development
-
-Can we understand word learning (and failure in learning as in Stager and Werker, 1997) in terms of developmental changes in the reliability (or the relative reliability) in the visual and auditory modalities?
-
-Computational principle behind bla bla
-
-What influence the combination is both the category dstribution (example), and also how rliabile at all (regarless of whether the token in)
-Here talk about theories of modality approp
-riateness theory. 
-Say that this is not what is going on here
-
-Talk about development
-In Experiment 1, the unceratinty was
-
- One possible explanation for this preference could be that people do not combine cross-modal uncertainties of a similar kind (e.g., ambiguity in both modalities) in the same way they would combine uncertainties of different kinds (e.g., ambiguity in one modality and noise in the other).
-For instance, it could be that the latter, but not the former, cause the over-reliance on a particular modality.
-
-There were, however, quantitative differences.
-Audio-visual presentation increased the level of randomness in the participants' responses.
-One possible explanation is that this phenomenon was caused by the arbitrary nature of the form-meaning mapping.
-Previous studies suggest that while redundant multimodal information improves performance (e.g., determining the frequency of a bouncing ball from visual and auditory cues), arbitrary mappings generally tends to hinder performance [for review, see @robinson2010].
-
-Interestingly, however, in Experiment 1 this increase in randomness occurred at a similar rate for both the auditory and the visual modality, and thus, it did not affect their relative weighting.
-The latter was primarily determined by informational reliability.
-Only when we intervened by adding  noise to one modality in Experiment 2, did participants show a systematic preference for the non-noisy modality.
-One possible explanation for this preference could be that people do not combine cross-modal uncertainties of a similar kind (e.g., ambiguity in both modalities) in the same way they would combine uncertainties of different kinds (e.g., ambiguity in one modality and noise in the other).
-For instance, it could be that the latter, but not the former, cause the over-reliance on a particular modality.
-
-Overall, in both Experiments, the majority of the variance could be explained by an ideal observer that combined multimodal information optimally.
-In the light of this main result, we can revisit some previous findings in the literature.
-For instance, @sloutsky2003 reported a dominance for the auditory modality in children.
-This dominance disappears or reverses in adults.
-Could this difference be driven by changes across development in the level of perceptual noise affecting the intrinsic relative reliability of modalities (by analogy to Experiment 2)?
-More work is needed to carefully examine this (and other) speculations, and more generally, to determine the extent to which the optimal combination account helps us better understand the mechanisms of word processing and learning.
-
--->
+$$\beta_v=\frac{\mu_{V1}-\mu_{V2}}{\sigma^2_{V}}.$$
+
+# Acknowledgements
+
+This work was supported by a post-doctoral grant from the Fyssen Foundation + XXX
 

### 2018-04-26 Writeup/ms.tex
modif ms

@@
   \abstract{Identifying a spoken word in a referential context requires both the
-ability to process and integrate multimodal input and the ability to
-reason under uncertainty. How do these tasks interact with one another?
-We introduce a task that allows us to examine how adults identify words
-under joint uncertainty in the auditory and visual modalities. We
-propose an ideal observer model which provides an account of how
-auditory and visual cues are combined optimally. Model predictions are
-tested in three experiments where word recognition is made under two
-kinds of uncertainty: category ambiguity and/or distorting noise. In all
-cases, the optimal model explains much of the variance in human mean
-judgments. In particular, when the signal is not distorted with noise,
-participants weight the auditory and visual cues optimally, that is,
-according to the relative reliability of each modality. But when one
-modality has noise added to it, human perceivers systematically prefer
-the unperturbed modality to a greater extent than the optimal model
-does. The study provides a formal framework which helps us understand
-precisely how word form and word meaning interact in word recognition
-under uncertainty. Moreover it offers a first step towards a model that
-accounts for form-meaning synergy in early word learning.}
+ability to integrate multimodal input and the ability to reason under
+uncertainty. How do these tasks interact with one another? We introduce
+a task that allows us to examine how adults identify words under joint
+uncertainty in the auditory and visual modalities. We propose an ideal
+observer model which provides an account of how auditory and visual cues
+are combined optimally. Model predictions are tested in three
+experiments where word recognition is made under two kinds of
+uncertainty: category ambiguity and/or distorting noise. In all cases,
+the optimal model explains much of the variance in human mean judgments.
+In particular, when the signal is not distorted with noise, participants
+weight the auditory and visual cues optimally, that is, according to the
+relative reliability of each modality. But when one modality has noise
+added to it, human perceivers systematically prefer the unperturbed
+modality to a greater extent than the optimal model does. The study
+provides a formal framework which helps us understand precisely how word
+form and word meaning interact in word recognition under uncertainty.
+Moreover it offers a first step towards a model that accounts for
+form-meaning synergy in early word learning.}
   \keywords{Language understanding; audio-visual processing; word learning; speech
@@
 considered to be an crucial instance of early word learning. For
-example, many studies focused on how children succeed in this task
+example, many studies focused on how children might succeed in this task
 despite high referential ambiguity (Medina, Snedeker, Trueswell, \&
@@
 words, listeners (both children and adults) often face the task of
-recognizing which word the speaker has uttered, especially under noisy
-circumstances. The purpose of the current study is to explore the
-special case of word recognition under uncertainty when adult observers
-have access to multimodal cues from the speech and the referent.
+recognizing which word the speaker utters, especially under noisy
+circumstances (Mattys, Davis, Bradlow, \& Scott, 2012; Peelle, 2018).
+The purpose of the current study is to explore novel word recognition by
+adults under multimodal uncertainty. We focus on the special case where
+people have access to multimodal cues from the auditory speech and the
+visual referent.
 
@@
   can also be seen as an instance of Marr's computational level of
-  analysis.} When there is uncertainty in the input, the ideal observer
-performs an optimal probabilistic inference. For example, in order to
-recognize an ambiguous linguistic input, the model uses all available
-probabilistic knowledge in order to maximize the accuracy of this
-recognition. The ideal observer model can be seen as a theoretical upper
-limit on performance. It is not so much a realistic model of human
+  analysis (Marr, 1982).} When there is uncertainty in the input, the
+ideal observer performs an optimal probabilistic inference. For example,
+in order to recognize an ambiguous linguistic input, the model uses all
+available probabilistic knowledge in order to maximize the accuracy of
+this recognition. The ideal observer model can be seen as a theoretical
+upper limit on performance. It is not so much a realistic model of human
 performance, as much as a baseline against which human performance can
@@
 judgments closely reflected the optimal predictions. In another work,
-Feldman et al. (2009) studied the perceptual magnet effect, which is a
-phenomenon that involves reduced discriminability near prototypical
-sounds in the native language (Kuhl, 1991). They showed that this effect
-can be explained as the consequence of optimally solving the problem of
+Feldman et al. (2009) studied the perceptual magnet effect, a phenomenon
+that involves reduced discriminability near prototypical sounds in the
+native language (Kuhl, 1991). They showed that this effect can be
+explained as the consequence of optimally solving the problem of
 perception under uncertainty.
@@
 whereas the visual input represents the \emph{meaning}. It has been
-suggested that because of its referential property, speech is a
-privileged signal for humans, starting in infancy (see Vouloumanos \&
-Waxman, 2014 for a review).\footnote{There is a debate as to whether
-  speech is privileged for children and adults for the same reasons.
-  Whereas some researchers suggest that speech is privileged for both
-  children and adults because of its ability to refer (e.g., Waxman \&
-  Markow, 1995), others suggest that speech might \emph{not} have a
-  referential status from the start. Rather, speech might be preferred
-  by children only because of a low level auditory ``overshadowing''
-  (e.g., Sloutsky \& Napolitano, 2003).} Thus, in a referential context,
-it is possible that listeners do not treat the auditory and visual
-modalities as equivalent sources of information. Instead, there could be
-a sub-optimal bias for the auditory modality beyond what is expected
-from informational reliability alone.
+shown that speech has a privileged status compared to other sensory
+stimuli (Edmiston \& Lupyan, 2015; Lupyan \& Thompson-Schill, 2012;
+Vouloumanos \& Waxman, 2014; Waxman \& Gelman, 2009; Waxman \& Markow,
+1995), and that this privilege is indeed related to the speech's ability
+to refer (Waxman \& Gelman, 2009).\footnote{There is, however, a debate
+  as to whether speech is privileged for children and adults for similar
+  reasons. Whereas some researchers suggest that speech is privileged
+  for both children and adults because of its ability to refer (e.g.,
+  Waxman \& Gelman, 2009), others suggest that speech might \emph{not}
+  have a referential status from the start. Rather, speech might be
+  preferred by children only because of a low level auditory
+  ``overshadowing'' (e.g., Sloutsky \& Napolitano, 2003).} Thus, in a
+referential context, it is possible that listeners do not treat the
+auditory and visual modalities as equivalent sources of information.
+Instead, there could be a sub-optimal bias for the auditory modality
+beyond what is expected from informational reliability alone.
 
@@
 degrees, do they weight each modality according to its relative
-reliability (which is the optimal strategy), or do they over-rely on a
-particular modality (which is a sub-optimal strategy)?
+reliability, which is the optimal strategy, or do they over-rely on a
+particular modality, which is a sub-optimal strategy?
 
@@
 
-We introduce a new task that tests word recognition in a referential
-context. We use two visual categories (cat and dog) and two auditory
-categories (/b/ and /d/ embedded in the minimal pair /aba/-/ada/). For
-each participant, an arbitrary pairing is set between the auditory and
-the visual categories, leading to two audio-visual word categories
-(e.g., dog-/aba/, cat-/ada/). In each trial, participants are presented
-with an audio-visual target (the prototype of the target category),
-immediately followed by an audio-visual test stimulus
+We introduce a task adapted from Sloutsky and Napolitano (2003). The
+original task has been used with both children and adults to probe
+audio-visual encoding (see Robinson \& Sloutsky, 2010 for a review).
+Here we use a slightly different version to test word recognition in a
+referential context. We use two visual categories (cat and dog) and two
+auditory categories (/b/ and /d/ embedded in the minimal pair
+/aba/-/ada/). For each participant, an arbitrary pairing is set between
+the auditory and the visual categories, leading to two audio-visual word
+categories (e.g., dog-/aba/, cat-/ada/). In each trial, participants are
+presented with an audio-visual target (the prototype of the target
+category), immediately followed by an audio-visual test stimulus
 (Figure~\ref{fig:task}). The test stimulus may differ from the target in
@@
 
-This paradigm is adapted from a previous task (Sloutsky \& Napolitano,
-2003), which has been used with both children and adults to probe
-audio-visual encoding (see Robinson \& Sloutsky, 2010 for a review). In
-the testing phase of the original task, participants are asked whether
-or not the two audio-visual presentations are \emph{identical}. In the
-current study, we are interested, rather, in the categorization, i.e.,
-determining whether or not two similar tokens are members of the same
-phonological/semantic category. Therefore, testing in our task is
-category-based: Participants are asked to press \enquote{same} if they
-think the second item (the test) belongs to the same category as the
-first (target) (e.g., dog-/aba/), even if there is a slight difference
-in the sound, in the referent, or in both. They are instructed to press
-\enquote{different} only if they think that the second stimulus was an
-instance of the other category (cat-/ada/). The task also includes
-trials where pictures are hidden (audio-only) or where sounds are muted
-(visual-only). These unimodal trials provide us with the participants'
-evaluation of the probabilistic information present in the auditory and
-visual categories. As we shall see, these unimodal distributions are
-used as inputs to the optimal cue combination model.
+In the testing phase of the original task (Sloutsky \& Napolitano,
+2003), participants are asked whether or not the two audio-visual
+presentations are \emph{identical}. In the current study, we are
+interested, rather, in the categorization, i.e., determining whether or
+not two similar tokens are members of the same phonological/semantic
+category. Therefore, testing in our task is category-based: Participants
+are asked to press \enquote{same} if they think the second item (the
+test) belongs to the same category as the first (target) (e.g.,
+dog-/aba/), even if there is a slight difference in the sound, in the
+referent, or in both. They are instructed to press \enquote{different}
+only if they think that the second stimulus was an instance of the other
+category (cat-/ada/). The task also includes trials where pictures are
+hidden (audio-only) or where sounds are muted (visual-only). These
+unimodal trials provide us with the participants' evaluation of the
+probabilistic information present in the auditory and visual categories.
+As we shall see, these unimodal distributions are used as inputs to the
+optimal cue combination model.
 
@@
 Bankieris, Bejjanki, \& Aslin, 2017; Bejjanki et al., 2011). In what
-follows, we describe a model that accounts for both type of variability.
-First, we describe the model in the simplified case of categorical
-variability only. Second, we augment this simplified model to account
-for sensory noise.
+follows, we describe a model that accounts for both types of
+variability. First, we describe the model in the simplified case of
+categorical variability only. Second, we augment this simplified model
+to account for sensory noise.
 
@@
 pronounced does not correlate with changes in any visual property of the
-object CAT, which is a valid
-assumption.\footnote{Note that this assumptions is more adequate in the case of arbitrary associations such as ours, and less so in the case of redundant association such as audio-visual speech.
+object CAT, which is a valid assumption in the context of our
+task.\footnote{Note that this assumptions is more adequate in the case of arbitrary associations such as ours, and less so in the case of redundant association such as audio-visual speech.
 In the latter, variation in the pronunciation is expected to correlate, at least to some extent, with lip movements.}
@@
 stimuli. Finally, observations from each modality (\(a\) and \(v\)) are
-weighted in Equation 1 according to their reliability:
+weighted in Equation 1 according to their reliability (that is,
+according to the \emph{inverse} of their variance):
 \[\beta_a \propto \frac{1}{\sigma^2_{A}}\]
@@
 distributed, that is, \(p(a | a_t) \sim N(a_t, \sigma^2_{N_A})\), then
-integrating over \(a_t\) leads to the following simple expression:
-\[ p(a | A) \sim N(\mu_{A}, \sigma^2_{A}+\sigma^2_{N_A})\] Similarly, in
-the case of sensory noise in the visual modality, we get
+integrating over \(a_t\) leads to this new expression of the probability
+distribution: \[ p(a | A) \sim N(\mu_{A}, \sigma^2_{A}+\sigma^2_{N_A})\]
+Similarly, in the case of sensory noise in the visual modality, we get:
 \[ p(a | V) \sim N(\mu_{V}, \sigma^2_{V}+\sigma^2_{N_V})\] Finally,
@@
 visual modalities can be combined to make categorical decisions.
-Parameters' estimates of the probability distributions in each modality
+Parameter estimates of the probability distributions in each modality
 are derived by fitting unimodal posteriors to the participants'
@@
 Using these derived parameters, the optimal model makes predictions
-about responses in the bimodal condition where participants both hear
-the sounds and see the pictures.
+about responses in the bimodal (i.e., audio-visual) condition where
+participants both hear the sounds and see the pictures.
 
@@
 measure of cross-modal weighting is because this proportion corresponds
-to the slope\footnote{Or more precisely the absolute value of the slope}
-of the decision threshold in the audio-visual space
+to the
+slope\footnote{Or more precisely the absolute value of the slope.} of
+the decision threshold in the audio-visual space
 (Figure~\ref{fig:model}). The decision threshold is defined as the set
@@
 Experiment 1, we studied the case where bimodal uncertainty was due to
-categorical variability, only. In Experiment 2 and 3 we added noise in
-the background on top of categorical variability.
+categorical variability, only. In Experiment 2 and 3 we added auditory
+and visual noise, respectively, on top of categorical variability.
 
@@
 negligible compared to categorical variability
-(\(\sigma^2_{A} \gg \sigma^2_{N_A}\), and
+(\(\sigma^2_{A} \gg \sigma^2_{N_A}\) and
 \(\sigma^2_{V} \gg \sigma^2_{N_V}\)). Thus, we use the following cue
@@
 of 70 trials/participant. Trials were blocked by condition and blocks
-were presented in random order. The experiment lasted around 15 minutes.
+were presented in random order. The experiment lasted around 15
+minutes.\footnote{The experiment can be accessed and played from the
+  github repository: \url{https://github.com/afourtassi/WordRec/}}
 
@@
 
-\paragraph{Unimodal condition}\label{unimodal-condition}
-
-Remember that data in this conditions allow us to derive the variances
+\paragraph{Unimodal conditions}\label{unimodal-conditions}
+
+Remember that data in these conditions allows us to derive the variances
 of both the auditory and the visual categories, and that these variances
@@
 statistical power to fit a different model for each individual
-participant. Instead, models were constructed with data collapsed across
-all participants. That being said, the distribution of responses from
-individual participants will also be analyzed. The fit was done with a
-nonlinear least squares regression using the NLS package in R (Bates \&
-Watts, 1988). We computed the values of the parameters, as well as their
-95\% confidence intervals, through non-parametric bootstrap (using 10000
-iterations).
+participant.\footnote{We had a relatively high number of trials spanning
+  all possible audio-visual matchings. Getting enough data points per
+  trial per participant would have required running the online
+  experimental for a much longer time (more than an hour). This could
+  have increased significantly the dropout rate and possibly affected
+  the quality of the data collected online.} Instead, models were
+constructed with data collapsed across all participants. That being
+said, we will also analyze the distribution of individual responses. The
+fit was done with a nonlinear least squares regression using the NLS
+package in R (Bates \& Watts, 1988). We computed the values of the
+parameters, as well as their 95\% confidence intervals, through
+non-parametric bootstrap (using 10000 iterations).
 
@@
 
-\subsubsection{Unimodal conditions}\label{unimodal-conditions}
+\subsubsection{Unimodal conditions}\label{unimodal-conditions-1}
 
@@
 categorically and whih higher certainty than they did with the visual
-tokens. For the auditory modality, we obtained the following
-values:\footnote{all CIs in the paper are 95\% confidence intervals.}
+tokens. For the auditory modality, we obtained the following values:
 \(b_A=\) -0.20 {[}0.02, -0.38{]} and \(\sigma^2_A=\) 2.04 {[}1.66,
@@
 \begin{figure}[!h]
-\includegraphics[width=\textwidth]{ms_files/figure-latex/unimodal-1} \caption{Human responses in the unimodal conditions.
+\includegraphics[width=\textwidth]{ms_files/figure-latex/unimodal-1} \caption{Human responses in the unimodal conditions across the three experiments.
 Points represent the proportion of `different' to `same' responses in the auditory-only condition (left), and visual-only condition (right).
 Error bars are 95\% confidence intervals.
-Solid lines represent best fits.}\label{fig:unimodal}
+Solid lines represent best unimodal posterior fits.}\label{fig:unimodal}
 \end{figure}
@@
 Figure~\ref{fig:bimodal} compares the predictions of the normative
-models against human responses. The visual, auditory and optimal model
-explained, respectively, 30\%, 67\%, and 89\% of total variance in mean
-responses.
+models against human responses. Remember that the normative models use
+variance estimates from the unimodal conditions (where people see input
+from only one modality) to predict data in the bimodal condition (where
+people see input from both modalities). Each point represents data form
+a particular audio-visual matching (e.g., the visual token \(v\) whose
+distance from the target \(v_t\) is \(|v-v_t|=3\), matched with the
+auditory token \(a\) whose distance from the target \(a_t\) is
+\(|a-a_t|=2\)). The visual, auditory and optimal model explained,
+respectively, 30\%, 67\%, and 89\% of total variance in mean responses.
 
@@
 \includegraphics[width=\textwidth]{ms_files/figure-latex/bimodal-1} \caption{Human responses vs.
-models' predictions in the bimodal condition.
-Shape represents auditory distance from the target, and color represents visual distance from the target.}\label{fig:bimodal}
+Models' predictions in the bimodal condition across the three experiments.
+Each point represents data form a particular audio-visual matching.
+Shape represents auditory distance from the target, and color represents visual distance from the target.
+Thus, each point is characterized by both  shape and color.}\label{fig:bimodal}
 \end{figure}
@@
 did not affect the relative weighting of both modalities, i.e., the
-population was weighting modalities according to the relative
+participants was weighting modalities according to the relative
 reliability predicted by the optimal model. This situation corresponds
@@
 \begin{figure}[!h]
-\includegraphics[width=\textwidth]{ms_files/figure-latex/individual-1} \caption{Histograms of the individual values of the visual variance relative to the auditory variance in Experiment 1.
-Light color represents the values derived from each individual participant, and dark color represents simulated individual responses sampled from the descriptive model.}\label{fig:individual}
+\includegraphics[width=\textwidth]{ms_files/figure-latex/individual-1} \caption{Distributions of individual values of the visual variance relative to the auditory variance in Experiment 1.
+Light color represents the real individual distribution, and dark color represents the simulated individual distribution sampled from the descriptive model.}\label{fig:individual}
 \end{figure}
@@
 deviation of \(sd=\) 2.24 which was larger than that of the simulated
-distribution (\(sd=\) 1.16), indicating that there was real
+distribution (\(sd=\) 1.10), indicating that there was real
 between-subject variation beyond sampling errors. This finding means
@@
 tokens can undergo distortions due to noisy factors in the environment
-(e.g., car noise in the background, blurry vision in a foggy
-weather,..). In Experiment 2 and 3, we explore this additional level of
-uncertainty.
+(e.g., car noise in the background, blurry vision in a foggy weather).
+In Experiment 2 and 3, we explore this additional level of uncertainty.
 
@@
 
-\subsubsection{Unimodal conditions}\label{unimodal-conditions-1}
+\subsubsection{Unimodal conditions}\label{unimodal-conditions-2}
 
@@
 total variance. Cross-validation using half the responses to predict the
-other half yielded \(r^2 =\) 0.95.
+other half yielded \(r^2 =\) 0.96.
 
@@
 10), the percentage of participants who relied exclusively on either
-modalities was 34.41\%, which is much higher than the percentage
-obtained in Experiment 1 (21.25\%). Moreover, the subset of participants
-relying exclusively on the visual modality (compared to those who relied
+modality was 34.41\%, which is much higher than the percentage obtained
+in Experiment 1 (21.25\%). Moreover, the subset of participants relying
+exclusively on the visual modality (compared to those who relied
 exclusively on the auditory modality) increased from 29.41\% in
@@
 editor GIMP (2.8.20). We used a Gaussian blur with a
-radius\footnote{A features that modulates the intensity of the blur} of
+radius\footnote{A features that modulates the intensity of the blur.} of
 10 pixels. The experimental procedure was exactly the same as in the
@@
 In these cases, deviation from  optimality is due to over-lying on the visual or the auditory input by a factor of 2 (green and blue dotted lines, respectively).
-B) The value of the decision threshold's slope derived from the descriptive model relative to that of the optimal model.
+B) An alternative way to represent the same data.
+Each point represents the value of the decision threshold's slope derived from the descriptive model relative to that of the optimal model (log-scaled).
+The lines represent the optimal case as well as the two hypothetical cases of modality preference.
 Error bars represent 95\% confidence intervals over the distribution obtained through non-parametric resampling.}\label{fig:bias}
@@
 
-\subsubsection{Unimodal conditions}\label{unimodal-conditions-2}
+\subsubsection{Unimodal conditions}\label{unimodal-conditions-3}
 
@@
 \caption{\label{tab:exclusive}The percentage of participants who relied exclusively on either the visual modality or the auditory modality, using a factor of 10 as a cut-off (e.g., we consider that a participant relied exclusively on the visual modality when their auditory variance is a at least 10 times larger than their visual variance).
-We show the percentage compared to the total number of participants in each Experiment (`Total').
+We show the percentage compared to the total number of participants in each Experiment (`of Total').
 From this subset of participants, we show the percentage of those who relied on the  auditory modality (`Auditory'), and the percentage of those who relied on the visual  modality (Visual').}
@@
 \toprule
-Experiment & \multicolumn{1}{c}{Total} & \multicolumn{1}{c}{Auditory} & \multicolumn{1}{c}{Visual}\\
+Experiment & \multicolumn{1}{c}{ofTotal} & \multicolumn{1}{c}{Auditory} & \multicolumn{1}{c}{Visual}\\
 \midrule
@@
 multimodal uncertainty in auditory speech and visual facial features
-(e.g. Bejjanki et al., 2011). The current work explored, for the first
-time, the case of word identification under uncertainty in speech (word
-form) and the visual \emph{referent}. More specifically, we conducted an
-ideal observer analysis of the task whereby a model provided predictions
-about how information from each modality should be combined in an
-optimal fashion. The predictions of the model were tested in a series of
-three experiments where instances of both the form and the meaning were
+(e.g. Bejjanki et al., 2011). The current work explored the case of word
+identification under uncertainty in speech (word form) and the visual
+\emph{referent}. More specifically, we conducted an ideal observer
+analysis of the task whereby a model provided predictions about how
+information from each modality should be combined in an optimal fashion.
+The predictions of the model were tested in a series of three
+experiments where instances of both the form and the meaning were
 ambiguous with respect to their category membership only (Experiment 1),
@@
 reliability. At the individual level, however, we found evidence of a
-between-subject variation: Some participants relied slightly more on the
-visual modality, whereas others relied slightly more on the auditory
-modality.
+between-subject variation: Some participants relied more on the visual
+modality, whereas others relied more on the auditory modality.
 
@@
 can cause general performance to drop. Indeed, there is evidence that
-cognitive load has a detrimental effect on word recognition. This
-phenomenon can be due to a reduction in perceptual acuity (e.g., Mattys
+cognitive load due to divided attention (e.g., when performing two tasks
+at the same time) has a detrimental effect on word recognition (Mattys
 \& Wiget, 2011).
@@
 besides providing more evidence to this documented fact, suggests that
-the apparent reduction in perceptual acuity may occurs simultaneously in
-both the auditory \emph{and} the visual modalities.
+the reduction in perceptual acuity may occur simultaneously in both the
+auditory \emph{and} the visual modalities.
 
@@
 participants had a systematic preference for the other (non-noisy)
-modality. From previous empirical studies, we know that when the speech
-signal is degraded, people tend to compensate by relying more on other
-sources of information such as the accompanying visual cues (i.e., lip
-movements) or the semantic/syntactic context (see Mattys, Davis,
-Bradlow, \& Scott, 2012 for a review). However, and generally speaking,
-these studies do not differentiate between an optimal compensatory
-strategy (i.e., relying more on the alternative source while using all
-information still available in the distorted signal), and a sub-optimal
-strategy (i.e., relying more on the alternative source while ignoring at
-least some of the information still available in the distorted signal).
-The formal approach followed in this paper allowed us to tease apart
-these two possibilities, and our analysis supports the sub-optimal
-compensatory strategy: The preference for the non-noisy modality is
-above and beyond what can be explained by the relative reliability
-alone, meaning that the participants tend to ignore at least part of the
-information still available in the noisy modality.
+modality. When the speech signal is degraded, people, in previous work,
+were shown to compensate by relying more on other sources of information
+such as the accompanying visual cues, the semantic/syntactic context, or
+the top-down expectations. This kind of compensation has been observed
+with adults (Mattys et al., 2012; McClelland, Mirman, \& Holt, 2006;
+Tanenhaus et al., 1995), and recent evidence suggests that it starts in
+childhood (K. MacDonald, Marchman, Fernald, \& Frank, 2018; Yurovsky,
+Case, \& Frank, 2017). However, and generally speaking, previous
+experimental studies have not differentiated between an optimal
+compensatory strategy (i.e., relying more on the alternative source
+while using all information still available in the distorted signal),
+and a sub-optimal strategy (i.e., relying more on the alternative source
+while ignoring at least some of the information still available in the
+distorted signal). The formal approach followed in this paper allowed us
+to tease apart these two possibilities, and our analysis supports the
+sub-optimal compensatory strategy: The preference for the non-noisy
+modality is above and beyond what can be explained by the relative
+reliability alone, meaning that the participants tend to ignore at least
+part of the information still available in the noisy modality.
 
@@
 that language understanding under degraded conditions is cognitively
-more taxing than language understanding under normal conditions (e.g.,
-Ronnberg, Rudner, Lunner, \& Zekveld, 2010). This fact can lead to a
-bias against the more noisy cue. One could also explain this phenomenon
-in terms of the metacognitive experience about the fluency with which
+more taxing than language understanding under normal conditions (Mattys
+et al., 2012; Peelle, 2018; Rönnberg, Rudner, Lunner, Zekveld, \&
+others, 2010). This fact can lead to a sub-optomal behavior (i.e.,
+over-reliance on the less noisy cue) as participants would seek to
+minimized cognitive effort. One could also explain this phenomenon in
+terms of the metacognitive experience about the fluency with which
 information is processed. The perceived perceptual fluency (e.g., the
@@
 referents (cat-dog) were similar and, thus, confusable. However, to what
-extent does such case occur in real languages? Cross-linguistic corpus
+extent does such a case occur in real languages? Cross-linguistic corpus
 analyses suggest that lexical encoding tends, surprisingly, towards
@@
 words.\linebreak That being said, besides the case of double ambiguity
-intrinsic to language, there are two situations where our mechanism
-might play a significant role. The first is when ambiguity in both the
-form and/or the referent is induced by an external noisy context even
-when these forms and referents are not confusable in normal situations.
-The second case is that of early word recognition/learning, and we will
-discuss this case in more detail in what follows.
+\emph{intrinsic} to language, our mechanism might play a more
+significant role when ambiguity in both the form and/or the referent is
+induced by an \emph{external} noisy context even when these forms and
+referents are not confusable in normal situations.
 
@@
 recognition under uncertainty, as well as the need to make the most of
-ambiguous cues, is a particularly pressing issue for children. In fact,
-whereas adults are mostly faced with uncertainty in the \emph{input},
-children have to deal with the additional uncertainty that results from
-their early unrefined \emph{representations} of both phonological and
-semantic categories. For example, upon hearing a noisy instance of
-\enquote{bee}, adults may have to decide whether the speaker intended to
-say \enquote{pea} or \enquote{bee}, but children can additionally be
-uncertain whether \enquote{bee} is a different word from \enquote{pee}
-(as opposed to, say, a valid within category variation), especially if
-these similar sounding words are newly learned (Creel, 2012; Merriman \&
+the available cues, is arguably more pressing for children. In fact,
+children have greater difficulties differentiating the meanings of novel
+similar-sounding words (e.g., \enquote{bin} vs. \enquote{din}), even
+when these words are uttered very clearly (Creel, 2012; Merriman \&
 Schuster, 1991; Stager \& Werker, 1997; Swingley, 2016; White \& Morgan,
-2008). Though similar word form representation can be shown to be
-differentiated under some circumstances (e.g., Yoshida, Fennell,
-Swingley, \& Werker, 2009), this differentiation is still not mature
-enough and is probably noisier than the adult-like representation and/or
-encoded with lower confidence (see Swingley, 2007).
-
-At the semantic level, early representations have, similarly, an
-intrinsically fragile and uncertain status. For example, upon seeing a
-bee in a foggy weather, adults may be uncertain if they saw a bee or a
-fly. But on top of this perceptual uncertainty, children may not be
-certain if the semantic category being named is that of bees and only
-bees, or if it includes other small flying insects like flies and
-beetles. In fact, though children can be fast at learning a first
-approximation of a given word's referent (Carey \& Bartlett, 1978), the
-refinement of this early approximation into a mature semantic category
-is a slow and gradual process (see also Bion, Borovsky, \& Fernald,
-2013; Carey, 2010; Fernald, Perfors, \& Marchman, 2006; McMurray, Horst,
-\& Samuelson, 2012). Among other things, children have to enrich this
-early representation with new features, and revise its extension in the
-light of new referential exposures. In sum, uncertainty in the
-representation associated with one modality (e.g., a bee and a fly) can
-be mitigated through the possibly more differentiated representations
-associated with the other modality (e.g., the sound \enquote{bee} is
-acoustically different from the sound \enquote{fly}).
+2008). Such similar-sounding words can be shown to be differentiated by
+infants in simplified experimental settings (e.g., Yoshida, Fennell,
+Swingley, \& Werker, 2009). Nevertheless, Swingley (2007) suggested this
+differentiation is not mature and is probably noisier than the
+adult-like representation and/or encoded with lower confidence. Thus, it
+looks like children, even more than adults, may greatly benefit from
+additional disambiguating cues during new word-referent encoding and
+recognition. For example, Dautriche, Swingley, and Christophe (2015)
+showed that 18-month-olds can leverage the difference in the syntactic
+category (noun vs.~verb). Further work is needed to explore whether
+salient referential cues also help children disambiguate similar
+sounding words.
 
 The multi-modal cue combination strategy might help children not only
-recognize an individual word instance, but also refine the underlying
-phonological and semantic representations in the process. Previous
-research in early word learning has---whether implicitly or
-explicitly---largely treated the process of learning form and of
-learning meaning as independent. However, the developmental data
-reviewed above shows that children do not wait to have completed the
-acquisition of form to start learning meanings, and that both form and
-meaning representations develop, rather, in a parallel fashion. A few
-studies pointed to the possibility of an interaction between sound and
-meaning in early acquisition. For instance, Waxman and Markow (1995)
-showed that labeling various objects with the same name helps infants
-form the broad semantic category (but see Sloutsky \& Napolitano, 2003).
-Vice versa, Yeung and Werker (2009) showed that pairing similar sounds
-with different objects help infants pay attention to subtle phonological
-contrasts. The present study proposes a first step towards a formal
-framework where isolated accounts of sound-meaning interaction in
-development can be unified and further explored.
+recognize words, but also refine the underlying phonological and
+semantic representations in the process. Previous research in early word
+learning has---whether implicitly or explicitly---largely treated the
+process of refining the word form and of refining the word meaning as
+follwing a linear timeline However, recent developmental data shows that
+children do not wait to have completed the acquisition of forms to start
+learning the meanings (Bergelson \& Swingley, 2012; Tincoff \& Jusczyk,
+1999). Rather, both form and meaning representations develop in a
+parallel fashion. A few studies pointed to the possibility of an
+interaction between sound and meaning in early acquisition. For
+instance, Waxman and Markow (1995) showed that labeling various objects
+with the same name helps infants form the underlying semantic category
+(but see Sloutsky \& Napolitano, 2003). Vice versa, Yeung and Werker
+(2009) showed that pairing similar sounds with different objects help
+infants enhance their sensitivity to the subtle phonological contrasts
+in their native language. The present study proposes a first step
+towards a formal framework where isolated accounts of sound-meaning
+interaction in development can be unified and further explored.
 
@@
 is likely to involve a multifaceted research approach,
-involving---besides laboratory experiments---analyses of corpora with a
-more realistic multimodal input (e.g., Fourtassi, Schatz, Varadarajan,
-\& Dupoux, 2014; Harwath, Torralba, \& Glass, 2016; B. C. Roy, Frank,
-DeCamp, \& Roy, 2015).
+involving---besides conducting laboratory experiments---testing
+computational mechanisms with an input that represents, more accurately,
+the complexity of multimodal variability in the learning environment
+(Dupoux, 2018; Fourtassi, Schatz, Varadarajan, \& Dupoux, 2014; Harwath,
+Torralba, \& Glass, 2016; B. C. Roy, Frank, DeCamp, \& Roy, 2015).
 
@@
 
-This work studied the mechanism of word identification under uncertainty
-in both the word form and the word referent. To our knowledge, this is
-the first study that performs an ideal observer analysis of this task.
-We found people to be near optimal in their cue combination: They
-weighted each modality according to its relative reliability. However,
-they also showed patterns of sub-optimality especially when the stimuli
-were perturbed with additional background noise. Though the present
-study did not directly address the issue of early word learning, it
-provides a framework where developmental questions can also be
+This work studied the mechanism of spoken word identification under
+uncertainty in both the form and the referent. We conducted an ideal
+observer analysis of this task. We found people to be near optimal in
+their cue combination (at least at the population level): They weighted
+each modality according to its relative reliability. However, they also
+showed patterns of sub-optimality especially when the stimuli were
+perturbed with additional background noise. This work provides a formal
+framework where old and new questions about word recognition in a
+referential context can be given a precise formulation. For instance, of
+particular interest is the case of iconicity, that is, when there is a
+resemblance between the sound of a word and its referent. Previous work
+has suggested that iconicity, among other things, helps with learning
+(and generalizing the meaning of) new words (see Dingemanse, Blasi,
+Lupyan, Christiansen, \& Monaghan, 2015 for a review). Using the
+research strategy in this paper, we can, for example, test whether
+iconicity has such an advantage becuase it mitigates the sub-optimal
+patterns observed with more arbitrary pairings. Finally, though the
+current framework only characterizes adult word recognition, it provides
+a first step towards a model where developmental questions can also be
 investigated. For instance, future work should explore whether children,
@@
 
-\hypertarget{ref-bion2013}{}
-Bion, R. A., Borovsky, A., \& Fernald, A. (2013). Fast mapping, slow
-learning: Disambiguation of novel word-object mappings in relation to
-vocabulary learning at 18, 24, and 30 months. \emph{Cognition},
-\emph{126}(1), 39--53.
+\hypertarget{ref-bergelson2012}{}
+Bergelson, E., \& Swingley, D. (2012). At 6 to 9 months, human infants
+know the meanings of many common nouns. \emph{Proceedings of the
+National Academy of Sciences}, \emph{109}(9).
 
@@
 
-\hypertarget{ref-carey2010}{}
-Carey, S. (2010). Beyond fast mapping. \emph{Language Learning and
-Development}, \emph{6}(3), 184--205.
-
-\hypertarget{ref-carey1978b}{}
-Carey, S., \& Bartlett, E. (1978). Acquiring a single new word. In
-\emph{Proceedings of the Stanford Child Language Conference} (Vol. 15,
-pp. 17--29).
-
 \hypertarget{ref-chater06}{}
@@
 100 languages. \emph{Cognitive Science}, \emph{41}(8), 2149--2169.
+
+\hypertarget{ref-dautriche2015}{}
+Dautriche, I., Swingley, D., \& Christophe, A. (2015). Learning novel
+phonological neighbors: Syntactic category matters. \emph{Cognition},
+\emph{143}, 77--86.
+
+\hypertarget{ref-dingemanse2015}{}
+Dingemanse, M., Blasi, D. E., Lupyan, G., Christiansen, M. H., \&
+Monaghan, P. (2015). Arbitrariness, iconicity, and systematicity in
+language. \emph{Trends in Cognitive Sciences}, \emph{19}(10), 603--615.
+
+\hypertarget{ref-dupoux2018}{}
+Dupoux, E. (2018). Cognitive science in the era of artificial
+intelligence: A roadmap for reverse-engineering the infant
+language-learner. \emph{Cognition}, \emph{173}, 43--59.
 
@@
 
+\hypertarget{ref-edmiston2015}{}
+Edmiston, P., \& Lupyan, G. (2015). What makes words special? Words as
+unmotivated cues. \emph{Cognition}, \emph{143}, 93--100.
+
 \hypertarget{ref-ernst02}{}
@@
 \emph{116}(4), 752--782.
-
-\hypertarget{ref-fernald2006}{}
-Fernald, A., Perfors, A., \& Marchman, V. (2006). Picking up speed in
-understanding: Speech processing efficiency and vocabulary growth across
-the 2nd year. \emph{Developmental Psychology}, \emph{42}(1), 98--116.
 
@@
 \hypertarget{ref-havy2016}{}
-Havy, M., \& Waxman, S. R. (2016). Naming influences 9-month-olds'
+Havy, M., \& Waxman, S. (2016). Naming influences 9-month-olds'
 identification of discrete categories along a perceptual continuum.
@@
 
+\hypertarget{ref-lupyan2012}{}
+Lupyan, G., \& Thompson-Schill, S. L. (2012). The evocative power of
+words: Activation of concepts by verbal and nonverbal means.
+\emph{Journal of Experimental Psychology: General}, \emph{141}(1), 170.
+
+\hypertarget{ref-macdonald2018}{}
+MacDonald, K., Marchman, V., Fernald, A., \& Frank, M. C. (2018). Adults
+and preschoolers seek visual information to support language
+comprehension in noisy environments. In \emph{Proceedings of the 40th
+Annual Conference of the Cognitive Science Society}.
+
+\hypertarget{ref-marr1982}{}
+Marr, D. (1982). \emph{Vision}. WH Freeman.
+
 \hypertarget{ref-mattys11}{}
@@
 
+\hypertarget{ref-mcclelland2006}{}
+McClelland, J. L., Mirman, D., \& Holt, L. L. (2006). Are there
+interactive processes in speech perception? \emph{Trends in Cognitive
+Sciences}, \emph{10}(8), 363--369.
+
 \hypertarget{ref-mcgurk1976}{}
@@
 \emph{Nature}, \emph{264}, 746--748.
-
-\hypertarget{ref-mcmurray2012}{}
-McMurray, B., Horst, J. S., \& Samuelson, L. K. (2012). Word learning
-emerges from the interaction of online referent selection and slow
-associative learning. \emph{Psychological Review}, \emph{119}.
 
@@
 
+\hypertarget{ref-peelle2018}{}
+Peelle, J. E. (2018). Listening effort: How the cognitive consequences
+of acoustic challenge are reflected in brain and behavior. \emph{Ear and
+Hearing}, \emph{39}(2), 204.
+
 \hypertarget{ref-pinker1989}{}
@@
 Rahnev, D., \& Denison, R. N. (2018). Suboptimality in perceptual
-decision making. \emph{Behavioral and Brain Sciences}, 1?107.
+decision making. \emph{Behavioral and Brain Sciences}, 1--107.
 
@@
 
-\hypertarget{ref-Ronnberg10}{}
-Ronnberg, J., Rudner, M., Lunner, T., \& Zekveld, A. (2010). When
-cognition kicks in: Working memory and speech understanding in noise.
-\emph{Noise and Health}, \emph{12}(49), 263--269.
-
 \hypertarget{ref-roy2015}{}
@@
 Sciences}, \emph{112}.
+
+\hypertarget{ref-ronnberg2010}{}
+Rönnberg, J., Rudner, M., Lunner, T., Zekveld, A. A., \& others. (2010).
+When cognition kicks in: Working memory and speech understanding in
+noise. \emph{Noise and Health}, \emph{12}(49), 263.
 
@@
 
+\hypertarget{ref-tincoff1999}{}
+Tincoff, R., \& Jusczyk, P. W. (1999). Some beginnings of word
+comprehension in 6-month-olds. \emph{Psychological Science},
+\emph{10}(2), 172--175.
+
 \hypertarget{ref-vlach2013}{}
@@
 
+\hypertarget{ref-waxman2009}{}
+Waxman, S., \& Gelman, S. (2009). Early word-learning entails reference,
+not merely associations. \emph{Trends in Cognitive Sciences}.
+
 \hypertarget{ref-waxman1995}{}
@@
 
+\hypertarget{ref-yurovsky2017}{}
+Yurovsky, D., Case, S., \& Frank, M. C. (2017). Preschoolers flexibly
+adapt to linguistic input in a noisy channel. \emph{Psychological
+Science}, \emph{28}(1), 132--140.
+
 \end{document}

### 2018-04-26 Writeup/ms.Rmd
modif ms

@@
 
- Identifying a spoken word in a referential context requires both the ability to process and integrate multimodal input and the ability to reason under uncertainty.
+ Identifying a spoken word in a referential context requires both the ability to integrate multimodal input and the ability to reason under uncertainty.
 How do these tasks interact with one another?
@@
 The task of matching the sound to the corresponding visual object has been extensively studied in the developmental literature since it is considered to be an crucial instance of early word learning.
-For example, many studies focused on how children succeed in this task despite high referential ambiguity [@smith08; @pinker1989; @medina2011; @vouloumanos2008; @yurovsky2015; @suanda2014; @vlach2013].
-However, even when they know the exact meanings of the words, listeners (both children and adults) often face the task of recognizing which word the speaker has uttered, especially under noisy circumstances.
-The purpose of the current study is to explore the special case of word recognition under uncertainty when adult observers have access to multimodal cues from the speech and the referent.
+For example, many studies focused on how children might succeed in this task despite high referential ambiguity [@smith08; @pinker1989; @medina2011; @vouloumanos2008; @yurovsky2015; @suanda2014; @vlach2013].
+However, even when they know the exact meanings of the words, listeners (both children and adults) often face the task of recognizing which word the speaker utters, especially under noisy circumstances [@mattys12; @peelle2018].
+The purpose of the current study is to explore novel word recognition by adults under multimodal uncertainty.
+We focus on the special case where people have access to multimodal cues from the auditory speech and the visual referent.
 
@@
 This research strategy provides a characterization of the task/goal and shows what the optimal performance should be under this characterization.^[It is, thus, a general instance of the rational approach to cognition [@anderson90].
-It can also be seen as an instance of Marr's computational level of analysis.] When there is uncertainty in the input, the ideal observer performs an optimal probabilistic inference.
+It can also be seen as an instance of Marr's computational level of analysis [@marr1982].] When there is uncertainty in the input, the ideal observer performs an optimal probabilistic inference.
 For example, in order to recognize an ambiguous linguistic input, the model uses all available probabilistic knowledge in order to maximize the accuracy of this recognition.
@@
 They found that humans were sensitive to these probabilistic cues and their judgments closely reflected the optimal predictions.
-In another work, @feldman2009 studied the perceptual magnet effect, which is a phenomenon that involves reduced discriminability near prototypical sounds in the native language [@kuhl1991].
+In another work, @feldman2009 studied the perceptual magnet effect, a phenomenon that involves reduced discriminability near prototypical sounds in the native language [@kuhl1991].
 They showed that this effect can be explained as the consequence of optimally solving the problem of perception under uncertainty.
@@
 Indeed, the auditory input represents the *symbol* whereas the visual input represents the *meaning*.
-It has been suggested that because of its referential property, speech is a privileged signal for humans, starting in infancy [see @vouloumanos2014 for a review].^[There is a debate as to whether speech is privileged for children and adults for the same reasons.
-Whereas some researchers suggest that speech is privileged for both children and adults because of its ability to refer [e.g., @waxman1995], others suggest that speech might *not* have a referential status from the start.
+It has been shown that speech has a privileged status compared to other sensory stimuli [@vouloumanos2014; @waxman2009; @waxman1995; @edmiston2015; @lupyan2012], and that this privilege is indeed related to the speech's ability to refer [@waxman2009].^[There is, however, a debate as to whether speech is privileged for children and adults for similar reasons.
+Whereas some researchers suggest that speech is privileged for both children and adults because of its ability to refer [e.g., @waxman2009], others suggest that speech might *not* have a referential status from the start.
 Rather, speech might be preferred by children only because of a low level auditory ``overshadowing'' [e.g., @sloutsky2003].] Thus, in a referential context, it is possible that listeners do not treat the auditory and visual modalities as equivalent sources of information.
@@
 Vice versa, if they are not sure if they saw a bee or a fly, does it make them rely more on the sound?
-More importantly, when input in both modalities is uncertain to varying degrees, do they weight each modality according to its relative reliability (which is the optimal strategy), or do they over-rely on a particular modality (which is a sub-optimal strategy)?
+More importantly, when input in both modalities is uncertain to varying degrees, do they weight each modality according to its relative reliability, which is the optimal strategy, or do they over-rely on a particular modality, which is a sub-optimal strategy?
 
@@
 
-We introduce a new task that tests word recognition in a referential context.
+We introduce a task adapted from @sloutsky2003.
+The original task has been used with both children and adults to probe audio-visual encoding [see @robinson2010 for a review].
+Here we use a slightly different version to test word recognition in a referential context.
 We use two visual categories (cat and dog) and two auditory categories (/b/ and /d/ embedded in the minimal pair /aba/-/ada/).
@@
 
-This paradigm is adapted from a previous task [@sloutsky2003], which has been used with both children and adults to probe audio-visual encoding [see @robinson2010 for a review].
-In the testing phase of the original task, participants are asked whether or not the two audio-visual presentations are *identical*.
+In the testing phase of the original task [@sloutsky2003], participants are asked whether or not the two audio-visual presentations are *identical*.
 In the current study, we are interested, rather, in the categorization, i.e., determining whether or not two similar tokens are members of the same phonological/semantic category.
@@
 Indeed, our task involves responses over categorical variables (phonemes and concepts), and therefore, the optimal model should take into account, not only the noise variability around an individual perceptual estimate, but also its *categorical variability*, i.e., the uncertainty related to whether this perceptual estimate belongs to a given category [see also @Bankieris17; @bejjanki2011].
-In what follows, we describe a model that accounts for both type of variability.
+In what follows, we describe a model that accounts for both types of variability.
 First, we describe the model in the simplified case of categorical variability only.
@@
 
-\noindent This assumption says that, given a word-object mapping, e.g., $W=$("cat"-CAT), variation in the way "cat" is pronounced does not correlate with changes in any visual property of the object CAT, which is a valid assumption.\footnote{Note that this assumptions is more adequate in the case of arbitrary associations such as ours, and less so in the case of redundant association such as audio-visual speech.
+\noindent This assumption says that, given a word-object mapping, e.g., $W=$("cat"-CAT), variation in the way "cat" is pronounced does not correlate with changes in any visual property of the object CAT, which is a valid assumption in the context of our task.\footnote{Note that this assumptions is more adequate in the case of arbitrary associations such as ours, and less so in the case of redundant association such as audio-visual speech.
 In the latter, variation in the pronunciation is expected to correlate, at least to some extent, with lip movements.}
@@
 As for the means, their values are fixed, and they correspond to the most typical tokens in our stimuli.
-Finally, observations from each modality ($a$ and $v$) are weighted in Equation 1 according to their reliability: $$\beta_a \propto \frac{1}{\sigma^2_{A}}$$ $$\beta_v \propto \frac{1}{\sigma^2_{V}}.$$
+Finally, observations from each modality ($a$ and $v$) are weighted in Equation 1 according to their reliability (that is, according to the *inverse* of their variance): $$\beta_a \propto \frac{1}{\sigma^2_{A}}$$ $$\beta_v \propto \frac{1}{\sigma^2_{V}}.$$
 
@@
 For example, the observer might not have access to the exact produced target, but only to the target perturbed by noise.
-If we assume this noise to be normally distributed, that is,  $p(a | a_t) \sim N(a_t, \sigma^2_{N_A})$, then integrating over $a_t$ leads to the following simple expression:
+If we assume this noise to be normally distributed, that is,  $p(a | a_t) \sim N(a_t, \sigma^2_{N_A})$, then integrating over $a_t$ leads to this new expression of the probability distribution:
 $$ p(a | A) \sim N(\mu_{A}, \sigma^2_{A}+\sigma^2_{N_A})$$
-Similarly, in the case of sensory noise in the visual modality, we get
+Similarly, in the case of sensory noise in the visual modality, we get:
 $$ p(a | V) \sim N(\mu_{V}, \sigma^2_{V}+\sigma^2_{N_V})$$
@@
 Equation 1 provides the optimal model's predictions for how probabilities that characterize uncertainty in the auditory and the visual modalities can be combined to make categorical decisions.
-Parameters' estimates of the probability distributions in each modality are derived by fitting unimodal posteriors to the participants' responses in the unimodal conditions, i.e., the condition where only the sounds are heard  or only the pictures are seen (Figure\ \@ref(fig:task)).\footnote{Further technical detail about model fitting in the unimodal conditions will be given in the method section of Experiment 1} Using these derived parameters, the optimal model makes predictions about responses in the bimodal condition where participants both hear the sounds and see the pictures.
+Parameter estimates of the probability distributions in each modality are derived by fitting unimodal posteriors to the participants' responses in the unimodal conditions, i.e., the condition where only the sounds are heard  or only the pictures are seen (Figure\ \@ref(fig:task)).\footnote{Further technical detail about model fitting in the unimodal conditions will be given in the method section of Experiment 1} Using these derived parameters, the optimal model makes predictions about responses in the bimodal (i.e., audio-visual) condition where participants both hear the sounds and see the pictures.
 
@@
 The second allows us to test the extent to which the weighting scheme follows the prediction of the optimal model.
-The reason we used the proportion of the variances as a measure of cross-modal weighting is because this proportion corresponds to the slope\footnote{Or more precisely the absolute value of the slope} of the decision threshold in the audio-visual space (Figure\ \@ref(fig:model)).
+The reason we used the proportion of the variances as a measure of cross-modal weighting is because this proportion corresponds to the slope\footnote{Or more precisely the absolute value of the slope.} of the decision threshold in the audio-visual space (Figure\ \@ref(fig:model)).
 The decision threshold is defined as the set of values in this audio-visual space along which the posterior is equal to 0.5.
@@
 In Experiment 1, we studied the case where bimodal uncertainty was due to categorical variability, only.
-In Experiment 2 and 3 we added noise in the background on top of categorical variability.
+In Experiment 2 and 3 we added auditory and visual noise, respectively, on top of categorical variability.
 
@@
 In this Experiment, we test the predictions of the model in the case where uncertainty is due to categorical variability only (i.e., ambiguity in terms of category membership).
-We do not add any external noise to the background and we assume that internal sensory noise is negligible compared to categorical variability ($\sigma^2_{A} \gg \sigma^2_{N_A}$, and $\sigma^2_{V} \gg \sigma^2_{N_V}$).
+We do not add any external noise to the background and we assume that internal sensory noise is negligible compared to categorical variability ($\sigma^2_{A} \gg \sigma^2_{N_A}$ and $\sigma^2_{V} \gg \sigma^2_{N_V}$).
 Thus, we use the following cue weighting scheme:
@@
 Trials were blocked by condition and blocks were presented in random order.
-The experiment lasted around 15 minutes.
+The experiment lasted around 15 minutes.^[The experiment can be accessed and played from the github repository: https://github.com/afourtassi/WordRec/]
 
@@
        aes(x = distance, y = mean)) + 
-  geom_point()+
+  #geom_point()+
   geom_pointrange(aes(ymin = lower, ymax = upper), 
-                  position = position_dodge(width = .1)) + 
+                  position = position_dodge(width = .1), size = 0.4, fatten = 2) + 
   #geom_line(data=uniV,aes(x=xV, y=yV))+
@@
 ### Model fitting details
-#### Unimodal condition
-Remember that data in this conditions allow us to derive the variances of both the auditory and the visual categories, and that these variances are used to make predictions about bimodal data (in the visual and auditory baselines as well as in the optimal model).
+#### Unimodal conditions
+Remember that data in these conditions allows us to derive the variances of both the auditory and the visual categories, and that these variances are used to make predictions about bimodal data (in the visual and auditory baselines as well as in the optimal model).
 These individual variances were derived as follows (we explain the derivation for the auditory-only case, but the same applies for the visual-only case).
@@
 
-Although the paradigm is within-subjects, we did not have enough statistical power to fit a different model for each individual participant.
-Instead, models were constructed with data collapsed across all participants.
-That being said, the distribution of responses from individual participants will also be analyzed.
+Although the paradigm is within-subjects, we did not have enough statistical power to fit a different model for each individual participant.^[We had a relatively high number of trials spanning all possible audio-visual matchings.
+Getting enough data points per trial per participant would have required running the online experimental for a much longer time (more than an hour).
+This could have increased significantly the dropout rate and possibly affected the quality of the data collected online.] Instead, models were constructed with data collapsed across all participants.
+That being said, we will also analyze the distribution of individual responses.
 The fit was done with a nonlinear least squares regression using the NLS package in R [@bates88].
@@
 The categorization function of the auditory condition was slightly steeper than that of the visual condition, meaning that participants perceived the sound tokens slightly more categorically and whih higher certainty than they did with the visual tokens.
-For the auditory modality, we obtained the following values:^[all CIs in the paper are 95% confidence intervals.] $b_A=$ `r audBias_val`  [`r audBias_ci2`, `r audBias_ci1`] and $\sigma^2_A=$ `r audVar_val` [`r audVar_ci1`, `r audVar_ci2`].
+For the auditory modality, we obtained the following values: $b_A=$ `r audBias_val`  [`r audBias_ci2`, `r audBias_ci1`] and $\sigma^2_A=$ `r audVar_val` [`r audVar_ci1`, `r audVar_ci2`].
 For the visual modality, we obtained $b_V=$ `r visBias_val` [`r visBias_ci2`, `r visBias_ci1`] and $\sigma^2_V=$ `r visVar_val` [`r visVar_ci1`, `r visVar_ci2`].
 
-```{r unimodal, out.width = "\\textwidth", fig.pos = "!h", fig.cap = "Human responses in the unimodal conditions.
+```{r unimodal, out.width = "\\textwidth", fig.pos = "!h", fig.cap = "Human responses in the unimodal conditions across the three experiments.
 Points represent the proportion of `different' to `same' responses in the auditory-only condition (left), and visual-only condition (right).
 Error bars are 95\\% confidence intervals.
-Solid lines represent best fits."}
+Solid lines represent best unimodal posterior fits."}
 
@@
            shape = factor(sound_dist))) + 
-  geom_point()+
+  geom_point(size =1)+
   scale_colour_solarized()+
@@
 Figure\ \@ref(fig:bimodal) compares the predictions of the normative models against human responses.
+Remember that the normative models use variance estimates from the unimodal conditions (where people see input from only one modality) to predict data in the bimodal condition (where people see input from both modalities).
+Each point represents data form a particular audio-visual matching (e.g., the visual token $v$ whose distance from the target $v_t$ is $|v-v_t|=3$, matched with the auditory token $a$ whose distance from the target $a_t$ is $|a-a_t|=2$).
 The visual, auditory and optimal model explained, respectively, `r 100*R2_visual_1`%, `r 100*R2_auditory_1`%, and `r 100*R2_optimal_1`% of total variance in mean responses.
@@
 ```{r bimodal, out.width = "\\textwidth", fig.pos = "!h", fig.cap = "Human responses vs.
-models' predictions in the bimodal condition.
-Shape represents auditory distance from the target, and color represents visual distance from the target."}
+Models' predictions in the bimodal condition across the three experiments.
+Each point represents data form a particular audio-visual matching.
+Shape represents auditory distance from the target, and color represents visual distance from the target.
+Thus, each point is characterized by both  shape and color."}
 
@@
 Note however that, despite this increase in randomness, our analysis of modality preference showed that the relative values of these variances were not different (Figure\ \@ref(fig:bias)), meaning that there was no evidence for a modality preference.
-Thus, 1) There was a simultaneous increase in the values of the auditory and visual variances in the bimodal condition compared to the unimodal condition, meaning that the bimodal input lead to an increase in response randomness, and 2) this increased randomness did not affect the relative weighting of both modalities, i.e., the population was weighting modalities according to the relative reliability predicted by the optimal model.
+Thus, 1) There was a simultaneous increase in the values of the auditory and visual variances in the bimodal condition compared to the unimodal condition, meaning that the bimodal input lead to an increase in response randomness, and 2) this increased randomness did not affect the relative weighting of both modalities, i.e., the participants was weighting modalities according to the relative reliability predicted by the optimal model.
 This situation corresponds to the first case of sub-optimally described in Figure\ \@ref(fig:subOptim).
@@
 
-```{r echo=FALSE, individual, out.width = "\\textwidth", fig.pos = "!h",fig.cap = "Histograms of the individual values of the visual variance relative to the auditory variance in Experiment 1.
-Light color represents the values derived from each individual participant, and dark color represents simulated individual responses sampled from the descriptive model."}
+```{r echo=FALSE, individual, out.width = "\\textwidth", fig.pos = "!h",fig.cap = "Distributions of individual values of the visual variance relative to the auditory variance in Experiment 1.
+Light color represents the real individual distribution, and dark color represents the simulated individual distribution sampled from the descriptive model."}
 
@@
 In Experiment 1, we tested word recognition when there was multimodal uncertainty in terms of category membership only.
-In real life, however, tokens can undergo distortions due to noisy factors in the environment (e.g., car noise in the background, blurry vision in a foggy weather,..).
+In real life, however, tokens can undergo distortions due to noisy factors in the environment (e.g., car noise in the background, blurry vision in a foggy weather).
 In Experiment 2 and 3, we explore this additional level of uncertainty.
@@
 We were also interested in whether noise in the auditory modality lead more participants to rely exclusively on the visual modality at the individual level.
-Using the same cut-off as in Experiment 1 (a factor of 10), the percentage of participants who relied exclusively on either modalities was `r 100*(only_visual_N_2+only_sound_N_2)/(only_visual_N_2+only_sound_N_2+both_N_2)`%, which is much higher than the percentage obtained in Experiment 1 (`r 100*(only_visual_N_1+only_sound_N_1)/(only_visual_N_1+only_sound_N_1+both_N_1)`%).
+Using the same cut-off as in Experiment 1 (a factor of 10), the percentage of participants who relied exclusively on either modality was `r 100*(only_visual_N_2+only_sound_N_2)/(only_visual_N_2+only_sound_N_2+both_N_2)`%, which is much higher than the percentage obtained in Experiment 1 (`r 100*(only_visual_N_1+only_sound_N_1)/(only_visual_N_1+only_sound_N_1+both_N_1)`%).
 Moreover, the subset of participants relying exclusively on the visual modality (compared to those who relied exclusively on the auditory modality)  increased from `r 100*exlusive_prop_1`% in Experiment 1 to `r 100*exlusive_prop_2`% in Experiment 2, indicating that noise in the auditory modality prompted more participants to rely exclusively and disproportionately on the visual modality (see Table \@ref(tab:exclusive)).
@@
 We also used the same visual stimuli, but we blurred the tokens using the free image editor GIMP (2.8.20).
-We used a Gaussian blur with a radius\footnote{A features that modulates the intensity of the blur} of 10 pixels.
+We used a Gaussian blur with a radius\footnote{A features that modulates the intensity of the blur.} of 10 pixels.
 The experimental procedure was exactly the same as in the previous Experiments.
@@
 In these cases, deviation from  optimality is due to over-lying on the visual or the auditory input by a factor of 2 (green and blue dotted lines, respectively).
-B) The value of the decision threshold's slope derived from the descriptive model relative to that of the optimal model.
+B) An alternative way to represent the same data.
+Each point represents the value of the decision threshold's slope derived from the descriptive model relative to that of the optimal model (log-scaled).
+The lines represent the optimal case as well as the two hypothetical cases of modality preference.
 Error bars represent 95\\% confidence intervals over the distribution obtained through non-parametric resampling."}
@@
   Experiment = c('Exp1', 'Exp2', 'Exp3'),
-  Total = c(100*total_excl_exp1, 100*total_excl_exp2, 100*total_excl_exp3),
+  ofTotal = c(100*total_excl_exp1, 100*total_excl_exp2, 100*total_excl_exp3),
   Auditory = c(100*(1-exlusive_prop_1), 100*(1-exlusive_prop_2), 100*(1-exlusive_prop_3)),
@@
   , caption = "The percentage of participants who relied exclusively on either the visual modality or the auditory modality, using a factor of 10 as a cut-off (e.g., we consider that a participant relied exclusively on the visual modality when their auditory variance is a at least 10 times larger than their visual variance).
-We show the percentage compared to the total number of participants in each Experiment (`Total').
+We show the percentage compared to the total number of participants in each Experiment (`of Total').
 From this subset of participants, we show the percentage of those who relied on the  auditory modality (`Auditory'), and the percentage of those who relied on the visual  modality (Visual')."
@@
 @bejjanki2011].
-The current work explored, for the first time, the case of word identification under uncertainty in speech (word form) and the visual *referent*.
+The current work explored the case of word identification under uncertainty in speech (word form) and the visual *referent*.
 More specifically, we conducted an ideal observer analysis of the task whereby a model provided predictions about how information from each modality should be combined in an optimal fashion.
@@
 In Experiment 1, which did not involve background noise, participants not only relied on both modalities, but generally weighted these modalities according to the prediction of the optimal model, that is, according to their relative reliability.
-At the individual level, however, we found evidence of a between-subject variation: Some participants relied slightly more on the visual modality, whereas others relied slightly more on the auditory modality.
+At the individual level, however, we found evidence of a between-subject variation: Some participants relied  more on the visual modality, whereas others relied  more on the auditory modality.
 
@@
 Retaining two separate cues at the same time instead of forming one unified percept (as in multisensory integration of redundant cues), or instead of retaining only one cue (as in the unimodal case), is likely to place extra-demand on cognitive resources, which, in turn, can cause general performance to drop.
-Indeed, there is evidence that cognitive load has a detrimental effect on word recognition.
-This phenomenon  can be due to a reduction in perceptual acuity [e.g., @mattys11].
+Indeed, there is evidence that cognitive load due to divided attention (e.g., when performing two tasks at the same time) has a detrimental effect on word recognition [@mattys11].
 
@@
 In agreement with the method and finding in the current study, @hofer2017 characterized the apparent reduction in perceptual acuity as an increase in the noise variance of the auditory modality.
-Our finding, besides providing more evidence to this documented fact, suggests that the  reduction in perceptual acuity may occurs simultaneously in both the auditory *and* the visual modalities.
+Our finding, besides providing more evidence to this documented fact, suggests that the  reduction in perceptual acuity may occur simultaneously in both the auditory *and* the visual modalities.
 
@@
 In contrast to Experiment 1 where the combination was indistinguishable from the optimal prediction, results of Experiment 2 and 3 which both involved background noise in one modality, showed that participants had a systematic preference for the other (non-noisy) modality.
-From previous empirical studies, we know that when the speech signal is degraded, people tend to compensate by relying more on other sources of information such as the accompanying visual cues (i.e., lip movements) or the semantic/syntactic context [see @mattys12 for a review].
-However, and generally speaking, these studies do not differentiate between an optimal compensatory strategy (i.e., relying more on the alternative source while using all information still available in the distorted signal), and a sub-optimal strategy (i.e., relying more on the alternative source while ignoring at least some of the information still available in the distorted signal).
+When the speech signal is degraded, people, in previous work, were shown to compensate by relying more on other sources of information such as the accompanying visual cues, the semantic/syntactic context, or the top-down expectations.
+This kind of compensation has been observed with adults [@mcclelland2006; @Tanenhaus1995; @mattys12], and recent evidence suggests that it starts in childhood [@yurovsky2017; @macdonald2018].
+However, and generally speaking, previous experimental studies have not differentiated between an optimal compensatory strategy (i.e., relying more on the alternative source while using all information still available in the distorted signal), and a sub-optimal strategy (i.e., relying more on the alternative source while ignoring at least some of the information still available in the distorted signal).
 The formal approach followed in this paper allowed us to tease apart these two possibilities, and our analysis supports the sub-optimal compensatory strategy: The preference for the non-noisy modality is above and beyond what can be explained by the relative reliability alone, meaning that the participants tend to ignore at least part of the information still available in the noisy modality.
 
-This second case of sub-optimal behavior is possibly related to the fact that language understanding under degraded  conditions is cognitively more taxing than language understanding under normal conditions [e.g., @Ronnberg10].
-This fact can lead to a bias against the more noisy cue.
+This second case of sub-optimal behavior is possibly related to the fact that language understanding under degraded  conditions is cognitively more taxing than language understanding under normal conditions [@ronnberg2010; @mattys12; @peelle2018].
+This fact can lead to a sub-optomal behavior (i.e., over-reliance on the less noisy cue) as participants would seek to minimized cognitive effort.
 One could also explain this phenomenon in terms of the metacognitive experience about the fluency with which information is processed.
@@
 Note that in order to test audio-visual cue combination under uncertainty, we had to use a case of double ambiguity, that is, a case where both the word forms ("ada"-"aba") and the referents (cat-dog) were similar and, thus, confusable.
-However, to what extent does such case occur in real languages?
+However, to what extent does such a case occur in real languages?
 Cross-linguistic corpus analyses suggest that lexical encoding tends, surprisingly, towards double ambiguity in many languages [@dautriche17; @Monaghan2014; @Tamariz2008].
 For instance, @dautriche17 analyzed 100 languages and found that words that are similar phonologically  tend to be similar semantically as well.
-These studies suggest that the case of double uncertainty, though perhaps not pervasive, could be a real issue in language as it increase the probability of confusability for many words.\linebreak That being said, besides the case of double ambiguity intrinsic to language, there are two situations where our mechanism might play a significant role.
-The first is when ambiguity in both the form and/or the referent is induced by an external noisy context even when these forms and referents are not confusable in normal situations.
-The second case is that of early word recognition/learning, and we will discuss this case in more detail in what follows.
-
-Though we only tested adults in this paper, the problem of word recognition under uncertainty, as well as the need to make the most of ambiguous cues, is a particularly pressing issue for children.
-In fact, whereas adults are mostly faced with uncertainty in the *input*, children have to deal with the additional uncertainty that results from their early unrefined *representations* of both phonological and semantic categories.
-For example, upon hearing a noisy instance of "bee", adults may have to decide whether the speaker intended to say "pea" or "bee", but children can additionally be uncertain whether "bee" is a different word from "pee" (as opposed to, say, a valid within category variation), especially if these similar sounding words are newly learned [@stager1997; @Merriman91; @Creel2012; @Swingley2016; @white2008b].
-Though similar word form representation can be shown to be differentiated under some circumstances [e.g., @yoshida2009], this differentiation is still not mature enough and is probably noisier than the adult-like representation and/or encoded with lower confidence [see @Swingley2007].
-
-At the semantic level, early representations have, similarly, an intrinsically fragile and uncertain status.
-For example, upon seeing a bee in a foggy weather, adults may be uncertain if they saw a bee or a fly.
-But on top of this perceptual uncertainty, children may not be certain if the semantic category being named is that of bees and only bees, or if it includes other small flying insects like flies and beetles.
-In fact,  though children can be fast at learning a first approximation of a given word's referent [@carey1978b], the refinement of this early approximation into a mature semantic category is a slow and gradual process [see also @bion2013;; @carey2010; @fernald2006; @mcmurray2012].
-Among other things, children have to enrich this early representation with new features, and revise its extension in the light of new referential exposures.
-In sum, uncertainty in the representation associated with one modality (e.g., a bee and a fly) can be mitigated through the possibly more differentiated representations associated with the other modality (e.g., the sound "bee" is acoustically different from the sound "fly").
-
-The multi-modal cue combination strategy might help children not only recognize an individual word instance, but also refine the underlying phonological and semantic representations in the process.
-Previous research in early word learning has---whether implicitly or explicitly---largely treated the process of learning form and of learning meaning as independent.
-However, the developmental data reviewed above shows that children do not wait to have completed the acquisition of form to start learning meanings, and that both form and meaning representations develop, rather, in a parallel fashion.
+These studies suggest that the case of double uncertainty, though perhaps not pervasive, could be a real issue in language as it increase the probability of confusability for many words.\linebreak That being said, besides the case of double ambiguity *intrinsic* to language, our mechanism might play a more significant role when ambiguity in both the form and/or the referent is induced by an *external* noisy context even when these forms and referents are not confusable in normal situations.
+
+Though we only tested adults in this paper, the problem of word recognition under uncertainty, as well as the need to make the most of the available cues, is arguably more pressing for children.
+In fact, children have greater difficulties differentiating the meanings of novel similar-sounding words (e.g., "bin" vs.
+"din"), even when these words are uttered very clearly [@stager1997; @Merriman91; @Creel2012; @Swingley2016; @white2008b].
+Such similar-sounding words can be shown to be differentiated by infants in simplified experimental settings [e.g., @yoshida2009].
+Nevertheless, @Swingley2007 suggested this differentiation is not mature  and is probably noisier than the adult-like representation and/or encoded with lower confidence.
+Thus, it looks like children, even more than adults, may greatly benefit from additional disambiguating cues during new word-referent encoding and recognition.
+For example, @dautriche2015 showed that 18-month-olds can leverage the difference in the syntactic category (noun vs.
+verb).
+Further work is needed to explore whether salient referential cues also help children disambiguate similar sounding words.
+
+The multi-modal cue combination strategy might help children not only recognize words, but also refine the underlying phonological and semantic representations in the process.
+Previous research in early word learning has---whether implicitly or explicitly---largely treated the process of refining the word form and of refining the word meaning as follwing a linear timeline However, recent developmental data shows that children do not wait to have completed the acquisition of forms to start learning the meanings [@bergelson2012; @tincoff1999].
+Rather, both form and meaning representations develop in a parallel fashion.
 A few studies pointed to the possibility of an interaction between sound and meaning in early acquisition.
-For instance, @waxman1995 showed that labeling various objects with the same name helps infants form the broad semantic category [but see @sloutsky2003].
-Vice versa, @yeung09 showed that pairing similar sounds with different objects help infants pay attention to subtle phonological contrasts.
+For instance, @waxman1995 showed that labeling various objects with the same name helps infants form the underlying semantic category [but see @sloutsky2003].
+Vice versa, @yeung09 showed that pairing similar sounds with different objects help infants enhance their sensitivity to the subtle phonological contrasts in their native language.
 The present study proposes a first step towards a formal framework where isolated accounts of sound-meaning interaction in development can be unified and further explored.
-<!--For example, one could imagine that, initially, visual and auditory categories have relatively large noise variances, and that development consists in reducing the values of the variances through a mutually constraining process as further multimodal data accumulates.
---->
 
@@
 It is an open question as to whether people use the same strategy in controlled laboratory conditions, as in more naturalistic settings where they have to deal with various levels of variability.
-An answer to this question is likely to involve a multifaceted research approach, involving---besides laboratory experiments---analyses of corpora with a more realistic multimodal input [e.g., @fourtassi2014b; @harwath2016; @roy2015].
+An answer to this question is likely to involve a multifaceted research approach, involving---besides conducting laboratory experiments---testing computational mechanisms with an input that represents, more accurately, the complexity of multimodal variability in the learning environment [@fourtassi2014b; @harwath2016; @roy2015; @dupoux2018].
 
 # Conclusion 
-This work studied the mechanism of word identification under uncertainty in both the word form and the word referent.
-To our knowledge, this is the first study that performs an ideal observer analysis of this task.
-We found people to be near optimal in their cue combination: They weighted each modality according to its relative reliability.
+This work studied the mechanism of spoken word identification under uncertainty in both the form and the referent.
+We conducted an ideal observer analysis of this task.
+We found people to be near optimal in their cue combination (at least at the population level): They weighted each modality according to its relative reliability.
 However, they also showed patterns of sub-optimality especially when the stimuli were perturbed with additional background noise.
-Though the present study did not directly address the issue of early word learning, it provides a framework where developmental questions can also be investigated.
+This work provides a formal framework where old and new questions about word recognition in a referential context can be given a precise formulation.
+For instance, of particular interest is the case of iconicity, that is, when there is a resemblance between the sound of a word and its referent.
+Previous work has suggested that iconicity, among other things, helps with learning (and generalizing the meaning of) new words [see @dingemanse2015 for a review].
+Using the research strategy in this paper, we can, for example, test whether iconicity has such an advantage because it mitigates the sub-optimal patterns observed with more arbitrary pairings.
+Finally, though the current framework only characterizes adult word recognition, it provides a first step towards a model where developmental questions can also be investigated.
 For instance, future work should explore whether children, like adults, use probabilistic cues from both the auditory and the visual input to recognize ambiguous words,  the extent to which they combine these cues in an optimal fashion, and whether these combination help them with refining their early phonological and semantic representations.

### 2018-04-26 Writeup/ms.tex
modif ms

@@
 predict the other half (averaging across 10 random partitions). The
-predictive power of the model remained very high (\(r^2\)=0.93).
+predictive power of the model remained very high (\(r^2\)=0.92).
 
@@
 deviation of \(sd=\) 2.24 which was larger than that of the simulated
-distribution (\(sd=\) 1.10), indicating that there was real
+distribution (\(sd=\) 1.15), indicating that there was real
 between-subject variation beyond sampling errors. This finding means
@@
 research strategy in this paper, we can, for example, test whether
-iconicity has such an advantage becuase it mitigates the sub-optimal
+iconicity has such an advantage because it mitigates the sub-optimal
 patterns observed with more arbitrary pairings. Finally, though the

### 2018-05-10 Writeup/ms.Rmd
mcf pass

@@
 How do these tasks interact with one another?
-We introduce a task that allows us to examine how adults identify words under joint uncertainty in the auditory and visual modalities.
-We propose an ideal observer model which provides an account of how auditory and visual cues are combined optimally.
-Model predictions are tested in three experiments where word recognition is made under two kinds of uncertainty: category ambiguity and/or distorting noise.
+We introduce a paradigm that allows us to examine how adults identify words under joint uncertainty in the auditory and visual modalities and propose an ideal observer model of how cues in these modalitiess are combined optimally.
+Model predictions are tested in three experiments where word recognition is made under two kinds of uncertainty: category ambiguity and perceptual noise.
 In all cases, the optimal model explains much of the variance in human mean judgments.
-In particular, when the signal is not distorted with noise, participants weight the auditory and visual cues optimally, that is, according to the relative reliability of each modality.
+When the signal is not distorted with noise, participants weight the auditory and visual cues optimally, that is, according to the relative reliability of each modality.
 But when one modality has noise added to it, human perceivers systematically prefer the unperturbed modality to a greater extent than the optimal model does.
-The study provides a formal framework which helps us understand precisely how word form and word meaning interact in word recognition under uncertainty.
-Moreover it offers a first step towards a model that accounts for form-meaning synergy in early word learning.
+The study provides a formal framework which helps to quantify how word form and word meaning interact in word recognition under uncertainty.
+Moreover it offers a first step towards a model that accounts for form-meaning synergies in early word learning.
 
@@
 
-Language uses symbols expressed in one modality, e.g., the auditory modality, in the case of speech, to communicate about the world, which we perceive through many different sensory modalities.
+Language uses symbols expressed in one modality -- the auditory modality, in the case of speech -- to communicate about the world, which we perceive through many different sensory modalities.
 Consider hearing someone yell "bee!" at a picnic, as a honey bee buzzes around the food.
@@
 And some tokens may be distorted additionally by mispronunciation or ambient noise.
-Perhaps the speaker was yelling "pea" and not "bee".
-Similarly, a sensory impression may not be enough to make a definitive identification of a visual category.\footnote{In the general case, language can of course be visual as well as auditory, and object identification can be done through many modalities.
+Perhaps the speaker was yelling "pea" and not "bee." Similarly, a sensory impression may not be enough to make a definitive identification of a visual category.\footnote{In the general case, language can of course be visual as well as auditory, and object identification can be done through many modalities.
 For simplicity, we focus on audio-visual matching here.} Perhaps the insect was a beetle or a fly instead.
@@
 
-The task of matching the sound to the corresponding visual object has been extensively studied in the developmental literature since it is considered to be an crucial instance of early word learning.
-For example, many studies focused on how children might succeed in this task despite high referential ambiguity [@smith08; @pinker1989; @medina2011; @vouloumanos2008; @yurovsky2015; @suanda2014; @vlach2013].
-However, even when they know the exact meanings of the words, listeners (both children and adults) often face the task of recognizing which word the speaker utters, especially under noisy circumstances [@mattys12; @peelle2018].
-The purpose of the current study is to explore novel word recognition by adults under multimodal uncertainty.
+As a simplified case study of early word learning, the task of matching sounds to corresponding visual objects has been studied extensively in the developmental literature.
+For example, many studies focus on how children might succeed in this type of task task despite referential ambiguity [@smith08; @pinker1989; @medina2011; @vouloumanos2008; @yurovsky2015; @suanda2014; @vlach2013].
+However, even when they *know* the meanings of a word, listeners (both children and adults) often still find it challenging to recognize which word the speaker has uttered, especially under noise [@mattys12; @peelle2018].
+The purpose of the current study is thus to explore word recognition by adults under multimodal uncertainty.
 We focus on the special case where people have access to multimodal cues from the auditory speech and the visual referent.
+In the General Discussion, we return to the question of how these findings relate to questiosn about word learning.
 
 One rigorous way to approach this question is through conducting an *ideal observer* analysis.
-This research strategy provides a characterization of the task/goal and shows what the optimal performance should be under this characterization.^[It is, thus, a general instance of the rational approach to cognition [@anderson90].
-It can also be seen as an instance of Marr's computational level of analysis [@marr1982].] When there is uncertainty in the input, the ideal observer performs an optimal probabilistic inference.
+This research strategy provides a characterization of the task/goal and shows what the optimal performance should be under this characterization.^[It is, thus, a general instance of the rational approach to cognition [@anderson90], instantiating Marr's computational level of analysis [@marr1982].] When there is uncertainty in the input, the ideal observer performs an optimal probabilistic inference.
 For example, in order to recognize an ambiguous linguistic input, the model uses all available probabilistic knowledge in order to maximize the accuracy of this recognition.
@@
 When there is a deviation from the ideal, it can reveal extra constraints on human cognition, such as limitations on the working memory or attentional resources.
-The ideal observer analysis has had a tremendous impact not only on speech related research [@Norris08; @clayard08; @feldman2009; @kleinschmidt2015], but also on many other disciplines in the cognitive sciences [for reviews, see @chater06; @Knill04; @tenenbaum11]
-
-Some of these ideal-observer-based studies are closely related to the question we are addressing in the current work.
+This approach has had a tremendous impact not only on speech-related research [@Norris08; @clayard08; @feldman2009; @kleinschmidt2015], but also on many other disciplines in the cognitive sciences [for reviews, see @chater06; @Knill04; @tenenbaum11]
+
+Some prior ideal observer studies are closely related to the question we are addressing in the current work.
 For instance, @clayard08 simulated auditory uncertainty by manipulating the probability distribution of a cue (Voice Onset Time) that differentiated similar words (e.g., "beach" and "peach").
 They found that humans were sensitive to these probabilistic cues and their judgments closely reflected the optimal predictions.
-In another work, @feldman2009 studied the perceptual magnet effect, a phenomenon that involves reduced discriminability near prototypical sounds in the native language [@kuhl1991].
-They showed that this effect can be explained as the consequence of optimally solving the problem of perception under uncertainty.
+And @feldman2009 studied the perceptual magnet effect, a phenomenon that involves reduced discriminability near prototypical sounds in the native language [@kuhl1991], showing that this effect can be explained as the consequence of optimally solving the problem of perception under uncertainty.
 
@@
 @bejjanki2011 offered a mathematical characterization of how probabilistic cues from speech and lip movements can be optimally combined.
-They showed that human performance during audio-visual phonemic labeling was consistent (at least at the qualitative level) with the behavior of the ideal observer.
-This previous research, however, did not systematically study speech understanding when the visual information is obtained, not through the speaker's facial features---as in audio-visual speech perception, but through the referential context.
-In fact, experimental findings showed that information about the identity of the semantic referent can be integrated with linguistic information to resolve lexical and syntactic ambiguities in speech [e.g., @Eberhard1995; @Tanenhaus1995; @spivey2002].
-To our knowledge, however, no study offered an ideal observer analysis of word identification in such context, that is, when the listener has to combine cues from the sound and the referent.
-
-On the face of it, the question of combining information from the sound and the visual referent might seem similar to that of audio-visual speech integration.
-Nevertheless, there are at least two fundamental differences between these two cases, and both can influence the way the auditory and visual cues are combined: First, in the case of audio-visual speech, both modalities offer information about the same underlying speech category.
-They may differ only in terms of their informational reliability.
-In a referential context, however, the auditory and visual modalities play different roles in the referential process---in addition to possible differences in informational reliability.
-Indeed, the auditory input represents the *symbol* whereas the visual input represents the *meaning*.
-It has been shown that speech has a privileged status compared to other sensory stimuli [@vouloumanos2014; @waxman2009; @waxman1995; @edmiston2015; @lupyan2012], and that this privilege is indeed related to the speech's ability to refer [@waxman2009].^[There is, however, a debate as to whether speech is privileged for children and adults for similar reasons.
+They showed that human performance during audio-visual phonemic labeling was consistent (at least at the qualitative level) with the predictions of an ideal observer.
+This previous research did not,  however, systematically study speech understanding when visual information was obtained through the referential context rather than through observation of speaker's face.
+Although some experimental findings show that information about the identity of a referent can be integrated with linguistic information to resolve lexical and syntactic ambiguities in speech [e.g., @Eberhard1995; @Tanenhaus1995; @spivey2002], to our knowledge no study has offered an ideal observer analysis of this task.
+
+Combining information between words and visual referents might seem similar to audio-visual speech integration, but there are at least two fundamental differences between these two cases, and both can influence the way the auditory and visual cues are combined.
+
+First, in the case of audio-visual speech, both modalities offer information about the same underlying speech category.
+They differ only in terms of their informational reliability.
+In a referential context, however, the auditory and visual modalities play different roles in the referential process -- the auditory input represents the *symbol* whereas the visual input represents the *meaning* (and these differences are in addition to possible differences in informational reliability).
+Further, speech is claimed to have a privileged status compared to other sensory stimuli [@vouloumanos2014; @waxman2009; @waxman1995; @edmiston2015; @lupyan2012], and that this privilege is suggested to be specifically related to the ability to refer [@waxman2009].^[There is, however, a debate as to whether speech is privileged for children and adults for similar reasons.
 Whereas some researchers suggest that speech is privileged for both children and adults because of its ability to refer [e.g., @waxman2009], others suggest that speech might *not* have a referential status from the start.
@@
 Second, in the case of audio-visual speech, the auditory and visual stimuli are expected to be perceptually correlated.
-The expectation for this correlation is such that when there is a mismatch between the auditory and visual input, people still integrate them into a unified (but illusory) percept [@mcgurk1976].
+The expectation for this correlation is strong enough that when there is a mismatch between the auditory and visual input, they are still integrated into a unified (but illusory) percept [e.g., the McGurk Effect; @mcgurk1976].
 In the case of referential language, however, the multimodal association is by nature *arbitrary* [@saussure1916; @greenberg1957].
-For instance, there is no logical/perceptual connection between the sound "bee" and the corresponding insect.
+For instance, there is no logical or perceptual connection between the sound "bee" and the corresponding insect.
 Moreover, variation in the way the sound "bee" is pronounced is generally not expected to correlate perceptually with variation in the shape (or any other visual property) in the category of bees.
@@
 
-We investigate how people combine cues from the auditory and the visual modality to recognize words in a referential context.
+We investigate how cues from the auditory and the visual modality are combined in recognizing words in a referential context.
 In particular, we study how this combination is performed under various degrees of uncertainty in both the auditory and the visual modality.
-Imagine, for example, that someone is uncertain whether they heard "pea" or "bee", does this uncertainty make them rely more on the referent (e.g., the object being pointed at)?
-Vice versa, if they are not sure if they saw a bee or a fly, does it make them rely more on the sound?
-More importantly, when input in both modalities is uncertain to varying degrees, do they weight each modality according to its relative reliability, which is the optimal strategy, or do they over-rely on a particular modality, which is a sub-optimal strategy?
-
-We perform a rational analysis of the task.
-First we propose an ideal observer model that performs the combination in an optimal fashion.
-Second we compare the predictions of the optimal model to human responses.
+Imagine, for example, that someone is uncertain whether they heard "pea" or "bee." Does this uncertainty make them rely more on the referent (e.g., the object being pointed at)?
+Or, if they are not sure if they saw a bee or a fly, does this uncertainty make them rely more on the sound?
+More importantly, when input in both modalities is uncertain to varying degrees, do they weight each modality according to its relative reliability (the optimal strategy), or do they over-rely on a particular modality?
+
+We begin by proposing an ideal observer model that performs the combination in an optimal fashion.
+We then compare the predictions of the optimal model to human responses.
 Humans can deviate from the ideal for several reasons.
-For instance, as mentioned above, a sub-optimality can be induced by the suggested privileged status of speech or by the arbitrariness of the referential association.
+For instance, as mentioned above, a sub-optimality can be induced by the privileged status a partiular modality or by the arbitrariness of the referential association.
 In order to study possible patterns of sub-optimality, we compare the optimal model (which provides a normative benchmark) to a descriptive model (which is fit to human responses).
@@
 In Experiment 1, audio-visual tokens were ambiguous with respect to their category membership only.
-In Experiment 2, we intervened by adding background noise to the auditory modality, and in Experiment 3, we intervened by adding background noise to the visual modality.
+In Experiment 2, we intervened by adding perceptual noise to the auditory modality, and in Experiment 3, we intervened by adding perceptual noise to the visual modality.
 In all experiments, participants were quantitatively near-optimal, though overall response precision was slightly lower than expected.
-Moreover, in Experiment 1 where neither of the modalities was perturbed with background noise, participants weighted auditory and visual cues according to the relative reliability predicted by the optimal model.
-In other words, we found no evidence for a modality bias towards either the auditory or the visual modality.
+In Experiment 1 -- where neither of the modalities was perturbed with background noise -- participants weighted auditory and visual cues according to the relative reliability predicted by the optimal model.
 However, in Experiment 2 and 3, participants over-relied on one modality when the other modality was perturbed with additional noise.
@@
 
-In this section we, first, briefly introduce the multimodal combination task. Then we explain how behavior in this paradigm can be characterized optimally with an ideal observer model.
+In this section we first briefly introduce the multimodal combination task. Then we explain how behavior in this paradigm can be characterized optimally with an ideal observer model.
 
@@
 
-We introduce a task adapted from @sloutsky2003.
-The original task has been used with both children and adults to probe audio-visual encoding [see @robinson2010 for a review].
+We introduce a paradigm adapted from a task usead by @sloutsky2003.
+The original was used with both children and adults to probe audio-visual encoding [see @robinson2010 for review].
 Here we use a slightly different version to test word recognition in a referential context.
@@
 
-In the testing phase of the original task [@sloutsky2003], participants are asked whether or not the two audio-visual presentations are *identical*.
+In the testing phase of the original task [@sloutsky2003], participants were asked whether or not the two audio-visual presentations are *identical*.
 In the current study, we are interested, rather, in the categorization, i.e., determining whether or not two similar tokens are members of the same phonological/semantic category.
@@
 We construct an ideal observer model that combines probabilistic information from the auditory and visual modalities.
-In contrast to the  model used in most research on multisensory integration [e.g., @ernst02]---which typically studies continuous stimuli (e.g., size, location)---the probabilistic information in our case cannot be characterized with *sensory noise*, only.
-Indeed, our task involves responses over categorical variables (phonemes and concepts), and therefore, the optimal model should take into account, not only the noise variability around an individual perceptual estimate, but also its *categorical variability*, i.e., the uncertainty related to whether this perceptual estimate belongs to a given category [see also @Bankieris17; @bejjanki2011].
+In contrast to the  model used in most research on multisensory integration [e.g., @ernst02], which typically studies continuous stimuli (e.g., size, location), the probabilistic information in our case cannot be characterized with *sensory noise* only.
+Since our task involves responses over categorical variables (phonemes and concepts), the optimal model should take into account not only the noise variability around an individual perceptual estimate but also its *categorical variability*, i.e., the uncertainty related to whether this perceptual estimate belongs to a given category [see also @Bankieris17; @bejjanki2011].
 In what follows, we describe a model that accounts for both types of variability.
@@
 ### Categorical variability
+
 We assume that both the auditory categories (i.e., /aba/ and /ada/) and the visual categories (cat and dog) are distributed along a single acoustic and semantic dimension, respectively (Figure\ \@ref(fig:model)).
@@
 
-So far, we only accounted for categorical variability. For instance, if the speaker generates a target production $a_t$ from an auditory category
+So far, we have only accounted for categorical variability. For instance, if the speaker generates a target production $a_t$ from an auditory category
 $p(a_t | A) \sim N(\mu_{A}, \sigma^2_{A})$, the ideal model assumes that it has direct access to this production token (i.e., $a=a_t$), and that all uncertainty is about the category membership of this token.
@@
 # General Discussion
-When identifying a spoken word under uncertainty, one often needs to make the most of the available cues.
-Some previous work studied optimal behavior under uncertainty from the auditory input only [e.g., @clayard08; @feldman2009], and others studied optimality under multimodal uncertainty in auditory speech and visual facial features [e.g.
-@bejjanki2011].
-The current work explored the case of word identification under uncertainty in speech (word form) and the visual *referent*.
-More specifically, we conducted an ideal observer analysis of the task whereby a model provided predictions about how information from each modality should be combined in an optimal fashion.
+
+In the current paper, we explored word identification under uncertainty about both words and their referents.
+We conducted an ideal observer analysis of this task whereby a model provided predictions about how information from each modality should be combined in an optimal fashion.
 The predictions of the model were tested in a series of three experiments where instances of both the form and the meaning were ambiguous with respect to their category membership only (Experiment 1), when instances of the form were perturbed with additional background noise (Experiment 2), and when instances of the referent were perturbed with additional visual noise (Experiment 3).
-
-In all Experiments, we found many patterns of optimal behavior.
+We discuss the findings of these studies first with respect to our ideal observer model and inferences about optimality and second with respect to their implications for word identification more generally.
+
+## Patterns of optimality and suboptimality
+
+In all of our experiments, at the highest level, we found generally optimal behavior.
 Quantitatively speaking, the optimal model accounted, respectively, for `r 100*R2_optimal_1`%, `r 100*R2_optimal_2`%, and `r 100*R2_optimal_3`% of the variance in mean responses.
@@
 Indeed, in Experiment 1 and 2, the optimal model accounted for more variance in mean responses than the auditory or the visual models did.
-In Experiment 3, participants appeared to rely on one modality, but this was likely a floor effect, due to the fact that noise made the visual input barely perceivable.
-In Experiment 1, which did not involve background noise, participants not only relied on both modalities, but generally weighted these modalities according to the prediction of the optimal model, that is, according to their relative reliability.
+In Experiment 3, participants appeared to rely on one modality, but this was likely a floor effect, due to the fact that noise made the visual input barely perceptable.
+Further, in Experiment 1, which did not involve background noise, participants not only relied on both modalities, but generally weighted these modalities according to the predictions of the optimal model, that is, according to their relative reliability.
 At the individual level, however, we found evidence of a between-subject variation: Some participants relied  more on the visual modality, whereas others relied  more on the auditory modality.
 
-We documented two major cases of sub-optimality.
-First, in all Experiments, the variance associated with each modality increased in the bimodal condition compared to the unimodal conditions.
-This fact means that participants responded slightly more randomly in the bimodal condition than they did in the unimodal conditions.
+Despite this overall pattern, we documented two major cases of sub-optimality.
+First, in all experiments, the variance associated with each modality increased in the bimodal condition compared to the unimodal conditions.
+Participants responded slightly more randomly in the bimodal condition than they did in the unimodal conditions.
 This finding contrasts with research on  multisensory integration where associations tend to lead to a higher precision [e.g., @ernst02].
@@
 In contrast, the word-referent association is usually arbitrary and, in particular, the cues are not expected to be correlated perceptually.
-Therefore the observer cannot form a unified percept, rather, it must encode information separately from both modalities and retain this encoding through the decision making process.
-Retaining two separate cues at the same time instead of forming one unified percept (as in multisensory integration of redundant cues), or instead of retaining only one cue (as in the unimodal case), is likely to place extra-demand on cognitive resources, which, in turn, can cause general performance to drop.
+Therefore the observer cannot form a unified percept, rather, information must be encoded separately from both modalities and must retain this encoding through the decision making process.
+Retaining two separate cues at the same time instead of forming one unified percept (as in multisensory integration of redundant cues), or instead of retaining only one cue (as in the unimodal case), is likely to place extra demands on cognitive resources, which, in turn, could cause general performance to drop.
 Indeed, there is evidence that cognitive load due to divided attention (e.g., when performing two tasks at the same time) has a detrimental effect on word recognition [@mattys11].
 
-Some previous research found a similar case of suboptimal behavior.
-For instance, studies that explored  the identification of ambiguous, newly learned pairs of word-referent associations all reported what appears to be a decrease in speech perception acuity in both children [@stager1997] and adults [@pajak2016].
+Some previous research bas found similar cases of suboptimal behavior.
+For instance, studies that have explored the identification of ambiguous, newly learned pairs of word-referent associations have reported what appears to be a decrease in speech perception acuity in both children [@stager1997] and adults [@pajak2016].
 Recently, @hofer2017 provided a probabilistic model of this phenomenon.
-In agreement with the method and finding in the current study, @hofer2017 characterized the apparent reduction in perceptual acuity as an increase in the noise variance of the auditory modality.
-Our finding, besides providing more evidence to this documented fact, suggests that the  reduction in perceptual acuity may occur simultaneously in both the auditory *and* the visual modalities.
+In agreement with the findings of our study, @hofer2017 characterized the apparent reduction in perceptual acuity as an increase in the noise variance of the auditory modality.
+Our findings, besides providing more evidence to this documented fact, suggest that the  reduction in perceptual acuity may occur simultaneously in both the auditory *and* the visual modalities.
 
 The second case of sub-optimality is related to how participants weighted the cues from the visual and the auditory modalities in a noisy context.
-In contrast to Experiment 1 where the combination was indistinguishable from the optimal prediction, results of Experiment 2 and 3 which both involved background noise in one modality, showed that participants had a systematic preference for the other (non-noisy) modality.
-When the speech signal is degraded, people, in previous work, were shown to compensate by relying more on other sources of information such as the accompanying visual cues, the semantic/syntactic context, or the top-down expectations.
+In contrast to Experiment 1 where the combination was indistinguishable from the optimal prediction, results of Experiment 2 and 3 suggested that participants had a systematic preference for the other (non-noisy) modality.
+This finding aligns with previous work that suggests that when speech signals are degraded, participants compensate by relying more on other sources of information such as the accompanying visual cues, the semantic/syntactic context, or the top-down expectations.
 This kind of compensation has been observed with adults [@mcclelland2006; @Tanenhaus1995; @mattys12], and recent evidence suggests that it starts in childhood [@yurovsky2017; @macdonald2018].
-However, and generally speaking, previous experimental studies have not differentiated between an optimal compensatory strategy (i.e., relying more on the alternative source while using all information still available in the distorted signal), and a sub-optimal strategy (i.e., relying more on the alternative source while ignoring at least some of the information still available in the distorted signal).
+Generally speaking, previous experimental studies have not differentiated between an optimal compensatory strategy (i.e., relying more on the alternative source while using all information still available in the distorted signal), and a sub-optimal strategy (i.e., relying more on the alternative source while ignoring at least some of the information still available in the distorted signal), however.
 The formal approach followed in this paper allowed us to tease apart these two possibilities, and our analysis supports the sub-optimal compensatory strategy: The preference for the non-noisy modality is above and beyond what can be explained by the relative reliability alone, meaning that the participants tend to ignore at least part of the information still available in the noisy modality.
 
-This second case of sub-optimal behavior is possibly related to the fact that language understanding under degraded  conditions is cognitively more taxing than language understanding under normal conditions [@ronnberg2010; @mattys12; @peelle2018].
-This fact can lead to a sub-optomal behavior (i.e., over-reliance on the less noisy cue) as participants would seek to minimized cognitive effort.
+This second case of sub-optimal behavior may be related to the fact that language understanding under degraded  conditions is cognitively more taxing than language understanding under normal conditions [@ronnberg2010; @mattys12; @peelle2018].
+Perhap these demands lead to sub-optimal behavior (i.e., over-reliance on the less noisy cue) as participants seek to minimized cognitive effort.
 One could also explain this phenomenon in terms of the metacognitive experience about the fluency with which information is processed.
 The perceived perceptual fluency (e.g., the ease with which a stimulus' physical identity can be identified) can affect a wide variety of human judgements [see @schwarz2004 for a review].
-In particular, variables that improve fluency tends to increase liking/preference [@reber98].
+In particular, variables that improve fluency tend to increase liking/preference [@reber98].
 In our case, the subjective experience of lower fluency in the noisy modality might cause people to underestimate information that can be extracted from this modality, especially when presented simultaneously with a higher fluency alternative.
 
-An important question to ask is how the combination mechanism---as revealed in our controlled study---scales up to real life situations.
-Note that in order to test audio-visual cue combination under uncertainty, we had to use a case of double ambiguity, that is, a case where both the word forms ("ada"-"aba") and the referents (cat-dog) were similar and, thus, confusable.
+## Word recognition in the wild
+
+An important question to ask is how the combination mechanism -- as revealed in our controlled study -- scales up to real life situations.
+Note that in order to test audio-visual cue combination under uncertainty, we had to use a case of double ambiguity, that is, a case where both the word forms ("ada"--"aba") and the referents (cat--dog) were similar and, thus, confusable.
 However, to what extent does such a case occur in real languages?
@@
 For instance, @dautriche17 analyzed 100 languages and found that words that are similar phonologically  tend to be similar semantically as well.
-These studies suggest that the case of double uncertainty, though perhaps not pervasive, could be a real issue in language as it increase the probability of confusability for many words.\linebreak That being said, besides the case of double ambiguity *intrinsic* to language, our mechanism might play a more significant role when ambiguity in both the form and/or the referent is induced by an *external* noisy context even when these forms and referents are not confusable in normal situations.
-
-Though we only tested adults in this paper, the problem of word recognition under uncertainty, as well as the need to make the most of the available cues, is arguably more pressing for children.
+These studies suggest that the case of double uncertainty, though perhaps not pervasive, could be a real issue in language as it increase the probability of confusability for many words.
+That said, the inferences discussed here might play a more significant role in naturalistic language comprehension when ambiguity in both the form and/or the referent is induced by an *external* noisy context -- e.g., a very noisy party or a far away referent -- even when these forms and referents are not confusable in normal situations.
+
+Though we only studied adult performance in this paper, the problem of word recognition under uncertainty is likely more pressing for children.
 In fact, children have greater difficulties differentiating the meanings of novel similar-sounding words (e.g., "bin" vs.
@@
 Such similar-sounding words can be shown to be differentiated by infants in simplified experimental settings [e.g., @yoshida2009].
-Nevertheless, @Swingley2007 suggested this differentiation is not mature  and is probably noisier than the adult-like representation and/or encoded with lower confidence.
-Thus, it looks like children, even more than adults, may greatly benefit from additional disambiguating cues during new word-referent encoding and recognition.
-For example, @dautriche2015 showed that 18-month-olds can leverage the difference in the syntactic category (noun vs.
-verb).
-Further work is needed to explore whether salient referential cues also help children disambiguate similar sounding words.
-
-The multi-modal cue combination strategy might help children not only recognize words, but also refine the underlying phonological and semantic representations in the process.
-Previous research in early word learning has---whether implicitly or explicitly---largely treated the process of refining the word form and of refining the word meaning as follwing a linear timeline However, recent developmental data shows that children do not wait to have completed the acquisition of forms to start learning the meanings [@bergelson2012; @tincoff1999].
+Nevertheless, @Swingley2007 suggested that the ability to make this differentiation is likely not mature in early childhood; children's repesentations are almost certainly noisier than the adults' representations and may also be encoded with lower confidence.
+Thus, children even more than adults might benefit from additional disambiguating cues during new word-referent encoding and recognition.
+<!-- For one example of such a benefit, @dautriche2015 showed that 18-month-olds can leverage the difference in the syntactic category (noun vs. verb).  -->
+<!-- Further work is needed to explore whether salient referential cues also help children disambiguate similar sounding words. -->
+
+A multi-modal cue combination strategy might help children not only recognize words, but also refine their underlying phonological and semantic representations in the process.
+Previous research in early word learning has -- whether implicitly or explicitly -- largely treated the process of refining the word form and of refining the word meaning as follwing a linear timeline However, recent developmental data reveal that children do not wait to have complete acquisition of word forms before they start learning their meanings [@bergelson2012; @tincoff1999].
 Rather, both form and meaning representations develop in a parallel fashion.
-A few studies pointed to the possibility of an interaction between sound and meaning in early acquisition.
+A few studies have already suggested the possibility of an interaction between sound and meaning in early acquisition.
 For instance, @waxman1995 showed that labeling various objects with the same name helps infants form the underlying semantic category [but see @sloutsky2003].
-Vice versa, @yeung09 showed that pairing similar sounds with different objects help infants enhance their sensitivity to the subtle phonological contrasts in their native language.
-The present study proposes a first step towards a formal framework where isolated accounts of sound-meaning interaction in development can be unified and further explored.
-
-One limitation of this work is that we used simplified stimuli.
+And in the opposite direction, @yeung09 showed that pairing similar sounds with different objects can helps infants enhance their sensitivity to subtle phonological contrasts in their native language.
+The present study proposes a first step towards a formal framework where these sorts of sound-meaning interactions in development can be unified and further explored.
+
+One salient limitation of our current work is that we used a restricted and highly simplified stimulus set.
 For the auditory modality, we used speech categories that varied along a single acoustic dimension.
-While this dimension might be sufficient to recognize  words in our specific case, in general the speech signal may be more complex, varying along several acoustic/phonetic dimensions.
+While this dimension might be sufficient to recognize  words in our specific case, in general the speech signal is far more complex, varying along several acoustic/phonetic dimensions.
 Additionally, these dimensions may be highly variable due to various kinds of speaker and context differences.
-The same thing can be said about the referential stimuli.
+The same thing can be said about our visual stimuli.
 Here we used a continuum along a single morph dimension in order to construct a multimodal input where the auditory and visual components have symmetrical properties.
@@
 Parameterizing semantic dimensions is a notoriously difficult problem, but morphs have been used in previous research as a reasonable proxy [@freedman2001; @havy2016; @sloutsky2004].
-It is an open question as to whether people use the same strategy in controlled laboratory conditions, as in more naturalistic settings where they have to deal with various levels of variability.
-An answer to this question is likely to involve a multifaceted research approach, involving---besides conducting laboratory experiments---testing computational mechanisms with an input that represents, more accurately, the complexity of multimodal variability in the learning environment [@fourtassi2014b; @harwath2016; @roy2015; @dupoux2018].
-
-# Conclusion 
-This work studied the mechanism of spoken word identification under uncertainty in both the form and the referent.
-We conducted an ideal observer analysis of this task.
-We found people to be near optimal in their cue combination (at least at the population level): They weighted each modality according to its relative reliability.
-However, they also showed patterns of sub-optimality especially when the stimuli were perturbed with additional background noise.
-This work provides a formal framework where old and new questions about word recognition in a referential context can be given a precise formulation.
+It is an open question whether people use the same strategy in controlled laboratory conditions and more naturalistic settings where they have to deal with various levels of variability.
+An answer to this question is likely to involve a multifaceted research approach that goes beyond controlled experimentation.
+We believe that one fruitful approach is to test computational mechanisms with an input that more accurately represents the full extent of multimodal variability in the learning environment [@fourtassi2014b; @harwath2016; @roy2015; @dupoux2018].
+
+# Conclusions
+
+Our work provides a formal framework where old and new questions about word recognition in a referential context can be given a precise formulation.
 For instance, of particular interest is the case of iconicity, that is, when there is a resemblance between the sound of a word and its referent.
@@
 Finally, though the current framework only characterizes adult word recognition, it provides a first step towards a model where developmental questions can also be investigated.
-For instance, future work should explore whether children, like adults, use probabilistic cues from both the auditory and the visual input to recognize ambiguous words,  the extent to which they combine these cues in an optimal fashion, and whether these combination help them with refining their early phonological and semantic representations.
+For instance, future work should explore whether children, like adults, use probabilistic cues from both the auditory and the visual input to recognize ambiguous words, the extent to which they combine these cues in an optimal fashion, and whether this cue combination help them to refine their early phonological and semantic representations.
 

### 2018-05-29 Writeup/ms.Rmd
last pass

@@
 ---
-title             : "Word-Referent Identification Under Multimodal Uncertainty"
+title             : "How Optimal is Word-Referent Identification Under Multimodal Uncertainty?"
 shorttitle        : "Word Identification Under Multimodal Uncertainty"
+#numbersections: true
 
@@
 How do these tasks interact with one another?
-We introduce a paradigm that allows us to examine how adults identify words under joint uncertainty in the auditory and visual modalities and propose an ideal observer model of how cues in these modalitiess are combined optimally.
+We introduce a paradigm that allows us to examine how adults identify words under joint uncertainty in the auditory and visual modalities and propose an ideal observer model of how cues in these modalities are combined optimally.
 Model predictions are tested in three experiments where word recognition is made under two kinds of uncertainty: category ambiguity and perceptual noise.
@@
 keywords          : "Language understanding; audio-visual processing; word learning; speech perception; computational modeling."
-
-wordcount         : "X"
 
@@
 
+# Introduction
 Language uses symbols expressed in one modality -- the auditory modality, in the case of speech -- to communicate about the world, which we perceive through many different sensory modalities.
@@
 As a simplified case study of early word learning, the task of matching sounds to corresponding visual objects has been studied extensively in the developmental literature.
-For example, many studies focus on how children might succeed in this type of task task despite referential ambiguity [@smith08; @pinker1989; @medina2011; @vouloumanos2008; @yurovsky2015; @suanda2014; @vlach2013].
+For example, many studies focus on how children might succeed in this type of task despite referential ambiguity [@smith08; @pinker1989; @medina2011; @vouloumanos2008; @yurovsky2015; @suanda2014; @vlach2013].
 However, even when they *know* the meanings of a word, listeners (both children and adults) often still find it challenging to recognize which word the speaker has uttered, especially under noise [@mattys12; @peelle2018].
@@
 We focus on the special case where people have access to multimodal cues from the auditory speech and the visual referent.
-In the General Discussion, we return to the question of how these findings relate to questiosn about word learning.
+In the General Discussion, we return to the question of how these findings relate to questions about word learning.
 
@@
 Humans can deviate from the ideal for several reasons.
-For instance, as mentioned above, a sub-optimality can be induced by the privileged status a partiular modality or by the arbitrariness of the referential association.
+For instance, as mentioned above, a sub-optimality can be induced by the privileged status of a particular modality or by the arbitrariness of the referential association.
 In order to study possible patterns of sub-optimality, we compare the optimal model (which provides a normative benchmark) to a descriptive model (which is fit to human responses).
@@
 
-We introduce a paradigm adapted from a task usead by @sloutsky2003.
+We introduce a paradigm adapted from a task used by @sloutsky2003.
 The original was used with both children and adults to probe audio-visual encoding [see @robinson2010 for review].
@@
 Equation 1 provides the optimal model's predictions for how probabilities that characterize uncertainty in the auditory and the visual modalities can be combined to make categorical decisions.
-Parameter estimates of the probability distributions in each modality are derived by fitting unimodal posteriors to the participants' responses in the unimodal conditions, i.e., the condition where only the sounds are heard  or only the pictures are seen (Figure\ \@ref(fig:task)).\footnote{Further technical detail about model fitting in the unimodal conditions will be given in the method section of Experiment 1} Using these derived parameters, the optimal model makes predictions about responses in the bimodal (i.e., audio-visual) condition where participants both hear the sounds and see the pictures.
+Parameter estimates of the probability distributions in each modality are derived by fitting unimodal posteriors to the participants' responses in the unimodal conditions, i.e., the condition where only the sounds are heard  or only the pictures are seen (Figure\ \@ref(fig:task)).\footnote{Further technical detail about model fitting in the unimodal conditions will be given in the method section of Experiment 1.} Using these derived parameters, the optimal model makes predictions about responses in the bimodal (i.e., audio-visual) condition where participants both hear the sounds and see the pictures.
 
@@
 That is, $\sigma^2_{Ab} \gg \sigma^2_{A}$ and $\sigma^2_{Vb} \geqslant \sigma^2_{V}$, leading to $\frac{\sigma^2_{Ab}}{\sigma^2_{Vb}} > \frac{\sigma^2_{A}}{\sigma^2_{V}}$.
-In this case, sub-optimally would consist not only in participants being more random in the bimodal condition, but also in having a systematic preference for the visual modality, even after accounting for informational reliability.
+In this case, sub-optimality would consist not only in participants being more random in the bimodal condition, but also in having a systematic preference for the visual modality, even after accounting for informational reliability.
 
@@
 Participants were excluded if they reported having experienced a technical problem of any sort during the online experiment (N=`r N_all_1 - N_noProb_1`), or if they had less than 50\% accurate responses on the unambiguous training trials (N=`r N_noProb_1 - N_good_1`).
-The final sample consisted of N = `r N_good_1` participants.\footnote{The sample size and exclusion criteria were specified in the pre-registration at https://osf.io/h7mzp/.}
+The final sample consisted of N = `r N_good_1` participants.
+All participants provided informed consent before taking the experiment.
+\footnote{The sample size and exclusion criteria were specified in the pre-registration at https://osf.io/h7mzp/.}
 
@@
 Average categorization judgments and best fits are shown in Figure\ \@ref(fig:unimodal).
-The categorization function of the auditory condition was slightly steeper than that of the visual condition, meaning that participants perceived the sound tokens slightly more categorically and whih higher certainty than they did with the visual tokens.
+The categorization function of the auditory condition was slightly steeper than that of the visual condition, meaning that participants perceived the sound tokens slightly more categorically and with higher certainty than they did with the visual tokens.
 For the auditory modality, we obtained the following values: $b_A=$ `r audBias_val`  [`r audBias_ci2`, `r audBias_ci1`] and $\sigma^2_A=$ `r audVar_val` [`r audVar_ci1`, `r audVar_ci2`].
@@
 Thus, 1) There was a simultaneous increase in the values of the auditory and visual variances in the bimodal condition compared to the unimodal condition, meaning that the bimodal input lead to an increase in response randomness, and 2) this increased randomness did not affect the relative weighting of both modalities, i.e., the participants was weighting modalities according to the relative reliability predicted by the optimal model.
-This situation corresponds to the first case of sub-optimally described in Figure\ \@ref(fig:subOptim).
+This situation corresponds to the first case of sub-optimality described in Figure\ \@ref(fig:subOptim).
 
@@
 As for the weighting scheme used by participants, contrary to Experiment 1 where modalities were weighted according to their relative reliability, we found in this experiment that the visual modality had a greater weight than what was expected from its relative reliability.
-This situation corresponds to the second case of sub-optimally described in Figure\ \@ref(fig:subOptim).
+This situation corresponds to the second case of sub-optimality described in Figure\ \@ref(fig:subOptim).
 
@@
 
-## Patterns of optimality and suboptimality
+## Patterns of optimality and sub-optimality
 
@@
 Indeed, in Experiment 1 and 2, the optimal model accounted for more variance in mean responses than the auditory or the visual models did.
-In Experiment 3, participants appeared to rely on one modality, but this was likely a floor effect, due to the fact that noise made the visual input barely perceptable.
+In Experiment 3, participants appeared to rely on one modality, but this was likely a floor effect, due to the fact that noise made the visual input barely perceptible.
 Further, in Experiment 1, which did not involve background noise, participants not only relied on both modalities, but generally weighted these modalities according to the predictions of the optimal model, that is, according to their relative reliability.
@@
 This finding aligns with previous work that suggests that when speech signals are degraded, participants compensate by relying more on other sources of information such as the accompanying visual cues, the semantic/syntactic context, or the top-down expectations.
-This kind of compensation has been observed with adults [@mcclelland2006; @Tanenhaus1995; @mattys12], and recent evidence suggests that it starts in childhood [@yurovsky2017; @macdonald2018].
+This kind of compensation has been observed with adults [@Tanenhaus1995; @mattys12], and recent evidence suggests that it starts in childhood [@yurovsky2017; @macdonald2018].
 Generally speaking, previous experimental studies have not differentiated between an optimal compensatory strategy (i.e., relying more on the alternative source while using all information still available in the distorted signal), and a sub-optimal strategy (i.e., relying more on the alternative source while ignoring at least some of the information still available in the distorted signal), however.
@@
 This second case of sub-optimal behavior may be related to the fact that language understanding under degraded  conditions is cognitively more taxing than language understanding under normal conditions [@ronnberg2010; @mattys12; @peelle2018].
-Perhap these demands lead to sub-optimal behavior (i.e., over-reliance on the less noisy cue) as participants seek to minimized cognitive effort.
+Perhaps these demands lead to sub-optimal behavior (i.e., over-reliance on the less noisy cue) as participants seek to minimized cognitive effort.
 One could also explain this phenomenon in terms of the metacognitive experience about the fluency with which information is processed.
@@
 Such similar-sounding words can be shown to be differentiated by infants in simplified experimental settings [e.g., @yoshida2009].
-Nevertheless, @Swingley2007 suggested that the ability to make this differentiation is likely not mature in early childhood; children's repesentations are almost certainly noisier than the adults' representations and may also be encoded with lower confidence.
+Nevertheless, @Swingley2007 suggested that the ability to make this differentiation is likely not mature in early childhood; children's representations are almost certainly noisier than the adults' representations and may also be encoded with lower confidence.
 Thus, children even more than adults might benefit from additional disambiguating cues during new word-referent encoding and recognition.
-<!-- For one example of such a benefit, @dautriche2015 showed that 18-month-olds can leverage the difference in the syntactic category (noun vs. verb).  -->
-<!-- Further work is needed to explore whether salient referential cues also help children disambiguate similar sounding words. -->
 
 A multi-modal cue combination strategy might help children not only recognize words, but also refine their underlying phonological and semantic representations in the process.
-Previous research in early word learning has -- whether implicitly or explicitly -- largely treated the process of refining the word form and of refining the word meaning as follwing a linear timeline However, recent developmental data reveal that children do not wait to have complete acquisition of word forms before they start learning their meanings [@bergelson2012; @tincoff1999].
+Previous research in early word learning has -- whether implicitly or explicitly -- largely treated the process of refining the word form and of refining the word meaning as following a linear timeline.
+However, developmental data reveal that children do not wait to have complete acquisition of word forms before they start learning their meanings [@bergelson2012; @tincoff1999].
 Rather, both form and meaning representations develop in a parallel fashion.
@@
 Our work provides a formal framework where old and new questions about word recognition in a referential context can be given a precise formulation.
-For instance, of particular interest is the case of iconicity, that is, when there is a resemblance between the sound of a word and its referent.
+While we focused on the case of arbitrary associations, it is possible to use the same framework to study, for instance, the case of \textit{iconicity}, that is, when there is a resemblance between the sound of a word and its referent.
 Previous work has suggested that iconicity, among other things, helps with learning (and generalizing the meaning of) new words [see @dingemanse2015 for a review].
@@
 
+# Acknowledgements
+This work was supported by a post-doctoral grant from the Fyssen Foundation.
+
+# Disclosure statement
+None of the authors have any financial interest or a conflict of interest regarding this work and this submission.
+
 # Appendix 1: derivation of the posterior (Equation 1)
@@
 
-# Acknowledgements
-
-This work was supported by a post-doctoral grant from the Fyssen Foundation + XXX
-
 # References

### 2018-05-29 Writeup/ms.tex
last pass

@@
             pdfauthor={},
-            pdftitle={Word-Referent Identification Under Multimodal Uncertainty},
+            pdftitle={How Optimal is Word-Referent Identification Under Multimodal Uncertainty?},
             colorlinks=true,
@@
 % Essential manuscript parts
-  \title{Word-Referent Identification Under Multimodal Uncertainty}
+  \title{How Optimal is Word-Referent Identification Under Multimodal
+Uncertainty?}
 
@@
 uncertainty. How do these tasks interact with one another? We introduce
-a task that allows us to examine how adults identify words under joint
-uncertainty in the auditory and visual modalities. We propose an ideal
-observer model which provides an account of how auditory and visual cues
-are combined optimally. Model predictions are tested in three
-experiments where word recognition is made under two kinds of
-uncertainty: category ambiguity and/or distorting noise. In all cases,
-the optimal model explains much of the variance in human mean judgments.
-In particular, when the signal is not distorted with noise, participants
-weight the auditory and visual cues optimally, that is, according to the
-relative reliability of each modality. But when one modality has noise
-added to it, human perceivers systematically prefer the unperturbed
-modality to a greater extent than the optimal model does. The study
-provides a formal framework which helps us understand precisely how word
-form and word meaning interact in word recognition under uncertainty.
-Moreover it offers a first step towards a model that accounts for
-form-meaning synergy in early word learning.}
+a paradigm that allows us to examine how adults identify words under
+joint uncertainty in the auditory and visual modalities and propose an
+ideal observer model of how cues in these modalities are combined
+optimally. Model predictions are tested in three experiments where word
+recognition is made under two kinds of uncertainty: category ambiguity
+and perceptual noise. In all cases, the optimal model explains much of
+the variance in human mean judgments. When the signal is not distorted
+with noise, participants weight the auditory and visual cues optimally,
+that is, according to the relative reliability of each modality. But
+when one modality has noise added to it, human perceivers systematically
+prefer the unperturbed modality to a greater extent than the optimal
+model does. The study provides a formal framework which helps to
+quantify how word form and word meaning interact in word recognition
+under uncertainty. Moreover it offers a first step towards a model that
+accounts for form-meaning synergies in early word learning.}
   \keywords{Language understanding; audio-visual processing; word learning; speech
@@
 
-    \indent Word count: X
   }
@@
 
-Language uses symbols expressed in one modality, e.g., the auditory
-modality, in the case of speech, to communicate about the world, which
+\section{Introduction}\label{introduction}
+
+Language uses symbols expressed in one modality -- the auditory
+modality, in the case of speech -- to communicate about the world, which
 we perceive through many different sensory modalities. Consider hearing
@@
 noise. Perhaps the speaker was yelling \enquote{pea} and not
-\enquote{bee}. Similarly, a sensory impression may not be enough to make
+\enquote{bee.} Similarly, a sensory impression may not be enough to make
 a definitive identification of a visual
@@
 
-The task of matching the sound to the corresponding visual object has
-been extensively studied in the developmental literature since it is
-considered to be an crucial instance of early word learning. For
-example, many studies focused on how children might succeed in this task
-despite high referential ambiguity (Medina, Snedeker, Trueswell, \&
-Gleitman, 2011; Pinker, 1989; Smith \& Yu, 2008; Suanda, Mugwanya, \&
-Namy, 2014; Vlach \& Johnson, 2013; Vouloumanos, 2008; Yurovsky \&
-Frank, 2015). However, even when they know the exact meanings of the
-words, listeners (both children and adults) often face the task of
-recognizing which word the speaker utters, especially under noisy
-circumstances (Mattys, Davis, Bradlow, \& Scott, 2012; Peelle, 2018).
-The purpose of the current study is to explore novel word recognition by
-adults under multimodal uncertainty. We focus on the special case where
-people have access to multimodal cues from the auditory speech and the
-visual referent.
+As a simplified case study of early word learning, the task of matching
+sounds to corresponding visual objects has been studied extensively in
+the developmental literature. For example, many studies focus on how
+children might succeed in this type of task despite referential
+ambiguity (Medina, Snedeker, Trueswell, \& Gleitman, 2011; Pinker, 1989;
+Smith \& Yu, 2008; Suanda, Mugwanya, \& Namy, 2014; Vlach \& Johnson,
+2013; Vouloumanos, 2008; Yurovsky \& Frank, 2015). However, even when
+they \emph{know} the meanings of a word, listeners (both children and
+adults) often still find it challenging to recognize which word the
+speaker has uttered, especially under noise (Mattys, Davis, Bradlow, \&
+Scott, 2012; Peelle, 2018). The purpose of the current study is thus to
+explore word recognition by adults under multimodal uncertainty. We
+focus on the special case where people have access to multimodal cues
+from the auditory speech and the visual referent. In the General
+Discussion, we return to the question of how these findings relate to
+questions about word learning.
 
@@
 should be under this characterization.\footnote{It is, thus, a general
-  instance of the rational approach to cognition (Anderson, 1990). It
-  can also be seen as an instance of Marr's computational level of
-  analysis (Marr, 1982).} When there is uncertainty in the input, the
-ideal observer performs an optimal probabilistic inference. For example,
-in order to recognize an ambiguous linguistic input, the model uses all
-available probabilistic knowledge in order to maximize the accuracy of
-this recognition. The ideal observer model can be seen as a theoretical
-upper limit on performance. It is not so much a realistic model of human
-performance, as much as a baseline against which human performance can
-be compared (Geisler, 2003; Rahnev \& Denison, 2018). When there is a
-deviation from the ideal, it can reveal extra constraints on human
-cognition, such as limitations on the working memory or attentional
-resources. The ideal observer analysis has had a tremendous impact not
-only on speech related research (Clayards, Tanenhaus, Aslin, \& Jacobs,
-2008; Feldman, Griffiths, \& Morgan, 2009; Kleinschmidt \& Jaeger, 2015;
-Norris \& McQueen, 2008), but also on many other disciplines in the
-cognitive sciences (for reviews, see Chater \& Manning, 2006; Knill \&
-Pouget, 2004; Tenenbaum, Kemp, Griffiths, \& Goodman, 2011)
-
-Some of these ideal-observer-based studies are closely related to the
-question we are addressing in the current work. For instance, Clayards
-et al. (2008) simulated auditory uncertainty by manipulating the
-probability distribution of a cue (Voice Onset Time) that differentiated
-similar words (e.g., \enquote{beach} and \enquote{peach}). They found
-that humans were sensitive to these probabilistic cues and their
-judgments closely reflected the optimal predictions. In another work,
-Feldman et al. (2009) studied the perceptual magnet effect, a phenomenon
-that involves reduced discriminability near prototypical sounds in the
-native language (Kuhl, 1991). They showed that this effect can be
-explained as the consequence of optimally solving the problem of
-perception under uncertainty.
+  instance of the rational approach to cognition (Anderson, 1990),
+  instantiating Marr's computational level of analysis (Marr, 1982).}
+When there is uncertainty in the input, the ideal observer performs an
+optimal probabilistic inference. For example, in order to recognize an
+ambiguous linguistic input, the model uses all available probabilistic
+knowledge in order to maximize the accuracy of this recognition. The
+ideal observer model can be seen as a theoretical upper limit on
+performance. It is not so much a realistic model of human performance,
+as much as a baseline against which human performance can be compared
+(Geisler, 2003; Rahnev \& Denison, 2018). When there is a deviation from
+the ideal, it can reveal extra constraints on human cognition, such as
+limitations on the working memory or attentional resources. This
+approach has had a tremendous impact not only on speech-related research
+(Clayards, Tanenhaus, Aslin, \& Jacobs, 2008; Feldman, Griffiths, \&
+Morgan, 2009; Kleinschmidt \& Jaeger, 2015; Norris \& McQueen, 2008),
+but also on many other disciplines in the cognitive sciences (for
+reviews, see Chater \& Manning, 2006; Knill \& Pouget, 2004; Tenenbaum,
+Kemp, Griffiths, \& Goodman, 2011)
+
+Some prior ideal observer studies are closely related to the question we
+are addressing in the current work. For instance, Clayards et al. (2008)
+simulated auditory uncertainty by manipulating the probability
+distribution of a cue (Voice Onset Time) that differentiated similar
+words (e.g., \enquote{beach} and \enquote{peach}). They found that
+humans were sensitive to these probabilistic cues and their judgments
+closely reflected the optimal predictions. And Feldman et al. (2009)
+studied the perceptual magnet effect, a phenomenon that involves reduced
+discriminability near prototypical sounds in the native language (Kuhl,
+1991), showing that this effect can be explained as the consequence of
+optimally solving the problem of perception under uncertainty.
 
@@
 audio-visual phonemic labeling was consistent (at least at the
-qualitative level) with the behavior of the ideal observer. This
-previous research, however, did not systematically study speech
-understanding when the visual information is obtained, not through the
-speaker's facial features---as in audio-visual speech perception, but
-through the referential context. In fact, experimental findings showed
-that information about the identity of the semantic referent can be
-integrated with linguistic information to resolve lexical and syntactic
-ambiguities in speech (e.g., Eberhard, Spivey-Knowlton, Sedivy, \&
-Tanenhaus, 1995; Spivey, Tanenhaus, Eberhard, \& Sedivy, 2002;
-Tanenhaus, Spivey-Knowlton, Eberhard, \& Sedivy, 1995). To our
-knowledge, however, no study offered an ideal observer analysis of word
-identification in such context, that is, when the listener has to
-combine cues from the sound and the referent.
-
-On the face of it, the question of combining information from the sound
-and the visual referent might seem similar to that of audio-visual
-speech integration. Nevertheless, there are at least two fundamental
-differences between these two cases, and both can influence the way the
-auditory and visual cues are combined: First, in the case of
-audio-visual speech, both modalities offer information about the same
-underlying speech category. They may differ only in terms of their
-informational reliability. In a referential context, however, the
-auditory and visual modalities play different roles in the referential
-process---in addition to possible differences in informational
-reliability. Indeed, the auditory input represents the \emph{symbol}
-whereas the visual input represents the \emph{meaning}. It has been
-shown that speech has a privileged status compared to other sensory
-stimuli (Edmiston \& Lupyan, 2015; Lupyan \& Thompson-Schill, 2012;
-Vouloumanos \& Waxman, 2014; Waxman \& Gelman, 2009; Waxman \& Markow,
-1995), and that this privilege is indeed related to the speech's ability
-to refer (Waxman \& Gelman, 2009).\footnote{There is, however, a debate
-  as to whether speech is privileged for children and adults for similar
-  reasons. Whereas some researchers suggest that speech is privileged
-  for both children and adults because of its ability to refer (e.g.,
-  Waxman \& Gelman, 2009), others suggest that speech might \emph{not}
-  have a referential status from the start. Rather, speech might be
-  preferred by children only because of a low level auditory
-  ``overshadowing'' (e.g., Sloutsky \& Napolitano, 2003).} Thus, in a
-referential context, it is possible that listeners do not treat the
-auditory and visual modalities as equivalent sources of information.
-Instead, there could be a sub-optimal bias for the auditory modality
-beyond what is expected from informational reliability alone.
+qualitative level) with the predictions of an ideal observer. This
+previous research did not, however, systematically study speech
+understanding when visual information was obtained through the
+referential context rather than through observation of speaker's face.
+Although some experimental findings show that information about the
+identity of a referent can be integrated with linguistic information to
+resolve lexical and syntactic ambiguities in speech (e.g., Eberhard,
+Spivey-Knowlton, Sedivy, \& Tanenhaus, 1995; Spivey, Tanenhaus,
+Eberhard, \& Sedivy, 2002; Tanenhaus, Spivey-Knowlton, Eberhard, \&
+Sedivy, 1995), to our knowledge no study has offered an ideal observer
+analysis of this task.
+
+Combining information between words and visual referents might seem
+similar to audio-visual speech integration, but there are at least two
+fundamental differences between these two cases, and both can influence
+the way the auditory and visual cues are combined.
+
+First, in the case of audio-visual speech, both modalities offer
+information about the same underlying speech category. They differ only
+in terms of their informational reliability. In a referential context,
+however, the auditory and visual modalities play different roles in the
+referential process -- the auditory input represents the \emph{symbol}
+whereas the visual input represents the \emph{meaning} (and these
+differences are in addition to possible differences in informational
+reliability). Further, speech is claimed to have a privileged status
+compared to other sensory stimuli (Edmiston \& Lupyan, 2015; Lupyan \&
+Thompson-Schill, 2012; Vouloumanos \& Waxman, 2014; Waxman \& Gelman,
+2009; Waxman \& Markow, 1995), and that this privilege is suggested to
+be specifically related to the ability to refer (Waxman \& Gelman,
+2009).\footnote{There is, however, a debate as to whether speech is
+  privileged for children and adults for similar reasons. Whereas some
+  researchers suggest that speech is privileged for both children and
+  adults because of its ability to refer (e.g., Waxman \& Gelman, 2009),
+  others suggest that speech might \emph{not} have a referential status
+  from the start. Rather, speech might be preferred by children only
+  because of a low level auditory ``overshadowing'' (e.g., Sloutsky \&
+  Napolitano, 2003).} Thus, in a referential context, it is possible
+that listeners do not treat the auditory and visual modalities as
+equivalent sources of information. Instead, there could be a sub-optimal
+bias for the auditory modality beyond what is expected from
+informational reliability alone.
 
@@
 stimuli are expected to be perceptually correlated. The expectation for
-this correlation is such that when there is a mismatch between the
-auditory and visual input, people still integrate them into a unified
-(but illusory) percept (McGurk \& MacDonald, 1976). In the case of
-referential language, however, the multimodal association is by nature
-\emph{arbitrary} (Greenberg, 1957; Saussure, 1916). For instance, there
-is no logical/perceptual connection between the sound \enquote{bee} and
-the corresponding insect. Moreover, variation in the way the sound
-\enquote{bee} is pronounced is generally not expected to correlate
-perceptually with variation in the shape (or any other visual property)
-in the category of bees. In sum, cue combination in the case of
-arbitrary audio-visual associations (word-referent) is likely to be less
-automatic, more effortful, and therefore less conducive to optimal
-integration than it is in the case of perceptually correlated
-associations (as in audio-visual speech perception).
+this correlation is strong enough that when there is a mismatch between
+the auditory and visual input, they are still integrated into a unified
+(but illusory) percept (e.g., the McGurk Effect; McGurk \& MacDonald,
+1976). In the case of referential language, however, the multimodal
+association is by nature \emph{arbitrary} (Greenberg, 1957; Saussure,
+1916). For instance, there is no logical or perceptual connection
+between the sound \enquote{bee} and the corresponding insect. Moreover,
+variation in the way the sound \enquote{bee} is pronounced is generally
+not expected to correlate perceptually with variation in the shape (or
+any other visual property) in the category of bees. In sum, cue
+combination in the case of arbitrary audio-visual associations
+(word-referent) is likely to be less automatic, more effortful, and
+therefore less conducive to optimal integration than it is in the case
+of perceptually correlated associations (as in audio-visual speech
+perception).
 
@@
 
-We investigate how people combine cues from the auditory and the visual
-modality to recognize words in a referential context. In particular, we
-study how this combination is performed under various degrees of
+We investigate how cues from the auditory and the visual modality are
+combined in recognizing words in a referential context. In particular,
+we study how this combination is performed under various degrees of
 uncertainty in both the auditory and the visual modality. Imagine, for
 example, that someone is uncertain whether they heard \enquote{pea} or
-\enquote{bee}, does this uncertainty make them rely more on the referent
-(e.g., the object being pointed at)? Vice versa, if they are not sure if
-they saw a bee or a fly, does it make them rely more on the sound? More
-importantly, when input in both modalities is uncertain to varying
-degrees, do they weight each modality according to its relative
-reliability, which is the optimal strategy, or do they over-rely on a
-particular modality, which is a sub-optimal strategy?
-
-We perform a rational analysis of the task. First we propose an ideal
-observer model that performs the combination in an optimal fashion.
-Second we compare the predictions of the optimal model to human
-responses. Humans can deviate from the ideal for several reasons. For
-instance, as mentioned above, a sub-optimality can be induced by the
-suggested privileged status of speech or by the arbitrariness of the
-referential association. In order to study possible patterns of
-sub-optimality, we compare the optimal model (which provides a normative
-benchmark) to a descriptive model (which is fit to human responses).
-Comparing parameter estimates between these two formulations allows us
-to quantify the degree of deviation from optimality.
+\enquote{bee.} Does this uncertainty make them rely more on the referent
+(e.g., the object being pointed at)? Or, if they are not sure if they
+saw a bee or a fly, does this uncertainty make them rely more on the
+sound? More importantly, when input in both modalities is uncertain to
+varying degrees, do they weight each modality according to its relative
+reliability (the optimal strategy), or do they over-rely on a particular
+modality?
+
+We begin by proposing an ideal observer model that performs the
+combination in an optimal fashion. We then compare the predictions of
+the optimal model to human responses. Humans can deviate from the ideal
+for several reasons. For instance, as mentioned above, a sub-optimality
+can be induced by the privileged status of a particular modality or by
+the arbitrariness of the referential association. In order to study
+possible patterns of sub-optimality, we compare the optimal model (which
+provides a normative benchmark) to a descriptive model (which is fit to
+human responses). Comparing parameter estimates between these two
+formulations allows us to quantify the degree of deviation from
+optimality.
 
@@
 audio-visual tokens were ambiguous with respect to their category
-membership only. In Experiment 2, we intervened by adding background
+membership only. In Experiment 2, we intervened by adding perceptual
 noise to the auditory modality, and in Experiment 3, we intervened by
-adding background noise to the visual modality. In all experiments,
+adding perceptual noise to the visual modality. In all experiments,
 participants were quantitatively near-optimal, though overall response
-precision was slightly lower than expected. Moreover, in Experiment 1
-where neither of the modalities was perturbed with background noise,
+precision was slightly lower than expected. In Experiment 1 -- where
+neither of the modalities was perturbed with background noise --
 participants weighted auditory and visual cues according to the relative
-reliability predicted by the optimal model. In other words, we found no
-evidence for a modality bias towards either the auditory or the visual
-modality. However, in Experiment 2 and 3, participants over-relied on
-one modality when the other modality was perturbed with additional
-noise.
+reliability predicted by the optimal model. However, in Experiment 2 and
+3, participants over-relied on one modality when the other modality was
+perturbed with additional noise.
 
@@
 
-In this section we, first, briefly introduce the multimodal combination
+In this section we first briefly introduce the multimodal combination
 task. Then we explain how behavior in this paradigm can be characterized
@@
 
-We introduce a task adapted from Sloutsky and Napolitano (2003). The
-original task has been used with both children and adults to probe
-audio-visual encoding (see Robinson \& Sloutsky, 2010 for a review).
-Here we use a slightly different version to test word recognition in a
-referential context. We use two visual categories (cat and dog) and two
-auditory categories (/b/ and /d/ embedded in the minimal pair
-/aba/-/ada/). For each participant, an arbitrary pairing is set between
-the auditory and the visual categories, leading to two audio-visual word
-categories (e.g., dog-/aba/, cat-/ada/). In each trial, participants are
-presented with an audio-visual target (the prototype of the target
-category), immediately followed by an audio-visual test stimulus
-(Figure~\ref{fig:task}). The test stimulus may differ from the target in
-both the auditory and the visual components. After these two
-presentations, participants press \enquote{same} or \enquote{different.}
+We introduce a paradigm adapted from a task used by Sloutsky and
+Napolitano (2003). The original was used with both children and adults
+to probe audio-visual encoding (see Robinson \& Sloutsky, 2010 for
+review). Here we use a slightly different version to test word
+recognition in a referential context. We use two visual categories (cat
+and dog) and two auditory categories (/b/ and /d/ embedded in the
+minimal pair /aba/-/ada/). For each participant, an arbitrary pairing is
+set between the auditory and the visual categories, leading to two
+audio-visual word categories (e.g., dog-/aba/, cat-/ada/). In each
+trial, participants are presented with an audio-visual target (the
+prototype of the target category), immediately followed by an
+audio-visual test stimulus (Figure~\ref{fig:task}). The test stimulus
+may differ from the target in both the auditory and the visual
+components. After these two presentations, participants press
+\enquote{same} or \enquote{different.}
 
@@
 In the testing phase of the original task (Sloutsky \& Napolitano,
-2003), participants are asked whether or not the two audio-visual
+2003), participants were asked whether or not the two audio-visual
 presentations are \emph{identical}. In the current study, we are
@@
 model used in most research on multisensory integration (e.g., Ernst \&
-Banks, 2002)---which typically studies continuous stimuli (e.g., size,
-location)---the probabilistic information in our case cannot be
-characterized with \emph{sensory noise}, only. Indeed, our task involves
-responses over categorical variables (phonemes and concepts), and
-therefore, the optimal model should take into account, not only the
-noise variability around an individual perceptual estimate, but also its
-\emph{categorical variability}, i.e., the uncertainty related to whether
-this perceptual estimate belongs to a given category (see also
-Bankieris, Bejjanki, \& Aslin, 2017; Bejjanki et al., 2011). In what
-follows, we describe a model that accounts for both types of
-variability. First, we describe the model in the simplified case of
-categorical variability only. Second, we augment this simplified model
-to account for sensory noise.
+Banks, 2002), which typically studies continuous stimuli (e.g., size,
+location), the probabilistic information in our case cannot be
+characterized with \emph{sensory noise} only. Since our task involves
+responses over categorical variables (phonemes and concepts), the
+optimal model should take into account not only the noise variability
+around an individual perceptual estimate but also its \emph{categorical
+variability}, i.e., the uncertainty related to whether this perceptual
+estimate belongs to a given category (see also Bankieris, Bejjanki, \&
+Aslin, 2017; Bejjanki et al., 2011). In what follows, we describe a
+model that accounts for both types of variability. First, we describe
+the model in the simplified case of categorical variability only.
+Second, we augment this simplified model to account for sensory noise.
 
@@
 
-So far, we only accounted for categorical variability. For instance, if
-the speaker generates a target production \(a_t\) from an auditory
-category \(p(a_t | A) \sim N(\mu_{A}, \sigma^2_{A})\), the ideal model
-assumes that it has direct access to this production token (i.e.,
-\(a=a_t\)), and that all uncertainty is about the category membership of
-this token. However, we might also want to account for internal noise in
-the brain and/or external noise in the environment. For example, the
-observer might not have access to the exact produced target, but only to
-the target perturbed by noise. If we assume this noise to be normally
-distributed, that is, \(p(a | a_t) \sim N(a_t, \sigma^2_{N_A})\), then
-integrating over \(a_t\) leads to this new expression of the probability
-distribution: \[ p(a | A) \sim N(\mu_{A}, \sigma^2_{A}+\sigma^2_{N_A})\]
-Similarly, in the case of sensory noise in the visual modality, we get:
+So far, we have only accounted for categorical variability. For
+instance, if the speaker generates a target production \(a_t\) from an
+auditory category \(p(a_t | A) \sim N(\mu_{A}, \sigma^2_{A})\), the
+ideal model assumes that it has direct access to this production token
+(i.e., \(a=a_t\)), and that all uncertainty is about the category
+membership of this token. However, we might also want to account for
+internal noise in the brain and/or external noise in the environment.
+For example, the observer might not have access to the exact produced
+target, but only to the target perturbed by noise. If we assume this
+noise to be normally distributed, that is,
+\(p(a | a_t) \sim N(a_t, \sigma^2_{N_A})\), then integrating over
+\(a_t\) leads to this new expression of the probability distribution:
+\[ p(a | A) \sim N(\mu_{A}, \sigma^2_{A}+\sigma^2_{N_A})\] Similarly, in
+the case of sensory noise in the visual modality, we get:
 \[ p(a | V) \sim N(\mu_{V}, \sigma^2_{V}+\sigma^2_{N_V})\] Finally,
@@
 sounds are heard or only the pictures are seen
-(Figure~\ref{fig:task}).\footnote{Further technical detail about model fitting in the unimodal conditions will be given in the method section of Experiment 1}
+(Figure~\ref{fig:task}).\footnote{Further technical detail about model fitting in the unimodal conditions will be given in the method section of Experiment 1.}
 Using these derived parameters, the optimal model makes predictions
@@
   \(\frac{\sigma^2_{Ab}}{\sigma^2_{Vb}} > \frac{\sigma^2_{A}}{\sigma^2_{V}}\).
-  In this case, sub-optimally would consist not only in participants
+  In this case, sub-optimality would consist not only in participants
   being more random in the bimodal condition, but also in having a
@@
 unambiguous training trials (N=6). The final sample consisted of N = 80
-participants.\footnote{The sample size and exclusion criteria were specified in the pre-registration at https://osf.io/h7mzp/.}
+participants. All participants provided informed consent before taking
+the experiment.
+\footnote{The sample size and exclusion criteria were specified in the pre-registration at https://osf.io/h7mzp/.}
 
@@
 meaning that participants perceived the sound tokens slightly more
-categorically and whih higher certainty than they did with the visual
+categorically and with higher certainty than they did with the visual
 tokens. For the auditory modality, we obtained the following values:
@@
 predict the other half (averaging across 10 random partitions). The
-predictive power of the model remained very high (\(r^2\)=0.92).
+predictive power of the model remained very high (\(r^2\)=0.93).
 
@@
 reliability predicted by the optimal model. This situation corresponds
-to the first case of sub-optimally described in
+to the first case of sub-optimality described in
 Figure~\ref{fig:subOptim}.
@@
 from its relative reliability. This situation corresponds to the second
-case of sub-optimally described in Figure~\ref{fig:subOptim}.
+case of sub-optimality described in Figure~\ref{fig:subOptim}.
 
@@
 
-When identifying a spoken word under uncertainty, one often needs to
-make the most of the available cues. Some previous work studied optimal
-behavior under uncertainty from the auditory input only (e.g., Clayards
-et al., 2008; Feldman et al., 2009), and others studied optimality under
-multimodal uncertainty in auditory speech and visual facial features
-(e.g. Bejjanki et al., 2011). The current work explored the case of word
-identification under uncertainty in speech (word form) and the visual
-\emph{referent}. More specifically, we conducted an ideal observer
-analysis of the task whereby a model provided predictions about how
+In the current paper, we explored word identification under uncertainty
+about both words and their referents. We conducted an ideal observer
+analysis of this task whereby a model provided predictions about how
 information from each modality should be combined in an optimal fashion.
@@
 noise (Experiment 2), and when instances of the referent were perturbed
-with additional visual noise (Experiment 3).
-
-In all Experiments, we found many patterns of optimal behavior.
-Quantitatively speaking, the optimal model accounted, respectively, for
-89\%, 91\%, and 97\% of the variance in mean responses. When compared to
-the predictions of the visual or the auditory models, participants
-generally relied on both modalities to make their decisions in the
-bimodal condition. Indeed, in Experiment 1 and 2, the optimal model
-accounted for more variance in mean responses than the auditory or the
-visual models did. In Experiment 3, participants appeared to rely on one
-modality, but this was likely a floor effect, due to the fact that noise
-made the visual input barely perceivable. In Experiment 1, which did not
-involve background noise, participants not only relied on both
-modalities, but generally weighted these modalities according to the
-prediction of the optimal model, that is, according to their relative
-reliability. At the individual level, however, we found evidence of a
-between-subject variation: Some participants relied more on the visual
-modality, whereas others relied more on the auditory modality.
-
-We documented two major cases of sub-optimality. First, in all
-Experiments, the variance associated with each modality increased in the
-bimodal condition compared to the unimodal conditions. This fact means
-that participants responded slightly more randomly in the bimodal
-condition than they did in the unimodal conditions. This finding
-contrasts with research on multisensory integration where associations
-tend to lead to a higher precision (e.g., Ernst \& Banks, 2002).
-Nevertheless, there is a crucial difference between these two situations
-(besides the obvious difference in terms of the models used). Research
-on multisensory integration (of which audio-visual speech is arguably an
-instance) deals with redundant multimodal cues, and these cues are
-integrated into a unified percept. In contrast, the word-referent
-association is usually arbitrary and, in particular, the cues are not
-expected to be correlated perceptually. Therefore the observer cannot
-form a unified percept, rather, it must encode information separately
-from both modalities and retain this encoding through the decision
-making process. Retaining two separate cues at the same time instead of
-forming one unified percept (as in multisensory integration of redundant
-cues), or instead of retaining only one cue (as in the unimodal case),
-is likely to place extra-demand on cognitive resources, which, in turn,
-can cause general performance to drop. Indeed, there is evidence that
-cognitive load due to divided attention (e.g., when performing two tasks
-at the same time) has a detrimental effect on word recognition (Mattys
-\& Wiget, 2011).
-
-Some previous research found a similar case of suboptimal behavior. For
-instance, studies that explored the identification of ambiguous, newly
-learned pairs of word-referent associations all reported what appears to
-be a decrease in speech perception acuity in both children (Stager \&
-Werker, 1997) and adults (Pajak, Creel, \& Levy, 2016). Recently, Hofer
-and Levy (2017) provided a probabilistic model of this phenomenon. In
-agreement with the method and finding in the current study, Hofer and
-Levy (2017) characterized the apparent reduction in perceptual acuity as
-an increase in the noise variance of the auditory modality. Our finding,
-besides providing more evidence to this documented fact, suggests that
-the reduction in perceptual acuity may occur simultaneously in both the
-auditory \emph{and} the visual modalities.
+with additional visual noise (Experiment 3). We discuss the findings of
+these studies first with respect to our ideal observer model and
+inferences about optimality and second with respect to their
+implications for word identification more generally.
+
+\subsection{Patterns of optimality and
+sub-optimality}\label{patterns-of-optimality-and-sub-optimality}
+
+In all of our experiments, at the highest level, we found generally
+optimal behavior. Quantitatively speaking, the optimal model accounted,
+respectively, for 89\%, 91\%, and 97\% of the variance in mean
+responses. When compared to the predictions of the visual or the
+auditory models, participants generally relied on both modalities to
+make their decisions in the bimodal condition. Indeed, in Experiment 1
+and 2, the optimal model accounted for more variance in mean responses
+than the auditory or the visual models did. In Experiment 3,
+participants appeared to rely on one modality, but this was likely a
+floor effect, due to the fact that noise made the visual input barely
+perceptible. Further, in Experiment 1, which did not involve background
+noise, participants not only relied on both modalities, but generally
+weighted these modalities according to the predictions of the optimal
+model, that is, according to their relative reliability. At the
+individual level, however, we found evidence of a between-subject
+variation: Some participants relied more on the visual modality, whereas
+others relied more on the auditory modality.
+
+Despite this overall pattern, we documented two major cases of
+sub-optimality. First, in all experiments, the variance associated with
+each modality increased in the bimodal condition compared to the
+unimodal conditions. Participants responded slightly more randomly in
+the bimodal condition than they did in the unimodal conditions. This
+finding contrasts with research on multisensory integration where
+associations tend to lead to a higher precision (e.g., Ernst \& Banks,
+2002). Nevertheless, there is a crucial difference between these two
+situations (besides the obvious difference in terms of the models used).
+Research on multisensory integration (of which audio-visual speech is
+arguably an instance) deals with redundant multimodal cues, and these
+cues are integrated into a unified percept. In contrast, the
+word-referent association is usually arbitrary and, in particular, the
+cues are not expected to be correlated perceptually. Therefore the
+observer cannot form a unified percept, rather, information must be
+encoded separately from both modalities and must retain this encoding
+through the decision making process. Retaining two separate cues at the
+same time instead of forming one unified percept (as in multisensory
+integration of redundant cues), or instead of retaining only one cue (as
+in the unimodal case), is likely to place extra demands on cognitive
+resources, which, in turn, could cause general performance to drop.
+Indeed, there is evidence that cognitive load due to divided attention
+(e.g., when performing two tasks at the same time) has a detrimental
+effect on word recognition (Mattys \& Wiget, 2011).
+
+Some previous research bas found similar cases of suboptimal behavior.
+For instance, studies that have explored the identification of
+ambiguous, newly learned pairs of word-referent associations have
+reported what appears to be a decrease in speech perception acuity in
+both children (Stager \& Werker, 1997) and adults (Pajak, Creel, \&
+Levy, 2016). Recently, Hofer and Levy (2017) provided a probabilistic
+model of this phenomenon. In agreement with the findings of our study,
+Hofer and Levy (2017) characterized the apparent reduction in perceptual
+acuity as an increase in the noise variance of the auditory modality.
+Our findings, besides providing more evidence to this documented fact,
+suggest that the reduction in perceptual acuity may occur simultaneously
+in both the auditory \emph{and} the visual modalities.
 
@@
 indistinguishable from the optimal prediction, results of Experiment 2
-and 3 which both involved background noise in one modality, showed that
-participants had a systematic preference for the other (non-noisy)
-modality. When the speech signal is degraded, people, in previous work,
-were shown to compensate by relying more on other sources of information
-such as the accompanying visual cues, the semantic/syntactic context, or
-the top-down expectations. This kind of compensation has been observed
-with adults (Mattys et al., 2012; McClelland, Mirman, \& Holt, 2006;
-Tanenhaus et al., 1995), and recent evidence suggests that it starts in
-childhood (K. MacDonald, Marchman, Fernald, \& Frank, 2018; Yurovsky,
-Case, \& Frank, 2017). However, and generally speaking, previous
-experimental studies have not differentiated between an optimal
+and 3 suggested that participants had a systematic preference for the
+other (non-noisy) modality. This finding aligns with previous work that
+suggests that when speech signals are degraded, participants compensate
+by relying more on other sources of information such as the accompanying
+visual cues, the semantic/syntactic context, or the top-down
+expectations. This kind of compensation has been observed with adults
+(Mattys et al., 2012; Tanenhaus et al., 1995), and recent evidence
+suggests that it starts in childhood (K. MacDonald, Marchman, Fernald,
+\& Frank, 2018; Yurovsky, Case, \& Frank, 2017). Generally speaking,
+previous experimental studies have not differentiated between an optimal
 compensatory strategy (i.e., relying more on the alternative source
@@
 while ignoring at least some of the information still available in the
-distorted signal). The formal approach followed in this paper allowed us
-to tease apart these two possibilities, and our analysis supports the
-sub-optimal compensatory strategy: The preference for the non-noisy
-modality is above and beyond what can be explained by the relative
-reliability alone, meaning that the participants tend to ignore at least
-part of the information still available in the noisy modality.
-
-This second case of sub-optimal behavior is possibly related to the fact
-that language understanding under degraded conditions is cognitively
-more taxing than language understanding under normal conditions (Mattys
-et al., 2012; Peelle, 2018; Rönnberg, Rudner, Lunner, Zekveld, \&
-others, 2010). This fact can lead to a sub-optomal behavior (i.e.,
-over-reliance on the less noisy cue) as participants would seek to
-minimized cognitive effort. One could also explain this phenomenon in
-terms of the metacognitive experience about the fluency with which
-information is processed. The perceived perceptual fluency (e.g., the
-ease with which a stimulus' physical identity can be identified) can
-affect a wide variety of human judgements (see Schwarz, 2004 for a
-review). In particular, variables that improve fluency tends to increase
-liking/preference (Reber, Winkielman, \& Schwarz, 1998). In our case,
-the subjective experience of lower fluency in the noisy modality might
-cause people to underestimate information that can be extracted from
-this modality, especially when presented simultaneously with a higher
-fluency alternative.
-
-An important question to ask is how the combination mechanism---as
-revealed in our controlled study---scales up to real life situations.
+distorted signal), however. The formal approach followed in this paper
+allowed us to tease apart these two possibilities, and our analysis
+supports the sub-optimal compensatory strategy: The preference for the
+non-noisy modality is above and beyond what can be explained by the
+relative reliability alone, meaning that the participants tend to ignore
+at least part of the information still available in the noisy modality.
+
+This second case of sub-optimal behavior may be related to the fact that
+language understanding under degraded conditions is cognitively more
+taxing than language understanding under normal conditions (Mattys et
+al., 2012; Peelle, 2018; Rönnberg, Rudner, Lunner, Zekveld, \& others,
+2010). Perhaps these demands lead to sub-optimal behavior (i.e.,
+over-reliance on the less noisy cue) as participants seek to minimized
+cognitive effort. One could also explain this phenomenon in terms of the
+metacognitive experience about the fluency with which information is
+processed. The perceived perceptual fluency (e.g., the ease with which a
+stimulus' physical identity can be identified) can affect a wide variety
+of human judgements (see Schwarz, 2004 for a review). In particular,
+variables that improve fluency tend to increase liking/preference
+(Reber, Winkielman, \& Schwarz, 1998). In our case, the subjective
+experience of lower fluency in the noisy modality might cause people to
+underestimate information that can be extracted from this modality,
+especially when presented simultaneously with a higher fluency
+alternative.
+
+\subsection{Word recognition in the
+wild}\label{word-recognition-in-the-wild}
+
+An important question to ask is how the combination mechanism -- as
+revealed in our controlled study -- scales up to real life situations.
 Note that in order to test audio-visual cue combination under
 uncertainty, we had to use a case of double ambiguity, that is, a case
-where both the word forms (\enquote{ada}-\enquote{aba}) and the
-referents (cat-dog) were similar and, thus, confusable. However, to what
-extent does such a case occur in real languages? Cross-linguistic corpus
-analyses suggest that lexical encoding tends, surprisingly, towards
-double ambiguity in many languages (Dautriche, Mahowald, Gibson, \&
-Piantadosi, 2017; Monaghan, Shillcock, Christiansen, \& Kirby, 2014;
+where both the word forms (\enquote{ada}--\enquote{aba}) and the
+referents (cat--dog) were similar and, thus, confusable. However, to
+what extent does such a case occur in real languages? Cross-linguistic
+corpus analyses suggest that lexical encoding tends, surprisingly,
+towards double ambiguity in many languages (Dautriche, Mahowald, Gibson,
+\& Piantadosi, 2017; Monaghan, Shillcock, Christiansen, \& Kirby, 2014;
 Tamariz, 2008). For instance, Dautriche et al. (2017) analyzed 100
@@
 in language as it increase the probability of confusability for many
-words.\linebreak That being said, besides the case of double ambiguity
-\emph{intrinsic} to language, our mechanism might play a more
-significant role when ambiguity in both the form and/or the referent is
-induced by an \emph{external} noisy context even when these forms and
-referents are not confusable in normal situations.
-
-Though we only tested adults in this paper, the problem of word
-recognition under uncertainty, as well as the need to make the most of
-the available cues, is arguably more pressing for children. In fact,
-children have greater difficulties differentiating the meanings of novel
-similar-sounding words (e.g., \enquote{bin} vs. \enquote{din}), even
-when these words are uttered very clearly (Creel, 2012; Merriman \&
+words. That said, the inferences discussed here might play a more
+significant role in naturalistic language comprehension when ambiguity
+in both the form and/or the referent is induced by an \emph{external}
+noisy context -- e.g., a very noisy party or a far away referent -- even
+when these forms and referents are not confusable in normal situations.
+
+Though we only studied adult performance in this paper, the problem of
+word recognition under uncertainty is likely more pressing for children.
+In fact, children have greater difficulties differentiating the meanings
+of novel similar-sounding words (e.g., \enquote{bin} vs. \enquote{din}),
+even when these words are uttered very clearly (Creel, 2012; Merriman \&
 Schuster, 1991; Stager \& Werker, 1997; Swingley, 2016; White \& Morgan,
@@
 infants in simplified experimental settings (e.g., Yoshida, Fennell,
-Swingley, \& Werker, 2009). Nevertheless, Swingley (2007) suggested this
-differentiation is not mature and is probably noisier than the
-adult-like representation and/or encoded with lower confidence. Thus, it
-looks like children, even more than adults, may greatly benefit from
+Swingley, \& Werker, 2009). Nevertheless, Swingley (2007) suggested that
+the ability to make this differentiation is likely not mature in early
+childhood; children's representations are almost certainly noisier than
+the adults' representations and may also be encoded with lower
+confidence. Thus, children even more than adults might benefit from
 additional disambiguating cues during new word-referent encoding and
-recognition. For example, Dautriche, Swingley, and Christophe (2015)
-showed that 18-month-olds can leverage the difference in the syntactic
-category (noun vs.~verb). Further work is needed to explore whether
-salient referential cues also help children disambiguate similar
-sounding words.
-
-The multi-modal cue combination strategy might help children not only
-recognize words, but also refine the underlying phonological and
+recognition.
+
+A multi-modal cue combination strategy might help children not only
+recognize words, but also refine their underlying phonological and
 semantic representations in the process. Previous research in early word
-learning has---whether implicitly or explicitly---largely treated the
+learning has -- whether implicitly or explicitly -- largely treated the
 process of refining the word form and of refining the word meaning as
-follwing a linear timeline However, recent developmental data shows that
-children do not wait to have completed the acquisition of forms to start
-learning the meanings (Bergelson \& Swingley, 2012; Tincoff \& Jusczyk,
-1999). Rather, both form and meaning representations develop in a
-parallel fashion. A few studies pointed to the possibility of an
-interaction between sound and meaning in early acquisition. For
-instance, Waxman and Markow (1995) showed that labeling various objects
-with the same name helps infants form the underlying semantic category
-(but see Sloutsky \& Napolitano, 2003). Vice versa, Yeung and Werker
-(2009) showed that pairing similar sounds with different objects help
-infants enhance their sensitivity to the subtle phonological contrasts
-in their native language. The present study proposes a first step
-towards a formal framework where isolated accounts of sound-meaning
-interaction in development can be unified and further explored.
-
-One limitation of this work is that we used simplified stimuli. For the
-auditory modality, we used speech categories that varied along a single
-acoustic dimension. While this dimension might be sufficient to
-recognize words in our specific case, in general the speech signal may
-be more complex, varying along several acoustic/phonetic dimensions.
-Additionally, these dimensions may be highly variable due to various
-kinds of speaker and context differences. The same thing can be said
-about the referential stimuli. Here we used a continuum along a single
-morph dimension in order to construct a multimodal input where the
-auditory and visual components have symmetrical properties. Though such
-morph is not the exact visual variability that people would encounter in
-their daily lives, it allowed us to precisely test the role of auditory
-and visual information in the cue combination process. Parameterizing
-semantic dimensions is a notoriously difficult problem, but morphs have
-been used in previous research as a reasonable proxy (Freedman et al.,
-2001; Havy \& Waxman, 2016; Sloutsky \& Fisher, 2004). It is an open
-question as to whether people use the same strategy in controlled
-laboratory conditions, as in more naturalistic settings where they have
-to deal with various levels of variability. An answer to this question
-is likely to involve a multifaceted research approach,
-involving---besides conducting laboratory experiments---testing
-computational mechanisms with an input that represents, more accurately,
-the complexity of multimodal variability in the learning environment
+following a linear timeline. However, developmental data reveal that
+children do not wait to have complete acquisition of word forms before
+they start learning their meanings (Bergelson \& Swingley, 2012; Tincoff
+\& Jusczyk, 1999). Rather, both form and meaning representations develop
+in a parallel fashion. A few studies have already suggested the
+possibility of an interaction between sound and meaning in early
+acquisition. For instance, Waxman and Markow (1995) showed that labeling
+various objects with the same name helps infants form the underlying
+semantic category (but see Sloutsky \& Napolitano, 2003). And in the
+opposite direction, Yeung and Werker (2009) showed that pairing similar
+sounds with different objects can helps infants enhance their
+sensitivity to subtle phonological contrasts in their native language.
+The present study proposes a first step towards a formal framework where
+these sorts of sound-meaning interactions in development can be unified
+and further explored.
+
+One salient limitation of our current work is that we used a restricted
+and highly simplified stimulus set. For the auditory modality, we used
+speech categories that varied along a single acoustic dimension. While
+this dimension might be sufficient to recognize words in our specific
+case, in general the speech signal is far more complex, varying along
+several acoustic/phonetic dimensions. Additionally, these dimensions may
+be highly variable due to various kinds of speaker and context
+differences. The same thing can be said about our visual stimuli. Here
+we used a continuum along a single morph dimension in order to construct
+a multimodal input where the auditory and visual components have
+symmetrical properties. Though such morph is not the exact visual
+variability that people would encounter in their daily lives, it allowed
+us to precisely test the role of auditory and visual information in the
+cue combination process. Parameterizing semantic dimensions is a
+notoriously difficult problem, but morphs have been used in previous
+research as a reasonable proxy (Freedman et al., 2001; Havy \& Waxman,
+2016; Sloutsky \& Fisher, 2004). It is an open question whether people
+use the same strategy in controlled laboratory conditions and more
+naturalistic settings where they have to deal with various levels of
+variability. An answer to this question is likely to involve a
+multifaceted research approach that goes beyond controlled
+experimentation. We believe that one fruitful approach is to test
+computational mechanisms with an input that more accurately represents
+the full extent of multimodal variability in the learning environment
 (Dupoux, 2018; Fourtassi, Schatz, Varadarajan, \& Dupoux, 2014; Harwath,
@@
 
-\section{Conclusion}\label{conclusion}
-
-This work studied the mechanism of spoken word identification under
-uncertainty in both the form and the referent. We conducted an ideal
-observer analysis of this task. We found people to be near optimal in
-their cue combination (at least at the population level): They weighted
-each modality according to its relative reliability. However, they also
-showed patterns of sub-optimality especially when the stimuli were
-perturbed with additional background noise. This work provides a formal
-framework where old and new questions about word recognition in a
-referential context can be given a precise formulation. For instance, of
-particular interest is the case of iconicity, that is, when there is a
-resemblance between the sound of a word and its referent. Previous work
-has suggested that iconicity, among other things, helps with learning
-(and generalizing the meaning of) new words (see Dingemanse, Blasi,
-Lupyan, Christiansen, \& Monaghan, 2015 for a review). Using the
-research strategy in this paper, we can, for example, test whether
-iconicity has such an advantage because it mitigates the sub-optimal
-patterns observed with more arbitrary pairings. Finally, though the
-current framework only characterizes adult word recognition, it provides
-a first step towards a model where developmental questions can also be
-investigated. For instance, future work should explore whether children,
-like adults, use probabilistic cues from both the auditory and the
-visual input to recognize ambiguous words, the extent to which they
-combine these cues in an optimal fashion, and whether these combination
-help them with refining their early phonological and semantic
-representations.
+\section{Conclusions}\label{conclusions}
+
+Our work provides a formal framework where old and new questions about
+word recognition in a referential context can be given a precise
+formulation. While we focused on the case of arbitrary associations, it
+is possible to use the same framework to study, for instance, the case
+of \textit{iconicity}, that is, when there is a resemblance between the
+sound of a word and its referent. Previous work has suggested that
+iconicity, among other things, helps with learning (and generalizing the
+meaning of) new words (see Dingemanse, Blasi, Lupyan, Christiansen, \&
+Monaghan, 2015 for a review). Using the research strategy in this paper,
+we can, for example, test whether iconicity has such an advantage
+because it mitigates the sub-optimal patterns observed with more
+arbitrary pairings. Finally, though the current framework only
+characterizes adult word recognition, it provides a first step towards a
+model where developmental questions can also be investigated. For
+instance, future work should explore whether children, like adults, use
+probabilistic cues from both the auditory and the visual input to
+recognize ambiguous words, the extent to which they combine these cues
+in an optimal fashion, and whether this cue combination help them to
+refine their early phonological and semantic representations.
 
@@
 \vspace{1em}
+
+\section{Acknowledgements}\label{acknowledgements}
+
+This work was supported by a post-doctoral grant from the Fyssen
+Foundation.
+
+\section{Disclosure statement}\label{disclosure-statement}
+
+None of the authors have any financial interest or a conflict of
+interest regarding this work and this submission.
 
@@
 
-\section{Acknowledgements}\label{acknowledgements}
-
-This work was supported by a post-doctoral grant from the Fyssen
-Foundation + XXX
-
 \section{References}\label{references}
@@
 100 languages. \emph{Cognitive Science}, \emph{41}(8), 2149--2169.
-
-\hypertarget{ref-dautriche2015}{}
-Dautriche, I., Swingley, D., \& Christophe, A. (2015). Learning novel
-phonological neighbors: Syntactic category matters. \emph{Cognition},
-\emph{143}, 77--86.
 
@@
 Geisler, W. S. (2003). Ideal observer analysis. In \emph{The visual
-neurosciences} (pp. 825--837)). Cambridge, MA: MIT Press.
+neurosciences} (pp. 825--837). Cambridge, MA: MIT Press.
 
@@
 
-\hypertarget{ref-mcclelland2006}{}
-McClelland, J. L., Mirman, D., \& Holt, L. L. (2006). Are there
-interactive processes in speech perception? \emph{Trends in Cognitive
-Sciences}, \emph{10}(8), 363--369.
-
 \hypertarget{ref-mcgurk1976}{}
@@
 grow a mind: Statistics, structure, and abstraction. \emph{Science},
-\emph{331}(11 March 2011), 1279--1285.
+\emph{331}(6022), 1279--1285.
 
@@
 Waxman, S., \& Gelman, S. (2009). Early word-learning entails reference,
-not merely associations. \emph{Trends in Cognitive Sciences}.
+not merely associations. \emph{Trends in Cognitive Sciences},
+\emph{13}(6).
 

### 2018-11-05 Writeup/ms.tex
revisions

@@
 deviation of \(sd=\) 2.24 which was larger than that of the simulated
-distribution (\(sd=\) 1.15), indicating that there was real
+distribution (\(sd=\) 1.14), indicating that there was real
 between-subject variation beyond sampling errors. This finding means

### 2018-11-05 Experiments/experiment1_rev.js

@@ -1,0 +1,956 @@
+//////////////////
+//Helper functions
+///////////////////
+
+// Shows slides. We're using jQuery here - the **$** is the jQuery selector function, which takes as input either a DOM element or a CSS selector string.
+function randomInteger(n) {
+	return Math.floor(Math.random()*n);
+}
+
+function randomElement(array) {
+  return array[randomInteger(array.length)];
+}
+
+function randomInt(min,max)
+{
+    return Math.floor(Math.random()*(max-min+1)+min);
+}
+
+function showSlide(id) {
+  // Hide all slides
+	$(".slide").hide();
+	// Show just the slide we want to show
+	$("#"+id).show();
+}
+
+//shuffle an array
+function shuffleArray(a) {
+
+    for (var i = a.length - 1; i > 0; i--) {
+        var j = Math.floor(Math.random() * (i + 1));
+        var temp = a[i];
+        a[i] = a[j];
+        a[j] = temp;
+    }
+    return a;
+}
+
+function randomElement(array) {
+  return array[randomInteger(array.length)];
+}
+
+//I should now work on the randomization
+var rando = randomInt(0,3);
+var first_word ='', second_word='', first_obj='', first_obj='';
+
+if (rando ==0) {
+//Dog-ABA, Cat-ADA    
+//Dog is the standard
+first_word="ABA";
+second_word="ADA";
+first_obj="Dog";
+second_obj="Cat";
+    
+var ConStim = ['dog1','dog2','dog3','dog4', 'dog5'];   
+var SounStim = ['aba01','aba03','aba05','aba07', 'aba09'];
+    
+var ConStim_preTask=['dog1','dog1', 'dog5','dog5'];
+var SounStim_preTask = ['aba01','aba01','aba09','aba09'];
+}
+
+if (rando ==1) {
+//Dog-ADA, Cat-ABA
+//Dog is the standard
+first_word="ADA";
+second_word="ABA";
+first_obj="Dog";
+second_obj="Cat";
+    
+var ConStim = ['dog1','dog2','dog3','dog4', 'dog5'];   
+var SounStim = ['aba09','aba07','aba05','aba03', 'aba01'];
+    
+var ConStim_preTask=['dog1','dog1', 'dog5','dog5'];
+var SounStim_preTask = ['aba09','aba09','aba01','aba01'];
+    
+}
+if (rando ==2) {
[…]

### 2018-11-05 Experiments/experiment1_rev.js
rev

@@ -126,9 +126,10 @@ var SounStim_preTask = ['aba09','aba09','aba01','aba01'];
 
     var preConcept_instructions= "In this part of the training, the other alien will only be able to see the objects, he will not be able to hear the words.<br><br> You should help him decide if the second item is another "+first_obj+"-"+first_word+" (by choosing 'same') or a "+second_obj+"-"+second_word+" (by choosing 'different')";
 
-    var Pause= "This is a small pause. When you are ready, click to continue the task!";
+    var Pause= "<center><font size='5'>This is a small pause.</br></br>When you are ready, click to continue the task!</font></center>";
 
-    
+
+
 
 $(".f_o").text(first_obj);
 $(".f_w").text(first_word);
@@ -230,9 +231,6 @@ $(".different-key").text("D");
 
 //Here we separete the sequences fo each condition in order to be able to randomize theur order for each subject
 var myTrials=[];
-var myTrials_sound=[];
-var myTrials_concept=[];
-var myTrials_joint=[]
 
 
 
@@ -392,10 +390,15 @@ for (i=0; i < total_pre_concept; i++){
 
 
 for (b=1; b < 3 ; b++){
+    
+var myTrials_sound=[];
+var myTrials_concept=[];
+var myTrials_joint=[]
   
 var chunk1 = "<center><font size='5'>You are now going to start: </br></br>The testing chunk number <b>"; 
     
-var chunk2= "</b> (out of <b>4</b>)</br></br>You may take a small pause.</br></br>Please stay focused till the end of the chunck!</font></center>";
+var chunk2= "</b> (out of <b>4</b>)</br></br>The task is the same in all the chunks.</br></br>You may take a small pause before the start.</br></br>Please stay focused till the end of the chunck!</font></center>";
+    
     
 myTrials.push(myTrial={
         trial_number: 0,
@@ -475,6 +478,22 @@ for (i=0; i < total_sound; i++){
     myTrials_sound.push(myTrial);
 }
 
+    //Pause between two blocks
+myTrials_sound.push(myTrial={
+        trial_number: '',
+        trial_order:'',
+        trial_type: "pause",
+        block:'',
+        chunk:'',
+        concept_l:'',
+        concept_r:'',
+        concept_dist:'',
+        sound_l:'',
+        sound_r:'',
+        sound_dist: '',
+        conditon:''
[…]

### 2018-11-05 Experiments/experiment1_rev.js
rev

@@ -289,6 +289,7 @@ myTrials.push(myTrial={
 
 //For the preTask trials, I give the correct answer in  "trial order"
 
+/*
 for (i=0; i < total_pre_joint; i++){
     myTrial = {
         trial_number: i+1,
@@ -376,6 +377,8 @@ for (i=0; i < total_pre_concept; i++){
     }
    myTrials.push(myTrial);
 }
+
+*/
 
 //the real Task
 //////////////////

### 2018-11-05 Experiments/experiment1_rev.js
rev

@@ -111,7 +111,7 @@ var SounStim_preTask = ['aba09','aba09','aba01','aba01'];
      
     var preTask_instruct="This first part of the experiment serves as a training for the task that you will perform later. Please take enough time to read and understand the following instructions. <br><br> An alien will be naming to his friend two objects from the planet Earth: a "+first_obj+" and a "+second_obj+". The alien will not be speaking in English, but in an alien language. In this language, a "+first_obj+" is called "+first_word+" and a "+second_obj+" is called "+second_word+". <br><br> In each situation, the alien will be naming two objects: the first object will show on the left, and will always be a "+first_obj+"-"+first_word+". The second object will show on the right and will be either another "+first_obj+"-"+first_word+", or a "+second_obj+"-"+second_word+".<br><br> Your task is to help the other alien decide if the second item is another "+first_obj+"-"+first_word+" (by choosing 'same') or a "+second_obj+"-"+second_word+" (by choosing 'different') <br><br> Click continue for further instructions!";
 
-    var Task_instruct="Now you will start the real experiment. Please take enough time to read and understand the following instructions. Your perfromance  should reflect this understanding:<br><br> Similar to the training, the first item will always involve the same "+first_obj+"-"+first_word+", however the second item will now bring two difficuties: <br><br> 1) The first difficulty is that there will be slight differences in the pronounciation, and it can sometimes be hard to distinguish "+first_word+" from "+second_word+". <br><br> 2) The second difficulty is that "+second_obj+"s and "+first_obj+"s now come in similar shapes, and it can sometimes be difficult to distinguish the picture of a "+second_obj+" from the picture of a "+first_obj+".<br><br> Click continue for instructions on how to overcome these difficulties!"
[…]

### 2018-11-05 Experiments/experiment1_rev.js
rev

@@ -950,7 +950,7 @@ var experiment = {
         experiment.data.tri_order.push(current_trial.trial_order);  
         experiment.data.tri_type.push(current_trial.trial_type);
         experiment.data.block.push(current_trial.block);  
-        experiment.data.block.push(current_trial.chunk); 
+        experiment.data.chunk.push(current_trial.chunk); 
         experiment.data.con_dist.push(current_trial.concept_dist);
         experiment.data.sou_dist.push(current_trial.sound_dist);
         

### 2018-11-05 Experiments/experiment1_rev.js
rev

@@ -481,21 +481,7 @@ for (i=0; i < total_sound; i++){
     myTrials_sound.push(myTrial);
 }
 
-    //Pause between two blocks
-myTrials_sound.push(myTrial={
-        trial_number: '',
-        trial_order:'',
-        trial_type: "pause",
-        block:'',
-        chunk:'',
-        concept_l:'',
-        concept_r:'',
-        concept_dist:'',
-        sound_l:'',
-        sound_r:'',
-        sound_dist: '',
-        conditon:''
-        });
+
 
 //second block
 for (i=0; i < total_sound; i++){

### 2018-11-06 Experiments/experiment1_rev.js
rev

@@ -669,7 +669,9 @@ for (i=0; i < total_joint; i++){
 var conditions=[[myTrials_joint,myTrials_sound,myTrials_concept],
  [myTrials_joint,myTrials_concept,myTrials_sound],
  [myTrials_sound,myTrials_concept,myTrials_joint],
- [myTrials_concept,myTrials_sound,myTrials_joint]
+ [myTrials_sound,myTrials_joint,myTrials_concept], 
+ [myTrials_concept,myTrials_sound,myTrials_joint],
+ [myTrials_concept,myTrials_joint,myTrials_sound]
            ];
 
 var myOrder = randomElement(conditions);

### 2018-11-08 Experiments/experiment1_rev.js
new rev

@@ -458,45 +458,29 @@ myTrials_sound.push(myTrial={
 //shuffle order of exposure for two consecutive blocks
 var Trials_S_1=shuffleArray([0,1,2,3,4]);
 var Trials_S_2=shuffleArray([0,1,2,3,4]);
+var Trials_S_3=shuffleArray([0,1,2,3,4]);
+var Trials_S_4=shuffleArray([0,1,2,3,4]);
 
-var total_sound= Trials_S_1.length;
+var Trials_S = Trials_S_1.concat(Trials_S_2,
+                                 Trials_S_3,
+                                 Trials_S_4); 
+    
+var total_sound= Trials_S.length;
 
 //first block
 for (i=0; i < total_sound; i++){
     myTrial = {
         trial_number: i+1,
-        trial_order:Trials_S_1[i]+1,
+        trial_order:Trials_S[i]+1,
         trial_type: "Task",
-        block:1,
+        block:0,
         chunk:b,
         concept_l:$grey_l,
         concept_r:$grey_r,
         concept_dist:0,
-        sound_l:$sound_0[Trials_S_1[i]],
-        sound_r:$sound_1[Trials_S_1[i]],
-        sound_dist: Trials_S_1[i],
-        conditon:'sound'
-    }
-    
-    myTrials_sound.push(myTrial);
-}
-
-
-
-//second block
-for (i=0; i < total_sound; i++){
-    myTrial = {
-        trial_number: i+1,
-        trial_order:Trials_S_2[i]+1,
-        trial_type: "Task",
-        block:2,
-        chunk:b,
-        concept_l:$grey_l,
-        concept_r:$grey_r,
-        concept_dist:0,
-        sound_l:$sound_0[Trials_S_2[i]],
-        sound_r:$sound_1[Trials_S_2[i]],
-        sound_dist: Trials_S_2[i],
+        sound_l:$sound_0[Trials_S[i]],
+        sound_r:$sound_1[Trials_S[i]],
+        sound_dist: Trials_S[i],
         conditon:'sound'
     }
     
@@ -524,20 +508,26 @@ myTrials_concept.push(myTrial={
 
 var Trials_C_1=shuffleArray([0,1,2,3,4]);
 var Trials_C_2=shuffleArray([0,1,2,3,4]);
+var Trials_C_3=shuffleArray([0,1,2,3,4]);
+var Trials_C_4=shuffleArray([0,1,2,3,4]);
+    
[…]

### 2018-11-13 Data_and_analysis/analysis_individual.Rmd
revisions analysis

---
title: "WordRec Experiment"
author: "A. Fourtassi & M. Frank"
date: "January 13, 2017"
output:
  html_document:
    number_sections: yes
    toc: yes
---

Libraries.

```{r}
#library(papaja)
library(broom)
  library(purrr)
  library(readr)
  library(ggplot2)
  library(dplyr)
  library(tidyr)
  #library(wordbankr)
  library(stringr)
  library(feather)
  library(lme4)
  library(boot)
  library(langcog)
  library(ggthemes)
  library(nlme)
  #library(rwebppl)
  library(jsonlite)
  library(Hmisc)
  library(poweRlaw)
  library(HDInterval)
  #library(kableExtra)
```

Data and processing
```{r}

#Skip the pre task trials 
#Filter subjects who had no technical problem
#Select subjects who got more than 50% correct answers on the pre task trials

exp1 <- read_delim("exp1_rev2_anonym.txt", delim = " ") %>%
  filter(type == "Task") %>%
  mutate(experiment='Experiment1')

N_all_1 <- exp1 %>%
  distinct(ID) %>%
  nrow()

exp1_noProb <- exp1 %>%
  filter(problem=="No")

N_noProb_1 <- exp1_noProb %>%
  distinct(ID) %>%
  nrow()

exp1_good <- exp1_noProb %>%
  filter(score > 0.5)

N_good_1 <- exp1_good %>%
  distinct(ID) %>%
  nrow()

sound_all_exp1 <- exp1_good %>%
    filter(condition == "sound")

concept_all_exp1 <- exp1_good %>%
    filter(condition == "concept")

joint_all_exp1 <- exp1_good %>%
    filter(condition == "joint")

```

Fit the aggregate  data 
```{r}
data_s <- sound_all_exp1 %>%
  group_by(sound_dist) %>%
  dplyr::summarise(mean = mean(answer),
                   sd = sd(answer),
                   n = n()) %>%
  mutate(se = sd / sqrt(n),
         lower = mean - qt(1 - (0.05 / 2), n - 1) * se,
         upper = mean + qt(1 - (0.05 / 2), n - 1) * se) %>%
  select(-sd, -n, -se,) %>%
  mutate(Experiment="Experiment 1", 
         Condition="Auditory") %>%
  rename(distance = sound_dist)

data_c <- concept_all_exp1 %>%
  group_by(concept_dist) %>%
  dplyr::summarise(mean = mean(answer),
                   sd = sd(answer),
                   n = n()) %>%
  mutate(se = sd / sqrt(n),
         lower = mean - qt(1 - (0.05 / 2), n - 1) * se,
         upper = mean + qt(1 - (0.05 / 2), n - 1) * se) %>%
  select(-sd, -n, -se,) %>%
  mutate(Experiment="Experiment 1", 
         Condition="Visual") %>%
  rename(distance = concept_dist)

data_j <- joint_all_exp1 %>%
  group_by(sound_dist, concept_dist) %>%
  dplyr::summarise(mean = mean(answer),
                   sd = sd(answer),
                   n = n()) %>%
  mutate(se = sd / sqrt(n),
         lower = mean - qt(1 - (0.05 / 2), n - 1) * se,
         upper = mean + qt(1 - (0.05 / 2), n - 1) * se) %>%
  select(-sd, -n, -se,) %>%
  mutate(Experiment="Experiment 1", 
         Condition="Joint")

data_all <- bind_rows(data_s, data_c)

model_s <- nls(answer ~ 1/(1+(1-e)*exp((-4/vrA)*sound_dist+(8/vrA))), data=sound_all_exp1, start = list(e=0, vrA=2))
model_c <- nls(answer ~ 1/(1+(1-e)*exp((-4/vrV)*concept_dist+(8/vrV))), data=concept_all_exp1, start = list(e=0, vrV=2))
model_j <- nls(answer ~ 1/(1+(1-e)*exp((-4/vrA_j)*sound_dist+(-4/vrV_j)*concept_dist+(8/vrA_j)+(8/vrV_j))), data=joint_all_exp1, start = list(e=0, vrA_j=2, vrV_j=2))

#Plot the data here
x <- seq(0, 4, 0.01)

y_s <- predict(model_s, list(sound_dist = x), type="response")
y_c <- predict(model_c, list(concept_dist = x), type="response")

pred_all <- bind_rows(data.frame(distance=x, prediction=y_s, Condition = "Auditory"), 
                      data.frame(distance=x, prediction=y_c, Condition = "Visual"))

#Derive values of the variance from the 
ggplot(data_all, 
       aes(x = distance, y = mean)) + 
  geom_point()+
  geom_pointrange(aes(ymin = lower, ymax = upper), 
                  position = position_dodge(width = .1), size = 0.4, fatten = 2) + 
  #geom_line(data=uniV,aes(x=xV, y=yV))+
  geom_line(data=pred_all, aes(x=distance, y=prediction), col='black')+
  #geom_line(data=uni_me_s, aes(x=distance, y=prediction), col='blue')+
  #geom_line(data=uni_nl_s, aes(x=distance, y=prediction), col='red')+
  xlab("Distance") +ylab("Prob. different")+
  scale_y_continuous(limits = c(0, 1))+#theme(aspect.ratio = 0.7)+
  theme_few()+
  theme(aspect.ratio = 0.7) + facet_grid(. ~ Condition)

```
Optimal model
```{r}
#Extract cefficieny

eA <- coefficients(model_s)["e"]
vrA <- coefficients(model_s)["vrA"]

eV <- coefficients(model_c)["e"]
vrV <- coefficients(model_c)["vrV"]

ej <- coefficients(model_j)["e"]
vrAj <- coefficients(model_j)["vrA_j"]
vrVj <- coefficients(model_j)["vrV_j"]

#The sound-only model
m_s <- function (x,y) {
  1/(1 + (1-eA)*exp((-4/vrA)*x+(8/vrA)))
}

#The visual-only model
m_c <- function (x,y) {
  1/(1 + (1-eV)*exp((-4/vrV)*y+(8/vrV)))
}

#Descriptive model (parameters are derived from fit to bimodal data)
m_opt <- function (x,y) {
   1/(1 + (1-ej)*exp((-4/vrA)*x+(-4/vrV)*y+(8/vrA)+(8/vrV)))
}

#The optimal model (parameters are derived from fit to unimodal data)
m_des <- function (x,y) {
    1/(1 + (1-ej)*exp((-4/vrAj)*x+(-4/vrVj)*y+(8/vrAj)+(8/vrVj)))
}

pred_all_comb <- data_j %>% 
  rename(joint = mean) %>%
  mutate(Descriptive = m_des(sound_dist, concept_dist)) %>%
  mutate(Optimal = m_opt(sound_dist, concept_dist)) %>%
  mutate(Auditory = m_s(sound_dist, concept_dist)) %>%
  mutate(Visual = m_c(sound_dist, concept_dist)) %>%
  gather(model, pred, Visual, Auditory, Optimal, Descriptive) %>%
  mutate(experiment = 'Experiment 1')

pred_all_comb$model <- factor(pred_all_comb$model, levels = c('Visual','Auditory', 'Optimal', 'Descriptive'))

correlations <- pred_all_comb %>%
  group_by(model) %>%
  summarise(cor = round(cor(joint, pred), 2))

ggplot(pred_all_comb, 
       aes(x = pred, y = joint)) +
           #col = factor(concept_dist), 
          # shape = factor(sound_dist))) + 
  geom_point(size =1)+
  scale_colour_solarized()+
 #geom_pointrange(aes(ymin = summary_ci_lower, ymax = summary_ci_upper), 
  #                position = position_dodge(width = .1), size=0.2) + 
  geom_abline(slope = 1, lty = 2) +
  xlab("Predictions") +ylab("Human data")+
  facet_grid(. ~ model)+
  theme_few()+
  geom_text(data=correlations, aes(label=paste("r=", cor, sep="")), x=0.5, y=0.95, size=2, fontface = "bold", col="red")+
theme(aspect.ratio = 0.7, 
      axis.text=element_text(size=6),
      strip.text.y = element_text(size = 8))+
  guides(color=guide_legend(title="Visual Distance")) +
  guides(shape=guide_legend(title="Auditory Distance"))

```

Human data by subject
```{r}

sounds_exp1 <- exp1_good %>%
  filter(condition == "sound") %>%
  group_by(ID, sound_dist) %>%
  dplyr::summarise(mean = mean(answer),
                   sd = sd(answer),
                   n = n()) %>%
  mutate(se = sd / sqrt(n),
         lower = mean - qt(1 - (0.05 / 2), n - 1) * se,
         upper = mean + qt(1 - (0.05 / 2), n - 1) * se) %>%
  select(-sd, -n, -se,) %>%
  mutate(Experiment="Experiment 1", 
         Condition="Auditory") %>%
  rename(distance = sound_dist)

concepts_exp1 <- exp1_good %>%
  filter(condition == "concept") %>%
  group_by(ID, concept_dist) %>%
  dplyr::summarise(mean = mean(answer),
                   sd = sd(answer),
                   n = n()) %>%
  mutate(se = sd / sqrt(n),
         lower = mean - qt(1 - (0.05 / 2), n - 1) * se,
         upper = mean + qt(1 - (0.05 / 2), n - 1) * se) %>%
  select(-sd, -n, -se,) %>%
  mutate(Experiment="Experiment 1", 
         Condition="Visual") %>%
  rename(distance = concept_dist)

joint_exp1 <- exp1_good %>%
  filter(condition == "joint") %>%
  group_by(ID, concept_dist, sound_dist) %>%
  summarise(mean = mean(answer)) %>%
  mutate(Experiment="Experiment 1", 
         Condition="Joint")

exp_uni_data <- bind_rows(sounds_exp1, concepts_exp1)
```

Here fit the same models for every subject
```{r}

#Models

#Sound Unimodal
fit_s <- function(data) {
  nls(answer ~ 1/(1+(1-e)*exp((-4/vrA)*sound_dist+(8/vrA))), 
                 data=data,
                 start = list(e=0, vrA=1),
                 nls.control(warnOnly = TRUE)) 
}
#Concept Unimodal
fit_c <- function(data) {
  nls(answer ~ 1/(1+(1-e)*exp((-4/vrV)*concept_dist+(8/vrV))), 
                 data=data,
                 start = list(e=0, vrV=1),
                 nls.control(warnOnly = TRUE)) 
}

#Joint sound-concept
fit_j <- function(data) {
  nls(answer ~1/(1+(1-e)*exp((-4/vrA_j)*sound_dist+(-4/vrV_j)*concept_dist+(8/vrA_j)+(8/vrV_j))), 
                 data=data,
                 start = list(e=0, vrA_j=1, vrV_j=1),
                 nls.control(warnOnly = TRUE)) 
}

##Fit the models for each subject

#Split data by subject 
data_by_subj_s <- split(sound_all_exp1, sound_all_exp1$ID) 
data_by_subj_c <- split(concept_all_exp1, concept_all_exp1$ID)
data_by_subj_j <- split(joint_all_exp1, joint_all_exp1$ID)

#.. and fit
model_by_subj_s <- map(data_by_subj_s, fit_s) 
model_by_subj_c <- map(data_by_subj_c, fit_c)
model_by_subj_j <- map(data_by_subj_j, fit_j)

```

Unimodal conditions
```{r}
## Generate model predictions to plot with human data in the unimodal conditions

x <- seq(0, 4, 0.01)

pred_s <- function(model, ID){
  y <- predict(model, list(sound_dist = x), type="response")
  data.frame(distance=x, prediction=y, ID=ID) 
}

pred_c <- function(model, ID){
  y <- predict(model, list(concept_dist = x), type="response")
  data.frame(distance=x, prediction=y, ID=ID) 
}

ID <- as.list(strsplit(names(model_by_subj_s), " "))

#Generate  predictions for each subject
pred_s <- map2(model_by_subj_s, ID, model_pred_s) %>%
  bind_rows()
pred_c <- map2(model_by_subj_c, ID, model_pred_c) %>%
  bind_rows()

##Plot

ggplot(sounds_exp1, 
       aes(x = distance, y = mean)) + 
  geom_point()+
  #geom_pointrange(aes(ymin = lower, ymax = upper), 
  #                position = position_dodge(width = .1), size = 0.4, fatten = 2) + 
  #geom_line(data=uniV,aes(x=xV, y=yV))+
  geom_line(data=pred_s, aes(x=distance, y=prediction), col='black')+
  #geom_line(data=uni_me_s, aes(x=distance, y=prediction), col='blue')+
  geom_line(data=pred_nl_s, aes(x=distance, y=prediction), col='red')+
  xlab("Distance") +ylab("Prob. different")+
  scale_y_continuous(limits = c(0, 1))+#theme(aspect.ratio = 0.7)+
  theme_few()+
  theme(aspect.ratio = 0.7) + facet_grid(. ~ ID)

ggplot(concepts_exp1, 
       aes(x = distance, y = mean)) + 
  geom_point()+
  #geom_pointrange(aes(ymin = lower, ymax = upper), 
  #                position = position_dodge(width = .1), size = 0.4, fatten = 2) + 
  #geom_line(data=uniV,aes(x=xV, y=yV))+
  geom_line(data=pred_c, aes(x=distance, y=prediction), col='black')+
  #geom_line(data=uni_me_s, aes(x=distance, y=prediction), col='blue')+
  geom_line(data=pred_nl_c, aes(x=distance, y=prediction), col='red')+
  xlab("Distance") +ylab("Prob. different")+
  scale_y_continuous(limits = c(0, 1))+#theme(aspect.ratio = 0.7)+
  theme_few()+
  theme(aspect.ratio = 0.7) + facet_grid(. ~ ID)

```

Here compute the optimal combination
```{r}

##Extract coefficients from unimodal condition to build the optimal model and compare to descriptive model

#Unimodal coefficients
 co_uni <- function(model, ID) {
   data.frame(bias=coefficients(model)[1], 
              variance=coefficients(model)[2], 
              ID=ID)
 }

 #Bimodal coefficients
 co_bim <- function(model, ID) {
   data.frame(bias=coefficients(model)[1],
              var_s=coefficients(model)[2],
              var_c=coefficients(model)[3],
              ID=ID)
 }

#Here extract ceofficients to build optimal model later
coef_s <- map2(model_by_subj_s, ID, co_uni) %>%
  bind_rows() %>%
  rename(vrA_u= variance,
         bA_u =  bias)

coef_c <- map2(model_by_subj_c, ID, co_uni) %>%
  bind_rows() %>%
  rename(vrV_u= variance,
         bV_u =  bias)

coef_j <- map2(model_by_subj_j, ID, co_bim) %>%
  bind_rows() %>%
  rename(vrA_j = var_s,
         vrV_j = var_c,  
         b =  bias)

## Below are functions that take sound and concept distances and return the predicted joint value in each model

# Sound only
model_s <- function (data, x,y) {
  vrA = unique(data$vrA_u)
  b = unique(data$bA_u)

  1/(1 + (1-b)*exp((-4/vrA)*x+(8/vrA)))
}

# Visual only
model_c <- function (data, x,y) {
  vrV = unique(data$vrV_u)
  b = unique(data$bV_u)

  1/(1 + (1-b)*exp((-4/vrV)*y+(8/vrV)))
}

# Optimal
model_opt <- function (data, x,y) {
  vrA = unique(data$vrA_u)
  vrV = unique(data$vrV_u)
  e   = unique(data$b)

  1/(1 + (1-e)*exp((-4/vrA)*x+(-4/vrV)*y+(8/vrA)+(8/vrV)))
}

# Descriptive
model_des <- function (data, x,y) {
  vrA = unique(data$vrA_j)
  vrV = unique(data$vrV_j)
  e   = unique(data$b)

  1/(1 + (1-e)*exp((-4/vrA)*x+(-4/vrV)*y+(8/vrA)+(8/vrV)))
}

data_models <- joint_exp1 %>%
  left_join(coef_s) %>%
  left_join(coef_c) %>%
  left_join(coef_j)

models <- function (subject_data) {
  subject_data %>% rename(Joint = mean) %>%
  mutate(Descriptive = model_des(subject_data, sound_dist, concept_dist)) %>%
  mutate(Optimal = model_opt(subject_data, sound_dist, concept_dist)) %>%
  mutate(Auditory = model_s(subject_data, sound_dist, concept_dist)) %>%
  mutate(Visual = model_c(subject_data, sound_dist, concept_dist)) %>%
  gather(model, pred, Visual, Auditory, Optimal, Descriptive) 
}

data_by_subj <- split(data_models, data_models$ID)

data_preds <- map(data_by_subj, models) %>%
  bind_rows()

data_preds$model <- factor(data_preds$model, levels = c('Visual','Auditory', 'Optimal', 'Descriptive'))

correlations <- data_preds %>%
  group_by(ID, model) %>%
  summarise(cor = round(cor(Joint, pred), 2))

ggplot(data_preds, 
       aes(x = pred, y = Joint)) +
           #col = factor(concept_dist), 
          # shape = factor(sound_dist))) + 
  geom_point(size =1)+
  scale_colour_solarized()+
 #geom_pointrange(aes(ymin = summary_ci_lower, ymax = summary_ci_upper), 
  #                position = position_dodge(width = .1), size=0.2) + 
  geom_abline(slope = 1, lty = 2) +
  xlab("Predictions") +ylab("Human data")+
  facet_grid(ID ~ model)+
  theme_few()+
  geom_text(data=correlations, aes(label=paste("r=", cor, sep="")), x=0.5, y=0.95, size=2, fontface = "bold", col="red")+
theme(aspect.ratio = 0.7, 
      axis.text=element_text(size=6),
      strip.text.y = element_text(size = 8))+
  guides(color=guide_legend(title="Visual Distance")) +
  guides(shape=guide_legend(title="Auditory Distance"))

```

```{r}

coef_s = tidy(fit_s, model) 
coef_nl_s = tidy(fit_nl_s, model)
#Posterior for visual-only condition
concept_nl1 <- nls(answer ~ 1/(1+(1-e)*exp((-4/vrV)*concept_dist+(8/vrV))), data=concept_all_exp1, start = list(e=0, vrV=2))

#Posterior for audio-visual condition (this is the descriptive model)
joint_nl1 <- nls(answer ~ 1/(1+(1-e)*exp((-4/vrA_j)*sound_dist+(-4/vrV_j)*concept_dist+(8/vrA_j)+(8/vrV_j))), data=joint_all_exp1, start = list(e=0, vrA_j=2, vrV_j=2))

##extract coefficient
eA_nl1 <- coef(sound_nl1)["e"]
vrA_nl1 <- coef(sound_nl1)["vrA"]

eV_nl1 <- coef(concept_nl1)["e"]
vrV_nl1 <- coef(concept_nl1)["vrV"]

eJ_nl1 <- coef(joint_nl1)["e"]
vrJ_A_nl1 <- coef(joint_nl1)["vrA_j"]
vrJ_V_nl1 <- coef(joint_nl1)["vrV_j"]
#######

### the fit functions
x <- seq(0, 4, 0.01)

y_sound_nl1 <- predict(sound_nl1, list(sound_dist = x), type="response")
y_concept_nl1 <- predict(concept_nl1, list(concept_dist = x), type="response")

uniS_nl1 <- data.frame(distance=x, prediction=y_sound_nl1) %>%
  mutate(Condition = 'Auditory', 
         Experiment ='Experiment 1')

uniV_nl1 <- data.frame(distance=x, prediction=y_concept_nl1) %>%
  mutate(Condition = 'Visual',
         Experiment ='Experiment 1')

```

Fit individual curves
```{r}
#Increase the number of unimodal (since this is where the models do not converge) and decrease the number of joint, to

#Sound Unimodal
fit_s <- sound_all_exp1 %>%
  group_by(ID) %>%
  do(model = glm(answer ~  sound_dist, 
                 data=., 
                 family = binomial()))

fit_nl_s <- sound_all_exp1 %>%
  group_by(ID) %>%
  do(model = nls(answer ~ 1/(1+(1-e)*exp((-4/vrA)*sound_dist+(8/vrA))), 
                 data=.,
                 start = list(e=0, vrA=1),
                 nls.control(warnOnly = TRUE)))

coef_s = tidy(fit_s, model) 
coef_nl_s = tidy(fit_nl_s, model)

#Concept Unimodal
fit_c <- concept_all_exp1 %>%
  group_by(ID) %>%
  do(model = glm(answer ~  concept_dist, 
                 data=., 
                 family = binomial()))

fit_nl_c <- concept_all_exp1 %>%
  group_by(ID) %>%
  do(model = nls(answer ~ 1/(1+(1-e)*exp((-4/vrV)*concept_dist+(8/vrV))), 
                 data=.,
                 start = list(e=0, vrV=1),
                 nls.control(warnOnly = TRUE)))

coef_c = tidy(fit_c, model) 
coef_nl_c = tidy(fit_nl_c, model)

x <- seq(0, 4, 0.01)

#This simulation is not working!
simul <- fit_s %>%
  rowwise() %>%
  do(sim = predict(model, list(sound_dist = x), type="response"))

#Joint 
fit_j <- joint_all_exp1 %>%
  group_by(ID) %>%
  do(model = glm(answer ~  sound_dist + concept_dist, 
                 data=., 
                 family = binomial()))

fit_nl_j <- joint_all_exp1 %>%
  group_by(ID) %>%
  do(model = nls(answer ~ 1/(1+(1-e)*exp((-4/vrA_j)*sound_dist+(-4/vrV_j)*concept_dist+(8/vrA_j)+(8/vrV_j))),
                 data=.,
                 start = list(e=0, vrA_j=2, vrV_j=2),
                 nls.control(warnOnly = TRUE)))

coef_j = tidy(fit_j, model) 
coef_nl_j = tidy(fit_nl_j, model)

#2 steps:
#1) Do the full model with Subjects as random effect 
#2) Show the distribution of cue integration at the individual level (instead of just the joint model); that is, computet the proportion of 1) the weighing of the indivisual model (V/S)_uni to th weighing of the

##extract coefficient
eA_nl1 <- coef(sound_nl1)["e"]
vrA_nl1 <- coef(sound_nl1)["vrA"]

eV_nl1 <- coef(concept_nl1)["e"]
vrV_nl1 <- coef(concept_nl1)["vrV"]

eJ_nl1 <- coef(joint_nl1)["e"]
vrJ_A_nl1 <- coef(joint_nl1)["vrA_j"]
vrJ_V_nl1 <- coef(joint_nl1)["vrV_j"]
#######

### the fit functions
x <- seq(0, 4, 0.01)

y_sound_nl1 <- predict(sound_nl1, list(sound_dist = x), type="response")
y_concept_nl1 <- predict(concept_nl1, list(concept_dist = x), type="response")

uniS_nl1 <- data.frame(distance=x, prediction=y_sound_nl1) %>%
  mutate(Condition = 'Auditory', 
         Experiment ='Experiment 1')

uniV_nl1 <- data.frame(distance=x, prediction=y_concept_nl1) %>%
  mutate(Condition = 'Visual',
         Experiment ='Experiment 1')

```

Plots
```{r}
ggplot(exp_uni_data, 
       aes(x = distance, y = mean)) + 
  geom_point()+
  geom_pointrange(aes(ymin = lower, ymax = upper), 
                  position = position_dodge(width = .1), size = 0.4, fatten = 2) + 
  #geom_line(data=uniV,aes(x=xV, y=yV))+
  #geom_line(data=all_uni_model, aes(x=distance, y=prediction), col='black')+
  xlab("Distance") +ylab("Prob. different")+
  #scale_y_continuous(limits = c(0, 1))+#theme(aspect.ratio = 0.7)+
  theme_few()+
  theme(aspect.ratio = 0.7) + facet_grid(ID ~ Condition)
  #stat_function(fun = Logistic_v, colour="red"))

```

Fit the models.
```{r}

#Fit the uniomodal sound condition
sound_data <- d %>%
    filter(condition == "sound")

concept_data <- d %>%
    filter(condition == "concept")

joint_data <- d %>%
    filter(condition == "joint")

#Fit the uniomodal sound condition with a logistic regression
fit_sound <- glm(answer ~ sound_dist, data=sound_data, family = binomial())

##extract coefficient
s_coef <- coef(fit_sound)["sound_dist"]
s_inter <- coef(fit_sound)["(Intercept)"]

#prameters of the sound distribution
s_var=4/(s_coef)
s_sum=-1*s_inter/s_coef

#Fit the uniomodal visual conditon
fit_concept <- glm(answer ~ concept_dist, data=concept_data, family = binomial())

##extract coefficient
c_coef <- coef(fit_concept)["concept_dist"]
c_inter <- coef(fit_concept)["(Intercept)"]

#prameters of the sound distribution
v_var=4/(c_coef)
v_sum=-1*c_inter/c_coef

#Fit the bimodal conditon
fit_joint <- glm(answer ~ sound_dist+concept_dist, data=joint_data, family = binomial())

##extract coefficient
j_coef_a <- coef(fit_joint)["sound_dist"]
j_coef_v <- coef(fit_joint)["concept_dist"]
j_inter <- coef(fit_joint)["(Intercept)"]

#prameters of the sound distribution (approx: the average mean sum equal to 0+4/2=2)
j_var_a=4/(j_coef_a)
j_var_v=4/(j_coef_v)

#decision_ideal=v_va/s_va

#decision_fit=j_va_v/j_va_s

# preference = decision_fit/decision_ideal

```

Analysis of the unimodal cases.
```{r}

#Recogniton functions from the unimodal fit 
x <- seq(0, 4, 0.01)

y_sound <- predict(fit_sound, list(sound_dist = x), type="response")
y_concept <- predict(fit_concept, list(concept_dist = x), type="response")

uniS <- data.frame(xS=x,yS=y_sound)
uniV <- data.frame(xV=x,yV=y_concept)

#Recognition functions from the bimodal fit (marginal distributions)
Logistic_a = function (x, A = j_coef_a , B = 2*j_coef_a) {
    1 / (1 + exp(-1*(-B +A * x)))
}

Logistic_v = function (x, A = j_coef_v , B = 2*j_coef_v) {
    1 / (1 + exp(-1*(-B +A * x)))
}

#Plot all these functions in the same graph

##The auditory case
ggplot(sounds, 
       aes(x = sound_dist, y = mean)) + 
  geom_pointrange(aes(ymin = summary_ci_lower, ymax = summary_ci_upper), 
                  position = position_dodge(width = .1)) + 
  geom_line(data=uniS,aes(x=xS, y=yS))+
  xlab("Auditory distance") +ylab("% different")+
  scale_y_continuous(limits = c(0, 1))+
  stat_function(fun = Logistic_a, colour="red")

##The visual case
ggplot(concepts, 
       aes(x = concept_dist, y = mean)) + 
  geom_pointrange(aes(ymin = summary_ci_lower, ymax = summary_ci_upper), 
                  position = position_dodge(width = .1)) + 
  geom_line(data=uniV,aes(x=xV, y=yV))+
  xlab("Visual distance") +ylab("% different")+
  scale_y_continuous(limits = c(0, 1))+
  stat_function(fun = Logistic_v, colour="red")

```
Individual analysis:

```{r}

#Fit the uniomodal sound condition

d <- d1

sound_bysub <- d %>%
  filter(condition == "sound") %>%
  group_by(ID) %>%
  do(fit_sound = glm(answer ~ sound_dist, data=., family = binomial()))

soundCoef = tidy(sound_bysub, fit_sound) %>%
  filter(term == 'sound_dist') %>%
  mutate(s_var = 4/(estimate)) %>%
  select(ID, s_var)

concept_bysub <- d %>%
  filter(condition == "concept") %>%
  group_by(ID) %>%
  do(fit_concept = glm(answer ~ concept_dist, data=., family = binomial()))

conceptCoef = tidy(concept_bysub, fit_concept) %>%
  filter(term == 'concept_dist') %>%
  mutate(c_var = 4/(estimate)) %>%
  select(ID, c_var)

unimodal_bysub <- soundCoef %>%
  left_join(conceptCoef) %>%
  mutate(unim = c_var/s_var)

joint_bysub <- d %>%
  filter(condition == "joint") %>%
  group_by(ID) %>%
  do(fit_joint = glm(answer ~ concept_dist+ sound_dist, data=., family = binomial()))

bimodal_bysub = tidy(joint_bysub, fit_joint) %>%
  filter(term == 'concept_dist' | term == 'sound_dist') %>%
  mutate(j_var = 4/(estimate)) %>%
  select(ID, term, j_var) %>%
  spread(term, j_var) %>%
  rename(j_c_var = concept_dist, 
         j_s_var = sound_dist) %>%
  mutate(bimod = j_c_var/j_s_var)

all_bysub <- unimodal_bysub  %>%
  left_join(bimodal_bysub) %>%
  mutate(ideal = bimod/unim)

```
```{r}
ggplot(data=all_bysub, aes(s_var)) + 
  geom_vline(xintercept=1, col='red')+
  geom_histogram(binwidth = 0.4) +
  xlim(-15,15)

ggplot(data=all_bysub, aes(c_var)) + 
  geom_vline(xintercept=1, col='red')+
  geom_histogram(binwidth = 0.4) +
  xlim(-15,15)

ggplot(data=all_bysub, aes(unim)) + 
  geom_vline(xintercept=1, col='red')+
  geom_histogram(binwidth = 0.4) +
  xlim(-15,15)

ggplot(data=all_bysub, aes(j_s_var)) + 
  geom_vline(xintercept=1, col='red')+
  geom_histogram(binwidth = 0.4) +
  xlim(-15,15)

ggplot(data=all_bysub, aes(j_c_var)) + 
  geom_vline(xintercept=1, col='red')+
  geom_histogram(binwidth = 0.4) +
  xlim(-15,15)

ggplot(data=all_bysub, aes(bimod)) + 
  geom_vline(xintercept=1, col='red')+
  geom_histogram(binwidth = 0.4) +
  xlim(-11,11)+
  scale_x_log10()

```

```{r}
neg_N <- bimodal_bysub %>%
  filter(bimod <  -0.1) %>%
  filter(bimod > -10)

joint_sub <- joint_all_exp1 %>%
  filter(ID == 'subject_13') %>%
  group_by(concept_dist, sound_dist) %>%
  multi_boot_standard(col = "answer")
```

```{r}
ggplot(joint_sub, 
       aes(x = concept_dist, y = mean, col = factor(sound_dist))) + 
  geom_line(lty = 2) + 
  xlab("Auditory distance") +ylab("% different")+
  scale_colour_discrete(name="Visual Dist")+
theme(legend.title = element_text(size=8))

```

The bimodal case
```{r}

# Bimodal recognition functions

##the bimodal fit 
model_fit <- function (x,y) {
   1/(1 + exp(-x*j_coef_a-y*j_coef_v+2*j_coef_a+2*j_coef_v))
}

##Values of the baseline
model_base <- function (x,y) {
   1/(1 + exp(-x*s_coef-y*c_coef+2*s_coef+2*c_coef))
}

# Add the fit the baeline to data

ms_all <- joint %>% 
  rename(joint = mean) %>%
  left_join(select(concepts, concept_dist, mean) %>% 
              rename(concepts = mean)) %>%
  left_join(select(sounds, sound_dist, mean) %>% 
              rename(sounds = mean)) %>%
  mutate(fit = model_fit(sound_dist, concept_dist)) %>%
  mutate(base = model_base(sound_dist, concept_dist)) %>%
  gather(model, pred, concepts, sounds, base, fit)

#Plot Heat map for the data
ggplot(data = ms_all, aes(x=sound_dist, y=concept_dist, fill=joint)) + 
  geom_tile()+scale_fill_continuous(limits=c(0, 1))+xlab("Auditory distance") +ylab("Visual distance")

#Plot Heatmap for the baseline
mybase <- ms_all %>%
  filter(model=="base")

ggplot(data = mybase, aes(x=sound_dist, y=concept_dist, fill=pred)) + 
  geom_tile()+scale_fill_continuous(limits=c(0, 1))+xlab("Auditory distance") +ylab("Visual distance")

myfilter <- ms_all %>%
  filter(model=="fit" | model=="base")

#Correlation models (baseline and fit) to bimodal data 
ggplot(myfilter, 
       aes(x = pred, y = joint, col = factor(concept_dist), 
           shape = factor(sound_dist))) +
 geom_pointrange(aes(ymin = ci_lower, ymax = ci_upper), 
                  position = position_dodge(width = .1)) + 
  geom_abline(slope = 1, lty = 2) +
  facet_grid(model~.)

```

The modality dominance
```{r}

#Modality dominance coeficent
a_fit=2
a_base=1
a_Vdom=2*a_base
a_Sdom=0.5*a_base

s_var=1
v_var=1
j_var_a=2
j_var_v=2

#Classification thresholds (prob=0.5) for:

##The basline (combination of the unimodal cases)
classif_base = function (x, A=a_base) {
    2*(A+1)-A*x
}

##Best bivariate fit 
classif_fit = function (x, A=a_fit) {
    2*(A+1)-A*x
}

##A baseline for visual domiance
classif_Vdom = function (x, A=a_Vdom) {
    2*(A+1)-A*x
}

##A baseline for auditory domiance
classif_Sdom = function (x, A=a_Sdom) {
    2*(A+1)-A*x
}

#Sample from the baseline bivariate distribution
Gaus_base <- data.frame(x=c(rnorm(1000,0,sqrt(s_var)),rnorm(1000,4,sqrt(s_var))),
          y=c(rnorm(1000,0,sqrt(v_var)),rnorm(1000,4,sqrt(v_var))))

#Plot samples from the bivariate distribution
ggplot(Gaus_base, aes(x,y)) +  stat_density2d(geom="contour",aes(alpha=..level..))+
  scale_alpha_continuous(limits=c(0,0.03),breaks=1e-6*seq(0,10,by=2))+
  stat_function(fun = classif_base, colour = "red") +xlab("Auditory") +ylab("Visual")+ scale_x_continuous(limits = c(-6, 10))+scale_y_continuous(limits = c(-6, 10))

#Sample from the best bivariate fit 
Gaus_fit <- data.frame(x=c(rnorm(1000,0,sqrt(j_var_a)),rnorm(1000,4,sqrt(j_var_a))),
          y=c(rnorm(1000,0,sqrt(j_var_v)),rnorm(1000,4,sqrt(j_var_v))))

#Plot samples from the best bivariate fit
ggplot(Gaus_fit, aes(x,y)) +  stat_density2d(geom="contour",aes(alpha=..level..))+
  scale_alpha_continuous(limits=c(0,0.03),breaks=1e-6*seq(0,10,by=2))+
  stat_function(fun = classif_fit, colour = "red") +xlab("Auditory") +ylab("Visual") + scale_x_continuous(limits = c(-6, 10))+scale_y_continuous(limits = c(-6, 10))

#Modality dominance?
ggplot(Gaus_fit, aes(x,y)) +
  stat_function(fun = classif_base, colour = "red", lty=2) +
  stat_function(fun = classif_Vdom, colour = "blue", lty=2 )+
  stat_function(fun = classif_Sdom, colour = "blue", lty=2)+
  stat_function(fun = classif_fit, colour = "black")+
  xlab("Auditory") +ylab("Visual") + scale_x_continuous(limits = c(-6, 10))+
  scale_y_continuous(limits = c(-6, 10))+theme(aspect.ratio = 1)

```

### 2018-11-26 Experiments/experiment1_rev.js
small changes on rev

@@ -415,7 +415,7 @@ var myTrials_joint=[]
   
 var chunk1 = "<center><font size='5'>You are now going to start: </br></br>The testing chunk number <b>"; 
     
-var chunk2= "</b> (out of <b>4</b>)</font></br></br>The task and instructions are the same in all the chunks.</br></br>You may take a small pause before every chunk.</br></br>Please stay focused till the end of the chunck!</center>";
+var chunk2= "</b> (out of <b>4</b>)</font></br></br>The task and instructions are the same in all the chunks.</br></br>You may take a small pause before every chunk.</br></br>Please stay focused till the end of the chunck! </br></br> <font color='red'> There will be a 2$ bonus for the top 50% performing participants! </font></center>";
     
     
 myTrials.push(myTrial={
@@ -460,10 +460,12 @@ var Trials_S_1=shuffleArray([0,1,2,3,4]);
 var Trials_S_2=shuffleArray([0,1,2,3,4]);
 var Trials_S_3=shuffleArray([0,1,2,3,4]);
 var Trials_S_4=shuffleArray([0,1,2,3,4]);
-
+var Trials_S_5=shuffleArray([0,1,2,3,4]);
+    
 var Trials_S = Trials_S_1.concat(Trials_S_2,
                                  Trials_S_3,
-                                 Trials_S_4); 
+                                 Trials_S_4,
+                                 Trials_S_5); 
     
 var total_sound= Trials_S.length;
 
@@ -487,7 +489,6 @@ for (i=0; i < total_sound; i++){
     myTrials_sound.push(myTrial);
 }
 
- 
 
 //Concept condition
 myTrials_concept.push(myTrial={
@@ -510,10 +511,12 @@ var Trials_C_1=shuffleArray([0,1,2,3,4]);
 var Trials_C_2=shuffleArray([0,1,2,3,4]);
 var Trials_C_3=shuffleArray([0,1,2,3,4]);
 var Trials_C_4=shuffleArray([0,1,2,3,4]);
+var Trials_C_5=shuffleArray([0,1,2,3,4]);
     
 var Trials_C = Trials_C_1.concat(Trials_C_2,
                                  Trials_C_3,
-                                 Trials_C_4);
+                                 Trials_C_4,
+                                 Trials_C_5);
 
 var total_concept= Trials_C.length;
 

### 2018-11-26 Data_and_analysis/revisons1_pilot.Rmd
revison pilot

--- 2018-11-13 Data_and_analysis/analysis_individual.Rmd
@@
 title: "WordRec Experiment"
-author: "A. Fourtassi & M. Frank"
-date: "January 13, 2017"
+author: "A. Fourtassi"
+date: "November 26, 2018"
 output:
@@
 ---
-
 Libraries.
@@
 ```
-
-```{r}
-
-coef_s = tidy(fit_s, model) 
-coef_nl_s = tidy(fit_nl_s, model)
-#Posterior for visual-only condition
-concept_nl1 <- nls(answer ~ 1/(1+(1-e)*exp((-4/vrV)*concept_dist+(8/vrV))), data=concept_all_exp1, start = list(e=0, vrV=2))
-
-#Posterior for audio-visual condition (this is the descriptive model)
-joint_nl1 <- nls(answer ~ 1/(1+(1-e)*exp((-4/vrA_j)*sound_dist+(-4/vrV_j)*concept_dist+(8/vrA_j)+(8/vrV_j))), data=joint_all_exp1, start = list(e=0, vrA_j=2, vrV_j=2))
-
-##extract coefficient
-eA_nl1 <- coef(sound_nl1)["e"]
-vrA_nl1 <- coef(sound_nl1)["vrA"]
-
-eV_nl1 <- coef(concept_nl1)["e"]
-vrV_nl1 <- coef(concept_nl1)["vrV"]
-
-eJ_nl1 <- coef(joint_nl1)["e"]
-vrJ_A_nl1 <- coef(joint_nl1)["vrA_j"]
-vrJ_V_nl1 <- coef(joint_nl1)["vrV_j"]
-#######
-
-### the fit functions
-x <- seq(0, 4, 0.01)
-
-y_sound_nl1 <- predict(sound_nl1, list(sound_dist = x), type="response")
-y_concept_nl1 <- predict(concept_nl1, list(concept_dist = x), type="response")
-
-uniS_nl1 <- data.frame(distance=x, prediction=y_sound_nl1) %>%
-  mutate(Condition = 'Auditory', 
-         Experiment ='Experiment 1')
-
-uniV_nl1 <- data.frame(distance=x, prediction=y_concept_nl1) %>%
-  mutate(Condition = 'Visual',
-         Experiment ='Experiment 1')
-
-```
-
-Fit individual curves
-```{r}
-#Increase the number of unimodal (since this is where the models do not converge) and decrease the number of joint, to
-
-#Sound Unimodal
-fit_s <- sound_all_exp1 %>%
-  group_by(ID) %>%
-  do(model = glm(answer ~  sound_dist, 
-                 data=., 
-                 family = binomial()))
-
-fit_nl_s <- sound_all_exp1 %>%
-  group_by(ID) %>%
-  do(model = nls(answer ~ 1/(1+(1-e)*exp((-4/vrA)*sound_dist+(8/vrA))), 
-                 data=.,
-                 start = list(e=0, vrA=1),
-                 nls.control(warnOnly = TRUE)))
-
-coef_s = tidy(fit_s, model) 
-coef_nl_s = tidy(fit_nl_s, model)
-
-#Concept Unimodal
-fit_c <- concept_all_exp1 %>%
-  group_by(ID) %>%
-  do(model = glm(answer ~  concept_dist, 
-                 data=., 
-                 family = binomial()))
-
-fit_nl_c <- concept_all_exp1 %>%
-  group_by(ID) %>%
-  do(model = nls(answer ~ 1/(1+(1-e)*exp((-4/vrV)*concept_dist+(8/vrV))), 
-                 data=.,
-                 start = list(e=0, vrV=1),
-                 nls.control(warnOnly = TRUE)))
-
-coef_c = tidy(fit_c, model) 
-coef_nl_c = tidy(fit_nl_c, model)
-
-x <- seq(0, 4, 0.01)
-
-#This simulation is not working!
-simul <- fit_s %>%
-  rowwise() %>%
-  do(sim = predict(model, list(sound_dist = x), type="response"))
-
-#Joint 
-fit_j <- joint_all_exp1 %>%
-  group_by(ID) %>%
-  do(model = glm(answer ~  sound_dist + concept_dist, 
-                 data=., 
-                 family = binomial()))
-
-fit_nl_j <- joint_all_exp1 %>%
-  group_by(ID) %>%
-  do(model = nls(answer ~ 1/(1+(1-e)*exp((-4/vrA_j)*sound_dist+(-4/vrV_j)*concept_dist+(8/vrA_j)+(8/vrV_j))),
-                 data=.,
-                 start = list(e=0, vrA_j=2, vrV_j=2),
-                 nls.control(warnOnly = TRUE)))
-
-coef_j = tidy(fit_j, model) 
-coef_nl_j = tidy(fit_nl_j, model)
-
-#2 steps:
-#1) Do the full model with Subjects as random effect 
-#2) Show the distribution of cue integration at the individual level (instead of just the joint model); that is, computet the proportion of 1) the weighing of the indivisual model (V/S)_uni to th weighing of the
-
-##extract coefficient
-eA_nl1 <- coef(sound_nl1)["e"]
-vrA_nl1 <- coef(sound_nl1)["vrA"]
-
-eV_nl1 <- coef(concept_nl1)["e"]
-vrV_nl1 <- coef(concept_nl1)["vrV"]
-
-eJ_nl1 <- coef(joint_nl1)["e"]
-vrJ_A_nl1 <- coef(joint_nl1)["vrA_j"]
-vrJ_V_nl1 <- coef(joint_nl1)["vrV_j"]
-#######
-
-### the fit functions
-x <- seq(0, 4, 0.01)
-
-y_sound_nl1 <- predict(sound_nl1, list(sound_dist = x), type="response")
-y_concept_nl1 <- predict(concept_nl1, list(concept_dist = x), type="response")
-
-uniS_nl1 <- data.frame(distance=x, prediction=y_sound_nl1) %>%
-  mutate(Condition = 'Auditory', 
-         Experiment ='Experiment 1')
-
-uniV_nl1 <- data.frame(distance=x, prediction=y_concept_nl1) %>%
-  mutate(Condition = 'Visual',
-         Experiment ='Experiment 1')
-
-```
-
-Plots
-```{r}
-ggplot(exp_uni_data, 
-       aes(x = distance, y = mean)) + 
-  geom_point()+
-  geom_pointrange(aes(ymin = lower, ymax = upper), 
-                  position = position_dodge(width = .1), size = 0.4, fatten = 2) + 
-  #geom_line(data=uniV,aes(x=xV, y=yV))+
-  #geom_line(data=all_uni_model, aes(x=distance, y=prediction), col='black')+
-  xlab("Distance") +ylab("Prob. different")+
-  #scale_y_continuous(limits = c(0, 1))+#theme(aspect.ratio = 0.7)+
-  theme_few()+
-  theme(aspect.ratio = 0.7) + facet_grid(ID ~ Condition)
-  #stat_function(fun = Logistic_v, colour="red"))
-
-```
-
-Fit the models.
-```{r}
-
-#Fit the uniomodal sound condition
-sound_data <- d %>%
-    filter(condition == "sound")
-
-concept_data <- d %>%
-    filter(condition == "concept")
-
-joint_data <- d %>%
-    filter(condition == "joint")
-
-#Fit the uniomodal sound condition with a logistic regression
-fit_sound <- glm(answer ~ sound_dist, data=sound_data, family = binomial())
-
-##extract coefficient
-s_coef <- coef(fit_sound)["sound_dist"]
-s_inter <- coef(fit_sound)["(Intercept)"]
-
-#prameters of the sound distribution
-s_var=4/(s_coef)
-s_sum=-1*s_inter/s_coef
-
-#Fit the uniomodal visual conditon
-fit_concept <- glm(answer ~ concept_dist, data=concept_data, family = binomial())
-
-##extract coefficient
-c_coef <- coef(fit_concept)["concept_dist"]
-c_inter <- coef(fit_concept)["(Intercept)"]
-
-#prameters of the sound distribution
-v_var=4/(c_coef)
-v_sum=-1*c_inter/c_coef
-
-#Fit the bimodal conditon
-fit_joint <- glm(answer ~ sound_dist+concept_dist, data=joint_data, family = binomial())
-
-##extract coefficient
-j_coef_a <- coef(fit_joint)["sound_dist"]
-j_coef_v <- coef(fit_joint)["concept_dist"]
-j_inter <- coef(fit_joint)["(Intercept)"]
-
-#prameters of the sound distribution (approx: the average mean sum equal to 0+4/2=2)
-j_var_a=4/(j_coef_a)
-j_var_v=4/(j_coef_v)
-
-#decision_ideal=v_va/s_va
-
-#decision_fit=j_va_v/j_va_s
-
-# preference = decision_fit/decision_ideal
-
-```
-
-Analysis of the unimodal cases.
-```{r}
-
-#Recogniton functions from the unimodal fit 
-x <- seq(0, 4, 0.01)
-
-y_sound <- predict(fit_sound, list(sound_dist = x), type="response")
-y_concept <- predict(fit_concept, list(concept_dist = x), type="response")
-
-uniS <- data.frame(xS=x,yS=y_sound)
-uniV <- data.frame(xV=x,yV=y_concept)
-
-#Recognition functions from the bimodal fit (marginal distributions)
-Logistic_a = function (x, A = j_coef_a , B = 2*j_coef_a) {
-    1 / (1 + exp(-1*(-B +A * x)))
-}
-
-Logistic_v = function (x, A = j_coef_v , B = 2*j_coef_v) {
-    1 / (1 + exp(-1*(-B +A * x)))
-}
-
-#Plot all these functions in the same graph
-
-##The auditory case
-ggplot(sounds, 
-       aes(x = sound_dist, y = mean)) + 
-  geom_pointrange(aes(ymin = summary_ci_lower, ymax = summary_ci_upper), 
-                  position = position_dodge(width = .1)) + 
-  geom_line(data=uniS,aes(x=xS, y=yS))+
-  xlab("Auditory distance") +ylab("% different")+
-  scale_y_continuous(limits = c(0, 1))+
-  stat_function(fun = Logistic_a, colour="red")
-
-##The visual case
-ggplot(concepts, 
-       aes(x = concept_dist, y = mean)) + 
-  geom_pointrange(aes(ymin = summary_ci_lower, ymax = summary_ci_upper), 
-                  position = position_dodge(width = .1)) + 
-  geom_line(data=uniV,aes(x=xV, y=yV))+
-  xlab("Visual distance") +ylab("% different")+
-  scale_y_continuous(limits = c(0, 1))+
-  stat_function(fun = Logistic_v, colour="red")
-
-```
-Individual analysis:
-
-```{r}
-
-#Fit the uniomodal sound condition
-
-d <- d1
-
-sound_bysub <- d %>%
-  filter(condition == "sound") %>%
-  group_by(ID) %>%
-  do(fit_sound = glm(answer ~ sound_dist, data=., family = binomial()))
-
-soundCoef = tidy(sound_bysub, fit_sound) %>%
-  filter(term == 'sound_dist') %>%
-  mutate(s_var = 4/(estimate)) %>%
-  select(ID, s_var)
-
-concept_bysub <- d %>%
-  filter(condition == "concept") %>%
-  group_by(ID) %>%
-  do(fit_concept = glm(answer ~ concept_dist, data=., family = binomial()))
-
-conceptCoef = tidy(concept_bysub, fit_concept) %>%
-  filter(term == 'concept_dist') %>%
-  mutate(c_var = 4/(estimate)) %>%
-  select(ID, c_var)
-
-unimodal_bysub <- soundCoef %>%
-  left_join(conceptCoef) %>%
-  mutate(unim = c_var/s_var)
-
-joint_bysub <- d %>%
-  filter(condition == "joint") %>%
-  group_by(ID) %>%
-  do(fit_joint = glm(answer ~ concept_dist+ sound_dist, data=., family = binomial()))
-
-bimodal_bysub = tidy(joint_bysub, fit_joint) %>%
-  filter(term == 'concept_dist' | term == 'sound_dist') %>%
-  mutate(j_var = 4/(estimate)) %>%
-  select(ID, term, j_var) %>%
-  spread(term, j_var) %>%
-  rename(j_c_var = concept_dist, 
-         j_s_var = sound_dist) %>%
-  mutate(bimod = j_c_var/j_s_var)
-
-all_bysub <- unimodal_bysub  %>%
-  left_join(bimodal_bysub) %>%
-  mutate(ideal = bimod/unim)
-
-```
-```{r}
-ggplot(data=all_bysub, aes(s_var)) + 
-  geom_vline(xintercept=1, col='red')+
-  geom_histogram(binwidth = 0.4) +
-  xlim(-15,15)
-
-ggplot(data=all_bysub, aes(c_var)) + 
-  geom_vline(xintercept=1, col='red')+
-  geom_histogram(binwidth = 0.4) +
-  xlim(-15,15)
-
-ggplot(data=all_bysub, aes(unim)) + 
-  geom_vline(xintercept=1, col='red')+
-  geom_histogram(binwidth = 0.4) +
-  xlim(-15,15)
-
-ggplot(data=all_bysub, aes(j_s_var)) + 
-  geom_vline(xintercept=1, col='red')+
-  geom_histogram(binwidth = 0.4) +
-  xlim(-15,15)
-
-ggplot(data=all_bysub, aes(j_c_var)) + 
-  geom_vline(xintercept=1, col='red')+
-  geom_histogram(binwidth = 0.4) +
-  xlim(-15,15)
-
-ggplot(data=all_bysub, aes(bimod)) + 
-  geom_vline(xintercept=1, col='red')+
-  geom_histogram(binwidth = 0.4) +
-  xlim(-11,11)+
-  scale_x_log10()
-
-```
-
-```{r}
-neg_N <- bimodal_bysub %>%
-  filter(bimod <  -0.1) %>%
-  filter(bimod > -10)
-
-joint_sub <- joint_all_exp1 %>%
-  filter(ID == 'subject_13') %>%
-  group_by(concept_dist, sound_dist) %>%
-  multi_boot_standard(col = "answer")
-```
-
-```{r}
-ggplot(joint_sub, 
-       aes(x = concept_dist, y = mean, col = factor(sound_dist))) + 
-  geom_line(lty = 2) + 
-  xlab("Auditory distance") +ylab("% different")+
-  scale_colour_discrete(name="Visual Dist")+
-theme(legend.title = element_text(size=8))
-
-```
-
-The bimodal case
-```{r}
-
-# Bimodal recognition functions
-
-##the bimodal fit 
-model_fit <- function (x,y) {
-   1/(1 + exp(-x*j_coef_a-y*j_coef_v+2*j_coef_a+2*j_coef_v))
-}
-
-##Values of the baseline
-model_base <- function (x,y) {
-   1/(1 + exp(-x*s_coef-y*c_coef+2*s_coef+2*c_coef))
-}
-
-# Add the fit the baeline to data
-
-ms_all <- joint %>% 
-  rename(joint = mean) %>%
-  left_join(select(concepts, concept_dist, mean) %>% 
-              rename(concepts = mean)) %>%
-  left_join(select(sounds, sound_dist, mean) %>% 
-              rename(sounds = mean)) %>%
-  mutate(fit = model_fit(sound_dist, concept_dist)) %>%
-  mutate(base = model_base(sound_dist, concept_dist)) %>%
-  gather(model, pred, concepts, sounds, base, fit)
-
-#Plot Heat map for the data
-ggplot(data = ms_all, aes(x=sound_dist, y=concept_dist, fill=joint)) + 
-  geom_tile()+scale_fill_continuous(limits=c(0, 1))+xlab("Auditory distance") +ylab("Visual distance")
-
-#Plot Heatmap for the baseline
-mybase <- ms_all %>%
-  filter(model=="base")
-
-ggplot(data = mybase, aes(x=sound_dist, y=concept_dist, fill=pred)) + 
-  geom_tile()+scale_fill_continuous(limits=c(0, 1))+xlab("Auditory distance") +ylab("Visual distance")
-
-myfilter <- ms_all %>%
-  filter(model=="fit" | model=="base")
-
-#Correlation models (baseline and fit) to bimodal data 
-ggplot(myfilter, 
-       aes(x = pred, y = joint, col = factor(concept_dist), 
-           shape = factor(sound_dist))) +
- geom_pointrange(aes(ymin = ci_lower, ymax = ci_upper), 
-                  position = position_dodge(width = .1)) + 
-  geom_abline(slope = 1, lty = 2) +
-  facet_grid(model~.)
-
-```
-
-The modality dominance
-```{r}
-
-#Modality dominance coeficent
-a_fit=2
-a_base=1
-a_Vdom=2*a_base
-a_Sdom=0.5*a_base
-
-s_var=1
-v_var=1
-j_var_a=2
-j_var_v=2
-
-#Classification thresholds (prob=0.5) for:
-
-##The basline (combination of the unimodal cases)
-classif_base = function (x, A=a_base) {
-    2*(A+1)-A*x
-}
-
-##Best bivariate fit 
-classif_fit = function (x, A=a_fit) {
-    2*(A+1)-A*x
-}
-
-##A baseline for visual domiance
-classif_Vdom = function (x, A=a_Vdom) {
-    2*(A+1)-A*x
-}
-
-##A baseline for auditory domiance
-classif_Sdom = function (x, A=a_Sdom) {
-    2*(A+1)-A*x
-}
-
-#Sample from the baseline bivariate distribution
-Gaus_base <- data.frame(x=c(rnorm(1000,0,sqrt(s_var)),rnorm(1000,4,sqrt(s_var))),
-          y=c(rnorm(1000,0,sqrt(v_var)),rnorm(1000,4,sqrt(v_var))))
-
-#Plot samples from the bivariate distribution
-ggplot(Gaus_base, aes(x,y)) +  stat_density2d(geom="contour",aes(alpha=..level..))+
-  scale_alpha_continuous(limits=c(0,0.03),breaks=1e-6*seq(0,10,by=2))+
-  stat_function(fun = classif_base, colour = "red") +xlab("Auditory") +ylab("Visual")+ scale_x_continuous(limits = c(-6, 10))+scale_y_continuous(limits = c(-6, 10))
-
-#Sample from the best bivariate fit 
-Gaus_fit <- data.frame(x=c(rnorm(1000,0,sqrt(j_var_a)),rnorm(1000,4,sqrt(j_var_a))),
-          y=c(rnorm(1000,0,sqrt(j_var_v)),rnorm(1000,4,sqrt(j_var_v))))
-
-#Plot samples from the best bivariate fit
-ggplot(Gaus_fit, aes(x,y)) +  stat_density2d(geom="contour",aes(alpha=..level..))+
-  scale_alpha_continuous(limits=c(0,0.03),breaks=1e-6*seq(0,10,by=2))+
-  stat_function(fun = classif_fit, colour = "red") +xlab("Auditory") +ylab("Visual") + scale_x_continuous(limits = c(-6, 10))+scale_y_continuous(limits = c(-6, 10))
-
-#Modality dominance?
-ggplot(Gaus_fit, aes(x,y)) +
-  stat_function(fun = classif_base, colour = "red", lty=2) +
-  stat_function(fun = classif_Vdom, colour = "blue", lty=2 )+
-  stat_function(fun = classif_Sdom, colour = "blue", lty=2)+
-  stat_function(fun = classif_fit, colour = "black")+
-  xlab("Auditory") +ylab("Visual") + scale_x_continuous(limits = c(-6, 10))+
-  scale_y_continuous(limits = c(-6, 10))+theme(aspect.ratio = 1)
-
-```

### 2018-11-26 Data_and_analysis/revisons1_pilot.Rmd
increase threshold for selection
sample size

@@
 
-#Skip the pre task trials 
-#Filter subjects who had no technical problem
-#Select subjects who got more than 50% correct answers on the pre task trials
+##We will collect N=50 participants, and the data will be processed as follows
 
@@
 exp1_good <- exp1_noProb %>%
-  filter(score > 0.5)
+  filter(score >= 0.75)
 

### 2019-03-15 Data_and_analysis/analyses.Rmd
revisions

---
title: "WordRec Experiment"
author: "A. Fourtassi"
date: "November 26, 2018"
output:
  html_document:
    number_sections: yes
    toc: yes
---
Libraries.

```{r}
library(papaja)
library(kableExtra)
library(readr)
library(purrr)
library(tidyr)
library(ggplot2)
library(cowplot)
library(knitr)
library(nlstools)
library(boot)
library(dplyr)
library(langcog)
library(ggthemes)
library(broom)
```

Data and processing
```{r}

#Data from the 3 experiments 
#############################
exp1 <- read_delim("data_exp1_anonym.txt", delim = " ") %>%
  filter(type == "Task") %>%
  mutate(experiment='Experiment1')

exp2 <- read_delim("data_exp2_anonym.txt", delim = " ") %>%
  filter(type == "Task") %>%
  mutate(experiment='Experiment2')

exp3 <- read_delim("data_exp3_anonym.txt", delim = " ") %>%
  filter(type == "Task") %>%
  mutate(experiment='Experiment3')

exp4 <- read_delim("data_rev_real1.txt", delim = " ") %>%
  filter(type == "Task") %>%
  mutate(experiment='Experiment4')

```

```{r}
#First Exlusion criteria:
#############################

#All data

N_all_1 <- exp1 %>%
  distinct(ID) %>%
  nrow()

N_all_2 <- exp2 %>%
  distinct(ID) %>%
  nrow()

N_all_3 <- exp3 %>%
  distinct(ID) %>%
  nrow()

N_all_4 <- exp4 %>%
  distinct(ID) %>%
  nrow()

#Participants who did not encounter a technical problem with the online experiment

#Exp1
exp1_noProb <- exp1 %>%
  filter(problem=="No")

N_noProb_1 <- exp1_noProb %>%
  distinct(ID) %>%
  nrow()

#Exp2
exp2_noProb <- exp2 %>%
  filter(problem=="No")

N_noProb_2 <- exp2_noProb %>%
  distinct(ID) %>%
  nrow()

#Exp3
exp3_noProb <- exp3 %>%
  filter(problem=="No")

N_noProb_3 <- exp3_noProb %>%
  distinct(ID) %>%
  nrow()

#Exp 4
exp4_noProb <- exp4 %>%
  filter(problem=="No")

N_noProb_4 <- exp4_noProb %>%
  distinct(ID) %>%
  nrow()

#Participants who who did not encounter a problem AND were above 50% accuracy on obvious trials

#Exp1
exp1_good <- exp1_noProb %>%
  filter(score > 0.5)

N_good_1 <- exp1_good %>%
  distinct(ID) %>%
  nrow()

#Exp2
exp2_good <- exp2_noProb %>%
  filter(score > 0.5)

N_good_2 <- exp2_good %>%
  distinct(ID) %>%
  nrow()

#Exp3
exp3_good <- exp3_noProb %>%
  filter(score > 0.5)

N_good_3 <- exp3_good %>%
  distinct(ID) %>%
  nrow()

#Exp 4 (The change in the selection threshold in 1 bis was re-registered: the longer experiment required stricter quality control)
exp4_good <- exp4_noProb %>%
  filter(score >= 0.75)

N_good_4 <- exp4_good %>%
  distinct(ID) %>%
  nrow()
```

```{r}
#Data subseting

#Experiment 1
##############

exp_good <- bind_rows(exp1_good, exp2_good, exp3_good, exp4_good)

sounds_exp <- exp_good %>%
  filter(condition == "sound") %>%
  group_by(experiment, sound_dist) %>%
  dplyr::summarise(mean = mean(answer),
                   sd = sd(answer),
                   n = n()) %>%
  mutate(se = sd / sqrt(n),
         lower = mean - qt(1 - (0.05 / 2), n - 1) * se,
         upper = mean + qt(1 - (0.05 / 2), n - 1) * se) %>%
  select(-sd, -n, -se,) %>%
  mutate(Condition="Auditory") %>%
  rename(distance = sound_dist)

concepts_exp <- exp_good %>%
  filter(condition == "concept") %>%
  group_by(experiment, concept_dist) %>%
  dplyr::summarise(mean = mean(answer),
                   sd = sd(answer),
                   n = n()) %>%
  mutate(se = sd / sqrt(n),
         lower = mean - qt(1 - (0.05 / 2), n - 1) * se,
         upper = mean + qt(1 - (0.05 / 2), n - 1) * se) %>%
  select(-sd, -n, -se,) %>%
  mutate(Condition="Visual") %>%
  rename(distance = concept_dist)

joint_exp <- exp_good %>%
  filter(condition == "joint") %>%
  group_by(experiment, concept_dist, sound_dist) %>%
  summarise(mean = mean(answer)) %>%
  mutate(Condition="joint")

#Combine all
exp_uni <- bind_rows(sounds_exp, concepts_exp)

#feather::write_feather(exp_uni, "saved_data/exp_uni.feather")
exp_uni <- feather::read_feather("saved_data/exp_uni.feather")
```

```{r}

#Fit models to the reponses

fit_s <- function(data){
  nls(answer ~ 1/(1+(1-e)*exp((-4/vrA)*sound_dist+(8/vrA))), data=data, start = list(e=0, vrA=2))
}

fit_c <- function(data){
  nls(answer ~ 1/(1+(1-e)*exp((-4/vrV)*concept_dist+(8/vrV))), data=data, start = list(e=0, vrV=2))
}

fit_j <- function(data){
  nls(answer ~ 1/(1+(1-e)*exp((-4/vrA_j)*sound_dist+(-4/vrV_j)*concept_dist+(8/vrA_j)+(8/vrV_j))), data=data, start = list(e=0, vrA_j=2, vrV_j=2))
}

exp_good_s <- exp_good %>% filter(condition =='sound')
exp_good_c <- exp_good %>% filter(condition =='concept')
exp_good_j <- exp_good %>% filter(condition =='joint')

data_by_exp_s <- split(exp_good_s, exp_good_s$experiment) 
data_by_exp_c <- split(exp_good_c, exp_good_c$experiment)
data_by_exp_j <- split(exp_good_j, exp_good_j$experiment)

model_by_exp_s <- map(data_by_exp_s, fit_s) 
model_by_exp_c <- map(data_by_exp_c, fit_c)
model_by_exp_j <- map(data_by_exp_j, fit_j)

```

Extract coefficients
```{r}
##Extract coefficients 
####################

#Unimodal coefficients
 co_s <- function(model, exp) {
   data.frame(bias_s=coefficients(model)[1],
              bias_s_low = confint2(model)[1,][1],
              bia_s_up = confint2(model)[1,][2],

              var_s=coefficients(model)[2], 
              var_s_low = confint2(model)[2,][1],
              var_s_up = confint2(model)[2,][2],

              experiment=exp)
 }

  co_c <- function(model, exp) {
   data.frame(bias_c=coefficients(model)[1],
              bias_c_low = confint2(model)[1,][1],
              bias_c_up = confint2(model)[1,][2],

              var_c= coefficients(model)[2], 
              var_c_low = confint2(model)[2,][1],
              var_c_up = confint2(model)[2,][2],

              experiment=exp)
 }

 #Bimodal coefficients
 co_j <- function(model, exp) {
   data.frame(bias_j=coefficients(model)[1],
              bias_j_low = confint2(model)[1,][1],
              bias_j_up = confint2(model)[1,][2],

              var_j_s=coefficients(model)[2],
              var_j_s_low = confint2(model)[2,][1],
              var_j_s_up = confint2(model)[2,][2],

              var_j_c=coefficients(model)[3],
              var_j_c_low = confint2(model)[3,][1],
              var_j_c_up = confint2(model)[3,][2],

              experiment=exp)
 }

 experiment <- as.list(strsplit(names(model_by_exp_s), " "))

coef_s <- map2(model_by_exp_s, experiment, co_s) %>%
  bind_rows()

coef_c <- map2(model_by_exp_c, experiment, co_c) %>%
  bind_rows()

coef_j <- map2(model_by_exp_j, experiment, co_j) %>%
  bind_rows()

parameters <- coef_s %>%
  right_join(coef_c) %>%
  right_join(coef_j) %>%
  select(experiment, bias_s, var_s, bias_c, var_c, bias_j, var_j_s, var_j_c)

feather::write_feather(parameters, "saved_data/parameters.feather")
parameters <- feather::read_feather("saved_data/parameters.feather")

```

Parameter values (! change kable format to "pdf")

```{r stats, results="asis", echo=FALSE}

kable(parameters, escape = FALSE, booktabs = TRUE,
      linesep = "", format.args = list(big.mark = ","),
      caption = "Statistics for the dataset we used."#,
      #col.names = c("Language",  "Nouns", "Ages", "N", "Nouns", "Ages","N")
      ) %>%
  add_header_above(c("", "Auditory" = 2, "Visual" = 2, "Bimodal" = 3 )) %>%
  column_spec(1, bold = TRUE) %>%
  kable_styling(position = "center")

```

Unuimodal condition
```{r}
##Generate predictions  
######################

x <- seq(0, 4, 0.01)

pr_s <- function(model, exp){
  y <- predict(model, list(sound_dist = x), type="response")
  data.frame(distance=x, prediction=y, experiment=exp, Condition = "Auditory") 
}

pr_c <- function(model, exp){
  y <- predict(model, list(concept_dist = x), type="response")
  data.frame(distance=x, prediction=y, experiment=exp, Condition = "Visual") 
}

pred_s <- map2(model_by_exp_s, experiment, pr_s) %>%
  bind_rows()

pred_c <- map2(model_by_exp_c, experiment, pr_c) %>%
  bind_rows()

pred_uni <- bind_rows(pred_s, pred_c)

feather::write_feather(pred_uni, "saved_data/pred_uni.feather")
pred_uni <- feather::read_feather("saved_data/pred_uni.feather")

### plot all
ggplot(exp_uni, 
       aes(x = distance, y = mean)) + 
  #geom_point()+
  geom_pointrange(aes(ymin = lower, ymax = upper), 
                  position = position_dodge(width = .1), size = 0.4, fatten = 2) + 
  #geom_line(data=uniV,aes(x=xV, y=yV))+
  geom_line(data=pred_uni, aes(x=distance, y=prediction), col='black')+
  xlab("Distance") +ylab("Prob. different")+
  scale_y_continuous(limits = c(0, 1))+#theme(aspect.ratio = 0.7)+
  theme_few()+
  theme(aspect.ratio = 0.7) + facet_grid(experiment ~ Condition)
  #stat_function(fun = Logistic_v, colour="red"))

```

Bimodal condition: iptimality analysis
```{r}

#First define all models

# Sound only
model_s <- function (data, x,y) {
  vrA = unique(data$var_s)
  b = unique(data$bias_s)

  1/(1 + (1-b)*exp((-4/vrA)*x+(8/vrA)))
}

# Visual only
model_c <- function (data, x,y) {
  vrV = unique(data$var_c)
  b = unique(data$bias_c)

  1/(1 + (1-b)*exp((-4/vrV)*y+(8/vrV)))
}

# Optimal
model_opt <- function (data, x,y) {
  vrA = unique(data$var_s)
  vrV = unique(data$var_c)
  e   = unique(data$bias_j)

  1/(1 + (1-e)*exp((-4/vrA)*x+(-4/vrV)*y+(8/vrA)+(8/vrV)))
}

# Descriptive
model_des <- function (data, x,y) {
  vrA = unique(data$var_j_s)
  vrV = unique(data$var_j_c)
  e   = unique(data$bias_j)

  1/(1 + (1-e)*exp((-4/vrA)*x+(-4/vrV)*y+(8/vrA)+(8/vrV)))
}

data_and_models <- joint_exp %>%
  left_join(coef_s) %>%
  left_join(coef_c) %>%
  left_join(coef_j)

models <- function (data) {
  data %>% rename(Joint = mean) %>%
  mutate(Descriptive = model_des(data, sound_dist, concept_dist)) %>%
  mutate(Optimal = model_opt(data, sound_dist, concept_dist)) %>%
  mutate(Auditory = model_s(data, sound_dist, concept_dist)) %>%
  mutate(Visual = model_c(data, sound_dist, concept_dist)) %>%
  gather(model, pred, Visual, Auditory, Optimal, Descriptive) 
}

data_by_exp <- split(data_and_models, data_and_models$experiment)

pred_bimod <- map(data_by_exp, models) %>%
  bind_rows()

#Caclculate correlation
modelCorr <- pred_bimod %>%
  group_by(experiment, model) %>%
  summarise(cor = round(cor(Joint, pred)^2, 2))

pred_bimod <- pred_bimod %>%
  left_join(modelCorr)

feather::write_feather(pred_bimod, "saved_data/all_bimod.feather")
pred_bimod <- feather::read_feather("saved_data/all_bimod.feather")
```
main plot 
```{r}
pred_bimod$model <- factor(pred_bimod$model, levels = c('Visual','Auditory', 'Optimal', 'Descriptive'))

ggplot(pred_bimod, 
       aes(x = pred, y = Joint, col = factor(concept_dist), 
           shape = factor(sound_dist))) + 
  geom_point(size =1)+
  scale_colour_solarized()+
 #geom_pointrange(aes(ymin = summary_ci_lower, ymax = summary_ci_upper), 
  #                position = position_dodge(width = .1), size=0.2) +

  geom_abline(slope = 1, lty = 2) +
  #annotate("text",aes(label=paste("R^2 ==", cor, sep="")), x=0.1, y=0.9, size=2, col='black', fontface = "bold", parse=TRUE)+
  geom_text(aes(label=paste("r^2 ==", cor, sep="")), x=0.15, y=0.9, size=2, col='black',fontface = "bold", parse=TRUE)+
  xlab("Predictions") +ylab("Human data")+
  facet_grid(experiment ~ model)+
  theme_few()+
theme(aspect.ratio = 0.7, 
      axis.text=element_text(size=6),
      strip.text.y = element_text(size = 8))+
  guides(color=guide_legend(title="Visual Distance")) +
  guides(shape=guide_legend(title="Auditory Distance")) 
```

Bootsrap resampling of the cue combination weights

```{r echo=FALSE}

#Bootstrap sample of parameters

lmfit <- function(data, indices) {

  myd = data[indices, ]

  s_data <- myd %>%
    filter(condition == "sound")

  v_data <- myd %>%
    filter(condition == "concept")

  j_data <- myd %>%
    filter(condition == "joint")

  s_nl <- nls(answer ~ 1/(1+(1-e)*exp((-4/vrA)*sound_dist+(8/vrA))), data=s_data, start = list(e=0, vrA=2), nls.control(warnOnly = TRUE))

 c_nl <- nls(answer ~ 1/(1+(1-e)*exp((-4/vrV)*concept_dist+(8/vrV))), data=v_data, start = list(e=0, vrV=2), nls.control(warnOnly = TRUE))

 j_nl <- nls(answer ~ 1/(1+(1-e)*exp((-4/vrA_j)*sound_dist+(-4/vrV_j)*concept_dist+(8/vrA_j)+(8/vrV_j))), data=j_data, start = list(e=0, vrA_j=2, vrV_j=2), nls.control(warnOnly = TRUE))

  s_va <- coefficients(s_nl)["vrA"]
  s_e <- coefficients(s_nl)["e"]

  v_va <- coefficients(c_nl)["vrV"]
  v_e <- coefficients(c_nl)["e"]

  decision_ideal=v_va/s_va

  j_va_s=coefficients(j_nl)["vrA_j"]
  j_va_v=coefficients(j_nl)["vrV_j"]
  j_e=coefficients(j_nl)["e"]

  decision_fit=j_va_v/j_va_s

  preference = decision_fit/decision_ideal

  MyBoot=c(s_va, s_e, v_va, v_e, j_va_s, j_va_v, j_e, decision_ideal, decision_fit, preference)

  return(MyBoot)

  }

```

experiment 1 (too long, need to re-write this)
```{r echo=FALSE}
#results1 <- boot(data=exp1_good, statistic = lmfit, R = 10000)

#dataSave1 <- data.frame(matrix(ncol = 5, nrow = 0))
#data_names <- c("variable", "estimate", "lower","upper", "Experiment")
#colnames(dataSave1) <- data_names

#Auditory variance:
#audVar=boot.ci(results1, index = 1, type = c("bca"), conf = 0.95)

#v1 <- data.frame('audVar', as.numeric(audVar$t0), as.numeric(audVar$bca[4]), as.numeric(audVar$bca[5]), 'Exp1')
#  colnames(v1) <- data_names

#Auditory bias:
#audBias=boot.ci(results1, index = 2, type = c("bca"), conf = 0.95)

#v2 <- data.frame('audBias', as.numeric(audBias$t0), as.numeric(audBias$bca[4]), as.numeric(audBias$bca[5]), 'Exp1')
#colnames(v2) <- data_names

#Visual variance:
#visVar=boot.ci(results1, index = 3, type = c("bca"), conf = 0.95)

#v3 <- data.frame('visVar', as.numeric(visVar$t0), as.numeric(visVar$bca[4]), as.numeric(visVar$bca[5]), 'Exp1')
#colnames(v3) <- data_names

#Visual bias:
#visBias=boot.ci(results1, index = 4, type = c("bca"), conf = 0.95)

#v4 <- data.frame('visBias', as.numeric(visBias$t0), as.numeric(visBias$bca[4]), as.numeric(visBias$bca[5]), 'Exp1')
#colnames(v4) <- data_names

#Bimodal Auditory variance:
#audVarBi=boot.ci(results1, index = 5, type = c("bca"), conf = 0.95)

#v5 <- data.frame('audVarBi', as.numeric(audVarBi$t0), as.numeric(audVarBi$bca[4]), as.numeric(audVarBi$bca[5]), 'Exp1')
#colnames(v5) <- data_names

#Bimodal Visual variance:
#visVarBi=boot.ci(results1, index = 6, type = c("bca"), conf = 0.95)

#v6 <- data.frame('visVarBi', as.numeric(visVarBi$t0), as.numeric(visVarBi$bca[4]), as.numeric(visVarBi$bca[5]), 'Exp1')
#colnames(v6) <- data_names

#Bimodal bias:
#BiasBi=boot.ci(results1, index = 7, type = c("bca"), conf = 0.95)

#v7 <- data.frame('BiasBi', as.numeric(BiasBi$t0), as.numeric(BiasBi$bca[4]), as.numeric(BiasBi$bca[5]), 'Exp1')
#colnames(v7) <- data_names

#Ideal modality wieghing
#prefIdeal=boot.ci(results1, index = 8, type = c("bca"), conf = 0.95)

#v8 <- data.frame('prefIdeal', as.numeric(prefIdeal$t0), as.numeric(prefIdeal$bca[4]), as.numeric(prefIdeal$bca[5]), 'Exp1')
#colnames(v8) <- data_names

#fit modality wieghing
#prefFit=boot.ci(results1, index = 9, type = c("bca"), conf = 0.95)

#v9 <- data.frame('prefFit', as.numeric(prefFit$t0), as.numeric(prefFit$bca[4]), as.numeric(prefFit$bca[5]), 'Exp1')
#colnames(v9) <- data_names

#Modality bias 
#bias=boot.ci(results1, index = 10, type = c("bca"), conf = 0.95)

#v10 <- data.frame('bias', as.numeric(bias$t0), as.numeric(bias$bca[4]), as.numeric(bias$bca[5]), 'Exp1')
#colnames(v10) <- data_names

#dataSave1 <- bind_rows(dataSave1, v1, v2, v3, v4, v5, v6, v7, v8, v9, v10)

#feather::write_feather(dataSave1, "dataExp1.feather")

dataSave1 <- feather::read_feather("dataExp1.feather")

###### Extract values from saved data 
##To reproduce the values, please uncomment the previous code following the function "lmfit"

prefIdeal_val_1=dataSave1$estimate[which(dataSave1$variable == "prefIdeal")]
prefIdeal_ci1_1=dataSave1$lower[which(dataSave1$variable == "prefIdeal")]
prefIdeal_ci2_1=dataSave1$upper[which(dataSave1$variable == "prefIdeal")]

prefFit_val_1=dataSave1$estimate[which(dataSave1$variable == "prefFit")]
prefFit_ci1_1=dataSave1$lower[which(dataSave1$variable == "prefFit")]
prefFit_ci2_1=dataSave1$upper[which(dataSave1$variable == "prefFit")]

bias_val_1=dataSave1$estimate[which(dataSave1$variable == "bias")]
bias_ci1_1=dataSave1$lower[which(dataSave1$variable == "bias")]
bias_ci2_1=dataSave1$upper[which(dataSave1$variable == "bias")]

#With exactly the same procedure, we get the paramters for experiment 2 and 3 (experiment 4 has its own, separate analysis)
dataSave2 <- feather::read_feather("dataExp2.feather")
dataSave3 <- feather::read_feather("dataExp3.feather")

#Exp2
prefIdeal_val_2=dataSave2$estimate[which(dataSave2$variable == "prefIdeal")]
prefIdeal_ci1_2=dataSave2$lower[which(dataSave2$variable == "prefIdeal")]
prefIdeal_ci2_2=dataSave2$upper[which(dataSave2$variable == "prefIdeal")]

prefFit_val_2=dataSave2$estimate[which(dataSave2$variable == "prefFit")]
prefFit_ci1_2=dataSave2$lower[which(dataSave2$variable == "prefFit")]
prefFit_ci2_2=dataSave2$upper[which(dataSave2$variable == "prefFit")]

bias_val_2=dataSave2$estimate[which(dataSave2$variable == "bias")]
bias_ci1_2=dataSave2$lower[which(dataSave2$variable == "bias")]
bias_ci2_2=dataSave2$upper[which(dataSave2$variable == "bias")]

#Exp3
prefIdeal_val_3=dataSave3$estimate[which(dataSave3$variable == "prefIdeal")]
prefIdeal_ci1_3=dataSave3$lower[which(dataSave3$variable == "prefIdeal")]
prefIdeal_ci2_3=dataSave3$upper[which(dataSave3$variable == "prefIdeal")]

prefFit_val_3=dataSave3$estimate[which(dataSave3$variable == "prefFit")]
prefFit_ci1_3=dataSave3$lower[which(dataSave3$variable == "prefFit")]
prefFit_ci2_3=dataSave3$upper[which(dataSave3$variable == "prefFit")]

bias_val_3=dataSave3$estimate[which(dataSave3$variable == "bias")]
bias_ci1_3=dataSave3$lower[which(dataSave3$variable == "bias")]
bias_ci2_3=dataSave3$upper[which(dataSave3$variable == "bias")]

```

Modality preference

```{r echo=FALSE, warning = FALSE}

#Modality preference in an audio-vidual space

# Decision threshold
classif = function (x, A) {
    2*A+2-A*x
}

pref_data <- data.frame(matrix(ncol = 7, nrow = 0))
names <- c("Auditory", "Visual", "Optimal", "Auditory bias", "Visual bias", "Fit", "Experiment")
colnames(pref_data) <- names

x=seq(-1,5,0.02)

pref_exp1 <- data.frame(x, x, 
                        classif(x, prefIdeal_val_1),
                        classif(x, 2*prefIdeal_val_1),
                        classif(x, 0.5*prefIdeal_val_1),
                        classif(x, prefFit_val_1),
                        'Exp1')
colnames(pref_exp1) <- names

pref_exp2 <- data.frame(x, x, 
                        classif(x, prefIdeal_val_2),
                        classif(x, 2*prefIdeal_val_2),
                        classif(x, 0.5*prefIdeal_val_2),
                        classif(x, prefFit_val_2),
                        'Exp2')
colnames(pref_exp2) <- names

pref_exp3 <- data.frame(x, x, 
                        classif(x, prefIdeal_val_3),
                        classif(x, 2*prefIdeal_val_3),
                        classif(x, 0.5*prefIdeal_val_3),
                        classif(x, prefFit_val_3),
                        'Exp3')
colnames(pref_exp3) <- names

pref_data <- bind_rows(pref_data, pref_exp1, pref_exp2, pref_exp3) %>%
  gather(model, value, Optimal:Fit)

pref_data$model <- factor(pref_data$model, levels = c("Optimal", "Fit","Auditory bias", "Visual bias"))

feather::write_feather(pref_data, "pref_data.feather")
pref_data <- feather::read_feather("pref_data.feather")

pref_thres <- ggplot(pref_data, aes(x=Auditory, y=value, col = factor(model))) +
  geom_line(aes(linetype = factor(model) )) +
  facet_grid(.~Experiment)+
  scale_colour_manual(values = c("Optimal" = "red", "Auditory bias" = "blue", "Visual bias" = "green", "Fit" = "black"))+
  scale_linetype_manual(values = c("Optimal" = "solid", "Auditory bias" = "dashed", "Visual bias" = "dashed", "Fit" = "solid"))+
  xlab("Auditory") +ylab("Visual") +
  scale_x_continuous(limits = c(1.7, 2.3))+
  scale_y_continuous(limits = c(1.7, 2.3))+
  theme_few()+
  theme(aspect.ratio = 1)+
  theme(legend.title = element_blank())

```

```{r echo=FALSE, warning = FALSE}

#Modality bias
preference = c(bias_val_1, bias_val_2, bias_val_3)
experiment =c("Exp 1 \n", "Exp 2", "Exp 3")
ci_low=c(bias_ci1_1, bias_ci1_2, bias_ci1_3)
ci_up=c(bias_ci2_1, bias_ci2_2, bias_ci2_3)

pref = data.frame(preference, ci_low, ci_up)

bias <- ggplot(pref, 
       aes(x = experiment, y=preference)) +
  geom_hline(yintercept = 1, linetype='solid', color="red", size=1)+
  geom_hline(yintercept = 0.5, linetype=2, color="green")+
  geom_hline(yintercept = 2, linetype=2, color="blue")+
  geom_point(size=3)+
  geom_errorbar(aes(ymin = ci_low, ymax = ci_up), 
                  width = 0.1,
                  position = position_dodge(width = 0.1))+
  theme_few()+
  theme(aspect.ratio = 1, axis.text=element_text(size=10))+
  xlab("") +ylab("Relative weighting")+
  scale_y_log10(breaks=c(0.5,1,2),labels=c("Visual bias","Optimal","Auditory bias"))

  #coord_cartesian(ylim=c(0, 2.5))

```

```{r bias, echo=FALSE, warning = FALSE, out.width = "\\textwidth", fig.pos = "!h", fig.cap = "Modality preference is characterized as a deviation from the optimal decision threshold. A) The decision thresholds of both the optimal and the descriptive models (solid red and black lines, respectively). Deviation from optimality is compared to two hypothetical cases of modality preference. In these cases, deviation from  optimality is due to over-lying on the visual or the auditory input by a factor of 2 (green and blue dotted lines, respectively). B) An alternative way to represent the same data. Each point represents the value of the decision threshold's slope derived from the descriptive model relative to that of the optimal model (log-scaled). The lines represent the optimal case as well as the two hypothetical cases of modality preference. Error bars represent 95\\% confidence intervals over the distribution obtained through non-parametric resampling."}

legend <- get_legend(pref_thres)
plot_noLegend <- plot_grid(pref_thres + theme(legend.position="none"), NULL, bias, labels = c("A", "", "B"), ncol = 1, align = "v", rel_heights = c(1.1, 0.1, 1.3))
plot_grid(plot_noLegend, legend, rel_widths = c(2, .5))

```

Individual analysis (Experiment 4)

```{r}
#Here anlysese of individual models

#Models

#Sound Unimodal
fit_s <- function(data) {
  nls(answer ~ 1/(1+(1-e)*exp((-4/vrA)*sound_dist+(8/vrA))), 
                 data=data,
                 start = list(e=0, vrA=1),
                 nls.control(warnOnly = TRUE)) 
}
#Concept Unimodal
fit_c <- function(data) {
  nls(answer ~ 1/(1+(1-e)*exp((-4/vrV)*concept_dist+(8/vrV))), 
                 data=data,
                 start = list(e=0, vrV=1),
                 nls.control(warnOnly = TRUE)) 
}

#Joint sound-concept
fit_j <- function(data) {
  nls(answer ~1/(1+(1-e)*exp((-4/vrA_j)*sound_dist+(-4/vrV_j)*concept_dist+(8/vrA_j)+(8/vrV_j))), 
                 data=data,
                 start = list(e=0, vrA_j=1, vrV_j=1),
                 nls.control(warnOnly = TRUE)) 
}

##Fit the models for each subject

exp4_good_s <- exp4_good %>% filter(condition =='sound')
exp4_good_c <- exp4_good %>% filter(condition =='concept')
exp4_good_j <- exp4_good %>% filter(condition =='joint')

#Split data by subject 
data_by_subj_s <- split(exp4_good_s, exp4_good_s$ID) 
data_by_subj_c <- split(exp4_good_c, exp4_good_c$ID)
data_by_subj_j <- split(exp4_good_j, exp4_good_j$ID)

#.. and fit
model_by_subj_s <- map(data_by_subj_s, fit_s) 
model_by_subj_c <- map(data_by_subj_c, fit_c)
model_by_subj_j <- map(data_by_subj_j, fit_j)

```

```{r}

##Extract coefficients

#Unimodal coefficients
 co_uni <- function(model, ID) {
   data.frame(bias=coefficients(model)[1], 
              variance=coefficients(model)[2], 
              ID=ID)
 }

 #Bimodal coefficients
 co_bim <- function(model, ID) {
   data.frame(bias=coefficients(model)[1],
              var_s=coefficients(model)[2],
              var_c=coefficients(model)[3],
              ID=ID)
 }

ID <- as.list(strsplit(names(model_by_subj_s), " "))

#Here extract ceofficients to build optimal model later
coef_s <- map2(model_by_subj_s, ID, co_uni) %>%
  bind_rows() %>%
  rename(vrA_u= variance,
         bA_u =  bias)

coef_c <- map2(model_by_subj_c, ID, co_uni) %>%
  bind_rows() %>%
  rename(vrV_u= variance,
         bV_u =  bias)

coef_j <- map2(model_by_subj_j, ID, co_bim) %>%
  bind_rows() %>%
  rename(vrA_j = var_s,
         vrV_j = var_c,  
         b =  bias)

```

```{r}
## Below are functions that take sound and concept distances and return the predicted joint value in each model

# Sound only
model_s <- function (data, x,y) {
  vrA = unique(data$vrA_u)
  b = unique(data$bA_u)

  1/(1 + (1-b)*exp((-4/vrA)*x+(8/vrA)))
}

# Visual only
model_c <- function (data, x,y) {
  vrV = unique(data$vrV_u)
  b = unique(data$bV_u)

  1/(1 + (1-b)*exp((-4/vrV)*y+(8/vrV)))
}

# Optimal
model_opt <- function (data, x,y) {
  vrA = unique(data$vrA_u)
  vrV = unique(data$vrV_u)
  e   = unique(data$b)

  1/(1 + (1-e)*exp((-4/vrA)*x+(-4/vrV)*y+(8/vrA)+(8/vrV)))
}

# Descriptive
model_des <- function (data, x,y) {
  vrA = unique(data$vrA_j)
  vrV = unique(data$vrV_j)
  e   = unique(data$b)

  1/(1 + (1-e)*exp((-4/vrA)*x+(-4/vrV)*y+(8/vrA)+(8/vrV)))
}

data_models <- exp_good %>%
  filter(condition == "joint",
         experiment == "Experiment4") %>%
  group_by(ID, concept_dist, sound_dist) %>%
  summarise(mean = mean(answer)) %>%
  left_join(coef_s) %>%
  left_join(coef_c) %>%
  left_join(coef_j)

models <- function (subject_data) {
  subject_data %>% rename(Joint = mean) %>%
  mutate(Descriptive = model_des(subject_data, sound_dist, concept_dist)) %>%
  mutate(Optimal = model_opt(subject_data, sound_dist, concept_dist)) %>%
  mutate(Auditory = model_s(subject_data, sound_dist, concept_dist)) %>%
  mutate(Visual = model_c(subject_data, sound_dist, concept_dist)) %>%
  gather(model, pred, Visual, Auditory, Optimal, Descriptive) 
}

data_by_subj <- split(data_models, data_models$ID)

data_preds <- map(data_by_subj, models) %>%
  bind_rows()

data_preds$model <- factor(data_preds$model, levels = c('Visual','Auditory', 'Optimal', 'Descriptive'))

correlations <- data_preds %>%
  group_by(ID, model) %>%
  summarise(cor = round(cor(Joint, pred)^2, 2))

```
Individual distribution

```{r}
weight <- data_models %>%
  group_by(ID, vrA_u, vrV_u, vrA_j, vrV_j) %>%
  select(ID, vrA_u, vrV_u, vrA_j, vrV_j) %>%
  unique() %>%
  mutate(weight_u = vrA_u/vrV_u,
         weight_b = vrA_j/vrV_j) %>%
  mutate(prop = weight_u/weight_b)

feather::write_feather(weight, "ind_weights.feather")
weight <- feather::read_feather("ind_weights.feather")

weight_separate <- weight %>%
  select(ID, weight_u, weight_b) %>%
  gather (key, value, weight_u, weight_b)

weight.boot <- boot(data=weight$prop, function(x,i) median(x[i]), R=10000)

weight.ci=boot.ci(weight.boot, 
                  conf = 0.95,
                  type = c('perc'))

#weights.dist <- weight$prop[weight$prop < 100 & weight$prop > 0.01]

weight.median <- weight.ci$t0
weight.median_low <- weight.ci$percent[4]
weight.median_up <- weight.ci$percent[5]

ggplot(data=weight, aes(x=prop, y=..count..)) +
  geom_histogram(alpha=0.5, binwidth = 0.4)+
  geom_vline(xintercept = weight.median, col='red')+
  geom_vline(xintercept = weight.median_low, linetype='dashed') +
  geom_vline(xintercept = weight.median_up, linetype='dashed') +
  #geom_histogram(data=subset(bimod_all, data=='simulation'), fill="blue", alpha=0.2, binwidth = 0.2)+
  #geom_histogram(binwidth = 0.2) +
 scale_x_log10(breaks =c(0.1,1,10)) +
   xlab("Optimal weighing relative to real weighing") +ylab("Count")+
  theme_few()+
  theme(aspect.ratio = 0.7) +
  coord_cartesian(xlim=c(0.01,100))

```

### 2019-03-15 Data_and_analysis/revisons1_pilot.Rmd
revisions

@@
 
-exp1 <- read_delim("exp1_rev2_anonym.txt", delim = " ") %>%
+exp1 <- read_delim("data_rev_real1.txt", delim = " ") %>%
   filter(type == "Task") %>%
@@
 
-Fit the aggregate  data 
+Fit the aggregate  data,
+
+This a replcition of the unimodal data with aggregated data
 ```{r}
@@
 Optimal model
+
+This is a replication of the optimality analysis for aggregated data
+
 ```{r}
@@
 
-Here fit the same models for every subject
+Here fit a different model for every subject
+There are probably convergence issues with some participants, should check this later
+(I think I should take those out of the analysis)
 ```{r}
@@
 
-Unimodal conditions
+How to plot this? (but this visualization is not crucial)
+Plot for every condition? or just change color for every participant (maybe too much to parse)
+PLot just the means and ci?
+
 ```{r}
@@
 ggplot(sounds_exp1, 
-       aes(x = distance, y = mean)) + 
+       aes(x = distance, y = mean, group = distance)) + 
+  geom_boxplot()+
+  #geom_line()+
+  #geom_smooth()+
+  #geom_pointrange(aes(ymin = lower, ymax = upper), 
+  #                position = position_dodge(width = .1), size = 0.4, fatten = 2) + 
+  #geom_line(data=uniV,aes(x=xV, y=yV))+
+  geom_smooth(data=pred_s, aes(x=distance, y=prediction), col='black')+
+  xlab("Distance") +ylab("Prob. different")+
+  scale_y_continuous(limits = c(0, 1))+#theme(aspect.ratio = 0.7)+
+  theme_few()+
+  theme(aspect.ratio = 0.7) #+ facet_grid(. ~ ID)
+
+ggplot(subset(concepts_exp1, ID=="subject_1"), 
+       aes(x = distance, y = mean, col = ID)) + 
   geom_point()+
@@
   #geom_line(data=uniV,aes(x=xV, y=yV))+
-  geom_line(data=pred_s, aes(x=distance, y=prediction), col='black')+
-  #geom_line(data=uni_me_s, aes(x=distance, y=prediction), col='blue')+
-  geom_line(data=pred_nl_s, aes(x=distance, y=prediction), col='red')+
+  geom_line(data=subset(pred_c,ID=="subject_1"), aes(x=distance, y=prediction), col='black')+
   xlab("Distance") +ylab("Prob. different")+
@@
   theme_few()+
-  theme(aspect.ratio = 0.7) + facet_grid(. ~ ID)
-
-ggplot(concepts_exp1, 
-       aes(x = distance, y = mean)) + 
-  geom_point()+
-  #geom_pointrange(aes(ymin = lower, ymax = upper), 
-  #                position = position_dodge(width = .1), size = 0.4, fatten = 2) + 
-  #geom_line(data=uniV,aes(x=xV, y=yV))+
-  geom_line(data=pred_c, aes(x=distance, y=prediction), col='black')+
-  #geom_line(data=uni_me_s, aes(x=distance, y=prediction), col='blue')+
-  geom_line(data=pred_nl_c, aes(x=distance, y=prediction), col='red')+
-  xlab("Distance") +ylab("Prob. different")+
-  scale_y_continuous(limits = c(0, 1))+#theme(aspect.ratio = 0.7)+
-  theme_few()+
-  theme(aspect.ratio = 0.7) + facet_grid(. ~ ID)
+  theme(aspect.ratio = 0.7) #+ facet_grid(. ~ ID)
 
 ```
-
-Here compute the optimal combination
+Here compute the cue combination analysis for each participant
 ```{r}
@@
 
+```
+
+Plot by subject, not sure how to do it 
+```{r}
 ggplot(data_preds, 
@@
 ```
+
+```{r}
+#Make hitogram of optimality
+
+histo_all <- correlations %>%
+  group_by(ID) %>%
+  filter(cor == max(cor)) %>%
+  arrange(ID, model, cor)
+
+histo_norm <- correlations %>%
+  filter(model != 'Descriptive') %>%
+  group_by(ID) %>%
+  filter(cor == max(cor)) %>%
+  arrange(ID, model, cor)
+
+ggplot(histo_all, 
+      aes(x = model)) +
+  stat_count(width = 0.5)+
+  #geom_histogram()+
+  #scale_x_log10() +
+  theme_few() + 
+  theme(aspect.ratio = 0.7, legend.title = element_text(size=8)) +#  facet_grid(Segmentation ~ language)+
+  #scale_y_continuous(labels = scales::percent)+
+  xlab("Model") +ylab("Count")
+
+ggplot(histo_norm, 
+      aes(x = model)) +
+  stat_count(width = 0.5)+
+  #geom_histogram()+
+  #scale_x_log10() +
+  theme_few() + 
+  theme(aspect.ratio = 0.7, legend.title = element_text(size=8)) +#  facet_grid(Segmentation ~ language)+
+  #scale_y_continuous(labels = scales::percent)+
+  xlab("Model") +ylab("Count")
+
+```
+Here I calculate the reliance on visual vs. auditory
+
+```{r}
+
+weight <- data_models %>%
+  group_by(ID, vrA_u, vrV_u, vrA_j, vrV_j) %>%
+  select(ID, vrA_u, vrV_u, vrA_j, vrV_j) %>%
+  unique() %>%
+  mutate(weight_u = vrA_u/vrV_u,
+         weight_b = vrA_j/vrV_j) %>%
+  mutate(prop = weight_u/weight_b)
+
+weight_sum <- weight %>% 
+  mutate(temp = 'temp') %>%
+  group_by(temp) %>%
+  multi_boot_standard(col = "prop")
+
+weight_separate <- weight %>%
+  select(ID, weight_u, weight_b) %>%
+  gather (key, value, weight_u, weight_b)
+
+weight.boot <- boot(data=weight$prop, function(x,i) median(x[i]), R=10000)
+
+weight.ci=boot.ci(weight.boot, 
+                  conf = 0.95,
+                  type = c('perc'))
+
+#weights.dist <- weight$prop[weight$prop < 100 & weight$prop > 0.01]
+
+weight.median <- weight.ci$t0
+weight.median_low <- weight.ci$percent[4]
+weight.median_up <- weight.ci$percent[5]
+
+ggplot(data=weight, aes(x=prop, y=..count..)) +
+  geom_histogram(alpha=0.5, binwidth = 0.4)+
+  geom_vline(xintercept = weight.median, col='red')+
+  geom_vline(xintercept = weight.median_low, linetype='dashed') +
+  geom_vline(xintercept = weight.median_up, linetype='dashed') +
+  #geom_histogram(data=subset(bimod_all, data=='simulation'), fill="blue", alpha=0.2, binwidth = 0.2)+
+  #geom_histogram(binwidth = 0.2) +
+ scale_x_log10(breaks =c(0.1,1,10)) +
+   xlab("Optimal weighing relative to real weighing") +ylab("Count")+
+  theme_few()+
+  theme(aspect.ratio = 0.7) +
+  coord_cartesian(xlim=c(0.01,100))
+
+```
+I should do a test whether the variance is due to measurement noise or to geniune between-subject variability 
+I should do the writing to see how these things will be intgrated
+Here do the modality preference test (the same analysis I did for the aggragated data)
+
+HERE
+Old indivudual analysis used in version 1 of the submitteed paper
+```{r echo=FALSE, warning = FALSE}
+
+##Here we fit logistic regression to each participant
+##The logitic regression is equivalent to the descriptive model without the bias term
+##We use logistic regressions  instead of the full descriptive model becuase the latter would not converge given the small data points available for each participant
+
+joint_bysub_1 <- joint_all_exp1 %>%
+  group_by(ID) %>%
+  do(fit_joint_1 = glm(answer ~ concept_dist+ sound_dist, data=., family = binomial()))
+
+joint_bysub_2 <- joint_all_exp2 %>%
+  group_by(ID) %>%
+  do(fit_joint_2 = glm(answer ~ concept_dist+ sound_dist, data=., family = binomial()))
+
+joint_bysub_3 <- joint_all_exp3 %>%
+  group_by(ID) %>%
+  do(fit_joint_3 = glm(answer ~ concept_dist+ sound_dist, data=., family = binomial()))
+
+##Extract auitory and visual variances for each participant
+
+#Exp1
+bimodal_bysub_1 = tidy(joint_bysub_1, fit_joint_1) %>%
+  filter(term == 'concept_dist' | term == 'sound_dist') %>%
+  mutate(j_var = 4/(estimate)) %>%
+  select(ID, term, j_var) %>%
+  spread(term, j_var) %>%
+  rename(j_c_var = concept_dist, 
+         j_s_var = sound_dist) %>%
+  mutate(bimod = j_c_var/j_s_var)
+
+#Exp2
+bimodal_bysub_2 = tidy(joint_bysub_2, fit_joint_2) %>%
+  filter(term == 'concept_dist' | term == 'sound_dist') %>%
+  mutate(j_var = 4/(estimate)) %>%
+  select(ID, term, j_var) %>%
+  spread(term, j_var) %>%
+  rename(j_c_var = concept_dist, 
+         j_s_var = sound_dist) %>%
+  mutate(bimod = j_c_var/j_s_var)
+
+#Exp3
+bimodal_bysub_3 = tidy(joint_bysub_3, fit_joint_3) %>%
+  filter(term == 'concept_dist' | term == 'sound_dist') %>%
+  mutate(j_var = 4/(estimate)) %>%
+  select(ID, term, j_var) %>%
+  spread(term, j_var) %>%
+  rename(j_c_var = concept_dist, 
+         j_s_var = sound_dist) %>%
+  mutate(bimod = j_c_var/j_s_var)
+
+```
+
+```{r echo=FALSE}
+#number of participants relying exlusiviely on one modality
+#cut off: a factor of 10
+
+#participants who rely on both modalities 
+bimodal_bysub_good_1 <- bimodal_bysub_1 %>%
+  filter(bimod > 0.1) %>%
+  filter(bimod < 10)
+
+#participants who rely only on the visual modality
+#(this includes participants who relied  only on the visual modality but gave noisy responses, leading to negative values of the variance, probably due to mistaking "same" for "different", or vice versa)
+only_visual_N_1 <- bimodal_bysub_1 %>%
+  filter(abs(bimod) < 0.1) %>%
+  nrow()
+
+#participants who rely only on the auditory modality
+
+only_sound_N_1 <- bimodal_bysub_1 %>%
+  filter(abs(bimod) > 10) %>%
+  nrow()
+
+#participants who relied on both modalities 
+both_N_1 <- bimodal_bysub_1 %>%
+  filter(abs(bimod) > 0.1) %>%
+  filter(abs(bimod) < 10) %>%
+  nrow()
+
+#participants with noisy negative variances
+neg_N_1 <- bimodal_bysub_1 %>%
+  filter(bimod <  -0.1) %>%
+  filter(bimod > -10) %>%
+  nrow()
+
+#Proportion of participants who relied only on the visual modality
+exlusive_prop_1 = only_visual_N_1/(only_sound_N_1+only_visual_N_1)
+
+```
+
+```{r echo=FALSE, warning = FALSE}
+
+#Simulated individual data from descriptive model model_fit0 without a bias term (equivalent to logitic regression)
+#(but the values are very similar to descriptive model with bias the term model_fit1)
+
+simulations <- data.frame()
+
+#We aggregate simulted values for 50 times the number of participants  (in order to get a stable final distribution)
+for (i in 1:50) {
+Simul_exp1 <- joint_all_exp1 %>%
+  select(ID, sound_dist, concept_dist) %>%
+  mutate(prob = model_fit0(sound_dist, concept_dist)) %>%
+  rowwise() %>%
+  mutate(answer = rbinom(1, 1, prob=prob))
+
+joint_bysub_sim_1 <- Simul_exp1 %>%
+  group_by(ID) %>%
+  do(fit_joint_sim_1 = glm(answer ~ concept_dist+ sound_dist, data=., family = binomial()))
+
+bimodal_bysub_sim_1 = tidy(joint_bysub_sim_1, fit_joint_sim_1) %>%
+  filter(term == 'concept_dist' | term == 'sound_dist') %>%
+  mutate(j_var = 4/(estimate)) %>%
+  select(ID, term, j_var) %>%
+  spread(term, j_var) %>%
+  rename(j_c_var = concept_dist, 
+         j_s_var = sound_dist) %>%
+  mutate(bimod = j_c_var/j_s_var) %>%
+  select(ID, bimod) %>%
+  filter(bimod > 0.1) %>%
+  filter(bimod < 10)
+
+  simulations <- bind_rows(simulations, bimodal_bysub_sim_1)
+}
+
+#Process and combine Real and Simulated data
+
+  bimod_sim <- simulations  %>%
+    mutate(data='simulation')
+
+  bimod_real <- bimodal_bysub_good_1  %>%
+    select(ID, bimod) %>%
+    mutate(data='real')
+
+  bimod_all <- bind_rows(bimod_real, bimod_sim)
+
+#compare the sd of the distribtutions
+ sd_ind<- bimod_all %>%
+  group_by(data) %>%
+  summarise(mean= mean(bimod),
+            sd = sd(bimod))
+```
+
+```{r echo=FALSE, individual, out.width = "\\textwidth", fig.pos = "!h",fig.cap = "Distributions of individual values of the visual variance relative to the auditory variance in Experiment 1.
+Light color represents the real individual distribution, and dark color represents the simulated individual distribution sampled from the descriptive model."}
+
+ggplot(data=bimod_all, aes(x=bimod, y=..ncount..)) +
+  geom_histogram(data=subset(bimod_all, data=='real'), fill="red", alpha=0.2, binwidth = 0.2)+
+  geom_histogram(data=subset(bimod_all, data=='simulation'), fill="blue", alpha=0.2, binwidth = 0.2)+
+  #geom_histogram(binwidth = 0.2) +
+  scale_x_log10() +
+   xlab("Visual variance relative to sound variance") +ylab("Count")+
+  theme_few()+
+  theme(aspect.ratio = 0.7)
+
+```
+-->

### 2019-03-15 Writeup/ms.Rmd
revisions

@@
 library(broom)
+library(kableExtra)
 #library("knitcitations")
@@
 
+exp4 <- read_delim("../Data_and_analysis/data_rev_real1.txt", delim = " ") %>%
+  filter(type == "Task") %>%
+  mutate(experiment='Experiment1')
+
 exp2 <- read_delim("../Data_and_analysis/data_exp2_anonym.txt", delim = " ") %>%
@@
 
+N_all_4 <- exp4 %>%
+  distinct(ID) %>%
+  nrow()
+
 #Participants who did not encounter a technical problem with the online experiment
@@
 
+#Exp 4
+exp4_noProb <- exp4 %>%
+  filter(problem=="No")
+
+N_noProb_4 <- exp4_noProb %>%
+  distinct(ID) %>%
+  nrow()
+
 #Participants who who did not encounter a problem AND were above 50% accuracy on obvious trials
@@
 
-```
-
-```{r}
-
-#Data subseting
-
-#Experiment 1
-##############
-
-sound_all_exp1 <- exp1_good %>%
-    filter(condition == "sound")
-
-concept_all_exp1 <- exp1_good %>%
-    filter(condition == "concept")
-
-joint_all_exp1 <- exp1_good %>%
-    filter(condition == "joint")
-
-#Summary
-
-sounds_exp1 <- exp1_good %>%
-  filter(condition == "sound") %>%
-  group_by(sound_dist) %>%
-  dplyr::summarise(mean = mean(answer),
-                   sd = sd(answer),
-                   n = n()) %>%
-  mutate(se = sd / sqrt(n),
-         lower = mean - qt(1 - (0.05 / 2), n - 1) * se,
-         upper = mean + qt(1 - (0.05 / 2), n - 1) * se) %>%
-  select(-sd, -n, -se,) %>%
-  mutate(Experiment="Experiment 1", 
-         Condition="Auditory") %>%
-  rename(distance = sound_dist)
-
-concepts_exp1 <- exp1_good %>%
-  filter(condition == "concept") %>%
-  group_by(concept_dist) %>%
-  dplyr::summarise(mean = mean(answer),
-                   sd = sd(answer),
-                   n = n()) %>%
-  mutate(se = sd / sqrt(n),
-         lower = mean - qt(1 - (0.05 / 2), n - 1) * se,
-         upper = mean + qt(1 - (0.05 / 2), n - 1) * se) %>%
-  select(-sd, -n, -se,) %>%
-  mutate(Experiment="Experiment 1", 
-         Condition="Visual") %>%
-  rename(distance = concept_dist)
-
-joint_exp1 <- exp1_good %>%
-  filter(condition == "joint") %>%
-  group_by(concept_dist, sound_dist) %>%
-  summarise(mean = mean(answer)) %>%
-  mutate(Experiment="Experiment 1", 
-         Condition="Joint")
-
-#Experiment2
-############
-
-sound_all_exp2 <- exp2_good %>%
-    filter(condition == "sound")
-
-concept_all_exp2 <- exp2_good %>%
-    filter(condition == "concept")
-
-joint_all_exp2 <- exp2_good %>%
-    filter(condition == "joint")
-
-#Summary
-sounds_exp2 <- exp2_good %>%
-  filter(condition == "sound") %>%
-  group_by(sound_dist) %>%
-  dplyr::summarise(mean = mean(answer),
-                   sd = sd(answer),
-                   n = n()) %>%
-  mutate(se = sd / sqrt(n),
-         lower = mean - qt(1 - (0.05 / 2), n - 1) * se,
-         upper = mean + qt(1 - (0.05 / 2), n - 1) * se) %>%
-  select(-sd, -n, -se,) %>%
-  mutate(Experiment="Experiment 2", 
-         Condition="Auditory") %>%
-  rename(distance = sound_dist)
-
-concepts_exp2 <- exp2_good %>%
-  filter(condition == "concept") %>%
-  group_by(concept_dist) %>%
-  dplyr::summarise(mean = mean(answer),
-                   sd = sd(answer),
-                   n = n()) %>%
-  mutate(se = sd / sqrt(n),
-         lower = mean - qt(1 - (0.05 / 2), n - 1) * se,
-         upper = mean + qt(1 - (0.05 / 2), n - 1) * se) %>%
-  select(-sd, -n, -se,) %>%
-  mutate(Experiment="Experiment 2", 
-         Condition="Visual") %>%
-  rename(distance = concept_dist)
-
-joint_exp2 <- exp2_good %>%
-  filter(condition == "joint") %>%
-  group_by(concept_dist, sound_dist) %>%
-  summarise(mean = mean(answer)) %>%
-  mutate(Experiment="Experiment 2", 
-         Condition="Joint")
-
-#Experiment3
-############
-
-sound_all_exp3 <- exp3_good %>%
-    filter(condition == "sound")
-
-concept_all_exp3 <- exp3_good %>%
-    filter(condition == "concept")
-
-joint_all_exp3 <- exp3_good %>%
-    filter(condition == "joint")
-
-#Summary
-sounds_exp3 <- exp3_good %>%
-  filter(condition == "sound") %>%
-  group_by(sound_dist) %>%
-  dplyr::summarise(mean = mean(answer),
-                   sd = sd(answer),
-                   n = n()) %>%
-  mutate(se = sd / sqrt(n),
-         lower = mean - qt(1 - (0.05 / 2), n - 1) * se,
-         upper = mean + qt(1 - (0.05 / 2), n - 1) * se) %>%
-  select(-sd, -n, -se,) %>%
-  mutate(Experiment="Experiment 3", 
-         Condition="Auditory") %>%
-  rename(distance = sound_dist)
-
-concepts_exp3 <- exp3_good %>%
-  filter(condition == "concept") %>%
-  group_by(concept_dist) %>%
-  dplyr::summarise(mean = mean(answer),
-                   sd = sd(answer),
-                   n = n()) %>%
-  mutate(se = sd / sqrt(n),
-         lower = mean - qt(1 - (0.05 / 2), n - 1) * se,
-         upper = mean + qt(1 - (0.05 / 2), n - 1) * se) %>%
-  select(-sd, -n, -se,) %>%
-  mutate(Experiment="Experiment 3", 
-         Condition="Visual") %>%
-  rename(distance = concept_dist)
-
-joint_exp3 <- exp3_good %>%
-  filter(condition == "joint") %>%
-  group_by(concept_dist, sound_dist) %>%
-  summarise(mean = mean(answer)) %>%
-  mutate(Experiment="Experiment 3", 
-         Condition="Joint")
-
-#Combine all
-exp_uni_data <- bind_rows(sounds_exp1, concepts_exp1,
-                     sounds_exp2, concepts_exp2,
-                     sounds_exp3, concepts_exp3)
-
+#Exp 4 (The change in the selection threshold in 1 bis was re-registered: the longer experiment required stricter quality control)
+exp4_good <- exp4_noProb %>%
+  filter(score >= 0.75)
+
+N_good_4 <- exp4_good %>%
+  distinct(ID) %>%
+  nrow()
 ```
@@
 
-```{r model, out.width = "\\textwidth", fig.pos = "!h", fig.cap = "Illustration of the model using simulated data.
+```{r model, out.width = '\\textwidth', fig.pos = "!h", fig.cap = "Illustration of the model using simulated data.
 A word category is defined as the joint bivariate distribution of an auditory category (horizontal, bottom panel) and a visual semantic category (vertical, left panel).
@@
 
-```{r echo=FALSE}
-
-#Bootstrap sample of parameters
-
-lmfit <- function(data, indices) {
-
-  myd = data[indices, ]
-
-  s_data <- myd %>%
-    filter(condition == "sound")
-
-  v_data <- myd %>%
-    filter(condition == "concept")
-
-  j_data <- myd %>%
-    filter(condition == "joint")
-
-  s_nl <- nls(answer ~ 1/(1+(1-e)*exp((-4/vrA)*sound_dist+(8/vrA))), data=s_data, start = list(e=0, vrA=2), nls.control(warnOnly = TRUE))
-
- c_nl <- nls(answer ~ 1/(1+(1-e)*exp((-4/vrV)*concept_dist+(8/vrV))), data=v_data, start = list(e=0, vrV=2), nls.control(warnOnly = TRUE))
-
- j_nl <- nls(answer ~ 1/(1+(1-e)*exp((-4/vrA_j)*sound_dist+(-4/vrV_j)*concept_dist+(8/vrA_j)+(8/vrV_j))), data=j_data, start = list(e=0, vrA_j=2, vrV_j=2), nls.control(warnOnly = TRUE))
-
-  s_va <- coef(s_nl)["vrA"]
-  s_e <- coef(s_nl)["e"]
-
-  v_va <- coef(c_nl)["vrV"]
-  v_e <- coef(c_nl)["e"]
-
-  decision_ideal=v_va/s_va
-
-  j_va_s=coef(j_nl)["vrA_j"]
-  j_va_v=coef(j_nl)["vrV_j"]
-  j_e=coef(j_nl)["e"]
-
-  decision_fit=j_va_v/j_va_s
-
-  preference = decision_fit/decision_ideal
-
-  MyBoot=c(s_va, s_e, v_va, v_e, j_va_s, j_va_v, j_e, decision_ideal, decision_fit, preference)
-
-  return(MyBoot)
-
-  }
-
-#results1 <- boot(data=exp1_good, statistic = lmfit, R = 10000)
-
-#dataSave1 <- data.frame(matrix(ncol = 5, nrow = 0))
-#data_names <- c("variable", "estimate", "lower","upper", "Experiment")
-#colnames(dataSave1) <- data_names
-
-#Auditory variance:
-#audVar=boot.ci(results1, index = 1, type = c("bca"), conf = 0.95)
-
-#v1 <- data.frame('audVar', as.numeric(audVar$t0), as.numeric(audVar$bca[4]), as.numeric(audVar$bca[5]), 'Exp1')
-#  colnames(v1) <- data_names
-
-#Auditory bias:
-#audBias=boot.ci(results1, index = 2, type = c("bca"), conf = 0.95)
-
-#v2 <- data.frame('audBias', as.numeric(audBias$t0), as.numeric(audBias$bca[4]), as.numeric(audBias$bca[5]), 'Exp1')
-#colnames(v2) <- data_names
-
-#Visual variance:
-#visVar=boot.ci(results1, index = 3, type = c("bca"), conf = 0.95)
-
-#v3 <- data.frame('visVar', as.numeric(visVar$t0), as.numeric(visVar$bca[4]), as.numeric(visVar$bca[5]), 'Exp1')
-#colnames(v3) <- data_names
-
-#Visual bias:
-#visBias=boot.ci(results1, index = 4, type = c("bca"), conf = 0.95)
-
-#v4 <- data.frame('visBias', as.numeric(visBias$t0), as.numeric(visBias$bca[4]), as.numeric(visBias$bca[5]), 'Exp1')
-#colnames(v4) <- data_names
-
-#Bimodal Auditory variance:
-#audVarBi=boot.ci(results1, index = 5, type = c("bca"), conf = 0.95)
-
-#v5 <- data.frame('audVarBi', as.numeric(audVarBi$t0), as.numeric(audVarBi$bca[4]), as.numeric(audVarBi$bca[5]), 'Exp1')
-#colnames(v5) <- data_names
-
-#Bimodal Visual variance:
-#visVarBi=boot.ci(results1, index = 6, type = c("bca"), conf = 0.95)
-
-#v6 <- data.frame('visVarBi', as.numeric(visVarBi$t0), as.numeric(visVarBi$bca[4]), as.numeric(visVarBi$bca[5]), 'Exp1')
-#colnames(v6) <- data_names
-
-#Bimodal bias:
-#BiasBi=boot.ci(results1, index = 7, type = c("bca"), conf = 0.95)
-
-#v7 <- data.frame('BiasBi', as.numeric(BiasBi$t0), as.numeric(BiasBi$bca[4]), as.numeric(BiasBi$bca[5]), 'Exp1')
-#colnames(v7) <- data_names
-
-#Ideal modality wieghing
-#prefIdeal=boot.ci(results1, index = 8, type = c("bca"), conf = 0.95)
-
-#v8 <- data.frame('prefIdeal', as.numeric(prefIdeal$t0), as.numeric(prefIdeal$bca[4]), as.numeric(prefIdeal$bca[5]), 'Exp1')
-#colnames(v8) <- data_names
-
-#fit modality wieghing
-#prefFit=boot.ci(results1, index = 9, type = c("bca"), conf = 0.95)
-
-#v9 <- data.frame('prefFit', as.numeric(prefFit$t0), as.numeric(prefFit$bca[4]), as.numeric(prefFit$bca[5]), 'Exp1')
-#colnames(v9) <- data_names
-
-#Modality bias 
-#bias=boot.ci(results1, index = 10, type = c("bca"), conf = 0.95)
-
-#v10 <- data.frame('bias', as.numeric(bias$t0), as.numeric(bias$bca[4]), as.numeric(bias$bca[5]), 'Exp1')
-#colnames(v10) <- data_names
-
-#dataSave1 <- bind_rows(dataSave1, v1, v2, v3, v4, v5, v6, v7, v8, v9, v10)
-
-#feather::write_feather(dataSave1, "dataExp1.feather")
-
-dataSave1 <- feather::read_feather("dataExp1.feather")
-
-###### Extract values from saved data 
-##To reproduce the values, please uncomment the previous code following the function "lmfit"
-
-audVar_val=dataSave1$estimate[which(dataSave1$variable == "audVar")]
-audVar_ci1=dataSave1$lower[which(dataSave1$variable == "audVar")]
-audVar_ci2=dataSave1$upper[which(dataSave1$variable == "audVar")]
-
-audBias_val=-dataSave1$estimate[which(dataSave1$variable == "audBias")]
-audBias_ci1=-dataSave1$upper[which(dataSave1$variable == "audBias")]
-audBias_ci2=-dataSave1$lower[which(dataSave1$variable == "audBias")]
-
-visVar_val=dataSave1$estimate[which(dataSave1$variable == "visVar")]
-visVar_ci1=dataSave1$lower[which(dataSave1$variable == "visVar")]
-visVar_ci2=dataSave1$upper[which(dataSave1$variable == "visVar")]
-
-visBias_val=-dataSave1$estimate[which(dataSave1$variable == "visBias")]
-visBias_ci1=-dataSave1$upper[which(dataSave1$variable == "visBias")]
-visBias_ci2=-dataSave1$lower[which(dataSave1$variable == "visBias")]
-
-audVarBi_val=dataSave1$estimate[which(dataSave1$variable == "audVarBi")]
-audVarBi_ci1=dataSave1$lower[which(dataSave1$variable == "audVarBi")]
-audVarBi_ci2=dataSave1$upper[which(dataSave1$variable == "audVarBi")]
-
-visVarBi_val=dataSave1$estimate[which(dataSave1$variable == "visVarBi")]
-visVarBi_ci1=dataSave1$lower[which(dataSave1$variable == "visVarBi")]
-visVarBi_ci2=dataSave1$upper[which(dataSave1$variable == "visVarBi")]
-
-BiasBi_val=-dataSave1$estimate[which(dataSave1$variable == "BiasBi")]
-BiasBi_ci1=-dataSave1$upper[which(dataSave1$variable == "BiasBi")]
-BiasBi_ci2=-dataSave1$lower[which(dataSave1$variable == "BiasBi")]
-
-prefIdeal_val_1=dataSave1$estimate[which(dataSave1$variable == "prefIdeal")]
-prefIdeal_ci1_1=dataSave1$lower[which(dataSave1$variable == "prefIdeal")]
-prefIdeal_ci2_1=dataSave1$upper[which(dataSave1$variable == "prefIdeal")]
-
-prefFit_val_1=dataSave1$estimate[which(dataSave1$variable == "prefFit")]
-prefFit_ci1_1=dataSave1$lower[which(dataSave1$variable == "prefFit")]
-prefFit_ci2_1=dataSave1$upper[which(dataSave1$variable == "prefFit")]
-
-bias_val_1=dataSave1$estimate[which(dataSave1$variable == "bias")]
-bias_ci1_1=dataSave1$lower[which(dataSave1$variable == "bias")]
-bias_ci2_1=dataSave1$upper[which(dataSave1$variable == "bias")]
-
-```
-
-```{r}
-
-#Fit the posteriors to the reponses
-
-##Experiment 1
-#############
-
-#Posterior for auditory-only condition
-sound_nl1 <- nls(answer ~ 1/(1+(1-e)*exp((-4/vrA)*sound_dist+(8/vrA))), data=sound_all_exp1, start = list(e=0, vrA=2))
-
-#Posterior for visual-only condition
-concept_nl1 <- nls(answer ~ 1/(1+(1-e)*exp((-4/vrV)*concept_dist+(8/vrV))), data=concept_all_exp1, start = list(e=0, vrV=2))
-
-#Posterior for audio-visual condition (this is the descriptive model)
-joint_nl1 <- nls(answer ~ 1/(1+(1-e)*exp((-4/vrA_j)*sound_dist+(-4/vrV_j)*concept_dist+(8/vrA_j)+(8/vrV_j))), data=joint_all_exp1, start = list(e=0, vrA_j=2, vrV_j=2))
-
-##extract coefficient
-eA_nl1 <- coef(sound_nl1)["e"]
-vrA_nl1 <- coef(sound_nl1)["vrA"]
-
-eV_nl1 <- coef(concept_nl1)["e"]
-vrV_nl1 <- coef(concept_nl1)["vrV"]
-
-eJ_nl1 <- coef(joint_nl1)["e"]
-vrJ_A_nl1 <- coef(joint_nl1)["vrA_j"]
-vrJ_V_nl1 <- coef(joint_nl1)["vrV_j"]
-#######
-
-### the fit functions
-x <- seq(0, 4, 0.01)
-
-y_sound_nl1 <- predict(sound_nl1, list(sound_dist = x), type="response")
-y_concept_nl1 <- predict(concept_nl1, list(concept_dist = x), type="response")
-
-uniS_nl1 <- data.frame(distance=x, prediction=y_sound_nl1) %>%
-  mutate(Condition = 'Auditory', 
-         Experiment ='Experiment 1')
-
-uniV_nl1 <- data.frame(distance=x, prediction=y_concept_nl1) %>%
-  mutate(Condition = 'Visual',
-         Experiment ='Experiment 1')
-
-##Experiment 2
-###############
-
-sound_nl2 <- nls(answer ~ 1/(1+(1-e)*exp((-4/vrA)*sound_dist+(8/vrA))), data=sound_all_exp2, start = list(e=0, vrA=2))
-
-concept_nl2 <- nls(answer ~ 1/(1+(1-e)*exp((-4/vrV)*concept_dist+(8/vrV))), data=concept_all_exp2, start = list(e=0, vrV=2))
-
-joint_nl2 <- nls(answer ~ 1/(1+(1-e)*exp((-4/vrA_j)*sound_dist+(-4/vrV_j)*concept_dist+(8/vrA_j)+(8/vrV_j))), data=joint_all_exp2, start = list(e=0, vrA_j=2, vrV_j=2))
-
-##extract coefficient
-eA_nl2 <- coef(sound_nl2)["e"]
-vrA_nl2 <- coef(sound_nl2)["vrA"]
-
-eV_nl2 <- coef(concept_nl2)["e"]
-vrV_nl2 <- coef(concept_nl2)["vrV"]
-
-eJ_nl2 <- coef(joint_nl2)["e"]
-vrJ_A_nl2 <- coef(joint_nl2)["vrA_j"]
-vrJ_V_nl2 <- coef(joint_nl2)["vrV_j"]
-#######
-
-### the fit functions
-x <- seq(0, 4, 0.01)
-
-y_sound_nl2 <- predict(sound_nl2, list(sound_dist = x), type="response")
-y_concept_nl2 <- predict(concept_nl2, list(concept_dist = x), type="response")
-
-uniS_nl2 <- data.frame(distance=x, prediction=y_sound_nl2) %>%
-  mutate(Condition = 'Auditory', 
-         Experiment ='Experiment 2')
-
-uniV_nl2 <- data.frame(distance=x, prediction=y_concept_nl2) %>%
-  mutate(Condition = 'Visual', 
-         Experiment ='Experiment 2')
-
-##Experiment 3
-###############
-
-sound_nl3 <- nls(answer ~ 1/(1+(1-e)*exp((-4/vrA)*sound_dist+(8/vrA))), data=sound_all_exp3, start = list(e=0, vrA=2))
-
-concept_nl3 <- nls(answer ~ 1/(1+(1-e)*exp((-4/vrV)*concept_dist+(8/vrV))), data=concept_all_exp3, start = list(e=0, vrV=2))
-
-joint_nl3 <- nls(answer ~ 1/(1+(1-e)*exp((-4/vrA_j)*sound_dist+(-4/vrV_j)*concept_dist+(8/vrA_j)+(8/vrV_j))), data=joint_all_exp3, start = list(e=0, vrA_j=2, vrV_j=2))
-
-##extract coefficient
-eA_nl3 <- coef(sound_nl3)["e"]
-vrA_nl3 <- coef(sound_nl3)["vrA"]
-
-eV_nl3 <- coef(concept_nl3)["e"]
-vrV_nl3 <- coef(concept_nl3)["vrV"]
-
-eJ_nl3 <- coef(joint_nl3)["e"]
-vrJ_A_nl3 <- coef(joint_nl3)["vrA_j"]
-vrJ_V_nl3 <- coef(joint_nl3)["vrV_j"]
-#######
-
-### the fit functions
-x <- seq(0, 4, 0.01)
-
-y_sound_nl3 <- predict(sound_nl3, list(sound_dist = x), type="response")
-y_concept_nl3 <- predict(concept_nl3, list(concept_dist = x), type="response")
-
-uniS_nl3 <- data.frame(distance=x, prediction=y_sound_nl3) %>%
-  mutate(Condition = 'Auditory', 
-         Experiment ='Experiment 3')
-
-uniV_nl3 <- data.frame(distance=x, prediction=y_concept_nl3) %>%
-  mutate(Condition = 'Visual', 
-         Experiment ='Experiment 3')
-
-#### Combine all the fit functions
-all_uni_model <- bind_rows(uniS_nl1, uniV_nl1,
-                           uniS_nl2, uniV_nl2,
-                           uniS_nl3, uniV_nl3)
-
-### plot unimodal data + fit functions 
-all_plot <- ggplot(exp_uni_data, 
-       aes(x = distance, y = mean)) + 
-  #geom_point()+
-  geom_pointrange(aes(ymin = lower, ymax = upper), 
-                  position = position_dodge(width = .1), size = 0.4, fatten = 2) + 
-  #geom_line(data=uniV,aes(x=xV, y=yV))+
-  geom_line(data=all_uni_model, aes(x=distance, y=prediction), col='black')+
-  xlab("Distance") +ylab("Prob. different")+
-  scale_y_continuous(limits = c(0, 1))+#theme(aspect.ratio = 0.7)+
-  theme_few()+
-  theme(aspect.ratio = 0.7) + facet_grid(Experiment ~ Condition)
-  #stat_function(fun = Logistic_v, colour="red"))
-
-```
-
 ### Model fitting details
@@
 
-Although the paradigm is within-subjects, we did not have enough statistical power to fit a different model for each individual participant.^[We had a relatively high number of trials spanning all possible audio-visual matchings.
-Getting enough data points per trial per participant would have required running the online experimental for a much longer time (more than an hour).
-This could have increased significantly the dropout rate and possibly affected the quality of the data collected online.] Instead, models were constructed with data collapsed across all participants.
-That being said, we will also analyze the distribution of individual responses.
+Although the paradigm is within-subjects, we did not have enough statistical power to fit a different model for each individual participant.
+Instead, models were constructed with data collapsed across all participants.
 The fit was done with a nonlinear least squares regression using the NLS package in R [@bates88].
 We computed the values of the parameters, as well as their 95% confidence intervals, through non-parametric bootstrap (using 10000 iterations).
+
+```{r stats, results="asis", echo=FALSE}
+
+parameters <- feather::read_feather("../Data_and_analysis/saved_data/parameters.feather")
+
+kable(parameters, format = "latex", escape = FALSE, booktabs = TRUE,
+      linesep = "", format.args = list(big.mark = ","),
+      caption = "Statistics for the dataset we used."#,
+      #col.names = c("Language",  "Nouns", "Ages", "N", "Nouns", "Ages","N")
+      ) %>%
+  add_header_above(c("", "Auditory" = 2, "Visual" = 2, "Bimodal" = 3 )) %>%
+  column_spec(1, bold = TRUE) %>%
+  kable_styling(position = "center")
+
+```
 
@@
 
-all_plot
+exp_uni <- feather::read_feather("../Data_and_analysis/saved_data/exp_uni.feather")
+pred_uni <- feather::read_feather("../Data_and_analysis/saved_data/pred_uni.feather")
+
+### plot unimodal data + fit functions 
+ggplot(exp_uni, 
+       aes(x = distance, y = mean)) + 
+  #geom_point()+
+  geom_pointrange(aes(ymin = lower, ymax = upper), 
+                  position = position_dodge(width = .1), size = 0.4, fatten = 2) + 
+  #geom_line(data=uniV,aes(x=xV, y=yV))+
+  geom_line(data=pred_uni, aes(x=distance, y=prediction), col='black')+
+  xlab("Distance") +ylab("Prob. different")+
+  scale_y_continuous(limits = c(0, 1))+#theme(aspect.ratio = 0.7)+
+  theme_few()+
+  theme(aspect.ratio = 0.7) + facet_grid(experiment ~ Condition)
+  #stat_function(fun = Logistic_v, colour="red"))
 
@@
 
-```{r  echo=FALSE}
-
-###Models to be tested against responses in the bimodal condition
-
-#Descriptive model without a terms for response bias 
-model_fit0 <- function (x,y) {
-   1/(1 + exp((-4/vrJ_A_nl1)*x+(-4/vrJ_V_nl1)*y+(8/vrJ_A_nl1)+(8/vrJ_V_nl1)))
+```{r}
+
+#Here we conduct cross-validation for the descriptive model, since this model is trained and tested on the same data
+
+#As the numbers show, the predictions on the held-out subset is almost as accurate as the predictions on the training set.  Over-fitting is generally not a problem with such simple models)
+
+#We conduct a cross-validation where half the responses are used predict the other half
+
+#The function "crossValid", below, takes the data to be cross-validated and return a score (coefficient of determination)
+
+crossValid <- function(data) {
+
+n <- nrow(data)
+frac <- 0.5
+ix <- sample(n, frac * n) # indexes of in sample rows
+
+fo <- answer ~ 1/(1+(1-e)*exp((-4/vrA_j)*sound_dist+(-4/vrV_j)*concept_dist+(8/vrA_j)+(8/vrV_j)))
+
+fm <- nls(fo, data, start = list(e=0, vrA_j=2, vrV_j=2), subset = ix) # fit the model to a subset (here half) the responses
+
+#Extract the values of the parameter
+
+data.test <- data[-ix, ] # out of sample data
+data.train <- data[ix, ]
+
+data.train.means <- data.train %>%
+  group_by(concept_dist, sound_dist) %>%
+  summarise(mean = mean(answer))
+
+data.test.means <- data.test %>%
+  group_by(concept_dist, sound_dist) %>%
+  summarise(mean = mean(answer))
+
+pred.train <-  predict(fm, new = data.train.means)
+pred.test <- predict(fm, new = data.test.means)
+
+cor.train <- cor(data.train.means$mean, pred.train)^2 
+cor.test <- cor(data.test.means$mean, pred.test)^2
+
+return(cor.test)
+
 }
 
-##Experiment 1
-##############
-
-#Descriptive model (parameters are derived from fit to bimodal data)
-model_fit1 <- function (x,y) {
-   1/(1 + (1-eJ_nl1)*exp((-4/vrJ_A_nl1)*x+(-4/vrJ_V_nl1)*y+(8/vrJ_A_nl1)+(8/vrJ_V_nl1)))
-}
-
-#The optimal model (parameters are derived from fit to unimodal data)
-model_ideal1 <- function (x,y) {
-    1/(1 + (1-eJ_nl1)*exp((-4/vrA_nl1)*x+(-4/vrV_nl1)*y+(8/vrA_nl1)+(8/vrV_nl1)))
-}
-
-#The sound-only model
-model_sound1 <- function (x,y) {
-  1/(1 + (1-eJ_nl1)*exp((-4/vrA_nl1)*x+(8/vrA_nl1)))
-}
-
-#The visual-only model
-model_concept1 <- function (x,y) {
-  1/(1 + (1-eJ_nl1)*exp((-4/vrV_nl1)*y+(8/vrV_nl1)))
-}
-
-##Experiment 2
-##############
-
-#Descriptive model (parameters are derived from fit to bimodal data)
-model_fit2 <- function (x,y) {
-   1/(1 + (1-eJ_nl2)*exp((-4/vrJ_A_nl2)*x+(-4/vrJ_V_nl2)*y+(8/vrJ_A_nl2)+(8/vrJ_V_nl2)))
-}
-
-#The optimal model (parameters are derived from fit to unimodal data)
-model_ideal2 <- function (x,y) {
-    1/(1 + (1-eJ_nl2)*exp((-4/vrA_nl2)*x+(-4/vrV_nl2)*y+(8/vrA_nl2)+(8/vrV_nl2)))
-}
-
-#The sound-only model
-model_sound2 <- function (x,y) {
-  1/(1 + (1-eJ_nl2)*exp((-4/vrA_nl2)*x+(8/vrA_nl2)))
-}
-
-#The visual-only model
-model_concept2 <- function (x,y) {
-  1/(1 + (1-eJ_nl2)*exp((-4/vrV_nl2)*y+(8/vrV_nl2)))
-}
-
-##Experiment 3
-##############
-
-#Descriptive model (parameters are derived from fit to bimodal data)
-model_fit3 <- function (x,y) {
-   1/(1 + (1-eJ_nl3)*exp((-4/vrJ_A_nl3)*x+(-4/vrJ_V_nl3)*y+(8/vrJ_A_nl3)+(8/vrJ_V_nl3)))
-}
-
-#The optimal model (parameters are derived from fit to unimodal data)
-model_ideal3 <- function (x,y) {
-    1/(1 + (1-eJ_nl3)*exp((-4/vrA_nl3)*x+(-4/vrV_nl3)*y+(8/vrA_nl3)+(8/vrV_nl3)))
-}
-
-#The sound-only model
-model_sound3 <- function (x,y) {
-  1/(1 + (1-eJ_nl3)*exp((-4/vrA_nl3)*x+(8/vrA_nl3)))
-}
-
-#The visual-only model
-model_concept3 <- function (x,y) {
-  1/(1 + (1-eJ_nl3)*exp((-4/vrV_nl3)*y+(8/vrV_nl3)))
-}
-
-```
-
-```{r echo=FALSE, fig.width=7, fig.height=8}
-
-#Generate prediction in the bimodal condition
-
-models_exp1 <- joint_exp1 %>% 
-  rename(joint = mean) %>%
-  mutate(Descriptive = model_fit1(sound_dist, concept_dist)) %>%
-  mutate(Optimal = model_ideal1(sound_dist, concept_dist)) %>%
-  mutate(Auditory = model_sound1(sound_dist, concept_dist)) %>%
-  mutate(Visual = model_concept1(sound_dist, concept_dist)) %>%
-  gather(model, pred, Visual, Auditory, Optimal, Descriptive) %>%
-  mutate(experiment = 'Experiment 1')
-
-models_exp2 <- joint_exp2 %>% 
-  rename(joint = mean) %>%
-  mutate(Descriptive = model_fit2(sound_dist, concept_dist)) %>%
-  mutate(Optimal = model_ideal2(sound_dist, concept_dist)) %>%
-  mutate(Auditory = model_sound2(sound_dist, concept_dist)) %>%
-  mutate(Visual = model_concept2(sound_dist, concept_dist)) %>%
-  gather(model, pred, Visual, Auditory, Optimal, Descriptive) %>%
-  mutate(experiment = 'Experiment 2')
-
-models_exp3 <- joint_exp3 %>% 
-  rename(joint = mean) %>%
-  mutate(Descriptive = model_fit3(sound_dist, concept_dist)) %>%
-  mutate(Optimal = model_ideal3(sound_dist, concept_dist)) %>%
-  mutate(Auditory = model_sound3(sound_dist, concept_dist)) %>%
-  mutate(Visual = model_concept3(sound_dist, concept_dist)) %>%
-  gather(model, pred, Visual, Auditory, Optimal, Descriptive) %>%
-  mutate(experiment = 'Experiment 3')
-
-##Combine all predictions
-
-models_all <- bind_rows (models_exp1, models_exp2, models_exp3)
-
-models_all$model <- factor(models_all$model, levels = c('Visual','Auditory', 'Optimal', 'Descriptive'))
-
-correlation_plot <- ggplot(models_all, 
-       aes(x = pred, y = joint, col = factor(concept_dist), 
+#Average across N partions, to render the pdf I am using a small value, but higher values can be used for the final version
+N_partitions = 10
+
+crossValid_exp1 <- replicate(N_partitions, {
+  crossValid(joint_all_exp1)
+  })
+
+CV_exp1_mean = mean(crossValid_exp1)
+error <- qt(0.975,df=length(crossValid_exp1)-1)*sd(crossValid_exp1)/sqrt(length(crossValid_exp1))
+CV_exp1_lower = CV_exp1_mean - error
+CV_exp1_upper = CV_exp1_mean + error
+
+crossValid_exp2 <- replicate(N_partitions, {
+  crossValid(joint_all_exp2)
+  })
+
+CV_exp2_mean = mean(crossValid_exp2)
+error <- qt(0.975,df=length(crossValid_exp2)-1)*sd(crossValid_exp2)/sqrt(length(crossValid_exp2))
+CV_exp2_lower = CV_exp2_mean - error
+CV_exp2_upper = CV_exp2_mean + error
+
+crossValid_exp3 <- replicate(N_partitions, {
+  crossValid(joint_all_exp3)
+  })
+
+CV_exp3_mean = mean(crossValid_exp3)
+error <- qt(0.975,df=length(crossValid_exp3)-1)*sd(crossValid_exp3)/sqrt(length(crossValid_exp3))
+CV_exp3_lower = CV_exp3_mean - error
+CV_exp3_upper = CV_exp3_mean + error
+
+```
+
+#### Normative models
+Figure\ \@ref(fig:bimodal) compares the predictions of the normative models against human responses.
+Remember that the normative models use variance estimates from the unimodal conditions (where people see input from only one modality) to predict data in the bimodal condition (where people see input from both modalities).
+Each point represents data form a particular audio-visual matching (e.g., the visual token $v$ whose distance from the target $v_t$ is $|v-v_t|=3$, matched with the auditory token $a$ whose distance from the target $a_t$ is $|a-a_t|=2$).
+The visual, auditory and optimal model explained, respectively, `r 100*R2_visual_1`%, `r 100*R2_auditory_1`%, and `r 100*R2_optimal_1`% of total variance in mean responses.
+
+#### Descriptive model
+In the descriptive model, all parameters are fit to human responses in the bimodal condition.
+We found $b=$ `r BiasBi_val` [`r BiasBi_ci2`, `r BiasBi_ci1`], $\sigma^2_{Ab}=$ `r audVarBi_val` [`r audVarBi_ci1`, `r audVarBi_ci2`] and $\sigma^2_{Vb}=$ `r visVarBi_val` [`r visVarBi_ci1`, `r visVarBi_ci2`].
+Note that the variance of both the auditory and visual modalities increased compared to the unimodal conditions.
+
+\noindent The descriptive model explained `r 100*R2_descriptive_1`% of total variance.
+However, since the descriptive model was fit to the same data, there is a risk that this high correlation is due to overfitting.
+To examine this possibility, we cross-validated the model using half the responses to predict the other half (averaging across `r N_partitions` random partitions).
+The predictive power of the model remained very high ($r^2$=`r CV_exp1_mean`).
+
+```{r bimodal, out.width = "\\textwidth", fig.pos = "!h", fig.cap = "Human responses vs.
+Models' predictions in the bimodal condition across the three experiments.
+Each point represents data form a particular audio-visual matching.
+Shape represents auditory distance from the target, and color represents visual distance from the target.
+Thus, each point is characterized by both  shape and color."}
+
+pred_bimod <- feather::read_feather("../Data_and_analysis/saved_data/all_bimod.feather")
+
+pred_bimod$model <- factor(pred_bimod$model, levels = c('Visual','Auditory', 'Optimal', 'Descriptive'))
+
+ggplot(pred_bimod, 
+       aes(x = pred, y = Joint, col = factor(concept_dist), 
            shape = factor(sound_dist))) + 
@@
   geom_abline(slope = 1, lty = 2) +
+  #annotate("text",aes(label=paste("R^2 ==", cor, sep="")), x=0.1, y=0.9, size=2, col='black', fontface = "bold", parse=TRUE)+
+  geom_text(aes(label=paste("r^2 ==", cor, sep="")), x=0.15, y=0.9, size=2, col='black',fontface = "bold", parse=TRUE)+
   xlab("Predictions") +ylab("Human data")+
@@
 
-#Correlation values
-
-#Exp 1
-optimal_1 <- subset(models_all, model=='Optimal' & experiment=='Experiment 1')
-descriptive_1 <- subset(models_all, model=='Descriptive' & experiment=='Experiment 1')
-auditory_1 <- subset(models_all, model=='Auditory' & experiment=='Experiment 1')
-visual_1 <- subset(models_all, model=='Visual' & experiment=='Experiment 1')
-
-R2_optimal_1  <- cor(optimal_1$joint, optimal_1$pred)^2 %>%
-  round(2)
-R2_descriptive_1 <- cor(descriptive_1$joint, descriptive_1$pred)^2 %>%
-  round(2)
-R2_auditory_1  <- cor(auditory_1$joint, auditory_1$pred)^2 %>%
-  round(2)
-R2_visual_1  <- cor(visual_1$joint, visual_1$pred)^2 %>%
-  round(2)
-
-#Exp 2
-optimal_2 <- subset(models_all, model=='Optimal' & experiment=='Experiment 2')
-descriptive_2 <- subset(models_all, model=='Descriptive' & experiment=='Experiment 2')
-auditory_2 <- subset(models_all, model=='Auditory' & experiment=='Experiment 2')
-visual_2 <- subset(models_all, model=='Visual' & experiment=='Experiment 2')
-
-R2_optimal_2  <- cor(optimal_2$joint, optimal_2$pred)^2  %>%
-  round(2)
-R2_descriptive_2 <- cor(descriptive_2$joint, descriptive_2$pred)^2 %>%
-  round(2)
-R2_auditory_2  <- cor(auditory_2$joint, auditory_2$pred)^2 %>%
-  round(2)
-R2_visual_2  <- cor(visual_2$joint, visual_2$pred)^2 %>%
-  round(2)
-
-#Exp 3
-optimal_3 <- subset(models_all, model=='Optimal' & experiment=='Experiment 3')
-descriptive_3 <- subset(models_all, model=='Descriptive' & experiment=='Experiment 3')
-auditory_3 <- subset(models_all, model=='Auditory' & experiment=='Experiment 3')
-visual_3 <- subset(models_all, model=='Visual' & experiment=='Experiment 3')
-
-R2_optimal_3  <- cor(optimal_3$joint, optimal_3$pred)^2 %>%
-  round(2)
-R2_descriptive_3 <- cor(descriptive_3$joint, descriptive_3$pred)^2 %>%
-  round(2)
-R2_auditory_3  <- cor(auditory_3$joint, auditory_3$pred)^2 %>%
-  round(2)
-R2_visual_3  <- cor(visual_3$joint, visual_3$pred)^2 %>%
-  round(2)
-
-```
-
-```{r}
-
-#Here we conduct cross-validation for the descriptive model, since this model is trained and tested on the same data
-
-#As the numbers show, the predictions on the held-out subset is almost as accurate as the predictions on the training set.  Over-fitting is generally not a problem with such simple models)
-
-#We conduct a cross-validation where half the responses are used predict the other half
-
-#The function "crossValid", below, takes the data to be cross-validated and return a score (coefficient of determination)
-
-crossValid <- function(data) {
-
-n <- nrow(data)
-frac <- 0.5
-ix <- sample(n, frac * n) # indexes of in sample rows
-
-fo <- answer ~ 1/(1+(1-e)*exp((-4/vrA_j)*sound_dist+(-4/vrV_j)*concept_dist+(8/vrA_j)+(8/vrV_j)))
-
-fm <- nls(fo, data, start = list(e=0, vrA_j=2, vrV_j=2), subset = ix) # fit the model to a subset (here half) the responses
-
-#Extract the values of the parameter
-
-data.test <- data[-ix, ] # out of sample data
-data.train <- data[ix, ]
-
-data.train.means <- data.train %>%
-  group_by(concept_dist, sound_dist) %>%
-  summarise(mean = mean(answer))
-
-data.test.means <- data.test %>%
-  group_by(concept_dist, sound_dist) %>%
-  summarise(mean = mean(answer))
-
-pred.train <-  predict(fm, new = data.train.means)
-pred.test <- predict(fm, new = data.test.means)
-
-cor.train <- cor(data.train.means$mean, pred.train)^2 
-cor.test <- cor(data.test.means$mean, pred.test)^2
-
-return(cor.test)
-
-}
-
-#Average across N partions, to render the pdf I am using a small value, but higher values can be used for the final version
-N_partitions = 10
-
-crossValid_exp1 <- replicate(N_partitions, {
-  crossValid(joint_all_exp1)
-  })
-
-CV_exp1_mean = mean(crossValid_exp1)
-error <- qt(0.975,df=length(crossValid_exp1)-1)*sd(crossValid_exp1)/sqrt(length(crossValid_exp1))
-CV_exp1_lower = CV_exp1_mean - error
-CV_exp1_upper = CV_exp1_mean + error
-
-crossValid_exp2 <- replicate(N_partitions, {
-  crossValid(joint_all_exp2)
-  })
-
-CV_exp2_mean = mean(crossValid_exp2)
-error <- qt(0.975,df=length(crossValid_exp2)-1)*sd(crossValid_exp2)/sqrt(length(crossValid_exp2))
-CV_exp2_lower = CV_exp2_mean - error
-CV_exp2_upper = CV_exp2_mean + error
-
-crossValid_exp3 <- replicate(N_partitions, {
-  crossValid(joint_all_exp3)
-  })
-
-CV_exp3_mean = mean(crossValid_exp3)
-error <- qt(0.975,df=length(crossValid_exp3)-1)*sd(crossValid_exp3)/sqrt(length(crossValid_exp3))
-CV_exp3_lower = CV_exp3_mean - error
-CV_exp3_upper = CV_exp3_mean + error
-
-```
-
-#### Normative models
-Figure\ \@ref(fig:bimodal) compares the predictions of the normative models against human responses.
-Remember that the normative models use variance estimates from the unimodal conditions (where people see input from only one modality) to predict data in the bimodal condition (where people see input from both modalities).
-Each point represents data form a particular audio-visual matching (e.g., the visual token $v$ whose distance from the target $v_t$ is $|v-v_t|=3$, matched with the auditory token $a$ whose distance from the target $a_t$ is $|a-a_t|=2$).
-The visual, auditory and optimal model explained, respectively, `r 100*R2_visual_1`%, `r 100*R2_auditory_1`%, and `r 100*R2_optimal_1`% of total variance in mean responses.
-
-#### Descriptive model
-In the descriptive model, all parameters are fit to human responses in the bimodal condition.
-We found $b=$ `r BiasBi_val` [`r BiasBi_ci2`, `r BiasBi_ci1`], $\sigma^2_{Ab}=$ `r audVarBi_val` [`r audVarBi_ci1`, `r audVarBi_ci2`] and $\sigma^2_{Vb}=$ `r visVarBi_val` [`r visVarBi_ci1`, `r visVarBi_ci2`].
-Note that the variance of both the auditory and visual modalities increased compared to the unimodal conditions.
-
-\noindent The descriptive model explained `r 100*R2_descriptive_1`% of total variance.
-However, since the descriptive model was fit to the same data, there is a risk that this high correlation is due to overfitting.
-To examine this possibility, we cross-validated the model using half the responses to predict the other half (averaging across `r N_partitions` random partitions).
-The predictive power of the model remained very high ($r^2$=`r CV_exp1_mean`).
-
-```{r bimodal, out.width = "\\textwidth", fig.pos = "!h", fig.cap = "Human responses vs.
-Models' predictions in the bimodal condition across the three experiments.
-Each point represents data form a particular audio-visual matching.
-Shape represents auditory distance from the target, and color represents visual distance from the target.
-Thus, each point is characterized by both  shape and color."}
-
-correlation_plot
-
 ```
@@
 
-```{r echo=FALSE, warning = FALSE}
-
-##Here we fit logistic regression to each participant
-##The logitic regression is equivalent to the descriptive model without the bias term
-##We use logistic regressions  instead of the full descriptive model becuase the latter would not converge given the small data points available for each participant
-
-joint_bysub_1 <- joint_all_exp1 %>%
-  group_by(ID) %>%
-  do(fit_joint_1 = glm(answer ~ concept_dist+ sound_dist, data=., family = binomial()))
-
-joint_bysub_2 <- joint_all_exp2 %>%
-  group_by(ID) %>%
-  do(fit_joint_2 = glm(answer ~ concept_dist+ sound_dist, data=., family = binomial()))
-
-joint_bysub_3 <- joint_all_exp3 %>%
-  group_by(ID) %>%
-  do(fit_joint_3 = glm(answer ~ concept_dist+ sound_dist, data=., family = binomial()))
-
-##Extract auitory and visual variances for each participant
-
-#Exp1
-bimodal_bysub_1 = tidy(joint_bysub_1, fit_joint_1) %>%
-  filter(term == 'concept_dist' | term == 'sound_dist') %>%
-  mutate(j_var = 4/(estimate)) %>%
-  select(ID, term, j_var) %>%
-  spread(term, j_var) %>%
-  rename(j_c_var = concept_dist, 
-         j_s_var = sound_dist) %>%
-  mutate(bimod = j_c_var/j_s_var)
-
-#Exp2
-bimodal_bysub_2 = tidy(joint_bysub_2, fit_joint_2) %>%
-  filter(term == 'concept_dist' | term == 'sound_dist') %>%
-  mutate(j_var = 4/(estimate)) %>%
-  select(ID, term, j_var) %>%
-  spread(term, j_var) %>%
-  rename(j_c_var = concept_dist, 
-         j_s_var = sound_dist) %>%
-  mutate(bimod = j_c_var/j_s_var)
-
-#Exp3
-bimodal_bysub_3 = tidy(joint_bysub_3, fit_joint_3) %>%
-  filter(term == 'concept_dist' | term == 'sound_dist') %>%
-  mutate(j_var = 4/(estimate)) %>%
-  select(ID, term, j_var) %>%
-  spread(term, j_var) %>%
-  rename(j_c_var = concept_dist, 
-         j_s_var = sound_dist) %>%
-  mutate(bimod = j_c_var/j_s_var)
-
-```
-
-```{r echo=FALSE}
-#number of participants relying exlusiviely on one modality
-#cut off: a factor of 10
-
-#participants who rely on both modalities 
-bimodal_bysub_good_1 <- bimodal_bysub_1 %>%
-  filter(bimod > 0.1) %>%
-  filter(bimod < 10)
-
-#participants who rely only on the visual modality
-#(this includes participants who relied  only on the visual modality but gave noisy responses, leading to negative values of the variance, probably due to mistaking "same" for "different", or vice versa)
-only_visual_N_1 <- bimodal_bysub_1 %>%
-  filter(abs(bimod) < 0.1) %>%
-  nrow()
-
-#participants who rely only on the auditory modality
-
-only_sound_N_1 <- bimodal_bysub_1 %>%
-  filter(abs(bimod) > 10) %>%
-  nrow()
-
-#participants who relied on both modalities 
-both_N_1 <- bimodal_bysub_1 %>%
-  filter(abs(bimod) > 0.1) %>%
-  filter(abs(bimod) < 10) %>%
-  nrow()
-
-#participants with noisy negative variances
-neg_N_1 <- bimodal_bysub_1 %>%
-  filter(bimod <  -0.1) %>%
-  filter(bimod > -10) %>%
-  nrow()
-
-#Proportion of participants who relied only on the visual modality
-exlusive_prop_1 = only_visual_N_1/(only_sound_N_1+only_visual_N_1)
-
-```
-
-```{r echo=FALSE, warning = FALSE}
-
-#Simulated individual data from descriptive model model_fit0 without a bias term (equivalent to logitic regression)
-#(but the values are very similar to descriptive model with bias the term model_fit1)
-
-simulations <- data.frame()
-
-#We aggregate simulted values for 50 times the number of participants  (in order to get a stable final distribution)
-for (i in 1:50) {
-Simul_exp1 <- joint_all_exp1 %>%
-  select(ID, sound_dist, concept_dist) %>%
-  mutate(prob = model_fit0(sound_dist, concept_dist)) %>%
-  rowwise() %>%
-  mutate(answer = rbinom(1, 1, prob=prob))
-
-joint_bysub_sim_1 <- Simul_exp1 %>%
-  group_by(ID) %>%
-  do(fit_joint_sim_1 = glm(answer ~ concept_dist+ sound_dist, data=., family = binomial()))
-
-bimodal_bysub_sim_1 = tidy(joint_bysub_sim_1, fit_joint_sim_1) %>%
-  filter(term == 'concept_dist' | term == 'sound_dist') %>%
-  mutate(j_var = 4/(estimate)) %>%
-  select(ID, term, j_var) %>%
-  spread(term, j_var) %>%
-  rename(j_c_var = concept_dist, 
-         j_s_var = sound_dist) %>%
-  mutate(bimod = j_c_var/j_s_var) %>%
-  select(ID, bimod) %>%
-  filter(bimod > 0.1) %>%
-  filter(bimod < 10)
-
-  simulations <- bind_rows(simulations, bimodal_bysub_sim_1)
-}
-
-#Process and combine Real and Simulated data
-
-  bimod_sim <- simulations  %>%
-    mutate(data='simulation')
-
-  bimod_real <- bimodal_bysub_good_1  %>%
-    select(ID, bimod) %>%
-    mutate(data='real')
-
-  bimod_all <- bind_rows(bimod_real, bimod_sim)
-
-#compare the sd of the distribtutions
- sd_ind<- bimod_all %>%
-  group_by(data) %>%
-  summarise(mean= mean(bimod),
-            sd = sd(bimod))
-```
-
-```{r echo=FALSE, individual, out.width = "\\textwidth", fig.pos = "!h",fig.cap = "Distributions of individual values of the visual variance relative to the auditory variance in Experiment 1.
-Light color represents the real individual distribution, and dark color represents the simulated individual distribution sampled from the descriptive model."}
-
-ggplot(data=bimod_all, aes(x=bimod, y=..ncount..)) +
-  geom_histogram(data=subset(bimod_all, data=='real'), fill="red", alpha=0.2, binwidth = 0.2)+
-  geom_histogram(data=subset(bimod_all, data=='simulation'), fill="blue", alpha=0.2, binwidth = 0.2)+
-  #geom_histogram(binwidth = 0.2) +
-  scale_x_log10() +
-   xlab("Visual variance relative to sound variance") +ylab("Count")+
-  theme_few()+
-  theme(aspect.ratio = 0.7)
-
-```
-
-As we noted earlier, the model addresses the question of optimality at the population level.
+<!--the model addresses the question of optimality at the population level.
 However, it is important to  know how individual responses are distributed.
@@
 This finding means that the participants varied in terms of how they weighted modalities: Compared to the predictions of the population-level model, some participants relied more on the auditory modality, whereas others relied more on the visual modality.
-
-In Experiment 1, we tested word recognition when there was multimodal uncertainty in terms of category membership only.
-In real life, however, tokens can undergo distortions due to noisy factors in the environment (e.g., car noise in the background, blurry vision in a foggy weather).
+-->
+
+As we noted earlier, we did not have enough statistical power to fit a different model for each individual participant.
+Instead, we fit one model using the data aggregated across all participants.
+This analysis is informative of behavior at the population level, only.
+However, optimality at the population level could be misleading.
+Imagine, for instance, that in the bimodal condition half the participants relied exclusively on the visual modality, whereas the other half relied exclusively on the auditory modality.
+This case could still lead to an aggregate behavior which appears optimal, but this optimality would be spurious.
+This, in the experiemnt below, we test the cue integration strategy at the individual level.
+To this end, we increase the statistical power by extending the length of the experiment, allowing us to collect the number of datapoints necessary to fit the models for each participant.
+
+# Experiment 4
+
+```{r}
+
+weight <- feather::read_feather("../Data_and_analysis/ind_weights.feather")
+
+weight.boot <- boot(data=weight$prop, function(x,i) median(x[i]), R=10000)
+
+weight.ci=boot.ci(weight.boot, 
+                  conf = 0.95,
+                  type = c('perc'))
+
+#weights.dist <- weight$prop[weight$prop < 100 & weight$prop > 0.01]
+
+weight.median <- weight.ci$t0
+weight.median_low <- weight.ci$percent[4]
+weight.median_up <- weight.ci$percent[5]
+
+ggplot(data=weight, aes(x=prop, y=..count..)) +
+  geom_histogram(alpha=0.5, binwidth = 0.4)+
+  geom_vline(xintercept = weight.median, col='red')+
+  geom_vline(xintercept = weight.median_low, linetype='dashed') +
+  geom_vline(xintercept = weight.median_up, linetype='dashed') +
+  #geom_histogram(data=subset(bimod_all, data=='simulation'), fill="blue", alpha=0.2, binwidth = 0.2)+
+  #geom_histogram(binwidth = 0.2) +
+ scale_x_log10(breaks =c(0.1,1,10)) +
+   xlab("Optimal weighing relative to real weighing") +ylab("Count")+
+  theme_few()+
+  theme(aspect.ratio = 0.7) +
+  coord_cartesian(xlim=c(0.01,100))
+
+```
+
+### Participants
+We recruited a planned sample of N=XX participants from Amazon Mechanical Turk.
+Only participants with US IP addresses and a task approval rate above 99\% were allowed to participate.
+They were paid at an hourly rate of \$6/hour.
+Participants were excluded if they reported having experienced a technical problem of any sort during the online experiment (N=XX), or if they had less than 75\% accurate responses on the unambiguous training trials (N=XX).
+The final sample consisted of N = XX participants.
+[I should also add how many participants I excluded because their models did not converge].
+All participants provided informed consent before taking the experiment.\footnote{The sample size and exclusion criteria were specified in the pre-registration at https://osf.io/h7mzp/.}
+
+### Stimuli
+We used the same stimuli as in Experiment 1.
+
+### Design and Procedure
+The design and procedure were similar to Experiment 1. The only difference was that we increased the number of datapoints elicited per subject from 70 to 300.
+
+## Results and analysis
+
+### Unimodal conditions
+
+We fit both population-level models to the aggregated data (as in Experiment 1), and individual models to data from each participant.
+For the populaton-level models, the results (shown in Figure\ \@ref(fig:unimodal)) replicated the results obtained in Experiment 1.
+As for the individual-level analysis, the models showed there to be between-subject variability as seen in the paramters's distribution in Figure XX.
+
+### Bimodal condition and Cue combination models
+
+We first generated poupulation-level normative and descriptive models.
+As shown in Figure\ \@ref(fig:bimodal), the predicted patterns of these models mirrored closely the results obtained in Experiment 1.
+In addition, the optimality analysis (i.e., done through comparing the optimal and descriptive models) shows that the fitted mean decision threshold was indisguisable form the optimal threshold, thus replicating the results of Experiment 1 (Figure\ \@ref(fig:bias) shows that).
+
+<!--As a first analysis, we show the histogram comparing the normative models, only (Figure XX).
+The histogram shows interesting between-subject variability: The optimal model explained the most variance in the majority of cases, showing that participants in these cases combined information from the auditory and visual modality to perform the task.
+However, the visual and auditory models were sufficient to explain most variance in a large number of participants.
+These partcipants relied predominantly on only one modality to perform the task.
+This is the crucial analysis which would allow us to test the extent to which participants were optimal at the individual level.
+We perfomed an optimality analysis following the procedure outlines above, i.e., through comparing the optimal and descriptive models.
+Firs, at the population level, the fitted mean decision threshold was indisguisable form the optimal threshold, thus replicating the results of Experiment 1 (Figure\ \@ref(fig:bias) shows that).
+-->
+
+At the individual level, we computed the distribution of optimal weighing relative to the fitted (i.e., descriptive) weighing and we show this distribution in Figure XX.
+The distribution centers around the optimal prediction (i.e., 1) with a median value of XX [XX,XX].
+The variance of the distribution indicates that, while most participants were near optimal in their cue combination, part of the participant tended to rely predominantly on the auditory modality and another part tended to rely predominantly on the visual modality.
+
+[Here compare to random model to see whether the resuls were due to measurement errors or to genuine betwee-subject variability, but isn't that what the CI around the median show?]
+
+## Discussion
+
+This experiment was an extension to Experiment 1.
+Through collecting larger-size data per subject, we were able to analyze the cue combination optimlity, not only at the population level, but also at the individual level.
+The population-level analysis replicated the results of Experiment 1.
+The individual-level analysis showed that participants' performance approximated a normal distribution centered around the optimal combination.
+The large variance of this distribution indicate that some participants tend to over-rely on the auditory modality and others tend to over-rely on the visual modality.
+
+In Experiment 1 and Experiment 1 bis, we tested word recognition when there was multimodal uncertainty in terms of category membership and inherent perceptual noise, only.
+In real life, however, both sound and visual tokens can undergo distortions due to noisy factors in the environment (e.g., car noise in the background, blurry vision in a foggy weather).
 In Experiment 2 and 3, we explore this additional level of uncertainty.
@@
 ## Results and analysis
-
-```{r echo=FALSE}
-
-#Bootstrap sample parameters
-
-lmfit <- function(data, indices) {
-
-  myd = data[indices, ]
-
-  s_data <- myd %>%
-    filter(condition == "sound")
-
-  v_data <- myd %>%
-    filter(condition == "concept")
-
-  j_data <- myd %>%
-    filter(condition == "joint")
-
-  s_nl <- nls(answer ~ 1/(1+(1-e)*exp((-4/vrA)*sound_dist+(8/vrA))), data=s_data, start = list(e=0, vrA=2), nls.control(warnOnly = TRUE))
-
- c_nl <- nls(answer ~ 1/(1+(1-e)*exp((-4/vrV)*concept_dist+(8/vrV))), data=v_data, start = list(e=0, vrV=2), nls.control(warnOnly = TRUE))
-
- j_nl <- nls(answer ~ 1/(1+(1-e)*exp((-4/vrA_j)*sound_dist+(-4/vrV_j)*concept_dist+(8/vrA_j)+(8/vrV_j))), data=j_data, start = list(e=0, vrA_j=2, vrV_j=2), nls.control(warnOnly = TRUE))
-
-  s_va <- coef(s_nl)["vrA"]
-  s_e <- coef(s_nl)["e"]
-
-  v_va <- coef(c_nl)["vrV"]
-  v_e <- coef(c_nl)["e"]
-
-  decision_ideal=v_va/s_va
-
-  j_va_s=coef(j_nl)["vrA_j"]
-  j_va_v=coef(j_nl)["vrV_j"]
-  j_e=coef(j_nl)["e"]
-
-  decision_fit=j_va_v/j_va_s
-
-  preference = decision_fit/decision_ideal
-
-  MyBoot=c(s_va, s_e, v_va, v_e, j_va_s, j_va_v, j_e, decision_ideal, decision_fit, preference)
-
-  return(MyBoot)
-
-  }
-
-#results2 <- boot(data=exp2_good, statistic = lmfit, R = 10000)
-
-#dataSave2 <- data.frame(matrix(ncol = 5, nrow = 0))
-#data_names <- c("variable", "estimate", "lower","upper", "Experiment")
-#colnames(dataSave2) <- data_names
-
-#Auditory variance:
-#audVar=boot.ci(results2, index = 1, type = c("bca"), conf = 0.95)
-
-#v1 <- data.frame('audVar', as.numeric(audVar$t0), as.numeric(audVar$bca[4]), as.numeric(audVar$bca[5]), 'Exp2')
-#  colnames(v1) <- data_names
-
-#Auditory bias:
-#audBias=boot.ci(results2, index = 2, type = c("bca"), conf = 0.95)
-
-#v2 <- data.frame('audBias', as.numeric(audBias$t0), as.numeric(audBias$bca[4]), as.numeric(audBias$bca[5]), 'Exp2')
-#  colnames(v2) <- data_names
-
-#Visual variance:
-#visVar=boot.ci(results2, index = 3, type = c("bca"), conf = 0.95)
-
-#v3 <- data.frame('visVar', as.numeric(visVar$t0), as.numeric(visVar$bca[4]), as.numeric(visVar$bca[5]), 'Exp1')
-#  colnames(v3) <- data_names
-
-#Visual bias:
-#visBias=boot.ci(results2, index = 4, type = c("bca"), conf = 0.95)
-
-#v4 <- data.frame('visBias', as.numeric(visBias$t0), as.numeric(visBias$bca[4]), as.numeric(visBias$bca[5]), 'Exp2')
-#colnames(v4) <- data_names
-
-#Bimodal Auditory variance:
-#audVarBi=boot.ci(results2, index = 5, type = c("bca"), conf = 0.95)
-
-#v5 <- data.frame('audVarBi', as.numeric(audVarBi$t0), as.numeric(audVarBi$bca[4]), as.numeric(audVarBi$bca[5]), 'Exp2')
-#  colnames(v5) <- data_names
-#
-
-#Bimodal Visual variance:
-#visVarBi=boot.ci(results2, index = 6, type = c("bca"), conf = 0.95)
-
-#v6 <- data.frame('visVarBi', as.numeric(visVarBi$t0), as.numeric(visVarBi$bca[4]), as.numeric(visVarBi$bca[5]), 'Exp2')
-#  colnames(v6) <- data_names
-
-#Bimodal bias:
-#BiasBi=boot.ci(results2, index = 7, type = c("bca"), conf = 0.95)
-
-#v7 <- data.frame('BiasBi', as.numeric(BiasBi$t0), as.numeric(BiasBi$bca[4]), as.numeric(BiasBi$bca[5]), 'Exp2')
-#  colnames(v7) <- data_names
-
-#Ideal modality wieghing
-#prefIdeal=boot.ci(results2, index = 8, type = c("bca"), conf = 0.95)
-
-#v8 <- data.frame('prefIdeal', as.numeric(prefIdeal$t0), as.numeric(prefIdeal$bca[4]), as.numeric(prefIdeal$bca[5]), 'Exp2')
-#  colnames(v8) <- data_names
-
-#fit modality wieghing
-#prefFit=boot.ci(results2, index = 9, type = c("bca"), conf = 0.95)
-
-#v9 <- data.frame('prefFit', as.numeric(prefFit$t0), as.numeric(prefFit$bca[4]), as.numeric(prefFit$bca[5]), 'Exp2')
-#  colnames(v9) <- data_names
-
-#Modality bias 
-#bias=boot.ci(results2, index = 10, type = c("bca"), conf = 0.95)
-
-#v10 <- data.frame('bias', as.numeric(bias$t0), as.numeric(bias$bca[4]), as.numeric(bias$bca[5]), 'Exp2')
-#  colnames(v10) <- data_names
-
-#dataSave2 <- bind_rows(dataSave2, v1, v2, v3, v4, v5, v6, v7, v8, v9, v10)
-
-#feather::write_feather(dataSave2, "dataExp2.feather")
-
-dataSave2 <- feather::read_feather("dataExp2.feather")
-
-#Extract values 
-audVar_val=dataSave2$estimate[which(dataSave2$variable == "audVar")]
-audVar_ci1=dataSave2$lower[which(dataSave2$variable == "audVar")]
-audVar_ci2=dataSave2$upper[which(dataSave2$variable == "audVar")]
-
-audBias_val=-dataSave2$estimate[which(dataSave2$variable == "audBias")]
-audBias_ci1=-dataSave2$upper[which(dataSave2$variable == "audBias")]
-audBias_ci2=-dataSave2$lower[which(dataSave2$variable == "audBias")]
-
-visVar_val=dataSave2$estimate[which(dataSave2$variable == "visVar")]
-visVar_ci1=dataSave2$lower[which(dataSave2$variable == "visVar")]
-visVar_ci2=dataSave2$upper[which(dataSave2$variable == "visVar")]
-
-visBias_val=-dataSave2$estimate[which(dataSave2$variable == "visBias")]
-visBias_ci1=-dataSave2$upper[which(dataSave2$variable == "visBias")]
-visBias_ci2=-dataSave2$lower[which(dataSave2$variable == "visBias")]
-
-audVarBi_val=dataSave2$estimate[which(dataSave2$variable == "audVarBi")]
-audVarBi_ci1=dataSave2$lower[which(dataSave2$variable == "audVarBi")]
-audVarBi_ci2=dataSave2$upper[which(dataSave2$variable == "audVarBi")]
-
-visVarBi_val=dataSave2$estimate[which(dataSave2$variable == "visVarBi")]
-visVarBi_ci1=dataSave2$lower[which(dataSave2$variable == "visVarBi")]
-visVarBi_ci2=dataSave2$upper[which(dataSave2$variable == "visVarBi")]
-
-BiasBi_val=-dataSave2$estimate[which(dataSave2$variable == "BiasBi")]
-BiasBi_ci1=-dataSave2$upper[which(dataSave2$variable == "BiasBi")]
-BiasBi_ci2=-dataSave2$lower[which(dataSave2$variable == "BiasBi")]
-
-prefIdeal_val_2=dataSave2$estimate[which(dataSave2$variable == "prefIdeal")]
-prefIdeal_ci1_2=dataSave2$lower[which(dataSave2$variable == "prefIdeal")]
-prefIdeal_ci2_2=dataSave2$upper[which(dataSave2$variable == "prefIdeal")]
-
-prefFit_val_2=dataSave2$estimate[which(dataSave2$variable == "prefFit")]
-prefFit_ci1_2=dataSave2$lower[which(dataSave2$variable == "prefFit")]
-prefFit_ci2_2=dataSave2$upper[which(dataSave2$variable == "prefFit")]
-
-bias_val_2=dataSave2$estimate[which(dataSave2$variable == "bias")]
-bias_ci1_2=dataSave2$lower[which(dataSave2$variable == "bias")]
-bias_ci2_2=dataSave2$upper[which(dataSave2$variable == "bias")]
-
-```
 
@@
 
-```{r echo=FALSE}
-
-#Bootstrap sample parameters
-
-lmfit <- function(data, indices) {
-
-  myd = data[indices, ]
-
-  s_data <- myd %>%
-    filter(condition == "sound")
-
-  v_data <- myd %>%
-    filter(condition == "concept")
-
-  j_data <- myd %>%
-    filter(condition == "joint")
-
-  s_nl <- nls(answer ~ 1/(1+(1-e)*exp((-4/vrA)*sound_dist+(8/vrA))), data=s_data, start = list(e=0, vrA=2), nls.control(warnOnly = TRUE))
-
- c_nl <- nls(answer ~ 1/(1+(1-e)*exp((-4/vrV)*concept_dist+(8/vrV))), data=v_data, start = list(e=0, vrV=2), nls.control(warnOnly = TRUE))
-
- j_nl <- nls(answer ~ 1/(1+(1-e)*exp((-4/vrA_j)*sound_dist+(-4/vrV_j)*concept_dist+(8/vrA_j)+(8/vrV_j))), data=j_data, start = list(e=0, vrA_j=2, vrV_j=2), nls.control(warnOnly = TRUE))
-
-  s_va <- coef(s_nl)["vrA"]
-  s_e <- coef(s_nl)["e"]
-
-  v_va <- coef(c_nl)["vrV"]
-  v_e <- coef(c_nl)["e"]
-
-  decision_ideal=v_va/s_va
-
-  j_va_s=coef(j_nl)["vrA_j"]
-  j_va_v=coef(j_nl)["vrV_j"]
-  j_e=coef(j_nl)["e"]
-
-  decision_fit=j_va_v/j_va_s
-
-  preference = decision_fit/decision_ideal
-
-  MyBoot=c(s_va, s_e, v_va, v_e, j_va_s, j_va_v, j_e, decision_ideal, decision_fit, preference)
-
-  return(MyBoot)
-
-  }
-
-#results3 <- boot(data=exp3_good, statistic = lmfit, R = 10000)
-
-#dataSave3 <- data.frame(matrix(ncol = 5, nrow = 0))
-#data_names <- c("variable", "estimate", "lower","upper", "Experiment")
-#colnames(dataSave3) <- data_names
-
-#Auditory variance:
-#audVar=boot.ci(results3, index = 1, type = c("bca"), conf = 0.95)
-
-#v1 <- data.frame('audVar', as.numeric(audVar$t0), as.numeric(audVar$bca[4]), as.numeric(audVar$bca[5]), 'Exp3')
-#  colnames(v1) <- data_names
-
-#Auditory bias:
-#audBias=boot.ci(results3, index = 2, type = c("bca"), conf = 0.95)
-
-#v2 <- data.frame('audBias', as.numeric(audBias$t0), as.numeric(audBias$bca[4]), as.numeric(audBias$bca[5]), 'Exp3')
-#  colnames(v2) <- data_names
-
-#Visual variance:
-#visVar=boot.ci(results3, index = 3, type = c("bca"), conf = 0.95)
-
-#v3 <- data.frame('visVar', as.numeric(visVar$t0), as.numeric(visVar$bca[4]), as.numeric(visVar$bca[5]), 'Exp3')
-#  colnames(v3) <- data_names
-
-#Visual bias:
-#visBias=boot.ci(results3, index = 4, type = c("bca"), conf = 0.95)
-
-#v4 <- data.frame('visBias', as.numeric(visBias$t0), as.numeric(visBias$bca[4]), as.numeric(visBias$bca[5]), 'Exp3')
-#  colnames(v4) <- data_names
-
-#Bimodal Auditory variance:
-#audVarBi=boot.ci(results3, index = 5, type = c("bca"), conf = 0.95)
-
-#v5 <- data.frame('audVarBi', as.numeric(audVarBi$t0), as.numeric(audVarBi$bca[4]), as.numeric(audVarBi$bca[5]), 'Exp3')
-#  colnames(v5) <- data_names
-
-#Bimodal Visual variance:
-#visVarBi=boot.ci(results3, index = 6, type = c("bca"), conf = 0.95)
-
-#v6 <- data.frame('visVarBi', as.numeric(visVarBi$t0), as.numeric(visVarBi$bca[4]), as.numeric(visVarBi$bca[5]), 'Exp3')
-#  colnames(v6) <- data_names
-
-#Bimodal bias:
-#BiasBi=boot.ci(results3, index = 7, type = c("bca"), conf = 0.95)
-
-#v7 <- data.frame('BiasBi', as.numeric(BiasBi$t0), as.numeric(BiasBi$bca[4]), as.numeric(BiasBi$bca[5]), 'Exp3')
-#  colnames(v7) <- data_names
-
-#Ideal modality wieghing
-#prefIdeal=boot.ci(results3, index = 8, type = c("bca"), conf = 0.95)
-
-#v8 <- data.frame('prefIdeal', as.numeric(prefIdeal$t0), as.numeric(prefIdeal$bca[4]), as.numeric(prefIdeal$bca[5]), 'Exp3')
-#  colnames(v8) <- data_names
-
-#fit modality wieghing
-#prefFit=boot.ci(results3, index = 9, type = c("bca"), conf = 0.95)
-
-#v9 <- data.frame('prefFit', as.numeric(prefFit$t0), as.numeric(prefFit$bca[4]), as.numeric(prefFit$bca[5]), 'Exp3')
-#  colnames(v9) <- data_names
-
-#Modality bias 
-#bias=boot.ci(results3, index = 10, type = c("bca"), conf = 0.95)
-
-#v10 <- data.frame('bias', as.numeric(bias$t0), as.numeric(bias$bca[4]), as.numeric(bias$bca[5]), 'Exp3')
-#  colnames(v10) <- data_names
-
-#dataSave3 <- bind_rows(dataSave3, v1, v2, v3, v4, v5, v6, v7, v8, v9, v10)
-#feather::write_feather(dataSave3, "dataExp3.feather")
-
-dataSave3 <- feather::read_feather("dataExp3.feather")
-
-#Extract values 
-audVar_val=dataSave3$estimate[which(dataSave3$variable == "audVar")]
-audVar_ci1=dataSave3$lower[which(dataSave3$variable == "audVar")]
-audVar_ci2=dataSave3$upper[which(dataSave3$variable == "audVar")]
-
-audBias_val=-dataSave3$estimate[which(dataSave3$variable == "audBias")]
-audBias_ci1=-dataSave3$upper[which(dataSave3$variable == "audBias")]
-audBias_ci2=-dataSave3$lower[which(dataSave3$variable == "audBias")]
-
-visVar_val=dataSave3$estimate[which(dataSave3$variable == "visVar")]
-visVar_ci1=dataSave3$lower[which(dataSave3$variable == "visVar")]
-visVar_ci2=dataSave3$upper[which(dataSave3$variable == "visVar")]
-
-visBias_val=-dataSave3$estimate[which(dataSave3$variable == "visBias")]
-visBias_ci1=-dataSave3$upper[which(dataSave3$variable == "visBias")]
-visBias_ci2=-dataSave3$lower[which(dataSave3$variable == "visBias")]
-
-audVarBi_val=dataSave3$estimate[which(dataSave3$variable == "audVarBi")]
-audVarBi_ci1=dataSave3$lower[which(dataSave3$variable == "audVarBi")]
-audVarBi_ci2=dataSave3$upper[which(dataSave3$variable == "audVarBi")]
-
-visVarBi_val=dataSave3$estimate[which(dataSave3$variable == "visVarBi")]
-visVarBi_ci1=dataSave3$lower[which(dataSave3$variable == "visVarBi")]
-visVarBi_ci2=dataSave3$upper[which(dataSave3$variable == "visVarBi")]
-
-BiasBi_val=-dataSave3$estimate[which(dataSave3$variable == "BiasBi")]
-BiasBi_ci1=-dataSave3$upper[which(dataSave3$variable == "BiasBi")]
-BiasBi_ci2=-dataSave3$lower[which(dataSave3$variable == "BiasBi")]
-
-prefIdeal_val_3=dataSave3$estimate[which(dataSave3$variable == "prefIdeal")]
-prefIdeal_ci1_3=dataSave3$lower[which(dataSave3$variable == "prefIdeal")]
-prefIdeal_ci2_3=dataSave3$upper[which(dataSave3$variable == "prefIdeal")]
-
-prefFit_val_3=dataSave3$estimate[which(dataSave3$variable == "prefFit")]
-prefFit_ci1_3=dataSave3$lower[which(dataSave3$variable == "prefFit")]
-prefFit_ci2_3=dataSave3$upper[which(dataSave3$variable == "prefFit")]
-
-bias_val_3=dataSave3$estimate[which(dataSave3$variable == "bias")]
-bias_ci1_3=dataSave3$lower[which(dataSave3$variable == "bias")]
-bias_ci2_3=dataSave3$upper[which(dataSave3$variable == "bias")]
-
-```
-
 ```{r echo=FALSE, warning = FALSE}
@@
 
-# Decision threshold
-classif = function (x, A) {
-    2*A+2-A*x
-}
-
-pref_data <- data.frame(matrix(ncol = 7, nrow = 0))
-names <- c("Auditory", "Visual", "Optimal", "Auditory bias", "Visual bias", "Fit", "Experiment")
-colnames(pref_data) <- names
-
-x=seq(-1,5,0.02)
-
-pref_exp1 <- data.frame(x, x, 
-                        classif(x, prefIdeal_val_1),
-                        classif(x, 2*prefIdeal_val_1),
-                        classif(x, 0.5*prefIdeal_val_1),
-                        classif(x, prefFit_val_1),
-                        'Exp1')
-colnames(pref_exp1) <- names
-
-pref_exp2 <- data.frame(x, x, 
-                        classif(x, prefIdeal_val_2),
-                        classif(x, 2*prefIdeal_val_2),
-                        classif(x, 0.5*prefIdeal_val_2),
-                        classif(x, prefFit_val_2),
-                        'Exp2')
-colnames(pref_exp2) <- names
-
-pref_exp3 <- data.frame(x, x, 
-                        classif(x, prefIdeal_val_3),
-                        classif(x, 2*prefIdeal_val_3),
-                        classif(x, 0.5*prefIdeal_val_3),
-                        classif(x, prefFit_val_3),
-                        'Exp3')
-colnames(pref_exp3) <- names
-
-pref_data <- bind_rows(pref_data, pref_exp1, pref_exp2, pref_exp3) %>%
-  gather(model, value, Optimal:Fit)
-
-pref_data$model <- factor(pref_data$model, levels = c("Optimal", "Fit","Auditory bias", "Visual bias"))
+pref_data <- feather::read_feather("../Data_and_analysis/pref_data.feather")
 
@@
 
+dataSave1 <- feather::read_feather("../Data_and_analysis/dataExp1.feather")
+dataSave2 <- feather::read_feather("../Data_and_analysis/dataExp2.feather")
+dataSave3 <- feather::read_feather("../Data_and_analysis/dataExp3.feather")
+
+bias_val_1=dataSave1$estimate[which(dataSave1$variable == "bias")]
+bias_ci1_1=dataSave1$lower[which(dataSave1$variable == "bias")]
+bias_ci2_1=dataSave1$upper[which(dataSave1$variable == "bias")]
+
+bias_val_2=dataSave2$estimate[which(dataSave2$variable == "bias")]
+bias_ci1_2=dataSave2$lower[which(dataSave2$variable == "bias")]
+bias_ci2_2=dataSave2$upper[which(dataSave2$variable == "bias")]
+
+bias_val_3=dataSave3$estimate[which(dataSave3$variable == "bias")]
+bias_ci1_3=dataSave3$lower[which(dataSave3$variable == "bias")]
+bias_ci2_3=dataSave3$upper[which(dataSave3$variable == "bias")]
+
 #Modality bias
-preference = c(bias_val_1, bias_val_2, bias_val_3 )
+preference = c(bias_val_1, bias_val_2, bias_val_3)
 experiment =c("Exp 1 \n", "Exp 2", "Exp 3")
@@
        aes(x = experiment, y=preference)) +
+  geom_hline(yintercept = 1, linetype='solid', color="red", size=1)+
+  geom_hline(yintercept = 0.5, linetype=2, color="green")+
+  geom_hline(yintercept = 2, linetype=2, color="blue")+
   geom_point(size=3)+
@@
                   position = position_dodge(width = 0.1))+
-  geom_hline(yintercept = 1, linetype='solid', color="red", size=1)+
-
-  geom_hline(yintercept = 0.5, linetype=2, color="green")+
-
-  geom_hline(yintercept = 2, linetype=2, color="blue")+
-
   theme_few()+
-
   theme(aspect.ratio = 1, axis.text=element_text(size=10))+

### 2019-03-15 Writeup/ms.tex
revisions

@@
-\documentclass[english,floatsintext,man]{apa6}
-
+\documentclass[english,,man,floatsintext]{apa6}
+\usepackage{lmodern}
 \usepackage{amssymb,amsmath}
@@
     \usepackage{mathspec}
-    \usepackage{xltxtra,xunicode}
   \else
@@
   \fi
-  \defaultfontfeatures{Mapping=tex-text,Scale=MatchLowercase}
-  \newcommand{\euro}{€}
+  \defaultfontfeatures{Ligatures=TeX,Scale=MatchLowercase}
 \fi
@@
 % use microtype if available
-\IfFileExists{microtype.sty}{\usepackage{microtype}}{}
-
-% Table formatting
-\usepackage{longtable, booktabs}
+\IfFileExists{microtype.sty}{%
+\usepackage{microtype}
+\UseMicrotypeSet[protrusion]{basicmath} % disable protrusion for tt fonts
+}{}
+\usepackage{hyperref}
+\hypersetup{unicode=true,
+            pdftitle={How Optimal is Word-Referent Identification Under Multimodal Uncertainty?},
+            pdfauthor={Abdellah Fourtassi~\& Michael C. Frank},
+            pdfkeywords={Language understanding; audio-visual processing; word learning; speech
+perception; computational modeling.},
+            pdfborder={0 0 0},
+            breaklinks=true}
+\urlstyle{same}  % don't use monospace font for urls
+\ifnum 0\ifxetex 1\fi\ifluatex 1\fi=0 % if pdftex
+  \usepackage[shorthands=off,main=english]{babel}
+\else
+  \usepackage{polyglossia}
+  \setmainlanguage[]{english}
+\fi
+\usepackage{graphicx,grffile}
+\makeatletter
+\def\maxwidth{\ifdim\Gin@nat@width>\linewidth\linewidth\else\Gin@nat@width\fi}
+\def\maxheight{\ifdim\Gin@nat@height>\textheight\textheight\else\Gin@nat@height\fi}
+\makeatother
+% Scale images if necessary, so that they will not overflow the page
+% margins by default, and it is still possible to overwrite the defaults
+% using explicit options in \includegraphics[width, height, ...]{}
+\setkeys{Gin}{width=\maxwidth,height=\maxheight,keepaspectratio}
+\IfFileExists{parskip.sty}{%
+\usepackage{parskip}
+}{% else
+\setlength{\parindent}{0pt}
+\setlength{\parskip}{6pt plus 2pt minus 1pt}
+}
+\setlength{\emergencystretch}{3em}  % prevent overfull lines
+\providecommand{\tightlist}{%
+  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}
+\setcounter{secnumdepth}{0}
+% Redefines (sub)paragraphs to behave more like sections
+\ifx\paragraph\undefined\else
+\let\oldparagraph\paragraph
+\renewcommand{\paragraph}[1]{\oldparagraph{#1}\mbox{}}
+\fi
+\ifx\subparagraph\undefined\else
+\let\oldsubparagraph\subparagraph
+\renewcommand{\subparagraph}[1]{\oldsubparagraph{#1}\mbox{}}
+\fi
+
+%%% Use protect on footnotes to avoid problems with footnotes in titles
+\let\rmarkdownfootnote\footnote%
+\def\footnote{\protect\rmarkdownfootnote}
+
+  \title{How Optimal is Word-Referent Identification Under Multimodal
+Uncertainty?}
+    \author{Abdellah Fourtassi\textsuperscript{1}~\& Michael C.
+Frank\textsuperscript{1}}
+    \date{}
+
+\shorttitle{Word Identification Under Multimodal Uncertainty}
+\affiliation{
+\vspace{0.5cm}
+\textsuperscript{1} Department of Psychology, Stanford University}
+\keywords{Language understanding; audio-visual processing; word learning; speech perception; computational modeling.}
+\usepackage{csquotes}
+\usepackage{upgreek}
+\captionsetup{font=singlespacing,justification=justified}
+
+\usepackage{longtable}
 \usepackage{lscape}
-% \usepackage[counterclockwise]{rotating}   % Landscape page setup for large tables
-\usepackage{multirow}		% Table styling
-\usepackage{tabularx}		% Control Column width
-\usepackage[flushleft]{threeparttable}	% Allows for three part tables with a specified notes section
-\usepackage{threeparttablex}            % Lets threeparttable work with longtable
-
-% Create new environments so endfloat can handle them
-% \newenvironment{ltable}
-%   {\begin{landscape}\begin{center}\begin{threeparttable}}
-%   {\end{threeparttable}\end{center}\end{landscape}}
-
-\newenvironment{lltable}
-  {\begin{landscape}\begin{center}\begin{ThreePartTable}}
-  {\end{ThreePartTable}\end{center}\end{landscape}}
-
-% The following enables adjusting longtable caption width to table width
-% Solution found at http://golatex.de/longtable-mit-caption-so-breit-wie-die-tabelle-t15767.html
+\usepackage{multirow}
+\usepackage{tabularx}
+\usepackage[flushleft]{threeparttable}
+\usepackage{threeparttablex}
+
+\newenvironment{lltable}{\begin{landscape}\begin{center}\begin{ThreePartTable}}{\end{ThreePartTable}\end{center}\end{landscape}}
+
 \makeatletter
@@
 \setlength{\longtablewidth}{1in}
-\newcommand\getlongtablewidth{%
- \begingroup
-  \ifcsname LT@\roman{LT@tables}\endcsname
-  \global\longtablewidth=0pt
-  \renewcommand\LT@entry[2]{\global\advance\longtablewidth by ##2\relax\gdef\LastLTentrywidth{##2}}%
-  \@nameuse{LT@\roman{LT@tables}}%
-  \fi
-\endgroup}
-
-\ifxetex
-  \usepackage[setpagesize=false, % page size defined by xetex
-              unicode=false, % unicode breaks when used with xetex
-              xetex]{hyperref}
-\else
-  \usepackage[unicode=true]{hyperref}
-\fi
-\hypersetup{breaklinks=true,
-            pdfauthor={},
-            pdftitle={How Optimal is Word-Referent Identification Under Multimodal Uncertainty?},
-            colorlinks=true,
-            citecolor=blue,
-            urlcolor=blue,
-            linkcolor=black,
-            pdfborder={0 0 0}}
-\urlstyle{same}  % don't use monospace font for urls
-
-\setlength{\parindent}{0pt}
-%\setlength{\parskip}{0pt plus 0pt minus 0pt}
-
-\setlength{\emergencystretch}{3em}  % prevent overfull lines
-
-\ifxetex
-  \usepackage{polyglossia}
-  \setmainlanguage{}
-\else
-  \usepackage[english]{babel}
-\fi
-
-% Manuscript styling
-\captionsetup{font=singlespacing,justification=justified}
-\usepackage{csquotes}
-\usepackage{upgreek}
-
- % Line numbering
+\newcommand{\getlongtablewidth}{\begingroup \ifcsname LT@\roman{LT@tables}\endcsname \global\longtablewidth=0pt \renewcommand{\LT@entry}[2]{\global\advance\longtablewidth by ##2\relax\gdef\LastLTentrywidth{##2}}\@nameuse{LT@\roman{LT@tables}} \fi \endgroup}
+
 \usepackage{lineno}
+
 \linenumbers
-
-\usepackage{tikz} % Variable definition to generate author note
-
-% fix for \tightlist problem in pandoc 1.14
-\providecommand{\tightlist}{%
-  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}
-
-% Essential manuscript parts
-  \title{How Optimal is Word-Referent Identification Under Multimodal
-Uncertainty?}
-
-  \shorttitle{Word Identification Under Multimodal Uncertainty}
-
-  \author{Abdellah Fourtassi\textsuperscript{1}~\& Michael C. Frank\textsuperscript{1}}
-
-  % \def\affdep{{"", ""}}%
-  % \def\affcity{{"", ""}}%
-
-  \affiliation{
-    \vspace{0.5cm}
-          \textsuperscript{1} Department of Psychology, Stanford University  }
-
-  \authornote{
-    Abdellah Fourtassi
+\usepackage[sortcites=false,sorting=none]{biblatex}
+
+\authornote{ Abdellah Fourtassi
 
@@
 Fourtassi, Postal address. E-mail:
-    \href{mailto:afourtas@stanford.edu}{\nolinkurl{afourtas@stanford.edu}}
-  }
-
-  \abstract{Identifying a spoken word in a referential context requires both the
+\href{mailto:afourtas@stanford.edu}{\nolinkurl{afourtas@stanford.edu}}}
+
+\abstract{
+Identifying a spoken word in a referential context requires both the
 ability to integrate multimodal input and the ability to reason under
@@
 under uncertainty. Moreover it offers a first step towards a model that
-accounts for form-meaning synergies in early word learning.}
-  \keywords{Language understanding; audio-visual processing; word learning; speech
-perception; computational modeling. \\
+accounts for form-meaning synergies in early word learning.
 
@@
 
-  \usepackage[sortcites=false,sorting=none]{biblatex}
-
 \usepackage{amsthm}
-\newtheorem{theorem}{Theorem}
-\newtheorem{lemma}{Lemma}
+\newtheorem{theorem}{Theorem}[section]
+\newtheorem{lemma}{Lemma}[section]
 \theoremstyle{definition}
-\newtheorem{definition}{Definition}
-\newtheorem{corollary}{Corollary}
-\newtheorem{proposition}{Proposition}
+\newtheorem{definition}{Definition}[section]
+\newtheorem{corollary}{Corollary}[section]
+\newtheorem{proposition}{Proposition}[section]
 \theoremstyle{definition}
-\newtheorem{example}{Example}
+\newtheorem{example}{Example}[section]
 \theoremstyle{definition}
-\newtheorem{exercise}{Exercise}
+\newtheorem{exercise}{Exercise}[section]
 \theoremstyle{remark}
@@
 \begin{document}
-
 \maketitle
 
-\setcounter{secnumdepth}{0}
+\begin{verbatim}
+## Warning: package 'bindrcpp' was built under R version 3.4.4
+\end{verbatim}
 
@@
 statistical power to fit a different model for each individual
-participant.\footnote{We had a relatively high number of trials spanning
-  all possible audio-visual matchings. Getting enough data points per
-  trial per participant would have required running the online
-  experimental for a much longer time (more than an hour). This could
-  have increased significantly the dropout rate and possibly affected
-  the quality of the data collected online.} Instead, models were
-constructed with data collapsed across all participants. That being
-said, we will also analyze the distribution of individual responses. The
-fit was done with a nonlinear least squares regression using the NLS
-package in R (Bates \& Watts, 1988). We computed the values of the
-parameters, as well as their 95\% confidence intervals, through
-non-parametric bootstrap (using 10000 iterations).
+participant. Instead, models were constructed with data collapsed across
+all participants. The fit was done with a nonlinear least squares
+regression using the NLS package in R (Bates \& Watts, 1988). We
+computed the values of the parameters, as well as their 95\% confidence
+intervals, through non-parametric bootstrap (using 10000 iterations).
 
@@
 
-As we noted earlier, the model addresses the question of optimality at
-the population level. However, it is important to know how individual
-responses are distributed. In fact, one could think of an extreme case
-where optimality at the population level would be misleading. Imagine,
-for instance, that in the bimodal condition half the participants relied
+As we noted earlier, we did not have enough statistical power to fit a
+different model for each individual participant. Instead, we fit one
+model using the data aggregated across all participants. This analysis
+is informative of behavior at the population level, only. However,
+optimality at the population level could be misleading. Imagine, for
+instance, that in the bimodal condition half the participants relied
 exclusively on the visual modality, whereas the other half relied
@@
 aggregate behavior which appears optimal, but this optimality would be
-spurious.
-
-To examine this possibility, we consider the distribution of individual
-cross-modal weighting in the bimodal condition (i.e.,
-\(\frac{\sigma^2_{Vb}}{\sigma^2_{Ab}}\)). Using a factor of 10 as a
-cut-off, we found that 5 participants relied almost exclusively on the
-visual modality, and 12 relied almost exclusively on the auditory
-modality. The percentage of both cases was relatively small compared to
-the total number of participants (21.25\%). When these outliers were
-removed, the distribution had a rather unimodal shape
-(Figure~\ref{fig:individual}). This finding indicates that the
-population's near optimality is not spurious, but based mostly on
-genuine cue combination at the individual level.
-
-As a second analysis, we asked whether the observed variance in the
-individual distribution was due to mere sampling errors or whether it
-corresponded to a real between-subject variability. We simulated
-individual responses from the posterior distribution whose parameters
-were fit to the population as a whole (i.e., the descriptive posterior).
-The resulting distribution is shown in Figure~\ref{fig:individual}. For
-ease of comparison, the simulated distribution was superimposed to the
-real distribution. We found that the real distribution had a standard
-deviation of \(sd=\) 2.24 which was larger than that of the simulated
-distribution (\(sd=\) 1.14), indicating that there was real
-between-subject variation beyond sampling errors. This finding means
-that the participants varied in terms of how they weighted modalities:
-Compared to the predictions of the population-level model, some
-participants relied more on the auditory modality, whereas others relied
-more on the visual modality.
-
-In Experiment 1, we tested word recognition when there was multimodal
-uncertainty in terms of category membership only. In real life, however,
-tokens can undergo distortions due to noisy factors in the environment
-(e.g., car noise in the background, blurry vision in a foggy weather).
-In Experiment 2 and 3, we explore this additional level of uncertainty.
+spurious. This, in the experiemnt below, we test the cue integration
+strategy at the individual level. To this end, we increase the
+statistical power by extending the length of the experiment, allowing us
+to collect the number of datapoints necessary to fit the models for each
+participant.
+
+\section{Experiment 1 bis}\label{experiment-1-bis}
+
+\subsubsection{Participants}\label{participants-1}
+
+We recruited a planned sample of N=XX participants from Amazon
+Mechanical Turk. Only participants with US IP addresses and a task
+approval rate above 99\% were allowed to participate. They were paid at
+an hourly rate of \$6/hour. Participants were excluded if they reported
+having experienced a technical problem of any sort during the online
+experiment (N=XX), or if they had less than 75\% accurate responses on
+the unambiguous training trials (N=XX). The final sample consisted of N
+= XX participants. {[}I should also add how many participants I excluded
+because their models did not converge{]}. All participants provided
+informed consent before taking the
+experiment.\footnote{The sample size and exclusion criteria were specified in the pre-registration at https://osf.io/h7mzp/.}
+
+\subsubsection{Stimuli}\label{stimuli-1}
+
+We used the same stimuli as in Experiment 1.
+
+\subsubsection{Design and Procedure}\label{design-and-procedure-1}
+
+The design and procedure were similar to Experiment 1. The only
+difference was that we increased the number of datapoints elicited per
+subject from 70 to 300.
+
+\subsection{Results and analysis}\label{results-and-analysis-1}
+
+\subsubsection{Unimodal conditions}\label{unimodal-conditions-2}
+
+We fit both population-level models to the aggregated data (as in
+Experiment 1), and individual models to data from each participant. For
+the populaton-level models, the results (shown in
+Figure~\ref{fig:unimodal}) replicated the results obtained in Experiment
+1. As for the individual-level analysis, the models showed there to be
+between-subject variability as seen in the paramters's distribution in
+Figure XX.
+
+\subsubsection{Bimodal condition and Cue combination
+models}\label{bimodal-condition-and-cue-combination-models}
+
+We first generated poupulation-level normative and descriptive models.
+As shown in Figure~\ref{fig:bimodal}, the predicted patterns of these
+models mirrored closely the results obtained in Experiment 1. In
+addition, the optimality analysis (i.e., done through comparing the
+optimal and descriptive models) shows that the fitted mean decision
+threshold was indisguisable form the optimal threshold, thus replicating
+the results of Experiment 1 (Figure~\ref{fig:bias} shows that).
+
+At the individual level, we computed the distribution of optimal
+weighing relative to the fitted (i.e., descriptive) weighing and we show
+this distribution in Figure XX. The distribution centers around the
+optimal prediction (i.e., 1) with a median value of XX {[}XX,XX{]}. The
+variance of the distribution indicates that, while most participants
+were near optimal in their cue combination, part of the participant
+tended to rely predominantly on the auditory modality and another part
+tended to rely predominantly on the visual modality.
+
+{[}Here compare to random model to see whether the resuls were due to
+measurement errors or to genuine betwee-subject variability, but isn't
+that what the CI around the median show?{]}
+
+\subsection{Discussion}\label{discussion-1}
+
+This experiment was an extension to Experiment 1. Through collecting
+larger-size data per subject, we were able to analyze the cue
+combination optimlity, not only at the population level, but also at the
+individual level. The population-level analysis replicated the results
+of Experiment 1. The individual-level analysis showed that participants'
+performance approximated a normal distribution centered around the
+optimal combination. The large variance of this distribution indicate
+that some participants tend to over-rely on the auditory modality and
+others tend to over-rely on the visual modality.
+
+In Experiment 1 and Experiment 1 bis, we tested word recognition when
+there was multimodal uncertainty in terms of category membership and
+inherent perceptual noise, only. In real life, however, both sound and
+visual tokens can undergo distortions due to noisy factors in the
+environment (e.g., car noise in the background, blurry vision in a foggy
+weather). In Experiment 2 and 3, we explore this additional level of
+uncertainty.
 
@@
 
-\subsubsection{Participants}\label{participants-1}
+\subsubsection{Participants}\label{participants-2}
 
@@
 
-\subsection{Results and analysis}\label{results-and-analysis-1}
-
-\subsubsection{Unimodal conditions}\label{unimodal-conditions-2}
+\subsection{Results and analysis}\label{results-and-analysis-2}
+
+\subsubsection{Unimodal conditions}\label{unimodal-conditions-3}
 
@@
 
-\subsection{Discussion}\label{discussion-1}
+\subsection{Discussion}\label{discussion-2}
 
@@
 
-\subsubsection{Participants}\label{participants-2}
+\subsubsection{Participants}\label{participants-3}
 
@@
 
-\subsection{Results and analysis}\label{results-and-analysis-2}
+\subsection{Results and analysis}\label{results-and-analysis-3}
 
@@
 
-\subsubsection{Unimodal conditions}\label{unimodal-conditions-3}
+\subsubsection{Unimodal conditions}\label{unimodal-conditions-4}
 
@@
 
-\subsection{Discussion}\label{discussion-2}
+\subsection{Discussion}\label{discussion-3}
 

### 2019-03-16 Writeup/ms.tex
revisions

@@
 statistical power to fit a different model for each individual
-participant. Instead, models were constructed with data collapsed across
-all participants. The fit was done with a nonlinear least squares
-regression using the NLS package in R (Bates \& Watts, 1988). We
-computed the values of the parameters, as well as their 95\% confidence
-intervals, through non-parametric bootstrap (using 10000 iterations).
+participant (but see Experiment 4). Instead, models were constructed
+with data collapsed across all participants. The fit was done with a
+nonlinear least squares regression using the NLS package in R (Bates \&
+Watts, 1988). We computed the values of the parameters, as well as their
+95\% confidence intervals, through non-parametric bootstrap (using 10000
+iterations).
+
+\begin{table}
+
+\caption{\label{tab:param}Statistics for the dataset we used.}
+\centering
+\begin{tabular}[t]{>{\bfseries}lrrrrrrr}
+\toprule
+\multicolumn{1}{c}{} & \multicolumn{2}{c}{Auditory} & \multicolumn{2}{c}{Visual} & \multicolumn{3}{c}{Bimodal} \\
+\cmidrule(l{2pt}r{2pt}){2-3} \cmidrule(l{2pt}r{2pt}){4-5} \cmidrule(l{2pt}r{2pt}){6-8}
+Experiment & b\textsubscript{A} & Var\textsubscript{A} & b\textsubscript{V} & Var\textsubscript{V} & b\textsubscript{b} & Var\textsubscript{Ab} & Var\textsubscript{Vb}\\
+\midrule
+Experiment1 & 0.20 & 2.04 & 0.12 & 3.33 & 0.34 & 4.96 & 7.06\\
+Experiment2 & 0.18 & 4.70 & 0.24 & 3.93 & 0.38 & 9.84 & 5.21\\
+Experiment3 & 0.24 & 1.94 & -0.11 & 13.00 & 0.35 & 3.00 & 39.42\\
+Experiment4 & 0.40 & 1.92 & 0.22 & 3.24 & 0.42 & 4.17 & 7.28\\
+\bottomrule
+\end{tabular}
+\end{table}
 
@@
 
-Average categorization judgments and best fits are shown in
-Figure~\ref{fig:unimodal}. The categorization function of the auditory
+Average categorization judgments and best fits are shown in Figure
+\ref{fig:unimodal}. The categorization function of the auditory
 condition was slightly steeper than that of the visual condition,
@@
 categorically and with higher certainty than they did with the visual
-tokens. For the auditory modality, we obtained the following values:
-\(b_A=\) -0.20 {[}0.02, -0.38{]} and \(\sigma^2_A=\) 2.04 {[}1.66,
-2.53{]}. For the visual modality, we obtained \(b_V=\) -0.12 {[}0.06,
--0.28{]} and \(\sigma^2_V=\) 3.33 {[}2.83, 3.92{]}.
+tokens. The unimodal models' estimates are shown in Table
+\ref{tab:param}.
 
@@
 from only one modality) to predict data in the bimodal condition (where
-people see input from both modalities). Each point represents data form
-a particular audio-visual matching (e.g., the visual token \(v\) whose
-distance from the target \(v_t\) is \(|v-v_t|=3\), matched with the
-auditory token \(a\) whose distance from the target \(a_t\) is
-\(|a-a_t|=2\)). The visual, auditory and optimal model explained,
-respectively, 30\%, 67\%, and 89\% of total variance in mean responses.
+people see input from both modalities). Figure \ref{fig:bimodal} shows
+the models' predictions comapred to human data.
 
@@
 In the descriptive model, all parameters are fit to human responses in
-the bimodal condition. We found \(b=\) -0.34 {[}-0.28, -0.39{]},
-\(\sigma^2_{Ab}=\) 4.96 {[}4.58, 5.40{]} and \(\sigma^2_{Vb}=\) 7.06
-{[}6.40, 7.84{]}. Note that the variance of both the auditory and visual
-modalities increased compared to the unimodal conditions.
-
-\noindent The descriptive model explained 95\% of total variance.
-However, since the descriptive model was fit to the same data, there is
-a risk that this high correlation is due to overfitting. To examine this
-possibility, we cross-validated the model using half the responses to
-predict the other half (averaging across 10 random partitions). The
-predictive power of the model remained very high (\(r^2\)=0.93).
+the bimodal condition. The prediction of this model are shown in Figure
+\ref{fig:bimodal}. Note that the descriptive model explained almost all
+the variance, which makes it a reasonble proxy for human real
+performance in the bimodal condition. Thus, to determine the extent to
+which human data deviated from optimality, we comapred the descriptive
+and optimal models follwoing the procedure outlined above (section XX).
 
@@
 Models' predictions in the bimodal condition across the three experiments.
-Each point represents data form a particular audio-visual matching.
+Each point represents data form a particular audio-visual matching (corresponding to an instance from the set of 5x5 possible matchings in the audio-visual space).
 Shape represents auditory distance from the target, and color represents visual distance from the target.
@@
 
-\paragraph{Cue combination and Modality
-preference}\label{cue-combination-and-modality-preference}
-
-We next analyzed if cue combination was performed in an optimal way, or
+\subsubsection{Analysis of optimality}\label{analysis-of-optimality}
+
+We analyzed if the cue combination was performed in an optimal way, or
 if there was a systematic preference for one modality when making
-decisions in the bimodal condition. As explained above, modality
-preference can be characterized formally as a deviation from the
-decision threshold predicted by the optimal model. Figure~\ref{fig:bias}
-(top) shows both the decision threshold derived from the descriptive
-model (in black) and the decision threshold predicted by the optimal
-model (in red). The deviation from optimality is compared to two
-hypothetical cases of modality preference (dotted lines). We found that
-the descriptive and optimal decision thresholds were almost identical.
-Indeed, non-parametric resampling of the data showed no evidence of a
-deviation from the optimal prediction (Figure~\ref{fig:bias}, bottom).
+decisions in the bimodal condition. As explained above
+(\ref{fig:subOptim}), modality preference can be characterized formally
+as a deviation from the decision threshold predicted by the optimal
+model. The results in Figure \ref{fig:bias} (top) show both the decision
+threshold derived from the descriptive model (in black) and the decision
+threshold predicted by the optimal model (in red). The deviation from
+optimality is compared to two hypothetical cases of modality preference
+(dotted lines). We found that the descriptive and optimal decision
+thresholds were almost identical. Indeed, non-parametric resampling of
+the data showed no evidence of a deviation from the optimal prediction
+(Figure~\ref{fig:bias}, bottom).
 
@@
 
-Overall, we found that the optimal model explained much of the variance
-in the mean judgments, and largely more than what can be explained with
-the auditory or the visual models alone. Moreover, the high value of the
-coefficient of determination in the optimal model (\(r^2\)=0.89)
-suggests that the population was near-optimal. However, we see in
-Figure~\ref{fig:bimodal} that the mean responses deviated systematically
-from the optimal prediction in that they were slightly pulled toward
-chance (i.e., the probability 0.5). This fact is due to the increase in
-the value of the variance associated with each modality. Note however
-that, despite this increase in randomness, our analysis of modality
-preference showed that the relative values of these variances were not
-different (Figure~\ref{fig:bias}), meaning that there was no evidence
-for a modality preference. Thus, 1) There was a simultaneous increase in
-the values of the auditory and visual variances in the bimodal condition
-compared to the unimodal condition, meaning that the bimodal input lead
-to an increase in response randomness, and 2) this increased randomness
-did not affect the relative weighting of both modalities, i.e., the
-participants was weighting modalities according to the relative
-reliability predicted by the optimal model. This situation corresponds
-to the first case of sub-optimality described in
-Figure~\ref{fig:subOptim}.
+We found that the optimal model explained largely more variance than
+what can be explained with the auditory or the visual models alone. in
+addition, the high correlation with the mean human data suggests that
+the population was, overall, near-optimal. However, we see in Figure
+\ref{fig:bimodal} that the responses deviated systematically from the
+optimal prediction in that they were slightly pulled toward chance
+(i.e., the probability 0.5). This fact is due to the increase in the
+value of the variance associated with each modality (as can be noted
+from Table \ref{tab:param}). Note however that, despite this increase in
+randomness, our analysis of modality preference showed that the relative
+values of these variances were not different (Figure~\ref{fig:bias}),
+meaning that there was no evidence for a modality preference. Thus, 1)
+There was a simultaneous increase in the values of the auditory and
+visual variances in the bimodal condition compared to the unimodal
+condition, meaning that the bimodal input lead to an increase in
+response randomness, and 2) this increased randomness did not affect the
+relative weighting of both modalities, i.e., the participants was
+weighting modalities according to the relative reliability predicted by
+the optimal model. This situation corresponds to the first case of
+sub-optimality described in Figure~\ref{fig:subOptim}.
+
+In Experiment 1, we tested word recognition when there was multimodal
+uncertainty in terms of category membership and inherent perceptual
+noise, only. In real life, however, both sound and visual tokens can
+undergo distortions due to noisy factors in the environment (e.g., car
+noise in the background, blurry vision in a foggy weather). In
+Experiment 2 and 3, we explore this additional level of uncertainty.
+
+\section{Experiment 2}\label{experiment-2}
+
+In this Experiment, we explored the effect of added noise on
+performance. We tested a case where the background noise was added to
+the auditory modality. We were interested to know if participants would
+treat this new source of uncertainty as predicted by the optimal model,
+that is, according to the following weighting scheme
+\[\beta_a \propto \frac{1}{\sigma^2_{A}+\sigma^2_{N_A}}\]
+\[\beta_v \propto \frac{1}{\sigma^2_{V}}.\] The alternative hypothesis
+is that noise in one modality leads to a systematic preference for the
+non-noisy modality.
+
+\subsection{Methods}\label{methods-1}
+
+\subsubsection{Participants}\label{participants-1}
+
+A sample of 100 participants was recruited online through Amazon
+Mechanical Turk. We used the same exclusion criteria as in Experiment 1.
+7 participants were excluded because they had less than 50\% accurate
+responses on the unambiguous training trials. The final sample consisted
+of N = 93 participants.
+
+\subsubsection{Stimuli and Procedure}\label{stimuli-and-procedure}
+
+We used the same visual stimuli as in Experiment 1. We also used the
+same auditory stimuli, but we convolved each item with Brown noise of
+amplitude 1 using the free sound editor Audacity (2.1.2). The average
+signal-to-noise ratio was - 4.4 dB. The procedure was exactly the same
+as in the previous experiment, except that the test stimuli (but not the
+target) were presented with the new noisy auditory stimuli.
+
+\subsection{Results}\label{results}
+
+The analysis are similar to the analysis we did in Experiment 1.
+
+\subsubsection{Unimodal condition}\label{unimodal-condition}
+
+We fit a model for each modality. Figure \ref{fig:unimodal} shows human
+responses together with their best fits. The visual data is a
+replication of the visual data in Experiment 1. As for the auditory
+data, in contrast to Experiment 1, responses were flatter, showing more
+uncertainty.
+
+\subsubsection{Bimodal condition}\label{bimodal-condition-2}
+
+We used the values derived from the unimodal condition (Table
+\ref{tab:param}) to construct the visual, auditory and optimal models.
+In addition, we fit a descriptive model which allows us to assess real
+human performance in this condition. Figure~\ref{fig:bimodal} compares
+the predictions of these models to human responses. Note that, in
+contrast to Experiment 1, the visual model explained more variance than
+the auditory model did.
+
+\subsubsection{Analysis of optimality}\label{analysis-of-optimality-1}
+
+Figure~\ref{fig:bias} (top) shows that the participants' decision
+threshold deviated from optimality, and that this deviation was biased
+towards the visual modality (the non-noisy modality). Indeed
+non-parametric resampling of the data showed a decrease in the value of
+the slope in the descriptive model compared to the optimal model
+(Figure~\ref{fig:bias}, bottom).
+
+\subsection{Discussion}\label{discussion-1}
+
+We found, similar to Experiment 1, that the optimal model explained more
+variance than the auditory or the visual models alone (Discuss the high
+correlation, and why this not in itself a necessary but not sufficient
+indicator of optimality). We also found a similar discrepancy between
+the descriptive and optimal models as precision dropped for both the
+auditory and the visual modalities. As for the weighting scheme used by
+participants, contrary to Experiment 1 where modalities were weighted
+according to their relative reliability, we found in this experiment
+that the visual modality had a greater weight than what was expected
+from its relative reliability. This situation corresponds to the second
+case of sub-optimality described in Figure \ref{fig:subOptim}.
+
+In Experiment 2, we tested the case of added background noise to the
+auditory modality. In Experiment 3, we test the case of added noise to
+the visual modality.
+
+\section{Experiment 3}\label{experiment-3}
+
+In this Experiment, we added background noise to the visual modality.
+Similar to Experiment 2, we were interested to know if participants
+would treat this new source of uncertainty as predicted by the optimal
+model, that is, according to the following weighting scheme:
+\[\beta_a \propto \frac{1}{\sigma^2_{A}}\]
+\[\beta_v \propto \frac{1}{\sigma^2_{V}+\sigma^2_{N_V}}.\] The
+alternative hypothesis is that noise in the visual modality would lead
+to a preference for the auditory input, just like noise in the auditory
+modality lead to a preference for the visual input in Experiment 2.
+
+\subsection{Methods}\label{methods-2}
+
+\subsubsection{Participants}\label{participants-2}
+
+A planned sample of 100 participants was recruited online through Amazon
+Mechanical Turk. We used the same exclusion criteria as in both previous
+experiments. N=2 participants were excluded because they reported having
+a technical problem, and N=10 participants were excluded because they
+had less than 50\% accurate responses on the unambiguous training
+trials. The final sample consisted of N = 88 participants.
+
+\subsubsection{Stimuli and Procedure}\label{stimuli-and-procedure-1}
+
+We used the same auditory stimuli as in Experiment 1. We also used the
+same visual stimuli, but we blurred the tokens using the free image
+editor GIMP (2.8.20). We used a Gaussian blur with a
+radius\footnote{A features that modulates the intensity of the blur.} of
+10 pixels. The experimental procedure was exactly the same as in the
+previous Experiments.
+
+\subsection{Results and analysis}\label{results-and-analysis-1}
 
 \begin{figure}[!h]
-\includegraphics[width=\textwidth]{ms_files/figure-latex/individual-1} \caption{Distributions of individual values of the visual variance relative to the auditory variance in Experiment 1.
-Light color represents the real individual distribution, and dark color represents the simulated individual distribution sampled from the descriptive model.}\label{fig:individual}
+\includegraphics[width=\textwidth]{ms_files/figure-latex/bias-1} \caption{Modality preference is characterized as a deviation from the optimal decision threshold.
+A) The decision thresholds of both the optimal and the descriptive models (solid red and black lines, respectively).
+Deviation from optimality is compared to two hypothetical cases of modality preference.
+In these cases, deviation from  optimality is due to over-lying on the visual or the auditory input by a factor of 2 (green and blue dotted lines, respectively).
+B) An alternative way to represent the same data.
+Each point represents the value of the decision threshold's slope derived from the descriptive model relative to that of the optimal model (log-scaled).
+The lines represent the optimal case as well as the two hypothetical cases of modality preference.
+Error bars represent 95\% confidence intervals over the distribution obtained through non-parametric resampling.}\label{fig:bias}
 \end{figure}
 
-As we noted earlier, we did not have enough statistical power to fit a
-different model for each individual participant. Instead, we fit one
-model using the data aggregated across all participants. This analysis
-is informative of behavior at the population level, only. However,
-optimality at the population level could be misleading. Imagine, for
-instance, that in the bimodal condition half the participants relied
-exclusively on the visual modality, whereas the other half relied
-exclusively on the auditory modality. This case could still lead to an
-aggregate behavior which appears optimal, but this optimality would be
-spurious. This, in the experiemnt below, we test the cue integration
-strategy at the individual level. To this end, we increase the
-statistical power by extending the length of the experiment, allowing us
-to collect the number of datapoints necessary to fit the models for each
-participant.
-
-\section{Experiment 1 bis}\label{experiment-1-bis}
-
-\subsubsection{Participants}\label{participants-1}
+\subsubsection{Unimodal conditions}\label{unimodal-conditions-2}
+
+For the auditory modality, our parameter estimates were. For the visual
+modality. Figure~\ref{fig:unimodal} shows responses in the unimodal
+conditions as well as the corresponding fits. The auditory data is a
+replication of the auditory data in Experiment 1. As for the visual
+data, we found that, in contrast to Experiment 1 and 2, responses were
+flatter, showing much more uncertainty.
+
+\subsubsection{Bimodal condition}\label{bimodal-condition-3}
+
+\paragraph{Normative models}\label{normative-models-1}
+
+Figure~\ref{fig:bimodal} compares the predictions of the visual,
+auditory and optimal models to human responses. \#\#\#\# Descriptive
+model Cross-validation using half the responses to predict the other
+half yielded \(r^2=\)
+
+\paragraph{Modality preferences}\label{modality-preferences}
+
+Participants' decision threshold suggested a preference for the auditory
+modality (the non-noisy modality). Indeed non-parametric resampling of
+the data showed an increase in the value of the slope in the descriptive
+model compared to the optimal model (Figure~\ref{fig:bias}).
+
+\subsection{Discussion}\label{discussion-2}
+
+We found that the optimal model accounted for almost all the variance.
+However, whereas in previous experiments the optimal model explained
+more variance than the auditory or the visual models, here the auditory
+model explained at least as much variance. Thus, though participants
+were still sensitive to variation in the noisy visual data in the
+unimodal condition, they tended to ignore this information in the
+bimodal condition, and relied almost exclusively on the non-noisy
+auditory modality. The reason why we saw this (floor) effect when we
+added noise to the visual modality (Experiment 3), and not when we added
+noise to the auditory modality (Experiment 2), is the fact that our
+visual stimuli were originally perceived less categorically and with
+less certainty than the auditory stimuli. This fact made it more likely
+for the visual categorization function to become flat and uninformative
+after a few drops in precision due to noise on the one had, and to the
+additional randomness induced by the bimodal presentation on the other
+hand.
+
+The general finding corresponds to the third case of sub-optimality
+described in Figure~\ref{fig:subOptim}. Indeed, precision dropped for
+both modalities in the bimodal condition compared to the unimodal
+condition. But the drop was much greater for the visual modality,
+resulting in a much lower weight assigned to it than what is expected
+from its reliability. Therefore, just like participants over-relied on
+the visual modality when the auditory modality was noisy (Experiment 2),
+they also over-relied on the auditory modality when the visual modality
+was noisy (Experiment 3).
+
+The past three experiments studied the problem of cue combination at the
+population level --- The models were fit to the data aggregted across
+all participants. However, optimality at the population level could be
+misleading. Imagine, for instance, that in the bimodal condition half
+the participants relied exclusively on the visual modality, whereas the
+other half relied exclusively on the auditory modality. This case could
+still lead to an aggregate behavior which appears optimal, but this
+optimality would be spurious. Thus, we need to test cue integration at
+the individual level as well. As we noted earlier, in previous
+experiments we did not have enough statistical power to fit a different
+model for each participant. In Experiment 4, below, we re-ran Experiment
+1 (where we found near optimal behavior at the population level) while
+extending its length, allowing us to collect the number of datapoints
+necessary to fit the models for each participant.
+
+\section{Experiment 4}\label{experiment-4}
+
+\begin{figure}[htbp]
+\centering
+\includegraphics{ms_files/figure-latex/weights-1.pdf}
+\caption{}
+\end{figure}
+
+\subsubsection{Participants}\label{participants-3}
 
@@
 
-\subsection{Results and analysis}\label{results-and-analysis-1}
-
-\subsubsection{Unimodal conditions}\label{unimodal-conditions-2}
+\subsection{Results}\label{results-1}
 
@@
 Experiment 1), and individual models to data from each participant. For
-the populaton-level models, the results (shown in
-Figure~\ref{fig:unimodal}) replicated the results obtained in Experiment
-1. As for the individual-level analysis, the models showed there to be
-between-subject variability as seen in the paramters's distribution in
-Figure XX.
-
-\subsubsection{Bimodal condition and Cue combination
-models}\label{bimodal-condition-and-cue-combination-models}
-
-We first generated poupulation-level normative and descriptive models.
-As shown in Figure~\ref{fig:bimodal}, the predicted patterns of these
-models mirrored closely the results obtained in Experiment 1. In
-addition, the optimality analysis (i.e., done through comparing the
-optimal and descriptive models) shows that the fitted mean decision
-threshold was indisguisable form the optimal threshold, thus replicating
-the results of Experiment 1 (Figure~\ref{fig:bias} shows that).
+the populaton-level models, the results are shown in Figure
+\ref{fig:unimodal}, Figure \ref{fig:bimodal}, and Table \ref{tab:param}.
+We note that the results mirrors the patterns obtained in Experiment 1.
 
@@
 weighing relative to the fitted (i.e., descriptive) weighing and we show
-this distribution in Figure XX. The distribution centers around the
-optimal prediction (i.e., 1) with a median value of XX {[}XX,XX{]}. The
-variance of the distribution indicates that, while most participants
-were near optimal in their cue combination, part of the participant
-tended to rely predominantly on the auditory modality and another part
-tended to rely predominantly on the visual modality.
+this distribution in Figure \ref{fig:weights}. The distribution centers
+around the optimal prediction (i.e., 1) with a median value of XX
+{[}XX,XX{]}. The variance of the distribution indicates that, while most
+participants were near optimal in their cue combination, part of the
+participant tended to rely predominantly on the auditory modality and
+another part tended to rely predominantly on the visual modality.
 
@@
 
-\subsection{Discussion}\label{discussion-1}
+\subsection{Discussion}\label{discussion-3}
 
@@
 others tend to over-rely on the visual modality.
-
-In Experiment 1 and Experiment 1 bis, we tested word recognition when
-there was multimodal uncertainty in terms of category membership and
-inherent perceptual noise, only. In real life, however, both sound and
-visual tokens can undergo distortions due to noisy factors in the
-environment (e.g., car noise in the background, blurry vision in a foggy
-weather). In Experiment 2 and 3, we explore this additional level of
-uncertainty.
-
-\section{Experiment 2}\label{experiment-2}
-
-In this Experiment, we explored the effect of added noise on
-performance. We tested a case where the background noise was added to
-the auditory modality. We were interested to know if participants would
-treat this new source of uncertainty as predicted by the optimal model,
-that is, according to the following weighting scheme
-\[\beta_a \propto \frac{1}{\sigma^2_{A}+\sigma^2_{N_A}}\]
-\[\beta_v \propto \frac{1}{\sigma^2_{V}}.\] The alternative hypothesis
-is that noise in one modality leads to a systematic preference for the
-non-noisy modality.
-
-\subsection{Methods}\label{methods-1}
-
-\subsubsection{Participants}\label{participants-2}
-
-A sample of 100 participants was recruited online through Amazon
-Mechanical Turk. We used the same exclusion criteria as in Experiment 1.
-7 participants were excluded because they had less than 50\% accurate
-responses on the unambiguous training trials. The final sample consisted
-of N = 93 participants.
-
-\subsubsection{Stimuli and Procedure}\label{stimuli-and-procedure}
-
-We used the same visual stimuli as in Experiment 1. We also used the
-same auditory stimuli, but we convolved each item with Brown noise of
-amplitude 1 using the free sound editor Audacity (2.1.2). The average
-signal-to-noise ratio was - 4.4 dB. The procedure was exactly the same
-as in the previous experiment, except that the test stimuli (but not the
-target) were presented with the new noisy auditory stimuli.
-
-\subsection{Results and analysis}\label{results-and-analysis-2}
-
-\subsubsection{Unimodal conditions}\label{unimodal-conditions-3}
-
-We fit a model for each modality. For the auditory modality, our
-parameter estimates were \(b_A=\) -0.18 {[}-0.05, -0.30{]} and
-\(\sigma^2_A+\sigma^2_N=\) 4.70 {[}4.03, 5.55{]}. For the visual
-modality, we found \(b_V=\) -0.24 {[}-0.10, -0.36{]} and \(\sigma^2_V=\)
-3.93 {[}3.43, 4.55{]}. Figure~\ref{fig:unimodal} shows responses in the
-unimodal conditions as well as the corresponding best fits. The visual
-data is a replication of the visual data in Experiment 1. As for the
-auditory data, in contrast to Experiment 1, responses were flatter,
-showing more uncertainty.
-
-\subsubsection{Bimodal condition}\label{bimodal-condition-2}
-
-\paragraph{Normative models}\label{normative-models-1}
-
-Figure~\ref{fig:bimodal} compares the predictions of the visual,
-auditory and optimal models to human responses. These normative models
-explained, respectively, 77\%, 21\%, and 91\% of total variance in mean
-judgements. Note that, in contrast to Experiment 1, the visual model
-explained more variance than the auditory model did.
-
-\paragraph{Descriptive model}\label{descriptive-model-1}
-
-We estimated \(b=\) -0.38 {[}-0.33, -0.42{]},
-\(\sigma^2_{Ab}+\sigma^2_{Nb}=\) 9.84 {[}8.75, 11.27{]}, and
-\(\sigma^2_{Vb}=\) 5.21 {[}4.84, 5.64{]}. The fit explained 0.97\% of
-total variance. Cross-validation using half the responses to predict the
-other half yielded \(r^2 =\) 0.96.
-
-\paragraph{Modality preferences}\label{modality-preferences}
-
-Figure~\ref{fig:bias} (top) shows that the participants' decision
-threshold deviated from optimality, and that this deviation was biased
-towards the visual modality (the non-noisy modality). Indeed
-non-parametric resampling of the data showed a decrease in the value of
-the slope in the descriptive model compared to the optimal model
-(Figure~\ref{fig:bias}, bottom).
-
-\subsection{Discussion}\label{discussion-2}
-
-We found, similar to Experiment 1, that the population was generally
-near optimal (\(r^2 =\) 0.91), and that the optimal model explained more
-variance than the auditory or the visual models alone. We also found a
-similar discrepancy from the optimal model as precision dropped for both
-the auditory and the visual modalities. As for the weighting scheme used
-by participants, contrary to Experiment 1 where modalities were weighted
-according to their relative reliability, we found in this experiment
-that the visual modality had a greater weight than what was expected
-from its relative reliability. This situation corresponds to the second
-case of sub-optimality described in Figure~\ref{fig:subOptim}.
-
-We were also interested in whether noise in the auditory modality lead
-more participants to rely exclusively on the visual modality at the
-individual level. Using the same cut-off as in Experiment 1 (a factor of
-10), the percentage of participants who relied exclusively on either
-modality was 34.41\%, which is much higher than the percentage obtained
-in Experiment 1 (21.25\%). Moreover, the subset of participants relying
-exclusively on the visual modality (compared to those who relied
-exclusively on the auditory modality) increased from 29.41\% in
-Experiment 1 to 68.75\% in Experiment 2, indicating that noise in the
-auditory modality prompted more participants to rely exclusively and
-disproportionately on the visual modality (see Table
-\ref{tab:exclusive}).
-
-In Experiment 2, we tested the case of added background noise to the
-auditory modality. In Experiment 3, we test the case of added noise to
-the visual modality.
-
-\section{Experiment 3}\label{experiment-3}
-
-In this Experiment, we added background noise to the visual modality.
-Similar to Experiment 2, we were interested to know if participants
-would treat this new source of uncertainty as predicted by the optimal
-model, that is, according to the following weighting scheme:
-\[\beta_a \propto \frac{1}{\sigma^2_{A}}\]
-\[\beta_v \propto \frac{1}{\sigma^2_{V}+\sigma^2_{N_V}}.\] The
-alternative hypothesis is that noise in the visual modality would lead
-to a preference for the auditory input, just like noise in the auditory
-modality lead to a preference for the visual input in Experiment 2.
-
-\subsection{Methods}\label{methods-2}
-
-\subsubsection{Participants}\label{participants-3}
-
-A planned sample of 100 participants was recruited online through Amazon
-Mechanical Turk. We used the same exclusion criteria as in both previous
-experiments. N=2 participants were excluded because they reported having
-a technical problem, and N=10 participants were excluded because they
-had less than 50\% accurate responses on the unambiguous training
-trials. The final sample consisted of N = 88 participants.
-
-\subsubsection{Stimuli and Procedure}\label{stimuli-and-procedure-1}
-
-We used the same auditory stimuli as in Experiment 1. We also used the
-same visual stimuli, but we blurred the tokens using the free image
-editor GIMP (2.8.20). We used a Gaussian blur with a
-radius\footnote{A features that modulates the intensity of the blur.} of
-10 pixels. The experimental procedure was exactly the same as in the
-previous Experiments.
-
-\subsection{Results and analysis}\label{results-and-analysis-3}
-
-\begin{figure}[!h]
-\includegraphics[width=\textwidth]{ms_files/figure-latex/bias-1} \caption{Modality preference is characterized as a deviation from the optimal decision threshold.
-A) The decision thresholds of both the optimal and the descriptive models (solid red and black lines, respectively).
-Deviation from optimality is compared to two hypothetical cases of modality preference.
-In these cases, deviation from  optimality is due to over-lying on the visual or the auditory input by a factor of 2 (green and blue dotted lines, respectively).
-B) An alternative way to represent the same data.
-Each point represents the value of the decision threshold's slope derived from the descriptive model relative to that of the optimal model (log-scaled).
-The lines represent the optimal case as well as the two hypothetical cases of modality preference.
-Error bars represent 95\% confidence intervals over the distribution obtained through non-parametric resampling.}\label{fig:bias}
-\end{figure}
-
-\subsubsection{Unimodal conditions}\label{unimodal-conditions-4}
-
-For the auditory modality, our parameter estimates were \(b_A=\) -0.24
-{[}-0.04, -0.42{]} and \(\sigma^2_A=\) 1.94 {[}1.61, 2.33{]}. For the
-visual modality, we found \(b_V=\) 0.11 {[}0.27, -0.03{]} and
-\(\sigma^2_V+\sigma^2_N=\) 13.00 {[}9.92, 18.94{]}.
-Figure~\ref{fig:unimodal} shows responses in the unimodal conditions as
-well as the corresponding fits. The auditory data is a replication of
-the auditory data in Experiment 1. As for the visual data, we found
-that, in contrast to Experiment 1 and 2, responses were flatter, showing
-much more uncertainty.
-
-\subsubsection{Bimodal condition}\label{bimodal-condition-3}
-
-\paragraph{Normative models}\label{normative-models-2}
-
-Figure~\ref{fig:bimodal} compares the predictions of the visual,
-auditory and optimal models to human responses. These normative models
-explained, respectively, 1\%, 98\%, and 97\% of total variance in the
-mean judgements.
-
-\paragraph{Descriptive model}\label{descriptive-model-2}
-
-We estimated \(b=\) -0.35 {[}-0.29, -0.40{]}, \(\sigma^2_{Ab}=\) 3.00
-{[}2.75, 3.25{]}, and \(\sigma^2_{Vb}+\sigma^2_{Nb}=\) 39.42 {[}25.06,
-98.96{]}. The fit explained 97\% of total variance. Cross-validation
-using half the responses to predict the other half yielded \(r^2=\)
-0.96.
-
-\paragraph{Modality preferences}\label{modality-preferences-1}
-
-Participants' decision threshold suggested a preference for the auditory
-modality (the non-noisy modality). Indeed non-parametric resampling of
-the data showed an increase in the value of the slope in the descriptive
-model compared to the optimal model (Figure~\ref{fig:bias}).
-
-\subsection{Discussion}\label{discussion-3}
-
-We found that the optimal model accounted for almost all the variance
-(\(r^2 =\) 0.97). However, whereas in previous experiments the optimal
-model explained more variance than the auditory or the visual models,
-here the auditory model explained at least as much variance (\(r^2 =\)
-0.98). Thus, though participants were still sensitive to variation in
-the noisy visual data in the unimodal condition, they tended to ignore
-this information in the bimodal condition, and relied almost exclusively
-on the non-noisy auditory modality. The reason why we saw this (floor)
-effect when we added noise to the visual modality (Experiment 3), and
-not when we added noise to the auditory modality (Experiment 2), is the
-fact that our visual stimuli were originally perceived less
-categorically and with less certainty than the auditory stimuli. This
-fact made it more likely for the visual categorization function to
-become flat and uninformative after a few drops in precision due to
-noise on the one had, and to the additional randomness induced by the
-bimodal presentation on the other hand.
-
-The general finding corresponds to the third case of sub-optimality
-described in Figure~\ref{fig:subOptim}. Indeed, precision dropped for
-both modalities in the bimodal condition compared to the unimodal
-condition. But the drop was much greater for the visual modality,
-resulting in a much lower weight assigned to it than what is expected
-from its reliability. Therefore, just like participants over-relied on
-the visual modality when the auditory modality was noisy (Experiment 2),
-they also over-relied on the auditory modality when the visual modality
-was noisy (Experiment 3).
-
-\begin{table}[tbp]
-\begin{center}
-\begin{threeparttable}
-\caption{\label{tab:exclusive}The percentage of participants who relied exclusively on either the visual modality or the auditory modality, using a factor of 10 as a cut-off (e.g., we consider that a participant relied exclusively on the visual modality when their auditory variance is a at least 10 times larger than their visual variance).
-We show the percentage compared to the total number of participants in each Experiment (`of Total').
-From this subset of participants, we show the percentage of those who relied on the  auditory modality (`Auditory'), and the percentage of those who relied on the visual  modality (Visual').}
-\begin{tabular}{llll}
-\toprule
-Experiment & \multicolumn{1}{c}{ofTotal} & \multicolumn{1}{c}{Auditory} & \multicolumn{1}{c}{Visual}\\
-\midrule
-Exp1 & 21.25 & 70.59 & 29.41\\
-Exp2 & 34.41 & 31.25 & 68.75\\
-Exp3 & 38.64 & 94.12 & 5.88\\
-\bottomrule
-\end{tabular}
-\end{threeparttable}
-\end{center}
-\end{table}
-
-The percentage of participants who relied exclusively on either the
-visual modality or the auditory modality was 38.64\%, which is closer to
-the percentage of Experiment 2, except that now almost all of them
-relied on the auditory modality (94.12\%). For ease of comparison, Table
-\ref{tab:exclusive} provides a summary of the numbers across the three
-experiments.
 
@@
 optimal behavior. Quantitatively speaking, the optimal model accounted,
-respectively, for 89\%, 91\%, and 97\% of the variance in mean
-responses. When compared to the predictions of the visual or the
-auditory models, participants generally relied on both modalities to
-make their decisions in the bimodal condition. Indeed, in Experiment 1
-and 2, the optimal model accounted for more variance in mean responses
-than the auditory or the visual models did. In Experiment 3,
-participants appeared to rely on one modality, but this was likely a
-floor effect, due to the fact that noise made the visual input barely
-perceptible. Further, in Experiment 1, which did not involve background
-noise, participants not only relied on both modalities, but generally
-weighted these modalities according to the predictions of the optimal
-model, that is, according to their relative reliability. At the
-individual level, however, we found evidence of a between-subject
-variation: Some participants relied more on the visual modality, whereas
-others relied more on the auditory modality.
+respectively, for xx, xx, and xx of the variance in mean responses. When
+compared to the predictions of the visual or the auditory models,
+participants generally relied on both modalities to make their decisions
+in the bimodal condition. Indeed, in Experiment 1 and 2, the optimal
+model accounted for more variance in mean responses than the auditory or
+the visual models did. In Experiment 3, participants appeared to rely on
+one modality, but this was likely a floor effect, due to the fact that
+noise made the visual input barely perceptible. Further, in Experiment
+1, which did not involve background noise, participants not only relied
+on both modalities, but generally weighted these modalities according to
+the predictions of the optimal model, that is, according to their
+relative reliability. At the individual level, however, we found
+evidence of a between-subject variation: Some participants relied more
+on the visual modality, whereas others relied more on the auditory
+modality.
 

### 2019-03-19 Writeup/ms.Rmd
revisions

@@
 
-## Descriptive model and analysis of sub-optimality
+## Descriptive model and analysis of (sub-)optimality
 
@@
 
-Although the paradigm is within-subjects, we did not have enough statistical power to fit a different model for each individual participant.
+Although the paradigm is within-subjects, we did not have enough statistical power to fit a different model for each individual participant (but see Experiment 4).
 Instead, models were constructed with data collapsed across all participants.
@@
 
-```{r stats, results="asis", echo=FALSE}
+```{r param, results="asis", echo=FALSE}
 
 parameters <- feather::read_feather("../Data_and_analysis/saved_data/parameters.feather")
+
+parameters[,-1] <-round(parameters[,-1],2)
+
+names(parameters) <- c("Experiment",  "b\\textsubscript{A}", "Var\\textsubscript{A}", "b\\textsubscript{V}", "Var\\textsubscript{V}", "b\\textsubscript{b}","Var\\textsubscript{Ab}","Var\\textsubscript{Vb}")
 
@@
       caption = "Statistics for the dataset we used."#,
-      #col.names = c("Language",  "Nouns", "Ages", "N", "Nouns", "Ages","N")
+      #col.names = c("Experiment",  "b~A~", expression("*o['T']*"), "b~V~", "sigma~V~", "b~b~","sigma~Ab~","sigma~Vb~")
       ) %>%
@@
 
-Average categorization judgments and best fits are shown in Figure\ \@ref(fig:unimodal).
+Average categorization judgments and best fits are shown in Figure \@ref(fig:unimodal).
 The categorization function of the auditory condition was slightly steeper than that of the visual condition, meaning that participants perceived the sound tokens slightly more categorically and with higher certainty than they did with the visual tokens.
-For the auditory modality, we obtained the following values: $b_A=$ `r audBias_val`  [`r audBias_ci2`, `r audBias_ci1`] and $\sigma^2_A=$ `r audVar_val` [`r audVar_ci1`, `r audVar_ci2`].
-For the visual modality, we obtained $b_V=$ `r visBias_val` [`r visBias_ci2`, `r visBias_ci1`] and $\sigma^2_V=$ `r visVar_val` [`r visVar_ci1`, `r visVar_ci2`].
+The unimodal models' estimates are shown in Table \@ref(tab:param).
 
@@
 
-```{r}
-
-#Here we conduct cross-validation for the descriptive model, since this model is trained and tested on the same data
-
-#As the numbers show, the predictions on the held-out subset is almost as accurate as the predictions on the training set.  Over-fitting is generally not a problem with such simple models)
-
-#We conduct a cross-validation where half the responses are used predict the other half
-
-#The function "crossValid", below, takes the data to be cross-validated and return a score (coefficient of determination)
-
-crossValid <- function(data) {
-
-n <- nrow(data)
-frac <- 0.5
-ix <- sample(n, frac * n) # indexes of in sample rows
-
-fo <- answer ~ 1/(1+(1-e)*exp((-4/vrA_j)*sound_dist+(-4/vrV_j)*concept_dist+(8/vrA_j)+(8/vrV_j)))
-
-fm <- nls(fo, data, start = list(e=0, vrA_j=2, vrV_j=2), subset = ix) # fit the model to a subset (here half) the responses
-
-#Extract the values of the parameter
-
-data.test <- data[-ix, ] # out of sample data
-data.train <- data[ix, ]
-
-data.train.means <- data.train %>%
-  group_by(concept_dist, sound_dist) %>%
-  summarise(mean = mean(answer))
-
-data.test.means <- data.test %>%
-  group_by(concept_dist, sound_dist) %>%
-  summarise(mean = mean(answer))
-
-pred.train <-  predict(fm, new = data.train.means)
-pred.test <- predict(fm, new = data.test.means)
-
-cor.train <- cor(data.train.means$mean, pred.train)^2 
-cor.test <- cor(data.test.means$mean, pred.test)^2
-
-return(cor.test)
-
-}
-
-#Average across N partions, to render the pdf I am using a small value, but higher values can be used for the final version
-N_partitions = 10
-
-crossValid_exp1 <- replicate(N_partitions, {
-  crossValid(joint_all_exp1)
-  })
-
-CV_exp1_mean = mean(crossValid_exp1)
-error <- qt(0.975,df=length(crossValid_exp1)-1)*sd(crossValid_exp1)/sqrt(length(crossValid_exp1))
-CV_exp1_lower = CV_exp1_mean - error
-CV_exp1_upper = CV_exp1_mean + error
-
-crossValid_exp2 <- replicate(N_partitions, {
-  crossValid(joint_all_exp2)
-  })
-
-CV_exp2_mean = mean(crossValid_exp2)
-error <- qt(0.975,df=length(crossValid_exp2)-1)*sd(crossValid_exp2)/sqrt(length(crossValid_exp2))
-CV_exp2_lower = CV_exp2_mean - error
-CV_exp2_upper = CV_exp2_mean + error
-
-crossValid_exp3 <- replicate(N_partitions, {
-  crossValid(joint_all_exp3)
-  })
-
-CV_exp3_mean = mean(crossValid_exp3)
-error <- qt(0.975,df=length(crossValid_exp3)-1)*sd(crossValid_exp3)/sqrt(length(crossValid_exp3))
-CV_exp3_lower = CV_exp3_mean - error
-CV_exp3_upper = CV_exp3_mean + error
-
-```
-
-#### Normative models
-Figure\ \@ref(fig:bimodal) compares the predictions of the normative models against human responses.
-Remember that the normative models use variance estimates from the unimodal conditions (where people see input from only one modality) to predict data in the bimodal condition (where people see input from both modalities).
-Each point represents data form a particular audio-visual matching (e.g., the visual token $v$ whose distance from the target $v_t$ is $|v-v_t|=3$, matched with the auditory token $a$ whose distance from the target $a_t$ is $|a-a_t|=2$).
-The visual, auditory and optimal model explained, respectively, `r 100*R2_visual_1`%, `r 100*R2_auditory_1`%, and `r 100*R2_optimal_1`% of total variance in mean responses.
-
-#### Descriptive model
-In the descriptive model, all parameters are fit to human responses in the bimodal condition.
-We found $b=$ `r BiasBi_val` [`r BiasBi_ci2`, `r BiasBi_ci1`], $\sigma^2_{Ab}=$ `r audVarBi_val` [`r audVarBi_ci1`, `r audVarBi_ci2`] and $\sigma^2_{Vb}=$ `r visVarBi_val` [`r visVarBi_ci1`, `r visVarBi_ci2`].
-Note that the variance of both the auditory and visual modalities increased compared to the unimodal conditions.
-
-\noindent The descriptive model explained `r 100*R2_descriptive_1`% of total variance.
-However, since the descriptive model was fit to the same data, there is a risk that this high correlation is due to overfitting.
-To examine this possibility, we cross-validated the model using half the responses to predict the other half (averaging across `r N_partitions` random partitions).
-The predictive power of the model remained very high ($r^2$=`r CV_exp1_mean`).
+Figure \@ref(fig:bimodal) compares the predictions of the normative and descriptive models against human responses.
+Remember that the normative models use the parameters estimated from the unimodal conditions (where people see input from only one modality) to predict behavior in the bimodal condition (where people see input from both modalities).
+The descriptive model has a similar structure than the optimal model, but is directly fit to human responses in the bimodal condition in order to allow us to assess deviation from optimaity.
+
+We found, through comparing the correlation values, that the optimal model explained more variance than the visual and auditory models did.
+However, the optimal model was not perfect: It explained less variance than the descriptive model did, which indicates a deviation from optimality.
+To investigate this deviation, we compare the parameter values of the optimal model to the values obtaied in the decriptive model (Table \@ref(tab:param)).\footnote{Note that the descriptive model explained almost all the variance in mean responses, which makes it a reasonble proxy for human real performance in the bimodal condition.}.
+We note an increase in *both* the auditory and visual variances.
+This increase in noise is compatible with the fact that human responses appear to be pulled towards chance (i.e., the value O.5) when compared to the optimal model (see \@ref(fig:bimodal)).
+Below we investigate if this deviation from optimality can be related to the cue combination strategy.
+
+### Cue combination
+
+We analyzed if the cue combination was performed in an optimal way, or if there was a systematic preference for one modality when making decisions in the bimodal condition.
+As explained in \@ref(fig:subOptim), modality preference can be characterized formally as a deviation from the decision threshold predicted by the optimal model.
+The results in Figure \@ref(fig:bias) (top) show both the decision threshold derived from the descriptive model (in black) and the decision threshold predicted by the optimal model (in red).
+We found that the descriptive and optimal decision thresholds were almost identical.
+Indeed, non-parametric resampling of the data showed no evidence of a deviation from the optimal prediction (Figure\ \@ref(fig:bias), bottom).
+
+<!--\noindent The descriptive model explained almost all the variance of total variance.
+However, unlike the normative models, the descriptive model was fit to the same bomodal data.
+Thus, there is a risk that this high correlation is due to overfitting.
+To examine this possibility, we cross-validated the model using half the responses to predict the other half (averaging across X random partitions).
+The predictive power of the model remained very high (XX).
+-->
 
@@
 
-#### Cue combination and Modality preference
-We next analyzed if cue combination was performed in an optimal way, or if there was a systematic preference for one modality when making decisions in the bimodal condition.
-As explained above, modality preference can be characterized formally as a deviation from the decision threshold predicted by the optimal model.
-Figure\ \@ref(fig:bias) (top) shows both the decision threshold derived from the descriptive model (in black) and the decision threshold predicted by the optimal model (in red).
-The deviation from optimality is compared to two hypothetical cases of modality preference (dotted lines).
-We found that the descriptive and optimal decision thresholds were almost identical.
-Indeed, non-parametric resampling of the data showed no evidence of a deviation from the optimal prediction (Figure\ \@ref(fig:bias), bottom).
-
 ## Discussion
-Overall, we found that the optimal model explained much of the variance in the mean judgments, and largely more than what can be explained with the auditory or the visual models alone.
-Moreover, the high value of the coefficient of determination in the optimal model ($r^2$=`r R2_optimal_1`) suggests that the population was near-optimal.
-However, we see in Figure\ \@ref(fig:bimodal) that the mean responses deviated systematically from the optimal prediction in that they were slightly pulled toward chance (i.e., the probability 0.5).
-This fact is due to the increase in the value of the variance associated with each modality.
-Note however that, despite this increase in randomness, our analysis of modality preference showed that the relative values of these variances were not different (Figure\ \@ref(fig:bias)), meaning that there was no evidence for a modality preference.
-Thus, 1) There was a simultaneous increase in the values of the auditory and visual variances in the bimodal condition compared to the unimodal condition, meaning that the bimodal input lead to an increase in response randomness, and 2) this increased randomness did not affect the relative weighting of both modalities, i.e., the participants was weighting modalities according to the relative reliability predicted by the optimal model.
+
+This experiment studied the way participants combine multimodal information to recognize novel words.
+We found that the optimal model explained more variance than the auditory or the visual models did, indicating that particiapants take into account both the auditory and visual cues when making a decision.
+That said, Figure \@ref(fig:bimodal) shows that the participants deviated slightly --- but systematically--- from the optimal prediction in that they were slightly pulled toward chance (i.e., the probability 0.5).
+This fact was captured by the increase in the value of the variance associated with each modality (as can be noted from Table \@ref(tab:param)).
+Note, however, that despite this increase response randomness in the bimodal condition, our analysis of modality preference showed that the *relative* values of these variances were not different (Figure\ \@ref(fig:bias)), meaning that there was no evidence for a modality preference.
+
+To sum up, 1) the participants used both the auditory and visual information, 2) they responded slightly more randomly that what was predicted, but 3) this increased randomness was general and did not influence the cue combination strategy, i.e., the participants still weighted modalities according to their relative reliability as predicted by the optimal model.
 This situation corresponds to the first case of sub-optimality described in Figure\ \@ref(fig:subOptim).
 
-<!--the model addresses the question of optimality at the population level.
-However, it is important to  know how individual responses are distributed.
-In fact, one could think of an extreme case where optimality at the population level would be misleading.
-Imagine, for instance, that in the bimodal condition half the participants relied exclusively on the visual modality, whereas the other half relied exclusively on the auditory modality.
-This case could still lead to an aggregate behavior which appears optimal, but this optimality would be spurious.
-
-To examine this possibility, we consider the distribution of individual cross-modal weighting in the bimodal condition (i.e., $\frac{\sigma^2_{Vb}}{\sigma^2_{Ab}}$).
-Using a factor of 10 as a cut-off, we found that `r only_visual_N_1` participants relied almost exclusively on the visual modality, and `r only_sound_N_1` relied almost exclusively on the auditory modality.
-The percentage of both cases was relatively small compared to the total number of participants (`r 100*(only_visual_N_1+only_sound_N_1)/(only_visual_N_1+only_sound_N_1+both_N_1)`%).
-When these outliers  were removed, the distribution had a rather unimodal shape (Figure\ \@ref(fig:individual)).
-This finding indicates that the population's near optimality is not spurious, but based mostly on genuine cue combination at the individual level.
-
-As a second analysis, we asked whether the observed variance in the individual distribution was due to mere sampling errors or whether it corresponded to a real between-subject variability.
-We simulated individual responses from the posterior distribution whose parameters were fit to the population as a whole (i.e., the descriptive posterior).
-The resulting distribution is shown in Figure\ \@ref(fig:individual).
-For ease of comparison, the simulated distribution was superimposed to the real distribution.
-We found that the real distribution had a standard deviation of $sd=$ `r subset(sd_ind, data=='real')$sd` which was larger than that of the simulated distribution ($sd=$ `r subset(sd_ind, data=='simulation')$sd`), indicating that there was real between-subject variation beyond sampling errors.
-This finding means that the participants varied in terms of how they weighted modalities: Compared to the predictions of the population-level model, some participants relied more on the auditory modality, whereas others relied more on the visual modality.
--->
-
-As we noted earlier, we did not have enough statistical power to fit a different model for each individual participant.
-Instead, we fit one model using the data aggregated across all participants.
-This analysis is informative of behavior at the population level, only.
-However, optimality at the population level could be misleading.
-Imagine, for instance, that in the bimodal condition half the participants relied exclusively on the visual modality, whereas the other half relied exclusively on the auditory modality.
-This case could still lead to an aggregate behavior which appears optimal, but this optimality would be spurious.
-This, in the experiemnt below, we test the cue integration strategy at the individual level.
-To this end, we increase the statistical power by extending the length of the experiment, allowing us to collect the number of datapoints necessary to fit the models for each participant.
-
-# Experiment 4
-
-```{r}
-
-weight <- feather::read_feather("../Data_and_analysis/ind_weights.feather")
-
-weight.boot <- boot(data=weight$prop, function(x,i) median(x[i]), R=10000)
-
-weight.ci=boot.ci(weight.boot, 
-                  conf = 0.95,
-                  type = c('perc'))
-
-#weights.dist <- weight$prop[weight$prop < 100 & weight$prop > 0.01]
-
-weight.median <- weight.ci$t0
-weight.median_low <- weight.ci$percent[4]
-weight.median_up <- weight.ci$percent[5]
-
-ggplot(data=weight, aes(x=prop, y=..count..)) +
-  geom_histogram(alpha=0.5, binwidth = 0.4)+
-  geom_vline(xintercept = weight.median, col='red')+
-  geom_vline(xintercept = weight.median_low, linetype='dashed') +
-  geom_vline(xintercept = weight.median_up, linetype='dashed') +
-  #geom_histogram(data=subset(bimod_all, data=='simulation'), fill="blue", alpha=0.2, binwidth = 0.2)+
-  #geom_histogram(binwidth = 0.2) +
- scale_x_log10(breaks =c(0.1,1,10)) +
-   xlab("Optimal weighing relative to real weighing") +ylab("Count")+
-  theme_few()+
-  theme(aspect.ratio = 0.7) +
-  coord_cartesian(xlim=c(0.01,100))
-
-```
-
-### Participants
-We recruited a planned sample of N=XX participants from Amazon Mechanical Turk.
-Only participants with US IP addresses and a task approval rate above 99\% were allowed to participate.
-They were paid at an hourly rate of \$6/hour.
-Participants were excluded if they reported having experienced a technical problem of any sort during the online experiment (N=XX), or if they had less than 75\% accurate responses on the unambiguous training trials (N=XX).
-The final sample consisted of N = XX participants.
-[I should also add how many participants I excluded because their models did not converge].
-All participants provided informed consent before taking the experiment.\footnote{The sample size and exclusion criteria were specified in the pre-registration at https://osf.io/h7mzp/.}
-
-### Stimuli
-We used the same stimuli as in Experiment 1.
-
-### Design and Procedure
-The design and procedure were similar to Experiment 1. The only difference was that we increased the number of datapoints elicited per subject from 70 to 300.
-
-## Results and analysis
-
-### Unimodal conditions
-
-We fit both population-level models to the aggregated data (as in Experiment 1), and individual models to data from each participant.
-For the populaton-level models, the results (shown in Figure\ \@ref(fig:unimodal)) replicated the results obtained in Experiment 1.
-As for the individual-level analysis, the models showed there to be between-subject variability as seen in the paramters's distribution in Figure XX.
-
-### Bimodal condition and Cue combination models
-
-We first generated poupulation-level normative and descriptive models.
-As shown in Figure\ \@ref(fig:bimodal), the predicted patterns of these models mirrored closely the results obtained in Experiment 1.
-In addition, the optimality analysis (i.e., done through comparing the optimal and descriptive models) shows that the fitted mean decision threshold was indisguisable form the optimal threshold, thus replicating the results of Experiment 1 (Figure\ \@ref(fig:bias) shows that).
-
-<!--As a first analysis, we show the histogram comparing the normative models, only (Figure XX).
-The histogram shows interesting between-subject variability: The optimal model explained the most variance in the majority of cases, showing that participants in these cases combined information from the auditory and visual modality to perform the task.
-However, the visual and auditory models were sufficient to explain most variance in a large number of participants.
-These partcipants relied predominantly on only one modality to perform the task.
-This is the crucial analysis which would allow us to test the extent to which participants were optimal at the individual level.
-We perfomed an optimality analysis following the procedure outlines above, i.e., through comparing the optimal and descriptive models.
-Firs, at the population level, the fitted mean decision threshold was indisguisable form the optimal threshold, thus replicating the results of Experiment 1 (Figure\ \@ref(fig:bias) shows that).
--->
-
-At the individual level, we computed the distribution of optimal weighing relative to the fitted (i.e., descriptive) weighing and we show this distribution in Figure XX.
-The distribution centers around the optimal prediction (i.e., 1) with a median value of XX [XX,XX].
-The variance of the distribution indicates that, while most participants were near optimal in their cue combination, part of the participant tended to rely predominantly on the auditory modality and another part tended to rely predominantly on the visual modality.
-
-[Here compare to random model to see whether the resuls were due to measurement errors or to genuine betwee-subject variability, but isn't that what the CI around the median show?]
-
-## Discussion
-
-This experiment was an extension to Experiment 1.
-Through collecting larger-size data per subject, we were able to analyze the cue combination optimlity, not only at the population level, but also at the individual level.
-The population-level analysis replicated the results of Experiment 1.
-The individual-level analysis showed that participants' performance approximated a normal distribution centered around the optimal combination.
-The large variance of this distribution indicate that some participants tend to over-rely on the auditory modality and others tend to over-rely on the visual modality.
-
-In Experiment 1 and Experiment 1 bis, we tested word recognition when there was multimodal uncertainty in terms of category membership and inherent perceptual noise, only.
+In Experiment 1, we tested word recognition when there was multimodal uncertainty in terms of category membership and inherent perceptual noise, only.
 In real life, however, both sound and visual tokens can undergo distortions due to noisy factors in the environment (e.g., car noise in the background, blurry vision in a foggy weather).
@@
 
-## Results and analysis
-
-### Unimodal conditions
-
+## Results
+
+The analysis are similar to the analysis we did in Experiment 1.
+
+### Unimodal condition
 We fit a model for each modality.
-For the auditory modality, our parameter estimates were $b_A=$ `r audBias_val` [`r audBias_ci2`, `r audBias_ci1`] and $\sigma^2_A+\sigma^2_N=$ `r audVar_val` [`r audVar_ci1`, `r audVar_ci2`].
-For the visual modality, we found $b_V=$ `r visBias_val` [`r visBias_ci2`, `r visBias_ci1`] and $\sigma^2_V=$ `r visVar_val` [`r visVar_ci1`, `r visVar_ci2`].
-Figure\ \@ref(fig:unimodal) shows responses in the unimodal conditions as well as the corresponding best fits.
+Figure \@ref(fig:unimodal) shows human responses together with their best fits.
 The visual data is a replication of the visual data in Experiment 1.
-As for the auditory data, in contrast to Experiment 1, responses were flatter, showing more uncertainty.
+The auditory data, in contrast, were flatter, showing more uncertainty.
 
 ### Bimodal condition
-
-#### Normative models
-Figure\ \@ref(fig:bimodal) compares the predictions of the visual, auditory and optimal models to human responses.
-These normative models explained, respectively, `r 100*R2_visual_2`%, `r 100*R2_auditory_2`%, and `r 100*R2_optimal_2`% of total variance in mean judgements.
-Note that, in contrast to Experiment 1, the visual model explained more variance than the auditory model did.
-
-#### Descriptive model
-We estimated $b=$ `r BiasBi_val` [`r BiasBi_ci2`, `r BiasBi_ci1`], $\sigma^2_{Ab}+\sigma^2_{Nb}=$ `r audVarBi_val` [`r audVarBi_ci1`, `r audVarBi_ci2`], and $\sigma^2_{Vb}=$ `r visVarBi_val` [`r visVarBi_ci1`, `r visVarBi_ci2`].
-The fit explained `r R2_descriptive_2`% of total variance.
-Cross-validation using half the responses to predict the other half yielded $r^2 =$ `r CV_exp2_mean`.
-
-#### Modality preferences
+We used the values derived from the unimodal condition to construct the visual, auditory and optimal models.
+In addition, we fit a descriptive model which allowed us to assess real human performance in this condition.
+Figure \@ref(fig:bimodal) shows that, similar to Experiment 1, the optimal model explained more variance than the auditory and visual models did (note, however, that the visual model explained more variance than the auditory model did).
+Also similar to Exeperiment 1, the values of the variances increased in the bimodal condition (Table \@ref(tab:param)).
+
+### Cue combination
+Here we investigated whethere the observed increase in the auditory and visual variances affected the relative weighting of the corresponding modalities.
 Figure\ \@ref(fig:bias) (top) shows that the participants' decision threshold deviated from optimality, and that this deviation was biased towards the visual modality (the non-noisy modality).
@@
 ## Discussion
-We found, similar to Experiment 1, that the population was generally near optimal ($r^2 =$ `r R2_optimal_2`), and that the optimal model explained more variance than the auditory or the visual models alone.
-We also found a similar discrepancy from the optimal model as precision dropped for both the auditory and the visual modalities.
-As for the weighting scheme used by participants, contrary to Experiment 1 where modalities were weighted according to their relative reliability, we found in this experiment that the visual modality had a greater weight than what was expected from its relative reliability.
-This situation corresponds to the second case of sub-optimality described in Figure\ \@ref(fig:subOptim).
-
-```{r echo=FALSE}
-#number of participants relying exlusiviely on one modality
-#cut off is a factor of 10
-
-bimodal_bysub_good_2 <- bimodal_bysub_2 %>%
-  filter(bimod > 0.1) %>%
-  filter(bimod < 10)
-
-#Visual modality 
-only_visual_N_2 <- bimodal_bysub_2 %>%
-  filter(abs(bimod) < 0.1) %>%
-  nrow()
-
-#Sound modality 
-only_sound_N_2 <- bimodal_bysub_2 %>%
-  filter(abs(bimod) > 10) %>%
-  nrow()
-
-#Both
-both_N_2 <- bimodal_bysub_2 %>%
-  filter(abs(bimod) > 0.1) %>%
-  filter(abs(bimod) < 10) %>%
-  nrow()
-
-neg_N_2 <- bimodal_bysub_2 %>%
-  filter(bimod <  -0.1) %>%
-  filter(bimod > -10) %>%
-  nrow()
-
-exlusive_prop_2 = only_visual_N_2/(only_sound_N_2+only_visual_N_2)
-
-```
-We were also interested in whether noise in the auditory modality lead more participants to rely exclusively on the visual modality at the individual level.
-Using the same cut-off as in Experiment 1 (a factor of 10), the percentage of participants who relied exclusively on either modality was `r 100*(only_visual_N_2+only_sound_N_2)/(only_visual_N_2+only_sound_N_2+both_N_2)`%, which is much higher than the percentage obtained in Experiment 1 (`r 100*(only_visual_N_1+only_sound_N_1)/(only_visual_N_1+only_sound_N_1+both_N_1)`%).
-Moreover, the subset of participants relying exclusively on the visual modality (compared to those who relied exclusively on the auditory modality)  increased from `r 100*exlusive_prop_1`% in Experiment 1 to `r 100*exlusive_prop_2`% in Experiment 2, indicating that noise in the auditory modality prompted more participants to rely exclusively and disproportionately on the visual modality (see Table \@ref(tab:exclusive)).
-
-In Experiment 2, we tested the case of added background noise to the auditory modality. In Experiment 3, we test the case of added noise to the visual modality.
+Experiment 2 tested audi-visual combination in the case where the auditory input was noisy.
+We found, similar to Experiment 1, that the optimal model explained more variance than the auditory or the visual models did.
+In other words, despite additional noise, participants still used information from the noisy modality to recognize words.
+We also found a similar discrepancy between the descriptive and optimal models as response randomness increased along both the auditory and the visual modalities.
+As for the relative weighting, and contrary to Experiment 1 where modalities were weighted optimally, we found in this experiment that the visual modality had a greater weight than what was expected from its relative reliability.
+This situation corresponds to the second case of sub-optimality described in Figure \@ref(fig:subOptim).
+
+Whereas in Experiment 2 we tested the case of added background noise to the auditory modality, in Experiment 3 we test the case of added noise to the visual modality.
 
@@
 
-In this Experiment, we added background noise to the visual modality.
-Similar to Experiment 2, we were interested to know if participants would treat this new source of uncertainty as predicted by the optimal model, that is, according to the following weighting scheme:  $$\beta_a \propto \frac{1}{\sigma^2_{A}}$$ $$\beta_v \propto \frac{1}{\sigma^2_{V}+\sigma^2_{N_V}}.$$
+Similar to Experiment 2, we were interested to know if participants would treat additional uncertainty as predicted by the optimal model, that is, according to the following weighting scheme:  $$\beta_a \propto \frac{1}{\sigma^2_{A}}$$ $$\beta_v \propto \frac{1}{\sigma^2_{V}+\sigma^2_{N_V}}.$$
 The alternative hypothesis is that noise in the visual modality would lead to a preference for the auditory input, just like noise in the auditory modality lead to a preference for the visual input in Experiment 2.
@@
 
-## Results and analysis
+## Results
 
@@
 ### Unimodal conditions
-For the auditory modality, our parameter estimates were $b_A=$ `r audBias_val` [`r audBias_ci2`, `r audBias_ci1`] and $\sigma^2_A=$ `r audVar_val` [`r audVar_ci1`, `r audVar_ci2`].
-For the visual modality, we found $b_V=$ `r visBias_val` [`r visBias_ci2`, `r visBias_ci1`] and $\sigma^2_V+\sigma^2_N=$ `r visVar_val` [`r visVar_ci1`, `r visVar_ci2`].
-Figure\ \@ref(fig:unimodal) shows responses in the unimodal conditions as well as the corresponding fits.
+Figure \@ref(fig:unimodal) shows responses in the unimodal conditions as well as the corresponding fits.
 The auditory data is a replication of the auditory data in Experiment 1.
@@
 ### Bimodal condition
-
-#### Normative models
-Figure\ \@ref(fig:bimodal) compares the predictions of the visual, auditory and optimal models to human responses.
-These normative models explained, respectively, `r 100*R2_visual_3`%, `r 100*R2_auditory_3`%, and `r 100*R2_optimal_3`% of total variance in the mean judgements.
-
-#### Descriptive model
-We estimated $b=$ `r BiasBi_val` [`r BiasBi_ci2`, `r BiasBi_ci1`], $\sigma^2_{Ab}=$ `r audVarBi_val` [`r audVarBi_ci1`, `r audVarBi_ci2`], and $\sigma^2_{Vb}+\sigma^2_{Nb}=$ `r visVarBi_val` [`r visVarBi_ci1`, `r visVarBi_ci2`].
-The fit explained `r 100*R2_descriptive_3`% of total variance.
-Cross-validation using half the responses to predict the other half yielded $r^2=$ `r CV_exp3_mean`.
-
-#### Modality preferences
-Participants' decision threshold suggested a preference for the auditory modality (the non-noisy modality).
+Figure \@ref(fig:bimodal) shows that almost all the variance was captured by the auditory model alone, the addition of visual information in the optomal model did not improve the prediction of human responses.
+Similar to Exeperiment 1 and 2, the values of the variances increased in the bimodal condition (Table \@ref(tab:param)).
+
+### Cue Combination
+Figure \@ref(fig:bias) indicates that the decision threshold was biased towards the auditory modality (the non-noisy modality).
 Indeed non-parametric resampling of the data showed an increase in the value of the slope in the descriptive model compared to the optimal model (Figure\ \@ref(fig:bias)).
@@
 ## Discussion
-We found that the optimal model accounted for almost all the variance ($r^2 =$ `r R2_optimal_3`).
-However, whereas in previous experiments the optimal model explained more variance than the auditory or the visual models, here the auditory model explained at least as much variance ($r^2 =$ `r R2_auditory_3`).
-Thus, though participants were still sensitive to variation in the noisy visual data in the unimodal condition, they tended to ignore this information in the bimodal condition, and relied almost exclusively on the non-noisy auditory modality.
-The reason why we saw this (floor) effect when we added noise to the visual modality (Experiment 3), and not when we added noise to the auditory modality (Experiment 2), is the fact that our visual stimuli were originally perceived less categorically and with less certainty than the auditory stimuli.
-This fact made it more likely for the visual categorization function to become flat and uninformative after a few drops in precision due to noise on the one had, and to the additional randomness induced by the bimodal presentation on the other hand.
-
-The general finding corresponds to the third case of sub-optimality described in Figure\ \@ref(fig:subOptim).
+
+Experiment 3 tested audi-visual combination in the case where the visual input was noisy.
+Whereas in previous experiments the optimal model explained more variance than the auditory or the visual models did, here the auditory model alone explained almost all the variance.
+In other words, though participants were sensitive to variation in the noisy visual input when presented in isolation (as shown in Figure \@ref(fig:unimodal)), they tended to ignore this information when the visual input was presented simultaneusel with the auditory input (i.e., in the bimodal condition).
+Instead, they relied almost exclusively on the non-noisy auditory modality.\footnote{The reason why we saw this (floor) effect when we added noise to the visual modality (Experiment 3), and not when we added noise to the auditory modality (Experiment 2), is the fact that our visual stimuli were originally perceived less categorically and with less certainty than the auditory stimuli (see Experiment 1 in \@ref(fig:unimodal)).
+This fact made it more likely for the visual categorization function to become flat and uninformative after a few drops in precision due to noise on the one had, and to the additional randomness induced by the bimodal presentation on the other hand.}
+
+This finding corresponds to the third case of sub-optimality described in Figure\ \@ref(fig:subOptim).
 Indeed, precision dropped for both modalities in the bimodal condition compared to the unimodal condition.
-But the drop was much greater for the visual modality, resulting in a much lower weight assigned to it than what is expected from its reliability.
+But the drop was much greater for the visual modality, resulting in a much lower weight assigned to it than what is expected from the optimal model.
 Therefore, just like participants over-relied on the visual modality when the auditory modality was noisy (Experiment 2), they also over-relied on the auditory modality when the visual modality was noisy (Experiment 3).
 
-```{r echo=FALSE}
-#number of participants relying exlusiviely on one modality
-#cut off is a factor of 10
-
-bimodal_bysub_good_3 <- bimodal_bysub_3 %>%
-  filter(bimod > 0.1) %>%
-  filter(bimod < 10)
-
-#Visual modality 
-only_visual_N_3 <- bimodal_bysub_3 %>%
-  filter(abs(bimod) < 0.1) %>%
-  nrow()
-
-#Sound modality 
-only_sound_N_3 <- bimodal_bysub_3 %>%
-  filter(abs(bimod) > 10) %>%
-  nrow()
-
-#Both
-both_N_3 <- bimodal_bysub_3 %>%
-  filter(abs(bimod) > 0.1) %>%
-  filter(abs(bimod) < 10) %>%
-  nrow()
-
-neg_N_3 <- bimodal_bysub_3 %>%
-  filter(bimod <  -0.1) %>%
-  filter(bimod > -10) %>%
-  nrow()
-
-exlusive_prop_3 = only_visual_N_3/(only_sound_N_3+only_visual_N_3)
-
-```
-
-```{r exclusive, results = "asis", landscape = FALSE}
-#Here make a table to analyze the exlusive reliance on one modality
-
-total_excl_exp1 <- (only_visual_N_1+only_sound_N_1)/(only_visual_N_1+only_sound_N_1+both_N_1)
-total_excl_exp2 <- (only_visual_N_2+only_sound_N_2)/(only_visual_N_2+only_sound_N_2+both_N_2)
-total_excl_exp3 <- (only_visual_N_3+only_sound_N_3)/(only_visual_N_3+only_sound_N_3+both_N_3)
-
-unimod <- data.frame(
-  Experiment = c('Exp1', 'Exp2', 'Exp3'),
-  ofTotal = c(100*total_excl_exp1, 100*total_excl_exp2, 100*total_excl_exp3),
-  Auditory = c(100*(1-exlusive_prop_1), 100*(1-exlusive_prop_2), 100*(1-exlusive_prop_3)),
-  Visual = c(100*exlusive_prop_1, 100*exlusive_prop_2, 100*exlusive_prop_3)
-)
-
-apa_table(
-  unimod
-  , caption = "The percentage of participants who relied exclusively on either the visual modality or the auditory modality, using a factor of 10 as a cut-off (e.g., we consider that a participant relied exclusively on the visual modality when their auditory variance is a at least 10 times larger than their visual variance).
-We show the percentage compared to the total number of participants in each Experiment (`of Total').
-From this subset of participants, we show the percentage of those who relied on the  auditory modality (`Auditory'), and the percentage of those who relied on the visual  modality (Visual')."
-
-)
-
-```
-
-The percentage of participants who relied exclusively on either the visual modality or the auditory modality was `r 100*(only_visual_N_3+only_sound_N_3)/(only_visual_N_3+only_sound_N_3+both_N_3)`%, which is closer to the percentage of Experiment 2, except that now almost all of them relied on the auditory modality (`r 100*(1-exlusive_prop_3)`%).
-For ease of comparison, Table \@ref(tab:exclusive) provides a summary of the numbers across the three experiments.
+So far we have studied the problem of cue combination at the population level --- the models were fit to the data aggregated across all participants.
+However, it is important to investigate individual variability, especially in Experiment 1 where we reported optimal cue combination.
+In fact, it is possible that a large part of the participants relied primarily on the visual modality and another part on the auditory modality.
+Such an extreme individual variability could possibly lead to an aggregate beahvior which appears optimal, but such optimality would be spurious.
+In order to rule out this extreme case, we need to examine the distribution of the specific cue combibination strategies followed by the participants.
+
+As we noted earlier, we did not have enough statistical power to fit a different model for each participant.
+Thus, in Experiment 4, below, we reran Experiment 1 while extending its length, allowing us to collect the number of datapoints necessary to fit the models for each participant.
+
+# Experiment 4
+
+```{r weights}
+
+weight <- feather::read_feather("../Data_and_analysis/ind_weights.feather")
+
+weight.boot <- boot(data=weight$prop, function(x,i) median(x[i]), R=10000)
+
+weight.ci=boot.ci(weight.boot, 
+                  conf = 0.95,
+                  type = c('perc'))
+
+#weights.dist <- weight$prop[weight$prop < 100 & weight$prop > 0.01]
+
+weight.median <- weight.ci$t0
+weight.median_low <- weight.ci$percent[4]
+weight.median_up <- weight.ci$percent[5]
+
+ggplot(data=weight, aes(x=prop, y=..count..)) +
+  geom_histogram(alpha=0.5, binwidth = 0.4)+
+  geom_vline(xintercept = weight.median, col='red')+
+  geom_vline(xintercept = weight.median_low, linetype='dashed') +
+  geom_vline(xintercept = weight.median_up, linetype='dashed') +
+  #geom_histogram(data=subset(bimod_all, data=='simulation'), fill="blue", alpha=0.2, binwidth = 0.2)+
+  #geom_histogram(binwidth = 0.2) +
+ scale_x_log10(breaks =c(0.1,1,10)) +
+   xlab("Optimal weighing relative to real weighing") +ylab("Count")+
+  theme_few()+
+  theme(aspect.ratio = 0.7) +
+  coord_cartesian(xlim=c(0.01,100))
+
+```
+
+### Participants
+A planned sample of $N =$ `r N_all_3` participants was recruited online through Amazon Mechanical Turk.
+We used the same exclusion criteria as in both previous experiments.
+$N =$ `r N_all_3 - N_noProb_3` participants were excluded because they reported having a technical problem, and N=`r N_noProb_3 - N_good_3` participants were excluded because they had less than 50\% accurate responses on the unambiguous training trials.
+The final sample consisted of $N =$ `r N_good_3` participants.
+
+We recruited a planned sample of $N=$ `r N_all_4` participants from Amazon Mechanical Turk.
+Only participants with US IP addresses and a task approval rate above 99\% were allowed to participate.
+They were paid at an hourly rate of \$6/hour.
+Participants were excluded if they reported having experienced a technical problem of any sort during the online experiment ($N=$ `r N_all_4 - N_noProb_4` ), or if they had less than 75\% accurate responses on the unambiguous training trials ($N=$ `r N_noProb_4 - N_good_4`).
+The final sample consisted of $N =$ `r N_good_4` participants.
+All participants provided informed consent before taking the experiment.\footnote{The sample size, exclusion criteria and the main analysese were pre-registered at https://osf.io/h7mzp/.}
+
+### Stimuli
+We used the same stimuli as in Experiment 1.
+
+### Design and Procedure
+The design and procedure were similar to Experiment 1. The only difference was that we increased the number of responses elicited per subject from 70 to 300.
+
+## Results
+
+### Unimodal and Bimodal conditions
+In order to replicate the analysis of Experiment 1, we started by fitting population-level models to the aggregated data.
+Indeed, we found that the results --- as shown in Figure \@ref(fig:unimodal), Figure \@ref(fig:bimodal), and Table \@ref(tab:param) --- mirror closely the patterns obtained in Experiment 1.
+
+<!--As a first analysis, we show the histogram comparing the normative models, only (Figure XX).
+The histogram shows interesting between-subject variability: The optimal model explained the most variance in the majority of cases, showing that participants in these cases combined information from the auditory and visual modality to perform the task.
+However, the visual and auditory models were sufficient to explain most variance in a large number of participants.
+These partcipants relied predominantly on only one modality to perform the task.
+This is the crucial analysis which would allow us to test the extent to which participants were optimal at the individual level.
+We perfomed an optimality analysis following the procedure outlines above, i.e., through comparing the optimal and descriptive models.
+Firs, at the population level, the fitted mean decision threshold was indisguisable form the optimal threshold, thus replicating the results of Experiment 1 (Figure\ \@ref(fig:bias) shows that).
+-->
+### Cue combinaton
+We analyzed cue combination at the individual level.
+For each participant, we computed the optimal weighing, $\frac{\sigma^2_{A}}{\sigma^2_{V}}$, relative to the fitted (i.e., descriptive) weighing, $\frac{\sigma^2_{Ab}}{\sigma^2_{Vb}}$.
+We show the resulting distribution in Figure \@ref(fig:weights).
+We found that the distribution centered around the optimal prediction (i.e., 1) with a median value of `r weight.median` [`weight.median_low`, `weight.median_up`].
+
+[Here compare to random model to see whether the resuls were due to measurement errors or to genuine betwee-subject variability, but isn't that what the CI around the median show?]
+
+## Discussion
+
+This experiment was an extension to Experiment 1.
+Through collecting larger-size data per subject, we were able to analyze the cue combination optim&lity, not only at the population level, but also at the individual level.
+The population-level analysis replicated the results of Experiment 1.
+The individual-level analysis showed that the distribution of cue combination scores had a unimodal shape (approximating a normal distribution) centered around the optimal combination.
+This finding rules out the hypotheis that optimality at the population level (obtained in Experiment 1) is a spurious finding, i.e., only obtained via the aggregation of sub-otimal strategies.
+That said, the large variance of this distribution indicates that some participants tend to over-rely on the auditory modality and others tend to over-rely on the visual modality (beyond measurement errors??).
 
@@
 We conducted an ideal observer analysis of this task whereby a model provided predictions about how information from each modality should be combined in an optimal fashion.
-The predictions of the model were tested in a series of three experiments where instances of both the form and the meaning were ambiguous with respect to their category membership only (Experiment 1), when instances of the form were perturbed with additional background noise (Experiment 2), and when instances of the referent were perturbed with additional visual noise (Experiment 3).
+The predictions of the model were tested in a series of four experiments where instances of both the form and the meaning were ambiguous with respect to their category membership only (Experiment 1 and 4), when instances of the form were perturbed with additional background noise (Experiment 2), and when instances of the referent were perturbed with additional visual noise (Experiment 3).
 We discuss the findings of these studies first with respect to our ideal observer model and inferences about optimality and second with respect to their implications for word identification more generally.
@@
 
-In all of our experiments, at the highest level, we found generally optimal behavior.
-Quantitatively speaking, the optimal model accounted, respectively, for `r 100*R2_optimal_1`%, `r 100*R2_optimal_2`%, and `r 100*R2_optimal_3`% of the variance in mean responses.
-When compared to the predictions of the visual or the auditory models, participants generally relied on both modalities to make their decisions in the bimodal condition.
+In all of our experiments,  and when compared to the predictions of the visual or the auditory models, participants generally relied on both modalities to make their decisions in the bimodal condition.
 Indeed, in Experiment 1 and 2, the optimal model accounted for more variance in mean responses than the auditory or the visual models did.
 In Experiment 3, participants appeared to rely on one modality, but this was likely a floor effect, due to the fact that noise made the visual input barely perceptible.
-Further, in Experiment 1, which did not involve background noise, participants not only relied on both modalities, but generally weighted these modalities according to the predictions of the optimal model, that is, according to their relative reliability.
+Further, in Experiment 1 and 4, which did not involve background noise, participants not only relied on both modalities, but generally weighted these modalities according to the predictions of the optimal model, that is, according to their relative reliability.
 At the individual level, however, we found evidence of a between-subject variation: Some participants relied  more on the visual modality, whereas others relied  more on the auditory modality.

### 2019-03-19 Writeup/ms.tex
revisions

@@
 \subsection{Descriptive model and analysis of
-sub-optimality}\label{descriptive-model-and-analysis-of-sub-optimality}
+(sub-)optimality}\label{descriptive-model-and-analysis-of-sub-optimality}
 
@@
 
-\paragraph{Normative models}\label{normative-models}
-
-Figure~\ref{fig:bimodal} compares the predictions of the normative
-models against human responses. Remember that the normative models use
-variance estimates from the unimodal conditions (where people see input
-from only one modality) to predict data in the bimodal condition (where
-people see input from both modalities). Figure \ref{fig:bimodal} shows
-the models' predictions comapred to human data.
-
-\paragraph{Descriptive model}\label{descriptive-model}
-
-In the descriptive model, all parameters are fit to human responses in
-the bimodal condition. The prediction of this model are shown in Figure
-\ref{fig:bimodal}. Note that the descriptive model explained almost all
-the variance, which makes it a reasonble proxy for human real
-performance in the bimodal condition. Thus, to determine the extent to
-which human data deviated from optimality, we comapred the descriptive
-and optimal models follwoing the procedure outlined above (section XX).
+Figure \ref{fig:bimodal} compares the predictions of the normative and
+descriptive models against human responses. Remember that the normative
+models use the parameters estimated from the unimodal conditions (where
+people see input from only one modality) to predict behavior in the
+bimodal condition (where people see input from both modalities). The
+descriptive model has a similar structure than the optimal model, but is
+directly fit to human responses in the bimodal condition in order to
+allow us to assess deviation from optimaity.
+
+We found, through comparing the correlation values, that the optimal
+model explained more variance than the visual and auditory models did.
+However, the optimal model was not perfect: It explained less variance
+than the descriptive model did, which indicates a deviation from
+optimality. To investigate this deviation, we compare the parameter
+values of the optimal model to the values obtaied in the decriptive
+model (Table
+\ref{tab:param}).\footnote{Note that the descriptive model explained almost all the variance in mean responses, which makes it a reasonble proxy for human real performance in the bimodal condition.}.
+We note an increase in \emph{both} the auditory and visual variances.
+This increase in noise is compatible with the fact that human responses
+appear to be pulled towards chance (i.e., the value O.5) when compared
+to the optimal model (see \ref{fig:bimodal}). Below we investigate if
+this deviation from optimality can be related to the cue combination
+strategy.
+
+\subsubsection{Cue combination}\label{cue-combination}
+
+We analyzed if the cue combination was performed in an optimal way, or
+if there was a systematic preference for one modality when making
+decisions in the bimodal condition. As explained in \ref{fig:subOptim},
+modality preference can be characterized formally as a deviation from
+the decision threshold predicted by the optimal model. The results in
+Figure \ref{fig:bias} (top) show both the decision threshold derived
+from the descriptive model (in black) and the decision threshold
+predicted by the optimal model (in red). We found that the descriptive
+and optimal decision thresholds were almost identical. Indeed,
+non-parametric resampling of the data showed no evidence of a deviation
+from the optimal prediction (Figure~\ref{fig:bias}, bottom).
 
@@
 
-\subsubsection{Analysis of optimality}\label{analysis-of-optimality}
-
-We analyzed if the cue combination was performed in an optimal way, or
-if there was a systematic preference for one modality when making
-decisions in the bimodal condition. As explained above
-(\ref{fig:subOptim}), modality preference can be characterized formally
-as a deviation from the decision threshold predicted by the optimal
-model. The results in Figure \ref{fig:bias} (top) show both the decision
-threshold derived from the descriptive model (in black) and the decision
-threshold predicted by the optimal model (in red). The deviation from
-optimality is compared to two hypothetical cases of modality preference
-(dotted lines). We found that the descriptive and optimal decision
-thresholds were almost identical. Indeed, non-parametric resampling of
-the data showed no evidence of a deviation from the optimal prediction
-(Figure~\ref{fig:bias}, bottom).
-
 \subsection{Discussion}\label{discussion}
 
-We found that the optimal model explained largely more variance than
-what can be explained with the auditory or the visual models alone. in
-addition, the high correlation with the mean human data suggests that
-the population was, overall, near-optimal. However, we see in Figure
-\ref{fig:bimodal} that the responses deviated systematically from the
-optimal prediction in that they were slightly pulled toward chance
-(i.e., the probability 0.5). This fact is due to the increase in the
-value of the variance associated with each modality (as can be noted
-from Table \ref{tab:param}). Note however that, despite this increase in
-randomness, our analysis of modality preference showed that the relative
-values of these variances were not different (Figure~\ref{fig:bias}),
-meaning that there was no evidence for a modality preference. Thus, 1)
-There was a simultaneous increase in the values of the auditory and
-visual variances in the bimodal condition compared to the unimodal
-condition, meaning that the bimodal input lead to an increase in
-response randomness, and 2) this increased randomness did not affect the
-relative weighting of both modalities, i.e., the participants was
-weighting modalities according to the relative reliability predicted by
-the optimal model. This situation corresponds to the first case of
+This experiment studied the way participants combine multimodal
+information to recognize novel words. We found that the optimal model
+explained more variance than the auditory or the visual models did,
+indicating that particiapants take into account both the auditory and
+visual cues when making a decision. That said, Figure \ref{fig:bimodal}
+shows that the participants deviated slightly --- but systematically---
+from the optimal prediction in that they were slightly pulled toward
+chance (i.e., the probability 0.5). This fact was captured by the
+increase in the value of the variance associated with each modality (as
+can be noted from Table \ref{tab:param}). Note, however, that despite
+this increase response randomness in the bimodal condition, our analysis
+of modality preference showed that the \emph{relative} values of these
+variances were not different (Figure~\ref{fig:bias}), meaning that there
+was no evidence for a modality preference.
+
+To sum up, 1) the participants used both the auditory and visual
+information, 2) they responded slightly more randomly that what was
+predicted, but 3) this increased randomness was general and did not
+influence the cue combination strategy, i.e., the participants still
+weighted modalities according to their relative reliability as predicted
+by the optimal model. This situation corresponds to the first case of
 sub-optimality described in Figure~\ref{fig:subOptim}.
@@
 responses together with their best fits. The visual data is a
-replication of the visual data in Experiment 1. As for the auditory
-data, in contrast to Experiment 1, responses were flatter, showing more
-uncertainty.
+replication of the visual data in Experiment 1. The auditory data, in
+contrast, were flatter, showing more uncertainty.
 
@@
 
-We used the values derived from the unimodal condition (Table
-\ref{tab:param}) to construct the visual, auditory and optimal models.
-In addition, we fit a descriptive model which allows us to assess real
-human performance in this condition. Figure~\ref{fig:bimodal} compares
-the predictions of these models to human responses. Note that, in
-contrast to Experiment 1, the visual model explained more variance than
-the auditory model did.
-
-\subsubsection{Analysis of optimality}\label{analysis-of-optimality-1}
-
-Figure~\ref{fig:bias} (top) shows that the participants' decision
-threshold deviated from optimality, and that this deviation was biased
-towards the visual modality (the non-noisy modality). Indeed
+We used the values derived from the unimodal condition to construct the
+visual, auditory and optimal models. In addition, we fit a descriptive
+model which allowed us to assess real human performance in this
+condition. Figure \ref{fig:bimodal} shows that, similar to Experiment 1,
+the optimal model explained more variance than the auditory and visual
+models did (note, however, that the visual model explained more variance
+than the auditory model did). Also similar to Exeperiment 1, the values
+of the variances increased in the bimodal condition (Table
+\ref{tab:param}).
+
+\subsubsection{Cue combination}\label{cue-combination-1}
+
+Here we investigated whethere the observed increase in the auditory and
+visual variances affected the relative weighting of the corresponding
+modalities. Figure~\ref{fig:bias} (top) shows that the participants'
+decision threshold deviated from optimality, and that this deviation was
+biased towards the visual modality (the non-noisy modality). Indeed
 non-parametric resampling of the data showed a decrease in the value of
@@
 
-We found, similar to Experiment 1, that the optimal model explained more
-variance than the auditory or the visual models alone (Discuss the high
-correlation, and why this not in itself a necessary but not sufficient
-indicator of optimality). We also found a similar discrepancy between
-the descriptive and optimal models as precision dropped for both the
-auditory and the visual modalities. As for the weighting scheme used by
-participants, contrary to Experiment 1 where modalities were weighted
-according to their relative reliability, we found in this experiment
+Experiment 2 tested audi-visual combination in the case where the
+auditory input was noisy. We found, similar to Experiment 1, that the
+optimal model explained more variance than the auditory or the visual
+models did. In other words, despite additional noise, participants still
+used information from the noisy modality to recognize words. We also
+found a similar discrepancy between the descriptive and optimal models
+as response randomness increased along both the auditory and the visual
+modalities. As for the relative weighting, and contrary to Experiment 1
+where modalities were weighted optimally, we found in this experiment
 that the visual modality had a greater weight than what was expected
@@
 
-In Experiment 2, we tested the case of added background noise to the
-auditory modality. In Experiment 3, we test the case of added noise to
-the visual modality.
+Whereas in Experiment 2 we tested the case of added background noise to
+the auditory modality, in Experiment 3 we test the case of added noise
+to the visual modality.
 
@@
 
-In this Experiment, we added background noise to the visual modality.
 Similar to Experiment 2, we were interested to know if participants
-would treat this new source of uncertainty as predicted by the optimal
-model, that is, according to the following weighting scheme:
+would treat additional uncertainty as predicted by the optimal model,
+that is, according to the following weighting scheme:
 \[\beta_a \propto \frac{1}{\sigma^2_{A}}\]
@@
 
-\subsection{Results and analysis}\label{results-and-analysis-1}
+\subsection{Results}\label{results-1}
 
@@
 
-For the auditory modality, our parameter estimates were. For the visual
-modality. Figure~\ref{fig:unimodal} shows responses in the unimodal
-conditions as well as the corresponding fits. The auditory data is a
-replication of the auditory data in Experiment 1. As for the visual
-data, we found that, in contrast to Experiment 1 and 2, responses were
-flatter, showing much more uncertainty.
+Figure \ref{fig:unimodal} shows responses in the unimodal conditions as
+well as the corresponding fits. The auditory data is a replication of
+the auditory data in Experiment 1. As for the visual data, we found
+that, in contrast to Experiment 1 and 2, responses were flatter, showing
+much more uncertainty.
 
@@
 
-\paragraph{Normative models}\label{normative-models-1}
-
-Figure~\ref{fig:bimodal} compares the predictions of the visual,
-auditory and optimal models to human responses. \#\#\#\# Descriptive
-model Cross-validation using half the responses to predict the other
-half yielded \(r^2=\)
-
-\paragraph{Modality preferences}\label{modality-preferences}
-
-Participants' decision threshold suggested a preference for the auditory
-modality (the non-noisy modality). Indeed non-parametric resampling of
-the data showed an increase in the value of the slope in the descriptive
-model compared to the optimal model (Figure~\ref{fig:bias}).
+Figure \ref{fig:bimodal} shows that almost all the variance was captured
+by the auditory model alone, the addition of visual information in the
+optomal model did not improve the prediction of human responses. Similar
+to Exeperiment 1 and 2, the values of the variances increased in the
+bimodal condition (Table \ref{tab:param}).
+
+\subsubsection{Cue Combination}\label{cue-combination-2}
+
+Figure \ref{fig:bias} indicates that the decision threshold was biased
+towards the auditory modality (the non-noisy modality). Indeed
+non-parametric resampling of the data showed an increase in the value of
+the slope in the descriptive model compared to the optimal model
+(Figure~\ref{fig:bias}).
 
@@
 
-We found that the optimal model accounted for almost all the variance.
-However, whereas in previous experiments the optimal model explained
-more variance than the auditory or the visual models, here the auditory
-model explained at least as much variance. Thus, though participants
-were still sensitive to variation in the noisy visual data in the
-unimodal condition, they tended to ignore this information in the
-bimodal condition, and relied almost exclusively on the non-noisy
-auditory modality. The reason why we saw this (floor) effect when we
-added noise to the visual modality (Experiment 3), and not when we added
-noise to the auditory modality (Experiment 2), is the fact that our
-visual stimuli were originally perceived less categorically and with
-less certainty than the auditory stimuli. This fact made it more likely
-for the visual categorization function to become flat and uninformative
-after a few drops in precision due to noise on the one had, and to the
-additional randomness induced by the bimodal presentation on the other
-hand.
-
-The general finding corresponds to the third case of sub-optimality
-described in Figure~\ref{fig:subOptim}. Indeed, precision dropped for
-both modalities in the bimodal condition compared to the unimodal
-condition. But the drop was much greater for the visual modality,
-resulting in a much lower weight assigned to it than what is expected
-from its reliability. Therefore, just like participants over-relied on
-the visual modality when the auditory modality was noisy (Experiment 2),
-they also over-relied on the auditory modality when the visual modality
-was noisy (Experiment 3).
-
-The past three experiments studied the problem of cue combination at the
-population level --- The models were fit to the data aggregted across
-all participants. However, optimality at the population level could be
-misleading. Imagine, for instance, that in the bimodal condition half
-the participants relied exclusively on the visual modality, whereas the
-other half relied exclusively on the auditory modality. This case could
-still lead to an aggregate behavior which appears optimal, but this
-optimality would be spurious. Thus, we need to test cue integration at
-the individual level as well. As we noted earlier, in previous
-experiments we did not have enough statistical power to fit a different
-model for each participant. In Experiment 4, below, we re-ran Experiment
-1 (where we found near optimal behavior at the population level) while
-extending its length, allowing us to collect the number of datapoints
-necessary to fit the models for each participant.
+Experiment 3 tested audi-visual combination in the case where the visual
+input was noisy. Whereas in previous experiments the optimal model
+explained more variance than the auditory or the visual models did, here
+the auditory model alone explained almost all the variance. In other
+words, though participants were sensitive to variation in the noisy
+visual input when presented in isolation (as shown in Figure
+\ref{fig:unimodal}), they tended to ignore this information when the
+visual input was presented simultaneusel with the auditory input (i.e.,
+in the bimodal condition). Instead, they relied almost exclusively on
+the non-noisy auditory
+modality.\footnote{The reason why we saw this (floor) effect when we added noise to the visual modality (Experiment 3), and not when we added noise to the auditory modality (Experiment 2), is the fact that our visual stimuli were originally perceived less categorically and with less certainty than the auditory stimuli (see Experiment 1 in \\ref{fig:unimodal}).
+This fact made it more likely for the visual categorization function to become flat and uninformative after a few drops in precision due to noise on the one had, and to the additional randomness induced by the bimodal presentation on the other hand.}
+
+This finding corresponds to the third case of sub-optimality described
+in Figure~\ref{fig:subOptim}. Indeed, precision dropped for both
+modalities in the bimodal condition compared to the unimodal condition.
+But the drop was much greater for the visual modality, resulting in a
+much lower weight assigned to it than what is expected from the optimal
+model. Therefore, just like participants over-relied on the visual
+modality when the auditory modality was noisy (Experiment 2), they also
+over-relied on the auditory modality when the visual modality was noisy
+(Experiment 3).
+
+So far we have studied the problem of cue combination at the population
+level --- the models were fit to the data aggregated across all
+participants. However, it is important to investigate individual
+variability, especially in Experiment 1 where we reported optimal cue
+combination. In fact, it is possible that a large part of the
+participants relied primarily on the visual modality and another part on
+the auditory modality. Such an extreme individual variability could
+possibly lead to an aggregate beahvior which appears optimal, but such
+optimality would be spurious. In order to rule out this extreme case, we
+need to examine the distribution of the specific cue combibination
+strategies followed by the participants.
+
+As we noted earlier, we did not have enough statistical power to fit a
+different model for each participant. Thus, in Experiment 4, below, we
+reran Experiment 1 while extending its length, allowing us to collect
+the number of datapoints necessary to fit the models for each
+participant.
 
@@
 
-We recruited a planned sample of N=XX participants from Amazon
+A planned sample of \(N =\) 100 participants was recruited online
+through Amazon Mechanical Turk. We used the same exclusion criteria as
+in both previous experiments. \(N =\) 2 participants were excluded
+because they reported having a technical problem, and N=10 participants
+were excluded because they had less than 50\% accurate responses on the
+unambiguous training trials. The final sample consisted of \(N =\) 88
+participants.
+
+We recruited a planned sample of \(N=\) 50 participants from Amazon
 Mechanical Turk. Only participants with US IP addresses and a task
@@
 having experienced a technical problem of any sort during the online
-experiment (N=XX), or if they had less than 75\% accurate responses on
-the unambiguous training trials (N=XX). The final sample consisted of N
-= XX participants. {[}I should also add how many participants I excluded
-because their models did not converge{]}. All participants provided
-informed consent before taking the
-experiment.\footnote{The sample size and exclusion criteria were specified in the pre-registration at https://osf.io/h7mzp/.}
+experiment (\(N=\) 0 ), or if they had less than 75\% accurate responses
+on the unambiguous training trials (\(N=\) 7). The final sample
+consisted of \(N =\) 43 participants. All participants provided informed
+consent before taking the
+experiment.\footnote{The sample size, exclusion criteria and the main analysese were pre-registered at https://osf.io/h7mzp/.}
 
@@
 The design and procedure were similar to Experiment 1. The only
-difference was that we increased the number of datapoints elicited per
+difference was that we increased the number of responses elicited per
 subject from 70 to 300.
 
-\subsection{Results}\label{results-1}
-
-We fit both population-level models to the aggregated data (as in
-Experiment 1), and individual models to data from each participant. For
-the populaton-level models, the results are shown in Figure
-\ref{fig:unimodal}, Figure \ref{fig:bimodal}, and Table \ref{tab:param}.
-We note that the results mirrors the patterns obtained in Experiment 1.
-
-At the individual level, we computed the distribution of optimal
-weighing relative to the fitted (i.e., descriptive) weighing and we show
-this distribution in Figure \ref{fig:weights}. The distribution centers
-around the optimal prediction (i.e., 1) with a median value of XX
-{[}XX,XX{]}. The variance of the distribution indicates that, while most
-participants were near optimal in their cue combination, part of the
-participant tended to rely predominantly on the auditory modality and
-another part tended to rely predominantly on the visual modality.
+\subsection{Results}\label{results-2}
+
+\subsubsection{Unimodal and Bimodal
+conditions}\label{unimodal-and-bimodal-conditions}
+
+In order to replicate the analysis of Experiment 1, we started by
+fitting population-level models to the aggregated data. Indeed, we found
+that the results --- as shown in Figure \ref{fig:unimodal}, Figure
+\ref{fig:bimodal}, and Table \ref{tab:param} --- mirror closely the
+patterns obtained in Experiment 1.
+
+\subsubsection{Cue combinaton}\label{cue-combinaton}
+
+We analyzed cue combination at the individual level. For each
+participant, we computed the optimal weighing,
+\(\frac{\sigma^2_{A}}{\sigma^2_{V}}\), relative to the fitted (i.e.,
+descriptive) weighing, \(\frac{\sigma^2_{Ab}}{\sigma^2_{Vb}}\). We show
+the resulting distribution in Figure \ref{fig:weights}. We found that
+the distribution centered around the optimal prediction (i.e., 1) with a
+median value of 1.07 {[}\texttt{weight.median\_low},
+\texttt{weight.median\_up}{]}.
 
@@
 larger-size data per subject, we were able to analyze the cue
-combination optimlity, not only at the population level, but also at the
-individual level. The population-level analysis replicated the results
-of Experiment 1. The individual-level analysis showed that participants'
-performance approximated a normal distribution centered around the
-optimal combination. The large variance of this distribution indicate
-that some participants tend to over-rely on the auditory modality and
-others tend to over-rely on the visual modality.
+combination optim\&lity, not only at the population level, but also at
+the individual level. The population-level analysis replicated the
+results of Experiment 1. The individual-level analysis showed that the
+distribution of cue combination scores had a unimodal shape
+(approximating a normal distribution) centered around the optimal
+combination. This finding rules out the hypotheis that optimality at the
+population level (obtained in Experiment 1) is a spurious finding, i.e.,
+only obtained via the aggregation of sub-otimal strategies. That said,
+the large variance of this distribution indicates that some participants
+tend to over-rely on the auditory modality and others tend to over-rely
+on the visual modality (beyond measurement errors??).
 
@@
 information from each modality should be combined in an optimal fashion.
-The predictions of the model were tested in a series of three
-experiments where instances of both the form and the meaning were
-ambiguous with respect to their category membership only (Experiment 1),
-when instances of the form were perturbed with additional background
-noise (Experiment 2), and when instances of the referent were perturbed
-with additional visual noise (Experiment 3). We discuss the findings of
-these studies first with respect to our ideal observer model and
-inferences about optimality and second with respect to their
-implications for word identification more generally.
+The predictions of the model were tested in a series of four experiments
+where instances of both the form and the meaning were ambiguous with
+respect to their category membership only (Experiment 1 and 4), when
+instances of the form were perturbed with additional background noise
+(Experiment 2), and when instances of the referent were perturbed with
+additional visual noise (Experiment 3). We discuss the findings of these
+studies first with respect to our ideal observer model and inferences
+about optimality and second with respect to their implications for word
+identification more generally.
 
@@
 
-In all of our experiments, at the highest level, we found generally
-optimal behavior. Quantitatively speaking, the optimal model accounted,
-respectively, for xx, xx, and xx of the variance in mean responses. When
-compared to the predictions of the visual or the auditory models,
-participants generally relied on both modalities to make their decisions
-in the bimodal condition. Indeed, in Experiment 1 and 2, the optimal
-model accounted for more variance in mean responses than the auditory or
-the visual models did. In Experiment 3, participants appeared to rely on
-one modality, but this was likely a floor effect, due to the fact that
-noise made the visual input barely perceptible. Further, in Experiment
-1, which did not involve background noise, participants not only relied
-on both modalities, but generally weighted these modalities according to
-the predictions of the optimal model, that is, according to their
-relative reliability. At the individual level, however, we found
-evidence of a between-subject variation: Some participants relied more
-on the visual modality, whereas others relied more on the auditory
-modality.
+In all of our experiments, and when compared to the predictions of the
+visual or the auditory models, participants generally relied on both
+modalities to make their decisions in the bimodal condition. Indeed, in
+Experiment 1 and 2, the optimal model accounted for more variance in
+mean responses than the auditory or the visual models did. In Experiment
+3, participants appeared to rely on one modality, but this was likely a
+floor effect, due to the fact that noise made the visual input barely
+perceptible. Further, in Experiment 1 and 4, which did not involve
+background noise, participants not only relied on both modalities, but
+generally weighted these modalities according to the predictions of the
+optimal model, that is, according to their relative reliability. At the
+individual level, however, we found evidence of a between-subject
+variation: Some participants relied more on the visual modality, whereas
+others relied more on the auditory modality.
 

### 2019-04-10 Data_and_analysis/analyses.Rmd
more revisions

@@
 
-feather::write_feather(parameters, "saved_data/parameters.feather")
+#feather::write_feather(parameters, "saved_data/parameters.feather")
 parameters <- feather::read_feather("saved_data/parameters.feather")
@@
 
-feather::write_feather(pred_uni, "saved_data/pred_uni.feather")
+#feather::write_feather(pred_uni, "saved_data/pred_uni.feather")
 pred_uni <- feather::read_feather("saved_data/pred_uni.feather")
@@
 
-feather::write_feather(pred_bimod, "saved_data/all_bimod.feather")
+#feather::write_feather(pred_bimod, "saved_data/all_bimod.feather")
 pred_bimod <- feather::read_feather("saved_data/all_bimod.feather")
 ```
+
 main plot 
@@
 
+First simulate answers based on the population level probabilistic model (we will analyse both real and simualted answers simultaneousely)
+```{r}
+#First define all models,
+
+param <- parameters %>%
+  filter(experiment =="Experiment4")
+
+vrA = param$var_s
+  bA = param$bias_s
+
+vrV = param$var_c
+  bV = param$bias_c
+
+vrAj = param$var_j_s
+vrVj = param$var_j_c
+  bj = param$bias_j
+
+# Sound only
+model_s <- function (x,y) {
+  1/(1 + (1-bA)*exp((-4/vrA)*x+(8/vrA)))
+}
+
+# Visual only
+model_c <- function (x,y) {
+  1/(1 + (1-bV)*exp((-4/vrV)*y+(8/vrV)))
+}
+
+# Optimal
+model_opt <- function (x,y) {
+
+  1/(1 + (1-bj)*exp((-4/vrA)*x+(-4/vrV)*y+(8/vrA)+(8/vrV)))
+}
+
+# Descriptive
+model_des <- function (x,y) {
+  1/(1 + (1-bj)*exp((-4/vrAj)*x+(-4/vrVj)*y+(8/vrAj)+(8/vrVj)))
+}
+
+exp4_s <- exp4_good %>% filter(condition =='sound')
+exp4_c <- exp4_good %>% filter(condition =='concept')
+exp4_j <- exp4_good %>% filter(condition =='joint')
+
+#Simulate sounds
+exp4_both_s <- exp4_s %>%
+  mutate(prob = model_s(sound_dist, concept_dist)) %>%
+  rowwise() %>%
+  mutate(answer_simu = rbinom(1, 1, prob=prob))
+
+exp4_both_c <- exp4_c %>%
+  mutate(prob = model_c(sound_dist, concept_dist)) %>%
+  rowwise() %>%
+  mutate(answer_simu = rbinom(1, 1, prob=prob))
+
+exp4_both_j <- exp4_j %>%
+  mutate(prob = model_des(sound_dist, concept_dist)) %>%
+  rowwise() %>%
+  mutate(answer_simu = rbinom(1, 1, prob=prob))
+
+#next used this new dataset to run the rest of the code
+
+```
+
 ```{r}
@@
 }
+
+fit_simu_s <- function(data) {
+  nls(answer_simu ~ 1/(1+(1-e)*exp((-4/vrA)*sound_dist+(8/vrA))), 
+                 data=data,
+                 start = list(e=0, vrA=1),
+                 nls.control(warnOnly = TRUE)) 
+}
 #Concept Unimodal
-fit_c <- function(data) {
+fit_c <- function(data, response) {
   nls(answer ~ 1/(1+(1-e)*exp((-4/vrV)*concept_dist+(8/vrV))), 
@@
 
+fit_simu_c <- function(data, response) {
+  nls(answer_simu ~ 1/(1+(1-e)*exp((-4/vrV)*concept_dist+(8/vrV))), 
+                 data=data,
+                 start = list(e=0, vrV=1),
+                 nls.control(warnOnly = TRUE)) 
+}
+
 #Joint sound-concept
-fit_j <- function(data) {
+fit_j <- function(data, response) {
   nls(answer ~1/(1+(1-e)*exp((-4/vrA_j)*sound_dist+(-4/vrV_j)*concept_dist+(8/vrA_j)+(8/vrV_j))), 
@@
 
+fit_simu_j <- function(data, response) {
+  nls(answer_simu ~1/(1+(1-e)*exp((-4/vrA_j)*sound_dist+(-4/vrV_j)*concept_dist+(8/vrA_j)+(8/vrV_j))), 
+                 data=data,
+                 start = list(e=0, vrA_j=1, vrV_j=1),
+                 nls.control(warnOnly = TRUE)) 
+}
+
 ##Fit the models for each subject
 
-exp4_good_s <- exp4_good %>% filter(condition =='sound')
-exp4_good_c <- exp4_good %>% filter(condition =='concept')
-exp4_good_j <- exp4_good %>% filter(condition =='joint')
-
 #Split data by subject 
-data_by_subj_s <- split(exp4_good_s, exp4_good_s$ID) 
-data_by_subj_c <- split(exp4_good_c, exp4_good_c$ID)
-data_by_subj_j <- split(exp4_good_j, exp4_good_j$ID)
-
-#.. and fit
+data_by_subj_s <- split(exp4_both_s, exp4_both_s$ID) 
+data_by_subj_c <- split(exp4_both_c, exp4_both_c$ID)
+data_by_subj_j <- split(exp4_both_j, exp4_both_j$ID)
+
+# fit the empirical data
 model_by_subj_s <- map(data_by_subj_s, fit_s) 
@@
 model_by_subj_j <- map(data_by_subj_j, fit_j)
+
+#.. and the simulated data
+model_by_subj_simu_s <- map(data_by_subj_s, fit_simu_s) 
+model_by_subj_simu_c <- map(data_by_subj_c, fit_simu_c)
+model_by_subj_simu_j <- map(data_by_subj_j, fit_simu_j)
+
+## Convergence info
 
@@
               variance=coefficients(model)[2], 
+              convergence=model$convInfo$stopMessage,
               ID=ID)
@@
               var_c=coefficients(model)[3],
+              convergence=model$convInfo$stopMessage,
               ID=ID)
@@
   rename(vrA_u= variance,
-         bA_u =  bias)
+         bA_u =  bias,
+         conv_A = convergence)
+
+coef_simu_s <- map2(model_by_subj_simu_s, ID, co_uni) %>%
+  bind_rows() %>%
+  rename(vrA_u= variance,
+         bA_u =  bias,
+         conv_A = convergence)
 
@@
   rename(vrV_u= variance,
-         bV_u =  bias)
+         bV_u =  bias,
+         conv_V = convergence)
+
+coef_simu_c <- map2(model_by_subj_simu_c, ID, co_uni) %>%
+  bind_rows() %>%
+  rename(vrV_u= variance,
+         bV_u =  bias,
+         conv_V = convergence)
 
@@
          vrV_j = var_c,  
-         b =  bias)
+         b =  bias,
+         conv_j = convergence)
+
+coef_simu_j <- map2(model_by_subj_simu_j, ID, co_bim) %>%
+  bind_rows() %>%
+  rename(vrA_j = var_s,
+         vrV_j = var_c,  
+         b =  bias,
+         conv_j = convergence)
 
@@
   summarise(mean = mean(answer)) %>%
+  ungroup() %>%
   left_join(coef_s) %>%
@@
   left_join(coef_j)
+
+data_models_simu <- exp_good %>%
+  filter(condition == "joint",
+         experiment == "Experiment4") %>%
+  group_by(ID, concept_dist, sound_dist) %>%
+  summarise(mean = mean(answer)) %>%
+  ungroup() %>%
+  left_join(coef_simu_s) %>%
+  left_join(coef_simu_c) %>%
+  left_join(coef_simu_j)
+
+data_models_good <- data_models %>%
+  filter(conv_A == "converged",
+         conv_V == "converged",
+         conv_j == "converged")
+
+data_models_good_simu <- data_models_simu %>%
+  filter(conv_A == "converged",
+         conv_V == "converged",
+         conv_j == "converged")
+
+N_conv <- data_models_good %>% 
+  distinct(ID) %>%
+  nrow()
+
+N_conv_simu <- data_models_good_simu %>% 
+  distinct(ID) %>%
+  nrow()
 
@@
 
-data_by_subj <- split(data_models, data_models$ID)
+data_by_subj <- split(data_models_good, data_models_good$ID)
 
@@
 ```{r}
-weight <- data_models %>%
+weight <- data_models_good %>%
   group_by(ID, vrA_u, vrV_u, vrA_j, vrV_j) %>%
@@
          weight_b = vrA_j/vrV_j) %>%
-  mutate(prop = weight_u/weight_b)
-
-feather::write_feather(weight, "ind_weights.feather")
-weight <- feather::read_feather("ind_weights.feather")
-
-weight_separate <- weight %>%
-  select(ID, weight_u, weight_b) %>%
-  gather (key, value, weight_u, weight_b)
-
-weight.boot <- boot(data=weight$prop, function(x,i) median(x[i]), R=10000)
-
-weight.ci=boot.ci(weight.boot, 
-                  conf = 0.95,
-                  type = c('perc'))
-
-#weights.dist <- weight$prop[weight$prop < 100 & weight$prop > 0.01]
-
-weight.median <- weight.ci$t0
-weight.median_low <- weight.ci$percent[4]
-weight.median_up <- weight.ci$percent[5]
-
-ggplot(data=weight, aes(x=prop, y=..count..)) +
-  geom_histogram(alpha=0.5, binwidth = 0.4)+
-  geom_vline(xintercept = weight.median, col='red')+
-  geom_vline(xintercept = weight.median_low, linetype='dashed') +
-  geom_vline(xintercept = weight.median_up, linetype='dashed') +
+  mutate(prop = weight_u/weight_b) %>%
+  mutate(type='real')
+
+weight_simu <- data_models_good_simu %>%
+  group_by(ID, vrA_u, vrV_u, vrA_j, vrV_j) %>%
+  select(ID, vrA_u, vrV_u, vrA_j, vrV_j) %>%
+  unique() %>%
+  mutate(weight_u = vrA_u/vrV_u,
+         weight_b = vrA_j/vrV_j) %>%
+  mutate(prop = weight_u/weight_b) %>%
+  mutate(type='simulated')
+
+weight_both <- weight %>%
+  bind_rows(weight_simu)
+
+#feather::write_feather(weight, "ind_weights.feather")
+#weight <- feather::read_feather("ind_weights.feather")
+
+weight_simu_low <- quantile(weight_simu$prop, 0.05)
+weight_simu_high <- quantile(weight_simu$prop, 0.95)
+
+ggplot(data=weight_both, aes(x=prop, y=..ncount..)) +
+  #geom_histogram(data=subset(weight_both, data=='real'), fill="red", alpha=0.2, binwidth = 0.4)+
+  geom_histogram(data=subset(weight_both, data=='simulated'), fill="blue", alpha=0.1, binwidth = 0.4)+
   #geom_histogram(data=subset(bimod_all, data=='simulation'), fill="blue", alpha=0.2, binwidth = 0.2)+
   #geom_histogram(binwidth = 0.2) +
+  geom_vline(xintercept = weight_simu_low, linetype='dashed') +
+  geom_vline(xintercept = weight_simu_high, linetype='dashed')+
  scale_x_log10(breaks =c(0.1,1,10)) +
@@
   theme_few()+
-  theme(aspect.ratio = 0.7) +
-  coord_cartesian(xlim=c(0.01,100))
-
-```
+  theme(aspect.ratio = 0.7) #+
+  #coord_cartesian(xlim=c(0.01,100))
+
+```
+
+Simulat random responses from the population level model
+
+First, take the real experimental data
+```{r}
+exp_exp4_s <- exp_good %>%
+  filter(condition =="sound",
+         experiment == "Experiment4")
+
+exp_exp4_c <- exp_good %>%
+  filter(condition =="concept",
+         experiment == "Experiment4")
+
+exp_exp4_j <- exp_good %>%
+  filter(condition =="joint",
+         experiment == "Experiment4")
+```
+
+Then, instead of the real answers, simulate new answers from the population-level model
+
+```{r}
+
+#What does the mean data say 
+#generate two data point from a binomial with probabilty model_fit1()
+#loop over visual and auditory distance/ or create  adataframe with
+
+#For each subject, simulate the auditory, and visual responses as well as bimodal (descriptive) mod
+
+simulations <- data.frame()
+#x <- c("ID", "bimod")
+#colnames(simlations) <- x
+
+#
+
+for (i in 1:50) {
+Simul_exp1 <- joint_all_exp1 %>%
+  select(ID, sound_dist, concept_dist) %>%
+  mutate(prob = model_fit1(sound_dist, concept_dist)) %>%
+  rowwise() %>%
+  mutate(answer = rbinom(1, 1, prob=prob))
+
+joint_bysub_sim_1 <- Simul_exp1 %>%
+  group_by(ID) %>%
+  do(fit_joint_sim_1 = glm(answer ~ concept_dist+ sound_dist, data=., family = binomial()))
+
+bimodal_bysub_sim_1 = tidy(joint_bysub_sim_1, fit_joint_sim_1) %>%
+  filter(term == 'concept_dist' | term == 'sound_dist') %>%
+  mutate(j_var = 4/(estimate)) %>%
+  select(ID, term, j_var) %>%
+  spread(term, j_var) %>%
+  rename(j_c_var = concept_dist, 
+         j_s_var = sound_dist) %>%
+  mutate(bimod = j_c_var/j_s_var) %>%
+  select(ID, bimod) %>%
+  filter(bimod > 0.1) %>%
+  filter(bimod < 10)
+
+  simulations <- bind_rows(simulations, bimodal_bysub_sim_1)
+}
+
+  #I need to take the average of this over multiple runs
+
+  bimod_sim <- simulations  %>%
+    mutate(data='simulation')
+
+  bimod_real <- bimodal_bysub_good_1  %>%
+    select(ID, bimod) %>%
+    mutate(data='real')
+
+  #n_remove <- nrow(bimod_sim)-nrow(bimod_real)
+
+  #bimod_sim <- head(bimod_sim, -n_remove)
+
+  bimod_all <- bind_rows(bimod_real, bimod_sim)
+
+```

### 2019-04-11 Data_and_analysis/analyses.Rmd
more revisions

@@
 
-#Simulate sounds
-exp4_both_s <- exp4_s %>%
+#next used this new dataset to run the rest of the code
+
+simu_s <- data.frame()
+simu_c <- data.frame()
+simu_j <- data.frame()
+#x <- c("ID", "bimod")
+#colnames(simlations) <- x
+
+#
+
+for (i in 1:50) {
+
+simu_temp_s <- exp4_s %>%
+  mutate(ID_2 = paste(ID,'_',i, sep="")) %>%
   mutate(prob = model_s(sound_dist, concept_dist)) %>%
   rowwise() %>%
-  mutate(answer_simu = rbinom(1, 1, prob=prob))
-
-exp4_both_c <- exp4_c %>%
+  mutate(answer_simu = rbinom(1, 1, prob=prob)) %>%
+  select(-ID) %>%
+  rename(ID=ID_2)
+
+simu_temp_c <- exp4_c %>%
+  mutate(ID_2 = paste(ID,'_',i, sep="")) %>%
   mutate(prob = model_c(sound_dist, concept_dist)) %>%
   rowwise() %>%
-  mutate(answer_simu = rbinom(1, 1, prob=prob))
-
-exp4_both_j <- exp4_j %>%
+  mutate(answer_simu = rbinom(1, 1, prob=prob)) %>%
+  select(-ID) %>%
+  rename(ID=ID_2)
+
+simu_temp_j <- exp4_j %>%
+  mutate(ID_2 = paste(ID,'_',i, sep="")) %>%
   mutate(prob = model_des(sound_dist, concept_dist)) %>%
   rowwise() %>%
-  mutate(answer_simu = rbinom(1, 1, prob=prob))
-
-#next used this new dataset to run the rest of the code
+  mutate(answer_simu = rbinom(1, 1, prob=prob)) %>%
+  select(-ID) %>%
+  rename(ID=ID_2)
+
+simu_s <- bind_rows(simu_s, simu_temp_s)
+simu_c <- bind_rows(simu_c, simu_temp_c)
+simu_j <- bind_rows(simu_j, simu_temp_j)
+
+}
 
@@
 
-#Split data by subject 
-data_by_subj_s <- split(exp4_both_s, exp4_both_s$ID) 
-data_by_subj_c <- split(exp4_both_c, exp4_both_c$ID)
-data_by_subj_j <- split(exp4_both_j, exp4_both_j$ID)
+#Split data by subject real
+data_by_subj_s <- split(exp4_s, exp4_s$ID) 
+data_by_subj_c <- split(exp4_c, exp4_c$ID)
+data_by_subj_j <- split(exp4_j, exp4_j$ID)
 
@@
 model_by_subj_j <- map(data_by_subj_j, fit_j)
+
+#Split data by subject simulated
+data_by_subj_s <- split(simu_s, simu_s$ID) 
+data_by_subj_c <- split(simu_c, simu_c$ID)
+data_by_subj_j <- split(simu_j, simu_j$ID)
 
@@
 
-ID <- as.list(strsplit(names(model_by_subj_s), " "))
+ID_real <- as.list(strsplit(names(model_by_subj_s), " "))
+ID_simu <- as.list(strsplit(names(model_by_subj_simu_s), " "))
 
 #Here extract ceofficients to build optimal model later
-coef_s <- map2(model_by_subj_s, ID, co_uni) %>%
+coef_s <- map2(model_by_subj_s, ID_real, co_uni) %>%
   bind_rows() %>%
@@
 
-coef_simu_s <- map2(model_by_subj_simu_s, ID, co_uni) %>%
+coef_simu_s <- map2(model_by_subj_simu_s, ID_simu, co_uni) %>%
   bind_rows() %>%
@@
 
-coef_c <- map2(model_by_subj_c, ID, co_uni) %>%
+coef_c <- map2(model_by_subj_c, ID_real, co_uni) %>%
   bind_rows() %>%
@@
 
-coef_simu_c <- map2(model_by_subj_simu_c, ID, co_uni) %>%
+coef_simu_c <- map2(model_by_subj_simu_c, ID_simu, co_uni) %>%
   bind_rows() %>%
@@
 
-coef_j <- map2(model_by_subj_j, ID, co_bim) %>%
+coef_j <- map2(model_by_subj_j, ID_real, co_bim) %>%
   bind_rows() %>%
@@
 
-coef_simu_j <- map2(model_by_subj_simu_j, ID, co_bim) %>%
+coef_simu_j <- map2(model_by_subj_simu_j, ID_simu, co_bim) %>%
   bind_rows() %>%
@@
 
-data_models_simu <- exp_good %>%
-  filter(condition == "joint",
-         experiment == "Experiment4") %>%
+data_models_simu <- simu_j %>%
   group_by(ID, concept_dist, sound_dist) %>%
@@
   nrow()
-
+```
+
+```{r}
 models <- function (subject_data) {
@@
 
-#feather::write_feather(weight, "ind_weights.feather")
+feather::write_feather(weight_both, "ind_weights.feather")
 #weight <- feather::read_feather("ind_weights.feather")
@@
 weight_simu_low <- quantile(weight_simu$prop, 0.05)
-weight_simu_high <- quantile(weight_simu$prop, 0.95)
+weight_simu_up <- quantile(weight_simu$prop, 0.95)
+
+#Number of subject relying on the visual modality (p < 0.05) and the auditory modality (p > 0.95)
+
+subj_all <- weight %>%
+  nrow()
+
+subj_vis <- weight %>%
+  filter(prop < weight_simu_low) %>%
+  nrow()
+
+subj_aud <- weight %>%
+  filter(prop > weight_simu_up) %>%
+  nrow()
 
 ggplot(data=weight_both, aes(x=prop, y=..ncount..)) +
-  #geom_histogram(data=subset(weight_both, data=='real'), fill="red", alpha=0.2, binwidth = 0.4)+
-  geom_histogram(data=subset(weight_both, data=='simulated'), fill="blue", alpha=0.1, binwidth = 0.4)+
+  geom_histogram(data=subset(weight_both, type=='real'), fill="red", alpha=0.2, binwidth = 0.4)+
+  geom_histogram(data=subset(weight_both, type=='simulated'), fill="blue", alpha=0.1, binwidth = 0.4)+
   #geom_histogram(data=subset(bimod_all, data=='simulation'), fill="blue", alpha=0.2, binwidth = 0.2)+
@@
 
-Simulat random responses from the population level model
-
-First, take the real experimental data
-```{r}
-exp_exp4_s <- exp_good %>%
-  filter(condition =="sound",
-         experiment == "Experiment4")
-
-exp_exp4_c <- exp_good %>%
-  filter(condition =="concept",
-         experiment == "Experiment4")
-
-exp_exp4_j <- exp_good %>%
-  filter(condition =="joint",
-         experiment == "Experiment4")
-```
-
-Then, instead of the real answers, simulate new answers from the population-level model
-
 ```{r}
@@
 
-simulations <- data.frame()
-#x <- c("ID", "bimod")
-#colnames(simlations) <- x
-
-#
-
-for (i in 1:50) {
-Simul_exp1 <- joint_all_exp1 %>%
-  select(ID, sound_dist, concept_dist) %>%
-  mutate(prob = model_fit1(sound_dist, concept_dist)) %>%
-  rowwise() %>%
-  mutate(answer = rbinom(1, 1, prob=prob))
-
-joint_bysub_sim_1 <- Simul_exp1 %>%
-  group_by(ID) %>%
-  do(fit_joint_sim_1 = glm(answer ~ concept_dist+ sound_dist, data=., family = binomial()))
-
-bimodal_bysub_sim_1 = tidy(joint_bysub_sim_1, fit_joint_sim_1) %>%
-  filter(term == 'concept_dist' | term == 'sound_dist') %>%
-  mutate(j_var = 4/(estimate)) %>%
-  select(ID, term, j_var) %>%
-  spread(term, j_var) %>%
-  rename(j_c_var = concept_dist, 
-         j_s_var = sound_dist) %>%
-  mutate(bimod = j_c_var/j_s_var) %>%
-  select(ID, bimod) %>%
-  filter(bimod > 0.1) %>%
-  filter(bimod < 10)
-
-  simulations <- bind_rows(simulations, bimodal_bysub_sim_1)
-}
-
-  #I need to take the average of this over multiple runs
-
-  bimod_sim <- simulations  %>%
-    mutate(data='simulation')
-
-  bimod_real <- bimodal_bysub_good_1  %>%
-    select(ID, bimod) %>%
-    mutate(data='real')
-
-  #n_remove <- nrow(bimod_sim)-nrow(bimod_real)
-
-  #bimod_sim <- head(bimod_sim, -n_remove)
-
-  bimod_all <- bind_rows(bimod_real, bimod_sim)
-
-```
+```

### 2019-04-11 Writeup/ms.Rmd
more revisions

@@
 ---
-title             : "How Optimal is Word-Referent Identification Under Multimodal Uncertainty?"
+title             : "How Optimal is Novel Word Recogntion Under Multimodal Uncertainty?"
 shorttitle        : "Word Identification Under Multimodal Uncertainty"
@@
 How do these tasks interact with one another?
-We introduce a paradigm that allows us to examine how adults identify words under joint uncertainty in the auditory and visual modalities and propose an ideal observer model of how cues in these modalities are combined optimally.
-Model predictions are tested in three experiments where word recognition is made under two kinds of uncertainty: category ambiguity and perceptual noise.
+We introduce a paradigm that allows us to examine how adults identify novel words under joint uncertainty in the auditory and visual modalities and propose an ideal observer model of how cues in these modalities are combined optimally.
+Model predictions are tested in three experiments where novel word recognition is made under two kinds of uncertainty: category ambiguity and perceptual noise.
 In all cases, the optimal model explains much of the variance in human mean judgments.
@@
 
-So far, we have only accounted for categorical variability. For instance, if the speaker generates a target production $a_t$ from an auditory category
-$p(a_t | A) \sim N(\mu_{A}, \sigma^2_{A})$, the ideal model assumes that it has direct access to this production token (i.e., $a=a_t$), and that all uncertainty is about the category membership of this token.
+So far, we have only accounted for categorical variability, i.e.,  $\sigma^2_{A} = \sigma^2_{A_C}$. For instance, if the speaker generates a target production $a_t$ from an auditory category
+$p(a_t | A) \sim N(\mu_{A}, \sigma^2_{A_C})$, the ideal model assumes that it has direct access to this production token (i.e., $a=a_t$), and that all uncertainty is about the category membership of this token.
 However, we might also want to account for internal noise in the brain and/or external noise in the environment.
 For example, the observer might not have access to the exact produced target, but only to the target perturbed by noise.
-If we assume this noise to be normally distributed, that is,  $p(a | a_t) \sim N(a_t, \sigma^2_{N_A})$, then integrating over $a_t$ leads to this new expression of the probability distribution:
-$$ p(a | A) \sim N(\mu_{A}, \sigma^2_{A}+\sigma^2_{N_A})$$
+If we assume this noise to be normally distributed, that is,  $p(a | a_t) \sim N(a_t, \sigma^2_{A_N})$, then integrating over $a_t$ leads to this new expression of the probability distribution:
+$$ p(a | A) \sim N(\mu_{A}, \sigma^2_{A_C}+\sigma^2_{A_N})$$
 Similarly, in the case of sensory noise in the visual modality, we get:
-$$ p(a | V) \sim N(\mu_{V}, \sigma^2_{V}+\sigma^2_{N_V})$$
+$$ p(a | V) \sim N(\mu_{V}, \sigma^2_{V}+\sigma^2_{V_N})$$
 Finally, using exactly the same derivation as above, we end up with the following multimodal weighting scheme in the optimal combination model (Equation 1) which takes into account both categorical and sensory variability:
 
- $$\beta_a \propto \frac{1}{\sigma^2_{A}+\sigma^2_{N_A}}$$ $$\beta_v \propto \frac{1}{\sigma^2_{V} +\sigma^2_{N_V}}.$$
+ $$\beta_a \propto \frac{1}{\sigma^2_{A_C}+\sigma^2_{A_N}}$$ 
+ $$\beta_v \propto \frac{1}{\sigma^2_{V_C} +\sigma^2_{V_N}}.$$
 
@@
 
-In this Experiment, we test the predictions of the model in the case where uncertainty is due to categorical variability only (i.e., ambiguity in terms of category membership).
-We do not add any external noise to the background and we assume that internal sensory noise is negligible compared to categorical variability ($\sigma^2_{A} \gg \sigma^2_{N_A}$ and $\sigma^2_{V} \gg \sigma^2_{N_V}$).
+In this Experiment, we test the predictions of the model in the case where uncertainty is due to categorical variability (i.e., ambiguity in terms of category membership) and inherent sensory noise only.
+We do not add any external noise to the background.
 Thus, we use the following cue weighting scheme:
 
-$$\beta_a \propto \frac{1}{\sigma^2_{A} + \sigma^2_{N_A}} \approx  \frac{1}{\sigma^2_{A} }$$
-$$\beta_v \propto \frac{1}{\sigma^2_{V} + \sigma^2_{N_V}} \approx  \frac{1}{\sigma^2_{V} }.$$
+$$\beta_a \propto \frac{1}{\sigma^2_{A}} = \frac{1}{\sigma^2_{A_C} + \sigma^2_{A_N}}$$
+$$\beta_v \propto \frac{1}{\sigma^2_{V}} = \frac{1}{\sigma^2_{V_C} + \sigma^2_{V_N}}.$$
 
@@
 
-In this Experiment, we explored the effect of added noise on performance.
+In this Experiment, we explored the effect of added envirnonmental noise $\sigma^2_{E}$ on performance.
 We tested a case where the background noise was added to the auditory modality.
-We were interested to know if participants would treat this new source of uncertainty as predicted by the optimal model, that is, according to the following weighting scheme  $$\beta_a \propto \frac{1}{\sigma^2_{A}+\sigma^2_{N_A}}$$ $$\beta_v \propto \frac{1}{\sigma^2_{V}}.$$
+We were interested to know if participants would treat this new source of uncertainty as predicted by the optimal model, that is, according to the following weighting scheme:
+
+$$\beta_a \propto \frac{1}{\sigma^2_{A}} = \frac{1}{\sigma^2_{C_A}+\sigma^2_{N_A} + \sigma^2_{E_A}}$$ 
+$$\beta_v \propto \frac{1}{\sigma^2_{V}} = \frac{1}{\sigma^2_{C_A}+\sigma^2_{N_A}}.$$
+
 The alternative hypothesis is that noise in one modality leads to a systematic preference for the non-noisy modality.
@@
 
-Similar to Experiment 2, we were interested to know if participants would treat additional uncertainty as predicted by the optimal model, that is, according to the following weighting scheme:  $$\beta_a \propto \frac{1}{\sigma^2_{A}}$$ $$\beta_v \propto \frac{1}{\sigma^2_{V}+\sigma^2_{N_V}}.$$
+Similar to Experiment 2, we were interested to know if participants would treat additional uncertainty as predicted by the optimal model, that is, according to the following weighting scheme:
+
+$$\beta_a \propto \frac{1}{\sigma^2_{A}} = \frac{1}{\sigma^2_{A_C}+\sigma^2_{A_N}}$$ 
+$$\beta_v \propto \frac{1}{\sigma^2_{V}} = \frac{1}{\sigma^2_{V_C}+\sigma^2_{V_N} + + \sigma^2_{V_E}}.$$
+
 The alternative hypothesis is that noise in the visual modality would lead to a preference for the auditory input, just like noise in the auditory modality lead to a preference for the visual input in Experiment 2.
@@
 
+# Experiment 4
+
 As we noted earlier, we did not have enough statistical power to fit a different model for each participant.
-Thus, in Experiment 4, below, we reran Experiment 1 while extending its length, allowing us to collect the number of datapoints necessary to fit the models for each participant.
-
-# Experiment 4
-
-```{r weights}
+Thus, in the current experiment, we re-ran Experiment 1 while extending its length, allowing us to collect the number of datapoints necessary to fit the models for each participant.
+
+```{r }
 
@@
 
-weight.boot <- boot(data=weight$prop, function(x,i) median(x[i]), R=10000)
-
-weight.ci=boot.ci(weight.boot, 
-                  conf = 0.95,
-                  type = c('perc'))
-
-#weights.dist <- weight$prop[weight$prop < 100 & weight$prop > 0.01]
-
-weight.median <- weight.ci$t0
-weight.median_low <- weight.ci$percent[4]
-weight.median_up <- weight.ci$percent[5]
-
-ggplot(data=weight, aes(x=prop, y=..count..)) +
-  geom_histogram(alpha=0.5, binwidth = 0.4)+
-  geom_vline(xintercept = weight.median, col='red')+
-  geom_vline(xintercept = weight.median_low, linetype='dashed') +
-  geom_vline(xintercept = weight.median_up, linetype='dashed') +
+weight_low <- quantile(subset(weight, type=='simulated')$prop, 0.025)
+weight_up <- quantile(subset(weight, type=='simulated')$prop, 0.975)
+
+subj_vis <- weight %>%
+  filter(type=='real') %>%
+  filter(prop < weight_low) %>%
+  nrow()
+
+subj_aud <- weight %>%
+  filter(type=='real') %>%
+  filter(prop > weight_up) %>%
+  nrow()
+
+weifhts_plots <- ggplot(data=weight, aes(x=prop, y=..ndensity..)) +
+  geom_histogram(data=subset(weight, type=='real'), fill="red", alpha=0.2,, binwidth = 0.4)+
+  geom_density(data=subset(weight, type=='simulated'), fill="black", alpha=0.05)+
   #geom_histogram(data=subset(bimod_all, data=='simulation'), fill="blue", alpha=0.2, binwidth = 0.2)+
   #geom_histogram(binwidth = 0.2) +
+  geom_vline(xintercept = weight_low, linetype='dashed') +
+  geom_vline(xintercept = 1, color='red') +
+  geom_vline(xintercept = weight_up, linetype='dashed')+
  scale_x_log10(breaks =c(0.1,1,10)) +
@@
   theme_few()+
-  theme(aspect.ratio = 0.7) +
-  coord_cartesian(xlim=c(0.01,100))
+  theme(aspect.ratio = 0.7) #+
+  #coord_cartesian(xlim=c(0.01,100))
 
@@
 ### Participants
-A planned sample of $N =$ `r N_all_3` participants was recruited online through Amazon Mechanical Turk.
-We used the same exclusion criteria as in both previous experiments.
-$N =$ `r N_all_3 - N_noProb_3` participants were excluded because they reported having a technical problem, and N=`r N_noProb_3 - N_good_3` participants were excluded because they had less than 50\% accurate responses on the unambiguous training trials.
-The final sample consisted of $N =$ `r N_good_3` participants.
-
 We recruited a planned sample of $N=$ `r N_all_4` participants from Amazon Mechanical Turk.
@@
 They were paid at an hourly rate of \$6/hour.
-Participants were excluded if they reported having experienced a technical problem of any sort during the online experiment ($N=$ `r N_all_4 - N_noProb_4` ), or if they had less than 75\% accurate responses on the unambiguous training trials ($N=$ `r N_noProb_4 - N_good_4`).
+Participants were excluded if they reported having experienced a technical problem of any sort during the online experiment ($N=$ `r N_all_4 - N_noProb_4`), or if they had less than 75\% accurate responses on the unambiguous training trials ($N=$ `r N_noProb_4 - N_good_4`).
 The final sample consisted of $N =$ `r N_good_4` participants.
@@
 ### Design and Procedure
-The design and procedure were similar to Experiment 1. The only difference was that we increased the number of responses elicited per subject from 70 to 300.
+The design and procedure were similar to Experiment 1.
+There were, however, two differences: 1) We increased the number of responses elicited per subject from 70 to 300, and 2) we randomized the order of the three blocks (i.e., visual-only, auditory-only, and audio-visual) *within* subject: Each participant saw the 3 blocks exactly 6 times, covering all possible ordering combinations.
+Unlike the between-subjet randomzation in Experiment 1, this choices allowed us to avoid any confounding effects due to the order of exposure.
+
+```{r weights, echo=FALSE, warning = FALSE, out.width = "\\textwidth", fig.pos = "!h", fig.cap = "The histogram shows the distribution of the participants' optimal cue weighing  relative the observed (i.e., descriptive) cue weigting (see Figure 3).
+Participant are optimal when this relative value is equal to 1 (red solid line).
+Values larger than 1 suggest over-reliance on the auditory modality whereas values lower than 1 suggest over-reliance on the visual modality.
+The density plot shows the distribution of simulated individual responses from the population-level probabilistic model.
+The dashed lines represent 95\\% confidence intreval on this simulated distribution.
+Participants that are outside this interval can be understood as over-relying on the auditory or visual modality in a non-random way (i.e., with p < 0.05)."}
+
+weifhts_plots
+
+```
 
@@
 ### Cue combinaton
-We analyzed cue combination at the individual level.
-For each participant, we computed the optimal weighing, $\frac{\sigma^2_{A}}{\sigma^2_{V}}$, relative to the fitted (i.e., descriptive) weighing, $\frac{\sigma^2_{Ab}}{\sigma^2_{Vb}}$.
+We analyzed the cue combination strategies at the individual level.
+For each participant, we computed the optimal weighing, $\frac{\sigma^2_{A}}{\sigma^2_{V}}$, relative to the observed (i.e., descriptive) weighing, $\frac{\sigma^2_{Ab}}{\sigma^2_{Vb}}$.
 We show the resulting distribution in Figure \@ref(fig:weights).
-We found that the distribution centered around the optimal prediction (i.e., 1) with a median value of `r weight.median` [`weight.median_low`, `weight.median_up`].
-
-[Here compare to random model to see whether the resuls were due to measurement errors or to genuine betwee-subject variability, but isn't that what the CI around the median show?]
+We note first that the distribution has a rather bimodal shape, centered around the optimal cue combination strategy.
+This finding rules out the hypotheis that optimality at the population level is a spurious finding, i.e., only obtained via aggregating over various sub-otimal strategies.
+
+In addition, we asked whether the observed variance in the individual distribution was due to the randomness inherent to the process of sampling from a probabilsitic model or whether it corresponded to a real between-subject variability induced by different cue weighing strategies.
+We simulated responses through sampling from the population-level models and we computed the resuting distribution of cue weighing for each simulated indivudual leading to the density function in Figure \@ref(fig:weights).
+We can observe that most empirical values fall within the 95% confidence interval of the simulated density, showing that this part of the variance can be due to mere sampling randomness.
+However, a few participants had values outide this interval, indicating that they systematically over-relied on the visual modality ($N=$ `r subj_vis`) or the auditory modality ($N=$ `r subj_aud`) with p-value$ < 0.05$.
 
@@
 This experiment was an extension to Experiment 1.
-Through collecting larger-size data per subject, we were able to analyze the cue combination optim&lity, not only at the population level, but also at the individual level.
+Through collecting larger-size data per subject, we were able to analyze the cue combination optimality, not only at the population level, but also at the individual level.
 The population-level analysis replicated the results of Experiment 1.
-The individual-level analysis showed that the distribution of cue combination scores had a unimodal shape (approximating a normal distribution) centered around the optimal combination.
-This finding rules out the hypotheis that optimality at the population level (obtained in Experiment 1) is a spurious finding, i.e., only obtained via the aggregation of sub-otimal strategies.
-That said, the large variance of this distribution indicates that some participants tend to over-rely on the auditory modality and others tend to over-rely on the visual modality (beyond measurement errors??).
+The individual-level analysis showed that the distribution of cue combination scores had a unimodal shape centered around the optimal combination, thus reflecting geuine cue combination at the individual level.
+That said, the  variance of this distribution indicates that a few participants tended to over-rely on the auditory modality and others tended to over-rely on the visual modality beyond sampling errors.
 
@@
 Further, in Experiment 1 and 4, which did not involve background noise, participants not only relied on both modalities, but generally weighted these modalities according to the predictions of the optimal model, that is, according to their relative reliability.
-At the individual level, however, we found evidence of a between-subject variation: Some participants relied  more on the visual modality, whereas others relied  more on the auditory modality.
+At the individual level, Experiment 4 showed that most participant were near-optimal.
+Only a few subjects over-relied on the auditory or visual modalities beyond sampling errors.
+
+ More generally, the idea is that it is easier to integrate correlated, redundant cues (e.g., the size of a an object based on both visual and haptic information) into a unified percept,  than it is to combine perceptually uncorrelated cues to make a categorization judgement ,e.g., recognizing a freshly learned object category based on its distinctive features such as shape and color.
+We argue that our task — which consists in combining perceptually uncorrelated cues from the auditory and visual modalities to recognize a novel word — is more similar to the second case.
 
@@
 This finding contrasts with research on  multisensory integration where associations tend to lead to a higher precision [e.g., @ernst02].
-Nevertheless, there is a crucial difference between these two situations (besides the obvious difference in terms of the models used).
-Research on  multisensory integration (of which audio-visual speech is arguably an instance) deals with redundant multimodal cues, and these cues are integrated into a unified percept.
-In contrast, the word-referent association is usually arbitrary and, in particular, the cues are not expected to be correlated perceptually.
-Therefore the observer cannot form a unified percept, rather, information must be encoded separately from both modalities and must retain this encoding through the decision making process.
-Retaining two separate cues at the same time instead of forming one unified percept (as in multisensory integration of redundant cues), or instead of retaining only one cue (as in the unimodal case), is likely to place extra demands on cognitive resources, which, in turn, could cause general performance to drop.
+Nevertheless, research on multisensory integration has typically dealt with a special case involving correlated, redundant multimodal cues, e.g., determining the size of an object based on visual and haptic information.
+Another possible case of multisensory integration involves perceptually uncorrelated cues, e.g., recognizing a novel category based on some features such as shape and color [e.g., @Bankieris17] or, in our case, recognizing novel words cues based on phonological and semantic cues.
+Perhaps it is harder to integrate uncorreated cues because information form these cues must be encoded separately through the decision making process.
+In fact, retaining two separate cues at the same time instead of forming one unified percept (as in multisensory integration of redundant cues), or instead of retaining only one cue (as in the unimodal case), is likely to place extra demands on cognitive resources, which, in turn, could cause general performance to drop.
 Indeed, there is evidence that cognitive load due to divided attention (e.g., when performing two tasks at the same time) has a detrimental effect on word recognition [@mattys11].
@@
 The second case of sub-optimality is related to how participants weighted the cues from the visual and the auditory modalities in a noisy context.
-In contrast to Experiment 1 where the combination was indistinguishable from the optimal prediction, results of Experiment 2 and 3 suggested that participants had a systematic preference for the other (non-noisy) modality.
-This finding aligns with previous work that suggests that when speech signals are degraded, participants compensate by relying more on other sources of information such as the accompanying visual cues, the semantic/syntactic context, or the top-down expectations.
+In contrast to Experiment 1 adn 4 where the combination was indistinguishable from the optimal prediction, results of Experiment 2 and 3 suggested that participants had a systematic preference for the other (non-noisy) modality.
+This finding aligns with previous work that suggests that when the auditory signal is degraded, participants compensate by relying more on other sources of information such as the accompanying visual cues, the semantic/syntactic context, or the top-down expectations.
 This kind of compensation has been observed with adults [@Tanenhaus1995; @mattys12], and recent evidence suggests that it starts in childhood [@yurovsky2017; @macdonald2018].
@@
 
-An important question to ask is how the combination mechanism -- as revealed in our controlled study -- scales up to real life situations.
+An important question to ask is how the combination mechanism --- as revealed in our controlled study --- scales up to real life situations.
 Note that in order to test audio-visual cue combination under uncertainty, we had to use a case of double ambiguity, that is, a case where both the word forms ("ada"--"aba") and the referents (cat--dog) were similar and, thus, confusable.
@@
 These studies suggest that the case of double uncertainty, though perhaps not pervasive, could be a real issue in language as it increase the probability of confusability for many words.
-That said, the inferences discussed here might play a more significant role in naturalistic language comprehension when ambiguity in both the form and/or the referent is induced by an *external* noisy context -- e.g., a very noisy party or a far away referent -- even when these forms and referents are not confusable in normal situations.
+That said, the inferences discussed here might play a more significant role in naturalistic language comprehension when ambiguity in both the form and/or the referent is induced by an *external* noisy context --- e.g., a very noisy party or a far away referent --- even when these forms and referents are not confusable in normal situations.
 
@@
 Additionally, these dimensions may be highly variable due to various kinds of speaker and context differences.
-The same thing can be said about our visual stimuli.
-Here we used a continuum along a single morph dimension in order to construct a multimodal input where the auditory and visual components have symmetrical properties.
-Though such morph is not the exact visual variability that people would encounter in their daily lives, it allowed us to precisely test the role of auditory and visual information in the cue combination process.
-Parameterizing semantic dimensions is a notoriously difficult problem, but morphs have been used in previous research as a reasonable proxy [@freedman2001; @havy2016; @sloutsky2004].
+
+As for the visual modality, simulating meaningful variability is a more difficult task.
+Indeed, parameterizing the semantic space has been a notoriously hard problem and thus requires more simplifying assumptions.
+Following previous studies [@freedman2001; @havy2016; @sloutsky2004], we used a visual continuum along a one-dimensional morph.
+This choice was motivated by the need to construct a multimodal input where the auditory and visual components are parametrized in a symmetrical fashion, allowing us to compare graded effects of auditory and visual information on categorical judgment.
+Though such a visual variability is clearly artificial (one does not encounters in real life an animal that is, e.g., 30 % dog and 70 % cat), we assume that the induced uncertainty form this visual stimuli has a similar effect on word recognition as the uncertainty induced by more naturalistic semantic variability.
+
 It is an open question whether people use the same strategy in controlled laboratory conditions and more naturalistic settings where they have to deal with various levels of variability.
@@
 
-Our work provides a formal framework where old and new questions about word recognition in a referential context can be given a precise formulation.
-While we focused on the case of arbitrary associations, it is possible to use the same framework to study, for instance, the case of \textit{iconicity}, that is, when there is a resemblance between the sound of a word and its referent.
+Our work provides a formal framework where old and new questions about word recognition as well as other categorical tasks involving uncorrelated cues can be given a precise formulation.
+We used a novel method which enabled us not only to test for optimality as in prevous studies  [e.g., @Bankieris17; @bejjanki2011], but also to examine systamtically how and by how much people deviate from optimality in their combination strategies.
+This exploration is important bla bla @rahnev2018 e.g we showed that though R^2 is large we had suboptimal behavior,;..
+
+While we focused on the case of arbitrary associations in novel word recognition, it is possible to use the same framework to study, for instance, the case of \textit{iconicity}, that is, when there is a resemblance between the sound of a word and its referent.
 Previous work has suggested that iconicity, among other things, helps with learning (and generalizing the meaning of) new words [see @dingemanse2015 for a review].
 Using the research strategy in this paper, we can, for example, test whether iconicity has such an advantage because it mitigates the sub-optimal patterns observed with more arbitrary pairings.
+
 Finally, though the current framework only characterizes adult word recognition, it provides a first step towards a model where developmental questions can also be investigated.

### 2019-04-11 Writeup/ms.tex
more revisions

@@
 \hypersetup{unicode=true,
-            pdftitle={How Optimal is Word-Referent Identification Under Multimodal Uncertainty?},
+            pdftitle={How Optimal is Novel Word Recogntion Under Multimodal Uncertainty?},
             pdfauthor={Abdellah Fourtassi~\& Michael C. Frank},
@@
 
-  \title{How Optimal is Word-Referent Identification Under Multimodal
-Uncertainty?}
+  \title{How Optimal is Novel Word Recogntion Under Multimodal Uncertainty?}
     \author{Abdellah Fourtassi\textsuperscript{1}~\& Michael C.
@@
 uncertainty. How do these tasks interact with one another? We introduce
-a paradigm that allows us to examine how adults identify words under
-joint uncertainty in the auditory and visual modalities and propose an
-ideal observer model of how cues in these modalities are combined
-optimally. Model predictions are tested in three experiments where word
-recognition is made under two kinds of uncertainty: category ambiguity
-and perceptual noise. In all cases, the optimal model explains much of
-the variance in human mean judgments. When the signal is not distorted
-with noise, participants weight the auditory and visual cues optimally,
-that is, according to the relative reliability of each modality. But
-when one modality has noise added to it, human perceivers systematically
-prefer the unperturbed modality to a greater extent than the optimal
-model does. The study provides a formal framework which helps to
-quantify how word form and word meaning interact in word recognition
-under uncertainty. Moreover it offers a first step towards a model that
-accounts for form-meaning synergies in early word learning.
+a paradigm that allows us to examine how adults identify novel words
+under joint uncertainty in the auditory and visual modalities and
+propose an ideal observer model of how cues in these modalities are
+combined optimally. Model predictions are tested in three experiments
+where novel word recognition is made under two kinds of uncertainty:
+category ambiguity and perceptual noise. In all cases, the optimal model
+explains much of the variance in human mean judgments. When the signal
+is not distorted with noise, participants weight the auditory and visual
+cues optimally, that is, according to the relative reliability of each
+modality. But when one modality has noise added to it, human perceivers
+systematically prefer the unperturbed modality to a greater extent than
+the optimal model does. The study provides a formal framework which
+helps to quantify how word form and word meaning interact in word
+recognition under uncertainty. Moreover it offers a first step towards a
+model that accounts for form-meaning synergies in early word learning.
 
@@
 
-So far, we have only accounted for categorical variability. For
-instance, if the speaker generates a target production \(a_t\) from an
-auditory category \(p(a_t | A) \sim N(\mu_{A}, \sigma^2_{A})\), the
-ideal model assumes that it has direct access to this production token
-(i.e., \(a=a_t\)), and that all uncertainty is about the category
-membership of this token. However, we might also want to account for
-internal noise in the brain and/or external noise in the environment.
-For example, the observer might not have access to the exact produced
-target, but only to the target perturbed by noise. If we assume this
-noise to be normally distributed, that is,
-\(p(a | a_t) \sim N(a_t, \sigma^2_{N_A})\), then integrating over
-\(a_t\) leads to this new expression of the probability distribution:
-\[ p(a | A) \sim N(\mu_{A}, \sigma^2_{A}+\sigma^2_{N_A})\] Similarly, in
-the case of sensory noise in the visual modality, we get:
-\[ p(a | V) \sim N(\mu_{V}, \sigma^2_{V}+\sigma^2_{N_V})\] Finally,
+So far, we have only accounted for categorical variability, i.e.,
+\(\sigma^2_{A} = \sigma^2_{A_C}\). For instance, if the speaker
+generates a target production \(a_t\) from an auditory category
+\(p(a_t | A) \sim N(\mu_{A}, \sigma^2_{A_C})\), the ideal model assumes
+that it has direct access to this production token (i.e., \(a=a_t\)),
+and that all uncertainty is about the category membership of this token.
+However, we might also want to account for internal noise in the brain
+and/or external noise in the environment. For example, the observer
+might not have access to the exact produced target, but only to the
+target perturbed by noise. If we assume this noise to be normally
+distributed, that is, \(p(a | a_t) \sim N(a_t, \sigma^2_{A_N})\), then
+integrating over \(a_t\) leads to this new expression of the probability
+distribution:
+\[ p(a | A) \sim N(\mu_{A}, \sigma^2_{A_C}+\sigma^2_{A_N})\] Similarly,
+in the case of sensory noise in the visual modality, we get:
+\[ p(a | V) \sim N(\mu_{V}, \sigma^2_{V}+\sigma^2_{V_N})\] Finally,
 using exactly the same derivation as above, we end up with the following
@@
 
-\[\beta_a \propto \frac{1}{\sigma^2_{A}+\sigma^2_{N_A}}\]
-\[\beta_v \propto \frac{1}{\sigma^2_{V} +\sigma^2_{N_V}}.\]
+\[\beta_a \propto \frac{1}{\sigma^2_{A_C}+\sigma^2_{A_N}}\]
+\[\beta_v \propto \frac{1}{\sigma^2_{V_C} +\sigma^2_{V_N}}.\]
 
@@
 In this Experiment, we test the predictions of the model in the case
-where uncertainty is due to categorical variability only (i.e.,
-ambiguity in terms of category membership). We do not add any external
-noise to the background and we assume that internal sensory noise is
-negligible compared to categorical variability
-(\(\sigma^2_{A} \gg \sigma^2_{N_A}\) and
-\(\sigma^2_{V} \gg \sigma^2_{N_V}\)). Thus, we use the following cue
+where uncertainty is due to categorical variability (i.e., ambiguity in
+terms of category membership) and inherent sensory noise only. We do not
+add any external noise to the background. Thus, we use the following cue
 weighting scheme:
 
-\[\beta_a \propto \frac{1}{\sigma^2_{A} + \sigma^2_{N_A}} \approx  \frac{1}{\sigma^2_{A} }\]
-\[\beta_v \propto \frac{1}{\sigma^2_{V} + \sigma^2_{N_V}} \approx  \frac{1}{\sigma^2_{V} }.\]
+\[\beta_a \propto \frac{1}{\sigma^2_{A}} = \frac{1}{\sigma^2_{A_C} + \sigma^2_{A_N}}\]
+\[\beta_v \propto \frac{1}{\sigma^2_{V}} = \frac{1}{\sigma^2_{V_C} + \sigma^2_{V_N}}.\]
 
@@
 
-In this Experiment, we explored the effect of added noise on
-performance. We tested a case where the background noise was added to
-the auditory modality. We were interested to know if participants would
-treat this new source of uncertainty as predicted by the optimal model,
-that is, according to the following weighting scheme
-\[\beta_a \propto \frac{1}{\sigma^2_{A}+\sigma^2_{N_A}}\]
-\[\beta_v \propto \frac{1}{\sigma^2_{V}}.\] The alternative hypothesis
-is that noise in one modality leads to a systematic preference for the
-non-noisy modality.
+In this Experiment, we explored the effect of added envirnonmental noise
+\(\sigma^2_{E}\) on performance. We tested a case where the background
+noise was added to the auditory modality. We were interested to know if
+participants would treat this new source of uncertainty as predicted by
+the optimal model, that is, according to the following weighting scheme:
+
+\[\beta_a \propto \frac{1}{\sigma^2_{A}} = \frac{1}{\sigma^2_{C_A}+\sigma^2_{N_A} + \sigma^2_{E_A}}\]
+\[\beta_v \propto \frac{1}{\sigma^2_{V}} = \frac{1}{\sigma^2_{C_A}+\sigma^2_{N_A}}.\]
+
+The alternative hypothesis is that noise in one modality leads to a
+systematic preference for the non-noisy modality.
 
@@
 that is, according to the following weighting scheme:
-\[\beta_a \propto \frac{1}{\sigma^2_{A}}\]
-\[\beta_v \propto \frac{1}{\sigma^2_{V}+\sigma^2_{N_V}}.\] The
-alternative hypothesis is that noise in the visual modality would lead
-to a preference for the auditory input, just like noise in the auditory
-modality lead to a preference for the visual input in Experiment 2.
+
+\[\beta_a \propto \frac{1}{\sigma^2_{A}} = \frac{1}{\sigma^2_{A_C}+\sigma^2_{A_N}}\]
+\[\beta_v \propto \frac{1}{\sigma^2_{V}} = \frac{1}{\sigma^2_{V_C}+\sigma^2_{V_N} + + \sigma^2_{V_E}}.\]
+
+The alternative hypothesis is that noise in the visual modality would
+lead to a preference for the auditory input, just like noise in the
+auditory modality lead to a preference for the visual input in
+Experiment 2.
 
@@
 
+\section{Experiment 4}\label{experiment-4}
+
 As we noted earlier, we did not have enough statistical power to fit a
-different model for each participant. Thus, in Experiment 4, below, we
-reran Experiment 1 while extending its length, allowing us to collect
-the number of datapoints necessary to fit the models for each
+different model for each participant. Thus, in the current experiment,
+we re-ran Experiment 1 while extending its length, allowing us to
+collect the number of datapoints necessary to fit the models for each
 participant.
 
-\section{Experiment 4}\label{experiment-4}
-
-\begin{figure}[htbp]
-\centering
-\includegraphics{ms_files/figure-latex/weights-1.pdf}
-\caption{}
-\end{figure}
-
 \subsubsection{Participants}\label{participants-3}
-
-A planned sample of \(N =\) 100 participants was recruited online
-through Amazon Mechanical Turk. We used the same exclusion criteria as
-in both previous experiments. \(N =\) 2 participants were excluded
-because they reported having a technical problem, and N=10 participants
-were excluded because they had less than 50\% accurate responses on the
-unambiguous training trials. The final sample consisted of \(N =\) 88
-participants.
 
@@
 having experienced a technical problem of any sort during the online
-experiment (\(N=\) 0 ), or if they had less than 75\% accurate responses
+experiment (\(N=\) 0), or if they had less than 75\% accurate responses
 on the unambiguous training trials (\(N=\) 7). The final sample
@@
 
-The design and procedure were similar to Experiment 1. The only
-difference was that we increased the number of responses elicited per
-subject from 70 to 300.
+The design and procedure were similar to Experiment 1. There were,
+however, two differences: 1) We increased the number of responses
+elicited per subject from 70 to 300, and 2) we randomized the order of
+the three blocks (i.e., visual-only, auditory-only, and audio-visual)
+\emph{within} subject: Each participant saw the 3 blocks exactly 6
+times, covering all possible ordering combinations. Unlike the
+between-subjet randomzation in Experiment 1, this choices allowed us to
+avoid any confounding effects due to the order of exposure.
+
+\begin{figure}[!h]
+\includegraphics[width=\textwidth]{ms_files/figure-latex/weights-1} \caption{The histogram shows the distribution of the participants' optimal cue weighing  relative the observed (i.e., descriptive) cue weigting (see Figure 3).
+Participant are optimal when this relative value is equal to 1 (red solid line).
+Values larger than 1 suggest over-reliance on the auditory modality whereas values lower than 1 suggest over-reliance on the visual modality.
+The density plot shows the distribution of simulated individual responses from the population-level probabilistic model.
+The dashed lines represent 95\% confidence intreval on this simulated distribution.
+Participants that are outside this interval can be understood as over-relying on the auditory or visual modality in a non-random way (i.e., with p < 0.05).}\label{fig:weights}
+\end{figure}
 
@@
 
-We analyzed cue combination at the individual level. For each
-participant, we computed the optimal weighing,
-\(\frac{\sigma^2_{A}}{\sigma^2_{V}}\), relative to the fitted (i.e.,
+We analyzed the cue combination strategies at the individual level. For
+each participant, we computed the optimal weighing,
+\(\frac{\sigma^2_{A}}{\sigma^2_{V}}\), relative to the observed (i.e.,
 descriptive) weighing, \(\frac{\sigma^2_{Ab}}{\sigma^2_{Vb}}\). We show
-the resulting distribution in Figure \ref{fig:weights}. We found that
-the distribution centered around the optimal prediction (i.e., 1) with a
-median value of 1.07 {[}\texttt{weight.median\_low},
-\texttt{weight.median\_up}{]}.
-
-{[}Here compare to random model to see whether the resuls were due to
-measurement errors or to genuine betwee-subject variability, but isn't
-that what the CI around the median show?{]}
+the resulting distribution in Figure \ref{fig:weights}. We note first
+that the distribution has a rather bimodal shape, centered around the
+optimal cue combination strategy. This finding rules out the hypotheis
+that optimality at the population level is a spurious finding, i.e.,
+only obtained via aggregating over various sub-otimal strategies.
+
+In addition, we asked whether the observed variance in the individual
+distribution was due to the randomness inherent to the process of
+sampling from a probabilsitic model or whether it corresponded to a real
+between-subject variability induced by different cue weighing
+strategies. We simulated responses through sampling from the
+population-level models and we computed the resuting distribution of cue
+weighing for each simulated indivudual leading to the density function
+in Figure \ref{fig:weights}. We can observe that most empirical values
+fall within the 95\% confidence interval of the simulated density,
+showing that this part of the variance can be due to mere sampling
+randomness. However, a few participants had values outide this interval,
+indicating that they systematically over-relied on the visual modality
+(\(N=\) 5) or the auditory modality (\(N=\) 6) with p-value\$
+\textless{} 0.05\$.
 
@@
 larger-size data per subject, we were able to analyze the cue
-combination optim\&lity, not only at the population level, but also at
+combination optimality, not only at the population level, but also at
 the individual level. The population-level analysis replicated the
 results of Experiment 1. The individual-level analysis showed that the
-distribution of cue combination scores had a unimodal shape
-(approximating a normal distribution) centered around the optimal
-combination. This finding rules out the hypotheis that optimality at the
-population level (obtained in Experiment 1) is a spurious finding, i.e.,
-only obtained via the aggregation of sub-otimal strategies. That said,
-the large variance of this distribution indicates that some participants
-tend to over-rely on the auditory modality and others tend to over-rely
-on the visual modality (beyond measurement errors??).
+distribution of cue combination scores had a unimodal shape centered
+around the optimal combination, thus reflecting geuine cue combination
+at the individual level. That said, the variance of this distribution
+indicates that a few participants tended to over-rely on the auditory
+modality and others tended to over-rely on the visual modality beyond
+sampling errors.
 
@@
 optimal model, that is, according to their relative reliability. At the
-individual level, however, we found evidence of a between-subject
-variation: Some participants relied more on the visual modality, whereas
-others relied more on the auditory modality.
+individual level, Experiment 4 showed that most participant were
+near-optimal. Only a few subjects over-relied on the auditory or visual
+modalities beyond sampling errors.
+
+More generally, the idea is that it is easier to integrate correlated,
+redundant cues (e.g., the size of a an object based on both visual and
+haptic information) into a unified percept, than it is to combine
+perceptually uncorrelated cues to make a categorization judgement ,e.g.,
+recognizing a freshly learned object category based on its distinctive
+features such as shape and color. We argue that our task --- which
+consists in combining perceptually uncorrelated cues from the auditory
+and visual modalities to recognize a novel word --- is more similar to
+the second case.
 
@@
 associations tend to lead to a higher precision (e.g., Ernst \& Banks,
-2002). Nevertheless, there is a crucial difference between these two
-situations (besides the obvious difference in terms of the models used).
-Research on multisensory integration (of which audio-visual speech is
-arguably an instance) deals with redundant multimodal cues, and these
-cues are integrated into a unified percept. In contrast, the
-word-referent association is usually arbitrary and, in particular, the
-cues are not expected to be correlated perceptually. Therefore the
-observer cannot form a unified percept, rather, information must be
-encoded separately from both modalities and must retain this encoding
-through the decision making process. Retaining two separate cues at the
+2002). Nevertheless, research on multisensory integration has typically
+dealt with a special case involving correlated, redundant multimodal
+cues, e.g., determining the size of an object based on visual and haptic
+information. Another possible case of multisensory integration involves
+perceptually uncorrelated cues, e.g., recognizing a novel category based
+on some features such as shape and color (e.g., Bankieris et al., 2017)
+or, in our case, recognizing novel words cues based on phonological and
+semantic cues. Perhaps it is harder to integrate uncorreated cues
+because information form these cues must be encoded separately through
+the decision making process. In fact, retaining two separate cues at the
 same time instead of forming one unified percept (as in multisensory
@@
 weighted the cues from the visual and the auditory modalities in a noisy
-context. In contrast to Experiment 1 where the combination was
+context. In contrast to Experiment 1 adn 4 where the combination was
 indistinguishable from the optimal prediction, results of Experiment 2
@@
 other (non-noisy) modality. This finding aligns with previous work that
-suggests that when speech signals are degraded, participants compensate
-by relying more on other sources of information such as the accompanying
-visual cues, the semantic/syntactic context, or the top-down
-expectations. This kind of compensation has been observed with adults
-(Mattys et al., 2012; Tanenhaus et al., 1995), and recent evidence
-suggests that it starts in childhood (K. MacDonald, Marchman, Fernald,
-\& Frank, 2018; Yurovsky, Case, \& Frank, 2017). Generally speaking,
-previous experimental studies have not differentiated between an optimal
-compensatory strategy (i.e., relying more on the alternative source
-while using all information still available in the distorted signal),
-and a sub-optimal strategy (i.e., relying more on the alternative source
-while ignoring at least some of the information still available in the
-distorted signal), however. The formal approach followed in this paper
-allowed us to tease apart these two possibilities, and our analysis
-supports the sub-optimal compensatory strategy: The preference for the
-non-noisy modality is above and beyond what can be explained by the
-relative reliability alone, meaning that the participants tend to ignore
-at least part of the information still available in the noisy modality.
+suggests that when the auditory signal is degraded, participants
+compensate by relying more on other sources of information such as the
+accompanying visual cues, the semantic/syntactic context, or the
+top-down expectations. This kind of compensation has been observed with
+adults (Mattys et al., 2012; Tanenhaus et al., 1995), and recent
+evidence suggests that it starts in childhood (K. MacDonald, Marchman,
+Fernald, \& Frank, 2018; Yurovsky, Case, \& Frank, 2017). Generally
+speaking, previous experimental studies have not differentiated between
+an optimal compensatory strategy (i.e., relying more on the alternative
+source while using all information still available in the distorted
+signal), and a sub-optimal strategy (i.e., relying more on the
+alternative source while ignoring at least some of the information still
+available in the distorted signal), however. The formal approach
+followed in this paper allowed us to tease apart these two
+possibilities, and our analysis supports the sub-optimal compensatory
+strategy: The preference for the non-noisy modality is above and beyond
+what can be explained by the relative reliability alone, meaning that
+the participants tend to ignore at least part of the information still
+available in the noisy modality.
 
@@
 
-An important question to ask is how the combination mechanism -- as
-revealed in our controlled study -- scales up to real life situations.
+An important question to ask is how the combination mechanism --- as
+revealed in our controlled study --- scales up to real life situations.
 Note that in order to test audio-visual cue combination under
@@
 in both the form and/or the referent is induced by an \emph{external}
-noisy context -- e.g., a very noisy party or a far away referent -- even
-when these forms and referents are not confusable in normal situations.
+noisy context --- e.g., a very noisy party or a far away referent ---
+even when these forms and referents are not confusable in normal
+situations.
 
@@
 be highly variable due to various kinds of speaker and context
-differences. The same thing can be said about our visual stimuli. Here
-we used a continuum along a single morph dimension in order to construct
-a multimodal input where the auditory and visual components have
-symmetrical properties. Though such morph is not the exact visual
-variability that people would encounter in their daily lives, it allowed
-us to precisely test the role of auditory and visual information in the
-cue combination process. Parameterizing semantic dimensions is a
-notoriously difficult problem, but morphs have been used in previous
-research as a reasonable proxy (Freedman et al., 2001; Havy \& Waxman,
-2016; Sloutsky \& Fisher, 2004). It is an open question whether people
-use the same strategy in controlled laboratory conditions and more
-naturalistic settings where they have to deal with various levels of
-variability. An answer to this question is likely to involve a
-multifaceted research approach that goes beyond controlled
-experimentation. We believe that one fruitful approach is to test
-computational mechanisms with an input that more accurately represents
-the full extent of multimodal variability in the learning environment
-(Dupoux, 2018; Fourtassi, Schatz, Varadarajan, \& Dupoux, 2014; Harwath,
-Torralba, \& Glass, 2016; B. C. Roy, Frank, DeCamp, \& Roy, 2015).
+differences.
+
+As for the visual modality, simulating meaningful variability is a more
+difficult task. Indeed, parameterizing the semantic space has been a
+notoriously hard problem and thus requires more simplifying assumptions.
+Following previous studies (Freedman et al., 2001; Havy \& Waxman, 2016;
+Sloutsky \& Fisher, 2004), we used a visual continuum along a
+one-dimensional morph. This choice was motivated by the need to
+construct a multimodal input where the auditory and visual components
+are parametrized in a symmetrical fashion, allowing us to compare graded
+effects of auditory and visual information on categorical judgment.
+Though such a visual variability is clearly artificial (one does not
+encounters in real life an animal that is, e.g., 30 \% dog and 70 \%
+cat), we assume that the induced uncertainty form this visual stimuli
+has a similar effect on word recognition as the uncertainty induced by
+more naturalistic semantic variability.
+
+It is an open question whether people use the same strategy in
+controlled laboratory conditions and more naturalistic settings where
+they have to deal with various levels of variability. An answer to this
+question is likely to involve a multifaceted research approach that goes
+beyond controlled experimentation. We believe that one fruitful approach
+is to test computational mechanisms with an input that more accurately
+represents the full extent of multimodal variability in the learning
+environment (Dupoux, 2018; Fourtassi, Schatz, Varadarajan, \& Dupoux,
+2014; Harwath, Torralba, \& Glass, 2016; B. C. Roy, Frank, DeCamp, \&
+Roy, 2015).
 
@@
 Our work provides a formal framework where old and new questions about
-word recognition in a referential context can be given a precise
-formulation. While we focused on the case of arbitrary associations, it
-is possible to use the same framework to study, for instance, the case
-of \textit{iconicity}, that is, when there is a resemblance between the
-sound of a word and its referent. Previous work has suggested that
-iconicity, among other things, helps with learning (and generalizing the
-meaning of) new words (see Dingemanse, Blasi, Lupyan, Christiansen, \&
-Monaghan, 2015 for a review). Using the research strategy in this paper,
-we can, for example, test whether iconicity has such an advantage
-because it mitigates the sub-optimal patterns observed with more
-arbitrary pairings. Finally, though the current framework only
-characterizes adult word recognition, it provides a first step towards a
-model where developmental questions can also be investigated. For
-instance, future work should explore whether children, like adults, use
-probabilistic cues from both the auditory and the visual input to
-recognize ambiguous words, the extent to which they combine these cues
-in an optimal fashion, and whether this cue combination help them to
-refine their early phonological and semantic representations.
+word recognition as well as other categorical tasks involving
+uncorrelated cues can be given a precise formulation. We used a novel
+method which enabled us not only to test for optimality as in prevous
+studies (e.g., Bankieris et al., 2017; Bejjanki et al., 2011), but also
+to examine systamtically how and by how much people deviate from
+optimality in their combination strategies. This exploration is
+important bla bla Rahnev and Denison (2018)
+
+While we focused on the case of arbitrary associations in novel word
+recognition, it is possible to use the same framework to study, for
+instance, the case of \textit{iconicity}, that is, when there is a
+resemblance between the sound of a word and its referent. Previous work
+has suggested that iconicity, among other things, helps with learning
+(and generalizing the meaning of) new words (see Dingemanse, Blasi,
+Lupyan, Christiansen, \& Monaghan, 2015 for a review). Using the
+research strategy in this paper, we can, for example, test whether
+iconicity has such an advantage because it mitigates the sub-optimal
+patterns observed with more arbitrary pairings.
+
+Finally, though the current framework only characterizes adult word
+recognition, it provides a first step towards a model where
+developmental questions can also be investigated. For instance, future
+work should explore whether children, like adults, use probabilistic
+cues from both the auditory and the visual input to recognize ambiguous
+words, the extent to which they combine these cues in an optimal
+fashion, and whether this cue combination help them to refine their
+early phonological and semantic representations.
 

### 2019-04-12 Data_and_analysis/analyses.Rmd
more revisions

@@
   right_join(coef_j) %>%
-  select(experiment, bias_s, var_s, bias_c, var_c, bias_j, var_j_s, var_j_c)
+  select(experiment, bias_s, var_s, bias_c, var_c, bias_j, var_j_s, var_j_c) %>%
+  mutate(bias_s = - bias_s,
+         bias_c = - bias_c, 
+         bias_j = - bias_j)
 

### 2019-04-12 Writeup/ms.Rmd
more revisions

@@
 ---
-title             : "How Optimal is Novel Word Recogntion Under Multimodal Uncertainty?"
+title             : "How Optimal is Word Recognition Under Multimodal Uncertainty?"
 shorttitle        : "Word Identification Under Multimodal Uncertainty"
@@
 How do these tasks interact with one another?
-We introduce a paradigm that allows us to examine how adults identify novel words under joint uncertainty in the auditory and visual modalities and propose an ideal observer model of how cues in these modalities are combined optimally.
-Model predictions are tested in three experiments where novel word recognition is made under two kinds of uncertainty: category ambiguity and perceptual noise.
-In all cases, the optimal model explains much of the variance in human mean judgments.
-When the signal is not distorted with noise, participants weight the auditory and visual cues optimally, that is, according to the relative reliability of each modality.
-But when one modality has noise added to it, human perceivers systematically prefer the unperturbed modality to a greater extent than the optimal model does.
-The study provides a formal framework which helps to quantify how word form and word meaning interact in word recognition under uncertainty.
-Moreover it offers a first step towards a model that accounts for form-meaning synergies in early word learning.
+We study how adults identify novel words under joint uncertainty in the auditory and visual modalities and we propose an ideal observer model of how cues in these modalities are combined optimally.
+Model predictions are tested in four experiments where recognition is made under various sources of uncertainty.
+We found that participants use both auditory and visual cues to recognize novel words.
+When the signal is not distorted with environmental noise, participants weight the auditory and visual cues optimally, that is, according to the relative reliability of each modality.
+In contrast, when one modality has noise added to it, human perceivers systematically prefer the unperturbed modality to a greater extent than the optimal model does.
+This work extends the literature of perceptual cue combination to the case of word recognition in a referential context, thus offering a first step towards a model that accounts for sound-meaning synergies in early word learning.
 
@@
 # Introduction
-Language uses symbols expressed in one modality -- the auditory modality, in the case of speech -- to communicate about the world, which we perceive through many different sensory modalities.
+Language uses symbols expressed in one modality --- the auditory modality, in the case of speech --- to communicate about the world, which we perceive through many different sensory modalities.
 Consider hearing someone yell "bee!" at a picnic, as a honey bee buzzes around the food.
@@
 A word is successfully identified when information from these modalities provide convergent evidence.
+
 However, word identification takes place in a noisy world, and the cues received through each modality may not provide a definitive answer.
@@
 For example, many studies focus on how children might succeed in this type of task despite referential ambiguity [@smith08; @pinker1989; @medina2011; @vouloumanos2008; @yurovsky2015; @suanda2014; @vlach2013].
-However, even when they *know* the meanings of a word, listeners (both children and adults) often still find it challenging to recognize which word the speaker has uttered, especially under noise [@mattys12; @peelle2018].
-The purpose of the current study is thus to explore word recognition by adults under multimodal uncertainty.
-We focus on the special case where people have access to multimodal cues from the auditory speech and the visual referent.
+However, even when they have learned the exact meaning of a word, observers (both children and adults) often still find it challenging to recognize which word the speaker has uttered, especially under noise [@mattys12; @peelle2018].
+The purpose of the current study is thus to explore word recognition by adults under multimodal uncertainty, focusing on the special case where people have access to multimodal cues from the auditory speech and the visual referent.
 In the General Discussion, we return to the question of how these findings relate to questions about word learning.
@@
 They found that humans were sensitive to these probabilistic cues and their judgments closely reflected the optimal predictions.
-And @feldman2009 studied the perceptual magnet effect, a phenomenon that involves reduced discriminability near prototypical sounds in the native language [@kuhl1991], showing that this effect can be explained as the consequence of optimally solving the problem of perception under uncertainty.
+And @feldman2009 studied the perceptual magnet effect, a phenomenon that involves reduced discriminability near prototypical sounds in the native language [@kuhl1991], showing that this effect can be explained as the consequence of optimally solving the problem of perception under uncertainty [see also @kronrod2016].
 
@@
 They showed that human performance during audio-visual phonemic labeling was consistent (at least at the qualitative level) with the predictions of an ideal observer.
-This previous research did not,  however, systematically study speech understanding when visual information was obtained through the referential context rather than through observation of speaker's face.
+This previous research did not,  however, study speech understanding when visual information was obtained through the referential context rather than through observation of speaker's face.
 Although some experimental findings show that information about the identity of a referent can be integrated with linguistic information to resolve lexical and syntactic ambiguities in speech [e.g., @Eberhard1995; @Tanenhaus1995; @spivey2002], to our knowledge no study has offered an ideal observer analysis of this task.
 
-Combining information between words and visual referents might seem similar to audio-visual speech integration, but there are at least two fundamental differences between these two cases, and both can influence the way the auditory and visual cues are combined.
+Combining information between words and visual referents might seem similar to audio-visual speech integration [e.g., @bejjanki2011], but there are at least two fundamental differences between these two cases, and both can influence the way the auditory and visual cues are combined.
 
@@
 In a referential context, however, the auditory and visual modalities play different roles in the referential process -- the auditory input represents the *symbol* whereas the visual input represents the *meaning* (and these differences are in addition to possible differences in informational reliability).
-Further, speech is claimed to have a privileged status compared to other sensory stimuli [@vouloumanos2014; @waxman2009; @waxman1995; @edmiston2015; @lupyan2012], and that this privilege is suggested to be specifically related to the ability to refer [@waxman2009].^[There is, however, a debate as to whether speech is privileged for children and adults for similar reasons.
+Further, speech is claimed to have a privileged status compared to other sensory stimuli [@vouloumanos2014; @waxman2009; @waxman1995; @edmiston2015; @lupyan2012], and this privilege is suggested to be specifically related to the ability to refer [@waxman2009].^[There is, however, a debate as to whether speech is privileged for children and adults for similar reasons.
 Whereas some researchers suggest that speech is privileged for both children and adults because of its ability to refer [e.g., @waxman2009], others suggest that speech might *not* have a referential status from the start.
@@
 
-We investigate how cues from the auditory and the visual modality are combined in recognizing words in a referential context.
+We investigate how cues from the auditory and the visual modality are combined to recognize novel words in a referential context.
 In particular, we study how this combination is performed under various degrees of uncertainty in both the auditory and the visual modality.
@@
 For instance, as mentioned above, a sub-optimality can be induced by the privileged status of a particular modality or by the arbitrariness of the referential association.
-In order to study possible patterns of sub-optimality, we compare the optimal model (which provides a normative benchmark) to a descriptive model (which is fit to human responses).
+In order to study possible patterns of sub-optimality, we compare the optimal normative model to a descriptive model (which is fit to actual responses).
 Comparing parameter estimates between these two formulations allows us to quantify the degree of deviation from optimality.
 
-We tested the ideal observer model's predictions in three behavioral experiments where we varied the source of uncertainty.
-In Experiment 1, audio-visual tokens were ambiguous with respect to their category membership only.
-In Experiment 2, we intervened by adding perceptual noise to the auditory modality, and in Experiment 3, we intervened by adding perceptual noise to the visual modality.
-In all experiments, participants were quantitatively near-optimal, though overall response precision was slightly lower than expected.
+We tested the ideal observer model's predictions in four behavioral experiments where we varied the source of uncertainty.
+In Experiment 1, audio-visual tokens were ambiguous with respect to their category membership (in addition to sensory noise).
+In Experiment 2, we intervened by adding environmental noise that degraded information from the auditory modality and in Experiment 3 we intervened by adding environmental noise that degraded information from the visual modality.
+Finally, Experiment 4 is a replication of Experiment 1 with a higher power design, allowing us to test cue combination at the individual level.
+
+<!--In all experiments, participants were quantitatively near-optimal, though overall response precision was slightly lower than expected.
 In Experiment 1 -- where neither of the modalities was perturbed with background noise -- participants weighted auditory and visual cues according to the relative reliability predicted by the optimal model.
 However, in Experiment 2 and 3, participants over-relied on one modality when the other modality was perturbed with additional noise.
+-->
 
@@
 
-We introduce a paradigm adapted from a task used by @sloutsky2003.
+We introduce an experimental paradigm adapted from a task used by @sloutsky2003.
 The original was used with both children and adults to probe audio-visual encoding [see @robinson2010 for review].
@@
 Since our task involves responses over categorical variables (phonemes and concepts), the optimal model should take into account not only the noise variability around an individual perceptual estimate but also its *categorical variability*, i.e., the uncertainty related to whether this perceptual estimate belongs to a given category [see also @Bankieris17; @bejjanki2011].
-In what follows, we describe a model that accounts for both types of variability.
+In what follows, we describe a probabilistic model that accounts for both types of variability.
 First, we describe the model in the simplified case of categorical variability only.
-Second, we augment this simplified model to account for sensory noise.
+Second, we augment this simplified model to account for sensory and envirnmental noise.
 
@@
 The optimal model (as well as the auditory and visual baselines) are *normative* models.
-Their predictions are made about human data in the bimodal condition, but their crucial parameters (i.e., variances associated with the visual and auditory modalities) are derived from data in the unimodal conditions.
+Their predictions are made about human data in the bimodal condition, but their  parameters (i.e., variances associated with the visual and auditory modalities) are derived from data in the unimodal conditions.
 In addition to these normative models, we consider a *descriptive* model.
@@
 We compared these models to human responses in three experiments.
-In Experiment 1, we studied the case where bimodal uncertainty was due to categorical variability, only.
-In Experiment 2 and 3 we added auditory and visual noise, respectively, on top of categorical variability.
+In Experiment 1, we studied the case where bimodal uncertainty was due to categorical variability and sensory noise.
+In Experiment 2 and 3 we added envirnmental noise to the auditory and the visual modalities, respectively.
 
@@
 
-In this Experiment, we test the predictions of the model in the case where uncertainty is due to categorical variability (i.e., ambiguity in terms of category membership) and inherent sensory noise only.
+In this Experiment, we test the predictions of the model in the case where uncertainty is due to categorical variability (i.e., ambiguity in terms of category membership) and inherent sensory noise.
 We do not add any external noise to the background.
-Thus, we use the following cue weighting scheme:
+Thus, we test the following (normative) cue weighting scheme:
 
@@
 The fit was done with a nonlinear least squares regression using the NLS package in R [@bates88].
-We computed the values of the parameters, as well as their 95% confidence intervals, through non-parametric bootstrap (using 10000 iterations).
+We computed the values of the parameters using non-parametric bootstrap (with 10000 iterations).
 
@@
 This fact was captured by the increase in the value of the variance associated with each modality (as can be noted from Table \@ref(tab:param)).
-Note, however, that despite this increase response randomness in the bimodal condition, our analysis of modality preference showed that the *relative* values of these variances were not different (Figure\ \@ref(fig:bias)), meaning that there was no evidence for a modality preference.
+Note, however, that despite this increase in response randomness, our analysis of modality preference showed that the *relative* values of these variances were not different (Figure\ \@ref(fig:bias)), meaning that there was no evidence for a modality preference.
 
@@
 
-In Experiment 1, we tested word recognition when there was multimodal uncertainty in terms of category membership and inherent perceptual noise, only.
+In Experiment 1, we tested word recognition when there was multimodal uncertainty in terms of category membership and perceptual noise.
 In real life, however, both sound and visual tokens can undergo distortions due to noisy factors in the environment (e.g., car noise in the background, blurry vision in a foggy weather).
@@
 So far we have studied the problem of cue combination at the population level --- the models were fit to the data aggregated across all participants.
-However, it is important to investigate individual variability, especially in Experiment 1 where we reported optimal cue combination.
-In fact, it is possible that a large part of the participants relied primarily on the visual modality and another part on the auditory modality.
-Such an extreme individual variability could possibly lead to an aggregate beahvior which appears optimal, but such optimality would be spurious.
-In order to rule out this extreme case, we need to examine the distribution of the specific cue combibination strategies followed by the participants.
+However, it is important to investigate individual variability, especially for cases when we reported optimal cue combination (i.e., Experiment 1).
+In fact, optimality at the population level can be spurious if it is obtained only on average while most individuals have sub-otimal strategies (e.g., over-relying on the visual or the auditory modalities).
+In Experiment 4, below, we examine how the average cue combination relates to individual strategies.
 
@@
 
-As we noted earlier, we did not have enough statistical power to fit a different model for each participant.
-Thus, in the current experiment, we re-ran Experiment 1 while extending its length, allowing us to collect the number of datapoints necessary to fit the models for each participant.
+As we noted earlier, we did not have enough statistical power in Experiment 1 to fit a different model for each participant.
+Thus, we used a higher power design, allowing us to collect the number of datapoints necessary to model cue combination at the individual level.
 
@@
 
-weifhts_plots <- ggplot(data=weight, aes(x=prop, y=..ndensity..)) +
+weights_plots <- ggplot(data=weight, aes(x=prop, y=..ndensity..)) +
   geom_histogram(data=subset(weight, type=='real'), fill="red", alpha=0.2,, binwidth = 0.4)+
@@
   geom_vline(xintercept = weight_up, linetype='dashed')+
+  annotate("text", x = 12, y = 0.7, size =5,  label = "Auditory bias") +
+  annotate("text", x = 0.15, y = 0.7, size =5,  label = "Visual bias") +
  scale_x_log10(breaks =c(0.1,1,10)) +
@@
 Only participants with US IP addresses and a task approval rate above 99\% were allowed to participate.
-They were paid at an hourly rate of \$6/hour.
+They were paid at an hourly rate of \$7/hour.
 Participants were excluded if they reported having experienced a technical problem of any sort during the online experiment ($N=$ `r N_all_4 - N_noProb_4`), or if they had less than 75\% accurate responses on the unambiguous training trials ($N=$ `r N_noProb_4 - N_good_4`).
@@
 There were, however, two differences: 1) We increased the number of responses elicited per subject from 70 to 300, and 2) we randomized the order of the three blocks (i.e., visual-only, auditory-only, and audio-visual) *within* subject: Each participant saw the 3 blocks exactly 6 times, covering all possible ordering combinations.
-Unlike the between-subjet randomzation in Experiment 1, this choices allowed us to avoid any confounding effects due to the order of exposure.
-
-```{r weights, echo=FALSE, warning = FALSE, out.width = "\\textwidth", fig.pos = "!h", fig.cap = "The histogram shows the distribution of the participants' optimal cue weighing  relative the observed (i.e., descriptive) cue weigting (see Figure 3).
-Participant are optimal when this relative value is equal to 1 (red solid line).
-Values larger than 1 suggest over-reliance on the auditory modality whereas values lower than 1 suggest over-reliance on the visual modality.
-The density plot shows the distribution of simulated individual responses from the population-level probabilistic model.
+Unlike the between-subjet randomzation that we used in Experiment 1, this choices allowed us to avoid a possible confound linked to the order of exposure.
+
+```{r weights, echo=FALSE, warning = FALSE, out.width = "\\textwidth", fig.pos = "!h", fig.cap = "The histogram shows the distribution of the participants' predicted (i.e., optimal) cue weighing relative the observed (i.e., descriptive) weigting (see Figure 3 for the details).
+The density plot shows the distriubtion of simulated data sampled from the population-level probabilistic model.
 The dashed lines represent 95\\% confidence intreval on this simulated distribution.
-Participants that are outside this interval can be understood as over-relying on the auditory or visual modality in a non-random way (i.e., with p < 0.05)."}
-
-weifhts_plots
+Optimal beahvior is observed when the value of the relative cue weighing is 1 (red solid line).
+Participants whose values are outside the confidence interval of the simulated dsitribution over-rely on the visual modalirty (left side) or auditory modality (right side) in a non-random way (i.e., with p < 0.05)."}
+
+weights_plots
 
@@
 We can observe that most empirical values fall within the 95% confidence interval of the simulated density, showing that this part of the variance can be due to mere sampling randomness.
-However, a few participants had values outide this interval, indicating that they systematically over-relied on the visual modality ($N=$ `r subj_vis`) or the auditory modality ($N=$ `r subj_aud`) with p-value$ < 0.05$.
+However, a few participants had values outide this interval, indicating that they systematically over-relied on the visual modality ($N=$ `r subj_vis`) or the auditory modality ($N=$ `r subj_aud`) with p-value $ < 0.05$.
 
@@
 
-In the current paper, we explored word identification under uncertainty about both words and their referents.
+In the current paper, we explored word recognition under uncertainty about both words and their referents.
 We conducted an ideal observer analysis of this task whereby a model provided predictions about how information from each modality should be combined in an optimal fashion.
@@
 Only a few subjects over-relied on the auditory or visual modalities beyond sampling errors.
-
- More generally, the idea is that it is easier to integrate correlated, redundant cues (e.g., the size of a an object based on both visual and haptic information) into a unified percept,  than it is to combine perceptually uncorrelated cues to make a categorization judgement ,e.g., recognizing a freshly learned object category based on its distinctive features such as shape and color.
-We argue that our task — which consists in combining perceptually uncorrelated cues from the auditory and visual modalities to recognize a novel word — is more similar to the second case.
-
-Despite this overall pattern, we documented two major cases of sub-optimality.
-First, in all experiments, the variance associated with each modality increased in the bimodal condition compared to the unimodal conditions.
-Participants responded slightly more randomly in the bimodal condition than they did in the unimodal conditions.
-This finding contrasts with research on  multisensory integration where associations tend to lead to a higher precision [e.g., @ernst02].
-Nevertheless, research on multisensory integration has typically dealt with a special case involving correlated, redundant multimodal cues, e.g., determining the size of an object based on visual and haptic information.
-Another possible case of multisensory integration involves perceptually uncorrelated cues, e.g., recognizing a novel category based on some features such as shape and color [e.g., @Bankieris17] or, in our case, recognizing novel words cues based on phonological and semantic cues.
-Perhaps it is harder to integrate uncorreated cues because information form these cues must be encoded separately through the decision making process.
-In fact, retaining two separate cues at the same time instead of forming one unified percept (as in multisensory integration of redundant cues), or instead of retaining only one cue (as in the unimodal case), is likely to place extra demands on cognitive resources, which, in turn, could cause general performance to drop.
-Indeed, there is evidence that cognitive load due to divided attention (e.g., when performing two tasks at the same time) has a detrimental effect on word recognition [@mattys11].
-
-Some previous research bas found similar cases of suboptimal behavior.
+<!--This finding contrasts with research on multisensory integration where associations tend to lead to a higher precision [e.g., @ernst02].
+Nevertheless, research on multisensory integration has typically dealt with correlated, redundant multimodal cues, e.g., determining the size of an object based on visual and haptic information.
+Another possible case of multisensory integration involves perceptually uncorrelated cues such as recognizing an object based on its features (e.g., shape and color) [e.g., @Bankieris17] or a word based on its phonological and semantic properties, as in the current study.
+-->
+
+Despite this overall near-optomal behavior, we documented two major cases of sub-optimality.
+First, in all experiments, the variance associated with each modality increased in the bimodal condition compared to the unimodal conditions: Participants responded slightly more randomly.
+This increase in randomness could be due limitation on cognitive resources: Retaining two separate cues at the same time instead of one cue (as in the unimodal case) is likely to place extra demands on working memory, causing general performance to drop [see @mattys11].
+
+Previous research bas found similar cases of suboptimal behavior.
 For instance, studies that have explored the identification of ambiguous, newly learned pairs of word-referent associations have reported what appears to be a decrease in speech perception acuity in both children [@stager1997] and adults [@pajak2016].
@@
 The second case of sub-optimality is related to how participants weighted the cues from the visual and the auditory modalities in a noisy context.
-In contrast to Experiment 1 adn 4 where the combination was indistinguishable from the optimal prediction, results of Experiment 2 and 3 suggested that participants had a systematic preference for the other (non-noisy) modality.
-This finding aligns with previous work that suggests that when the auditory signal is degraded, participants compensate by relying more on other sources of information such as the accompanying visual cues, the semantic/syntactic context, or the top-down expectations.
+In contrast to Experiment 1 and 4 where the cue combination was indistinguishable from the optimal predictions, results of Experiment 2 and 3 suggested that participants had a systematic preference for the non-noisy modality.
+This finding is reminiscent of the fact that humans tend to compensate for a degraded speech signal by relying more on other sources of information such as the accompanying visual cues, the semantic/syntactic context, or the top-down expectations.
 This kind of compensation has been observed with adults [@Tanenhaus1995; @mattys12], and recent evidence suggests that it starts in childhood [@yurovsky2017; @macdonald2018].
+
 Generally speaking, previous experimental studies have not differentiated between an optimal compensatory strategy (i.e., relying more on the alternative source while using all information still available in the distorted signal), and a sub-optimal strategy (i.e., relying more on the alternative source while ignoring at least some of the information still available in the distorted signal), however.
@@
 Note that in order to test audio-visual cue combination under uncertainty, we had to use a case of double ambiguity, that is, a case where both the word forms ("ada"--"aba") and the referents (cat--dog) were similar and, thus, confusable.
-However, to what extent does such a case occur in real languages?
+To what extent does such a case occur in real languages?
 Cross-linguistic corpus analyses suggest that lexical encoding tends, surprisingly, towards double ambiguity in many languages [@dautriche17; @Monaghan2014; @Tamariz2008].
@@
 Though we only studied adult performance in this paper, the problem of word recognition under uncertainty is likely more pressing for children.
-In fact, children have greater difficulties differentiating the meanings of novel similar-sounding words (e.g., "bin" vs.
+In fact, young children have greater difficulties learning the meanings of novel similar-sounding words (e.g., "bin" vs.
 "din"), even when these words are uttered very clearly [@stager1997; @Merriman91; @Creel2012; @Swingley2016; @white2008b].
@@
 
+## Limitations
+
 One salient limitation of our current work is that we used a restricted and highly simplified stimulus set.
@@
 
-As for the visual modality, simulating meaningful variability is a more difficult task.
-Indeed, parameterizing the semantic space has been a notoriously hard problem and thus requires more simplifying assumptions.
+Concerning the visual dimension, simulating meaningful variability has been a notoriousely difficult problem.
 Following previous studies [@freedman2001; @havy2016; @sloutsky2004], we used a visual continuum along a one-dimensional morph.
-This choice was motivated by the need to construct a multimodal input where the auditory and visual components are parametrized in a symmetrical fashion, allowing us to compare graded effects of auditory and visual information on categorical judgment.
+This simplification was motivated by the need to construct a multimodal input where the auditory and visual components are parametrized in a symmetrical fashion, allowing us to compare graded effects of auditory and visual information on categorical judgment.
 Though such a visual variability is clearly artificial (one does not encounters in real life an animal that is, e.g., 30 % dog and 70 % cat), we assume that the induced uncertainty form this visual stimuli has a similar effect on word recognition as the uncertainty induced by more naturalistic semantic variability.
@@
 
-# Conclusions
-
-Our work provides a formal framework where old and new questions about word recognition as well as other categorical tasks involving uncorrelated cues can be given a precise formulation.
-We used a novel method which enabled us not only to test for optimality as in prevous studies  [e.g., @Bankieris17; @bejjanki2011], but also to examine systamtically how and by how much people deviate from optimality in their combination strategies.
-This exploration is important bla bla @rahnev2018 e.g we showed that though R^2 is large we had suboptimal behavior,;..
+Finally, though we used the terminology of word recognition, our work is only indirectly related to the literature about how a *rich* lexicon is accessed [e.g., @mcclelland1986].
+We have used this term in a more specific way, describing access to a simplified lexicon made of two novel, ambiguous words.
+Such a simplified experimental context is not new and has been crucial to our understanding of early word learning and recognition [e.g., @stager1997].
+
+# Conclusions and future research directions
+
+Our work provides a formal framework where old and new questions about word recognition can be given a precise formulation.
+This framework enabled us not only to test optimality, but also to examine systamtically how and by how much people deviate from optimality in their combination strategies.
+Thus, our work is part of a growing effort to go byond optimality tests ---which have limited explanatory power--- and use models that also allow us to identify and explain various patterns of sub-otimlaity in human behavior [@rahnev2018].
 

### 2019-04-12 Writeup/ms.tex
more revisions

@@
 \hypersetup{unicode=true,
-            pdftitle={How Optimal is Novel Word Recogntion Under Multimodal Uncertainty?},
+            pdftitle={How Optimal is Word Recognition Under Multimodal Uncertainty?},
             pdfauthor={Abdellah Fourtassi~\& Michael C. Frank},
@@
 
-  \title{How Optimal is Novel Word Recogntion Under Multimodal Uncertainty?}
+  \title{How Optimal is Word Recognition Under Multimodal Uncertainty?}
     \author{Abdellah Fourtassi\textsuperscript{1}~\& Michael C.
@@
 ability to integrate multimodal input and the ability to reason under
-uncertainty. How do these tasks interact with one another? We introduce
-a paradigm that allows us to examine how adults identify novel words
-under joint uncertainty in the auditory and visual modalities and
-propose an ideal observer model of how cues in these modalities are
-combined optimally. Model predictions are tested in three experiments
-where novel word recognition is made under two kinds of uncertainty:
-category ambiguity and perceptual noise. In all cases, the optimal model
-explains much of the variance in human mean judgments. When the signal
-is not distorted with noise, participants weight the auditory and visual
-cues optimally, that is, according to the relative reliability of each
-modality. But when one modality has noise added to it, human perceivers
-systematically prefer the unperturbed modality to a greater extent than
-the optimal model does. The study provides a formal framework which
-helps to quantify how word form and word meaning interact in word
-recognition under uncertainty. Moreover it offers a first step towards a
-model that accounts for form-meaning synergies in early word learning.
+uncertainty. How do these tasks interact with one another? We study how
+adults identify novel words under joint uncertainty in the auditory and
+visual modalities and we propose an ideal observer model of how cues in
+these modalities are combined optimally. Model predictions are tested in
+four experiments where recognition is made under various sources of
+uncertainty. We found that participants use both auditory and visual
+cues to recognize novel words. When the signal is not distorted with
+environmental noise, participants weight the auditory and visual cues
+optimally, that is, according to the relative reliability of each
+modality. In contrast, when one modality has noise added to it, human
+perceivers systematically prefer the unperturbed modality to a greater
+extent than the optimal model does. This work extends the literature of
+perceptual cue combination to the case of word recognition in a
+referential context, thus offering a first step towards a model that
+accounts for sound-meaning synergies in early word learning.
 
@@
 
-Language uses symbols expressed in one modality -- the auditory
-modality, in the case of speech -- to communicate about the world, which
-we perceive through many different sensory modalities. Consider hearing
-someone yell \enquote{bee!} at a picnic, as a honey bee buzzes around
-the food. Identifying a word involves processing the auditory
+Language uses symbols expressed in one modality --- the auditory
+modality, in the case of speech --- to communicate about the world,
+which we perceive through many different sensory modalities. Consider
+hearing someone yell \enquote{bee!} at a picnic, as a honey bee buzzes
+around the food. Identifying a word involves processing the auditory
 information as well as other perceptual signals (e.g., the visual image
@@
 your arm). A word is successfully identified when information from these
-modalities provide convergent evidence. However, word identification
-takes place in a noisy world, and the cues received through each
-modality may not provide a definitive answer. On the auditory side,
-individual acoustic word tokens are almost always ambiguous with respect
-to the particular sequence of phonemes they represent, which is due to
-the inherent variability of how a phonetic category is realized
-acoustically (Hillenbrand, Getty, Clark, \& Wheeler, 1995). And some
-tokens may be distorted additionally by mispronunciation or ambient
-noise. Perhaps the speaker was yelling \enquote{pea} and not
-\enquote{bee.} Similarly, a sensory impression may not be enough to make
-a definitive identification of a visual
+modalities provide convergent evidence.
+
+However, word identification takes place in a noisy world, and the cues
+received through each modality may not provide a definitive answer. On
+the auditory side, individual acoustic word tokens are almost always
+ambiguous with respect to the particular sequence of phonemes they
+represent, which is due to the inherent variability of how a phonetic
+category is realized acoustically (Hillenbrand, Getty, Clark, \&
+Wheeler, 1995). And some tokens may be distorted additionally by
+mispronunciation or ambient noise. Perhaps the speaker was yelling
+\enquote{pea} and not \enquote{bee.} Similarly, a sensory impression may
+not be enough to make a definitive identification of a visual
 category.\footnote{In the general case, language can of course be visual as well as auditory, and object identification can be done through many modalities.
@@
 2013; Vouloumanos, 2008; Yurovsky \& Frank, 2015). However, even when
-they \emph{know} the meanings of a word, listeners (both children and
-adults) often still find it challenging to recognize which word the
+they have learned the exact meaning of a word, observers (both children
+and adults) often still find it challenging to recognize which word the
 speaker has uttered, especially under noise (Mattys, Davis, Bradlow, \&
 Scott, 2012; Peelle, 2018). The purpose of the current study is thus to
-explore word recognition by adults under multimodal uncertainty. We
-focus on the special case where people have access to multimodal cues
+explore word recognition by adults under multimodal uncertainty,
+focusing on the special case where people have access to multimodal cues
 from the auditory speech and the visual referent. In the General
@@
 1991), showing that this effect can be explained as the consequence of
-optimally solving the problem of perception under uncertainty.
+optimally solving the problem of perception under uncertainty (see also
+Kronrod, Coppess, \& Feldman, 2016).
 
@@
 qualitative level) with the predictions of an ideal observer. This
-previous research did not, however, systematically study speech
-understanding when visual information was obtained through the
-referential context rather than through observation of speaker's face.
-Although some experimental findings show that information about the
-identity of a referent can be integrated with linguistic information to
-resolve lexical and syntactic ambiguities in speech (e.g., Eberhard,
-Spivey-Knowlton, Sedivy, \& Tanenhaus, 1995; Spivey, Tanenhaus,
-Eberhard, \& Sedivy, 2002; Tanenhaus, Spivey-Knowlton, Eberhard, \&
-Sedivy, 1995), to our knowledge no study has offered an ideal observer
-analysis of this task.
+previous research did not, however, study speech understanding when
+visual information was obtained through the referential context rather
+than through observation of speaker's face. Although some experimental
+findings show that information about the identity of a referent can be
+integrated with linguistic information to resolve lexical and syntactic
+ambiguities in speech (e.g., Eberhard, Spivey-Knowlton, Sedivy, \&
+Tanenhaus, 1995; Spivey, Tanenhaus, Eberhard, \& Sedivy, 2002;
+Tanenhaus, Spivey-Knowlton, Eberhard, \& Sedivy, 1995), to our knowledge
+no study has offered an ideal observer analysis of this task.
 
 Combining information between words and visual referents might seem
-similar to audio-visual speech integration, but there are at least two
-fundamental differences between these two cases, and both can influence
-the way the auditory and visual cues are combined.
+similar to audio-visual speech integration (e.g., Bejjanki et al.,
+2011), but there are at least two fundamental differences between these
+two cases, and both can influence the way the auditory and visual cues
+are combined.
 
@@
 Thompson-Schill, 2012; Vouloumanos \& Waxman, 2014; Waxman \& Gelman,
-2009; Waxman \& Markow, 1995), and that this privilege is suggested to
-be specifically related to the ability to refer (Waxman \& Gelman,
+2009; Waxman \& Markow, 1995), and this privilege is suggested to be
+specifically related to the ability to refer (Waxman \& Gelman,
 2009).\footnote{There is, however, a debate as to whether speech is
@@
 We investigate how cues from the auditory and the visual modality are
-combined in recognizing words in a referential context. In particular,
-we study how this combination is performed under various degrees of
-uncertainty in both the auditory and the visual modality. Imagine, for
-example, that someone is uncertain whether they heard \enquote{pea} or
-\enquote{bee.} Does this uncertainty make them rely more on the referent
-(e.g., the object being pointed at)? Or, if they are not sure if they
-saw a bee or a fly, does this uncertainty make them rely more on the
-sound? More importantly, when input in both modalities is uncertain to
-varying degrees, do they weight each modality according to its relative
-reliability (the optimal strategy), or do they over-rely on a particular
-modality?
+combined to recognize novel words in a referential context. In
+particular, we study how this combination is performed under various
+degrees of uncertainty in both the auditory and the visual modality.
+Imagine, for example, that someone is uncertain whether they heard
+\enquote{pea} or \enquote{bee.} Does this uncertainty make them rely
+more on the referent (e.g., the object being pointed at)? Or, if they
+are not sure if they saw a bee or a fly, does this uncertainty make them
+rely more on the sound? More importantly, when input in both modalities
+is uncertain to varying degrees, do they weight each modality according
+to its relative reliability (the optimal strategy), or do they over-rely
+on a particular modality?
 
@@
 the arbitrariness of the referential association. In order to study
-possible patterns of sub-optimality, we compare the optimal model (which
-provides a normative benchmark) to a descriptive model (which is fit to
-human responses). Comparing parameter estimates between these two
-formulations allows us to quantify the degree of deviation from
-optimality.
-
-We tested the ideal observer model's predictions in three behavioral
+possible patterns of sub-optimality, we compare the optimal normative
+model to a descriptive model (which is fit to actual responses).
+Comparing parameter estimates between these two formulations allows us
+to quantify the degree of deviation from optimality.
+
+We tested the ideal observer model's predictions in four behavioral
 experiments where we varied the source of uncertainty. In Experiment 1,
 audio-visual tokens were ambiguous with respect to their category
-membership only. In Experiment 2, we intervened by adding perceptual
-noise to the auditory modality, and in Experiment 3, we intervened by
-adding perceptual noise to the visual modality. In all experiments,
-participants were quantitatively near-optimal, though overall response
-precision was slightly lower than expected. In Experiment 1 -- where
-neither of the modalities was perturbed with background noise --
-participants weighted auditory and visual cues according to the relative
-reliability predicted by the optimal model. However, in Experiment 2 and
-3, participants over-relied on one modality when the other modality was
-perturbed with additional noise.
+membership (in addition to sensory noise). In Experiment 2, we
+intervened by adding environmental noise that degraded information from
+the auditory modality and in Experiment 3 we intervened by adding
+environmental noise that degraded information from the visual modality.
+Finally, Experiment 4 is a replication of Experiment 1 with a higher
+power design, allowing us to test cue combination at the individual
+level.
 
@@
 
-We introduce a paradigm adapted from a task used by Sloutsky and
-Napolitano (2003). The original was used with both children and adults
-to probe audio-visual encoding (see Robinson \& Sloutsky, 2010 for
-review). Here we use a slightly different version to test word
+We introduce an experimental paradigm adapted from a task used by
+Sloutsky and Napolitano (2003). The original was used with both children
+and adults to probe audio-visual encoding (see Robinson \& Sloutsky,
+2010 for review). Here we use a slightly different version to test word
 recognition in a referential context. We use two visual categories (cat
@@
 Aslin, 2017; Bejjanki et al., 2011). In what follows, we describe a
-model that accounts for both types of variability. First, we describe
-the model in the simplified case of categorical variability only.
-Second, we augment this simplified model to account for sensory noise.
+probabilistic model that accounts for both types of variability. First,
+we describe the model in the simplified case of categorical variability
+only. Second, we augment this simplified model to account for sensory
+and envirnmental noise.
 
@@
 \emph{normative} models. Their predictions are made about human data in
-the bimodal condition, but their crucial parameters (i.e., variances
-associated with the visual and auditory modalities) are derived from
-data in the unimodal conditions. In addition to these normative models,
-we consider a \emph{descriptive} model. It is formally identical to the
-normative optimal model (Equation 1), except that the parameters are fit
-to actual responses in the bimodal condition. If the referential task
-induces sub-optimality (due, for instance, to the arbitrary nature of
-the sound-object association), then the descriptive model should explain
+the bimodal condition, but their parameters (i.e., variances associated
+with the visual and auditory modalities) are derived from data in the
+unimodal conditions. In addition to these normative models, we consider
+a \emph{descriptive} model. It is formally identical to the normative
+optimal model (Equation 1), except that the parameters are fit to actual
+responses in the bimodal condition. If the referential task induces
+sub-optimality (due, for instance, to the arbitrary nature of the
+sound-object association), then the descriptive model should explain
 more variance than the optimal model does.
@@
 Experiment 1, we studied the case where bimodal uncertainty was due to
-categorical variability, only. In Experiment 2 and 3 we added auditory
-and visual noise, respectively, on top of categorical variability.
+categorical variability and sensory noise. In Experiment 2 and 3 we
+added envirnmental noise to the auditory and the visual modalities,
+respectively.
 
@@
 where uncertainty is due to categorical variability (i.e., ambiguity in
-terms of category membership) and inherent sensory noise only. We do not
-add any external noise to the background. Thus, we use the following cue
-weighting scheme:
+terms of category membership) and inherent sensory noise. We do not add
+any external noise to the background. Thus, we test the following
+(normative) cue weighting scheme:
 
@@
 nonlinear least squares regression using the NLS package in R (Bates \&
-Watts, 1988). We computed the values of the parameters, as well as their
-95\% confidence intervals, through non-parametric bootstrap (using 10000
-iterations).
+Watts, 1988). We computed the values of the parameters using
+non-parametric bootstrap (with 10000 iterations).
 
@@
 \midrule
-Experiment1 & 0.20 & 2.04 & 0.12 & 3.33 & 0.34 & 4.96 & 7.06\\
-Experiment2 & 0.18 & 4.70 & 0.24 & 3.93 & 0.38 & 9.84 & 5.21\\
-Experiment3 & 0.24 & 1.94 & -0.11 & 13.00 & 0.35 & 3.00 & 39.42\\
-Experiment4 & 0.40 & 1.92 & 0.22 & 3.24 & 0.42 & 4.17 & 7.28\\
+Experiment1 & -0.20 & 2.04 & -0.12 & 3.33 & -0.34 & 4.96 & 7.06\\
+Experiment2 & -0.18 & 4.70 & -0.24 & 3.93 & -0.38 & 9.84 & 5.21\\
+Experiment3 & -0.24 & 1.94 & 0.11 & 13.00 & -0.35 & 3.00 & 39.42\\
+Experiment4 & -0.40 & 1.92 & -0.22 & 3.24 & -0.42 & 4.17 & 7.28\\
 \bottomrule
@@
 can be noted from Table \ref{tab:param}). Note, however, that despite
-this increase response randomness in the bimodal condition, our analysis
-of modality preference showed that the \emph{relative} values of these
-variances were not different (Figure~\ref{fig:bias}), meaning that there
-was no evidence for a modality preference.
+this increase in response randomness, our analysis of modality
+preference showed that the \emph{relative} values of these variances
+were not different (Figure~\ref{fig:bias}), meaning that there was no
+evidence for a modality preference.
 
@@
 In Experiment 1, we tested word recognition when there was multimodal
-uncertainty in terms of category membership and inherent perceptual
-noise, only. In real life, however, both sound and visual tokens can
-undergo distortions due to noisy factors in the environment (e.g., car
-noise in the background, blurry vision in a foggy weather). In
-Experiment 2 and 3, we explore this additional level of uncertainty.
+uncertainty in terms of category membership and perceptual noise. In
+real life, however, both sound and visual tokens can undergo distortions
+due to noisy factors in the environment (e.g., car noise in the
+background, blurry vision in a foggy weather). In Experiment 2 and 3, we
+explore this additional level of uncertainty.
 
@@
 participants. However, it is important to investigate individual
-variability, especially in Experiment 1 where we reported optimal cue
-combination. In fact, it is possible that a large part of the
-participants relied primarily on the visual modality and another part on
-the auditory modality. Such an extreme individual variability could
-possibly lead to an aggregate beahvior which appears optimal, but such
-optimality would be spurious. In order to rule out this extreme case, we
-need to examine the distribution of the specific cue combibination
-strategies followed by the participants.
+variability, especially for cases when we reported optimal cue
+combination (i.e., Experiment 1). In fact, optimality at the population
+level can be spurious if it is obtained only on average while most
+individuals have sub-otimal strategies (e.g., over-relying on the visual
+or the auditory modalities). In Experiment 4, below, we examine how the
+average cue combination relates to individual strategies.
 
@@
 
-As we noted earlier, we did not have enough statistical power to fit a
-different model for each participant. Thus, in the current experiment,
-we re-ran Experiment 1 while extending its length, allowing us to
-collect the number of datapoints necessary to fit the models for each
-participant.
+As we noted earlier, we did not have enough statistical power in
+Experiment 1 to fit a different model for each participant. Thus, we
+used a higher power design, allowing us to collect the number of
+datapoints necessary to model cue combination at the individual level.
 
@@
 approval rate above 99\% were allowed to participate. They were paid at
-an hourly rate of \$6/hour. Participants were excluded if they reported
+an hourly rate of \$7/hour. Participants were excluded if they reported
 having experienced a technical problem of any sort during the online
@@
 times, covering all possible ordering combinations. Unlike the
-between-subjet randomzation in Experiment 1, this choices allowed us to
-avoid any confounding effects due to the order of exposure.
+between-subjet randomzation that we used in Experiment 1, this choices
+allowed us to avoid a possible confound linked to the order of exposure.
 
 \begin{figure}[!h]
-\includegraphics[width=\textwidth]{ms_files/figure-latex/weights-1} \caption{The histogram shows the distribution of the participants' optimal cue weighing  relative the observed (i.e., descriptive) cue weigting (see Figure 3).
-Participant are optimal when this relative value is equal to 1 (red solid line).
-Values larger than 1 suggest over-reliance on the auditory modality whereas values lower than 1 suggest over-reliance on the visual modality.
-The density plot shows the distribution of simulated individual responses from the population-level probabilistic model.
+\includegraphics[width=\textwidth]{ms_files/figure-latex/weights-1} \caption{The histogram shows the distribution of the participants' predicted (i.e., optimal) cue weighing relative the observed (i.e., descriptive) weigting (see Figure 3 for the details).
+The density plot shows the distriubtion of simulated data sampled from the population-level probabilistic model.
 The dashed lines represent 95\% confidence intreval on this simulated distribution.
-Participants that are outside this interval can be understood as over-relying on the auditory or visual modality in a non-random way (i.e., with p < 0.05).}\label{fig:weights}
+Optimal beahvior is observed when the value of the relative cue weighing is 1 (red solid line).
+Participants whose values are outside the confidence interval of the simulated dsitribution over-rely on the visual modalirty (left side) or auditory modality (right side) in a non-random way (i.e., with p < 0.05).}\label{fig:weights}
 \end{figure}
@@
 indicating that they systematically over-relied on the visual modality
-(\(N=\) 5) or the auditory modality (\(N=\) 6) with p-value\$
+(\(N=\) 5) or the auditory modality (\(N=\) 6) with p-value \$
 \textless{} 0.05\$.
@@
 
-In the current paper, we explored word identification under uncertainty
+In the current paper, we explored word recognition under uncertainty
 about both words and their referents. We conducted an ideal observer
@@
 
-More generally, the idea is that it is easier to integrate correlated,
-redundant cues (e.g., the size of a an object based on both visual and
-haptic information) into a unified percept, than it is to combine
-perceptually uncorrelated cues to make a categorization judgement ,e.g.,
-recognizing a freshly learned object category based on its distinctive
-features such as shape and color. We argue that our task --- which
-consists in combining perceptually uncorrelated cues from the auditory
-and visual modalities to recognize a novel word --- is more similar to
-the second case.
-
-Despite this overall pattern, we documented two major cases of
-sub-optimality. First, in all experiments, the variance associated with
-each modality increased in the bimodal condition compared to the
-unimodal conditions. Participants responded slightly more randomly in
-the bimodal condition than they did in the unimodal conditions. This
-finding contrasts with research on multisensory integration where
-associations tend to lead to a higher precision (e.g., Ernst \& Banks,
-2002). Nevertheless, research on multisensory integration has typically
-dealt with a special case involving correlated, redundant multimodal
-cues, e.g., determining the size of an object based on visual and haptic
-information. Another possible case of multisensory integration involves
-perceptually uncorrelated cues, e.g., recognizing a novel category based
-on some features such as shape and color (e.g., Bankieris et al., 2017)
-or, in our case, recognizing novel words cues based on phonological and
-semantic cues. Perhaps it is harder to integrate uncorreated cues
-because information form these cues must be encoded separately through
-the decision making process. In fact, retaining two separate cues at the
-same time instead of forming one unified percept (as in multisensory
-integration of redundant cues), or instead of retaining only one cue (as
-in the unimodal case), is likely to place extra demands on cognitive
-resources, which, in turn, could cause general performance to drop.
-Indeed, there is evidence that cognitive load due to divided attention
-(e.g., when performing two tasks at the same time) has a detrimental
-effect on word recognition (Mattys \& Wiget, 2011).
-
-Some previous research bas found similar cases of suboptimal behavior.
-For instance, studies that have explored the identification of
-ambiguous, newly learned pairs of word-referent associations have
-reported what appears to be a decrease in speech perception acuity in
-both children (Stager \& Werker, 1997) and adults (Pajak, Creel, \&
-Levy, 2016). Recently, Hofer and Levy (2017) provided a probabilistic
-model of this phenomenon. In agreement with the findings of our study,
-Hofer and Levy (2017) characterized the apparent reduction in perceptual
-acuity as an increase in the noise variance of the auditory modality.
-Our findings, besides providing more evidence to this documented fact,
-suggest that the reduction in perceptual acuity may occur simultaneously
-in both the auditory \emph{and} the visual modalities.
+Despite this overall near-optomal behavior, we documented two major
+cases of sub-optimality. First, in all experiments, the variance
+associated with each modality increased in the bimodal condition
+compared to the unimodal conditions: Participants responded slightly
+more randomly. This increase in randomness could be due limitation on
+cognitive resources: Retaining two separate cues at the same time
+instead of one cue (as in the unimodal case) is likely to place extra
+demands on working memory, causing general performance to drop (see
+Mattys \& Wiget, 2011).
+
+Previous research bas found similar cases of suboptimal behavior. For
+instance, studies that have explored the identification of ambiguous,
+newly learned pairs of word-referent associations have reported what
+appears to be a decrease in speech perception acuity in both children
+(Stager \& Werker, 1997) and adults (Pajak, Creel, \& Levy, 2016).
+Recently, Hofer and Levy (2017) provided a probabilistic model of this
+phenomenon. In agreement with the findings of our study, Hofer and Levy
+(2017) characterized the apparent reduction in perceptual acuity as an
+increase in the noise variance of the auditory modality. Our findings,
+besides providing more evidence to this documented fact, suggest that
+the reduction in perceptual acuity may occur simultaneously in both the
+auditory \emph{and} the visual modalities.
 
@@
 weighted the cues from the visual and the auditory modalities in a noisy
-context. In contrast to Experiment 1 adn 4 where the combination was
-indistinguishable from the optimal prediction, results of Experiment 2
+context. In contrast to Experiment 1 and 4 where the cue combination was
+indistinguishable from the optimal predictions, results of Experiment 2
 and 3 suggested that participants had a systematic preference for the
-other (non-noisy) modality. This finding aligns with previous work that
-suggests that when the auditory signal is degraded, participants
-compensate by relying more on other sources of information such as the
-accompanying visual cues, the semantic/syntactic context, or the
-top-down expectations. This kind of compensation has been observed with
-adults (Mattys et al., 2012; Tanenhaus et al., 1995), and recent
-evidence suggests that it starts in childhood (K. MacDonald, Marchman,
-Fernald, \& Frank, 2018; Yurovsky, Case, \& Frank, 2017). Generally
-speaking, previous experimental studies have not differentiated between
-an optimal compensatory strategy (i.e., relying more on the alternative
-source while using all information still available in the distorted
-signal), and a sub-optimal strategy (i.e., relying more on the
-alternative source while ignoring at least some of the information still
-available in the distorted signal), however. The formal approach
-followed in this paper allowed us to tease apart these two
-possibilities, and our analysis supports the sub-optimal compensatory
-strategy: The preference for the non-noisy modality is above and beyond
-what can be explained by the relative reliability alone, meaning that
-the participants tend to ignore at least part of the information still
-available in the noisy modality.
+non-noisy modality. This finding is reminiscent of the fact that humans
+tend to compensate for a degraded speech signal by relying more on other
+sources of information such as the accompanying visual cues, the
+semantic/syntactic context, or the top-down expectations. This kind of
+compensation has been observed with adults (Mattys et al., 2012;
+Tanenhaus et al., 1995), and recent evidence suggests that it starts in
+childhood (K. MacDonald, Marchman, Fernald, \& Frank, 2018; Yurovsky,
+Case, \& Frank, 2017).
+
+Generally speaking, previous experimental studies have not
+differentiated between an optimal compensatory strategy (i.e., relying
+more on the alternative source while using all information still
+available in the distorted signal), and a sub-optimal strategy (i.e.,
+relying more on the alternative source while ignoring at least some of
+the information still available in the distorted signal), however. The
+formal approach followed in this paper allowed us to tease apart these
+two possibilities, and our analysis supports the sub-optimal
+compensatory strategy: The preference for the non-noisy modality is
+above and beyond what can be explained by the relative reliability
+alone, meaning that the participants tend to ignore at least part of the
+information still available in the noisy modality.
 
@@
 where both the word forms (\enquote{ada}--\enquote{aba}) and the
-referents (cat--dog) were similar and, thus, confusable. However, to
-what extent does such a case occur in real languages? Cross-linguistic
-corpus analyses suggest that lexical encoding tends, surprisingly,
-towards double ambiguity in many languages (Dautriche, Mahowald, Gibson,
-\& Piantadosi, 2017; Monaghan, Shillcock, Christiansen, \& Kirby, 2014;
+referents (cat--dog) were similar and, thus, confusable. To what extent
+does such a case occur in real languages? Cross-linguistic corpus
+analyses suggest that lexical encoding tends, surprisingly, towards
+double ambiguity in many languages (Dautriche, Mahowald, Gibson, \&
+Piantadosi, 2017; Monaghan, Shillcock, Christiansen, \& Kirby, 2014;
 Tamariz, 2008). For instance, Dautriche et al. (2017) analyzed 100
@@
 word recognition under uncertainty is likely more pressing for children.
-In fact, children have greater difficulties differentiating the meanings
+In fact, young children have greater difficulties learning the meanings
 of novel similar-sounding words (e.g., \enquote{bin} vs. \enquote{din}),
@@
 
+\subsection{Limitations}\label{limitations}
+
 One salient limitation of our current work is that we used a restricted
@@
 
-As for the visual modality, simulating meaningful variability is a more
-difficult task. Indeed, parameterizing the semantic space has been a
-notoriously hard problem and thus requires more simplifying assumptions.
-Following previous studies (Freedman et al., 2001; Havy \& Waxman, 2016;
-Sloutsky \& Fisher, 2004), we used a visual continuum along a
-one-dimensional morph. This choice was motivated by the need to
-construct a multimodal input where the auditory and visual components
-are parametrized in a symmetrical fashion, allowing us to compare graded
-effects of auditory and visual information on categorical judgment.
-Though such a visual variability is clearly artificial (one does not
-encounters in real life an animal that is, e.g., 30 \% dog and 70 \%
-cat), we assume that the induced uncertainty form this visual stimuli
-has a similar effect on word recognition as the uncertainty induced by
-more naturalistic semantic variability.
+Concerning the visual dimension, simulating meaningful variability has
+been a notoriousely difficult problem. Following previous studies
+(Freedman et al., 2001; Havy \& Waxman, 2016; Sloutsky \& Fisher, 2004),
+we used a visual continuum along a one-dimensional morph. This
+simplification was motivated by the need to construct a multimodal input
+where the auditory and visual components are parametrized in a
+symmetrical fashion, allowing us to compare graded effects of auditory
+and visual information on categorical judgment. Though such a visual
+variability is clearly artificial (one does not encounters in real life
+an animal that is, e.g., 30 \% dog and 70 \% cat), we assume that the
+induced uncertainty form this visual stimuli has a similar effect on
+word recognition as the uncertainty induced by more naturalistic
+semantic variability.
 
@@
 
-\section{Conclusions}\label{conclusions}
+Finally, though we used the terminology of word recognition, our work is
+only indirectly related to the literature about how a \emph{rich}
+lexicon is accessed (e.g., McClelland \& Elman, 1986). We have used this
+term in a more specific way, describing access to a simplified lexicon
+made of two novel, ambiguous words. Such a simplified experimental
+context is not new and has been crucial to our understanding of early
+word learning and recognition (e.g., Stager \& Werker, 1997).
+
+\section{Conclusions and future research
+directions}\label{conclusions-and-future-research-directions}
 
 Our work provides a formal framework where old and new questions about
-word recognition as well as other categorical tasks involving
-uncorrelated cues can be given a precise formulation. We used a novel
-method which enabled us not only to test for optimality as in prevous
-studies (e.g., Bankieris et al., 2017; Bejjanki et al., 2011), but also
-to examine systamtically how and by how much people deviate from
-optimality in their combination strategies. This exploration is
-important bla bla Rahnev and Denison (2018)
+word recognition can be given a precise formulation. This framework
+enabled us not only to test optimality, but also to examine
+systamtically how and by how much people deviate from optimality in
+their combination strategies. Thus, our work is part of a growing effort
+to go byond optimality tests ---which have limited explanatory power---
+and use models that also allow us to identify and explain various
+patterns of sub-otimlaity in human behavior (Rahnev \& Denison, 2018).
 
@@
 
+\hypertarget{ref-kronrod2016}{}
+Kronrod, Y., Coppess, E., \& Feldman, N. (2016). A unified account of
+categorical effects in phonetic perception. \emph{Psychonomic Bulletin
+\& Review}, \emph{23}(6).
+
 \hypertarget{ref-kuhl1991}{}
@@
 
+\hypertarget{ref-mcclelland1986}{}
+McClelland, J. L., \& Elman, J. L. (1986). The trace model of speech
+perception. \emph{Cognitive Psychology}, \emph{18}(1).
+
 \hypertarget{ref-mcgurk1976}{}

### 2019-04-12 Writeup/ms.Rmd
more revisions

@@
 In contrast, when one modality has noise added to it, human perceivers systematically prefer the unperturbed modality to a greater extent than the optimal model does.
-This work extends the literature of perceptual cue combination to the case of word recognition in a referential context, thus offering a first step towards a model that accounts for sound-meaning synergies in early word learning.
+This work extends the literature on perceptual cue combination to the case of word recognition in a referential context.
+In addition, this context offers a link to the study of multimodal information in word meaning learning.
 
@@
 First, we describe the model in the simplified case of categorical variability only.
-Second, we augment this simplified model to account for sensory and envirnmental noise.
+Second, we augment this simplified model to account for sensory and environmental noise.
 
@@
 In Experiment 1, we studied the case where bimodal uncertainty was due to categorical variability and sensory noise.
-In Experiment 2 and 3 we added envirnmental noise to the auditory and the visual modalities, respectively.
+In Experiment 2 and 3 we added environmental noise to the auditory and the visual modalities, respectively.
 
@@
 Only participants with US IP addresses and a task approval rate above 85\% were allowed to participate.
-They were paid at an hourly rate of \$6/hour.
 Participants were excluded if they reported having experienced a technical problem of any sort during the online experiment (N=`r N_all_1 - N_noProb_1`), or if they had less than 50\% accurate responses on the unambiguous training trials (N=`r N_noProb_1 - N_good_1`).
@@
 Remember that the normative models use the parameters estimated from the unimodal conditions (where people see input from only one modality) to predict behavior in the bimodal condition (where people see input from both modalities).
-The descriptive model has a similar structure than the optimal model, but is directly fit to human responses in the bimodal condition in order to allow us to assess deviation from optimaity.
+The descriptive model has a similar structure than the optimal model, but is directly fit to human responses in the bimodal condition in order to allow us to assess deviation from optimality.
 
@@
 However, the optimal model was not perfect: It explained less variance than the descriptive model did, which indicates a deviation from optimality.
-To investigate this deviation, we compare the parameter values of the optimal model to the values obtaied in the decriptive model (Table \@ref(tab:param)).\footnote{Note that the descriptive model explained almost all the variance in mean responses, which makes it a reasonble proxy for human real performance in the bimodal condition.}.
+To investigate this deviation, we compare the parameter values of the optimal model to the values obtained in the descriptive model (Table \@ref(tab:param)).\footnote{Note that the descriptive model explained almost all the variance in mean responses, which makes it a reasonable proxy for human real performance in the bimodal condition.}.
 We note an increase in *both* the auditory and visual variances.
-This increase in noise is compatible with the fact that human responses appear to be pulled towards chance (i.e., the value O.5) when compared to the optimal model (see \@ref(fig:bimodal)).
+This increase in noise is compatible with the fact that human responses appear to be pulled towards chance (i.e., the value 0.5) when compared to the optimal model (see \@ref(fig:bimodal)).
 Below we investigate if this deviation from optimality can be related to the cue combination strategy.
@@
 This experiment studied the way participants combine multimodal information to recognize novel words.
-We found that the optimal model explained more variance than the auditory or the visual models did, indicating that particiapants take into account both the auditory and visual cues when making a decision.
+We found that the optimal model explained more variance than the auditory or the visual models did, indicating that participants take into account both the auditory and visual cues when making a decision.
 That said, Figure \@ref(fig:bimodal) shows that the participants deviated slightly --- but systematically--- from the optimal prediction in that they were slightly pulled toward chance (i.e., the probability 0.5).
@@
 
-$$\beta_a \propto \frac{1}{\sigma^2_{A}} = \frac{1}{\sigma^2_{C_A}+\sigma^2_{N_A} + \sigma^2_{E_A}}$$ 
-$$\beta_v \propto \frac{1}{\sigma^2_{V}} = \frac{1}{\sigma^2_{C_A}+\sigma^2_{N_A}}.$$
+$$\beta_a \propto \frac{1}{\sigma^2_{A}} = \frac{1}{\sigma^2_{A_C}+\sigma^2_{A_N} + \sigma^2_{A_E}}$$ 
+$$\beta_v \propto \frac{1}{\sigma^2_{V}} = \frac{1}{\sigma^2_{V_C}+\sigma^2_{V_N}}.$$
 
@@
 Figure \@ref(fig:bimodal) shows that, similar to Experiment 1, the optimal model explained more variance than the auditory and visual models did (note, however, that the visual model explained more variance than the auditory model did).
-Also similar to Exeperiment 1, the values of the variances increased in the bimodal condition (Table \@ref(tab:param)).
+Also similar to Experiment 1, the values of the variances increased in the bimodal condition (Table \@ref(tab:param)).
 
 ### Cue combination
-Here we investigated whethere the observed increase in the auditory and visual variances affected the relative weighting of the corresponding modalities.
+Here we investigated whether the observed increase in the auditory and visual variances affected the relative weighting of the corresponding modalities.
 Figure\ \@ref(fig:bias) (top) shows that the participants' decision threshold deviated from optimality, and that this deviation was biased towards the visual modality (the non-noisy modality).
@@
 $$\beta_a \propto \frac{1}{\sigma^2_{A}} = \frac{1}{\sigma^2_{A_C}+\sigma^2_{A_N}}$$ 
-$$\beta_v \propto \frac{1}{\sigma^2_{V}} = \frac{1}{\sigma^2_{V_C}+\sigma^2_{V_N} + + \sigma^2_{V_E}}.$$
+$$\beta_v \propto \frac{1}{\sigma^2_{V}} = \frac{1}{\sigma^2_{V_C}+\sigma^2_{V_N} + \sigma^2_{V_E}}.$$
 
@@
 ### Bimodal condition
-Figure \@ref(fig:bimodal) shows that almost all the variance was captured by the auditory model alone, the addition of visual information in the optomal model did not improve the prediction of human responses.
-Similar to Exeperiment 1 and 2, the values of the variances increased in the bimodal condition (Table \@ref(tab:param)).
+Figure \@ref(fig:bimodal) shows that almost all the variance was captured by the auditory model alone, the addition of visual information in the optimal model did not improve the prediction of human responses.
+Similar to Experiments 1 and 2, the values of the variances increased in the bimodal condition (Table \@ref(tab:param)).
 
@@
 Whereas in previous experiments the optimal model explained more variance than the auditory or the visual models did, here the auditory model alone explained almost all the variance.
-In other words, though participants were sensitive to variation in the noisy visual input when presented in isolation (as shown in Figure \@ref(fig:unimodal)), they tended to ignore this information when the visual input was presented simultaneusel with the auditory input (i.e., in the bimodal condition).
+In other words, though participants were sensitive to variation in the noisy visual input when presented in isolation (as shown in Figure \@ref(fig:unimodal)), they tended to ignore this information when the visual input was presented simultaneously with the auditory input (i.e., in the bimodal condition).
 Instead, they relied almost exclusively on the non-noisy auditory modality.\footnote{The reason why we saw this (floor) effect when we added noise to the visual modality (Experiment 3), and not when we added noise to the auditory modality (Experiment 2), is the fact that our visual stimuli were originally perceived less categorically and with less certainty than the auditory stimuli (see Experiment 1 in \@ref(fig:unimodal)).
@@
  scale_x_log10(breaks =c(0.1,1,10)) +
-   xlab("Optimal weighing relative to real weighing") +ylab("Count")+
+   xlab("Optimal weighting relative to observed weighting") +ylab("Density")+
   theme_few()+
@@
 Only participants with US IP addresses and a task approval rate above 99\% were allowed to participate.
-They were paid at an hourly rate of \$7/hour.
 Participants were excluded if they reported having experienced a technical problem of any sort during the online experiment ($N=$ `r N_all_4 - N_noProb_4`), or if they had less than 75\% accurate responses on the unambiguous training trials ($N=$ `r N_noProb_4 - N_good_4`).
 The final sample consisted of $N =$ `r N_good_4` participants.
-All participants provided informed consent before taking the experiment.\footnote{The sample size, exclusion criteria and the main analysese were pre-registered at https://osf.io/h7mzp/.}
+All participants provided informed consent before taking the experiment.\footnote{The sample size, exclusion criteria and the main analyses were pre-registered at https://osf.io/h7mzp/.}
 
@@
 There were, however, two differences: 1) We increased the number of responses elicited per subject from 70 to 300, and 2) we randomized the order of the three blocks (i.e., visual-only, auditory-only, and audio-visual) *within* subject: Each participant saw the 3 blocks exactly 6 times, covering all possible ordering combinations.
-Unlike the between-subjet randomzation that we used in Experiment 1, this choices allowed us to avoid a possible confound linked to the order of exposure.
-
-```{r weights, echo=FALSE, warning = FALSE, out.width = "\\textwidth", fig.pos = "!h", fig.cap = "The histogram shows the distribution of the participants' predicted (i.e., optimal) cue weighing relative the observed (i.e., descriptive) weigting (see Figure 3 for the details).
-The density plot shows the distriubtion of simulated data sampled from the population-level probabilistic model.
-The dashed lines represent 95\\% confidence intreval on this simulated distribution.
-Optimal beahvior is observed when the value of the relative cue weighing is 1 (red solid line).
-Participants whose values are outside the confidence interval of the simulated dsitribution over-rely on the visual modalirty (left side) or auditory modality (right side) in a non-random way (i.e., with p < 0.05)."}
+Unlike the between-subject randomization that we used in Experiment 1, this choices allowed us to avoid a possible confound linked to the order of exposure.
+
+```{r weights, echo=FALSE, warning = FALSE, out.width = "\\textwidth", fig.pos = "!h", fig.cap = "The histogram shows the distribution of the participants' predicted (i.e., optimal) cue weighting relative the observed (i.e., descriptive) weighting (see Figure 3 for the details).
+The density plot shows the distribution of simulated data sampled from the population-level probabilistic model.
+The dashed lines represent 95\\% confidence interval on this simulated distribution.
+Optimal behavior is observed when the value of the relative cue weighting is 1 (red solid line).
+Participants whose values are outside the confidence interval of the simulated distribution over-rely on the visual modality (left side) or auditory modality (right side) beyond sampling-related randomness (i.e., with p < 0.05)."}
 
@@
 -->
-### Cue combinaton
+### Cue combination
 We analyzed the cue combination strategies at the individual level.
-For each participant, we computed the optimal weighing, $\frac{\sigma^2_{A}}{\sigma^2_{V}}$, relative to the observed (i.e., descriptive) weighing, $\frac{\sigma^2_{Ab}}{\sigma^2_{Vb}}$.
+For each participant, we computed the optimal weighting, $\frac{\sigma^2_{A}}{\sigma^2_{V}}$, relative to the observed (i.e., descriptive) weighting, $\frac{\sigma^2_{Ab}}{\sigma^2_{Vb}}$.
 We show the resulting distribution in Figure \@ref(fig:weights).
 We note first that the distribution has a rather bimodal shape, centered around the optimal cue combination strategy.
-This finding rules out the hypotheis that optimality at the population level is a spurious finding, i.e., only obtained via aggregating over various sub-otimal strategies.
-
-In addition, we asked whether the observed variance in the individual distribution was due to the randomness inherent to the process of sampling from a probabilsitic model or whether it corresponded to a real between-subject variability induced by different cue weighing strategies.
-We simulated responses through sampling from the population-level models and we computed the resuting distribution of cue weighing for each simulated indivudual leading to the density function in Figure \@ref(fig:weights).
+This finding rules out the hypothesis that optimality at the population level is a spurious finding, i.e., only obtained by aggregating over various sub-optimal strategies.
+
+In addition, we asked whether the observed variance in the individual distribution was due to the randomness inherent to the process of sampling from a probabilistic model or whether it corresponded to a real between-subject variability induced by different cue weighting strategies.
+We simulated responses through sampling from the population-level models and we computed the resulting distribution of cue weighting for each simulated individual leading to the density function in Figure \@ref(fig:weights).
 We can observe that most empirical values fall within the 95% confidence interval of the simulated density, showing that this part of the variance can be due to mere sampling randomness.
-However, a few participants had values outide this interval, indicating that they systematically over-relied on the visual modality ($N=$ `r subj_vis`) or the auditory modality ($N=$ `r subj_aud`) with p-value $ < 0.05$.
+However, a few participants had values outside this interval, indicating that they systematically over-relied on the visual modality ($N=$ `r subj_vis`, $p < 0.05$) or the auditory modality ($N=$ `r subj_aud`, $p < 0.05$).
 
@@
 The population-level analysis replicated the results of Experiment 1.
-The individual-level analysis showed that the distribution of cue combination scores had a unimodal shape centered around the optimal combination, thus reflecting geuine cue combination at the individual level.
-That said, the  variance of this distribution indicates that a few participants tended to over-rely on the auditory modality and others tended to over-rely on the visual modality beyond sampling errors.
+The individual-level analysis showed that the distribution of cue combination scores had a unimodally-shaped distribution centered around the optimal combination, thus reflecting genuine cue combination at the individual level.
+That said, the variance of this distribution indicates that a few participants tended to over-rely on the auditory modality and others tended to over-rely on the visual modality beyond sampling-related randomness.
 
@@
 Only a few subjects over-relied on the auditory or visual modalities beyond sampling errors.
-<!--This finding contrasts with research on multisensory integration where associations tend to lead to a higher precision [e.g., @ernst02].
-Nevertheless, research on multisensory integration has typically dealt with correlated, redundant multimodal cues, e.g., determining the size of an object based on visual and haptic information.
-Another possible case of multisensory integration involves perceptually uncorrelated cues such as recognizing an object based on its features (e.g., shape and color) [e.g., @Bankieris17] or a word based on its phonological and semantic properties, as in the current study.
--->
-
-Despite this overall near-optomal behavior, we documented two major cases of sub-optimality.
+
+Despite this overall near-optimal behavior, we documented two major cases of sub-optimality.
 First, in all experiments, the variance associated with each modality increased in the bimodal condition compared to the unimodal conditions: Participants responded slightly more randomly.
-This increase in randomness could be due limitation on cognitive resources: Retaining two separate cues at the same time instead of one cue (as in the unimodal case) is likely to place extra demands on working memory, causing general performance to drop [see @mattys11].
-
-Previous research bas found similar cases of suboptimal behavior.
+This increase in randomness could be due limitation on cognitive resources: Processing two separate --- and perceptually uncorrelated --- cues instead of one cue (as in the unimodal case) is likely to place extra demands on working memory, causing general performance to drop [see @mattys11].
+
+Previous research has found similar cases of suboptimal behavior.
 For instance, studies that have explored the identification of ambiguous, newly learned pairs of word-referent associations have reported what appears to be a decrease in speech perception acuity in both children [@stager1997] and adults [@pajak2016].
-Recently, @hofer2017 provided a probabilistic model of this phenomenon.
 In agreement with the findings of our study, @hofer2017 characterized the apparent reduction in perceptual acuity as an increase in the noise variance of the auditory modality.
@@
 This second case of sub-optimal behavior may be related to the fact that language understanding under degraded conditions is cognitively more taxing than language understanding under normal conditions [@ronnberg2010; @mattys12; @peelle2018].
-Perhaps these demands lead to sub-optimal behavior (i.e., over-reliance on the less noisy cue) as participants seek to minimized cognitive effort.
+Perhaps these demands lead to sub-optimal behavior (i.e., over-reliance on the less noisy cue) as participants seek to minimize cognitive effort.
 One could also explain this phenomenon in terms of the metacognitive experience about the fluency with which information is processed.
@@
 
-Concerning the visual dimension, simulating meaningful variability has been a notoriousely difficult problem.
+Concerning the visual dimension, simulating meaningful variability has been a notoriously difficult problem.
 Following previous studies [@freedman2001; @havy2016; @sloutsky2004], we used a visual continuum along a one-dimensional morph.
@@
 
-Finally, though we used the terminology of word recognition, our work is only indirectly related to the literature about how a *rich* lexicon is accessed [e.g., @mcclelland1986].
+Finally, though we used the terminology of word recognition, our work is only indirectly related to the literature about how a rich lexicon is accessed [e.g., @mcclelland1986].
 We have used this term in a more specific way, describing access to a simplified lexicon made of two novel, ambiguous words.
@@
 
-Our work provides a formal framework where old and new questions about word recognition can be given a precise formulation.
-This framework enabled us not only to test optimality, but also to examine systamtically how and by how much people deviate from optimality in their combination strategies.
-Thus, our work is part of a growing effort to go byond optimality tests ---which have limited explanatory power--- and use models that also allow us to identify and explain various patterns of sub-otimlaity in human behavior [@rahnev2018].
-
-While we focused on the case of arbitrary associations in novel word recognition, it is possible to use the same framework to study, for instance, the case of \textit{iconicity}, that is, when there is a resemblance between the sound of a word and its referent.
+Our work used an ideal observer model to study word recognition under audio-visual uncertainty.
+This framework enabled us not only to test optimality, but also to examine systematically how and by how much people deviate from optimality in their combination strategies.
+Thus, our work is part of a growing effort to go beyond optimality tests --- which have limited explanatory power --- and use models that also allow us to identify and explain various patterns of sub-optimality in human behavior [@rahnev2018].
+
+While we focused on the case of arbitrary associations in novel word recognition, it is possible to extend the framework to other cases such as that of \textit{iconicity}, i.e., when there is a resemblance between the sound of a word and its referent.
 Previous work has suggested that iconicity, among other things, helps with learning (and generalizing the meaning of) new words [see @dingemanse2015 for a review].
@@
 
-Finally, though the current framework only characterizes adult word recognition, it provides a first step towards a model where developmental questions can also be investigated.
-For instance, future work should explore whether children, like adults, use probabilistic cues from both the auditory and the visual input to recognize ambiguous words, the extent to which they combine these cues in an optimal fashion, and whether this cue combination help them to refine their early phonological and semantic representations.
+Finally, though the current framework only characterizes adult novel word recognition, it provides a first step towards a model where developmental questions can also be investigated.
+For instance, future work should explore whether children, like adults, use probabilistic cues from both the auditory and the visual input to recognize ambiguous words, the extent to which they combine these cues in an optimal fashion, and whether this cue combination help them learn words and refine their early phonological and semantic representations.
 

### 2019-04-12 Writeup/ms.tex
more revisions

@@
 perceivers systematically prefer the unperturbed modality to a greater
-extent than the optimal model does. This work extends the literature of
+extent than the optimal model does. This work extends the literature on
 perceptual cue combination to the case of word recognition in a
-referential context, thus offering a first step towards a model that
-accounts for sound-meaning synergies in early word learning.
+referential context. In addition, this context offers a link to the
+study of multimodal information in word meaning learning.
 
@@
 only. Second, we augment this simplified model to account for sensory
-and envirnmental noise.
+and environmental noise.
 
@@
 categorical variability and sensory noise. In Experiment 2 and 3 we
-added envirnmental noise to the auditory and the visual modalities,
+added environmental noise to the auditory and the visual modalities,
 respectively.
@@
 Turk. Only participants with US IP addresses and a task approval rate
-above 85\% were allowed to participate. They were paid at an hourly rate
-of \$6/hour. Participants were excluded if they reported having
-experienced a technical problem of any sort during the online experiment
-(N=14), or if they had less than 50\% accurate responses on the
-unambiguous training trials (N=6). The final sample consisted of N = 80
-participants. All participants provided informed consent before taking
-the experiment.
+above 85\% were allowed to participate. Participants were excluded if
+they reported having experienced a technical problem of any sort during
+the online experiment (N=14), or if they had less than 50\% accurate
+responses on the unambiguous training trials (N=6). The final sample
+consisted of N = 80 participants. All participants provided informed
+consent before taking the experiment.
 \footnote{The sample size and exclusion criteria were specified in the pre-registration at https://osf.io/h7mzp/.}
@@
 directly fit to human responses in the bimodal condition in order to
-allow us to assess deviation from optimaity.
+allow us to assess deviation from optimality.
 
@@
 optimality. To investigate this deviation, we compare the parameter
-values of the optimal model to the values obtaied in the decriptive
+values of the optimal model to the values obtained in the descriptive
 model (Table
-\ref{tab:param}).\footnote{Note that the descriptive model explained almost all the variance in mean responses, which makes it a reasonble proxy for human real performance in the bimodal condition.}.
+\ref{tab:param}).\footnote{Note that the descriptive model explained almost all the variance in mean responses, which makes it a reasonable proxy for human real performance in the bimodal condition.}.
 We note an increase in \emph{both} the auditory and visual variances.
 This increase in noise is compatible with the fact that human responses
-appear to be pulled towards chance (i.e., the value O.5) when compared
+appear to be pulled towards chance (i.e., the value 0.5) when compared
 to the optimal model (see \ref{fig:bimodal}). Below we investigate if
@@
 explained more variance than the auditory or the visual models did,
-indicating that particiapants take into account both the auditory and
+indicating that participants take into account both the auditory and
 visual cues when making a decision. That said, Figure \ref{fig:bimodal}
@@
 
-\[\beta_a \propto \frac{1}{\sigma^2_{A}} = \frac{1}{\sigma^2_{C_A}+\sigma^2_{N_A} + \sigma^2_{E_A}}\]
-\[\beta_v \propto \frac{1}{\sigma^2_{V}} = \frac{1}{\sigma^2_{C_A}+\sigma^2_{N_A}}.\]
+\[\beta_a \propto \frac{1}{\sigma^2_{A}} = \frac{1}{\sigma^2_{A_C}+\sigma^2_{A_N} + \sigma^2_{A_E}}\]
+\[\beta_v \propto \frac{1}{\sigma^2_{V}} = \frac{1}{\sigma^2_{V_C}+\sigma^2_{V_N}}.\]
 
@@
 models did (note, however, that the visual model explained more variance
-than the auditory model did). Also similar to Exeperiment 1, the values
+than the auditory model did). Also similar to Experiment 1, the values
 of the variances increased in the bimodal condition (Table
@@
 
-Here we investigated whethere the observed increase in the auditory and
+Here we investigated whether the observed increase in the auditory and
 visual variances affected the relative weighting of the corresponding
@@
 \[\beta_a \propto \frac{1}{\sigma^2_{A}} = \frac{1}{\sigma^2_{A_C}+\sigma^2_{A_N}}\]
-\[\beta_v \propto \frac{1}{\sigma^2_{V}} = \frac{1}{\sigma^2_{V_C}+\sigma^2_{V_N} + + \sigma^2_{V_E}}.\]
+\[\beta_v \propto \frac{1}{\sigma^2_{V}} = \frac{1}{\sigma^2_{V_C}+\sigma^2_{V_N} + \sigma^2_{V_E}}.\]
 
@@
 by the auditory model alone, the addition of visual information in the
-optomal model did not improve the prediction of human responses. Similar
-to Exeperiment 1 and 2, the values of the variances increased in the
+optimal model did not improve the prediction of human responses. Similar
+to Experiments 1 and 2, the values of the variances increased in the
 bimodal condition (Table \ref{tab:param}).
@@
 \ref{fig:unimodal}), they tended to ignore this information when the
-visual input was presented simultaneusel with the auditory input (i.e.,
+visual input was presented simultaneously with the auditory input (i.e.,
 in the bimodal condition). Instead, they relied almost exclusively on
@@
 Mechanical Turk. Only participants with US IP addresses and a task
-approval rate above 99\% were allowed to participate. They were paid at
-an hourly rate of \$7/hour. Participants were excluded if they reported
-having experienced a technical problem of any sort during the online
-experiment (\(N=\) 0), or if they had less than 75\% accurate responses
-on the unambiguous training trials (\(N=\) 7). The final sample
-consisted of \(N =\) 43 participants. All participants provided informed
-consent before taking the
-experiment.\footnote{The sample size, exclusion criteria and the main analysese were pre-registered at https://osf.io/h7mzp/.}
+approval rate above 99\% were allowed to participate. Participants were
+excluded if they reported having experienced a technical problem of any
+sort during the online experiment (\(N=\) 0), or if they had less than
+75\% accurate responses on the unambiguous training trials (\(N=\) 7).
+The final sample consisted of \(N =\) 43 participants. All participants
+provided informed consent before taking the
+experiment.\footnote{The sample size, exclusion criteria and the main analyses were pre-registered at https://osf.io/h7mzp/.}
 
@@
 times, covering all possible ordering combinations. Unlike the
-between-subjet randomzation that we used in Experiment 1, this choices
+between-subject randomization that we used in Experiment 1, this choices
 allowed us to avoid a possible confound linked to the order of exposure.
@@
 \begin{figure}[!h]
-\includegraphics[width=\textwidth]{ms_files/figure-latex/weights-1} \caption{The histogram shows the distribution of the participants' predicted (i.e., optimal) cue weighing relative the observed (i.e., descriptive) weigting (see Figure 3 for the details).
-The density plot shows the distriubtion of simulated data sampled from the population-level probabilistic model.
-The dashed lines represent 95\% confidence intreval on this simulated distribution.
-Optimal beahvior is observed when the value of the relative cue weighing is 1 (red solid line).
-Participants whose values are outside the confidence interval of the simulated dsitribution over-rely on the visual modalirty (left side) or auditory modality (right side) in a non-random way (i.e., with p < 0.05).}\label{fig:weights}
+\includegraphics[width=\textwidth]{ms_files/figure-latex/weights-1} \caption{The histogram shows the distribution of the participants' predicted (i.e., optimal) cue weighting relative the observed (i.e., descriptive) weighting (see Figure 3 for the details).
+The density plot shows the distribution of simulated data sampled from the population-level probabilistic model.
+The dashed lines represent 95\% confidence interval on this simulated distribution.
+Optimal behavior is observed when the value of the relative cue weighting is 1 (red solid line).
+Participants whose values are outside the confidence interval of the simulated distribution over-rely on the visual modality (left side) or auditory modality (right side) beyond sampling-related randomness (i.e., with p < 0.05).}\label{fig:weights}
 \end{figure}
@@
 
-\subsubsection{Cue combinaton}\label{cue-combinaton}
+\subsubsection{Cue combination}\label{cue-combination-3}
 
 We analyzed the cue combination strategies at the individual level. For
-each participant, we computed the optimal weighing,
+each participant, we computed the optimal weighting,
 \(\frac{\sigma^2_{A}}{\sigma^2_{V}}\), relative to the observed (i.e.,
-descriptive) weighing, \(\frac{\sigma^2_{Ab}}{\sigma^2_{Vb}}\). We show
+descriptive) weighting, \(\frac{\sigma^2_{Ab}}{\sigma^2_{Vb}}\). We show
 the resulting distribution in Figure \ref{fig:weights}. We note first
 that the distribution has a rather bimodal shape, centered around the
-optimal cue combination strategy. This finding rules out the hypotheis
+optimal cue combination strategy. This finding rules out the hypothesis
 that optimality at the population level is a spurious finding, i.e.,
-only obtained via aggregating over various sub-otimal strategies.
+only obtained by aggregating over various sub-optimal strategies.
 
@@
 distribution was due to the randomness inherent to the process of
-sampling from a probabilsitic model or whether it corresponded to a real
-between-subject variability induced by different cue weighing
+sampling from a probabilistic model or whether it corresponded to a real
+between-subject variability induced by different cue weighting
 strategies. We simulated responses through sampling from the
-population-level models and we computed the resuting distribution of cue
-weighing for each simulated indivudual leading to the density function
-in Figure \ref{fig:weights}. We can observe that most empirical values
-fall within the 95\% confidence interval of the simulated density,
-showing that this part of the variance can be due to mere sampling
-randomness. However, a few participants had values outide this interval,
-indicating that they systematically over-relied on the visual modality
-(\(N=\) 5) or the auditory modality (\(N=\) 6) with p-value \$
-\textless{} 0.05\$.
+population-level models and we computed the resulting distribution of
+cue weighting for each simulated individual leading to the density
+function in Figure \ref{fig:weights}. We can observe that most empirical
+values fall within the 95\% confidence interval of the simulated
+density, showing that this part of the variance can be due to mere
+sampling randomness. However, a few participants had values outside this
+interval, indicating that they systematically over-relied on the visual
+modality (\(N=\) 5, \(p < 0.05\)) or the auditory modality (\(N=\) 6,
+\(p < 0.05\)).
 
@@
 results of Experiment 1. The individual-level analysis showed that the
-distribution of cue combination scores had a unimodal shape centered
-around the optimal combination, thus reflecting geuine cue combination
-at the individual level. That said, the variance of this distribution
-indicates that a few participants tended to over-rely on the auditory
-modality and others tended to over-rely on the visual modality beyond
-sampling errors.
+distribution of cue combination scores had a unimodally-shaped
+distribution centered around the optimal combination, thus reflecting
+genuine cue combination at the individual level. That said, the variance
+of this distribution indicates that a few participants tended to
+over-rely on the auditory modality and others tended to over-rely on the
+visual modality beyond sampling-related randomness.
 
@@
 
-Despite this overall near-optomal behavior, we documented two major
+Despite this overall near-optimal behavior, we documented two major
 cases of sub-optimality. First, in all experiments, the variance
@@
 more randomly. This increase in randomness could be due limitation on
-cognitive resources: Retaining two separate cues at the same time
-instead of one cue (as in the unimodal case) is likely to place extra
-demands on working memory, causing general performance to drop (see
-Mattys \& Wiget, 2011).
-
-Previous research bas found similar cases of suboptimal behavior. For
+cognitive resources: Processing two separate --- and perceptually
+uncorrelated --- cues instead of one cue (as in the unimodal case) is
+likely to place extra demands on working memory, causing general
+performance to drop (see Mattys \& Wiget, 2011).
+
+Previous research has found similar cases of suboptimal behavior. For
 instance, studies that have explored the identification of ambiguous,
@@
 appears to be a decrease in speech perception acuity in both children
-(Stager \& Werker, 1997) and adults (Pajak, Creel, \& Levy, 2016).
-Recently, Hofer and Levy (2017) provided a probabilistic model of this
-phenomenon. In agreement with the findings of our study, Hofer and Levy
-(2017) characterized the apparent reduction in perceptual acuity as an
-increase in the noise variance of the auditory modality. Our findings,
-besides providing more evidence to this documented fact, suggest that
-the reduction in perceptual acuity may occur simultaneously in both the
+(Stager \& Werker, 1997) and adults (Pajak, Creel, \& Levy, 2016). In
+agreement with the findings of our study, Hofer and Levy (2017)
+characterized the apparent reduction in perceptual acuity as an increase
+in the noise variance of the auditory modality. Our findings, besides
+providing more evidence to this documented fact, suggest that the
+reduction in perceptual acuity may occur simultaneously in both the
 auditory \emph{and} the visual modalities.
@@
 2010). Perhaps these demands lead to sub-optimal behavior (i.e.,
-over-reliance on the less noisy cue) as participants seek to minimized
+over-reliance on the less noisy cue) as participants seek to minimize
 cognitive effort. One could also explain this phenomenon in terms of the
@@
 Concerning the visual dimension, simulating meaningful variability has
-been a notoriousely difficult problem. Following previous studies
+been a notoriously difficult problem. Following previous studies
 (Freedman et al., 2001; Havy \& Waxman, 2016; Sloutsky \& Fisher, 2004),
@@
 Finally, though we used the terminology of word recognition, our work is
-only indirectly related to the literature about how a \emph{rich}
-lexicon is accessed (e.g., McClelland \& Elman, 1986). We have used this
-term in a more specific way, describing access to a simplified lexicon
-made of two novel, ambiguous words. Such a simplified experimental
-context is not new and has been crucial to our understanding of early
-word learning and recognition (e.g., Stager \& Werker, 1997).
+only indirectly related to the literature about how a rich lexicon is
+accessed (e.g., McClelland \& Elman, 1986). We have used this term in a
+more specific way, describing access to a simplified lexicon made of two
+novel, ambiguous words. Such a simplified experimental context is not
+new and has been crucial to our understanding of early word learning and
+recognition (e.g., Stager \& Werker, 1997).
 
@@
 
-Our work provides a formal framework where old and new questions about
-word recognition can be given a precise formulation. This framework
-enabled us not only to test optimality, but also to examine
-systamtically how and by how much people deviate from optimality in
-their combination strategies. Thus, our work is part of a growing effort
-to go byond optimality tests ---which have limited explanatory power---
-and use models that also allow us to identify and explain various
-patterns of sub-otimlaity in human behavior (Rahnev \& Denison, 2018).
+Our work used an ideal observer model to study word recognition under
+audio-visual uncertainty. This framework enabled us not only to test
+optimality, but also to examine systematically how and by how much
+people deviate from optimality in their combination strategies. Thus,
+our work is part of a growing effort to go beyond optimality tests ---
+which have limited explanatory power --- and use models that also allow
+us to identify and explain various patterns of sub-optimality in human
+behavior (Rahnev \& Denison, 2018).
 
 While we focused on the case of arbitrary associations in novel word
-recognition, it is possible to use the same framework to study, for
-instance, the case of \textit{iconicity}, that is, when there is a
-resemblance between the sound of a word and its referent. Previous work
-has suggested that iconicity, among other things, helps with learning
-(and generalizing the meaning of) new words (see Dingemanse, Blasi,
-Lupyan, Christiansen, \& Monaghan, 2015 for a review). Using the
-research strategy in this paper, we can, for example, test whether
-iconicity has such an advantage because it mitigates the sub-optimal
-patterns observed with more arbitrary pairings.
-
-Finally, though the current framework only characterizes adult word
-recognition, it provides a first step towards a model where
+recognition, it is possible to extend the framework to other cases such
+as that of \textit{iconicity}, i.e., when there is a resemblance between
+the sound of a word and its referent. Previous work has suggested that
+iconicity, among other things, helps with learning (and generalizing the
+meaning of) new words (see Dingemanse, Blasi, Lupyan, Christiansen, \&
+Monaghan, 2015 for a review). Using the research strategy in this paper,
+we can, for example, test whether iconicity has such an advantage
+because it mitigates the sub-optimal patterns observed with more
+arbitrary pairings.
+
+Finally, though the current framework only characterizes adult novel
+word recognition, it provides a first step towards a model where
 developmental questions can also be investigated. For instance, future
@@
 words, the extent to which they combine these cues in an optimal
-fashion, and whether this cue combination help them to refine their
-early phonological and semantic representations.
+fashion, and whether this cue combination help them learn words and
+refine their early phonological and semantic representations.
 

### 2019-11-14 Writeup/ms_r2.Rmd
final

--- 2019-04-12 Writeup/ms.Rmd
@@
 header-includes:
-   #- \usepackage{bibentry}
+   - \usepackage{xcolor}
    - \usepackage[sortcites=false,sorting=none]{biblatex}
@@
 
-```{r load_packages, include = FALSE}
+```{r load_packages, message=FALSE, warning=FALSE, include=FALSE, include = FALSE}
+
 library(papaja)
@@
 library(kableExtra)
-#library("knitcitations")
-#cleanbib()
-#options("citation_format" = "pandoc")
+
 ```
@@
 Identifying a word involves processing the auditory information as well as other perceptual signals (e.g., the visual image of the bee, the sound of its wings, the sensation of the bee flying by your arm).
-A word is successfully identified when information from these modalities provide convergent evidence.
+A word is successfully identified when information from these modalities provides convergent evidence.
 
@@
 On the auditory side, individual acoustic word tokens are almost always ambiguous with respect to the particular sequence of phonemes they represent, which is due to the inherent variability of how a phonetic category is realized acoustically [@hillenbrand1995].
-And some tokens may be distorted additionally by mispronunciation or ambient noise.
-Perhaps the speaker was yelling "pea" and not "bee." Similarly, a sensory impression may not be enough to make a definitive identification of a visual category.\footnote{In the general case, language can of course be visual as well as auditory, and object identification can be done through many modalities.
+Moreover, some tokens may be distorted additionally by mispronunciation or ambient noise.
+Perhaps the speaker was yelling "pea" and not "bee." Similarly, a sensory impression may not be enough to make a definitive identification of a visual category.\footnote{In the general case, language can of course be visual as well as auditory, and object identification can be accomplished through many modalities.
 For simplicity, we focus on audio-visual matching here.} Perhaps the insect was a beetle or a fly instead.
@@
 It is not so much a realistic model of human performance, as much as a baseline against which human performance can be compared [@Geisler2003; @rahnev2018].
-When there is a deviation from the ideal, it can reveal extra constraints on human cognition, such as limitations on the working memory or attentional resources.
-This approach has had a tremendous impact not only on speech-related research [@Norris08; @clayard08; @feldman2009; @kleinschmidt2015], but also on many other disciplines in the cognitive sciences [for reviews, see @chater06; @Knill04; @tenenbaum11]
+When there is a deviation from the ideal, it can reveal extra constraints on human cognition, such as limitations on the working memory or on attentional resources.
+This approach has had a tremendous impact not only on speech-related research [@Norris08; @clayard08; @feldman2009; @kleinschmidt2015] but also on many other disciplines in the cognitive sciences [for reviews, see @chater06; @Knill04; @tenenbaum11].
 
@@
 They found that humans were sensitive to these probabilistic cues and their judgments closely reflected the optimal predictions.
-And @feldman2009 studied the perceptual magnet effect, a phenomenon that involves reduced discriminability near prototypical sounds in the native language [@kuhl1991], showing that this effect can be explained as the consequence of optimally solving the problem of perception under uncertainty [see also @kronrod2016].
+Moreover, @feldman2009 studied the perceptual magnet effect, a phenomenon that involves reduced discriminability near prototypical sounds in the native language [@kuhl1991], showing that this effect can be explained as the consequence of optimally solving the problem of perception under uncertainty [see also @kronrod2016].
 
@@
 They showed that human performance during audio-visual phonemic labeling was consistent (at least at the qualitative level) with the predictions of an ideal observer.
-This previous research did not,  however, study speech understanding when visual information was obtained through the referential context rather than through observation of speaker's face.
-Although some experimental findings show that information about the identity of a referent can be integrated with linguistic information to resolve lexical and syntactic ambiguities in speech [e.g., @Eberhard1995; @Tanenhaus1995; @spivey2002], to our knowledge no study has offered an ideal observer analysis of this task.
+This previous research did not, however, study speech understanding when visual information was obtained through the referential context rather than through observation of the speaker's face.
+Although some experimental findings show that information about the identity of a referent can be integrated with linguistic information to resolve lexical and syntactic ambiguities in speech [e.g., @Eberhard1995; @Tanenhaus1995; @spivey2002], to our knowledge no study has offered an ideal observer analysis of this task (as we do here).
 
@@
 They differ only in terms of their informational reliability.
-In a referential context, however, the auditory and visual modalities play different roles in the referential process -- the auditory input represents the *symbol* whereas the visual input represents the *meaning* (and these differences are in addition to possible differences in informational reliability).
-Further, speech is claimed to have a privileged status compared to other sensory stimuli [@vouloumanos2014; @waxman2009; @waxman1995; @edmiston2015; @lupyan2012], and this privilege is suggested to be specifically related to the ability to refer [@waxman2009].^[There is, however, a debate as to whether speech is privileged for children and adults for similar reasons.
+In a referential context, however, the auditory and visual modalities play different roles in the referential process --- the auditory input represents the *symbol* whereas the visual input represents the *meaning* (and these differences are in addition to possible differences in informational reliability).
+Speech is claimed to have a privileged status compared to other sensory stimuli [@vouloumanos2014; @waxman2009; @waxman1995; @edmiston2015; @lupyan2012], and this privilege is suggested to be specifically related to the ability to refer [@waxman2009].^[There is, however, a debate as to whether speech is privileged for children and adults for similar reasons.
 Whereas some researchers suggest that speech is privileged for both children and adults because of its ability to refer [e.g., @waxman2009], others suggest that speech might *not* have a referential status from the start.
-Rather, speech might be preferred by children only because of a low level auditory ``overshadowing'' [e.g., @sloutsky2003].] Thus, in a referential context, it is possible that listeners do not treat the auditory and visual modalities as equivalent sources of information.
-Instead, there could be a sub-optimal bias for the auditory modality beyond what is expected from informational reliability alone.
+Rather, speech might be preferred by children only because of a low level auditory ``overshadowing'' [e.g., @sloutsky2003].
+We do not take a stance on this issue here.] Thus, in a referential context, it is possible that listeners do not treat the auditory and visual modalities as equivalent sources of information.
+Instead, there could be a (potentially sub-optimal) bias for the auditory modality beyond what is expected from informational reliability alone.
 
@@
 In Experiment 2, we intervened by adding environmental noise that degraded information from the auditory modality and in Experiment 3 we intervened by adding environmental noise that degraded information from the visual modality.
-Finally, Experiment 4 is a replication of Experiment 1 with a higher power design, allowing us to test cue combination at the individual level.
+Finally, in Experiment 4, we replicated Experiment 1 with a higher power design, allowing us to test cue combination at the individual level.
 
@@
 
-In this section we first briefly introduce the multimodal combination task. Then we explain how behavior in this paradigm can be characterized optimally with an ideal observer model.
+In this section, we first briefly introduce the multimodal combination task. Then we explain how behavior in this paradigm can be characterized optimally with an ideal observer model.
 
@@
 In the current study, we are interested, rather, in the categorization, i.e., determining whether or not two similar tokens are members of the same phonological/semantic category.
-Therefore, testing in our task is category-based: Participants are asked to press "same" if they think the second item (the test) belongs to the same category as the first (target) (e.g.,  dog-/aba/), even if there is a slight difference in the sound, in the referent, or in both.
+Therefore, testing in our task is category-based: Participants are asked to press "same" if they think the second item (the test) belongs to the same category as the first (target) (e.g.,  cat-/aba/), even if there is a slight difference in the sound, in the referent, or in both.
 They are instructed to press "different" only if they think that the second stimulus was an instance of the other category (cat-/ada/).
@@
 An audio-visual signal $w=(a,v)$ can be represented as a point in the audio-visual space.
-These audio-visual tokens define bivariate distributions in the bi-dimentional space.
+These audio-visual tokens define bivariate distributions in the bi-dimensional space.
 We call these bivariate distributions *Word categories*, noted $W$, and are distributed as follows:
@@
 
-\noindent This assumption says that, given a word-object mapping, e.g., $W=$("cat"-CAT), variation in the way "cat" is pronounced does not correlate with changes in any visual property of the object CAT, which is a valid assumption in the context of our task.\footnote{Note that this assumptions is more adequate in the case of arbitrary associations such as ours, and less so in the case of redundant association such as audio-visual speech.
+\noindent This assumption says that, given a word-object mapping, e.g., $W=$("cat"-CAT), variation in the way "cat" is pronounced does not correlate with changes in any visual property of the object CAT, which is a valid assumption in the context of our task.\footnote{Note that this assumption is more adequate in the case of arbitrary associations such as ours, and less so in the case of redundant association such as audio-visual speech.
 In the latter, variation in the pronunciation is expected to correlate, at least to some extent, with lip movements.}
@@
 However, since the identity of word categories is randomized across participants, $b$ measures, rather, a response bias to "same" if $b > 0$, and a response bias to "different" if $b < 0$.
-We expect a general bias towards answering "different" because of the categorical nature of our same-different task: When two items are ambiguous but perceptually different, participants might have a slight preference for "different" over "same".
-As for the means, their values are fixed, and they correspond to the most typical tokens in our stimuli.
+We expect a general bias towards answering "different" because of the categorical nature of our same-different task: When two items are ambiguous but perceptually different, participants might have a slight preference for "different" over "same." As for the means, their values are fixed, and they correspond to the most typical tokens in our stimuli.
 Finally, observations from each modality ($a$ and $v$) are weighted in Equation 1 according to their reliability (that is, according to the *inverse* of their variance): $$\beta_a \propto \frac{1}{\sigma^2_{A}}$$ $$\beta_v \propto \frac{1}{\sigma^2_{V}}.$$
@@
 More precisely, these baseline models assume that the participants' responses in the bimodal condition will not be different from their response in either the visual-only or the auditory-only condition.
-However, if the participants rely on both the auditory and the visual modalities to make decision in the bimodal condition, the optimal model would explain more variance in human responses than the visual or the auditory model do.
+However, if the participants rely on both the auditory and the visual modalities to make decisions in the bimodal condition, the optimal model would explain more variance in human responses than the visual or the auditory model does.
 
@@
 The optimal model (as well as the auditory and visual baselines) are *normative* models.
-Their predictions are made about human data in the bimodal condition, but their  parameters (i.e., variances associated with the visual and auditory modalities) are derived from data in the unimodal conditions.
+Their predictions are made about human data in the bimodal condition, but their crucial parameters (i.e., variances associated with the visual and auditory modalities) are derived from data in the unimodal conditions.
 In addition to these normative models, we consider a *descriptive* model.
@@
 
-Comparison of the optimal and the descriptive models allows us, not only to quantify how much people deviate from optimality, but also to understand precisely the nature of this deviation.
+Comparison of the optimal and the descriptive models allows us, not only to quantify how much people deviate from optimality but also to understand precisely the nature of this deviation.
 Let $\sigma^2_{A}$ and $\sigma^2_{V}$ be the values of the variances used in the optimal model (derived from the unimodal conditions), and $\sigma^2_{Ab}$ and $\sigma^2_{Vb}$ be the values observed through the descriptive model in the bimodal condition.
@@
 The second allows us to test the extent to which the weighting scheme follows the prediction of the optimal model.
-The reason we used the proportion of the variances as a measure of cross-modal weighting is because this proportion corresponds to the slope\footnote{Or more precisely the absolute value of the slope.} of the decision threshold in the audio-visual space (Figure\ \@ref(fig:model)).
+The reason we used the proportion of the variances as a measure of cross-modal weighting is that this proportion corresponds to the slope\footnote{Or more precisely the absolute value of the slope.} of the decision threshold in the audio-visual space (Figure\ \@ref(fig:model)).
 The decision threshold is defined as the set of values in this audio-visual space along which the posterior is equal to 0.5.
@@
 
-We compared these models to human responses in three experiments.
+We compared these models to human responses in four experiments.
 In Experiment 1, we studied the case where bimodal uncertainty was due to categorical variability and sensory noise.
 In Experiment 2 and 3 we added environmental noise to the auditory and the visual modalities, respectively.
+Finally, in Experiment 4, we replicated Experiment 1 with a higher power design in order to test cue combination at the individual level
 
@@
 We do not add any external noise to the background.
-Thus, we test the following (normative) cue weighting scheme:
+Thus, we test the following (normative) cue weighting scheme.^[In all our analyses, we study the combined effect of both categorical and sensory uncertainties in the process of cue combination.
+We do not examine the specific role of each source of uncertainty separately.
+For example, in the auditory modality, the quantity $\sigma^2_{A_C} + \sigma^2_{A_N}$  will be treated as a single variable.
+This variable will be measured in the unimodal condition and tested in the bimodal condition.]
 
@@
 Only participants with US IP addresses and a task approval rate above 85\% were allowed to participate.
-Participants were excluded if they reported having experienced a technical problem of any sort during the online experiment (N=`r N_all_1 - N_noProb_1`), or if they had less than 50\% accurate responses on the unambiguous training trials (N=`r N_noProb_1 - N_good_1`).
-The final sample consisted of N = `r N_good_1` participants.
+Participants were excluded if they reported having experienced a technical problem of any sort during the online experiment ($N =$ `r N_all_1 - N_noProb_1`), or if they had less than 50\% accurate responses on the unambiguous training trials ($N =$ `r N_noProb_1 - N_good_1`).
+The final sample consisted of $N =$ `r N_good_1` participants.
 All participants provided informed consent before taking the experiment.
@@
 #### Unimodal conditions
-Remember that data in these conditions allows us to derive the variances of both the auditory and the visual categories, and that these variances are used to make predictions about bimodal data (in the visual and auditory baselines as well as in the optimal model).
-These individual variances were derived as follows (we explain the derivation for the auditory-only case, but the same applies for the visual-only case).
+Remember that data in these conditions allows us to derive the variances of both the auditory and the visual categories and that these variances are used to make predictions about bimodal data (in the visual and auditory baselines as well as in the optimal model).
+These individual variances were derived as follows (we explain the derivation for the auditory-only case, but the same applies to the visual-only case).
 We use the same Bayesian reasoning as we did in the derivation of the bimodal model: When presented with an audio instance $a$, the probability of choosing the sound category 2 (that is, to answer "different") is the posterior probability of this category $p(A_2|a)$.
@@
 Since the values of the means are fixed, we have 3 free parameters: the variances for the visual and the auditory modalities, respectively, and $b$, the response bias.
-The visual and auditory baselines as well as the optimal model are not fit to the bimodal data, but their predictions are tested against these bimodal data.
+The visual and auditory baselines, as well as the optimal model, are not fit to the bimodal data, but their predictions are tested against these bimodal data.
 All these normative models use the variances derived from the unimodal data and the bias term derived from the fit to bimodal data.
@@
       linesep = "", format.args = list(big.mark = ","),
-      caption = "Statistics for the dataset we used."#,
+      caption = "Estimates of the models' parameters."#,
       #col.names = c("Experiment",  "b~A~", expression("*o['T']*"), "b~V~", "sigma~V~", "b~b~","sigma~Ab~","sigma~Vb~")
@@
 The categorization function of the auditory condition was slightly steeper than that of the visual condition, meaning that participants perceived the sound tokens slightly more categorically and with higher certainty than they did with the visual tokens.
-The unimodal models' estimates are shown in Table \@ref(tab:param).
-
-```{r unimodal, out.width = "\\textwidth", fig.pos = "!h", fig.cap = "Human responses in the unimodal conditions across the three experiments.
+The unimodal models' estimates in each modality are shown in Table \@ref(tab:param).
+
+```{r unimodal, out.width = "\\textwidth", fig.pos = "!h", fig.cap = "Human responses in the unimodal conditions across the four experiments.
 Points represent the proportion of `different' to `same' responses in the auditory-only condition (left), and visual-only condition (right).
@@
 Remember that the normative models use the parameters estimated from the unimodal conditions (where people see input from only one modality) to predict behavior in the bimodal condition (where people see input from both modalities).
-The descriptive model has a similar structure than the optimal model, but is directly fit to human responses in the bimodal condition in order to allow us to assess deviation from optimality.
-
-We found, through comparing the correlation values, that the optimal model explained more variance than the visual and auditory models did.
+The descriptive model has a similar structure than the optimal model but is directly fit to human responses in the bimodal condition in order to allow us to assess deviation from optimality.
+
+We found, by comparing the correlation values, that the optimal model explained more variance than the visual and auditory models did.
 However, the optimal model was not perfect: It explained less variance than the descriptive model did, which indicates a deviation from optimality.
-To investigate this deviation, we compare the parameter values of the optimal model to the values obtained in the descriptive model (Table \@ref(tab:param)).\footnote{Note that the descriptive model explained almost all the variance in mean responses, which makes it a reasonable proxy for human real performance in the bimodal condition.}.
-We note an increase in *both* the auditory and visual variances.
-This increase in noise is compatible with the fact that human responses appear to be pulled towards chance (i.e., the value 0.5) when compared to the optimal model (see \@ref(fig:bimodal)).
+To investigate this deviation, we compare the parameter values of the optimal model to the values obtained in the descriptive model (Table \@ref(tab:param)).\footnote{Note that the descriptive model explained almost all the variance in mean responses, which makes it a reasonable proxy for human real performance in the bimodal condition.} We note an increase in *both* the auditory and visual variances.
+This increase in noise is compatible with the fact that human responses appear to be pulled towards chance (i.e., the value 0.5) when compared to the optimal model (see Figure \@ref(fig:bimodal)).
 Below we investigate if this deviation from optimality can be related to the cue combination strategy.
@@
 We analyzed if the cue combination was performed in an optimal way, or if there was a systematic preference for one modality when making decisions in the bimodal condition.
-As explained in \@ref(fig:subOptim), modality preference can be characterized formally as a deviation from the decision threshold predicted by the optimal model.
+As explained in Figure \@ref(fig:subOptim), modality preference can be characterized formally as a deviation from the decision threshold predicted by the optimal model.
 The results in Figure \@ref(fig:bias) (top) show both the decision threshold derived from the descriptive model (in black) and the decision threshold predicted by the optimal model (in red).
@@
 ```{r bimodal, out.width = "\\textwidth", fig.pos = "!h", fig.cap = "Human responses vs.
-Models' predictions in the bimodal condition across the three experiments.
-Each point represents data form a particular audio-visual matching (corresponding to an instance from the set of 5x5 possible matchings in the audio-visual space).
+Models' predictions in the bimodal condition across the four experiments.
+Each point represents data from a particular audio-visual matching (corresponding to an instance from the set of 5x5 possible matchings in the audio-visual space).
 Shape represents auditory distance from the target, and color represents visual distance from the target.
@@
 
-pred_bimod$model <- factor(pred_bimod$model, levels = c('Visual','Auditory', 'Optimal', 'Descriptive'))
+pred_bimod$model <- factor(pred_bimod$model, levels = c('Auditory','Visual', 'Optimal', 'Descriptive'))
 
@@
 In Experiment 1, we tested word recognition when there was multimodal uncertainty in terms of category membership and perceptual noise.
-In real life, however, both sound and visual tokens can undergo distortions due to noisy factors in the environment (e.g., car noise in the background, blurry vision in a foggy weather).
+In real life, however, both sound and visual tokens can undergo distortions due to noisy factors in the environment (e.g., car noise in the background, blurry vision in foggy weather).
 In Experiment 2 and 3, we explore this additional level of uncertainty.
@@
 
-A sample of `r N_all_2` participants was recruited online through Amazon Mechanical Turk.
+A sample of $N =$ `r N_all_2` participants was recruited online through Amazon Mechanical Turk.
 We used the same exclusion criteria as in Experiment 1.
-`r N_noProb_2 - N_good_2` participants were excluded because they had less than 50\% accurate responses on the unambiguous training trials.
-The final sample consisted of N = `r N_good_2` participants.
+$N =$ `r N_noProb_2 - N_good_2` participants were excluded because they had less than 50\% accurate responses on the unambiguous training trials.
+The final sample consisted of $N =$ `r N_good_2` participants.
 
@@
 
-The analysis are similar to the analysis we did in Experiment 1.
+The analysis is similar to the analysis we did in Experiment 1.
 
@@
 Here we investigated whether the observed increase in the auditory and visual variances affected the relative weighting of the corresponding modalities.
-Figure\ \@ref(fig:bias) (top) shows that the participants' decision threshold deviated from optimality, and that this deviation was biased towards the visual modality (the non-noisy modality).
+Figure\ \@ref(fig:bias) (top) shows that the participants' decision threshold deviated from optimality and that this deviation was biased towards the visual modality (the non-noisy modality).
 Indeed non-parametric resampling of the data showed a decrease in the value of the slope in the descriptive model compared to the optimal model (Figure\ \@ref(fig:bias), bottom).
@@
 ## Discussion
-Experiment 2 tested audi-visual combination in the case where the auditory input was noisy.
+Experiment 2 tested audio-visual combination in the case where the auditory input was noisy.
 We found, similar to Experiment 1, that the optimal model explained more variance than the auditory or the visual models did.
@@
 
-A planned sample of `r N_all_3` participants was recruited online through Amazon Mechanical Turk.
+A planned sample of $N =$ `r N_all_3` participants was recruited online through Amazon Mechanical Turk.
 We used the same exclusion criteria as in both previous experiments.
-N=`r N_all_3 - N_noProb_3` participants were excluded because they reported having a technical problem, and N=`r N_noProb_3 - N_good_3` participants were excluded because they had less than 50\% accurate responses on the unambiguous training trials.
-The final sample consisted of N = `r N_good_3` participants.
+$N =$ `r N_all_3 - N_noProb_3` participants were excluded because they reported having a technical problem, and $N =$ `r N_noProb_3 - N_good_3` participants were excluded because they had less than 50\% accurate responses on the unambiguous training trials.
+The final sample consisted of $N =$ `r N_good_3` participants.
 
@@
 We also used the same visual stimuli, but we blurred the tokens using the free image editor GIMP (2.8.20).
-We used a Gaussian blur with a radius\footnote{A features that modulates the intensity of the blur.} of 10 pixels.
+We used a Gaussian blur with a radius\footnote{A feature that modulates the intensity of the blur.} of 10 pixels.
 The experimental procedure was exactly the same as in the previous Experiments.
@@
 In other words, though participants were sensitive to variation in the noisy visual input when presented in isolation (as shown in Figure \@ref(fig:unimodal)), they tended to ignore this information when the visual input was presented simultaneously with the auditory input (i.e., in the bimodal condition).
-Instead, they relied almost exclusively on the non-noisy auditory modality.\footnote{The reason why we saw this (floor) effect when we added noise to the visual modality (Experiment 3), and not when we added noise to the auditory modality (Experiment 2), is the fact that our visual stimuli were originally perceived less categorically and with less certainty than the auditory stimuli (see Experiment 1 in \@ref(fig:unimodal)).
-This fact made it more likely for the visual categorization function to become flat and uninformative after a few drops in precision due to noise on the one had, and to the additional randomness induced by the bimodal presentation on the other hand.}
+Instead, they relied almost exclusively on the non-noisy auditory modality.\footnote{The reason why we saw this (floor) effect when we added noise to the visual modality (Experiment 3), and not when we added noise to the auditory modality (Experiment 2), is the fact that our visual stimuli were originally perceived less categorically and with less certainty than the auditory stimuli (see Experiment 1 in Figure 4).
+This fact made it more likely for the visual categorization function to become flat and uninformative after a few drops in precision due to noise on the one hand, and to the additional randomness induced by the bimodal presentation on the other hand.}
 
@@
 However, it is important to investigate individual variability, especially for cases when we reported optimal cue combination (i.e., Experiment 1).
-In fact, optimality at the population level can be spurious if it is obtained only on average while most individuals have sub-otimal strategies (e.g., over-relying on the visual or the auditory modalities).
+In fact, optimality at the population level can be spurious if it is obtained only on average while individuals have sub-optimal strategies (e.g., over-relying on the visual or the auditory modalities).
 In Experiment 4, below, we examine how the average cue combination relates to individual strategies.
@@
 As we noted earlier, we did not have enough statistical power in Experiment 1 to fit a different model for each participant.
-Thus, we used a higher power design, allowing us to collect the number of datapoints necessary to model cue combination at the individual level.
+Thus, here we used a higher power design, allowing us to collect the number of data points necessary to model cue combination at the individual level.
 
@@
 There were, however, two differences: 1) We increased the number of responses elicited per subject from 70 to 300, and 2) we randomized the order of the three blocks (i.e., visual-only, auditory-only, and audio-visual) *within* subject: Each participant saw the 3 blocks exactly 6 times, covering all possible ordering combinations.
-Unlike the between-subject randomization that we used in Experiment 1, this choices allowed us to avoid a possible confound linked to the order of exposure.
+Unlike the between-subject randomization that we used in Experiment 1, this choice allowed us to avoid a possible confound linked to the order of exposure.
 
@@
 The dashed lines represent 95\\% confidence interval on this simulated distribution.
-Optimal behavior is observed when the value of the relative cue weighting is 1 (red solid line).
-Participants whose values are outside the confidence interval of the simulated distribution over-rely on the visual modality (left side) or auditory modality (right side) beyond sampling-related randomness (i.e., with p < 0.05)."}
+Optimal behavior is exactly obtained when the value of the relative cue weighting is 1 (red solid line).
+Participants whose values are outside the confidence interval of the simulated distribution can be understood to be over-relying on the visual modality (left side) or on the auditory modality (right side) beyond sampling-related variation (i.e., with p < 0.05)."}
 
@@
 We show the resulting distribution in Figure \@ref(fig:weights).
-We note first that the distribution has a rather bimodal shape, centered around the optimal cue combination strategy.
+We note first that the distribution has a rather unimodal shape, centered around the optimal cue combination strategy.
 This finding rules out the hypothesis that optimality at the population level is a spurious finding, i.e., only obtained by aggregating over various sub-optimal strategies.
@@
 We simulated responses through sampling from the population-level models and we computed the resulting distribution of cue weighting for each simulated individual leading to the density function in Figure \@ref(fig:weights).
-We can observe that most empirical values fall within the 95% confidence interval of the simulated density, showing that this part of the variance can be due to mere sampling randomness.
+We can observe that most empirical values fall within the 95% confidence interval of the simulated density, showing that this part of the variance can be due to mere sampling variation.
 However, a few participants had values outside this interval, indicating that they systematically over-relied on the visual modality ($N=$ `r subj_vis`, $p < 0.05$) or the auditory modality ($N=$ `r subj_aud`, $p < 0.05$).
@@
 This experiment was an extension to Experiment 1.
-Through collecting larger-size data per subject, we were able to analyze the cue combination optimality, not only at the population level, but also at the individual level.
+Through collecting denser data per subject, we were able to analyze the cue combination optimality, not only at the population level but also at the individual level.
 The population-level analysis replicated the results of Experiment 1.
@@
 In Experiment 3, participants appeared to rely on one modality, but this was likely a floor effect, due to the fact that noise made the visual input barely perceptible.
-Further, in Experiment 1 and 4, which did not involve background noise, participants not only relied on both modalities, but generally weighted these modalities according to the predictions of the optimal model, that is, according to their relative reliability.
-At the individual level, Experiment 4 showed that most participant were near-optimal.
+Further, in Experiment 1 and 4, which did not involve background noise, participants not only relied on both modalities but generally weighted these modalities according to the predictions of the optimal model, that is, according to their relative reliability.
+At the individual level, Experiment 4 showed that most participants were near-optimal.
 Only a few subjects over-relied on the auditory or visual modalities beyond sampling errors.
@@
 First, in all experiments, the variance associated with each modality increased in the bimodal condition compared to the unimodal conditions: Participants responded slightly more randomly.
-This increase in randomness could be due limitation on cognitive resources: Processing two separate --- and perceptually uncorrelated --- cues instead of one cue (as in the unimodal case) is likely to place extra demands on working memory, causing general performance to drop [see @mattys11].
-
-Previous research has found similar cases of suboptimal behavior.
+This increase in randomness could be due to limitations on cognitive resources: Processing two separate --- and perceptually uncorrelated --- cues instead of one cue (as in the unimodal case) is likely to place extra demands on working memory, causing general performance to drop [see @mattys11].
+
+Previous research has found similar cases of sub-optimal behavior.
 For instance, studies that have explored the identification of ambiguous, newly learned pairs of word-referent associations have reported what appears to be a decrease in speech perception acuity in both children [@stager1997] and adults [@pajak2016].
@@
 One could also explain this phenomenon in terms of the metacognitive experience about the fluency with which information is processed.
-The perceived perceptual fluency (e.g., the ease with which a stimulus' physical identity can be identified) can affect a wide variety of human judgements [see @schwarz2004 for a review].
+The perceived perceptual fluency (e.g., the ease with which a stimulus' physical identity can be identified) can affect a wide variety of human judgments [see @schwarz2004 for a review].
 In particular, variables that improve fluency tend to increase liking/preference [@reber98].
@@
 
-An important question to ask is how the combination mechanism --- as revealed in our controlled study --- scales up to real life situations.
+An important question to ask is how the combination mechanism --- as revealed in our controlled study --- scales up to real-life situations.
 Note that in order to test audio-visual cue combination under uncertainty, we had to use a case of double ambiguity, that is, a case where both the word forms ("ada"--"aba") and the referents (cat--dog) were similar and, thus, confusable.
@@
 For instance, @dautriche17 analyzed 100 languages and found that words that are similar phonologically tend to be similar semantically as well.
-These studies suggest that the case of double uncertainty, though perhaps not pervasive, could be a real issue in language as it increase the probability of confusability for many words.
+These studies suggest that the case of double uncertainty, though perhaps not pervasive, could be a real issue in language as it increases the probability of confusability for many words.
 That said, the inferences discussed here might play a more significant role in naturalistic language comprehension when ambiguity in both the form and/or the referent is induced by an *external* noisy context --- e.g., a very noisy party or a far away referent --- even when these forms and referents are not confusable in normal situations.
@@
 A multi-modal cue combination strategy might help children not only recognize words, but also refine their underlying phonological and semantic representations in the process.
-Previous research in early word learning has -- whether implicitly or explicitly -- largely treated the process of refining the word form and of refining the word meaning as following a linear timeline.
-However, developmental data reveal that children do not wait to have complete acquisition of word forms before they start learning their meanings [@bergelson2012; @tincoff1999].
+Previous research in early word learning has --- whether implicitly or explicitly --- largely treated the process of refining the word form and of refining the word meaning as following a linear timeline.
+However, developmental data reveal that children do not wait to have completed the acquisition of word forms before they start learning their meanings [@bergelson2012; @tincoff1999].
 Rather, both form and meaning representations develop in a parallel fashion.
@@
 For instance, @waxman1995 showed that labeling various objects with the same name helps infants form the underlying semantic category [but see @sloutsky2003].
-And in the opposite direction, @yeung09 showed that pairing similar sounds with different objects can helps infants enhance their sensitivity to subtle phonological contrasts in their native language.
-The present study proposes a first step towards a formal framework where these sorts of sound-meaning interactions in development can be unified and further explored.
+And in the opposite direction, @yeung09 showed that pairing similar sounds with different objects can help infants enhance their sensitivity to subtle phonological contrasts in their native language.
+The present study offers a stepping stone towards a formal framework where these sorts of sound-meaning interactions in development can be unified and further explored.
+
+Note, however, that though our framework allows in principle for the study of how sound-meaning interaction influences the underlying categories, we did not explore this question in the current task.
+In fact, we used familiar categories both at the seamantic level (cat and dog) and at the phonological level (the phonemes /p/ and /b/).
+This choice allowed us to test the mechanims of cue integration separately from the question of category learning.
+Using novel categories would create a confound as participant would additionally have to learn the boundaries of the novel categories, making it difficult for us to tease apart how much of the suboptimal behavior is due to the difficulty of audio-visual integration, and how much it is due to variability in estimating the boundary of the novel categories.
+
+Though our task deals primarily with the mechanism of word recognition, the conclusions of the current study partially applies to word learning as well.
+While the typical task in the word learning literature involves mapping a new label to a novel object [e.g., @landau1988; @markman1991], several cases of word learning in the wild involve familiar object (as in our task).
+For example, adults learning a second language do map new labels to objects that are already familiar to them.
+Besides, children come to the task of word learning with a fairly refined knowledge about the semantic categories [e.g., @quinn93].
+That is, in several cases, they do not associate new labels with objects that they are seeing for the first time.
+Rather, they map labels onto concepts that they have refined over the course of earlier exposures [e.g., @bloom2000].
+
+Finally, our task was an adaptation of a task introduced originally by @sloutsky2003.
+This original work is part of a rich literature on  modality-dominance in coross-modal processing [e.g., @colavita1974; @robinson2010].
+Overall, this litartaure suggests that, when presented with au audio-visual stimuli, adults pay more attention to the visual component whereas children may pay more attention to the auditory component [@hirst2018; @barnhart2018].
+Our work shows that adults do not systematicallty prefere one modality over the other.
+Rather, they modulate this preference as a functon of noise (Experiment 2 and 3).
+That said, it is important to keep in mind that our task differs in its design and aim from the tasks used in this literature: While the literature on modality-dominance deals with low-level perceptual encoding, our task targets specifically high-level linguistic processing and categorizaton.
+It is possible that the underlying mechanisms in both cases are related (or even similar).
+However, we did not explore this possibility in the current study.
 
@@
 This simplification was motivated by the need to construct a multimodal input where the auditory and visual components are parametrized in a symmetrical fashion, allowing us to compare graded effects of auditory and visual information on categorical judgment.
-Though such a visual variability is clearly artificial (one does not encounters in real life an animal that is, e.g., 30 % dog and 70 % cat), we assume that the induced uncertainty form this visual stimuli has a similar effect on word recognition as the uncertainty induced by more naturalistic semantic variability.
+Though such a visual variability is clearly artificial (one does not encounters in real life an animal that is, e.g., 30 % dog and 70 % cat), we assume that the induced uncertainty form these visual stimuli has a similar effect on word recognition as the uncertainty induced by more naturalistic semantic variability.
 
@@
 
-Finally, though we used the terminology of word recognition, our work is only indirectly related to the literature about how a rich lexicon is accessed [e.g., @mcclelland1986].
+Finally, though we used the term "word recognition", our work is only indirectly related to the literature about how a rich lexicon is accessed [e.g., @mcclelland1986].
 We have used this term in a more specific way, describing access to a simplified lexicon made of two novel, ambiguous words.
@@
 Our work used an ideal observer model to study word recognition under audio-visual uncertainty.
-This framework enabled us not only to test optimality, but also to examine systematically how and by how much people deviate from optimality in their combination strategies.
+This framework enabled us not only to test optimality but also to examine systematically how and by how much people deviate from optimality in their combination strategies.
 Thus, our work is part of a growing effort to go beyond optimality tests --- which have limited explanatory power --- and use models that also allow us to identify and explain various patterns of sub-optimality in human behavior [@rahnev2018].
@@
 Finally, though the current framework only characterizes adult novel word recognition, it provides a first step towards a model where developmental questions can also be investigated.
-For instance, future work should explore whether children, like adults, use probabilistic cues from both the auditory and the visual input to recognize ambiguous words, the extent to which they combine these cues in an optimal fashion, and whether this cue combination help them learn words and refine their early phonological and semantic representations.
+For instance, future work should explore whether children, like adults, use probabilistic cues from both the auditory and the visual input to recognize ambiguous words, the extent to which they combine these cues in an optimal fashion, and whether this cue combination helps them learn words and refine their early phonological and semantic representations.
 

### 2019-11-14 Writeup/ms_r2.tex
final

--- 2019-04-12 Writeup/ms.tex
@@
 \linenumbers
+\usepackage{xcolor}
 \usepackage[sortcites=false,sorting=none]{biblatex}
@@
 your arm). A word is successfully identified when information from these
-modalities provide convergent evidence.
+modalities provides convergent evidence.
 
@@
 category is realized acoustically (Hillenbrand, Getty, Clark, \&
-Wheeler, 1995). And some tokens may be distorted additionally by
+Wheeler, 1995). Moreover, some tokens may be distorted additionally by
 mispronunciation or ambient noise. Perhaps the speaker was yelling
@@
 not be enough to make a definitive identification of a visual
-category.\footnote{In the general case, language can of course be visual as well as auditory, and object identification can be done through many modalities.
+category.\footnote{In the general case, language can of course be visual as well as auditory, and object identification can be accomplished through many modalities.
 For simplicity, we focus on audio-visual matching here.}
@@
 ambiguity (Medina, Snedeker, Trueswell, \& Gleitman, 2011; Pinker, 1989;
-Smith \& Yu, 2008; Suanda, Mugwanya, \& Namy, 2014; Vlach \& Johnson,
-2013; Vouloumanos, 2008; Yurovsky \& Frank, 2015). However, even when
-they have learned the exact meaning of a word, observers (both children
-and adults) often still find it challenging to recognize which word the
-speaker has uttered, especially under noise (Mattys, Davis, Bradlow, \&
-Scott, 2012; Peelle, 2018). The purpose of the current study is thus to
-explore word recognition by adults under multimodal uncertainty,
-focusing on the special case where people have access to multimodal cues
-from the auditory speech and the visual referent. In the General
-Discussion, we return to the question of how these findings relate to
-questions about word learning.
+L. B. Smith \& Yu, 2008; Suanda, Mugwanya, \& Namy, 2014; Vlach \&
+Johnson, 2013; Vouloumanos, 2008; Yurovsky \& Frank, 2015). However,
+even when they have learned the exact meaning of a word, observers (both
+children and adults) often still find it challenging to recognize which
+word the speaker has uttered, especially under noise (Mattys, Davis,
+Bradlow, \& Scott, 2012; Peelle, 2018). The purpose of the current study
+is thus to explore word recognition by adults under multimodal
+uncertainty, focusing on the special case where people have access to
+multimodal cues from the auditory speech and the visual referent. In the
+General Discussion, we return to the question of how these findings
+relate to questions about word learning.
 
@@
 the ideal, it can reveal extra constraints on human cognition, such as
-limitations on the working memory or attentional resources. This
+limitations on the working memory or on attentional resources. This
 approach has had a tremendous impact not only on speech-related research
 (Clayards, Tanenhaus, Aslin, \& Jacobs, 2008; Feldman, Griffiths, \&
-Morgan, 2009; Kleinschmidt \& Jaeger, 2015; Norris \& McQueen, 2008),
-but also on many other disciplines in the cognitive sciences (for
-reviews, see Chater \& Manning, 2006; Knill \& Pouget, 2004; Tenenbaum,
-Kemp, Griffiths, \& Goodman, 2011)
+Morgan, 2009; Kleinschmidt \& Jaeger, 2015; Norris \& McQueen, 2008) but
+also on many other disciplines in the cognitive sciences (for reviews,
+see Chater \& Manning, 2006; Knill \& Pouget, 2004; Tenenbaum, Kemp,
+Griffiths, \& Goodman, 2011).
 
@@
 humans were sensitive to these probabilistic cues and their judgments
-closely reflected the optimal predictions. And Feldman et al. (2009)
-studied the perceptual magnet effect, a phenomenon that involves reduced
-discriminability near prototypical sounds in the native language (Kuhl,
-1991), showing that this effect can be explained as the consequence of
-optimally solving the problem of perception under uncertainty (see also
-Kronrod, Coppess, \& Feldman, 2016).
+closely reflected the optimal predictions. Moreover, Feldman et al.
+(2009) studied the perceptual magnet effect, a phenomenon that involves
+reduced discriminability near prototypical sounds in the native language
+(Kuhl, 1991), showing that this effect can be explained as the
+consequence of optimally solving the problem of perception under
+uncertainty (see also Kronrod, Coppess, \& Feldman, 2016).
 
@@
 visual information was obtained through the referential context rather
-than through observation of speaker's face. Although some experimental
-findings show that information about the identity of a referent can be
-integrated with linguistic information to resolve lexical and syntactic
-ambiguities in speech (e.g., Eberhard, Spivey-Knowlton, Sedivy, \&
-Tanenhaus, 1995; Spivey, Tanenhaus, Eberhard, \& Sedivy, 2002;
-Tanenhaus, Spivey-Knowlton, Eberhard, \& Sedivy, 1995), to our knowledge
-no study has offered an ideal observer analysis of this task.
+than through observation of the speaker's face. Although some
+experimental findings show that information about the identity of a
+referent can be integrated with linguistic information to resolve
+lexical and syntactic ambiguities in speech (e.g., Eberhard,
+Spivey-Knowlton, Sedivy, \& Tanenhaus, 1995; Spivey, Tanenhaus,
+Eberhard, \& Sedivy, 2002; Tanenhaus, Spivey-Knowlton, Eberhard, \&
+Sedivy, 1995), to our knowledge no study has offered an ideal observer
+analysis of this task (as we do here).
 
@@
 however, the auditory and visual modalities play different roles in the
-referential process -- the auditory input represents the \emph{symbol}
+referential process --- the auditory input represents the \emph{symbol}
 whereas the visual input represents the \emph{meaning} (and these
 differences are in addition to possible differences in informational
-reliability). Further, speech is claimed to have a privileged status
-compared to other sensory stimuli (Edmiston \& Lupyan, 2015; Lupyan \&
+reliability). Speech is claimed to have a privileged status compared to
+other sensory stimuli (Edmiston \& Lupyan, 2015; Lupyan \&
 Thompson-Schill, 2012; Vouloumanos \& Waxman, 2014; Waxman \& Gelman,
@@
   because of a low level auditory ``overshadowing'' (e.g., Sloutsky \&
-  Napolitano, 2003).} Thus, in a referential context, it is possible
-that listeners do not treat the auditory and visual modalities as
-equivalent sources of information. Instead, there could be a sub-optimal
-bias for the auditory modality beyond what is expected from
-informational reliability alone.
+  Napolitano, 2003). We do not take a stance on this issue here.} Thus,
+in a referential context, it is possible that listeners do not treat the
+auditory and visual modalities as equivalent sources of information.
+Instead, there could be a (potentially sub-optimal) bias for the
+auditory modality beyond what is expected from informational reliability
+alone.
 
@@
 environmental noise that degraded information from the visual modality.
-Finally, Experiment 4 is a replication of Experiment 1 with a higher
-power design, allowing us to test cue combination at the individual
-level.
+Finally, in Experiment 4, we replicated Experiment 1 with a higher power
+design, allowing us to test cue combination at the individual level.
 
@@
 
-In this section we first briefly introduce the multimodal combination
+In this section, we first briefly introduce the multimodal combination
 task. Then we explain how behavior in this paradigm can be characterized
@@
 test) belongs to the same category as the first (target) (e.g.,
-dog-/aba/), even if there is a slight difference in the sound, in the
+cat-/aba/), even if there is a slight difference in the sound, in the
 referent, or in both. They are instructed to press \enquote{different}
@@
 audio-visual space. These audio-visual tokens define bivariate
-distributions in the bi-dimentional space. We call these bivariate
+distributions in the bi-dimensional space. We call these bivariate
 distributions \emph{Word categories}, noted \(W\), and are distributed
@@
 object CAT, which is a valid assumption in the context of our
-task.\footnote{Note that this assumptions is more adequate in the case of arbitrary associations such as ours, and less so in the case of redundant association such as audio-visual speech.
+task.\footnote{Note that this assumption is more adequate in the case of arbitrary associations such as ours, and less so in the case of redundant association such as audio-visual speech.
 In the latter, variation in the pronunciation is expected to correlate, at least to some extent, with lip movements.}
@@
 different, participants might have a slight preference for
-\enquote{different} over \enquote{same}. As for the means, their values
+\enquote{different} over \enquote{same.} As for the means, their values
 are fixed, and they correspond to the most typical tokens in our
@@
 participants rely on both the auditory and the visual modalities to make
-decision in the bimodal condition, the optimal model would explain more
-variance in human responses than the visual or the auditory model do.
+decisions in the bimodal condition, the optimal model would explain more
+variance in human responses than the visual or the auditory model does.
 
@@
 \emph{normative} models. Their predictions are made about human data in
-the bimodal condition, but their parameters (i.e., variances associated
-with the visual and auditory modalities) are derived from data in the
-unimodal conditions. In addition to these normative models, we consider
-a \emph{descriptive} model. It is formally identical to the normative
-optimal model (Equation 1), except that the parameters are fit to actual
-responses in the bimodal condition. If the referential task induces
-sub-optimality (due, for instance, to the arbitrary nature of the
-sound-object association), then the descriptive model should explain
+the bimodal condition, but their crucial parameters (i.e., variances
+associated with the visual and auditory modalities) are derived from
+data in the unimodal conditions. In addition to these normative models,
+we consider a \emph{descriptive} model. It is formally identical to the
+normative optimal model (Equation 1), except that the parameters are fit
+to actual responses in the bimodal condition. If the referential task
+induces sub-optimality (due, for instance, to the arbitrary nature of
+the sound-object association), then the descriptive model should explain
 more variance than the optimal model does.
@@
 Comparison of the optimal and the descriptive models allows us, not only
-to quantify how much people deviate from optimality, but also to
+to quantify how much people deviate from optimality but also to
 understand precisely the nature of this deviation. Let \(\sigma^2_{A}\)
@@
 optimal model. The reason we used the proportion of the variances as a
-measure of cross-modal weighting is because this proportion corresponds
-to the
-slope\footnote{Or more precisely the absolute value of the slope.} of
-the decision threshold in the audio-visual space
+measure of cross-modal weighting is that this proportion corresponds to
+the slope\footnote{Or more precisely the absolute value of the slope.}
+of the decision threshold in the audio-visual space
 (Figure~\ref{fig:model}). The decision threshold is defined as the set
@@
 
-We compared these models to human responses in three experiments. In
+We compared these models to human responses in four experiments. In
 Experiment 1, we studied the case where bimodal uncertainty was due to
@@
 added environmental noise to the auditory and the visual modalities,
-respectively.
+respectively. Finally, in Experiment 4, we replicated Experiment 1 with
+a higher power design in order to test cue combination at the individual
+level
 
@@
 any external noise to the background. Thus, we test the following
-(normative) cue weighting scheme:
+(normative) cue weighting scheme.\footnote{In all our analyses, we study
+  the combined effect of both categorical and sensory uncertainties in
+  the process of cue combination. We do not examine the specific role of
+  each source of uncertainty separately. For example, in the auditory
+  modality, the quantity \(\sigma^2_{A_C} + \sigma^2_{A_N}\) will be
+  treated as a single variable. This variable will be measured in the
+  unimodal condition and tested in the bimodal condition.}
 
@@
 they reported having experienced a technical problem of any sort during
-the online experiment (N=14), or if they had less than 50\% accurate
-responses on the unambiguous training trials (N=6). The final sample
-consisted of N = 80 participants. All participants provided informed
-consent before taking the experiment.
+the online experiment (\(N =\) 14), or if they had less than 50\%
+accurate responses on the unambiguous training trials (\(N =\) 6). The
+final sample consisted of \(N =\) 80 participants. All participants
+provided informed consent before taking the experiment.
 \footnote{The sample size and exclusion criteria were specified in the pre-registration at https://osf.io/h7mzp/.}
@@
 Remember that data in these conditions allows us to derive the variances
-of both the auditory and the visual categories, and that these variances
+of both the auditory and the visual categories and that these variances
 are used to make predictions about bimodal data (in the visual and
@@
 variances were derived as follows (we explain the derivation for the
-auditory-only case, but the same applies for the visual-only case). We
+auditory-only case, but the same applies to the visual-only case). We
 use the same Bayesian reasoning as we did in the derivation of the
@@
 and the auditory modalities, respectively, and \(b\), the response bias.
-The visual and auditory baselines as well as the optimal model are not
+The visual and auditory baselines, as well as the optimal model, are not
 fit to the bimodal data, but their predictions are tested against these
@@
 
-\caption{\label{tab:param}Statistics for the dataset we used.}
+\caption{\label{tab:param}Estimates of the models' parameters.}
 \centering
@@
 categorically and with higher certainty than they did with the visual
-tokens. The unimodal models' estimates are shown in Table
-\ref{tab:param}.
+tokens. The unimodal models' estimates in each modality are shown in
+Table \ref{tab:param}.
 
 \begin{figure}[!h]
-\includegraphics[width=\textwidth]{ms_files/figure-latex/unimodal-1} \caption{Human responses in the unimodal conditions across the three experiments.
+\includegraphics[width=\textwidth]{ms_r2_files/figure-latex/unimodal-1} \caption{Human responses in the unimodal conditions across the four experiments.
 Points represent the proportion of `different' to `same' responses in the auditory-only condition (left), and visual-only condition (right).
@@
 bimodal condition (where people see input from both modalities). The
-descriptive model has a similar structure than the optimal model, but is
+descriptive model has a similar structure than the optimal model but is
 directly fit to human responses in the bimodal condition in order to
@@
 
-We found, through comparing the correlation values, that the optimal
-model explained more variance than the visual and auditory models did.
+We found, by comparing the correlation values, that the optimal model
+explained more variance than the visual and auditory models did.
 However, the optimal model was not perfect: It explained less variance
@@
 model (Table
-\ref{tab:param}).\footnote{Note that the descriptive model explained almost all the variance in mean responses, which makes it a reasonable proxy for human real performance in the bimodal condition.}.
+\ref{tab:param}).\footnote{Note that the descriptive model explained almost all the variance in mean responses, which makes it a reasonable proxy for human real performance in the bimodal condition.}
 We note an increase in \emph{both} the auditory and visual variances.
@@
 appear to be pulled towards chance (i.e., the value 0.5) when compared
-to the optimal model (see \ref{fig:bimodal}). Below we investigate if
-this deviation from optimality can be related to the cue combination
-strategy.
+to the optimal model (see Figure \ref{fig:bimodal}). Below we
+investigate if this deviation from optimality can be related to the cue
+combination strategy.
 
@@
 if there was a systematic preference for one modality when making
-decisions in the bimodal condition. As explained in \ref{fig:subOptim},
-modality preference can be characterized formally as a deviation from
-the decision threshold predicted by the optimal model. The results in
-Figure \ref{fig:bias} (top) show both the decision threshold derived
-from the descriptive model (in black) and the decision threshold
-predicted by the optimal model (in red). We found that the descriptive
-and optimal decision thresholds were almost identical. Indeed,
-non-parametric resampling of the data showed no evidence of a deviation
-from the optimal prediction (Figure~\ref{fig:bias}, bottom).
+decisions in the bimodal condition. As explained in Figure
+\ref{fig:subOptim}, modality preference can be characterized formally as
+a deviation from the decision threshold predicted by the optimal model.
+The results in Figure \ref{fig:bias} (top) show both the decision
+threshold derived from the descriptive model (in black) and the decision
+threshold predicted by the optimal model (in red). We found that the
+descriptive and optimal decision thresholds were almost identical.
+Indeed, non-parametric resampling of the data showed no evidence of a
+deviation from the optimal prediction (Figure~\ref{fig:bias}, bottom).
 
 \begin{figure}[!h]
-\includegraphics[width=\textwidth]{ms_files/figure-latex/bimodal-1} \caption{Human responses vs.
-Models' predictions in the bimodal condition across the three experiments.
-Each point represents data form a particular audio-visual matching (corresponding to an instance from the set of 5x5 possible matchings in the audio-visual space).
+\includegraphics[width=\textwidth]{ms_r2_files/figure-latex/bimodal-1} \caption{Human responses vs.
+Models' predictions in the bimodal condition across the four experiments.
+Each point represents data from a particular audio-visual matching (corresponding to an instance from the set of 5x5 possible matchings in the audio-visual space).
 Shape represents auditory distance from the target, and color represents visual distance from the target.
@@
 due to noisy factors in the environment (e.g., car noise in the
-background, blurry vision in a foggy weather). In Experiment 2 and 3, we
+background, blurry vision in foggy weather). In Experiment 2 and 3, we
 explore this additional level of uncertainty.
@@
 
-A sample of 100 participants was recruited online through Amazon
+A sample of \(N =\) 100 participants was recruited online through Amazon
 Mechanical Turk. We used the same exclusion criteria as in Experiment 1.
-7 participants were excluded because they had less than 50\% accurate
-responses on the unambiguous training trials. The final sample consisted
-of N = 93 participants.
+\(N =\) 7 participants were excluded because they had less than 50\%
+accurate responses on the unambiguous training trials. The final sample
+consisted of \(N =\) 93 participants.
 
@@
 modalities. Figure~\ref{fig:bias} (top) shows that the participants'
-decision threshold deviated from optimality, and that this deviation was
+decision threshold deviated from optimality and that this deviation was
 biased towards the visual modality (the non-noisy modality). Indeed
@@
 
-Experiment 2 tested audi-visual combination in the case where the
+Experiment 2 tested audio-visual combination in the case where the
 auditory input was noisy. We found, similar to Experiment 1, that the
@@
 
-A planned sample of 100 participants was recruited online through Amazon
-Mechanical Turk. We used the same exclusion criteria as in both previous
-experiments. N=2 participants were excluded because they reported having
-a technical problem, and N=10 participants were excluded because they
-had less than 50\% accurate responses on the unambiguous training
-trials. The final sample consisted of N = 88 participants.
+A planned sample of \(N =\) 100 participants was recruited online
+through Amazon Mechanical Turk. We used the same exclusion criteria as
+in both previous experiments. \(N =\) 2 participants were excluded
+because they reported having a technical problem, and \(N =\) 10
+participants were excluded because they had less than 50\% accurate
+responses on the unambiguous training trials. The final sample consisted
+of \(N =\) 88 participants.
 
@@
 editor GIMP (2.8.20). We used a Gaussian blur with a
-radius\footnote{A features that modulates the intensity of the blur.} of
+radius\footnote{A feature that modulates the intensity of the blur.} of
 10 pixels. The experimental procedure was exactly the same as in the
@@
 \begin{figure}[!h]
-\includegraphics[width=\textwidth]{ms_files/figure-latex/bias-1} \caption{Modality preference is characterized as a deviation from the optimal decision threshold.
+\includegraphics[width=\textwidth]{ms_r2_files/figure-latex/bias-1} \caption{Modality preference is characterized as a deviation from the optimal decision threshold.
 A) The decision thresholds of both the optimal and the descriptive models (solid red and black lines, respectively).
@@
 the non-noisy auditory
-modality.\footnote{The reason why we saw this (floor) effect when we added noise to the visual modality (Experiment 3), and not when we added noise to the auditory modality (Experiment 2), is the fact that our visual stimuli were originally perceived less categorically and with less certainty than the auditory stimuli (see Experiment 1 in \\ref{fig:unimodal}).
-This fact made it more likely for the visual categorization function to become flat and uninformative after a few drops in precision due to noise on the one had, and to the additional randomness induced by the bimodal presentation on the other hand.}
+modality.\footnote{The reason why we saw this (floor) effect when we added noise to the visual modality (Experiment 3), and not when we added noise to the auditory modality (Experiment 2), is the fact that our visual stimuli were originally perceived less categorically and with less certainty than the auditory stimuli (see Experiment 1 in Figure 4).
+This fact made it more likely for the visual categorization function to become flat and uninformative after a few drops in precision due to noise on the one hand, and to the additional randomness induced by the bimodal presentation on the other hand.}
 
@@
 combination (i.e., Experiment 1). In fact, optimality at the population
-level can be spurious if it is obtained only on average while most
-individuals have sub-otimal strategies (e.g., over-relying on the visual
-or the auditory modalities). In Experiment 4, below, we examine how the
-average cue combination relates to individual strategies.
+level can be spurious if it is obtained only on average while
+individuals have sub-optimal strategies (e.g., over-relying on the
+visual or the auditory modalities). In Experiment 4, below, we examine
+how the average cue combination relates to individual strategies.
 
@@
 As we noted earlier, we did not have enough statistical power in
-Experiment 1 to fit a different model for each participant. Thus, we
-used a higher power design, allowing us to collect the number of
-datapoints necessary to model cue combination at the individual level.
+Experiment 1 to fit a different model for each participant. Thus, here
+we used a higher power design, allowing us to collect the number of data
+points necessary to model cue combination at the individual level.
 
@@
 times, covering all possible ordering combinations. Unlike the
-between-subject randomization that we used in Experiment 1, this choices
+between-subject randomization that we used in Experiment 1, this choice
 allowed us to avoid a possible confound linked to the order of exposure.
@@
 \begin{figure}[!h]
-\includegraphics[width=\textwidth]{ms_files/figure-latex/weights-1} \caption{The histogram shows the distribution of the participants' predicted (i.e., optimal) cue weighting relative the observed (i.e., descriptive) weighting (see Figure 3 for the details).
+\includegraphics[width=\textwidth]{ms_r2_files/figure-latex/weights-1} \caption{The histogram shows the distribution of the participants' predicted (i.e., optimal) cue weighting relative the observed (i.e., descriptive) weighting (see Figure 3 for the details).
 The density plot shows the distribution of simulated data sampled from the population-level probabilistic model.
 The dashed lines represent 95\% confidence interval on this simulated distribution.
-Optimal behavior is observed when the value of the relative cue weighting is 1 (red solid line).
-Participants whose values are outside the confidence interval of the simulated distribution over-rely on the visual modality (left side) or auditory modality (right side) beyond sampling-related randomness (i.e., with p < 0.05).}\label{fig:weights}
+Optimal behavior is exactly obtained when the value of the relative cue weighting is 1 (red solid line).
+Participants whose values are outside the confidence interval of the simulated distribution can be understood to be over-relying on the visual modality (left side) or on the auditory modality (right side) beyond sampling-related variation (i.e., with p < 0.05).}\label{fig:weights}
 \end{figure}
@@
 the resulting distribution in Figure \ref{fig:weights}. We note first
-that the distribution has a rather bimodal shape, centered around the
+that the distribution has a rather unimodal shape, centered around the
 optimal cue combination strategy. This finding rules out the hypothesis
@@
 density, showing that this part of the variance can be due to mere
-sampling randomness. However, a few participants had values outside this
+sampling variation. However, a few participants had values outside this
 interval, indicating that they systematically over-relied on the visual
@@
 This experiment was an extension to Experiment 1. Through collecting
-larger-size data per subject, we were able to analyze the cue
-combination optimality, not only at the population level, but also at
-the individual level. The population-level analysis replicated the
-results of Experiment 1. The individual-level analysis showed that the
-distribution of cue combination scores had a unimodally-shaped
-distribution centered around the optimal combination, thus reflecting
-genuine cue combination at the individual level. That said, the variance
-of this distribution indicates that a few participants tended to
-over-rely on the auditory modality and others tended to over-rely on the
-visual modality beyond sampling-related randomness.
+denser data per subject, we were able to analyze the cue combination
+optimality, not only at the population level but also at the individual
+level. The population-level analysis replicated the results of
+Experiment 1. The individual-level analysis showed that the distribution
+of cue combination scores had a unimodally-shaped distribution centered
+around the optimal combination, thus reflecting genuine cue combination
+at the individual level. That said, the variance of this distribution
+indicates that a few participants tended to over-rely on the auditory
+modality and others tended to over-rely on the visual modality beyond
+sampling-related randomness.
 
@@
 perceptible. Further, in Experiment 1 and 4, which did not involve
-background noise, participants not only relied on both modalities, but
+background noise, participants not only relied on both modalities but
 generally weighted these modalities according to the predictions of the
 optimal model, that is, according to their relative reliability. At the
-individual level, Experiment 4 showed that most participant were
+individual level, Experiment 4 showed that most participants were
 near-optimal. Only a few subjects over-relied on the auditory or visual
@@
 compared to the unimodal conditions: Participants responded slightly
-more randomly. This increase in randomness could be due limitation on
-cognitive resources: Processing two separate --- and perceptually
+more randomly. This increase in randomness could be due to limitations
+on cognitive resources: Processing two separate --- and perceptually
 uncorrelated --- cues instead of one cue (as in the unimodal case) is
@@
 
-Previous research has found similar cases of suboptimal behavior. For
+Previous research has found similar cases of sub-optimal behavior. For
 instance, studies that have explored the identification of ambiguous,
@@
 stimulus' physical identity can be identified) can affect a wide variety
-of human judgements (see Schwarz, 2004 for a review). In particular,
+of human judgments (see Schwarz, 2004 for a review). In particular,
 variables that improve fluency tend to increase liking/preference
@@
 An important question to ask is how the combination mechanism --- as
-revealed in our controlled study --- scales up to real life situations.
+revealed in our controlled study --- scales up to real-life situations.
 Note that in order to test audio-visual cue combination under
@@
 double uncertainty, though perhaps not pervasive, could be a real issue
-in language as it increase the probability of confusability for many
+in language as it increases the probability of confusability for many
 words. That said, the inferences discussed here might play a more
@@
 semantic representations in the process. Previous research in early word
-learning has -- whether implicitly or explicitly -- largely treated the
-process of refining the word form and of refining the word meaning as
-following a linear timeline. However, developmental data reveal that
-children do not wait to have complete acquisition of word forms before
-they start learning their meanings (Bergelson \& Swingley, 2012; Tincoff
-\& Jusczyk, 1999). Rather, both form and meaning representations develop
-in a parallel fashion. A few studies have already suggested the
+learning has --- whether implicitly or explicitly --- largely treated
+the process of refining the word form and of refining the word meaning
+as following a linear timeline. However, developmental data reveal that
+children do not wait to have completed the acquisition of word forms
+before they start learning their meanings (Bergelson \& Swingley, 2012;
+Tincoff \& Jusczyk, 1999). Rather, both form and meaning representations
+develop in a parallel fashion. A few studies have already suggested the
 possibility of an interaction between sound and meaning in early
@@
 opposite direction, Yeung and Werker (2009) showed that pairing similar
-sounds with different objects can helps infants enhance their
-sensitivity to subtle phonological contrasts in their native language.
-The present study proposes a first step towards a formal framework where
-these sorts of sound-meaning interactions in development can be unified
-and further explored.
+sounds with different objects can help infants enhance their sensitivity
+to subtle phonological contrasts in their native language. The present
+study offers a stepping stone towards a formal framework where these
+sorts of sound-meaning interactions in development can be unified and
+further explored.
+
+Note, however, that though our framework allows in principle for the
+study of how sound-meaning interaction influences the underlying
+categories, we did not explore this question in the current task. In
+fact, we used familiar categories both at the seamantic level (cat and
+dog) and at the phonological level (the phonemes /p/ and /b/). This
+choice allowed us to test the mechanims of cue integration separately
+from the question of category learning. Using novel categories would
+create a confound as participant would additionally have to learn the
+boundaries of the novel categories, making it difficult for us to tease
+apart how much of the suboptimal behavior is due to the difficulty of
+audio-visual integration, and how much it is due to variability in
+estimating the boundary of the novel categories.
+
+Though our task deals primarily with the mechanism of word recognition,
+the conclusions of the current study partially applies to word learning
+as well. While the typical task in the word learning literature involves
+mapping a new label to a novel object (e.g., Landau, Smith, \& Jones,
+1988; Markman, 1991), several cases of word learning in the wild involve
+familiar object (as in our task). For example, adults learning a second
+language do map new labels to objects that are already familiar to them.
+Besides, children come to the task of word learning with a fairly
+refined knowledge about the semantic categories (e.g., Quinn, Eimas, \&
+Rosenkrantz, 1993). That is, in several cases, they do not associate new
+labels with objects that they are seeing for the first time. Rather,
+they map labels onto concepts that they have refined over the course of
+earlier exposures (e.g., Bloom, 2000).
+
+Finally, our task was an adaptation of a task introduced originally by
+Sloutsky and Napolitano (2003). This original work is part of a rich
+literature on modality-dominance in coross-modal processing (e.g.,
+Colavita, 1974; Robinson \& Sloutsky, 2010). Overall, this litartaure
+suggests that, when presented with au audio-visual stimuli, adults pay
+more attention to the visual component whereas children may pay more
+attention to the auditory component (Barnhart, Rivera, \& Robinson,
+2018; Hirst, Cragg, \& Allen, 2018). Our work shows that adults do not
+systematicallty prefere one modality over the other. Rather, they
+modulate this preference as a functon of noise (Experiment 2 and 3).
+That said, it is important to keep in mind that our task differs in its
+design and aim from the tasks used in this literature: While the
+literature on modality-dominance deals with low-level perceptual
+encoding, our task targets specifically high-level linguistic processing
+and categorizaton. It is possible that the underlying mechanisms in both
+cases are related (or even similar). However, we did not explore this
+possibility in the current study.
 
@@
 an animal that is, e.g., 30 \% dog and 70 \% cat), we assume that the
-induced uncertainty form this visual stimuli has a similar effect on
+induced uncertainty form these visual stimuli has a similar effect on
 word recognition as the uncertainty induced by more naturalistic
@@
 
-Finally, though we used the terminology of word recognition, our work is
+Finally, though we used the term \enquote{word recognition}, our work is
 only indirectly related to the literature about how a rich lexicon is
@@
 audio-visual uncertainty. This framework enabled us not only to test
-optimality, but also to examine systematically how and by how much
-people deviate from optimality in their combination strategies. Thus,
-our work is part of a growing effort to go beyond optimality tests ---
-which have limited explanatory power --- and use models that also allow
-us to identify and explain various patterns of sub-optimality in human
+optimality but also to examine systematically how and by how much people
+deviate from optimality in their combination strategies. Thus, our work
+is part of a growing effort to go beyond optimality tests --- which have
+limited explanatory power --- and use models that also allow us to
+identify and explain various patterns of sub-optimality in human
 behavior (Rahnev \& Denison, 2018).
@@
 words, the extent to which they combine these cues in an optimal
-fashion, and whether this cue combination help them learn words and
+fashion, and whether this cue combination helps them learn words and
 refine their early phonological and semantic representations.
@@
 
+\hypertarget{ref-barnhart2018}{}
+Barnhart, W. R., Rivera, S., \& Robinson, C. W. (2018). Different
+patterns of modality dominance across development. \emph{Acta
+Psychologica}, \emph{182}.
+
 \hypertarget{ref-bates88}{}
@@
 
+\hypertarget{ref-bloom2000}{}
+Bloom, P. (2000). \emph{How children learn the meanings of words}.
+Cambridge, MA. MIT Press.
+
 \hypertarget{ref-Campbell2008}{}
@@
 \emph{Cognition}, \emph{108}.
+
+\hypertarget{ref-colavita1974}{}
+Colavita, F. B. (1974). Human sensory dominance. \emph{Attention,
+Perception, \& Psychophysics}, \emph{16}(2), 409--412.
 
@@
 
+\hypertarget{ref-hirst2018}{}
+Hirst, R. J., Cragg, L., \& Allen, H. A. (2018). Vision dominates
+audition in adults but not children: A meta-analysis of the colavita
+effect. \emph{Neuroscience \& Biobehavioral Reviews}, \emph{94}.
+
 \hypertarget{ref-hofer2017}{}
@@
 \emph{Perception \& Psychophysics}, \emph{50}(2), 93--107.
+
+\hypertarget{ref-landau1988}{}
+Landau, B., Smith, L., \& Jones, S. (1988). The importance of shape in
+early lexical learning. \emph{Cognitive Development}, \emph{3}.
 
@@
 
+\hypertarget{ref-markman1991}{}
+Markman, E. M. (1991). The whole-object, taxonomic, and mutual
+exclusivity assumptions as initial constraints on word meanings. In S.
+A. Gelman \& J. P. Byrnes (Eds.),.
+
 \hypertarget{ref-marr1982}{}
@@
 
+\hypertarget{ref-quinn93}{}
+Quinn, P. C., Eimas, P. D., \& Rosenkrantz, S. L. (1993). Evidence for
+representations of perceptually similar natural categories by
+3-month-old and 4-month-old infants. \emph{Perception}, \emph{22}(4),
+463--475.
+
 \hypertarget{ref-rahnev2018}{}
